### 2014-04-09 docs/results.tex
first commit

\documentclass[letterpaper]{article}
\setlength{\columnsep}{0.75cm}
\usepackage{algorithm2e}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{cite}
\usepackage{framed, color}
\usepackage{soul}
\definecolor{shadecolor}{rgb}{.93,.93,.93}
\definecolor{blu}{rgb}{0,0,1}
\newcommand{\td}[1]{{\color{blu}\hl{TODO: #1}}}
\definecolor{shadecolor}{rgb}{.93,.93,.93}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage{gensymb}
\usepackage[hmargin=1in,vmargin=1in]{geometry}
\setlength{\parindent}{0cm}
\setlength{\parskip}{4mm plus1mm minus1mm}
\usepackage[
	colorlinks=true,
	urlcolor=blue
]{hyperref}

\title{}
\author{}

\parindent0pt \parskip8pt
\begin{document}
\maketitle
\section{Classifier competence as a function of image}
\includegraphics[scale=0.75]{../figs/longitude0.pdf}

The following figure investigates the ability of a naive bayes classifier to 
classify workers who were primed under different treatments.  Specifically, 
we consider the binary classification task of classifying workers who drawn 
from either the cultural-images or ingredients-images treatments.

We train the classifier to perform a binary classification between workers 
from the two treatments, providing it 80 randomly selected workers from 
both treatments as a training set, and using 20 workers to test.  We train
the classifier using only the labels that workers provided for one of the
test images, and provide the classifier's performance results for when using
different images as the basis of classification.

For each such test of the classifier, we look at two cases, one in which we
treat each text input associated to an image in the HIT as as distinguished
source of featuers (tokens), and one in which no distinction is made between
the 5 text inputs associated to an image.  We denote the former as a 
classifier test with ``position-based features'', and the latter with 
``position-less featuers''.  So, in a test of the classifier with 
position-based features, an entry of ``soup'' into the first 
text input is regarded distinct from an entry of  ``soup'' into the second 
text input, whereas in a test with position-less features
these two token occurences are encoded as one and the same feature.

\end{document}

### 2014-04-09 docs/results/results.tex
first commit

--- 2014-04-09 docs/results.tex
@@
 \setlength{\columnsep}{0.75cm}
+\usepackage{python}
 \usepackage{algorithm2e}
@@
 \section{Classifier competence as a function of image}
-\includegraphics[scale=0.75]{../figs/longitude0.pdf}
 
-The following figure investigates the ability of a naive bayes classifier to 
-classify workers who were primed under different treatments.  Specifically, 
-we consider the binary classification task of classifying workers who drawn 
+\begin{center}
+\includegraphics[scale=0.65]{../figs/longitude_cult-ing-img.pdf}
+\end{center}
+
+The above figure investigates the ability of a naive bayes classifier to 
+classify workers who were primed under different treatments.   
+We perform binary classification of workers drawn 
 from either the cultural-images or ingredients-images treatments.
@@
 
+\begin{center}
+\includegraphics[scale=0.65]{../figs/longitude_cult-ing-fund.pdf}
+\end{center}
+This figure is similar to the previous one, but it compares the cultural-funder
+and ingredients-funder treatments.
+
+\begin{center}
+\includegraphics[scale=0.65]{../figs/longitude_cult-ing-img-fund.pdf}
+\end{center}
+And this one compares the cultural-funder-image and ingredients-funder-image
+treatments
+
+\begin{center}
+\includegraphics[scale=0.65]{../figs/cross-classification.pdf}
+\end{center}
+The above figure shows that, from the perspective of being able to distinguish
+priming treatments using a naive bayes classifier, in-task priming is has as
+great an effect as prominent disclusure of the research funder.
+
+\begin{center}
+\includegraphics[scale=0.65]{../figs/valenceComparison.pdf}
+\end{center}
+The above figure shows the effect of the various priming treatments in terms
+of the number of culture-related and food-related words used.
+
 \end{document}

### 2014-04-09 data/image_scavenging/images.js

@@ -1,0 +1,372 @@
+var images = {
+   "ambiguous": [
+      [
+         0, 
+         "https://encrypted-tbn3.gstatic.com/images?q=tbn:ANd9GcQ8OK4gFKU6yV_0tl1HoXd4o8zrCv6k02Ee2S4IsvDO8Tn1qN84"
+      ], 
+      [
+         1, 
+         "http://calabashbistro.com/wp-content/uploads/chicken.jpg"
+      ], 
+      [
+         2, 
+         "http://foxfm.com/files/2013/11/peppers.jpg"
+      ], 
+      [
+         3, 
+         "https://encrypted-tbn1.gstatic.com/images?q=tbn:ANd9GcQWI-PLRZNb7hY6yr_QpSQ4tMXIU1Ovr5fCAfSoQhzqUwSzADdd"
+      ], 
+      [
+         4, 
+         "http://2.bp.blogspot.com/_fogL-F6jDxo/S-hrZYJixBI/AAAAAAAABoQ/H2y1p4in8lk/s1600/steak.jpg"
+      ], 
+      [
+         5, 
+         "http://www.greatfoodwine.com/wp-content/uploads/2013/04/Food-Wine-3.jpg"
+      ], 
+      [
+         6, 
+         "http://4.bp.blogspot.com/-0TM-a1FeHRY/UjRoAj9YMZI/AAAAAAAAG5c/a1vWdycMv8U/s1600/COVER+SHOT+-+Food2+-+Fish+and+Seafood+-+Alex+Bielak.JPG"
+      ], 
+      [
+         7, 
+         "http://photos1.blogger.com/blogger/6981/1842/1600/marinated_pomphrets_chanduva_chepa.jpg"
+      ], 
+      [
+         8, 
+         "https://encrypted-tbn1.gstatic.com/images?q=tbn:ANd9GcTtdSv_F4j3zaiNTrEdCCk3uRDDD7eQiTyZtoQoTuNawtXVK3ZE"
+      ], 
+      [
+         9, 
+         "https://encrypted-tbn3.gstatic.com/images?q=tbn:ANd9GcSqU-XYghfssDfIhTr_afiqeJ6HxOFMV4gzf-Afr-eln5evX7wJmA"
+      ], 
+      [
+         10, 
+         "http://www.italian-food-lovers.com/wp-content/uploads/2011/05/Italian-Food.jpg"
+      ], 
+      [
+         11, 
[…]

### 2014-04-09 docs/results/latex.py

@@ -1,0 +1,1 @@
+jobname="results1"

### 2014-04-09 src/analysis.py

@@ -1,0 +1,522 @@
+import util
+import sys
+import random
+import naive_bayes
+import ontology
+import data_processing
+import numpy as np
+
+
+class ClassifierPerformanceResult(object):
+
+	def __init__(self, treatments):
+		self.treatments = treatments
+		self.results = {}
+		
+		for treatment in treatments:
+			self.results[treatment] = {
+				'numCorrect':0
+				, 'numIdentified':0
+				, 'numTested':0
+			}
+
+
+	def getPrecision(self, treatment):
+		numerator = self.results[treatment]['numCorrect']
+		denominator = float(self.results[treatment]['numIdentified'])
+		return numerator / denominator
+
+
+	def getRecall(self, treatment):
+		numerator = self.results[treatment]['numCorrect']
+		denominator = float(self.results[treatment]['numTested'])
+		return numerator / denominator
+
+
+	def getOverallAccuracy(self):
+		numCorrectOverall = 0
+		numTestedOverall = 0
+		for treatment, result in self.results.items():
+			numCorrectOverall += result['numCorrect']
+			numTestedOverall += result['numTested']
+
+		return numCorrectOverall / float(numTestedOverall)
+
+	def getF1(self, treatment):
+		recall = self.getRecall(treatment)
+		precision = self.getPrecision(treatment)
+		return 2*recall*precision / (recall + precision)
+
+
+
+class Analyzer(object):
+
+	# Constants
+	ONTOLOGY_FILE = 'ontology/test0.ontology.json'
+
+	def __init__(self, dataset=None, ontology=None):
+		if dataset is None:
+			self.readDataset()
+		else:
+			self.dataSet = dataset
+
+		if ontology is None:
+			self.readOntology()
+		else:
+			self.ontology = ontology
+
+
+	def compareNonCulturalSpecificity(
+		self, treatment1, treatment2, numToCompare=50):
+
+		# Mask food
+		self.ontology.mask('cultural')
+
+		# compare entries now that the mask is applied
+		result = self.compareSpecificity(
+			treatment1, treatment2, numToCompare)
+
+		# remove mask
+		self.ontology.clearMask()
+		
+		return result
+
+
+	def compareNonFoodSpecificity(
+		self, treatment1, treatment2, numToCompare=50):
+
+		# Mask food
+		self.ontology.mask('food')
+
+		# compare entries now that the mask is applied
+		result = self.compareSpecificity(
+			treatment1, treatment2, numToCompare)
+
+		# remove mask
[…]

### 2014-04-09 src/data_processing.py

@@ -1,0 +1,354 @@
+import util
+import random
+import json
+import csv
+
+def readDataset():
+	'''
+	Factory method that builds a CleanDataset from the original Amazon
+	Mechanical Turk CSV files
+	'''
+
+	# Create a new priming-image-label-experiment dataset
+	dataSet = CleanDataset()
+
+	# Read from the raw amt csv files.  
+	# Note: order matters!  The older files have duplicates workers that
+	# get ignored.  Make sure to read the newer file files earlier
+	dataSet.read_csv('amt_csv/amt1_cut.csv', True)
+	dataSet.read_csv('amt_csv/amt2_cut.csv', True)
+	dataSet.read_csv('amt_csv/amt3_cut.csv', True)
+
+	# The dataset needs to do some internal calts to refresh its state 
+	dataSet.aggregateCounts()
+	dataSet.calc_ktop(5)
+
+	return dataSet
+
+
+class CleanDataset(object):
+
+	# Constants
+	K = 5
+	NUM_IMAGES = 5
+	NUM_WORDS_PER_IMAGE = 5
+
+	def __init__(self):
+
+		# State flags
+		self.hasKtop = False		# whether ktop is up-to-date
+		self.isAggregated = False	# whether aggregated values are up-to-date
+
+		# Data
+		self.dictionary = set()		# a list of all words that occur 
+		self.entries = {}			# an entry holds the data for one worker
+		self.testEntries = {}		# holds the unused entries when sub-sampled
+		self.trainEntries = {}
+		self.workerIds = set()		# to prevent duplicates
+		self.counts = {}			# stores words and frequency of occurrence
+		self.ktops = {}
+
+
+	# In principle This should be moved to the NBDataset class, because this 
+	# separation
+	# is really a concern introduced by the desire to train a Naive Bayes
+	# Classifier on the data.  But for now it is here.  The reason is because
+	# I had written the function aggregateCounts also here, but really both
+	# should be moved to Naive Bayes Classifier.
+	def subsample(self, trainingSetSize, testSetSize=None):
+		'''
+		Partitions the dataset into a training set, and test set.  
+		'''
+		self.trainEntries = {}
+		self.testEntries = {}
+		self.unusedEntries = {}
+
+		# Split the entries of each treatment into testing and training sets
+		for treatment, entries in self.entries.items():
+
+			if testSetSize is None:
+				lTestSetSize = len(entries) - trainingSetSize
+				unusedSize = 0
+
[…]

### 2014-04-09 src/naive_bayes.py

@@ -1,0 +1,237 @@
+
+'''
+Given a dataset:
+- find the set of treatments
+- find the set of features
+- calculate the probability that an instance from a class has a property
+
+one way to calculate the probability of a word is just the number of instances
+of the word in the treatment divided by 100.  This assumes that people don't 
+repeat words, which is fair, but not guaranteed. At least at first I'll build 
+with this assumption.
+
+What are the features in my case?  Potentially it is a word-position-occurence,
+alternatively, it is a word-occurence.  The former takes into account which
+text input into which the word was entered, the latter only takes into account
+whether or not the word was entered into any text input of a particular
+picture.
+'''
+
+import random
+
+class NBDataset(object):
+	'''
+	Wraps an instance of the CleanDataset class, making an object that
+	is suitable for being passed to the constructor of the NaiveBayesModel
+	class.  This class satisfies the interface that the NaiveBayesModel expects
+	to be able to query in order to build up a model.
+	'''
+	dataSet = None
+	treatments = []
+	doConsiderPosition = False
+	instances = {}
+
+	def __init__(self, 
+		pDataSet, pTreatments=['treatment1','treatment2'], 
+		pImages=['test0'], pDoConsiderPosition=False, pTrainingSize=80,
+		pTestingSize=20):
+		'''
+		Specify the treatment ids to be included when building the classifier.
+		You may not always want to try to build a classifier that can 
+		categorize instances from all treatments.  For example, for the image 
+		priming data I am first trying to build a classifier for the three 
+		first treatments only, since the last three might be quite similar, and
+		are of less interest in this respect.
+		'''
+
+		self.treatments = pTreatments
+		self.dataSet = pDataSet
+		self.doConsiderPosition = pDoConsiderPosition
+		self.images = pImages
+		
+		self.dataSet.subsample(pTrainingSize, pTestingSize)
+
+
+	def getCategories(self):
+		return list(self.treatments)
+
+
+	# Make this specific to the treatment and image passed in the constructor
+	def getFeatures(self):
+		features = set()
+		for treatment, image, position in self.dataSet.counts:
+
+			# The labels given to priming images are of no interest
+			if image is not None and image.startswith('prime'):
+				continue
+
+			# We aren't interested in features that are aggregated accross 
+			# many treatments or many images
+			if treatment is None or image is None:
+				continue
+
[…]

### 2014-04-09 src/ontology.py

@@ -1,0 +1,266 @@
+import json
+import re
+
+class Ontology(object):
+	def __init__(self):
+		self.model = {}
+		self.translator = {}
+		self._mask = set([])		# nodes in the mask affect how compare works
+
+
+	def readEdgeList(self, fname):
+		fh = open(fname, 'r')
+		edgeList = fh.read().split('\n')
+		for line in edgeList:
+			cells = line.split('\t')
+			
+
+			# Ignore lines with an empty first cell
+			if cells[0].strip() == '':
+				continue
+
+			parents = map(lambda x: self.strip(x), cells[0].split(','))
+			child = self.strip(cells[1])
+
+			# check if there is a synonym for the child
+			if child in self.translator:
+				child = self.translator[child]
+
+			for p in parents:
+
+				# First check if there is a synonym for the parent
+				p = self.getSynonym(p)
+
+				if p not in self.model:
+					self.model[p] = []
+				self.model[p].append(child)
+
+
+	def mask(self, tokenToMask):
+		self._mask.add(self.getSynonym(tokenToMask))
+
+
+	def clearMask(self):
+		self._mask = set()
+
+	def unmask(self, tokenToUnmask):
+		self._mask.remove(self.getSynonym(tokenToUnmask))
+
+
+	def compare(self, token1, token2, strict=True):
+
+		# Resolve synonyms, then get the ancesters for the tokens
+		token1, token2 = map(self.getSynonym, [token1, token2])
+		ancesters1, ancesters2 = map(self.getAncesters, [token1, token2])
+
+
+		if strict:
+			# each token must have no masked ancesters at all
+			roots1 = (ancesters1 | set([token1])) & set(self.model['ROOT'])
+			roots2 = (ancesters2 | set([token2])) & set(self.model['ROOT'])
+			if (roots1 & self._mask) or (roots2 & self._mask):
+				return 0
+
+
+		else:
+			# each token has to have at least one non-masked ancester
+			roots1 = (ancesters1 | set([token1])) & set(self.model['ROOT'])
+			roots2 = (ancesters2 | set([token2])) & set(self.model['ROOT'])
+			if not (roots1 - self._mask) or not (roots2 - self._mask):
+				return 0
+
+		if token1 in self.getAncesters(token2):
+			return 1
+
+		if token2 in self.getAncesters(token1):
+			return -1
+
+		return 0
+
+
+	def getAncesters(self, token):
+
+		ancesters = set()
+
[…]

### 2014-04-09 src/plots.py

@@ -1,0 +1,312 @@
+import util
+import analysis
+import sys
+import random
+import naive_bayes
+import ontology
+import data_processing
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib 
+from matplotlib.ticker import FixedLocator, LinearLocator, FixedFormatter
+
+# z-score for two-tailed 99-percent confidence interval
+CONFIDENCE_99 = 2.975
+
+TREATMENT_NAMES = {
+	'treatment0': r'ambg'
+	, 'treatment1': 'cult$_{img}$'
+	, 'treatment2': 'ingr$_{img}$'
+	, 'treatment3': 'ingr$_{fund}$'
+	, 'treatment4': 'ingr$_{fund,img}$'
+	, 'treatment5': 'cult$_{fund}$'
+	, 'treatment6': 'cult$_{fund,img}$'
+}
+
+CROSS_COMPARISONS = [
+	('treatment1', 'treatment0')
+	, ('treatment2', 'treatment0')
+	, ('treatment1', 'treatment2')
+
+	, ('treatment3', 'treatment5')
+	, ('treatment4', 'treatment6')
+]
+
+def analyze():
+
+	# The effects of priming are persistent.  These plots show how the effect 
+	# priming varies as we move from one picture to the next
+	plotClassificationVsImage(
+		5, ['treatment4', 'treatment6'], 
+		'../docs/figs/longitude_cult-ing-img-fund.pdf')
+
+	plotClassificationVsImage(
+		5, ['treatment3', 'treatment5'], 
+		'../docs/figs/longitude_cult-ing-fund.pdf')
+
+	plotClassificationVsImage(
+		5, ['treatment1', 'treatment2'], 
+		'../docs/figs/longitude_cult-ing-img.pdf')
+
+
+	# Here we assess whether the cultural and ingredients treatments are
+	# distinguishable, when priming takes place through different mechanisms
+	plotCrossComparison(5, '../docs/figs/cross-classification.pdf')
+
+	treatments = ['treatment0', 'treatment1', 'treatment5', 'treatment6',
+			'treatment2', 'treatment3', 'treatment4']
+	plotValenceComparison(treatments, '../docs/figs/valenceComparison.pdf')
+
+
+
+def plotSpecificityComparison(basisTreatment, treatmentsToBeCompared, 
+	numToCompare, fname, dimension='overall'):
+
+	# The dimension specifies whether we are comparing specificity overall, or
[…]

### 2014-04-09 src/random.js

@@ -1,0 +1,36 @@
+var m_w = 123456789;
+var m_z = 987654321;
+var mask = 0xffffffff;
+
+// Takes any integer
+function seed(i) {
+    m_w = i;
+	m_z = 987654321;
+}
+
+// Returns number between 0 (inclusive) and 1.0 (exclusive),
+// just like Math.random().
+function random()
+{
+    m_z = (36969 * (m_z & 65535) + (m_z >> 16)) & mask;
+    m_w = (18000 * (m_w & 65535) + (m_w >> 16)) & mask;
+    var result = ((m_z << 16) + m_w) & mask;
+    result /= 4294967296;
+    return result + 0.5;
+}
+
+window.onload = init;
+
+function init() {
+	$('#seed').on('blur', function() {
+		seed($(this).val());
+		bins = [0,0,0,0,0,0,0]
+
+		for(var i=0; i<100; i++) {
+			bins[random()*9007199254740992%bins.length] += 1;
+		}
+		alert(bins);
+	});
+	alert(Math.floor(random()*100));
+}
+

### 2014-04-09 src/tests.py

@@ -1,0 +1,185 @@
+import util
+import unittest
+import analysis
+import naive_bayes as nb
+import data_processing as dp
+import ontology
+
+
+class OntologyTestCase(unittest.TestCase):
+	def setUp(self):
+		self.ont = ontology.Ontology()
+		self.ont.readOntology('ontology/test0.ontology.json')
+
+
+	def test_comparison(self):
+		# First more general than second returns 1
+		self.assertEqual(self.ont.compare('ethnic', 'indian'), 1)
+
+		# First mere specific than second returns 2
+		self.assertEqual(self.ont.compare('bread', 'food'), -1)
+
+		# Non-comparable returns 0
+		self.assertEqual(self.ont.compare('statue', 'saucy'), 0)
+
+
+	def test_maskedComparison(self):
+
+		# mask everything in the root of the test ontology except food
+		for token in ['thing', 'adj', 'activity', 'cultural']:
+			self.ont.mask(token)
+
+		# Now make a food-based comparison
+		self.assertEqual(self.ont.compare('food', 'bread'), 1)
+
+		# Now make a cultural comparison.  This yielts 0 because cultural
+		# is masked
+		self.assertEqual(self.ont.compare('ethnic', 'indian'), 0)
+
+		# Now make a cultural-food comparison.  
+		# Default behavior is to do strict comparison, meaning that naan gets
+		# masked since it descends from 'cultural' 
+		self.assertEqual(self.ont.compare('naan', 'bread'), 0)
+
+		# Now make a cultural-food comparison, but with strict=False
+		# since naan also descends from food, which is not masked, it 
+		# passes under non-strict comparison
+		self.assertEqual(self.ont.compare('naan', 'bread', strict=False), -1)
+
+
+
+class AnalysisTestCase(unittest.TestCase):
+	def setUp(self):
+		self.dataset = dp.CleanDataset()
+		self.dataset.read_csv('amt_csv/test.csv')
+
+
+		self.a = analysis.Analyzer(self.dataset)
+
+
+	def test_CompareSpecificity(self):
+
+		# In the testing dataset, treatment 3 has strictly more general terms
+		# than treatment 4
+		result = self.a.compareSpecificity('treatment3','treatment4', 2)
+		self.assertEqual(result['avgFirstMoreSpecific'], 0)
+		self.assertGreater(
+			result['avgFirstLessSpecific'], result['avgFirstMoreSpecific'])
+
+
+	def test_CompareCulturalSpecificity(self):
+
[…]

### 2014-04-09 src/util.py

@@ -1,0 +1,28 @@
+import sys
+import random
+
+def writeNow(string):
+	sys.stdout.write(string)
+	sys.stdout.flush()
+
+def randomPartition(collection, *args):
+	firstPartitionSize = args[0]
+
+	# randomly sample the first partition
+	firstPartition = random.sample(collection, firstPartitionSize)
+
+	# Set aside the remainin not-sampled elements
+	remaining = []
+	for i in collection:
+		if i not in firstPartition:
+			remaining.append(i)
+
+	# recursively partition the remainder
+	if len(args) > 1:
+		remainingPartitions = randomPartition(remaining, *args[1:])
+	else:
+		remainingPartitions = []
+
+	return [firstPartition] + remainingPartitions
+
+

### 2014-04-09 docs/draft/draft1.tex
start draft, add better plot of specificity

\documentclass[letterpaper, 11pt, twocolumn]{article}
\usepackage[margin=1in]{geometry}
\setlength{\columnsep}{0.75cm}

\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage{algorithm2e}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{cite}
\usepackage{framed, color}
\usepackage{color, soul}
\definecolor{shadecolor}{rgb}{.93,.93,.93}
\definecolor{blu}{rgb}{0,0,1}
\newcommand{\td}[1]{{\color{blu}\hl{TODO: #1}}}
\newcommand{\vwm}{$V_{w,n,k}$}
\newcommand{\wm}{$W_{w,n,k}$}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage{gensymb}

\title{Climate control for performant HPUs}
\author{}

\parindent0pt \parskip8pt
\begin{document}
\maketitle

\section*{Abstract}
\textbf{}
\section*{Introduction}
There are still many tasks for which humans outperform computers
These tend to be tasks that rely on a large repertoire of prior knowledge,
the excercise of common sense judgment, certain visual tasks, and 
tasks that require spontaneous hypothesis generation.

With the emergence of microtask platforms like Amazon Mechanical Turk (AMT),
comes the hope of building compute in which human intelligence can be accessed
on-demand.  This leads to an analogy of the human to the CPU, wherein we think
of human processing units.

A major challenge in building systems that deliver on this vision is the 
natual variability obtained in HPU output.  In some tasks, this variability
is desireable.  For example, in an image labelling task, the natural 
variability in
HPU output leads to greater coverage of the semantic space occupied by an 
image.  In other cases this variability can be problematic, such as in a 
transcription task, where there is only one corect output, and any variability
is only noise.

Whether desired or not, to build up efficient systems from HPUs, one must 
understand the natural variance quantitatively, and understand the factors that
influence it.

Here we model the variance between HPUs as comming from two sources.  The first
is a persistent, or intrinsic variability.  We imagine that this to encompass  
temperamental predispositions, life history, and developmental stage of the 
individual.  While
it may change over the course of a person's lifetime, in the view of the 
computational architect, it is essentially constant.

The seccond is a short-term variability, which arises from the fact that 
peoples immediate state is a function of recent events.  This would include
such things as an HPU becomming more efficient at a task once it has completed
a few tasks of the same type.  It would also include such things as the 
potentially detrimental effects of a noisy environment.

In this view, one can imagine HPUs being different in their specifications,
and also exhibiting hysteresis, whereby their output at some time $t$ is a
function of their inputs at time $t$, $t-1$, and so on.

In psychology, the act of producing these short-lived states that effect a
person's performance during a task is called \textit{priming}.  We will adopt
this term throughout the present work.

\section*{Prior Work}
Priming itself can be broken into many types, and many studies exist exploring
the effects of overt priming on the performance of HPUs. Priming may arise
due to how the task is framed.  This includes such things as the stated
purpose of the task, and the identity of the requester the task.

In \cite{chandler2013breaking}, the researchers investigate the effects of 
framing task either in a meaningful or meaningless way.  Compared to a 
zero-context control treatment, workers increase their output (for less pay),
when they are told that they are helping identify cancer, but there is no
change in quality.  When workers are told that their submissions will be 
discarded, there is no change in the amount of work done, but the quality 
declines.

Another source of priming can be due to what might be called 
\textit{sidestream information}: information that is presented to the 
individual but which is not actually salient to the task.

Other researchers have studied how having peer's responses available to 
the task could influence the worker.

In the present work, we focus on a more subtle source of priming, which arises
simply from the worker's performance in earlier stages of the task.

We compare this to priming arising from framing the task by disclosing a 
(fictitious) funding agency that is paying for the study in which they are 
participating.

\section*{Methods}

\bibliographystyle{plain}
\bibliography{bab.bib}
\end{document}

### 2014-04-09 src/analysis.py

@@ -98,6 +98,29 @@ class Analyzer(object):
 		return result
 
 
+	def compareValenceSpecificity(
+		self, valence, subjectTreatment, basisTreatment, numToCompare=50):
+
+		assert(valence in ['overall', 'cultural', 'food'])
+
+		if valence == 'overall':
+			return self.compareSpecificity(
+				subjectTreatment, basisTreatment, numToCompare)
+
+		elif valence == 'cultural':
+			return self.compareCulturalSpecificity(
+				subjectTreatment, basisTreatment, numToCompare)
+
+		elif valence == 'food':
+			return self.compareFoodSpecificity(
+				subjectTreatment, basisTreatment, numToCompare)
+
+		else:
+			raise ValueError("In Analyzer.compareValenceSpecificity: valence "\
+				"must be one of 'overall', 'cultural', or 'food'. Found '"\
+				+ valence + "'.")
+
+
 	def compareFoodSpecificity(
 		self, treatment1, treatment2, numToCompare=50):
 

### 2014-04-09 src/plots.py

@@ -1,3 +1,4 @@
+import json
 import util
 import analysis
 import sys
@@ -8,9 +9,11 @@ import data_processing
 import numpy as np
 import matplotlib.pyplot as plt
 import matplotlib 
+import matplotlib.gridspec as gridspec
 from matplotlib.ticker import FixedLocator, LinearLocator, FixedFormatter
 
 # z-score for two-tailed 99-percent confidence interval
+CONFIDENCE_95 = 1.96
 CONFIDENCE_99 = 2.975
 
 TREATMENT_NAMES = {
@@ -56,6 +59,205 @@ def analyze():
 	treatments = ['treatment0', 'treatment1', 'treatment5', 'treatment6',
 			'treatment2', 'treatment3', 'treatment4']
 	plotValenceComparison(treatments, '../docs/figs/valenceComparison.pdf')
+
+	plotSpecificityComparison(
+		'treatment1', 
+		['treatment5', 'treatment6', 'treatment2'],
+		10, 'figs/spec-treat0-overall.pdf', 'overall'
+	)
+
+def plotAllSpecificity():
+
+
+	for dimension in ['overall', 'cultural', 'food']:
+		plotSpecificityComparison(
+			'treatment1', 
+			['treatment5', 'treatment6', 'treatment2'],
+			50, 'figs/spec-treat1-%s.pdf'%dimension, 'overall'
+		)
+
+		plotSpecificityComparison(
+			'treatment2', 
+			['treatment3', 'treatment4', 'treatment1'],
+			50, 'figs/spec-treat2-%s.pdf'%dimension, 'overall'
+		)
+
+		plotSpecificityComparison(
+			'treatment0', 
+			['treatment1', 'treatment5', 'treatment6', 'treatment2', 
+				'treatment3','treatment4'],
+			50, 'figs/spec-treat0-%s.pdf'%dimension, 'overall'
+		)
+
+def plotAllSpecificityComparisons(fname='specificity/all.json'):
+
+	data = json.loads(open(fname).read())
+
+
+	fig = plt.figure(figsize=(10,11))
+	gs = gridspec.GridSpec(3,3, width_ratios=[25,13,9])
+	subplotCounter = 0
+
+
+	for valenceComparison in data:
+		valence = valenceComparison['valence']
+
+		
+		for basisComparison in valenceComparison['results']:
+			basis = basisComparison['basis']
+
+			comparisonData = basisComparison['results']
+
+			width=0.75
[…]

### 2014-04-09 docs/draft/draft1.tex
update to manuscript

@@
 
+We paid 900 AMT workers to perform an image-labelling task.  Each worker
+was randomly assigned to one of 6 priming treatments. A task consisted of 
+labelling 10 images, with 5 labels each.  The first 5 images were varied 
+depending on the priming treatment, and this was used to explore the effects
+of \textit{in-task} priming.  The last 5 images were the same accross all 
+treatments, and served as the primary means of assessing the effects of 
+the priming treatments.
+
+The test images were chosen with two ideals in mind.  First, we chose images
+that we felt would generate a diverse vocabulary of labels, such that the
+effects of priming could be detected.  Images that are sparse, and with a 
+very strong foreground might produce a narrow distribution of labels that 
+would not exhibit the effects of priming as much.
+
+Second, we chose images which would produce labels belonging to two broad
+concepts, food and culture.  The purpose of this was to test to what
+extent workers could be biased in favor of focusing on one concept or the other
+during labelling.
+
+We divide our treatments into three broad classes: \textit{ambiguous}, 
+\textit{culture}, and \textit{food}.
+\section*{Results}
+\begin{figure*}
+	\includegraphics[scale=0.65]{../figs/specificity.pdf}
+\end{figure*}
+
 \bibliographystyle{plain}

### 2014-04-09 src/plots.py

@@ -89,9 +89,10 @@ def plotAllSpecificity():
 			50, 'figs/spec-treat0-%s.pdf'%dimension, 'overall'
 		)
 
-def plotAllSpecificityComparisons(fname='specificity/all.json'):
+def plotAllSpecificityComparisons(readFname='specificities/all.json', 
+	writeFname='figs/specificity.pdf'):
 
-	data = json.loads(open(fname).read())
+	data = json.loads(open(readFname).read())
 
 
 	fig = plt.figure(figsize=(10,11))
@@ -188,6 +189,7 @@ def plotAllSpecificityComparisons(fname='specificity/all.json'):
 				plt.tight_layout()
 
 	plt.subplots_adjust(bottom=.10)
+	fig.savefig(writeFname)
 	plt.show()
 
 

### 2014-04-09 docs/draft/draft1.tex
update to manuscript -- added test and priming images

--- 2014-04-09 docs/draft/draft1.tex
@@
 
+We paid 900 AMT workers to perform an image-labelling task.  A task consisted 
+of labelling 10 images, with 5 labels each.  The first 5 images were varied 
+depending on the priming treatment, while the last 5 images were the same 
+accross all treatments.  Ordering of the images was kept constant.
+
+Workers were randomly assigned to one of 6 treatments.  The treatments differed
+from one another along two dimensions. The first dimension consisted of 
+varying the first 5 images shown to the worker.  This was used to test the
+effects of \textit{in-task} priming.
+
+The second dimension concerned disclosure of a (fictitious) organization,
+purportedly funding work as part of a research study.  Depending on the 
+treatment, one of two funding agencies was presented, or no indication was 
+made.
+
+The 5 test images, were chosen carefully with two ideals in mind.  
+First, we chose images that we judged would generate a diverse vocabulary of 
+labels, such that the effects of priming could be detected.  In other words,
+sparse images with a single object in the foreground were not considered good 
+candidates, since they would be less likely to elicit labels that varied from 
+one worker and one priming treatment to the next.
+
+Second, we chose images which would produce labels belonging to two broad
+concepts, which would serve as the targets of our priming: food and culture.  
+This created the opportunity to attempt to prime workers in a way that would
+bias them toward emitting food-related or culture-related labels.
+
+Under these considerations, we chose the images shown in 
+Fig.~\ref{fig:testImages}
+
+\begin{figure*}
+	\includegraphics[scale=1.00]{../figs/testImages.png}
+	\label{fig:testImages}
+\end{figure*}
+
+\begin{figure*}
+	\includegraphics[scale=1.00]{../figs/ambiguous.png}
+	\label{fig:ambiguous}
+\end{figure*}
+
+\begin{figure*}
+	\includegraphics[scale=1.00]{../figs/cultural.png}
+	\label{fig:cultural}
+\end{figure*}
+
+\begin{figure*}
+	\includegraphics[scale=1.00]{../figs/ingredients.png}
+	\label{fig:ingredients}
+\end{figure*}
+
+We chose the three sets of priming images to that end.  The first set, was 
+chosen to be 
+for the treatment
+
+\textit{culture}, and \textit{food}.
+\section*{Results}
+\begin{figure*}
+	\includegraphics[scale=0.65]{../figs/specificity.pdf}
+\end{figure*}
+
 \bibliographystyle{plain}

### 2014-04-09 src/plots.py

@@ -239,7 +239,7 @@ def computeAllSpecificityComparisons(
 
 				# compare basis treatment to subject treatment
 				rslt = a.compareValenceSpecificity(
-					valence, basisTreatment, subjectTreatment, numToCompare)
+					valence, subjectTreatment, basisTreatment, numToCompare)
 
 				# express the avg specificity in terms of the standard 
 				# deviations of the null comparison.  Store the result

### 2014-04-10 docs/draft/draft1.tex
add compound f1score plot, update manuscript

@@
 
+\usepackage{fixltx2e}
 \usepackage{tikz}
@@
 
+\textbf{Task set-up.}
 We paid 900 AMT workers to perform an image-labelling task.  A task consisted 
@@
 
-The 5 test images, were chosen carefully with two ideals in mind.  
+Tasks were presented to workers as a series of panels or flash cards.  The
+first panel provided brief instructions, and was identical for all treatments.
+Workers could see this panel when previewing the task, but could not advance.
+Depending on the treatment, the worker was either shown a second pannel 
+stating the name of 
+one of two fictitious organizations funding the work, or this panel was 
+skipped.  The next five pannels each consisting of a priming sub-tasks, 
+wherein the worker was asked to submit five descriptive labels.  The images
+used during the priming sub-task depended on the treatment.  The last 5 pannels
+consisted of testing subtasks, wherein, as for the priming sub-tasks, workers
+were asked to submit 5 descriptive labels.
+
+\textbf{Choice of images.}
+The 5 test images, were chosen with two ideals in mind.  
 First, we chose images that we judged would generate a diverse vocabulary of 
@@
 Under these considerations, we chose the images shown in 
-Fig.~\ref{fig:testImages}
+Fig.~\ref{fig:testImages}.  Each of these images has food as its main focus,
+but also has a strong and specific cultural reference due to the unique, 
+iconic character of the food and the artifacts depicted.
+
+To investigate in-task priming, we chose a set of images that highly
+recognizeable cultural settings and no food, and another set that contained
+separated food ingredients, without any overt cultural content.  The third
+set of images was chosen to be very much like the test images, showing prepared
+meals, and though prepared food is inseperable from culture, these images
+were chosen based on being culturally more muted or ambiguous.
+
+\textbf{Label ontology.}
+In order to provide a deeper analysis, we built an ontology
+of the corpus of all labels applied to the first test image.  The ontology
+was built as a directed acyclic graph starting
+
+\section*{Results and discussion}
+
+\subsection*{Priming affects HPU output.}
+Before looking for differences in the content of labels provided by workers
+from different treatments, we first demonstrate that each treatment has a
+distinguishable impact on worker output relative to the \textsc{ambg}.
+
+Using a naive bayes classifier, we are able to distinguish with high precision
+and specificity between workers from the \textsc{ambg} treatment and any of
+the other 5 treatments.  Fig~\ref{fig:classifier} shows F1-score for a
+naive bayes classifier when distinguishing between the \textsc{ambg} and 
+target treatments. The classifier was trained using random subsamples of 
+output 80 HPUs drawn from each of the \textsc{ambg} and target treatments, and
+tested on the ouput of 20 HPUs from each treatment.
+
+We find it remarkable that, using only the labels that workers provide, it is
+possible to infer with good accuracy the treatment to which the worker was 
+subjected.
 
 \begin{figure*}
-	\includegraphics[scale=1.00]{../figs/testImages.png}
+	\includegraphics[scale=0.65]{../figs/f1scores.pdf}
+	\caption{caption here}
+	\label{fig:classifier}
+\end{figure*}
+
+A natural question is to test the ability for the classifier to perform 
+distinguish between other pairings of treatments.  For example, can the 
+classifier distinguish $\textsc{cult}_{img}$ workers from 
+$\textsc{cult}_{fund}$ workers?
+
+% Graphics commented out because they make compiling take long!  
+% Uncomment when desired!
+\begin{figure*}
+%	\includegraphics[scale=1.00]{../figs/testImages.png}
+	\caption{caption here}
 	\label{fig:testImages}
@@
 \begin{figure*}
-	\includegraphics[scale=1.00]{../figs/ambiguous.png}
+%	\includegraphics[scale=1.00]{../figs/ambiguous.png}
+	\caption{caption here}
 	\label{fig:ambiguous}
@@
 \begin{figure*}
-	\includegraphics[scale=1.00]{../figs/cultural.png}
+%	\includegraphics[scale=1.00]{../figs/cultural.png}
+	\caption{caption here}
 	\label{fig:cultural}
@@
 \begin{figure*}
-	\includegraphics[scale=1.00]{../figs/ingredients.png}
+%	\includegraphics[scale=1.00]{../figs/ingredients.png}
+	\caption{caption here}
 	\label{fig:ingredients}
@@
 
-We chose the three sets of priming images to that end.  The first set, was 
-chosen to be 
-for the treatment
-
-\textit{culture}, and \textit{food}.
 \section*{Results}
 \begin{figure*}
-	\includegraphics[scale=0.65]{../figs/specificity.pdf}
+	\includegraphics[scale=0.65]{../figs/specificity2.pdf}
 \end{figure*}

### 2014-04-10 src/plots.py

@@ -17,13 +17,13 @@ CONFIDENCE_95 = 1.96
 CONFIDENCE_99 = 2.975
 
 TREATMENT_NAMES = {
-	'treatment0': r'ambg'
-	, 'treatment1': 'cult$_{img}$'
-	, 'treatment2': 'ingr$_{img}$'
-	, 'treatment3': 'ingr$_{fund}$'
-	, 'treatment4': 'ingr$_{fund,img}$'
-	, 'treatment5': 'cult$_{fund}$'
-	, 'treatment6': 'cult$_{fund,img}$'
+	'treatment0': 'AMBG'
+	, 'treatment1': 'CULT$_{img}$'
+	, 'treatment2': 'INGR$_{img}$'
+	, 'treatment3': 'INGR$_{fund}$'
+	, 'treatment4': 'INGR$_{fund,img}$'
+	, 'treatment5': 'CULT$_{fund}$'
+	, 'treatment6': 'CULT$_{fund,img}$'
 }
 
 CROSS_COMPARISONS = [
@@ -54,7 +54,7 @@ def analyze():
 
 	# Here we assess whether the cultural and ingredients treatments are
 	# distinguishable, when priming takes place through different mechanisms
-	plotCrossComparison(5, '../docs/figs/cross-classification.pdf')
+	plotDisting(5, '../docs/figs/cross-classification.pdf')
 
 	treatments = ['treatment0', 'treatment1', 'treatment5', 'treatment6',
 			'treatment2', 'treatment3', 'treatment4']
@@ -65,6 +65,7 @@ def analyze():
 		['treatment5', 'treatment6', 'treatment2'],
 		10, 'figs/spec-treat0-overall.pdf', 'overall'
 	)
+
 
 def plotAllSpecificity():
 
@@ -422,49 +423,149 @@ def plotValenceComparison(treatments, fname):
 
 
 
-def plotCrossComparison(numReplicates, fname, comparisons=CROSS_COMPARISONS):
+def computeAllDisting(numReplicates=50, fname='f1scores/all.json'):
+
+	fh = open(fname, 'w')
+
+	subplotComparisons = [
+		{'basis': 'treatment0', 
+		'subjects' : ['treatment1', 'treatment5', 'treatment6', 
+			'treatment2', 'treatment3', 'treatment4']}
+
+		, {'basis': 'treatment1', 
+		'subjects' : ['treatment5', 'treatment6', 
[…]

### 2014-04-10 docs/draft/draft1.tex
update to manuscript

@@
 
+\section*{Framework}
+At this point we have surveyed some of the conceptual framework traditionally
+used to discuss priming in the context of psychology.  Having the origin that
+they do, these frameworks are suited to describing the internal mechanisms of
+the mind from which they arise.  For our purposes here, we are interested 
+primarily in the \textit{effects} of priming, and so it makes sense to 
+adopt a position conducive to those ends.  Since our interest in priming 
+arises from a desire to construct computing systems from HPUs, we shall
+propose a well-defined algorithmic definition for priming.
+
+We must first remark that it does not make sense to speak of an un-primed 
+state.  A person can be no more un-primed than a ship at sea can have no 
+bearing.  Next, we propose that priming should generally be regarded as a
+property of a population of HPUs, rather than as the state of a single HPU.
+This is rather like the notion of temperature in thermodynamics.  Although
+it does make sense to speak of the kinetic energy of a single molecule, 
+Temperature is a statement about the distribution of kinetic energies in a
+population of molecules.  The definition of priming which we presently submit
+will also be defined in terms of populations.
+
+Two populations, \textsc{j} and \textsc{k} are said to be 
+\textit{differently primed} with respect to a task $\mathcal{T}$ if there 
+exists a polynomial-time algorithm $\mathcal{A}$ that can distinguish 
+(classify) members of \textsc{j} and \textsc{k} with accuracy $\theta$, when 
+$\mathcal{A}$ is provided the labelled work-products of HPUs from \textsc{j} 
+and \textsc{k} tasked with $\mathcal{T}$.
+When $\mathcal{A}$ exists, we say that \textsc{j} and \textsc{k} deviate by 
+$\theta$ in priming.
+
+The above definition is simply intended to provide a well-defined definition
+of what priming \textit{is}.  Naturally, it says nothing about the consequences
+of priming.  The significance of the priming of a given population will
+depend both on the nature of $\mathcal{T}$ and on the intended purpose of 
+the work products derived from HPUs performing $\mathcal{T}$.
+
 \section*{Methods}
@@
 
-\subsection*{Priming affects HPU output.}
+\begin{figure*}
+	\begin{center}
+		\includegraphics[scale=0.55]{../figs/f1scores.pdf}
+		\caption{caption here}
+		\label{fig:classifier}
+	\end{center}
+\end{figure*}
+
+\textbf{Priming affects HPU output.}
 Before looking for differences in the content of labels provided by workers
-from different treatments, we first demonstrate that each treatment has a
-distinguishable impact on worker output relative to the \textsc{ambg}.
+from different treatments, we first demonstrate that the treatments are
+distringuishable in an algorithmic sense.
 
@@
 and specificity between workers from the \textsc{ambg} treatment and any of
-the other 5 treatments.  Fig~\ref{fig:classifier} shows F1-score for a
+the other 5 treatments.  Fig~\ref{fig:classifier}A shows F1-score for a
 naive bayes classifier when distinguishing between the \textsc{ambg} and 
-target treatments. The classifier was trained using random subsamples of 
-output 80 HPUs drawn from each of the \textsc{ambg} and target treatments, and
-tested on the ouput of 20 HPUs from each treatment.
+the other treatments. The classifier achieves high precision and specificity
+in task.  Figure~\ref{fig:classifier}B shows the F1-score for binary
+classification between the $\textsc{cult}_{img}$ and the other treatments, 
+while \ref{fig:classifier}C shows that for $\textsc{ingr}_{img}$ and the other
+treatments.
+
+Not surprisingly, pairs of treatments in which one primes for culture, and the
+other primes for ingredients are easily distinguished.  However, it is quite
+surprising that high accuracy is achieved when classifying treatments within 
+the same valence (e.g. cultural).  This is especially true in such cases as
+the classification of  $\textsc{cult}_{img}$ and $\textsc{cult}_{fund,img}$
+($\text{F}_1 = 0.863$), where both treatments also share the priming images in 
+common.
 
 We find it remarkable that, using only the labels that workers provide, it is
-possible to infer with good accuracy the treatment to which the worker was 
+possible to infer with good accuracy (at least when given a choice between 
+two posibilities)  the treatment to which the worker was 
 subjected.
 
+\begin{figure}
+	\includegraphics[scale=0.65]{../figs/valenceComparison.pdf}
+	\caption{caption here}
+	\label{fig:valence}
+\end{figure}
+
+\textbf{Priming orients HPU focus.}
+Having established that each treatment does in fact consist of distinguishable 
+populations of the HPUs, we next look at the content of labels.  Two of the
+root labels in our ontology, \texttt{food} and \texttt{cultural}, map naturally
+onto the two concepts that laid behind the design of our priming treatments.
+A natural and straightforward expectation is that HPUs from treatments 
+$\textsc{cult}_x$ should emit more labels that are ontological descendents of
+\texttt{cultural}, while those from the $\textsc{ingr}_x$ treatments should
+emit more labels under $\textsc{food}$.
+
+In Fig.~\ref{fig:valence}, we exhibit the percentage of labels having a 
+cultural valence (i.e. descending from \texttt{cultural} in the ontology), and 
+the percentage having a food valence. Before making comparisons using this
+information, we remark that there is no reason to expect a balance in the 
+number of words having cultural or food valence overall.  The $\textsc{ambg}$
+treatment, which was designed to promote neither valence, exhibits a
+significant fraction of words from both the food and cultural valence, while
+significantly favoring the former.
+
+Both $\textsc{cult}_{img}$ and $\textsc{cult}_{fund,img}$ show a significant
+excess of culturally-oriented labels and fewer food-orientel labels.  
+Furthermore, HPUs in these treatments emit more culturally-oriented labels 
+even while emitting fewer labes that are simultaneously oriented toward 
+cultural and food (light bars in Fig.~\ref{fig:valence}).
+The deviation of these treatments from
+the others is well beyond the 95\% confidence interval.
+
+Interestingly, the $\textsc{cult}_{fund}$ treatment did not have this effect.
+Although we have demonstrated that $\textsc{cult}_{fund}$ is differently
+primed from \textsc{ambg} using a naive bayes classifier, in respect of 
+overal fraction of food- and culturally-oriented labels, no distinction 
+is to be made.
+
+In the case of $\textsc{ingr}_x$ treatments one expects to see an 
+enrichment of food-oriented labels. There is perhaps some evidence for this
+$\textsc{ingr}_{fund}$ and $\textsc{ingr}_{fund,img}$, but we cannat make any
+assertion with confidence.
+
 \begin{figure*}
-	\includegraphics[scale=0.65]{../figs/f1scores.pdf}
+	\includegraphics[scale=0.65]{../figs/specificity2.pdf}
 	\caption{caption here}
-	\label{fig:classifier}
+	\label{fig:specificity}
 \end{figure*}
 
-A natural question is to test the ability for the classifier to perform 
-distinguish between other pairings of treatments.  For example, can the 
-classifier distinguish $\textsc{cult}_{img}$ workers from 
-$\textsc{cult}_{fund}$ workers?
+\textbf{Priming affects attention to detail.}
+We next look at how alternately treated HPUs differ in their tendency to use
+more specific or more general labels. We use the ontology of labels emitted
+on the first test image to unambiguously establish a partial ordering of 
+label-specificity.  If one label $\ell_1$ is within the ancestry of another
+$\ell_2$, we say that $\ell_1$ is more general than $\ell_2$, otherwise they
+are not comparable.  Thus, the label \texttt{naan} is more 
+specific than both \texttt{bread} and \texttt{indian}, while uncomparable to
+\texttt{statue}.
 
+Label-specificity only generates a partial ordering---at least in our 
+experimental design.  A consequence of this is that it is not possible to
+assign an overall specificity score to a set of labels.  We submit that this
+reflects the underlying complexity of natural language semantics.  While
+we admit that there may be many ways to generate full orderings based on some
+notion of label specificity, we believe that this would inappropriately 
+collapse qualitative differences between labels, leading to results that are
+difficult to interpret.
+
+In Fig.~\ref{fig:specificity}, We show pairwise specificity comparisons 
+between various pairs of treatments.  Figure~\ref{fig:specificity}A shows
+the comparison of \textsc{ambg} with all other treatments.  Both treatments
+primed with cultural images ($\textsc{cult}_{img}$ and 
+$\textsc{cult}_{fund, img}$) exhibit an excess of more general words compared
+to \textsc{ambg}.  Meanwhile, $\textsc{ingr}_{fund}$ emitted an excess of 
+more specific words.
+
+We can seek to explain these observations by restricting the comparison to
+labels of a specific orientation (e.g. food or cultural).  When we perform
+the same comparisons but restricting to food-oriented labels, as shown in 
+Fig.~\ref{fig:specificity}G, we see some of the same tendencies as in A.
+However, when restricting to culturally-oriented labels 
+(Fig~\ref{fig:specificity}D) there are no significant comparative deviations 
+in specificity to speak of.
+
+A first conclusion that we can draw from this is that there is a significant
+loss of specificity in labels emitted by treatments having non-ambiguous 
+priming images.  In Fig.~\ref{fig:specificity}G, only $\textsc{cult}_{fund}$
+and $\textsc{ingr}_{fund}$ show no significant deviation.
+
+- through negative priming workers stop responding to generic features of images of prepared meals, which happens in the ambiguous case.
+
+- On the other hand, workers presented with either the cultural or ingredients images are initially struck by the gross differences, which draws generic 
+labels, especially with respect to food for which generic labels in ambiguous treatment had been suppressed through negative priming.
+
+- it seems, at first, inconsistent that $\textsc{cult}_{img}$ and 
+$\textsc{cult}_{fund,img}$ would at once enrich the fraction of 
+culturally-oriented words, but produce no change in the specificity of 
+culturally oriented words.  First of all, there is no logical incompatibility
+with producing a greater number of cultural terms, yet which are generic 
+in nature.  If we follow the hypothesis that focus (or orientation) is directed
+by positive priming (perhaps through the subconscious or conscious inference
+of reqeuster intent), while focusing on nuances comes from the inhibition
+of gross features through negative priming, then this combination of observations makes sense.  Having seen many cultural images, HPUs in 
+$\textsc{cult}_{img}$ and $\textsc{cult}_{fund,img}$ are primed to emit 
+cultural labels, however, since the diversity of images is high compared to
+other treatments on reaching the test images, there no opportunity for 
+focussing in to finer detail through the mechanism of negative priming.
+
+\begin{figure}
+	\includegraphics[scale=0.4]{../figs/longitude0.pdf}
+	\caption{caption here}
+	\label{fig:longitude}
+\end{figure}
+
+One interesting test of this hypothesis arises in 
 % Graphics commented out because they make compiling take long!  
@@
 
-\section*{Results}
-\begin{figure*}
-	\includegraphics[scale=0.65]{../figs/specificity2.pdf}
-\end{figure*}
-
 \bibliographystyle{plain}

### 2014-04-10 src/analysis.py

@@ -6,6 +6,8 @@ import ontology
 import data_processing
 import numpy as np
 
+CONFIDENCE_95 = 1.96
+CONFIDENCE_99 = 2.975
 
 class ClassifierPerformanceResult(object):
 
@@ -157,15 +159,13 @@ class Analyzer(object):
 		return result
 
 
-	def percentValence(self, valence, treatment, image=None):
+	def percentValence(self, treatment, image=None, 
+		significanceLevel=CONFIDENCE_95):
 		'''
 		Determine the percentage of culture-related tokens found in entries
 		of a given treatment.  If image is specified, restrict counts to
 		a specific image
 		Input: 
-			valence (str): root token in the ontology, e.g. 'food', or 
-				'cultural'.
-
 			treatmen (str): key for identifying a treatment, e.g.
 				'treatment0'.
 
@@ -178,59 +178,86 @@ class Analyzer(object):
 		'''
 
 		# counters
-		numValenceTokens = 0
-		numTokens = 0
-
-		valencePercentages = []
+		treatmentCounts = {'cultural':0, 'food':0, 'both':0, 'overall':0}
+		percentages = {'cultural': [], 'food': [], 'both': []}
 
 		entries = self.dataSet.entries[treatment]
 		for entry in entries:
 
-			# Figure out which images we're interested in
-			interestingImages = []
+			# Figure out which tokens we're interested in
+			tokenKeys = []
 
 			# if the image wasn't specified, just get all the keys that specify
 			# words entered for any test image
 			if image is None:
-				interestingImages = filter(
-					lambda imageKey: imageKey[0].startswith('test'), 
+				tokenKeys = filter(
+					lambda tokenKey: tokenKey[0].startswith('test'), 
 					entry.keys())
 
 			# But if the image was specified, just use that one
 			else:
-				interestingImages = filter(
-					lambda imageKey: imageKey[0] == image, entry.keys())
+				tokenKeys = filter(
+					lambda tokenKey: tokenKey[0] == image, entry.keys())
 
-			if not len(interestingImages):
+			if not len(tokenKeys):
 				raise Exception('Bad key for image')
 
 
-			thisNumValenceTokens = 0
-			thisNumTokens = 0
-			for imageKey in interestingImages:
-				numTokens += 1
-				thisNumTokens += 1
+			entryCounts = {'cultural': 0, 'food': 0, 'both': 0, 'overall': 0}
 
[…]

### 2014-04-10 src/plots.py

@@ -56,9 +56,7 @@ def analyze():
 	# distinguishable, when priming takes place through different mechanisms
 	plotDisting(5, '../docs/figs/cross-classification.pdf')
 
-	treatments = ['treatment0', 'treatment1', 'treatment5', 'treatment6',
-			'treatment2', 'treatment3', 'treatment4']
-	plotValenceComparison(treatments, '../docs/figs/valenceComparison.pdf')
+	plotValenceComparison()
 
 	plotSpecificityComparison(
 		'treatment1', 
@@ -361,59 +359,67 @@ def plotSpecificityComparison(basisTreatment, treatmentsToBeCompared,
 
 
 
-def plotValenceComparison(treatments, fname):
+def plotValenceComparison(fname='../docs/figs/valenceComparison.pdf'):
+
+	treatmentIds = [0,1,5,6,2,3,4]
+	treatments = ['treatment%d' % i for i in treatmentIds]
+
 	a = analysis.Analyzer()
-	percentValences = {'cultural':[], 'food':[]}
-	stdevValences = {'cultural':[], 'food':[]}
+	percentValences = {'cultural':[], 'food':[], 'both':[]}
+	stdValences = {'cultural':[], 'food':[], 'both':[]}
+
 	for treatment in treatments:
 
-		result = a.percentValence('cultural', treatment, 'test0')
-		percentValences['cultural'].append(result['mean'])
-		stdevValences['cultural'].append(result['stdev'])
+		result = a.percentValence(treatment, 'test0')
 
-		result = a.percentValence('food', treatment, 'test0')
-		percentValences['food'].append(result['mean'])
-		stdevValences['food'].append(result['stdev'])
+		percentValences['cultural'].append(result['mean']['cultural'])
+		percentValences['food'].append(result['mean']['food'])
+		percentValences['both'].append(result['mean']['both'])
 
-	
-	width = 0.35
+		stdValences['cultural'].append(result['stdev']['cultural'])
+		stdValences['food'].append(result['stdev']['food'])
+		stdValences['both'].append(result['stdev']['both'])
+
+	width = 0.375
 	X = range(len(treatments))
 	X2 = map(lambda x: x + width, X)
 	
-	fig, ax = plt.subplots()
+	fig = plt.figure(figsize=(5,5))
[…]

### 2014-04-10 docs/draft/draft1.tex
add annotations and captions to plots

@@
 
+\usepackage[font=footnotesize,labelfont=bf]{caption}
 \usepackage{fixltx2e}
@@
 		\includegraphics[scale=0.55]{../figs/f1scores.pdf}
-		\caption{caption here}
+		\caption{$F_1$-score for binary classification of HPUs from seperate
+			treatments using a naive Bayes classifier.  Each pannel shows
+			the performance of the classifier when distinguishing between 
+			a basis treatment (inset) and the treatments listed on the 
+			abscissa.
+		}
 		\label{fig:classifier}
@@
 surprising that high accuracy is achieved when classifying treatments within 
-the same valence (e.g. cultural).  This is especially true in such cases as
+the same orientation (e.g. cultural).  This is especially true in such cases as
 the classification of  $\textsc{cult}_{img}$ and $\textsc{cult}_{fund,img}$
@@
 	\includegraphics[scale=0.65]{../figs/valenceComparison.pdf}
-	\caption{caption here}
+	\caption{Percentage of labels of a food- or cultural- orientation, or
+	both.  In our ontology of labels, a label can have multiple parents. 
+	For example \texttt{naan} inherits from both \texttt{food} and 
+	\texttt{cultural} through its parent \texttt{indian food}.}
 	\label{fig:valence}
@@
 \texttt{cultural}, while those from the $\textsc{ingr}_x$ treatments should
-emit more labels under $\textsc{food}$.
+emit more labels under $\texttt{food}$.
 
 In Fig.~\ref{fig:valence}, we exhibit the percentage of labels having a 
-cultural valence (i.e. descending from \texttt{cultural} in the ontology), and 
-the percentage having a food valence. Before making comparisons using this
+cultural orientation (i.e. descending from \texttt{cultural} in the ontology), and 
+the percentage having a food orientation. Before making comparisons using this
 information, we remark that there is no reason to expect a balance in the 
-number of words having cultural or food valence overall.  The $\textsc{ambg}$
-treatment, which was designed to promote neither valence, exhibits a
-significant fraction of words from both the food and cultural valence, while
+number of words having cultural or food orientation overall.  The $\textsc{ambg}$
+treatment, which was designed to promote neither orientation, exhibits a
+significant fraction of words from both the food and cultural orientation, while
 significantly favoring the former.
@@
 \begin{figure*}
-	\includegraphics[scale=0.65]{../figs/specificity2.pdf}
-	\caption{caption here}
+	\begin{center}
+	\includegraphics[scale=0.55]{../figs/specificity2.pdf}
+	\caption{Pairwise comparisons of label specificity between different 
+	HPU treatments.  Each pannel presents a binary comparison between a 
+	basis treatment (inset) and the subject treatments indicated on the 
+	abscissa.  A positive specificity score indicates that the subject 
+	treatment emitted more specific words than the basis treatment overall.
+	In a given comparison, a sample of 50 HPUs from the   
+	each treatment was randomly sampled, and the specificity of labels from
+	the HPUs of oposing treatments were compared.
+	To compare two HPUs, each pair of labels from different HPUs are compared.
+	and the specificity score of subject HPU is the number of cases where its
+	label is more specific than the subject HPUs, less the number of cases 
+	where it is more general. This score is 
+	avereaged for all HPU pairings.  Statistical significance is guaged
+	by generating a null-comparison between two mutually exclusive subsamples 
+	from the basis treatment.  This null-comparison yields a distribution
+	of relative specificities whose mean is in principle zero.  The 
+	specificity scores are expressed in terms of standard deviations of
+	the null-comparison specificities.  
+	The dotted lines represent the 95\% confidence interval for rejecting 
+	the null Hypothesis that the basis treatment and subject treatment are
+	equally specific.
+	}
 	\label{fig:specificity}
+	\end{center}
 \end{figure*}
@@
 
+\textbf{In-task priming is stronger than framing.}
+Our experimental set-up includes two priming mechanisms: in-task priming, 
+produced by varying the first 5 images of the task, as well as what could be
+called sidestream priming, in which a fictitious funder is disclosed.
+The intention behind this set-up was to enable a direct comparison, and 
+our expectation was that in-task priming might produce some fraction of the
+effect produced by disclosing the funder.  To our surprise, in-task priming 
+produces a much stronger effect.
+
+There is a cautionary lesson here.  In-task priming, which is inherently 
+impossible to eliminate is may be far more severe than the more overt causes 
+of priming that more routinely attract concern during the design of an 
+experiment.   Depending on the final purpos of HPU work products, this may be
+quite restrictive.
+
+\textbf{Leveraging priming.}
+In a more positive view, the results of our study suggest that the ordering 
+of subtasks can be used as a way to direct the focus and attention to detail
+by HPUs.  If the designer desires more coarse-grained work-products, this
+can be achieved by presenting successive subtasks with high diversity.  On 
+the other hand if fine-grained work products are desired, then the designer
+should aim to sort subtasks into ``tracks'' that are highly homogeneous,
+and assign subsens of the pool of HPUs to specifict tracks.
+
+It is interesting to consider to what extent the output of HPUs can be driven
+toward nuanced detail using this technique.  Consider, for example, the 
+image labelling platform called the ESP Game.  Here Two HPUs are shown
+the same image and in order to derive what are in some sense the moset 
+characteristic labels, they are asked to attempt to produce the same labels
+for the image.  One could imagine a similar setup, but in which the designer
+attempts to produce the set of labels that best covers the semantic space 
+occupied by the image, by eliciting labels at coarser and finer levels of 
+specificity using the techniques suggested by the present work.
+
 \begin{figure}

### 2014-04-10 src/plots.py

@@ -88,11 +88,12 @@ def plotAllSpecificity():
 			50, 'figs/spec-treat0-%s.pdf'%dimension, 'overall'
 		)
 
-def plotAllSpecificityComparisons(readFname='specificities/all.json', 
+def plotAllSpecificityComparisons(readFname='specificity/all.json', 
 	writeFname='figs/specificity.pdf'):
 
 	data = json.loads(open(readFname).read())
 
+	subplotLabels = ['A','B','C','D','E','F','G','H','I']
 
 	fig = plt.figure(figsize=(10,11))
 	gs = gridspec.GridSpec(3,3, width_ratios=[25,13,9])
@@ -157,6 +158,19 @@ def plotAllSpecificityComparisons(readFname='specificities/all.json',
 			ylims = plt.ylim()
 			ypadding = (ylims[1] - ylims[0]) * 0.05
 			plt.ylim(ylims[0] - ypadding, ylims[1] + ypadding)
+
+			# Label each pannel
+			letterLabel = subplotLabels[subplotCounter]
+			ax.text(len(comparisonData) - 0.2, 9.9, letterLabel, 
+					va='top', ha='right', size=20)
+
+			# Label the basis treatment as an inset
+			basisTreatmentName = TREATMENT_NAMES[basis]
+			bbox_props =  {'facecolor': 'white'}
+			if subplotCounter%3 == 0:
+				bbox_props['pad'] = 8
+			ax.text(len(Y)-0.3,-9.4,basisTreatmentName, 
+					ha='right', va='bottom', bbox=bbox_props)
 
 			# handle x-axis labelling
 			if subplotCounter > 5:
@@ -410,7 +424,7 @@ def plotValenceComparison(fname='../docs/figs/valenceComparison.pdf'):
 	plt.xlim(xlims)
 	plt.ylim((0,55))
 
-	ax.set_ylabel("percent of labels having valence")
+	ax.set_ylabel("percent of labels having orientation", size=14)
 
 	xlabels = [TREATMENT_NAMES[t] for t in treatments]
 	ax.set_xticks(X2)
@@ -446,6 +460,7 @@ def computeAllDisting(numReplicates=50, fname='f1scores/all.json'):
 		'subjects' : ['treatment5', 'treatment6', 
 			'treatment3', 'treatment4']}
 	]
+
 
 	results = []
 
[…]

### 2014-04-10 docs/draft/draft1.tex
update to manuscript

@@
 \section*{Introduction}
-There are still many tasks for which humans outperform computers
-These tend to be tasks that rely on a large repertoire of prior knowledge,
-the excercise of common sense judgment, certain visual tasks, and 
-tasks that require spontaneous hypothesis generation.
+Although capabilities in artificial intelligence continue to advance, 
+there are still many tasks for which human performance exceeds that of 
+computers now and in the forseable future.  Tasks requiring repertoire of 
+general knowledge about the world, the use of common sense or expert judgment, 
+finding creative solutions to open-ended questions, and spontaneously 
+hypothesis generation outside any apparent framework, are all examples of 
+tasks that are routine for humans, but very difficult or impossible for 
+computers.  The image labelling task is perhaps the canonical human 
+intelligence task (HIT), perhaps because it is simply stated, nearly effortless
+for humans, but still extremely challenging for computers.
 
-With the emergence of microtask platforms like Amazon Mechanical Turk (AMT),
-comes the hope of building compute in which human intelligence can be accessed
-on-demand.  This leads to an analogy of the human to the CPU, wherein we think
-of human processing units.
+Rather than replicate human intelligence, there is an alternate vision in 
+which human intelligence can be freely accessed and meshed with artificial
+intelligenc.  The emergence of microtask platforms like Amazon Mechanical 
+Turk (AMT) has made this vision a reality to some extent.  In this paradigm,
+the human processing unit (HPU) becomes one component in a hybrid 
+computational system, analagous to the CPU.
 
-A major challenge in building systems that deliver on this vision is the 
-natual variability obtained in HPU output.  In some tasks, this variability
-is desireable.  For example, in an image labelling task, the natural 
-variability in
-HPU output leads to greater coverage of the semantic space occupied by an 
-image.  In other cases this variability can be problematic, such as in a 
-transcription task, where there is only one corect output, and any variability
-is only noise.
+But there are major challenges in building systems that deliver on this 
+vision.  People are far more complex than manufactured chips, 
+and so HPU performance is noisy, and subject to bias, leading to uncertain
+quality of output.  Of course, the effect that HPU noise has on a compute job 
+will depend on the application.
+In the image labelling task, some variability is desireable, because it helps
+generate sets of labels that in some sense cover semantic space occupied by an 
+image.  In other cases this variability can be problematic.  In a 
+transcription task, usually there is only one correct output, and so 
+variability in the output only degrades quality.
 
-Whether desired or not, to build up efficient systems from HPUs, one must 
-understand the natural variance quantitatively, and understand the factors that
-influence it.
+Regardless of the application, the understanding HPU variance quantititively,
+and the factors that influence it, will help design of efficient compute 
+systems built from HPUs.
 
-Here we model the variance between HPUs as comming from two sources.  The first
-is a persistent, or intrinsic variability.  We imagine that this to encompass  
-temperamental predispositions, life history, and developmental stage of the 
-individual.  While
-it may change over the course of a person's lifetime, in the view of the 
-computational architect, it is essentially constant.
+Much has been written on the factors that influence human input in 
+crowdsourcing platforms.  This has generally related to the context in which
+the HPU engages the task.  Unfortunately, especially for platforms like AMT,
+this context is out of the designers control, and the relative anonymity of
+workers makes it difficult to select for specific conditions.
 
-The seccond is a short-term variability, which arises from the fact that 
-peoples immediate state is a function of recent events.  This would include
-such things as an HPU becomming more efficient at a task once it has completed
-a few tasks of the same type.  It would also include such things as the 
-potentially detrimental effects of a noisy environment.
+In the present work, we compare influences that arise from the framing of the
+task to influences that arise in-task from the mere act of working.  What 
+are the effects of performance that arise simply from how the worker's 
+attention is influenced by the previous task, and how do these relate 
+quantititively to other pre-task influences?
 
-In this view, one can imagine HPUs being different in their specifications,
-and also exhibiting hysteresis, whereby their output at some time $t$ is a
-function of their inputs at time $t$, $t-1$, and so on.
-
-In psychology, the act of producing these short-lived states that effect a
-person's performance during a task is called \textit{priming}.  We will adopt
-this term throughout the present work.
+We pay workers on AMT to label images, and analyze the effects brought about
+by subjecting them to different priming treatments, either in the form of 
+disclosing a semantically charged name of a (fictitious) organization 
+funding the research, or by altering the first few images presented to the
+workers.  Surpisingly, simply altering the first few images produces a much
+stronger shift in subsequent labelling performance than does disclosing the 
+semantically-laden name of the funder.
 
 \section*{Prior Work}
-Priming itself can be broken into many types, and many studies exist exploring
-the effects of overt priming on the performance of HPUs. Priming may arise
-due to how the task is framed.  This includes such things as the stated
-purpose of the task, and the identity of the requester the task.
 
-In \cite{chandler2013breaking}, the researchers investigate the effects of 
-framing task either in a meaningful or meaningless way.  Compared to a 
-zero-context control treatment, workers increase their output (for less pay),
-when they are told that they are helping identify cancer, but there is no
-change in quality.  When workers are told that their submissions will be 
-discarded, there is no change in the amount of work done, but the quality 
-declines.
+When considering the design of computing systems based on HPUs, we can think
+of variability in HPU output as having a relatively persistent component,
+and a transient one.  The persistent component would include intrinsic
+qualities of a person, such as their temperament, life history, and their 
+current developmental stage.  Such characteristics cannot be influenced by
+the designer, but it may be possible to screen or at least characterise them 
+to some extent.
 
-Another source of priming can be due to what might be called 
-\textit{sidestream information}: information that is presented to the 
-individual but which is not actually salient to the task.
+The transient component of variability might include such factors as influence
+alertness, orientation focus, mood, meaningfulness of the task, and any number
+of aspects of mental state too subtle to describe.  Such aspects are partly
+in the control of the system designer, and can be controlled through how the
+task is framed and set up.
 
-Other researchers have studied how having peer's responses available to 
-the task could influence the worker.
+In psychology, the phenomenon of priming occurs when a prior stimulus 
+makes a person more likely to respond to a task in a particular way.  The 
+phenomenon is well-studied, and is believed to follow perceptual, semantic,
+or conceptual similarities between the priming stimulus and the ensuing 
+response.
 
-In the present work, we focus on a more subtle source of priming, which arises
-simply from the worker's performance in earlier stages of the task.
+Drawing from this insight, it is natural to wonder whether current HPU 
+performance might be modulated by recently performed tasks.
 
-We compare this to priming arising from framing the task by disclosing a 
-(fictitious) funding agency that is paying for the study in which they are 
-participating.
+Existing work on the effects of human input in crowdsourcing platforms has
+generally focused on effects arising from auxilliary information, which has
+been added into the task setting, or which frames the task during its 
+introduction.
 
-\section*{Framework}
-At this point we have surveyed some of the conceptual framework traditionally
-used to discuss priming in the context of psychology.  Having the origin that
-they do, these frameworks are suited to describing the internal mechanisms of
-the mind from which they arise.  For our purposes here, we are interested 
-primarily in the \textit{effects} of priming, and so it makes sense to 
-adopt a position conducive to those ends.  Since our interest in priming 
-arises from a desire to construct computing systems from HPUs, we shall
-propose a well-defined algorithmic definition for priming.
+For example, it was shown that framing a task in a meaningful or meaningless
+way influences both task quality and the willingness of workers to produce
+more output given a declining payment schedule \cite{chandler2013breaking}.
+Surprisingly, relative to a zero-context treatment, although workers who were
+told that there contributions would be used to help identify cancerous cells
+were willing to provide more work, their work was not of a sufficiencly higher
+quality.  The only effect on quality occered when workers were told that their
+output would be discarded, in which case quality declined.
 
-We must first remark that it does not make sense to speak of an un-primed 
-state.  A person can be no more un-primed than a ship at sea can have no 
-bearing.  Next, we propose that priming should generally be regarded as a
-property of a population of HPUs, rather than as the state of a single HPU.
-This is rather like the notion of temperature in thermodynamics.  Although
-it does make sense to speak of the kinetic energy of a single molecule, 
-Temperature is a statement about the distribution of kinetic energies in a
-population of molecules.  The definition of priming which we presently submit
-will also be defined in terms of populations.
+Another study investigated the influence of providing workers with information
+about one another.  This study found that workers were willing to provide
+more output, when they were able to see one another's names.  The effect was 
+stronger when workers could also see some basic self-reported demographic 
+information, and more still when they could see one another's responses.
 
-Two populations, \textsc{j} and \textsc{k} are said to be 
+In the present work, we focus on a perhaps unusual source of priming---that 
+arising from the task itself, and compare this to priming that results from 
+framing the work as part of study by a named organization.  Given that the 
+mechanisms of priming are believed to be related to the residual activation of
+perceptual, semantic, and conceptual representations, we hypothesize that 
+\textit{in-task} priming could produce effects quantitively comparable to those
+produced by framing.
+
+\section*{Theoretical Framework}
+Having discussed very briefly some mechanisms and cases of priming, we shall 
+now seek to put forward, as an additional testable contribution, a rigorous
+definition for priming that is suitable for the study of computing with HPUs.
+
+First, we remark that it does not make sense to speak of an un-primed 
+state.  When a person engages in a task, she comes to the task with some 
+state of mind.  We therefore do not attempt to define priming in an absolute
+sense, but rather, in a relative sense, that is, one priming can be said to 
+be different from another.
+
+Also, the effects of a given treatment will depend on the task to which the 
+HPUs are put.  In other words, a treatment which generates a strong effect on
+the output in one task, does not necessarily produce a strong effect on the
+output for other tasks.  On a related note, the study of the effects of priming
+on HPUs should be defined algorithmically.  Only effects on HPU output that
+can be detected algorithmically can be relevant to a computing system built 
+from HPUs.
+
+Further, since only the influence on populations of HPU outputs can be 
+meaningfully measured, and since accessing HPU power generally involves 
+sampling from a pool of HPU workers, we define priming as a property of a 
+population of HPU outputs.  Having said these remarks, we now present an
+algorithmic definition of HPU priming:
+
+Two populations of HPU outputs, \textsc{j} and \textsc{k}, are said to be 
 \textit{differently primed} with respect to a task $\mathcal{T}$ if there 
-exists a polynomial-time algorithm $\mathcal{A}$ that can distinguish 
-(classify) members of \textsc{j} and \textsc{k} with accuracy $\theta$, when 
-$\mathcal{A}$ is provided the labelled work-products of HPUs from \textsc{j} 
-and \textsc{k} tasked with $\mathcal{T}$.
-When $\mathcal{A}$ exists, we say that \textsc{j} and \textsc{k} deviate by 
-$\theta$ in priming.
+exists an algorithm $\mathcal{A}$ which runs in time polynomial in the size
+of \textsc{j} and \textsc{k}, that can distinguish 
+(classify) members of \textsc{j} and \textsc{k} with accuracy 
+$\frac{1+\theta}{2}$, on input \textsc{j} and \textsc{k}.  Further, $\theta$
+must be a non-negligible function of $|\textsc{j} + \textsc{k}|$.
+If such an $\mathcal{A}$ exists, 
+we say that \textsc{j} and \textsc{k} deviate by $\theta$ in priming.
 
@@
 \begin{figure}
-	\includegraphics[scale=0.4]{../figs/longitude0.pdf}
-	\caption{caption here}
+	\includegraphics[scale=0.58]{../figs/longitudinalF1scores.pdf}
+\caption{$F_1$-score for a naive Bayes classifier trained to distinguish
+	HPUs from $\textsc{ingr}_{img}$ and $\textsc{cult}_{img}$ based on 80  
+	instances from each treatment, and tested using 20 instances.  Here we
+	present the performance of the classifier when only the labels from 
+	specific images are presented, to exhibit whether its performance degrades 
+	as the number of subtasks since priming increases. 
+	}
 	\label{fig:longitude}

### 2014-04-10 src/plots.py

@@ -614,40 +614,47 @@ def plotDisting(numReplicates, fname, comparisons=CROSS_COMPARISONS):
 
 
 
-def plotClassificationVsImage(numClassificationReplicates, treatments, fname):
+def plotClassificationVsImage(numReplicates=50, 
+	treatments=('treatment1','treatment2'), fname='figs/longitudinalF1scores.pdf'):
 
 	# Assess the classifier's ability to classify as a function of the image 
 	# from which the labels used for classification are derived
 	a = analysis.NBCAnalyzer()
 	f1Results, stdevResults = a.longitudinal(
-			numClassificationReplicates, treatments)
+			numReplicates, treatments)
 
 	# Plot the result
 	numPics = 5
-	width = 0.35						# width of bars
+	width = 0.375						# width of bars
 	X1 = range(numPics + 1)				# x-position of series1 bars
 	X2 = map(lambda x: x + width, X1)	# x-position of series2 bars
-	xlabels = ['all images'] + ['Image %d' % i for i in range(numPics)]
+	xlabels = ['all images'] + ['image %d' % (i+1) for i in range(numPics)]
 
 	# Make a plot
-	fig, ax = plt.subplots()
+	fig = plt.figure(figsize=(5,5))
+	ax = plt.subplot(111)
 
 	# Plot the performance with position-based labels
 	series1 = ax.bar(
-		X1, f1Results['withPosition'], width, color='0.25',  ecolor='0.55',
-		yerr=stdevResults['withPosition'])
+		X1, f1Results['withPosition'], width, color='0.25')
 
 	# Plot the performance without position-less labels
 	series1 = ax.bar(
 		X2, 
-		f1Results['withoutPosition'], width, color='0.55', ecolor='0.25',
-		yerr=stdevResults['withoutPosition'])
+		f1Results['withoutPosition'], width, color='0.55')
 
 	# Do some labelling business with the plot
-	ax.set_ylabel("F1 Score")
+	ax.set_ylabel("$F_1$-score", size=14)
 	ax.set_xticks(X2)
-	ax.set_xticklabels( xlabels )
+	ax.set_xticklabels( xlabels, ha='right', rotation=45 )
+
+	padding = 0.25
+	plt.xlim((-padding, numPics + 2*width + padding))
+	plt.ylim((0,1))
 	
+	plt.draw()
+	plt.tight_layout()
+	plt.subplots_adjust(bottom=.16)
 
 	fig.savefig(fname)
 	plt.show()

### 2014-05-04 docs/draft/figs.tex
added pnas manuscript -- woops

%        File: figs.tex
%     Created: Fri May 02 05:00 pm 2014 E
% Last Change: Fri May 02 05:00 pm 2014 E
%
\documentclass[a4paper]{report}
\usepackage{algorithm2e}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{cite}
\usepackage{framed, color}
\usepackage{soul}
\definecolor{shadecolor}{rgb}{.93,.93,.93}
\definecolor{blu}{rgb}{0,0,1}
\newcommand{\td}[1]{{\color{blu}\hl{TODO: #1}}}
\definecolor{shadecolor}{rgb}{.93,.93,.93}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage{gensymb}
\setlength{\parindent}{1cm}
\setlength{\parskip}{1cm plus2mm minus2mm}
\usepackage[hmargin=1.4cm,vmargin=1.4cm]{geometry}
\setlength{\parindent}{0cm}
\setlength{\parskip}{4mm plus1mm minus1mm}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}

\begin{document}
\begin{figure}
	\includegraphics{figs/f1-thetas.pdf}
	\caption{ $F_1$ score and $\theta_\text{NB}$ for the various 
priming treatments, as measured using a Naive Bayes classifier. Each panel 
presents classifier performance results that indicate the difference in
priming between a basis 
treatment, indicated in the inset, and the other treatments, indicated on the
abscissa. }
\end{figure}

\begin{figure}
	\includegraphics{figs/longitudinalF1scores-t1-t2.pdf}
	\caption{ $F_1$ score and $\theta_\text{NB}$ for the classification of 
	$\textsc{cult}_{img}$ and $\textsc{ingr}_{img}$ using a Naive Bayes 
	classifier.  The classifier is provided only the labels attributed to
	particular images as indicated on the abscissa.}
\end{figure}

\begin{figure}
	\includegraphics{figs/orientationVsTreatment.pdf}
	\caption{Percent label composition (culture- vs food-oriented labels) for 
		various images and treatments.  Panel A shows the composition of 
		labels, aggregated over all treatments, as a function of test image.
		Panel B shows the composition of labels, aggregated over all images, as
		a function of treatment.  Panel C shows the composition of labels 
		attributed to the first test image by various treatments.}
\end{figure}

\begin{figure}
	\includegraphics{figs/excessCultureVsTreatment-t1.pdf}
	\caption{Excess culture-oriented label composition in the labels provided
		by $\textsc{cult}_{img}$ as compared to $\textsc{ambg}$, for various
		test images (see \textbf{Eq. 1} for calculation).
	}
\end{figure}

\begin{figure}
	\includegraphics{figs/specificity-allImages.pdf}
	\caption{Relative specificity of various treatments.
		Each panel shows the comparison between a basis treatment (inset) and 
		target treatments (abscissa).
		Bar heights indicate relative specificity of the target 
		treatment compared to the basis (a positive quantity means the target 
		is more specific), and are normalized to units of standard 
		deviations of the null comparison.  Dotted horizontal lines indicate
		the 95\% confidence interval for the null comparison, which necessarily
		has zero relative specificity (see \textbf{Methods} 
		for an explanation of the null comparison).  Panels D, E, and F 
		represent relative specificity calculated using only culture-oriented
		labels, while panels G, H, and I using only food-oriented labels.
		Labels that are both culture- and food-oriented are excluded from the
		calculations for panels D through I.
		}
\end{figure}

\begin{figure}
	\includegraphics{figs/specificity-test0.pdf}
	\caption{Relative specificity of various treatments, for labels attributed
		to the first test image.
		Each panel shows the comparison between a basis treatment (inset) and 
		target treatments (abscissa).
		Bar heights indicate relative specificity of the target 
		treatment compared to the basis (a positive quantity means the target 
		is more specific), and are normalized to units of standard 
		deviations of the null comparison.  Dotted horizontal lines indicate
		the 95\% confidence interval for the null comparison, which necessarily
		has zero relative specificity (see \textbf{Methods} 
		for an explanation of the null comparison).  Panels D, E, and F 
		represent relative specificity calculated using only culture-oriented
		labels, while panels G, H, and I using only food-oriented labels.
		Labels that are both culture- and food-oriented are excluded from the
		calculations for panels D through I.
		}
	\end{figure}

\end{document}

### 2014-05-04 docs/draft/pnas1.tex
added pnas manuscript -- woops

%        File: pnas1.tex
%     Created: Wed Apr 30 04:00 pm 2014 E
% Last Change: Wed Apr 30 04:00 pm 2014 E
%
\documentclass[a4paper]{report}
\usepackage[hmargin=1in,vmargin=1in]{geometry}

\usepackage{graphicx}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage{gensymb}
\usepackage{algorithm2e}
\usepackage{amsthm}

\newtheorem*{mydef}{Definition}

\usepackage{cite}

\usepackage{framed, color}
\usepackage{soul}
\usepackage[colorlinks=true, urlcolor=blue]{hyperref}

\newcommand{\td}[1]{{\color{blu}\hl{TODO: #1}}}

\definecolor{shadecolor}{rgb}{.93,.93,.93}
\definecolor{blu}{rgb}{0,0,1}
\setlength{\parindent}{0cm}
\setlength{\parskip}{4mm plus1mm minus1mm}

\title{The effects of priming in human computation}
\author{Edward Newel, Derek Ruths}

\parindent0pt \parskip8pt

\begin{document}
\maketitle
\section*{Abstract}
\section*{Significance Statement}
\section*{Introduction}

Platforms like Amazon Mechanical Turk (AMT) make it possible to submit 
batches of ``microtasks'' to a large pool of human workers, who do these 
tasks for fun and remuneration.  A typical task might be the flagging of
innapropriate images, something that people are still better at than 
computers.

AMT makes human cognition as fluid a
resource as compute cycles: it is available on demand in small units, with low 
transaction cost, from anywhere via the Internet. The result is that one can 
treat AMT like a compute cluster, and seemlessly integrate human and machine
intelligence in large-scale computations.

This development invites a new perspective on human cognition itself.  Authors 
have put forward the term HPU (Human Processing Unit) likening an AMT worker
to her machine equivalent, the CPU.  Thinking of people as networked 
processors is not new.  Allan Newell argued 
that a prime function human organizations, such as companies or 
governmental institutions, is actually information processing.

If we adopt this view, how do people differ from CPUs as processors?  
Common sense suggests a major difference is that people do not respond 
in a consistent way to given inputs.  Not only do people vary widely from 
one another, but they differ in time due to mood, level of alertness, and 
any number of other incidental factors. One expects this to be especially 
pronounced for high-level, ill-defined tasks---precisely those for which 
people are usually better-suited than computers.

Here we investigate an aspect of the variability of HPUs.  Specifically,
we look at how a person's output during a task is influenced by the completion
of earlier tasks.  In engineered systems, the phenomenon whereby a system's 
output depends not only on current inputs, but also on the history of inputs,
is called \textit{hysteresis}.  Thus, we investigate the hysteretic aspect
of HPUs.
\td{in psychology this is called priming}

We test hysteresis by presenting AMT workers with
five images that depict food with strong cultural overtones, and ask them to
label each image with descriptive words.  Before the workers label the test
images, we expose them to different priming treatments.  We then observe 
whether and how this effects workers' labels, by looking at how
often workers make explicit cultural references, and how specific their labels 
are.

We induce priming in two ways.  The first way consists of presenting 
workers with different `priming images'.  The workers must also label these 
images, and from the worker's perspective no distinction is
made between the test and priming images.  We call this 
priming modality \textit{in-task priming}, because it attempts to measure the
effects that earlier parts of a task have on later ones.

All workers are exposed to 
one of three priming image sets.  The set that we call \textit{ambiguous},
consists of images of food chosen to avoid obvious connection to a 
specific culture.  One could liken this treatment to a control, hovewer, as
we discuss later, the notion of a control treatment in the context of a priming
experiment is problematic.  The two other priming image sets are 
\textit{ingredients}, consisting of images of separated ingredients, and 
\textit{culture}, consisting of images of overt and specific cultural 
activities which do not feature food.

The natural expectation is that workers
shown the cultural images would provide more culture-oriented labels than
either of the other two image sets.  In the case of the ingredients image set,
beyond encouraging food-oriented labels, one might expect focus be drawn to 
the \textit{constituents} of meals, eliciting labels of higher specificity than
for the ambiguous set.

The second way we induce priming is by presenting the workers with the name 
of a (fictitious) research funder.  Workers are shown either the funder name  
``The National Foundation for Nutritional Awarenes'' or ``The Global
Foundation for Cultural Recognition'', or else they are shown no name.  These 
names were
chosen with the intent of biasing the workers to produce, respectively, more
food- and culture-oriented labels.  We call the second priming method 
\textit{framing}.

Framing is intended to pesent a biasing factor somewhat resembling that which 
the double-blind experimental design tries to avoid.  One might expect that, 
given the overt nature of the funder names, which strongly imply a research
intent, framing should have a strong effect.  We include it as reference point,
for comparison to in-task priming.  This allows us
to ask whether altering the first half of the task can have as strong an 
influence as does revealing an intent-laden funder name.

By taking a computational approach to human cognition, likening priming to
hysteresis effects of physical systems, we gain traction on the notion of 
priming itself. An important aspect of our contribution is to suggest
an algorithmic definition of priming based on so-called 
\textit{classifier algorithms}.  This definition makes the notion of priming
rigorous, and provides a universal approach to detecting priming effects which
can be implemented without knowing what the nature of the effects are.

We present this definition in the next section.  Following, we present
our results together with discussion, and describe our methodology last.

\section*{Text}
\subsection*{An algorithmic definition of priming}
One difficulty with the notion of priming is that there appears to be no 
defensible notion of an ``unprimed state''.  Consider the ambiguous image set 
in our experiment.  Would we be better to include a treatment with no
priming images at all?  We argue that, in that case, one would mainly observe  
effects of \textit{primacy}.  
Further, a participant always enters the experiment in \textit{some} state of 
mind, depending on her exposures prior to the experiment, which cannot be 
known by the experimenter.  By including a priming exposure that is in some 
sense `neutral' for the purposes of an experiment, one at least makes the 
priming of participants more uniform.

Because there
can be no unprimed state, we define priming relatively, and speak of one
treatment being \textit{differently primed} from another.

Another factor that we must consider is that the effects of priming will
depend on the task presented to the participant.  Two priming treatments that
produce markedly different performance for one task might produce 
indistinguishable performance for a diffirent task.  Thus, we define priming
in relation to the task.

A final factor that we must consider is the fact that, even when priming 
treatments are taken into account, the performance of participants in a task 
will differ due to the natural variance between people.  There would appear to
be no hope of accounting for the myriad factors that drive this variance.  Thus
to be practical, priming must be defined in relation to populations, not
individuals.

With these considerations, we propose the following algorithmic definition of
priming:

\begin{mydef}
	Two populations of people $J$ and $K$ that produce respectively two 
	populations of outputs $\mathcal{J}$ and $\mathcal{K}$ in the completion
	of a task $\mathcal{T}$, are said to \emph{differ in priming by 
	a degree at least $\theta$}, if there exists an algorithm $\mathcal{A}$ 
	that can distinguish (classify)
	a person drawn uniformly from $J$ or $K$ based on the outputs $x$ of the 
	person during $\mathcal{T}$ with accuracy $\frac{1+\theta}{2}$.
	$\mathcal{A}$ receives as input $\mathcal{J}$, $\mathcal{K}$, and $x$,
	and must have a running time that is polynomial in the size of its input.
\end{mydef}

In the language of computer science, $\mathcal{A}$ is a classifier.  Thus,
intuitively, if there exists a classifier that can distinguish two populations,
then they are differently primed.

Other than providing the usual running time constraint on $\mathcal{A}$, we
leave it completely undefined.  This is intentional since we want the 
definition to depend on the inherent distinguishability of populations, and
restricting the basis of distinction would arbitrarily mask certain kinds of
distinctness.

One consequence of this choice is that empirical measures of $\theta$ always
represent lower bounds on the theoretical value appearing in the definition.
So, empirically demonstrating non-negligible $\theta$ establishes a priming 
difference of \textit{at least} $\theta$, but on measuring a negligible 
$\theta$, one might argue that $\theta$ is not really negligible, and rather 
that a bad choice of classifier was made.

In practice we do not expect any serious difficulty on choosing a classifier
and establishing a meaningful value of $\theta$.  One of the simplest 
classifier algoritms, the \textit{Naive Bayes classifier}, performs very 
nearly as well as the most sophisticated classifiers in nearly all 
applications.  Therefore, we submit $\theta_\text{NB}$, as determined by a 
Naive Bayes classifier, to be a general-purpose measure of priming difference.

\subsection*{Results}
\paragraph{All treatments were differently primed.}
We test for priming effects using our definition proposed in the introduction,
implemented with a Naive Bayes classifier.  \textbf{Figure 1} shows
the classifier performance in distinguishing between different pairs of 
treatments, when provided workers' labels for the test images.

The classifier distinguishes the various treatments from one another (pairwise)
with high accuracy, confirming that both priming modalities 
(in-task and framing) were effective.  It is perhaps not surprising that
a Naive Bayes classifier can distinguish treatments tending toward a different 
``orientation'', e.g. $\textsc{cult}_{img}$ and $\textsc{ingr}_{img}$
(\textbf{Fig. 1A}).
But it is remarkable that, based only on the labels provided for the five test 
images, the classifier can distinguish workers from treatments of the 
\textit{same} orientation, such as $\textsc{cult}_{img}$ and 
$\textsc{cult}_{fund, img}$, with high accuracy (\textbf{Fig. 1B}).

Next we look at the degree to which labels from individual test images reveal 
priming.  It would stand to reason that, as workers proceed through 
the test images, the effects of priming might be ``washed out''.  
\textbf{Figure 2} shows the
performance of the Naive Bayes classifier when using the labels workers provide
for particular images.  This does show that, as we look to later test images, 
the treatments' difference in priming, $\theta_\text{NB}$, declines.

\paragraph{Priming orients focus.} Having demonstrated differential 
priming, we investigate the \textit{nature} of the priming.  To this
end, we construct an ontology of all the labels produced by the workers
for the five test images.  The ontology is a directed acyclic graph of terms,
with directed edges drawn from abstractions toward instances.  For example,
our ontology contains the path \texttt{food} $\to$ \texttt{ingredients} $\to$ 
\texttt{vegetables} 
$\to$ \texttt{tomato}.  In general, each of these terms is a label that
occured in the corpus of labels provided, but in some cases we added 
an abstraction when it was missing, to connect the ontology.

At the root of the ontology are the abstract classes \texttt{activity}, 
\texttt{adjective}, \texttt{culture}, \texttt{food}, and \texttt{thing}.
By simply counting the number of labels descended from \texttt{culture}
and \texttt{food}, we can guage effects on the orientation of workers's focus
with respect to these concepts.

\textbf{Figure 3} plots the composition of labels (fraction of culture- and 
food-oriented labels) for different treatments and images.  In 
panel \textbf{A}, we can see that, before considering the effects of 
treatments, there is significant variance in the composition of the labels 
for different images due to inherent differences in their content.  For our 
purpose, we are interested in the differential of composition between 
different treatments.

In \textbf{Fig. 3B} we exhibit the composition of labels for the various 
treatments (aggregating together the labels for all images for a given 
treatment).  We can see that the treatments which expose workers to the
cultural image sets do elicit significantly more culture-oriented and fewer
food-oriented labels compared to the other treatments ($\alpha=0.05$).  It 
also apperas that all the $\textsc{ingr}_x$ treatments produce more 
food-oriented labels, but we cannot assert this at significance 
$\alpha = 0.05$.

The effect size, however, is somewhat small.  Since we observed that priming 
difference ``wears off'', it may be the case 
that aggregating label compositions for all images actually masks the effects. 
In \textbf{Fig. 3C}, we plot label compositions for only the first
image.  This reveals that, in labeling the first test image, workers in the
$\textsc{cult}_{img,x}$ were strongly influenced to favor culture- over 
food-oriented labels.  The effect was strong enough to essentially reverse 
the proportions of these labels compared to the other treatments.

We next inspect this effect longitudinally, that is, as a function of 
the test image.  To do so, we compute the ``excess cultural orientation'' 
($\Delta_{cult}$) of
the $\textsc{cult}_{img}$ relative to $\textsc{ambg}$ as follows: 
\begin{align}
	\Delta_{cult}(i) = \frac{1}{N}\left[ \sum_{w\in\textsc{cult}_{img}} \left(N_{w,cult}^{(i)} - N_{w,food}^{(i)}\right)
	- \sum_{w\in\textsc{ambg}} \left(N_{w,cult}^{(i)} - N_{w,food}^{(i)}\right)\right],
\end{align}
where $N_{w,cult}^{(i)}$ stands for the number of culture-oriented labels 
attributed by worker $w$ to image $i$, while $N_{w,food}^{(i)}$ similarly 
counts food-oriented labels, and $N$ is the total number of labels in a 
treatment (2500).  
Intuitively, this is intended to capture how much 
more culture-oriented $\textsc{cult}_{img}$ is than $\textsc{ambg}$.  
\textbf{Figure 4} plots $\Delta_{cult}$ as a function of test image, $i$. It
clearly shows the strong influence on the labels attributed to the first image,
but this effect immediately drops below statistically measureable levels, while
remaining always positive.

\paragraph{Priming affects attention to detail.} Using the ontology described
in the previous section, we compare treatments in their degree of specificity.
When comparing two labels $\ell_1$ and $\ell_2$ produced by different workers,
we say that $\ell_2$ is more specific than $\ell_1$ if there is a 
\textit{directed path} from $\ell_1$ to $\ell_2$.  If there is no directed path
between $\ell_1$ and $\ell_2$, then they are uncomparable.  As an example,
\texttt{tomato} is more specific than \texttt{food}, while \texttt{statue}
and \texttt{food} are uncomparable.

We can compare the bulk specificity of two treatments by taking a subsample
of workers from each, and the labels of the workers in one
subsample to each of those in the other.  In drawing this comparison, we only 
compare labels that were attributed to the same image.  Thus the relative 
specificity of two treatments can then be computed as:
\begin{align}
	S(\textsc{x},\textsc{y}) = 
		\sum_{i=1}^5 \; 
		\sum_{\ell\in \mathcal{L}(\textsc{x},i)} \;
		\sum_{m\in \mathcal{L}
		(\textsc{y},i)} \left(\mathbf{1}[\ell > m] 
		- \mathbf{1}[m>\ell]\right),
\end{align}
Where \textsc{x} and \textsc{y} are treatment subsamples,
$\mathcal{L}(\textsc{x},i)$ is the set of all labels produced by workers in 
$\textsc{x}$ for test image $i$, and $\mathbf{1}[\ell > m]$ evaluates to 1 if 
$\ell$ is more specific than $m$, and 0 otherwise.  \textbf{Figure 5} 
exhibits the results.

In panel \textbf{A}, we see that when we compare each of the treatments to
$\textsc{ambg}$, all treatments in which the non-ambiguous image set was 
displayed have \textit{lower} specificity (though not all at $\alpha=0.05$).  
In panels \textbf{D} and \textbf{G} we compare the same pairs of treatments, 
but restrict to words of culture- and food-orientation respectively (words
of both orientations are excluded).  These plots show that the relative lack of specificity is mainly attributable to food-oriented words.

Likewise, in panels \textbf{B}, and \textbf{C}, 
wherever we see significant differences in specificity, it turns out that
these differences appear to mainly be due to differences in food specificity,
as can be seen by comparing to panels \textbf{E}, \textbf{F}, \textbf{H}, and 
\textbf{I}.  In fact, looking to panels \textbf{D}, \textbf{E}, and \textbf{F},
there are no significant differences in cultural specificity to speak of.

\subsection*{Discussion}

\paragraph{In-task priming is strong.}  Perhaps the most unexpected result of 
this study is the finding that the in-task priming was more influential than
framing.  We expected that the funder names would provide an overt signal of 
intent behind the task, and so would be stronger than in-task priming which 
we expected would not signal intent.  Perhaps in applications where priming 
is a concern, a certain portion of the task should be devoted to  
``burn-in''.  During burn-in, the participant would acclimatize to the task, 
while the effects of stimuli preceeding the task are washed out.

\paragraph{The rate of priming wash-out depends on how it is measured}
Seeing that $\theta_\text{NB}$ declines as one proceeds through the test 
images (\textbf{Fig. 2}), one should ask whether this actually represents 
priming wash-out.  One might also attribute this to 
differences in the \textit{content} of the images.  Nevertheless, we can
certainly assert that the effects of priming detected by the classifier 
persisted through the labelling of all five test images.

It is interesting to compare this to the result in \textbf{Fig. 4}, which
shows that the effect of priming on \textit{orientation} (culture vs food) 
decays much more quickly than the overall effects detected by
the classifier.  We take this to be the result of the complex network of 
mechanisms likely to be at play in priming, wherein the orientation of focus
is one mechanism that is particularly fast-responding.

\paragraph{Priming effects can be subtle even when strong.}
Just as the classifier continues to detect priming difference between 
$\textsc{cult}_{img}$ and \textsc{ambg} after the first test image,
it is able to differentiate both $\textsc{cult}_{fund}$ and 
$\textsc{ingr}_{fund}$ from \textsc{ambg}, even though we find no significant
differences in label orientation or specificity.

Clearly, the effects of
priming, even when definitive, can be subtle. Adopting the classifier-based
definition of priming allows one to detect effecs even if they are subtle or
not of an expected nature.

\paragraph{Priming did not affect cultural specificity.}
It was quite surpising that the effects on workers' specificity was essentially
confined to food-oriented labels, and that we observed no significant movements
in cultural specificity.   This might simply reflect the different roles
played by food and culture in the human lexicon.  This seems plausible when we 
consider the vital role of food, and the known result that people are less
discerning of characteristics of ``outsiders''.

Even considering the above explanation, is surprising that 
$\textsc{cult}_{img,x}$ could be strongly influenced to produce more 
cultur-oriented labels, and yet not show increased 
specificity in their use of culture-oriented labels.  Since effects on 
label composition were only appreciable for the first test image 
(see \textbf{Fig. 4}), we also
performed the specificity analysis restricting to labels from the first
test image (see \textbf{Fig. S1}).  But even focusing on the first test image
shows no significant increase in cultural specificity for 
$\textsc{cult}_{img,x}$.  Thus, we observe that orientation of focus and 
label specificity do not necessarily.

\paragraph{Similarity drives nuance.}
We observed already that treatments primed with the 
culture or ingredients image sets have less specificity compared to 
\textsc{ambg}.  Actually, nearly all the difference in specificity
can be explained by how different a treatment's priming images are from the 
test images.

Recall that the ambigouous set featured prepared meals, and 
was very similar to the test set.  The ingredients set at least featured 
food, although as separate ingredients instead of prepared meals, while the
culture image set was very different from the test images, containing no food
at all.
Indeed, not only is it true for comparisons to \textsc{ambg}, but in all the 
comparisons between treatments, specificity is higher for the 
treatments shown the ambiguous set than those shown ingredients set, 
and higher for those shown the ingredients set than those shown the culture 
set.

An appealing explanation for 
this is the notion of \textit{negative priming}, wherin the participant
becomes desensitized to stimuli that do not seem salient.  According to this 
argument, workers who have been shown successive images of prepared meals 
would be much less inclined to provide generic terms such as \texttt{food} or 
\texttt{meal} since these terms would no longer seem significant in the 
context of their priming treatment.

This suggests that, in the serial image labelling task, the worker
does not seek labels that are appropriate descriptors for the image so much 
as labels that distinguish the images from others she has recently seen.
It would be interesting to investigate whether this manifests other 
categorization and labeling tasks.

\paragraph{Priming for better HPU performance.}
Thus, if one seeks very nuanced sorting or labeling from human workers, 
we recommend assembling the HPUs in a hierarchical fashion, with the 
HPUs at the top of the hierarchy performing coarse sorting (or labeling), 
splitting objects into streams to be handled by HPUs performing more nuanced 
work.  To implement this for an
image-labeling task, one could first serve the images for coarse labelling,
then cluster the images based on the labels and a language model, and then 
reserve the images, ensuring that each HPU operates on images from a single 
cluster.  The ``denser'' the image set in terms of coverage of certain
regions of ``content space'', the more one might gain through repeated 
clustering and labelling.

This exhibits an interesting difference between HPUs and CPUs.  In general,
whenever an aspect of a problem can be parallelized when employing CPUs, one
gains efficiency.  But in the case of HPUs, which are hysteretic, we see an 
example where one might lose efficiency through parallelization.

\subsection*{Conclusion}
We have demonstrated that in-task priming has a strong effect.  It is stronger
in its direct effects on orientation of focus and specificity than is 
disclosing a funder name that signals the intent of the study.  
Rather than being a nuisance, in-task priming might be exploited to improve
task output, for example, to drive more (or less) nuanced responses.

Although the nature of the effects of framing were difficult to trace
in this experiment, we nevertheless demonstrated that those effects exist
and are strong, using our algorithmic definition of priming.  This exhibits
one of the main advantages of this definition: the analyst need 
not understand the details of \textit{how} priming influences a task to 
quantify its effect.

We advocate the view of priming as a form of hysteresis.  The notion of 
hysteresis is already used in varied disciplines like physics, engineering,
and economics.  This view invites the use of insights already gained from 
other fields, and application-independant models, to help understand human 
cognition.

\section*{Acknowledgements}
\section*{References}

\section*{Figure Legends}
\paragraph{Figure 1.}
$F_1$ score and $\theta_\text{NB}$ for the various 
priming treatments, as measured using a Naive Bayes classifier. Each panel 
presents classifier performance results that indicate the difference in
priming between a basis 
treatment, indicated in the inset, and the other treatments, indicated on the
abscissa.

\paragraph{Figure 2.}
$F_1$ score and $\theta_\text{NB}$ for the classification of 
$\textsc{cult}_{img}$ and $\textsc{ingr}_{img}$ using a Naive Bayes 
classifier.  The classifier is provided only the labels attributed to
particular images as indicated on the abscissa.

\paragraph{Figure 3.}
Percent label composition (culture- vs food-oriented labels) for 
various images and treatments.  Panel A shows the composition of 
labels, aggregated over all treatments, as a function of test image.
Panel B shows the composition of labels, aggregated over all images, as
a function of treatment.  Panel C shows the composition of labels 
attributed to the first test image by various treatments.

\paragraph{Figure 4.}
Excess culture-oriented label composition in the labels provided
by $\textsc{cult}_{img}$ as compared to $\textsc{ambg}$, for various
test images (see \textbf{Eq. 1} for calculation).

\paragraph{Figure 5.}
Relative specificity of various treatments.
Each panel shows the comparison between a basis treatment (inset) and 
target treatments (abscissa).
Bar heights indicate relative specificity of the target 
treatment compared to the basis (a positive quantity means the target 
is more specific), and are normalized to units of standard 
deviations of the null comparison.  Dotted horizontal lines indicate
the 95\% confidence interval for the null comparison, which necessarily
has zero relative specificity (see \textbf{Methods} 
for an explanation of the null comparison).  Panels D, E, and F 
represent relative specificity calculated using only culture-oriented
labels, while panels G, H, and I using only food-oriented labels.
Labels that are both culture- and food-oriented are excluded from the
calculations for panels D through I.

\paragraph{Figure S1}
Relative specificity of various treatments, for labels attributed
to the first test image.
Each panel shows the comparison between a basis treatment (inset) and 
target treatments (abscissa).
Bar heights indicate relative specificity of the target 
treatment compared to the basis (a positive quantity means the target 
is more specific), and are normalized to units of standard 
deviations of the null comparison.  Dotted horizontal lines indicate
the 95\% confidence interval for the null comparison, which necessarily
has zero relative specificity (see \textbf{Methods} 
for an explanation of the null comparison).  Panels D, E, and F 
represent relative specificity calculated using only culture-oriented
labels, while panels G, H, and I using only food-oriented labels.
Labels that are both culture- and food-oriented are excluded from the
calculations for panels D through I.

\end{document}

### 2014-05-07 docs/draft/pnas1.tex
work on manuscript: rework intro, add refs

@@
 
-Platforms like Amazon Mechanical Turk (AMT) make it possible to submit 
-batches of ``microtasks'' to a large pool of human workers, who do these 
-tasks for fun and remuneration.  A typical task might be the flagging of
-innapropriate images, something that people are still better at than 
-computers.
+Microtask crowdsourcing platforms like Amazon Mechanical Turk (AMT) make it 
+possible to submit batches of small tasks to a large pool of human workers, 
+who do the tasks for fun and remuneration.  A typical task might be the 
+flagging of innapropriate images, something that people are still better at 
+than computers.
 
-AMT makes human cognition as fluid a
-resource as compute cycles: it is available on demand in small units, with low 
-transaction cost, from anywhere via the Internet. The result is that one can 
-treat AMT like a compute cluster, and seemlessly integrate human and machine
-intelligence in large-scale computations.
+Such platforms human cognition as fluid a resource as compute cycles: it is 
+available on demand in small units, with low transaction cost, from anywhere 
+via the Internet \footnote{\href{http://mturk.com}{http://mturk.com}}.  The 
+result is that one can treat AMT like a compute cluster, and seemlessly 
+integrate human and machine intelligence in large-scale computations.
 
-This development invites a new perspective on human cognition itself.  Authors 
-have put forward the term HPU (Human Processing Unit) likening an AMT worker
-to her machine equivalent, the CPU.  Thinking of people as networked 
-processors is not new.  Allan Newell argued 
-that a prime function human organizations, such as companies or 
-governmental institutions, is actually information processing.
+This development invites a new perspective on the role of human cognition 
+itself in technical systems.  Researchers have put forward the term HPU 
+(Human co-Processing Unit)\footnote{We acknowledge the irony of this term:
+the original meaning of `computer' was a person who performs computations,
+its reference to machines being a personification brought into usage some time
+after 1900}, viewing the introduction of 
+microtask represents a fundamentally new computing architecture, in the same
+way that the GPUs differ from CPUs \cite{5543192}.  Thinking of networked 
+people as computate systems is not new.  Working in operations research, Simon 
+and Newell held the primary activity of human organizations to be 
+computation\cite{Simon:1958fp}.
 
-If we adopt this view, how do people differ from CPUs as processors?  
-Common sense suggests a major difference is that people do not respond 
-in a consistent way to given inputs.  Not only do people vary widely from 
-one another, but they differ in time due to mood, level of alertness, and 
-any number of other incidental factors. One expects this to be especially 
-pronounced for high-level, ill-defined tasks---precisely those for which 
-people are usually better-suited than computers.
+In adopting this view, we must contend with a stark difference between 
+people and CPUs: even when given the same instructions, people do not produce
+the same output.  In other words, one pays for the ``high level instructions 
+set'' of HPUs by accepting variability in outputs.
 
-Here we investigate an aspect of the variability of HPUs.  Specifically,
-we look at how a person's output during a task is influenced by the completion
-of earlier tasks.  In engineered systems, the phenomenon whereby a system's 
-output depends not only on current inputs, but also on the history of inputs,
-is called \textit{hysteresis}.  Thus, we investigate the hysteretic aspect
-of HPUs.
-\td{in psychology this is called priming}
+Variability raises a quality control issue. There have been many studies 
+into how user interface design, payments, social reputation schemes, and the 
+disclosure of the wider purpose of tasks affect worker outputs. We will 
+review the prior work in the section following this one.
+{\em Here, we report our investigation of worker {\em hysteresis}, that is, 
+the tendency of a worker's output during one task to be influenced by other 
+recently completed tasks}.
 
 We test hysteresis by presenting AMT workers with
-five images that depict food with strong cultural overtones, and ask them to
-label each image with descriptive words.  Before the workers label the test
-images, we expose them to different priming treatments.  We then observe 
-whether and how this effects workers' labels, by looking at how
-often workers make explicit cultural references, and how specific their labels 
-are.
+five images that depict meals with strong cultural overtones, and ask them to
+label each image with descriptive words.  Before presenting test images,
+we expose the workers to different priming treatments.  We observe how priming
+treatments effect the workers' subsequent choice of labels, by looking at 
+how specific the labels are in their meaning, and how often workers make 
+cultural references.
 
-We induce priming in two ways.  The first way consists of presenting 
-workers with different `priming images'.  The workers must also label these 
-images, and from the worker's perspective no distinction is
-made between the test and priming images.  We call this 
-priming modality \textit{in-task priming}, because it attempts to measure the
-effects that earlier parts of a task have on later ones.
+We employ two priming modalities in this study.  
+In the first modality, which we call \textit{in-task priming}, workers are 
+shown one of three sets of priming images.  The \textit{cultural}
+image set, \textbf{Fig. 2}, shows images chosen for their clear depiction of a 
+iconic cultural scene.  The \textit{ingredients} image set, \textbf{Fig. 3}, 
+shows separated food ingredients, as opposed to the prepared meals shown in 
+the test set, and avoids strong cultural signal.  The \textit{ambiguous} 
+image set contains images of prepared meals, similar to the test set, but 
+traces of cultural references are not prominent.  These images are shown right
+before the test images, and they must be labeled in the same way.  From the 
+workers' view-point there is no distinction between the priming and test 
+images.
 
-All workers are exposed to 
-one of three priming image sets.  The set that we call \textit{ambiguous},
-consists of images of food chosen to avoid obvious connection to a 
-specific culture.  One could liken this treatment to a control, hovewer, as
-we discuss later, the notion of a control treatment in the context of a priming
-experiment is problematic.  The two other priming image sets are 
-\textit{ingredients}, consisting of images of separated ingredients, and 
-\textit{culture}, consisting of images of overt and specific cultural 
-activities which do not feature food.
-
-The natural expectation is that workers
-shown the cultural images would provide more culture-oriented labels than
-either of the other two image sets.  In the case of the ingredients image set,
-beyond encouraging food-oriented labels, one might expect focus be drawn to 
-the \textit{constituents} of meals, eliciting labels of higher specificity than
-for the ambiguous set.
-
-The second way we induce priming is by presenting the workers with the name 
-of a (fictitious) research funder.  Workers are shown either the funder name  
+The second priming modality, which we call \textit{framing}, consists of
+presenting the workers with the name of a (fictitious) research funder before
+presenting any images to be labeled.  Workers are shown either the funder 
+name  
 ``The National Foundation for Nutritional Awarenes'' or ``The Global
 Foundation for Cultural Recognition'', or else they are shown no name.  These 
-names were
-chosen with the intent of biasing the workers to produce, respectively, more
-food- and culture-oriented labels.  We call the second priming method 
-\textit{framing}.
+names were chosen to signal interest, on the part of the requester, in the
+cultural or food-related aspects of the images.
 
-Framing is intended to pesent a biasing factor somewhat resembling that which 
-the double-blind experimental design tries to avoid.  One might expect that, 
-given the overt nature of the funder names, which strongly imply a research
-intent, framing should have a strong effect.  We include it as reference point,
-for comparison to in-task priming.  This allows us
-to ask whether altering the first half of the task can have as strong an 
-influence as does revealing an intent-laden funder name.
+Our primary interest lays in the hysteretic effects of in-task priming.  We
+include framing mainly as a point of comparison.  A defensible expectation is
+that the framing would produce a much stronger effect, because it clearly 
+signals the requester's interest in a specific aspect of image content. 
+Remarkably, with respect to the specificity of labels, and their content 
+(either food- or culture-orineted), in-task priming produces much stronger 
+effects.
 
-By taking a computational approach to human cognition, likening priming to
-hysteresis effects of physical systems, we gain traction on the notion of 
-priming itself. An important aspect of our contribution is to suggest
-an algorithmic definition of priming based on so-called 
-\textit{classifier algorithms}.  This definition makes the notion of priming
-rigorous, and provides a universal approach to detecting priming effects which
-can be implemented without knowing what the nature of the effects are.
+The measurement of priming effects, however, traditionally involves a prior
+assumption of what those effects will be.  At risk of circularity, but lacking
+alternatives, the definition of priming itself traditionally becomes 
+operationalized in terms of these effects\cite{}.  We seek to alleviate this 
+situation by providing an application-independant definition of priming 
+suitable for use in studying the computational properties of HPUs.
 
-We present this definition in the next section.  Following, we present
-our results together with discussion, and describe our methodology last.
+In the remainder of the introduction, we review prior work in human 
+computation and priming.  In the next section, \textbf{Analytical Framework},
+we introduce our definition of priming, before presenting our experimental 
+\textbf{Results}, \textbf{Discussion}, and \textbf{Conclusion}.  
+We present our \textbf{Methods} in detail at the end of the paper.
+
+\subsection*{Prior Work}
+- human computation pioneered by von Ahn and L Dabbish when they demonstrated
+	that images could be labeled by people via a game platform
+	\cite{von2004labeling}
+
+- Human computation is generally thought of in the context of crowdsourcing,
+	which implies soliciting work in the form of an open call to an 
+	unstructured pool of workers, general without any longterm engagement and 
+	limited ability to screen workers screening of workers. 
+	\cite{howe2008crowdsourcing}
+
+- As such, quality assurance has received a lot of attention.
+	- varying levels of attention and success \cite{kazai2013analysis}
+	- Widely varying reports on accuracy from very negative 
+	\cite{marsden2009crowdsourcing}, to positive 
+	\cite{alonso2009can, grady2010crowdsourcing}
+	- quality control \cite{lease2011quality}
+		o filtering 
+			- honeypots	\cite{snow2008cheap}
+		o averaging
+		- \cite{alonso2009can}, \cite{paolacci2010running}
+
+	- training \cite{le2010ensuring}
+
+	- prescreening, even for cultural effects
+		\cite{paolacci2010running}
+			- worker rep
+
+	- game theoretic treatments
+	- worker qualification 					  |	
+	- price									  | \cite{kazai2013analysis}
+	- task complexity						  |
+	- spam, variability, adversarial behavior |
+
+- effects of motivation
+	for fun does badly, for money does well
+	claimed expertize does badly
+	interest does better than boring, and boring performs faster, 
+	difficult does worse
+	pay 'ok' does best
+
+- studied effects of autonomy, skill use, and meaningfullness, in 
+- other studies study the effects of reputation and social standing
+- studied effect of giving workflow context\cite{Kinnaird2012281}
+- studied effects of task design (user interface): \cite{Finnerty2013}
+
+NOTES ON PRIMING
+- when shown an image, a person is better at recognizing the image in a 
+	tachistoscope up to 45 min later.\cite{BJOP:BJOP1796}
+	* the mechanisms are complex: showing an image of something that had the
+		same name also helps recognition, but being presented with a word and
+		reading it aloud does not
+
+- priming can be auditory(\cite{BJOP:BJOP1826}) or visual(\cite{BJOP:BJOP1796})
+
+- priming has been detected for words sharing morphemes 
+	(reflects vs reflecting) but not for semantically related words that such 
+	as held and holding.\cite{BJOP:BJOP1826}
+	- suggests stimulus encoding \cite{beller1971priming}\cite{BJOP:BJOP1826}
+	\cite{BJOP:BJOP1796} and memory access \cite{beller1971priming} priming 
+	effects exist.  Other studies provide definitive evidence that priming
+	leads to better application of object knowledge and top-down processes
+	\cite{Ghuman17062008}
+
+- existing work suggests that there are separble verbal- and image-based
+	semantic systems, as shown through studies of event-related brain 
+	potentials in response to high and low imageable words \cite{Swaab200299} 
+- priming is an effect whereby previous exposure to a stimulus leads to 
+	faster, more accurate responses to similar stimuli \cite{Ghuman17062008}, 
+	or lower response thresholds \cite{BJOP:BJOP1826}
 
@@
 \section*{References}
+\begingroup
+\renewcommand{\chapter}[2]{}
+\bibliography{newbib.bib}
+\endgroup
+\bibliographystyle{plain}
 

### 2014-05-07 docs/draft/pnas1.tex
finish reworking intro (pnas manuscript)

@@
 
-Such platforms human cognition as fluid a resource as compute cycles: it is 
-available on demand in small units, with low transaction cost, from anywhere 
+Such platforms render human cognition as fluid a resource as compute cycles: 
+it is available on demand in small units, with low transaction cost, from 
+anywhere 
 via the Internet \footnote{\href{http://mturk.com}{http://mturk.com}}.  The 
@@
 This development invites a new perspective on the role of human cognition 
-itself in technical systems.  Researchers have put forward the term HPU 
+in technical systems.  Researchers have put forward the term HPU 
 (Human co-Processing Unit)\footnote{We acknowledge the irony of this term:
 the original meaning of `computer' was a person who performs computations,
-its reference to machines being a personification brought into usage some time
-after 1900}, viewing the introduction of 
-microtask represents a fundamentally new computing architecture, in the same
-way that the GPUs differ from CPUs \cite{5543192}.  Thinking of networked 
-people as computate systems is not new.  Working in operations research, Simon 
-and Newell held the primary activity of human organizations to be 
+its reference to machines being a personification brought into usage in the 
+late 1800s\cite{Dictionary:hl}.}, viewing the introduction of 
+microtask platforms as a fundamentally new computing architecture
+\cite{5543192}.  Thinking of networked 
+people as compute systems is not new.  Working in operations research, Simon 
+and Newell viewed the primary activity of human organizations to be 
 computation\cite{Simon:1958fp}.
@@
 treatments effect the workers' subsequent choice of labels, by looking at 
-how specific the labels are in their meaning, and how often workers make 
+how specific the labels are, and how often workers make 
 cultural references.
@@
 shown one of three sets of priming images.  The \textit{cultural}
-image set, \textbf{Fig. 2}, shows images chosen for their clear depiction of a 
+image set, \textbf{Fig. 2}, shows images chosen for their clear depiction of an
 iconic cultural scene.  The \textit{ingredients} image set, \textbf{Fig. 3}, 
@@
 the test set, and avoids strong cultural signal.  The \textit{ambiguous} 
-image set contains images of prepared meals, similar to the test set, but 
-traces of cultural references are not prominent.  These images are shown right
+image set contains images of prepared meals, and is most similar to the test 
+set, but there are no prominent traces of cultural reference.  These images 
+are shown right
 before the test images, and they must be labeled in the same way.  From the 
@@
 
-The measurement of priming effects, however, traditionally involves a prior
-assumption of what those effects will be.  At risk of circularity, but lacking
-alternatives, the definition of priming itself traditionally becomes 
-operationalized in terms of these effects\cite{}.  We seek to alleviate this 
+However, to measure the effects of priming, one generally has to make an 
+assumption about what those effects will be.  At risk of circularity, the 
+definition of priming itself is traditionally operationalized in terms 
+of these effects \cite{}.  We seek to alleviate this 
 situation by providing an application-independant definition of priming 
-suitable for use in studying the computational properties of HPUs.
-
-In the remainder of the introduction, we review prior work in human 
-computation and priming.  In the next section, \textbf{Analytical Framework},
-we introduce our definition of priming, before presenting our experimental 
-\textbf{Results}, \textbf{Discussion}, and \textbf{Conclusion}.  
-We present our \textbf{Methods} in detail at the end of the paper.
+suitable for studying HPUs hysteresis.  We 
+present this definition following the section on prior work.
 

### 2014-05-08 docs/draft/pnas1.tex
finish prior work relating to amt quality studies

@@
 
-Variability raises a quality control issue. There have been many studies 
+Variability raises a quality control issue \cite{kazai2013analysis}. There 
+have been many studies 
 into how user interface design, payments, social reputation schemes, and the 
@@
 \subsection*{Prior Work}
-- human computation pioneered by von Ahn and L Dabbish when they demonstrated
-	that images could be labeled by people via a game platform
-	\cite{von2004labeling}
 
-- Human computation is generally thought of in the context of crowdsourcing,
-	which implies soliciting work in the form of an open call to an 
-	unstructured pool of workers, general without any longterm engagement and 
-	limited ability to screen workers screening of workers. 
-	\cite{howe2008crowdsourcing}
+The notion of human computation in its modern form is attributed to von Ahn 
+and L Dabbish for their demonstration of the \textit{ESP Game}, a system 
+through which people label images by trying to guess the labels given by 
+others \cite{von2004labeling}.  In this form, and on platforms like AMT,
+is a kind of Crowdsourcing.
 
-- As such, quality assurance has received a lot of attention.
-	- varying levels of attention and success \cite{kazai2013analysis}
-	- Widely varying reports on accuracy from very negative 
-	\cite{marsden2009crowdsourcing}, to positive 
-	\cite{alonso2009can, grady2010crowdsourcing}
-	- quality control \cite{lease2011quality}
-		o filtering 
-			- honeypots	\cite{snow2008cheap}
-		o averaging
-		- \cite{alonso2009can}, \cite{paolacci2010running}
+In crowdsourcing, an open call to is made an unstructured pool of workers 
+\cite{howe2008crowdsourcing}.  There is generally no long-term engagement 
+between worker and employer, and the ability 
+to screen workers (say, for expertise) is usually very limited 
+\cite{howe2008crowdsourcing}.  This raises its own quality issue 
+\cite{lease2011quality}, distinct from the effects of hysteresis.
 
-	- training \cite{le2010ensuring}
+Reports on the reliability of crowdsourced output using AMT vary from very
+bad \cite{marsden2009crowdsourcing} to quite good 
+\cite{alonso2009can, grady2010crowdsourcing}. Kazai et al find that 
+crowdsourced workers vary
+greatly in their levels of attentiveness and accuracy, and that this 
+variability in part depends on how interesting they find the task, whether they
+judge
+themselves to have expertise in the task domain, and whether they feel they
+are being paid enough \cite{kazai2013analysis}.  Interestingly, workers that
+indicated having expertise in the task were less likely to find it interesting,
+spent less time on the task, and did more poorly.
 
-	- prescreening, even for cultural effects
-		\cite{paolacci2010running}
-			- worker rep
+Generally, some portion of responses appear to be random probably because
+the worker is not bothering to actually perform the work as intended
+\cite{lease2011quality}(check).  By including honeypots (traps that workers who are
+catch workers who are not paying attention) such cheating can be screened out 
+to some degree \cite{snow2008cheap}, as can filtering out repsonses
+that have a very short completion time \cite{kazai2013analysis}.
 
-	- game theoretic treatments
-	- worker qualification 					  |	
-	- price									  | \cite{kazai2013analysis}
-	- task complexity						  |
-	- spam, variability, adversarial behavior |
+The above methods could be considered post-processing, but pre-screening 
+workers can be done as well. AMT provides the requester the ability to screen
+workers based on their history of accepted task completions. But Paolacci et al
+report good success in screening workers other attributes, even cultural ones
+\cite{paolacci2010running}.  Training workers is another straightforward way 
+to improve overall worker profficiency \cite{le2010ensuring}.
 
-- effects of motivation
-	for fun does badly, for money does well
-	claimed expertize does badly
-	interest does better than boring, and boring performs faster, 
-	difficult does worse
-	pay 'ok' does best
+Other researchers have investigated how motivation, context, framing, and 
+social factors affect worker performance.  Kazai et al found that workers 
+motivated by payment were more accurate \cite{kazai2013analysis}, especially
+if payment was neither too high nor too low.
+A carefully designed user interface also improves worker performance 
+\cite{Finnerty2013} as does telling the worker the wider workflow context that
+of which their task is a part \cite{Kinnaird2012281}. Chandler and Kapelner
+studied the effect of telling workers that their results would be used for
+medical research, and found that workers were more likely to participate, but
+did not provide more accurate work than when told nothing 
+\cite{chandler2013breaking}.
 
-- studied effects of autonomy, skill use, and meaningfullness, in 
-- other studies study the effects of reputation and social standing
-- studied effect of giving workflow context\cite{Kinnaird2012281}
-- studied effects of task design (user interface): \cite{Finnerty2013}
+Despite the wealth of research investigating the factors influencing 
+performance in crowdsourcing, we are unable to find any work showing the 
+effects of in-task priming as we have described it.  This is concerning 
+because, in the psychology literature, it is well known that priming can have 
+powerful effects especially for perceptual tasks related to recognizing 
+words, gender, and affect---precisely the types of tasks for which AMT is used
+\cite{yuen2011survey, snow2008cheap}.
 

### 2014-05-08 docs/draft/pnas1.tex
finish prior work section

@@
 because, in the psychology literature, it is well known that priming can have 
-powerful effects especially for perceptual tasks related to recognizing 
-words, gender, and affect---precisely the types of tasks for which AMT is used
-\cite{yuen2011survey, snow2008cheap}.
+powerful effects for perceptual tasks related to visual 
+recognition of objects \cite{BJOP:BJOP1796}, auditory recognition of words 
+\cite{BJOP:BJOP1826}, and the recognition
+of gender* and affect*.  These are, of course, precisely the types of tasks 
+for which AMT is used \cite{yuen2011survey, snow2008cheap}.
 
-NOTES ON PRIMING
-- when shown an image, a person is better at recognizing the image in a 
-	tachistoscope up to 45 min later.\cite{BJOP:BJOP1796}
-	* the mechanisms are complex: showing an image of something that had the
-		same name also helps recognition, but being presented with a word and
-		reading it aloud does not
+In psychology, priming is a phenomenon whereby previous exposure to a 
+stimulus leads to faster, or more accurate responses to similar stimuli 
+\cite{Ghuman17062008}, or to lower response thresholds \cite{BJOP:BJOP1826}.
+Priming works through various mechanisms.
 
-- priming can be auditory(\cite{BJOP:BJOP1826}) or visual(\cite{BJOP:BJOP1796})
+One mechanism appears to be 
+closely related to stimulus encoding \cite{BJOP:BJOP1826}.
+Participants are better able to recognize a word in a noisy background when 
+primed with a word that shares morphemes 
+(e.g. ``reflects'' and ``reflecting'').  However, priming 
+with a word that is semantically related, but does not share morphemes doesn't 
+help (e.g. ``held'' and ``holding'')\cite{BJOP:BJOP1826}.  Other studies seem
+to provide definitive evidence that priming leads to better 
+application of object knowledge and top-down processes \cite{Ghuman17062008},
+and can also act to facilitate memory access \cite{beller1971priming}.
 
-- priming has been detected for words sharing morphemes 
-	(reflects vs reflecting) but not for semantically related words that such 
-	as held and holding.\cite{BJOP:BJOP1826}
-	- suggests stimulus encoding \cite{beller1971priming}\cite{BJOP:BJOP1826}
-	\cite{BJOP:BJOP1796} and memory access \cite{beller1971priming} priming 
-	effects exist.  Other studies provide definitive evidence that priming
-	leads to better application of object knowledge and top-down processes
-	\cite{Ghuman17062008}
+But the the underlying mechanisms in priming
+can be exceedingly subtle \cite{BJOP:BJOP1796}.  As one expects exposing 
+participants to an image hels them subsequently recognise that 
+image when seen in a tachistoscope.  The researches demonstrated that priming 
+using an image that was visually different but of an object having the same 
+name also helped participants subsequently identify the image in the 
+tachistoscope.  But surprisingly, being presented with related word and 
+reading it aloud did not help.  On the basis of these 
+results, the researchers suggest the existence of a visual-semantic system,
+distinct from the linguistic one \cite{BJOP:BJOP1796}.
 
-- existing work suggests that there are separble verbal- and image-based
-	semantic systems, as shown through studies of event-related brain 
-	potentials in response to high and low imageable words \cite{Swaab200299} 
-- priming is an effect whereby previous exposure to a stimulus leads to 
-	faster, more accurate responses to similar stimuli \cite{Ghuman17062008}, 
-	or lower response thresholds \cite{BJOP:BJOP1826}
+Based on the compelling evidence for priming effects in task types often 
+employed on AMT, we hypothesize that workers' performance may be impacted
+by the very work they have recently performed.  However, we adapt the 
+operationalization of priming from one based on speed, accuracy, and 
+response threshold, to an algorithmic definition that makes no particular
+assumptions about the nature of priming effects.
 
@@
 
-Even considering the above explanation, is surprising that 
-$\textsc{cult}_{img,x}$ could be strongly influenced to produce more 
-cultur-oriented labels, and yet not show increased 
-specificity in their use of culture-oriented labels.  Since effects on 
+Another explanation is that food is more so-called \textit{imageable} than 
+culture, because although aspects of culture can be depicted in an image,
+culture itself cannot.  Studies show that the brain processes high- and 
+low-imageable words differently \cite{Swaab200299}, and it would not be 
+surprising if the effects of priming on image labeling were modulated by how 
+imageable the labels are.
+
+Even with the above explanations, is surprising that 
+$\textsc{cult}_{img,x}$ simultaneously could be strongly influenced to 
+produce a higher quantity of culture-oriented labels, and yet not a higher
+specificity of culture-oriented labels.  Since effects on 
 label composition were only appreciable for the first test image 

### 2014-05-08 docs/draft/figs.tex
add treatments table

@@
 \begin{document}
+\begin{table}[t]
+\centering
+	\begin{tabular}{ l  l  l }
+		\hline                       
+		Treatment & Funder$^a$ & Priming Image Set	\\ 
+		\hline                       
+		$\textsc{ambg}$ & None & Ambiguous\\
+		$\textsc{cult}_{img}$ & None & Cultural\\
+		$\textsc{cult}_{fund}$ & Cultural & Cultural\\
+		$\textsc{cult}_{fund,img}$ & Cultural & Cultural\\
+		$\textsc{ingr}_{img}$ & None & Ingredients\\
+		$\textsc{ingr}_{fund}$ & Nutritional & Ingredients\\
+		$\textsc{ingr}_{fund, img}$ & Nutritional & Ingredients\\
+		\hline  
+	\end{tabular}
+
+%\begin{addmargin}[11em]{11em}
+%	\vspace{2mm}
+%	$^a$\footnotesize{The full funder names used were ``The Glodal Foundation
+%		for Cultural Recognition'' and ``The National Foundation for 
+%		Nutritional Awareness''.}
+%\end{addmargin}
+
+	\caption{Experimental treatments.  Workers were uniformly randomly
+		assigned to one of the treatments listed above.  The full funder 
+		names used were ``The Glodal Foundation
+		for Cultural Recognition'' and ``The National Foundation for 
+		Nutritional Awareness''.  The ambiguous, cultural, and ingredients 
+		priming images used are shown in \textbf{Figs. B}, \textbf{C}, and 
+		\textbf{D}.}
+	\label{table:1}
+\end{table}
+
 \begin{figure}

### 2014-05-08 docs/draft/pnas1.tex
add treatments table

@@
 \usepackage{soul}
-\usepackage[colorlinks=true, urlcolor=blue]{hyperref}
+\usepackage[colorlinks=false, urlcolor=blue]{hyperref}
 
@@
 We test hysteresis by presenting AMT workers with
-five images that depict meals with strong cultural overtones, and ask them to
+five images that depict meals with strong cultural overtones 
+(see \textbf{Fig. A}), and ask them to
 label each image with descriptive words.  Before presenting test images,
@@
 shown one of three sets of priming images.  The \textit{cultural}
-image set, \textbf{Fig. 2}, shows images chosen for their clear depiction of an
-iconic cultural scene.  The \textit{ingredients} image set, \textbf{Fig. 3}, 
+image set, \textbf{Fig. B}, shows images chosen for their clear depiction of an
+iconic cultural scene.  The \textit{ingredients} image set, \textbf{Fig. C}, 
 shows separated food ingredients, as opposed to the prepared meals shown in 
 the test set, and avoids strong cultural signal.  The \textit{ambiguous} 
-image set contains images of prepared meals, and is most similar to the test 
-set, but there are no prominent traces of cultural reference.  These images 
-are shown right
+image set contains images of prepared meals (\textbf{Fig D}), and is most 
+similar to the test set, but there are no prominent traces of cultural 
+reference.  These images are shown right
 before the test images, and they must be labeled in the same way.  From the 
@@
 cultural or food-related aspects of the images.
+
+We also test interaction effects between framing and in-task priming.  The
+various treatments are listed in \textbf{Table 1}.
 
@@
 name also helped participants subsequently identify the image in the 
-tachistoscope.  But surprisingly, being presented with related word and 
+tachistoscope.  Surprisingly, being presented with related word and 
 reading it aloud did not help.  On the basis of these 
@@
 \section*{Figure Legends}
+
+\paragraph{Table 1.}
+	Experimental treatments.  Workers were uniformly randomly
+	assigned to one of the treatments listed above.  The full funder 
+	names used were ``The Glodal Foundation
+	for Cultural Recognition'' and ``The National Foundation for 
+	Nutritional Awareness''.  The ambiguous, cultural, and ingredients 
+	priming images used are shown in \textbf{Figs. B}, \textbf{C}, and 
+	\textbf{D}.
+
+\paragraph{Figure A.}
+	Testing image set. These images were presented to all workers in the order 
+	shown after the priming set of images.
+
+\paragraph{Figure B.}
+	Ambiguous image set. These images were presented to workers from certain
+	treatements (see \textbf{Table 1}) in the order shown.
+
+\paragraph{Figure C.}
+	Cultural image set. These images were presented to workers from certain
+	treatements (see \textbf{Table 1}) in the order shown.
+
+\paragraph{Figure D.}
+	Ingredients image set. These images were presented to workers from certain
+	treatements (see \textbf{Table 1}) in the order shown.
+
 \paragraph{Figure 1.}

### 2014-05-11 docs/draft/pnas2.tex
changes to manuscript and specificity computation

--- 2014-05-08 docs/draft/pnas1.tex
@@
 possible to submit batches of small tasks to a large pool of human workers, 
-who do the tasks for fun and remuneration.  A typical task might be the 
-flagging of innapropriate images, something that people are still better at 
-than computers.
+who do the tasks for fun and remuneration.  Tasks involving qualitative
+judgment (e.g. flagging innapropriate images), natural language annotation,
+and object recognition are commonplace, since people still outperform  
+computers in these areas.
 
@@
 it is available on demand in small units, with low transaction cost, from 
-anywhere 
-via the Internet \footnote{\href{http://mturk.com}{http://mturk.com}}.  The 
-result is that one can treat AMT like a compute cluster, and seemlessly 
-integrate human and machine intelligence in large-scale computations.
+anywhere via the Internet \footnote{\href{http://mturk.com}{http://mturk.com}}.
+The task requestor can interact with the platform like a compute server, 
+seemlessly 
+integrating human and machine computation.  Researchers have put forward the 
+term HPU (Human co-Processing Unit)\footnote{We acknowledge the irony of this 
+term: the original meaning of `computer' was a person who performs 
+computations, its reference to machines being a personification brought into 
+usage in the late 1800s\cite{Dictionary:hl}.}, viewing the introduction of 
+microtask platforms as a fundamentally new computing architecture
+\cite{5543192}.
 
-This development invites a new perspective on the role of human cognition 
-in technical systems.  Researchers have put forward the term HPU 
-(Human co-Processing Unit)\footnote{We acknowledge the irony of this term:
-the original meaning of `computer' was a person who performs computations,
-its reference to machines being a personification brought into usage in the 
-late 1800s\cite{Dictionary:hl}.}, viewing the introduction of 
-microtask platforms as a fundamentally new computing architecture
-\cite{5543192}.  Thinking of networked 
-people as compute systems is not new.  Working in operations research, Simon 
-and Newell viewed the primary activity of human organizations to be 
-computation\cite{Simon:1958fp}.
+Originally used to distribute clerical work, these platforms 
+increasingly serve as a cheap and fast means to engage experimental 
+participants and provide qualitative annotations of datasets in a research 
+setting.  Given the limited ability to screen workers, and their transient 
+low-commitment engagement with the employer, researchers have criticised the
+reliability of crowdsourced output \cite{marsden2009crowdsourcing}.
 
-In adopting this view, we must contend with a stark difference between 
-people and CPUs: even when given the same instructions, people do not produce
-the same output.  In other words, one pays for the ``high level instructions 
-set'' of HPUs by accepting variability in outputs.
-
-Variability raises a quality control issue \cite{kazai2013analysis}. There 
-have been many studies 
-into how user interface design, payments, social reputation schemes, and the 
-disclosure of the wider purpose of tasks affect worker outputs. We will 
-review the prior work in the section following this one.
-{\em Here, we report our investigation of worker {\em hysteresis}, that is, 
-the tendency of a worker's output during one task to be influenced by other 
-recently completed tasks}.
-
-We test hysteresis by presenting AMT workers with
-five images that depict meals with strong cultural overtones 
-(see \textbf{Fig. A}), and ask them to
-label each image with descriptive words.  Before presenting test images,
-we expose the workers to different priming treatments.  We observe how priming
-treatments effect the workers' subsequent choice of labels, by looking at 
-how specific the labels are, and how often workers make 
-cultural references.
-
-We employ two priming modalities in this study.  
-In the first modality, which we call \textit{in-task priming}, workers are 
-shown one of three sets of priming images.  The \textit{cultural}
-image set, \textbf{Fig. B}, shows images chosen for their clear depiction of an
-iconic cultural scene.  The \textit{ingredients} image set, \textbf{Fig. C}, 
-shows separated food ingredients, as opposed to the prepared meals shown in 
-the test set, and avoids strong cultural signal.  The \textit{ambiguous} 
-image set contains images of prepared meals (\textbf{Fig D}), and is most 
-similar to the test set, but there are no prominent traces of cultural 
-reference.  These images are shown right
-before the test images, and they must be labeled in the same way.  From the 
-workers' view-point there is no distinction between the priming and test 
-images.
-
-The second priming modality, which we call \textit{framing}, consists of
-presenting the workers with the name of a (fictitious) research funder before
-presenting any images to be labeled.  Workers are shown either the funder 
-name  
-``The National Foundation for Nutritional Awarenes'' or ``The Global
-Foundation for Cultural Recognition'', or else they are shown no name.  These 
-names were chosen to signal interest, on the part of the requester, in the
-cultural or food-related aspects of the images.
-
-We also test interaction effects between framing and in-task priming.  The
-various treatments are listed in \textbf{Table 1}.
-
-Our primary interest lays in the hysteretic effects of in-task priming.  We
-include framing mainly as a point of comparison.  A defensible expectation is
-that the framing would produce a much stronger effect, because it clearly 
-signals the requester's interest in a specific aspect of image content. 
-Remarkably, with respect to the specificity of labels, and their content 
-(either food- or culture-orineted), in-task priming produces much stronger 
-effects.
-
-However, to measure the effects of priming, one generally has to make an 
-assumption about what those effects will be.  At risk of circularity, the 
-definition of priming itself is traditionally operationalized in terms 
-of these effects \cite{}.  We seek to alleviate this 
-situation by providing an application-independant definition of priming 
-suitable for studying HPUs hysteresis.  We 
-present this definition following the section on prior work.
-
-\subsection*{Prior Work}
-
-The notion of human computation in its modern form is attributed to von Ahn 
-and L Dabbish for their demonstration of the \textit{ESP Game}, a system 
-through which people label images by trying to guess the labels given by 
-others \cite{von2004labeling}.  In this form, and on platforms like AMT,
-is a kind of Crowdsourcing.
-
-In crowdsourcing, an open call to is made an unstructured pool of workers 
-\cite{howe2008crowdsourcing}.  There is generally no long-term engagement 
-between worker and employer, and the ability 
-to screen workers (say, for expertise) is usually very limited 
-\cite{howe2008crowdsourcing}.  This raises its own quality issue 
-\cite{lease2011quality}, distinct from the effects of hysteresis.
-
-Reports on the reliability of crowdsourced output using AMT vary from very
-bad \cite{marsden2009crowdsourcing} to quite good 
-\cite{alonso2009can, grady2010crowdsourcing}. Kazai et al find that 
-crowdsourced workers vary
-greatly in their levels of attentiveness and accuracy, and that this 
-variability in part depends on how interesting they find the task, whether they
-judge
-themselves to have expertise in the task domain, and whether they feel they
-are being paid enough \cite{kazai2013analysis}.  Interestingly, workers that
-indicated having expertise in the task were less likely to find it interesting,
-spent less time on the task, and did more poorly.
-
-Generally, some portion of responses appear to be random probably because
-the worker is not bothering to actually perform the work as intended
-\cite{lease2011quality}(check).  By including honeypots (traps that workers who are
-catch workers who are not paying attention) such cheating can be screened out 
-to some degree \cite{snow2008cheap}, as can filtering out repsonses
-that have a very short completion time \cite{kazai2013analysis}.
-
-The above methods could be considered post-processing, but pre-screening 
-workers can be done as well. AMT provides the requester the ability to screen
-workers based on their history of accepted task completions. But Paolacci et al
-report good success in screening workers other attributes, even cultural ones
-\cite{paolacci2010running}.  Training workers is another straightforward way 
-to improve overall worker profficiency \cite{le2010ensuring}.
-
-Other researchers have investigated how motivation, context, framing, and 
-social factors affect worker performance.  Kazai et al found that workers 
-motivated by payment were more accurate \cite{kazai2013analysis}, especially
-if payment was neither too high nor too low.
-A carefully designed user interface also improves worker performance 
-\cite{Finnerty2013} as does telling the worker the wider workflow context that
-of which their task is a part \cite{Kinnaird2012281}. Chandler and Kapelner
-studied the effect of telling workers that their results would be used for
-medical research, and found that workers were more likely to participate, but
-did not provide more accurate work than when told nothing 
+For 
+example, cheating
+is a problem \cite{lease2011quality}, but straightforward methods have been 
+developped to screen out cheaters \cite{snow2008cheap, kazai2013analysis}.
+Still, there is a great deal of variance in worker attention and 
+accuracy \cite{kazai2013analysis}.  Researchers have found many factors that 
+modulate worker performance, such as level of pay\cite{kazai2013analysis}, 
+training\cite{le2010ensuring}, pre-screening 
+workers\cite{paolacci2010running},  user-interface design
+\cite{Finnerty2013}, providing context for the task in the wider workflow
+\cite{Kinnaird2012281}, and disclosing the purpose of the task 
 \cite{chandler2013breaking}.
 
-Despite the wealth of research investigating the factors influencing 
-performance in crowdsourcing, we are unable to find any work showing the 
-effects of in-task priming as we have described it.  This is concerning 
-because, in the psychology literature, it is well known that priming can have 
-powerful effects for perceptual tasks related to visual 
-recognition of objects \cite{BJOP:BJOP1796}, auditory recognition of words 
-\cite{BJOP:BJOP1826}, and the recognition
-of gender* and affect*.  These are, of course, precisely the types of tasks 
-for which AMT is used \cite{yuen2011survey, snow2008cheap}.
+Here we are concerned with effects of a more subtle origin: the influence that
+prior tasks have on subsequent ones.  Psychology experiments document the 
+strong effects that a prior exposure to stimulus can have on participants' 
+performance in related tasks, a phenomenon known as \textit{priming}.  Strong 
+priming effects have been demonstrated for
+perceptual tasks such as the visual recognition of 
+objects \cite{BJOP:BJOP1796},
+auditory recognition of words \cite{BJOP:BJOP1826}, and the recognition
+of gender* and affect*: precisely the kinds of tasks well-served by microtask 
+platforms \cite{yuen2011survey, snow2008cheap}.
 
-In psychology, priming is a phenomenon whereby previous exposure to a 
-stimulus leads to faster, or more accurate responses to similar stimuli 
-\cite{Ghuman17062008}, or to lower response thresholds \cite{BJOP:BJOP1826}.
-Priming works through various mechanisms.
+Reserearchers 
+have investigated various effects due to \textit{framing}, at the outset of 
+the task.  But psychological experiments show that priming is strongest when 
+delivered through the same modality as the task.  This suggests that it might
+be more important to investigate the effects of priming that occurs 
+\textit{during} tasks.  We call such effects \textit{in-task priming}.  
+Whereas requestors can take measures to frame 
+their task as they see fit, in-task priming would be unavoidable in many 
+contexts, with consequences for the validity of microtask platforms as a 
+research tool.
 
-One mechanism appears to be 
-closely related to stimulus encoding \cite{BJOP:BJOP1826}.
-Participants are better able to recognize a word in a noisy background when 
-primed with a word that shares morphemes 
-(e.g. ``reflects'' and ``reflecting'').  However, priming 
-with a word that is semantically related, but does not share morphemes doesn't 
-help (e.g. ``held'' and ``holding'')\cite{BJOP:BJOP1826}.  Other studies seem
-to provide definitive evidence that priming leads to better 
-application of object knowledge and top-down processes \cite{Ghuman17062008},
-and can also act to facilitate memory access \cite{beller1971priming}.
+We investigate the effects of in-task priming on using an image-labeling task
+on the AMT platform.  Each worker is required to label a \textit{prior set} of
+images followed by a \textit{posterior set}, but no distinction is made between
+these sets from the perspective of the worker.  The posterior set is
+always the same, but workers are randomly assigned one of three prior sets.
+We analyze effects on the labels given to the the posterior set in terms of 
+what aspects the workers focus on (``orientation of labels''), and the degree 
+of specificity of the labels, both of direct consequence to the quality of 
+labeling and classification.
 
-But the the underlying mechanisms in priming
-can be exceedingly subtle \cite{BJOP:BJOP1796}.  As one expects exposing 
-participants to an image hels them subsequently recognise that 
-image when seen in a tachistoscope.  The researches demonstrated that priming 
-using an image that was visually different but of an object having the same 
-name also helped participants subsequently identify the image in the 
-tachistoscope.  Surprisingly, being presented with related word and 
-reading it aloud did not help.  On the basis of these 
-results, the researchers suggest the existence of a visual-semantic system,
-distinct from the linguistic one \cite{BJOP:BJOP1796}.
+As a point of comparison, we subject some groups of workers to a kind of
+framing, by disclosing a semantically-loaded (fictitious) name of the 
+funder of the research.  Remarkably, we find that in-task priming has a much 
+stronger effect
+on label orientation and specificity.  This has major implications for the 
+design of qualitative labeling and classification tasks.  Our results show that
+significant bias in worker labelling can be introduced by the progression of 
+tasks.  On the other hand, our results suggest the progression of tasks can 
+alse be used to tune workers to produce more nuanced output.
 
-Based on the compelling evidence for priming effects in task types often 
-employed on AMT, we hypothesize that workers' performance may be impacted
-by the very work they have recently performed.  However, we adapt the 
-operationalization of priming from one based on speed, accuracy, and 
-response threshold, to an algorithmic definition that makes no particular
-assumptions about the nature of priming effects.
+Traditionally, priming effects are
+measured using methods chosen to elucidate the underlying psychological 
+mechanisms.  For the human computation context, we seek general 
+methods that detect any hysteresis effects in HPUs, whatever they may be.  
+Here we present a novel general-purpose method for detecting priming, based on 
+a rigorous algorithmic definition. 
+This method provides a powerful new tool for detecting priming in populations
+without having to know anything about how the priming was carried out, nor the 
+effects that it might be expected to have.
+We demonstrate the utility of this method by showing that
+it can detect priming effects of all treatments in our experiment, even when 
+they fail to be detected through their effects on label orientation and 
+specificity. This method has the potential for a wide range of applications 
+outside computer science.
 
@@
 \subsection*{An algorithmic definition of priming}
+Motivate the need for this kind of instrumentalization.
+
 One difficulty with the notion of priming is that there appears to be no 
@@
 
+\subsection{Experimental Setup}
+We test hysteresis by presenting AMT workers with
+five images that depict meals with strong cultural overtones 
+(see \textbf{Fig. A}), and ask them to
+label each image with descriptive words.  Before presenting test images,
+we expose the workers to different priming treatments.  We observe how priming
+treatments effect the workers' subsequent choice of labels, by looking at 
+how specific the labels are, and how often workers make 
+cultural references.
+
+We employ two priming modalities in this study.  
+In the first modality, which we call \textit{in-task priming}, workers are 
+shown one of three sets of priming images.  The \textit{cultural}
+image set, \textbf{Fig. B}, shows images chosen for their clear depiction of an
+iconic cultural scene.  The \textit{ingredients} image set, \textbf{Fig. C}, 
+shows separated food ingredients, as opposed to the prepared meals shown in 
+the test set, and avoids strong cultural signal.  The \textit{ambiguous} 
+image set contains images of prepared meals (\textbf{Fig D}), and is most 
+similar to the test set, but there are no prominent traces of cultural 
+reference.  These images are shown right
+before the test images, and they must be labeled in the same way.  From the 
+workers' view-point there is no distinction between the priming and test 
+images.
+
+The second priming modality, which we call \textit{framing}, consists of
+presenting the workers with the name of a (fictitious) research funder before
+presenting any images to be labeled.  Workers are shown either the funder 
+name  
+``The National Foundation for Nutritional Awarenes'' or ``The Global
+Foundation for Cultural Recognition'', or else they are shown no name.  These 
+names were chosen to signal interest, on the part of the requester, in the
+cultural or food-related aspects of the images.
+
+We also test interaction effects between framing and in-task priming.  The
+various treatments are listed in \textbf{Table 1}.
+
 \subsection*{Results}
@@
 We test for priming effects using our definition proposed in the introduction,
-implemented with a Naive Bayes classifier.  \textbf{Figure 1} shows
+implemented with a Naive Bayes classifier.  \textbf{Figure 5} shows
 the classifier performance in distinguishing between different pairs of 
@@
 ``orientation'', e.g. $\textsc{cult}_{img}$ and $\textsc{ingr}_{img}$
-(\textbf{Fig. 1A}).
+(\textbf{Fig. 5A}).
 But it is remarkable that, based only on the labels provided for the five test 
@@
 \textit{same} orientation, such as $\textsc{cult}_{img}$ and 
-$\textsc{cult}_{fund, img}$, with high accuracy (\textbf{Fig. 1B}).
+$\textsc{cult}_{fund, img}$, with high accuracy (\textbf{Fig. 5B}).
 
@@
 the test images, the effects of priming might be ``washed out''.  
-\textbf{Figure 2} shows the
+\textbf{Figure 6} shows the
 performance of the Naive Bayes classifier when using the labels workers provide
@@
 
-\textbf{Figure 3} plots the composition of labels (fraction of culture- and 
+\textbf{Figure 7} plots the composition of labels (fraction of culture- and 
 food-oriented labels) for different treatments and images.  In 
@@
 
-In \textbf{Fig. 3B} we exhibit the composition of labels for the various 
+In \textbf{Fig. 7B} we exhibit the composition of labels for the various 
 treatments (aggregating together the labels for all images for a given 
@@
 that aggregating label compositions for all images actually masks the effects. 
-In \textbf{Fig. 3C}, we plot label compositions for only the first
+In \textbf{Fig. 7C}, we plot label compositions for only the first
 image.  This reveals that, in labeling the first test image, workers in the
@@
 more culture-oriented $\textsc{cult}_{img}$ is than $\textsc{ambg}$.  
-\textbf{Figure 4} plots $\Delta_{cult}$ as a function of test image, $i$. It
+\textbf{Figure 8} plots $\Delta_{cult}$ as a function of test image, $i$. It
 clearly shows the strong influence on the labels attributed to the first image,
@@
 $\textsc{x}$ for test image $i$, and $\mathbf{1}[\ell > m]$ evaluates to 1 if 
-$\ell$ is more specific than $m$, and 0 otherwise.  \textbf{Figure 5} 
+$\ell$ is more specific than $m$, and 0 otherwise.  \textbf{Figure 9} 
 exhibits the results.
@@
 Seeing that $\theta_\text{NB}$ declines as one proceeds through the test 
-images (\textbf{Fig. 2}), one should ask whether this actually represents 
+images (\textbf{Fig. 6}), one should ask whether this actually represents 
 priming wash-out.  One might also attribute this to 
@@
 
-It is interesting to compare this to the result in \textbf{Fig. 4}, which
+It is interesting to compare this to the result in \textbf{Fig. 8}, which
 shows that the effect of priming on \textit{orientation} (culture vs food) 
@@
 label composition were only appreciable for the first test image 
-(see \textbf{Fig. 4}), we also
+(see \textbf{Fig. 8}), we also
 performed the specificity analysis restricting to labels from the first
@@
 
-\paragraph{Figure 1.}
+\paragraph{Figure 5.}
 $F_1$ score and $\theta_\text{NB}$ for the various 
@@
 
-\paragraph{Figure 2.}
+\paragraph{Figure 6.}
 $F_1$ score and $\theta_\text{NB}$ for the classification of 
@@
 
-\paragraph{Figure 3.}
+\paragraph{Figure 7.}
 Percent label composition (culture- vs food-oriented labels) for 
@@
 
-\paragraph{Figure 4.}
+\paragraph{Figure 8.}
 Excess culture-oriented label composition in the labels provided
@@
 
-\paragraph{Figure 5.}
+\paragraph{Figure 9.}
 Relative specificity of various treatments.

### 2014-05-11 docs/publications/2014.05.9_pnas/figs.tex
changes to manuscript and specificity computation

--- 2014-05-08 docs/draft/figs.tex
@@
 		\hline                       
-		Treatment & Funder$^a$ & Priming Image Set	\\ 
+		Treatment & Funder & Priming Image Set	\\ 
 		\hline                       
@@
 
-	\caption{Experimental treatments.  Workers were uniformly randomly
-		assigned to one of the treatments listed above.  The full funder 
-		names used were ``The Glodal Foundation
-		for Cultural Recognition'' and ``The National Foundation for 
-		Nutritional Awareness''.  The ambiguous, cultural, and ingredients 
-		priming images used are shown in \textbf{Figs. B}, \textbf{C}, and 
-		\textbf{D}.}
+	\caption{Workers were uniformly randomly
+		assigned to one of the treatments listed above.}
 	\label{table:1}
@@
 \begin{figure}
-	\includegraphics{figs/f1-thetas.pdf}
+	\includegraphics[scale=1.00]{../figs/taskImages/testImages.png}
+	\caption{Testing image set. These images were presented to all workers in 
+		the order shown after the priming set of images.}
+\end{figure}
+
+\begin{figure}
+	\includegraphics[scale=1.00]{../figs/taskImages/ambiguous.png}
+	\caption{ Ambiguous image set. These images were presented to workers from 
+		certain treatements (see \textbf{Table 1}) in the order shown.}
+\end{figure}
+
+\begin{figure}
+	\includegraphics[scale=1.00]{../figs/taskImages/cultural.png}
+	\caption{Cultural image set. These images were presented to workers from 
+		certain treatements (see \textbf{Table 1}) in the order shown.}
+\end{figure}
+
+\begin{figure}
+	\includegraphics[scale=1.00]{../figs/taskImages/ingredients.png}
+	\caption{ Ingredients image set. These images were presented to workers 
+		from certain treatements (see \textbf{Table 1}) in the order shown.}
+\end{figure}
+
+\begin{figure}
+	\includegraphics{../figs/f1-thetas.pdf}
 	\caption{ $F_1$ score and $\theta_\text{NB}$ for the various 
@@
 \begin{figure}
-	\includegraphics{figs/longitudinalF1scores-t1-t2.pdf}
+	\includegraphics{../figs/longitudinalF1scores-t1-t2.pdf}
 	\caption{ $F_1$ score and $\theta_\text{NB}$ for the classification of 
@@
 \begin{figure}
-	\includegraphics{figs/orientationVsTreatment.pdf}
+	\includegraphics{../figs/orientationVsTreatment.pdf}
 	\caption{Percent label composition (culture- vs food-oriented labels) for 
@@
 \begin{figure}
-	\includegraphics{figs/excessCultureVsTreatment-t1.pdf}
+	\includegraphics{../figs/excessCultureVsTreatment-t1.pdf}
 	\caption{Excess culture-oriented label composition in the labels provided
@@
 \begin{figure}
-	\includegraphics{figs/specificity-allImages.pdf}
+	\includegraphics{../figs/specificity-allImages.pdf}
 	\caption{Relative specificity of various treatments.
@@
 \begin{figure}
-	\includegraphics{figs/specificity-test0.pdf}
+	\includegraphics{../figs/specificity-test0.pdf}
 	\caption{Relative specificity of various treatments, for labels attributed

### 2014-05-11 docs/publications/2014.05.9_pnas/pnas2.tex
changes to manuscript and specificity computation

--- 2014-05-11 docs/draft/pnas2.tex
@@
 
-\subsection{Experimental Setup}
-We test hysteresis by presenting AMT workers with
-five images that depict meals with strong cultural overtones 
-(see \textbf{Fig. A}), and ask them to
-label each image with descriptive words.  Before presenting test images,
-we expose the workers to different priming treatments.  We observe how priming
-treatments effect the workers' subsequent choice of labels, by looking at 
-how specific the labels are, and how often workers make 
-cultural references.
+\subsection*{Experimental Setup}
+AMT workers are randomly assigned to one of seven treatments 
+(see \textbf{Table 1}).  After brief instructions, workers are either
+shown a credit for the research funder, which can be either 
+``The Global foundation for Cultural Recognition'', or 
+``The National Foundation for Nutritional Awareness'', or else they are 
+immediately presented with a prior image set.
 
-We employ two priming modalities in this study.  
-In the first modality, which we call \textit{in-task priming}, workers are 
-shown one of three sets of priming images.  The \textit{cultural}
-image set, \textbf{Fig. B}, shows images chosen for their clear depiction of an
-iconic cultural scene.  The \textit{ingredients} image set, \textbf{Fig. C}, 
-shows separated food ingredients, as opposed to the prepared meals shown in 
-the test set, and avoids strong cultural signal.  The \textit{ambiguous} 
-image set contains images of prepared meals (\textbf{Fig D}), and is most 
-similar to the test set, but there are no prominent traces of cultural 
-reference.  These images are shown right
-before the test images, and they must be labeled in the same way.  From the 
-workers' view-point there is no distinction between the priming and test 
-images.
+The prior and posterior images sets both consist of five images. Each image 
+must be assigned labelled five labels.  For the posterior image set we chose 
+images that contain prepared meals and feature a prominent, iconic culture 
+(see \textbf{Fig. 1}).  These images provide a wide array of possible labels, 
+may focus on food, culture or both.
 
-The second priming modality, which we call \textit{framing}, consists of
-presenting the workers with the name of a (fictitious) research funder before
-presenting any images to be labeled.  Workers are shown either the funder 
-name  
-``The National Foundation for Nutritional Awarenes'' or ``The Global
-Foundation for Cultural Recognition'', or else they are shown no name.  These 
-names were chosen to signal interest, on the part of the requester, in the
-cultural or food-related aspects of the images.
-
-We also test interaction effects between framing and in-task priming.  The
-various treatments are listed in \textbf{Table 1}.
+One of the prior image sets, which we call \textit{ambiguous}, was chosen to
+be most similar to the posterior image set, and contains images of prepared
+meals, but whose cultural features are less prominent (see \textbf{Fig. 2}).  
+The \textit{cultural} set features iconic cultural scenes, and no food at all
+(see \textbf{Fig. 3}).  Finally, images from
+the \textit{ingredients} image set depict separated ingredients, having no
+prominent cultural aspects (see \textbf{Fig. 4}).  \textbf{Table 1} shows the 
+combinations of framing and in task priming that we used for each 
+experimental treatment.  See the \textbf{Materials and Methods} section for
+further details.
 
@@
 specificity of two treatments can then be computed as:
+
+We can compare the specificity of two workers by comparing, for each image,
+labels given by one worker with those of the other.  Thus, we define the the
+relative specificity of worker $u$ to worker $v$ to be $s(u,v)$:
+
 \begin{align}
-	S(\textsc{x},\textsc{y}) = 
-		\sum_{i=1}^5 \; 
-		\sum_{\ell\in \mathcal{L}(\textsc{x},i)} \;
-		\sum_{m\in \mathcal{L}
-		(\textsc{y},i)} \left(\mathbf{1}[\ell > m] 
-		- \mathbf{1}[m>\ell]\right),
+	s(u,v) = \sum_{i=1}^5 \;
+	\sum_{\ell \in u(i) } \;
+	\sum_{m \in v(i)} 
+	\left(\mathbf{1}[\ell > m] - \mathbf{1}[m>\ell]\right),
+	\label{eq:worker-specificity}
 \end{align}
+
+We can then calculate the relative specificity of two treatments to be the
+average relative specificity of workers drawn uniformly from the treatments.
+
+\begin{align}
+	S(U,V) = 
+		\frac{1}{|U \times V|}
+		\sum_{(u,v) \; \in \; U \times V} \;
+		s(u,v)
+		\label{eq:specificity}
+\end{align}
+
 Where \textsc{x} and \textsc{y} are treatment subsamples,
@@
 
+\subsection*{Materials and Methods}
+
+\textbf{AMT Tasks.} The task desicribed in the \textbf{Experimental Setup}
+section was served to 900 workers, who were uniformly randomly assigned to
+treatments.  All treatments had at least 134 task completions.  Workers were
+only allowed to participate once and could not see the prior or posterior 
+images when previewing the task.
+
+\textbf{Building the ontology of terms.}  The ontology was built by hand, 
+starting from the corpus of labels. Labels occuring only once were discarded.  
+We created the 
+root classes \texttt{activity}, \texttt{adjective}, \texttt{culture}, 
+\texttt{food}, and \texttt{thing}. \texttt{culture} and \texttt{food} were 
+given top-level status because they were prominently represented in the corpus.
+Some labels descend from both \texttt{food} and \texttt{cultural}  
+(e.g. \texttt{naan}), but there were also \texttt{food} labels that had no
+obvious cultural association (e.g. \texttt{bread}). Whenever one label 
+could be regarded as a more specific case of another, they were given a 
+child-parent relationship. In some cases missing abstract labels were added to 
+the ontology.  Labels which were roughly synonymous were treated as identical,
+and misspellings were handled the same way.
+
+\textbf{Assessing relative specificity.}
+We used \textbf{Eq.~\ref{eq:specificity}} to compute the relative specificity
+of two treatments.  To analyze this similarity measure statistically
+we define the specificity of a worker $u$ relative to a 
+\textit{basis treatment} $V$ as $S_V(u)$:
+\begin{align}
+S_V(u) = \frac{1}{|V|} \sum_{v \in V} s(u,v),
+\end{align}
+And rewrite the relative specificity of $U$ and $V$ as the expected value of
+$S_V(u)$ for workers in $U$:
+\begin{align}
+	S(U,V) &= E\{S_V(u)\}, \\
+	\text{with} \quad\quad \text{Var}\{S(U,V)\} 
+		&= \frac{\text{Var}\{S_V(u)\}}{|U|}.
+\end{align}
+To decide if $U$ is significantly more (less) specific than $V$, we do
+a null comparison of $V$ to itself: $S(V,V)$.  This value is in principle zero,
+but the comparison yields $\text{Var}\{S(V,V)\}$ which we use to state and 
+test the null hypothesis that $U$ and $V$ are equally specific:
+\begin{align}
+	\mathbf{H_0}: \quad S(U,V)-S(V,V)=0
+\end{align}
+Note that since $S(V,V)=0$, $\mathbf{H_0}$ essentially states that $S(U,V)=0$,
+however, it is more stringent since we consider variance due to sampling both
+$U$ and $V$:
+\begin{align}
+\text{Var}\{S(U,V) - S(V,V)\} &= \text{Var}\{S(U,V)\} + \text{Var}\{S(V,V)\}\\
+						&> \text{Var}\{S(U,V)\}
+\end{align}
+Therefore, we find $U$ to be significantly more (less) specific than $V$ when:
+\begin{align}
+z = \frac{S(U,V)}{ \sqrt{ \text{Var}\{S(U,V)\} + \text{Var}\{S(V,V)\} }} 
+	> 1.96.
+\end{align}
+
+Due to 
+computational intensity, we randomly subsampled 65 workers from each treatment.
+To compute the relative food- or culture-specificity, we alter the calculation
+in \textbf{Eq.~\ref{eq:worker-specificity}} by only including labels 
+respectively of food- or culture-orientation, while excluding all labels that
+aro both food- and culture-oriented.
+
 \section*{Acknowledgements}
@@
 
-\paragraph{Figure A.}
+\paragraph{Figure 1.}
 	Testing image set. These images were presented to all workers in the order 
@@
 
-\paragraph{Figure B.}
+\paragraph{Figure 2.}
 	Ambiguous image set. These images were presented to workers from certain
@@
 
-\paragraph{Figure C.}
+\paragraph{Figure 3.}
 	Cultural image set. These images were presented to workers from certain
@@
 
-\paragraph{Figure D.}
+\paragraph{Figure 4.}
 	Ingredients image set. These images were presented to workers from certain

### 2014-05-11 src/analysis.py

@@ -299,7 +299,6 @@ class Analyzer(object):
 		being compared) are averaged and reported as the comparison results.
 		'''
 
-
 		# If the two treatments are the same, randomly partition them so we
 		# don't get any overlaps.  Each entry is the output of one worker.
 		if treatment1 == treatment2:
@@ -330,9 +329,9 @@ class Analyzer(object):
 			util.writeNow('.')
 
 			# Counters that characterize i's comparison to all j entries
-			numFirstMoreSpecific = 0
-			numFirstLessSpecific = 0
-			numUncomparable = 0
+			subFirstMoreSpecificCounts = []
+			subFirstLessSpecificCounts = []
+			subUncomparableCounts = []
 
 			for j in range(len(entries2)):
 
@@ -344,13 +343,20 @@ class Analyzer(object):
 				lessSpec, moreSpec, uncomp = self.compareEntries(
 					entry1, entry2, images)
 
-				numUncomparable += uncomp
-				numFirstLessSpecific += lessSpec
-				numFirstMoreSpecific += moreSpec
+				# Record results for this comparison
+				subUncomparableCounts.append(uncomp)
+				subFirstLessSpecificcounts.append(lessSpec)
+				subFirstMoreSpecificCounts.append(moreSpec)
 				
+			# Compute and record results for all comparisons of ith worker
+			numFirstMoreSpecific = np.mean(subFirstMoreSpecificCounts
+			numFirstLessSpecific = np.mean(subFirstLessSpecificCounts
+			numUncomparable = np.mean(subUncomparableCounts)
+
 			firstMoreSpecificCounts.append(numFirstMoreSpecific)
 			firstLessSpecificCounts.append(numFirstLessSpecific)
-			firstMoreMinusLess.append(numFirstMoreSpecific - numFirstLessSpecific)
+			firstMoreMinusLess.append(
+				numFirstMoreSpecific - numFirstLessSpecific)
 			uncomparableCounts.append(numUncomparable)
 
 		print ''

### 2014-05-11 src/plots.py

@@ -200,16 +200,18 @@ def plotAllSpecificityComparisons(readFname='specificity/all.json',
 	fig.savefig(writeFname)
 	plt.show()
 
-def computeAllSpecificityComparisons(numToCompare=65):
+def computeAllSpecificityComparisons(sampleSize=134, nullSampleSize=67):
 
 	for image in ['test%d' % i for i in range(5)]:
 		computeSpecificityComparisons(
 			fname='specificity/%s.json' % image,
-			numToCompare=numToCompare, images=[image])
+			sampleSize=sampleSize, nullSampleSize=nullSampleSize,
+			images=[image])
 
 
 def computeSpecificityComparisons(
-	fname='specificity/all.json', numToCompare=50, images=['test0']):
+	fname='specificity/allImages.json', sampleSize=134, nullSampleSize=67, 
+	images=['test%d'%i for i in range(5)]):
 	'''
 	Computes all of the interesting specificity comparisons between different
 	treatments, such that they can be plotted  in a big multi-pannel figure.
@@ -255,7 +257,7 @@ def computeSpecificityComparisons(
 			# observed when comparing samples when they are both taken from 
 			# the basis treatment, and establishes confidence intervals
 			rslt = a.compareValenceSpecificity(
-				valence, basisTreatment, basisTreatment, numToCompare, 
+				valence, basisTreatment, basisTreatment, nullSampleSize, 
 				images)
 
 			nullComparison = {
@@ -273,7 +275,7 @@ def computeSpecificityComparisons(
 
 				# compare basis treatment to subject treatment
 				rslt = a.compareValenceSpecificity(
-					valence, subjectTreatment, basisTreatment, numToCompare,
+					valence, subjectTreatment, basisTreatment, sampleSize,
 					images)
 
 				# express the avg specificity in terms of the standard 
@@ -294,106 +296,6 @@ def computeSpecificityComparisons(
 
 	return results
 
-
-def plotSpecificityComparison(basisTreatment, treatmentsToBeCompared, 
-	numToCompare, fname, dimension='overall'):
-	'''
-	This is like plotAllSpecificityComparisons(), except that it only produces
-	one pannel.  I'm keeping it around because it may be fun to be able to
-	separate out these plots.
-	'''
-
[…]

### 2014-05-11 src/analysis.py
small change to analysis.py

@@ -345,12 +345,12 @@ class Analyzer(object):
 
 				# Record results for this comparison
 				subUncomparableCounts.append(uncomp)
-				subFirstLessSpecificcounts.append(lessSpec)
+				subFirstLessSpecificCounts.append(lessSpec)
 				subFirstMoreSpecificCounts.append(moreSpec)
 				
 			# Compute and record results for all comparisons of ith worker
-			numFirstMoreSpecific = np.mean(subFirstMoreSpecificCounts
-			numFirstLessSpecific = np.mean(subFirstLessSpecificCounts
+			numFirstMoreSpecific = np.mean(subFirstMoreSpecificCounts)
+			numFirstLessSpecific = np.mean(subFirstLessSpecificCounts)
 			numUncomparable = np.mean(subUncomparableCounts)
 
 			firstMoreSpecificCounts.append(numFirstMoreSpecific)

### 2014-05-12 src/plots.py
change default number of treatments for specificity

@@ -208,7 +208,7 @@ def plotAllSpecificityComparisons(readFname='specificity/all.json',
 	fig.savefig(writeFname)
 	plt.show()
 
-#def computeAllSpecificityComparisons(sampleSize=134, nullSampleSize=67):
+#def computeAllSpecificityComparisons(sampleSize=126, nullSampleSize=63):
 #
 #	for image in ['test%d' % i for i in range(5)]:
 #		computeSpecificityComparisons(
@@ -216,7 +216,7 @@ def plotAllSpecificityComparisons(readFname='specificity/all.json',
 #			sampleSize=sampleSize, nullSampleSize=nullSampleSize,
 #			images=[image])
 
-def computeAllSpecificities(sampleSize=134, nullSampleSize=67,
+def computeAllSpecificities(sampleSize=126, nullSampleSize=63,
 		images=['test%d'%i for i in range(5)] ):
 	valences = ['overall', 'cultural', 'food']
 
@@ -252,8 +252,8 @@ def computeSpecificity(
 	basis='treatment0', 
 	subjects=['treatment%d'%i for i in range(1,7)],
 	valence='overall',
-	sampleSize=134,
-	nullSampleSize=67,
+	sampleSize=126,
+	nullSampleSize=63,
 	images=['test%d'%i for i in range(5)]
 	):
 
@@ -330,7 +330,7 @@ def computeSpecificity(
 
 
 def computeSpecificityComparisons(
-	fname='specificity/allImages.json', sampleSize=134, nullSampleSize=67, 
+	fname='specificity/allImages.json', sampleSize=126, nullSampleSize=63, 
 	images=['test%d'%i for i in range(5)]):
 	'''
 	Computes all of the interesting specificity comparisons between different

### 2014-05-14 docs/publications/2014.05.9_pnas/pnas2.tex
change default number of treatments for specificity
manuscript draft 2 at before final touches

@@
 possible to submit batches of small tasks to a large pool of human workers, 
-who do the tasks for fun and remuneration.  Tasks involving qualitative
+who do the tasks for fun and remuneration \cite{kazai2013analysis}.  Tasks 
+involving qualitative
 judgment (e.g. flagging innapropriate images), natural language annotation,
 and object recognition are commonplace, since people still outperform  
-computers in these areas.
+computers in these areas \cite{yuen2011survey}.
 
@@
 participants and provide qualitative annotations of datasets in a research 
-setting.  Given the limited ability to screen workers, and their transient 
+setting \cite{snow2008cheap}.  Given the limited ability to screen workers, and their transient 
 low-commitment engagement with the employer, researchers have criticised the
@@
 
-For 
-example, cheating
+For one, cheating
 is a problem \cite{lease2011quality}, but straightforward methods have been 
@@
 training\cite{le2010ensuring}, pre-screening 
-workers\cite{paolacci2010running},  user-interface design
-\cite{Finnerty2013}, providing context for the task in the wider workflow
-\cite{Kinnaird2012281}, and disclosing the purpose of the task 
-\cite{chandler2013breaking}.
+workers\cite{paolacci2010running}, and user-interface design
+\cite{Finnerty2013}.
 
@@
 
-Reserearchers 
-have investigated various effects due to \textit{framing}, at the outset of 
-the task.  But psychological experiments show that priming is strongest when 
-delivered through the same modality as the task.  This suggests that it might
-be more important to investigate the effects of priming that occurs 
-\textit{during} tasks.  We call such effects \textit{in-task priming}.  
-Whereas requestors can take measures to frame 
-their task as they see fit, in-task priming would be unavoidable in many 
-contexts, with consequences for the validity of microtask platforms as a 
-research tool.
+In this direction, reserearchers have investigated various effects due to 
+\textit{framing}, by describing the larger workflow context in which the 
+workers task is a part \cite{Kinnaird2012281}, or by describing the ultimate 
+purpose of the project to provide meaning \cite{chandler2013breaking}.
+It is certainly of value to investigate this kind of priming, but 
+psychological experiments show that priming is strongest when 
+delivered through the same modality as the task [***].  This leads us to 
+investigate priming that occurs \textit{during} one task, influencing output
+of subsequent similar tasks. We call such effects \textit{in-task priming}.
 
@@
 always the same, but workers are randomly assigned one of three prior sets.
-We analyze effects on the labels given to the the posterior set in terms of 
-what aspects the workers focus on (``orientation of labels''), and the degree 
-of specificity of the labels, both of direct consequence to the quality of 
-labeling and classification.
+We analyze the labels workers attribute to the posterior set to see if it is 
+affected by the prior set.  We consider what aspects of image content the 
+workers choose to label (the \textit{label orientation}), and on how specific 
+the labels are (the \textit{label specificity}), both of which have direct 
+consequence on the validity of using human computation to make qualitative 
+judgments.
 
 As a point of comparison, we subject some groups of workers to a kind of
-framing, by disclosing a semantically-loaded (fictitious) name of the 
-funder of the research.  Remarkably, we find that in-task priming has a much 
-stronger effect
-on label orientation and specificity.  This has major implications for the 
-design of qualitative labeling and classification tasks.  Our results show that
-significant bias in worker labelling can be introduced by the progression of 
-tasks.  On the other hand, our results suggest the progression of tasks can 
-alse be used to tune workers to produce more nuanced output.
+framing: we disclose a fictitious, semantically-loaded name for the 
+task-requestor, chosen to signal an interest in a specific aspect of the 
+image content.  One might expect that this would strongly sway the labelling 
+of the workers.  We detect the effects of these priming treatments, but 
+remarkably, we find that in-task priming has a much stronger effect on label 
+orientation and specificity.
 
-Traditionally, priming effects are
-measured using methods chosen to elucidate the underlying psychological 
-mechanisms.  For the human computation context, we seek general 
-methods that detect any hysteresis effects in HPUs, whatever they may be.  
-Here we present a novel general-purpose method for detecting priming, based on 
-a rigorous algorithmic definition. 
-This method provides a powerful new tool for detecting priming in populations
-without having to know anything about how the priming was carried out, nor the 
-effects that it might be expected to have.
-We demonstrate the utility of this method by showing that
-it can detect priming effects of all treatments in our experiment, even when 
-they fail to be detected through their effects on label orientation and 
-specificity. This method has the potential for a wide range of applications 
+This has major implications for the design of qualitative labeling and 
+classification tasks.  Our results show that prior tasks can introduce 
+significant bias in subsequent worker labelling.  On the other hand, our 
+results suggest that the progression of tasks can alse be used to tune 
+workers to produce more nuanced output.
+
+In psychology, priming is defined as the effect in which a prior stimulus leads
+to faster or more accurate responses in a subsequent task than without the
+stimulus, or where the stimulus allows the experimenter to the elicit 
+responses from subsequent stimuli that are less intense or noisier [***].
+We are interested in studying the effects of priming in a human computation
+context, so we wish to adopt a more general view of priming as a kind of 
+HPU hysteresis.  In our view, priming might have many effects other than
+those normally measured.  We therefore require a more general definition and a 
+more general tool for quantifying priming, suited to detecting general 
+hysteresis effects.
+
+For this purpose, we present an algorithmic definition of priming that
+yields a powerful method for detecting priming without knowing ahead of time 
+what effects one is looking for.  We demonstrate that this tool is capable of 
+distinguishing the priming treatments in our experiment even when the 
+differences are subtle.  We expect such a tool will have wide applications 
 outside computer science.
 
-\section*{Text}
 \subsection*{An algorithmic definition of priming}
-Motivate the need for this kind of instrumentalization.
 
 One difficulty with the notion of priming is that there appears to be no 
-defensible notion of an ``unprimed state''.  Consider the ambiguous image set 
-in our experiment.  Would we be better to include a treatment with no
-priming images at all?  We argue that, in that case, one would mainly observe  
-effects of \textit{primacy}.  
-Further, a participant always enters the experiment in \textit{some} state of 
-mind, depending on her exposures prior to the experiment, which cannot be 
-known by the experimenter.  By including a priming exposure that is in some 
-sense `neutral' for the purposes of an experiment, one at least makes the 
-priming of participants more uniform.
+defensible notion of an ``unprimed state''.  A participant always approaches
+a task from in \textit{some} state of mind.  This will be influenced by her
+exposures prior to the experiment, which cannot be known by the experimenter.  
+In our experiment, for example, we include a prior image set that is in some
+sense ``neutral'', but it is by no means a control group. The particular 
+images used would arguably produce different priming from another set that
+was also apparently ``neutral''.
 
-Because there
-can be no unprimed state, we define priming relatively, and speak of one
+We avoid this difficulty by defining priming relatively, and speak of one
 treatment being \textit{differently primed} from another.
@@
 Another factor that we must consider is that the effects of priming will
-depend on the task presented to the participant.  Two priming treatments that
-produce markedly different performance for one task might produce 
-indistinguishable performance for a diffirent task.  Thus, we define priming
+manifest differently depending on the task that participants perform 
+subsequent to priming.  Said differently, two priming treatments that
+produce markedly different output for one task might be 
+indistinguishable under another task.  Thus, we define priming
 in relation to the task.
 
-A final factor that we must consider is the fact that, even when priming 
-treatments are taken into account, the performance of participants in a task 
-will differ due to the natural variance between people.  There would appear to
-be no hope of accounting for the myriad factors that drive this variance.  Thus
-to be practical, priming must be defined in relation to populations, not
-individuals.
+A final factor to consider is that, individuals who are in the same priming 
+treatment will still in general produce different output for a task
+due to the natural variance between people.  Therefore, we defined in relation 
+to populations, not individuals.
 
-With these considerations, we propose the following algorithmic definition of
-priming:
+With these considerations, we are ready to propose the definition.
+Consider two populations of people $\mathcal{J}$ and $\mathcal{K}$, that 
+produce respectively two populations of outputs 
+$\mathcal{L}$ and $\mathcal{M}$ during the completion of a task $\mathcal{T}$:
 
+\vspace{2mm}
 \begin{mydef}
-	Two populations of people $J$ and $K$ that produce respectively two 
-	populations of outputs $\mathcal{J}$ and $\mathcal{K}$ in the completion
-	of a task $\mathcal{T}$, are said to \emph{differ in priming by 
-	a degree at least $\theta$}, if there exists an algorithm $\mathcal{A}$ 
-	that can distinguish (classify)
-	a person drawn uniformly from $J$ or $K$ based on the outputs $x$ of the 
-	person during $\mathcal{T}$ with accuracy $\frac{1+\theta}{2}$.
-	$\mathcal{A}$ receives as input $\mathcal{J}$, $\mathcal{K}$, and $x$,
-	and must have a running time that is polynomial in the size of its input.
+	\upshape
+	$\mathcal{J}$ and $\mathcal{K}$ 
+	\emph{differ in priming by a degree at least $\theta$},
+	if there exists an algorithm $\mathcal{A}$ that takes as input 
+	$L \subset \mathcal{L}$ and $M \subset \mathcal{M}$ and the output 
+	$o$ of a person $p$ chosen with equal probability from either 
+	$\mathcal{J}\setminus J$ or $\mathcal{K}\setminus K$, 
+	such that $\mathcal{A}$ determines the set from which $p$ was drawn
+	($\mathcal{J}$ or $\mathcal{K}$) with accuracy $\frac{1+\theta}{2}$.  
 \end{mydef}
@@
 
-Other than providing the usual running time constraint on $\mathcal{A}$, we
-leave it completely undefined.  This is intentional since we want the 
-definition to depend on the inherent distinguishability of populations, and
-restricting the basis of distinction would arbitrarily mask certain kinds of
-distinctness.
+We leave the details of $\mathcal{A}$ unrestricted.  This is 
+intentional since we want the definition to depend on the inherent 
+potential for two populations to be distinguished, rather than on the 
+performance of a particular classifier.
 
-One consequence of this choice is that empirical measures of $\theta$ always
+A consequence of this choice is that empirical measures of $\theta$ always
 represent lower bounds on the theoretical value appearing in the definition.
-So, empirically demonstrating non-negligible $\theta$ establishes a priming 
-difference of \textit{at least} $\theta$, but on measuring a negligible 
-$\theta$, one might argue that $\theta$ is not really negligible, and rather 
-that a bad choice of classifier was made.
+As a result, a measured $\theta$ that is greater than zero directly 
+supports the conclusion that two populations are differently 
+primed, up to the statistical significance of the measurement.  However, if 
+$\theta$ is not found to be statistically different from zero, one cannot 
+directly
+conlude that two populations are the same in priming.  Rather, the definition
+admits the possibility that there exists some other $\mathcal{A}'$ capable of 
+generating a measure of $\theta$ greater than zero. Interpreting a result
+that $\mathcal{A}$ fails to achieve accuracy significantly better than 
+chance depends on the capabilities of $\mathcal{A}$ and the state of the art
+of classifier algorithms.
 
-In practice we do not expect any serious difficulty on choosing a classifier
+In practice we do not anticipate serious difficulty in choosing a classifier
 and establishing a meaningful value of $\theta$.  One of the simplest 
@@
 nearly as well as the most sophisticated classifiers in nearly all 
-applications.  Therefore, we submit $\theta_\text{NB}$, as determined by a 
-Naive Bayes classifier, to be a general-purpose measure of priming difference.
+applications [**].  Therefore, we submit $\theta_\text{NB}$, as determined by 
+a Naive Bayes classifier, to be a general-purpose measure of priming 
+difference.
 
 \subsection*{Experimental Setup}
-AMT workers are randomly assigned to one of seven treatments 
-(see \textbf{Table 1}).  After brief instructions, workers are either
-shown a credit for the research funder, which can be either 
+We solicited 900 AMT workers to perform an image labeling task.  The workers
+were randomly assigned to one of seven treatments shown in 
+\textbf{Table 1}.  Workers were first shown brief instructions.
+Depending on their treatment, they were then either shown the name of 
+a research funder followed by a prior image set, or they were immediately 
+shown a prior image set. When shown, the funder name was either
 ``The Global foundation for Cultural Recognition'', or 
-``The National Foundation for Nutritional Awareness'', or else they are 
-immediately presented with a prior image set.
+``The National Foundation for Nutritional Awareness''.  Finally, workers were 
+presented the posterior image set, which was the same for all treatments.
 
-The prior and posterior images sets both consist of five images. Each image 
-must be assigned labelled five labels.  For the posterior image set we chose 
-images that contain prepared meals and feature a prominent, iconic culture 
-(see \textbf{Fig. 1}).  These images provide a wide array of possible labels, 
-may focus on food, culture or both.
+The prior and posterior images sets both consist of five images. Workers had
+to provide five labels for each image.  For the posterior image set we chose 
+images that contain prepared meals and feature a prominent, identifiable 
+culture (see \textbf{Fig. 1}).  We intended that the content of these images 
+would tend elicit labels focusing food or culture (or both).
 
@@
 be most similar to the posterior image set, and contains images of prepared
-meals, but whose cultural features are less prominent (see \textbf{Fig. 2}).  
-The \textit{cultural} set features iconic cultural scenes, and no food at all
-(see \textbf{Fig. 3}).  Finally, images from
-the \textit{ingredients} image set depict separated ingredients, having no
-prominent cultural aspects (see \textbf{Fig. 4}).  \textbf{Table 1} shows the 
-combinations of framing and in task priming that we used for each 
-experimental treatment.  See the \textbf{Materials and Methods} section for
-further details.
+meals, but whose cultural features are less prominent and more difficult to
+identify (see \textbf{Fig. 2}).  
+The \textit{cultural} prior set features iconic cultural scenes, but no food 
+at all (see \textbf{Fig. 3}).  Finally, images from
+the \textit{ingredients} prior image set depict separated ingredients, but, 
+like the ambiguous set, did not have prominent cultural features (see 
+\textbf{Fig. 4}).  See the \textbf{Materials and Methods} section for further 
+details.
 
 \subsection*{Results}
-\paragraph{All treatments were differently primed.}
+\paragraph{The priming of all treatments was easily detectible.}
 We test for priming effects using our definition proposed in the introduction,
@@
 the classifier performance in distinguishing between different pairs of 
-treatments, when provided workers' labels for the test images.
+treatments based on workers' labels for the test images, and the corresponding
+value for $\theta_\text{NB}$.
 
@@
 with high accuracy, confirming that both priming modalities 
-(in-task and framing) were effective.  It is perhaps not surprising that
-a Naive Bayes classifier can distinguish treatments tending toward a different 
-``orientation'', e.g. $\textsc{cult}_{img}$ and $\textsc{ingr}_{img}$
-(\textbf{Fig. 5A}).
-But it is remarkable that, based only on the labels provided for the five test 
-images, the classifier can distinguish workers from treatments of the 
-\textit{same} orientation, such as $\textsc{cult}_{img}$ and 
-$\textsc{cult}_{fund, img}$, with high accuracy (\textbf{Fig. 5B}).
+(in-task and framing) were effective.  Remarkably, the classifier not only 
+distinguishes treatments tending toward a different ``orientations'' 
+(e.g. $\textsc{cult}_{img}$ and $\textsc{ingr}_{img}$, \textbf{Fig. 5A}), 
+it also distinguishes workers from treatments of the \textit{same} 
+orientation with high accuracy 
+(e.g. $\textsc{cult}_{img}$ and $\textsc{cult}_{fund, img}$, \textbf{Fig. 5B}).
+Clearly the algorithmic definition of priming and its implementation as 
+$\theta_\text{NB}$ provides a sensitive means for detecting the presence of
+primed populations.
 
@@
 for particular images.  This does show that, as we look to later test images, 
-the treatments' difference in priming, $\theta_\text{NB}$, declines.
+the treatments' difference in priming, $\theta_\text{NB}$, declines.  In future
+work, we plan to investigate the dynamics of priming wash-out in greater 
+detail.
 
@@
 priming, we investigate the \textit{nature} of the priming.  To this
-end, we construct an ontology of all the labels produced by the workers
-for the five test images.  The ontology is a directed acyclic graph of terms,
+end, we construct an ontology of all the labels attributed to
+the test images.  The ontology is a directed acyclic graph of terms,
 with directed edges drawn from abstractions toward instances.  For example,
@@
 occured in the corpus of labels provided, but in some cases we added 
-an abstraction when it was missing, to connect the ontology.
+an abstraction when it was missing, to connect the ontology.  We provide more
+detail about the construction of the ontology in the 
+\textbf{Materials and Methods} section.
 
-At the root of the ontology are the abstract classes \texttt{activity}, 
-\texttt{adjective}, \texttt{culture}, \texttt{food}, and \texttt{thing}.
-By simply counting the number of labels descended from \texttt{culture}
-and \texttt{food}, we can guage effects on the orientation of workers's focus
-with respect to these concepts.
+We put the abstract classes  \texttt{activity}, 
+\texttt{adjective}, \texttt{culture}, \texttt{food}, and \texttt{thing} at 
+the root of the ontology.  We promote \texttt{food} and \texttt{culture}
+to the root of the ontology simply because of the prominence of food and 
+culture-related labels in the corpus.  We acknowledge that food is a 
+central aspect of culture, but we do not put \texttt{food} \textit{under} 
+\texttt{culture}
+(nor vice versa) because there are food-related labels that are culturally 
+ambiguous (e.g. \texttt{bread}), and there are culture-related labels without 
+a direct connection to food (e.g. \texttt{ganesha}).  The many words that are 
+both food and culture-related (e.g. \texttt{dim sum}) receive an inbound edge 
+(or path) from both \texttt{food} and \texttt{culture}.
+This allows us to guage effects on the orientation of workers' focus
+with respect to the concepts of food and culture by simply counting the number 
+of labels they provide that descend from \texttt{food} and \texttt{culture}.
 
@@
 food-oriented labels) for different treatments and images.  In 
-panel \textbf{A}, we can see that, before considering the effects of 
+panel \textbf{7A}, we can see that, before considering the effects of 
 treatments, there is significant variance in the composition of the labels 
 for different images due to inherent differences in their content.  For our 
-purpose, we are interested in the differential of composition between 
-different treatments.
+purpose, we are interested in the systematic differences between 
+the treatments.
 
@@
 the proportions of these labels compared to the other treatments.  
+This shows that in-task priming effects can dramatically distort the results 
+of human computation tasks.
 
 We next inspect this effect longitudinally, that is, as a function of 
-the test image.  To do so, we compute the ``excess cultural orientation'' 
+the test image.  To do so, we compute the \textit{excess cultural orientation} 
 ($\Delta_{cult}$) of
-the $\textsc{cult}_{img}$ relative to $\textsc{ambg}$ as follows: 
+$\textsc{cult}_{img}$ relative to $\textsc{ambg}$ as follows: 
 \begin{align}
@@
 counts food-oriented labels, and $N$ is the total number of labels in a 
-treatment (2500).  
+treatment.  
 Intuitively, this is intended to capture how much 
@@
 clearly shows the strong influence on the labels attributed to the first image,
-but this effect immediately drops below statistically measureable levels, while
-remaining always positive.
+but for later images this effect immediately drops below statistically 
+measureable levels, while remaining always positive.
 
@@
 
-We can compare the bulk specificity of two treatments by taking a subsample
-of workers from each, and the labels of the workers in one
-subsample to each of those in the other.  In drawing this comparison, we only 
-compare labels that were attributed to the same image.  Thus the relative 
-specificity of two treatments can then be computed as:
-
 We can compare the specificity of two workers by comparing, for each image,
-labels given by one worker with those of the other.  Thus, we define the the
-relative specificity of worker $u$ to worker $v$ to be $s(u,v)$:
+the labels given by one worker with those of the other.  Thus, we define the
+specificity of worker $u$ relative to worker $v$ to be $s(u,v)$:
 
@@
 	\sum_{m \in v(i)} 
-	\left(\mathbf{1}[\ell > m] - \mathbf{1}[m>\ell]\right),
+	\left(\mathbf{1}_{[\ell > m]} - \mathbf{1}_{[m>\ell]}\right),
 	\label{eq:worker-specificity}
 \end{align}
+where $u(i)$ denotes the set of labels attributed by worker $u$ to image $i$, 
+and $\mathbf{1}_{[\ell > m]}$ evaluates to 1 if $\ell$ is more specific than 
+$m$, and 0 otherwise.
 
 We can then calculate the relative specificity of two treatments to be the
-average relative specificity of workers drawn uniformly from the treatments.
+average relative specificity of workers drawn uniformly from the treatments:
 
@@
 		\sum_{(u,v) \; \in \; U \times V} \;
-		s(u,v)
+		s(u,v),
 		\label{eq:specificity}
@@
 
-Where \textsc{x} and \textsc{y} are treatment subsamples,
-$\mathcal{L}(\textsc{x},i)$ is the set of all labels produced by workers in 
-$\textsc{x}$ for test image $i$, and $\mathbf{1}[\ell > m]$ evaluates to 1 if 
-$\ell$ is more specific than $m$, and 0 otherwise.  \textbf{Figure 9} 
+where $U$ and $V$ are treatments, taken as sets of workers. \textbf{Figure 9} 
 exhibits the results.
 
-In panel \textbf{A}, we see that when we compare each of the treatments to
-$\textsc{ambg}$, all treatments in which the non-ambiguous image set was 
+In panel \textbf{9A}, we see that when we compare each of the treatments to
+$\textsc{ambg}$, all treatments in which a non-ambiguous prior image set was 
 displayed have \textit{lower} specificity (though not all at $\alpha=0.05$).  
-In panels \textbf{D} and \textbf{G} we compare the same pairs of treatments, 
+In panels \textbf{9D} and \textbf{9G} we compare the same pairs of treatments, 
 but restrict to words of culture- and food-orientation respectively (words
-of both orientations are excluded).  These plots show that the relative lack of specificity is mainly attributable to food-oriented words.
+of both orientations are excluded).  These plots show that the relative lack 
+of specificity is mainly attributable to food-oriented words.
 
-Likewise, in panels \textbf{B}, and \textbf{C}, 
+Likewise, in panels \textbf{9B}, and \textbf{9C}, 
 wherever we see significant differences in specificity, it turns out that
 these differences appear to mainly be due to differences in food specificity,
-as can be seen by comparing to panels \textbf{E}, \textbf{F}, \textbf{H}, and 
-\textbf{I}.  In fact, looking to panels \textbf{D}, \textbf{E}, and \textbf{F},
+as can be seen by comparing to panels \textbf{9E}, \textbf{9F}, \textbf{9H}, 
+and \textbf{9I}.  In fact, looking to panels \textbf{9D}, \textbf{9E}, and 
+\textbf{9F},
 there are no significant differences in cultural specificity to speak of. 
+Clearly, food and culture are not on equal footing.  Various psychological 
+explanations are possible, and we explore these in the discussion below.
 
@@
 
-\paragraph{In-task priming is strong.}  Perhaps the most unexpected result of 
-this study is the finding that the in-task priming was more influential than
-framing.  We expected that the funder names would provide an overt signal of 
-intent behind the task, and so would be stronger than in-task priming which 
-we expected would not signal intent.  Perhaps in applications where priming 
-is a concern, a certain portion of the task should be devoted to  
-``burn-in''.  During burn-in, the participant would acclimatize to the task, 
-while the effects of stimuli preceeding the task are washed out.
+\paragraph{In-task priming is strong.}  We expected that the funder names 
+would overtly signal to workers that the requester was interested in a 
+specific aspect of image content.  On the other hand, the we did not 
+expect the prior image set, though enriched in certain content, to overtly signal interest.  In turn, we expected that a signal of intent would 
+strongly affect how the workers approach the task.  Perhaps the most unexpected
+result of this study is the finding that the prior image set influenced 
+workers' focus (label orientation) and specificity far more strongly than did 
+framing the task with the funder names.
+
+This points to a serious hazard in conducting studies using human computation,
+academic or otherwise: even if the requester has 
+eliminated surrounding influences to every practical extent, 
+\textit{the greatest source of bias might lurk in the task itself}.
+
+Randomized ordering and replication of tasks is one method to abate this issue.
+But the requester could also include an initial set of tasks as a 
+``tuning phase''.  During the tuning phase, workers would be primed in a 
+controlled way, through exposure to tasks that had been specially picked to
+orient worker focus in a useful manner.  Moreover, this phase could double as a
+screening phase to select quality workers [***].
 
@@
 priming wash-out.  One might also attribute this to 
-differences in the \textit{content} of the images.  Nevertheless, we can
-certainly assert that the effects of priming detected by the classifier 
-persisted through the labelling of all five test images.
+differences in the \textit{content} of the images. It is interesting to 
+compare this to the result in \textbf{Fig. 8}, which
+shows that the effect of exposure to the prior image set on 
+\textit{orientation} (culture vs food) certainly
+decays much more quickly than the overall effects detected by
+the classifier.  This appears to be consistent with the notion that the 
+mechanisms of priming are multiple and complex [***].  Here we again see an
+advantage of using $\theta_\text{NB}$ to measure priming: it is able to detect 
+differences in priming even after the expected effects have worn off.
 
-It is interesting to compare this to the result in \textbf{Fig. 8}, which
-shows that the effect of priming on \textit{orientation} (culture vs food) 
-decays much more quickly than the overall effects detected by
-the classifier.  We take this to be the result of the complex network of 
-mechanisms likely to be at play in priming, wherein the orientation of focus
-is one mechanism that is particularly fast-responding.
-
-\paragraph{Priming effects can be subtle even when strong.}
-Just as the classifier continues to detect priming difference between 
-$\textsc{cult}_{img}$ and \textsc{ambg} after the first test image,
-it is able to differentiate both $\textsc{cult}_{fund}$ and 
-$\textsc{ingr}_{fund}$ from \textsc{ambg}, even though we find no significant
-differences in label orientation or specificity.
-
-Clearly, the effects of
-priming, even when definitive, can be subtle. Adopting the classifier-based
-definition of priming allows one to detect effecs even if they are subtle or
-not of an expected nature.
+\paragraph{Subtle priming effects can be detected with $\theta_\text{NB}$.}
+While the Naive Bayes classifier is able to distinguish all treatment pairs,
+many such pairs cannot be distinguished on the basis of label orientation and 
+specificity 
+(for example $\textsc{cult}_{fund}$ and $\textsc{ingr}_{fund}$).
+One might expect, then, that $\theta_\text{NB}$
+for the pair $\textsc{cult}_{fund}$ and $\textsc{ingr}_{fund}$, would be 
+smaller than for, say, $\textsc{cult}_{img}$ and \textsc{ambg}.  
+\textbf{Figure 5A} shows that this is not the case.  Thus, priming can be 
+strong without generating the effects one might expect, and in many 
+circumstances, such effects might go entirely undetected.  We believe this 
+is a strong argument in support of using $\theta_\text{NB}$ to supplement 
+methods designed to measure specific priming effects.
 
@@
 confined to food-oriented labels, and that we observed no significant movements
-in cultural specificity.   This might simply reflect the different roles
+in cultural specificity.   This might reflect the different roles
 played by food and culture in the human lexicon.  This seems plausible when we 
-consider the vital role of food, and the known result that people are less
-discerning of characteristics of ``outsiders''.
+consider the vital role of food on the one hand, and the bias in social 
+cognition known as \textit{out-group homogeneity}\cite{Vala2012491,Ray2012387,Ishii2011159,Boldry2007157}.
+Out-group homogeneity is a phenomenon whereby people perceive fewer 
+differences between members of an outgroup than between members of their 
+ingroup \cite{Boldry2007157}.  One manifestation is that people 
+spend less time observing outgroup members when asked to make a character 
+judgment \cite{Vala2012491}.  This phenomenon can be explained in terms of 
+adaptiveness: social cognition regarding one's ingroup is more consequencial
+\cite{Vala2012491}.  Thus, it would not be surprising to find that people had 
+less nuanced vocabulary for culture than for food, where a nuanced vocabulary 
+would be of direct survival benefit.
 
@@
 Even with the above explanations, is surprising that 
-$\textsc{cult}_{img,x}$ simultaneously could be strongly influenced to 
-produce a higher quantity of culture-oriented labels, and yet not a higher
+$\textsc{cult}_{img,x}$ is simultaneously induced to 
+produce a higher quantity of culture-oriented labels but not a higher
 specificity of culture-oriented labels.  Since effects on 
@@
 shows no significant increase in cultural specificity for 
-$\textsc{cult}_{img,x}$.  Thus, we observe that orientation of focus and 
-label specificity do not necessarily.
+$\textsc{cult}_{img,x}$.  Thus, we observe that priming effects on 
+orientation of focus and label specificity do not necessarily correlate.
 
@@
 culture or ingredients image sets have less specificity compared to 
-\textsc{ambg}.  Actually, nearly all the difference in specificity
-can be explained by how different a treatment's priming images are from the 
-test images.
+\textsc{ambg}.  We will now argue that the difference in specificity
+can be explained by how ``similar'' a treatment's prior 
+images are to the posterior images. The characterization of the content of an 
+image is deeply complex, and has been approached from the perspectives of art\cite{panofsky1939studies,shatford1986analyzing},
+psychology\cite{Tversky1977327}, and information retrieval\cite{Jaimes20002}.  Here, we will take the simplistic 
+approach of defining the similarity between two sets of images as the number of
+labels in common between both sets.
 
-Recall that the ambigouous set featured prepared meals, and 
-was very similar to the test set.  The ingredients set at least featured 
-food, although as separate ingredients instead of prepared meals, while the
-culture image set was very different from the test images, containing no food
-at all.
-Indeed, not only is it true for comparisons to \textsc{ambg}, but in all the 
-comparisons between treatments, specificity is higher for the 
-treatments shown the ambiguous set than those shown ingredients set, 
-and higher for those shown the ingredients set than those shown the culture 
-set.
+\dots Results to follow \dots
 
+This matches the intuition that the ambiguous set is most similar to the 
+posterior set in that they both feature prepared meals, while the ingredients
+set is more similar to the posterior set than is the cultural set, since the
+ingredients set at least features food prominently.  Although similarity 
+between the cultural set and the posterior set could be argued on the basis
+of cultural content, this content is less imageable, more abstract, and
+and according to the theory of \cite{Jaimes20002} should require more 
+knowledge to acertain.
+
+Under our measure of similarity based on shared labels, our results show that
+more specific labels are provided to the posterior images when the prior and
+posterior image sets are more similar.
 An appealing explanation for 
 this is the notion of \textit{negative priming}, wherin the participant
-becomes desensitized to stimuli that do not seem salient.  According to this 
-argument, workers who have been shown successive images of prepared meals 
+becomes desensitized to stimuli that do not seem salient [***].  Thus, workers 
+who have been shown successive images of prepared meals 
 would be much less inclined to provide generic terms such as \texttt{food} or 
-\texttt{meal} since these terms would no longer seem significant in the 
+\texttt{meal} since these terms would no longer seem salient in the 
 context of their priming treatment.
-
-This suggests that, in the serial image labelling task, the worker
-does not seek labels that are appropriate descriptors for the image so much 
-as labels that distinguish the images from others she has recently seen.
-It would be interesting to investigate whether this manifests other 
-categorization and labeling tasks.
 
@@
 reserve the images, ensuring that each HPU operates on images from a single 
-cluster.  The ``denser'' the image set in terms of coverage of certain
-regions of ``content space'', the more one might gain through repeated 
-clustering and labelling.
+cluster.  The more homogeneous that a cluster of images is in terms of 
+content, the more one might gain by serving the cluster for another round of
+labeling.
 
@@
 whenever an aspect of a problem can be parallelized when employing CPUs, one
-gains efficiency.  But in the case of HPUs, which are hysteretic, we see an 
+gains efficiency.  But in the case of hysteretic HPUs, we see an 
 example where one might lose efficiency through parallelization.
@@
 \subsection*{Conclusion}
-We have demonstrated that in-task priming has a strong effect.  It is stronger
-in its direct effects on orientation of focus and specificity than is 
-disclosing a funder name that signals the intent of the study.  
-Rather than being a nuisance, in-task priming might be exploited to improve
-task output, for example, to drive more (or less) nuanced responses.
+We demonstrated that in-task priming can have a strong effect.  
+For an image labeling task, in-task priming was stronger in its effects on 
+the orientation and specificity of labels than was the disclosure of funder 
+names chosen to signal the requester's interest in specific content.
+Employers on microtask platforms should 
+beware that strong biases may be introduced by the very tasks they provide,
+and further research into the nature of these effects is warranted.  At the 
+same time, in-task priming might be exploited to improve task output, for 
+example, to drive more (or less) nuanced responses.
 
-Although the nature of the effects of framing were difficult to trace
-in this experiment, we nevertheless demonstrated that those effects exist
-and are strong, using our algorithmic definition of priming.  This exhibits
-one of the main advantages of this definition: the analyst need 
-not understand the details of \textit{how} priming influences a task to 
-quantify its effect.
-
-We advocate the view of priming as a form of hysteresis.  The notion of 
-hysteresis is already used in varied disciplines like physics, engineering,
-and economics.  This view invites the use of insights already gained from 
-other fields, and application-independant models, to help understand human 
-cognition.
+We demonstrated that our algorithmic definition of priming, and its 
+implementation as the measure $\theta_\text{NB}$ provide a sensitive,
+general-purpose method for detecting priming.  Even when the expected effects 
+on label orientation and specificity could not be detected, $\theta_\text{NB}$ 
+was high.  $\theta_\text{NB}$ provides direct statistical evidence that 
+populations have been affected by priming, even when the effects are not 
+understood. With our proposed definition, we advocate a more general view of 
+priming as a form of hysteresis.
 
@@
 
-\textbf{AMT Tasks.} The task desicribed in the \textbf{Experimental Setup}
+\textbf{AMT Tasks.} The task described in the \textbf{Experimental Setup}
 section was served to 900 workers, who were uniformly randomly assigned to
-treatments.  All treatments had at least 134 task completions.  Workers were
+treatments.  All treatments had at least 126 task completions.  To obtain 
+uniformly sized treatments, we randomly selected 126 samples from each 
+treatment. Workers were
 only allowed to participate once and could not see the prior or posterior 
-images when previewing the task.
+images, nor the funder names when previewing the task.
 
-\textbf{Building the ontology of terms.}  The ontology was built by hand, 
-starting from the corpus of labels. Labels occuring only once were discarded.  
-We created the 
-root classes \texttt{activity}, \texttt{adjective}, \texttt{culture}, 
+\textbf{Naive Bayes Classifier.}
+The features provided to the Naive Bayes classifier consisted of the labels
+that the worker provided along with the image and specific location in which 
+the label was entered
+(each image had five distinct label inputs).  Thus, \texttt{wine} ocurring in 
+position 1 of image 2 would be considered as a distinct feature from 
+\texttt{wine} occuring in position 2 of image 2. The classifier 
+had better performance when this distinction was made.
+
+\textbf{Building the ontology of terms.}  The ontology was built manually
+by the experimenters, starting from the corpus of labels. Labels occuring only 
+once were discarded.  We created the root classes \texttt{activity}, 
+\texttt{adjective}, \texttt{culture}, 
 \texttt{food}, and \texttt{thing}. \texttt{culture} and \texttt{food} were 
 given top-level status because they were prominently represented in the corpus.
-Some labels descend from both \texttt{food} and \texttt{cultural}  
-(e.g. \texttt{naan}), but there were also \texttt{food} labels that had no
-obvious cultural association (e.g. \texttt{bread}). Whenever one label 
-could be regarded as a more specific case of another, they were given a 
-child-parent relationship. In some cases missing abstract labels were added to 
-the ontology.  Labels which were roughly synonymous were treated as identical,
-and misspellings were handled the same way.
+Whenever one label was judged be regarded as a more specific case of another, a
+directed edge was drawn from the more general to the more specific. This was a 
+judgment call was made by the experimenters.  However, the labels from all 
+treatments were aggregated before assembling the ontology.  This was done to 
+ensure that the construction of the ontology would not be affected by 
+information about the treatments from which a label originated. 
+Labels which were judged to be roughly synonymous were treated as identical,
+and labels judged to be misspellings were corrected.
 
-\textbf{Assessing relative specificity.}
+\textbf{Statistical significance for relative specificity.}
 We used \textbf{Eq.~\ref{eq:specificity}} to compute the relative specificity
-of two treatments.  To analyze this similarity measure statistically
-we define the specificity of a worker $u$ relative to a 
-\textit{basis treatment} $V$ as $S_V(u)$:
+of two treatments.  To analyze relative specificity statistically,
+we first provide an equivalent rephrasing of \textbf{Eq.~\ref{eq:specificity}}.
+Let the specificity of a worker $u$ relative to a 
+\textit{basis treatment} $V$, denoted $S_V(u)$, be the expected relative 
+specificity between $u$ and a worker uniformly sampled from $V$:
+
 \begin{align}
-S_V(u) = \frac{1}{|V|} \sum_{v \in V} s(u,v),
+	S_V(u) =  \text{E}\{s(u,v)\}, \quad v \in_R V.
 \end{align}
+Then, the relative specificity of two treatmens, $S(U,V)$, can be defined as:
+\begin{align}
+	S(U,V) = \text{E}\{S_V(u)\} \quad u \in_R U.
+\end{align}
+
+We can estimate this using the sample mean calculated from our treatments:
+\begin{align}
+	\hat{S}_V(u) &= \frac{1}{|V|} \sum_{v \in V} s(u,v), \\
+	\hat{S}(U,V) &= \frac{1}{|U|} \sum_{u \in V} S_V(u), \\
+	\text{Var}\{\hat{S}_V(u)\} &= \frac{\text{Var}\{s(u,v)\}}{|V|},\\
+	\text{Var}\{\hat{S}(U,V)\} &= \sum_{u\in U}\text{Var}\{\hat{S}_V(u)\}
+\end{align}
+
 And rewrite the relative specificity of $U$ and $V$ as the expected value of
@@
 Due to 
-computational intensity, we randomly subsampled 65 workers from each treatment.
+computational intensity, we randomly subsampled 63 workers from each treatment.
 To compute the relative food- or culture-specificity, we alter the calculation

### 2014-05-14 docs/publications/2014.05.9_pnas/pnas2.tex
redo discussion of statistics

@@
 
-We can then calculate the relative specificity of two treatments to be the
-average relative specificity of workers drawn uniformly from the treatments:
+We can then define the relative specificity of two treatments, 
+$S(\mathcal{U},\mathcal{V})$ to be the average
+relative specificity of workers drawn uniformly from the treatments.  
+$\hat{S}({\mathcal{U}, \mathcal{V}})$ estimates this using the sample mean:
 
 \begin{align}
-	S(U,V) = 
-		\frac{1}{|U \times V|}
-		\sum_{(u,v) \; \in \; U \times V} \;
+	\hat{S}(\mathcal{U},\mathcal{V}) = 
+	\frac{1}{|\mathcal{U} \times \mathcal{V}|}
+	\sum_{(u,v) \; \in \; \mathcal{U} \times \mathcal{V}} \;
 		s(u,v),
@@
 
-where $U$ and $V$ are treatments, taken as sets of workers. \textbf{Figure 9} 
+where $\mathcal{U}$ and $\mathcal{V}$ are treatments, taken as sets of workers.
+See \textbf{Materials and Methods} for statistical analysis of the relative 
+specificity of two treatments. 
+\textbf{Figure 9} 
 exhibits the results.
@@
 given top-level status because they were prominently represented in the corpus.
-Whenever one label was judged be regarded as a more specific case of another, a
-directed edge was drawn from the more general to the more specific. This was a 
+Whenever one label was judged to be a more specific case of another, a
+directed edge was drawn from the more general to the more specific. This
 judgment call was made by the experimenters.  However, the labels from all 
-treatments were aggregated before assembling the ontology.  This was done to 
-ensure that the construction of the ontology would not be affected by 
-information about the treatments from which a label originated. 
+treatments were aggregated before assembling the ontology,  to 
+ensure that the ontology construction would not be affected by 
+knowledge of the treatments from which labels originated. 
 Labels which were judged to be roughly synonymous were treated as identical,
@@
 of two treatments.  To analyze relative specificity statistically,
-we first provide an equivalent rephrasing of \textbf{Eq.~\ref{eq:specificity}}.
-Let the specificity of a worker $u$ relative to a 
-\textit{basis treatment} $V$, denoted $S_V(u)$, be the expected relative 
-specificity between $u$ and a worker uniformly sampled from $V$:
+we first develop \textbf{Eq.~\ref{eq:specificity}} from an intermediate 
+definition.  Let the specificity of a worker $u$ relative to a 
+\textit{basis treatment} $\mathcal{V}$, denoted $S_V(u)$, to be the expected 
+relative specificity between $u$ and a worker uniformly sampled from 
+$\mathcal{V}$:
 
 \begin{align}
-	S_V(u) =  \text{E}\{s(u,v)\}, \quad v \in_R V.
+	S_V(u) =  \text{E}_V\{s(u,V)\}, \quad V \in_R \mathcal{V},
+		\label{eq:basis-specificity}
 \end{align}
-Then, the relative specificity of two treatmens, $S(U,V)$, can be defined as:
+where $V$ is a random, uniformly sampled worker from $\mathcal{V}$.  We 
+subscript the expectation operator with $V$ to indicate 
+that the expectation is taken over the distribution of $V$.  Then, the relative specificity of two treatmens, $S(\mathcal{U},{V})$, can be 
+written as:
 \begin{align}
-	S(U,V) = \text{E}\{S_V(u)\} \quad u \in_R U.
+	S(\mathcal{U},\mathcal{V}) = 
+		\text{E}_U\{S_V(U)\}, \quad U \in_R \mathcal{U},
+		\label{eq:treatment-specificity}
 \end{align}
+where $U$ is a uniformly sampled worker from $\mathcal{U}$.  This yields 
+estimators for $S_V(u)$ and $S(\mathcal{U}, \mathcal{V})$, and their variances
+as shown below (note that 
+\textbf{Eq.~\ref{eq:treatment-specificity-estimator}} is
+equivalent to \textbf{Eq.~\ref{eq:specificity}}):
 
-We can estimate this using the sample mean calculated from our treatments:
 \begin{align}
-	\hat{S}_V(u) &= \frac{1}{|V|} \sum_{v \in V} s(u,v), \\
-	\hat{S}(U,V) &= \frac{1}{|U|} \sum_{u \in V} S_V(u), \\
-	\text{Var}\{\hat{S}_V(u)\} &= \frac{\text{Var}\{s(u,v)\}}{|V|},\\
-	\text{Var}\{\hat{S}(U,V)\} &= \sum_{u\in U}\text{Var}\{\hat{S}_V(u)\}
+	\hat{S}_V(u) &= \frac{1}{|\mathcal{V}|} \sum_{v \in \mathcal{V}} s(u,v), 
+		\label{eq:basis-specificity-estimator} \\
+		\hat{S}(\mathcal{U},\mathcal{V}) 
+			&= \frac{1}{|\mathcal{U}|} \sum_{u \in \mathcal{V}} S_V(u),
+		\label{eq:treatment-specificity-estimator} \\
+		\text{Var}_V\{\hat{S}_V(u)\} 
+			&= \frac{1}{|\mathcal{V}|}\text{Var}_V\{s(u,V)\},
+		\label{eq:basis-specificity-variance} \\
+		\text{Var}_{U,V}\{\hat{S}(\mathcal{U},\mathcal{V})\} 
+			&= \frac{1}{|\mathcal{V}|\cdot|\mathcal{U}|^2} 
+			\sum_{u\in U}\text{Var}_V\{{s}(u,V)\}.
+		\label{eq:treatment-specificity-variance}
 \end{align}
-
-And rewrite the relative specificity of $U$ and $V$ as the expected value of
-$S_V(u)$ for workers in $U$:
+$\text{Var}_V{s(u,V)}$ can be directly calculated as a sample variance, so
+\textbf{Eq.~\ref{eq:basis-specificity-estimator}} through \textbf{\ref{eq:treatment-specificity-variance}} provide enough information to test the hypothesese:
 \begin{align}
-	S(U,V) &= E\{S_V(u)\}, \\
-	\text{with} \quad\quad \text{Var}\{S(U,V)\} 
-		&= \frac{\text{Var}\{S_V(u)\}}{|U|}.
+	\begin{matrix}
+		\mathbf{H_0}: S(\mathcal{U}, \mathcal{V}) = 0 \\[0.5em]
+		\mathbf{H_1}: S(\mathcal{U}, \mathcal{V}) \neq 0
+	\end{matrix}
 \end{align}
-To decide if $U$ is significantly more (less) specific than $V$, we do
-a null comparison of $V$ to itself: $S(V,V)$.  This value is in principle zero,
-but the comparison yields $\text{Var}\{S(V,V)\}$ which we use to state and 
-test the null hypothesis that $U$ and $V$ are equally specific:
-\begin{align}
-	\mathbf{H_0}: \quad S(U,V)-S(V,V)=0
-\end{align}
-Note that since $S(V,V)=0$, $\mathbf{H_0}$ essentially states that $S(U,V)=0$,
-however, it is more stringent since we consider variance due to sampling both
-$U$ and $V$:
-\begin{align}
-\text{Var}\{S(U,V) - S(V,V)\} &= \text{Var}\{S(U,V)\} + \text{Var}\{S(V,V)\}\\
-						&> \text{Var}\{S(U,V)\}
-\end{align}
-Therefore, we find $U$ to be significantly more (less) specific than $V$ when:
-\begin{align}
-z = \frac{S(U,V)}{ \sqrt{ \text{Var}\{S(U,V)\} + \text{Var}\{S(V,V)\} }} 
-	> 1.96.
-\end{align}
-
-Due to 
-computational intensity, we randomly subsampled 63 workers from each treatment.
-To compute the relative food- or culture-specificity, we alter the calculation
-in \textbf{Eq.~\ref{eq:worker-specificity}} by only including labels 
-respectively of food- or culture-orientation, while excluding all labels that
-aro both food- and culture-oriented.
 

### 2014-05-14 docs/publications/2014.05.9_pnas/pnas2.tex
spellcheck

@@
 involving qualitative
-judgment (e.g. flagging innapropriate images), natural language annotation,
+judgment (e.g. flagging inappropriate images), natural language annotation,
 and object recognition are commonplace, since people still outperform  
@@
 The task requestor can interact with the platform like a compute server, 
-seemlessly 
+seamlessly 
 integrating human and machine computation.  Researchers have put forward the 
@@
 setting \cite{snow2008cheap}.  Given the limited ability to screen workers, and their transient 
-low-commitment engagement with the employer, researchers have criticised the
+low-commitment engagement with the employer, researchers have criticized the
 reliability of crowdsourced output \cite{marsden2009crowdsourcing}.
@@
 is a problem \cite{lease2011quality}, but straightforward methods have been 
-developped to screen out cheaters \cite{snow2008cheap, kazai2013analysis}.
+developed to screen out cheaters \cite{snow2008cheap, kazai2013analysis}.
 Still, there is a great deal of variance in worker attention and 
@@
 
-In this direction, reserearchers have investigated various effects due to 
+In this direction, researchers have investigated various effects due to 
 \textit{framing}, by describing the larger workflow context in which the 
@@
 task-requestor, chosen to signal an interest in a specific aspect of the 
-image content.  One might expect that this would strongly sway the labelling 
+image content.  One might expect that this would strongly sway the labeling 
 of the workers.  We detect the effects of these priming treatments, but 
@@
 classification tasks.  Our results show that prior tasks can introduce 
-significant bias in subsequent worker labelling.  On the other hand, our 
-results suggest that the progression of tasks can alse be used to tune 
+significant bias in subsequent worker labeling.  On the other hand, our 
+results suggest that the progression of tasks can also be used to tune 
 workers to produce more nuanced output.
@@
 directly
-conlude that two populations are the same in priming.  Rather, the definition
+conclude that two populations are the same in priming.  Rather, the definition
 admits the possibility that there exists some other $\mathcal{A}'$ capable of 
@@
 and establishing a meaningful value of $\theta$.  One of the simplest 
-classifier algoritms, the \textit{Naive Bayes classifier}, performs very 
+classifier algorithms, the \textit{Naive Bayes classifier}, performs very 
 nearly as well as the most sophisticated classifiers in nearly all 
@@
 $\to$ \texttt{tomato}.  In general, each of these terms is a label that
-occured in the corpus of labels provided, but in some cases we added 
+occurred in the corpus of labels provided, but in some cases we added 
 an abstraction when it was missing, to connect the ontology.  We provide more
@@
 (or path) from both \texttt{food} and \texttt{culture}.
-This allows us to guage effects on the orientation of workers' focus
+This allows us to gauge effects on the orientation of workers' focus
 with respect to the concepts of food and culture by simply counting the number 
@@
 food-oriented labels compared to the other treatments ($\alpha=0.05$).  It 
-also apperas that all the $\textsc{ingr}_x$ treatments produce more 
+also appeas that all the $\textsc{ingr}_x$ treatments produce more 
 food-oriented labels, but we cannot assert this at significance 
@@
 \textit{directed path} from $\ell_1$ to $\ell_2$.  If there is no directed path
-between $\ell_1$ and $\ell_2$, then they are uncomparable.  As an example,
+between $\ell_1$ and $\ell_2$, then they are non-comparable.  As an example,
 \texttt{tomato} is more specific than \texttt{food}, while \texttt{statue}
-and \texttt{food} are uncomparable.
+and \texttt{food} are non-comparable.
 
@@
 shows that the effect of exposure to the prior image set on 
-\textit{orientation} (culture vs food) certainly
+\textit{orientation} (culture vs. food) certainly
 decays much more quickly than the overall effects detected by
@@
 \paragraph{Priming did not affect cultural specificity.}
-It was quite surpising that the effects on workers' specificity was essentially
+It was quite surprising that the effects on workers' specificity was 
+essentially
 confined to food-oriented labels, and that we observed no significant movements
@@
 judgment \cite{Vala2012491}.  This phenomenon can be explained in terms of 
-adaptiveness: social cognition regarding one's ingroup is more consequencial
+adaptiveness: social cognition regarding one's ingroup is more consequential
 \cite{Vala2012491}.  Thus, it would not be surprising to find that people had 
@@
 and according to the theory of \cite{Jaimes20002} should require more 
-knowledge to acertain.
+knowledge to ascertain.
 
@@
 An appealing explanation for 
-this is the notion of \textit{negative priming}, wherin the participant
+this is the notion of \textit{negative priming}, wherein the participant
 becomes desensitized to stimuli that do not seem salient [***].  Thus, workers 
@@
 work.  To implement this for an
-image-labeling task, one could first serve the images for coarse labelling,
+image-labeling task, one could first serve the images for coarse labeling,
 then cluster the images based on the labels and a language model, and then 
@@
 the label was entered
-(each image had five distinct label inputs).  Thus, \texttt{wine} ocurring in 
+(each image had five distinct label inputs).  Thus, \texttt{wine} occurring in 
 position 1 of image 2 would be considered as a distinct feature from 
-\texttt{wine} occuring in position 2 of image 2. The classifier 
+\texttt{wine} occurring in position 2 of image 2. The classifier 
 had better performance when this distinction was made.
@@
 \textbf{Building the ontology of terms.}  The ontology was built manually
-by the experimenters, starting from the corpus of labels. Labels occuring only 
+by the experimenters, starting from the corpus of labels. Labels occurring only 
 once were discarded.  We created the root classes \texttt{activity}, 
@@
 subscript the expectation operator with $V$ to indicate 
-that the expectation is taken over the distribution of $V$.  Then, the relative specificity of two treatmens, $S(\mathcal{U},{V})$, can be 
+that the expectation is taken over the distribution of $V$.  Then, the 
+relative specificity of two treatments, $S(\mathcal{U},{V})$, can be 
 written as:
@@
 $\text{Var}_V{s(u,V)}$ can be directly calculated as a sample variance, so
-\textbf{Eq.~\ref{eq:basis-specificity-estimator}} through \textbf{\ref{eq:treatment-specificity-variance}} provide enough information to test the hypothesese:
+\textbf{Eq.~\ref{eq:basis-specificity-estimator}} through \textbf{\ref{eq:treatment-specificity-variance}} provide enough information to test the hypotheses:
 \begin{align}
@@
 	assigned to one of the treatments listed above.  The full funder 
-	names used were ``The Glodal Foundation
+	names used were ``The Global Foundation
 	for Cultural Recognition'' and ``The National Foundation for 
@@
 	Ambiguous image set. These images were presented to workers from certain
-	treatements (see \textbf{Table 1}) in the order shown.
+	treatments (see \textbf{Table 1}) in the order shown.
 
@@
 	Cultural image set. These images were presented to workers from certain
-	treatements (see \textbf{Table 1}) in the order shown.
+	treatments (see \textbf{Table 1}) in the order shown.
 
@@
 	Ingredients image set. These images were presented to workers from certain
-	treatements (see \textbf{Table 1}) in the order shown.
+	treatments (see \textbf{Table 1}) in the order shown.
 

### 2014-05-14 docs/publications/2014.05.9_pnas/pnas2.tex
remove grammer mistakes and awk areas in intro

@@
 anywhere via the Internet \footnote{\href{http://mturk.com}{http://mturk.com}}.
-The task requestor can interact with the platform like a compute server, 
+The task requester can interact with the platform like a compute server, 
 seamlessly 
@@
 setting \cite{snow2008cheap}.  Given the limited ability to screen workers, and their transient 
-low-commitment engagement with the employer, researchers have criticized the
+low-commitment engagement with the requester, researchers have criticized the
 reliability of crowdsourced output \cite{marsden2009crowdsourcing}.
@@
 strong effects that a prior exposure to stimulus can have on participants' 
-performance in related tasks, a phenomenon known as \textit{priming}.  Strong 
+performance in related tasks, a phenomenon known as \textit{priming}[***].  
+Strong 
 priming effects have been demonstrated for
@@
 auditory recognition of words \cite{BJOP:BJOP1826}, and the recognition
-of gender* and affect*: precisely the kinds of tasks well-served by microtask 
-platforms \cite{yuen2011survey, snow2008cheap}.
+of gender[***] and affect[***]: precisely the kinds of tasks well-serviced by 
+microtask platforms \cite{yuen2011survey, snow2008cheap}.
 
-In this direction, researchers have investigated various effects due to 
-\textit{framing}, by describing the larger workflow context in which the 
-workers task is a part \cite{Kinnaird2012281}, or by describing the ultimate 
-purpose of the project to provide meaning \cite{chandler2013breaking}.
-It is certainly of value to investigate this kind of priming, but 
-psychological experiments show that priming is strongest when 
+In the direction of priming, researchers have investigated various effects 
+due to \textit{framing}, by disclosing to the worker the functional role of
+their task in the workflow context \cite{Kinnaird2012281}, 
+or describing a meaningful ultimate purpose of the project in which their
+task is a part \cite{chandler2013breaking}.
+However, psychological experiments show that priming is strongest when 
 delivered through the same modality as the task [***].  This leads us to 
-investigate priming that occurs \textit{during} one task, influencing output
+investigate how priming that occurs \textit{during} a task influences output
 of subsequent similar tasks. We call such effects \textit{in-task priming}.
 
-We investigate the effects of in-task priming on using an image-labeling task
+We investigate the effects of in-task priming for an image-labeling task
 on the AMT platform.  Each worker is required to label a \textit{prior set} of
@@
 We analyze the labels workers attribute to the posterior set to see if it is 
-affected by the prior set.  We consider what aspects of image content the 
-workers choose to label (the \textit{label orientation}), and on how specific 
-the labels are (the \textit{label specificity}), both of which have direct 
-consequence on the validity of using human computation to make qualitative 
-judgments.
+affected by the prior set.  As effects, we consider what aspects of image 
+content the workers choose to label (the \textit{label orientation}), and how 
+specific the labels are (the \textit{label specificity}), both of which have 
+direct consequence on the validity of using human computation to make 
+qualitative judgments.
 
@@
 framing: we disclose a fictitious, semantically-loaded name for the 
-task-requestor, chosen to signal an interest in a specific aspect of the 
+task-requester, chosen to signal an interest in a specific aspect of the 
 image content.  One might expect that this would strongly sway the labeling 
-of the workers.  We detect the effects of these priming treatments, but 
-remarkably, we find that in-task priming has a much stronger effect on label 
-orientation and specificity.
+of the workers.  We do detect the effects of framing, but, remarkably, we find 
+that in-task priming has a much stronger effect on label orientation and 
+specificity.
 
@@
 responses from subsequent stimuli that are less intense or noisier [***].
-We are interested in studying the effects of priming in a human computation
-context, so we wish to adopt a more general view of priming as a kind of 
-HPU hysteresis.  In our view, priming might have many effects other than
-those normally measured.  We therefore require a more general definition and a 
-more general tool for quantifying priming, suited to detecting general 
-hysteresis effects.
+However priming might have many effects other than those traditionally 
+measured.  We are interested in studying the effects of priming in a human 
+computation, we adopt a more general view of priming as HPU hysteresis.
 

### 2014-05-20 docs/publications/2014.04_HCOMP/draft2.tex
reorganize the project files

--- 2014-04-10 docs/draft/draft1.tex
@@
-\documentclass[letterpaper, 11pt, twocolumn]{article}
-\usepackage[margin=1in]{geometry}
-\setlength{\columnsep}{0.75cm}
+\documentclass[letterpaper]{article}
 
-\usepackage[font=footnotesize,labelfont=bf]{caption}
 \usepackage{fixltx2e}
-\usepackage{tikz}
-\usetikzlibrary{calc}
 \usepackage{algorithm2e}
-\usepackage{multirow}
 \usepackage{graphicx}
@@
 \usepackage{cite}
-\usepackage{framed, color}
-\usepackage{color, soul}
-\definecolor{shadecolor}{rgb}{.93,.93,.93}
-\definecolor{blu}{rgb}{0,0,1}
-\newcommand{\td}[1]{{\color{blu}\hl{TODO: #1}}}
-\newcommand{\vwm}{$V_{w,n,k}$}
-\newcommand{\wm}{$W_{w,n,k}$}
 \usepackage{amssymb}
@@
 \usepackage{gensymb}
+\usepackage{aaai} 
+\usepackage{times} 
+\usepackage{helvet} 
+\usepackage{courier} 
+\setlength{\pdfpagewidth}{8.5in} 
+\setlength{\pdfpageheight}{11in} %%%%%%%%%%
+% PDFINFO for PDFLATEX
+% Uncomment and complete the following for metadata (your paper must compile with PDFLATEX)
+\pdfinfo{
+}%%%%%%%%%%
+% Section Numbers
+% Uncomment if you want to use section numbers % and change the 0 to a 1 or 2
+% \setcounter{secnumdepth}{0} %%%%%%%%%%
+% Title, Author, and Address Information
 
-\title{Climate control for performant HPUs}
-\author{}
+%\title{Climate control for performant HPUs}
+\title{Hysteresis effects in image labelling}
+\author{Authors undisclosed}
 
-\parindent0pt \parskip8pt
+%%%%%%%%%%
+% Body of Paper Begins
 \begin{document}
@@
 
-\section*{Abstract}
+%\usepackage{multirow}
+
+\begin{abstract}
+	It is well known in psychology that priming can bias people toward giving
+	certain responses in a task.  We investigate to what extent this mechanism 
+	comes into play for workers performing image-labelling tasks on the
+	microtask platform Amazon Mechanical Turk.  
+	We first present an algorithmic definition of priming, and then apply this
+	definition to show that workers become primed simply by the previous 
+	tasks they have performed, in the sense that a classifier can reliably
+	infer the treatment from which a worker was drawn.
+	In an image labelling task, varying the images presented in earlier tasks, 
+	influences workers focus and specificity
+	and demonstrates that a combination of positive priming, negative priming,
+	and novelty contribute to the effects observed.
+	To obtain greater detail-orientation in the image labelling task, 
+	workers should be presented with
+	tasks that are as similar to one another as possible.
+\end{abstract}
 \textbf{}
 \section*{Introduction}
+
 Although capabilities in artificial intelligence continue to advance, 
 there are still many tasks for which human performance exceeds that of 
-computers now and in the forseable future.  Tasks requiring repertoire of 
+computers now and in the forseeable future.  Tasks requiring repertoire of 
 general knowledge about the world, the use of common sense or expert judgment, 
@@
 the human processing unit (HPU) becomes one component in a hybrid 
-computational system, analagous to the CPU.
+computational system, analogous to the CPU \cite{5543192}.
 
 But there are major challenges in building systems that deliver on this 
-vision.  People are far more complex than manufactured chips, 
+vision\cite{kittur2008crowdsourcing}.  People are far more complex than manufactured chips, 
 and so HPU performance is noisy, and subject to bias, leading to uncertain
@@
 will depend on the application.
-In the image labelling task, some variability is desireable, because it helps
+In the image labelling task, some variability is desirable, because it helps
 generate sets of labels that in some sense cover semantic space occupied by an 
@@
 
-Regardless of the application, the understanding HPU variance quantititively,
+Regardless of the application, the understanding HPU variance quantitatively,
 and the factors that influence it, will help design of efficient compute 
@@
 attention is influenced by the previous task, and how do these relate 
-quantititively to other pre-task influences?
+quantitatively to other pre-task influences?
 
@@
 funding the research, or by altering the first few images presented to the
-workers.  Surpisingly, simply altering the first few images produces a much
+workers.  Surprisingly, simply altering the first few images produces a much
 stronger shift in subsequent labelling performance than does disclosing the 
@@
 current developmental stage.  Such characteristics cannot be influenced by
-the designer, but it may be possible to screen or at least characterise them 
+the designer, but it may be possible to screen or at least characterize them 
 to some extent.
@@
 In psychology, the phenomenon of priming occurs when a prior stimulus 
-makes a person more likely to respond to a task in a particular way.  The 
+makes a person more likely to respond to a task in a particular way
+\cite{schvaneveldt1973retrieval, No2007}.  The 
 phenomenon is well-studied, and is believed to follow perceptual, semantic,
@@
 Existing work on the effects of human input in crowdsourcing platforms has
-generally focused on effects arising from auxilliary information, which has
+generally focused on effects arising from auxiliary information, which has
 been added into the task setting, or which frames the task during its 
@@
 way influences both task quality and the willingness of workers to produce
-more output given a declining payment schedule \cite{chandler2013breaking}.
+more output given a declining payment schedule.
 Surprisingly, relative to a zero-context treatment, although workers who were
 told that there contributions would be used to help identify cancerous cells
-were willing to provide more work, their work was not of a sufficiencly higher
+were willing to provide more work, their work was not of a sufficiently higher
 quality.  The only effect on quality occered when workers were told that their
@@
 perceptual, semantic, and conceptual representations, we hypothesize that 
-\textit{in-task} priming could produce effects quantitively comparable to those
+\textit{in-task} priming could produce effects quantatively comparable to those
 produced by framing.
@@
 depending on the priming treatment, while the last 5 images were the same 
-accross all treatments.  Ordering of the images was kept constant.
+across all treatments.  Ordering of the images was kept constant.
 
@@
 Workers could see this panel when previewing the task, but could not advance.
-Depending on the treatment, the worker was either shown a second pannel 
+Depending on the treatment, the worker was either shown a second panel 
 stating the name of 
 one of two fictitious organizations funding the work, or this panel was 
-skipped.  The next five pannels each consisting of a priming sub-tasks, 
+skipped.  The next five panels each consisting of a priming sub-tasks, 
 wherein the worker was asked to submit five descriptive labels.  The images
-used during the priming sub-task depended on the treatment.  The last 5 pannels
+used during the priming sub-task depended on the treatment.  The last 5 panels
 consisted of testing subtasks, wherein, as for the priming sub-tasks, workers
 were asked to submit 5 descriptive labels.
+
+\begin{table*}[t]
+\centering
+	\begin{tabular}{ l  c  l }
+		\hline                       
+		Treatment & Funder & Image Set	\\ 
+		\hline                       
+		$\textsc{ambg}$ & None & Ambiguous meals\\
+		$\textsc{cult}_{img}$ & None & Cultural meals\\
+		$\textsc{cult}_{fund}$ & The Global Foundation for Cultural Recognition& Cultural meals\\
+		$\textsc{cult}_{fund,img}$ & The Global Foundation for Cultural Recognition& Cultural meals\\
+		$\textsc{ingr}_{img}$ & None & Separated ingredients\\
+		$\textsc{ingr}_{fund}$ & The National Foundation for Nutritional Awareness & Separated ingredients\\
+		$\textsc{ingr}_{fund, img}$ & The National Foundation for Nutritional Awareness   & Separated ingredients\\
+		\hline  
+	\end{tabular}
+	\caption{Treatments to which Amazon Mechanical Turk workers were 
+		placed when asked to perform an image labelling task. The images
+		used in the image sets are reproduced in 
+		Figs.~\ref{fig:testImages}, \ref{fig:ambiguous}, \ref{fig:cultural}, and \ref{fig:ingredients}.
+	}
+	\label{table:1}
+\end{table*}
+
+%\begin{tabular*}{ l  c  r }
+%	\hline                       
+%	Treatment & Funder & Image Set	\\ 
+%	\hline                       
+%	$\textsc{ambg}$ & None & Cultural\\
+%	$\textsc{cult}_{img}$ & None & Cultural\\
+%	$\textsc{cult}_{fund}$ & \begin{tabular}[x]{@{}c@{}}The Global Foundation\\for Cultural Recognition\end{tabular}    & Cultural\\
+%	$\textsc{cult}_{fund,img}$ & \begin{tabular}[x]{@{}c@{}}The Global Foundation\\for Cultural Recognition\end{tabular}    & Cultural\\
+%	$\textsc{ingr}_{img}$ & None & Cultural\\
+%	$\textsc{ingr}_{fund}$ & \begin{tabular}[x]{@{}c@{}} The National Foundation\\ for Nutritional Awareness\end{tabular}      & Cultural\\
+%	$\textsc{ingr}_{fund, img}$ & \begin{tabular}[x]{@{}c@{}} The National Foundation\\ for Nutritional Awareness\end{tabular}  & Cultural\\
+%	\hline  
+%\end{tabular*}
 
@@
 To investigate in-task priming, we chose a set of images that highly
-recognizeable cultural settings and no food, and another set that contained
+recognizable cultural settings and no food, and another set that contained
 separated food ingredients, without any overt cultural content.  The third
 set of images was chosen to be very much like the test images, showing prepared
-meals, and though prepared food is inseperable from culture, these images
+meals, and though prepared food is inseparable from culture, these images
 were chosen based on being culturally more muted or ambiguous.
@@
 
+We next look at how alternately treated HPUs differ in their tendency to use
+more specific or more general labels. We use the ontology of labels emitted
+on the first test image to unambiguously establish a partial ordering of 
+label-specificity.  If one label $\ell_1$ is within the ancestry of another
+$\ell_2$, we say that $\ell_1$ is more general than $\ell_2$, otherwise they
+are not comparable.  Thus, the label \texttt{naan} is more 
+specific than both \texttt{bread} and \texttt{indian}, while incomparable to
+\texttt{statue}.
+
 \section*{Results and discussion}
@@
 		\includegraphics[scale=0.55]{../figs/f1scores.pdf}
-		\caption{$F_1$-score for binary classification of HPUs from seperate
-			treatments using a naive Bayes classifier.  Each pannel shows
+		\caption{$F_1$-score for binary classification of HPUs from separate
+			treatments using a naive Bayes classifier.  Each panel shows
 			the performance of the classifier when distinguishing between 
@@
 \textbf{Priming affects HPU output.}
-Before looking for differences in the content of labels provided by workers
-from different treatments, we first demonstrate that the treatments are
-distringuishable in an algorithmic sense.
-
-Using a naive bayes classifier, we are able to distinguish with high precision
-and specificity between workers from the \textsc{ambg} treatment and any of
-the other 5 treatments.  Fig~\ref{fig:classifier}A shows F1-score for a
-naive bayes classifier when distinguishing between the \textsc{ambg} and 
-the other treatments. The classifier achieves high precision and specificity
-in task.  Figure~\ref{fig:classifier}B shows the F1-score for binary
-classification between the $\textsc{cult}_{img}$ and the other treatments, 
-while \ref{fig:classifier}C shows that for $\textsc{ingr}_{img}$ and the other
-treatments.
-
-Not surprisingly, pairs of treatments in which one primes for culture, and the
-other primes for ingredients are easily distinguished.  However, it is quite
-surprising that high accuracy is achieved when classifying treatments within 
-the same orientation (e.g. cultural).  This is especially true in such cases as
-the classification of  $\textsc{cult}_{img}$ and $\textsc{cult}_{fund,img}$
-($\text{F}_1 = 0.863$), where both treatments also share the priming images in 
-common.
-
-We find it remarkable that, using only the labels that workers provide, it is
-possible to infer with good accuracy (at least when given a choice between 
-two posibilities)  the treatment to which the worker was 
-subjected.
+We first demonstrate that in a completely general sense, the priming treatments
+had a noticeable effect on the labels that workers assigned to images.  We
+test this by building a naive Bayes, which distinguishes workers from 
+different treatments based on the labels they submitted for the test images.
 
@@
 
+Fig.~\ref{fig:classifier}A shows the F1-score for the binary classification 
+of workers from $\textsc{ambg}$ and each of the other treatments.  The 
+classifier is able to distinguish workers from these treatments with high
+sensitivity and precision.  This clearly demonstrates that these treatments
+are \textit{differently primed}.  In panel B of Fig.~\ref{fig:classifier}, 
+we show $F_1$-scores achieved for classifications involving $\textsc{cult}_{img}$ the other treatments, while panel C shows scores for classifications 
+involving $\textsc{ingr}_{img}$ and the other treatments.  In each case, 
+the naive Bayes classifier is capable of efficiently distinguishing the
+workers from each pairing of treatments, demonstrating that priming was effective.
+
+While it is not so surprising to find that $\textsc{cult}_x$ treatments are 
+can be distinguished from $\textsc{ingr}_x$, it is somewhat remarkable that
+$\textsc{cult}_{img}$ and $\textsc{cult}_{fund, img}$ can be distinguished.
+Workers from these treatments were both primed in a way to activate cultural concepts, and 
+both labelled the same priming pictures.  The same can be said for the 
+treatments $\textsc{ingr}_{img}$ and $\textsc{ingr}_{fund, img}$.
+
 \textbf{Priming orients HPU focus.}
-Having established that each treatment does in fact consist of distinguishable 
-populations of the HPUs, we next look at the content of labels.  Two of the
-root labels in our ontology, \texttt{food} and \texttt{cultural}, map naturally
-onto the two concepts that laid behind the design of our priming treatments.
-A natural and straightforward expectation is that HPUs from treatments 
-$\textsc{cult}_x$ should emit more labels that are ontological descendents of
-\texttt{cultural}, while those from the $\textsc{ingr}_x$ treatments should
-emit more labels under $\texttt{food}$.
+The main effect that we expect is that workers primed to focus on culture
+would provide more culturally-oriented labels, while workers primed to focus
+on ingredients would focus more on food, in particular focussing in on 
+ingredients.  Figure~\ref{fig:valence} presents the fraction of words having
+cultural- or food-orientation from each treatment.
 
-In Fig.~\ref{fig:valence}, we exhibit the percentage of labels having a 
-cultural orientation (i.e. descending from \texttt{cultural} in the ontology), and 
-the percentage having a food orientation. Before making comparisons using this
-information, we remark that there is no reason to expect a balance in the 
-number of words having cultural or food orientation overall.  The $\textsc{ambg}$
-treatment, which was designed to promote neither orientation, exhibits a
-significant fraction of words from both the food and cultural orientation, while
-significantly favoring the former.
+The effect of the cultural images, which comprised the first five images shown
+to workers from $\textsc{cult}_{img}$ and $\textsc{cult}_{fund, img}$ are
+sharply visible.  Not only do they use more culturally-oriented words, more
+of these words are exclusively culturally oriented (i.e not being also 
+food-oriented).
 
-Both $\textsc{cult}_{img}$ and $\textsc{cult}_{fund,img}$ show a significant
-excess of culturally-oriented labels and fewer food-orientel labels.  
-Furthermore, HPUs in these treatments emit more culturally-oriented labels 
-even while emitting fewer labes that are simultaneously oriented toward 
-cultural and food (light bars in Fig.~\ref{fig:valence}).
-The deviation of these treatments from
-the others is well beyond the 95\% confidence interval.
+Interestingly, we do not observe this effect for $\textsc{cult}_{fund}$.
+In-task exposure clearly outweighs the effects introduced by
+disclosing the funder of the research.  It is consistent with our view of 
+priming as a hysteresis effect.
 
-Interestingly, the $\textsc{cult}_{fund}$ treatment did not have this effect.
-Although we have demonstrated that $\textsc{cult}_{fund}$ is differently
-primed from \textsc{ambg} using a naive bayes classifier, in respect of 
-overal fraction of food- and culturally-oriented labels, no distinction 
-is to be made.
+Experiments in psychology show that priming is stronger when the modality of
+the priming stimulus is the same as that of the target response.  These
+results are is consistent with that view.  This suggests that more attention
+toward the progression of tasks is due, rather than considering only worker
+orientation (training) and the content of individual tasks.
 
-In the case of $\textsc{ingr}_x$ treatments one expects to see an 
-enrichment of food-oriented labels. There is perhaps some evidence for this
-$\textsc{ingr}_{fund}$ and $\textsc{ingr}_{fund,img}$, but we cannat make any
-assertion with confidence.
+Looking at the orientation of words for the $\textsc{ing}_{x}$ treatments, 
+we do not see a significant enrichment in food-related words.
+Based on the composition of labels coming from people in the \textsc{ambg} 
+treatment, it would seem to be the case that our testing images simply elicit
+more food-oriented words in general.  It seems likely that priming in the
+toward a concept that is already prominent in the images would 
+have a less observable effect overall.
 
@@
 	\caption{Pairwise comparisons of label specificity between different 
-	HPU treatments.  Each pannel presents a binary comparison between a 
+	HPU treatments.  Each panel presents a binary comparison between a 
 	basis treatment (inset) and the subject treatments indicated on the 
@@
 	each treatment was randomly sampled, and the specificity of labels from
-	the HPUs of oposing treatments were compared.
+	the HPUs of opposing treatments were compared.
 	To compare two HPUs, each pair of labels from different HPUs are compared.
@@
 	where it is more general. This score is 
-	avereaged for all HPU pairings.  Statistical significance is guaged
+	averaged for all HPU pairings.  Statistical significance is gauged
 	by generating a null-comparison between two mutually exclusive subsamples 
@@
 \textbf{Priming affects attention to detail.}
-We next look at how alternately treated HPUs differ in their tendency to use
-more specific or more general labels. We use the ontology of labels emitted
-on the first test image to unambiguously establish a partial ordering of 
-label-specificity.  If one label $\ell_1$ is within the ancestry of another
-$\ell_2$, we say that $\ell_1$ is more general than $\ell_2$, otherwise they
-are not comparable.  Thus, the label \texttt{naan} is more 
-specific than both \texttt{bread} and \texttt{indian}, while uncomparable to
-\texttt{statue}.
+We next investigate whether our priming conditions differ in the degree of 
+generality of the labels they submit.  For instance, it is natural to expect
+that in the the exposure to isolated ingredients and emphasis on nutrition
+in the $\textsc{ingr}_x$ conditions would predispose workers to provide 
+labels that name specific ingredients.
 
-Label-specificity only generates a partial ordering---at least in our 
-experimental design.  A consequence of this is that it is not possible to
-assign an overall specificity score to a set of labels.  We submit that this
-reflects the underlying complexity of natural language semantics.  While
-we admit that there may be many ways to generate full orderings based on some
-notion of label specificity, we believe that this would inappropriately 
-collapse qualitative differences between labels, leading to results that are
-difficult to interpret.
+Using the ontology generated from the labels of testing image 1 
+(Fig.~\ref{fig:testImages}.1), we are able to compare each treatment in respect
+of the specificity of words used.  
+In Fig.~\ref{fig:specificity}, We show relative specificity scores in 
+pairwise comparisons between treatments. Because an ontology only induces a 
+partial ordering, it is only possible to perform binary comparisons between
+between treatments.
 
-In Fig.~\ref{fig:specificity}, We show pairwise specificity comparisons 
-between various pairs of treatments.  Figure~\ref{fig:specificity}A shows
-the comparison of \textsc{ambg} with all other treatments.  Both treatments
+Figure~\ref{fig:specificity}A compares \textsc{ambg} with all other 
+treatments.  Both treatments
 primed with cultural images ($\textsc{cult}_{img}$ and 
-$\textsc{cult}_{fund, img}$) exhibit an excess of more general words compared
-to \textsc{ambg}.  Meanwhile, $\textsc{ingr}_{fund}$ emitted an excess of 
+$\textsc{cult}_{fund, img}$) exhibit more labelling compared
+to \textsc{ambg}.  Although, $\textsc{ingr}_{fund}$ emitted an excess of 
 more specific words.
 
-We can seek to explain these observations by restricting the comparison to
-labels of a specific orientation (e.g. food or cultural).  When we perform
-the same comparisons but restricting to food-oriented labels, as shown in 
-Fig.~\ref{fig:specificity}G, we see some of the same tendencies as in A.
-However, when restricting to culturally-oriented labels 
-(Fig~\ref{fig:specificity}D) there are no significant comparative deviations 
-in specificity to speak of.
+To try to see whether certain treatments are more specific within labels of 
+a given orientation, we can make specificity comparisons while restricting
+to words of a cultural or food orientation.  These comparisons are respectively
+shown for comparisons to $\textsc{ambg}$ in
+Figs.~\ref{fig:specificity}D and G.  In panel D, we can see that, although
+$\textsc{cult}_{img}$, and $\textsc{cult}_{fund, img}$ were enriched in the 
+\textit{amount} of cultural words, they do not use more \textit{specific}
+cultural words.
 
-A first conclusion that we can draw from this is that there is a significant
-loss of specificity in labels emitted by treatments having non-ambiguous 
-priming images.  In Fig.~\ref{fig:specificity}G, only $\textsc{cult}_{fund}$
-and $\textsc{ingr}_{fund}$ show no significant deviation.
+One simple explanation for these observations is that  would be that people 
+generally have more specific words for food-related concepts than for cultural 
+ones.  This would certainly stand to reason, in which case one would expect
+to see an enrichment in the quantity of cultural words, while the increase
+in specificity might be more difficult to measure.
 
-- through negative priming workers stop responding to generic features of images of prepared meals, which happens in the ambiguous case.
+Explaining the results for $\textsc{ingr}_{x}$ in panel D is more subtle,
+however.  As we mentioned above, one would expect that priming for ingredients
+and nutrition would elicit more specific words, but this is not observed for
+the two treatments in which the first five images featured isolated 
+ingredients.  In fact, these treatments showed significantly \textit{less}
+specificity.
 
-- On the other hand, workers presented with either the cultural or ingredients images are initially struck by the gross differences, which draws generic 
-labels, especially with respect to food for which generic labels in ambiguous treatment had been suppressed through negative priming.
+This surprising result and, along with the other results in panels A, D, and G
+can be explained if we consider the effects of novelty and negative priming.
+Although the ingredients images probably do encourage the workers to focus
+to some extent on ingredients, when they encounter the test images, they are
+presented with the novelty of prepared meals and table settings.  These 
+novelties naturally attract attention and become the subject of labels such
+as $\texttt{meal}$.
 
-- it seems, at first, inconsistent that $\textsc{cult}_{img}$ and 
-$\textsc{cult}_{fund,img}$ would at once enrich the fraction of 
-culturally-oriented words, but produce no change in the specificity of 
-culturally oriented words.  First of all, there is no logical incompatibility
-with producing a greater number of cultural terms, yet which are generic 
-in nature.  If we follow the hypothesis that focus (or orientation) is directed
-by positive priming (perhaps through the subconscious or conscious inference
-of reqeuster intent), while focusing on nuances comes from the inhibition
-of gross features through negative priming, then this combination of observations makes sense.  Having seen many cultural images, HPUs in 
-$\textsc{cult}_{img}$ and $\textsc{cult}_{fund,img}$ are primed to emit 
-cultural labels, however, since the diversity of images is high compared to
-other treatments on reaching the test images, there no opportunity for 
-focussing in to finer detail through the mechanism of negative priming.
+Negative priming on the other hand inhibits a person from responding to a
+stimulus that is repeated and regarded as not salient \cite{versace2001negative}.  
+Workers in the
+treatments exposed to the ambiguous image set, who have seen five images
+of prepared meals, might then be less likely to respond to the first test
+image by submitting $\texttt{meal}$ as one of the labels.
 
-\textbf{In-task priming is stronger than framing.}
-Our experimental set-up includes two priming mechanisms: in-task priming, 
-produced by varying the first 5 images of the task, as well as what could be
-called sidestream priming, in which a fictitious funder is disclosed.
-The intention behind this set-up was to enable a direct comparison, and 
-our expectation was that in-task priming might produce some fraction of the
-effect produced by disclosing the funder.  To our surprise, in-task priming 
-produces a much stronger effect.
+\section{Conclusion}
 
-There is a cautionary lesson here.  In-task priming, which is inherently 
-impossible to eliminate is may be far more severe than the more overt causes 
-of priming that more routinely attract concern during the design of an 
-experiment.   Depending on the final purpos of HPU work products, this may be
-quite restrictive.
+We provided a novel algorithmic definition for the notion of
+priming.  This opens up an avenue for rigorously demonstrating the existence 
+of priming by using existing algorithmic tools, such as a naive Bayes 
+classifier.  In our study we used this definition to test the effectiveness
+of our priming treatments.
 
-\textbf{Leveraging priming.}
-In a more positive view, the results of our study suggest that the ordering 
-of subtasks can be used as a way to direct the focus and attention to detail
-by HPUs.  If the designer desires more coarse-grained work-products, this
-can be achieved by presenting successive subtasks with high diversity.  On 
-the other hand if fine-grained work products are desired, then the designer
-should aim to sort subtasks into ``tracks'' that are highly homogeneous,
-and assign subsens of the pool of HPUs to specifict tracks.
+Our results demonstrate that a strong hysteresis effect can be observed in 
+workers performing an image labelling task.  This in-task priming effect 
+appears to be much stronger than that introduced by disclosing the funder
+of a study, even when the name of the funder caries an implicit semantic
+orientation resonant in the task.
 
-It is interesting to consider to what extent the output of HPUs can be driven
-toward nuanced detail using this technique.  Consider, for example, the 
-image labelling platform called the ESP Game.  Here Two HPUs are shown
-the same image and in order to derive what are in some sense the moset 
-characteristic labels, they are asked to attempt to produce the same labels
-for the image.  One could imagine a similar setup, but in which the designer
-attempts to produce the set of labels that best covers the semantic space 
-occupied by the image, by eliciting labels at coarser and finer levels of 
-specificity using the techniques suggested by the present work.
+The effects of in-task priming have some degree of subtlety.  While workers
+can be primed to focus on certain concepts simply by showing them exemplars, 
+the activation of target concepts can be counterbalanced by the novelty of
+their absence in subsequent tasks.
+
+It appears to be the case that one can encourage greater specificity in the
+labelling task by presenting a series of images that are similar to one 
+another.  This suggests a method for obtaining highly specific
+labels, by repeatedly putting images out to be labelled, clustering them based
+on the labels they recieve, and then re-serving the clustered images to 
+workers.  The clustered images will be similar in their gross features, driving
+workers to focus on their minutia.
+
+In summary, the hysteresis effect is strong in image labelling tasks, and 
+the designer of microtasks would be well-served by considering 
+not just the design of individual tasks, but also their progression.
 
@@
 \begin{figure*}
-%	\includegraphics[scale=1.00]{../figs/testImages.png}
-	\caption{caption here}
+	\includegraphics[scale=1.00]{../figs/taskImages/testImages.png}
+	\caption{Images used in the testing set.  These images were presented to
+	workers after having labelled five other images, either from the cultural
+	set (Fig.~\ref{fig:cultural}), ingredients set (Fig.~\ref{fig:ingredients}), or ambiguous set (Fig.~\ref{fig:ingredients}).}
 	\label{fig:testImages}
@@
 \begin{figure*}
-%	\includegraphics[scale=1.00]{../figs/ambiguous.png}
-	\caption{caption here}
+	\includegraphics[scale=1.00]{../figs/taskImages/ambiguous.png}
+	\caption{Ambiguous image set.  These images were chosen to be similar to 
+	the test images, but did not have predominant cultural orientation.}
 	\label{fig:ambiguous}
@@
 \begin{figure*}
-%	\includegraphics[scale=1.00]{../figs/cultural.png}
-	\caption{caption here}
+	\includegraphics[scale=1.00]{../figs/taskImages/cultural.png}
+	\caption{Cultural image set.  These images were chosen for their overt and
+	specific cultural orientation.}
 	\label{fig:cultural}
@@
 \begin{figure*}
-%	\includegraphics[scale=1.00]{../figs/ingredients.png}
-	\caption{caption here}
+	\includegraphics[scale=1.00]{../figs/taskImages/ingredients.png}
+	\caption{Ingredients image set.  These images were chosen for their focus on
+	food ingredients, with the intention of encouraging workers to produce labels
+	of higher specificity relating to food.}
 	\label{fig:ingredients}
@@
 \bibliography{bab.bib}
+
 \end{document}

### 2014-06-06 docs/publications/2014.05_PNAS/figs.tex
draft 3 for submission to Derek

--- 2014-05-11 docs/publications/2014.05.9_pnas/figs.tex
@@
 \usepackage[colorlinks=true,urlcolor=blue]{hyperref}
+\usepackage[figurewithin=none]{caption}
+\usepackage{dcolumn}
+\usepackage{multirow}
+\usepackage{booktabs}
+\newcolumntype{d}{D{.}{.}{4.0}}
+\newcolumntype{s}{D{.}{.}{1.4}}
 
@@
 
+\begin{table}
+\centering
+\begin{tabular}{ l  d  s }
+
+\toprule    
+\multirow{2}{*}{Image set} & \multicolumn{1}{c}{\# of unique} & 
+\multicolumn{1}{c}{Similarity } \\
+&  \multicolumn{1}{c}{labels} & \multicolumn{1}{c}{with test set} \\
+
+\midrule
+
+Ambiguous & 799 & 0.1661
+\\
+
+Cultural & 693 & 0.0576
+\\
+
+Ingredients & 728 & 0.1169
+\\
+
+Test & 1785 & 1.00 
+\\
+\bottomrule
+
+\end{tabular}
+\caption{Number of unique labels attributed to each image set, and their
+	similarity the test set based on \textbf{Eq. 4} }
+\label{table:2}
+\end{table}
+
 \begin{figure}
-	\includegraphics[scale=1.00]{../figs/taskImages/testImages.png}
+	\includegraphics[scale=1.00]{figs/taskImages/testImages.png}
 	\caption{Testing image set. These images were presented to all workers in 
@@
 \begin{figure}
-	\includegraphics[scale=1.00]{../figs/taskImages/ambiguous.png}
+	\includegraphics[scale=1.00]{figs/taskImages/ambiguous.png}
 	\caption{ Ambiguous image set. These images were presented to workers from 
@@
 \begin{figure}
-	\includegraphics[scale=1.00]{../figs/taskImages/cultural.png}
+	\includegraphics[scale=1.00]{figs/taskImages/cultural.png}
 	\caption{Cultural image set. These images were presented to workers from 
@@
 \begin{figure}
-	\includegraphics[scale=1.00]{../figs/taskImages/ingredients.png}
+	\includegraphics[scale=1.00]{figs/taskImages/ingredients.png}
 	\caption{ Ingredients image set. These images were presented to workers 
@@
 \begin{figure}
-	\includegraphics{../figs/f1-thetas.pdf}
+	\includegraphics{figs/f1-thetas.pdf}
 	\caption{ $F_1$ score and $\theta_\text{NB}$ for the various 
@@
 \begin{figure}
-	\includegraphics{../figs/longitudinalF1scores-t1-t2.pdf}
+	\includegraphics{figs/longitudinalF1scores-t1-t2.pdf}
 	\caption{ $F_1$ score and $\theta_\text{NB}$ for the classification of 
@@
 \begin{figure}
-	\includegraphics{../figs/orientationVsTreatment.pdf}
+	\includegraphics{figs/orientationVsTreatment.pdf}
 	\caption{Percent label composition (culture- vs food-oriented labels) for 
@@
 \begin{figure}
-	\includegraphics{../figs/excessCultureVsTreatment-t1.pdf}
+	\includegraphics{figs/excessCultureVsTreatment-t1.pdf}
 	\caption{Excess culture-oriented label composition in the labels provided
@@
 \begin{figure}
-	\includegraphics{../figs/specificity-allImages.pdf}
+	\includegraphics{figs/specificity-allImages.pdf}
 	\caption{Relative specificity of various treatments.
@@
 \begin{figure}
-	\includegraphics{../figs/specificity-test0.pdf}
-	\caption{Relative specificity of various treatments, for labels attributed
+	\includegraphics{figs/specificity-test0.pdf}
+	\caption*{Figure S1: Relative specificity of various treatments, for labels attributed
 		to the first test image.

### 2014-06-06 src/analysis.py

@@ -54,6 +54,88 @@ class Analyzer(object):
 			self.ontology = ontology
 
 
+	def compare_image_sets(self, fname='data/similarity.txt'):
+
+		fh = open(fname, 'w')
+
+		# collect the bag of words for each image set
+		ambiguous_labels = self.get_bag_of_labels(
+			treatments=['treatment0'],
+			images=['prime%d' %i for i in range(5)])
+
+		fh.write('ambg: %d\n' % len(ambiguous_labels))
+
+		cultural_labels = self.get_bag_of_labels(
+			treatments=['treatment1'],
+			images=['prime%d' %i for i in range(5)])
+
+		fh.write('cult: %d\n' % len(cultural_labels))
+
+		ingredients_labels = self.get_bag_of_labels(
+			treatments=['treatment2'],
+			images=['prime%d' %i for i in range(5)])
+
+		fh.write('ingr: %d\n' % len(ingredients_labels))
+
+		test_labels = self.get_bag_of_labels(
+			treatments=['treatment0', 'treatment1', 'treatment2'],
+			images=['test%d' %i for i in range(5)])
+
+		fh.write('test: %d\n' % len(test_labels))
+
+		# print the size of intersection for each
+		ambg_intersection = len(ambiguous_labels & test_labels)
+		ambg_union = len(ambiguous_labels | test_labels)
+		ambg_jacc = ambg_intersection / float(ambg_union) * 100
+
+		fh.write('ambg & test: %d / %d = %2.2f\n' % (
+			ambg_intersection, ambg_union, ambg_jacc))
+
+		cult_intersection = len(cultural_labels & test_labels)
+		cult_union = len(cultural_labels | test_labels)
+		cult_jacc = cult_intersection / float(cult_union) * 100
+
+		fh.write('cult & test: %d / %d = %2.2f\n' % (
+			cult_intersection, cult_union, cult_jacc))
+
+		ingr_intersection = len(ingredients_labels & test_labels)
+		ingr_union = len(ingredients_labels | test_labels)
+		ingr_jacc = ingr_intersection / float(ingr_union) * 100
+
+		fh.write('ingr & test: %d / %d = %2.2f\n' % (
+			ingr_intersection, ingr_union, ingr_jacc))
+
+		fh.close()
+
+
+	def get_bag_of_labels(
+		self,
+		treatments=['treatment0', 'treatment3', 'treatment5'],
+		images=['prime%d' %i for i in range(5)]
+		):
+
+		label_set = set()
+
+		for treatment in treatments:
[…]

### 2014-06-06 src/plots.py

@@ -598,14 +598,16 @@ def plotExcessCultureVsImage(readFname='orientation/orientation.json',
 
 	subplotLabels = ['A', 'B']
 
-	figWidth = 8.7/2.54
-	figHeight = figWidth*4/5.
+	figWidth = 17.4/2.54
+	figHeight = figWidth*2/5.
+	#figWidth = 8.7/2.54
+	#figHeight = figWidth*4/5.
 	fig = plt.figure(figsize=(figWidth, figHeight))
-	gs = gridspec.GridSpec(1,1)
+	gs = gridspec.GridSpec(1,2)
 
 	X = range(len(images))
 
-	subplots = [0]
+	subplots = [0,1]
 
 	for subplot in subplots:
 
@@ -650,7 +652,8 @@ def plotExcessCultureVsImage(readFname='orientation/orientation.json',
 		xlims = (-padding, len(X) - 1 + width + padding)
 		plt.xlim(xlims)
 
-		plt.ylim((0, plt.ylim()[1]))
+		#plt.ylim((0, plt.ylim()[1]))
+		plt.ylim((-20, plt.ylim()[1]))
 
 		plt.draw()
 		plt.tight_layout()

### 2014-06-06 docs/publications/2014.05_PNAS/manuscript.tex
reame pnas2.tex -> manuscript

--- 2014-05-14 docs/publications/2014.05.9_pnas/pnas2.tex
@@
 defensible notion of an ``unprimed state''.  A participant always approaches
-a task from in \textit{some} state of mind.  This will be influenced by her
+a task in \textit{some} state of mind.  This will be influenced by her
 exposures prior to the experiment, which cannot be known by the experimenter.  
@@
 sense ``neutral'', but it is by no means a control group. The particular 
-images used would arguably produce different priming from another set that
-was also apparently ``neutral''.
-
+images used would arguably induce different priming than that induced by 
+another set that was, in its own way, ``neutral''.
 We avoid this difficulty by defining priming relatively, and speak of one
@@
 A final factor to consider is that, individuals who are in the same priming 
-treatment will still in general produce different output for a task
-due to the natural variance between people.  Therefore, we defined in relation 
+treatment will still in general produce different output for a task,
+due to the natural variance between people.  Therefore, we define priming in 
+relation 
 to populations, not individuals.
 
-With these considerations, we are ready to propose the definition.
-Consider two populations of people $\mathcal{J}$ and $\mathcal{K}$, that 
-produce respectively two populations of outputs 
-$\mathcal{L}$ and $\mathcal{M}$ during the completion of a task $\mathcal{T}$:
+With these considerations, consider two populations of people 
+$\mathcal{J}$ and $\mathcal{K}$, that produce respectively two populations of 
+outputs $\mathcal{L}$ and $\mathcal{M}$ during the completion of a task 
+$\mathcal{T}$:
 
@@
 directly
-conclude that two populations are the same in priming.  Rather, the definition
+conclude that two populations are the same in priming.  The definition
 admits the possibility that there exists some other $\mathcal{A}'$ capable of 
-generating a measure of $\theta$ greater than zero. Interpreting a result
+generating a measure of $\theta$ statistically greater than zero. 
+Interpreting a result
 that $\mathcal{A}$ fails to achieve accuracy significantly better than 
 chance depends on the capabilities of $\mathcal{A}$ and the state of the art
-of classifier algorithms.
+of classifier algorithm design.
 
@@
 culture (see \textbf{Fig. 1}).  We intended that the content of these images 
-would tend elicit labels focusing food or culture (or both).
+would elicit labels focusing food or culture (or both).
 
 One of the prior image sets, which we call \textit{ambiguous}, was chosen to
-be most similar to the posterior image set, and contains images of prepared
-meals, but whose cultural features are less prominent and more difficult to
-identify (see \textbf{Fig. 2}).  
+be very similar to the posterior image set, in the sense that it consists of
+images of prepared meals.  However, the ambiguous image set was chosen such 
+that its cultural features are less prominent and more difficult to identify 
+(see \textbf{Fig. 2}).  
 The \textit{cultural} prior set features iconic cultural scenes, but no food 
@@
 the \textit{ingredients} prior image set depict separated ingredients, but, 
-like the ambiguous set, did not have prominent cultural features (see 
+like the ambiguous set, were chosen to avoid prominent cultural features (see 
 \textbf{Fig. 4}).  See the \textbf{Materials and Methods} section for further 
@@
 the classifier performance in distinguishing between different pairs of 
-treatments based on workers' labels for the test images, and the corresponding
+treatments based on workers' labels for the posterior images, and the corresponding
 value for $\theta_\text{NB}$.
@@
 (in-task and framing) were effective.  Remarkably, the classifier not only 
-distinguishes treatments tending toward a different ``orientations'' 
+distinguishes treatments tending toward different ``orientations'' 
 (e.g. $\textsc{cult}_{img}$ and $\textsc{ingr}_{img}$, \textbf{Fig. 5A}), 
@@
 
-Next we look at the degree to which labels from individual test images reveal 
+Next we look at the degree to which labels from individual posterior images reveal 
 priming.  It would stand to reason that, as workers proceed through 
-the test images, the effects of priming might be ``washed out''.  
+the posterior images, the effects of priming might be ``washed out''.  
 \textbf{Figure 6} shows the
 performance of the Naive Bayes classifier when using the labels workers provide
-for particular images.  This does show that, as we look to later test images, 
+for particular images.  This does show that, as we look to later posterior images, 
 the treatments' difference in priming, $\theta_\text{NB}$, declines.  In future
@@
 end, we construct an ontology of all the labels attributed to
-the test images.  The ontology is a directed acyclic graph of terms,
+the posterior images.  The ontology is a directed acyclic graph of terms,
 with directed edges drawn from abstractions toward instances.  For example,
@@
 \texttt{vegetables} 
-$\to$ \texttt{tomato}.  In general, each of these terms is a label that
-occurred in the corpus of labels provided, but in some cases we added 
-an abstraction when it was missing, to connect the ontology.  We provide more
-detail about the construction of the ontology in the 
-\textbf{Materials and Methods} section.
+$\to$ \texttt{tomato}. We provide more detail about the construction of the 
+ontology in the \textbf{Materials and Methods} section.
 
-We put the abstract classes  \texttt{activity}, 
-\texttt{adjective}, \texttt{culture}, \texttt{food}, and \texttt{thing} at 
-the root of the ontology.  We promote \texttt{food} and \texttt{culture}
-to the root of the ontology simply because of the prominence of food and 
-culture-related labels in the corpus.  We acknowledge that food is a 
-central aspect of culture, but we do not put \texttt{food} \textit{under} 
-\texttt{culture}
-(nor vice versa) because there are food-related labels that are culturally 
-ambiguous (e.g. \texttt{bread}), and there are culture-related labels without 
-a direct connection to food (e.g. \texttt{ganesha}).  The many words that are 
-both food and culture-related (e.g. \texttt{dim sum}) receive an inbound edge 
-(or path) from both \texttt{food} and \texttt{culture}.
-This allows us to gauge effects on the orientation of workers' focus
-with respect to the concepts of food and culture by simply counting the number 
-of labels they provide that descend from \texttt{food} and \texttt{culture}.
-
+The ontology allows us to algorithmically count the number of labels that are
+of cultural orientation (\texttt{ganesha}),  food orientation
+(\texttt{bread}), or both (\texttt{dim sum}).  We do this by counting the
+number of labels having have inbound paths leading from the abstract clasess 
+\texttt{culture} and/or \texttt{food}, which are present in the ontology.
 \textbf{Figure 7} plots the composition of labels (fraction of culture- and 
@@
 panel \textbf{7A}, we can see that, before considering the effects of 
-treatments, there is significant variance in the composition of the labels 
-for different images due to inherent differences in their content.  For our 
-purpose, we are interested in the systematic differences between 
-the treatments.
+treatments, there is significant variance in the composition of labels 
+for different images, probably due to inherent differences in their content.  
+For our purpose, we are interested in the systematic differences between 
+treatments.
 
 In \textbf{Fig. 7B} we exhibit the composition of labels for the various 
-treatments (aggregating together the labels for all images for a given 
+treatments (aggregating together the labels for all images of a given 
 treatment).  We can see that the treatments which expose workers to the
@@
 that aggregating label compositions for all images actually masks the effects. 
-In \textbf{Fig. 7C}, we plot label compositions for only the first
-image.  This reveals that, in labeling the first test image, workers in the
+In \textbf{Fig. 7C}, we plot label compositions for only the first posterior
+image.  This reveals that, in labeling the first posterior image, workers in 
 $\textsc{cult}_{img,x}$ were strongly influenced to favor culture- over 
@@
 We next inspect this effect longitudinally, that is, as a function of 
-the test image.  To do so, we compute the \textit{excess cultural orientation} 
+the posterior image.  To do so, we compute the \textit{excess cultural orientation} 
 ($\Delta_{cult}$) of
@@
 more culture-oriented $\textsc{cult}_{img}$ is than $\textsc{ambg}$.  
-\textbf{Figure 8} plots $\Delta_{cult}$ as a function of test image, $i$. It
-clearly shows the strong influence on the labels attributed to the first image,
-but for later images this effect immediately drops below statistically 
-measureable levels, while remaining always positive.
+\textbf{Figure 8} plots $\Delta_{cult}$ as a function of posterior image, $i$. 
+This clearly shows the strong influence on the labels attributed to the first 
+posterior image,
+but for later images the effect immediately drops below statistically 
+significant levels, while remaining always positive.
 
@@
 We can then define the relative specificity of two treatments, 
-$S(\mathcal{U},\mathcal{V})$ to be the average
+$S(\mathcal{U},\mathcal{V})$, to be the average
 relative specificity of workers drawn uniformly from the treatments.  
-$\hat{S}({\mathcal{U}, \mathcal{V}})$ estimates this using the sample mean:
+We obtain an estimator, $\hat{S}({\mathcal{U}, \mathcal{V}})$, using the 
+sample mean:
 
@@
 there are no significant differences in cultural specificity to speak of. 
-Clearly, food and culture are not on equal footing.  Various psychological 
-explanations are possible, and we explore these in the discussion below.
+Clearly, food and culture are not on equal footing in the experiment.  Various 
+psychological explanations are possible, and we explore these in the 
+discussion below.
 
@@
 would overtly signal to workers that the requester was interested in a 
-specific aspect of image content.  On the other hand, the we did not 
+specific aspect of image content.  On the other hand, we did not 
 expect the prior image set, though enriched in certain content, to overtly signal interest.  In turn, we expected that a signal of intent would 
-strongly affect how the workers approach the task.  Perhaps the most unexpected
-result of this study is the finding that the prior image set influenced 
-workers' focus (label orientation) and specificity far more strongly than did 
-framing the task with the funder names.
+strongly affect how the workers approach the task.  Perhaps the most 
+unexpected result of this study is that the prior image set influenced label 
+orientation and specificity far more than did framing the task by naming the
+funder.
 
@@
 
-Randomized ordering and replication of tasks is one method to abate this issue.
+Randomized ordering and replication of tasks is one method to abate this.
 But the requester could also include an initial set of tasks as a 
@@
 circumstances, such effects might go entirely undetected.  We believe this 
-is a strong argument in support of using $\theta_\text{NB}$ to supplement 
-methods designed to measure specific priming effects.
+is a strong argument in support of using $\theta_\text{NB}$ to determine 
+whether priming has occurred, without making narrow assumptions about what the 
+effects of priming will be.
 
@@
 consider the vital role of food on the one hand, and the bias in social 
-cognition known as \textit{out-group homogeneity}\cite{Vala2012491,Ray2012387,Ishii2011159,Boldry2007157}.
-Out-group homogeneity is a phenomenon whereby people perceive fewer 
+cognition known as \textit{outgroup homogeneity}\cite{Vala2012491,Ray2012387,Ishii2011159,Boldry2007157}.
+Outgroup homogeneity is a phenomenon whereby people perceive fewer 
 differences between members of an outgroup than between members of their 
@@
 adaptiveness: social cognition regarding one's ingroup is more consequential
-\cite{Vala2012491}.  Thus, it would not be surprising to find that people had 
-less nuanced vocabulary for culture than for food, where a nuanced vocabulary 
-would be of direct survival benefit.
+\cite{Vala2012491}.  Thus, it seems plausible that a nuanced cultural 
+vocabulary might be of limited advantage.  On the other hand,
+the differences between food and poison can be nuanced indeed, and so it would
+not be surprising to find that people have a more nuanced vocabulary for 
+food than for culture.
 
@@
 specificity of culture-oriented labels.  Since effects on 
-label composition were only appreciable for the first test image 
+label composition were only appreciable for the first posterior image 
 (see \textbf{Fig. 8}), we also
 performed the specificity analysis restricting to labels from the first
-test image (see \textbf{Fig. S1}).  But even focusing on the first test image
-shows no significant increase in cultural specificity for 
+posterior image (see \textbf{Fig. S1}).  But even when focusing on the first 
+posterior image we see no significant increase in cultural specificity for 
 $\textsc{cult}_{img,x}$.  Thus, we observe that priming effects on 
@@
 
-Under our measure of similarity based on shared labels, our results show that
+Under our measure of similarity, our results show that
 more specific labels are provided to the posterior images when the prior and
@@
 this is the notion of \textit{negative priming}, wherein the participant
-becomes desensitized to stimuli that do not seem salient [***].  Thus, workers 
-who have been shown successive images of prepared meals 
-would be much less inclined to provide generic terms such as \texttt{food} or 
-\texttt{meal} since these terms would no longer seem salient in the 
+becomes desensitized to stimuli that do not seem salient [***].  Thus, after 
+workers had been shown successive images of prepared meals in the ambiguous
+prior set, they would be much less inclined to provide generic terms such as 
+\texttt{food} or 
+\texttt{meal} to images in the posterior set, since these terms would no 
+longer seem salient in the 
 context of their priming treatment.
@@
 then cluster the images based on the labels and a language model, and then 
-reserve the images, ensuring that each HPU operates on images from a single 
-cluster.  The more homogeneous that a cluster of images is in terms of 
-content, the more one might gain by serving the cluster for another round of
-labeling.
+re-serve the images, ensuring that each HPU operates on images from a single 
+cluster.  The more ``homogeneous'' a cluster of images, the more one might gain
+by serving the cluster for another round of labeling.
 
@@
 Employers on microtask platforms should 
-beware that strong biases may be introduced by the very tasks they provide,
-and further research into the nature of these effects is warranted.  At the 
+beware that strong biases may be introduced by the very tasks they provide.
+Further research into the nature of these effects is warranted.  At the 
 same time, in-task priming might be exploited to improve task output, for 
@@
 populations have been affected by priming, even when the effects are not 
-understood. With our proposed definition, we advocate a more general view of 
-priming as a form of hysteresis.
+understood. Along with our proposed definition, we advocate a more general 
+view of priming as a form of hysteresis.
 
@@
 
-\textbf{AMT Tasks.} The task described in the \textbf{Experimental Setup}
-section was served to 900 workers, who were uniformly randomly assigned to
+\textbf{AMT Tasks.} The task described in \textbf{Experimental Setup}
+was served to 900 workers, who were uniformly randomly assigned to
 treatments.  All treatments had at least 126 task completions.  To obtain 
@@
 definition.  Let the specificity of a worker $u$ relative to a 
-\textit{basis treatment} $\mathcal{V}$, denoted $S_V(u)$, to be the expected 
+\textit{basis treatment} $\mathcal{V}$, denoted $S_V(u)$, be the expected 
 relative specificity between $u$ and a worker uniformly sampled from 
@@
 \end{align}
-where $U$ is a uniformly sampled worker from $\mathcal{U}$.  This yields 
+where $U$ is a random, uniformly sampled worker from $\mathcal{U}$.  This 
+yields 
 estimators for $S_V(u)$ and $S(\mathcal{U}, \mathcal{V})$, and their variances
@@
 		\hat{S}(\mathcal{U},\mathcal{V}) 
-			&= \frac{1}{|\mathcal{U}|} \sum_{u \in \mathcal{V}} S_V(u),
+		&= \frac{1}{|\mathcal{U}|} \sum_{u \in \mathcal{V}} \hat{S}_V(u),
 		\label{eq:treatment-specificity-estimator} \\
@@
 \end{align}
-$\text{Var}_V{s(u,V)}$ can be directly calculated as a sample variance, so
-\textbf{Eq.~\ref{eq:basis-specificity-estimator}} through \textbf{\ref{eq:treatment-specificity-variance}} provide enough information to test the hypotheses:
+$\text{Var}_V\{s(u,V)\}$ can be directly calculated as a sample variance.
+\textbf{Equations \ref{eq:basis-specificity-estimator}} through 
+\textbf{\ref{eq:treatment-specificity-variance}} provide enough information to test the hypotheses:
 \begin{align}
@@
 	Nutritional Awareness''.  The ambiguous, cultural, and ingredients 
-	priming images used are shown in \textbf{Figs. B}, \textbf{C}, and 
-	\textbf{D}.
+	prior image sets are shown in \textbf{Figs. 2}, \textbf{3}, and 
+	\textbf{4}.
 
 \paragraph{Figure 1.}
-	Testing image set. These images were presented to all workers in the order 
-	shown after the priming set of images.
+	Posterior image set. These images were presented to all workers after the 
+	prior image set, in the order shown.
 
 \paragraph{Figure 2.}
-	Ambiguous image set. These images were presented to workers from certain
-	treatments (see \textbf{Table 1}) in the order shown.
+	Ambiguous prior image set. These images were presented to workers from 
+	certain treatments (see \textbf{Table 1}) in the order shown.
 
 \paragraph{Figure 3.}
-	Cultural image set. These images were presented to workers from certain
-	treatments (see \textbf{Table 1}) in the order shown.
+	Cultural prior image set. These images were presented to workers from 
+	certain treatments (see \textbf{Table 1}) in the order shown.
 
 \paragraph{Figure 4.}
-	Ingredients image set. These images were presented to workers from certain
-	treatments (see \textbf{Table 1}) in the order shown.
+	Ingredients prior image set. These images were presented to workers from 
+	certain treatments (see \textbf{Table 1}) in the order shown.
 
@@
 $F_1$ score and $\theta_\text{NB}$ for the various 
-priming treatments, as measured using a Naive Bayes classifier. Each panel 
-presents classifier performance results that indicate the difference in
-priming between a basis 
-treatment, indicated in the inset, and the other treatments, indicated on the
+priming treatments, as measured using a Naive Bayes classifier. Dotted lines 
+show the 95\% confidence interval
+assuming the classifier performed no better than chance.  Each panel 
+presents performance results for the binary classification between a basis 
+treatment, indicated by the inset, and other treatments, indicated on the 
 abscissa.
@@
 $\textsc{cult}_{img}$ and $\textsc{ingr}_{img}$ using a Naive Bayes 
-classifier.  The classifier is provided only the labels attributed to
+classifier.  Dotted lines 
+show the 95\% confidence interval
+assuming the classifier performed no better than chance.  The classifier is provided only the labels attributed to
 particular images as indicated on the abscissa.
@@
 Percent label composition (culture- vs food-oriented labels) for 
-various images and treatments.  Panel A shows the composition of 
-labels, aggregated over all treatments, as a function of test image.
+various images and treatments.  Panel A shows the 
+composition of labels, aggregated over all treatments, as a function of 
+posterior image.
 Panel B shows the composition of labels, aggregated over all images, as
 a function of treatment.  Panel C shows the composition of labels 
-attributed to the first test image by various treatments.
+attributed to the first posterior image by various treatments.
 
@@
 by $\textsc{cult}_{img}$ as compared to $\textsc{ambg}$, for various
-test images (see \textbf{Eq. 1} for calculation).
+posterior images (see \textbf{Eq. 1} for calculation).
 
@@
 Relative specificity of various treatments, for labels attributed
-to the first test image.
+to the first posterior image.
 Each panel shows the comparison between a basis treatment (inset) and 

### 2014-06-06 docs/publications/2014.05_PNAS/manuscript.tex
rename pnas3.tex -> manuscript.tex

@@
 
-\title{The effects of priming in human computation}
-\author{Edward Newel, Derek Ruths}
+\title{Inter-task effects lead to an unexpected bias in human computation}
+\author{Edward Newell, Derek Ruths}
 
@@
 possible to submit batches of small tasks to a large pool of human workers, 
-who do the tasks for fun and remuneration \cite{kazai2013analysis}.  Tasks 
-involving qualitative
+who do the tasks for fun, a sense of purpose, and remuneration 
+\cite{kazai2013analysis, Antin20122925}.  
+Originally used to distribute clerical work, these platforms 
+increasingly serve as a cheap and fast means to engage experimental 
+participants and manually annotate of datasets in a research 
+setting \cite{snow2008cheap}.  
+Tasks involving qualitative
 judgment (e.g. flagging inappropriate images), natural language annotation,
-and object recognition are commonplace, since people still outperform  
-computers in these areas \cite{yuen2011survey}.
+and object recognition are commonplace, since it is difficult to achieve 
+comparable performance using only computers \cite{yuen2011survey}.
+%Generally the worker is first given some orientation to the task, and then 
+%performs the task repeatedly (e.g. label several images, one after 
+%the other).
 
-Such platforms render human cognition as fluid a resource as compute cycles: 
-it is available on demand in small units, with low transaction cost, from 
-anywhere via the Internet \footnote{\href{http://mturk.com}{http://mturk.com}}.
-The task requester can interact with the platform like a compute server, 
-seamlessly 
+Such platforms render human cognition into a fluid resource: it is available 
+on demand in small units, with low transaction 
+cost, from anywhere via the 
+Internet\footnote{\href{http://mturk.com}{http://mturk.com}}.
+The task requester can 
+interact with the platform like a compute server, seamlessly 
 integrating human and machine computation.  Researchers have put forward the 
@@
 
-Originally used to distribute clerical work, these platforms 
-increasingly serve as a cheap and fast means to engage experimental 
-participants and provide qualitative annotations of datasets in a research 
-setting \cite{snow2008cheap}.  Given the limited ability to screen workers, and their transient 
-low-commitment engagement with the requester, researchers have criticized the
-reliability of crowdsourced output \cite{marsden2009crowdsourcing}.
+Here, we highlight an important way in which HPUs differ from CPUs, with 
+serious implications for the design of tasks.  It is well known that people 
+are subject to priming effects 
+\cite{BJOP:BJOP1796, No2007, beller1971priming} and, in particular, task-repetition effects
+\cite{Gass1999549, sohn2001task}.  
+We investigate the effects that the content of earlier tasks has on workers'
+outputs in later tasks.  We call such effects 
+\textit{inter-task priming}.  Inter-task priming would amount to a kind of
+\textit{hysteresis}, meaning that HPU output is not only a function of the 
+current input, but also of the history of inputs.
 
-For one, cheating
-is a problem \cite{lease2011quality}, but straightforward methods have been 
-developed to screen out cheaters \cite{snow2008cheap, kazai2013analysis}.
-Still, there is a great deal of variance in worker attention and 
-accuracy \cite{kazai2013analysis}.  Researchers have found many factors that 
-modulate worker performance, such as level of pay\cite{kazai2013analysis}, 
+This work supplements the existing research into the factors that affect HPU 
+output.  Studies have shown that 
+there is a great deal of variance in worker attention and 
+accuracy \cite{kazai2013analysis}.
+Factors that affect the quality of HPU 
+output include level of pay\cite{kazai2013analysis}, 
 training\cite{le2010ensuring}, pre-screening 
 workers\cite{paolacci2010running}, and user-interface design
-\cite{Finnerty2013}.
+\cite{Finnerty2013}.  Research has also investigated \textit{framing}, 
+by disclosing to the worker the role of
+their task in a larger workflow context \cite{Kinnaird2012281}, 
+or describing a meaningful ultimate purpose of the project in which their
+task is a part \cite{chandler2013breaking}.  However, to our knowledge, no
+study has investigated the effects of inter-task priming.
 
-Here we are concerned with effects of a more subtle origin: the influence that
-prior tasks have on subsequent ones.  Psychology experiments document the 
-strong effects that a prior exposure to stimulus can have on participants' 
-performance in related tasks, a phenomenon known as \textit{priming}[***].  
-Strong 
-priming effects have been demonstrated for
-perceptual tasks such as the visual recognition of 
-objects \cite{BJOP:BJOP1796},
-auditory recognition of words \cite{BJOP:BJOP1826}, and the recognition
-of gender[***] and affect[***]: precisely the kinds of tasks well-serviced by 
-microtask platforms \cite{yuen2011survey, snow2008cheap}.
+To characterize such effects, we present a novel  
+\textit{algorithmic definition of priming}, and a corresponding method for
+measuring priming effects using machine learning algorithms.  
+Traditional methods for detecting priming are of limited use in characterizing 
+HPU hysteresis, because they are task-specific, and assume that priming results
+in a specific class of effects.
+Our approach can be applied to any task output, and does not rely on a prior 
+assumption about the particular effects brought about by priming.  This 
+enables the detection of priming even when the nature of the effects is not 
+understood.
 
-In the direction of priming, researchers have investigated various effects 
-due to \textit{framing}, by disclosing to the worker the functional role of
-their task in the workflow context \cite{Kinnaird2012281}, 
-or describing a meaningful ultimate purpose of the project in which their
-task is a part \cite{chandler2013breaking}.
-However, psychological experiments show that priming is strongest when 
-delivered through the same modality as the task [***].  This leads us to 
-investigate how priming that occurs \textit{during} a task influences output
-of subsequent similar tasks. We call such effects \textit{in-task priming}.
+In the present work we investigate inter-task priming for an image-labeling 
+task
+on the AMT platform.  Each worker is required to label ten images featuring 
+food and culture.  We regard these images as being made up of an 
+\textit{initial} and \textit{final set}, but, crucially, there is no
+distinction made between these sets, nor any interruption in the flow of tasks 
+from the view of the worker.
+The final image set is always the same, but we randomly assign one of three 
+initial sets, and analyze the effect this assignment has on labels attributed 
+to the final set.  We employ our novel method for detecting priming effects, as
+well as measuring effects on the content and specificity of attributed labels.
 
-We investigate the effects of in-task priming for an image-labeling task
-on the AMT platform.  Each worker is required to label a \textit{prior set} of
-images followed by a \textit{posterior set}, but no distinction is made between
-these sets from the perspective of the worker.  The posterior set is
-always the same, but workers are randomly assigned one of three prior sets.
-We analyze the labels workers attribute to the posterior set to see if it is 
-affected by the prior set.  As effects, we consider what aspects of image 
-content the workers choose to label (the \textit{label orientation}), and how 
-specific the labels are (the \textit{label specificity}), both of which have 
-direct consequence on the validity of using human computation to make 
-qualitative judgments.
+As a point of comparison, we also subject some groups of workers to a kind of
+\textit{framing}: we disclose a fictitious, semantically loaded name for the 
+task-requester.  The names are chosen to suggest the requester's interest in a 
+specific aspect of the image content.  One might reasonably expect that this 
+would orient workers to provide a greater quantity and specificity of labels 
+which relate to this ``preferred'' content.
 
-As a point of comparison, we subject some groups of workers to a kind of
-framing: we disclose a fictitious, semantically-loaded name for the 
-task-requester, chosen to signal an interest in a specific aspect of the 
-image content.  One might expect that this would strongly sway the labeling 
-of the workers.  We do detect the effects of framing, but, remarkably, we find 
-that in-task priming has a much stronger effect on label orientation and 
-specificity.
+Surprisingly, inter-task effects on label orientation and specificity are 
+much stronger than those brought about by framing tasks with a funder name. 
+Our results 
+show that initial tasks can introduce significant bias in subsequent worker 
+labeling.  On the other hand, we find evidence that a well-chosen progression 
+of tasks could tune workers to produce labels of greater (or lesser) 
+specificity.  This suggests that careful consideration should be given to
+the progression of tasks when designing a study using a microtask platform.
 
-This has major implications for the design of qualitative labeling and 
-classification tasks.  Our results show that prior tasks can introduce 
-significant bias in subsequent worker labeling.  On the other hand, our 
-results suggest that the progression of tasks can also be used to tune 
-workers to produce more nuanced output.
-
-In psychology, priming is defined as the effect in which a prior stimulus leads
-to faster or more accurate responses in a subsequent task than without the
-stimulus, or where the stimulus allows the experimenter to the elicit 
-responses from subsequent stimuli that are less intense or noisier [***].
-However priming might have many effects other than those traditionally 
-measured.  We are interested in studying the effects of priming in a human 
-computation, we adopt a more general view of priming as HPU hysteresis.
-
-For this purpose, we present an algorithmic definition of priming that
-yields a powerful method for detecting priming without knowing ahead of time 
-what effects one is looking for.  We demonstrate that this tool is capable of 
-distinguishing the priming treatments in our experiment even when the 
-differences are subtle.  We expect such a tool will have wide applications 
-outside computer science.
+Even when we are unable to detect priming in the form of a direct
+influence on label orientation or specificity, our novel measurement approach 
+clearly detects priming. This demonstrates a remarkable feature of the 
+approach, whereby priming effects can be quantified without knowing the nature 
+of said effects.
 
@@
 
-One difficulty with the notion of priming is that there appears to be no 
-defensible notion of an ``unprimed state''.  A participant always approaches
-a task in \textit{some} state of mind.  This will be influenced by her
+In psychology, the effects of priming are usually measured in terms of a 
+change in the  
+speed or accuracy of responses in a task, or in the ability to recognize a 
+stimulus object (e.g. a spoken word or an image) when the object is noisier, 
+fainter, or briefer [***].  Methods are also employed to measure processes
+in the brain of the participant, such as by fMRI.  These approaches are 
+well-suited to studying the underlying psychological mechanisms at work.
+
+Our purpose is different: we are interested in assessing the ramifications
+that priming of HPUs could have on the processes in which they are employed.
+This influences the approach we take to measurement in two ways.  First, we 
+switch from focusing on the internal mechanisms of HPUs to focusing strictly 
+on the HPU outputs.  Second, since we cannot \textit{a priori} know the 
+application for which HPUs are being employed, we favor generality in the 
+kinds of effects that can be detected.  We would like to measure any effects
+that could in principle impact the application.  These considerations motivate
+us to define priming effects in terms of algorithmic distinguishability of 
+the output.
+
+One difficulty in constructing a definition of priming is that there would 
+appear to be no defensible notion of a ``neutral'' or ``unprimed state''.  A 
+participant 
+always approaches a task in \textit{some} state of mind.  If no priming 
+condition is applied, then the participant is simply primed by her
 exposures prior to the experiment, which cannot be known by the experimenter.  
-In our experiment, for example, we include a prior image set that is in some
-sense ``neutral'', but it is by no means a control group. The particular 
-images used would arguably induce different priming than that induced by 
-another set that was, in its own way, ``neutral''.
-We avoid this difficulty by defining priming relatively, and speak of one
-treatment being \textit{differently primed} from another.
+While arguments can surely be made that one treatment or another is 
+\textit{more} 
+``neutral'', we refrain from proposing a canonical ``null priming treatment''. 
+Instead, we define priming relatively, and speak of one treatment being 
+\textit{differently primed} from another.
 
-Another factor that we must consider is that the effects of priming will
+A definition of priming must also consider that the effects of priming will
 manifest differently depending on the task that participants perform 
-subsequent to priming.  Said differently, two priming treatments that
+subsequent to priming:  two priming treatments that
 produce markedly different output for one task might be 
 indistinguishable under another task.  Thus, we define priming
-in relation to the task.
+with respect to a task.
 
-A final factor to consider is that, individuals who are in the same priming 
-treatment will still in general produce different output for a task,
-due to the natural variance between people.  Therefore, we define priming in 
-relation 
-to populations, not individuals.
+A final factor to consider is that people will always differ in their initial
+knowledge, specific aptitudes, and in many other intrinsic aspects.  Moreover,
+priming may not be ``complete'', in the sense that people's experiences before
+priming may continue to have residual effects.  Therefore, we define priming 
+in relation to populations, which we regard as having stable distributions of
+such latent attributes.
 
-With these considerations, consider two populations of people 
-$\mathcal{J}$ and $\mathcal{K}$, that produce respectively two populations of 
-outputs $\mathcal{L}$ and $\mathcal{M}$ during the completion of a task 
-$\mathcal{T}$:
+To set up the definition, when a population of people $\mathcal{J}$ performs
+a task $\mathcal{T}$ thus producing a population of task-outputs $\mathcal{L}$,
+we will write $\mathcal{T}(\mathcal{J}) = \mathcal{L}$. We will also write 
+$\mathcal{T}(j) = \ell$ to indicate that a single person, $j$, output $\ell$ 
+during $\mathcal{T}$.
 
@@
 	\upshape
-	$\mathcal{J}$ and $\mathcal{K}$ 
+	Two mutually exclusive populations of people, $\mathcal{J}$ and 
+	$\mathcal{K}$, are uniformly and randomly subsampled from an initial 
+	population $\mathcal{P}$, are exposed to (possibly) different priming 
+	treatments, and then perform a task $\mathcal{T}$, 
+	producing task-outputs $\mathcal{T}(\mathcal{J})$ and 
+	$\mathcal{T}(\mathcal{K})$.
+	We say that $\mathcal{J}$ and $\mathcal{K}$ 
 	\emph{differ in priming by a degree at least $\theta$},
 	if there exists an algorithm $\mathcal{A}$ that takes as input 
-	$L \subset \mathcal{L}$ and $M \subset \mathcal{M}$ and the output 
-	$o$ of a person $p$ chosen with equal probability from either 
-	$\mathcal{J}\setminus J$ or $\mathcal{K}\setminus K$, 
-	such that $\mathcal{A}$ determines the set from which $p$ was drawn
+	$\mathcal{T}(J)$, $\mathcal{T}(K)$, and $\mathcal{T}(p)$,
+	where $J \subset \mathcal{J}$, $K \subset \mathcal{K}$, and $p$ is a 
+	person chosen with equal probability from either $\mathcal{J}\setminus J$ 
+	or $\mathcal{K}\setminus K$, 
+	such that $\mathcal{A}$ outputs the set from which $p$ was drawn
 	($\mathcal{J}$ or $\mathcal{K}$) with accuracy $\frac{1+\theta}{2}$.  
@@
 In the language of computer science, $\mathcal{A}$ is a classifier.  Thus,
-intuitively, if there exists a classifier that can distinguish two populations,
-then they are differently primed.
+intuitively, if there exists a classifier that can distinguish populations 
+$\mathcal{J}$ and $\mathcal{K}$ based on their outputs, then they are 
+differently primed.
 
@@
 
-In practice we do not anticipate serious difficulty in choosing a classifier
-and establishing a meaningful value of $\theta$.  One of the simplest 
-classifier algorithms, the \textit{Naive Bayes classifier}, performs very 
-nearly as well as the most sophisticated classifiers in nearly all 
-applications [**].  Therefore, we submit $\theta_\text{NB}$, as determined by 
-a Naive Bayes classifier, to be a general-purpose measure of priming 
-difference.
+Note that this definition admits special cases that are equivalent to the
+traditional psychological definitions of priming.  If one can show by an
+experiment that 
+speed, accuracy, or the like, are statistically different for two priming 
+treatments, then said experiment could itself be run as a classifier.
+
+This definition substitutes one choice for another: given a task
+and two priming treatments, the experimenter need not choose specific effects
+to look for, but must instead choose a classifier.  This choice is inherently
+less restrictive.  Many general purpose classifiers exist that perform
+well in diverse applications [***].  The Naive Bayes classifier stands out as 
+a suitable first test to quantify the effects of priming,
+because it is simple to implement and requires no domain-specific tuning of 
+parameters [***].  We adopt this classifier in the present work and 
+denote the measured differences in priming as $\theta_\text{NB}$ to distinguish
+them from the theoretical value, $\theta$.
 
 \subsection*{Experimental Setup}
-We solicited 900 AMT workers to perform an image labeling task.  The workers
-were randomly assigned to one of seven treatments shown in 
-\textbf{Table 1}.  Workers were first shown brief instructions.
-Depending on their treatment, they were then either shown the name of 
-a research funder followed by a prior image set, or they were immediately 
-shown a prior image set. When shown, the funder name was either
-``The Global foundation for Cultural Recognition'', or 
-``The National Foundation for Nutritional Awareness''.  Finally, workers were 
-presented the posterior image set, which was the same for all treatments.
+We solicited 900 AMT workers to perform an image-labeling task relating to
+food and culture.  The workers were randomly assigned to one of seven 
+treatments shown in \textbf{Table 1}.  Workers were first shown brief 
+instructions.  Depending on their treatment, workers were then shown the 
+name of a research funder, or this step was skipped.  When shown, 
+the funder name was either
+``The Global Foundation for Cultural Recognition'', or 
+``The National Foundation for Nutritional Awareness''.  Next, workers were
+shown ten images, one at a time, and were required to label each image with
+five descriptive labels.  For the purpose of analysis, we divide the images
+into the \textit{initial} and \textit{final} sets, which are respectively the 
+first five and last five images shown.  However, from the perspective of the 
+worker, there was no 
+distinction or interruption between the initial and final sets. 
+The initial set was chosen from one of three sets, depending on the 
+treatment, while the final set was always the same.
 
-The prior and posterior images sets both consist of five images. Workers had
-to provide five labels for each image.  For the posterior image set we chose 
+For the final image set we chose 
 images that contain prepared meals and feature a prominent, identifiable 
@@
 would elicit labels focusing food or culture (or both).
-
-One of the prior image sets, which we call \textit{ambiguous}, was chosen to
-be very similar to the posterior image set, in the sense that it consists of
+One of the initial image sets, which we call \textit{ambiguous}, was chosen to
+be very similar to the final image set, in the sense that it consists of
 images of prepared meals.  However, the ambiguous image set was chosen such 
@@
 (see \textbf{Fig. 2}).  
-The \textit{cultural} prior set features iconic cultural scenes, but no food 
+The \textit{cultural} initial set features iconic cultural scenes, but no food 
 at all (see \textbf{Fig. 3}).  Finally, images from
-the \textit{ingredients} prior image set depict separated ingredients, but, 
+the \textit{ingredients} initial image set depict separated ingredients, but, 
 like the ambiguous set, were chosen to avoid prominent cultural features (see 
@@
 \subsection*{Results}
-\paragraph{The priming of all treatments was easily detectible.}
-We test for priming effects using our definition proposed in the introduction,
-implemented with a Naive Bayes classifier.  \textbf{Figure 5} shows
-the classifier performance in distinguishing between different pairs of 
-treatments based on workers' labels for the posterior images, and the corresponding
-value for $\theta_\text{NB}$.
+\paragraph{Earlier tasks and framing both prime workers.}
+We tested for priming effects using our definition proposed in the 
+introduction, implemented with a Naive Bayes classifier.  
+The classifier distinguished the various treatments from one another (pairwise)
+with high accuracy, confirming that both priming modalities 
+(inter-task and framing) were effective (\textbf{Fig. 5}).  Remarkably, the 
+classifier not only 
+distinguished treatments tending toward ``different orientations'' 
+(e.g. $\textsc{cult}_{img}$ and $\textsc{ingr}_{img}$; \textbf{Fig. 5A}), 
+it also distinguished treatments that one might expect would have similar
+effects.  For example the greatest accuracy was achieved in 
+distinguishing $\textsc{ingr}_{img}$ and $\textsc{ingr}_{fund, img}$, both
+of which are primed for a focus on food 
+(see \textbf{Fig. 5B}).
 
-The classifier distinguishes the various treatments from one another (pairwise)
-with high accuracy, confirming that both priming modalities 
-(in-task and framing) were effective.  Remarkably, the classifier not only 
-distinguishes treatments tending toward different ``orientations'' 
-(e.g. $\textsc{cult}_{img}$ and $\textsc{ingr}_{img}$, \textbf{Fig. 5A}), 
-it also distinguishes workers from treatments of the \textit{same} 
-orientation with high accuracy 
-(e.g. $\textsc{cult}_{img}$ and $\textsc{cult}_{fund, img}$, \textbf{Fig. 5B}).
-Clearly the algorithmic definition of priming and its implementation as 
-$\theta_\text{NB}$ provides a sensitive means for detecting the presence of
-primed populations.
+Next we looked at the degree to which labels from individual final images 
+reveal priming.  It would stand to reason that, as workers proceed through 
+the final images, the effects of priming might be ``washed out''.  
+Indeed, when labels from just one of the images
+in the final set were used, $\theta_\text{NB}$ was lower for later images (see
+\textbf{Figure 6}).
+Understanding the dynamics of priming wash-out in greater detail is an 
+important direction for future work.
 
-Next we look at the degree to which labels from individual posterior images reveal 
-priming.  It would stand to reason that, as workers proceed through 
-the posterior images, the effects of priming might be ``washed out''.  
-\textbf{Figure 6} shows the
-performance of the Naive Bayes classifier when using the labels workers provide
-for particular images.  This does show that, as we look to later posterior images, 
-the treatments' difference in priming, $\theta_\text{NB}$, declines.  In future
-work, we plan to investigate the dynamics of priming wash-out in greater 
-detail.
-
-\paragraph{Priming orients focus.} Having demonstrated differential 
-priming, we investigate the \textit{nature} of the priming.  To this
-end, we construct an ontology of all the labels attributed to
-the posterior images.  The ontology is a directed acyclic graph of terms,
+\paragraph{Earlier tasks orient focus during later tasks.} Having 
+demonstrated both inter-task and framing effects, we next
+investigated the \textit{nature} of these effects.  To this
+end, we constructed an ontology of all the labels attributed to
+the final images.   
+The ontology is a directed acyclic graph of terms,
 with directed edges drawn from abstractions toward instances.  For example,
@@
 
-The ontology allows us to algorithmically count the number of labels that are
-of cultural orientation (\texttt{ganesha}),  food orientation
-(\texttt{bread}), or both (\texttt{dim sum}).  We do this by counting the
-number of labels having have inbound paths leading from the abstract clasess 
-\texttt{culture} and/or \texttt{food}, which are present in the ontology.
-\textbf{Figure 7} plots the composition of labels (fraction of culture- and 
-food-oriented labels) for different treatments and images.  In 
-panel \textbf{7A}, we can see that, before considering the effects of 
-treatments, there is significant variance in the composition of labels 
-for different images, probably due to inherent differences in their content.  
-For our purpose, we are interested in the systematic differences between 
-treatments.
+We counted the number of labels that were of cultural- 
+or food-orientation,
+based on whether the label had inbound paths from the 
+abstract classes \texttt{culture} and/or \texttt{food} in the ontology. Of 
+course, food is a central feature of culture, so many labels turned out to be
+both culture- and food-oriented in this sense.  Nevertheless, there were many 
+food-oriented labels, such as \texttt{bread}, which were culturally highly 
+ambiguous, and did not have an inbound path from \texttt{culture} in the 
+ontology.  Meanwhile, there were many non-food, culture-oriented labels, such
+as \texttt{russian dolls}.
 
-In \textbf{Fig. 7B} we exhibit the composition of labels for the various 
-treatments (aggregating together the labels for all images of a given 
-treatment).  We can see that the treatments which expose workers to the
-cultural image sets do elicit significantly more culture-oriented and fewer
-food-oriented labels compared to the other treatments ($\alpha=0.05$).  It 
-also appeas that all the $\textsc{ingr}_x$ treatments produce more 
-food-oriented labels, but we cannot assert this at significance 
-$\alpha = 0.05$.
+%The ontology often contained 
+%alternative labels for food which were culturally more specific, for example 
+%\texttt{roti}, which are attributed cultural-orientation in the ontology.  
+%This provided a degree of freedom upon which inter-task priming and framing 
+%might act.
 
-The effect size, however, is somewhat small.  Since we observed that priming 
-difference ``wears off'', it may be the case 
-that aggregating label compositions for all images actually masks the effects. 
-In \textbf{Fig. 7C}, we plot label compositions for only the first posterior
-image.  This reveals that, in labeling the first posterior image, workers in 
-$\textsc{cult}_{img,x}$ were strongly influenced to favor culture- over 
-food-oriented labels.  The effect was strong enough to essentially reverse 
-the proportions of these labels compared to the other treatments.  
-This shows that in-task priming effects can dramatically distort the results 
-of human computation tasks.
+Taking the labels from all treatments together, we observed significant 
+variance in the label composition (fraction of food- and culture-oriented 
+labels) between the various 
+images in the final set (see \textbf{Fig. 7A}).  This is to be expected, due 
+to differences in the content of the images; for our purpose, we are 
+interested in the systematic differences between treatments, not between 
+images.
 
-We next inspect this effect longitudinally, that is, as a function of 
-the posterior image.  To do so, we compute the \textit{excess cultural orientation} 
+We compared the composition of labels between different treatments by
+aggregating labels attributed to all the images from the final set within a 
+given treatment (see \textbf{Fig. 7B}).  
+Treatments that began by labeling the cultural images, 
+subsequently attributed significantly more culture-oriented and fewer 
+food-oriented labels to the final images, as compared to the other 
+treatments ($\alpha=0.05$).  Meanwhile, all of the $\textsc{ingr}_x$ 
+treatments produced more food-oriented labels, but we cannot assert a 
+systematic effect at a significance of $\alpha = 0.05$.
+
+Although the effect on label composition, brought about by having workers 
+initially label cultural images, was statistically significant, the effect 
+size was admittedly somewhat small (\textbf{Fig 7B}). Since we observed that 
+priming 
+difference ``wears off'', we analyzed label composition on a per-image basis.
+Indeed, for the first image in the final set, workers from 
+$\textsc{cult}_{img,x}$ strongly favored culture- over 
+food-oriented labels (\textbf{Fig. 7C}). The effect was strong enough to 
+essentially invert the proportions of culture- and food-oriented labels 
+relative to all other treatments, which favored food-oriented labels.  
+This shows that \textit{inter-task effects can dramatically distort the results
+of human computation tasks}.
+
+To exhibit the effect longitudinally, as a function of the number of images
+labeled since exposure to the initial set, we computed the 
+\textit{excess cultural orientation} 
 ($\Delta_{cult}$) of
@@
 Intuitively, this is intended to capture how much 
-more culture-oriented $\textsc{cult}_{img}$ is than $\textsc{ambg}$.  
-\textbf{Figure 8} plots $\Delta_{cult}$ as a function of posterior image, $i$. 
-This clearly shows the strong influence on the labels attributed to the first 
-posterior image,
-but for later images the effect immediately drops below statistically 
-significant levels, while remaining always positive.
+more culture-oriented the labels from $\textsc{cult}_{img}$ are than those
+from $\textsc{ambg}$, for image $i$.
 
-\paragraph{Priming affects attention to detail.} Using the ontology described
-in the previous section, we compare treatments in their degree of specificity.
+The results from this calculation show the strong influence of the 
+initial image set on the labels attributed to the first image in the final set
+(see \textbf{Fig. 8}).  However, for later images, the effect immediately 
+drops below statistically significant levels, while remaining always positive.
+
+\paragraph{Earlier tasks affect attention to detail during later tasks.} 
+Using the ontology described
+in the previous section, we compared treatments in their degree of specificity.
 When comparing two labels $\ell_1$ and $\ell_2$ produced by different workers,
@@
 
-where $\mathcal{U}$ and $\mathcal{V}$ are treatments, taken as sets of workers.
-See \textbf{Materials and Methods} for statistical analysis of the relative 
-specificity of two treatments. 
-\textbf{Figure 9} 
-exhibits the results.
+where $\mathcal{U}$ and $\mathcal{V}$ are treatments, formally taken
+as sets of workers.
 
-In panel \textbf{9A}, we see that when we compare each of the treatments to
-$\textsc{ambg}$, all treatments in which a non-ambiguous prior image set was 
-displayed have \textit{lower} specificity (though not all at $\alpha=0.05$).  
-In panels \textbf{9D} and \textbf{9G} we compare the same pairs of treatments, 
-but restrict to words of culture- and food-orientation respectively (words
-of both orientations are excluded).  These plots show that the relative lack 
-of specificity is mainly attributable to food-oriented words.
+When we compared each of the treatments to \textsc{ambg} in this way, 
+all treatments in which a non-ambiguous initial image set was 
+displayed have \textit{lower} specificity 
+(most, but not all, at $\alpha=0.05$; see \textbf{Fig. 9A}).  To understand
+how relative specificity is being attributed, we repeated the calculation of 
+specificities relative to \textsc{ambg}, but including only the non-food-, culture-oriented 
+labels (see \textbf{Figs. 9D}), and only the non-culture-, food-oriented labels
+(see \textbf{Fig. 9G}).  These calculations show that the loss of 
+specificity of treatments that initially labeled images other than those from
+the ambiguous set, was attributable to specificity of food-oriented labels, 
+but not culture-oriented ones.
 
-Likewise, in panels \textbf{9B}, and \textbf{9C}, 
-wherever we see significant differences in specificity, it turns out that
-these differences appear to mainly be due to differences in food specificity,
-as can be seen by comparing to panels \textbf{9E}, \textbf{9F}, \textbf{9H}, 
-and \textbf{9I}.  In fact, looking to panels \textbf{9D}, \textbf{9E}, and 
-\textbf{9F},
-there are no significant differences in cultural specificity to speak of. 
-Clearly, food and culture are not on equal footing in the experiment.  Various 
-psychological explanations are possible, and we explore these in the 
-discussion below.
+It might be the case that labels of a certain semantic connection are less 
+influenced by inter-task effects with regard to specificity. Alternatively,
+there may have simply been too few cultural labels for an effect on specificity
+to manifest (see \textbf{Fig. 7}).
+The lower number of cultural labels might be due to the fact that people's 
+vocabulary for cultural concepts is less diverse than that for food, or that 
+culture, being more abstract, is less ``imageable'' \cite{Swaab200299}.
+
+Nevertheless, the dramatic drop in overall specificity relative to 
+\textsc{ambg}, induced when workers begin by labelling the culture or 
+ingredients images, demonstrates that 
+inter-task effects can strongly influence the specificity of task output.
+This is likely to be a major quality factor in nearly all HPU-driven studies.
+
+\td{count the number of occurrences of cultural and food-oriented labels, 
+	to see if the non-responsiveness of culture had to do with restricted
+number of labels}.
 
@@
 
-\paragraph{In-task priming is strong.}  We expected that the funder names 
-would overtly signal to workers that the requester was interested in a 
-specific aspect of image content.  On the other hand, we did not 
-expect the prior image set, though enriched in certain content, to overtly signal interest.  In turn, we expected that a signal of intent would 
-strongly affect how the workers approach the task.  Perhaps the most 
-unexpected result of this study is that the prior image set influenced label 
-orientation and specificity far more than did framing the task by naming the
-funder.
-
+\paragraph{Inter-task effects are strong.}  We expected that by showing
+workers the funder names ``The Global Foundation for Cultural Recognition'',
+and ``The National Foundation for Nutritional Awareness'', workers would 
+be strongly influenced, interpreting this as and indication of what content 
+is salient (culture or food).
+To our surprise, it turned out that changing the initial set of images that
+workers labeled had a much stronger influence on label orientation and 
+specificity than did framing the task by naming the funder.
 This points to a serious hazard in conducting studies using human computation,
@@
 eliminated surrounding influences to every practical extent, 
-\textit{the greatest source of bias might lurk in the task itself}.
+\textit{the greatest source of bias might lurk in the tasks themselves}.
 
-Randomized ordering and replication of tasks is one method to abate this.
-But the requester could also include an initial set of tasks as a 
+Replication of tasks with randomized ordering is one way to abate inter-task
+effects.  But the requester could also include an initial set of tasks as a 
 ``tuning phase''.  During the tuning phase, workers would be primed in a 
@@
 orient worker focus in a useful manner.  Moreover, this phase could double as a
-screening phase to select quality workers [***].
-
-\paragraph{The rate of priming wash-out depends on how it is measured}
-Seeing that $\theta_\text{NB}$ declines as one proceeds through the test 
-images (\textbf{Fig. 6}), one should ask whether this actually represents 
-priming wash-out.  One might also attribute this to 
-differences in the \textit{content} of the images. It is interesting to 
-compare this to the result in \textbf{Fig. 8}, which
-shows that the effect of exposure to the prior image set on 
-\textit{orientation} (culture vs. food) certainly
-decays much more quickly than the overall effects detected by
-the classifier.  This appears to be consistent with the notion that the 
-mechanisms of priming are multiple and complex [***].  Here we again see an
-advantage of using $\theta_\text{NB}$ to measure priming: it is able to detect 
-differences in priming even after the expected effects have worn off.
+screening phase to select quality workers [***].  However, a deeper 
+understanding of the persistence of inter-task effects is needed to know if 
+this is viable.
 
 \paragraph{Subtle priming effects can be detected with $\theta_\text{NB}$.}
-While the Naive Bayes classifier is able to distinguish all treatment pairs,
-many such pairs cannot be distinguished on the basis of label orientation and 
-specificity 
-(for example $\textsc{cult}_{fund}$ and $\textsc{ingr}_{fund}$).
-One might expect, then, that $\theta_\text{NB}$
-for the pair $\textsc{cult}_{fund}$ and $\textsc{ingr}_{fund}$, would be 
-smaller than for, say, $\textsc{cult}_{img}$ and \textsc{ambg}.  
-\textbf{Figure 5A} shows that this is not the case.  Thus, priming can be 
-strong without generating the effects one might expect, and in many 
-circumstances, such effects might go entirely undetected.  We believe this 
-is a strong argument in support of using $\theta_\text{NB}$ to determine 
-whether priming has occurred, without making narrow assumptions about what the 
-effects of priming will be.
+The Naive Bayes classifier uses the frequency of occurrence of all labels to
+classify workers.  Thus, it incorporates a quite general class of effects which
+could be subtle and difficult to anticipate.  This explains why 
+$\theta_\text{NB}$ 
+between $\textsc{cult}_{fund}$ and $\textsc{ignr}_{img}$ can be comparable with
+that between $\textsc{cult}_{fund}$ and $\textsc{cult}_{fund,img}$ 
+(see \textbf{Fig. 5}), even though the latter differ much more in label 
+orientation and specificity.  Similarly, while the differences in label
+orientation between $\textsc{cult}_{img}$ and $\textsc{ingr}_{img}$ drop below 
+significance after the first test image (see \textbf{Fig. 8}), 
+$\theta_\text{NB}$ remains significant through to the last image.
 
-\paragraph{Priming did not affect cultural specificity.}
-It was quite surprising that the effects on workers' specificity was 
-essentially
-confined to food-oriented labels, and that we observed no significant movements
-in cultural specificity.   This might reflect the different roles
-played by food and culture in the human lexicon.  This seems plausible when we 
-consider the vital role of food on the one hand, and the bias in social 
-cognition known as \textit{outgroup homogeneity}\cite{Vala2012491,Ray2012387,Ishii2011159,Boldry2007157}.
-Outgroup homogeneity is a phenomenon whereby people perceive fewer 
-differences between members of an outgroup than between members of their 
-ingroup \cite{Boldry2007157}.  One manifestation is that people 
-spend less time observing outgroup members when asked to make a character 
-judgment \cite{Vala2012491}.  This phenomenon can be explained in terms of 
-adaptiveness: social cognition regarding one's ingroup is more consequential
-\cite{Vala2012491}.  Thus, it seems plausible that a nuanced cultural 
-vocabulary might be of limited advantage.  On the other hand,
-the differences between food and poison can be nuanced indeed, and so it would
-not be surprising to find that people have a more nuanced vocabulary for 
-food than for culture.
+This demonstrates a powerful feature of the definition of priming in terms of 
+algorithmic distinguishability.  Leveraging classifier implementations from
+machine learning, one can systematically screen treatments that had allegedly 
+been primed differently, against a very large class of potential effects.  This
+would allow the analyst to detect that priming had occured without having to 
+know anything about what was done to achieve it.
 
-Another explanation is that food is more so-called \textit{imageable} than 
-culture, because although aspects of culture can be depicted in an image,
-culture itself cannot.  Studies show that the brain processes high- and 
-low-imageable words differently \cite{Swaab200299}, and it would not be 
-surprising if the effects of priming on image labeling were modulated by how 
-imageable the labels are.
+\paragraph{Inter-task similarity drives nuance.}
+We observed already that treatments which started by labeling the the 
+culture or ingredients image sets had less specificity compared to 
+those beginning with the ambiguous image set.  One possible explanation is that
+this is a manifestation of \textit{negative priming}.  Negative priming is a 
+phenomenon in which a person becomes desensitized to non-salient stimuli to 
+which she is repeatedly exposed [***].  Consider that workers who initially 
+labeled the ambiguous image set had already seen five images showing 
+prepared meals by the time they labeled the first test image.  At that point,
+the worker might not regard the labels \texttt{food} or \texttt{meal} to be 
+salient, since they do not distinguish the image she is labeling from any of 
+the others she had seen already.
 
-Even with the above explanations, is surprising that 
-$\textsc{cult}_{img,x}$ is simultaneously induced to 
-produce a higher quantity of culture-oriented labels but not a higher
-specificity of culture-oriented labels.  Since effects on 
-label composition were only appreciable for the first posterior image 
-(see \textbf{Fig. 8}), we also
-performed the specificity analysis restricting to labels from the first
-posterior image (see \textbf{Fig. S1}).  But even when focusing on the first 
-posterior image we see no significant increase in cultural specificity for 
-$\textsc{cult}_{img,x}$.  Thus, we observe that priming effects on 
-orientation of focus and label specificity do not necessarily correlate.
+We are suggesting that, although workers are not instructed to compare
+images in any way, prior tasks nevertheless create a frame of reference
+relative to which the content of later tasks are judged.  This in turn 
+influences the perception of salience. Thus, in a series of subjective 
+characterization tasks that have very similar content, the worker's focus 
+will tend to be directed away from generic, shared attributes, towards those 
+attributes that are specific and distinguishing.
 
-\paragraph{Similarity drives nuance.}
-We observed already that treatments primed with the 
-culture or ingredients image sets have less specificity compared to 
-\textsc{ambg}.  We will now argue that the difference in specificity
-can be explained by how ``similar'' a treatment's prior 
-images are to the posterior images. The characterization of the content of an 
-image is deeply complex, and has been approached from the perspectives of art\cite{panofsky1939studies,shatford1986analyzing},
-psychology\cite{Tversky1977327}, and information retrieval\cite{Jaimes20002}.  Here, we will take the simplistic 
-approach of defining the similarity between two sets of images as the number of
-labels in common between both sets.
+To support this
+claim, we must to assess the perceived similarity between the various 
+initial image sets (ambiguous, cultural, and ingredients) and the test set.  
+The characterization of image content is deeply complex and has been 
+approached from the perspectives of 
+art\cite{panofsky1939studies,shatford1986analyzing},
+psychology\cite{Tversky1977327}, and information retrieval\cite{Jaimes20002}.  
+However, using the labels attributed by workers, we can operationalize
+the similarity between two image sets, $X$ and $Y$, as the Jacquard index 
+between the sets of labels attributed to them:
+\begin{align}
+	\text{Sim}(X,Y) = \frac{L(X) \cap L(Y)}{L(X) \cup L(Y)},
+\end{align}
+where $L(X)$ denotes the set of labels attributed to $X$.  In calculating
+the similarity, we used the labels attributed by treatments that were not 
+shown a funder name:  \textsc{ambg}, $\textsc{cult}_{img}$, and 
+$\textsc{ingr}_{img}$.
 
-\dots Results to follow \dots
-
-This matches the intuition that the ambiguous set is most similar to the 
-posterior set in that they both feature prepared meals, while the ingredients
-set is more similar to the posterior set than is the cultural set, since the
-ingredients set at least features food prominently.  Although similarity 
-between the cultural set and the posterior set could be argued on the basis
-of cultural content, this content is less imageable, more abstract, and
-and according to the theory of \cite{Jaimes20002} should require more 
-knowledge to ascertain.
-
-Under our measure of similarity, our results show that
-more specific labels are provided to the posterior images when the prior and
-posterior image sets are more similar.
-An appealing explanation for 
-this is the notion of \textit{negative priming}, wherein the participant
-becomes desensitized to stimuli that do not seem salient [***].  Thus, after 
-workers had been shown successive images of prepared meals in the ambiguous
-prior set, they would be much less inclined to provide generic terms such as 
-\texttt{food} or 
-\texttt{meal} to images in the posterior set, since these terms would no 
-longer seem salient in the 
-context of their priming treatment.
+Calculated in this way, the ambiguous image set was the most similar to the 
+test set, followed by the ingredients set, and the cultural image set
+was most different from the test set (see \textbf{Table 2}.)  Comparing
+this to the relative specificities calculated for these treatments 
+(see \textbf{Fig. 9}) confirms that workers who labeled an initial 
+image set that was more similar to the test set attributed more specific 
+labels to the test set.
 
 \paragraph{Priming for better HPU performance.}
-Thus, if one seeks very nuanced sorting or labeling from human workers, 
-we recommend assembling the HPUs in a hierarchical fashion, with the 
-HPUs at the top of the hierarchy performing coarse sorting (or labeling), 
-splitting objects into streams to be handled by HPUs performing more nuanced 
-work.  To implement this for an
-image-labeling task, one could first serve the images for coarse labeling,
-then cluster the images based on the labels and a language model, and then 
-re-serve the images, ensuring that each HPU operates on images from a single 
-cluster.  The more ``homogeneous'' a cluster of images, the more one might gain
-by serving the cluster for another round of labeling.
+Thus, if one seeks very nuanced characterizations by human workers, 
+our results suggest that the artifacts to be characterized should first 
+be sorted into classes that are internally similar. This could be accomplished 
+with an iterative approach, which begins with a first, coarse 
+characterization of unsorted artifacts. The coarse characterization could then 
+be used to sort the artifacts, which could then be served for finer 
+characterization.  The sorting and re-characterization could in principle be
+repeated several times.
 
-This exhibits an interesting difference between HPUs and CPUs.  In general,
+In effect, this creates a hierarchical workflow, where the first, 
+coarsely-characterizing HPUs provide a stream of artifacts that is split and 
+fed to other HPUs for finer characterization.  This workflow exhibits an 
+interesting difference between HPUs and CPUs.  In general,
 whenever an aspect of a problem can be parallelized when employing CPUs, one
-gains efficiency.  But in the case of hysteretic HPUs, we see an 
-example where one might lose efficiency through parallelization.
+gains efficiency.  But here, because of HPU hysteresis, we see an example where
+one might lose efficiency through parallelization.
 
 \subsection*{Conclusion}
-We demonstrated that in-task priming can have a strong effect.  
-For an image labeling task, in-task priming was stronger in its effects on 
-the orientation and specificity of labels than was the disclosure of funder 
-names chosen to signal the requester's interest in specific content.
-Employers on microtask platforms should 
-beware that strong biases may be introduced by the very tasks they provide.
-Further research into the nature of these effects is warranted.  At the 
-same time, in-task priming might be exploited to improve task output, for 
+Inter-task priming can have a strong effect.  
+For an image-labeling task, inter-task priming was stronger in its effects on 
+the orientation and specificity of labels than was the disclosure of 
+semantically loaded funder names.  Requesters on microtask platforms should 
+beware that strong biases may be introduced do to the particular succession
+of tasks they serve to workers.
+At the 
+same time, inter-task priming might be exploited to improve task output, for 
 example, to drive more (or less) nuanced responses.
@@
 We demonstrated that our algorithmic definition of priming, and its 
-implementation as the measure $\theta_\text{NB}$ provide a sensitive,
+implementation using a Naive Bayes classifier, provides a sensitive,
 general-purpose method for detecting priming.  Even when the expected effects 
-on label orientation and specificity could not be detected, $\theta_\text{NB}$ 
-was high.  $\theta_\text{NB}$ provides direct statistical evidence that 
-populations have been affected by priming, even when the effects are not 
-understood. Along with our proposed definition, we advocate a more general 
-view of priming as a form of hysteresis.
+on label orientation and specificity were slight, $\theta_\text{NB}$ 
+was significant.  $\theta_\text{NB}$ provides direct statistical evidence that 
+populations have been affected by priming, even when the nature of the 
+effects are not understood.
 
@@
 treatment. Workers were
-only allowed to participate once and could not see the prior or posterior 
+only allowed to participate once and could not see the initial or final 
 images, nor the funder names when previewing the task.
@@
 \end{align}
+\td{There are problems with this.  I'm still trying to figure out how to
+	calculate the variance properly.}
 $\text{Var}_V\{s(u,V)\}$ can be directly calculated as a sample variance.
@@
 	Nutritional Awareness''.  The ambiguous, cultural, and ingredients 
-	prior image sets are shown in \textbf{Figs. 2}, \textbf{3}, and 
+	initial image sets are shown in \textbf{Figs. 2}, \textbf{3}, and 
 	\textbf{4}.
@@
 	Posterior image set. These images were presented to all workers after the 
-	prior image set, in the order shown.
+	initial image set, in the order shown.
 
 \paragraph{Figure 2.}
-	Ambiguous prior image set. These images were presented to workers from 
-	certain treatments (see \textbf{Table 1}) in the order shown.
+	Ambiguous image set. These images were presented to workers from certain
+	treatments (see \textbf{Table 1}) as the initial image set, in the order 
+	shown.
 
 \paragraph{Figure 3.}
-	Cultural prior image set. These images were presented to workers from 
-	certain treatments (see \textbf{Table 1}) in the order shown.
+	Cultural image set. These images were presented to workers from 
+	certain treatments (see \textbf{Table 1}) as the initial image set, in the 
+	order shown.
 
 \paragraph{Figure 4.}
-	Ingredients prior image set. These images were presented to workers from 
-	certain treatments (see \textbf{Table 1}) in the order shown.
+	Ingredients image set. These images were presented to workers from 
+	certain treatments (see \textbf{Table 1}) as the initial image set, in the 
+	order shown.
 
@@
 composition of labels, aggregated over all treatments, as a function of 
-posterior image.
+final image.
 Panel B shows the composition of labels, aggregated over all images, as
 a function of treatment.  Panel C shows the composition of labels 
-attributed to the first posterior image by various treatments.
+attributed to the first final image by various treatments.
 
@@
 by $\textsc{cult}_{img}$ as compared to $\textsc{ambg}$, for various
-posterior images (see \textbf{Eq. 1} for calculation).
+final images (see \textbf{Eq. 1} for calculation).
 
@@
 Relative specificity of various treatments, for labels attributed
-to the first posterior image.
+to the first final image.
 Each panel shows the comparison between a basis treatment (inset) and 

### 2014-06-09 docs/publications/2014.05_PNAS/manuscript.tex
small manuscript update and update to analysis.py

@@
 increasingly serve as a cheap and fast means to engage experimental 
-participants and manually annotate of datasets in a research 
+participants and manually annotate datasets in a research 
 setting \cite{snow2008cheap}.  
@@
 in a specific class of effects.
-Our approach can be applied to any task output, and does not rely on a prior 
-assumption about the particular effects brought about by priming.  This 
+Our approach can be applied to any task output, and does not rely on prior 
+assumptions about the particular effects brought about by priming.  This 
 enables the detection of priming even when the nature of the effects is not 
@@
 
-In the present work we investigate inter-task priming for an image-labeling 
+In the present work, we investigate inter-task priming for an image-labeling 
 task
@@
 Our purpose is different: we are interested in assessing the ramifications
-that priming of HPUs could have on the processes in which they are employed.
+that priming of HPUs could have on the applications to which they are employed.
 This influences the approach we take to measurement in two ways.  First, we 
 switch from focusing on the internal mechanisms of HPUs to focusing strictly 
-on the HPU outputs.  Second, since we cannot \textit{a priori} know the 
-application for which HPUs are being employed, we favor generality in the 
-kinds of effects that can be detected.  We would like to measure any effects
-that could in principle impact the application.  These considerations motivate
-us to define priming effects in terms of algorithmic distinguishability of 
-the output.
+on the HPU outputs.  Second, we cannot \textit{a priori} know the 
+application for which HPUs are being employed, but we would like to measure 
+any effects that could in principle impact the application.  These 
+considerations motivate us to define priming effects in terms of the 
+algorithmic distinguishability of primed output.
 

### 2014-06-09 src/analysis.py

@@ -535,7 +535,7 @@ class NBCAnalyzer(object):
 		self.dataSet = data_processing.readDataset()
 
 
-	def testNBC(self, pTrainingSize=80, pTestSize=20, 
+	def testNBC(self, pTrainingSize=106, pTestSize=20, 
 		treatments=['treatment1', 'treatment2'], 
 		images=['test0'], pDoConsiderPosition=False, show=False):
 		'''

### 2014-06-09 src/analysis.py
update classifier to use larger test-set

@@ -10,7 +10,6 @@ a classifier to distinguish between treatments as a function of the image
 used (i.e., taking into consideration only the labels that worker instances
 attribute to a particular image, and varying the image).
 
-
 `Analyzer` is used to analyze the difference between treatments on the basis
 of an ontology of the words used.  So, for example, it can assess to what 
 degree the workers in one treatment are using more specific words than the 
@@ -35,6 +34,16 @@ import numpy as np
 # normal variate
 CONFIDENCE_95 = 1.96
 CONFIDENCE_99 = 2.975
+
+
+def theta_NB_significance(n,k_star):
+	significance = 0
+
+	for k in range(k_star, n+1):
+		significance += util.choose(n,k) * (0.5**n)
+	
+	print significance
+
 
 
 class Analyzer(object):
@@ -624,7 +633,7 @@ class NBCAnalyzer(object):
 
 			for i in range(numReplicates):
 				allImages = ['test%d' % i for i in range(5)]
-				result = self.testNBC(80, 20, comparison, allImages, True)
+				result = self.testNBC(86, 40, comparison, allImages, True)
 				try:
 					comparisonF1Scores.append(result.getF1(firstTreatment))
 					comparisonAccuracies.append(result.getOverallAccuracy())

### 2014-06-09 docs/publications/2014.05_PNAS/manuscript.tex

@@
 
-\textbf{Statistical significance for relative specificity.}
+\textbf{Statistical significance of $\theta_\text{NB}$.}
+We test the significance two population's measured $\theta_\text{NB}$ against 
+the null hypothesis that that the two populations are in fact identical:
+\begin{align}
+	\mathbf{H_0}: \theta_\text{NB} = 0 \\
+	\mathbf{H_1}: \theta_\text{NB} > 0
+\end{align}
+If the populations are in fact identical, then the probability that the 
+classifier correctly classifies a worker is $\frac{1}{2}$, and the probability 
+of getting $k$ classifications during a cross-validation with $n$ 
+test-classifications is:
+\begin{align}
+	\text{Pr}\{K = k | n \} = { n \choose k } \left(\frac{1}{2}\right)^n.
+\end{align}
+Then, we have statistical significance if 
+$\theta_\text{NB}$ is greater than a critical value, 
+$\theta_\text{NB}^*$:
+\begin{align}
+	\theta_\text{NB} \geq 2k^* - 1
+\end{align}
+where $k^*$ is the minimum value required to satisfy
+\begin{align}
+	\sum_{k \in \{k^*, \dots, n\}} \text{Pr}\{K = k | n \} < \alpha.
+\end{align}
+For a test-set of $n=40$ workers, and a significance of $\alpha = 0.05$, we
+have $k^*=26 \implies \theta_\text{NB}^* = 0.65$.
+
+\textbf{Statistical significance of relative specificity.}
 We used \textbf{Eq.~\ref{eq:specificity}} to compute the relative specificity

### 2014-06-09 src/plots.py
add parameter to computAllF1Accuracy: subplotComparisons

@@ -849,7 +849,11 @@ def plotValenceComparison(
 	print percentValences
 
 
-def computeAllF1Accuracy(numReplicates=50, fname='f1scores/all.json'):
+def computeAllF1Accuracy(
+	numReplicates=50,
+	fname='f1scores/all.json',
+	subplotComparisons=None
+	):
 	'''
 	Computes the F1 score for a naive bayes classifier built to distinguish
 	between all the interesting pairings of treatments.
@@ -859,19 +863,20 @@ def computeAllF1Accuracy(numReplicates=50, fname='f1scores/all.json'):
 	'''
 	fh = open(fname, 'w')
 
-	subplotComparisons = [
-		{'basis': 'treatment0', 
-		'subjects' : ['treatment1', 'treatment5', 'treatment6', 
-			'treatment2', 'treatment3', 'treatment4']}
+	if subplotComparisons is None:
+		subplotComparisons = [
+			{'basis': 'treatment0', 
+			'subjects' : ['treatment1', 'treatment5', 'treatment6', 
+				'treatment2', 'treatment3', 'treatment4']}
 
-		, {'basis': 'treatment1', 
-		'subjects' : ['treatment5', 'treatment6', 
-			'treatment2', 'treatment3', 'treatment4']}
+			, {'basis': 'treatment1', 
+			'subjects' : ['treatment5', 'treatment6', 
+				'treatment2', 'treatment3', 'treatment4']}
 
-		, {'basis': 'treatment2', 
-		'subjects' : ['treatment5', 'treatment6', 
-			'treatment3', 'treatment4']}
-	]
+			, {'basis': 'treatment2', 
+			'subjects' : ['treatment5', 'treatment6', 
+				'treatment3', 'treatment4']}
+		]
 
 
 	results = []

### 2014-07-19 docs/publications/2014.05_PNAS/figs.tex
add cross validation to classifier test
I have substancially changed how NBCAnalyzer works.  It uses proper
cross-validation (instead of random replicates, which has no
interpretable statistics).

In the course of doing this, I realized that pollution was hapenning in
my Naive Bayes Classifier -- the training set included the test set.
Correcting this obviously changed the results, actually in a good way.

I altered the plotting of classifier results -- both the
cross-comparison one and the longitudinal one.  In the cross-comparison
one, I added more pairwise comparisons, so now the comparison

@@
 \begin{figure}
-	\includegraphics{figs/f1-thetas.pdf}
+	\includegraphics{figs/f1-thetas_full_pairwise50_img1.pdf}
 	\caption{ $F_1$ score and $\theta_\text{NB}$ for the various 
@@
 \begin{figure}
-	\includegraphics{figs/longitudinalF1scores-t1-t2.pdf}
+	\includegraphics{figs/longitudinalF1scores-t0-t1_50.pdf}
 	\caption{ $F_1$ score and $\theta_\text{NB}$ for the classification of 
-	$\textsc{cult}_{img}$ and $\textsc{ingr}_{img}$ using a Naive Bayes 
+	$\textsc{cult}_{img}$ and $\textsc{ambg}$ using a Naive Bayes 
 	classifier.  The classifier is provided only the labels attributed to

### 2014-07-19 docs/publications/2014.05_PNAS/manuscript.tex
add cross validation to classifier test
I have substancially changed how NBCAnalyzer works.  It uses proper
cross-validation (instead of random replicates, which has no
interpretable statistics).

In the course of doing this, I realized that pollution was hapenning in
my Naive Bayes Classifier -- the training set included the test set.
Correcting this obviously changed the results, actually in a good way.

I altered the plotting of classifier results -- both the
cross-comparison one and the longitudinal one.  In the cross-comparison
one, I added more pairwise comparisons, so now the comparison

@@
 If the populations are in fact identical, then the probability that the 
-classifier correctly classifies a worker is $\frac{1}{2}$, and the probability 
-of getting $k$ classifications during a cross-validation with $n$ 
-test-classifications is:
+classifier correctly classifies a worker is $\frac{1}{2}$. Let $K$ be a random
+variable which denotes the number of correct classifications when the 
+classifier is chalenged to classify a total of $n$ workers during 
+cross-validation.  Under $\mathbf{H_0}$, the probability distribution of $K$ 
+is:
 \begin{align}
@@
 \end{align}
-Then, we have statistical significance if 
-$\theta_\text{NB}$ is greater than a critical value, 
-$\theta_\text{NB}^*$:
+We can reject $\mathbf{H_0}$ at significance $\alpha$ if $\theta_\text{NB}$ 
+is greater than a critical value, $\theta_\text{NB}^*$:
 \begin{align}
-	\theta_\text{NB} \geq 2k^* - 1
+	\theta^*_\text{NB} = \frac{2k^*}{n} - 1
 \end{align}
-where $k^*$ is the minimum value required to satisfy
+where $k^*$ is the smallest integer in $\{0,\dots,n\}$ that satisfies 
 \begin{align}
@@
 \end{align}
-For a test-set of $n=40$ workers, and a significance of $\alpha = 0.05$, we
-have $k^*=26 \implies \theta_\text{NB}^* = 0.65$.
+For a 5-fold cross-validation with non-overlapping test sets containing 25 
+workers ($n = 125$), and a significance of $\alpha = 0.05$, we
+have $k^*=73 \implies \theta_\text{NB}^* = 0.168$.
 

### 2014-07-19 src/analysis.py

@@ -324,7 +324,7 @@ class Analyzer(object):
 					100 * entryCounts['cultural']/float(entryCounts['overall']))
 
 				percentages['excessCultural'].append(
-					100 * entryCounts['cultural']/float(entryCounts['overall']))
+					100 * entryCounts['excessCultural']/float(entryCounts['overall']))
 
 				percentages['food'].append(
 					100 * entryCounts['food']/float(entryCounts['overall']))
@@ -343,19 +343,17 @@ class Analyzer(object):
 		# To get the standard deviation of the mean, 
 		# take the standard deviation of the samples 
 		# and divide by square root of number of samples.
-		# Then, multiply by the number of standard deviations needed to 
-		# generate the desired significance level.
 		stdPercentage = {
-			'cultural': significanceLevel * (
+			'cultural': (
 				np.std(percentages['cultural']) / np.sqrt(len(entries)))
 
-			, 'excessCultural': significanceLevel * (
+			, 'excessCultural': (
 				np.std(percentages['excessCultural']) / np.sqrt(len(entries)))
 
-			, 'food': significanceLevel * (
+			, 'food': (
 				np.std(percentages['food']) / np.sqrt(len(entries)))
 
-			, 'both': significanceLevel * (
+			, 'both': (
 				np.std(percentages['both']) / np.sqrt(len(entries)))
 		}
 
@@ -502,18 +500,7 @@ class Analyzer(object):
 		'''
 
 		# Create a new priming-image-label-experiment dataset
-		self.dataSet = data_processing.CleanDataset()
-
-		# Read from the raw amt csv files.  
-		# Note: order matters!  The older files have duplicates workers that
-		# get ignored.  Make sure to read the newer file files earlier
-		self.dataSet.read_csv('amt_csv/amt1_cut.csv', True)
-		self.dataSet.read_csv('amt_csv/amt2_cut.csv', True)
-		self.dataSet.read_csv('amt_csv/amt3_cut.csv', True)
-
-		# The dataset needs to do some internal calts to refresh its state 
-		self.dataSet.aggregateCounts()
-		self.dataSet.calc_ktop(5)
+		self.dataSet = data_processing.readDataset()
 
 
 
@@ -544,9 +531,9 @@ class NBCAnalyzer(object):
 		self.dataSet = data_processing.readDataset()
 
 
-	def testNBC(self, pTrainingSize=106, pTestSize=20, 
+	def testNBC(self, testSetSize=25,
[…]

### 2014-07-19 src/data_processing.py

@@ -28,6 +28,8 @@ import json
 import csv
 
 
+
+
 def readDataset():
 	'''
 	Factory method that builds a CleanDataset from the original Amazon
@@ -48,8 +50,16 @@ def readDataset():
 	dataSet.aggregateCounts()
 	dataSet.calc_ktop(5)
 
+	dataSet.uniform_truncate(125)
 	return dataSet
 
+
+class CleanDatasetException(Exception):
+	pass
+
+
+class CleanDatasetRotationException(Exception):
+	pass
 
 class CleanDataset(object):
 
@@ -67,44 +77,131 @@ class CleanDataset(object):
 		# Data
 		self.dictionary = set()		# a list of all words that occur 
 		self.entries = {}			# an entry holds the data for one worker
-		self.testEntries = {}		# holds the unused entries when sub-sampled
+		self.testEntries = {}		# holds the entries for testing when 
+									# sub-sampled
+		self.unusedForTest = {}	# keeps track of which entries have 
+										# been used for testing so far
+
+		self.unusedEntries = {}		# used to hold entries that are removed
+									# during truncation
 		self.trainEntries = {}
 		self.workerIds = set()		# to prevent duplicates
 		self.counts = {}			# stores words and frequency of occurrence
 		self.ktops = {}
+		self.areTreatmentsEqual = False	# boolean, indicates whether all 
+										# treatments have the same number of 
+										# entries
 
 
-	# In principle This should be moved to the NBDataset class, because this 
-	# separation
-	# is really a concern introduced by the desire to train a Naive Bayes
-	# Classifier on the data.  But for now it is here.  The reason is because
-	# I had written the function aggregateCounts also here, but really both
-	# should be moved to Naive Bayes Classifier.
-	def subsample(self, trainingSetSize, testSetSize=None):
+	# Use this to make all of the treatments have the same size 
+	def uniform_truncate(self, truncateSize=None):
+
+		# Figure out size of smallest treatment
+		min_treatment_size = min(
+			[len(treatment) for treatment in self.entries.values()])
+
+		# if treatment size isn't specified, use size of smallest treatment
+		if truncateSize is None:
+			truncateSize = min_treatment_size
+
+		# else check that treatment size is not bigger than smallest treatment
+		else:
+			if truncateSize > min_treatment_size:
+				raise CleanDatasetException('CleanDataset.uniform_truncate: '\
+					'truncateSize must not be larger than smallest '\
+					'treatment size in data set.')
+
+		# Make all treatments the same size
[…]

### 2014-07-19 src/naive_bayes.py

@@ -56,8 +56,7 @@ class NBDataset(object):
 
 	def __init__(self, 
 		pDataSet, pTreatments=['treatment1','treatment2'], 
-		pImages=['test0'], pDoConsiderPosition=False, pTrainingSize=80,
-		pTestingSize=20):
+		pImages=['test0'], pDoConsiderPosition=False, testSetSize=25):
 		'''
 		Specify the treatment ids to be included when building the classifier.
 		You may not always want to try to build a classifier that can 
@@ -72,14 +71,17 @@ class NBDataset(object):
 		self.doConsiderPosition = pDoConsiderPosition
 		self.images = pImages
 		
-		self.dataSet.subsample(pTrainingSize, pTestingSize)
+		self.dataSet.subsample(testSetSize)
 
 
 	def getCategories(self):
 		return list(self.treatments)
 
 
-	# Make this specific to the treatment and image passed in the constructor
+	def rotateSubsample(self):
+		self.dataSet.rotateSubsample()
+
+
 	def getFeatures(self):
 		features = set()
 		for treatment, image, position in self.dataSet.counts:
@@ -128,8 +130,6 @@ class NBDataset(object):
 		return frequency / float(len(self.dataSet.entries[pCategory]))
 
 	
-	# TODO: the subsample size for the test set should be passed to the 
-	# underlying dataset
 	def getTestSet(self):
 		'''
 		Returns a set of instances from the test set, i.e. which were not
@@ -191,7 +191,17 @@ class NaiveBayesClassifier(object):
 
 		for feature in instance.getFeatures():
 			for category in self.categories:
-				scores[category] += self.condProbs[(category, feature)]
+
+				# If the feature arises for the given category, use the
+				# add the conditional probability of its occurrence given the
+				# category to the score for that category.  Otherwise add 0
+				add_to_score = 0
+				try:
+					add_to_score = self.condProbs[(category, feature)]
+				except KeyError:
+					pass
+
+				scores[category] += add_to_score
 
 		verdict = sorted(scores.items(), None, lambda x: x[1], True)[0][0]
 

### 2014-07-19 src/plots.py

@@ -472,6 +472,42 @@ def getTestDataset():
 	return dataset
 
 
+def checkOrientationSignificance(
+	readFname='orientation/orientation.json',
+	writeFname='orientation/significance.json',
+	populationSize = 126
+	):
+	''' Checks for a significant difference between the fraction of food-
+	and culture-oriented words for all treatments compared to AMBG.
+	'''
+
+	# Read the file.  We're interested in the data in panel 1, which corresponds
+	# To panel B of figure 7 in the manuscript
+	data = json.loads(open(readFname, 'r').read())['panel1']
+
+	results = []
+	for treatment in [1,5,6,2,3,4]:
+		result = {}
+		result['treatment_id'] = treatment
+		result['treatment_name'] = TREATMENT_NAMES['treatment%d'%treatment]
+		for valence in ['food', 'cultural', 'excessCultural']:
+			difference = (data['avg'][valence][treatment] 
+				- data['avg'][valence][0])
+			var_mean = (data['std'][valence][treatment]**2 
+				+ data['std'][valence][0]**2)
+			zscore = difference / np.sqrt(var_mean)
+
+			result['%s_difference'%valence] = difference
+			result['%s_var_mean'%valence] = var_mean
+			result['%s_zscore'%valence] = zscore
+
+		results.append(result)
+
+	fh = open(writeFname, 'w')
+	fh.write(json.dumps(results, indent=3))
+	fh.close()
+
+
 def computeOrientationVsTreatment(
 	fname='orientation/orientation.json', useTestData=False):
 	#fname='../docs/figs/valenceComparison.pdf'):
@@ -520,8 +556,8 @@ def computeOrientationVsTreatment(
 	]
 	for i, images in enumerate(imageSets):
 		plotData['panel%d'%(i+1)] = {
-			'avg':{'cultural':[], 'food':[], 'both':[]},
-			'std':{'cultural':[], 'food':[], 'both':[]}
+			'avg':{'cultural':[], 'food':[], 'both':[], 'excessCultural':[]},
+			'std':{'cultural':[], 'food':[], 'both':[], 'excessCultural':[]}
 		}
 		thisPlotData =  plotData['panel%d'%(i+1)]
 
@@ -532,10 +568,14 @@ def computeOrientationVsTreatment(
[…]

### 2014-07-19 src/tests.py

@@ -4,7 +4,7 @@ import analysis
 import naive_bayes as nb
 import data_processing as dp
 import ontology
-
+import copy
 
 class OntologyTestCase(unittest.TestCase):
 	def setUp(self):
@@ -202,7 +202,13 @@ class AnalysisTestCase(unittest.TestCase):
 
 class DataProcessingTestCase(unittest.TestCase):
 	def setUp(self):
-		self.dataset = dp.readDataset()
+		self.dataset = dp.CleanDataset()
+		self.dataset.read_csv('amt_csv/test100.csv', False)
+
+		self.dataset.aggregateCounts()
+		self.dataset.calc_ktop(5)
+		self.dataset.uniform_truncate(10)
+
 
 	def test_NoDuplicates(self):
 		seenWorkers = set()
@@ -224,39 +230,172 @@ class DataProcessingTestCase(unittest.TestCase):
 			treatments.append(treatment)
 			originalSizes[treatment] = len(entries)
 
-		# do the subsampling, first specifying only a training sample size
-		self.dataset.subsample(80)
+		# do the subsampling, specify a testSet of 20
+		self.dataset.subsample(2)
 
 		for treatment in treatments:
 			# We expect 80 entries in each training set
-			self.assertEqual(len(self.dataset.trainEntries[treatment]), 80)
-
-			# There shouldn't be any unused entries
-			self.assertEqual(len(self.dataset.unusedEntries[treatment]), 0)
+			self.assertEqual(len(self.dataset.trainEntries[treatment]), 8)
 
 			# The sum of entries in partitions should be the original total
 			totalInTreatment = (
 				len(self.dataset.trainEntries[treatment])
-				+ len(self.dataset.testEntries[treatment])
-				+ len(self.dataset.unusedEntries[treatment]))
+				+ len(self.dataset.testEntries[treatment]))
 			self.assertEqual(totalInTreatment, originalSizes[treatment])
+			self.assertEqual(len(self.dataset.testEntries[treatment]),2)
 
-		# Subsample again, this time specifying a test sample size too
-		self.dataset.subsample(80, 20)
 
-		for treatment in treatments:
-			# We expect 80 entries in each training set
-			self.assertEqual(len(self.dataset.trainEntries[treatment]), 80)
+	def test_subSampleTooLarge(self):
 
-			# We expect 20 entries in each test set
-			self.assertEqual(len(self.dataset.testEntries[treatment]), 20)
+		'''Specifying a testSetSize that is larger than the dataset --- should
+		raise an exception'''
 
[…]

### 2014-07-20 src/analysis.py
revise plots: classifier longitudinal and Orientation
Classifier longitudinal plots:
	- now plots classifier distinguishability of CULT_img and AMBG,
	  instead of CULT_img and INGR_img
	- make a separate panel for the all_images data point
	- use averages of many cross-validation runs, because the data is
	  sensitive to the particular partitioning of data into test and
	  training set.

Orientation treatment plots
	- Correct a small error in the calculation of varience

Orientation excess culture longitudinal plot
	- Plot only CULT_img compared to AMBG

@@ -284,15 +284,17 @@ class Analyzer(object):
 		'''
 
 		# counters
-		treatmentCounts = {'cultural':0, 'food':0, 'both':0, 'overall':0}
+		overall_counts = {'cultural':0, 'food':0, 'both':0, 'overall':0}
 		percentages = {
 			'cultural': [], 'excessCultural': [], 
 			'food': [], 'both': []
 		}
 
 		for treatment in treatments:
+			util.writeNow('\n\ttreatment: %s' % str(treatment))
 			entries = self.dataSet.entries[treatment]
 			for entry in entries:
+				util.writeNow('.')
 
 				# Figure out which tokens we're interested in
 				tokenKeys = []
@@ -320,7 +322,7 @@ class Analyzer(object):
 
 				for tokenKey in tokenKeys:
 
-					treatmentCounts['overall'] += 1
+					overall_counts['overall'] += 1
 					entryCounts['overall'] += 1
 
 					isCultural = self.isCultural(entry[tokenKey])
@@ -367,16 +369,20 @@ class Analyzer(object):
 		# and divide by square root of number of samples.
 		stdPercentage = {
 			'cultural': (
-				np.std(percentages['cultural']) / np.sqrt(len(entries)))
+				np.std(percentages['cultural']) / np.sqrt(
+				overall_counts['overall']))
 
 			, 'excessCultural': (
-				np.std(percentages['excessCultural']) / np.sqrt(len(entries)))
+				np.std(percentages['excessCultural']) / np.sqrt(
+				overall_counts['overall']))
 
 			, 'food': (
-				np.std(percentages['food']) / np.sqrt(len(entries)))
+				np.std(percentages['food']) / np.sqrt(
+				overall_counts['overall']))
 
 			, 'both': (
-				np.std(percentages['both']) / np.sqrt(len(entries)))
+				np.std(percentages['both']) / np.sqrt(
+				overall_counts['overall']))
 		}
 
 		return {'mean': meanPercentage, 'stdev':stdPercentage}

### 2014-07-20 src/plots.py

@@ -436,21 +436,6 @@ def computeSpecificityComparisons(
 	return results
 
 
-
-def plotValenceVsImage():
-	'''
-	This creates a figure with three pannels:
-	
-	1) Aggregation of all treatments orientation vs image
-	2) CULT_img treatment vs image
-	3) CULT_fund treatment vs image
-	'''
-
-	runs = [
-			
-			]
-
-
 def getTestDataset():
 	'''
 	Factory method that builds a CleanDataset from a small testing subset
@@ -477,8 +462,9 @@ def checkOrientationSignificance(
 	writeFname='orientation/significance.json',
 	populationSize = 126
 	):
-	''' Checks for a significant difference between the fraction of food-
-	and culture-oriented words for all treatments compared to AMBG.
+	''' 
+		Checks for a significant difference between the fraction of food-
+		and culture-oriented words for all treatments compared to AMBG.
 	'''
 
 	# Read the file.  We're interested in the data in panel 1, which corresponds
@@ -510,11 +496,13 @@ def checkOrientationSignificance(
 
 def computeOrientationVsTreatment(
 	fname='orientation/orientation.json', useTestData=False):
-	#fname='../docs/figs/valenceComparison.pdf'):
+
 	'''
-	This creates a figure with  X pannels:
-	1) Orientation vs treatment for image 1
-	2) Orientation vs treatment for all images
+	This computes the data for a figure with  3 pannels:
+
+	1) Orientation vs image (aggregating labels from all treatments)
+	2) Orientation vs treatment (aggregating all images)
+	3) Orientation vs treatment using labels from the image 'test0'
 	'''
 
 	fh = open(fname, 'w')
@@ -531,11 +519,13 @@ def computeOrientationVsTreatment(
 	plotData = {}
 
 	# First we will plot composition vs image, aggregating all treatments
+	print '\n\npreparing panel0 data: composition as a function of image'
 	plotData['panel0'] = {
 		'avg':{'cultural':[], 'food':[], 'both':[]},
 		'std':{'cultural':[], 'food':[], 'both':[]}
 	}
 	for image in ['test%d' % i for i in range(5)]:
+		print '\nImage: %s' %image
[…]

### 2014-07-31 docs/publications/2014.05_PNAS/figs.tex
revise plots: classifier longitudinal and Orientation
Classifier longitudinal plots:
	- now plots classifier distinguishability of CULT_img and AMBG,
	  instead of CULT_img and INGR_img
	- make a separate panel for the all_images data point
	- use averages of many cross-validation runs, because the data is
	  sensitive to the particular partitioning of data into test and
	  training set.

Orientation treatment plots
	- Correct a small error in the calculation of varience

Orientation excess culture longitudinal plot
	- Plot only CULT_img compared to AMBG
Worked on plots
- orientation vs treatm

--- 2014-06-06 docs/publications/2014.05_PNAS/figs.tex
@@
 \begin{figure}
-	\includegraphics{figs/f1-thetas.pdf}
+	\includegraphics{figs/f1-thetas_full_pairwise25_img1.pdf}
 	\caption{ $F_1$ score and $\theta_\text{NB}$ for the various 
@@
 
-\begin{figure}
-	\includegraphics{figs/longitudinalF1scores-t1-t2.pdf}
-	\caption{ $F_1$ score and $\theta_\text{NB}$ for the classification of 
-	$\textsc{cult}_{img}$ and $\textsc{ingr}_{img}$ using a Naive Bayes 
-	classifier.  The classifier is provided only the labels attributed to
-	particular images as indicated on the abscissa.}
-\end{figure}
+%\begin{figure}
+%	\includegraphics{figs/longitudinalF1scores-t0-t1_25.pdf}
+%	\caption{ $F_1$ score and $\theta_\text{NB}$ for the classification of 
+%	$\textsc{cult}_{img}$ and $\textsc{ambg}$ using a Naive Bayes 
+%	classifier.  The classifier is provided only the labels attributed to
+%	particular images as indicated on the abscissa.}
+%\end{figure}
 
@@
 \begin{figure}
-	\includegraphics{figs/excessCultureVsTreatment-t1.pdf}
+	\includegraphics{figs/longitudinal_theta_excess-culture.pdf}
 	\caption{Excess culture-oriented label composition in the labels provided
@@
 	\includegraphics{figs/specificity-allImages.pdf}
+	\caption{Relative specificity of various treatments.
+		Each panel shows the comparison between a basis treatment (inset) and 
+		target treatments (abscissa).
+		Bar heights indicate relative specificity of the target 
+		treatment compared to the basis (a positive quantity means the target 
+		is more specific), and are normalized to units of standard 
+		deviations of the null comparison.  Dotted horizontal lines indicate
+		the 95\% confidence interval for the null comparison, which necessarily
+		has zero relative specificity (see \textbf{Methods} 
+		for an explanation of the null comparison).  Panels D, E, and F 
+		represent relative specificity calculated using only culture-oriented
+		labels, while panels G, H, and I using only food-oriented labels.
+		Labels that are both culture- and food-oriented are excluded from the
+		calculations for panels D through I.
+		}
+\end{figure}
+
+\begin{figure}
+	\includegraphics{figs/orientationVsTreatment_full.pdf}
+	\caption{Percent label composition (culture- vs food-oriented labels) for 
+		various images and treatments.  Panel A shows the composition of 
+		labels, aggregated over all treatments, as a function of test image.
+		Panel B shows the composition of labels, aggregated over all images, as
+		a function of treatment.  Panel C shows the composition of labels 
+		attributed to the first test image by various treatments.}
+\end{figure}
+
+\begin{figure}
+	\includegraphics{figs/specificity-full-allImages.pdf}
 	\caption{Relative specificity of various treatments.

### 2014-07-31 src/plots.py

@@ -25,19 +25,6 @@ except:
 		'plotting functions.'
 	
 
-#
-#TODO: Review whether the computeAllSpecificityComparisons() function does
-#		so in a strict mode or not -- that is, whether calculating food
-#		specificity is done only for food words that are non-cultural, or 
-#		whether it does so for all words having food as a parent in the 
-#		ontology, or whether it does so for food words that are not just
-#		non-cultural, but also non-anything-else.  I think that the first
-#		way (food words that are non-cultural) is most informative.
-#
-#TODO: Create a plot that shows the deviation in number of cultural (food)
-#		references between each treatment and AMBG overall
-#
-
 # z-score for two-tailed 99-percent confidence interval
 CONFIDENCE_95 = 1.96
 CONFIDENCE_99 = 2.975
@@ -54,20 +41,132 @@ TREATMENT_NAMES = {
 }
 
 
-
-def plotAllSpecificityComparisons(
+def plotSomeSpecificityComparisons(
 	readFname='specificity/allComps_allImages_50.json', 
 	writeFname='figs/specificity-allImages.pdf',
 	normalize=False
 	):
 	'''
-	Plots all of the interesting specificity comparisons between different
-	treatments, such that they can be plotted  in a big multi-pannel figure.
-	This does overall specificity comparisons as well as food-specific and
-	culture-specific specificity comparisons.
+	Plots only the most interesting specificity comparisons between different
+	treatments.  It plots only overall specificity comparisons (neither 
+	food-specific nor culture-specific specificity comparisons are included).
+	'''
 
-	This only does the computation and writes the results to file; you need
-	to run `plotAllSpecificityComparisons()` to generate the plot.
+	# For this plot, we are interested in very particular data.  We'll be
+	# cherry picking the ones we want
+	data = json.loads(open(readFname).read())
+	picked_data = []
+	Y = []
+
[…]

### 2014-07-31 src/plots.py
add longitudinal specificity calc

@@ -40,6 +40,80 @@ TREATMENT_NAMES = {
 	, 'treatment6': 'CULT$_{fund,img}$'
 }
 
+def plotSpecificityLongitudinal(
+		readFnames=[
+			'specificity/t0-t1-test%d-overall.json' % i for i in range(5)],
+		writeFname='figs/specificity-longitudinal.pdf'
+	):
+
+	'''
+	Plots the relative specificiy of ambg <-> cult_img for each of the 
+	test images.  Comparison uses full ontology (is not restricted to 'food' 
+	or 'culture').
+
+	Later, this should get added on to the other longitudinal plots.
+	'''
+
+	# we'll open up each file, (there is one per image), and pull out the
+	# data that we want.  Assert statements make sure that some assumptions
+	# that are built into how we're picking data are met
+	pick_data = []
+	for fname in readFnames:
+		data = json.loads(open(fname, 'r').read())
+		data = data[0]
+		assert(data['valence'] == 'overall')
+		data = data['results'][0]
+		assert(data['basis'] == 'treatment0')
+		data = data['results'][0]
+		assert(data['subject'] == 'treatment1')
+		pick_data.append(data)
+
+	Y = [pd['avg'] for pd in pick_data]
+	Y_err = [pd['stdev']*CONFIDENCE_95 for pd in pick_data]
+	X = range(len(Y))
+
+	width=0.75
+	figWidth = 8.7 / 2.54 			# convert from PNAS spec in cm to inches
+	figHeight = (4/5.)*figWidth 	# a reasonable aspect ratio
+	fig = plt.figure(figsize=(figWidth,figHeight))
+	gs = gridspec.GridSpec(1,1)
+
+	ax = plt.subplot(gs[0])
+	series = ax.bar(X, Y, width, color='0.25', ecolor='0.55', 
+		yerr=Y_err)
+
+
+	# control the plot X limits
+	padding = 0.25
+	xlims = (-padding, len(Y) - 1 + width + padding)
+	plt.xlim(xlims)
+
+	# Annotate the plot with a line at Y=0
+	zero = ax.plot(
+		xlims, [0, 0], color='0.35', linestyle='-', zorder=0)
+
+	
+	# handle axis labelling
+	xlabels = ['image%d' %i for i in range(1,6)]
+	ax.tick_params(axis='both', which='major', labelsize=9)
+	ax.set_xticks([x + width/2. for x in  X])
+	ax.set_xticklabels(xlabels, rotation=45, horizontalalignment='right')
[…]

### 2014-07-31 src/plots.py
chg to params

@@ -444,9 +444,8 @@ def computeSpecificityLongitudinal():
 		image_name = 'test%d' % image_id
 
 		computeSpecificityComparisons(
-			fname='specificity/t0-t1-%s-overall.json' % image_name,
-			sampleSize=4,
-			nullSampleSize=4,
+			fname='specificity/t0-t1-%s-overall_50.json' % image_name,
+			sampleSize=50,
 			comparisons='__first__',
 			images = [image_name],
 			valences=['overall'],
@@ -456,7 +455,6 @@ def computeSpecificityLongitudinal():
 def computeSpecificityComparisons(
 	fname='specificity/allImages.json',
 	sampleSize=124,
-	nullSampleSize=62, 
 	comparisons='__all__',
 	images=['test%d'%i for i in range(5)],
 	valences=['overall', 'cultural', 'food'],

### 2014-07-31 src/plots.py
adjust params

@@ -437,7 +437,7 @@ def plotAllSpecificityComparisons(
 	plt.show()
 
 
-def computeSpecificityLongitudinal():
+def computeSpecificityLongitudinal(sampleSize=124):
 
 	for image_id in range(5):
 
@@ -445,7 +445,7 @@ def computeSpecificityLongitudinal():
 
 		computeSpecificityComparisons(
 			fname='specificity/t0-t1-%s-overall_50.json' % image_name,
-			sampleSize=50,
+			sampleSize=sampleSize,
 			comparisons='__first__',
 			images = [image_name],
 			valences=['overall'],

### 2014-08-01 docs/publications/2014.05_PNAS/manuscript.tex
embed figures in manuscript, merge orientation and specificity figs

@@
 \documentclass[a4paper]{report}
-\usepackage[hmargin=1in,vmargin=1in]{geometry}
+\usepackage[hmargin=2cm,vmargin=2cm]{geometry}
 
@@
 \subsection*{Experimental Setup}
+\begin{table}[t]
+\centering
+	\begin{tabular}{ l  l  l }
+		\hline                       
+		Treatment & Funder & Priming Image Set	\\ 
+		\hline                       
+		$\textsc{ambg}$ & None & Ambiguous\\
+		$\textsc{cult}_{img}$ & None & Cultural\\
+		$\textsc{cult}_{fund}$ & Cultural & Cultural\\
+		$\textsc{cult}_{fund,img}$ & Cultural & Cultural\\
+		$\textsc{ingr}_{img}$ & None & Ingredients\\
+		$\textsc{ingr}_{fund}$ & Nutritional & Ingredients\\
+		$\textsc{ingr}_{fund, img}$ & Nutritional & Ingredients\\
+		\hline  
+	\end{tabular}
+
+%\begin{addmargin}[11em]{11em}
+%	\vspace{2mm}
+%	$^a$\footnotesize{The full funder names used were ``The Glodal Foundation
+%		for Cultural Recognition'' and ``The National Foundation for 
+%		Nutritional Awareness''.}
+%\end{addmargin}
+
+	\caption{Workers were uniformly randomly
+		assigned to one of the treatments listed above.}
+	\label{table:1}
+\end{table}
+
+\begin{figure}
+	\includegraphics[scale=1.00]{figs/taskImages/testImages.jpg}
+	\caption{Testing image set. These images were presented to all workers in 
+		the order shown after the priming set of images.}
+\end{figure}
+
+\begin{figure}
+	\includegraphics[scale=1.00]{figs/taskImages/ambiguous.jpg}
+	\caption{ Ambiguous image set. These images were presented to workers from 
+		certain treatements (see \textbf{Table 1}) in the order shown.}
+\end{figure}
+
+\begin{figure}
+	\includegraphics[scale=1.00]{figs/taskImages/cultural.jpg}
+	\caption{Cultural image set. These images were presented to workers from 
+		certain treatements (see \textbf{Table 1}) in the order shown.}
+\end{figure}
+
+\begin{figure}
+	\includegraphics[scale=1.00]{figs/taskImages/ingredients.jpg}
+	\caption{ Ingredients image set. These images were presented to workers 
+		from certain treatements (see \textbf{Table 1}) in the order shown.}
+\end{figure}
+
 We solicited 900 AMT workers to perform an image-labeling task relating to
@@
 
+\begin{figure}
+	\includegraphics[scale=0.94]{figs/f1-thetas_full_pairwise25_img1.pdf}
+	\caption{ $F_1$ score and $\theta_\text{NB}$ for the various 
+priming treatments, as measured using a Naive Bayes classifier. Each panel 
+presents classifier performance results that indicate the difference in
+priming between a basis 
+treatment, indicated in the inset, and the other treatments, indicated on the
+abscissa. }
+\end{figure}
+
 Next we looked at the degree to which labels from individual final images 
@@
 
-\paragraph{Earlier tasks orient focus during later tasks.} Having 
-demonstrated both inter-task and framing effects, we next
+\paragraph{Earlier tasks orient focus during later tasks.} 
+\begin{figure}
+	\includegraphics[scale=0.94]{figs/orientation_specificity.pdf}
+	\caption{Percent label composition (culture- vs food-oriented labels) for 
+		various images and treatments.  Panel A shows the composition of 
+		labels, aggregated over all treatments, as a function of test image.
+		Panel B shows the composition of labels, aggregated over all images, as
+		a function of treatment.  Panel C shows the composition of labels 
+		attributed to the first test image by various treatments.}
+\end{figure}
+
+Having demonstrated both inter-task and framing effects, we next
 investigated the \textit{nature} of these effects.  To this
@@
 \paragraph{Earlier tasks affect attention to detail during later tasks.}
+
 Using the ontology described
@@
 number of labels}.
+
+\begin{figure}
+	\includegraphics{figs/longitudinal_theta_excess-culture.pdf}
+	\caption{Excess culture-oriented label composition in the labels provided
+		by $\textsc{cult}_{img}$ as compared to $\textsc{ambg}$, for various
+		test images (see \textbf{Eq. 1} for calculation).
+	}
+\end{figure}
 

### 2014-08-01 src/plots.py

@@ -845,6 +845,219 @@ def pick(picks, a):
 		return [a[p] for p in picks]
 
 
+def plotOrientationAndSpecificity(
+		readFname=[
+			'orientation/orientation.json',
+			'specificity/allComps_allImages_50.json'
+		],
+		writeFname='figs/orientation_specificity.pdf'
+	):
+
+	'''
+	Plots specificity and orientation for only the major treatments.
+	'''
+
+	# within the dataset, panel2 and panel3 have data organized by treatment
+	# in this order
+	treatmentIds = [0,1,5,6,2,3,4]
+
+	# we only want treatments 0,1, and 2, and so we have to 'pick' the data
+	# at positions 0,1, and 4
+	PICKS = [0,1,4]
+	treatmentIds = pick(PICKS, treatmentIds)
+
+	treatments = ['treatment%d' % i for i in treatmentIds]
+	images = ['image %d' % i for i in range(1,6)]
+
+	plotData = json.loads(open(readFname[0], 'r').read())
+
+	width = 0.42
+	padding = 1 - 2*width
+
+	figWidth = 17.8 / 2.54
+	figHeight = figWidth*5/10.
+	fig = plt.figure(figsize=(figWidth,figHeight))
+
+	gs_ratio = 4 * (len(PICKS) + 1) 
+	gs = gridspec.GridSpec(1,2, width_ratios=[9,5])
+
+	PANNEL = 2
+
+	ax = plt.subplot(gs[0])
+	X = range(len(treatments))
+
+	X2 = [x + width for x in X]
+	panel = 'panel%d' % PANNEL
+
+	thisPlotData = plotData[panel]
+
+	picks = PICKS
+
+	# as we plot, we adjust the error bars to plot the 95% confidence 
+	# intervals rather than standard errors
+	yerr_cult = pick(picks, thisPlotData['std']['cultural'])
+	yerr_cult = [y*1.95 for y in yerr_cult]
+	seriesCultural = ax.bar(
+		X, 
+		pick(picks, thisPlotData['avg']['cultural']),
+		width, color='0.25', 
+		ecolor='0.55', 
+		bottom=pick(picks, plotData[panel]['avg']['both']), 
+		yerr=yerr_cult)
+
+	yerr_food = pick(picks, thisPlotData['std']['food'])
+	yerr_food = [y*1.96 for y in yerr_food]
+	seriesFood = ax.bar(
+		X2,
[…]

### 2014-08-03 docs/publications/2014.05_PNAS/manuscript.tex
major edits to manuscript

@@
 \usepackage[hmargin=2cm,vmargin=2cm]{geometry}
-
+\usepackage{scrextend}
 \usepackage{graphicx}
@@
 \usepackage[colorlinks=false, urlcolor=blue]{hyperref}
+\usepackage{dcolumn}
+\usepackage{multirow}
+\usepackage{booktabs}
+\newcolumntype{d}{D{.}{.}{4.0}}
+\newcolumntype{s}{D{.}{.}{1.4}}
 
@@
 
-\title{Inter-task effects lead to an unexpected bias in human computation}
+\title{Inter-task effects introduce bias in crowdsourcing}
 \author{Edward Newell, Derek Ruths}
@@
 Originally used to distribute clerical work, these platforms 
-increasingly serve as a cheap and fast means to engage experimental 
+increasingly serve as a fast and cheap means to engage experimental 
 participants and manually annotate datasets in a research 
@@
 
-Such platforms render human cognition into a fluid resource: it is available 
+Such platforms make human cognition a fluid resource: it is available 
 on demand in small units, with low transaction 
@@
 usage in the late 1800s\cite{Dictionary:hl}.}, viewing the introduction of 
-microtask platforms as a fundamentally new computing architecture
+microtask platforms as a new computing architecture
 \cite{5543192}.
@@
 \cite{Gass1999549, sohn2001task}.  
-We investigate the effects that the content of earlier tasks has on workers'
-outputs in later tasks.  We call such effects 
+We investigate the effect that previously completed tasks have on workers'
+responses during subsequent ones. We call such effects 
 \textit{inter-task priming}.  Inter-task priming would amount to a kind of
@@
 
-This work supplements the existing research into the factors that affect HPU 
-output.  Studies have shown that 
+There has been considerable investigation into the factors that affect HPU 
+output on crowdsourced microtask platforms.  Studies have shown that 
 there is a great deal of variance in worker attention and 
-accuracy \cite{kazai2013analysis}.
-Factors that affect the quality of HPU 
+accuracy \cite{kazai2013analysis}.  Factors that affect the quality of HPU 
 output include level of pay\cite{kazai2013analysis}, 
-training\cite{le2010ensuring}, pre-screening 
-workers\cite{paolacci2010running}, and user-interface design
+training\cite{le2010ensuring}, screening workers\cite{paolacci2010running}, 
+and user-interface design
 \cite{Finnerty2013}.  Research has also investigated \textit{framing}, 
-by disclosing to the worker the role of
-their task in a larger workflow context \cite{Kinnaird2012281}, 
-or describing a meaningful ultimate purpose of the project in which their
-task is a part \cite{chandler2013breaking}.  However, to our knowledge, no
-study has investigated the effects of inter-task priming.
+by testing the effects of disclosing the role of a task within the 
+context of a study \cite{Kinnaird2012281}, and disclosing the ultimate 
+purpose of that study \cite{chandler2013breaking}.  However, to our knowledge, 
+no study has investigated the effects of inter-task priming.
 
-To characterize such effects, we present a novel  
-\textit{algorithmic definition of priming}, and a corresponding method for
-measuring priming effects using machine learning algorithms.  
-Traditional methods for detecting priming are of limited use in characterizing 
-HPU hysteresis, because they are task-specific, and assume that priming results
-in a specific class of effects.
-Our approach can be applied to any task output, and does not rely on prior 
-assumptions about the particular effects brought about by priming.  This 
-enables the detection of priming even when the nature of the effects is not 
-understood.
+To characterize the effects of inter-task priming, we present a novel  
+\textit{algorithmic definition of priming}, along with a general method 
+for measuring priming effects using machine learning algorithms.  
+Existing work on priming effects focuses on the internal psychological 
+mechanisms of priming[***], but here we are interested in how the treatment of 
+workers can impact an application of human computation. This leads us to 
+quantify priming in terms of the algorithmic distinguishability of priming
+treatments.
 
-In the present work, we investigate inter-task priming for an image-labeling 
-task
-on the AMT platform.  Each worker is required to label ten images featuring 
+In the present work, we investigate inter-task priming using image-labeling 
+tasks on the AMT platform.  
+(***why we are using image labelling as prototypical task***) 
+Each worker is required to label ten images 
+featuring 
 food and culture.  We regard these images as being made up of an 
@@
 from the view of the worker.
-The final image set is always the same, but we randomly assign one of three 
-initial sets, and analyze the effect this assignment has on labels attributed 
-to the final set.  We employ our novel method for detecting priming effects, as
-well as measuring effects on the content and specificity of attributed labels.
+Each worker is randomly assigned one of three initial sets, but the final set
+of images is always the same.  We analyze the effect that the assignment of 
+initial set has on workers' attribution of labels to the final set.  We 
+measure effects using our novel approach, as well as looking for changes in 
+the content of labels and label specificity based on an ontology we 
+developped for that purpose.
 
-As a point of comparison, we also subject some groups of workers to a kind of
-\textit{framing}: we disclose a fictitious, semantically loaded name for the 
-task-requester.  The names are chosen to suggest the requester's interest in a 
-specific aspect of the image content.  One might reasonably expect that this 
+As a point of comparison, we subject some groups of workers to a kind of
+\textit{framing}: we disclose a fictitious, semantically-loaded name for 
+requester funding the tasks.
+The names were chosen to suggest the requester's interest in 
+a specific aspect of the image content.  One might reasonably expect that this 
 would orient workers to provide a greater quantity and specificity of labels 
-which relate to this ``preferred'' content.
+which relate to this ``preferred'' content[***].
 
-Surprisingly, inter-task effects on label orientation and specificity are 
-much stronger than those brought about by framing tasks with a funder name. 
-Our results 
-show that initial tasks can introduce significant bias in subsequent worker 
-labeling.  On the other hand, we find evidence that a well-chosen progression 
-of tasks could tune workers to produce labels of greater (or lesser) 
-specificity.  This suggests that careful consideration should be given to
-the progression of tasks when designing a study using a microtask platform.
+Surprisingly, we find that inter-task effects on label orientation and 
+specificity are much stronger than those brought about by framing tasks with a 
+funder name.  Our results show that initial tasks can introduce significant 
+bias in subsequent worker labeling.  Interestingly, we find that inter-task
+effects can be used to induce greater specificity.  Our results suggest that
+workers attribute more specific labels when labelling a series of images that
+that are more similar to one another.  This suggests that careful 
+consideration should be given to the bundling of tasks when designing a study 
+using a microtask platform.
 
-Even when we are unable to detect priming in the form of a direct
-influence on label orientation or specificity, our novel measurement approach 
-clearly detects priming. This demonstrates a remarkable feature of the 
-approach, whereby priming effects can be quantified without knowing the nature 
-of said effects.
+Our analysis also highlights important advantages of our novel definition of 
+priming.  Our approach relies on no prior knowledge about the nature
+of the task task whatsoever.  In contrast, we also sought to detect priming
+based on its direct effects on label content and specificity, implicitly
+drawing on prior knowledge about the the images and label semantics.
+Remarkably, while being more general, our novel approach was also more 
+sensitive.  This suggests that our measurement approach could be applied in 
+cases where one does not \emph{a priori} know whether any priming has occured, 
+nor what the effects might be.
 
@@
 fainter, or briefer [***].  Methods are also employed to measure processes
-in the brain of the participant, such as by fMRI.  These approaches are 
+in the brain of the participant, such as by fMRI[***].  These approaches are 
 well-suited to studying the underlying psychological mechanisms at work.
@@
 a task $\mathcal{T}$ thus producing a population of task-outputs $\mathcal{L}$,
-we will write $\mathcal{T}(\mathcal{J}) = \mathcal{L}$. We will also write 
-$\mathcal{T}(j) = \ell$ to indicate that a single person, $j$, output $\ell$ 
-during $\mathcal{T}$.
+we will write $\mathcal{T}(\mathcal{J}) = \mathcal{L}$.
 
@@
 	\upshape
-	Two mutually exclusive populations of people, $\mathcal{J}$ and 
-	$\mathcal{K}$, are uniformly and randomly subsampled from an initial 
+	Two mutually exclusive populations of people, $\mathcal{P}_0$ and 
+	$\mathcal{P}_1$, are uniformly and randomly subsampled from an initial 
 	population $\mathcal{P}$, are exposed to (possibly) different priming 
 	treatments, and then perform a task $\mathcal{T}$, 
-	producing task-outputs $\mathcal{T}(\mathcal{J})$ and 
-	$\mathcal{T}(\mathcal{K})$.
-	We say that $\mathcal{J}$ and $\mathcal{K}$ 
+	producing task-outputs $\mathcal{T}(\mathcal{P}_0)$ and 
+	$\mathcal{T}(\mathcal{P}_1)$.
+	These populations are subsampled, producing 
+	$P_0 \subset \mathcal{P}_0$ and
+	$P_1 \subset \mathcal{P}_1$. A uniform, random bit is chosen, 
+	$b\in _R \{0,1\}$, and a single worker $p$ is uniformly and randomly 
+	sampled from 
+	$\mathcal{P}_b \setminus P_b$.
+	We say that $\mathcal{P}_0$ and $\mathcal{P}_1$ 
 	\emph{differ in priming by a degree at least $\theta$},
-	if there exists an algorithm $\mathcal{A}$ that takes as input 
-	$\mathcal{T}(J)$, $\mathcal{T}(K)$, and $\mathcal{T}(p)$,
-	where $J \subset \mathcal{J}$, $K \subset \mathcal{K}$, and $p$ is a 
-	person chosen with equal probability from either $\mathcal{J}\setminus J$ 
-	or $\mathcal{K}\setminus K$, 
-	such that $\mathcal{A}$ outputs the set from which $p$ was drawn
-	($\mathcal{J}$ or $\mathcal{K}$) with accuracy $\frac{1+\theta}{2}$.  
+	if there exists a \emph{distinguisher algorithm} $\mathcal{A}$ that takes as input 
+	$\langle\mathcal{T}(J)$, $\mathcal{T}(K)$, $\mathcal{T}(\{p\})\rangle$
+	and outputs a guess for $b$ with accuracy $\frac{1+\theta}{2}$.  
 \end{mydef}
 
-In the language of computer science, $\mathcal{A}$ is a classifier.  Thus,
-intuitively, if there exists a classifier that can distinguish populations 
-$\mathcal{J}$ and $\mathcal{K}$ based on their outputs, then they are 
-differently primed.
+In the language of computer science, $\mathcal{A}$ is a classifier performing
+a binary classification.  The measure $\theta$ can range between 0 and 1, and 
+indicates how much better the performance of the best possible classifier is 
+compared to a random guess. We intentionally leave the details of 
+$\mathcal{A}$ unrestricted because $\theta$ should depend on the pontential 
+for two populations to be distinguished, based on their inherent differences, 
+rather than on the performance of a particular classifier.
 
-We leave the details of $\mathcal{A}$ unrestricted.  This is 
-intentional since we want the definition to depend on the inherent 
-potential for two populations to be distinguished, rather than on the 
-performance of a particular classifier.
+In practice, some particular classifier $\mathcal{C}$ must be used and a 
+statistical estimate of its performance $\hat{\theta}_\mathcal{C}$ obtained. 
+$\hat{\theta}_\mathcal{C}$ acts as a lower bound for the 
+theoretical value $\theta$ from the definition, because there might 
+exist some other classifier $\mathcal{C}'$ with 
+$\hat{\theta}_\mathcal{C'}>\hat{\theta}_\mathcal{C}$.
+Here, we use a Naive Bayes classifier because it simple and performs well 
+accross a broad range of classification tasks[***].
 
-A consequence of this choice is that empirical measures of $\theta$ always
-represent lower bounds on the theoretical value appearing in the definition.
-As a result, a measured $\theta$ that is greater than zero directly 
-supports the conclusion that two populations are differently 
-primed, up to the statistical significance of the measurement.  However, if 
-$\theta$ is not found to be statistically different from zero, one cannot 
-directly
-conclude that two populations are the same in priming.  The definition
-admits the possibility that there exists some other $\mathcal{A}'$ capable of 
-generating a measure of $\theta$ statistically greater than zero. 
-Interpreting a result
-that $\mathcal{A}$ fails to achieve accuracy significantly better than 
-chance depends on the capabilities of $\mathcal{A}$ and the state of the art
-of classifier algorithm design.
-
-Note that this definition admits special cases that are equivalent to the
-traditional psychological definitions of priming.  If one can show by an
-experiment that 
-speed, accuracy, or the like, are statistically different for two priming 
-treatments, then said experiment could itself be run as a classifier.
-
-This definition substitutes one choice for another: given a task
-and two priming treatments, the experimenter need not choose specific effects
-to look for, but must instead choose a classifier.  This choice is inherently
-less restrictive.  Many general purpose classifiers exist that perform
-well in diverse applications [***].  The Naive Bayes classifier stands out as 
-a suitable first test to quantify the effects of priming,
-because it is simple to implement and requires no domain-specific tuning of 
-parameters [***].  We adopt this classifier in the present work and 
-denote the measured differences in priming as $\theta_\text{NB}$ to distinguish
-them from the theoretical value, $\theta$.
+To interpret $\hat{\theta}_\mathcal{C}$, imagine that some choice is to be
+made between two options on the basis of worker outputs (e.g. whether or not 
+to flag an image as innappropriate). Any such binary choice has a formal 
+structure of a trained classifier (i.e. a distinguisher which discards the 
+first two inputs). This means that $\hat{\theta}_\mathcal{C}$ estimates a 
+lower bound for the worst-case bias introduced in such a binary decision when 
+one failed to control for priming effects.
 
@@
 
-	\caption{Workers were uniformly randomly
-		assigned to one of the treatments listed above.}
+	\begin{addmargin}[4em]{4em}
+	\caption{ \footnotesize{ 
+		Workers were uniformly randomly assigned to one of the 
+		treatments listed above. 
+		The full funder names used were 
+		``The Global Foundation for Cultural Recognition'' and 
+		``The National Foundation for Nutritional Awareness''.  
+		The ambiguous, cultural, and ingredients initial image sets are shown 
+		in \textbf{Figs. 2}, \textbf{3}, and \textbf{4}.
+	}}
+	\end{addmargin}
 	\label{table:1}
 \end{table}
-
-\begin{figure}
-	\includegraphics[scale=1.00]{figs/taskImages/testImages.jpg}
-	\caption{Testing image set. These images were presented to all workers in 
-		the order shown after the priming set of images.}
-\end{figure}
-
-\begin{figure}
-	\includegraphics[scale=1.00]{figs/taskImages/ambiguous.jpg}
-	\caption{ Ambiguous image set. These images were presented to workers from 
-		certain treatements (see \textbf{Table 1}) in the order shown.}
-\end{figure}
-
-\begin{figure}
-	\includegraphics[scale=1.00]{figs/taskImages/cultural.jpg}
-	\caption{Cultural image set. These images were presented to workers from 
-		certain treatements (see \textbf{Table 1}) in the order shown.}
-\end{figure}
-
-\begin{figure}
-	\includegraphics[scale=1.00]{figs/taskImages/ingredients.jpg}
-	\caption{ Ingredients image set. These images were presented to workers 
-		from certain treatements (see \textbf{Table 1}) in the order shown.}
-\end{figure}
 
@@
 ``The Global Foundation for Cultural Recognition'', or 
-``The National Foundation for Nutritional Awareness''.  Next, workers were
-shown ten images, one at a time, and were required to label each image with
-five descriptive labels.  For the purpose of analysis, we divide the images
-into the \textit{initial} and \textit{final} sets, which are respectively the 
-first five and last five images shown.  However, from the perspective of the 
-worker, there was no 
+``The National Foundation for Nutritional Awareness''.
+
+Next, workers were
+shown ten images, one at a time. Workers were required to label each image 
+with five descriptive labels before moving on to the next.  For the purpose 
+of analysis, we divide the images
+into \textit{initial} and \textit{final} sets, comprising respectively the 
+first five and last five images shown.  As mentioned, from the perspective of 
+the worker, there was no 
 distinction or interruption between the initial and final sets. 
-The initial set was chosen from one of three sets, depending on the 
-treatment, while the final set was always the same.
+Depending on the treatment to which the worker was assigned, one of three 
+initial image sets was chosen. The final image set was the same for all 
+treatments.
 
-For the final image set we chose 
-images that contain prepared meals and feature a prominent, identifiable 
-culture (see \textbf{Fig. 1}).  We intended that the content of these images 
-would elicit labels focusing food or culture (or both).
-One of the initial image sets, which we call \textit{ambiguous}, was chosen to
-be very similar to the final image set, in the sense that it consists of
-images of prepared meals.  However, the ambiguous image set was chosen such 
-that its cultural features are less prominent and more difficult to identify 
-(see \textbf{Fig. 2}).  
-The \textit{cultural} initial set features iconic cultural scenes, but no food 
-at all (see \textbf{Fig. 3}).  Finally, images from
-the \textit{ingredients} initial image set depict separated ingredients, but, 
+For the final image set, we chose 
+images that contained prepared meals and featured a prominent, identifiable 
+culture (see \textbf{Fig. 4}).  We intended that the content of these images 
+would elicit labels focusing on food or culture (or both).
+We refer to the three initial image sets as the ``ambiguous'', ``cultural'', 
+and ``ingredients'' sets.  The ambiguous set was chosen to
+be very similar to the final image set, in the sense that it consisted of
+images of prepared meals (see \textbf{Fig. 5}).  However, its cultural 
+features were intended to be less prominent.  The cultural set featured 
+iconic cultural scenes, but no food at all (see \textbf{Fig. 6}).  Finally, 
+images from the 
+ingredients set depicted separated ingredients, but, 
 like the ambiguous set, were chosen to avoid prominent cultural features (see 
-\textbf{Fig. 4}).  See the \textbf{Materials and Methods} section for further 
+\textbf{Fig. 7}).  See the \textbf{Materials and Methods} section for further 
 details.
@@
 \subsection*{Results}
-\paragraph{Earlier tasks and framing both prime workers.}
-We tested for priming effects using our definition proposed in the 
-introduction, implemented with a Naive Bayes classifier.  
-The classifier distinguished the various treatments from one another (pairwise)
-with high accuracy, confirming that both priming modalities 
-(inter-task and framing) were effective (\textbf{Fig. 5}).  Remarkably, the 
-classifier not only 
-distinguished treatments tending toward ``different orientations'' 
-(e.g. $\textsc{cult}_{img}$ and $\textsc{ingr}_{img}$; \textbf{Fig. 5A}), 
-it also distinguished treatments that one might expect would have similar
-effects.  For example the greatest accuracy was achieved in 
-distinguishing $\textsc{ingr}_{img}$ and $\textsc{ingr}_{fund, img}$, both
-of which are primed for a focus on food 
-(see \textbf{Fig. 5B}).
+\paragraph{Inter-task priming was strong, while framing was weak.}
+We tested for priming effects using our algorithmic definition, implemented 
+with a Naive Bayes classifier.  This involved measuring the classifier's 
+accuracy in classifying workers chosen from a pair of treatments during 
+cross-validation (see \textbf{Methods} for details).  The classifier's accuracy
+for cross-validations involving each pair of treatments is shown in 
+\textbf{Fig.1}.
+
+With some exceptions, the classifier performed significantly better 
+than chance when distinguishing treatments that had different initial image 
+sets.  This demonstrates that inter-task effects were strong for the labelling 
+tasks.  Of the sixteen treatment pairs having different initial images, there 
+were three cases where the classifier performance was on par with chance. 
+Each of these cases involved distinguishing workers shown the ambiguous set 
+from ones shown the the ingredients set.  The reason for the low 
+distinguishability of workers from these treatments might be because
+the ambiguous and ingredients sets are somewhat similar to one another.
+We will come back to this point later when we discuss the degree of similarity 
+between image sets.
+
+In contrast, the classifier never performed significantly better than chance
+when distinguishing treatments that differed only in the funder name shown. 
+Thus, framing effects were rather weak.
 
@@
 	\includegraphics[scale=0.94]{figs/f1-thetas_full_pairwise25_img1.pdf}
-	\caption{ $F_1$ score and $\theta_\text{NB}$ for the various 
-priming treatments, as measured using a Naive Bayes classifier. Each panel 
-presents classifier performance results that indicate the difference in
-priming between a basis 
-treatment, indicated in the inset, and the other treatments, indicated on the
-abscissa. }
+	\caption{ \footnotesize{
+		Empirical difference in priming, $\hat{\theta}_\text{NB}$, between 
+		various treatments.  The difference in priming between each pair of 
+		treatments 
+		was determined by cross-validation of a Naive Bayes classifier trained
+		to classify workers based on the labels they attributed to the first
+		image of the final image set. Each panel compares a basis treatment,
+		indicated above the pannel, to various treatments indicated on the
+		abscissa.  We can conclude, with 95\% confidence, that the classifier
+		is performing better than chance when $\hat{\theta}_\text{NB}$ 
+		exceeds 0.168, indicated by the dotted line.  See \textbf{Methods} for
+		the calculation of this confidence threshold.
+	}}
 \end{figure}
 
-Next we looked at the degree to which labels from individual final images 
-reveal priming.  It would stand to reason that, as workers proceed through 
-the final images, the effects of priming might be ``washed out''.  
-Indeed, when labels from just one of the images
-in the final set were used, $\theta_\text{NB}$ was lower for later images (see
-\textbf{Figure 6}).
-Understanding the dynamics of priming wash-out in greater detail is an 
-important direction for future work.
+\paragraph{Earlier tasks orient workers' focus during later tasks.} 
+We next investigated the \textit{nature} of the inter-task effects.  Since the
+initial images were chosen to emphasize either food (ingredients set) or 
+culture (cultural set), we looked for effects in the number of culture- and 
+food-oriented labels that workers attributed to the final image set.
 
-\paragraph{Earlier tasks orient focus during later tasks.} 
+To this end, we constructed an ontology of labels attributed to the final 
+images.  The ontology was constructed as a directed acyclic graph, with edges 
+pointing from more general labels to more specific ones.
+For example, our ontology contains the path \texttt{food} $\to$ 
+\texttt{ingredients} $\to$ \texttt{vegetables} $\to$ \texttt{tomato}. We 
+provide more detail about the construction of the ontology in the 
+\textbf{Materials and Methods} section.
+
+We counted labels as being culture- and/or food-oriented based on 
+whether the label had inbound paths from the abstract labels \texttt{culture} 
+or \texttt{food} in the ontology. Since food is a central feature 
+of culture, there were many labels that were both culture- and food-oriented 
+in this sense.  Nevertheless, there were many food-oriented labels, such as 
+\texttt{bread}, which lacked specific cultural connections.  Meanwhile, there 
+were many non-food, culture-oriented labels, such as \texttt{russian dolls}.
+
+When we tallied labels attributed to the first image of the final set, 
+we found that workers shown the cultural initial set produced significantly 
+more culture-oriented labels and less food-oriented ones 
+(see \textbf{Fig. 2A}).  In fact, the inter-task
+effect was so strong that it essentially reversed the proportion of culture- 
+and food-oriented labels seen for the ambiguous set.  On the other hand, the 
+composition of labels attributed by 
+workers shown the ingredients image set was not significantly different from 
+that attributed by workers shown the ambiguous set.  This shows that inter-task
+effects can profoundly alter workers' focus, but the effects brought 
+about by showing workers the ambiguous and ingredients sets were not 
+significantly different.
+
+\paragraph{Earlier tasks influenced workers' level of specificity.} 
 \begin{figure}
-	\includegraphics[scale=0.94]{figs/orientation_specificity.pdf}
-	\caption{Percent label composition (culture- vs food-oriented labels) for 
-		various images and treatments.  Panel A shows the composition of 
-		labels, aggregated over all treatments, as a function of test image.
-		Panel B shows the composition of labels, aggregated over all images, as
-		a function of treatment.  Panel C shows the composition of labels 
-		attributed to the first test image by various treatments.}
+	\begin{center}
+		\includegraphics[scale=0.70]{figs/orientation_specificity.pdf}
+	\caption{\footnotesize{
+		\textbf{A}) Percent label composition (culture- vs food-oriented 
+		labels) for 
+		various images and treatments.  
+		\textbf{B}) Relative specificities of treatments
+		indicated along the abscissa compared to those indicated above the 
+		plot.  The size of the bar indicates how much more specific
+		the labels from one treatment are compared to the other, and points 
+		toward in the direction of the more specific treatment.
+	}}
+	\end{center}
 \end{figure}
 
-Having demonstrated both inter-task and framing effects, we next
-investigated the \textit{nature} of these effects.  To this
-end, we constructed an ontology of all the labels attributed to
-the final images.   
-The ontology is a directed acyclic graph of terms,
-with directed edges drawn from abstractions toward instances.  For example,
-our ontology contains the path \texttt{food} $\to$ \texttt{ingredients} $\to$ 
-\texttt{vegetables} 
-$\to$ \texttt{tomato}. We provide more detail about the construction of the 
-ontology in the \textbf{Materials and Methods} section.
+Using the ontology described in the previous section, we compared treatments 
+in their degree of specificity.  When comparing two labels $\ell_1$ and 
+$\ell_2$ produced by different workers, we say that $\ell_2$ is more specific 
+than $\ell_1$ if there is a \textit{directed path} from $\ell_1$ to $\ell_2$.  
+If there is no directed path between $\ell_1$ and $\ell_2$, then they are 
+non-comparable.  As an example, \texttt{tomato} is more specific than 
+\texttt{food}, while \texttt{statue} and \texttt{food} are non-comparable.
 
-We counted the number of labels that were of cultural- 
-or food-orientation,
-based on whether the label had inbound paths from the 
-abstract classes \texttt{culture} and/or \texttt{food} in the ontology. Of 
-course, food is a central feature of culture, so many labels turned out to be
-both culture- and food-oriented in this sense.  Nevertheless, there were many 
-food-oriented labels, such as \texttt{bread}, which were culturally highly 
-ambiguous, and did not have an inbound path from \texttt{culture} in the 
-ontology.  Meanwhile, there were many non-food, culture-oriented labels, such
-as \texttt{russian dolls}.
+We can compare the degree of specificity of two workers by comparing the 
+labels each gives to some image in the final set.  Thus, we define the relative
+specificity of worker $u$ and $v$ for the $i$th image in the final set to be
+$s_i(u,v)$:
 
-%The ontology often contained 
-%alternative labels for food which were culturally more specific, for example 
-%\texttt{roti}, which are attributed cultural-orientation in the ontology.  
-%This provided a degree of freedom upon which inter-task priming and framing 
-%might act.
+\begin{align}
+	s_i(u,v) = \sum_{\ell \in u(i) } \;
+	\sum_{m \in v(i)} 
+	\left(\mathbf{1}_{[\ell > m]} - \mathbf{1}_{[m>\ell]}\right),
+	\label{eq:worker-specificity}
+\end{align}
 
-Taking the labels from all treatments together, we observed significant 
-variance in the label composition (fraction of food- and culture-oriented 
-labels) between the various 
-images in the final set (see \textbf{Fig. 7A}).  This is to be expected, due 
-to differences in the content of the images; for our purpose, we are 
-interested in the systematic differences between treatments, not between 
-images.
+where $u(i)$ denotes the set of labels attributed by worker $u$ to image $i$, 
+and $\mathbf{1}_{[\ell > m]}$ evaluates to 1 if $\ell$ is more specific than 
+$m$, and 0 otherwise.
 
-We compared the composition of labels between different treatments by
-aggregating labels attributed to all the images from the final set within a 
-given treatment (see \textbf{Fig. 7B}).  
-Treatments that began by labeling the cultural images, 
-subsequently attributed significantly more culture-oriented and fewer 
-food-oriented labels to the final images, as compared to the other 
-treatments ($\alpha=0.05$).  Meanwhile, all of the $\textsc{ingr}_x$ 
-treatments produced more food-oriented labels, but we cannot assert a 
-systematic effect at a significance of $\alpha = 0.05$.
+We can then define the relative specificity of treatments $\mathcal{U}$ and 
+$\mathcal{V}$, with regard to
+the $i$th image, $S_i(\mathcal{U},\mathcal{V})$, to be the mean
+relative specificity of two workers drawn uniformly from the treatments.  
+We obtain the estimator, $\hat{S}_i(\mathcal{U},\mathcal{V})$, by computing
+the sample average for our experimental data:
 
-Although the effect on label composition, brought about by having workers 
-initially label cultural images, was statistically significant, the effect 
-size was admittedly somewhat small (\textbf{Fig 7B}). Since we observed that 
-priming 
-difference ``wears off'', we analyzed label composition on a per-image basis.
-Indeed, for the first image in the final set, workers from 
-$\textsc{cult}_{img,x}$ strongly favored culture- over 
-food-oriented labels (\textbf{Fig. 7C}). The effect was strong enough to 
-essentially invert the proportions of culture- and food-oriented labels 
-relative to all other treatments, which favored food-oriented labels.  
-This shows that \textit{inter-task effects can dramatically distort the results
-of human computation tasks}.
+\begin{align}
+	\hat{S}_i(\mathcal{U},\mathcal{V}) = 
+	\frac{1}{|\mathcal{U}| |\mathcal{V}|}
+	\sum_{u \in \mathcal{U}} \;
+	\sum_{v \in \mathcal{V}} \;
+		s_i(u,v).
+		\label{eq:specificity}
+\end{align}
 
-To exhibit the effect longitudinally, as a function of the number of images
-labeled since exposure to the initial set, we computed the 
-\textit{excess cultural orientation} 
-($\Delta_{cult}$) of
-$\textsc{cult}_{img}$ relative to $\textsc{ambg}$ as follows: 
+Further details for the estimation of relative specificity and the standard
+error of the estimation are given in \textbf{Methods}.
+
+We found that, with regard to labels attributed to the first image of the 
+final set, workers from \textsc{AMBG} were more specific than workers from
+either $\textsc{CULT}_{img}$ or $\textsc{INGR}_{img}$.  When we compare 
+$\textsc{CULT}_{img}$ to $\textsc{INGR}_{img}$, we found that workers from
+$\textsc{INGR}_{img}$ were more specific.  This shows that inter-task 
+effects substantially influence the specificity of labels that workers provide.
+
+\paragraph{Inter-task effects ``wash out'' quickly.}  
+\begin{figure}
+	\includegraphics[scale=0.7]{figs/longitudinal_theta_excess-culture.pdf}
+	\caption{\footnotesize{
+		\textbf{A}) Difference in priming between \textsc{AMBG} and 
+		$\textsc{CULT}_{img}$ measured based on the accuracy of a Naive Bayes 
+		classifier during cross-validation, when trained on labels from the
+		test images indicated along the abscissa.
+		\textbf{B}) Excess cultural orientation of labels attributed to
+		the test images indicated on the abscissa, by workers from
+		$\textsc{CULT}_{img}$ relative to those attributed by workers from
+		\textsc{AMBG}, calculated using \textbf{Eq. 3}.
+	}}
+\end{figure}
+At this point we have 
+investigated the inter-task effects induced on only the first image of the 
+final image set.  This is because, as mentioned, the effects are strongest on 
+for first image.  We now examine how the inter-task effects vary as workers 
+proceed through the images in the final set.  Since the final images are the
+same for all treatments, it would stand to reason that the inter-task effects
+induced by the initial image sets would fade away, being washed out by the
+inter-task effects of the final set.
+
+Looking at the classifier performance, $\hat{\theta}_{NB}$, with respect to the
+treatments \textsc{AMBG} and $\textsc{CULT}_{img}$, we find that performance
+drops off dramatically after just the first image (see \textbf{Fig. 3A}).
+This suggests that inter-task effects mainly arise between consecutive tasks.
+However, a residual distinguishability between these two treatments does 
+persist until the final image (although for the fourth image we cannot assert
+this with 95\% confidence).
+
+We can similarly look at how the inter-task effects on label composition
+(i.e. fraction of culture- and food-oriented words) play out as workers 
+progress through the final image set.  To do this, we define the 
+\textit{excess cultural orientation} as the number of culture-orientod labels 
+minus the number of food oriented ones.  Tracking the excess cultural 
+orientation across the images is, however, not in itself meaningful,
+because some images will inherently carry more cultural content than others. 
+To account for this, we calculate the excess cultural content for both 
+\textsc{AMBG} and $\textsc{CULT}_{img}$, and subtract the former from the 
+latter, yeilding the \textit{relative} excess cultural content, 
+$\Delta_{cult}$.  Formally,
+
 \begin{align}
@@
 \end{align}
+
 where $N_{w,cult}^{(i)}$ stands for the number of culture-oriented labels 
@@
 treatment.
-Intuitively, this is intended to capture how much 
-more culture-oriented the labels from $\textsc{cult}_{img}$ are than those
-from $\textsc{ambg}$, for image $i$.
 
-The results from this calculation show the strong influence of the 
-initial image set on the labels attributed to the first image in the final set
-(see \textbf{Fig. 8}).  However, for later images, the effect immediately 
-drops below statistically significant levels, while remaining always positive.
+The relative excess cultural content varied as workers proceed through the
+final image set in much the same way that $\hat{\theta}_\text{NB}$ did: for the
+first test image, it is significantly greater than zero, but drops off rapidly
+thereafter.  Unlike $\hat{\theta}_\text{NB}$, $\Delta_{cult}$ ceases to
+be significantly greater than zero after the second test image, so it would 
+seem that $\hat{\theta}_\text{NB}$ is the more sensitive of the two in
+detecting inter-task effects.
 
-\paragraph{Earlier tasks affect attention to detail during later tasks.}
+\paragraph{Inter-task similarity encourages more specific labels.}
+For the next part of the analysis, it will be useful to speak of the
+``similarity'' between two image sets. In general, the characterization of 
+image content 
+is deeply complex and has been approached from the perspectives of 
+art\cite{panofsky1939studies,shatford1986analyzing},
+psychology\cite{Tversky1977327}, and information retrieval\cite{Jaimes20002}.
+Furthermore, the perception of \textit{similarity} is a particularly subtle 
+psychological phenomenon.  For example, a figure $A$ can appear simultaneously
+both \textit{more} and \textit{less} similar to an object $C$ than some other 
+object $B$[***].
 
-Using the ontology described
-in the previous section, we compared treatments in their degree of specificity.
-When comparing two labels $\ell_1$ and $\ell_2$ produced by different workers,
-we say that $\ell_2$ is more specific than $\ell_1$ if there is a 
-\textit{directed path} from $\ell_1$ to $\ell_2$.  If there is no directed path
-between $\ell_1$ and $\ell_2$, then they are non-comparable.  As an example,
-\texttt{tomato} is more specific than \texttt{food}, while \texttt{statue}
-and \texttt{food} are non-comparable.
-
-We can compare the specificity of two workers by comparing, for each image,
-the labels given by one worker with those of the other.  Thus, we define the
-specificity of worker $u$ relative to worker $v$ to be $s(u,v)$:
+In the present study, we are more interested in the ultimate outputs of 
+workers' rather than the psychological details which lead to them (though 
+these are interesting in their own right).  This allows us to sidestep the 
+complication in attributing similarity: we asses how similar two sets of 
+images are, 
+\textit{with respect to the labelling task}, by looking at the fraction of 
+labels that they share.  Formally, we compute the similarity of two images
+sets $X$ and $Y$ by computing the Jacquard index between the sets of labels 
+attributed to them:
 
 \begin{align}
-	s(u,v) = \sum_{i=1}^5 \;
-	\sum_{\ell \in u(i) } \;
-	\sum_{m \in v(i)} 
-	\left(\mathbf{1}_{[\ell > m]} - \mathbf{1}_{[m>\ell]}\right),
-	\label{eq:worker-specificity}
-\end{align}
-where $u(i)$ denotes the set of labels attributed by worker $u$ to image $i$, 
-and $\mathbf{1}_{[\ell > m]}$ evaluates to 1 if $\ell$ is more specific than 
-$m$, and 0 otherwise.
-
-We can then define the relative specificity of two treatments, 
-$S(\mathcal{U},\mathcal{V})$, to be the average
-relative specificity of workers drawn uniformly from the treatments.  
-We obtain an estimator, $\hat{S}({\mathcal{U}, \mathcal{V}})$, using the 
-sample mean:
-
-\begin{align}
-	\hat{S}(\mathcal{U},\mathcal{V}) = 
-	\frac{1}{|\mathcal{U} \times \mathcal{V}|}
-	\sum_{(u,v) \; \in \; \mathcal{U} \times \mathcal{V}} \;
-		s(u,v),
-		\label{eq:specificity}
+	\text{Sim}(X,Y) = \frac{L(X) \cap L(Y)}{L(X) \cup L(Y)},
 \end{align}
 
-where $\mathcal{U}$ and $\mathcal{V}$ are treatments, formally taken
-as sets of workers.
+\begin{table}
+\centering
+\begin{tabular}{ l  d  s s s s}
 
-When we compared each of the treatments to \textsc{ambg} in this way, 
-all treatments in which a non-ambiguous initial image set was 
-displayed have \textit{lower} specificity 
-(most, but not all, at $\alpha=0.05$; see \textbf{Fig. 9A}).  To understand
-how relative specificity is being attributed, we repeated the calculation of 
-specificities relative to \textsc{ambg}, but including only the non-food-, culture-oriented 
-labels (see \textbf{Figs. 9D}), and only the non-culture-, food-oriented labels
-(see \textbf{Fig. 9G}).  These calculations show that the loss of 
-specificity of treatments that initially labeled images other than those from
-the ambiguous set, was attributable to specificity of food-oriented labels, 
-but not culture-oriented ones.
+\toprule    
+\multirow{2}{*}{Image set} & \multicolumn{1}{c}{\# of unique} & 
+\multicolumn{4}{c}{Similarity}  \\
+\cline{3-6}
 
-It might be the case that labels of a certain semantic connection are less 
-influenced by inter-task effects with regard to specificity. Alternatively,
-there may have simply been too few cultural labels for an effect on specificity
-to manifest (see \textbf{Fig. 7}).
-The lower number of cultural labels might be due to the fact that people's 
-vocabulary for cultural concepts is less diverse than that for food, or that 
-culture, being more abstract, is less ``imageable'' \cite{Swaab200299}.
+&  \multicolumn{1}{c}{labels} 
+& \multicolumn{1}{c}{Ambiguous} 
+& \multicolumn{1}{c}{Cultural} 
+& \multicolumn{1}{c}{Ingredients}
+& \multicolumn{1}{c}{Test} \\
 
-Nevertheless, the dramatic drop in overall specificity relative to 
-\textsc{ambg}, induced when workers begin by labelling the culture or 
-ingredients images, demonstrates that 
-inter-task effects can strongly influence the specificity of task output.
-This is likely to be a major quality factor in nearly all HPU-driven studies.
+\midrule
 
-\td{count the number of occurrences of cultural and food-oriented labels, 
-	to see if the non-responsiveness of culture had to do with restricted
-number of labels}.
+Ambiguous & 763 & 1 & 0.0418 & 0.142 & 0.167 \\
 
-\begin{figure}
-	\includegraphics{figs/longitudinal_theta_excess-culture.pdf}
-	\caption{Excess culture-oriented label composition in the labels provided
-		by $\textsc{cult}_{img}$ as compared to $\textsc{ambg}$, for various
-		test images (see \textbf{Eq. 1} for calculation).
-	}
-\end{figure}
+Cultural & 659 & 0.0418  & 1 & 0.0347 & 0.0561 \\
 
-\subsection*{Discussion}
+Ingredients & 681 & 0.142  & 0.0347 & 1 & 0.110 \\
 
-\paragraph{Inter-task effects are strong.}  We expected that by showing
-workers the funder names ``The Global Foundation for Cultural Recognition'',
-and ``The National Foundation for Nutritional Awareness'', workers would 
-be strongly influenced, interpreting this as and indication of what content 
-is salient (culture or food).
-To our surprise, it turned out that changing the initial set of images that
-workers labeled had a much stronger influence on label orientation and 
-specificity than did framing the task by naming the funder.
-This points to a serious hazard in conducting studies using human computation,
-academic or otherwise: even if the requester has 
-eliminated surrounding influences to every practical extent, 
-\textit{the greatest source of bias might lurk in the tasks themselves}.
+Test & 1695 & 0.167  & 0.0561 & 0.110 & 1
+\\
+\bottomrule
 
-Replication of tasks with randomized ordering is one way to abate inter-task
-effects.  But the requester could also include an initial set of tasks as a 
-``tuning phase''.  During the tuning phase, workers would be primed in a 
-controlled way, through exposure to tasks that had been specially picked to
-orient worker focus in a useful manner.  Moreover, this phase could double as a
-screening phase to select quality workers [***].  However, a deeper 
-understanding of the persistence of inter-task effects is needed to know if 
-this is viable.
+\end{tabular}
+\caption{\footnotesize{
+	Number of unique labels attributed to each image set, and their
+	similarities based on \textbf{Eq. 4} 
+}}
+\label{table:2}
+\end{table}
 
-\paragraph{Subtle priming effects can be detected with $\theta_\text{NB}$.}
-The Naive Bayes classifier uses the frequency of occurrence of all labels to
-classify workers.  Thus, it incorporates a quite general class of effects which
-could be subtle and difficult to anticipate.  This explains why 
-$\theta_\text{NB}$ 
-between $\textsc{cult}_{fund}$ and $\textsc{ignr}_{img}$ can be comparable with
-that between $\textsc{cult}_{fund}$ and $\textsc{cult}_{fund,img}$ 
-(see \textbf{Fig. 5}), even though the latter differ much more in label 
-orientation and specificity.  Similarly, while the differences in label
-orientation between $\textsc{cult}_{img}$ and $\textsc{ingr}_{img}$ drop below 
-significance after the first test image (see \textbf{Fig. 8}), 
-$\theta_\text{NB}$ remains significant through to the last image.
+where $L(X)$ denotes the set of labels attributed to $X$.  See \textbf{Methods}
+for additional details regarding the calculation of similarity.
 
-This demonstrates a powerful feature of the definition of priming in terms of 
-algorithmic distinguishability.  Leveraging classifier implementations from
-machine learning, one can systematically screen treatments that had allegedly 
-been primed differently, against a very large class of potential effects.  This
-would allow the analyst to detect that priming had occured without having to 
-know anything about what was done to achieve it.
+The similarities of the various image sets are presented in \textbf{Table 2}. 
+First, observe that the ambiguous and ingredients sets are much more similar 
+to eachother than either is to the culture set.  This is consistent with our
+finding that $\hat{\theta}_\text{NB}$ between \textsc{AMBG} and 
+$\textsc{INGR}_{img}$ was not significant (see \textbf{Fig 1}).
 
-\paragraph{Inter-task similarity drives nuance.}
-We observed already that treatments which started by labeling the the 
-culture or ingredients image sets had less specificity compared to 
-those beginning with the ambiguous image set.  One possible explanation is that
-this is a manifestation of \textit{negative priming}.  Negative priming is a 
-phenomenon in which a person becomes desensitized to non-salient stimuli to 
-which she is repeatedly exposed [***].  Consider that workers who initially 
+Next we draw attention to the similarity between the initial sets and the test 
+set.  The ambiguous set is the most similar to the test set, followed by the
+ingredients set, and the cultural set was most different from the test set.
+Observe that these levels of similarity mirror the label specificity for the 
+corresponding treatments (c.f. \textbf{Fig. 2B}).
+
+This suggests that labelling a series of images that are similar to 
+one another might encourage workers to use more specific terminology.
+Such a phenomenon would be consistent with the psychological mechanism known 
+as \textit{negative priming}.  Negative priming occurs when a person becomes 
+desensitized to non-salient stimuli to which she is repeatedly 
+exposed [***].  Consider that workers who initially 
 labeled the ambiguous image set had already seen five images showing 
-prepared meals by the time they labeled the first test image.  At that point,
-the worker might not regard the labels \texttt{food} or \texttt{meal} to be 
-salient, since they do not distinguish the image she is labeling from any of 
-the others she had seen already.
+prepared meals once they labelled the first test image.  At that point,
+a worker might not regard the labels \texttt{food} or \texttt{meal} to be 
+salient, since they do not distinguish the image from those she had seen 
+already.
 
@@
 images in any way, prior tasks nevertheless create a frame of reference
-relative to which the content of later tasks are judged.  This in turn 
+relative to which later tasks are judged.  This in turn 
 influences the perception of salience. Thus, in a series of subjective 
@@
 
-To support this
-claim, we must to assess the perceived similarity between the various 
-initial image sets (ambiguous, cultural, and ingredients) and the test set.  
-The characterization of image content is deeply complex and has been 
-approached from the perspectives of 
-art\cite{panofsky1939studies,shatford1986analyzing},
-psychology\cite{Tversky1977327}, and information retrieval\cite{Jaimes20002}.  
-However, using the labels attributed by workers, we can operationalize
-the similarity between two image sets, $X$ and $Y$, as the Jacquard index 
-between the sets of labels attributed to them:
-\begin{align}
-	\text{Sim}(X,Y) = \frac{L(X) \cap L(Y)}{L(X) \cup L(Y)},
-\end{align}
-where $L(X)$ denotes the set of labels attributed to $X$.  In calculating
-the similarity, we used the labels attributed by treatments that were not 
-shown a funder name:  \textsc{ambg}, $\textsc{cult}_{img}$, and 
-$\textsc{ingr}_{img}$.
+\subsection*{Discussion}
 
-Calculated in this way, the ambiguous image set was the most similar to the 
-test set, followed by the ingredients set, and the cultural image set
-was most different from the test set (see \textbf{Table 2}.)  Comparing
-this to the relative specificities calculated for these treatments 
-(see \textbf{Fig. 9}) confirms that workers who labeled an initial 
-image set that was more similar to the test set attributed more specific 
-labels to the test set.
+\paragraph{Inter-task effects should be considered during task design.}  
+Our results show that inter-task effects can have a strong influence on how
+workers label images.  In particular, we observed that prior tasks influence
+the specificity and content of labels.  Surprisingly, framing a task by 
+indicating a semantically-loaded funder had much milder effects on worker 
+outputs, generally below the statistical power of our tests.
 
-\paragraph{Priming for better HPU performance.}
-Thus, if one seeks very nuanced characterizations by human workers, 
-our results suggest that the artifacts to be characterized should first 
-be sorted into classes that are internally similar. This could be accomplished 
-with an iterative approach, which begins with a first, coarse 
-characterization of unsorted artifacts. The coarse characterization could then 
-be used to sort the artifacts, which could then be served for finer 
-characterization.  The sorting and re-characterization could in principle be
-repeated several times.
+We therefore caution those designing studies using human computation: even if 
+the requester has eliminated surrounding influences to every practical extent, 
+\textit{the greatest source of bias might lurk in the tasks themselves}.
+Due consideration should be given to how tasks are bundled together.
+While our measurements of $\hat{\theta}_\text{NB}$ indicated that inter-task 
+effects persisted even to the fifth test image, the most severe effects arise 
+between consecutive tasks.
+
+\paragraph{$\theta$ provides a general purpose measure of priming effects.}
+When used three approaches to detecting priming effects: 1) using a Naive Bayes
+classifier to measure $\hat{\theta}_\text{NB}$, 2) tallying the number of 
+culture- and food-oriented labels, and 3) comparing the relative specificity
+of labels based on an ontology.  Of the three, measuring $
+\hat{\theta}_\text{NB}$ was the most sensitive.
+
+In one sense, this is not surprising because the Naive 
+Bayes classifier takes into account the frequency of occurence of all labels 
+encountered during training.  But it is remarkable that the 
+method which encorporates neither prior knowledge about the image contents nor 
+label semantics, outperforms those that do.  This is a powerful feature 
+because, given the outputs from two sets of workers, one can test whether they 
+have been differently primed without knowing how that priming might manifest.
+
+Our algorithmic definition of priming is phrased in terms of worker outputs
+rather than psychological phenomena.  This provides a connection between
+the priming effects and their potential to impact decisions made on the basis
+of worker outputs.  In the case of a binary decision, $\theta$
+describes the worst-case bias introduced by failing to control for priming 
+effects.
+
+\paragraph{Batching tasks for better HPU performance.}
+Our proposed connection between similarity and specificity during 
+image-labelling might be used to tune the specificity of labels.  For example,
+If one seeks very nuanced labelling, our results suggest that the images 
+should first be sorted into batches based on their similarity. This could be 
+accomplished by beginning with a first, coarse characterization of unsorted 
+images, followed by batching based on the labels obtained. Then, the batches
+of similar images could be served for a second round of finer labelling. 
+The sorting and re-labelling could then in principle be repeated.
 
 In effect, this creates a hierarchical workflow, where the first, 
-coarsely-characterizing HPUs provide a stream of artifacts that is split and 
-fed to other HPUs for finer characterization.  This workflow exhibits an 
-interesting difference between HPUs and CPUs.  In general,
+coarsely-characterizing HPUs provide a stream of labelled images that is 
+split (batched) and fed to other HPUs for finer characterization.  This 
+workflow exhibits an interesting difference between HPUs and CPUs.  In general,
 whenever an aspect of a problem can be parallelized when employing CPUs, one
 gains efficiency.  But here, because of HPU hysteresis, we see an example where
-one might lose efficiency through parallelization.
+one might sacrifice accuracy through parallelization.
 
 \subsection*{Conclusion}
+
 Inter-task priming can have a strong effect.  
-For an image-labeling task, inter-task priming was stronger in its effects on 
-the orientation and specificity of labels than was the disclosure of 
+For a canonical image-labeling task, inter-task priming was stronger in its 
+effects on the orientation and specificity of labels than was the disclosure of
 semantically loaded funder names.  Requesters on microtask platforms should 
-beware that strong biases may be introduced do to the particular succession
-of tasks they serve to workers.
-At the 
-same time, inter-task priming might be exploited to improve task output, for 
+take care to avoid introducing biases due to the batching and ordering tasks 
+they serve to workers.  At the same time, inter-task priming might be exploited to improve task output, for 
 example, to drive more (or less) nuanced responses.
@@
 was served to 900 workers, who were uniformly randomly assigned to
-treatments.  All treatments had at least 126 task completions.  To obtain 
+treatments.  Each treatment had at least 126 task completions.  To obtain 
 uniformly sized treatments, we randomly selected 126 samples from each 
@@
 We can reject $\mathbf{H_0}$ at significance $\alpha$ if $\theta_\text{NB}$ 
-is greater than a critical value, $\theta_\text{NB}^*$:
+is greater than or equal to a critical value, $\theta_\text{NB}^*$:
 \begin{align}
@@
 
+\begin{figure}
+	\includegraphics[scale=1.00]{figs/taskImages/testImages.jpg}
+	\caption{Testing image set. These images were presented to all workers in 
+		the order shown after the priming set of images.}
+\end{figure}
+
+\begin{figure}
+	\includegraphics[scale=1.00]{figs/taskImages/ambiguous.jpg}
+	\caption{ Ambiguous image set. These images were presented to workers from 
+		certain treatements (see \textbf{Table 1}) in the order shown.}
+\end{figure}
+
+\begin{figure}
+	\includegraphics[scale=1.00]{figs/taskImages/cultural.jpg}
+	\caption{Cultural image set. These images were presented to workers from 
+		certain treatements (see \textbf{Table 1}) in the order shown.}
+\end{figure}
+
+\begin{figure}
+	\includegraphics[scale=1.00]{figs/taskImages/ingredients.jpg}
+	\caption{ Ingredients image set. These images were presented to workers 
+		from certain treatements (see \textbf{Table 1}) in the order shown.}
+\end{figure}
 \section*{Acknowledgements}
@@
 
-\section*{Figure Legends}
-
-\paragraph{Table 1.}
-	Experimental treatments.  Workers were uniformly randomly
-	assigned to one of the treatments listed above.  The full funder 
-	names used were ``The Global Foundation
-	for Cultural Recognition'' and ``The National Foundation for 
-	Nutritional Awareness''.  The ambiguous, cultural, and ingredients 
-	initial image sets are shown in \textbf{Figs. 2}, \textbf{3}, and 
-	\textbf{4}.
-
-\paragraph{Figure 1.}
-	Posterior image set. These images were presented to all workers after the 
-	initial image set, in the order shown.
-
-\paragraph{Figure 2.}
-	Ambiguous image set. These images were presented to workers from certain
-	treatments (see \textbf{Table 1}) as the initial image set, in the order 
-	shown.
-
-\paragraph{Figure 3.}
-	Cultural image set. These images were presented to workers from 
-	certain treatments (see \textbf{Table 1}) as the initial image set, in the 
-	order shown.
-
-\paragraph{Figure 4.}
-	Ingredients image set. These images were presented to workers from 
-	certain treatments (see \textbf{Table 1}) as the initial image set, in the 
-	order shown.
-
-\paragraph{Figure 5.}
-$F_1$ score and $\theta_\text{NB}$ for the various 
-priming treatments, as measured using a Naive Bayes classifier. Dotted lines 
-show the 95\% confidence interval
-assuming the classifier performed no better than chance.  Each panel 
-presents performance results for the binary classification between a basis 
-treatment, indicated by the inset, and other treatments, indicated on the 
-abscissa.
-
-\paragraph{Figure 6.}
-$F_1$ score and $\theta_\text{NB}$ for the classification of 
-$\textsc{cult}_{img}$ and $\textsc{ingr}_{img}$ using a Naive Bayes 
-classifier.  Dotted lines 
-show the 95\% confidence interval
-assuming the classifier performed no better than chance.  The classifier is provided only the labels attributed to
-particular images as indicated on the abscissa.
-
-\paragraph{Figure 7.}
-Percent label composition (culture- vs food-oriented labels) for 
-various images and treatments.  Panel A shows the 
-composition of labels, aggregated over all treatments, as a function of 
-final image.
-Panel B shows the composition of labels, aggregated over all images, as
-a function of treatment.  Panel C shows the composition of labels 
-attributed to the first final image by various treatments.
-
-\paragraph{Figure 8.}
-Excess culture-oriented label composition in the labels provided
-by $\textsc{cult}_{img}$ as compared to $\textsc{ambg}$, for various
-final images (see \textbf{Eq. 1} for calculation).
-
-\paragraph{Figure 9.}
-Relative specificity of various treatments.
-Each panel shows the comparison between a basis treatment (inset) and 
-target treatments (abscissa).
-Bar heights indicate relative specificity of the target 
-treatment compared to the basis (a positive quantity means the target 
-is more specific), and are normalized to units of standard 
-deviations of the null comparison.  Dotted horizontal lines indicate
-the 95\% confidence interval for the null comparison, which necessarily
-has zero relative specificity (see \textbf{Methods} 
-for an explanation of the null comparison).  Panels D, E, and F 
-represent relative specificity calculated using only culture-oriented
-labels, while panels G, H, and I using only food-oriented labels.
-Labels that are both culture- and food-oriented are excluded from the
-calculations for panels D through I.
-
-\paragraph{Figure S1}
-Relative specificity of various treatments, for labels attributed
-to the first final image.
-Each panel shows the comparison between a basis treatment (inset) and 
-target treatments (abscissa).
-Bar heights indicate relative specificity of the target 
-treatment compared to the basis (a positive quantity means the target 
-is more specific), and are normalized to units of standard 
-deviations of the null comparison.  Dotted horizontal lines indicate
-the 95\% confidence interval for the null comparison, which necessarily
-has zero relative specificity (see \textbf{Methods} 
-for an explanation of the null comparison).  Panels D, E, and F 
-represent relative specificity calculated using only culture-oriented
-labels, while panels G, H, and I using only food-oriented labels.
-Labels that are both culture- and food-oriented are excluded from the
-calculations for panels D through I.
-
 \end{document}

### 2014-08-03 src/analysis.py

@@ -28,7 +28,7 @@ import naive_bayes
 import ontology
 import data_processing
 import numpy as np
-
+import json
 
 # Number of stardard deviations equivalent to the % condifdence for a 
 # normal variate
@@ -85,58 +85,103 @@ class Analyzer(object):
 			self.ontology = ontology
 
 
-	def compare_image_sets(self, fname='data/similarity.txt'):
+	def compare_image_sets(self, fname='data/similarity_new.txt'):
+
+		print 'yo'
 
 		fh = open(fname, 'w')
+		label_sets = {}
+		similarities = {}
 
-		# collect the bag of words for each image set
-		ambiguous_labels = self.get_bag_of_labels(
-			treatments=['treatment0'],
-			images=['prime%d' %i for i in range(5)])
+		# first, collect the bag of labels for the initial image sets
 
-		fh.write('ambg: %d\n' % len(ambiguous_labels))
+		# The label specs indicate where to collect the labels for each 
+		# image set.  Each label spec has the form:
+		# ('image-set-name', [ <list of treatments> ], [ <list of images>])
+		label_specs = [
+			('ambiguous', ['treatment0'], ['prime%d' % i for i in range(5)]),
+			('cultural', ['treatment1'], ['prime%d' % i for i in range(5)]),
+			('ingredients', ['treatment2'], ['prime%d' % i for i in range(5)]),
+			('test', ['treatment%d' % i for i in range(3)], 
+				['test%d' % i for i in range(5)])
+		]
 
-		cultural_labels = self.get_bag_of_labels(
-			treatments=['treatment1'],
-			images=['prime%d' %i for i in range(5)])
+		# Get the bag of labels for each image set specified in label_specs
+		for set_name, treatments, images in label_specs:
+			print set_name, treatments, images
+			label_sets[set_name] = self.get_bag_of_labels(
+				treatments=treatments, images=images)
 
-		fh.write('cult: %d\n' % len(cultural_labels))
+		# Calculate the number of unique labels, and the similarity between 
+		# the bag of labels for each image_set
+		for set_name_i, treatments_i, images_i in label_specs:
 
-		ingredients_labels = self.get_bag_of_labels(
-			treatments=['treatment2'],
-			images=['prime%d' %i for i in range(5)])
[…]

### 2014-08-03 src/plots.py

@@ -68,7 +68,8 @@ def plotSpecificityLongitudinal(
 		assert(data['subject'] == 'treatment1')
 		pick_data.append(data)
 
-	Y = [pd['avg'] for pd in pick_data]
+	# Plotting the inverse (-) is more intuitive
+	Y = [-pd['avg'] for pd in pick_data]
 	Y_err = [pd['stdev']*CONFIDENCE_95 for pd in pick_data]
 	X = range(len(Y))
 
@@ -952,6 +953,10 @@ def plotOrientationAndSpecificity(
 		ncol=3, borderaxespad=0.
 	)
 
+	# Label the subplot
+	ax.text(-0.03, 48, 'A', 
+			va='top', ha='left', size=20)
+
 	ax.yaxis.set_label_coords(-0.10,0.5)
 
 	fig.savefig(writeFname)
@@ -1021,6 +1026,10 @@ def plotOrientationAndSpecificity(
 	zero = ax.plot(
 		xlims, [0, 0], color='0.35', linestyle='-', zorder=0)
 	
+	# label the subplot
+	ax.text(-0.03, 7.5, 'B', 
+			va='top', ha='left', size=20)
+
 	# handle x-axis labelling
 	ax.tick_params(axis='both', which='major', labelsize=9)
 	ax.set_xticks(map(lambda x: x + width/2., X))
@@ -1443,7 +1452,7 @@ def plotAllF1Theta(
 		if i == 0:
 			ax = plt.subplot(gs[i])
 			ax0 = ax
-			ax.set_ylabel(r'$\theta_{NB}$', size=9)
+			ax.set_ylabel(r'$\hat{\theta}_{NB}$', size=9)
 		else:
 			ax = plt.subplot(gs[i], sharey=ax0)
 			plt.setp(ax.get_yticklabels(), visible=False)
@@ -1497,7 +1506,7 @@ def plotAllF1Theta(
 
 
 	y_low, y_high = plt.ylim()
-	plt.ylim(y_low-0.04, y_high)
+	plt.ylim(-0.09, y_high)
 
 	fig.subplots_adjust(wspace=0.05, top=0.77, right=0.97, left=0.09, 
 			bottom=0.24)
@@ -1971,7 +1980,7 @@ def longitudinal_theta_valence(
 	significance_bar = ax_theta.plot(xlims, [theta_star, theta_star],
 		color='0.55', linestyle=':')
 	
[…]

### 2014-08-03 docs/publications/2014.05_PNAS/manuscript.tex
fix selling

@@
 tasks on the AMT platform.  
-(***why we are using image labelling as prototypical task***) 
+(***why we are using image labeling as prototypical task***) 
 Each worker is required to label ten images 
@@
 the content of labels and label specificity based on an ontology we 
-developped for that purpose.
+developed for that purpose.
 
@@
 effects can be used to induce greater specificity.  Our results suggest that
-workers attribute more specific labels when labelling a series of images that
+workers attribute more specific labels when labeling a series of images that
 that are more similar to one another.  This suggests that careful 
@@
 based on its direct effects on label content and specificity, implicitly
-drawing on prior knowledge about the the images and label semantics.
+drawing on prior knowledge about the images and label semantics.
 Remarkably, while being more general, our novel approach was also more 
 sensitive.  This suggests that our measurement approach could be applied in 
-cases where one does not \emph{a priori} know whether any priming has occured, 
+cases where one does not \emph{a priori} know whether any priming has occurred, 
 nor what the effects might be.
@@
 compared to a random guess. We intentionally leave the details of 
-$\mathcal{A}$ unrestricted because $\theta$ should depend on the pontential 
+$\mathcal{A}$ unrestricted because $\theta$ should depend on the potential 
 for two populations to be distinguished, based on their inherent differences, 
@@
 Here, we use a Naive Bayes classifier because it simple and performs well 
-accross a broad range of classification tasks[***].
+across a broad range of classification tasks[***].
 
@@
 made between two options on the basis of worker outputs (e.g. whether or not 
-to flag an image as innappropriate). Any such binary choice has a formal 
+to flag an image as inappropriate). Any such binary choice has a formal 
 structure of a trained classifier (i.e. a distinguisher which discards the 
@@
 	\end{tabular}
-
-%\begin{addmargin}[11em]{11em}
-%	\vspace{2mm}
-%	$^a$\footnotesize{The full funder names used were ``The Glodal Foundation
-%		for Cultural Recognition'' and ``The National Foundation for 
-%		Nutritional Awareness''.}
-%\end{addmargin}
 
@@
 than chance when distinguishing treatments that had different initial image 
-sets.  This demonstrates that inter-task effects were strong for the labelling 
+sets.  This demonstrates that inter-task effects were strong for the labeling 
 tasks.  Of the sixteen treatment pairs having different initial images, there 
@@
 Each of these cases involved distinguishing workers shown the ambiguous set 
-from ones shown the the ingredients set.  The reason for the low 
+from ones shown the ingredients set.  The reason for the low 
 distinguishability of workers from these treatments might be because
@@
 		image of the final image set. Each panel compares a basis treatment,
-		indicated above the pannel, to various treatments indicated on the
+		indicated above the panel, to various treatments indicated on the
 		abscissa.  We can conclude, with 95\% confidence, that the classifier
@@
 progress through the final image set.  To do this, we define the 
-\textit{excess cultural orientation} as the number of culture-orientod labels 
+\textit{excess cultural orientation} as the number of culture-oriented labels 
 minus the number of food oriented ones.  Tracking the excess cultural 
@@
 \textsc{AMBG} and $\textsc{CULT}_{img}$, and subtract the former from the 
-latter, yeilding the \textit{relative} excess cultural content, 
+latter, yielding the \textit{relative} excess cultural content, 
 $\Delta_{cult}$.  Formally,
@@
 images are, 
-\textit{with respect to the labelling task}, by looking at the fraction of 
+\textit{with respect to the labeling task}, by looking at the fraction of 
 labels that they share.  Formally, we compute the similarity of two images
@@
 First, observe that the ambiguous and ingredients sets are much more similar 
-to eachother than either is to the culture set.  This is consistent with our
+to each other than either is to the culture set.  This is consistent with our
 finding that $\hat{\theta}_\text{NB}$ between \textsc{AMBG} and 
@@
 
-This suggests that labelling a series of images that are similar to 
+This suggests that labeling a series of images that are similar to 
 one another might encourage workers to use more specific terminology.
@@
 labeled the ambiguous image set had already seen five images showing 
-prepared meals once they labelled the first test image.  At that point,
+prepared meals once they labeled the first test image.  At that point,
 a worker might not regard the labels \texttt{food} or \texttt{meal} to be 
@@
 In one sense, this is not surprising because the Naive 
-Bayes classifier takes into account the frequency of occurence of all labels 
+Bayes classifier takes into account the frequency of occurrence of all labels 
 encountered during training.  But it is remarkable that the 
-method which encorporates neither prior knowledge about the image contents nor 
+method which incorporates neither prior knowledge about the image contents nor 
 label semantics, outperforms those that do.  This is a powerful feature 
@@
 Our proposed connection between similarity and specificity during 
-image-labelling might be used to tune the specificity of labels.  For example,
-If one seeks very nuanced labelling, our results suggest that the images 
+image-labeling might be used to tune the specificity of labels.  For example,
+If one seeks very nuanced labeling, our results suggest that the images 
 should first be sorted into batches based on their similarity. This could be 
@@
 images, followed by batching based on the labels obtained. Then, the batches
-of similar images could be served for a second round of finer labelling. 
-The sorting and re-labelling could then in principle be repeated.
+of similar images could be served for a second round of finer labeling. 
+The sorting and re-labeling could then in principle be repeated.
 
 In effect, this creates a hierarchical workflow, where the first, 
-coarsely-characterizing HPUs provide a stream of labelled images that is 
+coarsely-characterizing HPUs provide a stream of labeled images that is 
 split (batched) and fed to other HPUs for finer characterization.  This 
@@
 variable which denotes the number of correct classifications when the 
-classifier is chalenged to classify a total of $n$ workers during 
+classifier is challenged to classify a total of $n$ workers during 
 cross-validation.  Under $\mathbf{H_0}$, the probability distribution of $K$ 
@@
 	\caption{ Ambiguous image set. These images were presented to workers from 
-		certain treatements (see \textbf{Table 1}) in the order shown.}
+		certain treatments (see \textbf{Table 1}) in the order shown.}
 \end{figure}
@@
 	\caption{Cultural image set. These images were presented to workers from 
-		certain treatements (see \textbf{Table 1}) in the order shown.}
+		certain treatments (see \textbf{Table 1}) in the order shown.}
 \end{figure}
@@
 	\caption{ Ingredients image set. These images were presented to workers 
-		from certain treatements (see \textbf{Table 1}) in the order shown.}
+		from certain treatments (see \textbf{Table 1}) in the order shown.}
 \end{figure}
-\section*{Acknowledgements}
+\section*{Acknowledgments}
 \section*{References}

### 2014-08-03 docs/publications/2014.05_PNAS/manuscript.tex
add abstract

@@
 
-\title{Inter-task effects introduce bias in crowdsourcing}
+\title{Inter-task effects induce bias in crowdsourcing}
 \author{Edward Newell, Derek Ruths}
@@
 \section*{Abstract}
+Microtask platforms like Amazon Mechanical Turk provide a cheap and fast means
+to engage participants for scientific reasearch.  
+Workers on such platforms prefer to work on batches of tasks of the same 
+type[***], so we investigate the potential for the content of earlier tasks 
+to influence worker performance in later tasks, which we call ``inter-task'' 
+effects.  
+Existing research investigates the impact of various design factors, such as 
+``framing'', on the quality of crowdsourced content, but does not, to 
+our knowledge, address inter-task effects.  
+We employ a canonical image-labeling task on the Amazon Mechanical Turk 
+platform, to measure both inter-task and framing effects, in terms of their 
+impact to the content and specificity of the labels workers provide.
+We also introduce an algorithmic definition of priming, which measures the 
+worst-case bias that priming effects introduce into crowdsourced content.
+We find that inter-task effects produce a much stronger impact than framing, 
+and find that our algorithmic definition yields a powerful, generalized measure
+for priming effects when combined with machine learning algorithms.
+
 \section*{Significance Statement}

### 2014-08-04 docs/publications/2014.05_PNAS/man.tex
make version for hcomp PhD consortium submission

--- 2014-08-03 docs/publications/2014.05_PNAS/manuscript.tex
@@
 %
-\documentclass[a4paper]{report}
-\usepackage[hmargin=2cm,vmargin=2cm]{geometry}
+\documentclass[letterpaper]{article} 
+\usepackage{aaai} 
+\usepackage{times} 
+\usepackage{helvet} 
+\usepackage{courier} 
+\setlength{\pdfpagewidth}{8.5in} 
+\setlength{\pdfpageheight}{11in} 
+%%%%%%%%%%
+% PDFINFO for PDFLATEX
+% Uncomment and complete the following for metadata (your paper must compile with PDFLATEX)
+\pdfinfo{
+	/Title Inter-Task Effects induce Bias in Crowdsourcing
+	/Author Edward Newell
+	/Keywords priming, framing, micro-task, crowdsourcing
+}
+
 \usepackage{scrextend}
 \usepackage{graphicx}
-
 \usepackage{amsmath}
@@
 \newtheorem*{mydef}{Definition}
-
-\usepackage{cite}
 
@@
 
-\newcommand{\td}[1]{{\color{blu}\hl{TODO: #1}}}
+%\setlength{\parindent}{0cm}
+%\setlength{\parskip}{4mm plus1mm minus1mm}
 
-\definecolor{shadecolor}{rgb}{.93,.93,.93}
-\definecolor{blu}{rgb}{0,0,1}
-\setlength{\parindent}{0cm}
-\setlength{\parskip}{4mm plus1mm minus1mm}
-
-\title{Inter-task effects introduce bias in crowdsourcing}
-\author{Edward Newell, Derek Ruths}
-
-\parindent0pt \parskip8pt
-
+%%%%%%%%%%
+% Section Numbers
+% Uncomment if you want to use section numbers % and change the 0 to a 1 or 2
+% \setcounter{secnumdepth}{0} %%%%%%%%%%
+\title{Inter-Task Effects induce Bias in Crowdsourcing}
+\author{Edward Newell \and Derek Ruths\\
+	McGill University, School of Computer Science, Montreal, Canada\\
+}
+%%%%%%%%%%
+% Body of Paper Begins
 \begin{document}
@@
 \section*{Abstract}
-\section*{Significance Statement}
+Microtask platforms allow researchers to engage participants quickly and 
+inexpensively.
+Workers on such platforms probably perform many tasks in succession,
+so we investigate interactions between earlier tasks and later ones, which we 
+call ``inter-task'' effects.  
+Existing research investigates many task design factors, such as 
+``framing'', on the quality of responses, but to our knowledge, does not 
+address inter-task effects.  
+We use a canonical image-labeling task on Amazon Mechanical Turk 
+to measure the impact of inter-task and framing effects on the focus and 
+specificity of labels that workers provide.
+We also introduce an algorithmic definition of priming, which measures the 
+worst-case bias introduced into repsonses.
+We find that inter-task effects produced a much stronger impact than framing, 
+and demonstrate that our novel priming definition yields a generalized 
+measure of priming effects when combined with machine learning algorithms.
+
 \section*{Introduction}
@@
 who do the tasks for fun, a sense of purpose, and remuneration 
-\cite{kazai2013analysis, Antin20122925}.  
+\cite{kazai2013analysis,Antin20122925}.  
 Originally used to distribute clerical work, these platforms 
 increasingly serve as a fast and cheap means to engage experimental 
-participants and manually annotate datasets in a research 
+participants in a research 
 setting \cite{snow2008cheap}.
-Tasks involving qualitative
-judgment (e.g. flagging inappropriate images), natural language annotation,
-and object recognition are commonplace, since it is difficult to achieve 
-comparable performance using only computers \cite{yuen2011survey}.
-%Generally the worker is first given some orientation to the task, and then 
-%performs the task repeatedly (e.g. label several images, one after 
-%the other).
 
-Such platforms make human cognition a fluid resource: it is available 
-on demand in small units, with low transaction 
-cost, from anywhere via the 
-Internet\footnote{\href{http://mturk.com}{http://mturk.com}}.
-The task requester can 
-interact with the platform like a compute server, seamlessly 
+The task requester can interact with the platform like a compute server, 
+seamlessly 
 integrating human and machine computation.  Researchers have put forward the 
-term HPU (Human co-Processing Unit)\footnote{We acknowledge the irony of this 
-term: the original meaning of `computer' was a person who performs 
-computations, its reference to machines being a personification brought into 
-usage in the late 1800s\cite{Dictionary:hl}.}, viewing the introduction of 
+term HPU (Human co-Processing Unit), viewing the introduction of 
 microtask platforms as a new computing architecture
@@
 are subject to priming effects 
-\cite{BJOP:BJOP1796, No2007, beller1971priming} and, in particular, task-repetition effects
-\cite{Gass1999549, sohn2001task}.  
+\cite{BJOP1796,No2007,beller1971priming} and, in particular, task-repetition effects
+\cite{Gass1999549,sohn2001task}.  
 We investigate the effect that previously completed tasks have on workers'
@@
 
-There has been considerable investigation into the factors that affect HPU 
-output on crowdsourced microtask platforms.  Studies have shown that 
-there is a great deal of variance in worker attention and 
-accuracy \cite{kazai2013analysis}.  Factors that affect the quality of HPU 
-output include level of pay\cite{kazai2013analysis}, 
-training\cite{le2010ensuring}, screening workers\cite{paolacci2010running}, 
-and user-interface design
+There has been considerable investigation into the factors that affect the 
+quality and quantity of micro-task completion.  These include the level of 
+pay \cite{kazai2013analysis}, training \cite{le2010ensuring}, screening of 
+workers \cite{paolacci2010running}, and user-interface design 
 \cite{Finnerty2013}.  Research has also investigated \textit{framing}, 
-by testing the effects of disclosing the role of a task within the 
-context of a study \cite{Kinnaird2012281}, and disclosing the ultimate 
-purpose of that study \cite{chandler2013breaking}.  However, to our knowledge, 
-no study has investigated the effects of inter-task priming.
+by testing the effects of disclosing the workflow context 
+\cite{Kinnaird2012281}, and the purpose of tasks 
+\cite{chandler2013breaking}.  To our knowledge, no study has investigated the 
+effects of inter-task priming.
 
 To characterize the effects of inter-task priming, we present a novel  
-\textit{algorithmic definition of priming}, along with a general method 
+\textit{algorithmic definition of priming}, and a general method 
 for measuring priming effects using machine learning algorithms.  
-Existing work on priming effects focuses on the internal psychological 
-mechanisms of priming[***], but here we are interested in how the treatment of 
-workers can impact an application of human computation. This leads us to 
-quantify priming in terms of the algorithmic distinguishability of priming
-treatments.
+Studies of priming typically focus on the internal psychological 
+mechanisms[***], but our definition focuses on the impact that priming has to
+the downstream application of human computation.
 
-In the present work, we investigate inter-task priming using image-labeling 
-tasks on the AMT platform.  
-(***why we are using image labeling as prototypical task***) 
-Each worker is required to label ten images 
-featuring 
+In the present work, we investigate inter-task priming on the Amazon 
+Mechanical Turk platform, using an image-labeling task, one of the most common 
+kinds of tasks on that platform [***].  The task requires workers to label ten 
+images featuring 
 food and culture.  We regard these images as being made up of an 
@@
 from the view of the worker.
-Each worker is randomly assigned one of three initial sets, but the final set
-of images is always the same.  We analyze the effect that the assignment of 
-initial set has on workers' attribution of labels to the final set.  We 
-measure effects using our novel approach, as well as looking for changes in 
-the content of labels and label specificity based on an ontology we 
-developed for that purpose.
+We vary the initial set of images, while keeping the final set the same to 
+analyze the effect that that the initial images have on the labels that 
+workers' attribute to the final set.  We measure effects using our novel 
+approach, as well as looking for changes in the content of labels and label 
+specificity based on an ontology we developed for that purpose.
 
@@
 \textit{framing}: we disclose a fictitious, semantically-loaded name for 
-requester funding the tasks.
-The names were chosen to suggest the requester's interest in 
-a specific aspect of the image content.  One might reasonably expect that this 
-would orient workers to provide a greater quantity and specificity of labels 
-which relate to this ``preferred'' content[***].
+the requester funding the tasks.
+The names were chosen to suggest the requester's interest in a specific 
+aspect of the image content.  We expect this would cause workers 
+to provide more labels, and greater specificity, relating to this 
+``preferred'' content.
 
-Surprisingly, we find that inter-task effects on label orientation and 
-specificity are much stronger than those brought about by framing tasks with a 
-funder name.  Our results show that initial tasks can introduce significant 
-bias in subsequent worker labeling.  Interestingly, we find that inter-task
+Surprisingly, we find that inter-task effects are much stronger than the 
+framing.  Our results show that initial tasks can significantly alter the 
+focus of worker's labels.  Interestingly, we find that inter-task
 effects can be used to induce greater specificity.  Our results suggest that
@@
 Our analysis also highlights important advantages of our novel definition of 
-priming.  Our approach relies on no prior knowledge about the nature
-of the task task whatsoever.  In contrast, we also sought to detect priming
-based on its direct effects on label content and specificity, implicitly
+priming.  Our approach incorporates no prior knowledge about the nature
+of the task whatsoever.  In contrast, we also sought to detect priming
+based on its direct effects on label content and specificity,
 drawing on prior knowledge about the images and label semantics.
-Remarkably, while being more general, our novel approach was also more 
-sensitive.  This suggests that our measurement approach could be applied in 
-cases where one does not \emph{a priori} know whether any priming has occurred, 
-nor what the effects might be.
-
+Remarkably, while being more general, our definition yields a more sensitive
+measure of priming when combined with machine learning algorithms. 
+This approach could be applied to detect priming when one does not 
+\emph{a priori} know whether any priming has occurred, 
+nor what the nature of the effects might be.
 \subsection*{An algorithmic definition of priming}
-
 In psychology, the effects of priming are usually measured in terms of a 
@@
 stimulus object (e.g. a spoken word or an image) when the object is noisier, 
-fainter, or briefer [***].  Methods are also employed to measure processes
-in the brain of the participant, such as by fMRI[***].  These approaches are 
-well-suited to studying the underlying psychological mechanisms at work.
-
-Our purpose is different: we are interested in assessing the ramifications
-that priming of HPUs could have on the applications to which they are employed.
-This influences the approach we take to measurement in two ways.  First, we 
-switch from focusing on the internal mechanisms of HPUs to focusing strictly 
-on the HPU outputs.  Second, we cannot \textit{a priori} know the 
-application for which HPUs are being employed, but we would like to measure 
-any effects that could in principle impact the application.  These 
-considerations motivate us to define priming effects in terms of the 
-algorithmic distinguishability of primed output.
+fainter, or briefer.  Methods are also employed to measure processes
+in the brain of the participant, such as by fMRI.  Our purpose is different: 
+we are interested in assessing the ramifications that priming of HPUs could 
+have on the applications to which they are employed.
+Thus, we choose to define priming effects in terms of the algorithmic 
+distinguishability of the content of primed output.
 
 One difficulty in constructing a definition of priming is that there would 
-appear to be no defensible notion of a ``neutral'' or ``unprimed state''.  A 
-participant 
-always approaches a task in \textit{some} state of mind.  If no priming 
-condition is applied, then the participant is simply primed by her
-exposures prior to the experiment, which cannot be known by the experimenter.  
-While arguments can surely be made that one treatment or another is 
+appear to be no defensible notion of a ``neutral'' or ``unprimed state''.  
+While arguments could perhaps be made that one treatment or another is 
 \textit{more} 
-``neutral'', we refrain from proposing a canonical ``null priming treatment''. 
-Instead, we define priming relatively, and speak of one treatment being 
-\textit{differently primed} from another.
+``neutral'', we choose to define priming relatively, and speak of one 
+treatment being \textit{differently primed} from another.
 
-A definition of priming must also consider that the effects of priming will
-manifest differently depending on the task that participants perform 
-subsequent to priming:  two priming treatments that
-produce markedly different output for one task might be 
-indistinguishable under another task.  Thus, we define priming
-with respect to a task.
-
-A final factor to consider is that people will always differ in their initial
-knowledge, specific aptitudes, and in many other intrinsic aspects.  Moreover,
-priming may not be ``complete'', in the sense that people's experiences before
+From the point of view of applications, the interest of priming is in how it
+affects task performance. Thus, we define priming with respect to a task $\mathcal{T}$.  People will always differ in their initial knowledge, specific 
+aptitudes, and in many other intrinsic aspects.  Moreover, priming may not be 
+``complete'', in the sense that people's experiences before
 priming may continue to have residual effects.  Therefore, we define priming 
@@
 
-To set up the definition, when a population of people $\mathcal{J}$ performs
+To set up the definition, when a population of people $\mathcal{P}$ performs
 a task $\mathcal{T}$ thus producing a population of task-outputs $\mathcal{L}$,
-we will write $\mathcal{T}(\mathcal{J}) = \mathcal{L}$.
+we will write $\mathcal{T}(\mathcal{P}) = \mathcal{L}$.
 
@@
 	$\mathcal{P}_1$, are uniformly and randomly subsampled from an initial 
-	population $\mathcal{P}$, are exposed to (possibly) different priming 
-	treatments, and then perform a task $\mathcal{T}$, 
+	population $\mathcal{P}$, and are exposed to (possibly) different priming 
+	treatments. Each population performs a task $\mathcal{T}$, 
 	producing task-outputs $\mathcal{T}(\mathcal{P}_0)$ and 
@@
 
+\begin{figure*}
+	\centering{
+	\includegraphics[scale=0.94]{figs/f1-thetas_full_pairwise25_img1.pdf}
+	\caption{ \footnotesize{
+		Empirical difference in priming, $\hat{\theta}_\text{NB}$, between 
+		various treatments.  The difference in priming between each pair of 
+		treatments 
+		was determined by cross-validation of a Naive Bayes classifier trained
+		to classify workers based on the labels they attributed to the first
+		image of the final image set. Each panel compares a basis treatment,
+		indicated above the panel, to various treatments indicated on the
+		abscissa.  We can conclude, with 95\% confidence, that the classifier
+		is performing better than chance when $\hat{\theta}_\text{NB}$ 
+		exceeds 0.168, indicated by the dotted line.  See \textbf{Methods} for
+		the calculation of this confidence threshold.
+	}}
+}
+\end{figure*}
+
 In the language of computer science, $\mathcal{A}$ is a classifier performing
@@
 compared to a random guess. We intentionally leave the details of 
-$\mathcal{A}$ unrestricted because $\theta$ should depend on the potential 
-for two populations to be distinguished, based on their inherent differences, 
-rather than on the performance of a particular classifier.
+$\mathcal{A}$ unrestricted because the theoretical value of $\theta$ should 
+depend on the inherent differences between the populations, rather than on 
+the performance of a particular classifier.
 
-In practice, some particular classifier $\mathcal{C}$ must be used and a 
-statistical estimate of its performance $\hat{\theta}_\mathcal{C}$ obtained. 
+In practice, some particular classifier $\mathcal{C}$ is tested (using e.g. 
+cross-validation) yielding a statistical estimate of its performance 
+$\hat{\theta}_\mathcal{C}$. This
 $\hat{\theta}_\mathcal{C}$ acts as a lower bound for the 
-theoretical value $\theta$ from the definition, because there might 
+theoretical value of $\theta$, because there might 
 exist some other classifier $\mathcal{C}'$ with 
 $\hat{\theta}_\mathcal{C'}>\hat{\theta}_\mathcal{C}$.
-Here, we use a Naive Bayes classifier because it simple and performs well 
-across a broad range of classification tasks[***].
+For our experiment, we use a Naive Bayes classifier because it is easy to
+implement and performs well across a broad range of classification tasks[***].
 
-To interpret $\hat{\theta}_\mathcal{C}$, imagine that some choice is to be
-made between two options on the basis of worker outputs (e.g. whether or not 
-to flag an image as inappropriate). Any such binary choice has a formal 
-structure of a trained classifier (i.e. a distinguisher which discards the 
-first two inputs). This means that $\hat{\theta}_\mathcal{C}$ estimates a 
-lower bound for the worst-case bias introduced in such a binary decision when 
-one failed to control for priming effects.
-
+To interpret $\hat{\theta}_\mathcal{C}$, imagine that some choice 
+$\mathcal{C}$ is to be made between two options on the basis of worker 
+outputs (e.g. whether or not to flag an image as inappropriate). Any such 
+binary choice has the formal structure of a distinguisher that only considers 
+the last of its three inputs. Thus, we can directly compare $\mathcal{C}$ to 
+the optimal distinguisher, $\mathcal{A}$.  If, prior to knowing the input to 
+$\mathcal{C}$, either of its outcomes is equally likely, then the worst 
+possible bias that priming can introduce is bounded above by $\theta$. 
+This means that $\hat{\theta}_\mathcal{C}$ estimates a 
+lower bound for the worst-case bias introduced in a binary 
+decision that provides a full bit of information, made on the basis of worker 
+outputs, when one failed to control for the corresponding priming treatments.
 \subsection*{Experimental Setup}
@@
 
-	\begin{addmargin}[4em]{4em}
 	\caption{ \footnotesize{ 
@@
 	}}
-	\end{addmargin}
 	\label{table:1}
 \end{table}
-
 We solicited 900 AMT workers to perform an image-labeling task relating to
 food and culture.  The workers were randomly assigned to one of seven 
-treatments shown in \textbf{Table 1}.  Workers were first shown brief 
-instructions.  Depending on their treatment, workers were then shown the 
-name of a research funder, or this step was skipped.  When shown, 
-the funder name was either
-``The Global Foundation for Cultural Recognition'', or 
-``The National Foundation for Nutritional Awareness''.
+treatments shown in \textbf{Table 1}.  Depending on their treatment, workers were then shown the 
+name of a research funder, or this step was skipped.
+Next, workers were shown ten images, one at a time and were required to provide
+five labels for each.  For the purpose of analysis, we divide the images
+into \textit{initial} and \textit{final} sets, comprising respectively the 
+first five and last five images.  From the perspective of the worker, there 
+was no distinction or interruption between the initial and final sets. 
+Depending on the treatment, one of three initial image sets was chosen, but
+the final set was always the same.
 
-Next, workers were
-shown ten images, one at a time. Workers were required to label each image 
-with five descriptive labels before moving on to the next.  For the purpose 
-of analysis, we divide the images
-into \textit{initial} and \textit{final} sets, comprising respectively the 
-first five and last five images shown.  As mentioned, from the perspective of 
-the worker, there was no 
-distinction or interruption between the initial and final sets. 
-Depending on the treatment to which the worker was assigned, one of three 
-initial image sets was chosen. The final image set was the same for all 
-treatments.
-
-For the final image set, we chose 
-images that contained prepared meals and featured a prominent, identifiable 
-culture (see \textbf{Fig. 4}).  We intended that the content of these images 
-would elicit labels focusing on food or culture (or both).
-We refer to the three initial image sets as the ``ambiguous'', ``cultural'', 
-and ``ingredients'' sets.  The ambiguous set was chosen to
-be very similar to the final image set, in the sense that it consisted of
-images of prepared meals (see \textbf{Fig. 5}).  However, its cultural 
-features were intended to be less prominent.  The cultural set featured 
-iconic cultural scenes, but no food at all (see \textbf{Fig. 6}).  Finally, 
-images from the 
-ingredients set depicted separated ingredients, but, 
-like the ambiguous set, were chosen to avoid prominent cultural features (see 
-\textbf{Fig. 7}).  See the \textbf{Materials and Methods} section for further 
-details.
-
+The final image set, comprised images containing prepared meals and featured a 
+prominent, identifiable culture (see \textbf{Fig. 4}).
+To identify the initial image sets, we use the names ``ambiguous'', 
+``cultural'', and ``ingredients''.  The ambiguous set was chosen to
+be similar to the final image set, in the sense that it consisted of
+images of prepared meals (see \textbf{Fig. 5}),  but its cultural 
+features were less prominent.  The cultural set featured 
+iconic cultural scenes, but no food at all (see \textbf{Fig. 6}).  Images from 
+the ingredients set depicted separated ingredients, but, 
+like the ambiguous set, avoided prominent cultural features (see 
+\textbf{Fig. 7}).
 \subsection*{Results}
@@
 We tested for priming effects using our algorithmic definition, implemented 
-with a Naive Bayes classifier.  This involved measuring the classifier's 
-accuracy in classifying workers chosen from a pair of treatments during 
-cross-validation (see \textbf{Methods} for details).  The classifier's accuracy
-for cross-validations involving each pair of treatments is shown in 
+with a Naive Bayes classifier.  The classifier's accuracy
+in cross-validations involving each pair of treatments is shown in 
 \textbf{Fig.1}.
@@
 With some exceptions, the classifier performed significantly better 
-than chance when distinguishing treatments that had different initial image 
-sets.  This demonstrates that inter-task effects were strong for the labeling 
-tasks.  Of the sixteen treatment pairs having different initial images, there 
-were three cases where the classifier performance was on par with chance. 
-Each of these cases involved distinguishing workers shown the ambiguous set 
-from ones shown the ingredients set.  The reason for the low 
-distinguishability of workers from these treatments might be because
-the ambiguous and ingredients sets are somewhat similar to one another.
-We will come back to this point later when we discuss the degree of similarity 
-between image sets.
+than chance when distinguishing treatments that had different initial tasks.  
+This demonstrates that inter-task effects were strong. Of the sixteen 
+treatment pairs having different initial tasks, the classifier was unable to
+distinguish treatments significantly better than chance in three cases.
+Each cases involved distinguishing treatments having the ambiguous and 
+ingredients set.  Later we discuss the similarity between image sets, and 
+we will argue that this is because the ambiguous and ingredients sets are 
+similar.
 
-In contrast, the classifier never performed significantly better than chance
-when distinguishing treatments that differed only in the funder name shown. 
-Thus, framing effects were rather weak.
-
-\begin{figure}
-	\includegraphics[scale=0.94]{figs/f1-thetas_full_pairwise25_img1.pdf}
-	\caption{ \footnotesize{
-		Empirical difference in priming, $\hat{\theta}_\text{NB}$, between 
-		various treatments.  The difference in priming between each pair of 
-		treatments 
-		was determined by cross-validation of a Naive Bayes classifier trained
-		to classify workers based on the labels they attributed to the first
-		image of the final image set. Each panel compares a basis treatment,
-		indicated above the panel, to various treatments indicated on the
-		abscissa.  We can conclude, with 95\% confidence, that the classifier
-		is performing better than chance when $\hat{\theta}_\text{NB}$ 
-		exceeds 0.168, indicated by the dotted line.  See \textbf{Methods} for
-		the calculation of this confidence threshold.
-	}}
-\end{figure}
-
-\paragraph{Earlier tasks orient workers' focus during later tasks.} 
-We next investigated the \textit{nature} of the inter-task effects.  Since the
-initial images were chosen to emphasize either food (ingredients set) or 
-culture (cultural set), we looked for effects in the number of culture- and 
-food-oriented labels that workers attributed to the final image set.
-
-To this end, we constructed an ontology of labels attributed to the final 
-images.  The ontology was constructed as a directed acyclic graph, with edges 
-pointing from more general labels to more specific ones.
-For example, our ontology contains the path \texttt{food} $\to$ 
-\texttt{ingredients} $\to$ \texttt{vegetables} $\to$ \texttt{tomato}. We 
-provide more detail about the construction of the ontology in the 
-\textbf{Materials and Methods} section.
-
-We counted labels as being culture- and/or food-oriented based on 
-whether the label had inbound paths from the abstract labels \texttt{culture} 
-or \texttt{food} in the ontology. Since food is a central feature 
-of culture, there were many labels that were both culture- and food-oriented 
-in this sense.  Nevertheless, there were many food-oriented labels, such as 
-\texttt{bread}, which lacked specific cultural connections.  Meanwhile, there 
-were many non-food, culture-oriented labels, such as \texttt{russian dolls}.
-
-When we tallied labels attributed to the first image of the final set, 
-we found that workers shown the cultural initial set produced significantly 
-more culture-oriented labels and less food-oriented ones 
-(see \textbf{Fig. 2A}).  In fact, the inter-task
-effect was so strong that it essentially reversed the proportion of culture- 
-and food-oriented labels seen for the ambiguous set.  On the other hand, the 
-composition of labels attributed by 
-workers shown the ingredients image set was not significantly different from 
-that attributed by workers shown the ambiguous set.  This shows that inter-task
-effects can profoundly alter workers' focus, but the effects brought 
-about by showing workers the ambiguous and ingredients sets were not 
-significantly different.
-
-\paragraph{Earlier tasks influenced workers' level of specificity.} 
-\begin{figure}
-	\begin{center}
+\begin{figure*}
+	\centering{
 		\includegraphics[scale=0.70]{figs/orientation_specificity.pdf}
@@
 	}}
-	\end{center}
-\end{figure}
+}
+\end{figure*}
+In contrast, the classifier never performed significantly better than chance
+when distinguishing treatments that differed only in framing.  Thus, framing 
+effects were rather weak.  In fact, framing effects were generally weak in
+our results, so we omit treatments involving framing from the remainder of
+our presentation to save space.  We encourage the interested reader to look
+at the results for these treatments in the supplementary material.
+\paragraph{Earlier tasks orient workers' focus during later tasks.} 
+Since the initial images were chosen to emphasize either food (ingredients set)
+or culture (cultural set), we looked for effects on the number of culture- and 
+food-oriented labels that workers attributed to the final image set.
 
-Using the ontology described in the previous section, we compared treatments 
-in their degree of specificity.  When comparing two labels $\ell_1$ and 
-$\ell_2$ produced by different workers, we say that $\ell_2$ is more specific 
-than $\ell_1$ if there is a \textit{directed path} from $\ell_1$ to $\ell_2$.  
-If there is no directed path between $\ell_1$ and $\ell_2$, then they are 
-non-comparable.  As an example, \texttt{tomato} is more specific than 
-\texttt{food}, while \texttt{statue} and \texttt{food} are non-comparable.
+To this end, we constructed an ontology from the labels attributed to the 
+test images.  In the ontology, edges point from more general labels to more 
+specific ones.  For example, the ontology contains the path \texttt{food} 
+$\to$ \texttt{ingredients} $\to$ \texttt{vegetables} $\to$ \texttt{tomato}.
+We provide more detail about the construction of the ontology in the 
+\textbf{Materials and Methods} section.
 
-We can compare the degree of specificity of two workers by comparing the 
-labels each gives to some image in the final set.  Thus, we define the relative
-specificity of worker $u$ and $v$ for the $i$th image in the final set to be
-$s_i(u,v)$:
+Since food is a central feature 
+of culture, our ontology contains many labels that have both \texttt{food}
+and \texttt{culture} in their ancestry.  Nevertheless, there were many 
+food-oriented labels, such as \texttt{bread}, which lacked specific cultural 
+connections, as well as non-food, culture-oriented labels, such as 
+\texttt{russian dolls}.
 
-\begin{align}
-	s_i(u,v) = \sum_{\ell \in u(i) } \;
-	\sum_{m \in v(i)} 
-	\left(\mathbf{1}_{[\ell > m]} - \mathbf{1}_{[m>\ell]}\right),
-	\label{eq:worker-specificity}
-\end{align}
-
-where $u(i)$ denotes the set of labels attributed by worker $u$ to image $i$, 
-and $\mathbf{1}_{[\ell > m]}$ evaluates to 1 if $\ell$ is more specific than 
-$m$, and 0 otherwise.
-
-We can then define the relative specificity of treatments $\mathcal{U}$ and 
-$\mathcal{V}$, with regard to
-the $i$th image, $S_i(\mathcal{U},\mathcal{V})$, to be the mean
-relative specificity of two workers drawn uniformly from the treatments.  
-We obtain the estimator, $\hat{S}_i(\mathcal{U},\mathcal{V})$, by computing
-the sample average for our experimental data:
-
-\begin{align}
-	\hat{S}_i(\mathcal{U},\mathcal{V}) = 
-	\frac{1}{|\mathcal{U}| |\mathcal{V}|}
-	\sum_{u \in \mathcal{U}} \;
-	\sum_{v \in \mathcal{V}} \;
-		s_i(u,v).
-		\label{eq:specificity}
-\end{align}
-
-Further details for the estimation of relative specificity and the standard
-error of the estimation are given in \textbf{Methods}.
-
-We found that, with regard to labels attributed to the first image of the 
-final set, workers from \textsc{AMBG} were more specific than workers from
-either $\textsc{CULT}_{img}$ or $\textsc{INGR}_{img}$.  When we compare 
-$\textsc{CULT}_{img}$ to $\textsc{INGR}_{img}$, we found that workers from
-$\textsc{INGR}_{img}$ were more specific.  This shows that inter-task 
-effects substantially influence the specificity of labels that workers provide.
-
-\paragraph{Inter-task effects ``wash out'' quickly.}  
 \begin{figure}
+	\centering{
 	\includegraphics[scale=0.7]{figs/longitudinal_theta_excess-culture.pdf}
@@
 	}}
+}
 \end{figure}
-At this point we have 
-investigated the inter-task effects induced on only the first image of the 
-final image set.  This is because, as mentioned, the effects are strongest on 
-for first image.  We now examine how the inter-task effects vary as workers 
-proceed through the images in the final set.  Since the final images are the
-same for all treatments, it would stand to reason that the inter-task effects
-induced by the initial image sets would fade away, being washed out by the
-inter-task effects of the final set.
+When we tallied labels attributed to the first image of the final set, 
+we found that workers from $\textsc{CULT}_{img}$ produced significantly 
+more culture-oriented labels and less food-oriented ones than those from
+\textsc{AMBG}
+(see \textbf{Fig. 2A}).  The inter-task effect was so strong that the 
+proportion of food- and culture-oriented labels in $\textsc{CULT}_{img}$ was
+essentially the reverse of that in \textsc{AMBG}.  However, the 
+composition of labels attributed by $\textsc{INGR}_{img}$
+was not significantly different from those attributed by \textsc{AMBG}.  This 
+shows that inter-task effects \textit{can} profoundly alter workers' focus. 
+Again, we 
+will argue later that the ambiguous and ingredients image sets are, in fact, 
+quite similar.
+\paragraph{Earlier tasks influenced workers' level of specificity.} 
+Using the ontology described in the previous section, we can compare the 
+specificity of two labels $\ell_1$ and $\ell_2$. We say that $\ell_2$ is more 
+specific than $\ell_1$ if there is a \textit{directed path} from $\ell_1$ to 
+$\ell_2$.  If there is no directed path between labels, we say they are  
+\textit{non-comparable}.  For example, \texttt{tomato} was more specific than 
+\texttt{food}, while \texttt{statue} and \texttt{food} were non-comparable.
 
-Looking at the classifier performance, $\hat{\theta}_{NB}$, with respect to the
-treatments \textsc{AMBG} and $\textsc{CULT}_{img}$, we find that performance
-drops off dramatically after just the first image (see \textbf{Fig. 3A}).
-This suggests that inter-task effects mainly arise between consecutive tasks.
-However, a residual distinguishability between these two treatments does 
-persist until the final image (although for the fourth image we cannot assert
-this with 95\% confidence).
-
-We can similarly look at how the inter-task effects on label composition
-(i.e. fraction of culture- and food-oriented words) play out as workers 
-progress through the final image set.  To do this, we define the 
-\textit{excess cultural orientation} as the number of culture-oriented labels 
-minus the number of food oriented ones.  Tracking the excess cultural 
-orientation across the images is, however, not in itself meaningful,
-because some images will inherently carry more cultural content than others. 
-To account for this, we calculate the excess cultural content for both 
-\textsc{AMBG} and $\textsc{CULT}_{img}$, and subtract the former from the 
-latter, yielding the \textit{relative} excess cultural content, 
-$\Delta_{cult}$.  Formally,
+We can then define the relative specificity of two workers with respect to 
+test-image $i$ as $s_i(u,v)$:
 
 \begin{align}
-	\Delta_{cult}(i) = \frac{1}{N}\left[ \sum_{w\in\textsc{cult}_{img}} \left(N_{w,cult}^{(i)} - N_{w,food}^{(i)}\right)
-	- \sum_{w\in\textsc{ambg}} \left(N_{w,cult}^{(i)} - N_{w,food}^{(i)}\right)\right],
+	s_i(u,v) = \sum_{\ell \in u(i) } \;
+	\sum_{m \in v(i)} 
+	\left(\mathbf{1}_{[\ell > m]} - \mathbf{1}_{[m>\ell]}\right),
+	\label{eq:worker-specificity}
+\end{align}
+where $u(i)$ denotes the set of labels attributed by worker $u$ to image $i$, 
+and $\mathbf{1}_{[\ell > m]}$ evaluates to 1 if $\ell$ is more specific than 
+$m$, and 0 otherwise.
+We then define the relative specificity of two treatments, $\mathcal{U}$ and 
+$\mathcal{V}$, the $i$th image, denoted $S_i(\mathcal{U},\mathcal{V})$, to be 
+the mean relative specificity of two uniformly drawn workers:  
+\begin{align}
+	\hat{S}_i(\mathcal{U},\mathcal{V}) = 
+	\frac{1}{|\mathcal{U}| |\mathcal{V}|}
+	\sum_{u \in \mathcal{U}} \;
+	\sum_{v \in \mathcal{V}} \;
+		s_i(u,v).
+		\label{eq:specificity}
 \end{align}
 
+Looking at labels attributed to the first test image, we found that workers 
+from \textsc{AMBG} were more specific than workers from
+either $\textsc{CULT}_{img}$ or $\textsc{INGR}_{img}$.  When we compare 
+$\textsc{CULT}_{img}$ to $\textsc{INGR}_{img}$, we found that workers from
+$\textsc{INGR}_{img}$ were more specific.  This shows that inter-task 
+effects do substantially influence the specificity of labels that workers 
+provide.  When we discuss image simalarity, below, we will explore a possible
+mechanism for this effect.
+\paragraph{Inter-task effects ``wash out'' quickly.}  
+It would stand to reason that, as workers proceed through the test images, 
+priming from the initial images would be ``washed out'', diminishing the 
+observed inter-task effects.
+Looking at the classifier performance, $\hat{\theta}_\text{NB}$, with respect 
+to the treatments \textsc{AMBG} and $\textsc{CULT}_{img}$, we find that 
+performance does drop off dramatically after just the first image 
+(see \textbf{Fig. 3A}).
+This suggests that inter-task effects primarily arise between consecutive 
+tasks, but that a residual effect can persist for at least five tasks (we 
+note, however that although the classifier performance seemed better than 
+chance for the fourth test image, this cannot be asserted with 95\% 
+confidence).
+
+Next we observed how inter-task effects on label composition (i.e. food- vs 
+culture-orientel labels) evolve as workers proceed through test images.
+We define the \textit{excess cultural orientation} as the number of 
+culture-oriented labels minus the number of food oriented ones.  To 
+meaningfully compare the excess cultural orientation between test images, we 
+must, however, account for the fact that some images inherently carry more 
+cultural content than others. In keeping with our notion of priming 
+\textit{difference}, we calculate the excess cultural content for both 
+$\textsc{CULT}_{img}$ and \textsc{AMBG}, and take their difference to be
+the \textit{relative} excess cultural content, $\Delta_{cult}$.  Formally,
+\begin{align}
+	\begin{split}
+	\Delta_{cult}(i) = \frac{1}{N}\left[ \sum_{w\in\textsc{cult}_{img}} \left(N_{w,cult}^{(i)} - N_{w,food}^{(i)}\right)\right. \\
+\left.	- \sum_{w\in\textsc{ambg}} \left(N_{w,cult}^{(i)} - N_{w,food}^{(i)}\right)\right],
+	\end{split}
+\end{align}
 where $N_{w,cult}^{(i)}$ stands for the number of culture-oriented labels 
@@
 
-The relative excess cultural content varied as workers proceed through the
-final image set in much the same way that $\hat{\theta}_\text{NB}$ did: for the
-first test image, it is significantly greater than zero, but drops off rapidly
-thereafter.  Unlike $\hat{\theta}_\text{NB}$, $\Delta_{cult}$ ceases to
-be significantly greater than zero after the second test image, so it would 
-seem that $\hat{\theta}_\text{NB}$ is the more sensitive of the two in
-detecting inter-task effects.
+We found $\Delta_{cult}$ was largest for the first test image, but dropped off 
+rapidly, remaining positive but not to a statistically significant extent
+(see \textbf{Fig. 3B}).  
+This is similar to the behavior of $\hat{\theta}_\text{NB}$, however, because
+the statistical significance of $\Delta_{cult}$ dropped more quickly, 
+$\hat{\theta}_\text{NB}$ appears to be a more sensitive measure of inter-task 
+effects.
+\paragraph{Inter-task similarity encourages more specific labels.}
+To continue with the analysis, we seek a measure of image similarity.  The 
+characterization of image content is a deeply complex issue that has been 
+approached by many disciplines 
+\cite{panofsky1939studies,shatford1986analyzing,Tversky1977327,Jaimes20002}.
+\textit{Perceptual similarity} is a particularly recalcitrant concept[***].
 
-\paragraph{Inter-task similarity encourages more specific labels.}
-For the next part of the analysis, it will be useful to speak of the
-``similarity'' between two image sets. In general, the characterization of 
-image content 
-is deeply complex and has been approached from the perspectives of 
-art\cite{panofsky1939studies,shatford1986analyzing},
-psychology\cite{Tversky1977327}, and information retrieval\cite{Jaimes20002}.
-Furthermore, the perception of \textit{similarity} is a particularly subtle 
-psychological phenomenon.  For example, a figure $A$ can appear simultaneously
-both \textit{more} and \textit{less} similar to an object $C$ than some other 
-object $B$[***].
-
-In the present study, we are more interested in the ultimate outputs of 
-workers' rather than the psychological details which lead to them (though 
-these are interesting in their own right).  This allows us to sidestep the 
-complication in attributing similarity: we asses how similar two sets of 
-images are, 
-\textit{with respect to the labeling task}, by looking at the fraction of 
-labels that they share.  Formally, we compute the similarity of two images
-sets $X$ and $Y$ by computing the Jacquard index between the sets of labels 
-attributed to them:
-
+However, in the present study, we are more interested how similar two 
+sets of images are, \textit{with respect to the labeling task}, which is much
+simpler to operationalize than general perceptual similarity.  Here, we 
+measure image similarity by looking at the fraction of labels that they share. 
+Formally, to measure the similarity between two \textit{sets of images}, $X$ 
+and $Y$, we compute the Jacquard index between the sets of labels attributed 
+to them:
 \begin{align}
@@
 \end{align}
-
 \begin{table}
 \centering
-\begin{tabular}{ l  d  s s s s}
+\begin{tabular}{ l  s s s s}
 
 \toprule    
-\multirow{2}{*}{Image set} & \multicolumn{1}{c}{\# of unique} & 
-\multicolumn{4}{c}{Similarity}  \\
-\cline{3-6}
-
-&  \multicolumn{1}{c}{labels} 
-& \multicolumn{1}{c}{Ambiguous} 
+Image set   
+& \multicolumn{1}{c}{Ambig.} 
 & \multicolumn{1}{c}{Cultural} 
-& \multicolumn{1}{c}{Ingredients}
+& \multicolumn{1}{c}{Ingr.}
 & \multicolumn{1}{c}{Test} \\
@@
 
-Ambiguous & 763 & 1 & 0.0418 & 0.142 & 0.167 \\
+Ambiguous  & 1 & 0.0418 & 0.142 & 0.167 \\
 
-Cultural & 659 & 0.0418  & 1 & 0.0347 & 0.0561 \\
+Cultural  & 0.0418  & 1 & 0.0347 & 0.0561 \\
 
-Ingredients & 681 & 0.142  & 0.0347 & 1 & 0.110 \\
+Ingredients  & 0.142  & 0.0347 & 1 & 0.110 \\
 
-Test & 1695 & 0.167  & 0.0561 & 0.110 & 1
+Test & 0.167  & 0.0561 & 0.110 & 1
 \\
@@
 \end{table}
+where $L(X)$ denotes the set of labels attributed to $X$.
 
-where $L(X)$ denotes the set of labels attributed to $X$.  See \textbf{Methods}
-for additional details regarding the calculation of similarity.
-
-The similarities of the various image sets are presented in \textbf{Table 2}. 
+The pairwise similarities of the image sets are presented in \textbf{Table 2}. 
 First, observe that the ambiguous and ingredients sets are much more similar 
-to each other than either is to the culture set.  This is consistent with our
-finding that $\hat{\theta}_\text{NB}$ between \textsc{AMBG} and 
-$\textsc{INGR}_{img}$ was not significant (see \textbf{Fig 1}).
+to each other than either is to the culture set.  Recalling the data presented
+in \textbf{Fig. 1}, this helps explain why two treatments could not be 
+distinguished on the basis of having differing initial sets corresponding to
+ambiguous and cultural.  This also explains why \textsc{ambg} and 
+$\textsc{cult}_{img}$ had similar label compositions in \textbf{Fig. 2A}.
 
@@
 set.  The ambiguous set is the most similar to the test set, followed by the
-ingredients set, and the cultural set was most different from the test set.
+ingredients set, with the cultural set being most different.
 Observe that these levels of similarity mirror the label specificity for the 
@@
 desensitized to non-salient stimuli to which she is repeatedly 
-exposed [***].  Consider that workers who initially 
+exposed.  Consider that workers who initially 
 labeled the ambiguous image set had already seen five images showing 
 prepared meals once they labeled the first test image.  At that point,
-a worker might not regard the labels \texttt{food} or \texttt{meal} to be 
-salient, since they do not distinguish the image from those she had seen 
-already.
+a worker might not regard the generic labels \texttt{food} or \texttt{meal} 
+to be salient, and opt instead for \texttt{bread}, or \texttt{pasta}.
 
@@
 influences the perception of salience. Thus, in a series of subjective 
-characterization tasks that have very similar content, the worker's focus 
+characterization tasks that have very similar content, workers' focus 
 will tend to be directed away from generic, shared attributes, towards those 
 attributes that are specific and distinguishing.
-
 \subsection*{Discussion}
-
 \paragraph{Inter-task effects should be considered during task design.}  
@@
 between consecutive tasks.
-
 \paragraph{$\theta$ provides a general purpose measure of priming effects.}
@@
 effects.
-
 \paragraph{Batching tasks for better HPU performance.}
@@
 one might sacrifice accuracy through parallelization.
-
 \subsection*{Conclusion}
-
 Inter-task priming can have a strong effect.  
@@
 effects are not understood. 
-
 \subsection*{Materials and Methods}
-
-\textbf{AMT Tasks.} The task described in \textbf{Experimental Setup}
-was served to 900 workers, who were uniformly randomly assigned to
-treatments.  Each treatment had at least 126 task completions.  To obtain 
-uniformly sized treatments, we randomly selected 126 samples from each 
-treatment. Workers were
-only allowed to participate once and could not see the initial or final 
-images, nor the funder names when previewing the task.
-
-\textbf{Naive Bayes Classifier.}
-The features provided to the Naive Bayes classifier consisted of the labels
-that the worker provided along with the image and specific location in which 
-the label was entered
-(each image had five distinct label inputs).  Thus, \texttt{wine} occurring in 
-position 1 of image 2 would be considered as a distinct feature from 
-\texttt{wine} occurring in position 2 of image 2. The classifier 
-had better performance when this distinction was made.
-
-\textbf{Building the ontology of terms.}  The ontology was built manually
-by the experimenters, starting from the corpus of labels. Labels occurring only 
-once were discarded.  We created the root classes \texttt{activity}, 
-\texttt{adjective}, \texttt{culture}, 
-\texttt{food}, and \texttt{thing}. \texttt{culture} and \texttt{food} were 
-given top-level status because they were prominently represented in the corpus.
-Whenever one label was judged to be a more specific case of another, a
-directed edge was drawn from the more general to the more specific. This
-judgment call was made by the experimenters.  However, the labels from all 
-treatments were aggregated before assembling the ontology,  to 
-ensure that the ontology construction would not be affected by 
-knowledge of the treatments from which labels originated. 
-Labels which were judged to be roughly synonymous were treated as identical,
-and labels judged to be misspellings were corrected.
-
-\textbf{Statistical significance of $\theta_\text{NB}$.}
-We test the significance two population's measured $\theta_\text{NB}$ against 
-the null hypothesis that that the two populations are in fact identical:
-\begin{align}
-	\mathbf{H_0}: \theta_\text{NB} = 0 \\
-	\mathbf{H_1}: \theta_\text{NB} > 0
-\end{align}
-If the populations are in fact identical, then the probability that the 
-classifier correctly classifies a worker is $\frac{1}{2}$. Let $K$ be a random
-variable which denotes the number of correct classifications when the 
-classifier is challenged to classify a total of $n$ workers during 
-cross-validation.  Under $\mathbf{H_0}$, the probability distribution of $K$ 
-is:
-\begin{align}
-	\text{Pr}\{K = k | n \} = { n \choose k } \left(\frac{1}{2}\right)^n.
-\end{align}
-We can reject $\mathbf{H_0}$ at significance $\alpha$ if $\theta_\text{NB}$ 
-is greater than or equal to a critical value, $\theta_\text{NB}^*$:
-\begin{align}
-	\theta^*_\text{NB} = \frac{2k^*}{n} - 1
-\end{align}
-where $k^*$ is the smallest integer in $\{0,\dots,n\}$ that satisfies 
-\begin{align}
-	\sum_{k \in \{k^*, \dots, n\}} \text{Pr}\{K = k | n \} < \alpha.
-\end{align}
-For a 5-fold cross-validation with non-overlapping test sets containing 25 
-workers ($n = 125$), and a significance of $\alpha = 0.05$, we
-have $k^*=73 \implies \theta_\text{NB}^* = 0.168$.
-
-\textbf{Statistical significance of relative specificity.}
-We used \textbf{Eq.~\ref{eq:specificity}} to compute the relative specificity
-of two treatments.  To analyze relative specificity statistically,
-we first develop \textbf{Eq.~\ref{eq:specificity}} from an intermediate 
-definition.  Let the specificity of a worker $u$ relative to a 
-\textit{basis treatment} $\mathcal{V}$, denoted $S_V(u)$, be the expected 
-relative specificity between $u$ and a worker uniformly sampled from 
-$\mathcal{V}$:
-
-\begin{align}
-	S_V(u) =  \text{E}_V\{s(u,V)\}, \quad V \in_R \mathcal{V},
-		\label{eq:basis-specificity}
-\end{align}
-where $V$ is a random, uniformly sampled worker from $\mathcal{V}$.  We 
-subscript the expectation operator with $V$ to indicate 
-that the expectation is taken over the distribution of $V$.  Then, the 
-relative specificity of two treatments, $S(\mathcal{U},{V})$, can be 
-written as:
-\begin{align}
-	S(\mathcal{U},\mathcal{V}) = 
-		\text{E}_U\{S_V(U)\}, \quad U \in_R \mathcal{U},
-		\label{eq:treatment-specificity}
-\end{align}
-where $U$ is a random, uniformly sampled worker from $\mathcal{U}$.  This 
-yields 
-estimators for $S_V(u)$ and $S(\mathcal{U}, \mathcal{V})$, and their variances
-as shown below (note that 
-\textbf{Eq.~\ref{eq:treatment-specificity-estimator}} is
-equivalent to \textbf{Eq.~\ref{eq:specificity}}):
-
-\begin{align}
-	\hat{S}_V(u) &= \frac{1}{|\mathcal{V}|} \sum_{v \in \mathcal{V}} s(u,v), 
-		\label{eq:basis-specificity-estimator} \\
-		\hat{S}(\mathcal{U},\mathcal{V}) 
-		&= \frac{1}{|\mathcal{U}|} \sum_{u \in \mathcal{V}} \hat{S}_V(u),
-		\label{eq:treatment-specificity-estimator} \\
-		\text{Var}_V\{\hat{S}_V(u)\} 
-			&= \frac{1}{|\mathcal{V}|}\text{Var}_V\{s(u,V)\},
-		\label{eq:basis-specificity-variance} \\
-		\text{Var}_{U,V}\{\hat{S}(\mathcal{U},\mathcal{V})\} 
-			&= \frac{1}{|\mathcal{V}|\cdot|\mathcal{U}|^2} 
-			\sum_{u\in U}\text{Var}_V\{{s}(u,V)\}.
-		\label{eq:treatment-specificity-variance}
-\end{align}
-\td{There are problems with this.  I'm still trying to figure out how to
-	calculate the variance properly.}
-$\text{Var}_V\{s(u,V)\}$ can be directly calculated as a sample variance.
-\textbf{Equations \ref{eq:basis-specificity-estimator}} through 
-\textbf{\ref{eq:treatment-specificity-variance}} provide enough information to test the hypotheses:
-\begin{align}
-	\begin{matrix}
-		\mathbf{H_0}: S(\mathcal{U}, \mathcal{V}) = 0 \\[0.5em]
-		\mathbf{H_1}: S(\mathcal{U}, \mathcal{V}) \neq 0
-	\end{matrix}
-\end{align}
-
-\begin{figure}
-	\includegraphics[scale=1.00]{figs/taskImages/testImages.jpg}
-	\caption{Testing image set. These images were presented to all workers in 
-		the order shown after the priming set of images.}
-\end{figure}
-
-\begin{figure}
-	\includegraphics[scale=1.00]{figs/taskImages/ambiguous.jpg}
-	\caption{ Ambiguous image set. These images were presented to workers from 
-		certain treatments (see \textbf{Table 1}) in the order shown.}
-\end{figure}
-
-\begin{figure}
-	\includegraphics[scale=1.00]{figs/taskImages/cultural.jpg}
-	\caption{Cultural image set. These images were presented to workers from 
-		certain treatments (see \textbf{Table 1}) in the order shown.}
-\end{figure}
-
-\begin{figure}
-	\includegraphics[scale=1.00]{figs/taskImages/ingredients.jpg}
-	\caption{ Ingredients image set. These images were presented to workers 
-		from certain treatments (see \textbf{Table 1}) in the order shown.}
-\end{figure}
-\section*{Acknowledgments}
-\section*{References}
-\begingroup
-\renewcommand{\chapter}[2]{}
+Omitted due to length.  This will be added to supplementary material.
 \bibliography{newbib.bib} 
-\endgroup
-\bibliographystyle{plain}
-
+\bibliographystyle{aaai}
 \end{document}
+\subsection*{Motivation}
+I am near the beginning of my PhD studies, and have joined Derek Ruths' lab 
+with the expressed purpose of performing human computation research.
+My interests lay at the intersection of game theory, psychology, and 
+computation.  The overarching goal for my research relates to group 
+decisionmaking, and can be phrased in the following way: ``what are the factors
+that influence the social efficiency of collective decisionmaking?'' I
+view decisionmaking as the central activity of all social organizations, and 
+I view this as a computational process.  My reason for 
+wanting to attend the PhD Consortium at HCOMP is threefold.  First, I wish to
+discuss my ideas with others, get feedback, and learn more about how the 
+community frames such questions, to help me as I finalize my PhD proposal 
+into concrete research aims.  Second, I hope to make connections to other 
+researchers who are interested in similar research questions.  Finally, I wish
+to obtain feedback on a crowdsourcing platform that I have implemented (and
+hopefully pique other researcher's interest), which I intend to use in my
+research.
+\end{document}

### 2014-08-04 docs/publications/2014.05_PNAS/supplementary_figs.tex
make version for hcomp PhD consortium submission

--- 2014-08-03 docs/publications/2014.05_PNAS/manuscript.tex
@@
 %
-\documentclass[a4paper]{report}
-\usepackage[hmargin=2cm,vmargin=2cm]{geometry}
+\documentclass[letterpaper]{article}
+\usepackage[hmargin=0.75cm,vmargin=0.75cm]{geometry}
 \usepackage{scrextend}
@@
 
-\title{Inter-task effects introduce bias in crowdsourcing}
-\author{Edward Newell, Derek Ruths}
-
 \parindent0pt \parskip8pt
@@
 \begin{document}
-\maketitle
-\section*{Abstract}
-\section*{Significance Statement}
-\section*{Introduction}
-
-Microtask crowdsourcing platforms like Amazon Mechanical Turk (AMT) make it 
-possible to submit batches of small tasks to a large pool of human workers, 
-who do the tasks for fun, a sense of purpose, and remuneration 
-\cite{kazai2013analysis, Antin20122925}.  
-Originally used to distribute clerical work, these platforms 
-increasingly serve as a fast and cheap means to engage experimental 
-participants and manually annotate datasets in a research 
-setting \cite{snow2008cheap}.  
-Tasks involving qualitative
-judgment (e.g. flagging inappropriate images), natural language annotation,
-and object recognition are commonplace, since it is difficult to achieve 
-comparable performance using only computers \cite{yuen2011survey}.
-%Generally the worker is first given some orientation to the task, and then 
-%performs the task repeatedly (e.g. label several images, one after 
-%the other).
-
-Such platforms make human cognition a fluid resource: it is available 
-on demand in small units, with low transaction 
-cost, from anywhere via the 
-Internet\footnote{\href{http://mturk.com}{http://mturk.com}}.
-The task requester can 
-interact with the platform like a compute server, seamlessly 
-integrating human and machine computation.  Researchers have put forward the 
-term HPU (Human co-Processing Unit)\footnote{We acknowledge the irony of this 
-term: the original meaning of `computer' was a person who performs 
-computations, its reference to machines being a personification brought into 
-usage in the late 1800s\cite{Dictionary:hl}.}, viewing the introduction of 
-microtask platforms as a new computing architecture
-\cite{5543192}.
-
-Here, we highlight an important way in which HPUs differ from CPUs, with 
-serious implications for the design of tasks.  It is well known that people 
-are subject to priming effects 
-\cite{BJOP:BJOP1796, No2007, beller1971priming} and, in particular, task-repetition effects
-\cite{Gass1999549, sohn2001task}.  
-We investigate the effect that previously completed tasks have on workers'
-responses during subsequent ones. We call such effects 
-\textit{inter-task priming}.  Inter-task priming would amount to a kind of
-\textit{hysteresis}, meaning that HPU output is not only a function of the 
-current input, but also of the history of inputs.
-
-There has been considerable investigation into the factors that affect HPU 
-output on crowdsourced microtask platforms.  Studies have shown that 
-there is a great deal of variance in worker attention and 
-accuracy \cite{kazai2013analysis}.  Factors that affect the quality of HPU 
-output include level of pay\cite{kazai2013analysis}, 
-training\cite{le2010ensuring}, screening workers\cite{paolacci2010running}, 
-and user-interface design
-\cite{Finnerty2013}.  Research has also investigated \textit{framing}, 
-by testing the effects of disclosing the role of a task within the 
-context of a study \cite{Kinnaird2012281}, and disclosing the ultimate 
-purpose of that study \cite{chandler2013breaking}.  However, to our knowledge, 
-no study has investigated the effects of inter-task priming.
-
-To characterize the effects of inter-task priming, we present a novel  
-\textit{algorithmic definition of priming}, along with a general method 
-for measuring priming effects using machine learning algorithms.  
-Existing work on priming effects focuses on the internal psychological 
-mechanisms of priming[***], but here we are interested in how the treatment of 
-workers can impact an application of human computation. This leads us to 
-quantify priming in terms of the algorithmic distinguishability of priming
-treatments.
-
-In the present work, we investigate inter-task priming using image-labeling 
-tasks on the AMT platform.  
-(***why we are using image labeling as prototypical task***) 
-Each worker is required to label ten images 
-featuring 
-food and culture.  We regard these images as being made up of an 
-\textit{initial} and \textit{final set}, but, crucially, there is no
-distinction made between these sets, nor any interruption in the flow of tasks 
-from the view of the worker.
-Each worker is randomly assigned one of three initial sets, but the final set
-of images is always the same.  We analyze the effect that the assignment of 
-initial set has on workers' attribution of labels to the final set.  We 
-measure effects using our novel approach, as well as looking for changes in 
-the content of labels and label specificity based on an ontology we 
-developed for that purpose.
-
-As a point of comparison, we subject some groups of workers to a kind of
-\textit{framing}: we disclose a fictitious, semantically-loaded name for 
-requester funding the tasks.
-The names were chosen to suggest the requester's interest in 
-a specific aspect of the image content.  One might reasonably expect that this 
-would orient workers to provide a greater quantity and specificity of labels 
-which relate to this ``preferred'' content[***].
-
-Surprisingly, we find that inter-task effects on label orientation and 
-specificity are much stronger than those brought about by framing tasks with a 
-funder name.  Our results show that initial tasks can introduce significant 
-bias in subsequent worker labeling.  Interestingly, we find that inter-task
-effects can be used to induce greater specificity.  Our results suggest that
-workers attribute more specific labels when labeling a series of images that
-that are more similar to one another.  This suggests that careful 
-consideration should be given to the bundling of tasks when designing a study 
-using a microtask platform.
-
-Our analysis also highlights important advantages of our novel definition of 
-priming.  Our approach relies on no prior knowledge about the nature
-of the task task whatsoever.  In contrast, we also sought to detect priming
-based on its direct effects on label content and specificity, implicitly
-drawing on prior knowledge about the images and label semantics.
-Remarkably, while being more general, our novel approach was also more 
-sensitive.  This suggests that our measurement approach could be applied in 
-cases where one does not \emph{a priori} know whether any priming has occurred, 
-nor what the effects might be.
-
-\subsection*{An algorithmic definition of priming}
-
-In psychology, the effects of priming are usually measured in terms of a 
-change in the  
-speed or accuracy of responses in a task, or in the ability to recognize a 
-stimulus object (e.g. a spoken word or an image) when the object is noisier, 
-fainter, or briefer [***].  Methods are also employed to measure processes
-in the brain of the participant, such as by fMRI[***].  These approaches are 
-well-suited to studying the underlying psychological mechanisms at work.
-
-Our purpose is different: we are interested in assessing the ramifications
-that priming of HPUs could have on the applications to which they are employed.
-This influences the approach we take to measurement in two ways.  First, we 
-switch from focusing on the internal mechanisms of HPUs to focusing strictly 
-on the HPU outputs.  Second, we cannot \textit{a priori} know the 
-application for which HPUs are being employed, but we would like to measure 
-any effects that could in principle impact the application.  These 
-considerations motivate us to define priming effects in terms of the 
-algorithmic distinguishability of primed output.
-
-One difficulty in constructing a definition of priming is that there would 
-appear to be no defensible notion of a ``neutral'' or ``unprimed state''.  A 
-participant 
-always approaches a task in \textit{some} state of mind.  If no priming 
-condition is applied, then the participant is simply primed by her
-exposures prior to the experiment, which cannot be known by the experimenter.  
-While arguments can surely be made that one treatment or another is 
-\textit{more} 
-``neutral'', we refrain from proposing a canonical ``null priming treatment''. 
-Instead, we define priming relatively, and speak of one treatment being 
-\textit{differently primed} from another.
-
-A definition of priming must also consider that the effects of priming will
-manifest differently depending on the task that participants perform 
-subsequent to priming:  two priming treatments that
-produce markedly different output for one task might be 
-indistinguishable under another task.  Thus, we define priming
-with respect to a task.
-
-A final factor to consider is that people will always differ in their initial
-knowledge, specific aptitudes, and in many other intrinsic aspects.  Moreover,
-priming may not be ``complete'', in the sense that people's experiences before
-priming may continue to have residual effects.  Therefore, we define priming 
-in relation to populations, which we regard as having stable distributions of
-such latent attributes.
-
-To set up the definition, when a population of people $\mathcal{J}$ performs
-a task $\mathcal{T}$ thus producing a population of task-outputs $\mathcal{L}$,
-we will write $\mathcal{T}(\mathcal{J}) = \mathcal{L}$.
-
-\vspace{2mm}
-\begin{mydef}
-	\upshape
-	Two mutually exclusive populations of people, $\mathcal{P}_0$ and 
-	$\mathcal{P}_1$, are uniformly and randomly subsampled from an initial 
-	population $\mathcal{P}$, are exposed to (possibly) different priming 
-	treatments, and then perform a task $\mathcal{T}$, 
-	producing task-outputs $\mathcal{T}(\mathcal{P}_0)$ and 
-	$\mathcal{T}(\mathcal{P}_1)$.
-	These populations are subsampled, producing 
-	$P_0 \subset \mathcal{P}_0$ and
-	$P_1 \subset \mathcal{P}_1$. A uniform, random bit is chosen, 
-	$b\in _R \{0,1\}$, and a single worker $p$ is uniformly and randomly 
-	sampled from 
-	$\mathcal{P}_b \setminus P_b$.
-	We say that $\mathcal{P}_0$ and $\mathcal{P}_1$ 
-	\emph{differ in priming by a degree at least $\theta$},
-	if there exists a \emph{distinguisher algorithm} $\mathcal{A}$ that takes as input 
-	$\langle\mathcal{T}(J)$, $\mathcal{T}(K)$, $\mathcal{T}(\{p\})\rangle$
-	and outputs a guess for $b$ with accuracy $\frac{1+\theta}{2}$.  
-\end{mydef}
-
-In the language of computer science, $\mathcal{A}$ is a classifier performing
-a binary classification.  The measure $\theta$ can range between 0 and 1, and 
-indicates how much better the performance of the best possible classifier is 
-compared to a random guess. We intentionally leave the details of 
-$\mathcal{A}$ unrestricted because $\theta$ should depend on the potential 
-for two populations to be distinguished, based on their inherent differences, 
-rather than on the performance of a particular classifier.
-
-In practice, some particular classifier $\mathcal{C}$ must be used and a 
-statistical estimate of its performance $\hat{\theta}_\mathcal{C}$ obtained. 
-$\hat{\theta}_\mathcal{C}$ acts as a lower bound for the 
-theoretical value $\theta$ from the definition, because there might 
-exist some other classifier $\mathcal{C}'$ with 
-$\hat{\theta}_\mathcal{C'}>\hat{\theta}_\mathcal{C}$.
-Here, we use a Naive Bayes classifier because it simple and performs well 
-across a broad range of classification tasks[***].
-
-To interpret $\hat{\theta}_\mathcal{C}$, imagine that some choice is to be
-made between two options on the basis of worker outputs (e.g. whether or not 
-to flag an image as inappropriate). Any such binary choice has a formal 
-structure of a trained classifier (i.e. a distinguisher which discards the 
-first two inputs). This means that $\hat{\theta}_\mathcal{C}$ estimates a 
-lower bound for the worst-case bias introduced in such a binary decision when 
-one failed to control for priming effects.
-
-\subsection*{Experimental Setup}
-\begin{table}[t]
-\centering
-	\begin{tabular}{ l  l  l }
-		\hline                       
-		Treatment & Funder & Priming Image Set	\\ 
-		\hline                       
-		$\textsc{ambg}$ & None & Ambiguous\\
-		$\textsc{cult}_{img}$ & None & Cultural\\
-		$\textsc{cult}_{fund}$ & Cultural & Cultural\\
-		$\textsc{cult}_{fund,img}$ & Cultural & Cultural\\
-		$\textsc{ingr}_{img}$ & None & Ingredients\\
-		$\textsc{ingr}_{fund}$ & Nutritional & Ingredients\\
-		$\textsc{ingr}_{fund, img}$ & Nutritional & Ingredients\\
-		\hline  
-	\end{tabular}
-
-	\begin{addmargin}[4em]{4em}
-	\caption{ \footnotesize{ 
-		Workers were uniformly randomly assigned to one of the 
-		treatments listed above. 
-		The full funder names used were 
-		``The Global Foundation for Cultural Recognition'' and 
-		``The National Foundation for Nutritional Awareness''.  
-		The ambiguous, cultural, and ingredients initial image sets are shown 
-		in \textbf{Figs. 2}, \textbf{3}, and \textbf{4}.
-	}}
-	\end{addmargin}
-	\label{table:1}
-\end{table}
-
-We solicited 900 AMT workers to perform an image-labeling task relating to
-food and culture.  The workers were randomly assigned to one of seven 
-treatments shown in \textbf{Table 1}.  Workers were first shown brief 
-instructions.  Depending on their treatment, workers were then shown the 
-name of a research funder, or this step was skipped.  When shown, 
-the funder name was either
-``The Global Foundation for Cultural Recognition'', or 
-``The National Foundation for Nutritional Awareness''.
-
-Next, workers were
-shown ten images, one at a time. Workers were required to label each image 
-with five descriptive labels before moving on to the next.  For the purpose 
-of analysis, we divide the images
-into \textit{initial} and \textit{final} sets, comprising respectively the 
-first five and last five images shown.  As mentioned, from the perspective of 
-the worker, there was no 
-distinction or interruption between the initial and final sets. 
-Depending on the treatment to which the worker was assigned, one of three 
-initial image sets was chosen. The final image set was the same for all 
-treatments.
-
-For the final image set, we chose 
-images that contained prepared meals and featured a prominent, identifiable 
-culture (see \textbf{Fig. 4}).  We intended that the content of these images 
-would elicit labels focusing on food or culture (or both).
-We refer to the three initial image sets as the ``ambiguous'', ``cultural'', 
-and ``ingredients'' sets.  The ambiguous set was chosen to
-be very similar to the final image set, in the sense that it consisted of
-images of prepared meals (see \textbf{Fig. 5}).  However, its cultural 
-features were intended to be less prominent.  The cultural set featured 
-iconic cultural scenes, but no food at all (see \textbf{Fig. 6}).  Finally, 
-images from the 
-ingredients set depicted separated ingredients, but, 
-like the ambiguous set, were chosen to avoid prominent cultural features (see 
-\textbf{Fig. 7}).  See the \textbf{Materials and Methods} section for further 
-details.
-
-\subsection*{Results}
-\paragraph{Inter-task priming was strong, while framing was weak.}
-We tested for priming effects using our algorithmic definition, implemented 
-with a Naive Bayes classifier.  This involved measuring the classifier's 
-accuracy in classifying workers chosen from a pair of treatments during 
-cross-validation (see \textbf{Methods} for details).  The classifier's accuracy
-for cross-validations involving each pair of treatments is shown in 
-\textbf{Fig.1}.
-
-With some exceptions, the classifier performed significantly better 
-than chance when distinguishing treatments that had different initial image 
-sets.  This demonstrates that inter-task effects were strong for the labeling 
-tasks.  Of the sixteen treatment pairs having different initial images, there 
-were three cases where the classifier performance was on par with chance. 
-Each of these cases involved distinguishing workers shown the ambiguous set 
-from ones shown the ingredients set.  The reason for the low 
-distinguishability of workers from these treatments might be because
-the ambiguous and ingredients sets are somewhat similar to one another.
-We will come back to this point later when we discuss the degree of similarity 
-between image sets.
-
-In contrast, the classifier never performed significantly better than chance
-when distinguishing treatments that differed only in the funder name shown. 
-Thus, framing effects were rather weak.
-
-\begin{figure}
-	\includegraphics[scale=0.94]{figs/f1-thetas_full_pairwise25_img1.pdf}
-	\caption{ \footnotesize{
-		Empirical difference in priming, $\hat{\theta}_\text{NB}$, between 
-		various treatments.  The difference in priming between each pair of 
-		treatments 
-		was determined by cross-validation of a Naive Bayes classifier trained
-		to classify workers based on the labels they attributed to the first
-		image of the final image set. Each panel compares a basis treatment,
-		indicated above the panel, to various treatments indicated on the
-		abscissa.  We can conclude, with 95\% confidence, that the classifier
-		is performing better than chance when $\hat{\theta}_\text{NB}$ 
-		exceeds 0.168, indicated by the dotted line.  See \textbf{Methods} for
-		the calculation of this confidence threshold.
-	}}
-\end{figure}
-
-\paragraph{Earlier tasks orient workers' focus during later tasks.} 
-We next investigated the \textit{nature} of the inter-task effects.  Since the
-initial images were chosen to emphasize either food (ingredients set) or 
-culture (cultural set), we looked for effects in the number of culture- and 
-food-oriented labels that workers attributed to the final image set.
-
-To this end, we constructed an ontology of labels attributed to the final 
-images.  The ontology was constructed as a directed acyclic graph, with edges 
-pointing from more general labels to more specific ones.
-For example, our ontology contains the path \texttt{food} $\to$ 
-\texttt{ingredients} $\to$ \texttt{vegetables} $\to$ \texttt{tomato}. We 
-provide more detail about the construction of the ontology in the 
-\textbf{Materials and Methods} section.
-
-We counted labels as being culture- and/or food-oriented based on 
-whether the label had inbound paths from the abstract labels \texttt{culture} 
-or \texttt{food} in the ontology. Since food is a central feature 
-of culture, there were many labels that were both culture- and food-oriented 
-in this sense.  Nevertheless, there were many food-oriented labels, such as 
-\texttt{bread}, which lacked specific cultural connections.  Meanwhile, there 
-were many non-food, culture-oriented labels, such as \texttt{russian dolls}.
-
-When we tallied labels attributed to the first image of the final set, 
-we found that workers shown the cultural initial set produced significantly 
-more culture-oriented labels and less food-oriented ones 
-(see \textbf{Fig. 2A}).  In fact, the inter-task
-effect was so strong that it essentially reversed the proportion of culture- 
-and food-oriented labels seen for the ambiguous set.  On the other hand, the 
-composition of labels attributed by 
-workers shown the ingredients image set was not significantly different from 
-that attributed by workers shown the ambiguous set.  This shows that inter-task
-effects can profoundly alter workers' focus, but the effects brought 
-about by showing workers the ambiguous and ingredients sets were not 
-significantly different.
-
-\paragraph{Earlier tasks influenced workers' level of specificity.} 
-\begin{figure}
-	\begin{center}
-		\includegraphics[scale=0.70]{figs/orientation_specificity.pdf}
-	\caption{\footnotesize{
-		\textbf{A}) Percent label composition (culture- vs food-oriented 
-		labels) for 
-		various images and treatments.  
-		\textbf{B}) Relative specificities of treatments
-		indicated along the abscissa compared to those indicated above the 
-		plot.  The size of the bar indicates how much more specific
-		the labels from one treatment are compared to the other, and points 
-		toward in the direction of the more specific treatment.
-	}}
-	\end{center}
-\end{figure}
-
-Using the ontology described in the previous section, we compared treatments 
-in their degree of specificity.  When comparing two labels $\ell_1$ and 
-$\ell_2$ produced by different workers, we say that $\ell_2$ is more specific 
-than $\ell_1$ if there is a \textit{directed path} from $\ell_1$ to $\ell_2$.  
-If there is no directed path between $\ell_1$ and $\ell_2$, then they are 
-non-comparable.  As an example, \texttt{tomato} is more specific than 
-\texttt{food}, while \texttt{statue} and \texttt{food} are non-comparable.
-
-We can compare the degree of specificity of two workers by comparing the 
-labels each gives to some image in the final set.  Thus, we define the relative
-specificity of worker $u$ and $v$ for the $i$th image in the final set to be
-$s_i(u,v)$:
-
-\begin{align}
-	s_i(u,v) = \sum_{\ell \in u(i) } \;
-	\sum_{m \in v(i)} 
-	\left(\mathbf{1}_{[\ell > m]} - \mathbf{1}_{[m>\ell]}\right),
-	\label{eq:worker-specificity}
-\end{align}
-
-where $u(i)$ denotes the set of labels attributed by worker $u$ to image $i$, 
-and $\mathbf{1}_{[\ell > m]}$ evaluates to 1 if $\ell$ is more specific than 
-$m$, and 0 otherwise.
-
-We can then define the relative specificity of treatments $\mathcal{U}$ and 
-$\mathcal{V}$, with regard to
-the $i$th image, $S_i(\mathcal{U},\mathcal{V})$, to be the mean
-relative specificity of two workers drawn uniformly from the treatments.  
-We obtain the estimator, $\hat{S}_i(\mathcal{U},\mathcal{V})$, by computing
-the sample average for our experimental data:
-
-\begin{align}
-	\hat{S}_i(\mathcal{U},\mathcal{V}) = 
-	\frac{1}{|\mathcal{U}| |\mathcal{V}|}
-	\sum_{u \in \mathcal{U}} \;
-	\sum_{v \in \mathcal{V}} \;
-		s_i(u,v).
-		\label{eq:specificity}
-\end{align}
-
-Further details for the estimation of relative specificity and the standard
-error of the estimation are given in \textbf{Methods}.
-
-We found that, with regard to labels attributed to the first image of the 
-final set, workers from \textsc{AMBG} were more specific than workers from
-either $\textsc{CULT}_{img}$ or $\textsc{INGR}_{img}$.  When we compare 
-$\textsc{CULT}_{img}$ to $\textsc{INGR}_{img}$, we found that workers from
-$\textsc{INGR}_{img}$ were more specific.  This shows that inter-task 
-effects substantially influence the specificity of labels that workers provide.
-
-\paragraph{Inter-task effects ``wash out'' quickly.}  
-\begin{figure}
-	\includegraphics[scale=0.7]{figs/longitudinal_theta_excess-culture.pdf}
-	\caption{\footnotesize{
-		\textbf{A}) Difference in priming between \textsc{AMBG} and 
-		$\textsc{CULT}_{img}$ measured based on the accuracy of a Naive Bayes 
-		classifier during cross-validation, when trained on labels from the
-		test images indicated along the abscissa.
-		\textbf{B}) Excess cultural orientation of labels attributed to
-		the test images indicated on the abscissa, by workers from
-		$\textsc{CULT}_{img}$ relative to those attributed by workers from
-		\textsc{AMBG}, calculated using \textbf{Eq. 3}.
-	}}
-\end{figure}
-At this point we have 
-investigated the inter-task effects induced on only the first image of the 
-final image set.  This is because, as mentioned, the effects are strongest on 
-for first image.  We now examine how the inter-task effects vary as workers 
-proceed through the images in the final set.  Since the final images are the
-same for all treatments, it would stand to reason that the inter-task effects
-induced by the initial image sets would fade away, being washed out by the
-inter-task effects of the final set.
-
-Looking at the classifier performance, $\hat{\theta}_{NB}$, with respect to the
-treatments \textsc{AMBG} and $\textsc{CULT}_{img}$, we find that performance
-drops off dramatically after just the first image (see \textbf{Fig. 3A}).
-This suggests that inter-task effects mainly arise between consecutive tasks.
-However, a residual distinguishability between these two treatments does 
-persist until the final image (although for the fourth image we cannot assert
-this with 95\% confidence).
-
-We can similarly look at how the inter-task effects on label composition
-(i.e. fraction of culture- and food-oriented words) play out as workers 
-progress through the final image set.  To do this, we define the 
-\textit{excess cultural orientation} as the number of culture-oriented labels 
-minus the number of food oriented ones.  Tracking the excess cultural 
-orientation across the images is, however, not in itself meaningful,
-because some images will inherently carry more cultural content than others. 
-To account for this, we calculate the excess cultural content for both 
-\textsc{AMBG} and $\textsc{CULT}_{img}$, and subtract the former from the 
-latter, yielding the \textit{relative} excess cultural content, 
-$\Delta_{cult}$.  Formally,
-
-\begin{align}
-	\Delta_{cult}(i) = \frac{1}{N}\left[ \sum_{w\in\textsc{cult}_{img}} \left(N_{w,cult}^{(i)} - N_{w,food}^{(i)}\right)
-	- \sum_{w\in\textsc{ambg}} \left(N_{w,cult}^{(i)} - N_{w,food}^{(i)}\right)\right],
-\end{align}
-
-where $N_{w,cult}^{(i)}$ stands for the number of culture-oriented labels 
-attributed by worker $w$ to image $i$, while $N_{w,food}^{(i)}$ similarly 
-counts food-oriented labels, and $N$ is the total number of labels in a 
-treatment.
-
-The relative excess cultural content varied as workers proceed through the
-final image set in much the same way that $\hat{\theta}_\text{NB}$ did: for the
-first test image, it is significantly greater than zero, but drops off rapidly
-thereafter.  Unlike $\hat{\theta}_\text{NB}$, $\Delta_{cult}$ ceases to
-be significantly greater than zero after the second test image, so it would 
-seem that $\hat{\theta}_\text{NB}$ is the more sensitive of the two in
-detecting inter-task effects.
-
-\paragraph{Inter-task similarity encourages more specific labels.}
-For the next part of the analysis, it will be useful to speak of the
-``similarity'' between two image sets. In general, the characterization of 
-image content 
-is deeply complex and has been approached from the perspectives of 
-art\cite{panofsky1939studies,shatford1986analyzing},
-psychology\cite{Tversky1977327}, and information retrieval\cite{Jaimes20002}.
-Furthermore, the perception of \textit{similarity} is a particularly subtle 
-psychological phenomenon.  For example, a figure $A$ can appear simultaneously
-both \textit{more} and \textit{less} similar to an object $C$ than some other 
-object $B$[***].
-
-In the present study, we are more interested in the ultimate outputs of 
-workers' rather than the psychological details which lead to them (though 
-these are interesting in their own right).  This allows us to sidestep the 
-complication in attributing similarity: we asses how similar two sets of 
-images are, 
-\textit{with respect to the labeling task}, by looking at the fraction of 
-labels that they share.  Formally, we compute the similarity of two images
-sets $X$ and $Y$ by computing the Jacquard index between the sets of labels 
-attributed to them:
-
-\begin{align}
-	\text{Sim}(X,Y) = \frac{L(X) \cap L(Y)}{L(X) \cup L(Y)},
-\end{align}
-
-\begin{table}
-\centering
-\begin{tabular}{ l  d  s s s s}
-
-\toprule    
-\multirow{2}{*}{Image set} & \multicolumn{1}{c}{\# of unique} & 
-\multicolumn{4}{c}{Similarity}  \\
-\cline{3-6}
-
-&  \multicolumn{1}{c}{labels} 
-& \multicolumn{1}{c}{Ambiguous} 
-& \multicolumn{1}{c}{Cultural} 
-& \multicolumn{1}{c}{Ingredients}
-& \multicolumn{1}{c}{Test} \\
-
-\midrule
-
-Ambiguous & 763 & 1 & 0.0418 & 0.142 & 0.167 \\
-
-Cultural & 659 & 0.0418  & 1 & 0.0347 & 0.0561 \\
-
-Ingredients & 681 & 0.142  & 0.0347 & 1 & 0.110 \\
-
-Test & 1695 & 0.167  & 0.0561 & 0.110 & 1
-\\
-\bottomrule
-
-\end{tabular}
-\caption{\footnotesize{
-	Number of unique labels attributed to each image set, and their
-	similarities based on \textbf{Eq. 4} 
-}}
-\label{table:2}
-\end{table}
-
-where $L(X)$ denotes the set of labels attributed to $X$.  See \textbf{Methods}
-for additional details regarding the calculation of similarity.
-
-The similarities of the various image sets are presented in \textbf{Table 2}. 
-First, observe that the ambiguous and ingredients sets are much more similar 
-to each other than either is to the culture set.  This is consistent with our
-finding that $\hat{\theta}_\text{NB}$ between \textsc{AMBG} and 
-$\textsc{INGR}_{img}$ was not significant (see \textbf{Fig 1}).
-
-Next we draw attention to the similarity between the initial sets and the test 
-set.  The ambiguous set is the most similar to the test set, followed by the
-ingredients set, and the cultural set was most different from the test set.
-Observe that these levels of similarity mirror the label specificity for the 
-corresponding treatments (c.f. \textbf{Fig. 2B}).
-
-This suggests that labeling a series of images that are similar to 
-one another might encourage workers to use more specific terminology.
-Such a phenomenon would be consistent with the psychological mechanism known 
-as \textit{negative priming}.  Negative priming occurs when a person becomes 
-desensitized to non-salient stimuli to which she is repeatedly 
-exposed [***].  Consider that workers who initially 
-labeled the ambiguous image set had already seen five images showing 
-prepared meals once they labeled the first test image.  At that point,
-a worker might not regard the labels \texttt{food} or \texttt{meal} to be 
-salient, since they do not distinguish the image from those she had seen 
-already.
-
-We are suggesting that, although workers are not instructed to compare
-images in any way, prior tasks nevertheless create a frame of reference
-relative to which later tasks are judged.  This in turn 
-influences the perception of salience. Thus, in a series of subjective 
-characterization tasks that have very similar content, the worker's focus 
-will tend to be directed away from generic, shared attributes, towards those 
-attributes that are specific and distinguishing.
-
-\subsection*{Discussion}
-
-\paragraph{Inter-task effects should be considered during task design.}  
-Our results show that inter-task effects can have a strong influence on how
-workers label images.  In particular, we observed that prior tasks influence
-the specificity and content of labels.  Surprisingly, framing a task by 
-indicating a semantically-loaded funder had much milder effects on worker 
-outputs, generally below the statistical power of our tests.
-
-We therefore caution those designing studies using human computation: even if 
-the requester has eliminated surrounding influences to every practical extent, 
-\textit{the greatest source of bias might lurk in the tasks themselves}.
-Due consideration should be given to how tasks are bundled together.
-While our measurements of $\hat{\theta}_\text{NB}$ indicated that inter-task 
-effects persisted even to the fifth test image, the most severe effects arise 
-between consecutive tasks.
-
-\paragraph{$\theta$ provides a general purpose measure of priming effects.}
-When used three approaches to detecting priming effects: 1) using a Naive Bayes
-classifier to measure $\hat{\theta}_\text{NB}$, 2) tallying the number of 
-culture- and food-oriented labels, and 3) comparing the relative specificity
-of labels based on an ontology.  Of the three, measuring $
-\hat{\theta}_\text{NB}$ was the most sensitive.
-
-In one sense, this is not surprising because the Naive 
-Bayes classifier takes into account the frequency of occurrence of all labels 
-encountered during training.  But it is remarkable that the 
-method which incorporates neither prior knowledge about the image contents nor 
-label semantics, outperforms those that do.  This is a powerful feature 
-because, given the outputs from two sets of workers, one can test whether they 
-have been differently primed without knowing how that priming might manifest.
-
-Our algorithmic definition of priming is phrased in terms of worker outputs
-rather than psychological phenomena.  This provides a connection between
-the priming effects and their potential to impact decisions made on the basis
-of worker outputs.  In the case of a binary decision, $\theta$
-describes the worst-case bias introduced by failing to control for priming 
-effects.
-
-\paragraph{Batching tasks for better HPU performance.}
-Our proposed connection between similarity and specificity during 
-image-labeling might be used to tune the specificity of labels.  For example,
-If one seeks very nuanced labeling, our results suggest that the images 
-should first be sorted into batches based on their similarity. This could be 
-accomplished by beginning with a first, coarse characterization of unsorted 
-images, followed by batching based on the labels obtained. Then, the batches
-of similar images could be served for a second round of finer labeling. 
-The sorting and re-labeling could then in principle be repeated.
-
-In effect, this creates a hierarchical workflow, where the first, 
-coarsely-characterizing HPUs provide a stream of labeled images that is 
-split (batched) and fed to other HPUs for finer characterization.  This 
-workflow exhibits an interesting difference between HPUs and CPUs.  In general,
-whenever an aspect of a problem can be parallelized when employing CPUs, one
-gains efficiency.  But here, because of HPU hysteresis, we see an example where
-one might sacrifice accuracy through parallelization.
-
-\subsection*{Conclusion}
-
-Inter-task priming can have a strong effect.  
-For a canonical image-labeling task, inter-task priming was stronger in its 
-effects on the orientation and specificity of labels than was the disclosure of
-semantically loaded funder names.  Requesters on microtask platforms should 
-take care to avoid introducing biases due to the batching and ordering tasks 
-they serve to workers.  At the same time, inter-task priming might be exploited to improve task output, for 
-example, to drive more (or less) nuanced responses.
-
-We demonstrated that our algorithmic definition of priming, and its 
-implementation using a Naive Bayes classifier, provides a sensitive,
-general-purpose method for detecting priming.  Even when the expected effects 
-on label orientation and specificity were slight, $\theta_\text{NB}$ 
-was significant.  $\theta_\text{NB}$ provides direct statistical evidence that 
-populations have been affected by priming, even when the nature of the 
-effects are not understood.
-
-\subsection*{Materials and Methods}
-
-\textbf{AMT Tasks.} The task described in \textbf{Experimental Setup}
-was served to 900 workers, who were uniformly randomly assigned to
-treatments.  Each treatment had at least 126 task completions.  To obtain 
-uniformly sized treatments, we randomly selected 126 samples from each 
-treatment. Workers were
-only allowed to participate once and could not see the initial or final 
-images, nor the funder names when previewing the task.
-
-\textbf{Naive Bayes Classifier.}
-The features provided to the Naive Bayes classifier consisted of the labels
-that the worker provided along with the image and specific location in which 
-the label was entered
-(each image had five distinct label inputs).  Thus, \texttt{wine} occurring in 
-position 1 of image 2 would be considered as a distinct feature from 
-\texttt{wine} occurring in position 2 of image 2. The classifier 
-had better performance when this distinction was made.
-
-\textbf{Building the ontology of terms.}  The ontology was built manually
-by the experimenters, starting from the corpus of labels. Labels occurring only 
-once were discarded.  We created the root classes \texttt{activity}, 
-\texttt{adjective}, \texttt{culture}, 
-\texttt{food}, and \texttt{thing}. \texttt{culture} and \texttt{food} were 
-given top-level status because they were prominently represented in the corpus.
-Whenever one label was judged to be a more specific case of another, a
-directed edge was drawn from the more general to the more specific. This
-judgment call was made by the experimenters.  However, the labels from all 
-treatments were aggregated before assembling the ontology,  to 
-ensure that the ontology construction would not be affected by 
-knowledge of the treatments from which labels originated. 
-Labels which were judged to be roughly synonymous were treated as identical,
-and labels judged to be misspellings were corrected.
-
-\textbf{Statistical significance of $\theta_\text{NB}$.}
-We test the significance two population's measured $\theta_\text{NB}$ against 
-the null hypothesis that that the two populations are in fact identical:
-\begin{align}
-	\mathbf{H_0}: \theta_\text{NB} = 0 \\
-	\mathbf{H_1}: \theta_\text{NB} > 0
-\end{align}
-If the populations are in fact identical, then the probability that the 
-classifier correctly classifies a worker is $\frac{1}{2}$. Let $K$ be a random
-variable which denotes the number of correct classifications when the 
-classifier is challenged to classify a total of $n$ workers during 
-cross-validation.  Under $\mathbf{H_0}$, the probability distribution of $K$ 
-is:
-\begin{align}
-	\text{Pr}\{K = k | n \} = { n \choose k } \left(\frac{1}{2}\right)^n.
-\end{align}
-We can reject $\mathbf{H_0}$ at significance $\alpha$ if $\theta_\text{NB}$ 
-is greater than or equal to a critical value, $\theta_\text{NB}^*$:
-\begin{align}
-	\theta^*_\text{NB} = \frac{2k^*}{n} - 1
-\end{align}
-where $k^*$ is the smallest integer in $\{0,\dots,n\}$ that satisfies 
-\begin{align}
-	\sum_{k \in \{k^*, \dots, n\}} \text{Pr}\{K = k | n \} < \alpha.
-\end{align}
-For a 5-fold cross-validation with non-overlapping test sets containing 25 
-workers ($n = 125$), and a significance of $\alpha = 0.05$, we
-have $k^*=73 \implies \theta_\text{NB}^* = 0.168$.
-
-\textbf{Statistical significance of relative specificity.}
-We used \textbf{Eq.~\ref{eq:specificity}} to compute the relative specificity
-of two treatments.  To analyze relative specificity statistically,
-we first develop \textbf{Eq.~\ref{eq:specificity}} from an intermediate 
-definition.  Let the specificity of a worker $u$ relative to a 
-\textit{basis treatment} $\mathcal{V}$, denoted $S_V(u)$, be the expected 
-relative specificity between $u$ and a worker uniformly sampled from 
-$\mathcal{V}$:
-
-\begin{align}
-	S_V(u) =  \text{E}_V\{s(u,V)\}, \quad V \in_R \mathcal{V},
-		\label{eq:basis-specificity}
-\end{align}
-where $V$ is a random, uniformly sampled worker from $\mathcal{V}$.  We 
-subscript the expectation operator with $V$ to indicate 
-that the expectation is taken over the distribution of $V$.  Then, the 
-relative specificity of two treatments, $S(\mathcal{U},{V})$, can be 
-written as:
-\begin{align}
-	S(\mathcal{U},\mathcal{V}) = 
-		\text{E}_U\{S_V(U)\}, \quad U \in_R \mathcal{U},
-		\label{eq:treatment-specificity}
-\end{align}
-where $U$ is a random, uniformly sampled worker from $\mathcal{U}$.  This 
-yields 
-estimators for $S_V(u)$ and $S(\mathcal{U}, \mathcal{V})$, and their variances
-as shown below (note that 
-\textbf{Eq.~\ref{eq:treatment-specificity-estimator}} is
-equivalent to \textbf{Eq.~\ref{eq:specificity}}):
-
-\begin{align}
-	\hat{S}_V(u) &= \frac{1}{|\mathcal{V}|} \sum_{v \in \mathcal{V}} s(u,v), 
-		\label{eq:basis-specificity-estimator} \\
-		\hat{S}(\mathcal{U},\mathcal{V}) 
-		&= \frac{1}{|\mathcal{U}|} \sum_{u \in \mathcal{V}} \hat{S}_V(u),
-		\label{eq:treatment-specificity-estimator} \\
-		\text{Var}_V\{\hat{S}_V(u)\} 
-			&= \frac{1}{|\mathcal{V}|}\text{Var}_V\{s(u,V)\},
-		\label{eq:basis-specificity-variance} \\
-		\text{Var}_{U,V}\{\hat{S}(\mathcal{U},\mathcal{V})\} 
-			&= \frac{1}{|\mathcal{V}|\cdot|\mathcal{U}|^2} 
-			\sum_{u\in U}\text{Var}_V\{{s}(u,V)\}.
-		\label{eq:treatment-specificity-variance}
-\end{align}
-\td{There are problems with this.  I'm still trying to figure out how to
-	calculate the variance properly.}
-$\text{Var}_V\{s(u,V)\}$ can be directly calculated as a sample variance.
-\textbf{Equations \ref{eq:basis-specificity-estimator}} through 
-\textbf{\ref{eq:treatment-specificity-variance}} provide enough information to test the hypotheses:
-\begin{align}
-	\begin{matrix}
-		\mathbf{H_0}: S(\mathcal{U}, \mathcal{V}) = 0 \\[0.5em]
-		\mathbf{H_1}: S(\mathcal{U}, \mathcal{V}) \neq 0
-	\end{matrix}
-\end{align}
+\section*{Supplementary Figures}
 
@@
 \end{figure}
-\section*{Acknowledgments}
-\section*{References}
-\begingroup
-\renewcommand{\chapter}[2]{}
-\bibliography{newbib.bib}
-\endgroup
-\bibliographystyle{plain}
 

### 2014-08-04 docs/publications/2014.08_HCOMP/_man.tex
make version for hcomp PhD consortium submission

--- 2014-08-03 docs/publications/2014.05_PNAS/manuscript.tex
@@
 %
-\documentclass[a4paper]{report}
-\usepackage[hmargin=2cm,vmargin=2cm]{geometry}
+\documentclass[letterpaper,twocolumn]{article}
+\usepackage[hmargin=0.75cm,vmargin=0.75cm]{geometry}
 \usepackage{scrextend}
@@
 Workers on such platforms prefer to work on batches of tasks of the same 
-type[***], so we investigate the potential for the content of earlier tasks 
+type, so we investigate the potential for the content of earlier tasks 
 to influence worker performance in later tasks, which we call ``inter-task'' 
@@
 
-\section*{Significance Statement}
 \section*{Introduction}
@@
 Existing work on priming effects focuses on the internal psychological 
-mechanisms of priming[***], but here we are interested in how the treatment of 
+mechanisms of priming, but here we are interested in how the treatment of 
 workers can impact an application of human computation. This leads us to 
@@
 tasks on the AMT platform.  
-(***why we are using image labeling as prototypical task***) 
 Each worker is required to label ten images 
@@
 would orient workers to provide a greater quantity and specificity of labels 
-which relate to this ``preferred'' content[***].
+which relate to this ``preferred'' content.
 
@@
 stimulus object (e.g. a spoken word or an image) when the object is noisier, 
-fainter, or briefer [***].  Methods are also employed to measure processes
-in the brain of the participant, such as by fMRI[***].  These approaches are 
+fainter, or briefer.  Methods are also employed to measure processes
+in the brain of the participant, such as by fMRI.  These approaches are 
 well-suited to studying the underlying psychological mechanisms at work.
@@
 Here, we use a Naive Bayes classifier because it simple and performs well 
-across a broad range of classification tasks[***].
+across a broad range of classification tasks.
 
@@
 \subsection*{Experimental Setup}
+
+\begin{figure*}
+	\centering{
+	\includegraphics[scale=0.94]{figs/f1-thetas_full_pairwise25_img1.pdf}
+	\caption{ \footnotesize{
+		Empirical difference in priming, $\hat{\theta}_\text{NB}$, between 
+		various treatments.  The difference in priming between each pair of 
+		treatments 
+		was determined by cross-validation of a Naive Bayes classifier trained
+		to classify workers based on the labels they attributed to the first
+		image of the final image set. Each panel compares a basis treatment,
+		indicated above the panel, to various treatments indicated on the
+		abscissa.  We can conclude, with 95\% confidence, that the classifier
+		is performing better than chance when $\hat{\theta}_\text{NB}$ 
+		exceeds 0.168, indicated by the dotted line.  See \textbf{Methods} for
+		the calculation of this confidence threshold.
+	}}
+}
+\end{figure*}
+
 \begin{table}[t]
@@
 	}}
-	\end{addmargin}
 	\label{table:1}
@@
 
-\begin{figure}
-	\includegraphics[scale=0.94]{figs/f1-thetas_full_pairwise25_img1.pdf}
-	\caption{ \footnotesize{
-		Empirical difference in priming, $\hat{\theta}_\text{NB}$, between 
-		various treatments.  The difference in priming between each pair of 
-		treatments 
-		was determined by cross-validation of a Naive Bayes classifier trained
-		to classify workers based on the labels they attributed to the first
-		image of the final image set. Each panel compares a basis treatment,
-		indicated above the panel, to various treatments indicated on the
-		abscissa.  We can conclude, with 95\% confidence, that the classifier
-		is performing better than chance when $\hat{\theta}_\text{NB}$ 
-		exceeds 0.168, indicated by the dotted line.  See \textbf{Methods} for
-		the calculation of this confidence threshold.
+\paragraph{Earlier tasks influenced workers' level of specificity.} 
+\begin{figure*}
+	\centering{
+		\includegraphics[scale=0.70]{figs/orientation_specificity.pdf}
+	\caption{\footnotesize{
+		\textbf{A}) Percent label composition (culture- vs food-oriented 
+		labels) for 
+		various images and treatments.  
+		\textbf{B}) Relative specificities of treatments
+		indicated along the abscissa compared to those indicated above the 
+		plot.  The size of the bar indicates how much more specific
+		the labels from one treatment are compared to the other, and points 
+		toward in the direction of the more specific treatment.
 	}}
-\end{figure}
+}
+\end{figure*}
 
@@
 
-To this end, we constructed an ontology of labels attributed to the final 
-images.  The ontology was constructed as a directed acyclic graph, with edges 
-pointing from more general labels to more specific ones.
+To this end, we constructed an ontology from the labels attributed to the 
+test images.  The ontology was constructed as a directed acyclic graph, with 
+edges pointing from more general labels to more specific ones.
 For example, our ontology contains the path \texttt{food} $\to$ 
@@
 significantly different.
-
-\paragraph{Earlier tasks influenced workers' level of specificity.} 
-\begin{figure}
-	\begin{center}
-		\includegraphics[scale=0.70]{figs/orientation_specificity.pdf}
-	\caption{\footnotesize{
-		\textbf{A}) Percent label composition (culture- vs food-oriented 
-		labels) for 
-		various images and treatments.  
-		\textbf{B}) Relative specificities of treatments
-		indicated along the abscissa compared to those indicated above the 
-		plot.  The size of the bar indicates how much more specific
-		the labels from one treatment are compared to the other, and points 
-		toward in the direction of the more specific treatment.
-	}}
-	\end{center}
-\end{figure}
 
@@
 \begin{figure}
+	\centering{
 	\includegraphics[scale=0.7]{figs/longitudinal_theta_excess-culture.pdf}
@@
 	}}
+}
 \end{figure}
@@
 \begin{align}
-	\Delta_{cult}(i) = \frac{1}{N}\left[ \sum_{w\in\textsc{cult}_{img}} \left(N_{w,cult}^{(i)} - N_{w,food}^{(i)}\right)
-	- \sum_{w\in\textsc{ambg}} \left(N_{w,cult}^{(i)} - N_{w,food}^{(i)}\right)\right],
+	\Delta_{cult}(i) = \frac{1}{N}\left[ \sum_{w\in\textsc{cult}_{img}} \left(N_{w,cult}^{(i)} - N_{w,food}^{(i)}\right)\right. \\
+\left.	- \sum_{w\in\textsc{ambg}} \left(N_{w,cult}^{(i)} - N_{w,food}^{(i)}\right)\right],
 \end{align}
@@
 both \textit{more} and \textit{less} similar to an object $C$ than some other 
-object $B$[***].
+object $B$.
 
@@
 
-\begin{table}
+\begin{table*}
 \centering
@@
 \label{table:2}
-\end{table}
+\end{table*}
 
@@
 desensitized to non-salient stimuli to which she is repeatedly 
-exposed [***].  Consider that workers who initially 
+exposed.  Consider that workers who initially 
 labeled the ambiguous image set had already seen five images showing 
@@
 \subsection*{Materials and Methods}
+Omitted due to length.  This will be added to supplementary material.
 
-\textbf{AMT Tasks.} The task described in \textbf{Experimental Setup}
-was served to 900 workers, who were uniformly randomly assigned to
-treatments.  Each treatment had at least 126 task completions.  To obtain 
-uniformly sized treatments, we randomly selected 126 samples from each 
-treatment. Workers were
-only allowed to participate once and could not see the initial or final 
-images, nor the funder names when previewing the task.
-
-\textbf{Naive Bayes Classifier.}
-The features provided to the Naive Bayes classifier consisted of the labels
-that the worker provided along with the image and specific location in which 
-the label was entered
-(each image had five distinct label inputs).  Thus, \texttt{wine} occurring in 
-position 1 of image 2 would be considered as a distinct feature from 
-\texttt{wine} occurring in position 2 of image 2. The classifier 
-had better performance when this distinction was made.
-
-\textbf{Building the ontology of terms.}  The ontology was built manually
-by the experimenters, starting from the corpus of labels. Labels occurring only 
-once were discarded.  We created the root classes \texttt{activity}, 
-\texttt{adjective}, \texttt{culture}, 
-\texttt{food}, and \texttt{thing}. \texttt{culture} and \texttt{food} were 
-given top-level status because they were prominently represented in the corpus.
-Whenever one label was judged to be a more specific case of another, a
-directed edge was drawn from the more general to the more specific. This
-judgment call was made by the experimenters.  However, the labels from all 
-treatments were aggregated before assembling the ontology,  to 
-ensure that the ontology construction would not be affected by 
-knowledge of the treatments from which labels originated. 
-Labels which were judged to be roughly synonymous were treated as identical,
-and labels judged to be misspellings were corrected.
-
-\textbf{Statistical significance of $\theta_\text{NB}$.}
-We test the significance two population's measured $\theta_\text{NB}$ against 
-the null hypothesis that that the two populations are in fact identical:
-\begin{align}
-	\mathbf{H_0}: \theta_\text{NB} = 0 \\
-	\mathbf{H_1}: \theta_\text{NB} > 0
-\end{align}
-If the populations are in fact identical, then the probability that the 
-classifier correctly classifies a worker is $\frac{1}{2}$. Let $K$ be a random
-variable which denotes the number of correct classifications when the 
-classifier is challenged to classify a total of $n$ workers during 
-cross-validation.  Under $\mathbf{H_0}$, the probability distribution of $K$ 
-is:
-\begin{align}
-	\text{Pr}\{K = k | n \} = { n \choose k } \left(\frac{1}{2}\right)^n.
-\end{align}
-We can reject $\mathbf{H_0}$ at significance $\alpha$ if $\theta_\text{NB}$ 
-is greater than or equal to a critical value, $\theta_\text{NB}^*$:
-\begin{align}
-	\theta^*_\text{NB} = \frac{2k^*}{n} - 1
-\end{align}
-where $k^*$ is the smallest integer in $\{0,\dots,n\}$ that satisfies 
-\begin{align}
-	\sum_{k \in \{k^*, \dots, n\}} \text{Pr}\{K = k | n \} < \alpha.
-\end{align}
-For a 5-fold cross-validation with non-overlapping test sets containing 25 
-workers ($n = 125$), and a significance of $\alpha = 0.05$, we
-have $k^*=73 \implies \theta_\text{NB}^* = 0.168$.
-
-\textbf{Statistical significance of relative specificity.}
-We used \textbf{Eq.~\ref{eq:specificity}} to compute the relative specificity
-of two treatments.  To analyze relative specificity statistically,
-we first develop \textbf{Eq.~\ref{eq:specificity}} from an intermediate 
-definition.  Let the specificity of a worker $u$ relative to a 
-\textit{basis treatment} $\mathcal{V}$, denoted $S_V(u)$, be the expected 
-relative specificity between $u$ and a worker uniformly sampled from 
-$\mathcal{V}$:
-
-\begin{align}
-	S_V(u) =  \text{E}_V\{s(u,V)\}, \quad V \in_R \mathcal{V},
-		\label{eq:basis-specificity}
-\end{align}
-where $V$ is a random, uniformly sampled worker from $\mathcal{V}$.  We 
-subscript the expectation operator with $V$ to indicate 
-that the expectation is taken over the distribution of $V$.  Then, the 
-relative specificity of two treatments, $S(\mathcal{U},{V})$, can be 
-written as:
-\begin{align}
-	S(\mathcal{U},\mathcal{V}) = 
-		\text{E}_U\{S_V(U)\}, \quad U \in_R \mathcal{U},
-		\label{eq:treatment-specificity}
-\end{align}
-where $U$ is a random, uniformly sampled worker from $\mathcal{U}$.  This 
-yields 
-estimators for $S_V(u)$ and $S(\mathcal{U}, \mathcal{V})$, and their variances
-as shown below (note that 
-\textbf{Eq.~\ref{eq:treatment-specificity-estimator}} is
-equivalent to \textbf{Eq.~\ref{eq:specificity}}):
-
-\begin{align}
-	\hat{S}_V(u) &= \frac{1}{|\mathcal{V}|} \sum_{v \in \mathcal{V}} s(u,v), 
-		\label{eq:basis-specificity-estimator} \\
-		\hat{S}(\mathcal{U},\mathcal{V}) 
-		&= \frac{1}{|\mathcal{U}|} \sum_{u \in \mathcal{V}} \hat{S}_V(u),
-		\label{eq:treatment-specificity-estimator} \\
-		\text{Var}_V\{\hat{S}_V(u)\} 
-			&= \frac{1}{|\mathcal{V}|}\text{Var}_V\{s(u,V)\},
-		\label{eq:basis-specificity-variance} \\
-		\text{Var}_{U,V}\{\hat{S}(\mathcal{U},\mathcal{V})\} 
-			&= \frac{1}{|\mathcal{V}|\cdot|\mathcal{U}|^2} 
-			\sum_{u\in U}\text{Var}_V\{{s}(u,V)\}.
-		\label{eq:treatment-specificity-variance}
-\end{align}
-\td{There are problems with this.  I'm still trying to figure out how to
-	calculate the variance properly.}
-$\text{Var}_V\{s(u,V)\}$ can be directly calculated as a sample variance.
-\textbf{Equations \ref{eq:basis-specificity-estimator}} through 
-\textbf{\ref{eq:treatment-specificity-variance}} provide enough information to test the hypotheses:
-\begin{align}
-	\begin{matrix}
-		\mathbf{H_0}: S(\mathcal{U}, \mathcal{V}) = 0 \\[0.5em]
-		\mathbf{H_1}: S(\mathcal{U}, \mathcal{V}) \neq 0
-	\end{matrix}
-\end{align}
-
-\begin{figure}
-	\includegraphics[scale=1.00]{figs/taskImages/testImages.jpg}
-	\caption{Testing image set. These images were presented to all workers in 
-		the order shown after the priming set of images.}
-\end{figure}
-
-\begin{figure}
-	\includegraphics[scale=1.00]{figs/taskImages/ambiguous.jpg}
-	\caption{ Ambiguous image set. These images were presented to workers from 
-		certain treatments (see \textbf{Table 1}) in the order shown.}
-\end{figure}
-
-\begin{figure}
-	\includegraphics[scale=1.00]{figs/taskImages/cultural.jpg}
-	\caption{Cultural image set. These images were presented to workers from 
-		certain treatments (see \textbf{Table 1}) in the order shown.}
-\end{figure}
-
-\begin{figure}
-	\includegraphics[scale=1.00]{figs/taskImages/ingredients.jpg}
-	\caption{ Ingredients image set. These images were presented to workers 
-		from certain treatments (see \textbf{Table 1}) in the order shown.}
-\end{figure}
-\section*{Acknowledgments}
-\section*{References}
 \begingroup
@@
 
+\subsection*{Motivation}
+I am near the beginning of my PhD studies, and have joined Derek Ruths' lab 
+with the expressed purpose of performing human computation research.
+My interests lay at the intersection of game theory, psychology, and 
+computation.  The overarching goal for my research relates to group 
+decisionmaking, and can be phrased in the following way: ``what are the factors
+that influence the social efficiency of collective decisionmaking?'' I
+view decisionmaking as the central activity of all social organizations, and 
+I view this as a computational process.  My reason for 
+wanting to attend the PhD Consortium at HCOMP is threefold.  First, I wish to
+discuss my ideas with others, get feedback, and learn more about how the 
+community frames such questions, to help me as I finalize my PhD proposal 
+into concrete research aims.  Second, I hope to make connections to other 
+researchers who are interested in similar research questions.  Finally, I wish
+to obtain feedback on a crowdsourcing platform that I have implemented (and
+hopefully pique other researcher's interest), which I intend to use in my
+research.
 \end{document}

### 2014-08-04 docs/publications/2014.08_HCOMP/supp.tex
make version for hcomp PhD consortium submission

--- 2014-08-04 docs/publications/2014.05_PNAS/man.tex
@@
 \documentclass[letterpaper]{article} 
+\usepackage{caption} 
 \usepackage{aaai} 
@@
 
-\usepackage{scrextend}
 \usepackage{graphicx}
@@
 \title{Inter-Task Effects induce Bias in Crowdsourcing}
-\author{Edward Newell \and Derek Ruths\\
-	McGill University, School of Computer Science, Montreal, Canada\\
+\author{Edward Newell\footnote{bla} \and Derek Ruths\\
+School of Computer Science, McGill University, Montreal, Canada\\
+$^*$\texttt{edward.newell@mail.mcgill.ca}\\
 }
@@
 \begin{document}
-\maketitle
-\section*{Abstract}
-Microtask platforms allow researchers to engage participants quickly and 
-inexpensively.
-Workers on such platforms probably perform many tasks in succession,
-so we investigate interactions between earlier tasks and later ones, which we 
-call ``inter-task'' effects.  
-Existing research investigates many task design factors, such as 
-``framing'', on the quality of responses, but to our knowledge, does not 
-address inter-task effects.  
-We use a canonical image-labeling task on Amazon Mechanical Turk 
-to measure the impact of inter-task and framing effects on the focus and 
-specificity of labels that workers provide.
-We also introduce an algorithmic definition of priming, which measures the 
-worst-case bias introduced into repsonses.
-We find that inter-task effects produced a much stronger impact than framing, 
-and demonstrate that our novel priming definition yields a generalized 
-measure of priming effects when combined with machine learning algorithms.
-
-\section*{Introduction}
-
-Microtask crowdsourcing platforms like Amazon Mechanical Turk (AMT) make it 
-possible to submit batches of small tasks to a large pool of human workers, 
-who do the tasks for fun, a sense of purpose, and remuneration 
-\cite{kazai2013analysis,Antin20122925}.  
-Originally used to distribute clerical work, these platforms 
-increasingly serve as a fast and cheap means to engage experimental 
-participants in a research 
-setting \cite{snow2008cheap}.
-
-The task requester can interact with the platform like a compute server, 
-seamlessly 
-integrating human and machine computation.  Researchers have put forward the 
-term HPU (Human co-Processing Unit), viewing the introduction of 
-microtask platforms as a new computing architecture
-\cite{5543192}.
-
-Here, we highlight an important way in which HPUs differ from CPUs, with 
-serious implications for the design of tasks.  It is well known that people 
-are subject to priming effects 
-\cite{BJOP1796,No2007,beller1971priming} and, in particular, task-repetition effects
-\cite{Gass1999549,sohn2001task}.  
-We investigate the effect that previously completed tasks have on workers'
-responses during subsequent ones. We call such effects 
-\textit{inter-task priming}.  Inter-task priming would amount to a kind of
-\textit{hysteresis}, meaning that HPU output is not only a function of the 
-current input, but also of the history of inputs.
-
-There has been considerable investigation into the factors that affect the 
-quality and quantity of micro-task completion.  These include the level of 
-pay \cite{kazai2013analysis}, training \cite{le2010ensuring}, screening of 
-workers \cite{paolacci2010running}, and user-interface design 
-\cite{Finnerty2013}.  Research has also investigated \textit{framing}, 
-by testing the effects of disclosing the workflow context 
-\cite{Kinnaird2012281}, and the purpose of tasks 
-\cite{chandler2013breaking}.  To our knowledge, no study has investigated the 
-effects of inter-task priming.
-
-To characterize the effects of inter-task priming, we present a novel  
-\textit{algorithmic definition of priming}, and a general method 
-for measuring priming effects using machine learning algorithms.  
-Studies of priming typically focus on the internal psychological 
-mechanisms[***], but our definition focuses on the impact that priming has to
-the downstream application of human computation.
-
-In the present work, we investigate inter-task priming on the Amazon 
-Mechanical Turk platform, using an image-labeling task, one of the most common 
-kinds of tasks on that platform [***].  The task requires workers to label ten 
-images featuring 
-food and culture.  We regard these images as being made up of an 
-\textit{initial} and \textit{final set}, but, crucially, there is no
-distinction made between these sets, nor any interruption in the flow of tasks 
-from the view of the worker.
-We vary the initial set of images, while keeping the final set the same to 
-analyze the effect that that the initial images have on the labels that 
-workers' attribute to the final set.  We measure effects using our novel 
-approach, as well as looking for changes in the content of labels and label 
-specificity based on an ontology we developed for that purpose.
-
-As a point of comparison, we subject some groups of workers to a kind of
-\textit{framing}: we disclose a fictitious, semantically-loaded name for 
-the requester funding the tasks.
-The names were chosen to suggest the requester's interest in a specific 
-aspect of the image content.  We expect this would cause workers 
-to provide more labels, and greater specificity, relating to this 
-``preferred'' content.
-
-Surprisingly, we find that inter-task effects are much stronger than the 
-framing.  Our results show that initial tasks can significantly alter the 
-focus of worker's labels.  Interestingly, we find that inter-task
-effects can be used to induce greater specificity.  Our results suggest that
-workers attribute more specific labels when labeling a series of images that
-that are more similar to one another.  This suggests that careful 
-consideration should be given to the bundling of tasks when designing a study 
-using a microtask platform.
-
-Our analysis also highlights important advantages of our novel definition of 
-priming.  Our approach incorporates no prior knowledge about the nature
-of the task whatsoever.  In contrast, we also sought to detect priming
-based on its direct effects on label content and specificity,
-drawing on prior knowledge about the images and label semantics.
-Remarkably, while being more general, our definition yields a more sensitive
-measure of priming when combined with machine learning algorithms. 
-This approach could be applied to detect priming when one does not 
-\emph{a priori} know whether any priming has occurred, 
-nor what the nature of the effects might be.
-\subsection*{An algorithmic definition of priming}
-In psychology, the effects of priming are usually measured in terms of a 
-change in the  
-speed or accuracy of responses in a task, or in the ability to recognize a 
-stimulus object (e.g. a spoken word or an image) when the object is noisier, 
-fainter, or briefer.  Methods are also employed to measure processes
-in the brain of the participant, such as by fMRI.  Our purpose is different: 
-we are interested in assessing the ramifications that priming of HPUs could 
-have on the applications to which they are employed.
-Thus, we choose to define priming effects in terms of the algorithmic 
-distinguishability of the content of primed output.
-
-One difficulty in constructing a definition of priming is that there would 
-appear to be no defensible notion of a ``neutral'' or ``unprimed state''.  
-While arguments could perhaps be made that one treatment or another is 
-\textit{more} 
-``neutral'', we choose to define priming relatively, and speak of one 
-treatment being \textit{differently primed} from another.
-
-From the point of view of applications, the interest of priming is in how it
-affects task performance. Thus, we define priming with respect to a task $\mathcal{T}$.  People will always differ in their initial knowledge, specific 
-aptitudes, and in many other intrinsic aspects.  Moreover, priming may not be 
-``complete'', in the sense that people's experiences before
-priming may continue to have residual effects.  Therefore, we define priming 
-in relation to populations, which we regard as having stable distributions of
-such latent attributes.
-
-To set up the definition, when a population of people $\mathcal{P}$ performs
-a task $\mathcal{T}$ thus producing a population of task-outputs $\mathcal{L}$,
-we will write $\mathcal{T}(\mathcal{P}) = \mathcal{L}$.
-
-\vspace{2mm}
-\begin{mydef}
-	\upshape
-	Two mutually exclusive populations of people, $\mathcal{P}_0$ and 
-	$\mathcal{P}_1$, are uniformly and randomly subsampled from an initial 
-	population $\mathcal{P}$, and are exposed to (possibly) different priming 
-	treatments. Each population performs a task $\mathcal{T}$, 
-	producing task-outputs $\mathcal{T}(\mathcal{P}_0)$ and 
-	$\mathcal{T}(\mathcal{P}_1)$.
-	These populations are subsampled, producing 
-	$P_0 \subset \mathcal{P}_0$ and
-	$P_1 \subset \mathcal{P}_1$. A uniform, random bit is chosen, 
-	$b\in _R \{0,1\}$, and a single worker $p$ is uniformly and randomly 
-	sampled from 
-	$\mathcal{P}_b \setminus P_b$.
-	We say that $\mathcal{P}_0$ and $\mathcal{P}_1$ 
-	\emph{differ in priming by a degree at least $\theta$},
-	if there exists a \emph{distinguisher algorithm} $\mathcal{A}$ that takes as input 
-	$\langle\mathcal{T}(J)$, $\mathcal{T}(K)$, $\mathcal{T}(\{p\})\rangle$
-	and outputs a guess for $b$ with accuracy $\frac{1+\theta}{2}$.  
-\end{mydef}
+\begin{figure*}
+	\includegraphics[scale=1.00]{figs/taskImages/testImages.jpg}
+	\caption*{Figure S1: Testing image set. These images were presented to all workers in 
+		the order shown after the initial set of images.}
+\end{figure*}
 
 \begin{figure*}
-	\centering{
-	\includegraphics[scale=0.94]{figs/f1-thetas_full_pairwise25_img1.pdf}
-	\caption{ \footnotesize{
-		Empirical difference in priming, $\hat{\theta}_\text{NB}$, between 
-		various treatments.  The difference in priming between each pair of 
-		treatments 
-		was determined by cross-validation of a Naive Bayes classifier trained
-		to classify workers based on the labels they attributed to the first
-		image of the final image set. Each panel compares a basis treatment,
-		indicated above the panel, to various treatments indicated on the
-		abscissa.  We can conclude, with 95\% confidence, that the classifier
-		is performing better than chance when $\hat{\theta}_\text{NB}$ 
-		exceeds 0.168, indicated by the dotted line.  See \textbf{Methods} for
-		the calculation of this confidence threshold.
-	}}
-}
+	\includegraphics[scale=1.00]{figs/taskImages/ambiguous.jpg}
+	\caption*{Figure S2: Ambiguous image set. These images were presented to workers from 
+		certain treatments (see \textbf{Table 1}) in the main text.}
 \end{figure*}
 
-In the language of computer science, $\mathcal{A}$ is a classifier performing
-a binary classification.  The measure $\theta$ can range between 0 and 1, and 
-indicates how much better the performance of the best possible classifier is 
-compared to a random guess. We intentionally leave the details of 
-$\mathcal{A}$ unrestricted because the theoretical value of $\theta$ should 
-depend on the inherent differences between the populations, rather than on 
-the performance of a particular classifier.
-
-In practice, some particular classifier $\mathcal{C}$ is tested (using e.g. 
-cross-validation) yielding a statistical estimate of its performance 
-$\hat{\theta}_\mathcal{C}$. This
-$\hat{\theta}_\mathcal{C}$ acts as a lower bound for the 
-theoretical value of $\theta$, because there might 
-exist some other classifier $\mathcal{C}'$ with 
-$\hat{\theta}_\mathcal{C'}>\hat{\theta}_\mathcal{C}$.
-For our experiment, we use a Naive Bayes classifier because it is easy to
-implement and performs well across a broad range of classification tasks[***].
-
-To interpret $\hat{\theta}_\mathcal{C}$, imagine that some choice 
-$\mathcal{C}$ is to be made between two options on the basis of worker 
-outputs (e.g. whether or not to flag an image as inappropriate). Any such 
-binary choice has the formal structure of a distinguisher that only considers 
-the last of its three inputs. Thus, we can directly compare $\mathcal{C}$ to 
-the optimal distinguisher, $\mathcal{A}$.  If, prior to knowing the input to 
-$\mathcal{C}$, either of its outcomes is equally likely, then the worst 
-possible bias that priming can introduce is bounded above by $\theta$. 
-This means that $\hat{\theta}_\mathcal{C}$ estimates a 
-lower bound for the worst-case bias introduced in a binary 
-decision that provides a full bit of information, made on the basis of worker 
-outputs, when one failed to control for the corresponding priming treatments.
-\subsection*{Experimental Setup}
-\begin{table}[t]
-\centering
-	\begin{tabular}{ l  l  l }
-		\hline                       
-		Treatment & Funder & Priming Image Set	\\ 
-		\hline                       
-		$\textsc{ambg}$ & None & Ambiguous\\
-		$\textsc{cult}_{img}$ & None & Cultural\\
-		$\textsc{cult}_{fund}$ & Cultural & Cultural\\
-		$\textsc{cult}_{fund,img}$ & Cultural & Cultural\\
-		$\textsc{ingr}_{img}$ & None & Ingredients\\
-		$\textsc{ingr}_{fund}$ & Nutritional & Ingredients\\
-		$\textsc{ingr}_{fund, img}$ & Nutritional & Ingredients\\
-		\hline  
-	\end{tabular}
-
-	\caption{ \footnotesize{ 
-		Workers were uniformly randomly assigned to one of the 
-		treatments listed above. 
-		The full funder names used were 
-		``The Global Foundation for Cultural Recognition'' and 
-		``The National Foundation for Nutritional Awareness''.  
-		The ambiguous, cultural, and ingredients initial image sets are shown 
-		in \textbf{Figs. 2}, \textbf{3}, and \textbf{4}.
-	}}
-	\label{table:1}
-\end{table}
-We solicited 900 AMT workers to perform an image-labeling task relating to
-food and culture.  The workers were randomly assigned to one of seven 
-treatments shown in \textbf{Table 1}.  Depending on their treatment, workers were then shown the 
-name of a research funder, or this step was skipped.
-Next, workers were shown ten images, one at a time and were required to provide
-five labels for each.  For the purpose of analysis, we divide the images
-into \textit{initial} and \textit{final} sets, comprising respectively the 
-first five and last five images.  From the perspective of the worker, there 
-was no distinction or interruption between the initial and final sets. 
-Depending on the treatment, one of three initial image sets was chosen, but
-the final set was always the same.
-
-The final image set, comprised images containing prepared meals and featured a 
-prominent, identifiable culture (see \textbf{Fig. 4}).
-To identify the initial image sets, we use the names ``ambiguous'', 
-``cultural'', and ``ingredients''.  The ambiguous set was chosen to
-be similar to the final image set, in the sense that it consisted of
-images of prepared meals (see \textbf{Fig. 5}),  but its cultural 
-features were less prominent.  The cultural set featured 
-iconic cultural scenes, but no food at all (see \textbf{Fig. 6}).  Images from 
-the ingredients set depicted separated ingredients, but, 
-like the ambiguous set, avoided prominent cultural features (see 
-\textbf{Fig. 7}).
-\subsection*{Results}
-\paragraph{Inter-task priming was strong, while framing was weak.}
-We tested for priming effects using our algorithmic definition, implemented 
-with a Naive Bayes classifier.  The classifier's accuracy
-in cross-validations involving each pair of treatments is shown in 
-\textbf{Fig.1}.
-
-With some exceptions, the classifier performed significantly better 
-than chance when distinguishing treatments that had different initial tasks.  
-This demonstrates that inter-task effects were strong. Of the sixteen 
-treatment pairs having different initial tasks, the classifier was unable to
-distinguish treatments significantly better than chance in three cases.
-Each cases involved distinguishing treatments having the ambiguous and 
-ingredients set.  Later we discuss the similarity between image sets, and 
-we will argue that this is because the ambiguous and ingredients sets are 
-similar.
+\begin{figure*}
+	\includegraphics[scale=1.00]{figs/taskImages/cultural.jpg}
+	\caption*{Figure S3: Cultural image set. These images were presented to workers from 
+		certain treatments (see \textbf{Table 1}) the main text.}
+\end{figure*}
 
 \begin{figure*}
-	\centering{
-		\includegraphics[scale=0.70]{figs/orientation_specificity.pdf}
-	\caption{\footnotesize{
-		\textbf{A}) Percent label composition (culture- vs food-oriented 
-		labels) for 
-		various images and treatments.  
-		\textbf{B}) Relative specificities of treatments
-		indicated along the abscissa compared to those indicated above the 
-		plot.  The size of the bar indicates how much more specific
-		the labels from one treatment are compared to the other, and points 
-		toward in the direction of the more specific treatment.
-	}}
-}
+	\includegraphics[scale=1.00]{figs/taskImages/ingredients.jpg}
+	\caption*{Figure S4: Ingredients image set. These images were presented to workers 
+		from certain treatments (see \textbf{Table 1}) in the main text.}
 \end{figure*}
-In contrast, the classifier never performed significantly better than chance
-when distinguishing treatments that differed only in framing.  Thus, framing 
-effects were rather weak.  In fact, framing effects were generally weak in
-our results, so we omit treatments involving framing from the remainder of
-our presentation to save space.  We encourage the interested reader to look
-at the results for these treatments in the supplementary material.
-\paragraph{Earlier tasks orient workers' focus during later tasks.} 
-Since the initial images were chosen to emphasize either food (ingredients set)
-or culture (cultural set), we looked for effects on the number of culture- and 
-food-oriented labels that workers attributed to the final image set.
 
-To this end, we constructed an ontology from the labels attributed to the 
-test images.  In the ontology, edges point from more general labels to more 
-specific ones.  For example, the ontology contains the path \texttt{food} 
-$\to$ \texttt{ingredients} $\to$ \texttt{vegetables} $\to$ \texttt{tomato}.
-We provide more detail about the construction of the ontology in the 
-\textbf{Materials and Methods} section.
-
-Since food is a central feature 
-of culture, our ontology contains many labels that have both \texttt{food}
-and \texttt{culture} in their ancestry.  Nevertheless, there were many 
-food-oriented labels, such as \texttt{bread}, which lacked specific cultural 
-connections, as well as non-food, culture-oriented labels, such as 
-\texttt{russian dolls}.
-
-\begin{figure}
-	\centering{
-	\includegraphics[scale=0.7]{figs/longitudinal_theta_excess-culture.pdf}
-	\caption{\footnotesize{
-		\textbf{A}) Difference in priming between \textsc{AMBG} and 
-		$\textsc{CULT}_{img}$ measured based on the accuracy of a Naive Bayes 
-		classifier during cross-validation, when trained on labels from the
-		test images indicated along the abscissa.
-		\textbf{B}) Excess cultural orientation of labels attributed to
-		the test images indicated on the abscissa, by workers from
-		$\textsc{CULT}_{img}$ relative to those attributed by workers from
-		\textsc{AMBG}, calculated using \textbf{Eq. 3}.
-	}}
-}
-\end{figure}
-When we tallied labels attributed to the first image of the final set, 
-we found that workers from $\textsc{CULT}_{img}$ produced significantly 
-more culture-oriented labels and less food-oriented ones than those from
-\textsc{AMBG}
-(see \textbf{Fig. 2A}).  The inter-task effect was so strong that the 
-proportion of food- and culture-oriented labels in $\textsc{CULT}_{img}$ was
-essentially the reverse of that in \textsc{AMBG}.  However, the 
-composition of labels attributed by $\textsc{INGR}_{img}$
-was not significantly different from those attributed by \textsc{AMBG}.  This 
-shows that inter-task effects \textit{can} profoundly alter workers' focus. 
-Again, we 
-will argue later that the ambiguous and ingredients image sets are, in fact, 
-quite similar.
-\paragraph{Earlier tasks influenced workers' level of specificity.} 
-Using the ontology described in the previous section, we can compare the 
-specificity of two labels $\ell_1$ and $\ell_2$. We say that $\ell_2$ is more 
-specific than $\ell_1$ if there is a \textit{directed path} from $\ell_1$ to 
-$\ell_2$.  If there is no directed path between labels, we say they are  
-\textit{non-comparable}.  For example, \texttt{tomato} was more specific than 
-\texttt{food}, while \texttt{statue} and \texttt{food} were non-comparable.
-
-We can then define the relative specificity of two workers with respect to 
-test-image $i$ as $s_i(u,v)$:
-
-\begin{align}
-	s_i(u,v) = \sum_{\ell \in u(i) } \;
-	\sum_{m \in v(i)} 
-	\left(\mathbf{1}_{[\ell > m]} - \mathbf{1}_{[m>\ell]}\right),
-	\label{eq:worker-specificity}
-\end{align}
-where $u(i)$ denotes the set of labels attributed by worker $u$ to image $i$, 
-and $\mathbf{1}_{[\ell > m]}$ evaluates to 1 if $\ell$ is more specific than 
-$m$, and 0 otherwise.
-We then define the relative specificity of two treatments, $\mathcal{U}$ and 
-$\mathcal{V}$, the $i$th image, denoted $S_i(\mathcal{U},\mathcal{V})$, to be 
-the mean relative specificity of two uniformly drawn workers:  
-\begin{align}
-	\hat{S}_i(\mathcal{U},\mathcal{V}) = 
-	\frac{1}{|\mathcal{U}| |\mathcal{V}|}
-	\sum_{u \in \mathcal{U}} \;
-	\sum_{v \in \mathcal{V}} \;
-		s_i(u,v).
-		\label{eq:specificity}
-\end{align}
-
-Looking at labels attributed to the first test image, we found that workers 
-from \textsc{AMBG} were more specific than workers from
-either $\textsc{CULT}_{img}$ or $\textsc{INGR}_{img}$.  When we compare 
-$\textsc{CULT}_{img}$ to $\textsc{INGR}_{img}$, we found that workers from
-$\textsc{INGR}_{img}$ were more specific.  This shows that inter-task 
-effects do substantially influence the specificity of labels that workers 
-provide.  When we discuss image simalarity, below, we will explore a possible
-mechanism for this effect.
-\paragraph{Inter-task effects ``wash out'' quickly.}  
-It would stand to reason that, as workers proceed through the test images, 
-priming from the initial images would be ``washed out'', diminishing the 
-observed inter-task effects.
-Looking at the classifier performance, $\hat{\theta}_\text{NB}$, with respect 
-to the treatments \textsc{AMBG} and $\textsc{CULT}_{img}$, we find that 
-performance does drop off dramatically after just the first image 
-(see \textbf{Fig. 3A}).
-This suggests that inter-task effects primarily arise between consecutive 
-tasks, but that a residual effect can persist for at least five tasks (we 
-note, however that although the classifier performance seemed better than 
-chance for the fourth test image, this cannot be asserted with 95\% 
-confidence).
-
-Next we observed how inter-task effects on label composition (i.e. food- vs 
-culture-orientel labels) evolve as workers proceed through test images.
-We define the \textit{excess cultural orientation} as the number of 
-culture-oriented labels minus the number of food oriented ones.  To 
-meaningfully compare the excess cultural orientation between test images, we 
-must, however, account for the fact that some images inherently carry more 
-cultural content than others. In keeping with our notion of priming 
-\textit{difference}, we calculate the excess cultural content for both 
-$\textsc{CULT}_{img}$ and \textsc{AMBG}, and take their difference to be
-the \textit{relative} excess cultural content, $\Delta_{cult}$.  Formally,
-\begin{align}
-	\begin{split}
-	\Delta_{cult}(i) = \frac{1}{N}\left[ \sum_{w\in\textsc{cult}_{img}} \left(N_{w,cult}^{(i)} - N_{w,food}^{(i)}\right)\right. \\
-\left.	- \sum_{w\in\textsc{ambg}} \left(N_{w,cult}^{(i)} - N_{w,food}^{(i)}\right)\right],
-	\end{split}
-\end{align}
-where $N_{w,cult}^{(i)}$ stands for the number of culture-oriented labels 
-attributed by worker $w$ to image $i$, while $N_{w,food}^{(i)}$ similarly 
-counts food-oriented labels, and $N$ is the total number of labels in a 
-treatment.
-
-We found $\Delta_{cult}$ was largest for the first test image, but dropped off 
-rapidly, remaining positive but not to a statistically significant extent
-(see \textbf{Fig. 3B}).  
-This is similar to the behavior of $\hat{\theta}_\text{NB}$, however, because
-the statistical significance of $\Delta_{cult}$ dropped more quickly, 
-$\hat{\theta}_\text{NB}$ appears to be a more sensitive measure of inter-task 
-effects.
-\paragraph{Inter-task similarity encourages more specific labels.}
-To continue with the analysis, we seek a measure of image similarity.  The 
-characterization of image content is a deeply complex issue that has been 
-approached by many disciplines 
-\cite{panofsky1939studies,shatford1986analyzing,Tversky1977327,Jaimes20002}.
-\textit{Perceptual similarity} is a particularly recalcitrant concept[***].
-
-However, in the present study, we are more interested how similar two 
-sets of images are, \textit{with respect to the labeling task}, which is much
-simpler to operationalize than general perceptual similarity.  Here, we 
-measure image similarity by looking at the fraction of labels that they share. 
-Formally, to measure the similarity between two \textit{sets of images}, $X$ 
-and $Y$, we compute the Jacquard index between the sets of labels attributed 
-to them:
-\begin{align}
-	\text{Sim}(X,Y) = \frac{L(X) \cap L(Y)}{L(X) \cup L(Y)},
-\end{align}
-\begin{table}
-\centering
-\begin{tabular}{ l  s s s s}
-
-\toprule    
-Image set   
-& \multicolumn{1}{c}{Ambig.} 
-& \multicolumn{1}{c}{Cultural} 
-& \multicolumn{1}{c}{Ingr.}
-& \multicolumn{1}{c}{Test} \\
-
-\midrule
-
-Ambiguous  & 1 & 0.0418 & 0.142 & 0.167 \\
-
-Cultural  & 0.0418  & 1 & 0.0347 & 0.0561 \\
-
-Ingredients  & 0.142  & 0.0347 & 1 & 0.110 \\
-
-Test & 0.167  & 0.0561 & 0.110 & 1
-\\
-\bottomrule
-
-\end{tabular}
-\caption{\footnotesize{
-	Number of unique labels attributed to each image set, and their
-	similarities based on \textbf{Eq. 4} 
-}}
-\label{table:2}
-\end{table}
-where $L(X)$ denotes the set of labels attributed to $X$.
-
-The pairwise similarities of the image sets are presented in \textbf{Table 2}. 
-First, observe that the ambiguous and ingredients sets are much more similar 
-to each other than either is to the culture set.  Recalling the data presented
-in \textbf{Fig. 1}, this helps explain why two treatments could not be 
-distinguished on the basis of having differing initial sets corresponding to
-ambiguous and cultural.  This also explains why \textsc{ambg} and 
-$\textsc{cult}_{img}$ had similar label compositions in \textbf{Fig. 2A}.
-
-Next we draw attention to the similarity between the initial sets and the test 
-set.  The ambiguous set is the most similar to the test set, followed by the
-ingredients set, with the cultural set being most different.
-Observe that these levels of similarity mirror the label specificity for the 
-corresponding treatments (c.f. \textbf{Fig. 2B}).
-
-This suggests that labeling a series of images that are similar to 
-one another might encourage workers to use more specific terminology.
-Such a phenomenon would be consistent with the psychological mechanism known 
-as \textit{negative priming}.  Negative priming occurs when a person becomes 
-desensitized to non-salient stimuli to which she is repeatedly 
-exposed.  Consider that workers who initially 
-labeled the ambiguous image set had already seen five images showing 
-prepared meals once they labeled the first test image.  At that point,
-a worker might not regard the generic labels \texttt{food} or \texttt{meal} 
-to be salient, and opt instead for \texttt{bread}, or \texttt{pasta}.
-
-We are suggesting that, although workers are not instructed to compare
-images in any way, prior tasks nevertheless create a frame of reference
-relative to which later tasks are judged.  This in turn 
-influences the perception of salience. Thus, in a series of subjective 
-characterization tasks that have very similar content, workers' focus 
-will tend to be directed away from generic, shared attributes, towards those 
-attributes that are specific and distinguishing.
-\subsection*{Discussion}
-\paragraph{Inter-task effects should be considered during task design.}  
-Our results show that inter-task effects can have a strong influence on how
-workers label images.  In particular, we observed that prior tasks influence
-the specificity and content of labels.  Surprisingly, framing a task by 
-indicating a semantically-loaded funder had much milder effects on worker 
-outputs, generally below the statistical power of our tests.
-
-We therefore caution those designing studies using human computation: even if 
-the requester has eliminated surrounding influences to every practical extent, 
-\textit{the greatest source of bias might lurk in the tasks themselves}.
-Due consideration should be given to how tasks are bundled together.
-While our measurements of $\hat{\theta}_\text{NB}$ indicated that inter-task 
-effects persisted even to the fifth test image, the most severe effects arise 
-between consecutive tasks.
-\paragraph{$\theta$ provides a general purpose measure of priming effects.}
-When used three approaches to detecting priming effects: 1) using a Naive Bayes
-classifier to measure $\hat{\theta}_\text{NB}$, 2) tallying the number of 
-culture- and food-oriented labels, and 3) comparing the relative specificity
-of labels based on an ontology.  Of the three, measuring $
-\hat{\theta}_\text{NB}$ was the most sensitive.
-
-In one sense, this is not surprising because the Naive 
-Bayes classifier takes into account the frequency of occurrence of all labels 
-encountered during training.  But it is remarkable that the 
-method which incorporates neither prior knowledge about the image contents nor 
-label semantics, outperforms those that do.  This is a powerful feature 
-because, given the outputs from two sets of workers, one can test whether they 
-have been differently primed without knowing how that priming might manifest.
-
-Our algorithmic definition of priming is phrased in terms of worker outputs
-rather than psychological phenomena.  This provides a connection between
-the priming effects and their potential to impact decisions made on the basis
-of worker outputs.  In the case of a binary decision, $\theta$
-describes the worst-case bias introduced by failing to control for priming 
-effects.
-\paragraph{Batching tasks for better HPU performance.}
-Our proposed connection between similarity and specificity during 
-image-labeling might be used to tune the specificity of labels.  For example,
-If one seeks very nuanced labeling, our results suggest that the images 
-should first be sorted into batches based on their similarity. This could be 
-accomplished by beginning with a first, coarse characterization of unsorted 
-images, followed by batching based on the labels obtained. Then, the batches
-of similar images could be served for a second round of finer labeling. 
-The sorting and re-labeling could then in principle be repeated.
-
-In effect, this creates a hierarchical workflow, where the first, 
-coarsely-characterizing HPUs provide a stream of labeled images that is 
-split (batched) and fed to other HPUs for finer characterization.  This 
-workflow exhibits an interesting difference between HPUs and CPUs.  In general,
-whenever an aspect of a problem can be parallelized when employing CPUs, one
-gains efficiency.  But here, because of HPU hysteresis, we see an example where
-one might sacrifice accuracy through parallelization.
-\subsection*{Conclusion}
-Inter-task priming can have a strong effect.  
-For a canonical image-labeling task, inter-task priming was stronger in its 
-effects on the orientation and specificity of labels than was the disclosure of
-semantically loaded funder names.  Requesters on microtask platforms should 
-take care to avoid introducing biases due to the batching and ordering tasks 
-they serve to workers.  At the same time, inter-task priming might be exploited to improve task output, for 
-example, to drive more (or less) nuanced responses.
-
-We demonstrated that our algorithmic definition of priming, and its 
-implementation using a Naive Bayes classifier, provides a sensitive,
-general-purpose method for detecting priming.  Even when the expected effects 
-on label orientation and specificity were slight, $\theta_\text{NB}$ 
-was significant.  $\theta_\text{NB}$ provides direct statistical evidence that 
-populations have been affected by priming, even when the nature of the 
-effects are not understood. 
-\subsection*{Materials and Methods}
-Omitted due to length.  This will be added to supplementary material.
-\bibliography{newbib.bib} 
-\bibliographystyle{aaai}
 \end{document}
-\subsection*{Motivation}
-I am near the beginning of my PhD studies, and have joined Derek Ruths' lab 
-with the expressed purpose of performing human computation research.
-My interests lay at the intersection of game theory, psychology, and 
-computation.  The overarching goal for my research relates to group 
-decisionmaking, and can be phrased in the following way: ``what are the factors
-that influence the social efficiency of collective decisionmaking?'' I
-view decisionmaking as the central activity of all social organizations, and 
-I view this as a computational process.  My reason for 
-wanting to attend the PhD Consortium at HCOMP is threefold.  First, I wish to
-discuss my ideas with others, get feedback, and learn more about how the 
-community frames such questions, to help me as I finalize my PhD proposal 
-into concrete research aims.  Second, I hope to make connections to other 
-researchers who are interested in similar research questions.  Finally, I wish
-to obtain feedback on a crowdsourcing platform that I have implemented (and
-hopefully pique other researcher's interest), which I intend to use in my
-research.
-\end{document}

### 2014-09-22 docs/publications/2014.09_SCIENCE/man.tex
add spell-checker and start of Science manuscript

% Use only LaTeX2e, calling the article.cls class and 12-point type.

\documentclass[12pt]{article}

% My packages

\usepackage{graphicx}
\usepackage{amsthm}
\newtheorem*{mydef}{Definition}
\usepackage{dcolumn}
\usepackage{multirow}
\usepackage{booktabs}
\newcolumntype{d}{D{.}{.}{4.0}}
\newcolumntype{s}{D{.}{.}{1.4}}

% Users of the {thebibliography} environment or BibTeX should use the
% scicite.sty package, downloadable from *Science* at
% www.sciencemag.org/about/authors/prep/TeX_help/ .
% This package should properly format in-text
% reference calls and reference-list numbers.

\usepackage{scicite}

% Use times if you have the font installed; otherwise, comment out the
% following line.

\usepackage{times}

% The preamble here sets up a lot of new/revised commands and
% environments.  It's annoying, but please do *not* try to strip these
% out into a separate .sty file (which could lead to the loss of some
% information when we convert the file to other formats).  Instead, keep
% them in the preamble of your main LaTeX source file.

% The following parameters seem to provide a reasonable page setup.

\topmargin 0.0cm
\oddsidemargin 0.2cm
\textwidth 16cm 
\textheight 21cm
\footskip 1.0cm

%The next command sets up an environment for the abstract to your paper.

\newenvironment{sciabstract}{%
\begin{quote} \bf}
{\end{quote}}

% If your reference list includes text notes as well as references,
% include the following line; otherwise, comment it out.

\renewcommand\refname{References and Notes}

% The following lines set up an environment for the last note in the
% reference list, which commonly includes acknowledgments of funding,
% help, etc.  It's intended for users of BibTeX or the {thebibliography}
% environment.  Users who are hand-coding their references at the end
% using a list environment such as {enumerate} can simply add another
% item at the end, and it will be numbered automatically.

\newcounter{lastnote}
\newenvironment{scilastnote}{%
\setcounter{lastnote}{\value{enumiv}}%
\addtocounter{lastnote}{+1}%
\begin{list}%
{\arabic{lastnote}.}
{\setlength{\leftmargin}{.22in}}
{\setlength{\labelsep}{.5em}}}
{\end{list}}

% Include your paper's title here

\title{Human computational hysteresis: measuring inter-task effects}

% Place the author information here.  Please hand-code the contact
% information and notecalls; do *not* use \footnote commands.  Let the
% author contact information appear immediately below the author names
% as shown.  We would also prefer that you don't change the type-size
% settings shown here.

\author
{John Smith,$^{1\ast}$ Jane Doe,$^{1}$ Joe Scientist$^{2}$\\
\\
\normalsize{$^{1}$Department of Chemistry, University of Wherever,}\\
\normalsize{An Unknown Address, Wherever, ST 00000, USA}\\
\normalsize{$^{2}$Another Unknown Address, Palookaville, ST 99999, USA}\\
\\
\normalsize{$^\ast$To whom correspondence should be addressed; E-mail:  jsmith@wherever.edu.}
}

% Include the date command, but leave its argument blank.

\date{}

%%%%%%%%%%%%%%%%% END OF PREAMBLE %%%%%%%%%%%%%%%%

\begin{document}

% Double-space the manuscript.

\baselineskip24pt

% Make the title.

\maketitle

% Place your abstract within the special {sciabstract} environment.

\begin{sciabstract}
Microtask platforms offer a fast, flexble, and inexpensive source of labour for
clerical tasks \cite{Finnerty2013, chandler2013breaking, Berinsky2012351} and 
recently have been adopted by researchers to augment datasets and solicit 
participants \cite{paolacci2010running, Berinsky2012351, chandler2013breaking}.
Some computer scientists describe such platforms as a new computing 
architecture, and seek to characterize “human co-processing units” (HPUs) in 
analogy to CPUs and GPUs \cite{5543192}. However, it is known that people are 
susceptible to 
priming effects\cite{No2007,Swaab200299,Gopher2000308,sohn2001task,Ghuman17062008,BJOP1796,BJOP1826,Gass1999549}, which stands to complicate the HPU 
perspective.  Here, we introduce a framework to recast this psychological 
phenomenon as a kind of computational hysteresis. 
We apply this framework to study \textit{inter-task effects} that arise when 
microtask 
workers perform a sequence of tasks. Surprisingly, earlier tasks can have a 
very strong influence on workers during later tasks---stronger than overtly
framing the tasks as serving different research goals.   
This result has major implications for the design of crowdsourcing initiatives.
The framework we introduce provides a general measure of priming severity, 
and, in combination with machine learning tools, enables measurement without
knowing ahead of time how priming will affect output.
\end{sciabstract}

\section*{Introduction}
Microtask crowdsourcing platforms like Amazon Mechanical Turk (MTurk) make it 
possible to submit batches of small tasks to a large pool of human workers, 
who do the tasks for fun, a sense of purpose, and remuneration 
\cite{kazai2013analysis,Antin20122925}.  
Originally used to distribute clerical work, these platforms 
increasingly serve as a fast and cheap means to engage experimental 
participants in a research 
setting \cite{paolacci2010running,Berinsky2012351,snow2008cheap,alonso2009can}.
Typical tasks include flagging inapropriate images, annotiting sentiment in 
text excerpts, or judging the relevancy of search results.

The task requester can interact with the platform like a compute server, 
seamlessly 
integrating human and machine computation.  Researchers have put forward the 
term HPU (Human co-Processing Unit), viewing the introduction of 
microtask platforms as a new computing architecture
\cite{5543192}.

Here, we highlight an important way in which HPUs differ from CPUs, with 
serious implications for the design of tasks.  It is well known that people 
are subject to priming effects 
\cite{BJOP1796,No2007,beller1971priming} and, in particular, task-repetition effects
\cite{Gass1999549,sohn2001task}.  
We investigate the effect that previously completed tasks have on workers'
responses during subsequent ones. We call such effects 
\textit{inter-task priming}.  Inter-task priming would amount to a kind of
\textit{hysteresis}, meaning that HPU output is not only a function of the 
current input, but also of the history of inputs.

There has been considerable investigation into the factors that affect the 
quality and nature of microtask work.  These include the level of 
pay \cite{kazai2013analysis}, training \cite{le2010ensuring}, pre-screening of 
workers \cite{paolacci2010running}, and user-interface design 
\cite{Finnerty2013}.  Research has also investigated \textit{framing}, 
by testing the effects of describing the workflow context 
\cite{Kinnaird2012281}, the purpose of tasks 
\cite{chandler2013breaking}, or using an alternative problem discription
\cite{thibodeau2013natural}.  To our knowledge, no study has investigated the 
effects of inter-task effects in microtask work.

To characterize inter-task effects, we present a novel, generalized definition 
of \textit{HPU priming}. Although priming is traditionally used to elucidate 
internal 
psychological mechanisms, our definition characterizes a computational 
property of the HPU, and corresponds to the worst-case bias introduced into an 
algorithm ``running'' on primed HPUs. This definition enables a direct, 
quantititive comparison of HPU priming effects accross domains and 
applications, while offering a practical, intuitive interpretation. We 
demonstrate that machine learning tools can be used to detect priming, an 
approach that could be used to detect priming effects without knowing in 
advance what the nature of the effects might be, nor how priming was imposed.

In the present work, we investigate inter-task priming on the Amazon 
Mechanical Turk platform, using an image-labeling task, one of the most common 
kinds of tasks on that platform 
\cite{chandler2013breaking,Berinsky2012351,Finnerty2013,paolacci2010running}.  
The task requires workers to label images featuring food, table-settings, and 
related utensils and cookware. We divide the set of images shown to a worker 
into an \textit{initial} and \textit{test} set, but, crucially, there was no 
distinction made between these sets, nor any interruption in the flow of tasks 
from the view of the worker. We varied the initial set of images, while 
keeping the test set the same, to analyze the effect that that the initial 
images have on the labels that workers attribute to the test set.

As a point of comparison, we conduct a similar experiment where we induce 
\textit{framing}. Before the workers label images, we indicate that the work 
was funded by a research lab having a particular area of interest, to see the 
influence this has on the workers’ subsequent labels. In both experiments, we 
measure effects using our novel approach, as well as looking for changes in 
the content of labels and label specificity based on an ontology we developed 
for that purpose.

Surprisingly, we found that inter-task effects are much stronger than framing. 
Our results show that initial tasks can significantly alter the focus of 
worker's labels. We also found that inter-task effects can induce workers to 
provide labels of greater specificity. This suggests that careful consideration
should be given to the bundling of tasks when designing a study using a
microtask platform.

Our analysis also highlights important advantages of our novel definition of 
priming.  Our approach incorporates no prior knowledge about the nature
of the task whatsoever.  In contrast, we also sought to detect priming
based on its direct effects on label content and specificity,
drawing on prior knowledge about the images and label semantics.
Remarkably, while being more general, our definition yields a more sensitive
measure of priming when combined with machine learning algorithms. 
This approach could be applied to detect priming when one does not 
\emph{a priori} know whether any priming has occurred, 
nor what the nature of the effects might be.

\paragraph*{Priming as computational hysteresis.}
In psychology, priming effects are studied because they hint at the 
psychological mechanisms at play during certain cognitive tasks. But in the 
context of human computation, the focus should be on the outward consequences: 
the potential for algorithms to execute differently when ``run'' on differently
primed HPUs.

We will present three definitions of priming with this practical concern in 
mind, and then describe how to measure priming in practice. To proceed with 
the definitions, we will assume that two populations of HPU’s, $\mathcal{P}$ 
and $\mathcal{Q}$ were 
sampled randomly from the same initial population $\mathcal{R}$, and then were 
exposed to (possibly) different priming treatments. The HPUs in $\mathcal{P}$ 
and $\mathcal{Q}$ perform some 
task, leading to popualtions of work-products, $P$ and $Q$.

For the first defenition, let us address the concern that differently primed 
HPUs may produce ``biased'' work-products.

\begin{mydef}
	{\upshape Maximum Bias $\theta_\mathrm{bias}$:}
	Let $\mathcal{D}$ be a binary decision algorithm, which takes a 
	work-product
	$r \in P \cup Q$ as input, and outputs a bit $\mathcal{D}(r)=b$, where 
	$b \in \{0,1\}$. Denote the \emph{bias} of $\mathcal{D}$, due to the
	different priming of $\mathcal{P}$ and $\mathcal{Q}$ by
	$\theta^\mathcal{D}_\mathrm{bias}(P,Q)$ and define it to be the difference 
	in the expected output of $\mathcal{D}$ when acting on work-products from 
	$P$ vs $Q$:
	$$
	\theta^\mathcal{D}_\mathrm{bias}(P,Q) = 
		\left| 
			\mathrm{E}\left\{ \mathcal{D}(p) \right\} 
			- \mathrm{E}\left\{ \mathcal{D}(q) \right\} 
		\right|,
	$$
	where $p \in P$, $q \in Q$.  Then, define the difference in priming 
	between $P$ and $Q$ to be the worst-case bias, i.e. the bias of the most
	susceptible decision:
	$$
	\theta_\mathrm{bias} = 
		\sup_\mathcal{D} \theta^\mathcal{D}_\mathrm{bias}(P,Q)
	$$
\end{mydef}

Thus, $\theta_\mathrm{bias}$ has a straightforward interpretation as an upper 
bound on the amount of bias induced on any yes-or-no decision, due to the 
difference in priming of $\mathcal{P}$ and $\mathcal{Q}$.

For the next definition, we attempt to address directly the extent to which 
two populations of work-products are ``different'', by supposing that they are 
different to the extent that they can be distinguished algorithmically. To 
facilitate this definition, we make use of the notions of a 
\textit{distinguisher} and a \textit{validation} test.

\begin{mydef}
	{\upshape Algorithmic distinctness $\theta_\mathrm{dist}$:}
	Let $\mathcal{D}$ be a distinguisher algorithm, which takes work-product 
	$r \in P \cup Q$ as input, and outputs a \emph{guess} 
	$\mathcal{D}(r) \in \{0, 1\}$. Now define a validation test 
	$V(\mathcal{D}, R_0, R_1)$ as follows. A bit is drawn uniformly at random, 
	$b \in_R \{0, 1\}$, and then a work-product $r$ is chosen uniformly at 
	random from one of the populations, decided by the bit: $r \in_R R_b$. 
	Feed $r$ to $\mathcal{D}$, and if $\mathcal{D}(r) = b$, we say 
	$\mathcal{D}$ guessed correctly, and the value of $V$ is 1, 
	otherwise V = 0.

	A distinguisher that guesses randomly will still be correct half of the 
	time. Therefore, denote the performance of $\mathcal{D}$ as 
	$\eta_\mathcal{D}(P, Q)$, and define:
	$$ 
		\theta_\mathrm{dist} = \sup_\mathcal{D} \eta_\mathcal{D}(P,Q)
	$$

\end{mydef}
In the above definition, the performance simply rescales accuracy, so that when
accuracy is 1/2 (i.e. as good as chance) performance is 0, and when accuracy 
is perfect, performance is 1. This definition casts the measurement of priming 
effects in terms of a binary classification problem, which is well-studied in 
the field of machine learning.

The two definitions we have already mentioned are, in fact, equivalent, and 
correspond to a third, more fundamental formulation known as the total 
\textit{variational distance}, or $l_1$-distance, or simply the “statistical 
distance” ($D_{l_1}$):
$$
	D_{l_1}(P,Q) \equiv \frac{1}{2} \sum_{x \in \mathcal{X}} 
	\left| 
		f_P(x) - f_Q(x)
	\right|,
$$
where $f_P(x)$ denotes the probability of observing x when sampling from P. 
This leads us to our third definition:

\begin{mydef}
	{\upshape Priming as $l_1$-distance:}
	The difference in priming of $\mathcal{P}$ and $\mathcal{Q}$ is the 
	$l_1$-distance between the distributions of their work-products, 
	$D_{l_1}(P,Q)$.
\end{mydef}

We provide proofs of the equivalence between these definitions in the 
supplementary material. Despite their equivalence, we show the three 
definitions because they offer different theoretical, practical, and 
interpretive entry points. Definition 1 provides a practical motivation, and 
the straighforward interpretation of priming as bias. Definition 3 draws a 
clear link to existing statistical theory. And Definition 2 introduces machine 
learning tools, which allow us to gain traction when the purely statistical 
tools fail.

\paragraph{Measuring priming.}
Care must be taken in estimating $D_{l_1}$ from samples so as not to obtain
an inflated estimate. In the so-called naive approach, one uses the frequency 
with which a given work-product $x$ is obtained from HPUs in $\mathcal{P}$ to 
estimate the probability mass function at $x$; 
$\hat{f}_P(x) = (\sum_{X\in P} \mathbf{1}_{[X=x]})/|P|$.
One can then estimate 
$D_{l_1} = \sum_{x \in \mathcal{X}} \left|\hat{f}_P(x) - \hat{f}_Q(x) \right|/2$ using only the sample frequencies. But the number of samples, $|P|$ and 
$|Q|$, must be much larger than the number of possible work-outputs, 
$|\mathcal{X}|$, otherwise, this method produces an enormously inflated 
estimate.

Recently, attempts have been made to provide better estimators. Valiant, 
provides a canonical estimation approach based on first estimating the unseen 
region of the support. This algorithm appears to perform very well in practice.
Batu provided an alternative approach, which bypasses estimating the 
probability mass functions, and relies on the more fundamental concept of 
\textit{collisions}.

Both methods converge much more quickly than the naive approach. However, two 
limitations remain that prevent their application. First, these relatively 
recent approaches are not accompanied by any absolute guarantees of 
statistical confidence, so it is not yet clear how to build confidence 
intervals for a given estimate. Second, sophisticated as these methods are, 
they still cannot provide reliable estimates when none of the elements of the 
support recur in the samples (that is, when we never observe the same 
work-product twice in our sample sets).

It may seem unreasonable to hope to measure $D_{l_1}$ when our samples are so 
megre that no specific work-product recurrs, but this level of sparsity is 
routinely faced in classification tasks. As a concrete example, a facial 
recognition 
system (which classifies images as face or non- face) is expected to work on 
images that have never been seen before, and its design cannot be predicated on
covering a significant fraction of all possible images during training. In our 
experiment, we demonstrate that the quintessential microtask, image labeling, 
is one for which the measurement of priming effects can be approached using 
classifiers.

\paragraph{Experimental setup.}
We solicited 2300 MTurk workers to perform an image-labeling task using images 
that depicted meals, place-settings, and related items such as dishes, and 
kitchenware, and other artifacts naturally arising in dining contexts. Workers 
were randomly assigned into one of four treatments, described below. In all 
treatments, workers were given brief instruc- tions before labeling any images.
In some treatments, workers were then also shown a \textit{framing slide}, 
indicating 
the tasks were funded by a group having a particular research focus. The tasks 
consisted of single images, and workers were asked to provide five descriptive 
labels for each. The last five images that workers labeled, the 
\textit{test set}, were the same for all treatments.

The first two treatments, IMG:OBJ and IMG:FOOD, tested inter-task effects. 
Workers in these treatments labelled ten images. In the IMG:OBJ treatment, the 
\textit{initial set} of five images labeled by workers contained objects such 
as utensils, kitchenware, and table-settings, but no food items. In the 
\textsc{img:food}, the initial set contained centered close-ups of meals, 
without
any surrounding objects (except sometimes the dish supporting the food). No 
interruption or distinction made between the initial and test sets from the 
view of the workers. To study the positional dependance of inter-task effects,
these treatments were subdivided, and workers were shown one of five 
permutations. There are of course 5! = 120 permutations of five images, but 
investigating all permutations was too expensive, and probably redundant, so 
we chose 5 permutations that ensure each image occupies each position within 
the test set. We discuss the benefits and drawbacks of this choice in the 
supplementary material.

Workers in the treatments \textsc{frm:food} and \textsc{frm:obj} were shown a 
framing slide, which bore a message reading: ``Funded by the laboratory for 
the visual perception of \{Food and Ingredients $\vert$ Objects and Tools\}''. 
After the framing slide, workers in these treatments proceeded directly to 
the test set (and so labeled only 5 images).

\paragraph{The strength of inter-task effects}
We tested for inter-task effects by training a Naive Bayes classifier to 
classify work-products among IMG:OBJ and IMG:FOOD, using only the labels 
attributed to the test set of images. Based on Definition 2, no classifier 
can perform better than the actual difference in priming, so the performance 
of Naive Bayes classifier provides a lower bound on priming difference. We 
used leave-one-out validation to estimate the classifier per- formance. We 
tested for framing effects in a similar way, by training a Naive Bayes 
classifier to classify work-products among \textsc{frm:food} and 
\textsc{frm:obj}.

Overall, the first image in the test set showed the strongest signal for 
priming effects. Fig. 3 shows the empirical lower bound for difference in 
priming due to inter-task effects and framing based on the classifier 
performance when using labels from the first test image. Statistically 
significant levels of priming were detected for both modalities, but the 
inter-task effects were stronger (hypothesis test). This suggests that strong 
bias can result solely from the sequence of tasks performed by a worker, even 
when those tasks are of the same type.

In contrast, the classifier never performed significantly better than chance 
when distinguish- ing treatments that differed only in framing. Thus, framing 
effects were rather weak. In fact, framing effects were generally weak in our 
results, so we omit treatments involving framing from the remainder of our 
presentation to save space. We encourage the interested reader to look at the 
results for these treatments in the supplementary material.

\paragraph{Inter-task effects and the orientation of focus.}
Since the initial images were chosen to emphasize either food (ingredients 
set) or culture (cultural set), we looked for effects on the number of 
culture- and food-oriented labels that workers attributed to the test image 
set.

To this end, we constructed an ontology from the labels attributed to the test 
images. In the ontology, edges point from more general labels to more 
specific ones. For example, the ontology contains the path \texttt{food} $\to$ 
\texttt{ingredients} $\to$ \texttt{vegetables} $\to$ \texttt{tomato}.

Since food is a central feature of culture, our ontology contains many labels 
that have both food and culture in their ancestry. Nevertheless, there were 
many food-oriented labels, such as bread, which lacked specific cultural 
connections, as well as non-food, culture- orientedlabels,suchasrussian dolls.

When we tallied labels attributed to the first image of the test set, we found 
that workers from CULTimg produced significantly more culture-oriented labels 
and less food-oriented ones than those from AMBG (see Fig. 2A). The inter-task 
effect was so strong that the proportion of food- and culture-oriented labels 
in CULTimg was essentially the reverse of that in AMBG. However, the 
composition of labels attributed by INGRimg was not significantly different 
from those attributed by AMBG. This shows that inter-task effects can 
profoundly alter workers' focus. Again, we will argue later that the ambiguous 
and ingredients image sets are, in fact, quite similar.

\paragraph{Inter-task effects and specificity.}
Using the ontology described in the previous section, we can compare the 
specificity of two labels $\ell_1$ and $\ell_2$. We say that $\ell_2$ is more specific 
than $\ell_1$ if there is a directed path from $\ell_1$ to $\ell_2$. If there is no 
directed path between labels, we say they are \textit{non-comparable}. For 
example, \texttt{tomato} was more specific than \texttt{food}, while 
\texttt{statue} and \texttt{food} were non-comparable.

We can then define the relative specificity of two workers with respect to 
test-image $i$ as $s_i(u, v)$:
$$
	s_i(u,v) = \sum_{\ell \in u(i)} \sum_{\ell \in v(i)} 
	\left( \mathbf{1}_{[\ell > m]} - \mathbf{1}_{[m>\ell]} \right),
$$
where $u(i)$ denotes the set of labels attributed by worker $u$ to image $i$, 
and $\mathbf{1}_{[l>m]}$ evaluates to 1 if $\ell$ is more specific than $m$, 
and 0 otherwise. We then define the relative specificity of two treatments, 
$U$ and $V$, relative to the $i$th image, denoted $S_i(U,V)$, to be the mean 
relative specificity of two uniformly drawn workers:
$$
	\hat{S}_i(U,V) = \frac{1}{|U \times V|} \sum_{u \in U} \sum_{v in V}
		s_i(u,v).
$$
Looking at labels attributed to the first test image, we found that workers 
from \textsc{ambg} were more specific than workers from either 
$\textsc{CULT}_{img}$ or $\textsc{ingr}_{img}$.  When we compare CULTimg to 
INGRimg, we found that workers from INGRimg were more specific. This shows 
that inter-task effects do substantially influence the specificity of labels 
that workers provide. When we discuss image similarity, below, we will explore 
a possible mechanism for this effect.

\paragraph{The role of task position in inter-task effects.}
It would stand to reason that, as workers proceed through the test images, 
priming from the initial images would be ``washed out'', diminishing the 
observed
inter-task effects. Looking at the classifier performance, 
$\hat{\theta}_\mathrm{NB}$, with respect to the treatments AMBG and CULTimg, 
we find that performance does drop off dramatically after just the first image 
(see Fig. 3A). This suggests that inter-task effects primarily arise between 
consecutive tasks, but that a residual effect can persist for at least five 
tasks (we note, however that although the classifier performance seemed better 
than chance for the fourth test image, this cannot be asserted with 95\% 
confidence).

Next we observed how inter-task effects on label composition (i.e. food- vs 
culture-oriented labels) evolve as workers proceed through test images. We 
define the excess cultural orientation as the number of culture-oriented 
labels minus the number of food oriented ones. To meaning- fully compare the 
excess cultural orientation between test images, we must, however, account 
for the fact that some images inherently carry more cultural content than 
others. In keeping with our notion of priming difference, we calculate the 
excess cultural content for both CULTimg and

AMBG, and take their difference to be the relative excess cultural content, 
$\Delta_{cult}$. Formally,

		*** Formula for delta cult\ldots

where $N^(i)_{w,cult}$ stands for the number of culture-oriented labels 
attributed by worker w to image i, while $N^(i)_{w,food}$ similarly counts
food-oriented labels, and $N$ is the total number of labels in a treatment.

We found $\Delta_{cult}$ was largest for the first test image, but dropped off 
rapidly, 
remaining positive but not to a statistically significant extent (see Fig. 3B).
This is similar to the behavior of $\hat{\theta}_\mathrm{NB}$, however, 
because the statistical significance of $\Delta_{cult}$ dropped more quickly, 
$\hat{\theta}_\mathrm{NB}$ appears to be a more sensitive measure of 
inter-task effects.

\paragraph{Leveraging inter-task effects for detailed responses.}
\begin{table}
\centering
\begin{tabular}{ l  s s s s}

\toprule    
Image set   
& \multicolumn{1}{c}{Ambig.} 
& \multicolumn{1}{c}{Cultural} 
& \multicolumn{1}{c}{Ingr.}
& \multicolumn{1}{c}{Test} \\

\midrule

Ambiguous  & 1 & 0.0418 & 0.142 & 0.167 \\

Cultural  & 0.0418  & 1 & 0.0347 & 0.0561 \\

Ingredients  & 0.142  & 0.0347 & 1 & 0.110 \\

Test & 0.167  & 0.0561 & 0.110 & 1
\\
\bottomrule

\end{tabular}
\caption{\footnotesize{
Pairwise similarities of each image set based on the labels attributed to them (see \textbf{Eq. 4}).
}}
\label{table:2}
\end{table}

To continue with the analysis, we seek a measure of image similarity. The 
characterization of image content is a deeply complex issue that has been 
approached by many disciplines \cite{panofsky1939studies,shatford1986analyzing,Tversky1977327,Jaimes20002}. \textit{Perceptual similarity} is a 
particularly recalcitrant concept.

However, in the present study, we are more interested how similar two sets of 
images are, with respect to the labeling task, which is much simpler to 
operationalize than general percep- tual similarity. Here, we measure image 
similarity by looking at the fraction of labels that they share. Formally, to 
measure the similarity between two sets of images, X and Y , we compute the 
Jacquard index between the sets of labels attributed to them:
$$
	\mathrm{Sim}(X,Y) = \frac{L(X) \cap L(Y)}{L(X) \cup L(Y)}
$$
where $L(X)$ denotes the set of labels attributed to $X$.

The pairwise similarities of the image sets are presented in Table 2. First, 
observe that the ambiguous and ingredients sets are much more similar to each 
other than either is to the culture set. Recalling the data presented in 
Fig. 1, this helps explain why two treatments could not be distinguished on 
the basis of having differing initial sets corresponding to ambiguous and 
cultural. This also explains why AMBG and CULTimg had similar label 
compositions in Fig. 2A.

Next we draw attention to the similarity between the initial sets and the test 
set. The am- biguous set is the most similar to the test set, followed by the 
ingredients set, with the cultural set being most different. Observe that these
levels of similarity mirror the label specificity for the corresponding 
treatments (c.f. Fig. 2B).

This suggests that labeling a series of images that are similar to one another 
might encourage workers to use more specific terminology. Such a phenomenon 
would be consistent with the psychological mechanism known as 
\textit{negative priming}.
Negative priming occurs when a person becomes desensitized to non-salient 
stimuli to which she is repeatedly exposed. Consider that workers who 
initially labeled the ambiguous image set had already seen five images 
showing prepared meals once they labeled the first test image. At that point, 
a worker might not regard the generic labels \texttt{food} or \texttt{meal} to 
be salient, and opt instead for \texttt{bread}, or \texttt{pasta}.

We are suggesting that, although workers are not instructed to compare images 
in any way, prior tasks nevertheless create a frame of reference relative to 
which later tasks are judged. This in turn influences the perception of 
salience. Thus, in a series of subjective characterization tasks that have 
very similar content, workers' focus will tend to be directed away from 
generic, shared attributes, towards those attributes that are specific and 
distinguishing.

\paragraph{Conclusions.}
Our results show that inter-task effects can have a strong influence on how 
workers label images. In particular, we observed that prior tasks influence 
the specificity and content of labels. Surprisingly, framing a task by 
indicating a semantically-loaded funder had much milder effects on worker 
outputs, generally below the statistical power of our tests.

We therefore caution those designing studies using human computation: even if 
the requester has eliminated surrounding influences to every practical extent, 
\textit{the greatest source of bias might lurk in the tasks themselves}. Due 
consideration should be given to how tasks are bundled together. While our 
measurements of $\hat{\theta}_\mathrm{NB}$ indicated that inter-task effects 
persisted even to the fifth test image, the most severe effects arise between 
consecutive tasks.

Our proposed priming definition yields general purpose measure of priming 
effects. We used three approaches to detect priming effects: 1) using a Naive 
Bayes classifier to measure $\hat{\theta}_\mathrm{NB}$, 2) tallying the 
number of culture- and food-oriented labels, and 3) comparing the relative
specificity of labels based on an ontology. Of the three, $\theta_\mathrm{NB}$ 
was the most sensitive.

In one sense, this is not surprising because the Naive Bayes classifier takes 
into account the frequency of occurrence of all labels encountered during 
training. But it is remarkable that the method which incorporates neither 
prior knowledge about the image contents nor label semantics, outperforms 
those that do. This is a powerful feature because, given the outputs from two 
sets of workers, one can test whether they have been differently primed 
without knowing how that priming might manifest.

Our algorithmic definition of priming is phrased in terms of worker outputs 
rather than psychological phenomena. This provides a connection between the 
priming effects and their potential to impact decisions made on the basis of 
worker outputs. In the case of a 1-bit binary decision, $\theta$ describes the 
worst-case bias introduced by failing to control for priming effects.

Batching similar tasks together appears to yield higher more specific HPU 
outputs. Our proposed connection between similarity and specificity during 
image-labeling might be used to tune the specificity of labels. For example, 
If one seeks very nuanced labeling, our results suggest that the images 
should first be sorted into batches based on their similarity. This could be 
accomplished by beginning with a first, coarse labeling of unsorted images, 
followed by bundling based on the similarity of coarse labels. Then, bundles 
of similar images could be served for a second round of finer labeling. The 
sorting and re-labeling could in principle be repeated.

Such a workflow involves serial processing, which points to an interesting 
possible differ- ence difference between HPUs and CPUs. In general, whenever 
an aspect of a problem can be parallelized when employing CPUs, one gains 
efficiency. But here, because of HPU hysteresis, one might gain precision by 
using HPUs with a more serialized algorithm. Further testing is needed to 
determine the gain in precision from this approach.

\bibliography{newbib}
\bibliographystyle{Science}

\end{document}

### 2014-09-22 src/runnable_analysis.py

@@ -2,12 +2,18 @@ from collections import defaultdict
 import data_processing as dp
 import naive_bayes as nb
 
+
 def calc_priming_differences():
 	OLD_DATASET = False
 	NEW_DATASET = True
 	NUM_FOLDS = 125
 	NUM_IMAGES = 5
 
+	# this provides a mapping that shows which treatment should be used to
+	# find a given image at a given position.  The image is the key, and 
+	# the positions are the array index.  Example: the image 'test0' was in
+	# position 0 for treatment 0, in position 1 for treatment 4, in position
+	# 3 for treatment 3 etc. (this is reading off the first line).
 	treatment_offsets = {
 			'test0': [0,4,3,2,1],
 			'test1': [1,0,4,3,2],

### 2014-09-22 src/wordnet_analysis.py

@@ -5,6 +5,135 @@ import re
 
 SPLIT_RE = re.compile('[^-a-zA-Z]')
 
+
+
+def filter_misspelled(labels):
+	words = set(reduce(lambda x,y: x + y.split(), labels, []))
+	misspelled = filter(lambda x: len(wn.synsets(x)) == 0, words)
+	return misspelled
+	
+
+def find_misspelled_words(dataset):
+
+	misspelled = {}
+	for image in ['test%d' % i for i in range(dataset.NUM_IMAGES)]:
+		words = dataset.get_counts_for_treatment_image(None, image).keys()
+		misspelled[image] = filter_misspelled(words)
+
+	return misspelled
+
+
+class WordnetSpellChecker(object):
+
+	ALPH = 'abcdefghijklmnopqrstuvwxyz_'
+	W = re.compile(r'[^a-z ]')
+
+	def __init__(self):
+		pass
+
+	def is_ok(self, word):
+		return bool(len(wn.synsets(word))>0)
+
+
+	def get_neighbors(self, word):
+
+		w = word
+
+		splits = [(w[:i], w[i:]) for i in range(len(w) + 1)]
+
+		deletes = [a + b[1:] for a,b in splits if b]
+		transposes = [a + b[1] + b[0] + b[2:] for a,b in splits if len(b)>1]
+		replaces = [a + c + b[1:] 
+			for a,b in splits for c in self.ALPH if b]
+		inserts = [a + c + b for a,b in splits for c in self.ALPH]
+
+		# if there are non-word characters, try replacing with spaces
+		if self.W.search(w):
+			separations = [self.W.sub(' ', w)]
+
+		# otherwise try inserting spaces in all possible positions
+		else:
+			separations = [a + ' ' + b for a,b in splits]
+
+		return set(deletes + transposes + replaces + inserts + separations)
+
+
+	def auto_correct(self, corpus):
+
+		# First, we read all of the words.
+		# Sort out the ones that are misspelled.  Among the ones that 
+		# are correctly spelled, accumulate the frequencies of occurence
+		# to guide the spell checker
+
+		frequencies = Counter()
+		misspelled = set()
+
+		for phrase in corpus:
+			for word in phrase.split():
+
+				if self.is_ok(word):
+					frequencies[word] += 1
+
+				else:
+					misspelled.add(word)
+
+		print 'found %d misspelled words...' % len(misspelled)
+
+		# Now try to correct the spellings
+		corrections = {}
[…]

### 2014-09-23 docs/publications/2014.09_SCIENCE/man.tex
backup work on manuscript

@@
 Microtask crowdsourcing platforms like Amazon Mechanical Turk (MTurk) make it 
-possible to submit batches of small tasks to a large pool of human workers, 
-who do the tasks for fun, a sense of purpose, and remuneration 
+possible for requesters to submit batches of small tasks to a large pool of 
+workers, who do the tasks for fun, a sense of purpose, and remuneration 
 \cite{kazai2013analysis,Antin20122925}.  
 Originally used to distribute clerical work, these platforms 
-increasingly serve as a fast and cheap means to engage experimental 
+increasingly serve as a means to engage experimental 
 participants in a research 
 setting \cite{paolacci2010running,Berinsky2012351,snow2008cheap,alonso2009can}.
-Typical tasks include flagging inapropriate images, annotiting sentiment in 
-text excerpts, or judging the relevancy of search results.
+Typical tasks include tagging and categorizing images 
+\cite{6116320,Zhai2012357}, transcribing voice recordings 
+\cite{chandler2013breaking,paolacci2010running}
+or handwritten notes \cite{Berinsky2012351,Finnerty2013}, and judging the 
+relevancy of search results \cite{le2010ensuring,grady2010crowdsourcing,alonso2009can,kazai2013analysis}
 
@@
 seamlessly 
-integrating human and machine computation.  Researchers have put forward the 
-term HPU (Human co-Processing Unit), viewing the introduction of 
-microtask platforms as a new computing architecture
-\cite{5543192}.
+integrating human and machine computation.  Researchers coined the 
+term HPU (Human co-Processing Unit), viewing the introduction 
+of microtask platforms as a new computing architecture\cite{5543192}.  
+Attempts have been made to formalize the HPU instruction set, and libraries 
+that provide high-level APIs (Application Programming Interfaces) for writing 
+algorithms involving human computation have been developed \cite{little2010turkit,minder2011crowdlang,minder2012crowdlang,kittur2011crowdforge}.
 
 Here, we highlight an important way in which HPUs differ from CPUs, with 
-serious implications for the design of tasks.  It is well known that people 
-are subject to priming effects 
-\cite{BJOP1796,No2007,beller1971priming} and, in particular, task-repetition effects
-\cite{Gass1999549,sohn2001task}.  
-We investigate the effect that previously completed tasks have on workers'
-responses during subsequent ones. We call such effects 
-\textit{inter-task priming}.  Inter-task priming would amount to a kind of
-\textit{hysteresis}, meaning that HPU output is not only a function of the 
-current input, but also of the history of inputs.
+serious implications for any crowdsourcing initiative.  Common sense would 
+dictate that people's output during a task will be stochastic: when the same
+task is given to different people, or given to the same person at different 
+times,
+the outputs may, in general, differ.  Stochasticity is not itself problematic,
+since the analysis of probabilistic algorithms is fairly 
+well-understood. But other non-random effects may also bear on HPU output. 
+It is known that people are susceptible to priming effects 
+\cite{BJOP1796,No2007,beller1971priming}, and, in particular, task-repetition 
+effects \cite{Gass1999549,sohn2001task}.
+
+Such repetition effects, or
+\textit{inter-task effects}, are neither random, nor are they formally part 
+of the instructions given to the HPU.  The ``leakage'' of information from 
+recently performed tasks into HPU outputs is a potentially strong source of 
+systematic bias, which complicates the the algorithmic view of HPUs. 
+Inter-task effects would amount to a kind of \textit{hysteresis}, meaning 
+that HPU output is not only a function of the current input, but also of the 
+history of inputs.
+
+Here we make two contributions towards understanding inter-task effects
+and HPU hysteresis in general.  We present a framework for treating this 
+source of bias in the context of HPU algorithms, and we measure the impact of
+inter-task effects experimentally in a canonical HPU task: the labeling of 
+images.
+
+Using the  Amazon Mechanical Turk (Mturk) platform, we solicited workers to 
+perform a series of image-labeling tasks.  
+In these tasks, workers labeled images featuring iconic cultural scenes,
+food, table-settings, and various utensils and cookware. We divided the set of 
+images shown to a given worker into an \textit{initial} and \textit{test} set, 
+but, crucially, there was no apparent distinction between these sets from the
+perspective of the worker.  We varied the initial set of images, while 
+keeping the test set the same, to analyze the effect that that the initial 
+images had on the labels that workers attributed to the test set.
 
 There has been considerable investigation into the factors that affect the 
-quality and nature of microtask work.  These include the level of 
+quality and nature of microtask work.  These include such factors as the 
+level of 
 pay \cite{kazai2013analysis}, training \cite{le2010ensuring}, pre-screening of 
 workers \cite{paolacci2010running}, and user-interface design 
-\cite{Finnerty2013}.  Research has also investigated \textit{framing}, 
+\cite{Finnerty2013}.  Researchers have also investigated \textit{framing}, 
 by testing the effects of describing the workflow context 
@@
 \cite{chandler2013breaking}, or using an alternative problem discription
-\cite{thibodeau2013natural}.  To our knowledge, no study has investigated the 
-effects of inter-task effects in microtask work.
+\cite{thibodeau2013natural}.  To our knowledge, no study has investigated 
+inter-task effects on microtask platforms.
+
+As a point of comparison, we included treatments in which we induce 
+\textit{framing}.
+Before the workers label images, we indicate that the work 
+was funded by a research lab having a particular area of interest, to see the 
+influence this has on the workers’ subsequent labels. 
+Surprisingly, inter-task effects were stronger than framing, in some cases 
+about twice as strong. 
+Our results show that initial tasks can significantly alter the subject 
+matter on which worker's labels focus. We also found that inter-task 
+effects can induce workers to provide labels of greater or lesser specificity. 
+This suggests that careful consideration should be given to the bundling of 
+tasks when designing a study using a microtask platform.
 
 To characterize inter-task effects, we present a novel, generalized definition 
-of \textit{HPU priming}. Although priming is traditionally used to elucidate 
-internal 
-psychological mechanisms, our definition characterizes a computational 
-property of the HPU, and corresponds to the worst-case bias introduced into an 
-algorithm ``running'' on primed HPUs. This definition enables a direct, 
-quantititive comparison of HPU priming effects accross domains and 
-applications, while offering a practical, intuitive interpretation. We 
-demonstrate that machine learning tools can be used to detect priming, an 
-approach that could be used to detect priming effects without knowing in 
-advance what the nature of the effects might be, nor how priming was imposed.
-
-In the present work, we investigate inter-task priming on the Amazon 
-Mechanical Turk platform, using an image-labeling task, one of the most common 
-kinds of tasks on that platform 
-\cite{chandler2013breaking,Berinsky2012351,Finnerty2013,paolacci2010running}.  
-The task requires workers to label images featuring food, table-settings, and 
-related utensils and cookware. We divide the set of images shown to a worker 
-into an \textit{initial} and \textit{test} set, but, crucially, there was no 
-distinction made between these sets, nor any interruption in the flow of tasks 
-from the view of the worker. We varied the initial set of images, while 
-keeping the test set the same, to analyze the effect that that the initial 
-images have on the labels that workers attribute to the test set.
-
-As a point of comparison, we conduct a similar experiment where we induce 
-\textit{framing}. Before the workers label images, we indicate that the work 
-was funded by a research lab having a particular area of interest, to see the 
-influence this has on the workers’ subsequent labels. In both experiments, we 
-measure effects using our novel approach, as well as looking for changes in 
-the content of labels and label specificity based on an ontology we developed 
-for that purpose.
-
-Surprisingly, we found that inter-task effects are much stronger than framing. 
-Our results show that initial tasks can significantly alter the focus of 
-worker's labels. We also found that inter-task effects can induce workers to 
-provide labels of greater specificity. This suggests that careful consideration
-should be given to the bundling of tasks when designing a study using a
-microtask platform.
-
-Our analysis also highlights important advantages of our novel definition of 
-priming.  Our approach incorporates no prior knowledge about the nature
-of the task whatsoever.  In contrast, we also sought to detect priming
-based on its direct effects on label content and specificity,
-drawing on prior knowledge about the images and label semantics.
-Remarkably, while being more general, our definition yields a more sensitive
-measure of priming when combined with machine learning algorithms. 
-This approach could be applied to detect priming when one does not 
-\emph{a priori} know whether any priming has occurred, 
-nor what the nature of the effects might be.
+of \textit{HPU priming}. Priming is traditionally used to elucidate the
+internal psychological mechanisms of cognition.  But here we are concerned with
+understanding the outward effects that priming phenomena have on HPU 
+algorithms. Thus, before we discuss inter-task effects experimentally, we 
+discuss formal definitions for priming as computational phenomenon.  Our
+discussion will lead to a natural definition of priming that enables 
+comparisons of the severity priming effects accross applications, and enables
+the measurement of priming using machine learning tools.
 
@@
 \paragraph{Experimental setup.}
+
+image labeling is common\ldots
+\cite{chandler2013breaking,Berinsky2012351,Finnerty2013,paolacci2010running}.
+
 We solicited 2300 MTurk workers to perform an image-labeling task using images 

### 2014-09-23 docs/publications/2014.09_SCIENCE/man.tex
backup work on manuscript

@@
 \usepackage{amsthm}
-\newtheorem*{mydef}{Definition}
+\newtheorem{mydef}{Definition}
 \usepackage{dcolumn}
@@
 participants \cite{paolacci2010running, Berinsky2012351, chandler2013breaking}.
-Some computer scientists describe such platforms as a new computing 
+Computer scientists have described such platforms as a new computing 
 architecture, and seek to characterize “human co-processing units” (HPUs) in 
@@
 \paragraph*{Priming as computational hysteresis.}
-In psychology, priming effects are studied because they hint at the 
-psychological mechanisms at play during certain cognitive tasks. But in the 
-context of human computation, the focus should be on the outward consequences: 
-the potential for algorithms to execute differently when ``run'' on differently
-primed HPUs.
-
-We will present three definitions of priming with this practical concern in 
-mind, and then describe how to measure priming in practice. To proceed with 
-the definitions, we will assume that two populations of HPU’s, $\mathcal{P}$ 
-and $\mathcal{Q}$ were 
+To begin, we adopt the perspective that there is no canonical neutral or
+unprimed state.  Rather, we will speak of one HPU population being 
+\textit{differently primed} from another.  We present three definitions for 
+the difference in priming between HPU populations, each having different 
+merits, and then we discuss their relationships. To proceed with the 
+definitions, we will assume that two populations of HPU’s, $\mathcal{P}$ and 
+$\mathcal{Q}$ were 
 sampled randomly from the same initial population $\mathcal{R}$, and then were 
 exposed to (possibly) different priming treatments. The HPUs in $\mathcal{P}$ 
-and $\mathcal{Q}$ perform some 
-task, leading to popualtions of work-products, $P$ and $Q$.
+and $\mathcal{Q}$ perform some task, leading to popualtions of work-products, 
+$P$ and $Q$.
 
-For the first defenition, let us address the concern that differently primed 
-HPUs may produce ``biased'' work-products.
+For the first defenition, we focus on the direct effects that running an 
+algorithm on differently primed HPUs has on the algorithm's output.
 
 \begin{mydef}
+	\label{def:bias}
 	{\upshape Maximum Bias $\theta_\mathrm{bias}$:}
@@
 	in the expected output of $\mathcal{D}$ when acting on work-products from 
-	$P$ vs $Q$:
+	$P$ and $Q$:
 	$$
@@
 	where $p \in P$, $q \in Q$.  Then, define the difference in priming 
-	between $P$ and $Q$ to be the worst-case bias, i.e. the bias of the most
-	susceptible decision:
+	between $\mathcal{P}$ and $\mathcal{Q}$ to be the worst-case bias, i.e. 
+	the bias of the most susceptible decision:
 	$$
@@
 \end{mydef}
+Thus, in \textbf{Definition \ref{def:bias}}, $\theta_\mathrm{bias}$ has a 
+straightforward interpretation as an upper bound on the amount of bias induced 
+on any yes-or-no decision, due to the difference in priming of 
+$\mathcal{P}$ and $\mathcal{Q}$.  Although easy to interpret, it is, however, 
+not clear how $\theta_\mathbf{bias}$ could be measured in practice.
 
-Thus, $\theta_\mathrm{bias}$ has a straightforward interpretation as an upper 
-bound on the amount of bias induced on any yes-or-no decision, due to the 
-difference in priming of $\mathcal{P}$ and $\mathcal{Q}$.
-
-For the next definition, we attempt to address directly the extent to which 
-two populations of work-products are ``different'', by supposing that they are 
-different to the extent that they can be distinguished algorithmically. To 
-facilitate this definition, we make use of the notions of a 
-\textit{distinguisher} and a \textit{validation} test.
-
+Next we attempt to phase the difference in priming between $\mathcal{P}$ and
+$\mathcal{Q}$ in terms of the extent to which their work products are 
+distinguishable algorithmically. To facilitate this definition, we make 
+use of the notions of a \textit{distinguisher} and a \textit{validation} test.
 \begin{mydef}
@@
 	$\mathcal{D}$ guessed correctly, and the value of $V$ is 1, 
-	otherwise V = 0.
+	otherwise $V = 0$.
 
@@
 	time. Therefore, denote the performance of $\mathcal{D}$ as 
-	$\eta_\mathcal{D}(P, Q)$, and define:
+	$\eta_\mathcal{D}(P, Q)$:
+	$$
+		\eta_\mathcal{D}(P,Q) = 2\cdot \mathrm{E}\{V(\mathcal{D},P,Q)\} - 1
+	$$
+	Then define the difference in priming between $\mathcal{P}$ and 
+	$\mathcal{Q}$ to be the performance of the best possible distinguisher:
 	$$ 
@@
 	$$
-
 \end{mydef}
@@
 accuracy is 1/2 (i.e. as good as chance) performance is 0, and when accuracy 
-is perfect, performance is 1. This definition casts the measurement of priming 
-effects in terms of a binary classification problem, which is well-studied in 
-the field of machine learning.
+is perfect, performance is 1. This definition formulates the measurement of 
+priming effects in terms of a binary classification problem. As we will show,
+this allows us to apply tools from the machine learning field to the 
+measurement of difference in priming.  However, it is not immediately clear 
+how this measure relates to the potential for priming to cause bias.
 
-The two definitions we have already mentioned are, in fact, equivalent, and 
-correspond to a third, more fundamental formulation known as the total 
-\textit{variational distance}, or $l_1$-distance, or simply the “statistical 
-distance” ($D_{l_1}$):
+For the third definition, we focus on describing the inherent, statistical
+difference between work-products in $P$ and $Q$. Thus we define the difference
+in priming to be equal to the \textit{total variational distance}, or $l_1$-distance (denoted $D_{l_1}$) between $P$ and $Q$. 
+\begin{mydef}
+	\label{def:l1}
+	{\upshape total variational distance $\theta_{l_1}$:}
 	$$
-	D_{l_1}(P,Q) \equiv \frac{1}{2} \sum_{x \in \mathcal{X}} 
+	\theta_{l_1} = D_{l_1}(P,Q) \equiv \frac{1}{2} \sum_{x \in \mathcal{X}} 
 	\left| 
@@
 	where $f_P(x)$ denotes the probability of observing x when sampling from P.
-This leads us to our third definition:
+\end{mydef}
+The abvantage of definition \ref{def:l1} is that it provides connections
+to statistical and information theory.
 
-\begin{mydef}
-	{\upshape Priming as $l_1$-distance:}
-	The difference in priming of $\mathcal{P}$ and $\mathcal{Q}$ is the 
-	$l_1$-distance between the distributions of their work-products, 
-	$D_{l_1}(P,Q)$.
-\end{mydef}
-
-We provide proofs of the equivalence between these definitions in the 
-supplementary material. Despite their equivalence, we show the three 
-definitions because they offer different theoretical, practical, and 
-interpretive entry points. Definition 1 provides a practical motivation, and 
-the straighforward interpretation of priming as bias. Definition 3 draws a 
-clear link to existing statistical theory. And Definition 2 introduces machine 
-learning tools, which allow us to gain traction when the purely statistical 
-tools fail.
+Remarkably, all three definitions are, in fact, equivalent, and from here on
+we simply denote the difference in priming as $\theta$.  We provide proofs
+in the supplementary material to demostrate this fact.  This means that we
+can use machine learning tools to measure priming, while interpreting the
+results either in terms of the  leakage of information from a prime into an 
+HPU output or in terms of the potential to bias a decision.
 
 \paragraph{Measuring priming.}
+Before proceeding, we offer a few words of caution regarding the measurement 
+of $\theta$.
+
 Care must be taken in estimating $D_{l_1}$ from samples so as not to obtain

### 2014-10-12 docs/publications/2014.08_HCOMP/_man.tex
work on manuscript

@@
 %
-\documentclass[letterpaper,twocolumn]{article}
-\usepackage[hmargin=0.75cm,vmargin=0.75cm]{geometry}
-\usepackage{scrextend}
+\documentclass[letterpaper]{article} 
+\usepackage{aaai} 
+\usepackage{times} 
+\usepackage{helvet} 
+\usepackage{courier} 
+\setlength{\pdfpagewidth}{8.5in} 
+\setlength{\pdfpageheight}{11in} 
+%%%%%%%%%%
+% PDFINFO for PDFLATEX
+% Uncomment and complete the following for metadata (your paper must compile with PDFLATEX)
+\pdfinfo{
+	/Title Inter-Task Effects Induce Bias in Crowdsourcing
+	/Author Edward Newell
+	/Keywords priming, framing, crowdsourcing
+}
+
 \usepackage{graphicx}
-
 \usepackage{amsmath}
@@
 \usepackage{amsthm}
+\usepackage{caption}
 
 \newtheorem*{mydef}{Definition}
-
-\usepackage{cite}
 
@@
 
-\newcommand{\td}[1]{{\color{blu}\hl{TODO: #1}}}
+%\setlength{\parindent}{0cm}
+%\setlength{\parskip}{4mm plus1mm minus1mm}
 
-\definecolor{shadecolor}{rgb}{.93,.93,.93}
-\definecolor{blu}{rgb}{0,0,1}
-\setlength{\parindent}{0cm}
-\setlength{\parskip}{4mm plus1mm minus1mm}
-
-\title{Inter-task effects induce bias in crowdsourcing}
-\author{Edward Newell, Derek Ruths}
-
-\parindent0pt \parskip8pt
-
+%%%%%%%%%%
+% Section Numbers
+% Uncomment if you want to use section numbers % and change the 0 to a 1 or 2
+% \setcounter{secnumdepth}{0} %%%%%%%%%%
+\title{Inter-Task Effects Induce Bias in Crowdsourcing}
+\author{Edward Newell\footnote{bla} \and Derek Ruths\\
+School of Computer Science, McGill University, Montreal, Canada\\
+$^*$\texttt{edward.newell@mail.mcgill.ca}\\
+}
+%%%%%%%%%%
+% Body of Paper Begins
 \begin{document}
@@
 \section*{Abstract}
-Microtask platforms like Amazon Mechanical Turk provide a cheap and fast means
-to engage participants for scientific reasearch.  
-Workers on such platforms prefer to work on batches of tasks of the same 
-type, so we investigate the potential for the content of earlier tasks 
-to influence worker performance in later tasks, which we call ``inter-task'' 
-effects.  
-Existing research investigates the impact of various design factors, such as 
-``framing'', on the quality of crowdsourced content, but does not, to 
-our knowledge, address inter-task effects.  
-We employ a canonical image-labeling task on the Amazon Mechanical Turk 
-platform, to measure both inter-task and framing effects, in terms of their 
-impact to the content and specificity of the labels workers provide.
+Microtask platforms allow researchers to engage participants quickly and 
+inexpensively.
+Workers on such platforms probably perform many tasks in succession,
+so we investigate interactions between earlier tasks and later ones, which we 
+call ``inter-task'' effects.  
+Existing research investigates many task design factors, such as 
+``framing'', on the quality of responses, but to our knowledge, does not 
+address inter-task effects.  
+We use a canonical image-labeling task on Amazon Mechanical Turk 
+to measure the impact of inter-task and framing effects on the focus and 
+specificity of labels that workers provide.
 We also introduce an algorithmic definition of priming, which measures the 
-worst-case bias that priming effects introduce into crowdsourced content.
-We find that inter-task effects produce a much stronger impact than framing, 
-and find that our algorithmic definition yields a powerful, generalized measure
-for priming effects when combined with machine learning algorithms.
-
+worst-case bias introduced into responses.
+We find that inter-task effects produced a much stronger impact than framing, 
+and demonstrate that our novel priming definition yields a generalized 
+measure of priming effects when combined with machine learning algorithms.
+\paragraph{Keywords:} priming, framing, crowdsourcing.
 \section*{Introduction}
-
-Microtask crowdsourcing platforms like Amazon Mechanical Turk (AMT) make it 
+Microtask crowdsourcing platforms like Amazon Mechanical Turk (MTurk) make it 
 possible to submit batches of small tasks to a large pool of human workers, 
 who do the tasks for fun, a sense of purpose, and remuneration 
-\cite{kazai2013analysis, Antin20122925}.  
+\cite{kazai2013analysis,Antin20122925}.  
 Originally used to distribute clerical work, these platforms 
 increasingly serve as a fast and cheap means to engage experimental 
-participants and manually annotate datasets in a research 
+participants in a research 
 setting \cite{snow2008cheap}.
-Tasks involving qualitative
-judgment (e.g. flagging inappropriate images), natural language annotation,
-and object recognition are commonplace, since it is difficult to achieve 
-comparable performance using only computers \cite{yuen2011survey}.
-%Generally the worker is first given some orientation to the task, and then 
-%performs the task repeatedly (e.g. label several images, one after 
-%the other).
 
-Such platforms make human cognition a fluid resource: it is available 
-on demand in small units, with low transaction 
-cost, from anywhere via the 
-Internet\footnote{\href{http://mturk.com}{http://mturk.com}}.
-The task requester can 
-interact with the platform like a compute server, seamlessly 
+The task requester can interact with the platform like a compute server, 
+seamlessly 
 integrating human and machine computation.  Researchers have put forward the 
-term HPU (Human co-Processing Unit)\footnote{We acknowledge the irony of this 
-term: the original meaning of `computer' was a person who performs 
-computations, its reference to machines being a personification brought into 
-usage in the late 1800s\cite{Dictionary:hl}.}, viewing the introduction of 
+term HPU (Human co-Processing Unit), viewing the introduction of 
 microtask platforms as a new computing architecture
@@
 
-There has been considerable investigation into the factors that affect HPU 
-output on crowdsourced microtask platforms.  Studies have shown that 
-there is a great deal of variance in worker attention and 
-accuracy \cite{kazai2013analysis}.  Factors that affect the quality of HPU 
-output include level of pay\cite{kazai2013analysis}, 
-training\cite{le2010ensuring}, screening workers\cite{paolacci2010running}, 
-and user-interface design
+There has been considerable investigation into the factors that affect the 
+quality and quantity of micro-task completion.  These include the level of 
+pay \cite{kazai2013analysis}, training \cite{le2010ensuring}, screening of 
+workers \cite{paolacci2010running}, and user-interface design 
 \cite{Finnerty2013}.  Research has also investigated \textit{framing}, 
-by testing the effects of disclosing the role of a task within the 
-context of a study \cite{Kinnaird2012281}, and disclosing the ultimate 
-purpose of that study \cite{chandler2013breaking}.  However, to our knowledge, 
-no study has investigated the effects of inter-task priming.
+by testing the effects of disclosing the workflow context 
+\cite{Kinnaird2012281}, and the purpose of tasks 
+\cite{chandler2013breaking}.  To our knowledge, no study has investigated the 
+effects of inter-task priming.
 
 To characterize the effects of inter-task priming, we present a novel  
-\textit{algorithmic definition of priming}, along with a general method 
+\textit{algorithmic definition of priming}, and a general method 
 for measuring priming effects using machine learning algorithms.  
-Existing work on priming effects focuses on the internal psychological 
-mechanisms of priming, but here we are interested in how the treatment of 
-workers can impact an application of human computation. This leads us to 
-quantify priming in terms of the algorithmic distinguishability of priming
-treatments.
+Rather than focus on internal psychological mechanisms, our definition 
+focuses on the impact that priming has to the downstream application of human 
+computation, providing a generalized measure of bias.
 
-In the present work, we investigate inter-task priming using image-labeling 
-tasks on the AMT platform.  
-Each worker is required to label ten images 
-featuring 
+In the present work, we investigate inter-task priming on the Amazon 
+Mechanical Turk platform, using an image-labeling task, one of the most common 
+kinds of tasks on that platform 
+\cite{chandler2013breaking,Berinsky2012351,Finnerty2013,paolacci2010running}.  The task requires workers to label ten 
+images featuring 
 food and culture.  We regard these images as being made up of an 
-\textit{initial} and \textit{final set}, but, crucially, there is no
+\textit{initial} and \textit{test set}, but, crucially, there is no
 distinction made between these sets, nor any interruption in the flow of tasks 
 from the view of the worker.
-Each worker is randomly assigned one of three initial sets, but the final set
-of images is always the same.  We analyze the effect that the assignment of 
-initial set has on workers' attribution of labels to the final set.  We 
-measure effects using our novel approach, as well as looking for changes in 
-the content of labels and label specificity based on an ontology we 
-developed for that purpose.
+We vary the initial set of images, while keeping the test set the same to 
+analyze the effect that that the initial images have on the labels that 
+workers' attribute to the test set.  We measure effects using our novel 
+approach, as well as looking for changes in the content of labels and label 
+specificity based on an ontology we developed for that purpose.
 
@@
 \textit{framing}: we disclose a fictitious, semantically-loaded name for 
-requester funding the tasks.
-The names were chosen to suggest the requester's interest in 
-a specific aspect of the image content.  One might reasonably expect that this 
-would orient workers to provide a greater quantity and specificity of labels 
-which relate to this ``preferred'' content.
+the requester funding the tasks.
+The names were chosen to suggest the requester's interest in a specific 
+aspect of the image content.  We expect this would cause workers 
+to provide more labels, and greater specificity, relating to this 
+``preferred'' content.
 
-Surprisingly, we find that inter-task effects on label orientation and 
-specificity are much stronger than those brought about by framing tasks with a 
-funder name.  Our results show that initial tasks can introduce significant 
-bias in subsequent worker labeling.  Interestingly, we find that inter-task
+Surprisingly, we find that inter-task effects are much stronger than the 
+framing.  Our results show that initial tasks can significantly alter the 
+focus of worker's labels.  Interestingly, we find that inter-task
 effects can be used to induce greater specificity.  Our results suggest that
@@
 Our analysis also highlights important advantages of our novel definition of 
-priming.  Our approach relies on no prior knowledge about the nature
-of the task task whatsoever.  In contrast, we also sought to detect priming
-based on its direct effects on label content and specificity, implicitly
+priming.  Our approach incorporates no prior knowledge about the nature
+of the task whatsoever.  In contrast, we also sought to detect priming
+based on its direct effects on label content and specificity,
 drawing on prior knowledge about the images and label semantics.
-Remarkably, while being more general, our novel approach was also more 
-sensitive.  This suggests that our measurement approach could be applied in 
-cases where one does not \emph{a priori} know whether any priming has occurred, 
-nor what the effects might be.
+Remarkably, while being more general, our definition yields a more sensitive
+measure of priming when combined with machine learning algorithms. 
+This approach could be applied to detect priming when one does not 
+\emph{a priori} know whether any priming has occurred, 
+nor what the nature of the effects might be.
+\subsection*{An algorithmic definition of priming}
+Our goal in creating a definition of priming is to capture the effects of 
+priming on human computation \textit{applications}.  This motivates us to 
+seek a definition of priming in terms of its ability alter HPU 
+output rather than in terms of psychological mechanisms.
 
-\subsection*{An algorithmic definition of priming}
-
-In psychology, the effects of priming are usually measured in terms of a 
-change in the  
-speed or accuracy of responses in a task, or in the ability to recognize a 
-stimulus object (e.g. a spoken word or an image) when the object is noisier, 
-fainter, or briefer.  Methods are also employed to measure processes
-in the brain of the participant, such as by fMRI.  These approaches are 
-well-suited to studying the underlying psychological mechanisms at work.
-
-Our purpose is different: we are interested in assessing the ramifications
-that priming of HPUs could have on the applications to which they are employed.
-This influences the approach we take to measurement in two ways.  First, we 
-switch from focusing on the internal mechanisms of HPUs to focusing strictly 
-on the HPU outputs.  Second, we cannot \textit{a priori} know the 
-application for which HPUs are being employed, but we would like to measure 
-any effects that could in principle impact the application.  These 
-considerations motivate us to define priming effects in terms of the 
-algorithmic distinguishability of primed output.
-
-One difficulty in constructing a definition of priming is that there would 
-appear to be no defensible notion of a ``neutral'' or ``unprimed state''.  A 
-participant 
-always approaches a task in \textit{some} state of mind.  If no priming 
-condition is applied, then the participant is simply primed by her
-exposures prior to the experiment, which cannot be known by the experimenter.  
-While arguments can surely be made that one treatment or another is 
-\textit{more} 
-``neutral'', we refrain from proposing a canonical ``null priming treatment''. 
-Instead, we define priming relatively, and speak of one treatment being 
-\textit{differently primed} from another.
-
-A definition of priming must also consider that the effects of priming will
-manifest differently depending on the task that participants perform 
-subsequent to priming:  two priming treatments that
-produce markedly different output for one task might be 
-indistinguishable under another task.  Thus, we define priming
-with respect to a task.
-
-A final factor to consider is that people will always differ in their initial
-knowledge, specific aptitudes, and in many other intrinsic aspects.  Moreover,
-priming may not be ``complete'', in the sense that people's experiences before
+We define priming with respect to a task $\mathcal{T}$.  People will always differ in their initial knowledge, specific 
+aptitudes, and in many other intrinsic aspects.  Moreover, priming may not be 
+``complete'', in the sense that people's experiences before
 priming may continue to have residual effects.  Therefore, we define priming 
@@
 
-To set up the definition, when a population of people $\mathcal{J}$ performs
-a task $\mathcal{T}$ thus producing a population of task-outputs $\mathcal{L}$,
-we will write $\mathcal{T}(\mathcal{J}) = \mathcal{L}$.
+One difficulty in constructing a definition of priming is that there would 
+appear to be no defensible notion of a ``neutral'' or ``unprimed state''.  
+While arguments could perhaps be made that one treatment or another is 
+\textit{more} ``neutral'', we choose to define priming relatively, and speak 
+of one treatment being \textit{differently primed} from another.
+
+To set up the definition, when a population of people $\mathcal{P}$ performs
+a task $\mathcal{T}$ thus producing outputs $\mathcal{L}$,
+we will write $\mathcal{T}(\mathcal{P}) = \mathcal{L}$.
 
@@
 	$\mathcal{P}_1$, are uniformly and randomly subsampled from an initial 
-	population $\mathcal{P}$, are exposed to (possibly) different priming 
-	treatments, and then perform a task $\mathcal{T}$, 
-	producing task-outputs $\mathcal{T}(\mathcal{P}_0)$ and 
+	population $\mathcal{P}$, and are exposed to (possibly) different priming 
+	treatments. Each population performs a task $\mathcal{T}$, 
+	producing outputs $\mathcal{T}(\mathcal{P}_0)$ and 
 	$\mathcal{T}(\mathcal{P}_1)$.
@@
 
-In the language of computer science, $\mathcal{A}$ is a classifier performing
-a binary classification.  The measure $\theta$ can range between 0 and 1, and 
-indicates how much better the performance of the best possible classifier is 
-compared to a random guess. We intentionally leave the details of 
-$\mathcal{A}$ unrestricted because $\theta$ should depend on the potential 
-for two populations to be distinguished, based on their inherent differences, 
-rather than on the performance of a particular classifier.
-
-In practice, some particular classifier $\mathcal{C}$ must be used and a 
-statistical estimate of its performance $\hat{\theta}_\mathcal{C}$ obtained. 
-$\hat{\theta}_\mathcal{C}$ acts as a lower bound for the 
-theoretical value $\theta$ from the definition, because there might 
-exist some other classifier $\mathcal{C}'$ with 
-$\hat{\theta}_\mathcal{C'}>\hat{\theta}_\mathcal{C}$.
-Here, we use a Naive Bayes classifier because it simple and performs well 
-across a broad range of classification tasks.
-
-To interpret $\hat{\theta}_\mathcal{C}$, imagine that some choice is to be
-made between two options on the basis of worker outputs (e.g. whether or not 
-to flag an image as inappropriate). Any such binary choice has a formal 
-structure of a trained classifier (i.e. a distinguisher which discards the 
-first two inputs). This means that $\hat{\theta}_\mathcal{C}$ estimates a 
-lower bound for the worst-case bias introduced in such a binary decision when 
-one failed to control for priming effects.
-
-\subsection*{Experimental Setup}
-
 \begin{figure*}
@@
 		to classify workers based on the labels they attributed to the first
-		image of the final image set. Each panel compares a basis treatment,
+		image of the test set. Each panel compares a basis treatment,
 		indicated above the panel, to various treatments indicated on the
@@
 		is performing better than chance when $\hat{\theta}_\text{NB}$ 
-		exceeds 0.168, indicated by the dotted line.  See \textbf{Methods} for
-		the calculation of this confidence threshold.
+		exceeds 0.168, indicated by the dotted line.
 	}}
@@
 
+In the language of computer science, $\mathcal{A}$ is a classifier performing
+a binary classification.  The measure $\theta$ can range between 0 and 1, and 
+indicates how much better the performance of the best possible classifier is 
+compared to a random guess. We intentionally leave the details of 
+$\mathcal{A}$ unrestricted because the theoretical value of $\theta$ should 
+depend on the inherent differences between the populations, rather than on 
+the performance of a particular classifier.
+
+In practice, some particular classifier $\mathcal{C}$ is tested (using e.g. 
+cross-validation) yielding a statistical estimate of its performance 
+$\hat{\theta}_\mathcal{C}$. This
+$\hat{\theta}_\mathcal{C}$ acts as a lower bound for the 
+theoretical value of $\theta$, because there might 
+exist some other classifier $\mathcal{C}'$ with 
+$\hat{\theta}_\mathcal{C'}>\hat{\theta}_\mathcal{C}$.
+For our experiment, we use a Naive Bayes classifier because it is easy to
+implement and performs well across a broad range of classification tasks.
+
+To interpret $\hat{\theta}_\mathcal{C}$, imagine that some choice 
+$\mathcal{C}$ is to be made between two options on the basis of worker 
+outputs (e.g. whether or not to flag an image as inappropriate). Any such 
+binary choice has the formal structure of a distinguisher that only considers 
+the last of its three inputs. Thus, we can directly compare $\mathcal{C}$ to 
+the optimal distinguisher, $\mathcal{A}$.  If, prior to knowing the input to 
+$\mathcal{C}$, either of its outcomes is equally likely, then the worst 
+possible bias that priming can introduce is bounded above by $\theta$. 
+This means that $\hat{\theta}_\mathcal{C}$ estimates a 
+lower bound for the worst-case bias introduced in a binary 
+decision that provides a full bit of information, made on the basis of worker 
+outputs, when one failed to control for the corresponding priming treatments.
+\subsection*{Experimental Setup}
 \begin{table}[t]
@@
 		The ambiguous, cultural, and ingredients initial image sets are shown 
-		in \textbf{Figs. 2}, \textbf{3}, and \textbf{4}.
+		in \textbf{Figs. S2}, \textbf{S3}, and \textbf{S4}.
 	}}
@@
 \end{table}
+We solicited 900 MTurk workers to perform an image-labeling task relating to
+food and culture.  The workers were randomly assigned to one of seven 
+treatments shown in \textbf{Table 1}.  Depending on their treatment, workers were then shown the 
+name of a research funder, or this step was skipped.
+Next, workers were shown ten images, one at a time and were required to provide
+five labels for each.  For the purpose of analysis, we divide the images
+into \textit{initial} and \textit{test} sets, comprising respectively the 
+first five and last five images.  From the perspective of the worker, there 
+was no distinction or interruption between the initial and test sets. 
+Depending on the treatment, one of three initial image sets was chosen, but
+the test set was always the same.
 
-We solicited 900 AMT workers to perform an image-labeling task relating to
-food and culture.  The workers were randomly assigned to one of seven 
-treatments shown in \textbf{Table 1}.  Workers were first shown brief 
-instructions.  Depending on their treatment, workers were then shown the 
-name of a research funder, or this step was skipped.  When shown, 
-the funder name was either
-``The Global Foundation for Cultural Recognition'', or 
-``The National Foundation for Nutritional Awareness''.
-
-Next, workers were
-shown ten images, one at a time. Workers were required to label each image 
-with five descriptive labels before moving on to the next.  For the purpose 
-of analysis, we divide the images
-into \textit{initial} and \textit{final} sets, comprising respectively the 
-first five and last five images shown.  As mentioned, from the perspective of 
-the worker, there was no 
-distinction or interruption between the initial and final sets. 
-Depending on the treatment to which the worker was assigned, one of three 
-initial image sets was chosen. The final image set was the same for all 
-treatments.
-
-For the final image set, we chose 
-images that contained prepared meals and featured a prominent, identifiable 
-culture (see \textbf{Fig. 4}).  We intended that the content of these images 
-would elicit labels focusing on food or culture (or both).
-We refer to the three initial image sets as the ``ambiguous'', ``cultural'', 
-and ``ingredients'' sets.  The ambiguous set was chosen to
-be very similar to the final image set, in the sense that it consisted of
-images of prepared meals (see \textbf{Fig. 5}).  However, its cultural 
-features were intended to be less prominent.  The cultural set featured 
-iconic cultural scenes, but no food at all (see \textbf{Fig. 6}).  Finally, 
-images from the 
-ingredients set depicted separated ingredients, but, 
-like the ambiguous set, were chosen to avoid prominent cultural features (see 
-\textbf{Fig. 7}).  See the \textbf{Materials and Methods} section for further 
-details.
-
+The test image set comprised images containing prepared meals and featured a 
+prominent, identifiable culture (see \textbf{Fig. S1}).
+To identify the initial image sets, we use the names ``ambiguous'', 
+``cultural'', and ``ingredients''.  The ambiguous set was chosen to
+be similar to the test set, in the sense that it consisted of
+images of prepared meals (see \textbf{Fig. S2}),  but its cultural 
+features were less prominent.  The cultural set featured 
+iconic cultural scenes, but no food at all (see \textbf{Fig. S3}).  Images from 
+the ingredients set depicted separated ingredients, but, 
+like the ambiguous set, avoided prominent cultural features (see 
+\textbf{Fig. S4}).
 \subsection*{Results}
@@
 With some exceptions, the classifier performed significantly better 
-than chance when distinguishing treatments that had different initial image 
-sets.  This demonstrates that inter-task effects were strong for the labeling 
-tasks.  Of the sixteen treatment pairs having different initial images, there 
-were three cases where the classifier performance was on par with chance. 
-Each of these cases involved distinguishing workers shown the ambiguous set 
-from ones shown the ingredients set.  The reason for the low 
-distinguishability of workers from these treatments might be because
-the ambiguous and ingredients sets are somewhat similar to one another.
-We will come back to this point later when we discuss the degree of similarity 
-between image sets.
+than chance when distinguishing treatments that had different initial tasks.  
+This demonstrates that inter-task effects were strong. Of the sixteen 
+treatment pairs having different initial tasks, the classifier was unable to
+distinguish treatments significantly better than chance in three cases.
+Each cases involved distinguishing treatments having the ambiguous and 
+ingredients set.  Later we discuss the similarity between image sets, and 
+we will argue that this is because the ambiguous and ingredients sets are 
+similar.
 
-In contrast, the classifier never performed significantly better than chance
-when distinguishing treatments that differed only in the funder name shown. 
-Thus, framing effects were rather weak.
-
-\paragraph{Earlier tasks influenced workers' level of specificity.} 
 \begin{figure*}
@@
 		the labels from one treatment are compared to the other, and points 
-		toward in the direction of the more specific treatment.
+		toward in the direction of the more specific treatment.  Error bars
+		indicate 95\% confidence intervals.
 	}}
@@
 \end{figure*}
-
+In contrast, the classifier never performed significantly better than chance
+when distinguishing treatments that differed only in framing.  Thus, framing 
+effects were rather weak.  In fact, framing effects were generally weak in
+our results, so we omit treatments involving framing from the remainder of
+our presentation to save space.  We encourage the interested reader to look
+at the results for these treatments in the supplementary material.
 \paragraph{Earlier tasks orient workers' focus during later tasks.} 
-We next investigated the \textit{nature} of the inter-task effects.  Since the
-initial images were chosen to emphasize either food (ingredients set) or 
-culture (cultural set), we looked for effects in the number of culture- and 
-food-oriented labels that workers attributed to the final image set.
+Since the initial images were chosen to emphasize either food (ingredients set)
+or culture (cultural set), we looked for effects on the number of culture- and 
+food-oriented labels that workers attributed to the test image set.
 
 To this end, we constructed an ontology from the labels attributed to the 
-test images.  The ontology was constructed as a directed acyclic graph, with 
-edges pointing from more general labels to more specific ones.
-For example, our ontology contains the path \texttt{food} $\to$ 
-\texttt{ingredients} $\to$ \texttt{vegetables} $\to$ \texttt{tomato}. We 
-provide more detail about the construction of the ontology in the 
-\textbf{Materials and Methods} section.
+test images.  In the ontology, edges point from more general labels to more 
+specific ones.  For example, the ontology contains the path \texttt{food} 
+$\to$ \texttt{ingredients} $\to$ \texttt{vegetables} $\to$ \texttt{tomato}.
 
-We counted labels as being culture- and/or food-oriented based on 
-whether the label had inbound paths from the abstract labels \texttt{culture} 
-or \texttt{food} in the ontology. Since food is a central feature 
-of culture, there were many labels that were both culture- and food-oriented 
-in this sense.  Nevertheless, there were many food-oriented labels, such as 
-\texttt{bread}, which lacked specific cultural connections.  Meanwhile, there 
-were many non-food, culture-oriented labels, such as \texttt{russian dolls}.
+Since food is a central feature 
+of culture, our ontology contains many labels that have both \texttt{food}
+and \texttt{culture} in their ancestry.  Nevertheless, there were many 
+food-oriented labels, such as \texttt{bread}, which lacked specific cultural 
+connections, as well as non-food, culture-oriented labels, such as 
+\texttt{russian dolls}.
 
-When we tallied labels attributed to the first image of the final set, 
-we found that workers shown the cultural initial set produced significantly 
-more culture-oriented labels and less food-oriented ones 
-(see \textbf{Fig. 2A}).  In fact, the inter-task
-effect was so strong that it essentially reversed the proportion of culture- 
-and food-oriented labels seen for the ambiguous set.  On the other hand, the 
-composition of labels attributed by 
-workers shown the ingredients image set was not significantly different from 
-that attributed by workers shown the ambiguous set.  This shows that inter-task
-effects can profoundly alter workers' focus, but the effects brought 
-about by showing workers the ambiguous and ingredients sets were not 
-significantly different.
+\begin{figure}
+	\centering{
+	\includegraphics[scale=0.7]{figs/longitudinal_theta_excess-culture.pdf}
+	\caption{\footnotesize{
+		\textbf{A}) Difference in priming between \textsc{ambg} and 
+		$\textsc{cult}_{img}$ measured based on the accuracy of a Naive Bayes 
+		classifier during cross-validation, when trained on labels from the
+		test images indicated along the abscissa.
+		\textbf{B}) Excess cultural orientation of labels attributed to
+		the test images indicated on the abscissa, by workers from
+		$\textsc{cult}_{img}$ relative to those attributed by workers from
+		\textsc{ambg}, calculated using \textbf{Eq. 3}.  Error bars indicate
+		95\% confidence intervals.
+	}}
+}
+\end{figure}
+When we tallied labels attributed to the first image of the test set, 
+we found that workers from $\textsc{cult}_{img}$ produced significantly 
+more culture-oriented labels and less food-oriented ones than those from
+\textsc{ambg}
+(see \textbf{Fig. 2A}).  The inter-task effect was so strong that the 
+proportion of food- and culture-oriented labels in $\textsc{cult}_{img}$ was
+essentially the reverse of that in \textsc{ambg}.  However, the 
+composition of labels attributed by $\textsc{ingr}_{img}$
+was not significantly different from those attributed by \textsc{ambg}.  This 
+shows that inter-task effects \textit{can} profoundly alter workers' focus. 
+Again, we 
+will argue later that the ambiguous and ingredients image sets are, in fact, 
+quite similar.
+\paragraph{Earlier tasks influenced workers' level of specificity.} 
+Using the ontology described in the previous section, we can compare the 
+specificity of two labels $\ell_1$ and $\ell_2$. We say that $\ell_2$ is more 
+specific than $\ell_1$ if there is a \textit{directed path} from $\ell_1$ to 
+$\ell_2$.  If there is no directed path between labels, we say they are  
+\textit{non-comparable}.  For example, \texttt{tomato} was more specific than 
+\texttt{food}, while \texttt{statue} and \texttt{food} were non-comparable.
 
-Using the ontology described in the previous section, we compared treatments 
-in their degree of specificity.  When comparing two labels $\ell_1$ and 
-$\ell_2$ produced by different workers, we say that $\ell_2$ is more specific 
-than $\ell_1$ if there is a \textit{directed path} from $\ell_1$ to $\ell_2$.  
-If there is no directed path between $\ell_1$ and $\ell_2$, then they are 
-non-comparable.  As an example, \texttt{tomato} is more specific than 
-\texttt{food}, while \texttt{statue} and \texttt{food} are non-comparable.
-
-We can compare the degree of specificity of two workers by comparing the 
-labels each gives to some image in the final set.  Thus, we define the relative
-specificity of worker $u$ and $v$ for the $i$th image in the final set to be
-$s_i(u,v)$:
+We can then define the relative specificity of two workers with respect to 
+test-image $i$ as $s_i(u,v)$:
 
@@
 \end{align}
-
 where $u(i)$ denotes the set of labels attributed by worker $u$ to image $i$, 
@@
 $m$, and 0 otherwise.
-
-We can then define the relative specificity of treatments $\mathcal{U}$ and 
-$\mathcal{V}$, with regard to
-the $i$th image, $S_i(\mathcal{U},\mathcal{V})$, to be the mean
-relative specificity of two workers drawn uniformly from the treatments.  
-We obtain the estimator, $\hat{S}_i(\mathcal{U},\mathcal{V})$, by computing
-the sample average for our experimental data:
-
+We then define the relative specificity of two treatments, $\mathcal{U}$ and 
+$\mathcal{V}$, the $i$th image, denoted $S_i(\mathcal{U},\mathcal{V})$, to be 
+the mean relative specificity of two uniformly drawn workers:  
 \begin{align}
@@
 
-Further details for the estimation of relative specificity and the standard
-error of the estimation are given in \textbf{Methods}.
+Looking at labels attributed to the first test image, we found that workers 
+from \textsc{ambg} were more specific than workers from
+either $\textsc{cult}_{img}$ or $\textsc{ingr}_{img}$.  When we compare 
+$\textsc{cult}_{img}$ to $\textsc{ingr}_{img}$, we found that workers from
+$\textsc{ingr}_{img}$ were more specific.  This shows that inter-task 
+effects do substantially influence the specificity of labels that workers 
+provide.  When we discuss image similarity, below, we will explore a possible
+mechanism for this effect.
+\paragraph{Inter-task effects ``wash out'' quickly.}  
+It would stand to reason that, as workers proceed through the test images, 
+priming from the initial images would be ``washed out'', diminishing the 
+observed inter-task effects.
+Looking at the classifier performance, $\hat{\theta}_\text{NB}$, with respect 
+to the treatments \textsc{ambg} and $\textsc{cult}_{img}$, we find that 
+performance does drop off dramatically after just the first image 
+(see \textbf{Fig. 3A}).
+This suggests that inter-task effects primarily arise between consecutive 
+tasks, but that a residual effect can persist for at least five tasks (we 
+note, however that although the classifier performance seemed better than 
+chance for the fourth test image, this cannot be asserted with 95\% 
+confidence).
 
-We found that, with regard to labels attributed to the first image of the 
-final set, workers from \textsc{AMBG} were more specific than workers from
-either $\textsc{CULT}_{img}$ or $\textsc{INGR}_{img}$.  When we compare 
-$\textsc{CULT}_{img}$ to $\textsc{INGR}_{img}$, we found that workers from
-$\textsc{INGR}_{img}$ were more specific.  This shows that inter-task 
-effects substantially influence the specificity of labels that workers provide.
-
-\paragraph{Inter-task effects ``wash out'' quickly.}  
-\begin{figure}
-	\centering{
-	\includegraphics[scale=0.7]{figs/longitudinal_theta_excess-culture.pdf}
-	\caption{\footnotesize{
-		\textbf{A}) Difference in priming between \textsc{AMBG} and 
-		$\textsc{CULT}_{img}$ measured based on the accuracy of a Naive Bayes 
-		classifier during cross-validation, when trained on labels from the
-		test images indicated along the abscissa.
-		\textbf{B}) Excess cultural orientation of labels attributed to
-		the test images indicated on the abscissa, by workers from
-		$\textsc{CULT}_{img}$ relative to those attributed by workers from
-		\textsc{AMBG}, calculated using \textbf{Eq. 3}.
-	}}
-}
-\end{figure}
-At this point we have 
-investigated the inter-task effects induced on only the first image of the 
-final image set.  This is because, as mentioned, the effects are strongest on 
-for first image.  We now examine how the inter-task effects vary as workers 
-proceed through the images in the final set.  Since the final images are the
-same for all treatments, it would stand to reason that the inter-task effects
-induced by the initial image sets would fade away, being washed out by the
-inter-task effects of the final set.
-
-Looking at the classifier performance, $\hat{\theta}_{NB}$, with respect to the
-treatments \textsc{AMBG} and $\textsc{CULT}_{img}$, we find that performance
-drops off dramatically after just the first image (see \textbf{Fig. 3A}).
-This suggests that inter-task effects mainly arise between consecutive tasks.
-However, a residual distinguishability between these two treatments does 
-persist until the final image (although for the fourth image we cannot assert
-this with 95\% confidence).
-
-We can similarly look at how the inter-task effects on label composition
-(i.e. fraction of culture- and food-oriented words) play out as workers 
-progress through the final image set.  To do this, we define the 
-\textit{excess cultural orientation} as the number of culture-oriented labels 
-minus the number of food oriented ones.  Tracking the excess cultural 
-orientation across the images is, however, not in itself meaningful,
-because some images will inherently carry more cultural content than others. 
-To account for this, we calculate the excess cultural content for both 
-\textsc{AMBG} and $\textsc{CULT}_{img}$, and subtract the former from the 
-latter, yielding the \textit{relative} excess cultural content, 
-$\Delta_{cult}$.  Formally,
-
+Next we observed how inter-task effects on label composition (i.e. food- vs 
+culture-oriented labels) evolve as workers proceed through test images.
+We define the \textit{excess cultural orientation} as the number of 
+culture-oriented labels minus the number of food oriented ones.  To 
+meaningfully compare the excess cultural orientation between test images, we 
+must, however, account for the fact that some images inherently carry more 
+cultural content than others. In keeping with our notion of priming 
+\textit{difference}, we calculate the excess cultural content for both 
+$\textsc{cult}_{img}$ and \textsc{ambg}, and take their difference to be
+the \textit{relative} excess cultural content, $\Delta_{cult}$.  Formally,
 \begin{align}
+	\begin{split}
 	\Delta_{cult}(i) = \frac{1}{N}\left[ \sum_{w\in\textsc{cult}_{img}} \left(N_{w,cult}^{(i)} - N_{w,food}^{(i)}\right)\right. \\
 \left.	- \sum_{w\in\textsc{ambg}} \left(N_{w,cult}^{(i)} - N_{w,food}^{(i)}\right)\right],
+	\end{split}
 \end{align}
-
 where $N_{w,cult}^{(i)}$ stands for the number of culture-oriented labels 
@@
 
-The relative excess cultural content varied as workers proceed through the
-final image set in much the same way that $\hat{\theta}_\text{NB}$ did: for the
-first test image, it is significantly greater than zero, but drops off rapidly
-thereafter.  Unlike $\hat{\theta}_\text{NB}$, $\Delta_{cult}$ ceases to
-be significantly greater than zero after the second test image, so it would 
-seem that $\hat{\theta}_\text{NB}$ is the more sensitive of the two in
-detecting inter-task effects.
+We found $\Delta_{cult}$ was largest for the first test image, but dropped off 
+rapidly, remaining positive but not to a statistically significant extent
+(see \textbf{Fig. 3B}).  
+This is similar to the behavior of $\hat{\theta}_\text{NB}$, however, because
+the statistical significance of $\Delta_{cult}$ dropped more quickly, 
+$\hat{\theta}_\text{NB}$ appears to be a more sensitive measure of inter-task 
+effects.
+\paragraph{Inter-task similarity encourages more specific labels.}
+To continue with the analysis, we seek a measure of image similarity.  The 
+characterization of image content is a deeply complex issue that has been 
+approached by many disciplines 
+\cite{panofsky1939studies,shatford1986analyzing,Tversky1977327,Jaimes20002}.
+\textit{Perceptual similarity} is a particularly recalcitrant concept.
 
-\paragraph{Inter-task similarity encourages more specific labels.}
-For the next part of the analysis, it will be useful to speak of the
-``similarity'' between two image sets. In general, the characterization of 
-image content 
-is deeply complex and has been approached from the perspectives of 
-art\cite{panofsky1939studies,shatford1986analyzing},
-psychology\cite{Tversky1977327}, and information retrieval\cite{Jaimes20002}.
-Furthermore, the perception of \textit{similarity} is a particularly subtle 
-psychological phenomenon.  For example, a figure $A$ can appear simultaneously
-both \textit{more} and \textit{less} similar to an object $C$ than some other 
-object $B$.
-
-In the present study, we are more interested in the ultimate outputs of 
-workers' rather than the psychological details which lead to them (though 
-these are interesting in their own right).  This allows us to sidestep the 
-complication in attributing similarity: we asses how similar two sets of 
-images are, 
-\textit{with respect to the labeling task}, by looking at the fraction of 
-labels that they share.  Formally, we compute the similarity of two images
-sets $X$ and $Y$ by computing the Jacquard index between the sets of labels 
-attributed to them:
-
+However, in the present study, we are more interested how similar two 
+sets of images are, \textit{with respect to the labeling task}, which is much
+simpler to operationalize than general perceptual similarity.  Here, we 
+measure image similarity by looking at the fraction of labels that they share. 
+Formally, to measure the similarity between two \textit{sets of images}, $X$ 
+and $Y$, we compute the Jacquard index between the sets of labels attributed 
+to them:
 \begin{align}
@@
 \end{align}
-
-\begin{table*}
+\begin{table}
 \centering
-\begin{tabular}{ l  d  s s s s}
+\begin{tabular}{ l  s s s s}
 
 \toprule    
-\multirow{2}{*}{Image set} & \multicolumn{1}{c}{\# of unique} & 
-\multicolumn{4}{c}{Similarity}  \\
-\cline{3-6}
-
-&  \multicolumn{1}{c}{labels} 
-& \multicolumn{1}{c}{Ambiguous} 
+Image set   
+& \multicolumn{1}{c}{Ambig.} 
 & \multicolumn{1}{c}{Cultural} 
-& \multicolumn{1}{c}{Ingredients}
+& \multicolumn{1}{c}{Ingr.}
 & \multicolumn{1}{c}{Test} \\
@@
 \caption{\footnotesize{
-	Number of unique labels attributed to each image set, and their
-	similarities based on \textbf{Eq. 4} 
+Pairwise similarities of each image set based on the labels attributed to them (see \textbf{Eq. 4}).
 }}
 \label{table:2}
-\end{table*}
+\end{table}
+where $L(X)$ denotes the set of labels attributed to $X$.
 
-where $L(X)$ denotes the set of labels attributed to $X$.  See \textbf{Methods}
-for additional details regarding the calculation of similarity.
-
-The similarities of the various image sets are presented in \textbf{Table 2}. 
+The pairwise similarities of the image sets are presented in \textbf{Table 2}. 
 First, observe that the ambiguous and ingredients sets are much more similar 
-to each other than either is to the culture set.  This is consistent with our
-finding that $\hat{\theta}_\text{NB}$ between \textsc{AMBG} and 
-$\textsc{INGR}_{img}$ was not significant (see \textbf{Fig 1}).
+to each other than either is to the culture set.  Recalling the data presented
+in \textbf{Fig. 1}, this helps explain why two treatments could not be 
+distinguished on the basis of having differing initial sets corresponding to
+ambiguous and cultural.  This also explains why \textsc{ambg} and 
+$\textsc{cult}_{img}$ had similar label compositions in \textbf{Fig. 2A}.
 
@@
 prepared meals once they labeled the first test image.  At that point,
-a worker might not regard the labels \texttt{food} or \texttt{meal} to be 
-salient, since they do not distinguish the image from those she had seen 
-already.
+a worker might not regard the generic labels \texttt{food} or \texttt{meal} 
+to be salient, and opt instead for \texttt{bread}, or \texttt{pasta}.
 
@@
 influences the perception of salience. Thus, in a series of subjective 
-characterization tasks that have very similar content, the worker's focus 
+characterization tasks that have very similar content, workers' focus 
 will tend to be directed away from generic, shared attributes, towards those 
 attributes that are specific and distinguishing.
-
-\subsection*{Discussion}
-
+\subsection*{Conclusions}
 \paragraph{Inter-task effects should be considered during task design.}  
@@
 between consecutive tasks.
-
-\paragraph{$\theta$ provides a general purpose measure of priming effects.}
-When used three approaches to detecting priming effects: 1) using a Naive Bayes
+\paragraph{Our proposed priming definition yields general purpose measure of priming effects.}
+We used three approaches to detect priming effects: 1) using a Naive Bayes
 classifier to measure $\hat{\theta}_\text{NB}$, 2) tallying the number of 
 culture- and food-oriented labels, and 3) comparing the relative specificity
-of labels based on an ontology.  Of the three, measuring $
-\hat{\theta}_\text{NB}$ was the most sensitive.
+of labels based on an ontology.  Of the three, $\hat{\theta}_\text{NB}$ was 
+the most sensitive.
 
@@
 the priming effects and their potential to impact decisions made on the basis
-of worker outputs.  In the case of a binary decision, $\theta$
+of worker outputs.  In the case of a 1-bit binary decision, $\theta$
 describes the worst-case bias introduced by failing to control for priming 
 effects.
-
 \paragraph{Batching tasks for better HPU performance.}
@@
 should first be sorted into batches based on their similarity. This could be 
-accomplished by beginning with a first, coarse characterization of unsorted 
-images, followed by batching based on the labels obtained. Then, the batches
-of similar images could be served for a second round of finer labeling. 
-The sorting and re-labeling could then in principle be repeated.
+accomplished by beginning with a first, coarse labeling of unsorted 
+images, followed by bundling based on the similarity of coarse labels. Then, 
+bundles of similar images could be served for a second round of finer 
+labeling.  The sorting and re-labeling could in principle be repeated.
 
-In effect, this creates a hierarchical workflow, where the first, 
-coarsely-characterizing HPUs provide a stream of labeled images that is 
-split (batched) and fed to other HPUs for finer characterization.  This 
-workflow exhibits an interesting difference between HPUs and CPUs.  In general,
-whenever an aspect of a problem can be parallelized when employing CPUs, one
-gains efficiency.  But here, because of HPU hysteresis, we see an example where
-one might sacrifice accuracy through parallelization.
+Such a workflow involves serial processing, which points to an interesting  
+possible difference difference between HPUs and CPUs.  In general, whenever 
+an aspect 
+of a problem can be parallelized when employing CPUs, one gains efficiency.  
+But here, because of HPU hysteresis, one might gain precision by using HPUs 
+with a more serialized algorithm. Further
+testing is needed to determine the gain in precision from this approach.
 
-\subsection*{Conclusion}
+\bibliography{newbib.bib} 
+\bibliographystyle{aaai}
+\begin{figure*}
+	\centering{
+		\includegraphics[scale=0.90]{figs/taskImages/testImages.jpg}
+		\caption*{Figure S1: Testing image set. These images were presented 
+			to all workers in the order shown after the initial set of images.}
+	}
+\end{figure*}
 
-Inter-task priming can have a strong effect.  
-For a canonical image-labeling task, inter-task priming was stronger in its 
-effects on the orientation and specificity of labels than was the disclosure of
-semantically loaded funder names.  Requesters on microtask platforms should 
-take care to avoid introducing biases due to the batching and ordering tasks 
-they serve to workers.  At the same time, inter-task priming might be exploited to improve task output, for 
-example, to drive more (or less) nuanced responses.
+\begin{figure*}
+	\centering{
+	\includegraphics[scale=0.90]{figs/taskImages/ambiguous.jpg}
+	\caption*{Figure S2: Ambiguous image set. These images were presented to 
+		workers from certain treatments (see \textbf{Table 1}) in the main 
+		text.}
+	}
+\end{figure*}
 
-We demonstrated that our algorithmic definition of priming, and its 
-implementation using a Naive Bayes classifier, provides a sensitive,
-general-purpose method for detecting priming.  Even when the expected effects 
-on label orientation and specificity were slight, $\theta_\text{NB}$ 
-was significant.  $\theta_\text{NB}$ provides direct statistical evidence that 
-populations have been affected by priming, even when the nature of the 
-effects are not understood.
+\begin{figure*}
+	\centering{
+		\includegraphics[scale=0.90]{figs/taskImages/cultural.jpg}
+		\caption*{Figure S3: Cultural image set. These images were presented 
+			to workers from certain treatments (see \textbf{Table 1}) the 
+			main text.}
+	}
+\end{figure*}
 
-\subsection*{Materials and Methods}
-Omitted due to length.  This will be added to supplementary material.
-
-\begingroup
-\renewcommand{\chapter}[2]{}
-\bibliography{newbib.bib}
-\endgroup
-\bibliographystyle{plain}
-
-\subsection*{Motivation}
-I am near the beginning of my PhD studies, and have joined Derek Ruths' lab 
-with the expressed purpose of performing human computation research.
-My interests lay at the intersection of game theory, psychology, and 
-computation.  The overarching goal for my research relates to group 
-decisionmaking, and can be phrased in the following way: ``what are the factors
-that influence the social efficiency of collective decisionmaking?'' I
-view decisionmaking as the central activity of all social organizations, and 
-I view this as a computational process.  My reason for 
-wanting to attend the PhD Consortium at HCOMP is threefold.  First, I wish to
-discuss my ideas with others, get feedback, and learn more about how the 
-community frames such questions, to help me as I finalize my PhD proposal 
-into concrete research aims.  Second, I hope to make connections to other 
-researchers who are interested in similar research questions.  Finally, I wish
-to obtain feedback on a crowdsourcing platform that I have implemented (and
-hopefully pique other researcher's interest), which I intend to use in my
-research.
+\begin{figure*}
+	\centering{
+		\includegraphics[scale=0.90]{figs/taskImages/ingredients.jpg}
+		\caption*{Figure S4: Ingredients image set. These images were presented
+			to workers from certain treatments (see \textbf{Table 1}) in the 
+			main text.}
+	}
+\end{figure*}
 \end{document}

### 2014-10-12 docs/publications/2014.08_HCOMP/abridged_man.tex
work on manuscript

--- 2014-10-12 docs/publications/2014.08_HCOMP/_man.tex
@@
 \begin{document}
+
 \maketitle
@@
 so we investigate interactions between earlier tasks and later ones, which we 
-call ``inter-task'' effects.  
+call \textit{inter-task} effects.  
 Existing research investigates many task design factors, such as 
-``framing'', on the quality of responses, but to our knowledge, does not 
+\textit{framing}, on the quality of responses, but to our knowledge, does not 
 address inter-task effects.  
-We use a canonical image-labeling task on Amazon Mechanical Turk 
+We used a canonical image-labeling task on Amazon Mechanical Turk 
 to measure the impact of inter-task and framing effects on the focus and 
 specificity of labels that workers provide.
-We also introduce an algorithmic definition of priming, which measures the 
-worst-case bias introduced into responses.
-We find that inter-task effects produced a much stronger impact than framing, 
-and demonstrate that our novel priming definition yields a generalized 
-measure of priming effects when combined with machine learning algorithms.
+We found that inter-task effects had a much stronger impact than framing, 
+and that workers provided more specific labels when labeling 
+a series of images that were similar to one another.
+
 \paragraph{Keywords:} priming, framing, crowdsourcing.
@@
 Here, we highlight an important way in which HPUs differ from CPUs, with 
-serious implications for the design of tasks.  It is well known that people 
+serious implications for the design of tasks.  It is well-known that people 
 are subject to priming effects 
@@
 responses during subsequent ones. We call such effects 
-\textit{inter-task priming}.  Inter-task priming would amount to a kind of
+\textit{inter-task effects}.  Inter-task effects would amount to a kind of
 \textit{hysteresis}, meaning that HPU output is not only a function of the 
@@
 workers \cite{paolacci2010running}, and user-interface design 
-\cite{Finnerty2013}.  Research has also investigated \textit{framing}, 
+\cite{Finnerty2013}.  Researchers have also investigated \textit{framing}, 
 by testing the effects of disclosing the workflow context 
 \cite{Kinnaird2012281}, and the purpose of tasks 
-\cite{chandler2013breaking}.  To our knowledge, no study has investigated the 
-effects of inter-task priming.
+\cite{chandler2013breaking}.  To our knowledge, no study has investigated 
+inter-task effects.
 
-To characterize the effects of inter-task priming, we present a novel  
-\textit{algorithmic definition of priming}, and a general method 
-for measuring priming effects using machine learning algorithms.  
-Rather than focus on internal psychological mechanisms, our definition 
-focuses on the impact that priming has to the downstream application of human 
-computation, providing a generalized measure of bias.
+We investigated inter-task effects on the MTurk platform, using image-labeling 
+tasks, one of the most common kinds of tasks on MTurk
+\cite{chandler2013breaking,Berinsky2012351,Finnerty2013,paolacci2010running}.  
+Workers were required to label images featuring 
+food and culture.  We regard these tasks as consisting of an 
+\textit{initial} and a \textit{test set}, but, crucially, no
+distinction was made between these sets from the view of the worker.
+We varied the images in the initial tasks, while keeping those in the test set 
+the same, to analyze the effects that the initial tasks had on the 
+content and specificity of labels attributed in the test set.
 
-In the present work, we investigate inter-task priming on the Amazon 
-Mechanical Turk platform, using an image-labeling task, one of the most common 
-kinds of tasks on that platform 
-\cite{chandler2013breaking,Berinsky2012351,Finnerty2013,paolacci2010running}.  The task requires workers to label ten 
-images featuring 
-food and culture.  We regard these images as being made up of an 
-\textit{initial} and \textit{test set}, but, crucially, there is no
-distinction made between these sets, nor any interruption in the flow of tasks 
-from the view of the worker.
-We vary the initial set of images, while keeping the test set the same to 
-analyze the effect that that the initial images have on the labels that 
-workers' attribute to the test set.  We measure effects using our novel 
-approach, as well as looking for changes in the content of labels and label 
-specificity based on an ontology we developed for that purpose.
-
-As a point of comparison, we subject some groups of workers to a kind of
-\textit{framing}: we disclose a fictitious, semantically-loaded name for 
+As a point of comparison, we subjected some groups of workers to a kind of
+\textit{framing}, by disclosing a fictitious, semantically-loaded name for 
 the requester funding the tasks.
 The names were chosen to suggest the requester's interest in a specific 
-aspect of the image content.  We expect this would cause workers 
+aspect of the image content.  We expected this would cause workers 
 to provide more labels, and greater specificity, relating to this 
@@
 
-Surprisingly, we find that inter-task effects are much stronger than the 
+Surprisingly, we found that inter-task effects were much stronger than
 framing.  Our results show that initial tasks can significantly alter the 
@@
 
-Our analysis also highlights important advantages of our novel definition of 
-priming.  Our approach incorporates no prior knowledge about the nature
-of the task whatsoever.  In contrast, we also sought to detect priming
-based on its direct effects on label content and specificity,
-drawing on prior knowledge about the images and label semantics.
-Remarkably, while being more general, our definition yields a more sensitive
-measure of priming when combined with machine learning algorithms. 
-This approach could be applied to detect priming when one does not 
-\emph{a priori} know whether any priming has occurred, 
-nor what the nature of the effects might be.
-\subsection*{An algorithmic definition of priming}
-Our goal in creating a definition of priming is to capture the effects of 
-priming on human computation \textit{applications}.  This motivates us to 
-seek a definition of priming in terms of its ability alter HPU 
-output rather than in terms of psychological mechanisms.
-
-We define priming with respect to a task $\mathcal{T}$.  People will always differ in their initial knowledge, specific 
-aptitudes, and in many other intrinsic aspects.  Moreover, priming may not be 
-``complete'', in the sense that people's experiences before
-priming may continue to have residual effects.  Therefore, we define priming 
-in relation to populations, which we regard as having stable distributions of
-such latent attributes.
-
-One difficulty in constructing a definition of priming is that there would 
-appear to be no defensible notion of a ``neutral'' or ``unprimed state''.  
-While arguments could perhaps be made that one treatment or another is 
-\textit{more} ``neutral'', we choose to define priming relatively, and speak 
-of one treatment being \textit{differently primed} from another.
-
-To set up the definition, when a population of people $\mathcal{P}$ performs
-a task $\mathcal{T}$ thus producing outputs $\mathcal{L}$,
-we will write $\mathcal{T}(\mathcal{P}) = \mathcal{L}$.
-
-\vspace{2mm}
-\begin{mydef}
-	\upshape
-	Two mutually exclusive populations of people, $\mathcal{P}_0$ and 
-	$\mathcal{P}_1$, are uniformly and randomly subsampled from an initial 
-	population $\mathcal{P}$, and are exposed to (possibly) different priming 
-	treatments. Each population performs a task $\mathcal{T}$, 
-	producing outputs $\mathcal{T}(\mathcal{P}_0)$ and 
-	$\mathcal{T}(\mathcal{P}_1)$.
-	These populations are subsampled, producing 
-	$P_0 \subset \mathcal{P}_0$ and
-	$P_1 \subset \mathcal{P}_1$. A uniform, random bit is chosen, 
-	$b\in _R \{0,1\}$, and a single worker $p$ is uniformly and randomly 
-	sampled from 
-	$\mathcal{P}_b \setminus P_b$.
-	We say that $\mathcal{P}_0$ and $\mathcal{P}_1$ 
-	\emph{differ in priming by a degree at least $\theta$},
-	if there exists a \emph{distinguisher algorithm} $\mathcal{A}$ that takes as input 
-	$\langle\mathcal{T}(J)$, $\mathcal{T}(K)$, $\mathcal{T}(\{p\})\rangle$
-	and outputs a guess for $b$ with accuracy $\frac{1+\theta}{2}$.  
-\end{mydef}
-
-\begin{figure*}
-	\centering{
-	\includegraphics[scale=0.94]{figs/f1-thetas_full_pairwise25_img1.pdf}
-	\caption{ \footnotesize{
-		Empirical difference in priming, $\hat{\theta}_\text{NB}$, between 
-		various treatments.  The difference in priming between each pair of 
-		treatments 
-		was determined by cross-validation of a Naive Bayes classifier trained
-		to classify workers based on the labels they attributed to the first
-		image of the test set. Each panel compares a basis treatment,
-		indicated above the panel, to various treatments indicated on the
-		abscissa.  We can conclude, with 95\% confidence, that the classifier
-		is performing better than chance when $\hat{\theta}_\text{NB}$ 
-		exceeds 0.168, indicated by the dotted line.
-	}}
-}
-\end{figure*}
-
-In the language of computer science, $\mathcal{A}$ is a classifier performing
-a binary classification.  The measure $\theta$ can range between 0 and 1, and 
-indicates how much better the performance of the best possible classifier is 
-compared to a random guess. We intentionally leave the details of 
-$\mathcal{A}$ unrestricted because the theoretical value of $\theta$ should 
-depend on the inherent differences between the populations, rather than on 
-the performance of a particular classifier.
-
-In practice, some particular classifier $\mathcal{C}$ is tested (using e.g. 
-cross-validation) yielding a statistical estimate of its performance 
-$\hat{\theta}_\mathcal{C}$. This
-$\hat{\theta}_\mathcal{C}$ acts as a lower bound for the 
-theoretical value of $\theta$, because there might 
-exist some other classifier $\mathcal{C}'$ with 
-$\hat{\theta}_\mathcal{C'}>\hat{\theta}_\mathcal{C}$.
-For our experiment, we use a Naive Bayes classifier because it is easy to
-implement and performs well across a broad range of classification tasks.
-
-To interpret $\hat{\theta}_\mathcal{C}$, imagine that some choice 
-$\mathcal{C}$ is to be made between two options on the basis of worker 
-outputs (e.g. whether or not to flag an image as inappropriate). Any such 
-binary choice has the formal structure of a distinguisher that only considers 
-the last of its three inputs. Thus, we can directly compare $\mathcal{C}$ to 
-the optimal distinguisher, $\mathcal{A}$.  If, prior to knowing the input to 
-$\mathcal{C}$, either of its outcomes is equally likely, then the worst 
-possible bias that priming can introduce is bounded above by $\theta$. 
-This means that $\hat{\theta}_\mathcal{C}$ estimates a 
-lower bound for the worst-case bias introduced in a binary 
-decision that provides a full bit of information, made on the basis of worker 
-outputs, when one failed to control for the corresponding priming treatments.
 \subsection*{Experimental Setup}
@@
 		\hline                       
-		Treatment & Funder & Priming Image Set	\\ 
+		Treatment & Funder & Initial Image Set	\\ 
 		\hline                       
@@
 	\caption{ \footnotesize{ 
-		Workers were uniformly randomly assigned to one of the 
+		Workers were assigned uniformly at random to one of the 
 		treatments listed above. 
@@
 \end{table}
-We solicited 900 MTurk workers to perform an image-labeling task relating to
-food and culture.  The workers were randomly assigned to one of seven 
-treatments shown in \textbf{Table 1}.  Depending on their treatment, workers were then shown the 
-name of a research funder, or this step was skipped.
-Next, workers were shown ten images, one at a time and were required to provide
-five labels for each.  For the purpose of analysis, we divide the images
+We solicited 900 MTurk workers to perform image-labeling tasks relating to
+food and culture.  The workers were randomly assigned to one of the treatments
+shown in \textbf{Table 1}.  The treatments $\textsc{ingr}_{fund,img}$ and 
+$\textsc{cult}_{fund,img}$ used (respectively) the image sets of 
+$\textsc{ingr}_{img}$ and $\textsc{cult}_{img}$, but also 
+incorporated framing.  The addition of framing did not have a substantial
+impact on the results for these treatments, so we do not discuss 
+$\textsc{ingr}_{fund,img}$ and $\textsc{cult}_{fund,img}$ further.
+
+Workers from all treatments were shown brief instructions.  Depending on 
+their treatment, workers were then 
+shown the name of a research funder, or this step was skipped.
+Next, workers were given a series of ten image-labeling tasks.  Each task 
+required workers to privide five discriptive labels for an image.  For the 
+purpose of analysis, we divided the tasks
 into \textit{initial} and \textit{test} sets, comprising respectively the 
-first five and last five images.  From the perspective of the worker, there 
+first five and last five tasks.  From the perspective of the worker, there 
 was no distinction or interruption between the initial and test sets. 
-Depending on the treatment, one of three initial image sets was chosen, but
-the test set was always the same.
+Depending on the treatment, one of three sets of images was used for the
+initial tasks, but the images in the test set were always the same.
 
-The test image set comprised images containing prepared meals and featured a 
+The images from the test set contained prepared meals and featured a 
 prominent, identifiable culture (see \textbf{Fig. S1}).
@@
 \subsection*{Results}
-\paragraph{Inter-task priming was strong, while framing was weak.}
-We tested for priming effects using our algorithmic definition, implemented 
-with a Naive Bayes classifier.  The classifier's accuracy
-in cross-validations involving each pair of treatments is shown in 
-\textbf{Fig.1}.
-
-With some exceptions, the classifier performed significantly better 
-than chance when distinguishing treatments that had different initial tasks.  
-This demonstrates that inter-task effects were strong. Of the sixteen 
-treatment pairs having different initial tasks, the classifier was unable to
-distinguish treatments significantly better than chance in three cases.
-Each cases involved distinguishing treatments having the ambiguous and 
-ingredients set.  Later we discuss the similarity between image sets, and 
-we will argue that this is because the ambiguous and ingredients sets are 
-similar.
-
 \begin{figure*}
@@
 		labels) for 
-		various images and treatments.  
-		\textbf{B}) Relative specificities of treatments
-		indicated along the abscissa compared to those indicated above the 
-		plot.  The size of the bar indicates how much more specific
+		various treatments.  
+		\textbf{B}) Relative specificities of treatments,
+		indicated along the abscissa, compared to those indicated above the 
+		plot, according to \textbf{Eq. 2}.  The size of the bar indicates how 
+		much more specific
 		the labels from one treatment are compared to the other, and points 
-		toward in the direction of the more specific treatment.  Error bars
+		toward the more specific treatment.  Error bars
 		indicate 95\% confidence intervals.
@@
 \end{figure*}
-In contrast, the classifier never performed significantly better than chance
-when distinguishing treatments that differed only in framing.  Thus, framing 
-effects were rather weak.  In fact, framing effects were generally weak in
-our results, so we omit treatments involving framing from the remainder of
-our presentation to save space.  We encourage the interested reader to look
-at the results for these treatments in the supplementary material.
-\paragraph{Earlier tasks orient workers' focus during later tasks.} 
+
+\paragraph{Earlier tasks oriented workers' focus during later tasks.} 
 Since the initial images were chosen to emphasize either food (ingredients set)
@@
 
-\begin{figure}
-	\centering{
-	\includegraphics[scale=0.7]{figs/longitudinal_theta_excess-culture.pdf}
-	\caption{\footnotesize{
-		\textbf{A}) Difference in priming between \textsc{ambg} and 
-		$\textsc{cult}_{img}$ measured based on the accuracy of a Naive Bayes 
-		classifier during cross-validation, when trained on labels from the
-		test images indicated along the abscissa.
-		\textbf{B}) Excess cultural orientation of labels attributed to
-		the test images indicated on the abscissa, by workers from
-		$\textsc{cult}_{img}$ relative to those attributed by workers from
-		\textsc{ambg}, calculated using \textbf{Eq. 3}.  Error bars indicate
-		95\% confidence intervals.
-	}}
-}
-\end{figure}
 When we tallied labels attributed to the first image of the test set, 
@@
 more culture-oriented labels and less food-oriented ones than those from
-\textsc{ambg}
-(see \textbf{Fig. 2A}).  The inter-task effect was so strong that the 
-proportion of food- and culture-oriented labels in $\textsc{cult}_{img}$ was
-essentially the reverse of that in \textsc{ambg}.  However, the 
-composition of labels attributed by $\textsc{ingr}_{img}$
-was not significantly different from those attributed by \textsc{ambg}.  This 
-shows that inter-task effects \textit{can} profoundly alter workers' focus. 
-Again, we 
-will argue later that the ambiguous and ingredients image sets are, in fact, 
-quite similar.
+\textsc{ambg} (see \textbf{Fig. 1A}).  The inter-task effects were so 
+strong that the proportion of food- and culture-oriented labels in 
+$\textsc{cult}_{img}$ was essentially the reverse of that in \textsc{ambg},  
+showing that inter-task effects \textit{can} profoundly alter workers' focus.
+
+\paragraph{Inter-task effects were stronger than framing effects.}
+On the other hand, the labels attributed by 
+$\textsc{ingr}_{fund}$ were not significantly different in composition from 
+those attributed by $\textsc{cult}_{fund}$.  Workers from the
+these treatments were told that the tasks were funded by, respectively, 
+the ``Foundation for Nutritional Awareness'' and the ``Foundation for Cultural 
+Recognition''.  We find it remarkable that inter-task effects were stronger
+than those brought about by framing the tasks with reference to specific 
+image content.
+
 \paragraph{Earlier tasks influenced workers' level of specificity.} 
-Using the ontology described in the previous section, we can compare the 
+The ontology described in the previous section allows us to define the relative
 specificity of two labels $\ell_1$ and $\ell_2$. We say that $\ell_2$ is more 
@@
 $m$, and 0 otherwise.
-We then define the relative specificity of two treatments, $\mathcal{U}$ and 
-$\mathcal{V}$, the $i$th image, denoted $S_i(\mathcal{U},\mathcal{V})$, to be 
-the mean relative specificity of two uniformly drawn workers:  
+We can then define the relative specificity of two treatments, $\mathcal{U}$ 
+and $\mathcal{V}$, with respect to the $i$th image, denoted $S_i(\mathcal{U},\mathcal{V})$, 
+to be the mean relative specificity of two uniformly drawn workers:  
 \begin{align}
@@
 
-Looking at labels attributed to the first test image, we found that workers 
+The relative specificities of various treatments, based on \textbf{Eq. 2},
+are shown in \textbf{Fig. 1B}.  We found that workers 
 from \textsc{ambg} were more specific than workers from
-either $\textsc{cult}_{img}$ or $\textsc{ingr}_{img}$.  When we compare 
+either $\textsc{cult}_{img}$ or $\textsc{ingr}_{img}$.  Comparing
 $\textsc{cult}_{img}$ to $\textsc{ingr}_{img}$, we found that workers from
@@
 effects do substantially influence the specificity of labels that workers 
-provide.  When we discuss image similarity, below, we will explore a possible
-mechanism for this effect.
-\paragraph{Inter-task effects ``wash out'' quickly.}  
+provide.  We will return to this point below, where we propose a mechanism to 
+explain these differences in specificity.
+
+\paragraph{Inter-task effects ``washed out'' quickly.}  
 It would stand to reason that, as workers proceed through the test images, 
@@
 observed inter-task effects.
-Looking at the classifier performance, $\hat{\theta}_\text{NB}$, with respect 
-to the treatments \textsc{ambg} and $\textsc{cult}_{img}$, we find that 
-performance does drop off dramatically after just the first image 
-(see \textbf{Fig. 3A}).
-This suggests that inter-task effects primarily arise between consecutive 
-tasks, but that a residual effect can persist for at least five tasks (we 
-note, however that although the classifier performance seemed better than 
-chance for the fourth test image, this cannot be asserted with 95\% 
-confidence).
 
-Next we observed how inter-task effects on label composition (i.e. food- vs 
-culture-oriented labels) evolve as workers proceed through test images.
-We define the \textit{excess cultural orientation} as the number of 
-culture-oriented labels minus the number of food oriented ones.  To 
-meaningfully compare the excess cultural orientation between test images, we 
-must, however, account for the fact that some images inherently carry more 
+\begin{figure}
+	\centering{
+	\includegraphics[scale=0.7]{figs/longitudinal_theta_excess-culture_cut_for_hcomp.pdf}
+	\caption{\footnotesize{
+		Excess cultural orientation ($\Delta_\mathbf{cult}$) of labels 
+		attributed by $\textsc{cult}_{img}$ relative to those attributed by 
+		\textsc{ambg} 
+		($\Delta_\mathbf{cult}$ is defined in \textbf{Eq. 3}).  Error bars 
+		indicate 95\% confidence intervals.
+	}}
+}
+\end{figure}
+To investigate the evolution of inter-task effects, we define the 
+\textit{excess cultural orientation} to be the number of 
+culture-oriented labels minus the number of food oriented ones.  This measures
+how culture-oriented a given image is.  Of course, we must account for the 
+fact that some images inherently carry more 
 cultural content than others. In keeping with our notion of priming 
-\textit{difference}, we calculate the excess cultural content for both 
-$\textsc{cult}_{img}$ and \textsc{ambg}, and take their difference to be
+\textit{difference}, we calculate the excess cultural content for 
+both $\textsc{cult}_{img}$ and \textsc{ambg}, and take their difference to be
 the \textit{relative} excess cultural content, $\Delta_{cult}$.  Formally,
@@
 rapidly, remaining positive but not to a statistically significant extent
-(see \textbf{Fig. 3B}).  
-This is similar to the behavior of $\hat{\theta}_\text{NB}$, however, because
-the statistical significance of $\Delta_{cult}$ dropped more quickly, 
-$\hat{\theta}_\text{NB}$ appears to be a more sensitive measure of inter-task 
-effects.
-\paragraph{Inter-task similarity encourages more specific labels.}
-To continue with the analysis, we seek a measure of image similarity.  The 
+(see \textbf{Fig. 2}).
+
+\paragraph{Inter-task similarity encouraged more specific labels.}
+To continue with the analysis, we sought a measure of image similarity.  The 
 characterization of image content is a deeply complex issue that has been 
@@
 \cite{panofsky1939studies,shatford1986analyzing,Tversky1977327,Jaimes20002}.
-\textit{Perceptual similarity} is a particularly recalcitrant concept.
-
-However, in the present study, we are more interested how similar two 
-sets of images are, \textit{with respect to the labeling task}, which is much
-simpler to operationalize than general perceptual similarity.  Here, we 
-measure image similarity by looking at the fraction of labels that they share. 
+However, in the present study we are more interested how similar two 
+sets of images are, \textit{with respect to the labeling task}, which is
+simpler to operationalize than general perceptual similarity.  For this purpose
+we measured the similarity between two sets of images by looking at the 
+fraction of labels that they shared. 
 Formally, to measure the similarity between two \textit{sets of images}, $X$ 
-and $Y$, we compute the Jacquard index between the sets of labels attributed 
+and $Y$, we computed the Jaccard index between the sets of labels attributed 
 to them:
@@
 \end{align}
+where $L(X)$ denotes the set of labels attributed to $X$.
+
 \begin{table}
@@
 \end{table}
-where $L(X)$ denotes the set of labels attributed to $X$.
 
 The pairwise similarities of the image sets are presented in \textbf{Table 2}. 
-First, observe that the ambiguous and ingredients sets are much more similar 
-to each other than either is to the culture set.  Recalling the data presented
-in \textbf{Fig. 1}, this helps explain why two treatments could not be 
-distinguished on the basis of having differing initial sets corresponding to
-ambiguous and cultural.  This also explains why \textsc{ambg} and 
-$\textsc{cult}_{img}$ had similar label compositions in \textbf{Fig. 2A}.
+In particular, we draw the reader's attention to the similarity between the 
+three initial sets and the test set.  The ambiguous set was the most similar 
+to the test set, followed by the
+ingredients set, while the cultural set was most different.
+Note the correspondence between these degrees of similarity and the ensuing 
+relative specificity of labels: the more similar the 
+initial images were to those in the the test set, the more 
+specific were the labels attributed to the test set  (c.f. \textbf{Fig. 1B}).
 
-Next we draw attention to the similarity between the initial sets and the test 
-set.  The ambiguous set is the most similar to the test set, followed by the
-ingredients set, with the cultural set being most different.
-Observe that these levels of similarity mirror the label specificity for the 
-corresponding treatments (c.f. \textbf{Fig. 2B}).
-
-This suggests that labeling a series of images that are similar to 
-one another might encourage workers to use more specific terminology.
+This suggests that presenting a series of very similar images elicits more 
+specific labels.
 Such a phenomenon would be consistent with the psychological mechanism known 
@@
 desensitized to non-salient stimuli to which she is repeatedly 
-exposed.  Consider that workers who initially 
+exposed \cite{versace2001negative,mayr2007negative,de2008negative}.  Consider that workers who initially 
 labeled the ambiguous image set had already seen five images showing 
@@
 characterization tasks that have very similar content, workers' focus 
-will tend to be directed away from generic, shared attributes, towards those 
+will tend to be directed away from generic, shared attributes, toward those 
 attributes that are specific and distinguishing.
@@
 workers label images.  In particular, we observed that prior tasks influence
-the specificity and content of labels.  Surprisingly, framing a task by 
-indicating a semantically-loaded funder had much milder effects on worker 
-outputs, generally below the statistical power of our tests.
+the specificity and content of labels.  Surprisingly, inter-task effects were 
+much stronger than framing the tasks by disclosing a semantically-loaded 
+name for the task-funder.
 
-We therefore caution those designing studies using human computation: even if 
+We caution those designing studies using human computation: even if 
 the requester has eliminated surrounding influences to every practical extent, 
@@
 Due consideration should be given to how tasks are bundled together.
-While our measurements of $\hat{\theta}_\text{NB}$ indicated that inter-task 
-effects persisted even to the fifth test image, the most severe effects arise 
-between consecutive tasks.
-\paragraph{Our proposed priming definition yields general purpose measure of priming effects.}
-We used three approaches to detect priming effects: 1) using a Naive Bayes
-classifier to measure $\hat{\theta}_\text{NB}$, 2) tallying the number of 
-culture- and food-oriented labels, and 3) comparing the relative specificity
-of labels based on an ontology.  Of the three, $\hat{\theta}_\text{NB}$ was 
-the most sensitive.
 
-In one sense, this is not surprising because the Naive 
-Bayes classifier takes into account the frequency of occurrence of all labels 
-encountered during training.  But it is remarkable that the 
-method which incorporates neither prior knowledge about the image contents nor 
-label semantics, outperforms those that do.  This is a powerful feature 
-because, given the outputs from two sets of workers, one can test whether they 
-have been differently primed without knowing how that priming might manifest.
-
-Our algorithmic definition of priming is phrased in terms of worker outputs
-rather than psychological phenomena.  This provides a connection between
-the priming effects and their potential to impact decisions made on the basis
-of worker outputs.  In the case of a 1-bit binary decision, $\theta$
-describes the worst-case bias introduced by failing to control for priming 
-effects.
 \paragraph{Batching tasks for better HPU performance.}
@@
 image-labeling might be used to tune the specificity of labels.  For example,
-If one seeks very nuanced labeling, our results suggest that the images 
+if one seeks very nuanced labeling, our results suggest that the images 
 should first be sorted into batches based on their similarity. This could be 
@@
 Such a workflow involves serial processing, which points to an interesting  
-possible difference difference between HPUs and CPUs.  In general, whenever 
-an aspect 
-of a problem can be parallelized when employing CPUs, one gains efficiency.  
-But here, because of HPU hysteresis, one might gain precision by using HPUs 
-with a more serialized algorithm. Further
-testing is needed to determine the gain in precision from this approach.
+potential difference between HPUs and CPUs.  In general, whenever 
+an aspect of a problem can be parallelized when employing CPUs, one gains 
+efficiency.  This is, of course, without any sacrifice to precision.  
+But here, because of HPU 
+hysteresis, one might gain precision by using HPUs with a more serialized 
+algorithm. Further testing is needed to determine the gain in precision from 
+this approach.
 

### 2014-10-12 docs/publications/2014.09_SCIENCE/ban.tex
work on manuscript

--- 2014-09-23 docs/publications/2014.09_SCIENCE/man.tex
@@
 
-\title{Human computational hysteresis: measuring inter-task effects}
+\title{Computational hysteresis:\\ inter-task effects in human computation}
 
@@
 \author
-{John Smith,$^{1\ast}$ Jane Doe,$^{1}$ Joe Scientist$^{2}$\\
+{Edward Newell, Derek Ruths,\\
 \\
-\normalsize{$^{1}$Department of Chemistry, University of Wherever,}\\
-\normalsize{An Unknown Address, Wherever, ST 00000, USA}\\
-\normalsize{$^{2}$Another Unknown Address, Palookaville, ST 99999, USA}\\
+\normalsize{\texttt{edward.newell@mail.mcgill.ca}}\\
+\normalsize{\texttt{druths@networkdynamics.org}}\\
+\normalsize{School of computer science, McGill University,}\\
+\normalsize{3630 rue University, Montreal, Quebec, H3A 0C6, Canada}\\
 \\
-\normalsize{$^\ast$To whom correspondence should be addressed; E-mail:  jsmith@wherever.edu.}
 }
@@
 \textit{inter-task effects}, are neither random, nor are they formally part 
-of the instructions given to the HPU.  The ``leakage'' of information from 
-recently performed tasks into HPU outputs is a potentially strong source of 
-systematic bias, which complicates the the algorithmic view of HPUs. 
+of the instructions given to the HPU.  The ``leakage'' of information, 
+from recently performed tasks, into HPU outputs, is a potentially strong 
+source of systematic bias.
 Inter-task effects would amount to a kind of \textit{hysteresis}, meaning 
@@
 
-Here we make two contributions towards understanding inter-task effects
+Here we make two contributions towards understanding inter-task effects,
 and HPU hysteresis in general.  We present a framework for treating this 
 source of bias in the context of HPU algorithms, and we measure the impact of
-inter-task effects experimentally in a canonical HPU task: the labeling of 
-images.
+inter-task effects experimentally.
 
 Using the  Amazon Mechanical Turk (Mturk) platform, we solicited workers to 
-perform a series of image-labeling tasks.  
+perform a series of image-labeling tasks.  We chose this as the canonical
+microtask because image labeling tasks are one of the most common kinds of
+microtasks
+\cite{chandler2013breaking,Berinsky2012351,Finnerty2013,paolacci2010running}, 
+and it seems likely that human computation will have a long-term role
+in computer vision research \cite{5543192}.
 In these tasks, workers labeled images featuring iconic cultural scenes,
@@
 about twice as strong. 
-Our results show that initial tasks can significantly alter the subject 
-matter on which worker's labels focus. We also found that inter-task 
-effects can induce workers to provide labels of greater or lesser specificity. 
-This suggests that careful consideration should be given to the bundling of 
+Our results suggest that initial tasks can change what workers choose to focus
+in in later tasks.  We also found that inter-task 
+effects altered the level of specificity of worker's labels.  This suggests 
+that careful consideration should be given to the bundling of 
 tasks when designing a study using a microtask platform.
@@
 algorithms. Thus, before we discuss inter-task effects experimentally, we 
-discuss formal definitions for priming as computational phenomenon.  Our
-discussion will lead to a natural definition of priming that enables 
-comparisons of the severity priming effects accross applications, and enables
-the measurement of priming using machine learning tools.
+describe candidate definitions for priming as computational phenomenon.  This 
+leads to a natural definition of priming that provides a consistent measure of 
+the severity of priming accross applications, and enables the measurement of 
+priming using machine learning tools.
 
@@
 \textit{differently primed} from another.  We present three definitions for 
-the difference in priming between HPU populations, each having different 
-merits, and then we discuss their relationships. To proceed with the 
+the difference in priming between HPU populations, each with different 
+advantages, and then we discuss their relationships. To proceed with the 
 definitions, we will assume that two populations of HPU’s, $\mathcal{P}$ and 
@@
 
-For the first defenition, we focus on the direct effects that running an 
-algorithm on differently primed HPUs has on the algorithm's output.
+For the first defenition, we focus on the effect that differently primed
+HPUs can have on the output of a human computation algorithm.
 
@@
 \end{mydef}
-Thus, in \textbf{Definition \ref{def:bias}}, $\theta_\mathrm{bias}$ has a 
+In \textbf{Definition \ref{def:bias}}, $\theta_\mathrm{bias}$ has the 
 straightforward interpretation as an upper bound on the amount of bias induced 
 on any yes-or-no decision, due to the difference in priming of 
-$\mathcal{P}$ and $\mathcal{Q}$.  Although easy to interpret, it is, however, 
+$\mathcal{P}$ and $\mathcal{Q}$.  Though easy to interpret, it is admittedly
 not clear how $\theta_\mathbf{bias}$ could be measured in practice.
 
-Next we attempt to phase the difference in priming between $\mathcal{P}$ and
-$\mathcal{Q}$ in terms of the extent to which their work products are 
+Next we to phrase the difference in priming between $\mathcal{P}$ and
+$\mathcal{Q}$ in terms of the extent to which their work-products are 
 distinguishable algorithmically. To facilitate this definition, we make 
-use of the notions of a \textit{distinguisher} and a \textit{validation} test.
+use of the notions of a \textit{distinguisher} and a \textit{validation test}.
 \begin{mydef}
@@
 	random from one of the populations, decided by the bit: $r \in_R R_b$. 
-	Feed $r$ to $\mathcal{D}$, and if $\mathcal{D}(r) = b$, we say 
-	$\mathcal{D}$ guessed correctly, and the value of $V$ is 1, 
+	Input $r$ into $\mathcal{D}$, and if $\mathcal{D}(r) = b$, we say 
+	$\mathcal{D}$ \emph{guessed correctly}, and the value of $V$ is 1, 
 	otherwise $V = 0$.
@@
 	A distinguisher that guesses randomly will still be correct half of the 
-	time. Therefore, denote the performance of $\mathcal{D}$ as 
-	$\eta_\mathcal{D}(P, Q)$:
+	time. Therefore, denote the performance of $\mathcal{D}$ by 
+	$\eta_\mathcal{D}(P, Q)$, and let
 	$$
-		\eta_\mathcal{D}(P,Q) = 2\cdot \mathrm{E}\{V(\mathcal{D},P,Q)\} - 1
+		\eta_\mathcal{D}(P,Q) = 2\cdot \mathrm{E}\{V(\mathcal{D},P,Q)\} - 1.
 	$$
@@
 	$$
+	\label{def:dist}
 \end{mydef}
-In the above definition, the performance simply rescales accuracy, so that when
-accuracy is 1/2 (i.e. as good as chance) performance is 0, and when accuracy 
-is perfect, performance is 1. This definition formulates the measurement of 
+In \textbf{definition \ref{def:dist}}, the performance simply rescales 
+accuracy, so that when
+accuracy is 1/2 (i.e. no better than chance) performance is 0, and when 
+accuracy is perfect, performance is 1. This definition formulates the 
+measurement of 
 priming effects in terms of a binary classification problem. As we will show,
-this allows us to apply tools from the machine learning field to the 
-measurement of difference in priming.  However, it is not immediately clear 
+this allows us to apply machine learning tools to the 
+measurement of priming.  However, it is not immediately clear 
 how this measure relates to the potential for priming to cause bias.
@@
 For the third definition, we focus on describing the inherent, statistical
-difference between work-products in $P$ and $Q$. Thus we define the difference
-in priming to be equal to the \textit{total variational distance}, or $l_1$-distance (denoted $D_{l_1}$) between $P$ and $Q$. 
+difference between work-products in $P$ and $Q$.  
 \begin{mydef}
 	\label{def:l1}
-	{\upshape total variational distance $\theta_{l_1}$:}
+	{\upshape Total variational distance $\theta_{l_1}$:}
+	Define the difference in priming between $\mathcal{P}$ and $\mathcal{Q}$ 
+	to be equal to the total variational distance (also known as 
+	$l_1$-distance, denoted $D_{l_1}$) between the work-products $P$ and $Q$:
 	$$
@@
 \end{mydef}
-The abvantage of definition \ref{def:l1} is that it provides connections
+The advantage of \textbf{definition \ref{def:l1}} is that it provides connections
 to statistical and information theory.
@@
 we simply denote the difference in priming as $\theta$.  We provide proofs
-in the supplementary material to demostrate this fact.  This means that we
+of this fact in the supplementary material.  This means that we
 can use machine learning tools to measure priming, while interpreting the
@@
 Before proceeding, we offer a few words of caution regarding the measurement 
-of $\theta$.
-
-Care must be taken in estimating $D_{l_1}$ from samples so as not to obtain
-an inflated estimate. In the so-called naive approach, one uses the frequency 
+of $\theta$.  In the so-called naive approach, one uses the frequency 
 with which a given work-product $x$ is obtained from HPUs in $\mathcal{P}$ to 
@@
 One can then estimate 
-$D_{l_1} = \sum_{x \in \mathcal{X}} \left|\hat{f}_P(x) - \hat{f}_Q(x) \right|/2$ using only the sample frequencies. But the number of samples, $|P|$ and 
+$
+D_{l_1} = 
+	\sum_{x \in \mathcal{X}} \left|\hat{f}_P(x) - \hat{f}_Q(x) \right|/2
+$ 
+using only the sample frequencies. But the number of samples, $|P|$ and 
 $|Q|$, must be much larger than the number of possible work-outputs, 
 $|\mathcal{X}|$, otherwise, this method produces an enormously inflated 
-estimate.
+estimate \cite{val-thesis}.
 
@@
 provides a canonical estimation approach based on first estimating the unseen 
-region of the support. This algorithm appears to perform very well in practice.
-Batu provided an alternative approach, which bypasses estimating the 
-probability mass functions, and relies on the more fundamental concept of 
-\textit{collisions}.
+region of the support\cite{val-thesis}. This algorithm appears to perform 
+very well in practice.  Batu provided an alternative approach, which bypasses 
+estimating the probability mass functions, and relies on the more fundamental 
+concept of \textit{collisions}\cite{batu2000testing,batu2013testing}, which 
+has recently been simplified \cite{chan2014optimal}.
 
 Both methods converge much more quickly than the naive approach. However, two 
-limitations remain that prevent their application. First, these relatively 
-recent approaches are not accompanied by any absolute guarantees of 
-statistical confidence, so it is not yet clear how to build confidence 
-intervals for a given estimate. Second, sophisticated as these methods are, 
-they still cannot provide reliable estimates when none of the elements of the 
-support recur in the samples (that is, when we never observe the same 
-work-product twice in our sample sets).
+basic limitations remain. First, these relatively recent approaches are not 
+accompanied by any absolute guarantees of statistical confidence, so it is not 
+clear how to build confidence intervals for a given estimate. Second, these 
+cannot provide reliable estimates if none of the elements of the support 
+recur in the samples (that is, when we never observe the same work-product 
+twice in our sample sets).
 
-It may seem unreasonable to hope to measure $D_{l_1}$ when our samples are so 
-megre that no specific work-product recurrs, but this level of sparsity is 
-routinely faced in classification tasks. As a concrete example, a facial 
-recognition 
-system (which classifies images as face or non- face) is expected to work on 
-images that have never been seen before, and its design cannot be predicated on
-covering a significant fraction of all possible images during training. In our 
-experiment, we demonstrate that the quintessential microtask, image labeling, 
-is one for which the measurement of priming effects can be approached using 
-classifiers.
+It may seem unreasonable to hope to measure $\theta$ when our samples are so 
+sparse in the space of work-products.  However, in machine learning,
+classifiers can succeed in the face of this much sparsity, and we can use
+this fact to estimate a lower bound on $\theta$ via \textbf{definition \ref{def:dist}}.
 
 \paragraph{Experimental setup.}
+We performed two experiments, soliciting respectively 900 and 2300 MTurk 
+workers to
+label images that depicting iconic cultural scenes, meals, ingredients, 
+table-settings, and various utensils and cookware. In these experiments,
+workers were randomly assigned to treatments, and depending on this 
+assignment, were exposed to different framing primes, given a different 
+set of initial images, and shown a different permutation of the test images. 
+In all treatments (for both experiments), workers were 
+given the same brief set of instructions before labeling any images.  The
+framing prime, if one was shown, followed the instructions.  Workers then
+labelled images, one at a time, providing five labels per image.  
+For the purpose of analysis, we denote the first five images as the 
+\textit{initial set}, and the last five as the \textit{test set}, but, 
+cruicially, from
+the perspective of the worker, no distinction was aparent.
+In the second experiment, treatments which received framing primes were
+not shown an initial set, so labeled only five images (the test set).
+Table 1 sumarizes the various experimental treatments for both 
+experiments.
 
-image labeling is common\ldots
-\cite{chandler2013breaking,Berinsky2012351,Finnerty2013,paolacci2010running}.
+\begin{table}[t]
+\centering
+	\begin{tabular}{ l  l  l }
+		\hline                       
+		Treatment & Framing prime & Initial image set	\\ 
+		\hline                       
+		$\textsc{ambg}$ & None & Ambiguous\\
+		$\textsc{img:cult}$ & None & Cultural\\
+		$\textsc{img:ingr}$ & None & Ingredients\\
+		$\textsc{frm:cult}$ & Cultural & Cultural\\
+		$\textsc{frm:ingr}$ & Cultural & Cultural\\
+		\hline  
+	\end{tabular}
 
-We solicited 2300 MTurk workers to perform an image-labeling task using images 
-that depicted meals, place-settings, and related items such as dishes, and 
-kitchenware, and other artifacts naturally arising in dining contexts. Workers 
-were randomly assigned into one of four treatments, described below. In all 
-treatments, workers were given brief instruc- tions before labeling any images.
-In some treatments, workers were then also shown a \textit{framing slide}, 
-indicating 
-the tasks were funded by a group having a particular research focus. The tasks 
-consisted of single images, and workers were asked to provide five descriptive 
-labels for each. The last five images that workers labeled, the 
-\textit{test set}, were the same for all treatments.
+	\caption{ \footnotesize{ 
+		Workers were uniformly randomly assigned to one of the 
+		treatments listed above. 
+		The full funder names used were 
+		``The Global Foundation for Cultural Recognition'' and 
+		``The National Foundation for Nutritional Awareness''.  
+		The ambiguous, cultural, and ingredients initial image sets are shown 
+		in \textbf{Figs. 2}, \textbf{3}, and \textbf{4}.
+	}}
+	\label{table:1}
+\end{table}
 
-The first two treatments, IMG:OBJ and IMG:FOOD, tested inter-task effects. 
-Workers in these treatments labelled ten images. In the IMG:OBJ treatment, the 
-\textit{initial set} of five images labeled by workers contained objects such 
-as utensils, kitchenware, and table-settings, but no food items. In the 
-\textsc{img:food}, the initial set contained centered close-ups of meals, 
-without
-any surrounding objects (except sometimes the dish supporting the food). No 
-interruption or distinction made between the initial and test sets from the 
-view of the workers. To study the positional dependance of inter-task effects,
-these treatments were subdivided, and workers were shown one of five 
-permutations. There are of course 5! = 120 permutations of five images, but 
-investigating all permutations was too expensive, and probably redundant, so 
-we chose 5 permutations that ensure each image occupies each position within 
-the test set. We discuss the benefits and drawbacks of this choice in the 
-supplementary material.
-
-Workers in the treatments \textsc{frm:food} and \textsc{frm:obj} were shown a 
-framing slide, which bore a message reading: ``Funded by the laboratory for 
-the visual perception of \{Food and Ingredients $\vert$ Objects and Tools\}''. 
-After the framing slide, workers in these treatments proceeded directly to 
-the test set (and so labeled only 5 images).
+\begin{figure}
+	\centering
+	\includegraphics[scale=0.7]{figs/tasks.pdf}
+	\caption{Examples of slides used for the image labeling tasks.
+A) instructions shown to all workers; B) a framing slide; C) a slide from the initial set for treatment IMG:FOOD; D) a slide from the initial set for treatment IMG:OBJ; E) a slide from the test set shown in all treatments.
+The full set of slides used for all treatments is presented in the supplementary material.}
+	\label{fig:task}
+\end{figure}
 
 \paragraph{The strength of inter-task effects}
-We tested for inter-task effects by training a Naive Bayes classifier to 
-classify work-products among IMG:OBJ and IMG:FOOD, using only the labels 
-attributed to the test set of images. Based on Definition 2, no classifier 
+The purpose of the first experiment was to compare the relative strength
+of inter-task and framing effects.  In this experiment, the treatment 
+\textsc{ambg} served as a base-case.  The other treatments differed from
+\textsc{ambg} either in terms of the initial image set, or by the addition of a
+framing prime.
+
+The test images in this experiment 1 consisted of meals having
+a strong, specific cultural connection (Fig. \ref{fig:task} shows an example).
+The \textsc{ambg} treatment had an initial set which also consisted of meals,
+but without more muted cultural overtones.  The initial images for treatment 
+\textsc{img:cult} featured iconic cultural scenes (devoid of food) while 
+those for treatment \textsc{img:ingr} consisted of isolated ingredients.
+Treatments \textsc{frm:cult} and \textsc{frm:ingr} had the same initail images
+as \textsc{ambg}, but had respectively a framing prime indicating that the
+tasks were funded by a foundation for ``cultural recognition'' and
+``nutritional awareness''.
+
+We tested for inter-task effects by evaluating the performance of a Naive 
+Bayes classifier when distinguishing the work-products from 
+\textsc{img:cult} and \textsc{img:ingr}, and, separately, when distinguishing
+those from \textsc{frm:cult} and \textsc{frm:ingr},
+using only the labels that workers from these treatments
+attributed to the test set of images.
+
 can perform better than the actual difference in priming, so the performance 
@@
 
+%The first two treatments, IMG:OBJ and IMG:FOOD, tested inter-task effects. 
+%Workers in these treatments labelled ten images. In the IMG:OBJ treatment, the 
+%\textit{initial set} of five images labeled by workers contained objects such 
+%as utensils, kitchenware, and table-settings, but no food items. In the 
+%\textsc{img:food}, the initial set contained centered close-ups of meals, 
+%without
+%any surrounding objects (except sometimes the dish supporting the food). No 
+%interruption or distinction made between the initial and test sets from the 
+%view of the workers. To study the positional dependance of inter-task effects,
+%these treatments were subdivided, and workers were shown one of five 
+%permutations. There are of course 5! = 120 permutations of five images, but 
+%investigating all permutations was too expensive, and probably redundant, so 
+%we chose 5 permutations that ensure each image occupies each position within 
+%the test set. We discuss the benefits and drawbacks of this choice in the 
+%supplementary material.
+%
+%Workers in the treatments \textsc{frm:food} and \textsc{frm:obj} were shown a 
+%framing slide, which bore a message reading: ``Funded by the laboratory for 
+%the visual perception of \{Food and Ingredients $\vert$ Objects and Tools\}''. 
+%After the framing slide, workers in these treatments proceeded directly to 
+%the test set (and so labeled only 5 images).
 \paragraph{Inter-task effects and the orientation of focus.}

### 2014-10-12 src/new_plots.py

@@ -1,0 +1,154 @@
+'''
+This module provides a collection of functions that produce the figures used
+in the paper
+'''
+
+import json
+import util
+import analysis
+import sys
+import random
+import naive_bayes
+import ontology
+import data_processing
+import numpy as np
+import time
+
+try:
+	import matplotlib.pyplot as plt
+	import matplotlib 
+	import matplotlib.gridspec as gridspec
+	from matplotlib.ticker import FixedLocator, LinearLocator, FixedFormatter
+
+except:
+	print 'matplotlib not installed.  You can do computations but not '\
+		'plotting functions.'
+	
+
+# z-score for two-tailed 99-percent confidence interval
+CONFIDENCE_95 = 1.96
+CONFIDENCE_99 = 2.975
+
+
+TREATMENT_NAMES = {
+	'treatment0': 'AMBG'
+	, 'treatment1': 'CULT$_{img}$'
+	, 'treatment2': 'INGR$_{img}$'
+	, 'treatment3': 'INGR$_{fund}$'
+	, 'treatment4': 'INGR$_{fund,img}$'
+	, 'treatment5': 'CULT$_{fund}$'
+	, 'treatment6': 'CULT$_{fund,img}$'
+}
+
+
+def plotAllF1Theta(
+		readFname='data/new_data/l1.json',
+		writeFname='figs/l1_longitudinal.pdf',
+		n=125,
+		alpha=0.05
+	):
+
+	'''
+	Plots the theta value for a naive bayes classifier built to distinguish
+	between all the interesting pairings of treatments.  See the manuscript
+	in <project-root>/docs/drafts for an explanation of theta.
+
+	This function only plots; the data must first be generated by running
+	`computeAllF1Accuracy()`
+	'''
+
+	subplotLabels = ['A','B','C', 'D', 'E', 'F', 'G']
+
+	# Read the data from file
+	f1scores = json.loads(open(readFname, 'r').read())['img_food_obj']
+
+	# Start a figure 
+	figWidth = 8.7 / 2.54 	# conversion from PNAS spec in cm to inches
+	figHeight = figWidth * 3.	# a reasonable aspect ratio
+	fig = plt.figure(figsize=(figWidth, figHeight))
+
+	# calculate the gridspec.  The width ratios are based on the width of
+	# each bar-plot-group, spacing between them, and plot padding
[…]

### 2014-10-12 src/plots.py

@@ -864,7 +864,7 @@ def plotOrientationAndSpecificity(
 
 	# we only want treatments 0,1, and 2, and so we have to 'pick' the data
 	# at positions 0,1, and 4
-	PICKS = [0,1,4]
+	PICKS = [0,1,4,2,5]
 	treatmentIds = pick(PICKS, treatmentIds)
 
 	treatments = ['treatment%d' % i for i in treatmentIds]
@@ -936,8 +936,8 @@ def plotOrientationAndSpecificity(
 	ax.set_xticklabels(xlabels, rotation=45, 
 		horizontalalignment='right', size=9)
 
-	#ylims = plt.ylim()
-	#plt.ylim(ylims[0], ylims[1]*1.12)
+	ylims = plt.ylim()
+	plt.ylim(ylims[0], ylims[1]*1.04)
 
 	xlims = (-padding, len(X) - 1 + 2*width + padding)
 	plt.xlim(xlims)
@@ -954,7 +954,7 @@ def plotOrientationAndSpecificity(
 	)
 
 	# Label the subplot
-	ax.text(-0.03, 48, 'A', 
+	ax.text(-0.03, 50, 'A', 
 			va='top', ha='left', size=20)
 
 	ax.yaxis.set_label_coords(-0.10,0.5)

### 2014-10-12 src/runnable_analysis.py

@@ -28,7 +28,7 @@ def calc_priming_differences():
 	# labels from the first image as features
 	old_results = {}
 	print 'calculation'
-	old_results['cult_vs_ambg'] =  test_binary_classification(
+	old_results['cult_vs_ambg'] = test_binary_classification(
 		False, ['treatment0', 'treatment1'], ['test0'])
 
 	print 'calculation'

### 2014-10-22 docs/publications/2014.09_SCIENCE/man.tex
work on paper.  Introduce new data analysis and plots

--- 2014-09-23 docs/publications/2014.09_SCIENCE/man.tex
@@
 \begin{sciabstract}
-Microtask platforms offer a fast, flexble, and inexpensive source of labour for
-clerical tasks \cite{Finnerty2013, chandler2013breaking, Berinsky2012351} and 
-recently have been adopted by researchers to augment datasets and solicit 
-participants \cite{paolacci2010running, Berinsky2012351, chandler2013breaking}.
-Some computer scientists describe such platforms as a new computing 
-architecture, and seek to characterize “human co-processing units” (HPUs) in 
-analogy to CPUs and GPUs \cite{5543192}. However, it is known that people are 
-susceptible to 
-priming effects\cite{No2007,Swaab200299,Gopher2000308,sohn2001task,Ghuman17062008,BJOP1796,BJOP1826,Gass1999549}, which stands to complicate the HPU 
-perspective.  Here, we introduce a framework to recast this psychological 
-phenomenon as a kind of computational hysteresis. 
-We apply this framework to study \textit{inter-task effects} that arise when 
-microtask 
-workers perform a sequence of tasks. Surprisingly, earlier tasks can have a 
-very strong influence on workers during later tasks---stronger than overtly
-framing the tasks as serving different research goals.   
-This result has major implications for the design of crowdsourcing initiatives.
-The framework we introduce provides a general measure of priming severity, 
-and, in combination with machine learning tools, enables measurement without
-knowing ahead of time how priming will affect output.
+
+People still outperform sophisticated artificial 
+intelligince systems in many tasks requiring general knowledge, 
+qualitative judgment, and visuo-spatial reasoning. Recently, microtask 
+platforms enable the programmer to import human judgment directly into 
+algorithms: programs can post tasks, to be completed by users of such 
+platforms in near real-time.
+Some computer scientists consider microtask platforms to be a fundamentally
+new computing architecture, but psychological effects can introduce systematic
+bias. 
+Here we investigate the effects that earlier tasks have on the results of 
+subsequent ones, which we call \textit{inter-task effects}.
+In a canonical image labeling task, we found that inter-task effects are
+very strong---stronger than overtly framing tasks in terms of 
+particular research goals.  However, in some cases, inter-task effects can
+be leveraged to elicit more nuanced responses.
+To study inter-task effects we introduce a framework that characterizes HPU 
+bias in an application-independant way, based on its potential to alter an 
+algorithm's path of execution.  Our findings suggest that careful consideration
+should be given to inter-task effects when designing crowdsourcing studies.
+
+%microtask worker performs a series of tasks.  We find that early tasks can
+%have a strong effect on later tasks, and that these effects can be stronger
+%than those brought about by framing.
+%
+%course of human computation algorithms.
+%application-independant quantity that measures the
+%severity of priming.  We apply this framework to measure 
+%
+%in many
+%tasks, especially ones requiring general knowledge about the world, qualitative
+%judgment, and visuo-spatial reasoning.  Recently, microtask web platforms have 
+%emerged. One can upload a batch of tasks to be completed by users who are paid 
+%for their efforts.
+%Though simple on the surface, these platforms dramatically enlarge the
+%programmers toolkit: in effect they allow the programmer to import human 
+%judgment into algorithms.  Some computer scientists consider
+%such platforms to be a new computing architecture.  But people are very 
+%different from electronic processors.  For example, context affects how a 
+%person will respond to a prompt, and this complicates the formal treatment of 
+%human computation.  To approach this issue, we introduce a framework 
+%that quantifies the severity of priming in an application-independant way.
+%We apply this technique to reveal an unforseen source of bias: the bias 
+%induced by one task on another.  Surprisingly we find that 
+%\textit{inter-task effects} introduce more bias than \textit{framing}, which
+%has received more attention.
+%
+%more well-known 
+%\textit{framing}, a more well-studied form of priming.
+%
+%Microtask platforms offer a fast, flexble, and inexpensive source of labour for
+%clerical tasks \cite{Finnerty2013, chandler2013breaking, Berinsky2012351} and 
+%recently have been adopted by researchers to augment datasets and solicit 
+%participants \cite{paolacci2010running, Berinsky2012351, chandler2013breaking}.
+%Computer scientists have described such platforms as a new computing 
+%architecture, and seek to characterize “human co-processing units” (HPUs) in 
+%analogy to CPUs and GPUs \cite{5543192}. However, it is known that people are 
+%susceptible to 
+%priming effects\cite{No2007,Swaab200299,Gopher2000308,sohn2001task,Ghuman17062008,BJOP1796,BJOP1826,Gass1999549}, which stands to complicate the HPU 
+%perspective.  Here, we introduce a framework to recast this psychological 
+%phenomenon as a kind of computational hysteresis. 
+%We apply this framework to study \textit{inter-task effects} that arise when 
+%microtask 
+%workers perform a sequence of tasks. Surprisingly, earlier tasks can have a 
+%very strong influence on workers during later tasks---stronger than overtly
+%framing the tasks as serving different research goals.   
+%This result has major implications for the design of crowdsourcing initiatives.
+%The framework we introduce provides a general measure of priming severity, 
+%and, in combination with machine learning tools, enables measurement without
+%knowing ahead of time how priming will affect output.
 \end{sciabstract}
@@
 
-The task requester can interact with the platform like a compute server, 
-seamlessly 
-integrating human and machine computation.  Researchers coined the 
-term HPU (Human co-Processing Unit), viewing the introduction 
-of microtask platforms as a new computing architecture\cite{5543192}.  
-Attempts have been made to formalize the HPU instruction set, and libraries 
-that provide high-level APIs (Application Programming Interfaces) for writing 
-algorithms involving human computation have been developed \cite{little2010turkit,minder2011crowdlang,minder2012crowdlang,kittur2011crowdforge}.
+These platforms make it possible to seemlessly integrate human and 
+machine computation.  Researchers coined the term HPU 
+(Human co-Processing Unit) in analogy to CPUs and GPUs \cite{5543192}.  
+Attempts have been made to establish an HPU instruction set.  For example,
+the X library provides function calls such as 
+\texttt{X.vote()}, and \texttt{X.map()}
+ \cite{little2010turkit,minder2011crowdlang,minder2012crowdlang,kittur2011crowdforge}.
 
-Here, we highlight an important way in which HPUs differ from CPUs, with 
-serious implications for any crowdsourcing initiative.  Common sense would 
-dictate that people's output during a task will be stochastic: when the same
-task is given to different people, or given to the same person at different 
-times,
-the outputs may, in general, differ.  Stochasticity is not itself problematic,
-since the analysis of probabilistic algorithms is fairly 
-well-understood. But other non-random effects may also bear on HPU output. 
+Of course, there are obvious differences between HPUs and their silicone
+counterparts.  When facing the same task, people do not generally
+respond in the same way.  Common sense would dictate that a certain amount
+of variability in responses made by people is inescapable.  But an important 
+part of the variation is bound to be systematic, due to psychological or 
+demographic factors.
+
+Here, we highlight an important source of bias with
+serious implications for any crowdsourcing initiative. 
 It is known that people are susceptible to priming effects 
 \cite{BJOP1796,No2007,beller1971priming}, and, in particular, task-repetition 
-effects \cite{Gass1999549,sohn2001task}.
-
-Such repetition effects, or
-\textit{inter-task effects}, are neither random, nor are they formally part 
-of the instructions given to the HPU.  The ``leakage'' of information from 
-recently performed tasks into HPU outputs is a potentially strong source of 
-systematic bias, which complicates the the algorithmic view of HPUs. 
-Inter-task effects would amount to a kind of \textit{hysteresis}, meaning 
-that HPU output is not only a function of the current input, but also of the 
-history of inputs.
-
-Here we make two contributions towards understanding inter-task effects
-and HPU hysteresis in general.  We present a framework for treating this 
-source of bias in the context of HPU algorithms, and we measure the impact of
-inter-task effects experimentally in a canonical HPU task: the labeling of 
-images.
-
-Using the  Amazon Mechanical Turk (Mturk) platform, we solicited workers to 
-perform a series of image-labeling tasks.  
-In these tasks, workers labeled images featuring iconic cultural scenes,
-food, table-settings, and various utensils and cookware. We divided the set of 
-images shown to a given worker into an \textit{initial} and \textit{test} set, 
-but, crucially, there was no apparent distinction between these sets from the
-perspective of the worker.  We varied the initial set of images, while 
-keeping the test set the same, to analyze the effect that that the initial 
-images had on the labels that workers attributed to the test set.
+effects \cite{Gass1999549,sohn2001task}.  Thus, a worker's response during
+one task may depend in part on previous ones.  Such \textit{inter-task} effects
+would amount to a kind of \textit{hysteresis}, meaning that HPU outputs are not
+only a function of the current input, but also of the history of inputs.
 
 There has been considerable investigation into the factors that affect the 
-quality and nature of microtask work.  These include such factors as the 
+output from microtask work.  These include such factors as the 
 level of 
@@
 
+We make two contributions towards understanding inter-task effects,
+and systematic bias in HPUs in general.  First, we present a framework for 
+quantifying bias in HPU outputs in terms of their potential impact 
+algorithms.  This yields an approach for measuring the severity of bias 
+that removes the need to understand the underlying psychological or 
+demographic factors at play.  Second, we apply our framework to measure the
+severity of inter-task effects on a canonical microtask: image labeling.
+
+Using the  Amazon Mechanical Turk (Mturk) platform, we solicited workers to 
+perform a series of image-labeling tasks.  We chose image labeling because it 
+is one of the most common kinds of microtasks
+\cite{chandler2013breaking,Berinsky2012351,Finnerty2013,paolacci2010running}, 
+and it seems likely that this will remain the case in the long term because
+of applications in computer vision research \cite{5543192}.
+%In these tasks, workers labeled images featuring iconic cultural scenes,
+%food, table-settings, and various utensils and cookware. 
+We divided the tasks into an \textit{initial} and \textit{test} set, 
+but, crucially, there was no distinction between these sets from the
+perspective of the worker.  We varied the initial tasks, while 
+keeping the test set the same, to analyze the effect of initial tasks on 
+the labels provided during the test tasks.
+
 As a point of comparison, we included treatments in which we induce 
 \textit{framing}.
-Before the workers label images, we indicate that the work 
-was funded by a research lab having a particular area of interest, to see the 
+Before the workers labeled images, we indicated that the work 
+was funded by a research lab with a particular area of interest, to see the 
 influence this has on the workers’ subsequent labels. 
@@
 about twice as strong. 
-Our results show that initial tasks can significantly alter the subject 
-matter on which worker's labels focus. We also found that inter-task 
-effects can induce workers to provide labels of greater or lesser specificity. 
-This suggests that careful consideration should be given to the bundling of 
-tasks when designing a study using a microtask platform.
+Our results demonstrate that initial tasks can change workers' focus in later 
+tasks.  We also found that inter-task effects altered the level of specificity 
+of worker's labels.  Our findings suggest that careful consideration should be 
+given to the bundling of tasks when designing a study using a microtask 
+platform.
 
-To characterize inter-task effects, we present a novel, generalized definition 
-of \textit{HPU priming}. Priming is traditionally used to elucidate the
-internal psychological mechanisms of cognition.  But here we are concerned with
-understanding the outward effects that priming phenomena have on HPU 
-algorithms. Thus, before we discuss inter-task effects experimentally, we 
-discuss formal definitions for priming as computational phenomenon.  Our
-discussion will lead to a natural definition of priming that enables 
-comparisons of the severity priming effects accross applications, and enables
-the measurement of priming using machine learning tools.
+\paragraph*{Computational hysteresis.}
+Before describing our experiments, we dedicate some space to discussing
+how we characterize and measure priming in HPU outputs.  Since HPU outputs are
+stochastic, determining the effect of priming on an HPU population
+amounts to determining the resulting change to the HPU population's 
+distribution of outputs.
 
-\paragraph*{Priming as computational hysteresis.}
-In psychology, priming effects are studied because they hint at the 
-psychological mechanisms at play during certain cognitive tasks. But in the 
-context of human computation, the focus should be on the outward consequences: 
-the potential for algorithms to execute differently when ``run'' on differently
-primed HPUs.
+To refine this, we distinguish between methods that determine \textit{whether}
+two random sources have the same distribution 
+(e.g. Pearson's chi squared test), from those that determine
+\textit{the extent} of that difference (e.g. one of the many measures of 
+statistical divergence).  We are interested in measuring the extent of
+difference because our practical concern is the potential for such
+differences to alter the course of an algorithm.
 
-We will present three definitions of priming with this practical concern in 
-mind, and then describe how to measure priming in practice. To proceed with 
-the definitions, we will assume that two populations of HPU’s, $\mathcal{P}$ 
-and $\mathcal{Q}$ were 
-sampled randomly from the same initial population $\mathcal{R}$, and then were 
-exposed to (possibly) different priming treatments. The HPUs in $\mathcal{P}$ 
-and $\mathcal{Q}$ perform some 
-task, leading to popualtions of work-products, $P$ and $Q$.
+To measure the effect of some priming treatment, we must of course draw a 
+comparison to some standard population.  In many cases, there may be an 
+obvious comparison between a primed and unprimed population.  However, we 
+refrain from proposing a canonical neutrally-primed HPU population; what is 
+considered ``unprimed'' in one scenario may be ``primed'' in another. 
+Instead, we speak of two HPU populations being \textit{differently primed}.
 
-For the first defenition, let us address the concern that differently primed 
-HPUs may produce ``biased'' work-products.
+We present three alternative, equivalent definitions for the 
+\textit{difference in priming} of two HPU populations, $\mathcal{P}$, and 
+$\mathcal{Q}$, which we denote $\theta(P,Q)$.  To set up the definitions,
+we will assume that $\mathcal{P}$ and $\mathcal{Q}$ 
+were sampled randomly from the same initial population $\mathcal{R}$, and 
+then were exposed to (possibly) different priming treatments. Then, the HPUs 
+in $\mathcal{P}$ and $\mathcal{Q}$ perform some task, leading to popualtions 
+of work-products, $P$ and $Q$.
+
+The first definition provides the motivation for our choice of divergence
+measure, because it directly measures the proportion of the time that a
+binary decision will be changed due to priming effects:
 
 \begin{mydef}
-	{\upshape Maximum Bias $\theta_\mathrm{bias}$:}
-	Let $\mathcal{D}$ be a binary decision algorithm, which takes a 
+	\label{def:bias}
+	{\upshape Maximum Bias:}
+	Let $\mathcal{D}$ be a binary decision function, which takes a 
 	work-product
@@
 	different priming of $\mathcal{P}$ and $\mathcal{Q}$ by
-	$\theta^\mathcal{D}_\mathrm{bias}(P,Q)$ and define it to be the difference 
+	$\theta_\mathcal{D}(P,Q)$ and define it to be the difference 
 	in the expected output of $\mathcal{D}$ when acting on work-products from 
-	$P$ vs $Q$:
+	$P$ and $Q$:
 	$$
-	\theta^\mathcal{D}_\mathrm{bias}(P,Q) = 
+	\theta_\mathcal{D}(P,Q) = 
 		\left| 
@@
 	where $p \in P$, $q \in Q$.  Then, define the difference in priming 
-	between $P$ and $Q$ to be the worst-case bias, i.e. the bias of the most
-	susceptible decision:
+	between $\mathcal{P}$ and $\mathcal{Q}$ to be the worst-case bias, i.e. 
+	the bias of the most susceptible decision:
 	$$
-	\theta_\mathrm{bias} = 
-		\sup_\mathcal{D} \theta^\mathcal{D}_\mathrm{bias}(P,Q)
+	\theta(P,Q) = 
+		\sup_\mathcal{D} \theta_\mathcal{D}(P,Q)
 	$$
 \end{mydef}
+If $\mathcal{D}$ is the condition of an \texttt{if}-statement, then the 
+definition above is the change in the fraction of the time that a given 
+path of execution is followed due to HPU priming.
 
-Thus, $\theta_\mathrm{bias}$ has a straightforward interpretation as an upper 
-bound on the amount of bias induced on any yes-or-no decision, due to the 
-difference in priming of $\mathcal{P}$ and $\mathcal{Q}$.
-
-For the next definition, we attempt to address directly the extent to which 
-two populations of work-products are ``different'', by supposing that they are 
-different to the extent that they can be distinguished algorithmically. To 
-facilitate this definition, we make use of the notions of a 
-\textit{distinguisher} and a \textit{validation} test.
+While this is precisely what we want to measure, it is not at all clear how
+to go about doing it.  The second formulation provides a practical connection
+by rephrasing priming in terms of its distinguishability:
 
 \begin{mydef}
-	{\upshape Algorithmic distinctness $\theta_\mathrm{dist}$:}
+	{\upshape Distinguishability:}
 	Let $\mathcal{D}$ be a distinguisher algorithm, which takes work-product 
@@
 	random from one of the populations, decided by the bit: $r \in_R R_b$. 
-	Feed $r$ to $\mathcal{D}$, and if $\mathcal{D}(r) = b$, we say 
-	$\mathcal{D}$ guessed correctly, and the value of $V$ is 1, 
-	otherwise V = 0.
+	Input $r$ into $\mathcal{D}$, and if $\mathcal{D}(r) = b$, we say 
+	$\mathcal{D}$ \emph{guessed correctly}, and the value of $V$ is 1, 
+	otherwise $V = 0$.
 
 	A distinguisher that guesses randomly will still be correct half of the 
-	time. Therefore, denote the performance of $\mathcal{D}$ as 
-	$\eta_\mathcal{D}(P, Q)$, and define:
+	time. Therefore, denote the performance of $\mathcal{D}$ by 
+	$\eta_\mathcal{D}(P, Q)$, and let
 	$$
-		\theta_\mathrm{dist} = \sup_\mathcal{D} \eta_\mathcal{D}(P,Q)
+		\eta_\mathcal{D}(P,Q) = 2\cdot \mathrm{E}\{V(\mathcal{D},P,Q)\} - 1.
+	$$
+	Then define the difference in priming between $\mathcal{P}$ and 
+	$\mathcal{Q}$ to be the performance of the best possible distinguisher:
+	$$ 
+		\theta(P,Q) = \sup_\mathcal{D} \eta_\mathcal{D}(P,Q)
+	$$
+	\label{def:dist}
+\end{mydef}
+
+\textbf{Definition 2} relates the difference in priming to the 
+\textit{optimal Bayes classifier} for determining whether a given HPU output
+came from $P$ or $Q$.  This means that we can obtain a lower bound on
+$\theta(P,Q)$ based on the performance of an actual classifier, which provides
+recourse when purely statistical methods fail.
+
+The statistical divergence measure underlying the previous definitions is the
+divergence measure known as the ``total variational distance'' or 
+$l_1$-distance:
+\begin{mydef}
+	\label{def:l1}
+	{\upshape Total variational distance $\theta_{l_1}$:}
+	Define the difference in priming between $\mathcal{P}$ and $\mathcal{Q}$ 
+	to be equal to the total variational distance between the work-products 
+	$P$ and $Q$:
+	$$
+	\theta_{l_1}
+	= \sup_{A \subset \mathcal{X}} \left| \sum_{x \in A} f_P(x) - f_Q(x)\right|
+	= \frac{1}{2} \sum_{x \in \mathcal{X}} \left| f_P(x) - f_Q(x) \right|,
+	$$
+	where $f_P(x)$ denotes the probability of observing x when sampling from P.
+\end{mydef}
+The equivalent formulation for $\theta(P,Q)$ in 
+\textbf{definition \ref{def:l1}} provides a grounding in a fundamental
+measure of statistical divergence, and a connection to information theory.  
+The equivalence of the three definitions
+follows from the known fact that no algorithm can have output that differs
+on inputs $P$ and $Q$ more than $l_1 \times 100\%$ of the time.  We provide
+proofs in the supplementary material.
+
+The difficulty of measuring $\theta(P,Q)$ depends on what the universe of
+possible outputs are, as well as how $P$ and $Q$ are actually distributed,
+both of which are mainly determined by the task that the HPUs are asked to 
+perform.  In the case where workers label an image with a free-text input, 
+the number of different possible labels can be in the thousands or more.  If
+the support, $\mathcal{X} = P \cup Q$, is large compared to the number of 
+HPU outputs sampled, so that many labels appear only once (which in any case
+is expected from Zipv's law), then estimating $\theta$ directly from the
+observed frequencies of labels is difficult.
+
+One approach to estimating the $l_1$-distance from samples, which appears
+reasonable on the surface, is to use the observed frequencies of each output
+$x$ from $P$ and $Q$ to estimate $f_P(x)$ and $f_Q(x)$, and calculate 
+$\theta(P,Q)$ directly from \textbf{definition 3}.  This is the so-called naive
+approach to estimating $l_1$-distances, and is aptly named because it tends
+to produce very inflated values.  More recent techniques have for estimating
+$l_1$ have been suggested by Valiant \cite{val-thesis}, and Batu 
+\cite{batu2000testing,batu2013testing}.  We reserve the discission of these
+techniques to the supplementary material; they do not turn out to be useful
+because they do not provide confidence intervals.  Thus our only recourse is
+to test the performance of classifiers at distinquishing $p \in P$ from 
+$q \in Q$, which allows us to estimate a lower bound on $\theta(P,Q)$.  This 
+turns out to be sufficient, and has the advantage that, so long as they are
+learnable, it is not necessary to understand exactly how $P$ and $Q$ differ.
+
+\paragraph{Experimental setup.}
+We performed two experiments, soliciting respectively 900 and 2300 MTurk 
+workers to label images depicting iconic cultural scenes, meals, ingredients, 
+table-settings, and various utensils and cookware. In these experiments,
+workers were randomly assigned to treatments, and depending on this 
+assignment, were exposed to different framing primes, given a different 
+set of initial images, and shown a different permutation of the test images. 
+For both experiments, workers were first shown brief instructions.  
+The framing prime was then shown, unless the given 
+treatment involved no framing.  Workers then performed a series of 
+image-labeling tasks and had to provide five labels per image. 
+For the purpose of analysis, we denote the first five images as the 
+\textit{initial set}, and the last five as the \textit{test set}, but no
+distingction was made from
+the perspective of the worker.
+Table 1 sumarizes the various experimental treatments for both 
+experiments.
+
+\begin{table}[t]
+\centering
+	\begin{tabular}{ l  l  l }
+		\hline                       
+		Treatment & Framing prime & Initial image set	\\ 
+		\hline                       
+		\textit{Experiment 1}\\
+		$\textsc{ambg}$ & None & Ambiguous\\
+		$\textsc{img:cult}$ & None & Cultural\\
+		$\textsc{img:ingr}$ & None & Ingredients\\
+		$\textsc{frm:cult}$ & Cultural & Ambiguous\\
+		$\textsc{frm:ingr}$ & Ingredients & Ambiguous\\
+		\hline  
+		\textit{Experiment 2}\\
+		$\textsc{img:food}$ & None & Food\\
+		$\textsc{img:obj}$ & None & Objects\\
+		$\textsc{frm:food}$ & Food & None\\
+		$\textsc{frm:obj}$ & Objects & None\\
+		\hline  
+	\end{tabular}
+
+	\caption{ \footnotesize{ 
+		Workers were uniformly randomly assigned to one of the 
+		treatments listed above. 
+		The full funder names used were 
+		Cultural: ``The Global Foundation for Cultural Recognition'' and 
+		Ingredients: ``The National Foundation for Nutritional Awareness''.  
+		The ambiguous, cultural, and ingredients initial image sets are shown 
+		in \textbf{Figs. 2}, \textbf{3}, and \textbf{4}.
+	}}
+	\label{table:1}
+\end{table}
+
+\begin{figure}
+	\centering
+	\includegraphics[scale=0.7]{figs/tasks.pdf}
+	\caption{Examples of slides used for the image labeling tasks.
+A) instructions shown to all workers; B) a framing slide; C) a slide from the initial set for treatment IMG:FOOD; D) a slide from the initial set for treatment IMG:OBJ; E) a slide from the test set shown in all treatments.
+The full set of slides used for all treatments is presented in the supplementary material.}
+	\label{fig:task}
+\end{figure}
+
+\paragraph{The strength of inter-task effects.}
+\begin{figure}
+	\centering
+	\includegraphics[scale=1]{figs/theta.pdf}
+	\caption{
+		Difference in priming observed for various pairs of worker populations.
+		The pairs of populations differed in terms of the initial tasks they
+		performed (bars labeled by \textit{inter-t.}) or in terms of the framing
+		to which they were exposed (bars labeled by \textit{frame}; see table 1 for
+		details about the treatments).  The difference in priming was 
+		measured based on the accuracy of a naive Bayes classifier in 
+		resolving which treatment workers belonged to, as described in the 
+		text.  
+	}
+	\label{fig:theta}
+\end{figure}
+
+%\paragraph{Dynamics of inter-task effects}
+%\begin{figure}
+%	\centering
+%	\includegraphics[scale=0.7]{figs/theta_by_pos_img.pdf}
+%	\caption{
+%		Difference in priming observed for various pairs of worker populations.
+%		The pairs of populations differed in terms of the initial tasks they
+%		performed (bars labeled by ``inter-t.'') or in terms of the framing
+%		to which they were exposed (bars labeled by ``frame''; see table 1 for
+%		details about the treatments).  The difference in priming was 
+%		measured based on the accuracy of a naive Bayes classifier in 
+%		resolving which treatment workers belonged to, as described in the 
+%		text.  
+%	}
+%	\label{fig:theta_pos_img}
+%\end{figure}
+
+We analyzed the overall strength of inter-task effects and framing, by looking
+at pairs of treatments that performed the same test tasks, but had done
+different initial tasks or had been exposed to different framing.
+For each such pair, we assessed the performance of classifier
+in predicting which treatment workers belonged to, based on the labels they
+provided during the test tasks (see fig 2).  
+Based on \textbf{Definition 2}, this is a lower bound on the amount 
+bias introduced by the initial tasks and framing.
+
+In experiment \textit{inter-t.1}, the test tasks required workers to
+label relatively cluttered images of table settings, which had various items
+of food, utensils, dishware, and other objects natural to such settings.
+For one treatment, the images in the initial tasks consisted exclusively of 
+food, and for the other, they consisted exclusively of non-food objects, 
+particularly cookware and utensils.  We saw a strong effect of priming, 
+based on the classifier performance (see fig. 2).
+
+In a related experiment, \textit{frame1}, workers were given the same test tasks
+as in \textit{inter-t.1}, but were either told 
+that ``The purpose of this study is to understand the viusual perception of
+Food and Ingredients'' or ``\ldots of Objects and Tools''.  This overt framing
+of the task in terms of a specific research objective had remarkably milder
+effects on workers than the initial tasks (see fig. 2).
+
+We performed another set of experiments based on a different set of test 
+tasks, and where the initial tasks and framing were directed along a different
+conceptual axis.  In \textit{inter-t.2} and \textit{frame2}, the images in the test 
+tasks displayed prepared meals from a variety of ethnic backgrounds.  We then
+designed the framing and initial tasks to focus either on food or cultural 
+elements.  In the previous experiments, the primes were always focused on 
+concrete ``highly imageable'' concepts (food and objects), these experiments
+mixed a concrete concept (food) with an abstract concept (culture).
+The initial tasks in \textit{inter-t.2} either depicted prepared meals (but having
+ambiguous cultural association), or iconic cultural scenes (including music, 
+dance, and sport).  Workers in \textit{frame2} were told that the ``This study
+was proudly funded by the National Foundation for Nutritional Awareness'' 
+or the ``\ldots Global Foundation for Cultural Recognition''.
+
+The results for \textit{inter-t.2} and \textit{frame2} confirmed that 
+inter-task effects are much stronger than framing (see fig. 2).  In fact, 
+intertask effects were even stronger in this experiment than the previous.
+
+\paragraph{Sufficiency of framing.} Given just how much stronger
+inter-task effects were, the reader may wonder whether the framing was 
+in some sense ``sufficient''.  
+We designed our framing tasks based on
+work that had previously studied framing effects in micro-task settings.  
+Prior studies have shown that framing the purpose of a task, or indeed, 
+simply changing a single, seemingly non-critical word in a task description, 
+has significant effects on worker's resonses.  Perhaps more importantly, the 
+framing treatments were included to provide a reasonable basis for comparison,
+and it is clear from our results that the prior tasks performed by a 
+worker are much stranger than the effects induced by descriptions of a task's
+purpose, or the requester's mandate.
+
+Nevertheless, we included one more experiment, \textit{frame*3}, to test the 
+effect of framing when the worker is required to \textit{echo} the framing 
+statement.  \textit{frame*3} was based on \textit{frame2}, but the worker
+had to indicate, using a menu option, what the purpose of the study was,
+before they could proceed.  In one sense, this seems to go beyond what one
+might mean by ``framing''.  By forcing the worker to echo the frame, we provide
+a clear indication that the frame is a particularly important detail, 
+elevating its importance above even the instructions that had been provided
+beforehand.
+
+The framing effect in \textit{frame*3} was quite strong, being on par with the
+inter-task effects we had observed (see fig. 2).  We are not sure whether
+the \textit{frame*3} should be considered framing,
+or whether it should be considered as an instruction, or perhaps as a 
+screening-task.  Regardless, our results show that worker's responses are 
+profoundly affected by recently completed tasks.
+
+\paragraph{Dynamics of intertask effects.} 
+In the results shown above, we considered the aggregate effect that the
+first five initial tasks had on the last five test tasks.  But it would stand
+to reason that the first test task might be
+most strongly influenced, and that, as the worker proceeds, the intervening 
+test tasks would tend to wash out the priming induced by the initial tasks.
+
+One complication to this is the fact that the strength of intertask effects
+should also depend on the task: that is, workers performing one task are not
+necessarily as susceptible to inter-task effects as when performing another 
+task.  To account for this, we performed five replicates of the 
+\textit{inter-t.1} experiment, each using a different permutation of the 
+test tasks.  We ensured that each test task appeared in each of the 
+five possible relative positions.  This allowed us to measure the inter-task
+effects as a function of task position, independant of the particular image
+used in the task (see fig. 2B).  We found that, as one would expect,
+the first test task tends to be the most strongly affected.  The effect drops
+considerably for the second task, and continues to fall for the third and 
+fourth.  Interestingly, the last test task consistently showed a small increase
+in priming effect.  We also observed this in \textit{inter-t.1}. 
+We do not know the psychological mechanism behind this phonomenon, but we 
+speculate that, since the worker knows that there are ten tasks in total,
+they might reflect on the task overall batch of tasks as they near the end,
+and in so-doing might partially re-activate the influence of the initial tasks.
+
+While the strength of inter-task effects appeared to depend strongly on
+the position of the task, it was considerably less dependant on exactly what
+was in the task (see fig. 2C).  To be sure, we intended for the tasks to be 
+similar, and it does appear that the various test tasks had similar 
+susceptibilities to inter-task effects.
+
+\paragraph{Initial tasks' affect on the direction of focus} 
+\begin{figure}
+	\centering
+	\includegraphics[scale=1]{figs/food_specificity.pdf}
+	\caption{
+		Difference in priming observed for various pairs of worker populations.
+		The pairs of populations differed in terms of the initial tasks they
+		performed (bars labeled by \textit{inter-t.}) or in terms of the framing
+		to which they were exposed (bars labeled by \textit{frame}; see table 1 for
+		details about the treatments).  The difference in priming was 
+		measured based on the accuracy of a naive Bayes classifier in 
+		resolving which treatment workers belonged to, as described in the 
+		text.  
+	}
+	\label{fig:food_specificity}
+\end{figure}
+
+At this point we have only discussed priming effects in terms of a 
+classifier's ability to detect them.
+We have said nothing qualitative about the \textit{nature} of these effects.  
+This is one of the advantages of measuring priming using classifiers: one need 
+not know beforehand how workers were primed, nor, 
+how it might affect worker's responses.  Machine learning algorithms are
+specifically designed to generalize inductively from examples, which makes
+it possible to estimate how different two populations with little prior 
+knowledge.
+
+Having shown that workers are strongly primed by initial tasks, a natural
+question is whether workers were biased to provide labels that reflected, 
+in some way, the content of the initial tasks.  All of the experiments 
+we performed involved a treatment exposed to a food-related prime, as well
+as a treatment exposed to a non-food prime (objects/tools or culture), so
+we can test the effects on the content of labels by determining the fraction
+of food-related labels that workers provide during the test tasks.
+
+We used wordnet, via the nltk package for python, to detect labels that are 
+food-related.  Wordnet is an extensive corpus for English that contains a 
+detailed set of hypernym-hyponym relationships for nouns.  Hypernyms are 
+generalizations, while hyponyms are specific instances or types.  For example,
+\textit{pumpernickel} is a type of \textit{bread}, so bread is a hypernym of 
+\textit{pumpernickel}, and \textit{pumpernickel} is a hyponym of 
+\textit{bread}.  We identified the top-level food-related entries in wordnet 
+and considered all hyponym-descendants of these words to be food-related.
+
+We use this to test the effect of initial tasks on the direction of workers
+focus in both \textit{inter-t.1}, \textit{frame2}, and \textit{frame}*3.  
+Recall that this experiment involved
+workers either primed for the concept of food or objects/tools, using either
+initial tasks or framing.  Our findings matched the straightforward
+expectation that workers exposed to food related-primes are biased to 
+provide more food-related labels during test tasks.  But the strength of
+the bias does not account for the degree of priming we measured using a 
+classifier (c.f. fig 2A).  Although we do see the expected
+bias towards providing food labels, the bulk of inter-task effects would appear
+to be of a more subtle nature.
+
+Inspecting the labels manually, one striking observation was some treatments
+had substantially more generic labels, for example providing labels such as
+\texttt{food} or \texttt{meal} as opposed to \texttt{spaghetti}.  To test this
+rigorously, we used the hypernym-hyponym relationships provided by wordnet.  
+To compare the relative specificity of two sets of labels $P$ and $Q$, we first
+define the relative specificity of a single label $p \in P$ in the context of
+$Q$:
+$$
+s(p,Q) = \left\{
+	\begin{array}{l l}
+		\frac{N_>(p,Q) - N_<(p,Q)}{N(p,Q)} &\mathrm{if}\quad N(p,Q) > 0\\
+		0 &\mathrm{else}
+	\end{array}
+	\right.,
+$$
+where $N_>(p,Q)$ is the number hyponyms of $p$ found in $Q$, and $N_<(p,Q)$ is
+the number of hypernyms of $p$ found $Q$.  For this calculation, we consider 
+the ``hypernyms of $p$'' to include hypernyms of hypernyms of p, etc., 
+adopting the analogous interpretation for hyponyms.  Then, the relative
+specificity of the entire set $P$ relative to $Q$ as:
+$$
+	S(P,Q) = \frac{1}{|P|}\sum_{p \in P} s(p,Q).
 $$
 
-\end{mydef}
-In the above definition, the performance simply rescales accuracy, so that when
-accuracy is 1/2 (i.e. as good as chance) performance is 0, and when accuracy 
-is perfect, performance is 1. This definition casts the measurement of priming 
-effects in terms of a binary classification problem, which is well-studied in 
-the field of machine learning.
+To see how the initial tasks and the framing affected 
+the focus of the workers' labels, we classified all the labels provided
+on test tasks as either \texttt{culture}, \texttt{food}, \texttt{both}, or 
+\texttt{neither} (we describe the label classification method in more detail
+in the supplementary material).  Focusing on the labels provided to the first 
+test task,
+workers that had initially labeled cultural images provided far more cultural
+labels during test tasks, and fewer food labels, than workers that initially
+labeled images depicting ingredients (see \textbf{Fig. 2}).  On the other 
+hand, the framing primes had no statistically significant effect.
 
-The two definitions we have already mentioned are, in fact, equivalent, and 
-correspond to a third, more fundamental formulation known as the total 
-\textit{variational distance}, or $l_1$-distance, or simply the “statistical 
-distance” ($D_{l_1}$):
-$$
-	D_{l_1}(P,Q) \equiv \frac{1}{2} \sum_{x \in \mathcal{X}} 
-	\left| 
-		f_P(x) - f_Q(x)
-	\right|,
-$$
-where $f_P(x)$ denotes the probability of observing x when sampling from P. 
-This leads us to our third definition:
-
-\begin{mydef}
-	{\upshape Priming as $l_1$-distance:}
-	The difference in priming of $\mathcal{P}$ and $\mathcal{Q}$ is the 
-	$l_1$-distance between the distributions of their work-products, 
-	$D_{l_1}(P,Q)$.
-\end{mydef}
-
-We provide proofs of the equivalence between these definitions in the 
-supplementary material. Despite their equivalence, we show the three 
-definitions because they offer different theoretical, practical, and 
-interpretive entry points. Definition 1 provides a practical motivation, and 
-the straighforward interpretation of priming as bias. Definition 3 draws a 
-clear link to existing statistical theory. And Definition 2 introduces machine 
-learning tools, which allow us to gain traction when the purely statistical 
-tools fail.
-
-\paragraph{Measuring priming.}
-Care must be taken in estimating $D_{l_1}$ from samples so as not to obtain
-an inflated estimate. In the so-called naive approach, one uses the frequency 
-with which a given work-product $x$ is obtained from HPUs in $\mathcal{P}$ to 
-estimate the probability mass function at $x$; 
-$\hat{f}_P(x) = (\sum_{X\in P} \mathbf{1}_{[X=x]})/|P|$.
-One can then estimate 
-$D_{l_1} = \sum_{x \in \mathcal{X}} \left|\hat{f}_P(x) - \hat{f}_Q(x) \right|/2$ using only the sample frequencies. But the number of samples, $|P|$ and 
-$|Q|$, must be much larger than the number of possible work-outputs, 
-$|\mathcal{X}|$, otherwise, this method produces an enormously inflated 
-estimate.
-
-Recently, attempts have been made to provide better estimators. Valiant, 
-provides a canonical estimation approach based on first estimating the unseen 
-region of the support. This algorithm appears to perform very well in practice.
-Batu provided an alternative approach, which bypasses estimating the 
-probability mass functions, and relies on the more fundamental concept of 
-\textit{collisions}.
-
-Both methods converge much more quickly than the naive approach. However, two 
-limitations remain that prevent their application. First, these relatively 
-recent approaches are not accompanied by any absolute guarantees of 
-statistical confidence, so it is not yet clear how to build confidence 
-intervals for a given estimate. Second, sophisticated as these methods are, 
-they still cannot provide reliable estimates when none of the elements of the 
-support recur in the samples (that is, when we never observe the same 
-work-product twice in our sample sets).
-
-It may seem unreasonable to hope to measure $D_{l_1}$ when our samples are so 
-megre that no specific work-product recurrs, but this level of sparsity is 
-routinely faced in classification tasks. As a concrete example, a facial 
-recognition 
-system (which classifies images as face or non- face) is expected to work on 
-images that have never been seen before, and its design cannot be predicated on
-covering a significant fraction of all possible images during training. In our 
-experiment, we demonstrate that the quintessential microtask, image labeling, 
-is one for which the measurement of priming effects can be approached using 
-classifiers.
-
-\paragraph{Experimental setup.}
-
-image labeling is common\ldots
-\cite{chandler2013breaking,Berinsky2012351,Finnerty2013,paolacci2010running}.
-
-We solicited 2300 MTurk workers to perform an image-labeling task using images 
-that depicted meals, place-settings, and related items such as dishes, and 
-kitchenware, and other artifacts naturally arising in dining contexts. Workers 
-were randomly assigned into one of four treatments, described below. In all 
-treatments, workers were given brief instruc- tions before labeling any images.
-In some treatments, workers were then also shown a \textit{framing slide}, 
-indicating 
-the tasks were funded by a group having a particular research focus. The tasks 
-consisted of single images, and workers were asked to provide five descriptive 
-labels for each. The last five images that workers labeled, the 
-\textit{test set}, were the same for all treatments.
-
-The first two treatments, IMG:OBJ and IMG:FOOD, tested inter-task effects. 
-Workers in these treatments labelled ten images. In the IMG:OBJ treatment, the 
-\textit{initial set} of five images labeled by workers contained objects such 
-as utensils, kitchenware, and table-settings, but no food items. In the 
-\textsc{img:food}, the initial set contained centered close-ups of meals, 
-without
-any surrounding objects (except sometimes the dish supporting the food). No 
-interruption or distinction made between the initial and test sets from the 
-view of the workers. To study the positional dependance of inter-task effects,
-these treatments were subdivided, and workers were shown one of five 
-permutations. There are of course 5! = 120 permutations of five images, but 
-investigating all permutations was too expensive, and probably redundant, so 
-we chose 5 permutations that ensure each image occupies each position within 
-the test set. We discuss the benefits and drawbacks of this choice in the 
-supplementary material.
-
-Workers in the treatments \textsc{frm:food} and \textsc{frm:obj} were shown a 
-framing slide, which bore a message reading: ``Funded by the laboratory for 
-the visual perception of \{Food and Ingredients $\vert$ Objects and Tools\}''. 
-After the framing slide, workers in these treatments proceeded directly to 
-the test set (and so labeled only 5 images).
-
-\paragraph{The strength of inter-task effects}
-We tested for inter-task effects by training a Naive Bayes classifier to 
-classify work-products among IMG:OBJ and IMG:FOOD, using only the labels 
-attributed to the test set of images. Based on Definition 2, no classifier 
-can perform better than the actual difference in priming, so the performance 
-of Naive Bayes classifier provides a lower bound on priming difference. We 
-used leave-one-out validation to estimate the classifier per- formance. We 
-tested for framing effects in a similar way, by training a Naive Bayes 
-classifier to classify work-products among \textsc{frm:food} and 
-\textsc{frm:obj}.
-
-Overall, the first image in the test set showed the strongest signal for 
-priming effects. Fig. 3 shows the empirical lower bound for difference in 
-priming due to inter-task effects and framing based on the classifier 
-performance when using labels from the first test image. Statistically 
-significant levels of priming were detected for both modalities, but the 
-inter-task effects were stronger (hypothesis test). This suggests that strong 
-bias can result solely from the sequence of tasks performed by a worker, even 
-when those tasks are of the same type.
-
-In contrast, the classifier never performed significantly better than chance 
-when distinguish- ing treatments that differed only in framing. Thus, framing 
-effects were rather weak. In fact, framing effects were generally weak in our 
-results, so we omit treatments involving framing from the remainder of our 
-presentation to save space. We encourage the interested reader to look at the 
-results for these treatments in the supplementary material.
-
-\paragraph{Inter-task effects and the orientation of focus.}
-Since the initial images were chosen to emphasize either food (ingredients 
-set) or culture (cultural set), we looked for effects on the number of 
-culture- and food-oriented labels that workers attributed to the test image 
-set.
-
-To this end, we constructed an ontology from the labels attributed to the test 
-images. In the ontology, edges point from more general labels to more 
-specific ones. For example, the ontology contains the path \texttt{food} $\to$ 
-\texttt{ingredients} $\to$ \texttt{vegetables} $\to$ \texttt{tomato}.
-
-Since food is a central feature of culture, our ontology contains many labels 
-that have both food and culture in their ancestry. Nevertheless, there were 
-many food-oriented labels, such as bread, which lacked specific cultural 
-connections, as well as non-food, culture- orientedlabels,suchasrussian dolls.
-
-When we tallied labels attributed to the first image of the test set, we found 
-that workers from CULTimg produced significantly more culture-oriented labels 
-and less food-oriented ones than those from AMBG (see Fig. 2A). The inter-task 
-effect was so strong that the proportion of food- and culture-oriented labels 
-in CULTimg was essentially the reverse of that in AMBG. However, the 
-composition of labels attributed by INGRimg was not significantly different 
-from those attributed by AMBG. This shows that inter-task effects can 
-profoundly alter workers' focus. Again, we will argue later that the ambiguous 
-and ingredients image sets are, in fact, quite similar.
+%The first two treatments, IMG:OBJ and IMG:FOOD, tested inter-task effects. 
+%Workers in these treatments labelled ten images. In the IMG:OBJ treatment, the 
+%\textit{initial set} of five images labeled by workers contained objects such 
+%as utensils, kitchenware, and table-settings, but no food items. In the 
+%\textsc{img:food}, the initial set contained centered close-ups of meals, 
+%without
+%any surrounding objects (except sometimes the dish supporting the food). No 
+%interruption or distinction made between the initial and test sets from the 
+%view of the workers. To study the positional dependance of inter-task effects,
+%these treatments were subdivided, and workers were shown one of five 
+%permutations. There are of course 5! = 120 permutations of five images, but 
+%investigating all permutations was too expensive, and probably redundant, so 
+%we chose 5 permutations that ensure each image occupies each position within 
+%the test set. We discuss the benefits and drawbacks of this choice in the 
+%supplementary material.
+%
+%Workers in the treatments \textsc{frm:food} and \textsc{frm:obj} were shown a 
+%framing slide, which bore a message reading: ``Funded by the laboratory for 
+%the visual perception of \{Food and Ingredients $\vert$ Objects and Tools\}''. 
+%After the framing slide, workers in these treatments proceeded directly to 
+%the test set (and so labeled only 5 images).
 
 \paragraph{Inter-task effects and specificity.}
-Using the ontology described in the previous section, we can compare the 
-specificity of two labels $\ell_1$ and $\ell_2$. We say that $\ell_2$ is more specific 
-than $\ell_1$ if there is a directed path from $\ell_1$ to $\ell_2$. If there is no 
-directed path between labels, we say they are \textit{non-comparable}. For 
-example, \texttt{tomato} was more specific than \texttt{food}, while 
-\texttt{statue} and \texttt{food} were non-comparable.
-
-We can then define the relative specificity of two workers with respect to 
-test-image $i$ as $s_i(u, v)$:
+Still using the results of the first experiment, we investigated how initial 
+tasks affect the degree of specificity during the test tasks.
+To measure the relative specificity of labels, we used the hypernym-hyponym
+relationships provided by the wordnet corpus.  Hypernym relationships point
+from specific types to generalizations, while hyponyms point in the opposite
+direction.  For example, the word \texttt{bread} has the hypernym 
+\texttt{baked-goods}, and the hyponym \texttt{naan}.
+We calculated the relative specificity $s_i(u,v)$ of the labels attributed by 
+two workers $u$ and $v$ to image $i$ as follows:
 $$
@@
 where $u(i)$ denotes the set of labels attributed by worker $u$ to image $i$, 
-and $\mathbf{1}_{[l>m]}$ evaluates to 1 if $\ell$ is more specific than $m$, 
-and 0 otherwise. We then define the relative specificity of two treatments, 
-$U$ and $V$, relative to the $i$th image, denoted $S_i(U,V)$, to be the mean 
+and $\mathbf{1}_{[l>m]}$ evaluates to 1 if $\ell$ is more specific than $m$
+(meaning that $m$ can be reached from $\ell$ by following hypernyms), 
+and 0 otherwise. We then define the relative specificity $S_i(U,V)$ of two 
+treatments $U$ and $V$ relative to image $i$ to be the mean 
 relative specificity of two uniformly drawn workers:
+$$
+S_i(U,V) = \mathrm{E}_{u,v}\{s_i(u,v)\}   
+$$
 $$
@@
 $$
-Looking at labels attributed to the first test image, we found that workers 
-from \textsc{ambg} were more specific than workers from either 
-$\textsc{CULT}_{img}$ or $\textsc{ingr}_{img}$.  When we compare CULTimg to 
-INGRimg, we found that workers from INGRimg were more specific. This shows 
-that inter-task effects do substantially influence the specificity of labels 
-that workers provide. When we discuss image similarity, below, we will explore 
-a possible mechanism for this effect.
+Looking at labels attributed to the first test image, we found workers 
+that initially labeled images of ingredients were more specific 
+than those that initially labeled cultural scenes (see \textbf{Fig. 3}).  One 
+possible reason for
+this is that the images of ingredients directed workers' attention toward
+the component parts in the images.  To try to corroborate this, we can look
+at the specificity of workers whose initial tasks contained images of prepared
+meals.  Since these images contained whole prepared meals, rather than 
+separated ingredients, we can isolate the effects due to showing the presence
+of food in the initial images from the presentation of isolated parts.
 
-\paragraph{The role of task position in inter-task effects.}
-It would stand to reason that, as workers proceed through the test images, 
-priming from the initial images would be ``washed out'', diminishing the 
-observed
-inter-task effects. Looking at the classifier performance, 
-$\hat{\theta}_\mathrm{NB}$, with respect to the treatments AMBG and CULTimg, 
-we find that performance does drop off dramatically after just the first image 
-(see Fig. 3A). This suggests that inter-task effects primarily arise between 
-consecutive tasks, but that a residual effect can persist for at least five 
-tasks (we note, however that although the classifier performance seemed better 
-than chance for the fourth test image, this cannot be asserted with 95\% 
-confidence).
+In fact, the workers that intially labeled prepared meals were even
+more specific than those that initially labeled ingredients.  Recall that the
+test tasks also depicted prepared meals.  Thus, it would appear that it is 
+the similarity of initial and test tasks which drove similarity, and not the
+depiction of isolated parts (ingredients).
 
-Next we observed how inter-task effects on label composition (i.e. food- vs 
-culture-oriented labels) evolve as workers proceed through test images. We 
-define the excess cultural orientation as the number of culture-oriented 
-labels minus the number of food oriented ones. To meaning- fully compare the 
-excess cultural orientation between test images, we must, however, account 
-for the fact that some images inherently carry more cultural content than 
-others. In keeping with our notion of priming difference, we calculate the 
-excess cultural content for both CULTimg and
-
-AMBG, and take their difference to be the relative excess cultural content, 
-$\Delta_{cult}$. Formally,
-
-		*** Formula for delta cult\ldots
-
-where $N^(i)_{w,cult}$ stands for the number of culture-oriented labels 
-attributed by worker w to image i, while $N^(i)_{w,food}$ similarly counts
-food-oriented labels, and $N$ is the total number of labels in a treatment.
-
-We found $\Delta_{cult}$ was largest for the first test image, but dropped off 
-rapidly, 
-remaining positive but not to a statistically significant extent (see Fig. 3B).
-This is similar to the behavior of $\hat{\theta}_\mathrm{NB}$, however, 
-because the statistical significance of $\Delta_{cult}$ dropped more quickly, 
-$\hat{\theta}_\mathrm{NB}$ appears to be a more sensitive measure of 
-inter-task effects.
-
-\paragraph{Leveraging inter-task effects for detailed responses.}
 \begin{table}
@@
 
-To continue with the analysis, we seek a measure of image similarity. The 
+One weakness of the above analysis is the reliance on the informal notion
+of the similarity of one set of images to another. The 
 characterization of image content is a deeply complex issue that has been 
 approached by many disciplines \cite{panofsky1939studies,shatford1986analyzing,Tversky1977327,Jaimes20002}. \textit{Perceptual similarity} is a 
-particularly recalcitrant concept.
-
-However, in the present study, we are more interested how similar two sets of 
-images are, with respect to the labeling task, which is much simpler to 
-operationalize than general percep- tual similarity. Here, we measure image 
-similarity by looking at the fraction of labels that they share. Formally, to 
-measure the similarity between two sets of images, X and Y , we compute the 
-Jacquard index between the sets of labels attributed to them:
+particularly recalcitrant concept.   But to formalize our claim, we seek a 
+measure of similarity between two sets of images, 
+\textit{with respect to the labeling task}.  This can be operationalized
+in a straightforward way, by using the similarity of the labels given to images
+as a proxy for the similarity of the images.  Thus, to measure the 
+similarity between two sets of images, X and Y , we computed the Jacquard 
+index between the sets of labels attributed to them:
 $$
@@
 $$
-where $L(X)$ denotes the set of labels attributed to $X$.
+where $L(X)$ denotes the set of labels attributed to images in $X$.
 
-The pairwise similarities of the image sets are presented in Table 2. First, 
-observe that the ambiguous and ingredients sets are much more similar to each 
-other than either is to the culture set. Recalling the data presented in 
-Fig. 1, this helps explain why two treatments could not be distinguished on 
-the basis of having differing initial sets corresponding to ambiguous and 
-cultural. This also explains why AMBG and CULTimg had similar label 
-compositions in Fig. 2A.
+The pairwise similarities of the image sets are presented in Table 2. This 
+shows that the workers that yielded higher specificity labels were from 
+treatments whose initial tasks were more similar to the test tasks (c.f.
+\textbf{Fig 3}).
 
-Next we draw attention to the similarity between the initial sets and the test 
-set. The am- biguous set is the most similar to the test set, followed by the 
-ingredients set, with the cultural set being most different. Observe that these
-levels of similarity mirror the label specificity for the corresponding 
-treatments (c.f. Fig. 2B).
-
-This suggests that labeling a series of images that are similar to one another 
-might encourage workers to use more specific terminology. Such a phenomenon 
-would be consistent with the psychological mechanism known as 
+Such a phenomenon would be consistent with the psychological mechanism known as
 \textit{negative priming}.
 Negative priming occurs when a person becomes desensitized to non-salient 
-stimuli to which she is repeatedly exposed. Consider that workers who 
-initially labeled the ambiguous image set had already seen five images 
-showing prepared meals once they labeled the first test image. At that point, 
-a worker might not regard the generic labels \texttt{food} or \texttt{meal} to 
-be salient, and opt instead for \texttt{bread}, or \texttt{pasta}.
+stimuli to which she is repeatedly exposed. Consider that, workers that 
+initially labeled images depicting prepared meals might no longer
+regard the generic labels \texttt{food} or \texttt{meal} to be salient, and 
+opt instead for \texttt{bread}, or \texttt{pasta}.  But for workers that
+initially labeled cultural images, these rather generic labels might well seem
+appropriate.
 
@@
 distinguishing.
+
+\paragraph{The role of task position in inter-task effects.}
+Up to this point, we have focused on the inter-task effects induced on 
+the first test task.  Not suprisingly, this task was, in general, more 
+strongly affected than the others.  It would stand to reason that, as workers 
+proceed through the test images, priming induced by the initial tasks would
+be ``washed out'', and replaced by the effects of the test tasks themselves,
+which do not differ between treatments.
+
+To investigate this, we performed a second experiment, in which we permuted
+the test tasks in such a way that every test task appears in each of the
+5 locations equally often.  This allows us to track the intertask effects for
+a given test task as it is rotated through the five positions.  Workers were
+again given one of two initial sets of tasks, which either involved labeling
+utensils, cookware, and table settings (but no food), or isolated close-up
+images of prepared meals.  We measured the performance of a Naive Bayes 
+classifier in distinguishing whether labels attributed to a given test 
+image were provided by a worker that labeled objects or meals, as shown in 
+\textbf{Fig. 4}.
+
+The strength of inter-task effects show a clear trend based on the position of
+the test task.  We see that, in general, the first test image is most severely
+affected, and the severity of effect drops off.  Curiously, the severity then
+rises again for the second last, and, especially, final test image.  We 
+speculate that this is related to the workers being aware that they are 
+reaching the end of the batch of labeling tasks.  To be transparent about the
+rate of compensation, we informed workers that they would complete a total
+of ten image-labeling tasks.  Perhaps as the worker nears the end of the batch
+of tasks, she reflects on the overall experience, and in activating the
+memory of the early tasks, is partially re-primed.
 
@@
 \end{document}
+
+%Next we observed how inter-task effects on label composition (i.e. food- vs 
+%culture-oriented labels) evolve as workers proceed through test images. We 
+%define the excess cultural orientation as the number of culture-oriented 
+%labels minus the number of food oriented ones. To meaning- fully compare the 
+%excess cultural orientation between test images, we must, however, account 
+%for the fact that some images inherently carry more cultural content than 
+%others. In keeping with our notion of priming difference, we calculate the 
+%excess cultural content for both CULTimg and
+%
+%AMBG, and take their difference to be the relative excess cultural content, 
+%$\Delta_{cult}$. Formally,
+%
+%		*** Formula for delta cult\ldots
+%
+%where $N^(i)_{w,cult}$ stands for the number of culture-oriented labels 
+%attributed by worker w to image i, while $N^(i)_{w,food}$ similarly counts
+%food-oriented labels, and $N$ is the total number of labels in a treatment.
+%
+%We found $\Delta_{cult}$ was largest for the first test image, but dropped off 
+%rapidly, 
+%remaining positive but not to a statistically significant extent (see Fig. 3B).
+%This is similar to the behavior of $\hat{\theta}_\mathrm{NB}$, however, 
+%because the statistical significance of $\Delta_{cult}$ dropped more quickly, 
+%$\hat{\theta}_\mathrm{NB}$ appears to be a more sensitive measure of 
+%inter-task effects.

### 2014-10-22 src/analysis.py

@@ -29,6 +29,7 @@ import numpy as np
 import json
 import wordnet_analysis as wna
 from collections import defaultdict, Counter
+import os
 
 # Number of stardard deviations equivalent to the % condifdence for a 
 # normal variate
@@ -36,7 +37,233 @@ CONFIDENCE_95 = 1.96
 CONFIDENCE_99 = 2.975
 TEST_IMAGES = ['test%d'%i for i in range(5)]
 
-def bound_l1(fname='data/new_data/l1.json'):
+EXP1_TREATMENTS = {
+	'1_img_food': [0],
+	'1_img_cult': [1],
+	'1_img_ingr': [2],
+	'1_wfrm_food': [3],
+	'1_wfrm_cult': [5],
+}
+EXP2_TREATMENTS = {
+	'2_img_food': range(5),
+	'2_img_obj': range(5,10),
+	'2_wfrm_food': [10],
+	'2_wfrm_obj': [11],
+	'2_sfrm_food': [12],
+	'2_sfrm_obj': [13],
+}
+
+def get_word_counts(experiment, treatments, image):
+	d = data_processing.SimpleDataset(
+		which_experiment=experiment,
+		show_token_pos=False,
+		show_token_img=False,
+		do_split=False,
+		class_idxs=treatments,
+		img_idxs=[image],
+	)
+	return d.vocab_counts
+
+
+def calculate_all_relative_specificities():
+
+	fname= 'data/new_data/specificity.json'
+	write_fh = open(fname, 'w')
+
+	#images = ['test%d'% i for i in range(5)]
+	images = range(5,10)
+	results = {}
+
+	## start with experiment 1
+	results['img_food_cult'] = []
+	results['img_food_ingr'] = []
+	results['img_ingr_cult'] = []
+	results['frm_food_cult'] = []
+
+	results['wfrm_food_cult'] = []
+	results['img_food_obj'] = []
+	results['wfrm_food_obj'] = []
+	results['sfrm_food_obj'] = []
+	results['img_food_sfrm_food'] = []
+	results['img_obj_sfrm_obj'] = []
+	results['img_cult_wfrm_cult'] = []
+	results['img_food_wfrm_food'] = []
+
+	for image in images:
+		# compare the img_priming
+		counts_food = get_word_counts(1, [0], image)
+		counts_cult = get_word_counts(1, [1], image)
+		results['img_food_cult'].append(wna.calculate_relative_specificity(
+			counts_food, counts_cult))
+
[…]

### 2014-10-22 src/data_processing.py

@@ -31,6 +31,7 @@ import csv
 from collections import defaultdict, Counter
 from random import shuffle
 from nltk.corpus import wordnet as wn
+import nltk
 
 
 def readDataset(is_exp_2_dataset=False):
@@ -117,11 +118,19 @@ def get_pos(img_idx, class_idx, offset=False):
 	return (img_idx - class_idx) % 5 + 5
 
 
-
+SPLIT_RE = re.compile(r'[^a-zA-Z0-9]')
 def clean_dataset_adaptor(
 		clean_dataset, 
 		treatments=['treatment0', 'treatment1'], 
-		images=['test0']
+		images=['test0'],
+		show_token_pos=True,
+		show_plain_token=True,
+		do_split=True,
+		remove_stops=True,
+		lemmatize=True,
+#		spellcheck=True,
+#		experiment=2,
+		weight='tfidf', # Not implemented does nothing
 	):
 	'''
 	extracts a dataset from the clean_dataset object in the format expected
@@ -130,6 +139,18 @@ def clean_dataset_adaptor(
 
 	# we'll accumulate the new dataset in here
 	naive_bayes_dataset = defaultdict(lambda: [])
+
+	# we might need a dictionary of spelling corrections
+	#if spellcheck:
+	#	dictionary = json.loads(open('data/new_data/dictionary.json').read())
+
+	# we might need a lemmatizer
+	if lemmatize:
+		lmtzr = nltk.stem.wordnet.WordNetLemmatizer()
+
+	# we might need the stopwords list
+	if remove_stops:
+		stops = set(nltk.corpus.stopwords.words('english'))
 
 	# walk over all the treatments
 	for treatment in treatments:
@@ -150,10 +171,54 @@ def clean_dataset_adaptor(
 			for image in images:
 				labels_for_image = filter(lambda x: x[0][0]==image, all_items)
 
-				# this may look a bit strange.  We're just repacking the
-				# info we want -- features are image-label tuples 
-				features_for_image = [
-					(image, word) for (image, pos), word in labels_for_image]
+				features_for_image = []
+
+				for label in labels_for_image:
+
+					# take apart the label components
+					(img_idx, pos), word = label
+
+					# maybe split up multiple words entered in same input
+					if do_split:
+						words = SPLIT_RE.split(word)
+					else:
+						words = [word]
+
+					# maybe remove stopwords
+					if remove_stops:
+						words = [w for w in words if w not in stops]
+
+#					# maybe correct spelling
+#					if spellcheck:
[…]

### 2014-10-22 src/new_plots.py

@@ -13,12 +13,13 @@ import ontology
 import data_processing
 import numpy as np
 import time
+import os
 
 try:
 	import matplotlib.pyplot as plt
 	import matplotlib 
 	import matplotlib.gridspec as gridspec
-	from matplotlib.ticker import FixedLocator, LinearLocator, FixedFormatter
+	from matplotlib.ticker import MultipleLocator, FormatStrFormatter
 
 except:
 	print 'matplotlib not installed.  You can do computations but not '\
@@ -39,6 +40,461 @@ TREATMENT_NAMES = {
 	, 'treatment5': 'CULT$_{fund}$'
 	, 'treatment6': 'CULT$_{fund,img}$'
 }
+
+TEST_NAMES = [
+	'img_food_cult',
+	'img_food_obj',
+	'wfrm_food_cult',
+	'wfrm_food_obj',
+	'sfrm_food_obj'
+]
+
+EXPERIMENT_NAMES = {
+	'img_food_cult': 'inter-t. 1',
+	'img_food_obj': 'inter-t. 2',
+	'wfrm_food_cult': 'frame 1',
+	'wfrm_food_obj': 'frame 2',
+	'sfrm_food_obj': 'frame 3'
+}
+
+IMAGE_NAMES = ['test%d' %i for i in range(5)]
+
+DATA_DIR = 'data/new_data'
+FIGS_DIR = 'figs/'
+
+
+def plot_food_specificity(
+		read_food_fname='data/new_data/food.json',
+		read_specificity_fname='data/new_data/specificity.json',
+		write_fname='figs/food_specificity.pdf'
+	):
+
+	# open files
+	food_data = json.loads(open(read_food_fname).read())
+	specificity_data = json.loads(open(read_specificity_fname).read())
+
+	# make a figure with two subplots
+	figWidth = 16.78 / 2.54 	# conversion from PNAS spec in cm to inches
+	figHeight = 3/5.*figWidth	# a reasonable aspect ratio
+	fig = plt.figure(figsize=(figWidth, figHeight))
+	gs = gridspec.GridSpec(1, 2)
+
+	width = 0.325
+
+
+	# plot food data first
+	ax1 = plt.subplot(gs[0])
+		
+	pairs = [
+		('2_img_obj', '2_img_food'),
+		#('1_img_cult', '1_img_food'),
+		('2_wfrm_obj', '2_wfrm_food'),
+		#('1_wfrm_cult', '1_wfrm_food'),
[…]

### 2014-10-22 src/plots.py

@@ -40,6 +40,8 @@ TREATMENT_NAMES = {
 	, 'treatment6': 'CULT$_{fund,img}$'
 }
 
+
+
 def plotSpecificityLongitudinal(
 		readFnames=[
 			'specificity/t0-t1-test%d-overall.json' % i for i in range(5)],

### 2014-10-22 src/runnable_analysis.py

@@ -85,12 +85,6 @@ def find_best_svm_params(write_fname=BEST_PARAMS_FNAME):
 	write_fh.close()
 
 
-
-
-
-
-
-
 class LognormalSimulatedAnnealer(object):
 
 	RESULTS_PATH = SVM_OPTIMIZATION_DIR
@@ -434,18 +428,11 @@ def calc_priming_diff_svm(fname=SVM_EXP2_L1_FNAME):
 
 
 
-
-
-
-
 def calc_priming_differences():
 	'''
 	Calculates a whole bunch of priming differences based on binary 
 	classification using a naive Bayes classifier and the CleanDataset
 	representation.
-
-	This is basically obsolete because I have moved to using SVM as a
-	classifier.
 	'''
 
 	OLD_DATASET = False

### 2014-10-22 src/tests.py

@@ -307,6 +307,28 @@ class DFSTestCase(unittest.TestCase):
 		return False
 
 
+	def test_dfs_cycle_safe(self):
+		# make a dfs using the callbacks and 
+		self.dfs = wna.DFS(
+			self.get_node_hash,
+			self.get_children_callback,
+			self.inter_node_callback,
+			self.leaf_node_callback,
+			self.abort_branch_callback,
+			allow_double_process=True
+		)
+
+		# introduce a cycle
+		self.c2['children'].append(self.c0)
+
+		# attempt to walk the graph containing a cycle
+		# a max-recursion depth error will occur if cycle protection fails
+		expected_walk = 'c0 -> c1 -> c3; c4; c2 -> c3; c5'
+		found_walk = self.dfs.start_walk(self.c0)
+
+		self.assertEqual(expected_walk, found_walk)
+
+
 	def test_dfs_duplicate_allowed(self):
 		# make a dfs using the callbacks and 
 		self.dfs = wna.DFS(
@@ -318,7 +340,7 @@ class DFSTestCase(unittest.TestCase):
 			allow_double_process=True
 		)
 
-		found_walk = self.dfs.walk(self.c0)
+		found_walk = self.dfs.start_walk(self.c0)
 		expected_walk = 'c0 -> c1 -> c3; c4; c2 -> c3; c5'
 
 		self.assertEqual(expected_walk, found_walk)
@@ -335,7 +357,7 @@ class DFSTestCase(unittest.TestCase):
 			allow_double_process=False
 		)
 
-		found_walk = self.dfs.walk(self.c0)
+		found_walk = self.dfs.start_walk(self.c0)
 		expected_walk = 'c0 -> c1 -> c3; c4; c2 -> c5'
 
 		self.assertEqual(expected_walk, found_walk)

### 2014-10-22 src/wordnet_analysis.py

@@ -163,7 +163,7 @@ def get_all_synsets(label):
 	return synsets
 
 
-def map_to_synsets(clean_dataset, treatment, images):
+def map_to_synsets(word_counts):
 	'''
 	given a CleanDataset, a treatment name, and image name, 
 	get all the labels that workers from the given treatment attribute to
@@ -172,22 +172,26 @@ def map_to_synsets(clean_dataset, treatment, images):
 	(Note that the map from labels to synsets is many to many.)
 	'''
 
-	# get a counter for the words associated to the treatment and image
-	label_counts = Counter()
-	for image in images:
-		label_counts += clean_dataset.get_counts_for_treatment_image(
-			treatment, image)
-
 	synset_counts = Counter()
-	for label in label_counts:
-		synsets = get_all_synsets(label)
-		add_to_counts = dict([(s, label_counts[label]) for s in synsets])
+	for word in word_counts:
+		count = word_counts[word]
+		synsets = get_all_synsets(word)
+		add_to_counts = dict([(s, count) for s in synsets])
 		synset_counts.update(add_to_counts)
 
 	return synset_counts
 
 
-def calculate_relative_specificity(synset_counts_1, synset_counts_2):
+def calculate_relative_specificity(word_counts_1, word_counts_2):
+	'''
+	returns the relative specificity between to sets of synsets.
+	This is positive when synset_counts_1 is more specific overall than
+	synset_counts_2.  Reversing the order of the arguments reverses the sign, 
+	but gives the same result.
+	'''
+
+	synset_counts_1 = map_to_synsets(word_counts_1)
+	synset_counts_2 = map_to_synsets(word_counts_2)
 
 	# Make relative counters based on synset_counts_2
 	ancester_counter = WordnetRelativesCalculator(synset_counts_2, True)
@@ -199,11 +203,12 @@ def calculate_relative_specificity(synset_counts_1, synset_counts_2):
 	# minus the number of ancesters to get the net relative specificity
 
 	for synset_name, count in synset_counts_1.iteritems():
-		synset = wn.synset(synset_name)
-		specificity_score += count * ancester_counter.count(synset)
-		specificity_score -= count * descendant_counter.count(synset)
+		syn = wn.synset(synset_name)
+		specificity_score += count * ancester_counter.count(syn)
+		specificity_score -= count * descendant_counter.count(syn)
 
[…]

### 2014-10-23 docs/publications/2014.09_SCIENCE/man.tex
more work on manuscript

@@
 We have said nothing qualitative about the \textit{nature} of these effects.  
-This is one of the advantages of measuring priming using classifiers: one need 
-not know beforehand how workers were primed, nor, 
-how it might affect worker's responses.  Machine learning algorithms are
-specifically designed to generalize inductively from examples, which makes
+This demonstrates an advantage of using classifiers to measure priming.  
+Machine learning algorithms are designed to find salient differences 
+by generalizing, inductively, from examples, so one
+need not know beforehand how workers were primed, nor the natuer of the  
+priming effects.  Machine learning algorithms are specifically designed to 
+generalize inductively from examples, which makes
 it possible to estimate how different two populations with little prior 
@@
 
-Having shown that workers are strongly primed by initial tasks, a natural
-question is whether workers were biased to provide labels that reflected, 
-in some way, the content of the initial tasks.  All of the experiments 
-we performed involved a treatment exposed to a food-related prime, as well
-as a treatment exposed to a non-food prime (objects/tools or culture), so
-we can test the effects on the content of labels by determining the fraction
-of food-related labels that workers provide during the test tasks.
+But once having shown that workers are strongly primed by initial tasks, it is
+natural ask whether workers were biased to provide labels that reflected, 
+in some way, the \textit{content} of the initial tasks.  The conceptual basis
+for the primes in experiment 2 were eithre \textit{food} or 
+\textit{objects and tools}.  Thus, we can test whether workers exposed to food
+primes produced more food-related.
 
-We used wordnet, via the nltk package for python, to detect labels that are 
-food-related.  Wordnet is an extensive corpus for English that contains a 
-detailed set of hypernym-hyponym relationships for nouns.  Hypernyms are 
-generalizations, while hyponyms are specific instances or types.  For example,
-\textit{pumpernickel} is a type of \textit{bread}, so bread is a hypernym of 
-\textit{pumpernickel}, and \textit{pumpernickel} is a hyponym of 
-\textit{bread}.  We identified the top-level food-related entries in wordnet 
-and considered all hyponym-descendants of these words to be food-related.
+To identify food-related labels, we used the wordnet corpus.  Wordnet
+is an extensive corpus for English, that includes hypernym-hyponym 
+relationships between words.  The hypernym relation correpsonds to conceptual
+abstraction.  For example \textit{bread} is a hypernym of 
+\textit{pumpernickel} because pumpernickel is a \textit{type of} bread.
+The hyponym relation is simply the converse: pumpernickel is a hyponym
+of bread.  For the purpose of our analysis, when we refer to hypernyms,
+we will mean both direct hypernyms, as well as the hypernyms of hypernims,
+and so on, with an analogous interpretation for hyponyms.
 
-We use this to test the effect of initial tasks on the direction of workers
-focus in both \textit{inter-t.1}, \textit{frame2}, and \textit{frame}*3.  
-Recall that this experiment involved
-workers either primed for the concept of food or objects/tools, using either
-initial tasks or framing.  Our findings matched the straightforward
-expectation that workers exposed to food related-primes are biased to 
-provide more food-related labels during test tasks.  But the strength of
-the bias does not account for the degree of priming we measured using a 
-classifier (c.f. fig 2A).  Although we do see the expected
-bias towards providing food labels, the bulk of inter-task effects would appear
-to be of a more subtle nature.
+We collectod a small set of top-level food-related nouns in wordnet,
+together with all of their hyponyms, and took the resulting set of 
+3589 lemmas as an operational definition for the set of English food-related 
+words.  This set is quite extensive, containing somewhat obscure forms such as
+``burgoo'' and ``barmbrack'', and consumables at the fringe of what might
+be considered food such as ``vitamin B'' (or if you prefer, 
+``B complex''), as well as more common lemmas like
+``banana'',  ``bread'', and of course ``banana bread''.  We found that,
+for the data in experiment 1, this method produced excellent aggreement with 
+human annotation of food-related words (see supplementary material).  
+For the analysis exp2, the variety of non-English names for ethnic dishes 
+forced us to rely on a manual approach.  This corroborated our results
+for exp1, and we encourage the interested reader to read our discussion of
+the manual approach in the supplementary material.
 
-Inspecting the labels manually, one striking observation was some treatments
-had substantially more generic labels, for example providing labels such as
-\texttt{food} or \texttt{meal} as opposed to \texttt{spaghetti}.  To test this
-rigorously, we used the hypernym-hyponym relationships provided by wordnet.  
-To compare the relative specificity of two sets of labels $P$ and $Q$, we first
-define the relative specificity of a single label $p \in P$ in the context of
-$Q$:
+Our findings matched the straightforward expectation that workers exposed to 
+food related-primes were biased to provide more food-related labels during 
+test tasks (see Fig. 3A).  Had we relied on the intuition that workers 
+should be biased to label according to the underlying concept of their prime,
+we would have underestimated the strength of priming effects.  This
+again illustrates the advantage of using classifiers to detect priming as
+opposed to testing for the effects that one might intuitively expect.  
+Though present, the expected influence on the number of food-related words
+cannot account for the bulk of inter-taks effects.
+
+\paragraph{Effects on label vocabulary.}
+Inspecting the labels manually, one striking observation was that in
+\textit{test-t.2}, workers that initially images of cultural scenes seemed
+more likely to give generic labels, compared to those that initially labeled 
+images depicting prepared meals.  Recall that, for these treatments, the test 
+tasks contained images depicting prepared meals, which are very similar in
+content to the initial tasks for the latter set of workers.  Workers that
+had already labeled 5 images depicting food were less likely to attribute
+the generic label ``food'' during the first test task, doing so only 16 times,
+compared to 76 times by workers that had labeled culture-related images 
+containing no food.  This observation suggests that, when workers label a 
+series of very similar images.
+
+One straightforward way to test whether workers from exp2.task.food are 
+being more specific than those from exp2.taks.cult is to look at the number 
+of unique labels they provided for each image.  Workers attributing more
+specific labels should produce a larger vocabulary of unique labels for a 
+given, which is indeed what we found (see Fig. 3B).  Workers from 
+exp2.task.food produced as much as 33\% more unique labels per image than 
+workers from exp2.task.cult, and the relative excess of the vocabulary size
+followed the general trend of inter-task effects that we observed in 
+Fig. 2B.
+
+To confirm our expectation that the larger vocabulary corresponds to a 
+the use of \textit{more nuanced} words, we used the 
+hypernym-hyponym of wordnet to operationalize a notion of relative 
+specificity.  We define the relative specificity of two sets of labels $P$ 
+and $Q$ as:
 $$
-s(p,Q) = \left\{
-	\begin{array}{l l}
-		\frac{N_>(p,Q) - N_<(p,Q)}{N(p,Q)} &\mathrm{if}\quad N(p,Q) > 0\\
-		0 &\mathrm{else}
-	\end{array}
-	\right.,
+	S(P,Q) = \frac{1}{|P \times Q|}\sum_{p \in P} \sum_{q \in Q} 
+		\left(\mathbf{1}_{[p>q]} - \mathbf{1}_{[q>p]}\right),
 $$
-where $N_>(p,Q)$ is the number hyponyms of $p$ found in $Q$, and $N_<(p,Q)$ is
-the number of hypernyms of $p$ found $Q$.  For this calculation, we consider 
-the ``hypernyms of $p$'' to include hypernyms of hypernyms of p, etc., 
-adopting the analogous interpretation for hyponyms.  Then, the relative
-specificity of the entire set $P$ relative to $Q$ as:
-$$
-	S(P,Q) = \frac{1}{|P|}\sum_{p \in P} s(p,Q).
-$$
+where $\mathbf{1}_{[p>q]}$ evaluates to 1 if $p$ is a hyponym of $q$.
+Using the above equation, we found that, for every images in the 
+test set, the labels attributed by workers in exp2.task.food were more 
+specific than those by workers in exp2.task.cult.
+
+Thus, when workers perform a series of similar image labeling tasks it would
+appear that they tend to avoid generic words, opting instead for more specific
+ones, and yielding a richer vocabulary of labels.  Qualitative 
+characterisation and classification is one of the most comman applications of 
+microtask platforms, and this finding suggests that bundling similar tasks 
+together substantially increases the specificity of HPU output.
+
+Our observations of the effects on specificity would appear to be consistent
+with the phenomenon of negative priming.
+Negative priming occurs when a person becomes desensitized to non-salient 
+stimuli to which she is repeatedly exposed. Consider that, workers that 
+initially labeled images depicting prepared meals might no longer
+regard the generic labels \texttt{food} or \texttt{meal} to be salient, and 
+opt instead for \texttt{bread}, or \texttt{pasta}.  But for workers that
+initially labeled cultural images, these rather generic labels might well seem
+appropriate.
+
+We are suggesting that, although workers are not instructed to compare images 
+in any way, prior tasks nevertheless create a frame of reference relative to 
+which later tasks are judged. This in turn influences the perception of 
+salience. Thus, in a series of subjective characterization tasks that have 
+very similar content, workers' focus will tend to be directed away from 
+generic, shared attributes, towards those attributes that are specific and 
+distinguishing.
 
@@
 hand, the framing primes had no statistically significant effect.
-
-%The first two treatments, IMG:OBJ and IMG:FOOD, tested inter-task effects. 
-%Workers in these treatments labelled ten images. In the IMG:OBJ treatment, the 
-%\textit{initial set} of five images labeled by workers contained objects such 
-%as utensils, kitchenware, and table-settings, but no food items. In the 
-%\textsc{img:food}, the initial set contained centered close-ups of meals, 
-%without
-%any surrounding objects (except sometimes the dish supporting the food). No 
-%interruption or distinction made between the initial and test sets from the 
-%view of the workers. To study the positional dependance of inter-task effects,
-%these treatments were subdivided, and workers were shown one of five 
-%permutations. There are of course 5! = 120 permutations of five images, but 
-%investigating all permutations was too expensive, and probably redundant, so 
-%we chose 5 permutations that ensure each image occupies each position within 
-%the test set. We discuss the benefits and drawbacks of this choice in the 
-%supplementary material.
-%
-%Workers in the treatments \textsc{frm:food} and \textsc{frm:obj} were shown a 
-%framing slide, which bore a message reading: ``Funded by the laboratory for 
-%the visual perception of \{Food and Ingredients $\vert$ Objects and Tools\}''. 
-%After the framing slide, workers in these treatments proceeded directly to 
-%the test set (and so labeled only 5 images).
-
-\paragraph{Inter-task effects and specificity.}
-Still using the results of the first experiment, we investigated how initial 
-tasks affect the degree of specificity during the test tasks.
-To measure the relative specificity of labels, we used the hypernym-hyponym
-relationships provided by the wordnet corpus.  Hypernym relationships point
-from specific types to generalizations, while hyponyms point in the opposite
-direction.  For example, the word \texttt{bread} has the hypernym 
-\texttt{baked-goods}, and the hyponym \texttt{naan}.
-We calculated the relative specificity $s_i(u,v)$ of the labels attributed by 
-two workers $u$ and $v$ to image $i$ as follows:
-$$
-	s_i(u,v) = \sum_{\ell \in u(i)} \sum_{\ell \in v(i)} 
-	\left( \mathbf{1}_{[\ell > m]} - \mathbf{1}_{[m>\ell]} \right),
-$$
-where $u(i)$ denotes the set of labels attributed by worker $u$ to image $i$, 
-and $\mathbf{1}_{[l>m]}$ evaluates to 1 if $\ell$ is more specific than $m$
-(meaning that $m$ can be reached from $\ell$ by following hypernyms), 
-and 0 otherwise. We then define the relative specificity $S_i(U,V)$ of two 
-treatments $U$ and $V$ relative to image $i$ to be the mean 
-relative specificity of two uniformly drawn workers:
-$$
-S_i(U,V) = \mathrm{E}_{u,v}\{s_i(u,v)\}   
-$$
-$$
-\hat{S}_i(U,V) = \frac{1}{|U \times V|} \sum_{u \in U} \sum_{v in V}
-		s_i(u,v).
-$$
-Looking at labels attributed to the first test image, we found workers 
-that initially labeled images of ingredients were more specific 
-than those that initially labeled cultural scenes (see \textbf{Fig. 3}).  One 
-possible reason for
-this is that the images of ingredients directed workers' attention toward
-the component parts in the images.  To try to corroborate this, we can look
-at the specificity of workers whose initial tasks contained images of prepared
-meals.  Since these images contained whole prepared meals, rather than 
-separated ingredients, we can isolate the effects due to showing the presence
-of food in the initial images from the presentation of isolated parts.
-
-In fact, the workers that intially labeled prepared meals were even
-more specific than those that initially labeled ingredients.  Recall that the
-test tasks also depicted prepared meals.  Thus, it would appear that it is 
-the similarity of initial and test tasks which drove similarity, and not the
-depiction of isolated parts (ingredients).
 
@@
 \textit{negative priming}.
-Negative priming occurs when a person becomes desensitized to non-salient 
-stimuli to which she is repeatedly exposed. Consider that, workers that 
-initially labeled images depicting prepared meals might no longer
-regard the generic labels \texttt{food} or \texttt{meal} to be salient, and 
-opt instead for \texttt{bread}, or \texttt{pasta}.  But for workers that
-initially labeled cultural images, these rather generic labels might well seem
-appropriate.
-
-We are suggesting that, although workers are not instructed to compare images 
-in any way, prior tasks nevertheless create a frame of reference relative to 
-which later tasks are judged. This in turn influences the perception of 
-salience. Thus, in a series of subjective characterization tasks that have 
-very similar content, workers' focus will tend to be directed away from 
-generic, shared attributes, towards those attributes that are specific and 
-distinguishing.
-
 \paragraph{The role of task position in inter-task effects.}

### 2014-10-23 src/analysis.py

@@ -53,16 +53,99 @@ EXP2_TREATMENTS = {
 	'2_sfrm_obj': [13],
 }
 
-def get_word_counts(experiment, treatments, image):
+
+
+def get_all_word_counts(fname='data/new_data/vocabulary.json'):
+
+	results = {}
+	treatments = {
+		'exp1.task.food': (1,0),
+		'exp1.task.cult': (1,1),
+		'exp1.task.ingr': (1,2),
+		'exp1.frame.ingr': (1,3),
+		'exp1.frame.cult': (1,5),
+		'exp2.task.food': (2,0),
+		'exp2.task.obj': (2,5),
+		'exp2.frame.food': (2,10),
+		'exp2.frame.obj': (2,11),
+		'exp2.frame*.food': (2,12),
+		'exp2.frame*.obj': (2,13),
+	}
+
+	experiment = 1
+	vocab_sizes = {}
+	
+	for key, (exp, treatment) in treatments.items():
+
+		this_vocabs = []
+		vocab_sizes[key] = this_vocabs
+
+		for image in range(5,10):
+
+			this_vocabs.append(
+				len(get_word_counts(exp, [treatment], [image])))
+
+	return vocab_sizes
+
+
+
+def get_word_counts(experiment, treatments, images):
 	d = data_processing.SimpleDataset(
 		which_experiment=experiment,
 		show_token_pos=False,
 		show_token_img=False,
 		do_split=False,
 		class_idxs=treatments,
-		img_idxs=[image],
+		img_idxs=images,
 	)
+	d.balance_classes(119)
 	return d.vocab_counts
+
+
+def calculate_similarity(fname='data/new_data/similarity.json'):
+
+	# open the file that we will write to
+	results_file = open(fname, 'w')
+	treatments = {
+		'exp1.task.food': (1,0),
+		'exp1.task.cult': (1,1),
+		'exp1.task.ingr': (1,2),
+		#'exp1.frame.ingr': (1,3),
+		#'exp1.frame.cult': (1,5),
+		'exp2.task.food': (2,0),
+		'exp2.task.obj': (2,5),
+		#'exp2.frame.food': (2,10),
+		#'exp2.frame.obj': (2,11),
+		#'exp2.frame*.food': (2,12),
+		#'exp2.frame*.obj': (2,13),
+	}
+
+	test_sets = {
+		'exp1': (1, [0,1,2]),
+		'exp2': (2, [0,5])
+	}
+
[…]

### 2014-10-23 src/data_processing.py

@@ -299,13 +299,15 @@ class SimpleDataset(object):
 
 		# read in the raw data
 		self.read_raw_data()
-		self.balance_classes()
+		if balance_classes:
+			self.balance_classes()
 
 
-	def balance_classes(self):
+	def balance_classes(self, truncate_to=None):
 
 		# what is the min number of examples in each class?
-		truncate_to = min([len(self.data[idx]) for idx in self.data])
+		if truncate_to is None:
+			truncate_to = min([len(self.data[idx]) for idx in self.data])
 
 		# truncate all data (randomly) to even out number of examples
 		for idx in self.data:

### 2014-10-23 src/wordnet_analysis.py

@@ -1,3 +1,4 @@
+import copy
 from nltk.corpus import wordnet as wn
 from collections import Counter
 import re
@@ -213,15 +214,17 @@ def calculate_relative_specificity(word_counts_1, word_counts_2):
 
 class WordnetFoodDetector(object):
 	def __init__(self):
-		self.foodish_cache = {
-			'food.n.02': True, 
-			'food.n.01': True, 
-			'helping.n.01': True,
-			'taste.n.01': True, 
-			'taste.n.05': True, 
-			'taste.n.06': True, 
-			'taste.n.07': True
-		}
+		self.food_synsets = [
+			'food.n.02', 
+			'food.n.01', 
+			'helping.n.01',
+			'taste.n.01', 
+			'taste.n.05', 
+			'taste.n.06', 
+			'taste.n.07'
+		]
+
+		self.foodish_cache = dict([(s,True) for s in self.food_synsets])
 
 		# We will build a DFS walker to help with the calculation
 		# To do so, we need to define a bunch of callbacks
@@ -268,6 +271,55 @@ class WordnetFoodDetector(object):
 			abort_branch_callback,
 			allow_double_process
 		)
+
+
+	def get_food_vocab(self):
+
+		# we will bulid a DFS that accumulates all of the food-related lemmas
+		# begin by defining the DFS's callback functions
+		def get_node_hash(node):
+			return node.name
+
+		def get_children_callback(node):
+			return node.hyponyms()
+		
+		def inter_node_callback(node, child_vals=[]):
+			this_result = [l.name for l in node.lemmas]
+
+			# each child returns a list, flatten this to one list
+			child_results = reduce(lambda x,y: x + y, child_vals, [])
+
+			print this_result + child_results
+
+			return this_result + child_results
+
+		def abort_branch_callback(node):
+			return False
+
+		allow_double_process = False
+
+		# build the DFS
+		food_vocab_counter = DFS(
+			get_node_hash,
+			get_children_callback,
+			inter_node_callback,
+			inter_node_callback,	# this callback works for leaves too
+			abort_branch_callback,
+			allow_double_process
+		)
+
+		# for each top-level food synset, 
+		# walk the DFS to collect the vocabulary
+		vocab = []
+		for syn_name in self.food_synsets:
+			syn = wn.synset(syn_name)
+			vocab += food_vocab_counter.start_walk(syn)
+
+		# eliminate duplicates
+		vocab = set(vocab)
+
+		# done!
+		return vocab
 
 
 	def is_food(self, label):

### 2014-10-27 docs/publications/2014.09_SCIENCE/man.tex
more analysis work (dictionary) and manuscript work

@@
 	$$
+	\mathcal{D}(P,Q) = 
+		\left| 
+			\mathrm{E}\left\{ \mathcal{D}(p) \right\} 
+			- \mathrm{E}\left\{ \mathcal{D}(q) \right\} 
+		\right|,
 	\theta_\mathcal{D}(P,Q) = 
@@
 \paragraph{Effects on label vocabulary.}
-Inspecting the labels manually, one striking observation was that in
-\textit{test-t.2}, workers that initially images of cultural scenes seemed
-more likely to give generic labels, compared to those that initially labeled 
-images depicting prepared meals.  Recall that, for these treatments, the test 
-tasks contained images depicting prepared meals, which are very similar in
-content to the initial tasks for the latter set of workers.  Workers that
-had already labeled 5 images depicting food were less likely to attribute
-the generic label ``food'' during the first test task, doing so only 16 times,
-compared to 76 times by workers that had labeled culture-related images 
-containing no food.  This observation suggests that, when workers label a 
-series of very similar images.
+When manually inspecting the labels of \textit{test-t.2}, one striking 
+observation was that workers that initially labeled images of cultural scenes 
+were more likely to use generic words when labeling the test images, compared 
+to workers that initially labeled images of meals.  For example, 76\% of the 
+workers from \textit{exp2.task.cult} gave the very generic label 
+\texttt{food}, compared to only 16\% of \textit{exp2.task.food} workers 
+(recall that the test tasks for both treatments depicted prepared meals).
+One interpretation is that workers who have already labeled 5 images relating
+to food are more likely to focus on aspects of the images that are different
+from one another, and refrain from so generic a term as \texttt{food}.
 
-One straightforward way to test whether workers from exp2.task.food are 
-being more specific than those from exp2.taks.cult is to look at the number 
-of unique labels they provided for each image.  Workers attributing more
-specific labels should produce a larger vocabulary of unique labels for a 
-given, which is indeed what we found (see Fig. 3B).  Workers from 
-exp2.task.food produced as much as 33\% more unique labels per image than 
-workers from exp2.task.cult, and the relative excess of the vocabulary size
-followed the general trend of inter-task effects that we observed in 
-Fig. 2B.
+Based on this observation, we tested the degree of specificity of labels 
+accross all treatments.  We appraoched measuring specificity in two ways.
+Our first method was based on the reasoning that, if a given group of 
+workers uses more specific labels, they will then provide, on the whole,
+a larger set of unique labels for any given image.  For example,
+suppose the workers from \textit{exp2.task.food} who do not use the label 
+\texttt{food} had chosen more specific labels instead.  In being more 
+specific, they must choose a particular detail to describe, from a large 
+number of possibilities, and so are more likely to provide unique labels.
+Indeed
+for all images in the test set, workers from \textit{exp2.task.food} gave
+more unique labels than did those from \textit{exp2.task.cult}, as shown 
+in fig 2B.  Note how the the relative vocabulary sizes follows
+the same trend, as a function of test task, as was observed for the 
+classifier-based detection of general priming differences (c.f. fig X).
 
-To confirm our expectation that the larger vocabulary corresponds to a 
-the use of \textit{more nuanced} words, we used the 
-hypernym-hyponym of wordnet to operationalize a notion of relative 
-specificity.  We define the relative specificity of two sets of labels $P$ 
+Our second approach to measuring relative specificity used the 
+hypernym-hyponym relationships of wordnet.
+We operationalized the relative specificity of two sets of labels $P$ 
 and $Q$ as:
@@
 Using the above equation, we found that, for every images in the 
-test set, the labels attributed by workers in exp2.task.food were more 
-specific than those by workers in exp2.task.cult.
+test set, the labels attributed by workers in \textit{exp2.task.food} were 
+more specific than those by workers in \textit{exp2.task.cult}.
 
-Thus, when workers perform a series of similar image labeling tasks it would
-appear that they tend to avoid generic words, opting instead for more specific
-ones, and yielding a richer vocabulary of labels.  Qualitative 
-characterisation and classification is one of the most comman applications of 
-microtask platforms, and this finding suggests that bundling similar tasks 
-together substantially increases the specificity of HPU output.
+Initialy we hypothesized that the similarity of initial and test tasks was
+driving a relative increase in specificity.  While this seems reasonable,
+we also notice a similar effect occuring for \textit{exp1.task} in which
+the test tasks consisted of both food and non-food objects, and the initial
+tasks were either food or non-food objects.  In this case, it is difficult
+to argue that one set of initial tasks is more similar to another.  In fact
+we devise a method to operationalize image similarity, and find that 
+the initial images of \textit{exp1.task.food} are equally similar to the
+test tasks as the initial images of \textit{exp1.task.obj}.  Furthermore,
+we see strong effects on relative specificity for framing as well.
 
-Our observations of the effects on specificity would appear to be consistent
-with the phenomenon of negative priming.
-Negative priming occurs when a person becomes desensitized to non-salient 
-stimuli to which she is repeatedly exposed. Consider that, workers that 
-initially labeled images depicting prepared meals might no longer
-regard the generic labels \texttt{food} or \texttt{meal} to be salient, and 
-opt instead for \texttt{bread}, or \texttt{pasta}.  But for workers that
-initially labeled cultural images, these rather generic labels might well seem
-appropriate.
-
-We are suggesting that, although workers are not instructed to compare images 
-in any way, prior tasks nevertheless create a frame of reference relative to 
-which later tasks are judged. This in turn influences the perception of 
-salience. Thus, in a series of subjective characterization tasks that have 
-very similar content, workers' focus will tend to be directed away from 
-generic, shared attributes, towards those attributes that are specific and 
-distinguishing.
-
-To see how the initial tasks and the framing affected 
-the focus of the workers' labels, we classified all the labels provided
-on test tasks as either \texttt{culture}, \texttt{food}, \texttt{both}, or 
-\texttt{neither} (we describe the label classification method in more detail
-in the supplementary material).  Focusing on the labels provided to the first 
-test task,
-workers that had initially labeled cultural images provided far more cultural
-labels during test tasks, and fewer food labels, than workers that initially
-labeled images depicting ingredients (see \textbf{Fig. 2}).  On the other 
-hand, the framing primes had no statistically significant effect.
-
-\begin{table}
-\centering
-\begin{tabular}{ l  s s s s}
-
-\toprule    
-Image set   
-& \multicolumn{1}{c}{Ambig.} 
-& \multicolumn{1}{c}{Cultural} 
-& \multicolumn{1}{c}{Ingr.}
-& \multicolumn{1}{c}{Test} \\
-
-\midrule
-
-Ambiguous  & 1 & 0.0418 & 0.142 & 0.167 \\
-
-Cultural  & 0.0418  & 1 & 0.0347 & 0.0561 \\
-
-Ingredients  & 0.142  & 0.0347 & 1 & 0.110 \\
-
-Test & 0.167  & 0.0561 & 0.110 & 1
-\\
-\bottomrule
-
-\end{tabular}
-\caption{\footnotesize{
-Pairwise similarities of each image set based on the labels attributed to them (see \textbf{Eq. 4}).
-}}
-\label{table:2}
-\end{table}
-
-One weakness of the above analysis is the reliance on the informal notion
-of the similarity of one set of images to another. The 
-characterization of image content is a deeply complex issue that has been 
-approached by many disciplines \cite{panofsky1939studies,shatford1986analyzing,Tversky1977327,Jaimes20002}. \textit{Perceptual similarity} is a 
-particularly recalcitrant concept.   But to formalize our claim, we seek a 
-measure of similarity between two sets of images, 
-\textit{with respect to the labeling task}.  This can be operationalized
-in a straightforward way, by using the similarity of the labels given to images
-as a proxy for the similarity of the images.  Thus, to measure the 
-similarity between two sets of images, X and Y , we computed the Jacquard 
-index between the sets of labels attributed to them:
-$$
-	\mathrm{Sim}(X,Y) = \frac{L(X) \cap L(Y)}{L(X) \cup L(Y)}
-$$
-where $L(X)$ denotes the set of labels attributed to images in $X$.
-
-The pairwise similarities of the image sets are presented in Table 2. This 
-shows that the workers that yielded higher specificity labels were from 
-treatments whose initial tasks were more similar to the test tasks (c.f.
-\textbf{Fig 3}).
-
-Such a phenomenon would be consistent with the psychological mechanism known as
-\textit{negative priming}.
-\paragraph{The role of task position in inter-task effects.}
-Up to this point, we have focused on the inter-task effects induced on 
-the first test task.  Not suprisingly, this task was, in general, more 
-strongly affected than the others.  It would stand to reason that, as workers 
-proceed through the test images, priming induced by the initial tasks would
-be ``washed out'', and replaced by the effects of the test tasks themselves,
-which do not differ between treatments.
-
-To investigate this, we performed a second experiment, in which we permuted
-the test tasks in such a way that every test task appears in each of the
-5 locations equally often.  This allows us to track the intertask effects for
-a given test task as it is rotated through the five positions.  Workers were
-again given one of two initial sets of tasks, which either involved labeling
-utensils, cookware, and table settings (but no food), or isolated close-up
-images of prepared meals.  We measured the performance of a Naive Bayes 
-classifier in distinguishing whether labels attributed to a given test 
-image were provided by a worker that labeled objects or meals, as shown in 
-\textbf{Fig. 4}.
-
-The strength of inter-task effects show a clear trend based on the position of
-the test task.  We see that, in general, the first test image is most severely
-affected, and the severity of effect drops off.  Curiously, the severity then
-rises again for the second last, and, especially, final test image.  We 
-speculate that this is related to the workers being aware that they are 
-reaching the end of the batch of labeling tasks.  To be transparent about the
-rate of compensation, we informed workers that they would complete a total
-of ten image-labeling tasks.  Perhaps as the worker nears the end of the batch
-of tasks, she reflects on the overall experience, and in activating the
-memory of the early tasks, is partially re-primed.
+In general, it is of great practical interest to control the level of 
+specificity of qualitative characeterzations.  In many applications the
+task-designer will probably want obtain characterizations that are more
+discriminative.  Thus, when designing microtasks, one should give careful
+consideration to inter-task effects.  Unfortunately, we are not sure
+why certain initial tasks produced increased specificity as opposed to others, 
+and this is a question we intend to pursue in future research.
 
@@
 
+\section*{Supplementary Material}
+
+\subsection*{Assessing task similarity}
+\begin{table}
+\centering
+\begin{tabular}{ l  s s s s}
+
+\toprule    
+Image set   
+& \multicolumn{1}{c}{Ambig.} 
+& \multicolumn{1}{c}{Cultural} 
+& \multicolumn{1}{c}{Ingr.}
+& \multicolumn{1}{c}{Test} \\
+
+\midrule
+
+Ambiguous  & 1 & 0.0418 & 0.142 & 0.167 \\
+
+Cultural  & 0.0418  & 1 & 0.0347 & 0.0561 \\
+
+Ingredients  & 0.142  & 0.0347 & 1 & 0.110 \\
+
+Test & 0.167  & 0.0561 & 0.110 & 1
+\\
+\bottomrule
+
+\end{tabular}
+\caption{\footnotesize{
+Pairwise similarities of each image set based on the labels attributed to them (see \textbf{Eq. 4}).
+}}
+\label{table:2}
+\end{table}
+
+One weakness of the above analysis is the reliance on the informal notion
+of the similarity of one set of images to another. The 
+characterization of image content is a deeply complex issue that has been 
+approached by many disciplines \cite{panofsky1939studies,shatford1986analyzing,Tversky1977327,Jaimes20002}. \textit{Perceptual similarity} is a 
+particularly recalcitrant concept.   But to formalize our claim, we seek a 
+measure of similarity between two sets of images, 
+\textit{with respect to the labeling task}.  This can be operationalized
+in a straightforward way, by using the similarity of the labels given to images
+as a proxy for the similarity of the images.  Thus, to measure the 
+similarity between two sets of images, X and Y , we computed the Jacquard 
+index between the sets of labels attributed to them:
+$$
+	\mathrm{Sim}(X,Y) = \frac{L(X) \cap L(Y)}{L(X) \cup L(Y)}
+$$
+where $L(X)$ denotes the set of labels attributed to images in $X$.
+
+The pairwise similarities of the image sets are presented in Table 2. This 
+shows that the workers that yielded higher specificity labels were from 
+treatments whose initial tasks were more similar to the test tasks (c.f.
+\textbf{Fig 3}).
+
+Such a phenomenon would be consistent with the psychological mechanism known as
+\textit{negative priming}.
+
 \end{document}

### 2014-10-27 src/analysis.py

@@ -24,7 +24,7 @@ import sys
 import random
 import naive_bayes
 import ontology
-import data_processing
+import data_processing as dp
 import numpy as np
 import json
 import wordnet_analysis as wna
@@ -52,6 +52,42 @@ EXP2_TREATMENTS = {
 	'2_sfrm_food': [12],
 	'2_sfrm_obj': [13],
 }
+
+
+class SpellingCorrector(object):
+	'''
+	loads the specified portion of the dataset, and uses the 
+	WordnetSpellChecker to find misspelled words and their plausible correct
+	spellings.  This is basically an adaptor between the SimpleDataset, 
+	the WordnetSpellChecker, and the SimSweeper (which allows for 
+	multiprocessing.
+	'''
+
+	def __init__(self):
+		pass
+
+
+	def run(
+		self,
+		which_experiment=1,
+		class_idxs=[0,1],
+		img_idxs=range(5,10),
+	):
+		corpus = dp.SimpleDataset(
+			which_experiment=which_experiment,
+			show_token_pos=False,
+			show_plain_token=True,
+			show_token_img=False,
+			do_split=False,
+			class_idxs=class_idxs,
+			img_idxs=img_idxs,
+			spellcheck=False,
+			get_syns=False,
+			balance_classes=True,
+		).vocab_list
+
+		spell_checker = wna.WordnetSpellChecker()
+		return spell_checker.auto_correct(corpus)
 
 
 
@@ -90,7 +126,7 @@ def get_all_word_counts(fname='data/new_data/vocabulary.json'):
 
 
 def get_word_counts(experiment, treatments, images):
-	d = data_processing.SimpleDataset(
+	d = dp.SimpleDataset(
 		which_experiment=experiment,
 		show_token_pos=False,
 		show_token_img=False,
@@ -100,6 +136,35 @@ def get_word_counts(experiment, treatments, images):
 	)
 	d.balance_classes(119)
 	return d.vocab_counts
+
+
+def calculate_vocabulary_sizes(fname='data/new_data/vocabulary.json'):
+	results_file = open(fname, 'w')
+
+	treatments = {
+		'exp1.task.food': (1,0),
+		'exp1.task.cult': (1,1),
+		'exp1.task.ingr': (1,2),
+		'exp1.frame.food': (1,3),
+		'exp1.frame.cult': (1,5),
+		'exp2.task.food': (2,0),
[…]

### 2014-10-27 src/new_plots.py

@@ -63,6 +63,187 @@ DATA_DIR = 'data/new_data'
 FIGS_DIR = 'figs/'
 
 
+def plot_vocab_specificity(
+		read_specificity_fnames = ('data/new_data/specificity.json',
+			'data/new_data/specificity_ignore_food.json'),
+		read_vocab_fname = 'data/new_data/vocabulary.json',
+		write_fname = 'figs/vocab_specificity.pdf'
+	):
+
+	vocab_data = json.loads(open(read_vocab_fname).read())
+	exp1_task_food = vocab_data['exp1.task.food']
+	exp1_task_cult = vocab_data['exp1.task.cult']
+
+	# make a figure with two subplots
+	figWidth = 16.78 / 2.54 	# conversion from PNAS spec in cm to inches
+	figHeight = 3/5.*figWidth	# a reasonable aspect ratio
+	fig = plt.figure(figsize=(figWidth, figHeight))
+	gs = gridspec.GridSpec(1, 3)
+
+	# now plot the vocabulary data
+	ax1 = plt.subplot(gs[0])
+	width = 0.75
+
+	Y_1 = []
+	for image in range(5):
+		vocab_food, vocab_cult = exp1_task_food[image], exp1_task_cult[image]
+		Y_1.append((vocab_food - vocab_cult) / float(vocab_cult))
+
+	X_1 = range(len(Y_1))
+
+	series_1 = ax1.bar(X_1, Y_1, width, color='0.25')
+
+	padding = 0.25
+	xlims = (-padding, len(X_1) - 1 + width + padding)
+	plt.xlim(xlims)
+
+	ax1.set_ylabel(r'relative increase in vocabulary', size=12)
+
+	xlabels = ['image %d' % i for i in range(1,6)]
+
+	ax1.set_xticks([x + width/2. for x in X_1])
+	ax1.set_xticklabels(xlabels, rotation=45, size=12,
+		horizontalalignment='right')
+	ax1.set_yticks([0.1,0.2,0.3,0.4])
+
+
+	# plot vocabulary data accross all experiments
+	ax2 = plt.subplot(gs[1], sharey=ax1)
+
+	comparisons = [
+		('exp1.task.food', 'exp1.task.cult'),
+		('exp1.frame.food', 'exp1.frame.cult'),
[…]

### 2014-10-27 src/run_spell_corrector.py

@@ -1,0 +1,40 @@
+import sys
+import analysis as a
+from sim_sweep import sim_sweep
+
+SIM_CLASS = a.SpellingCorrector
+
+FNAME_1 = 'data/new_data/dictionary_1.json'
+FNAME_2 = 'data/new_data/dictionary_2.json'
+
+SCHEDULE_1 = {
+	'which_experiment': [1],
+	'class_idxs' : [[0,1,2,3,5]],
+	'img_idxs': [[5],[6],[7],[8],[9],[10]]
+}
+
+SCHEDULE_2 = {
+	'which_experiment': [2],
+	'class_idxs': [range(14)],
+	'img_idxs': [[5],[6],[7],[8],[9],[10]]
+}
+
+RUNS = [(FNAME_1, SCHEDULE_1), (FNAME_2, SCHEDULE_2)]
+
+def do_corrections(num_procs):
+	for fname, schedule in RUNS:
+		sim_sweep(SIM_CLASS, fname, schedule, num_procs=num_procs)
+
+
+if __name__ == '__main__':
+
+	# The number of processes can be passed as a command line argument.
+	# By default the number of processes will equal the number of processors.
+	num_procs = None
+	if len(sys.argv) == 2:
+		num_procs = sys.argv[1]
+	elif len(sys.argv) > 2:
+		raise ValueError('Expected at most one command line argument.  '
+			'Found %d: %s.' % (len(sys.argv)-1, ', '.join(sys.argv)))
+
+	do_corrections(num_procs)

### 2014-10-27 src/wordnet_analysis.py

@@ -1,7 +1,9 @@
 import copy
 from nltk.corpus import wordnet as wn
+from nltk.corpus import stopwords
 from collections import Counter
 import re
+import numpy as np
 
 
 SPLIT_RE = re.compile('[^-a-zA-Z]')
@@ -28,15 +30,26 @@ class WordnetSpellChecker(object):
 
 	ALPH = 'abcdefghijklmnopqrstuvwxyz_'
 	W = re.compile(r'[^a-z ]')
+	stops = stopwords.words('english')
 
 	def __init__(self):
 		pass
 
 	def is_ok(self, word):
-		return bool(len(wn.synsets(word))>0)
+		return len(wn.synsets(word))>0 or word in self.stops
+
+	def all_ok(self, word):
+		return all([self.is_ok(token) for token in word.split()])
+
+	def get_all_neighbors(self, words_and_scores):
+		all_neighbors = set()
+		for word, score in words_and_scores:
+			all_neighbors.update(self.get_neighbors(word, score))
+
+		return all_neighbors
 
 
-	def get_neighbors(self, word):
+	def get_neighbors(self, word, score):
 
 		w = word
 
@@ -56,7 +69,14 @@ class WordnetSpellChecker(object):
 		else:
 			separations = [a + ' ' + b for a,b in splits]
 
-		return set(deletes + transposes + replaces + inserts + separations)
+		# return all the possibilities, but the separations get half-score
+		# as a penalty
+		return_neighbors = set(
+			[(s,score*0.50) for s in deletes + transposes + replaces + inserts]
+		)
+		return_neighbors |= set([(s,score*0.1) for s in separations])
+
+		return return_neighbors
 
 
 	def auto_correct(self, corpus):
@@ -84,31 +104,23 @@ class WordnetSpellChecker(object):
 		corrections = {}
 		for w in misspelled:
 
-			single_edits = self.get_neighbors(w)
-			double_edits = reduce(
-				lambda x,y: x | self.get_neighbors(y), 
-				single_edits, 
-				set()
-			)
+			candidates = self.get_neighbors(w,1)
+			candidates |= self.get_all_neighbors(candidates)
 
-			first_candidates = filter(
-				lambda x: 
-					all([self.is_ok(y) for y in x.split()])
-					and len(x.split())>0,
-				single_edits)
+			# remove nonsense candidates
+			candidates = filter(lambda x: self.all_ok(x[0]), candidates)
 
-			second_candidates = filter(
-				lambda x: 
[…]

### 2014-10-27 src/run_spell_corrector.py
bug in run_spell_corrector

@@ -32,7 +32,7 @@ if __name__ == '__main__':
 	# By default the number of processes will equal the number of processors.
 	num_procs = None
 	if len(sys.argv) == 2:
-		num_procs = sys.argv[1]
+		num_procs = int(sys.argv[1])
 	elif len(sys.argv) > 2:
 		raise ValueError('Expected at most one command line argument.  '
 			'Found %d: %s.' % (len(sys.argv)-1, ', '.join(sys.argv)))

### 2014-11-06 docs/publications/2014.09_SCIENCE/man.tex
add self-specificity analysis and crawler

@@
 	$$
-	\mathcal{D}(P,Q) = 
+	\theta_\mathcal{D}(\mathcal{P},\mathcal{Q}) = 
 		\left| 
-			\mathrm{E}\left\{ \mathcal{D}(p) \right\} 
-			- \mathrm{E}\left\{ \mathcal{D}(q) \right\} 
-		\right|,
-	\theta_\mathcal{D}(P,Q) = 
-		\left| 
-			\mathrm{E}\left\{ \mathcal{D}(p) \right\} 
-			- \mathrm{E}\left\{ \mathcal{D}(q) \right\} 
+			\mathrm{E}\left\{ \mathcal{D}(P) \right\} 
+			- \mathrm{E}\left\{ \mathcal{D}(Q) \right\} 
 		\right|,
@@
 	$$
-	\theta(P,Q) = 
+	\theta(\mathcal{P},\mathcal{Q}) = 
 		\sup_\mathcal{D} \theta_\mathcal{D}(P,Q)
@@
 simply changing a single, seemingly non-critical word in a task description, 
-has significant effects on worker's resonses.  Perhaps more importantly, the 
+has significant effects on worker's resonses \cite{thibodeau2013natural}.  Perhaps more importantly, the 
 framing treatments were included to provide a reasonable basis for comparison,

### 2014-11-06 src/analysis.py

@@ -30,6 +30,7 @@ import json
 import wordnet_analysis as wna
 from collections import defaultdict, Counter
 import os
+import copy
 
 # Number of stardard deviations equivalent to the % condifdence for a 
 # normal variate
@@ -52,6 +53,10 @@ EXP2_TREATMENTS = {
 	'2_sfrm_food': [12],
 	'2_sfrm_obj': [13],
 }
+
+
+class AnalysisError(Exception):
+	pass
 
 
 class SpellingCorrector(object):
@@ -125,7 +130,11 @@ def get_all_word_counts(fname='data/new_data/vocabulary.json'):
 
 
 
-def get_word_counts(experiment, treatments, images):
+def get_word_counts(experiment, treatments, images, balance=119):
+	'''
+		set balance=0 to apply no truncation of the dataset (which is 
+		normally done to balance the number of data points per treatment).
+	'''
 	d = dp.SimpleDataset(
 		which_experiment=experiment,
 		show_token_pos=False,
@@ -134,7 +143,10 @@ def get_word_counts(experiment, treatments, images):
 		class_idxs=treatments,
 		img_idxs=images,
 	)
-	d.balance_classes(119)
+
+	if balance > 0:
+		d.balance_classes(119)
+
 	return d.vocab_counts
 
 
@@ -211,6 +223,83 @@ def calculate_similarity(fname='data/new_data/similarity.json'):
 
 	results_file.write(json.dumps(similarities, indent=2))
 	return similarities
+
+
+
+def calculate_longit_self_specificity():
+	'''
+	This analysis looks at whether the labels attributed to a *test* image
+	become *more specific* as the image moves from position 1 in the test
+	set through position 5.  The comparison is not between two priming 
+	treatments (which is what is usually done), but between the labels
+	attributed to the image in the position in question and the pool of
+	labels attributed to that image at all other positions.
+	'''
+	fname = 'data/new_data/self_specificity.json'
+	results_fh = open(fname, 'w')
+
+	all_specificities = {}
+	for treatment_set in ['food', 'object']:
+
+		specificities = []
+		all_specificities[treatment_set] = specificities
+
+		if treatment_set == 'food':
+			treatments_of_interest = range(5) 
+		elif treatment_set == 'object':
+			treatments_of_interest = range(5,10)
+		else:
+			raise AnalysisError(
+				'Inconsistent value for treatmens of interest')
+
+		for image in range(5,10):
+
+			this_image_results = []
+			specificities.append(this_image_results)
[…]

### 2014-11-06 src/crawl.py

@@ -1,0 +1,346 @@
+import random as r
+import time
+import json
+import os
+from urlparse import urlparse, urlunparse, urljoin
+from collections import deque, OrderedDict
+from bs4 import BeautifulSoup as bs
+import requests
+import re
+
+
+START = 'http://allrecipes.com/Recipes/World-Cuisine/'
+HOST = 'http://allrecipes.com'
+
+
+class Crawler(object):
+
+	URL_QUEUE_FNAME = 'data/html/url_queue.json'
+	RECIPE_URL_QUEUE_FNAME = 'data/html/recipe_url_queue.json'
+	CORPUS_FNAME = 'data/html/corpus.txt'
+	MAX_TRIES = 3
+	TIMEOUT = 3
+
+	SLEEP = 2
+	REST = 60
+	BACKOFF = 60 * 5
+	COOL_OFF = 60 * 30
+
+
+	def __init__(self, start=START):
+
+		# initialize the url queue based on logs stored on disk
+		self.url_queue = self.read_queue()
+
+		# if no url logi is found use initialize with the starting url 
+		if self.url_queue is None:
+			self.url_queue = OrderedDict({
+				self.normalize(start, start): {
+					'url':start,
+					'visited':False,
+					'tries':0
+				}
+			})
+
+		self.strings = []
+		self.sync_disk()
+		self.check_files()
+
+
+	def crawl(self):
+
+		i = 0
+		num_failures = 0
+		for url_key in self.url_queue:
+
+			url_obj = self.url_queue[url_key]
+			if url_obj['visited'] or url_obj['tries'] > self.MAX_TRIES:
+				continue
+
+
+			print 'Crawling %s...' % url_key
+
+			url_obj = self.url_queue[url_key]
+			url = url_obj['url']
+
+			success = self.process_page(url)
+
+			if success:
+				url_obj['visited'] = True
+				num_failures = 0
+			else:
+				url_obj['tries'] += 1
+				num_failures += 1
+
+			# sleep a bit
+			time.sleep(self.get_sleep_time())
+
+			# periodically give the site a rest, and record progress
+			if i % 8 == 7:
+				self.sync_disk()
+				time.sleep(self.REST)
+
+			# if we've had too many failures, backoff for awhile
+			if num_failures > 30:
+				time.sleep(self.COOL_OFF)
+
+			elif num_failures > 10:
+				time.sleep(self.BACKOFF)
+
[…]

### 2014-11-06 src/new_plots.py

@@ -63,6 +63,33 @@ DATA_DIR = 'data/new_data'
 FIGS_DIR = 'figs/'
 
 
+def plot_self_specificity(
+		read_fname = 'data/new_data/self_specificity.json',
+		write_fname = 'figs/self_specificity.pdf'
+	):
+
+	self_specificity = json.loads(open(read_fname).read())
+
+	# make a figure with three subplots
+	figWidth = 16.78 / 2.54 	# conversion from PNAS spec in cm to inches
+	figHeight = 4/5.*figWidth	# a reasonable aspect ratio
+	fig = plt.figure(figsize=(figWidth, figHeight))
+	gs = gridspec.GridSpec(1, 2)
+
+	width = 0.75
+
+	# now plot the vocabulary data
+	ax1 = plt.subplot(gs[0])
+	Y_food = np.mean(self_specificity['food'], 1)
+	X = range(len(Y_food))
+	series_1 = ax1.bar(X, Y_food, width, color='0.25')
+
+	ax1 = plt.subplot(gs[1])
+	Y_object = np.mean(self_specificity['object'], 1)
+	series_2 = ax1.bar(X, Y_object, width, color='0.25')
+
+
+
 def plot_vocab_specificity(
 		read_specificity_fnames = ('data/new_data/specificity.json',
 			'data/new_data/specificity_ignore_food.json'),
@@ -74,7 +101,7 @@ def plot_vocab_specificity(
 	exp1_task_food = vocab_data['exp1.task.food']
 	exp1_task_cult = vocab_data['exp1.task.cult']
 
-	# make a figure with two subplots
+	# make a figure with three subplots
 	figWidth = 16.78 / 2.54 	# conversion from PNAS spec in cm to inches
 	figHeight = 3/5.*figWidth	# a reasonable aspect ratio
 	fig = plt.figure(figsize=(figWidth, figHeight))
@@ -484,7 +511,7 @@ def plot_theta(
 
 	plt.draw()
 	plt.tight_layout()
-	fig.subplots_adjust(wspace=0.05, top=0.99, right=0.99, left=0.10, 
+	fig.subplots_adjust(wspace=0.05, top=0.99, right=0.99, left=0.11, 
 		bottom=0.29)
 	fig.savefig(os.path.join(FIGS_DIR, write_fname))
 

### 2014-11-06 src/tests.py

@@ -12,6 +12,72 @@ import wordnet_analysis as wna
 from nltk.corpus import wordnet as wn
 
 
+class CountsComplimentTestCase(unittest.TestCase):
+
+	def test_get_counts_compliment(self):
+
+		image = 5
+		treatments = [0, 4, 3, 2, 1]
+		individual_word_counts = {}
+		for t in treatments:
+			individual_word_counts[t] = analysis.get_word_counts(
+					2, [t], [image], balance=0) 
+
+		expected_word_counts_compliment = []
+		for t in treatments:
+
+			this_word_counts = individual_word_counts[t]
+			other_treatments = [t_ for t_ in treatments if t_ != t]
+			other_word_counts = analysis.get_word_counts(
+				2, other_treatments, [image], balance=0)
+
+			expected_word_counts_compliment.append({
+				'for_i' : this_word_counts,
+				'not_i' : other_word_counts
+			})
+
+		found_word_counts_compliment = analysis.get_counts_compliment(
+			image, balance=0)
+
+		self.assertEqual(
+			found_word_counts_compliment, 
+			expected_word_counts_compliment
+		)
+
+
+	def test_get_counts_compliment_2(self):
+
+		image = 8
+		treatments = [3, 2, 1, 0, 4]
+		individual_word_counts = {}
+		for t in treatments:
+			individual_word_counts[t] = analysis.get_word_counts(
+					2, [t], [image], balance=0) 
+
+		expected_word_counts_compliment = []
+		for t in treatments:
+
+			this_word_counts = individual_word_counts[t]
+			other_treatments = [t_ for t_ in treatments if t_ != t]
+			other_word_counts = analysis.get_word_counts(
+				2, other_treatments, [image], balance=0)
+
+			expected_word_counts_compliment.append({
+				'for_i' : this_word_counts,
+				'not_i' : other_word_counts
+			})
+
+		found_word_counts_compliment = analysis.get_counts_compliment(
+			image, balance=0)
+
+		self.assertEqual(
+			found_word_counts_compliment, 
+			expected_word_counts_compliment
+		)
+
+
+
+
 class SimilarityTestCase(unittest.TestCase):
 
 	def test_similality(self):

### 2014-11-06 src/crawl.py
dont remove page parameter from query string in crawler

@@ -26,6 +26,7 @@ class Crawler(object):
 	BACKOFF = 60 * 5
 	COOL_OFF = 60 * 30
 
+	PAGE_REGEX = re.compile(r'Page=\d+')
 
 	def __init__(self, start=START):
 
@@ -158,8 +159,17 @@ class Crawler(object):
 
 
 	def strip_query(self, url):
-		''' remove the query string '''
-		return urlunparse(urlparse(url)[:3] + ('',)*3)
+		''' remove the query string, but not if it has a page #! '''
+		page_param = self.PAGE_REGEX.match(url)
+		stripped = urlunparse(urlparse(url)[:3] + ('',)*3)
+
+		# we don't want to strip page numbers though
+		if page_param:
+			stripped += '?' + page_param
+
+		return stripped
+
+
 
 	
 	def normalize(self, url, base):

### 2014-11-06 src/crawl.py
small change

@@ -22,7 +22,7 @@ class Crawler(object):
 	TIMEOUT = 3
 
 	SLEEP = 2
-	REST = 60
+	REST = 10
 	BACKOFF = 60 * 5
 	COOL_OFF = 60 * 30
 
@@ -76,15 +76,18 @@ class Crawler(object):
 			time.sleep(self.get_sleep_time())
 
 			# periodically give the site a rest, and record progress
-			if i % 8 == 7:
+			if i % 20 == 19:
 				self.sync_disk()
+				print 'Resting...'
 				time.sleep(self.REST)
 
 			# if we've had too many failures, backoff for awhile
 			if num_failures > 30:
+				print 'Cooling off...'
 				time.sleep(self.COOL_OFF)
 
 			elif num_failures > 10:
+				print 'Backing off...'
 				time.sleep(self.BACKOFF)
 
 			i += 1

### 2014-11-16 docs/publications/2014.09_SCIENCE/new_man.tex
further analysis, plots, manuscript work

--- 2014-10-27 docs/publications/2014.09_SCIENCE/man.tex
@@
 
-People still outperform sophisticated artificial 
-intelligince systems in many tasks requiring general knowledge, 
-qualitative judgment, and visuo-spatial reasoning. Recently, microtask 
-platforms enable the programmer to import human judgment directly into 
-algorithms: programs can post tasks, to be completed by users of such 
-platforms in near real-time.
-Some computer scientists consider microtask platforms to be a fundamentally
-new computing architecture, but psychological effects can introduce systematic
-bias. 
-Here we investigate the effects that earlier tasks have on the results of 
-subsequent ones, which we call \textit{inter-task effects}.
-In a canonical image labeling task, we found that inter-task effects are
-very strong---stronger than overtly framing tasks in terms of 
-particular research goals.  However, in some cases, inter-task effects can
-be leveraged to elicit more nuanced responses.
-To study inter-task effects we introduce a framework that characterizes HPU 
-bias in an application-independant way, based on its potential to alter an 
-algorithm's path of execution.  Our findings suggest that careful consideration
-should be given to inter-task effects when designing crowdsourcing studies.
-
-%microtask worker performs a series of tasks.  We find that early tasks can
-%have a strong effect on later tasks, and that these effects can be stronger
-%than those brought about by framing.
-%
-%course of human computation algorithms.
-%application-independant quantity that measures the
-%severity of priming.  We apply this framework to measure 
-%
-%in many
-%tasks, especially ones requiring general knowledge about the world, qualitative
-%judgment, and visuo-spatial reasoning.  Recently, microtask web platforms have 
-%emerged. One can upload a batch of tasks to be completed by users who are paid 
-%for their efforts.
-%Though simple on the surface, these platforms dramatically enlarge the
-%programmers toolkit: in effect they allow the programmer to import human 
-%judgment into algorithms.  Some computer scientists consider
-%such platforms to be a new computing architecture.  But people are very 
-%different from electronic processors.  For example, context affects how a 
-%person will respond to a prompt, and this complicates the formal treatment of 
-%human computation.  To approach this issue, we introduce a framework 
-%that quantifies the severity of priming in an application-independant way.
-%We apply this technique to reveal an unforseen source of bias: the bias 
-%induced by one task on another.  Surprisingly we find that 
-%\textit{inter-task effects} introduce more bias than \textit{framing}, which
-%has received more attention.
-%
-%more well-known 
-%\textit{framing}, a more well-studied form of priming.
-%
-%Microtask platforms offer a fast, flexble, and inexpensive source of labour for
-%clerical tasks \cite{Finnerty2013, chandler2013breaking, Berinsky2012351} and 
-%recently have been adopted by researchers to augment datasets and solicit 
-%participants \cite{paolacci2010running, Berinsky2012351, chandler2013breaking}.
-%Computer scientists have described such platforms as a new computing 
-%architecture, and seek to characterize “human co-processing units” (HPUs) in 
-%analogy to CPUs and GPUs \cite{5543192}. However, it is known that people are 
-%susceptible to 
-%priming effects\cite{No2007,Swaab200299,Gopher2000308,sohn2001task,Ghuman17062008,BJOP1796,BJOP1826,Gass1999549}, which stands to complicate the HPU 
-%perspective.  Here, we introduce a framework to recast this psychological 
-%phenomenon as a kind of computational hysteresis. 
-%We apply this framework to study \textit{inter-task effects} that arise when 
-%microtask 
-%workers perform a sequence of tasks. Surprisingly, earlier tasks can have a 
-%very strong influence on workers during later tasks---stronger than overtly
-%framing the tasks as serving different research goals.   
-%This result has major implications for the design of crowdsourcing initiatives.
-%The framework we introduce provides a general measure of priming severity, 
-%and, in combination with machine learning tools, enables measurement without
-%knowing ahead of time how priming will affect output.
+Microtask platforms combine the efforts of large numbers 
+of people to perform tasks that are difficult to automate with computers 
+alone.  These platforms support near-real-time task completion, mimicking a
+compute server, and fundamentally shift the role of the human from being a
+consumer to being a producer of computing resources.  To realize its full
+potential, we must understand how human computation differs from machine 
+computation, and in particular address the biases known to be inherent in 
+human cognition.  Here we show that when a worker completes a series of 
+microtasks, the responses in later tasks are strongly influenced by the 
+content of earlier ones.  Our findings are not solely cautionary. We find
+evidence that these \textit{inter-task effects} can be
+harnessed to improve the quality of responses, and help to achieve 
+expert-level judgments, to increase the scope and reliability of citizen 
+science and crowdsourcing initiatives.
 \end{sciabstract}
@@
 
-These platforms make it possible to seemlessly integrate human and 
+These platforms make it possible to tightly integrate human and 
 machine computation.  Researchers coined the term HPU 
 (Human co-Processing Unit) in analogy to CPUs and GPUs \cite{5543192}.  
-Attempts have been made to establish an HPU instruction set.  For example,
-the X library provides function calls such as 
-\texttt{X.vote()}, and \texttt{X.map()}
- \cite{little2010turkit,minder2011crowdlang,minder2012crowdlang,kittur2011crowdforge}.
+Ongoing research pursues the establishment of an HPU instruction set
+including basic operators like \texttt{vote}, \texttt{subdivide}, \texttt{map},
+\texttt{reduce}, \texttt{sentiment}, and \texttt{image\_tag}.  As was 
+done with GPU programming, libraries are being developped to give the 
+programmer more seamless access to HPU resources 
+ \cite{little2010turkit,minder2011crowdlang,minder2012crowdlang,kittur2011crowdforge}.  The availability of human computing platforms makes whole new classes
+of problems tractible for the programmer.  For example ***.
 
-Of course, there are obvious differences between HPUs and their silicone
-counterparts.  When facing the same task, people do not generally
-respond in the same way.  Common sense would dictate that a certain amount
-of variability in responses made by people is inescapable.  But an important 
-part of the variation is bound to be systematic, due to psychological or 
-demographic factors.
-
-Here, we highlight an important source of bias with
-serious implications for any crowdsourcing initiative. 
-It is known that people are susceptible to priming effects 
-\cite{BJOP1796,No2007,beller1971priming}, and, in particular, task-repetition 
-effects \cite{Gass1999549,sohn2001task}.  Thus, a worker's response during
-one task may depend in part on previous ones.  Such \textit{inter-task} effects
-would amount to a kind of \textit{hysteresis}, meaning that HPU outputs are not
-only a function of the current input, but also of the history of inputs.
+But the ability to program with high-level human instructions comes with a 
+cost: HPU output is inherently noisy.  Part of this noise could be 
+explained by the random differences between workers.  Meanwhile, systematic 
+cognitive biases also play a role.  
+The phenomenon we attend to here represents yet
+another dimension of HPU variance, and arises from the fact that a worker's 
+performance changes as a function of the content of previous tasks.
 
@@
 
-We make two contributions towards understanding inter-task effects,
-and systematic bias in HPUs in general.  First, we present a framework for 
-quantifying bias in HPU outputs in terms of their potential impact 
-algorithms.  This yields an approach for measuring the severity of bias 
-that removes the need to understand the underlying psychological or 
-demographic factors at play.  Second, we apply our framework to measure the
-severity of inter-task effects on a canonical microtask: image labeling.
+It is known that people are susceptible to priming effects 
+\cite{BJOP1796,No2007,beller1971priming}, and, in particular, task-repetition 
+effects \cite{Gass1999549,sohn2001task}.  Thus, a worker's response during
+one task may depend in part on previous ones.  Such \textit{inter-task} effects
+would amount to a kind of \textit{hysteresis}, meaning that HPU outputs are not
+only a function of the current input, but also of the history of inputs, with
+important implications for crowdsourcing initiatives.
 
-Using the  Amazon Mechanical Turk (Mturk) platform, we solicited workers to 
-perform a series of image-labeling tasks.  We chose image labeling because it 
-is one of the most common kinds of microtasks
+Here we describe a series of experiments using the Amazon Mechanical
+Turk (MTurk) microtask platform that studied inter-task effects
+for image-labeling microtasks.  Image-labeling tasks are among the most 
+common kinds of microtasks
 \cite{chandler2013breaking,Berinsky2012351,Finnerty2013,paolacci2010running}, 
 and it seems likely that this will remain the case in the long term because
-of applications in computer vision research \cite{5543192}.
-%In these tasks, workers labeled images featuring iconic cultural scenes,
-%food, table-settings, and various utensils and cookware. 
-We divided the tasks into an \textit{initial} and \textit{test} set, 
-but, crucially, there was no distinction between these sets from the
-perspective of the worker.  We varied the initial tasks, while 
-keeping the test set the same, to analyze the effect of initial tasks on 
-the labels provided during the test tasks.
+they provide a source of ground truth in computer vision research 
+\cite{5543192}.  
+During the experiments, workers performed a series of image labeling tasks, 
+and the first five images
+they labeled were varied depending on the experimental group to which they
+were assigned.  We studied the effects that changing the initial tasks 
+had on the labels provided in the final tasks.
 
-As a point of comparison, we included treatments in which we induce 
+As a point of comparison, we included treatments in which we induced
 \textit{framing}.
-Before the workers labeled images, we indicated that the work 
-was funded by a research lab with a particular area of interest, to see the 
-influence this has on the workers’ subsequent labels. 
-Surprisingly, inter-task effects were stronger than framing, in some cases 
-about twice as strong. 
-Our results demonstrate that initial tasks can change workers' focus in later 
-tasks.  We also found that inter-task effects altered the level of specificity 
-of worker's labels.  Our findings suggest that careful consideration should be 
-given to the bundling of tasks when designing a study using a microtask 
-platform.
+In the framing treatments, before workers begin the tasks, we told them that 
+the study was funded by a lab with a particular area of interest, for example,
+in the visual perception of food in one case, or the perception of tools in
+another.
 
-\paragraph*{Computational hysteresis.}
-Before describing our experiments, we dedicate some space to discussing
-how we characterize and measure priming in HPU outputs.  Since HPU outputs are
-stochastic, determining the effect of priming on an HPU population
-amounts to determining the resulting change to the HPU population's 
-distribution of outputs.
+Surprisingly, inter-task effects were much stronger than framing.  
+Our results demonstrate that initial tasks can change 
+workers' focus in later tasks.  We also found that inter-task effects altered 
+the level of specificity, and the diversity of vocabulary that workers used,
+in ways that were not reproduced using framing.
+Contrary to our initial expectations, our findings suggest that by carefully
+designing workflows, the HPU programmer can leverage inter-task effects to
+direct focus, tune specificity, and activate worker expressivity.  Our 
+findings carry two lessons for the task designer: inter-task
+effects can severely bias HPU output if HPU hysteresis is not taken into 
+account, but at the same time, inter-task effects provide another technique
+for improving HPU output and may help elicit expert-level annotation.
 
-To refine this, we distinguish between methods that determine \textit{whether}
-two random sources have the same distribution 
-(e.g. Pearson's chi squared test), from those that determine
-\textit{the extent} of that difference (e.g. one of the many measures of 
-statistical divergence).  We are interested in measuring the extent of
-difference because our practical concern is the potential for such
-differences to alter the course of an algorithm.
+\paragraph*{Measuring computational hysteresis.}
+In setting out to measure the computational hysteresis induced by priming, 
+it is important to remember that we are only interested in the practical 
+impact of priming on the execution of HPU algorithms.  
+The distinction between measuring priming and measuring computational 
+hysteresis is subtle, but it is crucial to ensure that our findings are of 
+practical significance to crowdsourcing applications.
 
-To measure the effect of some priming treatment, we must of course draw a 
-comparison to some standard population.  In many cases, there may be an 
-obvious comparison between a primed and unprimed population.  However, we 
-refrain from proposing a canonical neutrally-primed HPU population; what is 
-considered ``unprimed'' in one scenario may be ``primed'' in another. 
-Instead, we speak of two HPU populations being \textit{differently primed}.
+This distinction dictates our choice of tools for detecting HPU hysteresis.
+A common practice for demonstrating that one population is different from
+another (e.g., HPUs exposed to one prime vs another), is to use a 
+$\chi^2$ test. This would suffice to demonstrate \textit{whether} priming of 
+HPUs had occured, however it says nothing about the \textit{extent} of 
+priming, and in particular, does not demonstrate the extent to which primed 
+HPUs would execute an algorithm differently.
 
-We present three alternative, equivalent definitions for the 
-\textit{difference in priming} of two HPU populations, $\mathcal{P}$, and 
-$\mathcal{Q}$, which we denote $\theta(P,Q)$.  To set up the definitions,
-we will assume that $\mathcal{P}$ and $\mathcal{Q}$ 
-were sampled randomly from the same initial population $\mathcal{R}$, and 
-then were exposed to (possibly) different priming treatments. Then, the HPUs 
-in $\mathcal{P}$ and $\mathcal{Q}$ perform some task, leading to popualtions 
-of work-products, $P$ and $Q$.
-
-The first definition provides the motivation for our choice of divergence
-measure, because it directly measures the proportion of the time that a
-binary decision will be changed due to priming effects:
-
-\begin{mydef}
-	\label{def:bias}
-	{\upshape Maximum Bias:}
-	Let $\mathcal{D}$ be a binary decision function, which takes a 
-	work-product
-	$r \in P \cup Q$ as input, and outputs a bit $\mathcal{D}(r)=b$, where 
-	$b \in \{0,1\}$. Denote the \emph{bias} of $\mathcal{D}$, due to the
-	different priming of $\mathcal{P}$ and $\mathcal{Q}$ by
-	$\theta_\mathcal{D}(P,Q)$ and define it to be the difference 
-	in the expected output of $\mathcal{D}$ when acting on work-products from 
-	$P$ and $Q$:
-	$$
-	\mathcal{D}(P,Q) = 
-		\left| 
-			\mathrm{E}\left\{ \mathcal{D}(p) \right\} 
-			- \mathrm{E}\left\{ \mathcal{D}(q) \right\} 
-		\right|,
-	\theta_\mathcal{D}(P,Q) = 
-		\left| 
-			\mathrm{E}\left\{ \mathcal{D}(p) \right\} 
-			- \mathrm{E}\left\{ \mathcal{D}(q) \right\} 
-		\right|,
-	$$
-	where $p \in P$, $q \in Q$.  Then, define the difference in priming 
-	between $\mathcal{P}$ and $\mathcal{Q}$ to be the worst-case bias, i.e. 
-	the bias of the most susceptible decision:
-	$$
-	\theta(P,Q) = 
-		\sup_\mathcal{D} \theta_\mathcal{D}(P,Q)
-	$$
-\end{mydef}
-If $\mathcal{D}$ is the condition of an \texttt{if}-statement, then the 
-definition above is the change in the fraction of the time that a given 
-path of execution is followed due to HPU priming.
-
-While this is precisely what we want to measure, it is not at all clear how
-to go about doing it.  The second formulation provides a practical connection
-by rephrasing priming in terms of its distinguishability:
-
-\begin{mydef}
-	{\upshape Distinguishability:}
-	Let $\mathcal{D}$ be a distinguisher algorithm, which takes work-product 
-	$r \in P \cup Q$ as input, and outputs a \emph{guess} 
-	$\mathcal{D}(r) \in \{0, 1\}$. Now define a validation test 
-	$V(\mathcal{D}, R_0, R_1)$ as follows. A bit is drawn uniformly at random, 
-	$b \in_R \{0, 1\}$, and then a work-product $r$ is chosen uniformly at 
-	random from one of the populations, decided by the bit: $r \in_R R_b$. 
-	Input $r$ into $\mathcal{D}$, and if $\mathcal{D}(r) = b$, we say 
-	$\mathcal{D}$ \emph{guessed correctly}, and the value of $V$ is 1, 
-	otherwise $V = 0$.
-
-	A distinguisher that guesses randomly will still be correct half of the 
-	time. Therefore, denote the performance of $\mathcal{D}$ by 
-	$\eta_\mathcal{D}(P, Q)$, and let
-	$$
-		\eta_\mathcal{D}(P,Q) = 2\cdot \mathrm{E}\{V(\mathcal{D},P,Q)\} - 1.
-	$$
-	Then define the difference in priming between $\mathcal{P}$ and 
-	$\mathcal{Q}$ to be the performance of the best possible distinguisher:
-	$$ 
-		\theta(P,Q) = \sup_\mathcal{D} \eta_\mathcal{D}(P,Q)
-	$$
-	\label{def:dist}
-\end{mydef}
-
-\textbf{Definition 2} relates the difference in priming to the 
-\textit{optimal Bayes classifier} for determining whether a given HPU output
-came from $P$ or $Q$.  This means that we can obtain a lower bound on
-$\theta(P,Q)$ based on the performance of an actual classifier, which provides
-recourse when purely statistical methods fail.
-
-The statistical divergence measure underlying the previous definitions is the
-divergence measure known as the ``total variational distance'' or 
-$l_1$-distance:
-\begin{mydef}
-	\label{def:l1}
-	{\upshape Total variational distance $\theta_{l_1}$:}
-	Define the difference in priming between $\mathcal{P}$ and $\mathcal{Q}$ 
-	to be equal to the total variational distance between the work-products 
-	$P$ and $Q$:
-	$$
-	\theta_{l_1}
-	= \sup_{A \subset \mathcal{X}} \left| \sum_{x \in A} f_P(x) - f_Q(x)\right|
-	= \frac{1}{2} \sum_{x \in \mathcal{X}} \left| f_P(x) - f_Q(x) \right|,
-	$$
-	where $f_P(x)$ denotes the probability of observing x when sampling from P.
-\end{mydef}
-The equivalent formulation for $\theta(P,Q)$ in 
-\textbf{definition \ref{def:l1}} provides a grounding in a fundamental
-measure of statistical divergence, and a connection to information theory.  
-The equivalence of the three definitions
-follows from the known fact that no algorithm can have output that differs
-on inputs $P$ and $Q$ more than $l_1 \times 100\%$ of the time.  We provide
-proofs in the supplementary material.
-
-The difficulty of measuring $\theta(P,Q)$ depends on what the universe of
-possible outputs are, as well as how $P$ and $Q$ are actually distributed,
-both of which are mainly determined by the task that the HPUs are asked to 
-perform.  In the case where workers label an image with a free-text input, 
-the number of different possible labels can be in the thousands or more.  If
-the support, $\mathcal{X} = P \cup Q$, is large compared to the number of 
-HPU outputs sampled, so that many labels appear only once (which in any case
-is expected from Zipv's law), then estimating $\theta$ directly from the
-observed frequencies of labels is difficult.
-
-One approach to estimating the $l_1$-distance from samples, which appears
-reasonable on the surface, is to use the observed frequencies of each output
-$x$ from $P$ and $Q$ to estimate $f_P(x)$ and $f_Q(x)$, and calculate 
-$\theta(P,Q)$ directly from \textbf{definition 3}.  This is the so-called naive
-approach to estimating $l_1$-distances, and is aptly named because it tends
-to produce very inflated values.  More recent techniques have for estimating
-$l_1$ have been suggested by Valiant \cite{val-thesis}, and Batu 
-\cite{batu2000testing,batu2013testing}.  We reserve the discission of these
-techniques to the supplementary material; they do not turn out to be useful
-because they do not provide confidence intervals.  Thus our only recourse is
-to test the performance of classifiers at distinquishing $p \in P$ from 
-$q \in Q$, which allows us to estimate a lower bound on $\theta(P,Q)$.  This 
-turns out to be sufficient, and has the advantage that, so long as they are
-learnable, it is not necessary to understand exactly how $P$ and $Q$ differ.
+We opt instead to measure HPU hysteresis using
+machine learning algorithms (classifiers), that have been trained to 
+distinguish HPUs that were subjected to one prime, from those subjected to 
+another.  If a classifier
+can distinguish HPUs subjected to different primes, then it serves as 
+a kind of certificate, proving 
+(up to statistical confidence) that there exists 
+an algorithm whose execution is affected by the priming of individual HPUs
+(namely, the classifier itself).  This demonstrates that, for some algorithms,
+using HPUs primed one way vs another will lead an algorithm to follow a 
+different branch of execution with a certain frequency.
+Statistically, our approach is grounded in the 
+statistical divergence metric called L1-distance 
+(alternatively \textit{total variational distance}), via the following 
+inequality:
+\begin{equation}
+	D_\mathrm{L1} \geq 2 \eta - 1, 
+	\label{l1}
+\end{equation}
+where $D_\mathrm{L1}$ is the L1-distance, and $\eta$ is the accuracy of
+any binary classifier during validation (provided mild conditions are met). 
+Since a classifer's performance estimates
+a lower bound on the L1 distance, we shall denote 
+$D_\mathrm{L1}^-\equiv 2\eta-1$.
+The value of $D_\mathrm{L1}$ ranges from 0 to 1; when $D_\mathrm{L1} = 0$ HPUs 
+shown one prime or another are 
+indistinguishable, wheras if $D_\mathrm{L1} = 1$ priming is so complete that 
+differently primed HPUs can be distinguished perfectly.
+The
+interested reader will find further discussion of the statistical properties
+of our approach and proofs of the above claims in the supplementary material.
 
 \paragraph{Experimental setup.}
-We performed two experiments, soliciting respectively 900 and 2300 MTurk 
-workers to label images depicting iconic cultural scenes, meals, ingredients, 
-table-settings, and various utensils and cookware. In these experiments,
-workers were randomly assigned to treatments, and depending on this 
-assignment, were exposed to different framing primes, given a different 
-set of initial images, and shown a different permutation of the test images. 
-For both experiments, workers were first shown brief instructions.  
-The framing prime was then shown, unless the given 
-treatment involved no framing.  Workers then performed a series of 
-image-labeling tasks and had to provide five labels per image. 
-For the purpose of analysis, we denote the first five images as the 
-\textit{initial set}, and the last five as the \textit{test set}, but no
-distingction was made from
-the perspective of the worker.
-Table 1 sumarizes the various experimental treatments for both 
-experiments.
+We performed two experiments, soliciting respectively 2300, and 900 MTurk 
+workers to label images depicting food, kitchen- and dinnerware, and cultural
+scenes.  Both experiments had four treatments, and in all treatments of a 
+given experiment, the last five ``test'' tasks performed by the workers were 
+the same.  Two treatments for each experiment were used to explore inter-task 
+effects, by making the initial five tasks for these treatments different.  
+For example, in the first 
+experiment, the test images depicted clutterd scenes of food and objects,
+while ``initial'' images depicted either food only, or non-food objects 
+(see Fig. 1).  Although we divide the tasks into initial tasks and test tasks,
+no distinction is apparent from the perspective of the worker. Another two 
+treatments in both experiments explored framing, 
+by presenting the worker with language suggesting a particular research 
+intent.  For example, in the first experiment, we stated 
+``funded by the laborotary for the visual perception of \{ Objects and Tools 
+$\vert$ Food and Ingredients \}''.  For emphasis, the frame text was presented
+free of surrounding text, with the variable text in boldface and larger font.
 
+The experiments and treatments are 
+summarized in Table 1, which also introduces short names which we will use to 
+identify specific experimental treatments and groupings.
+An additional difference between \texttt{exp1} and \texttt{exp2} is that,
+in both treatments for \texttt{task1}, workers were shown the test tasks in
+one of five permutations, which allows us to analyze the dependance of 
+inter-task effects on task proximity, independant of task content.
+We provide a fuller account of the experimental design, and exhibit all the
+task materials used, in the supplementary material.
+
+\setlength{\tabcolsep}{3pt}
 \begin{table}[t]
 \centering
-	\begin{tabular}{ l  l  l }
-		\hline                       
-		Treatment & Framing prime & Initial image set	\\ 
-		\hline                       
-		\textit{Experiment 1}\\
-		$\textsc{ambg}$ & None & Ambiguous\\
-		$\textsc{img:cult}$ & None & Cultural\\
-		$\textsc{img:ingr}$ & None & Ingredients\\
-		$\textsc{frm:cult}$ & Cultural & Ambiguous\\
-		$\textsc{frm:ingr}$ & Ingredients & Ambiguous\\
-		\hline  
-		\textit{Experiment 2}\\
-		$\textsc{img:food}$ & None & Food\\
-		$\textsc{img:obj}$ & None & Objects\\
-		$\textsc{frm:food}$ & Food & None\\
-		$\textsc{frm:obj}$ & Objects & None\\
-		\hline  
+\begin{tabular}{ c c c c c }
+		\hline \noalign{\smallskip}
+		\multicolumn{3}{c}{\textbf{Treatment name}} & \parbox[c]{1.6cm}{\centering \textbf{Framing\\ Prime}} & \parbox[c]{1.7cm}{\centering \textbf{Initial\\ image set}}	\\
+
+		\noalign{\smallskip} \hline \noalign{\smallskip}
+
+		\multirow{6}{*}{ \parbox[c]{1cm}{ \phantom{XXX} exp1}} 
+			& \multirow{2}{*}{task1} & food & none & food\\
+			& & obj & none & objects\\
+
+			\noalign{\smallskip} \cline{2-5} \noalign{\smallskip}
+			& \multirow{2}{*}{frame1} & food & food & none\\
+			& & obj & objects & none\\
+
+			\noalign{\smallskip} \cline{2-5} \noalign{\smallskip}
+			& \multirow{2}{*}{echo} & food & food & none\\
+			& & obj & objects & none\\
+
+		\noalign{\smallskip} \hline \noalign{\smallskip}
+
+		\multirow{4}{*}{exp2} 
+			& \multirow{2}{*}{task2}  &  food & none & food\\
+			& 	&  cult & none & culture\\
+			\noalign{\smallskip} \cline{2-5} \noalign{\smallskip}
+			& \multirow{2}{*}{frame2} & food & food & food\\
+			& 	& cult & culture & food\\
+
+		\noalign{\smallskip} \hline  
 	\end{tabular}
@@
 	\caption{ \footnotesize{ 
-		Workers were uniformly randomly assigned to one of the 
-		treatments listed above. 
-		The full funder names used were 
-		Cultural: ``The Global Foundation for Cultural Recognition'' and 
-		Ingredients: ``The National Foundation for Nutritional Awareness''.  
-		The ambiguous, cultural, and ingredients initial image sets are shown 
-		in \textbf{Figs. 2}, \textbf{3}, and \textbf{4}.
+		We use the treatment names shown to refer to specific sections of 
+		the data collected.  For example, \texttt{task2:food} refers to the
+		treatment in the second experiment which was not exposed to a frame, 
+		and whose initial tasks contained images of food (7th row).
 	}}
@@
 
-\paragraph{The strength of inter-task effects.}
+\paragraph{The strength of intertask effects.}
+
+We assessed the strength of intertask and framing effects
+by training a multinomial naive Bayes classifier to predict a worker's 
+treatment (from two possibilities) based on the labels they provided 
+in the test tasks (see Fig.~\ref{fig:theta}).
+We found that in \texttt{task1}, whether a worker had labeled food or non-food 
+objects during initial tasks, had a strong effect on their subsequent labels, 
+biasing them by more than 30\%.  In comparison, the framing effect in \texttt{frame1} did 
+not influence workers' labels enough for the classifier predict their treatment
+with an accuracy significantly better than chance.  The results for 
+\texttt{exp2} show a similar, but even more pronounced trend, with the bias
+induced by intertask effects in \texttt{task2} probably exceeding 40\%.
+
+It is worth noting that \texttt{task1} and \texttt{task2} differ in the kind
+of comparison that they make.  In \texttt{task1},
+the prime concepts (``food'' and ``objects'') are, in certain ways, very 
+similar: both are relatively concrete, well-defined concepts, corresponding
+to bounded physical entities that can be directly photographed.
+But in \texttt{task2}, the prime concepts (``food'' and ``culture''), 
+are very different:  culture is far more abstract and difficult to define
+than food, and is not a bounded physical entity.  We will come back to this 
+point, but note 
+here that these pairs of prime concepts both lead to strong intertask effects
+despite exploring very different conceptual dimensions.
+
+As another point of comparison, we included additional framing-like 
+treatments in \texttt{exp1} in which we attempted to increase the effect.
+In the \texttt{echo} treatment pair, we used a more strongly worded frame:
+``The purpose of this study is to understand the visual perception of
+\{ Objects and Tools $\vert$ Food and Ingredients \}'', and then worker was
+asked to reiterate back the purpose of the study, using a combo-box input.
+We expected this to induce a strong effect because it signals that this detail
+is of particular concern to the task requester, and more important than any of 
+the instructions given beforehand.  
+The overall effect of these primes was on par with the intertask 
+effects in \texttt{task1} (see Fig.~\ref{fig:theta}), which shows just how
+powerful intertask effects are.
+
 \begin{figure}
@@
 
-%\paragraph{Dynamics of inter-task effects}
-%\begin{figure}
-%	\centering
-%	\includegraphics[scale=0.7]{figs/theta_by_pos_img.pdf}
-%	\caption{
-%		Difference in priming observed for various pairs of worker populations.
-%		The pairs of populations differed in terms of the initial tasks they
-%		performed (bars labeled by ``inter-t.'') or in terms of the framing
-%		to which they were exposed (bars labeled by ``frame''; see table 1 for
-%		details about the treatments).  The difference in priming was 
-%		measured based on the accuracy of a naive Bayes classifier in 
-%		resolving which treatment workers belonged to, as described in the 
-%		text.  
-%	}
-%	\label{fig:theta_pos_img}
-%\end{figure}
+\paragraph{Dynamics of intertask effects.} Following the observation that
+intertask effects are strong, it is natural to ask how the effect of an early
+task wanes as the worker proceeds through subsequent ones.  To investigate
+this, in \texttt{task1} workers performed the test tasks in one of five 
+permutations.  This allows us to average the intertask effect accross different
+test tasks when they occupy the same position.  We found that the effect was
+strongest for the first test image, and that a significant effect persisted
+through the five test tasks (see Fig.~\ref{fig:theta}B).  This shows the 
+extent to which the first 
+test task re-primes workers, washing out the effect of initial tasks, but that
+the effect is quite persistent.  In future work, it would be interesting to
+investigate whether the first few tasks have a particularly strong priming
+effect because they ``set the tone'' for the batch.
 
-We analyzed the overall strength of inter-task effects and framing, by looking
-at pairs of treatments that performed the same test tasks, but had done
-different initial tasks or had been exposed to different framing.
-For each such pair, we assessed the performance of classifier
-in predicting which treatment workers belonged to, based on the labels they
-provided during the test tasks (see fig 2).  
-Based on \textbf{Definition 2}, this is a lower bound on the amount 
-bias introduced by the initial tasks and framing.
+This set-up also allows us to see how much the each test tasks differ in their 
+susceptibility to intertask effects, independant of their position among the
+others.  There does appear to be substantial differences, but relative
+position of the test task is more important (Fig.~\ref{fig:theta}C).
 
-In experiment \textit{inter-t.1}, the test tasks required workers to
-label relatively cluttered images of table settings, which had various items
-of food, utensils, dishware, and other objects natural to such settings.
-For one treatment, the images in the initial tasks consisted exclusively of 
-food, and for the other, they consisted exclusively of non-food objects, 
-particularly cookware and utensils.  We saw a strong effect of priming, 
-based on the classifier performance (see fig. 2).
-
-In a related experiment, \textit{frame1}, workers were given the same test tasks
-as in \textit{inter-t.1}, but were either told 
-that ``The purpose of this study is to understand the viusual perception of
-Food and Ingredients'' or ``\ldots of Objects and Tools''.  This overt framing
-of the task in terms of a specific research objective had remarkably milder
-effects on workers than the initial tasks (see fig. 2).
-
-We performed another set of experiments based on a different set of test 
-tasks, and where the initial tasks and framing were directed along a different
-conceptual axis.  In \textit{inter-t.2} and \textit{frame2}, the images in the test 
-tasks displayed prepared meals from a variety of ethnic backgrounds.  We then
-designed the framing and initial tasks to focus either on food or cultural 
-elements.  In the previous experiments, the primes were always focused on 
-concrete ``highly imageable'' concepts (food and objects), these experiments
-mixed a concrete concept (food) with an abstract concept (culture).
-The initial tasks in \textit{inter-t.2} either depicted prepared meals (but having
-ambiguous cultural association), or iconic cultural scenes (including music, 
-dance, and sport).  Workers in \textit{frame2} were told that the ``This study
-was proudly funded by the National Foundation for Nutritional Awareness'' 
-or the ``\ldots Global Foundation for Cultural Recognition''.
-
-The results for \textit{inter-t.2} and \textit{frame2} confirmed that 
-inter-task effects are much stronger than framing (see fig. 2).  In fact, 
-intertask effects were even stronger in this experiment than the previous.
-
-\paragraph{Sufficiency of framing.} Given just how much stronger
-inter-task effects were, the reader may wonder whether the framing was 
-in some sense ``sufficient''.  
-We designed our framing tasks based on
-work that had previously studied framing effects in micro-task settings.  
-Prior studies have shown that framing the purpose of a task, or indeed, 
-simply changing a single, seemingly non-critical word in a task description, 
-has significant effects on worker's resonses.  Perhaps more importantly, the 
-framing treatments were included to provide a reasonable basis for comparison,
-and it is clear from our results that the prior tasks performed by a 
-worker are much stranger than the effects induced by descriptions of a task's
-purpose, or the requester's mandate.
-
-Nevertheless, we included one more experiment, \textit{frame*3}, to test the 
-effect of framing when the worker is required to \textit{echo} the framing 
-statement.  \textit{frame*3} was based on \textit{frame2}, but the worker
-had to indicate, using a menu option, what the purpose of the study was,
-before they could proceed.  In one sense, this seems to go beyond what one
-might mean by ``framing''.  By forcing the worker to echo the frame, we provide
-a clear indication that the frame is a particularly important detail, 
-elevating its importance above even the instructions that had been provided
-beforehand.
-
-The framing effect in \textit{frame*3} was quite strong, being on par with the
-inter-task effects we had observed (see fig. 2).  We are not sure whether
-the \textit{frame*3} should be considered framing,
-or whether it should be considered as an instruction, or perhaps as a 
-screening-task.  Regardless, our results show that worker's responses are 
-profoundly affected by recently completed tasks.
-
-\paragraph{Dynamics of intertask effects.} 
-In the results shown above, we considered the aggregate effect that the
-first five initial tasks had on the last five test tasks.  But it would stand
-to reason that the first test task might be
-most strongly influenced, and that, as the worker proceeds, the intervening 
-test tasks would tend to wash out the priming induced by the initial tasks.
-
-One complication to this is the fact that the strength of intertask effects
-should also depend on the task: that is, workers performing one task are not
-necessarily as susceptible to inter-task effects as when performing another 
-task.  To account for this, we performed five replicates of the 
-\textit{inter-t.1} experiment, each using a different permutation of the 
-test tasks.  We ensured that each test task appeared in each of the 
-five possible relative positions.  This allowed us to measure the inter-task
-effects as a function of task position, independant of the particular image
-used in the task (see fig. 2B).  We found that, as one would expect,
-the first test task tends to be the most strongly affected.  The effect drops
-considerably for the second task, and continues to fall for the third and 
-fourth.  Interestingly, the last test task consistently showed a small increase
-in priming effect.  We also observed this in \textit{inter-t.1}. 
-We do not know the psychological mechanism behind this phonomenon, but we 
-speculate that, since the worker knows that there are ten tasks in total,
-they might reflect on the task overall batch of tasks as they near the end,
-and in so-doing might partially re-activate the influence of the initial tasks.
-
-While the strength of inter-task effects appeared to depend strongly on
-the position of the task, it was considerably less dependant on exactly what
-was in the task (see fig. 2C).  To be sure, we intended for the tasks to be 
-similar, and it does appear that the various test tasks had similar 
-susceptibilities to inter-task effects.
-
-\paragraph{Initial tasks' affect on the direction of focus} 
+\paragraph{Effects on workers' direction of focus} 
 \begin{figure}
 	\centering
-	\includegraphics[scale=1]{figs/food_specificity.pdf}
+	\includegraphics[scale=1]{figs/delta_food.pdf}
 	\caption{
@@
 	}
-	\label{fig:food_specificity}
+	\label{fig:food}
 \end{figure}
 
-At this point we have only discussed priming effects in terms of a 
-classifier's ability to detect them.
-We have said nothing qualitative about the \textit{nature} of these effects.  
-This demonstrates an advantage of using classifiers to measure priming.  
-Machine learning algorithms are designed to find salient differences 
-by generalizing, inductively, from examples, so one
-need not know beforehand how workers were primed, nor the natuer of the  
-priming effects.  Machine learning algorithms are specifically designed to 
-generalize inductively from examples, which makes
-it possible to estimate how different two populations with little prior 
-knowledge.
+It is reasonable to expect that exposing a worker to tasks containing images
+of food would increase her propensity to provide food-related labels in 
+subsequent tasks.  To test whether this straightforward elicitation occured,
+we used the wordnet corpus to operationalize the notion of food-related 
+labels.  While the coverage of most western food-related words is quite good
+we found that the names of many ethnic foods are missing, so we augmented
+the corpus by crawling the world food section of the recipes website 
+allrecipes.com.  We discuss the validation of our operationalization of 
+food-words in detail in the supplementary material.
 
-But once having shown that workers are strongly primed by initial tasks, it is
-natural ask whether workers were biased to provide labels that reflected, 
-in some way, the \textit{content} of the initial tasks.  The conceptual basis
-for the primes in experiment 2 were eithre \textit{food} or 
-\textit{objects and tools}.  Thus, we can test whether workers exposed to food
-primes produced more food-related.
+For \texttt{task1} and \texttt{frame1} we did find that exposing workers to 
+food-oriented primes led them to increase their provision of food-related 
+labels by about 2-3\% (see Fig.~\ref{fig:food}).  
+In \texttt{echo} this effect was stronger
+\texttt{echo:food} provided about 8\% more food-related words than 
+\texttt{echo:obj}.  Indeed, the \%-increase in food labels observed for
+\texttt{echo} was significantly larger than that for \texttt{taks1}, which is 
+interesting
+given that the overall priming effect observed for \texttt{task1} and 
+\texttt{echo} were on par (c.f. Fig.~\ref{fig:theta}).
+This makes sense, given that \texttt{echo:food} explicitly calls for a focus 
+on food, whereas \texttt{task1:food} probably works by activating certain 
+memories and concepts, with a more complex impact on labels.
 
-To identify food-related labels, we used the wordnet corpus.  Wordnet
-is an extensive corpus for English, that includes hypernym-hyponym 
-relationships between words.  The hypernym relation correpsonds to conceptual
-abstraction.  For example \textit{bread} is a hypernym of 
-\textit{pumpernickel} because pumpernickel is a \textit{type of} bread.
-The hyponym relation is simply the converse: pumpernickel is a hyponym
-of bread.  For the purpose of our analysis, when we refer to hypernyms,
-we will mean both direct hypernyms, as well as the hypernyms of hypernims,
-and so on, with an analogous interpretation for hyponyms.
+In \texttt{exp2} we see a strikingly different effect: workers initially 
+exposed to food-related tasks actually show fewer food-related labels for the
+test tasks.  Recalling the content of the test tasks helps to explain this
+observation.  The test tasks in \texttt{exp2} embed both the prime concepts
+of food and culture, which we accomplished by using images of food having
+very particular and identifiable cultural origins.  The initial tasks in
+\texttt{task2:food} were, by comparison, culturally ambiguous, and the worker
+would presumably be struck by the appearance of strong cultural overtones
+in the test tasks.  On the other hand, due to the effect of negative priming,
+workers in \texttt{task2:cult} might be somewhat desensitized to the cultural
+content in the images, and instead be struck by the sudden appearance of food.
 
-We collectod a small set of top-level food-related nouns in wordnet,
-together with all of their hyponyms, and took the resulting set of 
-3589 lemmas as an operational definition for the set of English food-related 
-words.  This set is quite extensive, containing somewhat obscure forms such as
-``burgoo'' and ``barmbrack'', and consumables at the fringe of what might
-be considered food such as ``vitamin B'' (or if you prefer, 
-``B complex''), as well as more common lemmas like
-``banana'',  ``bread'', and of course ``banana bread''.  We found that,
-for the data in experiment 1, this method produced excellent aggreement with 
-human annotation of food-related words (see supplementary material).  
-For the analysis exp2, the variety of non-English names for ethnic dishes 
-forced us to rely on a manual approach.  This corroborated our results
-for exp1, and we encourage the interested reader to read our discussion of
-the manual approach in the supplementary material.
+\paragraph{Effects on label vocabulary and specificity.}
+\begin{figure}
+	\centering
+	\includegraphics[scale=1]{figs/vocab_specificity.pdf}
+	\caption{
+		Difference in priming observed for various pairs of worker populations.
+		The pairs of populations differed in terms of the initial tasks they
+		performed (bars labeled by \textit{inter-t.}) or in terms of the framing
+		to which they were exposed (bars labeled by \textit{frame}; see table 1 for
+		details about the treatments).  The difference in priming was 
+		measured based on the accuracy of a naive Bayes classifier in 
+		resolving which treatment workers belonged to, as described in the 
+		text.  
+	}
+	\label{fig:specificity}
+\end{figure}
 
-Our findings matched the straightforward expectation that workers exposed to 
-food related-primes were biased to provide more food-related labels during 
-test tasks (see Fig. 3A).  Had we relied on the intuition that workers 
-should be biased to label according to the underlying concept of their prime,
-we would have underestimated the strength of priming effects.  This
-again illustrates the advantage of using classifiers to detect priming as
-opposed to testing for the effects that one might intuitively expect.  
-Though present, the expected influence on the number of food-related words
-cannot account for the bulk of inter-taks effects.
+We gain some insight into the induced intertask effects by looking at the
+labels whose frequencies changed the most due to workers' early task exposure. 
+For example, the ``food'' is the most strongly suppressed label among 
+workers exposed to food-related initial tasks.  At first, this may seem 
+unexpected, since, for \texttt{task1:food}, food labels are more common 
+overall.  But ``food'' is the most generic possible food-related label, 
+so this means that \texttt{task1:food} workers are trading their usage of
+``food'' for more specific food references.
 
-\paragraph{Effects on label vocabulary.}
+The richness and specificity of vocabulary that a worker brings to a 
+characterization task is of great importance in crowdsourcing.  For example,
+in the Galaxy Zoo citizen science project, workers are 
+trained to develop a lexicon of galaxy features such as the smoothness,
+the presence of rings, dustlanes, digital disturbances, etc.  In our set-up,
+the workers lexicon is unconstrained and un-scaffolded, so we can see 
+how initial tasks alter the workers lexicon spantaneously.
+
+To investigate this we used the wordnet corpus, which has embeds a rich
+nested ontology of concepts in the form of hypernym-hyponym noun relationships.
+A hypernym is a generalization, while a hyponym is a specialization; for 
+example ``bread'' is a hypernym of ``pumpernickel''.  Using wordnet, we 
+can represent the labels produced by one group of workers, for example 
+\texttt{task1:food}, and compare it to those labelled by \texttt{taks1:obj}.
+We describe the details of this comparison in the supplementary material,
+but the result is a net tally of all the cases where a word of the first 
+group is more specific than one from the second, less the cases where the 
+word of the second group is more specific.
+
+By performing this specificity comparison, while restricting our focus to
+food-related words, we can see that workers are in fact induced to be 
+significantly more specific in their usage of food-related words (see Fig.XX).
+
+in their usage 
+food-related terms in \texttt{task1:food}
+than in \texttt{task1:obj}.
+
+one 
+to be more specific, less those found to be less specific, in comparing the 
+words of the one to those of the other.
+
+citizen science efferts, like galaxy zoo.
+
+food-related labels.
+to \textit{more specific} food-labels.
+
+food-related labels are,
+overall, 
+food-  This is true even when the there are more food-related
+terms overall
+
+tasks.  Interestingly, we see that the label ``food'' is always suppressed
+in food-primed treatments, but this effect is particularly strong for the
+
+changing initial tasks (and frames) by looking at those labels that show
+the greatest frequency change
+primes 
 When manually inspecting the labels of \textit{test-t.2}, one striking 

### 2014-11-16 src/new_plots.py

@@ -15,75 +15,24 @@ import numpy as np
 import time
 import os
 
-import matplotlib.pyplot as plt
-import matplotlib 
-import matplotlib.gridspec as gridspec
-from matplotlib.ticker import MultipleLocator, FormatStrFormatter
+try:
+	import matplotlib.pyplot as plt
+	import matplotlib 
+	import matplotlib.gridspec as gridspec
+	from matplotlib.ticker import MultipleLocator, FormatStrFormatter
+except ImportError:
+	print 'could not import matplotlib.'
 
-	
 
+# ** Constants ** #
 #z-score for two-tailed 99-percent confidence interval
 CONFIDENCE_95 = 1.96
 CONFIDENCE_99 = 2.975
-
-
-TREATMENT_NAMES = {
-	'treatment0': 'AMBG'
-	, 'treatment1': 'CULT$_{img}$'
-	, 'treatment2': 'INGR$_{img}$'
-	, 'treatment3': 'INGR$_{fund}$'
-	, 'treatment4': 'INGR$_{fund,img}$'
-	, 'treatment5': 'CULT$_{fund}$'
-	, 'treatment6': 'CULT$_{fund,img}$'
-}
-
-TEST_NAMES = [
-	'img_food_cult',
-	'img_food_obj',
-	'wfrm_food_cult',
-	'wfrm_food_obj',
-	'sfrm_food_obj'
-]
-
-EXPERIMENT_NAMES = {
-	'img_food_cult': 'inter-t. 1',
-	'img_food_obj': 'inter-t. 2',
-	'wfrm_food_cult': 'frame 1',
-	'wfrm_food_obj': 'frame 2',
-	'sfrm_food_obj': 'frame 3'
-}
 
 IMAGE_NAMES = ['test%d' %i for i in range(5)]
 
 DATA_DIR = 'data/new_data'
 FIGS_DIR = 'figs/'
-
-
-def plot_self_specificity(
-		read_fname = 'data/new_data/self_specificity.json',
-		write_fname = 'figs/self_specificity.pdf'
-	):
-
-	self_specificity = json.loads(open(read_fname).read())
-
-	# make a figure with three subplots
-	figWidth = 16.78 / 2.54 	# conversion from PNAS spec in cm to inches
-	figHeight = 4/5.*figWidth	# a reasonable aspect ratio
-	fig = plt.figure(figsize=(figWidth, figHeight))
-	gs = gridspec.GridSpec(1, 2)
-
[…]

### 2014-11-16 src/util.py

@@ -5,6 +5,24 @@ def writeNow(string):
 	sys.stdout.write(string)
 	sys.stdout.flush()
 
+
+def counter_relative_diff(c1, c2):
+	result = {}
+	for key in set(c1.keys() + c2.keys()):
+		diff = c1[key] - c2[key]
+		avg = (c1[key] + c2[key]) / 2.0
+		result[key] = diff / avg
+
+	return result
+
+
+def counter_subtract(c1, c2):
+	result = {}
+	for key in set(c1.keys() + c2.keys()):
+		result[key] = c1[key] - c2[key]
+
+	return result
+
 def randomPartition(collection, *args):
 	firstPartitionSize = args[0]
 

### 2014-11-16 src/wordnet_analysis.py

@@ -453,13 +453,21 @@ def map_to_synsets(word_counts):
 	return synset_counts
 
 
-def strip_food_words(word_counts):
+def filter_word_counts(word_counts, include_food=True, include_nonfood=True):
 	food_detector = WordnetFoodDetector()
 
-	#Make a new copy of the word counts, but only include non-food words
+	# If everything is included, there is nothing to filter out
+	if include_food and include_nonfood:
+		return word_counts
+
+	# Copy the word counts, but only include the desired kinds of words
 	new_counts = {}
 	for key in word_counts.keys():
-		if not food_detector.is_food(key):
+
+		if include_food and food_detector.is_food(key):
+			new_counts[key] = word_counts[key]
+
+		if include_nonfood and (not food_detector.is_food(key)):
 			new_counts[key] = word_counts[key]
 
 	return new_counts
@@ -469,7 +477,9 @@ def strip_food_words(word_counts):
 def calculate_relative_specificity(
 		word_counts_1, 
 		word_counts_2,
-		ignore_food=False
+		include_food=True,
+		include_nonfood=False,
+		normalize=True
 	):
 	'''
 	returns the relative specificity between to sets of synsets.
@@ -478,11 +488,12 @@ def calculate_relative_specificity(
 	but gives the same result.
 	'''
 
-	if ignore_food:
-		print len(word_counts_1), len(word_counts_2)
-		word_counts_1 = strip_food_words(word_counts_1)
-		word_counts_2 = strip_food_words(word_counts_2)
-		print len(word_counts_1), len(word_counts_2)
+	print len(word_counts_1), len(word_counts_2)
+	word_counts_1 = filter_word_counts(
+		word_counts_1, include_food, include_nonfood)
+	word_counts_2 = filter_word_counts(
+		word_counts_2, include_food, include_nonfood)
+	print len(word_counts_1), len(word_counts_2)
 
 	synset_counts_1 = map_to_synsets(word_counts_1)
 	synset_counts_2 = map_to_synsets(word_counts_2)
@@ -492,17 +503,30 @@ def calculate_relative_specificity(
 	descendant_counter = WordnetRelativesCalculator(synset_counts_2, False)
 
 	specificity_score = 0
+	num_actual_comparisons = 0
 
 	# for every synset in synset_counts_1, add the number of descendants
 	# minus the number of ancesters to get the net relative specificity
 
 	for synset_name, count in synset_counts_1.iteritems():
 		syn = ewn.synset(synset_name)
[…]

### 2014-11-17 docs/publications/2014.09_SCIENCE/new_man.tex
work on manuscript

@@
 \paragraph{Effects on workers' direction of focus}
-\begin{figure}
-	\centering
-	\includegraphics[scale=1]{figs/delta_food.pdf}
-	\caption{
-		Difference in priming observed for various pairs of worker populations.
-		The pairs of populations differed in terms of the initial tasks they
-		performed (bars labeled by \textit{inter-t.}) or in terms of the framing
-		to which they were exposed (bars labeled by \textit{frame}; see table 1 for
-		details about the treatments).  The difference in priming was 
-		measured based on the accuracy of a naive Bayes classifier in 
-		resolving which treatment workers belonged to, as described in the 
-		text.  
+
+Having observed significant effects from framing and task-exposure,
+we looked in greater detail at the nature of the effects.  For instance,
+does a food-oriented exposure induce workers to provide more food-related
+labels?  And if so, does this explain the classifier's ability to distinguish
+a worker's initial exposure?
+
+To answer these questions we used the wordnet corpus, augmented with names of
+ethnic foods learned from the Internet.  Wordnet provides a (roughly)
+hierarchical set of relationships between nouns, called hypernym-hyponym
+relationships.  A hypernym is a generalization, while a hyponym is a 
+specialization.  So, for example, ``bread'' is hypernym to ``rye bread'' 
+and hyponym to ``baked goods''.
+
+Using the hypernym-hyponyms structure of wordnet to identify nouns depicting
+food, we found that, for the experimental pairings in \texttt{exp1}, the
+food-exposed treatments did produce a significantly larger fraction of 
+food-related labels (see Fig.~\ref{fig:specificity}A).  While the shift in 
+focus with regard to food does help explain how workers differ depending on 
+their exposure, it still leaves most of this difference unexplained.
+Furthermore, in \texttt{exp2:task2} we see a significant but reversed effect
+(see Fig.~\ref{fig:specificity}A).
+Given the difference between the food-culture and food-object axes, it should
+not be surprising that the effect of exposure is different.  This tells us that
+the differences induced by exposure to frames or initial tasks are significant,
+but would appear to be the result of countervailing influences, with the
+overall outcome dependant on the particular axis of the exposures, we will
+come back to this momentarily.
+
+To explore these effects further, we looked more closely at which particular
+labels are most suppressed (activated) by a workers exposure.  We found that, 
+for all treatment pairs, ``food'' was always the most suppressed label among 
+the food-exposed workers.  This is surprising, given that we have just seen 
+that the bulk incidence of food-related labels \textit{increased} among 
+food-exposed workers in most treatment pairs.
+Since ``food'' is the most generic food-related word in the wordnet-based
+ontology, it follows that food-exposed workers have opted to provide more
+specialized references to food rather than using ``food''.
+
+Considerable thought must be given to shaping the the vocabulary with which
+a worker engages a task.  To draw an example from the domain of citizen 
+science, in galaxy zoo, workers catalogue images of galaxies in terms of
+smoothness, rings, dustlanes, digital disturbances, and so on.  Shaping this
+vocabulary, is accomplished through a combination of positive and negative
+examples during training, peer-to-peer and peer-to-expert engagement in 
+discussion areas, and using the interface to constrain and prompt the 
+worker.
+
+In our set-up, where the worker's vocabulary is unconstrained, we can 
+directly see the effects that frames and initial tasks induce on worker 
+vocabulary.
+By looking at the number of unique food-related labels that workers 
+produced, we assesed the richness of vocabulary that workers used when 
+referring to food (see Fig.~\ref{fig:specificity}B.  We found that the 
+food-exposed workers use a richer vocabulary of 
+food-related words, even in cases like \texttt{task2:food}, where the 
+food-exposed treatment made fewer references to food overall.  
+Interestingly, in this respect, initial taske exposure had a stronger effect
+than framing, including the \texttt{echo} treatment pair. This makes sense, 
+given that the various images shown in the initial
+tasks would tend to activate a variety of memories and concepts related to 
+food, reducing the threshold for later activation during the test-tasks.
+
+Using the ontology of food induced by wordnet, we perform a more detailed
+calculation of the relative specificity of workers from different treatments.
+To do this, we considered all the labels from one treatment
+(for example \texttt{task1:food}) and compared these to all the labels from 
+another (\texttt{task1:obj}).  For all possible comparisons, we observed 
+which treatment's label was more specific more often.  We normalied this
+as a percentage (details in supplementary material) so that we can compare the
+relative change in specificity between different treatment pairs  .
+
+Performing the above-mentioned calculation while restricting focus to 
+food-related labels (see Fig.~\ref{fig:specificity}C), we found that 
+the food-exposed workers always provided food-references of substantially 
+greater specificity.  In this respect, the effect induced by 
+echoed framing was stronger than that induced by the initial task exposures in
+\texttt{task1}.
+
+Taking the all the results shown in Fig.~\ref{fig:specificity} together,
+a picture emerges which explains the differing natures of intertask and framing
+effects.  First, both negative and positive priming would appear to be at play.
+Negative priming occurs when a repeated stimulus, which is perceived to be
+nonsalient, begins to be ignored.  As a worker from \texttt{task1:food}
+proceeds through the initial tasks, food-related memories and concepts are
+activated, reducing increasing the likelihood that she provides a variety of
+different food-related labels.  This increases the number of food-related
+labels, and increases the richness and specificity of her food-related 
+vocabulary.  But meanwhile, in the most general sense, the fact that the 
+pictures contain food becomes negatively primed.  She does not regard ``food''
+to be a meaningful label, and is inhibited in providing it.   
+As for the worker in \texttt{task2}, similar effects occur as she proceeds
+through the initial tasks.  Upon viewing the first test task, the introduction
+of a very prominent cultural element is novel, and is attended to, whereas
+her counterpart in \texttt{task2:cult} has seen several images containing 
+cultural themes, and is negatively primed to the general setting of culture,
+but responds to the novelty of the introduction of food.  Finally, looking at
+the results for \texttt{echo}, we see evidence of its effects operating through
+the executive faculties of the worker.  There is considerably more
+restriction to food-related labels, and even a greater specificity of such 
+labels, but, lacking the diverse activations of food-related memories and 
+concepts from initial tasks, the richness of vocabulary is lower.
+
+Based on these observations, we submit several recommendations for the 
+consideration for the designers of croudsourced initiatives.
+\begin{enumerate}
+	\item{
+		Examples provide a valuable way to clarify intstructions, but 
+		training tasks should be preferred, since they activate concepts and 
+		faculties relevant to the subsequent task.
 	}
-	\label{fig:food}
-\end{figure}
+	\item{
+		Examples used for training should not be too ``clean'', but should 
+		contain the same distribution of noise, or distracting features, as 
+		is observed in the real dataset.
+		This may help desensitize the worker to the nonsalient features.
+		Using training tasks that are too clean will make the subsequent noise
+		more novel and thus more distracting.
+	}
+	\item{
+		It is common practice to plant \textit{validation tasks}, for which the
+		correct answer is known, to verify worker reliability.
+		These tasks should simultaneously be considered as 
+		\textit{callibration tasks}, which help
+		the worker to maintain an optimally primed state.
+		Giving feedback, for both correct and incorrect callibration tasks, 
+		may help further reinforce the salient features for the tasks.
+	}
+	\item{
+		Some tasks require the classification of imbalanced datasets.
+		For example, in the detection of pre-ictal (pre-siezure) EEG traces,
+		the majority of traces are normal.  The absence of exposure to the 
+		positive class can lead to a loss of activation for the
+		salient features and a drifting conceptualization of the class.
+		Using callibration tasks drawn from the underrepresented class may 
+		help sustain workers' attention and recall for that class.
+	}
+	\item{
+		When a very precice classification is needed, it may be helpful to
+		performing the classification in multiple steps.  For example, in a 
+		binary classification, the workers could initially perform a coarse
+		classification, using three options for response: 
+		``definitely class 0'', ``definitely class 1'', and 
+		``borderline''.  Following the coarse classification, the 
+		``borderline'' examples could be served in batches together, 
+		allowing workers to focus on finer distinctions which are salient 
+		in the context of borderline examples.
+	}
+\end{enumerate}
 
-It is reasonable to expect that exposing a worker to tasks containing images
-of food would increase her propensity to provide food-related labels in 
-subsequent tasks.  To test whether this straightforward elicitation occured,
-we used the wordnet corpus to operationalize the notion of food-related 
-labels.  While the coverage of most western food-related words is quite good
-we found that the names of many ethnic foods are missing, so we augmented
-the corpus by crawling the world food section of the recipes website 
-allrecipes.com.  We discuss the validation of our operationalization of 
-food-words in detail in the supplementary material.
+Each of these techniques can and should be tested directly, and the the
+lessons derived from those experiments should be encorporated into the best 
+practices for human computation.
 
-For \texttt{task1} and \texttt{frame1} we did find that exposing workers to 
-food-oriented primes led them to increase their provision of food-related 
-labels by about 2-3\% (see Fig.~\ref{fig:food}).  
-In \texttt{echo} this effect was stronger
-\texttt{echo:food} provided about 8\% more food-related words than 
-\texttt{echo:obj}.  Indeed, the \%-increase in food labels observed for
-\texttt{echo} was significantly larger than that for \texttt{taks1}, which is 
-interesting
-given that the overall priming effect observed for \texttt{task1} and 
-\texttt{echo} were on par (c.f. Fig.~\ref{fig:theta}).
-This makes sense, given that \texttt{echo:food} explicitly calls for a focus 
-on food, whereas \texttt{task1:food} probably works by activating certain 
-memories and concepts, with a more complex impact on labels.
+\paragraph{Conclusion.}
+Our results definitively show that intertask effects can
+be as strong as framing effects, and appear in general to be stronger.
+Intertask effects have are similar in strength to direct 
+statements about the purpose of the tasks, followed by the reiteration of the
+purpose by the worker.  However, they differ in the detailed effects that
+they bring about.  Initial tasks had a greater effect on richness of 
+spontaneously elicited vocabulary used to refer to the primed concept,
+whereas the echoed purpose had a somewhat stronger effect increasing the 
+quantity of references to the primed concept.
 
-In \texttt{exp2} we see a strikingly different effect: workers initially 
-exposed to food-related tasks actually show fewer food-related labels for the
-test tasks.  Recalling the content of the test tasks helps to explain this
-observation.  The test tasks in \texttt{exp2} embed both the prime concepts
-of food and culture, which we accomplished by using images of food having
-very particular and identifiable cultural origins.  The initial tasks in
-\texttt{task2:food} were, by comparison, culturally ambiguous, and the worker
-would presumably be struck by the appearance of strong cultural overtones
-in the test tasks.  On the other hand, due to the effect of negative priming,
-workers in \texttt{task2:cult} might be somewhat desensitized to the cultural
-content in the images, and instead be struck by the sudden appearance of food.
+The task designer would do well to give consideration to intetask effects
+when performing task batching, and when designing training and validation
+tasks.  Despite all efforts to eliminate biases in the microtask setup,
+the greatest source of biases may lurk in the tasks themselves.  
+But the task designer need not seek to factor out intertask effects altogether.
+Rather we advocate regarding intertask effects as a tunable parameter which
+can be used to optimize HPU performance.  By correctly directing attention
+and conceptual activation, intertask effects may be helpful in exceeding
+expert annotations using non-expert HPU computing in a wider variety of
+applications.
 

### 2014-11-19 docs/publications/2014.09_SCIENCE/new_man.tex
work on manuscript and plots

--- 2014-11-16 docs/publications/2014.09_SCIENCE/new_man.tex
@@
-% Use only LaTeX2e, calling the article.cls class and 12-point type.
+% ULaTeX2e, calling the article.cls class and 12-point type.
 
@@
 
-\title{Computational hysteresis:\\ inter-task effects in human computation}
+\title{Hysteresis in human computation:\\ how one task affects another}
 
@@
 alone.  These platforms support near-real-time task completion, mimicking a
-compute server, and fundamentally shift the role of the human from being a
-consumer to being a producer of computing resources.  To realize its full
+compute server, and fundamentally shift the role of the human from consumer to 
+producer of computing resources.  To realize its full
 potential, we must understand how human computation differs from machine 
-computation, and in particular address the biases known to be inherent in 
-human cognition.  Here we show that when a worker completes a series of 
-microtasks, the responses in later tasks are strongly influenced by the 
-content of earlier ones.  Our findings are not solely cautionary. We find
-evidence that these \textit{inter-task effects} can be
-harnessed to improve the quality of responses, and help to achieve 
-expert-level judgments, to increase the scope and reliability of citizen 
-science and crowdsourcing initiatives.
+computation, and address the biases known to be inherent in 
+human cognition.  The effects of various task-design variables on worker
+performance have been investigated, but there has been little 
+investigation into how consecutive tasks influence one another. Here we show 
+that the responses in later tasks are strongly influenced by the content of 
+earlier ones, an effect that is as strong or stronger than the effect of 
+framing.  Our findings are not solely cautionary; we find
+that these \textit{intertask effects} can be harnessed to improve the quality 
+of responses, and thereby help to achieve expert-level judgments in citizen 
+science and other crowdsourcing initiatives. 
+As an ancillary contribution, we demonstrate the use of machine learning 
+algorithms measure exposure-induced human bias, in terms of its ability to 
+influence human computations. 
 \end{sciabstract}
@@
 Microtask crowdsourcing platforms like Amazon Mechanical Turk (MTurk) make it 
-possible for requesters to submit batches of small tasks to a large pool of 
+possible for requesters to submit batches of tasks to a large pool of 
 workers, who do the tasks for fun, a sense of purpose, and remuneration 
 \cite{kazai2013analysis,Antin20122925}.  
-Originally used to distribute clerical work, these platforms 
-increasingly serve as a means to engage experimental 
-participants in a research 
-setting \cite{paolacci2010running,Berinsky2012351,snow2008cheap,alonso2009can}.
 Typical tasks include tagging and categorizing images 
@@
 or handwritten notes \cite{Berinsky2012351,Finnerty2013}, and judging the 
-relevancy of search results \cite{le2010ensuring,grady2010crowdsourcing,alonso2009can,kazai2013analysis}
+relevancy of search results 
+\cite{le2010ensuring,grady2010crowdsourcing,alonso2009can,kazai2013analysis}.
+Originally used to distribute clerical work, these platforms 
+increasingly serve as a means to engage experimental participants in a 
+research 
+setting \cite{paolacci2010running,Berinsky2012351,snow2008cheap,alonso2009can}.
+This trend has seeded considerable interest in characterizing the parameters
+of task design, and validating the microtask platform methodology (\#).
 
-These platforms make it possible to tightly integrate human and 
-machine computation.  Researchers coined the term HPU 
+Computer scientists view microtask platforms in the context of general
+computation.  In this regard, the platforms enable a tight integration of 
+human and machine computation.  Researchers coined the term HPU 
 (Human co-Processing Unit) in analogy to CPUs and GPUs \cite{5543192}.  
@@
 including basic operators like \texttt{vote}, \texttt{subdivide}, \texttt{map},
-\texttt{reduce}, \texttt{sentiment}, and \texttt{image\_tag}.  As was 
-done with GPU programming, libraries are being developped to give the 
-programmer more seamless access to HPU resources 
- \cite{little2010turkit,minder2011crowdlang,minder2012crowdlang,kittur2011crowdforge}.  The availability of human computing platforms makes whole new classes
-of problems tractible for the programmer.  For example ***.
+\texttt{reduce}, \texttt{sentiment}, and \texttt{image\_tag} (\#).  Libraries 
+are being developed to give the programmer more seamless access to HPU 
+resources 
+ \cite{little2010turkit,minder2011crowdlang,minder2012crowdlang,kittur2011crowdforge}.  
+As with other architectures, the HPU architecture makes entirely new classes 
+of problems tractable for the programmer (\#).
 
 But the ability to program with high-level human instructions comes with a 
-cost: HPU output is inherently noisy.  Part of this noise could be 
-explained by the random differences between workers.  Meanwhile, systematic 
-cognitive biases also play a role.  
-The phenomenon we attend to here represents yet
-another dimension of HPU variance, and arises from the fact that a worker's 
-performance changes as a function of the content of previous tasks.
-
-There has been considerable investigation into the factors that affect the 
-output from microtask work.  These include such factors as the 
-level of 
+cost: HPU output is inherently noisy.  Part of this noise can be explained
+in terms of worker demography (\#).  But systematic cognitive biases also 
+play a role (\#), a dimension of variability we investigate here.   
+So far, investigation has explored such design factors as the level of 
 pay \cite{kazai2013analysis}, training \cite{le2010ensuring}, pre-screening of 
@@
 \cite{Kinnaird2012281}, the purpose of tasks 
-\cite{chandler2013breaking}, or using an alternative problem discription
+\cite{chandler2013breaking}, or using alternate problem descriptions
 \cite{thibodeau2013natural}.  To our knowledge, no study has investigated 
-inter-task effects on microtask platforms.
+the influences that consecutive microtasks exert on one another.
 
@@
 effects \cite{Gass1999549,sohn2001task}.  Thus, a worker's response during
-one task may depend in part on previous ones.  Such \textit{inter-task} effects
+one task may depend in part on previous ones.  Such \textit{intertask} effects
 would amount to a kind of \textit{hysteresis}, meaning that HPU outputs are not
 only a function of the current input, but also of the history of inputs, with
-important implications for crowdsourcing initiatives.
+important implications for the design of crowdsourcing initiatives.
 
 Here we describe a series of experiments using the Amazon Mechanical
-Turk (MTurk) microtask platform that studied inter-task effects
-for image-labeling microtasks.  Image-labeling tasks are among the most 
+Turk (MTurk) microtask platform in which we studied intertask effects
+for image-labeling tasks.  Image-labeling tasks are among the most 
 common kinds of microtasks
@@
 \cite{5543192}.  
-During the experiments, workers performed a series of image labeling tasks, 
-and the first five images
-they labeled were varied depending on the experimental group to which they
-were assigned.  We studied the effects that changing the initial tasks 
-had on the labels provided in the final tasks.
+During the experiments, workers were presented with a series of images (one at
+a time), and had to provide five descriptive words (\textit{labels}) for each.
+We varied first five images (hereafter the \textit{initial tasks})
+and observed the effect this had on the workers' labels for the last five
+(\textit{test tasks}).
+
+The initial tasks were chosen to embed a certain \textit{prime concept}.
+In our first experiment, our prime concepts were \textit{food} and (non-food) 
+\textit{objects}.  In our second experiment, the prime concepts were 
+\textit{food} and \textit{culture}.  The test tasks for the experiments used 
+images that combined both prime concepts. Any given worker performed in only 
+one experiment, and was randomly assigned initial tasks based on one of the 
+prime concepts.  From the perspective of the worker, we made no distinction 
+between the initial tasks and test tasks.
 
@@
 In the framing treatments, before workers begin the tasks, we told them that 
-the study was funded by a lab with a particular area of interest, for example,
-in the visual perception of food in one case, or the perception of tools in
-another.
+the purpose of study was to understand the visual perception of 
+``food and ingredients'' in one case, or the 
+perception of ``objects and tools'' in another.  We varied the language of 
+the framing text (hereafter simply the \textit{frame}), and experimented with 
+requiring the worker to echo the frame using a combo-box input.
 
-Surprisingly, inter-task effects were much stronger than framing.  
+We found that intertask effects were stronger than framing, unless the worker
+was required to echo the frame, in which case both exposures were on par.  
 Our results demonstrate that initial tasks can change 
-workers' focus in later tasks.  We also found that inter-task effects altered 
-the level of specificity, and the diversity of vocabulary that workers used,
-in ways that were not reproduced using framing.
-Contrary to our initial expectations, our findings suggest that by carefully
-designing workflows, the HPU programmer can leverage inter-task effects to
-direct focus, tune specificity, and activate worker expressivity.  Our 
-findings carry two lessons for the task designer: inter-task
-effects can severely bias HPU output if HPU hysteresis is not taken into 
-account, but at the same time, inter-task effects provide another technique
-for improving HPU output and may help elicit expert-level annotation.
+workers' focus in later tasks.  We also found that intertask effects 
+significantly altered the level of specificity, and the diversity of 
+vocabulary that workers used, and did so in ways that differed from framing.
+Contrary to our initial expectations, our findings suggest that the HPU 
+programmer can leverage intertask effects.  By carefully designing workflows,
+worker focus, specificity, and expressivity can be tuned.  Our 
+findings carry two lessons for the task designer: intertask
+effects can severely bias HPU output if uncontrolled, but if properly 
+controlled, intertask effects might be optimized, which may be of significant 
+utility in achieving expert-level output.
 
 \paragraph*{Measuring computational hysteresis.}
-In setting out to measure the computational hysteresis induced by priming, 
-it is important to remember that we are only interested in the practical 
-impact of priming on the execution of HPU algorithms.  
-The distinction between measuring priming and measuring computational 
-hysteresis is subtle, but it is crucial to ensure that our findings are of 
-practical significance to crowdsourcing applications.
+Before describing the details of our experiments, we explain some 
+choices made in measuring intertask and framing effects 
+(hereafter collectively \textit{exposure effects}).  
+It might be tempting to invoke the concept of a ``neutral frame of mind'' 
+which would serve as a baseline for drawing comparisons.  But such a concept 
+seems both difficult to define, and unlikely to arise.
+Therefore, we instead always consider the effect of one exposure 
+\textit{relative} to another.  Thus, our experiments consist of 
+pairs of treatments between which we can make meaningful comparisons.
 
-This distinction dictates our choice of tools for detecting HPU hysteresis.
-A common practice for demonstrating that one population is different from
-another (e.g., HPUs exposed to one prime vs another), is to use a 
-$\chi^2$ test. This would suffice to demonstrate \textit{whether} priming of 
-HPUs had occured, however it says nothing about the \textit{extent} of 
-priming, and in particular, does not demonstrate the extent to which primed 
-HPUs would execute an algorithm differently.
+Our goal in measuring exposure effects is to show that they can actually 
+alter the course of algorithms.
+We could, by means of a $\chi^2$ test, reject the null hypothesis that
+differently exposed HPUs have the same distribution of outputs.
+However, this alone would not demonstrate a practically significant effect, in 
+terms altering the execution path of algorithms.
 
-We opt instead to measure HPU hysteresis using
-machine learning algorithms (classifiers), that have been trained to 
-distinguish HPUs that were subjected to one prime, from those subjected to 
-another.  If a classifier
-can distinguish HPUs subjected to different primes, then it serves as 
-a kind of certificate, proving 
-(up to statistical confidence) that there exists 
-an algorithm whose execution is affected by the priming of individual HPUs
-(namely, the classifier itself).  This demonstrates that, for some algorithms,
-using HPUs primed one way vs another will lead an algorithm to follow a 
-different branch of execution with a certain frequency.
-Statistically, our approach is grounded in the 
-statistical divergence metric called L1-distance 
-(alternatively \textit{total variational distance}), via the following 
-inequality:
+For this reason, we develop a measure in which we train classifier algorithms 
+to infer the exposure of an HPU from its outputs.
+If a classifier infers an HPU's exposure with significantly 
+better accuracy than provided by chance, then the HPU outputs must have 
+been affected by the exposure.  
+But in addition, the classifier serves as a kind of certificate, since it is 
+an example of an algorithm whose path of execution is influenced by the 
+exposure of 
+individual HPUs.  In the supplementary material, we ground our approach 
+rigorously in terms of the L1-distance metric, which is a measure of 
+divergence between distributions.  The L1-distance ranges from 
+0 to 1.  In our case, a value of 1 indicates that the HPU's exposure
+influences its output so strongly that the exposure can be inferred from the
+output without ambiguity.  A value of 0 indicates that the exposure has no
+impact on the HPU's outputs.  The connection between the
+L1-distance, $D_\mathrm{L1}$, and a classifier's accuracy, $\eta$, is given by:
 \begin{equation}
@@
 \end{equation}
-where $D_\mathrm{L1}$ is the L1-distance, and $\eta$ is the accuracy of
-any binary classifier during validation (provided mild conditions are met). 
-Since a classifer's performance estimates
-a lower bound on the L1 distance, we shall denote 
-$D_\mathrm{L1}^-\equiv 2\eta-1$.
-The value of $D_\mathrm{L1}$ ranges from 0 to 1; when $D_\mathrm{L1} = 0$ HPUs 
-shown one prime or another are 
-indistinguishable, wheras if $D_\mathrm{L1} = 1$ priming is so complete that 
-differently primed HPUs can be distinguished perfectly.
-The
-interested reader will find further discussion of the statistical properties
-of our approach and proofs of the above claims in the supplementary material.
+Since a classifier's performance provides a lower bound on the L1-distance, 
+we shall denote $D_\mathrm{L1}^-\equiv 2\eta-1$.
+The L1-distance admits the following interpretation: if two distributions
+$P$ and $Q$ have an L1-distance $d$, then in the worst case, the 
+frequency with which a binary algorithm operating on samples
+from $P$ outputs a 1, will differ from that when operating on samples from 
+$Q$ by $d \times 100\%$.  
+Thus, we can interpret $D_\mathrm{L1}^-$ as a kind of
+lower bound for the worst-case bias induced by HPU hysteresis.
+We provide further discussion of the statistical properties of our approach 
+in the supplementary material.
 
 \paragraph{Experimental setup.}
+\begin{figure}
+	\centering
+	\includegraphics[scale=0.7]{figs/images.jpg}
+	\caption{
+		Examples of images used in labeling tasks. Images from initial
+		tasks: A) \textit{task1:food}, B) 
+		\textit{task1:obj}, D) \textit{task2:food}, 
+		E) \textit{task2:cult}.  Images from  test tasks: C) \textit{exp1}, 
+		F) \textit{exp2}.  The full set of experimental materials is 
+		shown in the supplementary material.
+	}
+
+	\label{fig:task}
+\end{figure}
 We performed two experiments, soliciting respectively 2300, and 900 MTurk 
-workers to label images depicting food, kitchen- and dinnerware, and cultural
-scenes.  Both experiments had four treatments, and in all treatments of a 
-given experiment, the last five ``test'' tasks performed by the workers were 
-the same.  Two treatments for each experiment were used to explore inter-task 
-effects, by making the initial five tasks for these treatments different.  
-For example, in the first 
-experiment, the test images depicted clutterd scenes of food and objects,
-while ``initial'' images depicted either food only, or non-food objects 
-(see Fig. 1).  Although we divide the tasks into initial tasks and test tasks,
-no distinction is apparent from the perspective of the worker. Another two 
-treatments in both experiments explored framing, 
-by presenting the worker with language suggesting a particular research 
-intent.  For example, in the first experiment, we stated 
-``funded by the laborotary for the visual perception of \{ Objects and Tools 
-$\vert$ Food and Ingredients \}''.  For emphasis, the frame text was presented
-free of surrounding text, with the variable text in boldface and larger font.
+workers to label images depicting food, kitchen- and dining-ware, and cultural
+scenes.  In a given experiment, all workers performed the same test
+tasks, the output of which was our main dependent variable.  Before performing
+the test tasks, workers were subjected to an exposure, via one of 
+two \textit{modalities}: either they completed a set of initial tasks, or 
+were exposed to a frame, or both.  As mentioned, from the perspective of the worker, 
+there was no distinction or discontinuity between initial and test tasks.
 
-The experiments and treatments are 
-summarized in Table 1, which also introduces short names which we will use to 
-identify specific experimental treatments and groupings.
-An additional difference between \texttt{exp1} and \texttt{exp2} is that,
-in both treatments for \texttt{task1}, workers were shown the test tasks in
-one of five permutations, which allows us to analyze the dependance of 
-inter-task effects on task proximity, independant of task content.
-We provide a fuller account of the experimental design, and exhibit all the
-task materials used, in the supplementary material.
+We organized the experiments into \textit{treatment pairs}.  Both treatments in a 
+pair involved the same exposure modality, but differed in the
+content of the exposure.  In Table 1, we summarize the various experimental
+treatments, and introduce a naming convention that we use to refer to 
+treatments and treatment pairs.
+In the treatment pairs that studied intertask effects (\textit{task1} and
+\textit{task2}), workers performed 10 image-labeling tasks, with the first 
+five tasks comprising the initial tasks and the last five tasks comprising the
+test tasks.
+
+In the first experiment, the content of the exposures was based on the prime
+concepts \textit{food} and \textit{objects} (throughout, ``objects'' should be
+taken to imply ``non-edible objects'').  So, 
+in \textit{task1:food}, the initial tasks contained images depicting food, 
+while in \textit{task1:obj}, they contained images depicting objects, 
+including kitchen and dining-ware (see Fig~\ref{fig:task}).  Meanwhile, 
+for the exposures in \textit{frame1} we indicating that the study was
+``funded by the laboratory for the visual perception of \{ Food and Ingredients
+$\vert$ Objects and Tools~\}''.  To further strengthen the frame, we 
+introduced another pair of framing treatments, \textit{echo}, with stronger
+wording: ``The purpose of this study is to understand the visual perception
+of \{ Food and Ingredients $\vert$ Objects and Tools~\}'', and required
+the worker to echo the purpose of the study by selecting it among other 
+options in a combo-box input.
+
+Note that food and objects are both relatively well-defined classes of 
+physical entities.  To explore a different conceptual axis, in 
+\textit{exp2} we adopted the prime concepts food and \textit{culture}.
+Compared to food and objects, culture is more abstract, difficult to define, 
+and, rather than comprising a class of physical entities, it encapsulates
+sets of beliefs, values, and practices.  Examples of images from the initial 
+tasks in \textit{task2} are shown in Fig.~\ref{fig:task}, and the full 
+collection of 
+experimental materials is presented in the supplementary material.  We 
+ensured that workers only participated in one treatment of one experiment.
 
@@
 		We use the treatment names shown to refer to specific sections of 
-		the data collected.  For example, \texttt{task2:food} refers to the
+		the data collected.  For example, \textit{task2:food} refers to the
 		treatment in the second experiment which was not exposed to a frame, 
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[scale=0.7]{figs/tasks.pdf}
-	\caption{Examples of slides used for the image labeling tasks.
-A) instructions shown to all workers; B) a framing slide; C) a slide from the initial set for treatment IMG:FOOD; D) a slide from the initial set for treatment IMG:OBJ; E) a slide from the test set shown in all treatments.
-The full set of slides used for all treatments is presented in the supplementary material.}
-	\label{fig:task}
-\end{figure}
-
 \paragraph{The strength of intertask effects.}
@@
 We assessed the strength of intertask and framing effects
-by training a multinomial naive Bayes classifier to predict a worker's 
-treatment (from two possibilities) based on the labels they provided 
-in the test tasks (see Fig.~\ref{fig:theta}).
-We found that in \texttt{task1}, whether a worker had labeled food or non-food 
-objects during initial tasks, had a strong effect on their subsequent labels, 
-biasing them by more than 30\%.  In comparison, the framing effect in \texttt{frame1} did 
-not influence workers' labels enough for the classifier predict their treatment
-with an accuracy significantly better than chance.  The results for 
-\texttt{exp2} show a similar, but even more pronounced trend, with the bias
-induced by intertask effects in \texttt{task2} probably exceeding 40\%.
+by training a multinomial naive Bayes classifier to infer a worker's exposure
+based on the labels provided in the test tasks (see Fig.~\ref{fig:theta}).
+This inference was made over the two possibilities given the treatment pair
+to which the worker had been assigned.
+We found that in \textit{task1}, whether a worker performed food- or 
+object-containing initial tasks, had a strong effect on their subsequent 
+labels, introducing a bias that probably exceeds 30\%.  In comparison, the 
+framing effect in \textit{frame1} did 
+not influence workers' labels enough for the classifier to make predictions 
+with significantly better accuracy than that afforded by chance.  The results 
+for \textit{exp2} show a similar, but even more pronounced trend, with the bias
+induced by intertask effects in \textit{task2} probably exceeding 50\%.
 
-It is worth noting that \texttt{task1} and \texttt{task2} differ in the kind
-of comparison that they make.  In \texttt{task1},
-the prime concepts (``food'' and ``objects'') are, in certain ways, very 
-similar: both are relatively concrete, well-defined concepts, corresponding
-to bounded physical entities that can be directly photographed.
-But in \texttt{task2}, the prime concepts (``food'' and ``culture''), 
-are very different:  culture is far more abstract and difficult to define
-than food, and is not a bounded physical entity.  We will come back to this 
-point, but note 
-here that these pairs of prime concepts both lead to strong intertask effects
-despite exploring very different conceptual dimensions.
-
-As another point of comparison, we included additional framing-like 
-treatments in \texttt{exp1} in which we attempted to increase the effect.
-In the \texttt{echo} treatment pair, we used a more strongly worded frame:
-``The purpose of this study is to understand the visual perception of
-\{ Objects and Tools $\vert$ Food and Ingredients \}'', and then worker was
-asked to reiterate back the purpose of the study, using a combo-box input.
-We expected this to induce a strong effect because it signals that this detail
-is of particular concern to the task requester, and more important than any of 
-the instructions given beforehand.  
-The overall effect of these primes was on par with the intertask 
-effects in \texttt{task1} (see Fig.~\ref{fig:theta}), which shows just how
-powerful intertask effects are.
+We see a comparable effect size in the \textit{echo} treatment pair.
+We expected \textit{echo} to show a very strong effect because, by requiring
+the worker to echo the purported purpose of the task, we signal that it
+is of particular importance, more so than the instructions provided
+beforehand.  The fact that the intertask effects were on par with the framing 
+effects in \textit{echo} shows just how powerful intertask effects can be.
 
@@
 	\caption{
-		Difference in priming observed for various pairs of worker populations.
-		The pairs of populations differed in terms of the initial tasks they
-		performed (bars labeled by \textit{inter-t.}) or in terms of the framing
-		to which they were exposed (bars labeled by \textit{frame}; see table 1 for
-		details about the treatments).  The difference in priming was 
-		measured based on the accuracy of a naive Bayes classifier in 
-		resolving which treatment workers belonged to, as described in the 
-		text.  
+		Lower-bound estimates for the  worst-case bias introduced in image
+		labeling tasks due to worker exposure effects.  The estimate was 
+		based on the performance of a multinomial naive Bayes classifier,
+		trained to infer an HPUs exposure. A) bias induced through various
+		modalities and prime concepts (see Table 1). B) Bias induced in 
+		\textit{task1}, as a function of test task position.  Error bars
+		show the one-tailed 95\% confidence interval.
 	}
@@
 
-\paragraph{Dynamics of intertask effects.} Following the observation that
-intertask effects are strong, it is natural to ask how the effect of an early
-task wanes as the worker proceeds through subsequent ones.  To investigate
-this, in \texttt{task1} workers performed the test tasks in one of five 
-permutations.  This allows us to average the intertask effect accross different
-test tasks when they occupy the same position.  We found that the effect was
-strongest for the first test image, and that a significant effect persisted
-through the five test tasks (see Fig.~\ref{fig:theta}B).  This shows the 
-extent to which the first 
-test task re-primes workers, washing out the effect of initial tasks, but that
-the effect is quite persistent.  In future work, it would be interesting to
-investigate whether the first few tasks have a particularly strong priming
-effect because they ``set the tone'' for the batch.
+\paragraph{Dynamics of intertask effects.} It is natural to expect 
+intertask effects to attenuate as a worker proceeds through test tasks.  
+In \textit{task1}, we permuted the test tasks, allowing us to 
+measure intertask effects as a function of test task position, while factoring
+out the content-dependant differences between test tasks
+(see Fig.~\ref{fig:theta}B). 
+We found intertask effects were most pronounced for the first test image,
+dropping off substantially for the second test task, but maintaining a 
+significant effect through until the 5th test task.  
+This shows that the range of intertask effects extend accross at least 5 
+tasks, and probably substantially more.
+This makes intertask effects of greater concern, but as we will show, it also
+makes intertask effects of greater potential utility.
+In future work, it would be interesting to investigate whether a worker's
+susceptibility to intertask effects varies accross a large batch.  For example,
+It is conceivable that the first few tasks induce especially strong
+or long-lasting effects, in effect ``setting the tone'' for the rest of the batch.
 
-This set-up also allows us to see how much the each test tasks differ in their 
-susceptibility to intertask effects, independant of their position among the
-others.  There does appear to be substantial differences, but relative
-position of the test task is more important (Fig.~\ref{fig:theta}C).
-
-\paragraph{Effects on workers' direction of focus} 
-\begin{figure}
-	\centering
-	\includegraphics[scale=1]{figs/delta_food.pdf}
-	\caption{
-		Difference in priming observed for various pairs of worker populations.
-		The pairs of populations differed in terms of the initial tasks they
-		performed (bars labeled by \textit{inter-t.}) or in terms of the framing
-		to which they were exposed (bars labeled by \textit{frame}; see table 1 for
-		details about the treatments).  The difference in priming was 
-		measured based on the accuracy of a naive Bayes classifier in 
-		resolving which treatment workers belonged to, as described in the 
-		text.  
-	}
-	\label{fig:food}
-\end{figure}
-
-It is reasonable to expect that exposing a worker to tasks containing images
-of food would increase her propensity to provide food-related labels in 
-subsequent tasks.  To test whether this straightforward elicitation occured,
-we used the wordnet corpus to operationalize the notion of food-related 
-labels.  While the coverage of most western food-related words is quite good
-we found that the names of many ethnic foods are missing, so we augmented
-the corpus by crawling the world food section of the recipes website 
-allrecipes.com.  We discuss the validation of our operationalization of 
-food-words in detail in the supplementary material.
-
-For \texttt{task1} and \texttt{frame1} we did find that exposing workers to 
-food-oriented primes led them to increase their provision of food-related 
-labels by about 2-3\% (see Fig.~\ref{fig:food}).  
-In \texttt{echo} this effect was stronger
-\texttt{echo:food} provided about 8\% more food-related words than 
-\texttt{echo:obj}.  Indeed, the \%-increase in food labels observed for
-\texttt{echo} was significantly larger than that for \texttt{taks1}, which is 
-interesting
-given that the overall priming effect observed for \texttt{task1} and 
-\texttt{echo} were on par (c.f. Fig.~\ref{fig:theta}).
-This makes sense, given that \texttt{echo:food} explicitly calls for a focus 
-on food, whereas \texttt{task1:food} probably works by activating certain 
-memories and concepts, with a more complex impact on labels.
-
-In \texttt{exp2} we see a strikingly different effect: workers initially 
-exposed to food-related tasks actually show fewer food-related labels for the
-test tasks.  Recalling the content of the test tasks helps to explain this
-observation.  The test tasks in \texttt{exp2} embed both the prime concepts
-of food and culture, which we accomplished by using images of food having
-very particular and identifiable cultural origins.  The initial tasks in
-\texttt{task2:food} were, by comparison, culturally ambiguous, and the worker
-would presumably be struck by the appearance of strong cultural overtones
-in the test tasks.  On the other hand, due to the effect of negative priming,
-workers in \texttt{task2:cult} might be somewhat desensitized to the cultural
-content in the images, and instead be struck by the sudden appearance of food.
-
-\paragraph{Effects on label vocabulary and specificity.}
+\paragraph{Detailed influences on worker outputs.} 
 \begin{figure}
@@
 	\caption{
-		Difference in priming observed for various pairs of worker populations.
-		The pairs of populations differed in terms of the initial tasks they
-		performed (bars labeled by \textit{inter-t.}) or in terms of the framing
-		to which they were exposed (bars labeled by \textit{frame}; see table 1 for
-		details about the treatments).  The difference in priming was 
-		measured based on the accuracy of a naive Bayes classifier in 
-		resolving which treatment workers belonged to, as described in the 
-		text.  
+		Detailed exposure effects on workers label vocabulary, for various
+		exposure modalities and prime concepts (see Table 1).  A) Change in 
+		the number of food-related labels used. B) Change in the total number 
+		of \textit{unique} food-related labels used. C) Relative specificity
+		of treatment pairs, when considering food-related labels.  For all
+		plots, a positive bar height indicates an increase for the 
+		food-exposed treatment.
 	}
@@
 
-We gain some insight into the induced intertask effects by looking at the
-labels whose frequencies changed the most due to workers' early task exposure. 
-For example, the ``food'' is the most strongly suppressed label among 
-workers exposed to food-related initial tasks.  At first, this may seem 
-unexpected, since, for \texttt{task1:food}, food labels are more common 
-overall.  But ``food'' is the most generic possible food-related label, 
-so this means that \texttt{task1:food} workers are trading their usage of
-``food'' for more specific food references.
+Having observed significant effects from framing and task-exposure,
+we looked in greater detail at the nature of the effects.  For instance,
+does a food-oriented exposure induce workers to provide more food-related
+labels?  And if so, does this explain the classifier's ability to distinguish
+a worker's initial exposure?
 
-The richness and specificity of vocabulary that a worker brings to a 
-characterization task is of great importance in crowdsourcing.  For example,
-in the Galaxy Zoo citizen science project, workers are 
-trained to develop a lexicon of galaxy features such as the smoothness,
-the presence of rings, dustlanes, digital disturbances, etc.  In our set-up,
-the workers lexicon is unconstrained and un-scaffolded, so we can see 
-how initial tasks alter the workers lexicon spantaneously.
+To answer these questions, we used the wordnet corpus, augmented with names of
+ethnic foods learned from the Internet.  Wordnet provides a (roughly)
+hierarchical set of relationships between nouns, called hypernym-hyponym
+relationships.  A hypernym is a generalization, while a hyponym is a 
+specialization.  So, for example, ``bread'' is hypernym to ``rye bread'' 
+and hyponym to ``baked goods''.
 
-To investigate this we used the wordnet corpus, which has embeds a rich
-nested ontology of concepts in the form of hypernym-hyponym noun relationships.
-A hypernym is a generalization, while a hyponym is a specialization; for 
-example ``bread'' is a hypernym of ``pumpernickel''.  Using wordnet, we 
-can represent the labels produced by one group of workers, for example 
-\texttt{task1:food}, and compare it to those labelled by \texttt{taks1:obj}.
-We describe the details of this comparison in the supplementary material,
-but the result is a net tally of all the cases where a word of the first 
-group is more specific than one from the second, less the cases where the 
-word of the second group is more specific.
+Using an augmented hypernym-hyponym structure of wordnet to identify nouns 
+depicting food, we found that, for the experimental pairings in 
+\textit{exp1}, the
+food-exposed treatments did produce a significantly larger fraction of 
+food-related labels (see Fig.~\ref{fig:specificity}A).  While the shift in 
+focus with regard to food does help explain the classifier's ability to 
+infer workers exposure, it still leaves most of this difference unexplained 
+(*).
+Furthermore, such a simple relationship cannot explain the observation for
+\textit{exp2:task2} where we see a significant but reversed effect
+(see Fig.~\ref{fig:specificity}A).
+Given the difference between the food-culture and food-object axes, it should
+not be surprising that the effect of exposure is different.  We must therefore
+be prepared to accomodate multiple, countervailing factors which influencing 
+the bulk number of references to the prime concept (food).  We will come back 
+to this notion momentarily.
 
-By performing this specificity comparison, while restricting our focus to
-food-related words, we can see that workers are in fact induced to be 
-significantly more specific in their usage of food-related words (see Fig.XX).
+To explore these effects further, we looked more closely at which particular
+labels are most suppressed (activated) by a worker's exposure.  Remarkably,
+we found that, for all treatment pairs, ``food'' was always the most 
+suppressed label among 
+the food-exposed workers.  This is surprising, considering 
+that the bulk incidence of food-related labels mostly \textit{increased} among 
+food-exposed workers.  But taken together, the increase in references to food 
+and the decrease in the incidence of ``food'' per se (which is the most generic
+food-reference in the wordnet-based ontology), necessarily implies that
+food-exposed workers have traded ``food'' for more specialized references to 
+food.
 
-in their usage 
-food-related terms in \texttt{task1:food}
-than in \texttt{task1:obj}.
+In a crowdsourcing task, considerable effort must be given to shaping the 
+vocabulary with which a worker engages a task.  To draw an example from the 
+domain of citizen science, in galaxy zoo, workers catalog images of galaxies 
+in terms of smoothness, and the presence of rings, dust lanes, digital 
+disturbances, and so on.  Shaping this vocabulary is crucial to the reliability
+of results.  In galaxy zoo, the interface contstrains and prompts the user
+with this basic vocabulary.  But this would not appear to be sufficient, since
+a set of positive and negative training examples are used, together with
+peer-to-peer and peer-to-expert exchange in discussion areas, presumably to
+refine and homogenize the vocabulary (\#).
 
-one 
-to be more specific, less those found to be less specific, in comparing the 
-words of the one to those of the other.
+In our set-up, where the worker's vocabulary is unconstrained, we can 
+directly observe the effects that frames and initial tasks have on worker 
+vocabulary.  By looking at the number of unique food-related labels that 
+workers produced, we assessed the richness of vocabulary that workers used when
+referring to food (see Fig.~\ref{fig:specificity}B.  We found that the 
+food-exposed workers use a richer vocabulary of 
+food-related words, even in cases like \textit{task2:food}, where they 
+made fewer references to food overall.  
+Interestingly, task-based exposure to food had a stronger enriching effect 
+(for food-vocabulary) than did framing-based exposures. (* explain why vocab 
+diversity is useful.)
 
-citizen science efferts, like galaxy zoo.
+Using the ontology of food induced by wordnet, we were able to directly
+calculate the relative specificity of workers from different treatments.
+To do this, we considered all the labels from one treatment
+(for example \textit{task1:food}) and compared these to all the labels from 
+another (\textit{task1:obj}).  For all possible comparisons, we observed 
+which treatment's label was more specific more often, and normalized this
+quantity as a percentage (we provide greater detail in the supplementary 
+material).
 
-food-related labels.
-to \textit{more specific} food-labels.
+We calculated the relative specificity for all treatment pairs, while 
+restricting focus to 
+food-related labels (see Fig.~\ref{fig:specificity}C).  We found that 
+the food-exposed workers always provided food-references of substantially 
+greater specificity.  Workers that had labeled images containing food 
+were about 12\% more specific than those that labeled images of objects,
+and about 20\% more specific than those that labeled images of cultural 
+scenes.  With respect to the specificity of food references, framing effects 
+were on par with intertask effects.
 
-food-related labels are,
-overall, 
-food-  This is true even when the there are more food-related
-terms overall
+Taken together, the results presented in Fig.~\ref{fig:specificity} can 
+be explained by a combination of priming and a context-dependant appraisal
+of salience resembling \textit{negative} priming.
+Negative priming occurs when a repeated stimulus, which is perceived to be
+non-salient, begins to be ignored.
 
-tasks.  Interestingly, we see that the label ``food'' is always suppressed
-in food-primed treatments, but this effect is particularly strong for the
+We propose that, as a worker from \textit{task1:food} proceeds through the 
+initial tasks, food-related memories and concepts are activated, increasing 
+the likelihood that she uses a variety of food-related labels.  This accounts
+for the overall increases the number of food-related labels, as well as the 
+richness and specificity of her food-related vocabulary.  At the same time,
+the fact that the images contain food at all begins to appear non-salient 
+since due to its constancy, suppressing the most generic labels, such as 
+``food''.  Thus, there is a simultaneous emphasis of the specialized 
+references to the prime concept and de-emphasis of generic references.
 
-changing initial tasks (and frames) by looking at those labels that show
-the greatest frequency change
-primes 
-When manually inspecting the labels of \textit{test-t.2}, one striking 
-observation was that workers that initially labeled images of cultural scenes 
-were more likely to use generic words when labeling the test images, compared 
-to workers that initially labeled images of meals.  For example, 76\% of the 
-workers from \textit{exp2.task.cult} gave the very generic label 
-\texttt{food}, compared to only 16\% of \textit{exp2.task.food} workers 
-(recall that the test tasks for both treatments depicted prepared meals).
-One interpretation is that workers who have already labeled 5 images relating
-to food are more likely to focus on aspects of the images that are different
-from one another, and refrain from so generic a term as \texttt{food}.
+This view accounts for the observation that there are fewer
+food-related references overall in \textit{task2:food} compared to 
+\textit{task2:cult}.  Workers in \textit{task2:food} are primed to use
+specialized food references and negatively primed against using generic
+ones.  Then, when workers encounter images with much more prominent 
+cultural content in the test tasks, they attends to this novel content, 
+decreasing the balance of food references.  
+Meanwhile, workers in 
+\textit{task2:cult} experience novelty from the introduction of food-oriented 
+content, and, attending to it, drive the relative difference in the quantity 
+of food-related labels further negative in in Fig.~\ref{fig:specificity}A.
 
-Based on this observation, we tested the degree of specificity of labels 
-accross all treatments.  We appraoched measuring specificity in two ways.
-Our first method was based on the reasoning that, if a given group of 
-workers uses more specific labels, they will then provide, on the whole,
-a larger set of unique labels for any given image.  For example,
-suppose the workers from \textit{exp2.task.food} who do not use the label 
-\texttt{food} had chosen more specific labels instead.  In being more 
-specific, they must choose a particular detail to describe, from a large 
-number of possibilities, and so are more likely to provide unique labels.
-Indeed
-for all images in the test set, workers from \textit{exp2.task.food} gave
-more unique labels than did those from \textit{exp2.task.cult}, as shown 
-in fig 2B.  Note how the the relative vocabulary sizes follows
-the same trend, as a function of test task, as was observed for the 
-classifier-based detection of general priming differences (c.f. fig X).
+Based on these observations, we submit the following ideas for consideration 
+by the designers of crowdsourced initiatives.
+\begin{enumerate}
+	\item{
+		Training tasks should be preferred over examples, since the immediate
+		active use of information appears to increase its impact.
+	}
+	\item{
+		Training tasks should contain the same distribution of 
+		noise (or ``distracting features''), as the real dataset.
+		Exposing workers to irrelevant features and identifying them as such
+		will help direct focus toward salient features by virtue of
+		negative priming.
+	}
+	\item{
+		\textit{Validation tasks}, for which the correct output is known,
+		are often used as a quality control measure.
+		These should be dually considered as \textit{calibration tasks}, and
+		should be designed to help worker to maintain an optimally primed 
+		state. Feedback, for both correct and incorrect responses, 
+		may further reinforce salient features.
+	}
+	\item{
+		In many applications, such as the detection of pre-ictal 
+		(pre-seizure) EEG traces, workers encounter few positive examples
+		(most traces are not pre-ictal).  In the absence of positive examples,
+		the target concept may degrade or drift.
+		Drawing calibration tasks drawn from the underrepresented class may 
+		help sustain the target concept.
+	}
+	\item{
+		For the most precise classifications, it may be helpful to
+		begin with a coarse classification.  For example, workers could 
+		initially choose from  \texttt{class 0}, \texttt{class 1}, and 
+		\texttt{borderline}.  Following the coarse classification, the 
+		\texttt{borderline} examples could be batched together, allowing 
+		workers to focus on finer distinctions which are only salient for fine 
+		distinctions.
+	}
+\end{enumerate}
 
-Our second approach to measuring relative specificity used the 
-hypernym-hyponym relationships of wordnet.
-We operationalized the relative specificity of two sets of labels $P$ 
-and $Q$ as:
-$$
-	S(P,Q) = \frac{1}{|P \times Q|}\sum_{p \in P} \sum_{q \in Q} 
-		\left(\mathbf{1}_{[p>q]} - \mathbf{1}_{[q>p]}\right),
-$$
-where $\mathbf{1}_{[p>q]}$ evaluates to 1 if $p$ is a hyponym of $q$.
-Using the above equation, we found that, for every images in the 
-test set, the labels attributed by workers in \textit{exp2.task.food} were 
-more specific than those by workers in \textit{exp2.task.cult}.
+These techniques follow logically from our observations, but they are educated 
+guesses.  We leave their direct testing to future work.
 
-Initialy we hypothesized that the similarity of initial and test tasks was
-driving a relative increase in specificity.  While this seems reasonable,
-we also notice a similar effect occuring for \textit{exp1.task} in which
-the test tasks consisted of both food and non-food objects, and the initial
-tasks were either food or non-food objects.  In this case, it is difficult
-to argue that one set of initial tasks is more similar to another.  In fact
-we devise a method to operationalize image similarity, and find that 
-the initial images of \textit{exp1.task.food} are equally similar to the
-test tasks as the initial images of \textit{exp1.task.obj}.  Furthermore,
-we see strong effects on relative specificity for framing as well.
+\paragraph{Conclusion.}
+Our results show that intertask effects are 
+as strong as framing effects, and are stronger when the frame is not echoed.
+Our analysis using wordnet reveals that intertask and framing effects
+act on workers' vocabulary in subtle ways.  Both exposure modalities 
+increased the richness of workers' vocabulary in reference to the prime 
+concept, but more so in the case of task-based exposure.  Both modalities 
+also increased the specialization of workers' vocabulary in reference to the 
+prime concept.
 
-In general, it is of great practical interest to control the level of 
-specificity of qualitative characeterzations.  In many applications the
-task-designer will probably want obtain characterizations that are more
-discriminative.  Thus, when designing microtasks, one should give careful
-consideration to inter-task effects.  Unfortunately, we are not sure
-why certain initial tasks produced increased specificity as opposed to others, 
-and this is a question we intend to pursue in future research.
-
-\paragraph{Conclusions.}
-Our results show that inter-task effects can have a strong influence on how 
-workers label images. In particular, we observed that prior tasks influence 
-the specificity and content of labels. Surprisingly, framing a task by 
-indicating a semantically-loaded funder had much milder effects on worker 
-outputs, generally below the statistical power of our tests.
-
-We therefore caution those designing studies using human computation: even if 
-the requester has eliminated surrounding influences to every practical extent, 
-\textit{the greatest source of bias might lurk in the tasks themselves}. Due 
-consideration should be given to how tasks are bundled together. While our 
-measurements of $\hat{\theta}_\mathrm{NB}$ indicated that inter-task effects 
-persisted even to the fifth test image, the most severe effects arise between 
-consecutive tasks.
-
-Our proposed priming definition yields general purpose measure of priming 
-effects. We used three approaches to detect priming effects: 1) using a Naive 
-Bayes classifier to measure $\hat{\theta}_\mathrm{NB}$, 2) tallying the 
-number of culture- and food-oriented labels, and 3) comparing the relative
-specificity of labels based on an ontology. Of the three, $\theta_\mathrm{NB}$ 
-was the most sensitive.
-
-In one sense, this is not surprising because the Naive Bayes classifier takes 
-into account the frequency of occurrence of all labels encountered during 
-training. But it is remarkable that the method which incorporates neither 
-prior knowledge about the image contents nor label semantics, outperforms 
-those that do. This is a powerful feature because, given the outputs from two 
-sets of workers, one can test whether they have been differently primed 
-without knowing how that priming might manifest.
-
-Our algorithmic definition of priming is phrased in terms of worker outputs 
-rather than psychological phenomena. This provides a connection between the 
-priming effects and their potential to impact decisions made on the basis of 
-worker outputs. In the case of a 1-bit binary decision, $\theta$ describes the 
-worst-case bias introduced by failing to control for priming effects.
-
-Batching similar tasks together appears to yield higher more specific HPU 
-outputs. Our proposed connection between similarity and specificity during 
-image-labeling might be used to tune the specificity of labels. For example, 
-If one seeks very nuanced labeling, our results suggest that the images 
-should first be sorted into batches based on their similarity. This could be 
-accomplished by beginning with a first, coarse labeling of unsorted images, 
-followed by bundling based on the similarity of coarse labels. Then, bundles 
-of similar images could be served for a second round of finer labeling. The 
-sorting and re-labeling could in principle be repeated.
-
-Such a workflow involves serial processing, which points to an interesting 
-possible differ- ence difference between HPUs and CPUs. In general, whenever 
-an aspect of a problem can be parallelized when employing CPUs, one gains 
-efficiency. But here, because of HPU hysteresis, one might gain precision by 
-using HPUs with a more serialized algorithm. Further testing is needed to 
-determine the gain in precision from this approach.
+We recommend that intertask effects be considered when designing crowdsourced
+studies.  Despite efforts to eliminate biases from the context of tasks,
+the greatest source of biases may lurk in the tasks themselves.
+At the same time, their positive effects on workers' vocabulary suggests 
+that, when properly controlled, intertask effects may be
+used to optimize HPU performance.  Based on the enriching effects we observed
+for worker vocabulary, intertask effects might be leveraged to achieve 
+expert-level annotation in a wider variety of applications.
 
@@
 \end{document}
-
-%Next we observed how inter-task effects on label composition (i.e. food- vs 
-%culture-oriented labels) evolve as workers proceed through test images. We 
-%define the excess cultural orientation as the number of culture-oriented 
-%labels minus the number of food oriented ones. To meaning- fully compare the 
-%excess cultural orientation between test images, we must, however, account 
-%for the fact that some images inherently carry more cultural content than 
-%others. In keeping with our notion of priming difference, we calculate the 
-%excess cultural content for both CULTimg and
-%
-%AMBG, and take their difference to be the relative excess cultural content, 
-%$\Delta_{cult}$. Formally,
-%
-%		*** Formula for delta cult\ldots
-%
-%where $N^(i)_{w,cult}$ stands for the number of culture-oriented labels 
-%attributed by worker w to image i, while $N^(i)_{w,food}$ similarly counts
-%food-oriented labels, and $N$ is the total number of labels in a treatment.
-%
-%We found $\Delta_{cult}$ was largest for the first test image, but dropped off 
-%rapidly, 
-%remaining positive but not to a statistically significant extent (see Fig. 3B).
-%This is similar to the behavior of $\hat{\theta}_\mathrm{NB}$, however, 
-%because the statistical significance of $\Delta_{cult}$ dropped more quickly, 
-%$\hat{\theta}_\mathrm{NB}$ appears to be a more sensitive measure of 
-%inter-task effects.

### 2014-11-19 src/new_plots.py

@@ -296,10 +296,13 @@ def plot_theta(
 	data = json.loads(open(os.path.join(DATA_DIR, read_fname)).read())
 
 	# make a figure with two subplots
-	figWidth = 14.78 / 2.54 	# conversion from PNAS spec in cm to inches
-	figHeight = 2/5.*figWidth	# a reasonable aspect ratio
+	figWidth = 10.0 / 2.54 	# conversion from PNAS spec in cm to inches
+	figHeight = 3/5.*figWidth	# a reasonable aspect ratio
+	#figWidth = 14.78 / 2.54 	# conversion from PNAS spec in cm to inches
+	#figHeight = 2/5.*figWidth	# a reasonable aspect ratio
 	fig = plt.figure(figsize=(figWidth, figHeight))
-	gs = gridspec.GridSpec(1, 3, width_ratios=(3,5,5))
+	gs = gridspec.GridSpec(1, 2)
+	#gs = gridspec.GridSpec(1, 3, width_ratios=(5,5,5))
 
 	width = 0.75
 
@@ -310,14 +313,15 @@ def plot_theta(
 	# the img_food_obj test was tried under multiple permutations -- take avg
 	this_data['exp2.task'] = np.mean(this_data['exp2.task'])
 
-	test_names = ['exp2.task', 'exp2.frame', 'exp2.*']
+	test_names = ['exp2.task', 'exp2.frame', 'exp2.*', 'exp1.task', 
+			'exp1.frame']
 	accuracies = [this_data[tn] for tn in test_names]
 
 	# convert accuracy to priming difference (which is what we want to plot)
 	Y_aggregate = [2*a-1 for a in accuracies]
 	err_low = [
 		2*binomial_lower_confidence_p(n, int(n*a)) - 1
-		for a,n in zip(accuracies,[595,119,119])
+		for a,n in zip(accuracies,[595,119,119,119,119])
 	]
 	err_low = [y-y_err for y, y_err in zip(Y_aggregate, err_low)]
 	err_high = [0 for e in err_low]
@@ -335,9 +339,9 @@ def plot_theta(
 	#singificance_line = ax1.plot(
 	#		xlims, [theta_star, theta_star], color='0.55', linestyle=':')
 
-	ax1.set_ylabel(r'$\hat{\theta}_\mathrm{NB}$', size=12)
[…]

### 2014-11-19 docs/publications/2014.09_SCIENCE/new_man.tex
proof read manuscript and improve theta plot

@@
 alone.  These platforms support near-real-time task completion, mimicking a
-compute server, and fundamentally shift the role of the human from consumer to 
+compute server, and shift the role of the human from consumer to 
 producer of computing resources.  To realize its full
 potential, we must understand how human computation differs from machine 
-computation, and address the biases known to be inherent in 
+computation, and address the biases inherent in 
 human cognition.  The effects of various task-design variables on worker
@@
 that these \textit{intertask effects} can be harnessed to improve the quality 
-of responses, and thereby help to achieve expert-level judgments in citizen 
-science and other crowdsourcing initiatives. 
+of responses, and might thereby help to achieve expert-level judgments in 
+citizen science and other crowdsourcing initiatives. 
 As an ancillary contribution, we demonstrate the use of machine learning 
@@
 in terms of worker demography (\#).  But systematic cognitive biases also 
-play a role (\#), a dimension of variability we investigate here.   
-So far, investigation has explored such design factors as the level of 
+play a role (\#).   
+So far, investigation has explored how worker performance is influenced by
+such design factors as the level of 
 pay \cite{kazai2013analysis}, training \cite{le2010ensuring}, pre-screening of 
@@
 effects \cite{Gass1999549,sohn2001task}.  Thus, a worker's response during
-one task may depend in part on previous ones.  Such \textit{intertask} effects
+one task may depend on previous ones.  Such \textit{intertask} effects
 would amount to a kind of \textit{hysteresis}, meaning that HPU outputs are not
@@
 
-Here we describe a series of experiments using the Amazon Mechanical
-Turk (MTurk) microtask platform in which we studied intertask effects
+Here we describe a series of experiments, using the Amazon Mechanical
+Turk (MTurk) microtask platform, in which we studied intertask effects
 for image-labeling tasks.  Image-labeling tasks are among the most 
@@
 \textit{food} and \textit{culture}.  The test tasks for the experiments used 
-images that combined both prime concepts. Any given worker performed in only 
-one experiment, and was randomly assigned initial tasks based on one of the 
+images that combined both prime concepts used in the initial tasks. Workers 
+participated in only one treatment of one experiment, and were randomly 
+assigned initial tasks based on one of the 
 prime concepts.  From the perspective of the worker, we made no distinction 
@@
 We found that intertask effects were stronger than framing, unless the worker
-was required to echo the frame, in which case both exposures were on par.  
+was required to echo the frame, in which case the effects of both exposures were on par.  
 Our results demonstrate that initial tasks can change 
-workers' focus in later tasks.  We also found that intertask effects 
-significantly altered the level of specificity, and the diversity of 
-vocabulary that workers used, and did so in ways that differed from framing.
+workers' focus in later tasks.  Using the wordnet corpus, we analyzed 
+the effects on the vocabulary used by workers when 
+labeling test tasks. 
+Exposure to both framing and initial tasks significantly altered the 
+diversity of vocabulary that workers used when refering to the prime concept,
+as well as the degree to which workers used specialized (rather than generic) 
+words.
+
 Contrary to our initial expectations, our findings suggest that the HPU 
 programmer can leverage intertask effects.  By carefully designing workflows,
-worker focus, specificity, and expressivity can be tuned.  Our 
+it is possible to tune worker focus, specificity, and expressivity.  Our 
 findings carry two lessons for the task designer: intertask
 effects can severely bias HPU output if uncontrolled, but if properly 
-controlled, intertask effects might be optimized, which may be of significant 
-utility in achieving expert-level output.
+controlled, intertask effects might be of significant utility in achieving 
+expert-level output.
 
@@
 (hereafter collectively \textit{exposure effects}).  
-It might be tempting to invoke the concept of a ``neutral frame of mind'' 
-which would serve as a baseline for drawing comparisons.  But such a concept 
-seems both difficult to define, and unlikely to arise.
-Therefore, we instead always consider the effect of one exposure 
-\textit{relative} to another.  Thus, our experiments consist of 
-pairs of treatments between which we can make meaningful comparisons.
+In trying to establish a mesure of exposure effects, it might be tempting to 
+invoke the notion of a ``neutral frame of mind'' to serve as a baseline. 
+But such a concept seems both difficult to define, and unlikely to arise.
+Therefore, we always consider the effect of one exposure 
+\textit{relative} to another.  We organized our experiments 
+into pairs of treatments, between which it is possible to make meaningful 
+comparisons.
 
@@
 
-For this reason, we develop a measure in which we train classifier algorithms 
+We developed a more stringent measure in which we train classifier algorithms 
 to infer the exposure of an HPU from its outputs.
@@
 	\caption{
-		Examples of images used in labeling tasks. Images from initial
-		tasks: A) \textit{task1:food}, B) 
+		Examples of images used in labeling tasks. (The italicized treatment 
+		names that follow are defined in Table \ref{table:treatments}.) Images 
+		from initial tasks: A) \textit{task1:food}, B) 
 		\textit{task1:obj}, D) \textit{task2:food}, 
@@
 tasks, the output of which was our main dependent variable.  Before performing
-the test tasks, workers were subjected to an exposure, via one of 
-two \textit{modalities}: either they completed a set of initial tasks, or 
+the test tasks, workers were subjected to an exposure, via two 
+\textit{modalities}: either they completed a set of initial tasks, or 
 were exposed to a frame, or both.  As mentioned, from the perspective of the worker, 
@@
 physical entities.  To explore a different conceptual axis, in 
-\textit{exp2} we adopted the prime concepts food and \textit{culture}.
-Compared to food and objects, culture is more abstract, difficult to define, 
-and, rather than comprising a class of physical entities, it encapsulates
+\textit{exp2} we adopted the prime concepts \textit{food} and \textit{culture}.
+Compared to food and objects, culture is more abstract, and, rather than 
+comprising a class of physical entities, it encapsulates
 sets of beliefs, values, and practices.  Examples of images from the initial 
@@
 experimental materials is presented in the supplementary material.  We 
-ensured that workers only participated in one treatment of one experiment.
+ensured that all workers only participated in one treatment of one experiment.
 
@@
 		\hline \noalign{\smallskip}
-		\multicolumn{3}{c}{\textbf{Treatment name}} & \parbox[c]{1.6cm}{\centering \textbf{Framing\\ Prime}} & \parbox[c]{1.7cm}{\centering \textbf{Initial\\ image set}}	\\
+		\multicolumn{3}{c}{\textbf{Treatment name}} & \parbox[c]{1.6cm}{\centering \textbf{Frame}} & \parbox[c]{1.3cm}{\centering \textbf{Initial\\ tasks}}	\\
 
@@
 
-		\multirow{6}{*}{ \parbox[c]{1cm}{ \phantom{XXX} exp1}} 
+		\multirow{6}{*}{ \parbox[c]{0.7cm}{ \phantom{XXX} exp1}} 
 			& \multirow{2}{*}{task1} & food & none & food\\
@@
 	}}
-	\label{table:1}
+	\label{table:treatments}
 \end{table}
@@
 based on the labels provided in the test tasks (see Fig.~\ref{fig:theta}).
-This inference was made over the two possibilities given the treatment pair
-to which the worker had been assigned.
+This inference was made over the two possibilities for a given treatment pair.
 We found that in \textit{task1}, whether a worker performed food- or 
-object-containing initial tasks, had a strong effect on their subsequent 
+object-containing initial tasks had a strong effect on their subsequent 
 labels, introducing a bias that probably exceeds 30\%.  In comparison, the 
@@
 the worker to echo the purported purpose of the task, we signal that it
-is of particular importance, more so than the instructions provided
-beforehand.  The fact that the intertask effects were on par with the framing 
+is of particular importance.  The fact that the intertask effects were on par with the framing 
 effects in \textit{echo} shows just how powerful intertask effects can be.
@@
 		based on the performance of a multinomial naive Bayes classifier,
-		trained to infer an HPUs exposure. A) bias induced through various
+		trained to infer HPU exposures. A) Bias induced through various
 		modalities and prime concepts (see Table 1). B) Bias induced in 
@@
 \paragraph{Dynamics of intertask effects.} It is natural to expect 
-intertask effects to attenuate as a worker proceeds through test tasks.  
+intertask effects to attenuate as a worker proceeds through the test tasks.  
 In \textit{task1}, we permuted the test tasks, allowing us to 
-measure intertask effects as a function of test task position, while factoring
-out the content-dependant differences between test tasks
+measure intertask effects as a function of task position, while factoring
+out the content-dependant differences between tasks
 (see Fig.~\ref{fig:theta}B). 
-We found intertask effects were most pronounced for the first test image,
-dropping off substantially for the second test task, but maintaining a 
-significant effect through until the 5th test task.  
-This shows that the range of intertask effects extend accross at least 5 
+We found intertask effects were most pronounced for the first test task,
+dropping off substantially for the second, but maintaining a 
+significant effect through until the fifth test task.  
+This shows that the range of intertask effects extends accross at least five 
 tasks, and probably substantially more.
@@
 	\caption{
-		Detailed exposure effects on workers label vocabulary, for various
+		Detailed exposure effects on workers' label vocabulary, for various
 		exposure modalities and prime concepts (see Table 1).  A) Change in 
@@
 		plots, a positive bar height indicates an increase for the 
-		food-exposed treatment.
+		food-exposed treatment for the pair indicated on the abscissa.
 	}
@@
 
-Using an augmented hypernym-hyponym structure of wordnet to identify nouns 
+Using the augmented hypernym-hyponym structure of wordnet to identify nouns 
 depicting food, we found that, for the experimental pairings in 
@@
 focus with regard to food does help explain the classifier's ability to 
-infer workers exposure, it still leaves most of this difference unexplained 
+infer worker exposures, it is insufficient to explain the observed performance
 (*).
-Furthermore, such a simple relationship cannot explain the observation for
-\textit{exp2:task2} where we see a significant but reversed effect
-(see Fig.~\ref{fig:specificity}A).
-Given the difference between the food-culture and food-object axes, it should
-not be surprising that the effect of exposure is different.  We must therefore
-be prepared to accomodate multiple, countervailing factors which influencing 
-the bulk number of references to the prime concept (food).  We will come back 
-to this notion momentarily.
+Furthermore, in \textit{exp2:task2} we see a significant but reversed effect
+(see Fig.~\ref{fig:specificity}A), which suggests a more complicated 
+relationship between exposure and label usage.
+Given the difference between the food-culture and food-object conceptual axes, 
+it should perhaps not be surprising that the effect of initial task exposure 
+is different.  It would appear that we must be prepared to accomodate multiple 
+countervailing factors influencing the number of references to the prime 
+concept (food).  We will come back to this point momentarily.
 
 To explore these effects further, we looked more closely at which particular
-labels are most suppressed (activated) by a worker's exposure.  Remarkably,
+labels were most suppressed (activated) by a worker's exposure.  Remarkably,
 we found that, for all treatment pairs, ``food'' was always the most 
@@
 the food-exposed workers.  This is surprising, considering 
-that the bulk incidence of food-related labels mostly \textit{increased} among 
-food-exposed workers.  But taken together, the increase in references to food 
+that the overall incidence of food-related labels mostly \textit{increased} 
+among food-exposed workers.  But taken together, the increase in references to 
+food 
 and the decrease in the incidence of ``food'' per se (which is the most generic
 food-reference in the wordnet-based ontology), necessarily implies that
-food-exposed workers have traded ``food'' for more specialized references to 
-food.
+food-exposed workers have opted for more specialized references in place of 
+``food''.
 
@@
 domain of citizen science, in galaxy zoo, workers catalog images of galaxies 
-in terms of smoothness, and the presence of rings, dust lanes, digital 
-disturbances, and so on.  Shaping this vocabulary is crucial to the reliability
-of results.  In galaxy zoo, the interface contstrains and prompts the user
-with this basic vocabulary.  But this would not appear to be sufficient, since
+in terms of \textit{smoothness}, and the presence of \textit{rings}, 
+\textit{dust lanes}, \textit{digital disturbances}, and so on.  Shaping this 
+vocabulary is crucial to the reliability of results.  The interface of
+galaxy zoo helps by contstraining and prompting the user with this basic 
+vocabulary.  But this would not appear to be sufficient, since
 a set of positive and negative training examples are used, together with
 peer-to-peer and peer-to-expert exchange in discussion areas, presumably to
-refine and homogenize the vocabulary (\#).
+further refine and standardize the vocabulary (\#).
 
@@
 workers produced, we assessed the richness of vocabulary that workers used when
-referring to food (see Fig.~\ref{fig:specificity}B.  We found that the 
+referring to food (see Fig.~\ref{fig:specificity}B).  We found that the 
 food-exposed workers use a richer vocabulary of 
@@
 Interestingly, task-based exposure to food had a stronger enriching effect 
-(for food-vocabulary) than did framing-based exposures. (* explain why vocab 
+ than did framing-based exposures. (* explain why vocab 
 diversity is useful.)
 
-Using the ontology of food induced by wordnet, we were able to directly
-calculate the relative specificity of workers from different treatments.
+Using the ontology of food induced by wordnet, along with foods learned from
+the Internet, we were able to directly calculate the relative specificity of 
+workers from different treatments.
 To do this, we considered all the labels from one treatment
@@
 Taken together, the results presented in Fig.~\ref{fig:specificity} can 
-be explained by a combination of priming and a context-dependant appraisal
-of salience resembling \textit{negative} priming.
+be explained by a combination of priming and  \textit{negative} priming.
 Negative priming occurs when a repeated stimulus, which is perceived to be
-non-salient, begins to be ignored.
+non-salient, begins to be ignored (\#).
 
@@
 richness and specificity of her food-related vocabulary.  At the same time,
-the fact that the images contain food at all begins to appear non-salient 
-since due to its constancy, suppressing the most generic labels, such as 
-``food''.  Thus, there is a simultaneous emphasis of the specialized 
+since all images up to that point contained food, \textit{whether or not}
+an image contains food begins to appear non-salient, suppressing the most 
+generic references, such as ``food''.  Thus, there is a simultaneous emphasis of the specialized 
 references to the prime concept and de-emphasis of generic references.
 
-This view accounts for the observation that there are fewer
+This view can account for the observation that there are fewer
 food-related references overall in \textit{task2:food} compared to 
-\textit{task2:cult}.  Workers in \textit{task2:food} are primed to use
+\textit{task2:cult}.  Workers in \textit{task2:food}, like those in 
+\textit{task1:food}, are primed to use
 specialized food references and negatively primed against using generic
-ones.  Then, when workers encounter images with much more prominent 
-cultural content in the test tasks, they attends to this novel content, 
-decreasing the balance of food references.  
-Meanwhile, workers in 
-\textit{task2:cult} experience novelty from the introduction of food-oriented 
-content, and, attending to it, drive the relative difference in the quantity 
-of food-related labels further negative in in Fig.~\ref{fig:specificity}A.
+ones.  Then, when these workers encounter the test tasks, with images 
+containing more prominent cultural content, they attend to this novel content, 
+decreasing their balance of food references.  
+Meanwhile, workers in \textit{task2:cult}, having seen only cultural scenes,
+experience novelty from the appearance of food-oriented content in the test 
+tasks, and, attending to it, drive the relative difference in the quantity of 
+food-related labels further toward the negative in in 
+Fig.~\ref{fig:specificity}A.
 
@@
 		noise (or ``distracting features''), as the real dataset.
-		Exposing workers to irrelevant features and identifying them as such
-		will help direct focus toward salient features by virtue of
+		Exposing workers to irrelevant features, and identifying them as such,
+		will free up worker attention for salient features, by virtue of
 		negative priming.
@@
 		These should be dually considered as \textit{calibration tasks}, and
-		should be designed to help worker to maintain an optimally primed 
+		should be designed to help workers maintain an optimally primed 
 		state. Feedback, for both correct and incorrect responses, 
@@
 		(pre-seizure) EEG traces, workers encounter few positive examples
-		(most traces are not pre-ictal).  In the absence of positive examples,
-		the target concept may degrade or drift.
-		Drawing calibration tasks drawn from the underrepresented class may 
+		(most traces are not pre-ictal)(\#).  In the absence of positive 
+		examples, the target concept may degrade or drift.
+		Drawing calibration tasks from the underrepresented class may 
 		help sustain the target concept.
@@
 		begin with a coarse classification.  For example, workers could 
-		initially choose from  \texttt{class 0}, \texttt{class 1}, and 
+		initially choose from  \texttt{class0}, \texttt{class1}, and 
 		\texttt{borderline}.  Following the coarse classification, the 
 		\texttt{borderline} examples could be batched together, allowing 
-		workers to focus on finer distinctions which are only salient for fine 
+		workers to focus on features that are only salient for such fine 
 		distinctions.
@@
 
-These techniques follow logically from our observations, but they are educated 
-guesses.  We leave their direct testing to future work.
+These recommendations follow logically from our observations, but they are 
+educated guesses.  We leave their direct testing to future work.
 
@@
 the greatest source of biases may lurk in the tasks themselves.
-At the same time, their positive effects on workers' vocabulary suggests 
+At the same time, their positive effects on workers' vocabulary suggest 
 that, when properly controlled, intertask effects may be

### 2014-11-19 src/new_plots.py

@@ -341,12 +341,13 @@ def plot_theta(
 
 	ax1.set_ylabel(r'$D^-_\mathrm{L1}$', size=12)
 
-	xlabels = [r'task1', r'frame1', r'echo', 'task2', 'frame2']
+	xlabels = [r'$task1$', r'$frame1$', r'$echo$', '$task2$', '$frame2$']
 
-	ax1.set_xticks(map(lambda x: x + width/2., X))
+	eps = 0.2
+	ax1.set_xticks(map(lambda x: x + width/2. + eps, X))
+	ax1.tick_params(axis='x', colors='0.25')
 	ax1.set_xticklabels(xlabels, rotation=45, size=12,
-		horizontalalignment='right')
-
+		horizontalalignment='right', color='k')
 
 	# Plot the by_pos data series
 	ax2 = plt.subplot(gs[1], sharey=ax1)
@@ -377,11 +378,13 @@ def plot_theta(
 	xlims = (-padding, len(X) - 1 + width + padding)
 	plt.xlim(xlims)
 
-	xlabels = ['1st', '2nd', '3rd', '4th', '5th']
+	xlabels = ['1', '2', '3', '4', '5']
 
 	ax2.set_xticks(map(lambda x: x + width/2., X))
-	ax2.set_xticklabels(xlabels, rotation=45, size=12,
-		horizontalalignment='right')
+	ax2.tick_params(axis='x', colors='0.25')
+	ax2.set_xticklabels(xlabels, rotation=0, size=12,
+		horizontalalignment='center', color='k')
+	ax2.set_xlabel(r'test task position', size=12)
 
 #	# Plot the by_img data series
 #	ax3 = plt.subplot(gs[2], sharey=ax1)

### 2014-11-19 docs/publications/2014.09_SCIENCE/man.tex
spell check

--- 2014-10-27 docs/publications/2014.09_SCIENCE/man.tex
@@
 
-People still outperform sophisticated artificial 
-intelligince systems in many tasks requiring general knowledge, 
-qualitative judgment, and visuo-spatial reasoning. Recently, microtask 
-platforms enable the programmer to import human judgment directly into 
-algorithms: programs can post tasks, to be completed by users of such 
-platforms in near real-time.
-Some computer scientists consider microtask platforms to be a fundamentally
-new computing architecture, but psychological effects can introduce systematic
-bias. 
-Here we investigate the effects that earlier tasks have on the results of 
-subsequent ones, which we call \textit{inter-task effects}.
-In a canonical image labeling task, we found that inter-task effects are
-very strong---stronger than overtly framing tasks in terms of 
-particular research goals.  However, in some cases, inter-task effects can
-be leveraged to elicit more nuanced responses.
-To study inter-task effects we introduce a framework that characterizes HPU 
-bias in an application-independant way, based on its potential to alter an 
-algorithm's path of execution.  Our findings suggest that careful consideration
-should be given to inter-task effects when designing crowdsourcing studies.
-
-%microtask worker performs a series of tasks.  We find that early tasks can
-%have a strong effect on later tasks, and that these effects can be stronger
-%than those brought about by framing.
-%
-%course of human computation algorithms.
-%application-independant quantity that measures the
-%severity of priming.  We apply this framework to measure 
-%
-%in many
-%tasks, especially ones requiring general knowledge about the world, qualitative
-%judgment, and visuo-spatial reasoning.  Recently, microtask web platforms have 
-%emerged. One can upload a batch of tasks to be completed by users who are paid 
-%for their efforts.
-%Though simple on the surface, these platforms dramatically enlarge the
-%programmers toolkit: in effect they allow the programmer to import human 
-%judgment into algorithms.  Some computer scientists consider
-%such platforms to be a new computing architecture.  But people are very 
-%different from electronic processors.  For example, context affects how a 
-%person will respond to a prompt, and this complicates the formal treatment of 
-%human computation.  To approach this issue, we introduce a framework 
-%that quantifies the severity of priming in an application-independant way.
-%We apply this technique to reveal an unforseen source of bias: the bias 
-%induced by one task on another.  Surprisingly we find that 
-%\textit{inter-task effects} introduce more bias than \textit{framing}, which
-%has received more attention.
-%
-%more well-known 
-%\textit{framing}, a more well-studied form of priming.
-%
-%Microtask platforms offer a fast, flexble, and inexpensive source of labour for
-%clerical tasks \cite{Finnerty2013, chandler2013breaking, Berinsky2012351} and 
-%recently have been adopted by researchers to augment datasets and solicit 
-%participants \cite{paolacci2010running, Berinsky2012351, chandler2013breaking}.
-%Computer scientists have described such platforms as a new computing 
-%architecture, and seek to characterize “human co-processing units” (HPUs) in 
-%analogy to CPUs and GPUs \cite{5543192}. However, it is known that people are 
-%susceptible to 
-%priming effects\cite{No2007,Swaab200299,Gopher2000308,sohn2001task,Ghuman17062008,BJOP1796,BJOP1826,Gass1999549}, which stands to complicate the HPU 
-%perspective.  Here, we introduce a framework to recast this psychological 
-%phenomenon as a kind of computational hysteresis. 
-%We apply this framework to study \textit{inter-task effects} that arise when 
-%microtask 
-%workers perform a sequence of tasks. Surprisingly, earlier tasks can have a 
-%very strong influence on workers during later tasks---stronger than overtly
-%framing the tasks as serving different research goals.   
-%This result has major implications for the design of crowdsourcing initiatives.
-%The framework we introduce provides a general measure of priming severity, 
-%and, in combination with machine learning tools, enables measurement without
-%knowing ahead of time how priming will affect output.
+Microtask platforms combine the efforts of large numbers 
+of people to perform tasks that are difficult to automate with computers 
+alone.  These platforms support near-real-time task completion, mimicking a
+compute server, and shift the role of the human from consumer to 
+producer of computing resources.  To realize its full
+potential, we must understand how human computation differs from machine 
+computation, and address the biases inherent in 
+human cognition.  The effects of various task-design variables on worker
+performance have been investigated, but there has been little 
+investigation into how consecutive tasks influence one another. Here we show 
+that the responses in later tasks are strongly influenced by the content of 
+earlier ones, an effect that is as strong or stronger than the effect of 
+framing.  Our findings are not solely cautionary; we find
+that these \textit{intertask effects} can be harnessed to improve the quality 
+of responses, and might thereby help to achieve expert-level judgments in 
+citizen science and other crowdsourcing initiatives. 
+As an ancillary contribution, we demonstrate the use of machine learning 
+algorithms measure exposure-induced human bias, in terms of its ability to 
+influence human computations. 
 \end{sciabstract}
@@
 or handwritten notes \cite{Berinsky2012351,Finnerty2013}, and judging the 
-relevancy of search results \cite{le2010ensuring,grady2010crowdsourcing,alonso2009can,kazai2013analysis}
+relevancy of search results 
+\cite{le2010ensuring,grady2010crowdsourcing,alonso2009can,kazai2013analysis}.
+Originally used to distribute clerical work, these platforms 
+increasingly serve as a means to engage experimental participants in a 
+research 
+setting \cite{paolacci2010running,Berinsky2012351,snow2008cheap,alonso2009can}.
+This trend has seeded considerable interest in characterizing the parameters
+of task design, and validating the microtask platform methodology (\#).
 
-These platforms make it possible to seemlessly integrate human and 
-machine computation.  Researchers coined the term HPU 
+Computer scientists view microtask platforms in the context of general
+computation.  In this regard, the platforms enable a tight integration of 
+human and machine computation.  Researchers coined the term HPU 
 (Human co-Processing Unit) in analogy to CPUs and GPUs \cite{5543192}.  
-Attempts have been made to establish an HPU instruction set.  For example,
-the X library provides function calls such as 
-\texttt{X.vote()}, and \texttt{X.map()}
+Ongoing research pursues the establishment of an HPU instruction set
+including basic operators like \texttt{vote}, \texttt{subdivide}, \texttt{map},
+\texttt{reduce}, \texttt{sentiment}, and \texttt{image\_tag} (\#).  Libraries 
+are being developed to give the programmer more seamless access to HPU 
+resources 
  \cite{little2010turkit,minder2011crowdlang,minder2012crowdlang,kittur2011crowdforge}.  
+As with other architectures, the HPU architecture makes entirely new classes 
+of problems tractable for the programmer (\#).
 
-Of course, there are obvious differences between HPUs and their silicone
-counterparts.  When facing the same task, people do not generally
-respond in the same way.  Common sense would dictate that a certain amount
-of variability in responses made by people is inescapable.  But an important 
-part of the variation is bound to be systematic, due to psychological or 
-demographic factors.
-
-Here, we highlight an important source of bias with
-serious implications for any crowdsourcing initiative. 
-It is known that people are susceptible to priming effects 
-\cite{BJOP1796,No2007,beller1971priming}, and, in particular, task-repetition 
-effects \cite{Gass1999549,sohn2001task}.  Thus, a worker's response during
-one task may depend in part on previous ones.  Such \textit{inter-task} effects
-would amount to a kind of \textit{hysteresis}, meaning that HPU outputs are not
-only a function of the current input, but also of the history of inputs.
-
-There has been considerable investigation into the factors that affect the 
-output from microtask work.  These include such factors as the 
-level of 
+But the ability to program with high-level human instructions comes with a 
+cost: HPU output is inherently noisy.  Part of this noise can be explained
+in terms of worker demography (\#).  But systematic cognitive biases also 
+play a role (\#).   
+So far, investigation has explored how worker performance is influenced by
+such design factors as the level of 
 pay \cite{kazai2013analysis}, training \cite{le2010ensuring}, pre-screening of 
@@
 \cite{Kinnaird2012281}, the purpose of tasks 
-\cite{chandler2013breaking}, or using an alternative problem discription
+\cite{chandler2013breaking}, or using alternate problem descriptions
 \cite{thibodeau2013natural}.  To our knowledge, no study has investigated 
-inter-task effects on microtask platforms.
+the influences that consecutive microtasks exert on one another.
 
-We make two contributions towards understanding inter-task effects,
-and systematic bias in HPUs in general.  First, we present a framework for 
-quantifying bias in HPU outputs in terms of their potential impact 
-algorithms.  This yields an approach for measuring the severity of bias 
-that removes the need to understand the underlying psychological or 
-demographic factors at play.  Second, we apply our framework to measure the
-severity of inter-task effects on a canonical microtask: image labeling.
+It is known that people are susceptible to priming effects 
+\cite{BJOP1796,No2007,beller1971priming}, and, in particular, task-repetition 
+effects \cite{Gass1999549,sohn2001task}.  Thus, a worker's response during
+one task may depend on previous ones.  Such \textit{intertask} effects
+would amount to a kind of \textit{hysteresis}, meaning that HPU outputs are not
+only a function of the current input, but also of the history of inputs, with
+important implications for the design of crowdsourcing initiatives.
 
-Using the  Amazon Mechanical Turk (Mturk) platform, we solicited workers to 
-perform a series of image-labeling tasks.  We chose image labeling because it 
-is one of the most common kinds of microtasks
+Here we describe a series of experiments, using the Amazon Mechanical
+Turk (MTurk) microtask platform, in which we studied intertask effects
+for image-labeling tasks.  Image-labeling tasks are among the most 
+common kinds of microtasks
 \cite{chandler2013breaking,Berinsky2012351,Finnerty2013,paolacci2010running}, 
 and it seems likely that this will remain the case in the long term because
-of applications in computer vision research \cite{5543192}.
-%In these tasks, workers labeled images featuring iconic cultural scenes,
-%food, table-settings, and various utensils and cookware. 
-We divided the tasks into an \textit{initial} and \textit{test} set, 
-but, crucially, there was no distinction between these sets from the
-perspective of the worker.  We varied the initial tasks, while 
-keeping the test set the same, to analyze the effect of initial tasks on 
-the labels provided during the test tasks.
+they provide a source of ground truth in computer vision research 
+\cite{5543192}.  
+During the experiments, workers were presented with a series of images (one at
+a time), and had to provide five descriptive words (\textit{labels}) for each.
+We varied first five images (hereafter the \textit{initial tasks})
+and observed the effect this had on the workers' labels for the last five
+(\textit{test tasks}).
 
-As a point of comparison, we included treatments in which we induce 
+The initial tasks were chosen to embed a certain \textit{prime concept}.
+In our first experiment, our prime concepts were \textit{food} and (non-food) 
+\textit{objects}.  In our second experiment, the prime concepts were 
+\textit{food} and \textit{culture}.  The test tasks for the experiments used 
+images that combined both prime concepts used in the initial tasks. Workers 
+participated in only one treatment of one experiment, and were randomly 
+assigned initial tasks based on one of the 
+prime concepts.  From the perspective of the worker, we made no distinction 
+between the initial tasks and test tasks.
+
+As a point of comparison, we included treatments in which we induced
 \textit{framing}.
-Before the workers labeled images, we indicated that the work 
-was funded by a research lab with a particular area of interest, to see the 
-influence this has on the workers’ subsequent labels. 
-Surprisingly, inter-task effects were stronger than framing, in some cases 
-about twice as strong. 
-Our results demonstrate that initial tasks can change workers' focus in later 
-tasks.  We also found that inter-task effects altered the level of specificity 
-of worker's labels.  Our findings suggest that careful consideration should be 
-given to the bundling of tasks when designing a study using a microtask 
-platform.
+In the framing treatments, before workers begin the tasks, we told them that 
+the purpose of study was to understand the visual perception of 
+``food and ingredients'' in one case, or the 
+perception of ``objects and tools'' in another.  We varied the language of 
+the framing text (hereafter simply the \textit{frame}), and experimented with 
+requiring the worker to echo the frame using a combo-box input.
 
-\paragraph*{Computational hysteresis.}
-Before describing our experiments, we dedicate some space to discussing
-how we characterize and measure priming in HPU outputs.  Since HPU outputs are
-stochastic, determining the effect of priming on an HPU population
-amounts to determining the resulting change to the HPU population's 
-distribution of outputs.
+We found that intertask effects were stronger than framing, unless the worker
+was required to echo the frame, in which case the effects of both exposures were on par.  
+Our results demonstrate that initial tasks can change 
+workers' focus in later tasks.  Using the wordnet corpus, we analyzed 
+the effects on the vocabulary used by workers when 
+labeling test tasks. 
+Exposure to both framing and initial tasks significantly altered the 
+diversity of vocabulary that workers used when referring to the prime concept,
+as well as the degree to which workers used specialized (rather than generic) 
+words.
 
-To refine this, we distinguish between methods that determine \textit{whether}
-two random sources have the same distribution 
-(e.g. Pearson's chi squared test), from those that determine
-\textit{the extent} of that difference (e.g. one of the many measures of 
-statistical divergence).  We are interested in measuring the extent of
-difference because our practical concern is the potential for such
-differences to alter the course of an algorithm.
+Contrary to our initial expectations, our findings suggest that the HPU 
+programmer can leverage intertask effects.  By carefully designing workflows,
+it is possible to tune worker focus, specificity, and expressivity.  Our 
+findings carry two lessons for the task designer: intertask
+effects can severely bias HPU output if uncontrolled, but if properly 
+controlled, intertask effects might be of significant utility in achieving 
+expert-level output.
 
-To measure the effect of some priming treatment, we must of course draw a 
-comparison to some standard population.  In many cases, there may be an 
-obvious comparison between a primed and unprimed population.  However, we 
-refrain from proposing a canonical neutrally-primed HPU population; what is 
-considered ``unprimed'' in one scenario may be ``primed'' in another. 
-Instead, we speak of two HPU populations being \textit{differently primed}.
+\paragraph*{Measuring computational hysteresis.}
+Before describing the details of our experiments, we explain some 
+choices made in measuring intertask and framing effects 
+(hereafter collectively \textit{exposure effects}).  
+In trying to establish a measure of exposure effects, it might be tempting to 
+invoke the notion of a ``neutral frame of mind'' to serve as a baseline. 
+But such a concept seems both difficult to define, and unlikely to arise.
+Therefore, we always consider the effect of one exposure 
+\textit{relative} to another.  We organized our experiments 
+into pairs of treatments, between which it is possible to make meaningful 
+comparisons.
 
-We present three alternative, equivalent definitions for the 
-\textit{difference in priming} of two HPU populations, $\mathcal{P}$, and 
-$\mathcal{Q}$, which we denote $\theta(P,Q)$.  To set up the definitions,
-we will assume that $\mathcal{P}$ and $\mathcal{Q}$ 
-were sampled randomly from the same initial population $\mathcal{R}$, and 
-then were exposed to (possibly) different priming treatments. Then, the HPUs 
-in $\mathcal{P}$ and $\mathcal{Q}$ perform some task, leading to popualtions 
-of work-products, $P$ and $Q$.
+Our goal in measuring exposure effects is to show that they can actually 
+alter the course of algorithms.
+We could, by means of a $\chi^2$ test, reject the null hypothesis that
+differently exposed HPUs have the same distribution of outputs.
+However, this alone would not demonstrate a practically significant effect, in 
+terms altering the execution path of algorithms.
 
-The first definition provides the motivation for our choice of divergence
-measure, because it directly measures the proportion of the time that a
-binary decision will be changed due to priming effects:
-
-\begin{mydef}
-	\label{def:bias}
-	{\upshape Maximum Bias:}
-	Let $\mathcal{D}$ be a binary decision function, which takes a 
-	work-product
-	$r \in P \cup Q$ as input, and outputs a bit $\mathcal{D}(r)=b$, where 
-	$b \in \{0,1\}$. Denote the \emph{bias} of $\mathcal{D}$, due to the
-	different priming of $\mathcal{P}$ and $\mathcal{Q}$ by
-	$\theta_\mathcal{D}(P,Q)$ and define it to be the difference 
-	in the expected output of $\mathcal{D}$ when acting on work-products from 
-	$P$ and $Q$:
-	$$
-	\mathcal{D}(P,Q) = 
-		\left| 
-			\mathrm{E}\left\{ \mathcal{D}(p) \right\} 
-			- \mathrm{E}\left\{ \mathcal{D}(q) \right\} 
-		\right|,
-	\theta_\mathcal{D}(P,Q) = 
-		\left| 
-			\mathrm{E}\left\{ \mathcal{D}(p) \right\} 
-			- \mathrm{E}\left\{ \mathcal{D}(q) \right\} 
-		\right|,
-	$$
-	where $p \in P$, $q \in Q$.  Then, define the difference in priming 
-	between $\mathcal{P}$ and $\mathcal{Q}$ to be the worst-case bias, i.e. 
-	the bias of the most susceptible decision:
-	$$
-	\theta(P,Q) = 
-		\sup_\mathcal{D} \theta_\mathcal{D}(P,Q)
-	$$
-\end{mydef}
-If $\mathcal{D}$ is the condition of an \texttt{if}-statement, then the 
-definition above is the change in the fraction of the time that a given 
-path of execution is followed due to HPU priming.
-
-While this is precisely what we want to measure, it is not at all clear how
-to go about doing it.  The second formulation provides a practical connection
-by rephrasing priming in terms of its distinguishability:
-
-\begin{mydef}
-	{\upshape Distinguishability:}
-	Let $\mathcal{D}$ be a distinguisher algorithm, which takes work-product 
-	$r \in P \cup Q$ as input, and outputs a \emph{guess} 
-	$\mathcal{D}(r) \in \{0, 1\}$. Now define a validation test 
-	$V(\mathcal{D}, R_0, R_1)$ as follows. A bit is drawn uniformly at random, 
-	$b \in_R \{0, 1\}$, and then a work-product $r$ is chosen uniformly at 
-	random from one of the populations, decided by the bit: $r \in_R R_b$. 
-	Input $r$ into $\mathcal{D}$, and if $\mathcal{D}(r) = b$, we say 
-	$\mathcal{D}$ \emph{guessed correctly}, and the value of $V$ is 1, 
-	otherwise $V = 0$.
-
-	A distinguisher that guesses randomly will still be correct half of the 
-	time. Therefore, denote the performance of $\mathcal{D}$ by 
-	$\eta_\mathcal{D}(P, Q)$, and let
-	$$
-		\eta_\mathcal{D}(P,Q) = 2\cdot \mathrm{E}\{V(\mathcal{D},P,Q)\} - 1.
-	$$
-	Then define the difference in priming between $\mathcal{P}$ and 
-	$\mathcal{Q}$ to be the performance of the best possible distinguisher:
-	$$ 
-		\theta(P,Q) = \sup_\mathcal{D} \eta_\mathcal{D}(P,Q)
-	$$
-	\label{def:dist}
-\end{mydef}
-
-\textbf{Definition 2} relates the difference in priming to the 
-\textit{optimal Bayes classifier} for determining whether a given HPU output
-came from $P$ or $Q$.  This means that we can obtain a lower bound on
-$\theta(P,Q)$ based on the performance of an actual classifier, which provides
-recourse when purely statistical methods fail.
-
-The statistical divergence measure underlying the previous definitions is the
-divergence measure known as the ``total variational distance'' or 
-$l_1$-distance:
-\begin{mydef}
-	\label{def:l1}
-	{\upshape Total variational distance $\theta_{l_1}$:}
-	Define the difference in priming between $\mathcal{P}$ and $\mathcal{Q}$ 
-	to be equal to the total variational distance between the work-products 
-	$P$ and $Q$:
-	$$
-	\theta_{l_1}
-	= \sup_{A \subset \mathcal{X}} \left| \sum_{x \in A} f_P(x) - f_Q(x)\right|
-	= \frac{1}{2} \sum_{x \in \mathcal{X}} \left| f_P(x) - f_Q(x) \right|,
-	$$
-	where $f_P(x)$ denotes the probability of observing x when sampling from P.
-\end{mydef}
-The equivalent formulation for $\theta(P,Q)$ in 
-\textbf{definition \ref{def:l1}} provides a grounding in a fundamental
-measure of statistical divergence, and a connection to information theory.  
-The equivalence of the three definitions
-follows from the known fact that no algorithm can have output that differs
-on inputs $P$ and $Q$ more than $l_1 \times 100\%$ of the time.  We provide
-proofs in the supplementary material.
-
-The difficulty of measuring $\theta(P,Q)$ depends on what the universe of
-possible outputs are, as well as how $P$ and $Q$ are actually distributed,
-both of which are mainly determined by the task that the HPUs are asked to 
-perform.  In the case where workers label an image with a free-text input, 
-the number of different possible labels can be in the thousands or more.  If
-the support, $\mathcal{X} = P \cup Q$, is large compared to the number of 
-HPU outputs sampled, so that many labels appear only once (which in any case
-is expected from Zipv's law), then estimating $\theta$ directly from the
-observed frequencies of labels is difficult.
-
-One approach to estimating the $l_1$-distance from samples, which appears
-reasonable on the surface, is to use the observed frequencies of each output
-$x$ from $P$ and $Q$ to estimate $f_P(x)$ and $f_Q(x)$, and calculate 
-$\theta(P,Q)$ directly from \textbf{definition 3}.  This is the so-called naive
-approach to estimating $l_1$-distances, and is aptly named because it tends
-to produce very inflated values.  More recent techniques have for estimating
-$l_1$ have been suggested by Valiant \cite{val-thesis}, and Batu 
-\cite{batu2000testing,batu2013testing}.  We reserve the discission of these
-techniques to the supplementary material; they do not turn out to be useful
-because they do not provide confidence intervals.  Thus our only recourse is
-to test the performance of classifiers at distinquishing $p \in P$ from 
-$q \in Q$, which allows us to estimate a lower bound on $\theta(P,Q)$.  This 
-turns out to be sufficient, and has the advantage that, so long as they are
-learnable, it is not necessary to understand exactly how $P$ and $Q$ differ.
+We developed a more stringent measure in which we train classifier algorithms 
+to infer the exposure of an HPU from its outputs.
+If a classifier infers an HPU's exposure with significantly 
+better accuracy than provided by chance, then the HPU outputs must have 
+been affected by the exposure.  
+But in addition, the classifier serves as a kind of certificate, since it is 
+an example of an algorithm whose path of execution is influenced by the 
+exposure of 
+individual HPUs.  In the supplementary material, we ground our approach 
+rigorously in terms of the L1-distance metric, which is a measure of 
+divergence between distributions.  The L1-distance ranges from 
+0 to 1.  In our case, a value of 1 indicates that the HPU's exposure
+influences its output so strongly that the exposure can be inferred from the
+output without ambiguity.  A value of 0 indicates that the exposure has no
+impact on the HPU's outputs.  The connection between the
+L1-distance, $D_\mathrm{L1}$, and a classifier's accuracy, $\eta$, is given by:
+\begin{equation}
+	D_\mathrm{L1} \geq 2 \eta - 1, 
+	\label{l1}
+\end{equation}
+Since a classifier's performance provides a lower bound on the L1-distance, 
+we shall denote $D_\mathrm{L1}^-\equiv 2\eta-1$.
+The L1-distance admits the following interpretation: if two distributions
+$P$ and $Q$ have an L1-distance $d$, then in the worst case, the 
+frequency with which a binary algorithm operating on samples
+from $P$ outputs a 1, will differ from that when operating on samples from 
+$Q$ by $d \times 100\%$.  
+Thus, we can interpret $D_\mathrm{L1}^-$ as a kind of
+lower bound for the worst-case bias induced by HPU hysteresis.
+We provide further discussion of the statistical properties of our approach 
+in the supplementary material.
 
 \paragraph{Experimental setup.}
-We performed two experiments, soliciting respectively 900 and 2300 MTurk 
-workers to label images depicting iconic cultural scenes, meals, ingredients, 
-table-settings, and various utensils and cookware. In these experiments,
-workers were randomly assigned to treatments, and depending on this 
-assignment, were exposed to different framing primes, given a different 
-set of initial images, and shown a different permutation of the test images. 
-For both experiments, workers were first shown brief instructions.  
-The framing prime was then shown, unless the given 
-treatment involved no framing.  Workers then performed a series of 
-image-labeling tasks and had to provide five labels per image. 
-For the purpose of analysis, we denote the first five images as the 
-\textit{initial set}, and the last five as the \textit{test set}, but no
-distingction was made from
-the perspective of the worker.
-Table 1 sumarizes the various experimental treatments for both 
-experiments.
+\begin{figure}
+	\centering
+	\includegraphics[scale=0.7]{figs/images.jpg}
+	\caption{
+		Examples of images used in labeling tasks. (The italicized treatment 
+		names that follow are defined in Table \ref{table:treatments}.) Images 
+		from initial tasks: A) \textit{task1:food}, B) 
+		\textit{task1:obj}, D) \textit{task2:food}, 
+		E) \textit{task2:cult}.  Images from  test tasks: C) \textit{exp1}, 
+		F) \textit{exp2}.  The full set of experimental materials is 
+		shown in the supplementary material.
+	}
 
+	\label{fig:task}
+\end{figure}
+We performed two experiments, soliciting respectively 2300, and 900 MTurk 
+workers to label images depicting food, kitchen- and dining-ware, and cultural
+scenes.  In a given experiment, all workers performed the same test
+tasks, the output of which was our main dependent variable.  Before performing
+the test tasks, workers were subjected to an exposure, via two 
+\textit{modalities}: either they completed a set of initial tasks, or 
+were exposed to a frame, or both.  As mentioned, from the perspective of the worker, 
+there was no distinction or discontinuity between initial and test tasks.
+
+We organized the experiments into \textit{treatment pairs}.  Both treatments in a 
+pair involved the same exposure modality, but differed in the
+content of the exposure.  In Table 1, we summarize the various experimental
+treatments, and introduce a naming convention that we use to refer to 
+treatments and treatment pairs.
+In the treatment pairs that studied intertask effects (\textit{task1} and
+\textit{task2}), workers performed 10 image-labeling tasks, with the first 
+five tasks comprising the initial tasks and the last five tasks comprising the
+test tasks.
+
+In the first experiment, the content of the exposures was based on the prime
+concepts \textit{food} and \textit{objects} (throughout, ``objects'' should be
+taken to imply ``non-edible objects'').  So, 
+in \textit{task1:food}, the initial tasks contained images depicting food, 
+while in \textit{task1:obj}, they contained images depicting objects, 
+including kitchen and dining-ware (see Fig~\ref{fig:task}).  Meanwhile, 
+for the exposures in \textit{frame1} we indicating that the study was
+``funded by the laboratory for the visual perception of \{ Food and Ingredients
+$\vert$ Objects and Tools~\}''.  To further strengthen the frame, we 
+introduced another pair of framing treatments, \textit{echo}, with stronger
+wording: ``The purpose of this study is to understand the visual perception
+of \{ Food and Ingredients $\vert$ Objects and Tools~\}'', and required
+the worker to echo the purpose of the study by selecting it among other 
+options in a combo-box input.
+
+Note that food and objects are both relatively well-defined classes of 
+physical entities.  To explore a different conceptual axis, in 
+\textit{exp2} we adopted the prime concepts \textit{food} and \textit{culture}.
+Compared to food and objects, culture is more abstract, and, rather than 
+comprising a class of physical entities, it encapsulates
+sets of beliefs, values, and practices.  Examples of images from the initial 
+tasks in \textit{task2} are shown in Fig.~\ref{fig:task}, and the full 
+collection of 
+experimental materials is presented in the supplementary material.  We 
+ensured that all workers only participated in one treatment of one experiment.
+
+\setlength{\tabcolsep}{3pt}
 \begin{table}[t]
 \centering
-	\begin{tabular}{ l  l  l }
-		\hline                       
-		Treatment & Framing prime & Initial image set	\\ 
-		\hline                       
-		\textit{Experiment 1}\\
-		$\textsc{ambg}$ & None & Ambiguous\\
-		$\textsc{img:cult}$ & None & Cultural\\
-		$\textsc{img:ingr}$ & None & Ingredients\\
-		$\textsc{frm:cult}$ & Cultural & Ambiguous\\
-		$\textsc{frm:ingr}$ & Ingredients & Ambiguous\\
-		\hline  
-		\textit{Experiment 2}\\
-		$\textsc{img:food}$ & None & Food\\
-		$\textsc{img:obj}$ & None & Objects\\
-		$\textsc{frm:food}$ & Food & None\\
-		$\textsc{frm:obj}$ & Objects & None\\
-		\hline  
+\begin{tabular}{ c c c c c }
+		\hline \noalign{\smallskip}
+		\multicolumn{3}{c}{\textbf{Treatment name}} & \parbox[c]{1.6cm}{\centering \textbf{Frame}} & \parbox[c]{1.3cm}{\centering \textbf{Initial\\ tasks}}	\\
+
+		\noalign{\smallskip} \hline \noalign{\smallskip}
+
+		\multirow{6}{*}{ \parbox[c]{0.7cm}{ \phantom{XXX} exp1}} 
+			& \multirow{2}{*}{task1} & food & none & food\\
+			& & obj & none & objects\\
+
+			\noalign{\smallskip} \cline{2-5} \noalign{\smallskip}
+			& \multirow{2}{*}{frame1} & food & food & none\\
+			& & obj & objects & none\\
+
+			\noalign{\smallskip} \cline{2-5} \noalign{\smallskip}
+			& \multirow{2}{*}{echo} & food & food & none\\
+			& & obj & objects & none\\
+
+		\noalign{\smallskip} \hline \noalign{\smallskip}
+
+		\multirow{4}{*}{exp2} 
+			& \multirow{2}{*}{task2}  &  food & none & food\\
+			& 	&  cult & none & culture\\
+			\noalign{\smallskip} \cline{2-5} \noalign{\smallskip}
+			& \multirow{2}{*}{frame2} & food & food & food\\
+			& 	& cult & culture & food\\
+
+		\noalign{\smallskip} \hline  
 	\end{tabular}
@@
 	\caption{ \footnotesize{ 
-		Workers were uniformly randomly assigned to one of the 
-		treatments listed above. 
-		The full funder names used were 
-		Cultural: ``The Global Foundation for Cultural Recognition'' and 
-		Ingredients: ``The National Foundation for Nutritional Awareness''.  
-		The ambiguous, cultural, and ingredients initial image sets are shown 
-		in \textbf{Figs. 2}, \textbf{3}, and \textbf{4}.
+		We use the treatment names shown to refer to specific sections of 
+		the data collected.  For example, \textit{task2:food} refers to the
+		treatment in the second experiment which was not exposed to a frame, 
+		and whose initial tasks contained images of food (7th row).
 	}}
-	\label{table:1}
+	\label{table:treatments}
 \end{table}
 
-\begin{figure}
-	\centering
-	\includegraphics[scale=0.7]{figs/tasks.pdf}
-	\caption{Examples of slides used for the image labeling tasks.
-A) instructions shown to all workers; B) a framing slide; C) a slide from the initial set for treatment IMG:FOOD; D) a slide from the initial set for treatment IMG:OBJ; E) a slide from the test set shown in all treatments.
-The full set of slides used for all treatments is presented in the supplementary material.}
-	\label{fig:task}
-\end{figure}
+\paragraph{The strength of intertask effects.}
 
-\paragraph{The strength of inter-task effects.}
+We assessed the strength of intertask and framing effects
+by training a multinomial naive Bayes classifier to infer a worker's exposure
+based on the labels provided in the test tasks (see Fig.~\ref{fig:theta}).
+This inference was made over the two possibilities for a given treatment pair.
+We found that in \textit{task1}, whether a worker performed food- or 
+object-containing initial tasks had a strong effect on their subsequent 
+labels, introducing a bias that probably exceeds 30\%.  In comparison, the 
+framing effect in \textit{frame1} did 
+not influence workers' labels enough for the classifier to make predictions 
+with significantly better accuracy than that afforded by chance.  The results 
+for \textit{exp2} show a similar, but even more pronounced trend, with the bias
+induced by intertask effects in \textit{task2} probably exceeding 50\%.
+
+We see a comparable effect size in the \textit{echo} treatment pair.
+We expected \textit{echo} to show a very strong effect because, by requiring
+the worker to echo the purported purpose of the task, we signal that it
+is of particular importance.  The fact that the intertask effects were on par with the framing 
+effects in \textit{echo} shows just how powerful intertask effects can be.
+
 \begin{figure}
@@
 	\caption{
-		Difference in priming observed for various pairs of worker populations.
-		The pairs of populations differed in terms of the initial tasks they
-		performed (bars labeled by \textit{inter-t.}) or in terms of the framing
-		to which they were exposed (bars labeled by \textit{frame}; see table 1 for
-		details about the treatments).  The difference in priming was 
-		measured based on the accuracy of a naive Bayes classifier in 
-		resolving which treatment workers belonged to, as described in the 
-		text.  
+		Lower-bound estimates for the  worst-case bias introduced in image
+		labeling tasks due to worker exposure effects.  The estimate was 
+		based on the performance of a multinomial naive Bayes classifier,
+		trained to infer HPU exposures. A) Bias induced through various
+		modalities and prime concepts (see Table 1). B) Bias induced in 
+		\textit{task1}, as a function of test task position.  Error bars
+		show the one-tailed 95\% confidence interval.
 	}
@@
 
-%\paragraph{Dynamics of inter-task effects}
-%\begin{figure}
-%	\centering
-%	\includegraphics[scale=0.7]{figs/theta_by_pos_img.pdf}
-%	\caption{
-%		Difference in priming observed for various pairs of worker populations.
-%		The pairs of populations differed in terms of the initial tasks they
-%		performed (bars labeled by ``inter-t.'') or in terms of the framing
-%		to which they were exposed (bars labeled by ``frame''; see table 1 for
-%		details about the treatments).  The difference in priming was 
-%		measured based on the accuracy of a naive Bayes classifier in 
-%		resolving which treatment workers belonged to, as described in the 
-%		text.  
-%	}
-%	\label{fig:theta_pos_img}
-%\end{figure}
+\paragraph{Dynamics of intertask effects.} It is natural to expect 
+intertask effects to attenuate as a worker proceeds through the test tasks.  
+In \textit{task1}, we permuted the test tasks, allowing us to 
+measure intertask effects as a function of task position, while factoring
+out the content-dependent differences between tasks
+(see Fig.~\ref{fig:theta}B). 
+We found intertask effects were most pronounced for the first test task,
+dropping off substantially for the second, but maintaining a 
+significant effect through until the fifth test task.  
+This shows that the range of intertask effects extends across at least five 
+tasks, and probably substantially more.
+This makes intertask effects of greater concern, but as we will show, it also
+makes intertask effects of greater potential utility.
+In future work, it would be interesting to investigate whether a worker's
+susceptibility to intertask effects varies across a large batch.  For example,
+It is conceivable that the first few tasks induce especially strong
+or long-lasting effects, in effect ``setting the tone'' for the rest of the batch.
 
-We analyzed the overall strength of inter-task effects and framing, by looking
-at pairs of treatments that performed the same test tasks, but had done
-different initial tasks or had been exposed to different framing.
-For each such pair, we assessed the performance of classifier
-in predicting which treatment workers belonged to, based on the labels they
-provided during the test tasks (see fig 2).  
-Based on \textbf{Definition 2}, this is a lower bound on the amount 
-bias introduced by the initial tasks and framing.
-
-In experiment \textit{inter-t.1}, the test tasks required workers to
-label relatively cluttered images of table settings, which had various items
-of food, utensils, dishware, and other objects natural to such settings.
-For one treatment, the images in the initial tasks consisted exclusively of 
-food, and for the other, they consisted exclusively of non-food objects, 
-particularly cookware and utensils.  We saw a strong effect of priming, 
-based on the classifier performance (see fig. 2).
-
-In a related experiment, \textit{frame1}, workers were given the same test tasks
-as in \textit{inter-t.1}, but were either told 
-that ``The purpose of this study is to understand the viusual perception of
-Food and Ingredients'' or ``\ldots of Objects and Tools''.  This overt framing
-of the task in terms of a specific research objective had remarkably milder
-effects on workers than the initial tasks (see fig. 2).
-
-We performed another set of experiments based on a different set of test 
-tasks, and where the initial tasks and framing were directed along a different
-conceptual axis.  In \textit{inter-t.2} and \textit{frame2}, the images in the test 
-tasks displayed prepared meals from a variety of ethnic backgrounds.  We then
-designed the framing and initial tasks to focus either on food or cultural 
-elements.  In the previous experiments, the primes were always focused on 
-concrete ``highly imageable'' concepts (food and objects), these experiments
-mixed a concrete concept (food) with an abstract concept (culture).
-The initial tasks in \textit{inter-t.2} either depicted prepared meals (but having
-ambiguous cultural association), or iconic cultural scenes (including music, 
-dance, and sport).  Workers in \textit{frame2} were told that the ``This study
-was proudly funded by the National Foundation for Nutritional Awareness'' 
-or the ``\ldots Global Foundation for Cultural Recognition''.
-
-The results for \textit{inter-t.2} and \textit{frame2} confirmed that 
-inter-task effects are much stronger than framing (see fig. 2).  In fact, 
-intertask effects were even stronger in this experiment than the previous.
-
-\paragraph{Sufficiency of framing.} Given just how much stronger
-inter-task effects were, the reader may wonder whether the framing was 
-in some sense ``sufficient''.  
-We designed our framing tasks based on
-work that had previously studied framing effects in micro-task settings.  
-Prior studies have shown that framing the purpose of a task, or indeed, 
-simply changing a single, seemingly non-critical word in a task description, 
-has significant effects on worker's resonses.  Perhaps more importantly, the 
-framing treatments were included to provide a reasonable basis for comparison,
-and it is clear from our results that the prior tasks performed by a 
-worker are much stranger than the effects induced by descriptions of a task's
-purpose, or the requester's mandate.
-
-Nevertheless, we included one more experiment, \textit{frame*3}, to test the 
-effect of framing when the worker is required to \textit{echo} the framing 
-statement.  \textit{frame*3} was based on \textit{frame2}, but the worker
-had to indicate, using a menu option, what the purpose of the study was,
-before they could proceed.  In one sense, this seems to go beyond what one
-might mean by ``framing''.  By forcing the worker to echo the frame, we provide
-a clear indication that the frame is a particularly important detail, 
-elevating its importance above even the instructions that had been provided
-beforehand.
-
-The framing effect in \textit{frame*3} was quite strong, being on par with the
-inter-task effects we had observed (see fig. 2).  We are not sure whether
-the \textit{frame*3} should be considered framing,
-or whether it should be considered as an instruction, or perhaps as a 
-screening-task.  Regardless, our results show that worker's responses are 
-profoundly affected by recently completed tasks.
-
-\paragraph{Dynamics of intertask effects.} 
-In the results shown above, we considered the aggregate effect that the
-first five initial tasks had on the last five test tasks.  But it would stand
-to reason that the first test task might be
-most strongly influenced, and that, as the worker proceeds, the intervening 
-test tasks would tend to wash out the priming induced by the initial tasks.
-
-One complication to this is the fact that the strength of intertask effects
-should also depend on the task: that is, workers performing one task are not
-necessarily as susceptible to inter-task effects as when performing another 
-task.  To account for this, we performed five replicates of the 
-\textit{inter-t.1} experiment, each using a different permutation of the 
-test tasks.  We ensured that each test task appeared in each of the 
-five possible relative positions.  This allowed us to measure the inter-task
-effects as a function of task position, independant of the particular image
-used in the task (see fig. 2B).  We found that, as one would expect,
-the first test task tends to be the most strongly affected.  The effect drops
-considerably for the second task, and continues to fall for the third and 
-fourth.  Interestingly, the last test task consistently showed a small increase
-in priming effect.  We also observed this in \textit{inter-t.1}. 
-We do not know the psychological mechanism behind this phonomenon, but we 
-speculate that, since the worker knows that there are ten tasks in total,
-they might reflect on the task overall batch of tasks as they near the end,
-and in so-doing might partially re-activate the influence of the initial tasks.
-
-While the strength of inter-task effects appeared to depend strongly on
-the position of the task, it was considerably less dependant on exactly what
-was in the task (see fig. 2C).  To be sure, we intended for the tasks to be 
-similar, and it does appear that the various test tasks had similar 
-susceptibilities to inter-task effects.
-
-\paragraph{Initial tasks' affect on the direction of focus} 
+\paragraph{Detailed influences on worker outputs.} 
 \begin{figure}
 	\centering
-	\includegraphics[scale=1]{figs/food_specificity.pdf}
+	\includegraphics[scale=1]{figs/vocab_specificity.pdf}
 	\caption{
-		Difference in priming observed for various pairs of worker populations.
-		The pairs of populations differed in terms of the initial tasks they
-		performed (bars labeled by \textit{inter-t.}) or in terms of the framing
-		to which they were exposed (bars labeled by \textit{frame}; see table 1 for
-		details about the treatments).  The difference in priming was 
-		measured based on the accuracy of a naive Bayes classifier in 
-		resolving which treatment workers belonged to, as described in the 
-		text.  
+		Detailed exposure effects on workers' label vocabulary, for various
+		exposure modalities and prime concepts (see Table 1).  A) Change in 
+		the number of food-related labels used. B) Change in the total number 
+		of \textit{unique} food-related labels used. C) Relative specificity
+		of treatment pairs, when considering food-related labels.  For all
+		plots, a positive bar height indicates an increase for the 
+		food-exposed treatment for the pair indicated on the abscissa.
 	}
-	\label{fig:food_specificity}
+	\label{fig:specificity}
 \end{figure}
 
-At this point we have only discussed priming effects in terms of a 
-classifier's ability to detect them.
-We have said nothing qualitative about the \textit{nature} of these effects.  
-This demonstrates an advantage of using classifiers to measure priming.  
-Machine learning algorithms are designed to find salient differences 
-by generalizing, inductively, from examples, so one
-need not know beforehand how workers were primed, nor the natuer of the  
-priming effects.  Machine learning algorithms are specifically designed to 
-generalize inductively from examples, which makes
-it possible to estimate how different two populations with little prior 
-knowledge.
+Having observed significant effects from framing and task-exposure,
+we looked in greater detail at the nature of the effects.  For instance,
+does a food-oriented exposure induce workers to provide more food-related
+labels?  And if so, does this explain the classifier's ability to distinguish
+a worker's initial exposure?
 
-But once having shown that workers are strongly primed by initial tasks, it is
-natural ask whether workers were biased to provide labels that reflected, 
-in some way, the \textit{content} of the initial tasks.  The conceptual basis
-for the primes in experiment 2 were eithre \textit{food} or 
-\textit{objects and tools}.  Thus, we can test whether workers exposed to food
-primes produced more food-related.
+To answer these questions, we used the wordnet corpus, augmented with names of
+ethnic foods learned from the Internet.  Wordnet provides a (roughly)
+hierarchical set of relationships between nouns, called hypernym-hyponym
+relationships.  A hypernym is a generalization, while a hyponym is a 
+specialization.  So, for example, ``bread'' is hypernym to ``rye bread'' 
+and hyponym to ``baked goods''.
 
-To identify food-related labels, we used the wordnet corpus.  Wordnet
-is an extensive corpus for English, that includes hypernym-hyponym 
-relationships between words.  The hypernym relation correpsonds to conceptual
-abstraction.  For example \textit{bread} is a hypernym of 
-\textit{pumpernickel} because pumpernickel is a \textit{type of} bread.
-The hyponym relation is simply the converse: pumpernickel is a hyponym
-of bread.  For the purpose of our analysis, when we refer to hypernyms,
-we will mean both direct hypernyms, as well as the hypernyms of hypernims,
-and so on, with an analogous interpretation for hyponyms.
+Using the augmented hypernym-hyponym structure of wordnet to identify nouns 
+depicting food, we found that, for the experimental pairings in 
+\textit{exp1}, the
+food-exposed treatments did produce a significantly larger fraction of 
+food-related labels (see Fig.~\ref{fig:specificity}A).  While the shift in 
+focus with regard to food does help explain the classifier's ability to 
+infer worker exposures, it is insufficient to explain the observed performance
+(*).
+Furthermore, in \textit{exp2:task2} we see a significant but reversed effect
+(see Fig.~\ref{fig:specificity}A), which suggests a more complicated 
+relationship between exposure and label usage.
+Given the difference between the food-culture and food-object conceptual axes, 
+it should perhaps not be surprising that the effect of initial task exposure 
+is different.  It would appear that we must be prepared to accommodate 
+multiple 
+countervailing factors influencing the number of references to the prime 
+concept (food).  We will come back to this point momentarily.
 
-We collectod a small set of top-level food-related nouns in wordnet,
-together with all of their hyponyms, and took the resulting set of 
-3589 lemmas as an operational definition for the set of English food-related 
-words.  This set is quite extensive, containing somewhat obscure forms such as
-``burgoo'' and ``barmbrack'', and consumables at the fringe of what might
-be considered food such as ``vitamin B'' (or if you prefer, 
-``B complex''), as well as more common lemmas like
-``banana'',  ``bread'', and of course ``banana bread''.  We found that,
-for the data in experiment 1, this method produced excellent aggreement with 
-human annotation of food-related words (see supplementary material).  
-For the analysis exp2, the variety of non-English names for ethnic dishes 
-forced us to rely on a manual approach.  This corroborated our results
-for exp1, and we encourage the interested reader to read our discussion of
-the manual approach in the supplementary material.
+To explore these effects further, we looked more closely at which particular
+labels were most suppressed (activated) by a worker's exposure.  Remarkably,
+we found that, for all treatment pairs, ``food'' was always the most 
+suppressed label among 
+the food-exposed workers.  This is surprising, considering 
+that the overall incidence of food-related labels mostly \textit{increased} 
+among food-exposed workers.  But taken together, the increase in references to 
+food 
+and the decrease in the incidence of ``food'' per se (which is the most generic
+food-reference in the wordnet-based ontology), necessarily implies that
+food-exposed workers have opted for more specialized references in place of 
+``food''.
 
-Our findings matched the straightforward expectation that workers exposed to 
-food related-primes were biased to provide more food-related labels during 
-test tasks (see Fig. 3A).  Had we relied on the intuition that workers 
-should be biased to label according to the underlying concept of their prime,
-we would have underestimated the strength of priming effects.  This
-again illustrates the advantage of using classifiers to detect priming as
-opposed to testing for the effects that one might intuitively expect.  
-Though present, the expected influence on the number of food-related words
-cannot account for the bulk of inter-taks effects.
+In a crowdsourcing task, considerable effort must be given to shaping the 
+vocabulary with which a worker engages a task.  To draw an example from the 
+domain of citizen science, in galaxy zoo, workers catalog images of galaxies 
+in terms of \textit{smoothness}, and the presence of \textit{rings}, 
+\textit{dust lanes}, \textit{digital disturbances}, and so on.  Shaping this 
+vocabulary is crucial to the reliability of results.  The interface of
+galaxy zoo helps by constraining and prompting the user with this basic 
+vocabulary.  But this would not appear to be sufficient, since
+a set of positive and negative training examples are used, together with
+peer-to-peer and peer-to-expert exchange in discussion areas, presumably to
+further refine and standardize the vocabulary (\#).
 
-\paragraph{Effects on label vocabulary.}
-When manually inspecting the labels of \textit{test-t.2}, one striking 
-observation was that workers that initially labeled images of cultural scenes 
-were more likely to use generic words when labeling the test images, compared 
-to workers that initially labeled images of meals.  For example, 76\% of the 
-workers from \textit{exp2.task.cult} gave the very generic label 
-\texttt{food}, compared to only 16\% of \textit{exp2.task.food} workers 
-(recall that the test tasks for both treatments depicted prepared meals).
-One interpretation is that workers who have already labeled 5 images relating
-to food are more likely to focus on aspects of the images that are different
-from one another, and refrain from so generic a term as \texttt{food}.
+In our set-up, where the worker's vocabulary is unconstrained, we can 
+directly observe the effects that frames and initial tasks have on worker 
+vocabulary.  By looking at the number of unique food-related labels that 
+workers produced, we assessed the richness of vocabulary that workers used when
+referring to food (see Fig.~\ref{fig:specificity}B).  We found that the 
+food-exposed workers use a richer vocabulary of 
+food-related words, even in cases like \textit{task2:food}, where they 
+made fewer references to food overall.  
+Interestingly, task-based exposure to food had a stronger enriching effect 
+ than did framing-based exposures. (* explain why vocab 
+diversity is useful.)
 
-Based on this observation, we tested the degree of specificity of labels 
-accross all treatments.  We appraoched measuring specificity in two ways.
-Our first method was based on the reasoning that, if a given group of 
-workers uses more specific labels, they will then provide, on the whole,
-a larger set of unique labels for any given image.  For example,
-suppose the workers from \textit{exp2.task.food} who do not use the label 
-\texttt{food} had chosen more specific labels instead.  In being more 
-specific, they must choose a particular detail to describe, from a large 
-number of possibilities, and so are more likely to provide unique labels.
-Indeed
-for all images in the test set, workers from \textit{exp2.task.food} gave
-more unique labels than did those from \textit{exp2.task.cult}, as shown 
-in fig 2B.  Note how the the relative vocabulary sizes follows
-the same trend, as a function of test task, as was observed for the 
-classifier-based detection of general priming differences (c.f. fig X).
+Using the ontology of food induced by wordnet, along with foods learned from
+the Internet, we were able to directly calculate the relative specificity of 
+workers from different treatments.
+To do this, we considered all the labels from one treatment
+(for example \textit{task1:food}) and compared these to all the labels from 
+another (\textit{task1:obj}).  For all possible comparisons, we observed 
+which treatment's label was more specific more often, and normalized this
+quantity as a percentage (we provide greater detail in the supplementary 
+material).
 
-Our second approach to measuring relative specificity used the 
-hypernym-hyponym relationships of wordnet.
-We operationalized the relative specificity of two sets of labels $P$ 
-and $Q$ as:
-$$
-	S(P,Q) = \frac{1}{|P \times Q|}\sum_{p \in P} \sum_{q \in Q} 
-		\left(\mathbf{1}_{[p>q]} - \mathbf{1}_{[q>p]}\right),
-$$
-where $\mathbf{1}_{[p>q]}$ evaluates to 1 if $p$ is a hyponym of $q$.
-Using the above equation, we found that, for every images in the 
-test set, the labels attributed by workers in \textit{exp2.task.food} were 
-more specific than those by workers in \textit{exp2.task.cult}.
+We calculated the relative specificity for all treatment pairs, while 
+restricting focus to 
+food-related labels (see Fig.~\ref{fig:specificity}C).  We found that 
+the food-exposed workers always provided food-references of substantially 
+greater specificity.  Workers that had labeled images containing food 
+were about 12\% more specific than those that labeled images of objects,
+and about 20\% more specific than those that labeled images of cultural 
+scenes.  With respect to the specificity of food references, framing effects 
+were on par with intertask effects.
 
-Initialy we hypothesized that the similarity of initial and test tasks was
-driving a relative increase in specificity.  While this seems reasonable,
-we also notice a similar effect occuring for \textit{exp1.task} in which
-the test tasks consisted of both food and non-food objects, and the initial
-tasks were either food or non-food objects.  In this case, it is difficult
-to argue that one set of initial tasks is more similar to another.  In fact
-we devise a method to operationalize image similarity, and find that 
-the initial images of \textit{exp1.task.food} are equally similar to the
-test tasks as the initial images of \textit{exp1.task.obj}.  Furthermore,
-we see strong effects on relative specificity for framing as well.
+Taken together, the results presented in Fig.~\ref{fig:specificity} can 
+be explained by a combination of priming and  \textit{negative} priming.
+Negative priming occurs when a repeated stimulus, which is perceived to be
+non-salient, begins to be ignored (\#).
 
-In general, it is of great practical interest to control the level of 
-specificity of qualitative characeterzations.  In many applications the
-task-designer will probably want obtain characterizations that are more
-discriminative.  Thus, when designing microtasks, one should give careful
-consideration to inter-task effects.  Unfortunately, we are not sure
-why certain initial tasks produced increased specificity as opposed to others, 
-and this is a question we intend to pursue in future research.
+We propose that, as a worker from \textit{task1:food} proceeds through the 
+initial tasks, food-related memories and concepts are activated, increasing 
+the likelihood that she uses a variety of food-related labels.  This accounts
+for the overall increases the number of food-related labels, as well as the 
+richness and specificity of her food-related vocabulary.  At the same time,
+since all images up to that point contained food, \textit{whether or not}
+an image contains food begins to appear non-salient, suppressing the most 
+generic references, such as ``food''.  Thus, there is a simultaneous emphasis of the specialized 
+references to the prime concept and de-emphasis of generic references.
 
-\paragraph{Conclusions.}
-Our results show that inter-task effects can have a strong influence on how 
-workers label images. In particular, we observed that prior tasks influence 
-the specificity and content of labels. Surprisingly, framing a task by 
-indicating a semantically-loaded funder had much milder effects on worker 
-outputs, generally below the statistical power of our tests.
+This view can account for the observation that there are fewer
+food-related references overall in \textit{task2:food} compared to 
+\textit{task2:cult}.  Workers in \textit{task2:food}, like those in 
+\textit{task1:food}, are primed to use
+specialized food references and negatively primed against using generic
+ones.  Then, when these workers encounter the test tasks, with images 
+containing more prominent cultural content, they attend to this novel content, 
+decreasing their balance of food references.  
+Meanwhile, workers in \textit{task2:cult}, having seen only cultural scenes,
+experience novelty from the appearance of food-oriented content in the test 
+tasks, and, attending to it, drive the relative difference in the quantity of 
+food-related labels further toward the negative in in 
+Fig.~\ref{fig:specificity}A.
 
-We therefore caution those designing studies using human computation: even if 
-the requester has eliminated surrounding influences to every practical extent, 
-\textit{the greatest source of bias might lurk in the tasks themselves}. Due 
-consideration should be given to how tasks are bundled together. While our 
-measurements of $\hat{\theta}_\mathrm{NB}$ indicated that inter-task effects 
-persisted even to the fifth test image, the most severe effects arise between 
-consecutive tasks.
+Based on these observations, we submit the following ideas for consideration 
+by the designers of crowdsourced initiatives.
+\begin{enumerate}
+	\item{
+		Training tasks should be preferred over examples, since the immediate
+		active use of information appears to increase its impact.
+	}
+	\item{
+		Training tasks should contain the same distribution of 
+		noise (or ``distracting features''), as the real dataset.
+		Exposing workers to irrelevant features, and identifying them as such,
+		will free up worker attention for salient features, by virtue of
+		negative priming.
+	}
+	\item{
+		\textit{Validation tasks}, for which the correct output is known,
+		are often used as a quality control measure.
+		These should be dually considered as \textit{calibration tasks}, and
+		should be designed to help workers maintain an optimally primed 
+		state. Feedback, for both correct and incorrect responses, 
+		may further reinforce salient features.
+	}
+	\item{
+		In many applications, such as the detection of pre-ictal 
+		(pre-seizure) EEG traces, workers encounter few positive examples
+		(most traces are not pre-ictal)(\#).  In the absence of positive 
+		examples, the target concept may degrade or drift.
+		Drawing calibration tasks from the underrepresented class may 
+		help sustain the target concept.
+	}
+	\item{
+		For the most precise classifications, it may be helpful to
+		begin with a coarse classification.  For example, workers could 
+		initially choose from  \texttt{class0}, \texttt{class1}, and 
+		\texttt{borderline}.  Following the coarse classification, the 
+		\texttt{borderline} examples could be batched together, allowing 
+		workers to focus on features that are only salient for such fine 
+		distinctions.
+	}
+\end{enumerate}
 
-Our proposed priming definition yields general purpose measure of priming 
-effects. We used three approaches to detect priming effects: 1) using a Naive 
-Bayes classifier to measure $\hat{\theta}_\mathrm{NB}$, 2) tallying the 
-number of culture- and food-oriented labels, and 3) comparing the relative
-specificity of labels based on an ontology. Of the three, $\theta_\mathrm{NB}$ 
-was the most sensitive.
+These recommendations follow logically from our observations, but they are 
+educated guesses.  We leave their direct testing to future work.
 
-In one sense, this is not surprising because the Naive Bayes classifier takes 
-into account the frequency of occurrence of all labels encountered during 
-training. But it is remarkable that the method which incorporates neither 
-prior knowledge about the image contents nor label semantics, outperforms 
-those that do. This is a powerful feature because, given the outputs from two 
-sets of workers, one can test whether they have been differently primed 
-without knowing how that priming might manifest.
+\paragraph{Conclusion.}
+Our results show that intertask effects are 
+as strong as framing effects, and are stronger when the frame is not echoed.
+Our analysis using wordnet reveals that intertask and framing effects
+act on workers' vocabulary in subtle ways.  Both exposure modalities 
+increased the richness of workers' vocabulary in reference to the prime 
+concept, but more so in the case of task-based exposure.  Both modalities 
+also increased the specialization of workers' vocabulary in reference to the 
+prime concept.
 
-Our algorithmic definition of priming is phrased in terms of worker outputs 
-rather than psychological phenomena. This provides a connection between the 
-priming effects and their potential to impact decisions made on the basis of 
-worker outputs. In the case of a 1-bit binary decision, $\theta$ describes the 
-worst-case bias introduced by failing to control for priming effects.
-
-Batching similar tasks together appears to yield higher more specific HPU 
-outputs. Our proposed connection between similarity and specificity during 
-image-labeling might be used to tune the specificity of labels. For example, 
-If one seeks very nuanced labeling, our results suggest that the images 
-should first be sorted into batches based on their similarity. This could be 
-accomplished by beginning with a first, coarse labeling of unsorted images, 
-followed by bundling based on the similarity of coarse labels. Then, bundles 
-of similar images could be served for a second round of finer labeling. The 
-sorting and re-labeling could in principle be repeated.
-
-Such a workflow involves serial processing, which points to an interesting 
-possible differ- ence difference between HPUs and CPUs. In general, whenever 
-an aspect of a problem can be parallelized when employing CPUs, one gains 
-efficiency. But here, because of HPU hysteresis, one might gain precision by 
-using HPUs with a more serialized algorithm. Further testing is needed to 
-determine the gain in precision from this approach.
+We recommend that intertask effects be considered when designing crowdsourced
+studies.  Despite efforts to eliminate biases from the context of tasks,
+the greatest source of biases may lurk in the tasks themselves.
+At the same time, their positive effects on workers' vocabulary suggest 
+that, when properly controlled, intertask effects may be
+used to optimize HPU performance.  Based on the enriching effects we observed
+for worker vocabulary, intertask effects might be leveraged to achieve 
+expert-level annotation in a wider variety of applications.
 

### 2014-11-25 docs/publications/2014.09_SCIENCE/man.tex
significant portion of supplementary material done

@@
 
+\usepackage{framed, color}
+\usepackage{soul}
+\definecolor{blu}{rgb}{0,0,1}
+\newcommand{\td}[1]{{\color{blu}\hl{TODO: #1}}}
 \usepackage{graphicx}
@@
 \cite{le2010ensuring,grady2010crowdsourcing,alonso2009can,kazai2013analysis}.
-Originally used to distribute clerical work, these platforms 
+Originally used to distribute clerical work (\#), these platforms 
 increasingly serve as a means to engage experimental participants in a 
@@
 Computer scientists view microtask platforms in the context of general
-computation.  In this regard, the platforms enable a tight integration of 
-human and machine computation.  Researchers coined the term HPU 
+computation(\#).  In this regard, the platforms enable a tight integration of 
+human and machine computation(\#).  Researchers coined the term HPU 
 (Human co-Processing Unit) in analogy to CPUs and GPUs \cite{5543192}.  
@@
 But the ability to program with high-level human instructions comes with a 
-cost: HPU output is inherently noisy.  Part of this noise can be explained
+cost: HPU output is inherently noisy (\#).  Part of this noise can be explained
 in terms of worker demography (\#).  But systematic cognitive biases also 
@@
 Here we describe a series of experiments, using the Amazon Mechanical
-Turk (MTurk) microtask platform, in which we studied intertask effects
+Turk (MTurk) microtask platform (\#), in which we studied intertask effects
 for image-labeling tasks.  Image-labeling tasks are among the most 
@@
 The initial tasks were chosen to embed a certain \textit{prime concept}.
-In our first experiment, our prime concepts were \textit{food} and (non-food) 
-\textit{objects}.  In our second experiment, the prime concepts were 
-\textit{food} and \textit{culture}.  The test tasks for the experiments used 
-images that combined both prime concepts used in the initial tasks. Workers 
-participated in only one treatment of one experiment, and were randomly 
-assigned initial tasks based on one of the 
-prime concepts.  From the perspective of the worker, we made no distinction 
-between the initial tasks and test tasks.
+Our first experiment compares the prime concepts \textit{food} and (non-food) 
+\textit{objects}, while our second experiment compares \textit{food} and 
+\textit{culture}.  For both experiments, The test tasks used images that
+combined both prime concepts used for the initial tasks \td{reword}.  Workers participated 
+in only one treatment of one experiment, and were randomly assigned initial 
+tasks based on one of the prime concepts.  From the perspective of the worker, 
+we made no distinction between the initial tasks and test tasks.
 
 As a point of comparison, we included treatments in which we induced
-\textit{framing}.
+\textit{framing}. \td{what is framing?}
 In the framing treatments, before workers begin the tasks, we told them that 
@@
 perception of ``objects and tools'' in another.  We varied the language of 
-the framing text (hereafter simply the \textit{frame}), and experimented with 
-requiring the worker to echo the frame using a combo-box input.
+the framing text (hereafter simply the \textit{frame}), and for some treatments
+we required the worker to echo the frame using a combo-box input.
 
@@
 	\centering
-	\includegraphics[scale=0.7]{figs/images.jpg}
+	\includegraphics[scale=0.7]{figs/images.pdf}
 	\caption{
@@
 		F) \textit{exp2}.  The full set of experimental materials is 
-		shown in the supplementary material.
+		shown in the supplementary material (S1).
 	}
@@
 collection of 
-experimental materials is presented in the supplementary material.  We 
+experimental materials is presented in the supplementary material (S1).  We 
 ensured that all workers only participated in one treatment of one experiment.
 
-\setlength{\tabcolsep}{3pt}
+\setlength{\tabcolsep}{2pt}
 \begin{table}[t]
@@
 
-\subsection*{Assessing task similarity}
+\subsection*{S1: Experimental materials}
+The tasks for both experiments were presented as a series of slides.  In
+both cases, the first slide consisted of a brief set of instructions, followed
+by the frame if shown (only some treatments involved a frame), see 
+Fig. S\ref{fig:hit_preamble}.  Following the instructions and prime, a set
+of initial tasks was shown (except for the treatments in \textit{frame2}
+and \textit{echo}) followed by (in all cases) a set of test tasks.  In
+\textit{exp1}, two kinds of frame were used, one simple frame, and one where
+the worker was required to echo the frame using a combo-box input.  The
+instructions, both kinds of frame, and an example task slide, are shown 
+in Fig. S1.
+\begin{figure}
+	\includegraphics[scale=0.8]{figs/tasks.pdf}
+	\label{fig:hit_preamble}
+	\caption{Examples of A) instructions; B) a frame, as shown in 
+		\textit{frame1:obj}, and similar to those shown in 
+		\textit{frame1:food} and \textit{frame2:food}, and 
+		\textit{frame2:cult};  
+		C) an echoed frame, as used in \textit{echo:obj}, and similar to that
+		used in \textit{echo:food}; and D) an 
+		example of an image labeling task.
+	}
+\end{figure}
+
+All of the initial tasks had the format shown in Fig. S1D.  The images used
+in the initial tasks for \textit{task1:food} and \textit{task1:obj} are
+shown in Fig. S2 and S3, and the images used in the test tasks for 
+\textit{exp1} are shown in Fig. S4.  The images used in the initial tasks
+for \textit{task2:food} and \textit{task2:cult} are shown in Fig. S5 and
+Fig. S6 respectively, and the images used in the test tasks for \textit{exp2} 
+are shown in Fig. S7.
+
+\begin{figure}
+	\includegraphics{figs/task1-food.pdf}
+	\label{fig:task1:food}
+	\caption{
+		Figure S2: Images used in the initial tasks for 
+		\textit{task1:food}.  The numbers show the order in which the 
+		images were presented to workers.
+	}
+\end{figure}
+
+\begin{figure}
+	\includegraphics{figs/task1-obj.pdf}
+	\label{fig:task1:obj}
+	\caption{
+		Figure S3: Images used in the initial tasks for 
+		\textit{task1:obj}.  The numbers show the order in which the 
+		images were presented to workers.
+	}
+\end{figure}
+
+\begin{figure}
+	\includegraphics{figs/task1-test.pdf}
+	\label{fig:task1:test}
+	\caption{
+		Figure S2: Images used in the test tasks for 
+		\textit{exp1}.  The numbers show the order in which the 
+		images were presented to workers.
+	}
+\end{figure}
+
+\begin{figure}
+	\includegraphics{figs/task2-food.pdf}
+	\label{fig:task2:food}
+	\caption{
+		Figure S2: Images used in the initial tasks for 
+		\textit{task2:food}.  The numbers show the order in which the 
+		images were presented to workers.
+	}
+\end{figure}
+
+\begin{figure}
+	\includegraphics{figs/task2-cult.pdf}
+	\label{fig:task2:cult}
+	\caption{
+		Figure S2: Images used in the initial tasks for 
+		\textit{task2:cult}.  The numbers show the order in which the 
+		images were presented to workers.
+	}
+\end{figure}
+
+\begin{figure}
+	\includegraphics{figs/task2-test.pdf}
+	\label{fig:task2:test}
+	\caption{
+		Figure S2: Images used in the test tasks for 
+		\textit{exp2}.  The numbers show the order in which the 
+		images were presented to workers.
+	}
+\end{figure}
+
+\subsection*{S2: Access to raw data and code}
+The raw data and source code needed to reproduce the analyses 
+shown here and in the main text can be downloaded from 
+http://networkdynamics.org/publications/public/priming2014.09.
+
+\subsection*{S3: Additional results not shown in the main text}
+\begin{itemize}
+	\item{
+		the top 5 most suppressed and most activated terms between treatment
+		pairs.
+	}
+\end{itemize}
+
+\subsection*{S4: Data preprocessing}
+	\paragraph{Splitting, Lemmatization, removal of stop-words, and 
+		addition of position tags.}
+
+	Before performing any analysis on the labels that workers provided, we
+	performed a series of preprocessing steps.  
+	\td{does this reflect the actual order in which the steps were done?}
+	First, words wore lematized 
+	using the
+	\td{whatzit} lemmatizer.  This lemmatizer is very mild, tending only to 
+	change plural words to their singular form.  Common
+	words such as ``the'', ``to'', or ``with'', were found using the
+	the \td{whatzit} stop-word list and removed.  Then, misspelled words were
+	automatically corrected using a spelling correction algorithm described 
+	below.  Finally, labels that contained
+	multiple words (separated by spaces or punctuation) were split, with
+	punctuation removed, and the separated words were treated as distinct 
+	features in subsequent analysis.
+
+	For the purpose of training and testing a naive Bayes classifier, we 
+	performed an additional preprocessing step.  We tagged words with the
+	position in which they had been entered (i.e. which of the five text 
+	inputs in the task interface) as well as the test tasks in which the word 
+	had been provided.
+	So, if the word ``wine'' was entered into the second text-input for 
+	the third test-task, after preprocessing, the feature ``3\_2\_wine'' would
+	appear.  Prepending the task number onto words was simply a means to 
+	retain correct attribution, which itself was essential since providing a
+	word during one task is not equivalent to providing the same word during 
+	another task.
+
+	\paragraph{Spelling correction.}  
+	Spelling correction was performed using an algorithm that first detected
+	if a word was likely to be misspelled, then generated a set of candidate 
+	corrections, and chose the best candidate based on a scoring mechanism.
+
+	A word was considered misspelled if it was not contained in the 
+	\textit{legal set}, which was formed by the union of
+	the wordnet corpus, the stop-word list, and a set of words seen while 
+	crawling the world food section of the allrecipes.com website.  We
+	describe the crawling of the allrecipes.com website in a section below.
+
+	To correct misspellings, we first produced all possible modified forms 
+	that could be obtained applying one or two edits.  An edit consisted of 
+	adding or removing a letter, changing one letter into another, or 
+	swapping the positions of two adjacent letters.  For the purpose of these 
+	edits, spaces were treated as any other letter.
+
+	The candidates produced by these edits which were in the legal set were
+	then ranked based on a scoring mechanism, and the highest scoring word
+	was chosen as the correction.  A candidate $w$'s score, $s_w$, was 
+	calculated according to the following formula:
+	\begin{equation}
+		s_w = (f_w + 1) * p_1 * p_2,
+	\end{equation}
+	where $f_w$ is the frequency with wich the word occured (correctly 
+	spelled)
+	within the given task, $p_1$ was a penalty for the first edit, and
+	$p_2$ was a penalty for the second edit.  If the word was made using only
+	one edit, then $p_2 = 1$.  Any edit that did not involve adding a space
+	(i.e. separating a word) incured a penalty of 0.5, while the addition of
+	a space incurred a penalty of 0.1.  Word-separation edits were more 
+	strongly penalized because it is often possible to split a series of 
+	letters into many short two- or three-letter words, which otherwise leads 
+	to many erroneous corrections.  We found that setting the penalty for
+	word splitting at 0.1 worked well by testing on words taken from
+	initial tasks.
+
+	After all of our analyses had been performed, we checked the accuracy of 
+	the spelling correction algorithm using three human coders.  The coders
+	were shown a set of 
+	500 words that were randomly sampled from the labels attirubuted during 
+	test tasks (50 for each test task).  Before sampling, the labels from all
+	experimental treatments, for the given test task, were pooled together.
+	The coders did not know which treatment any given word came from.  
+	In addition to the words, coders were shown the spelling correction 
+	produced by the algorithm, as well as the image from the test task.
+	The coders were asked to identify any misspelled words which had not 
+	been corrected, as well as any corrections that appeared to be erroneous,
+	by indicating their own correction.
+
+	Based on this exercise, we found that, according to the human coders,
+	17\% of the words were misspelled, but that after applying the 
+	automated spelling correction, only 3.2\% of words were misspelled.
+
+	\paragraph{Crawling the world food section of allrecipes.com.}
+	The website allrecipes.com was accessed on 3-4 November 2014 using 
+	automated scripts.  A total of 2642 recipe listings and 15621 recipe
+	instruction pages were crawled.  Recipe listings were pages that provided 
+	lists of recipes, and contained a title and short description for each.  
+	The recipe instruction pages had lists of ingredients and preparation 
+	instructions.  All of the words found in recipe titles, short
+	descriptions, ingredients lists, and preparation instructions were
+	collected, and saved as an auxiliary set to aument the \textit{legal set}
+	used in spelling correction.
+
+\subsection*{S5: Identification of food-related terms}
+The wordnet corpus is composed of synsets, which are particular senses 
+(meanings) and a set of word forms bearing that meaning. A given word form, 
+such as ``ring'' has multiple senses (``to ring a bell'', ``a wedding ring''), 
+and so can be part of many synsets.  Since the wordnet corpus was designed
+to carry semantic information, the synset is the basic organizing element
+of wordnet.
+
+We chose the synsets \textit{food.n.01} and \textit{food.n.02} to act as roots
+in defining which words should be considered food-related.  Any word form
+belonging to a synset which was a hyponym of one of the two root synsets
+identified above was considered to be a reference to food.  Here, as in the
+main text, when we say hyponym, we mean either a direct hyponym, or a hyponym
+of a hyponym, and so on.
+
+This is a stringent notion of a word being a food reference.  It roughly
+corresponds to whether or not a given thing is reasonably considered 
+consumable.  So, ``orange'' is food, but ``salty'' is not.  Although ``salty''
+would usually refer to something edible, it is not itself an edible thing.
+On the other hand, ``salt'' would be considered a reference to food under 
+this operationalization.
+
+The subset of the wordnet corpus induced by the hyponyms of \textit{food.n.01}
+and \textit{food.n.02} provide an extensive set of \td{X} words.  Manual
+testing appeared to show that the coverage was very extensive, except in 
+some cases references to ethnic foods were missing.  Since, especially in
+\textit{exp2} we had images containing many ethnic foods, we decided to 
+augment the wordnet corpus with words learned by crawling the world food
+section of the allrecipes.com website.
+
+After collecting a set of words using an automated script 
+(\td{described above}), we collected the set of words that had been used by
+workers and which had been seen during crawling of the allrecipes.com website,
+but which were not included in wordnet.  We graphted these extra words into
+the wordnet hyponym-hypernym graph manually, which ensured that any references
+to ethnic words learned from crawling would be properly classified as 
+food references.
+
+\paragraph{Validation of the detection of food references.}
+To determine whether our extended version of wordnet provided a good approach
+to detecting food-related words, we sampled 500 words from the set of labels
+produced by workers and had three human coders manually decide if they were 
+food-related or not.  The method for randomly sampling the 500 words was 
+described in above in \td{section number}.
+
+The coders were instructed to consider whether a word was a noun signifying
+an edible item.  The guiding principle was, for the coder to ask herself,
+``can I eat this X'', where X is the word she is coding.  The coders were
+shown the used in the task from which the word came, to help resolve ambiguity
+in the sense of the word that had been given.  Coders were also shown the 
+spelling correction (if any) that the spell-correction algorithm had made,
+to help interpret mispelled words \td{we describe the spelling correction 
+algorithm in section X}.
+
+We evaluated the food detection algorithm in two ways.  First, we measured
+the inter-rater reliability between the three human coders and the algorithm
+(treating the algorithm just like any other coder).  Second, adopting the 
+majority code given by the human coders, we determined the accuracy of the
+food-detection algorithm.  Data sumarizing this validation process are given
+in table S1.
+
 \begin{table}
 \centering
-\begin{tabular}{ l  s s s s}
-
+\setlength{\tabcolsep}{12pt}
+\begin{tabular}{ r | c }
 \toprule    
-Image set   
-& \multicolumn{1}{c}{Ambig.} 
-& \multicolumn{1}{c}{Cultural} 
-& \multicolumn{1}{c}{Ingr.}
-& \multicolumn{1}{c}{Test} \\
-
-\midrule
-
-Ambiguous  & 1 & 0.0418 & 0.142 & 0.167 \\
-
-Cultural  & 0.0418  & 1 & 0.0347 & 0.0561 \\
-
-Ingredients  & 0.142  & 0.0347 & 1 & 0.110 \\
-
-Test & 0.167  & 0.0561 & 0.110 & 1
-\\
+\# terms coded & 500 \\
+\# food references & 130 \\
+\# correct machine codes & 440 \\
+inter-rater reliability & 82.4\% \\
+human-machine code agreement & 88\% \\
+%machine recall & 80 \% \\
+%machine precision & 75.4 \% \\
+%machine code F1 & 0.78 \\
 \bottomrule
-
 \end{tabular}
 \caption{\footnotesize{
-Pairwise similarities of each image set based on the labels attributed to them (see \textbf{Eq. 4}).
+	\td{remove the automatic numbering}. Table S1. Results for the validation 
+	of the automatic detection of food references, by comparison to
+	human-generated coding on randomly sampled words.  In calculating the 
+	human-machine code agreement, the majority human code was used.
+	Inter-rater reliability was calculated as Krippendorff's alpha.
 }}
-\label{table:2}
 \end{table}
 
-One weakness of the above analysis is the reliance on the informal notion
-of the similarity of one set of images to another. The 
-characterization of image content is a deeply complex issue that has been 
-approached by many disciplines \cite{panofsky1939studies,shatford1986analyzing,Tversky1977327,Jaimes20002}. \textit{Perceptual similarity} is a 
-particularly recalcitrant concept.   But to formalize our claim, we seek a 
-measure of similarity between two sets of images, 
-\textit{with respect to the labeling task}.  This can be operationalized
-in a straightforward way, by using the similarity of the labels given to images
-as a proxy for the similarity of the images.  Thus, to measure the 
-similarity between two sets of images, X and Y , we computed the Jacquard 
-index between the sets of labels attributed to them:
-$$
-	\mathrm{Sim}(X,Y) = \frac{L(X) \cap L(Y)}{L(X) \cup L(Y)}
-$$
-where $L(X)$ denotes the set of labels attributed to images in $X$.
+The results show that good inter-rater reliability was achieved during the
+validation (82.4\%).  Looking at the agreement between the 
+machine codes and the majority human-generated codes, we find they agree
+88\% of the time.  This means that the concept used to instruct human coders
+provides a good approximation to what the wordnet-based machine codes actually
+represent. In other words, the machine codes correspond closely to indicating
+which words correspond to nouns that refer to edible things, and which ones
+don't, which provides a clear and simple interpretation for the machine
+coding of food and non-food words.
 
-The pairwise similarities of the image sets are presented in Table 2. This 
-shows that the workers that yielded higher specificity labels were from 
-treatments whose initial tasks were more similar to the test tasks (c.f.
-\textbf{Fig 3}).
+\subsection*{S6: Calculation of relative specificity}
+In the main text we present results for the relative specificity of labels
+produced by two experimental treatments.  In performing this calculation,
+we used the wordnet corpus, which has a set of hypernym-hyponym relationships
+as described in the main text.  The first step in performing this calculation
+was therefore to map the words occuring from (the labels of) a given 
+experimental treatment onto the wordnet synsets.  In general, a given word
+form can have multiple meanings, and therefore maps onto multiple wordnet 
+synsets.
 
-Such a phenomenon would be consistent with the psychological mechanism known as
-\textit{negative priming}.
+The result of mapping the words from two treatments onto the wordnet 
+hypernym-hyponym graph two sets of counts, one set per treatment, 
+indicating the number of times a word from a given synset occured among the
+labels of the treatment.  Then, for every synset in one treatment, we looked
+at the number of synsets in the other treatment that were more generic
+(reachable by following hypernym relations) less the number of words that
+were more specific (reachable by following hyponym relations).  This quantity
+tallied for all words in the original synset gives a (non-normalied) measure
+of the degree to which words from the first treatment are more specific
+than words from the second treatment, overall.  We then normalized this 
+quantity by the total number of possible comparisons between the words of
+one treatment to those of the other, where two words are considered comparable
+only if one word is the hypernym or hyponym of the other.  Hence, ``statue'' 
+and ``bread'' are not comparable, but ``pumpernickel'' and ``bread'' are.
+
+This calculation can be summarized by the following equation:
+\begin{equation}
+	S(P,Q) = \frac{
+		\sum_{w\in P}\sum_{v\in Q} \left(
+			\mathbf{1}_{[w>v]} - \mathbf{1}_{[v>w]} \right)
+	}{
+		\sum_{w\in P}\sum_{v\in Q} \left(
+			\mathbf{1}_{[w>v]} + \mathbf{1}_{[v>w]} \right)
+	},
+\end{equation}
+where $P$ and $Q$ are sets of synsets, and $\mathbf{1}_{[w>v]}$ evaluates
+to 1 if synset $w$ is more specific than (i.e. is a hyponym of) synset $v$.
+This measure counts the excess of cases where synsets from $P$ are more
+specific then synsets from $Q$, as a fraction of all comparable synset pairs.
+
+In computing this quantity between two treatments, we first computed it 
+using the labels attributed to a particular test task, and then
+averaged the result obtained in this way for each of the five test tasks.
+
+\subsection*{S7: Analysis of variance}
+\begin{itemize}
+	\item{
+		classifier accuracy.  Why we used a one-tail CI.  
+		Why certain error bars are smaller.
+	}
+	\item{error in $\delta$ \%food.}
+	\item{error in size of food vocabulary}
+	\item{error in food specificity}
+\end{itemize}
+
+\subsection*{S8: Measuring computational hysteresis}
+\begin{itemize}
+	\item{principled use of cross-validation without optimization.}
+	\item{Adopting Naive Bayes due to the lack of optimization required.}
+	\item{
+		Usage of a principled set of pre-processing and representation 
+		techniques.
+	}
+	\item{
+		Comparison to other choices of representation
+	}
+	\item{
+		Comparison to SVM classifier
+	}
+	\item{
+		Reiterate why we cannot report optimized results.
+	}
+\end{itemize}
+
+\subsection*{S9: Justifications and statistical properties of classifier-based measurement of computational hysteresis}
+\begin{itemize}
+	\item{Relationship to L1-Distance}
+	\item{Relationship to bias}
+	\item{Relationship to Jenson-Shannon divergence}
+	\item{Other approaches to measuring L1-distance}
+	\item{Comparison to hypothesis testing using $\chi^2$}
+\end{itemize}
+
+%\subsection*{Assessing task similarity}
+%\begin{table}
+%\centering
+%\begin{tabular}{ l  s s s s}
+%
+%\toprule    
+%Image set   
+%& \multicolumn{1}{c}{Ambig.} 
+%& \multicolumn{1}{c}{Cultural} 
+%& \multicolumn{1}{c}{Ingr.}
+%& \multicolumn{1}{c}{Test} \\
+%  
+%\midrule
+%
+%Ambiguous  & 1 & 0.0418 & 0.142 & 0.167 \\
+%
+%Cultural  & 0.0418  & 1 & 0.0347 & 0.0561 \\
+%
+%Ingredients  & 0.142  & 0.0347 & 1 & 0.110 \\
+%
+%Test & 0.167  & 0.0561 & 0.110 & 1
+%\\
+%\bottomrule
+%
+%\end{tabular}
+%\caption{\footnotesize{
+%Pairwise similarities of each image set based on the labels attributed to them (see \textbf{Eq. 4}).
+%}}
+%\label{table:2}
+%\end{table}
+%
+%One weakness of the above analysis is the reliance on the informal notion
+%of the similarity of one set of images to another. The 
+%characterization of image content is a deeply complex issue that has been 
+%approached by many disciplines \cite{panofsky1939studies,shatford1986analyzing,Tversky1977327,Jaimes20002}. \textit{Perceptual similarity} is a 
+%particularly recalcitrant concept.   But to formalize our claim, we seek a 
+%measure of similarity between two sets of images, 
+%\textit{with respect to the labeling task}.  This can be operationalized
+%in a straightforward way, by using the similarity of the labels given to images
+%as a proxy for the similarity of the images.  Thus, to measure the 
+%similarity between two sets of images, X and Y , we computed the Jacquard 
+%index between the sets of labels attributed to them:
+%$$
+%	\mathrm{Sim}(X,Y) = \frac{L(X) \cap L(Y)}{L(X) \cup L(Y)}
+%$$
+%where $L(X)$ denotes the set of labels attributed to images in $X$.
+%
+%The pairwise similarities of the image sets are presented in Table 2. This 
+%shows that the workers that yielded higher specificity labels were from 
+%treatments whose initial tasks were more similar to the test tasks (c.f.
+%\textbf{Fig 3}).
+%
+%Such a phenomenon would be consistent with the psychological mechanism known as
+%\textit{negative priming}.
 

### 2014-11-25 src/analysis.py

@@ -84,6 +84,169 @@ class AnalysisError(Exception):
 	pass
 
 
+def assess_raters(
+		read_fname='data/new_data/food_coding_test/all_raters.csv',
+		write_fname='data/new_data/food_coding_test/rater_assessment.json'
+	):
+	'''
+		Calculate interrater reliability, and accuracy for the food coding
+		and spelling correction.
+	'''
+
+	rater_test_fh = open(read_fname)
+	rater_test = csv.reader(rater_test_fh)
+	rater_assessment_fh = open(write_fname, 'w')
+
+	# skip the line containing column headings
+	rater_test.next()
+
+	num_terms = 0
+	num_food_terms = 0	# based on majority human-coder consensus
+	num_misspelled = 0
+	num_machine_corrections = 0
+	num_machine_should_not_have_corrected = 0
+	num_correct_machine_corrections = 0
+	TP = 0				# True positives for machine classification as food
+	FP = 0				# False positives
+	TN = 0				# True negatives
+	FN = 0				# False negatives
+	num_correct_machine_food_ratings = 0	# machine tries to detect food
+	num_correct_machine_interp = 0			# machine recognizes words and 
+											# tries to interpret misspellings
+	for row in rater_test:
+
+		# parse the row
+		term, machine_correction = row[:2]
+		human_food_ratings = [t.strip() for t in row[2:5]]
+		machine_food_rating = row[5]
+		human_corrections = row[6:]
+
+		# is the majority rating food, and does the machine coding match?
+		num_positive_human_ratings = sum(
+			[int(fr.strip()=='y') for fr in human_food_ratings])
+		num_terms += 1
+		if num_positive_human_ratings > 1:
+			num_food_terms += 1
+			if machine_food_rating == 'y':
+				TP += 1
+				num_correct_machine_food_ratings += 1
+			else:
+				FN += 1
+
+		else:
+			if machine_food_rating == '':
+				TN += 1
+				num_correct_machine_food_ratings += 1
+			else:
+				FP += 1
+
+		# get the term that the machine used
+		machine_accepted = (machine_correction or term).strip()
+		human_accepted = [hc.strip() for hc in human_corrections]
+
+		# if the machine made a correction
+		if machine_correction.strip():
+			# but the humans think it was okay
+			if sum([hc == term for hc in human_accepted])>1:
+				num_machine_should_not_have_corrected += 1
+			# and the humans agree it needs correcting
[…]

### 2014-11-25 src/wordnet_analysis.py

@@ -78,7 +78,6 @@ class ExtendedWordnet(object):
 
 		# add the synset for new_word to the hyponyms of its parent
 		altered_synset._hyponyms.append(self.new_words[new_word])
-		print altered_synset.hyponyms()
 
 		# register the altered synset
 		self.altered_synsets[syn_spec] = altered_synset
@@ -488,12 +487,10 @@ def calculate_relative_specificity(
 	but gives the same result.
 	'''
 
-	print len(word_counts_1), len(word_counts_2)
 	word_counts_1 = filter_word_counts(
 		word_counts_1, include_food, include_nonfood)
 	word_counts_2 = filter_word_counts(
 		word_counts_2, include_food, include_nonfood)
-	print len(word_counts_1), len(word_counts_2)
 
 	synset_counts_1 = map_to_synsets(word_counts_1)
 	synset_counts_2 = map_to_synsets(word_counts_2)
@@ -606,8 +603,6 @@ class WordnetFoodDetector(object):
 			# each child returns a list, flatten this to one list
 			child_results = reduce(lambda x,y: x + y, child_vals, [])
 
-			print this_result + child_results
-
 			return this_result + child_results
 
 		def abort_branch_callback(node):
@@ -692,15 +687,12 @@ class WordnetRelativesCalculator(object):
 			node_name = node.name
 
 			if node_name in self.num_relatives_cache:
-				# print node_name, '(:)', self.num_relatives_cache[node_name]
 				return self.num_relatives_cache[node_name]
 
 			cur_node_val = synset_counts[node_name] + sum(child_vals)
 
 			# cache this for next time
 			self.num_relatives_cache[node_name] = cur_node_val
-
-			# print node_name, ' : ', cur_node_val
 
 			return cur_node_val 
 

### 2014-11-26 docs/publications/2014.09_SCIENCE/man.tex
improve .gitignore

@@
 \subsection*{S3: Additional results not shown in the main text}
-\begin{itemize}
-	\item{
 		the top 5 most suppressed and most activated terms between treatment
 		pairs.
-	}
-\end{itemize}
+
+\begin{table}
+	\centering
+	\setlength{\tabcolsep}{10pt}
+	\begin{tabular}{ c c c c c }
+
+		\setlength{\tabcolsep}{4pt}
+		\begin{tabular}{ r | c }
+		\toprule
+		\multicolumn{2}{c}{\textit{task1}} \\
+		\toprule
+		coffee & 38 \\
+		meal & 34 \\
+		cheese & 34 \\
+		apple & 32 \\
+		dessert & 21 \\
+		cup & -30 \\
+		glass & -45 \\
+		table & -70 \\
+		candle & -74 \\
+		food & -80 \\
+		\bottomrule
+		\end{tabular}
+
+&
+
+		\setlength{\tabcolsep}{4pt}
+		\begin{tabular}{ r | c }
+		\toprule
+		\multicolumn{2}{c}{\textit{frame1}} \\
+		\toprule
+		bread & 18 \\
+		wine & 18 \\
+		cheese & 16 \\
+		apple & 14 \\
+		oil & 12 \\
+		table & -9 \\
+		meal & -10 \\
+		candle & -12 \\
+		dinner & -13 \\
+		food & -32 \\
+		\bottomrule
+		\end{tabular}
+
+&
+
+		\setlength{\tabcolsep}{4pt}
+		\begin{tabular}{ r | c }
+		\toprule
+		\multicolumn{2}{c}{\textit{echo}} \\
+		\toprule
+		apple & 24 \\
+		cheese & 23 \\
+		wine & 15 \\
+		coffee & 14 \\
+		oil & 7 \\
+		knife & -24 \\
+		dinner & -26 \\
+		fork & -27 \\
+		candle & -35 \\
+		food & -55 \\
+		\bottomrule
+		\end{tabular}
+
+&
+
+		\setlength{\tabcolsep}{4pt}
+		\begin{tabular}{ r | c }
+		\toprule
+		\multicolumn{2}{c}{\textit{task2}} \\
+		\toprule
+		spicy & 26 \\
+		sauce & 17 \\
+		indian & 15 \\
+		buffet & 14 \\
+		exotic & 12 \\
+		festival & -11 \\
+		offering & -12 \\
+		statue & -15 \\
+		india & -20 \\
+		food & -56 \\
+		\bottomrule
+		\end{tabular}
+
+&
+
+		\setlength{\tabcolsep}{4pt}
+		\begin{tabular}{ r | c }
+		\toprule
+		\multicolumn{2}{c}{\textit{frame2}} \\
+		\toprule
+		indian & 11 \\
+		banquet & 8 \\
+		spicy & 7 \\
+		asian & 6 \\
+		variety & 6 \\
+		delicious & -6 \\
+		meat & -7 \\
+		festival & -7 \\
+		spice & -7 \\
+		food & -9 \\
+		\bottomrule
+		\end{tabular}
+
+	\end{tabular}
+	\caption{blah}
+\end{table}
 
@@
 \begin{itemize}
-	\item{principled use of cross-validation without optimization.}
+	\paragraph{Using cross-validation accuracy to lower-bound L1-distance.}
+	In order for Eq.~\ref{l1} to be applicable, it is necessary to obtain
+	an unbiased estimate of a classifier's performance.  One well-known
+	pitfall in measuring this error is to underestimate it due to 
+	over-fitting of the data used.  As an example, if one were to try 
+	a large number of classifiers, eventually one would find one that
+	classifies the data perfectly, even though it might non generalize to
+	new data.
+
+	It is customary to use part of a data set to optimize hyperparameters of
+	a model, and then test the model on as-yet unseen data.  In our case,
+	don't have enough samples in each treatment to do this.  Instead, for 
+	this reason, we make principled decisions for all of the options used
+	in our classifier, and then test it's accuracy using cross validation,
+	with no optimization performed on the data.  It was cruicial for 
+	the statistical validity of our approach that we test our classifier on 
+	each datum only once, and report these results without any optimizations
+	of the classifier.
+
+	In performing the classification we had various options, and since we
+	could not optimize these choices, we made principled decisions based on
+	prior knowledge from text classification applications.  We describe the
+	options we faced and the choices we made below.
+
+	\textit{whether to correct misspelled words.}  Because we used free-text
+	entry for the labels, there was bound to be many spelling mistakes.
+	This would tend to reduce the accuracy of a classifier, because the 
+	entries ``bread'' and ``braed'' would be regarded as completely different
+	features, even though they clearly correspond to the same 
+	\textit{intended word}.  While no algorithm can determine a worker's 
+	intentions, it is possible to check words against a corpus, and, in the
+	case of a misspelled word, look for plausible corrections based on 
+	edit distance.
+
+	\textit{Whether to split multiple words.}  Although workers were 
+	instructed to put one word per text input, many put multiple words.
+	Theoretically the original multi-word entry might bear additional 
+	information that could be useful in discerning a worker's exposure. 
+	In practice, it would be necessary for that word combination to recur,
+	which is unlikely.  Therefore we chose to split multi-word entries,
+	using the individual words as features.  This meant that the outputs of
+	some workers generated more features than those of others.
+
+	\textit{Lemmatization.}  In some cases it is helpful to simplify words 
+	before providing them to the classifier.  For example, the words 
+	``berries'' and ``berry'' only differ in number, but would normally be
+	treated as completely different features.  Lemmatization ensures that
+	nouns are in their sigular form, which helps to eliminate variations in
+	labels that increase sparsity without conveying discriminative 
+	information.
+
+	\textit{Removal of stop-words.}  Certain very common words such as `the',
+	``to'', and ``it'' are extremely common but don't help discriminate a 
+	worker's exposure.  Removing these words is a common practice because
+	they otherwise introduce noise into the classifier learning process.
+
+	the were many
+	missipellings
+
+		\item{whether to split multiple words 
+	\end{itemize}
+
+	opt for a one-shot approach where we do not optimize any 
 	\item{Adopting Naive Bayes due to the lack of optimization required.}

### 2014-11-26 src/analysis.py

@@ -60,7 +60,6 @@ EXP2_TREATMENTS = {
 	'echo:obj': [13],
 }
 
-
 PAIRS = [
 	[
 		('task2:food', 'task2:cult'),
@@ -82,6 +81,9 @@ COMPARISONS = [
 
 class AnalysisError(Exception):
 	pass
+
+
+
 
 
 def assess_raters(

### 2014-11-26 src/new_plots.py

@@ -35,6 +35,58 @@ DATA_DIR = 'data/new_data'
 FIGS_DIR = 'figs/'
 
 
+def delta_counts_to_table(
+		read_fname = 'data/new_data/delta_counts.json',
+		write_fname = 'data/new_data/delta_counts_tables.txt'
+	):
+	'''
+		writes the delta food out as latex tables
+	'''
+
+	# open files
+	data = json.loads(open(read_fname).read())
+	write_fh = open(write_fname, 'w')
+
+	START_TABLE_SERIES = r'''
+	\setlength{\tabcolsep}{12pt}
+	\begin{tabular}{ c c c c c }
+	'''
+
+	END_TABLE_SERIES = r'''
+	\end{tabular}'''
+
+	START_TABLE = r'''
+		\setlength{\tabcolsep}{2pt}
+		\begin{tabular}{ r | c }
+		\toprule
+		\multicolumn{2}{c}{\textit{%s}} \\
+		\toprule'''
+
+	END_TABLE = r'''
+		\bottomrule
+		\end{tabular}'''
+
+	pairs = ['task1', 'frame1', 'echo', 'task2', 'frame2']
+	first = True
+	write_fh.write(START_TABLE_SERIES)
+	for pair_name in pairs:
+		deltas = data[pair_name]
+
+		if first:
+			first = False
+		else:
+			write_fh.write('\n&\n')
+
+		write_fh.write(START_TABLE % pair_name)
+
+		for word, delta_count in deltas:
+			write_fh.write('\n\t\t%s & %d \\\\' % (word, delta_count))
+
+		write_fh.write(END_TABLE + '\n')
+
+	write_fh.write(END_TABLE_SERIES)
+
+
 def plot_longit_vocab(
 		read_vocab_fname = 'data/new_data/vocabulary.json',
 		write_fname = 'figs/longit_vocab.pdf'

### 2014-12-03 docs/publications/2014.09_SCIENCE/man.tex
re-map figs symlink
substancially shorten science manuscript

@@
 
-Microtask platforms combine the efforts of large numbers 
-of people to perform tasks that are difficult to automate with computers 
-alone.  These platforms support near-real-time task completion, mimicking a
-compute server, and shift the role of the human from consumer to 
-producer of computing resources.  To realize its full
-potential, we must understand how human computation differs from machine 
-computation, and address the biases inherent in 
-human cognition.  The effects of various task-design variables on worker
-performance have been investigated, but there has been little 
-investigation into how consecutive tasks influence one another. Here we show 
-that the responses in later tasks are strongly influenced by the content of 
-earlier ones, an effect that is as strong or stronger than the effect of 
-framing.  Our findings are not solely cautionary; we find
-that these \textit{intertask effects} can be harnessed to improve the quality 
-of responses, and might thereby help to achieve expert-level judgments in 
-citizen science and other crowdsourcing initiatives. 
-As an ancillary contribution, we demonstrate the use of machine learning 
-algorithms measure exposure-induced human bias, in terms of its ability to 
-influence human computations. 
+Faced with the scale and complexity of the data revolution, researchers and
+industry are increasingly relying on \textit{human computation}.  Microtask
+platforms, like Amazon Mechanical Turk, act like a human compute server,
+making it possible to access human cognition quickly and inexpensively. 
+This has lead to broad adoption across a spectrum of disciplines
+in the humanities and computer science, in research into medical imaging
+technologies, and in many applications where expert opinion would normally be 
+sought.  Here we show that an inherent
+feature of microtask platforms, the repetition of similar tasks,
+acts as a strong, but as yet unexplored source of bias.  
+These \textit{intertask effects}, rival the
+severity of overtly framing a task's purpose.  
+Using image labeling as a canonical microtask, we found that prior 
+tasks influences the vocabulary that a worker uses when labeling 
+subsequent images in profound an nuanced ways.  Prior tasks not only 
+alter what a worker focuses on, 
+but also modulate the richness and specialization of her vocabulary.  
+While they can be a source of systematic bias, our
+results suggest that intertask effects can be leveraged
+to hone worker focus and specificity.  Though we focused on microtask 
+platforms due to their emerging prominence, our results apply to  
+citizen science, crowdsourcing, and any application involving repetitive 
+tasks relying on human judgment.
 \end{sciabstract}
@@
 \section*{Introduction}
-Microtask crowdsourcing platforms like Amazon Mechanical Turk (MTurk) make it 
-possible for requesters to submit batches of tasks to a large pool of 
-workers, who do the tasks for fun, a sense of purpose, and remuneration 
+Microtask platforms are online marketplaces on which \textit{requesters} 
+post batches of tasks, and \textit{workers} complete them
+for remuneration, a sense of purpose, and for fun
 \cite{kazai2013analysis,Antin20122925}.  
@@
 \cite{le2010ensuring,grady2010crowdsourcing,alonso2009can,kazai2013analysis}.
-Originally used to distribute clerical work (\#), these platforms 
-increasingly serve as a means to engage experimental participants in a 
-research 
-setting \cite{paolacci2010running,Berinsky2012351,snow2008cheap,alonso2009can}.
-This trend has seeded considerable interest in characterizing the parameters
-of task design, and validating the microtask platform methodology (\#).
-
-Computer scientists view microtask platforms in the context of general
-computation(\#).  In this regard, the platforms enable a tight integration of 
-human and machine computation(\#).  Researchers coined the term HPU 
-(Human co-Processing Unit) in analogy to CPUs and GPUs \cite{5543192}.  
-Ongoing research pursues the establishment of an HPU instruction set
-including basic operators like \texttt{vote}, \texttt{subdivide}, \texttt{map},
-\texttt{reduce}, \texttt{sentiment}, and \texttt{image\_tag} (\#).  Libraries 
-are being developed to give the programmer more seamless access to HPU 
-resources 
+
+While microtask platforms have been widely adopted as a research tool,
+computer scientists also hold such platforms as the object of 
+research, viewing  microtask platforms as a new kind of computing 
+architecture.  In analogy to CPUs (central 
+processing units) and GPUs (graphics processing units), 
+Davis \textit{et al} invoked the \textit{human processing unit}, or HPU \cite{5543192}.
+Meanwhile, researchers have sought to define a basic HPU instruction set, and
+libraries for HPU programming are under active development
  \cite{little2010turkit,minder2011crowdlang,minder2012crowdlang,kittur2011crowdforge}.
-As with other architectures, the HPU architecture makes entirely new classes 
-of problems tractable for the programmer (\#).
-
-But the ability to program with high-level human instructions comes with a 
-cost: HPU output is inherently noisy (\#).  Part of this noise can be explained
-in terms of worker demography (\#).  But systematic cognitive biases also 
-play a role (\#).   
-So far, investigation has explored how worker performance is influenced by
-such design factors as the level of 
-pay \cite{kazai2013analysis}, training \cite{le2010ensuring}, pre-screening of 
-workers \cite{paolacci2010running}, and user-interface design 
-\cite{Finnerty2013}.  Researchers have also investigated \textit{framing}, 
-by testing the effects of describing the workflow context 
+
+Unlike CPUs and GPUs, the experiments we present here suggest HPUs
+are subject to \textit{hysteresis}, meaning that their output depends
+on the history of their inputs.  Given the
+increasing prevalence of microtask-based methodologies, other factors 
+affecting HPU outputs have received considerable attention.
+This includes various task-design parameters such as the level of 
+pay \cite{kazai2013analysis}, the training \cite{le2010ensuring} and 
+pre-screening \cite{paolacci2010running} of workers, and user-interface 
+design factors \cite{Finnerty2013}.  
+Researchers have also investigated \textit{framing} effects, 
+such as the effects of describing the workflow context 
 \cite{Kinnaird2012281}, the purpose of tasks 
-\cite{chandler2013breaking}, or using alternate problem descriptions
-\cite{thibodeau2013natural}.  To our knowledge, no study has investigated 
-the influences that consecutive microtasks exert on one another.
-
-It is known that people are susceptible to priming effects 
-\cite{BJOP1796,No2007,beller1971priming}, and, in particular, task-repetition 
-effects \cite{Gass1999549,sohn2001task}.  Thus, a worker's response during
-one task may depend on previous ones.  Such \textit{intertask} effects
-would amount to a kind of \textit{hysteresis}, meaning that HPU outputs are not
-only a function of the current input, but also of the history of inputs, with
-important implications for the design of crowdsourcing initiatives.
-
-Here we describe a series of experiments, using the Amazon Mechanical
-Turk (MTurk) microtask platform (\#), in which we studied intertask effects
-for image-labeling tasks.  Image-labeling tasks are among the most 
-common kinds of microtasks
-\cite{chandler2013breaking,Berinsky2012351,Finnerty2013,paolacci2010running}, 
-and it seems likely that this will remain the case in the long term because
-they provide a source of ground truth in computer vision research 
+\cite{chandler2013breaking}, or altering the problem description
+\cite{thibodeau2013natural}.  Results in psychology show that people are 
+susceptible to various kinds of priming 
+\cite{BJOP1796,No2007,beller1971priming}, and, in particular, 
+task-repetition effects \cite{Gass1999549,sohn2001task}.  But to our 
+knowledge, no study has investigated the practical ramifications 
+of intertask effects on human computation.
+
+We investigated intertask effects using image-labeling tasks on the Amazon 
+Mechanical Turk (MTurk) microtask platform.  Image labeling tasks are among
+the most common MTurk tasks \cite{chandler2013breaking,Berinsky2012351,Finnerty2013,paolacci2010running}, a trend which will probably continue 
+in the long term because of their role in computer vision research 
 \cite{5543192}.
-During the experiments, workers were presented with a series of images (one at
-a time), and had to provide five descriptive words (\textit{labels}) for each.
-We varied first five images (hereafter the \textit{initial tasks})
-and observed the effect this had on the workers' labels for the last five
-(\textit{test tasks}).
-
-The initial tasks were chosen to embed a certain \textit{prime concept}.
-Our first experiment compares the prime concepts \textit{food} and (non-food) 
-\textit{objects}, while our second experiment compares \textit{food} and 
-\textit{culture}.  For both experiments, The test tasks used images that
-combined both prime concepts used for the initial tasks \td{reword}.  Workers participated 
-in only one treatment of one experiment, and were randomly assigned initial 
-tasks based on one of the prime concepts.  From the perspective of the worker, 
-we made no distinction between the initial tasks and test tasks.
-
-As a point of comparison, we included treatments in which we induced
-\textit{framing}. \td{what is framing?}
-In the framing treatments, before workers begin the tasks, we told them that 
-the purpose of study was to understand the visual perception of 
-``food and ingredients'' in one case, or the 
-perception of ``objects and tools'' in another.  We varied the language of 
-the framing text (hereafter simply the \textit{frame}), and for some treatments
-we required the worker to echo the frame using a combo-box input.
-
-We found that intertask effects were stronger than framing, unless the worker
-was required to echo the frame, in which case the effects of both exposures were on par.  
-Our results demonstrate that initial tasks can change 
-workers' focus in later tasks.  Using the wordnet corpus, we analyzed 
-the effects on the vocabulary used by workers when 
-labeling test tasks. 
-Exposure to both framing and initial tasks significantly altered the 
-diversity of vocabulary that workers used when referring to the prime concept,
-as well as the degree to which workers used specialized (rather than generic) 
-words.
-
-Contrary to our initial expectations, our findings suggest that the HPU 
-programmer can leverage intertask effects.  By carefully designing workflows,
-it is possible to tune worker focus, specificity, and expressivity.  Our 
-findings carry two lessons for the task designer: intertask
-effects can severely bias HPU output if uncontrolled, but if properly 
-controlled, intertask effects might be of significant utility in achieving 
-expert-level output.
-
-\paragraph*{Measuring computational hysteresis.}
-Before describing the details of our experiments, we explain some 
-choices made in measuring intertask and framing effects 
-(hereafter collectively \textit{exposure effects}).  
-In trying to establish a measure of exposure effects, it might be tempting to 
-invoke the notion of a ``neutral frame of mind'' to serve as a baseline. 
-But such a concept seems both difficult to define, and unlikely to arise.
-Therefore, we always consider the effect of one exposure 
-\textit{relative} to another.  We organized our experiments 
-into pairs of treatments, between which it is possible to make meaningful 
-comparisons.
-
-Our goal in measuring exposure effects is to show that they can actually 
-alter the course of algorithms.
-We could, by means of a $\chi^2$ test, reject the null hypothesis that
-differently exposed HPUs have the same distribution of outputs.
-However, this alone would not demonstrate a practically significant effect, in 
-terms altering the execution path of algorithms.
-
-We developed a more stringent measure in which we train classifier algorithms 
-to infer the exposure of an HPU from its outputs.
-If a classifier infers an HPU's exposure with significantly 
-better accuracy than provided by chance, then the HPU outputs must have 
-been affected by the exposure.  
-But in addition, the classifier serves as a kind of certificate, since it is 
-an example of an algorithm whose path of execution is influenced by the 
-exposure of 
-individual HPUs.  In the supplementary material, we ground our approach 
-rigorously in terms of the L1-distance metric, which is a measure of 
-divergence between distributions.  The L1-distance ranges from 
-0 to 1.  In our case, a value of 1 indicates that the HPU's exposure
-influences its output so strongly that the exposure can be inferred from the
-output without ambiguity.  A value of 0 indicates that the exposure has no
-impact on the HPU's outputs.  The connection between the
-L1-distance, $D_\mathrm{L1}$, and a classifier's accuracy, $\eta$, is given by:
-\begin{equation}
-	D_\mathrm{L1} \geq 2 \eta - 1, 
-	\label{l1}
-\end{equation}
-Since a classifier's performance provides a lower bound on the L1-distance, 
-we shall denote $D_\mathrm{L1}^-\equiv 2\eta-1$.
-The L1-distance admits the following interpretation: if two distributions
-$P$ and $Q$ have an L1-distance $d$, then in the worst case, the 
-frequency with which a binary algorithm operating on samples
-from $P$ outputs a 1, will differ from that when operating on samples from 
-$Q$ by $d \times 100\%$.  
-Thus, we can interpret $D_\mathrm{L1}^-$ as a kind of
-lower bound for the worst-case bias induced by HPU hysteresis.
-We provide further discussion of the statistical properties of our approach 
-in the supplementary material.
+In our experiments, workers performed a set of \textit{initial tasks}, 
+followed by a set of \textit{test tasks}. Crucially, no distinction was
+made between these sets from the perspective of the worker. We varied the 
+initial tasks (for example, having workers label images of food or objects), 
+and observed the ensuing effects on responses in test tasks.  
+As a point of 
+comparison, we also included treatments in which we framed the tasks in terms 
+of different purposes.
+
+The results showed that intertask effects are stronger than framing effects.  
+Framing effects were comparable to intertask effects only when we had the
+workers actively reiterate the frame by means of a combo-box input.
+Using the wordnet corpus (\#), we found that intertask 
+effects can hone a worker's focus, and boost the specialization
+and lexical richness of her labels.  Thus, while intertask effects may be a 
+serious source of bias, they can also be leveraged to help achieve
+expert-level performance in crowdsourcing when properly controlled.
 
@@
 	\caption{
-		Examples of images used in labeling tasks. (The italicized treatment 
-		names that follow are defined in Table \ref{table:treatments}.) Images 
-		from initial tasks: A) \textit{task1:food}, B) 
-		\textit{task1:obj}, D) \textit{task2:food}, 
-		E) \textit{task2:cult}.  Images from  test tasks: C) \textit{exp1}, 
-		F) \textit{exp2}.  The full set of experimental materials is 
-		shown in the supplementary material (S1).
+		Examples of images used for various experiments and treatments:
+		A) initial tasks for \textit{task1:food}, B) initial tasks for 
+		\textit{task1:obj}, C) test tasks for treatments in \textit{exp1}, 
+		D) initial tasks for \textit{task2:food}, 
+		E) initial tasks for \textit{task2:cult},  
+		F) test tasks for \textit{exp2}.  The full set of experimental 
+		materials is shown in the supplementary material.
 	}
@@
 \end{figure}
-We performed two experiments, soliciting respectively 2300, and 900 MTurk 
-workers to label images depicting food, kitchen- and dining-ware, and cultural
-scenes.  In a given experiment, all workers performed the same test
-tasks, the output of which was our main dependent variable.  Before performing
-the test tasks, workers were subjected to an exposure, via two 
-\textit{modalities}: either they completed a set of initial tasks, or 
-were exposed to a frame, or both.  As mentioned, from the perspective of the worker, 
-there was no distinction or discontinuity between initial and test tasks.
-
-We organized the experiments into \textit{treatment pairs}.  Both treatments in a 
-pair involved the same exposure modality, but differed in the
-content of the exposure.  In Table 1, we summarize the various experimental
-treatments, and introduce a naming convention that we use to refer to 
-treatments and treatment pairs.
-In the treatment pairs that studied intertask effects (\textit{task1} and
-\textit{task2}), workers performed 10 image-labeling tasks, with the first 
-five tasks comprising the initial tasks and the last five tasks comprising the
-test tasks.
-
-In the first experiment, the content of the exposures was based on the prime
-concepts \textit{food} and \textit{objects} (throughout, ``objects'' should be
-taken to imply ``non-edible objects'').  So, 
-in \textit{task1:food}, the initial tasks contained images depicting food, 
-while in \textit{task1:obj}, they contained images depicting objects, 
-including kitchen and dining-ware (see Fig~\ref{fig:task}).  Meanwhile, 
-for the exposures in \textit{frame1} we indicating that the study was
-``funded by the laboratory for the visual perception of \{ Food and Ingredients
-$\vert$ Objects and Tools~\}''.  To further strengthen the frame, we 
-introduced another pair of framing treatments, \textit{echo}, with stronger
-wording: ``The purpose of this study is to understand the visual perception
-of \{ Food and Ingredients $\vert$ Objects and Tools~\}'', and required
-the worker to echo the purpose of the study by selecting it among other 
-options in a combo-box input.
-
-Note that food and objects are both relatively well-defined classes of 
-physical entities.  To explore a different conceptual axis, in 
-\textit{exp2} we adopted the prime concepts \textit{food} and \textit{culture}.
-Compared to food and objects, culture is more abstract, and, rather than 
-comprising a class of physical entities, it encapsulates
-sets of beliefs, values, and practices.  Examples of images from the initial 
-tasks in \textit{task2} are shown in Fig.~\ref{fig:task}, and the full 
-collection of 
-experimental materials is presented in the supplementary material (S1).  We 
-ensured that all workers only participated in one treatment of one experiment.
+
+We performed two experiments, \textit{exp1} and \textit{exp2}, which consisted
+of various pairs of treatments.  The treatments in each pair were subjected to
+the same exposure modality, either initial tasks or framing, but differed in
+the content of the exposure.  Table \ref{table:treatments}  
+summarizes the treatments and introduces a naming convention that we use 
+in what follows.
+In \textit{exp1}, workers in the treatment pair \textit{task1} initially
+labeled 5 images containing either food (treatment \textit{task1:food}), or 
+objects, (treatment \textit{task1:obj}), and then performed test tasks, in 
+which they 
+labeled images containing both food and objects (see Fig.~\ref{fig:task} for 
+examples of the images used). In \textit{exp1}, we included two other 
+treatment pairs, \textit{frame1} and \textit{echo1}, in which workers did not 
+perform initial tasks, but instead were given information which framed the 
+purpose of the tasks.  Workers in \textit{frame1} were told that the tasks 
+were ``Funded by the laboratory for the visual perception of 
+\{ Food and Ingredients $\vert$ Objects and Tools~\}''.  In \textit{echo1},
+we sharpened the frame, by indicating that ``The purpose of this study is to 
+understand the visual perception of 
+\{ Food and Ingredients $\vert$ Objects and Tools~\}'' and then asking the
+worker to reiterate the purpose of the task using a combo-box input.
+
+In contrast to \textit{exp1}, which was based on concepts of food and
+objects, \textit{exp2} was based food and \textit{culture}.
+Since culture is more abstract, one might expect different effects 
+in \textit{exp2}.  We again compared
+intertask effects (in treatment pair \textit{task2}) to framing effects 
+(\textit{frame2}), but with a slight variation in the framing treatments.
+In \textit{frame2}, workers were not only exposed to a frame, but also 
+performed a set of initial tasks before the test tasks.  Since its purpose 
+was still
+to investigate framing effects, the initial tasks in \textit{frame2}
+were not varied. Thus, \textit{frame2} provides insight into the moderating 
+effect that intervening tasks might have on framing effects.
+
+In all treatments, workers were shown images one at a time, and provided
+5 labels for each.  From the perspective of the worker, there was no
+distinction or interruption between the initial and test tasks.  We used
+workers' unique identifiers to ensure that they only participated in a 
+one treatment of a single experiment.
 
@@
 		We use the treatment names shown to refer to specific sections of 
-		the data collected.  For example, \textit{task2:food} refers to the
-		treatment in the second experiment which was not exposed to a frame, 
-		and whose initial tasks contained images of food (7th row).
+		the experimental data.
 	}}
@@
 
-\paragraph{The strength of intertask effects.}
-
-We assessed the strength of intertask and framing effects
-by training a multinomial naive Bayes classifier to infer a worker's exposure
-based on the labels provided in the test tasks (see Fig.~\ref{fig:theta}).
-This inference was made over the two possibilities for a given treatment pair.
-We found that in \textit{task1}, whether a worker performed food- or 
-object-containing initial tasks had a strong effect on their subsequent 
-labels, introducing a bias that probably exceeds 30\%.  In comparison, the 
-framing effect in \textit{frame1} did 
-not influence workers' labels enough for the classifier to make predictions 
-with significantly better accuracy than that afforded by chance.  The results 
-for \textit{exp2} show a similar, but even more pronounced trend, with the bias
-induced by intertask effects in \textit{task2} probably exceeding 50\%.
-
-We see a comparable effect size in the \textit{echo} treatment pair.
-We expected \textit{echo} to show a very strong effect because, by requiring
-the worker to echo the purported purpose of the task, we signal that it
-is of particular importance.  The fact that the intertask effects were on par with the framing 
-effects in \textit{echo} shows just how powerful intertask effects can be.
+\paragraph*{Measuring computational hysteresis.}
+While our study builds on research into the psychological mechanisms
+of task performance, there is a crucial difference in the question at issue. 
+Our goal is to measure the practical ramifications of intertask effects on 
+the microtask methodology. Whereas a statistically significant effect, even 
+if small, might be sufficient to distinguish one psychological mechanism 
+from another (\#), in our study 
+\textit{effect size} is central.  Thus our main goal is not merely to reject 
+the null hypothesis that initial tasks have no effect
+(we do this in the supplementary text).
+
+To couch intertask effects in a practical yet general setting, we imagine
+that, after a worker performs a task, her response is used to make some 
+kind of yes-or-no decision, $\mathcal{D}$.  For example, this decision 
+could be whether or not to flag a certain comment
+below a news article as inappropriate; but for now, we leave 
+$\mathcal{D}$ unspecified.  Since worker's responses may
+vary, repeating the same task might lead to different outcomes for 
+$\mathcal{D}$.  We shall define the notion of \textit{bias} in terms of the
+effect that prior tasks have on the probability of a positive outcome
+from $\mathcal{D}$.
+
+The nature of $\mathcal{D}$ will affect our measurement of bias.
+If $\mathcal{D}$ has random output, or if it always outputs ``yes'' 
+irrespective of the worker's response, then of course we will 
+find zero bias.  Likewise, there is an upper limit to the bias induced on $\mathcal{D}$. In a precise sense, the bias of $\mathcal{D}$ can only be as
+great as the bias inherent in the worker's response 
+(this is formalized in the supplementary text).  Therefore, to estimate the 
+bias induced in workers' outputs, we adopt an 
+adversarial approach: we seek to construct the decision that 
+is the most susceptible to workers' biases. In the supplementary text, we 
+show that this
+problem can be formulated as a  machine learning problem, wherein one
+constructs a classifier that infers the exposure of a worker from her 
+responses in test tasks.  The bias, $\theta$, induced by 
+prior exposures, can then be bounded using the classifier's accuracy, 
+$\eta$ (\#):
+\begin{equation}
+	\theta \geq 2\eta - 1
+	\label{l1}
+\end{equation}
+
+\paragraph{The strength and dynamics of intertask effects.}
+For each treatment pair, we trained a naive Bayes classifier (\# in the 
+supplementary material we discuss the choice of classifier, the
+approach to measuring accuracy, and draw a comparison to results using 
+a support vector machine in place of the naive Bayes classifier) to 
+distinguish workers from one treatment
+(e.g \textit{task1:food}) from those of the conjugate treatment 
+(e.g. \textit{task1:obj}).  In \textit{task1} and \textit{task2}, intertask 
+effects profoundly biased worker outputs, whereas we could not detect 
+a statistically significant bias induced by framing in \textit{frame1} and 
+\textit{frame2} (see Fig.~\ref{fig:theta}).  The bias induced
+by framing was only of a comparable level to that induced by intertask 
+effects in \textit{echo1}.  
+Moreover, asking workers to reiterate the
+frame, as was done in \textit{echo1}, is probably interpreted as
+a direct signal from the requester that the frame should be acted upon.  In that sense, 
+\textit{echo1} is perhaps more indicative of the effects of an 
+\textit{instruction}.  This shows that
+intertask effects profoundly affect the responses of workers, producing an
+effect that is stronger than framing, and on par with the combination of 
+framing and reiteration.
 
@@
 
-\paragraph{Dynamics of intertask effects.} It is natural to expect 
-intertask effects to attenuate as a worker proceeds through the test tasks.  
-In \textit{task1}, we permuted the test tasks, allowing us to 
-measure intertask effects as a function of task position, while factoring
-out the content-dependent differences between tasks
-(see Fig.~\ref{fig:theta}B). 
-We found intertask effects were most pronounced for the first test task,
-dropping off substantially for the second, but maintaining a 
-significant effect through until the fifth test task.  
-This shows that the range of intertask effects extends across at least five 
-tasks, and probably substantially more.
-This makes intertask effects of greater concern, but as we will show, it also
-makes intertask effects of greater potential utility.
-In future work, it would be interesting to investigate whether a worker's
-susceptibility to intertask effects varies across a large batch.  For example,
-It is conceivable that the first few tasks induce especially strong
-or long-lasting effects, in effect ``setting the tone'' for the rest of the batch.
+To observe the dynamics of intertask effects, we trained a naive Bayes
+classifier to distinguish workers in \textit{task1} based on responses to
+individual test tasks.  We permuted 
+the test tasks to eliminate effects arising from differences in the images 
+therein (more details are provided in the supplementary text). The first test 
+task shows the greatest bias, after which the effects drop off, but 
+substantial bias persists through the fifth test task
+(see Fig. \ref{fig:theta}B).  Presumably, this decay profile reflects the
+fact that workers are also influenced by their exposure to the test tasks, 
+which washes out the effects of initial tasks.
 
@@
 
-Having observed significant effects from framing and task-exposure,
-we looked in greater detail at the nature of the effects.  For instance,
-does a food-oriented exposure induce workers to provide more food-related
-labels?  And if so, does this explain the classifier's ability to distinguish
-a worker's initial exposure?
-
-To answer these questions, we used the wordnet corpus, augmented with names of
-ethnic foods learned from the Internet.  Wordnet provides a (roughly)
-hierarchical set of relationships between nouns, called hypernym-hyponym
-relationships.  A hypernym is a generalization, while a hyponym is a 
-specialization.  So, for example, ``bread'' is hypernym to ``rye bread'' 
-and hyponym to ``baked goods''.
-
-Using the augmented hypernym-hyponym structure of wordnet to identify nouns 
-depicting food, we found that, for the experimental pairings in 
-\textit{exp1}, the
-food-exposed treatments did produce a significantly larger fraction of 
-food-related labels (see Fig.~\ref{fig:specificity}A).  While the shift in 
-focus with regard to food does help explain the classifier's ability to 
-infer worker exposures, it is insufficient to explain the observed performance
-(*).
-Furthermore, in \textit{exp2:task2} we see a significant but reversed effect
-(see Fig.~\ref{fig:specificity}A), which suggests a more complicated 
-relationship between exposure and label usage.
-Given the difference between the food-culture and food-object conceptual axes, 
-it should perhaps not be surprising that the effect of initial task exposure 
-is different.  It would appear that we must be prepared to accommodate 
-multiple 
-countervailing factors influencing the number of references to the prime 
-concept (food).  We will come back to this point momentarily.
-
-To explore these effects further, we looked more closely at which particular
-labels were most suppressed (activated) by a worker's exposure.  Remarkably,
-we found that, for all treatment pairs, ``food'' was always the most 
-suppressed label among 
-the food-exposed workers.  This is surprising, considering 
-that the overall incidence of food-related labels mostly \textit{increased} 
-among food-exposed workers.  But taken together, the increase in references to 
-food 
-and the decrease in the incidence of ``food'' per se (which is the most generic
-food-reference in the wordnet-based ontology), necessarily implies that
-food-exposed workers have opted for more specialized references in place of 
-``food''.
-
-In a crowdsourcing task, considerable effort must be given to shaping the 
-vocabulary with which a worker engages a task.  To draw an example from the 
-domain of citizen science, in galaxy zoo, workers catalog images of galaxies 
-in terms of \textit{smoothness}, and the presence of \textit{rings}, 
-\textit{dust lanes}, \textit{digital disturbances}, and so on.  Shaping this 
-vocabulary is crucial to the reliability of results.  The interface of
-galaxy zoo helps by constraining and prompting the user with this basic 
-vocabulary.  But this would not appear to be sufficient, since
-a set of positive and negative training examples are used, together with
-peer-to-peer and peer-to-expert exchange in discussion areas, presumably to
-further refine and standardize the vocabulary (\#).
-
-In our set-up, where the worker's vocabulary is unconstrained, we can 
-directly observe the effects that frames and initial tasks have on worker 
-vocabulary.  By looking at the number of unique food-related labels that 
-workers produced, we assessed the richness of vocabulary that workers used when
-referring to food (see Fig.~\ref{fig:specificity}B).  We found that the 
-food-exposed workers use a richer vocabulary of 
-food-related words, even in cases like \textit{task2:food}, where they 
-made fewer references to food overall.  
-Interestingly, task-based exposure to food had a stronger enriching effect 
- than did framing-based exposures. (* explain why vocab 
-diversity is useful.)
-
-Using the ontology of food induced by wordnet, along with foods learned from
-the Internet, we were able to directly calculate the relative specificity of 
-workers from different treatments.
-To do this, we considered all the labels from one treatment
-(for example \textit{task1:food}) and compared these to all the labels from 
-another (\textit{task1:obj}).  For all possible comparisons, we observed 
-which treatment's label was more specific more often, and normalized this
-quantity as a percentage (we provide greater detail in the supplementary 
-material).
-
-We calculated the relative specificity for all treatment pairs, while 
-restricting focus to 
-food-related labels (see Fig.~\ref{fig:specificity}C).  We found that 
-the food-exposed workers always provided food-references of substantially 
-greater specificity.  Workers that had labeled images containing food 
-were about 12\% more specific than those that labeled images of objects,
-and about 20\% more specific than those that labeled images of cultural 
-scenes.  With respect to the specificity of food references, framing effects 
-were on par with intertask effects.
-
-Taken together, the results presented in Fig.~\ref{fig:specificity} can 
-be explained by a combination of priming and  \textit{negative} priming.
-Negative priming occurs when a repeated stimulus, which is perceived to be
-non-salient, begins to be ignored (\#).
-
-We propose that, as a worker from \textit{task1:food} proceeds through the 
-initial tasks, food-related memories and concepts are activated, increasing 
-the likelihood that she uses a variety of food-related labels.  This accounts
-for the overall increases the number of food-related labels, as well as the 
-richness and specificity of her food-related vocabulary.  At the same time,
-since all images up to that point contained food, \textit{whether or not}
-an image contains food begins to appear non-salient, suppressing the most 
-generic references, such as ``food''.  Thus, there is a simultaneous emphasis of the specialized 
-references to the prime concept and de-emphasis of generic references.
-
-This view can account for the observation that there are fewer
-food-related references overall in \textit{task2:food} compared to 
-\textit{task2:cult}.  Workers in \textit{task2:food}, like those in 
-\textit{task1:food}, are primed to use
-specialized food references and negatively primed against using generic
-ones.  Then, when these workers encounter the test tasks, with images 
-containing more prominent cultural content, they attend to this novel content, 
-decreasing their balance of food references.  
-Meanwhile, workers in \textit{task2:cult}, having seen only cultural scenes,
-experience novelty from the appearance of food-oriented content in the test 
-tasks, and, attending to it, drive the relative difference in the quantity of 
-food-related labels further toward the negative in in 
-Fig.~\ref{fig:specificity}A.
-
-Based on these observations, we submit the following ideas for consideration 
-by the designers of crowdsourced initiatives.
+Using the wordnet corpus, we analyzed exposure effects in finer detail.
+Wordnet encodes semantic information in various ways, including in the form 
+of synsets (groups of synonymous words), and hypernym-hyponym relations.
+Hypernyms are generalizations (``bread'' is a hypernym of ``pumpernickel''),
+while hyponyms are specialisations.
+
+First, we used wordnet to identify nouns depicting foods (\# We 
+operationalized food-references by taking all hyponyms of the synsets 
+\texttt{food.n.01} and \texttt{food.n.02}, with the addition of ethnic foods 
+learned by crawling a recipe website, as described in the supplementary text),
+to see whether 
+workers from the various food-exposed treatments (\textit{*:food}), 
+provided more references to food than their conjugate treatments, overall.
+The \textit{exp1:*:food} treatments
+did produce more food references, but, unexpectedly, 
+the number of food references in \textit{task2:food} was
+less than that in \textit{task2:cult}. Also, the effects on the
+number of food references was, overall, somewhat smaller than one might 
+have expected given the extent of bias observed for \textit{task1}, 
+\textit{echo1}, and \textit{task2}.  This means that task and frame exposures
+induce other effects which are more subtle than a bulk shift in number 
+of references to the primed concept (food).
+
+Next, we looked at the change in the frequency of occurrence of particular 
+words.  Surprisingly, the word ``food'' was the \textit{most suppressed} word
+for workers in \textit{*:food} across all treatment pairs (Table S1 shows the
+top five most promoted and suppressed words for each treatment pair).
+Initially, this seems at odds with the fact that (at least in \textit{exp1})
+the \textit{*:food} treatments had more food references than their conjugate
+treatments.  But taken together, these facts indicate that workers are opting 
+to use more specialized food-references in place of ``food''.  
+Indeed, when we look at the total number of unique
+words (lexical richness) used to refer to food, we found that 
+a significantly richer lexicon was used by all \textit{*:food} treatments,
+except in \textit{frame2} (see Fig.~\ref{fig:specificity}B).  This effect 
+was especially pronounced in \textit{task1} and 
+\textit{task2}.
+
+Finally, we directly calculated the degree of specialization of food 
+references using wordnet's hypernym-hyponym relations.  To determine the 
+relative specialization between the words of two treatments, we computed 
+the proportion of words in the first treatment that were hyponyms of the 
+those in the 
+second, less those in the first that were hypernyms of those in the second 
+(this calculation is formalized in the supplementary text).  Except in the
+case of \textit{frame2}, workers in \textit{*:food} treatments used 
+substantially more specialized terms in reference to food than workers 
+from the conjugate treatments.
+
+\paragraph{Positive and negative priming.}
+Taken together, the results of the experiments presented here can be 
+explained through a combination of positive and negative priming.
+Positive priming (usually simply ``priming'') occurs when a prior stimulus 
+predisposes a person to give certain responses in an ensuing task, and
+is often observed as an increase in the speed or accuracy of a response, or
+the ability to recognize objects in a briefer, quieter, or noisier signal (\#).
+Negative priming occurs when repeated exposure to a stimulus that is 
+perceived to be non-salient begins to be ignored (\#).
+
+Workers exposed to images containing food will be (positively) primed, 
+as memories, concepts, and vocabulary related to food are activated.  
+However, as the worker labels successive images containing food, the basic 
+fact that an image contains food does not appear to be salient, since it 
+does not serve to distinguish one image from another.  Thus, the most 
+generic reference to the fact that food appears, namely the label ``food'', 
+is suppressed, as by negative priming, while more specialized
+references are activated.  Whether workers in \textit{*:food} treatments
+produce an excess of food references overall depends in part on the balance 
+of these factors.  The reduction in food references from workers in 
+\textit{task2:food} relative
+to those in \textit{task2:cult} may also be related to the novelty that 
+workers in 
+\textit{task2:cult} experience when they first encounter food in the test 
+tasks.
+
+More generally, we are suggesting that, even though workers are not 
+instructed to compare the content of tasks in any way, prior tasks form a 
+context relative to which workers judge salience.  Thus, a worker's focus 
+in repeated tasks tends to be directed away from generic, shared features, 
+toward specific and distinguishing ones.
+
+Based on our observations throughout, we submit the following 
+recommendations for the consideration of those in the position of designing 
+any microtask, citizen science, or crowdsourcing initiative:
 \begin{enumerate}
 	\item{
-		Training tasks should be preferred over examples, since the immediate
-		active use of information appears to increase its impact.
+		Require active feedback to emphasize important details, 
+		as we did in \textit{echo1}.  Similarly, use training tasks rather
+		than (only) examples.
 	}
 	\item{
-		Training tasks should contain the same distribution of 
-		noise (or ``distracting features''), as the real dataset.
-		Exposing workers to irrelevant features, and identifying them as such,
-		will free up worker attention for salient features, by virtue of
-		negative priming.
+		Although ``clean'' examples may be useful to provide clarity,
+		training tasks should contain the same kinds of noise or otherwise
+		distracting features as are expected in the real tasks.
+		This exposure will negatively prime the worker against non-salient 
+		features.
 	}
@@
 		are often used as a quality control measure.
-		These should be dually considered as \textit{calibration tasks}, and
-		should be designed to help workers maintain an optimally primed 
-		state. Feedback, for both correct and incorrect responses, 
-		may further reinforce salient features.
+		These should be dually considered as \textit{calibration tasks}.  
+		Feedback, for both correct and incorrect responses may further 
+		reinforce the desired competency. \label{item:valid}
 	}
 	\item{
-		In many applications, such as the detection of pre-ictal 
-		(pre-seizure) EEG traces, workers encounter few positive examples
-		(most traces are not pre-ictal)(\#).  In the absence of positive 
+		A special case of item~\ref{item:valid} applies when workers are 
+		required to detect rare occurrences.
+		For example, in the detection of pre-ictal (pre-seizure) EEG traces, 
+		most traces are not negative (\#).  In the absence of positive 
 		examples, the target concept may degrade or drift.
-		Drawing calibration tasks from the underrepresented class may 
-		help sustain the target concept.
+		Drawing validation/calibration tasks from the underrepresented class,
+		while providing feedback might help sustain the target concept.
 	}
 	\item{
-		For the most precise classifications, it may be helpful to
-		begin with a coarse classification.  For example, workers could 
-		initially choose from  \texttt{class0}, \texttt{class1}, and 
-		\texttt{borderline}.  Following the coarse classification, the 
-		\texttt{borderline} examples could be batched together, allowing 
-		workers to focus on features that are only salient for such fine 
-		distinctions.
+		For more precise classifications, it may help to begin with
+		an initial coarse classification.  For example, in detecting 
+		inappropriate comments, workers might initially choose from  
+		\texttt{okay}, \texttt{inappropriate}, and \texttt{borderline}.  
+		Following the coarse classification, the 
+		\texttt{borderline} examples could be batched together.  Workers could
+		then calibrate to finer distinctions while coding a more homogeneous 
+		set of images.
 	}
@@
 
-These recommendations follow logically from our observations, but they are 
-educated guesses.  We leave their direct testing to future work.
+While these recommendations are informed by the observations we have made 
+here, we hope to see them tested directly in future work.
 
 \paragraph{Conclusion.}
-Our results show that intertask effects are 
-as strong as framing effects, and are stronger when the frame is not echoed.
-Our analysis using wordnet reveals that intertask and framing effects
-act on workers' vocabulary in subtle ways.  Both exposure modalities 
-increased the richness of workers' vocabulary in reference to the prime 
-concept, but more so in the case of task-based exposure.  Both modalities 
-also increased the specialization of workers' vocabulary in reference to the 
-prime concept.
-
-We recommend that intertask effects be considered when designing crowdsourced
-studies.  Despite efforts to eliminate biases from the context of tasks,
-the greatest source of biases may lurk in the tasks themselves.
-At the same time, their positive effects on workers' vocabulary suggest 
-that, when properly controlled, intertask effects may be
-used to optimize HPU performance.  Based on the enriching effects we observed
-for worker vocabulary, intertask effects might be leveraged to achieve 
-expert-level annotation in a wider variety of applications.
+We have shown that intertask effects are stronger than framing effects, and
+as strong as the effects induced when framing is combined with reiteration.
+Intertask and framing effects act on workers' vocabulary in subtle ways.  
+Both increase the richness of workers' vocabulary in reference a target
+concept, with a more pronounced effect induced by task exposure.
+Both exposures also increase the specialization of workers' vocabulary in 
+reference to the target concept.  Framing, and other aspects of task design 
+have received substantial methodological scrutiny; our results show that 
+intertask effects, which were overlooked until now, merit similar 
+consideration.  Although we found that intertask effects can be a major 
+source of bias, they might be used to drive tune workers' attention and 
+specificity relative to
+a target concept.  Microtask work, citizen science, and other crowdsourcing
+initiatives, as well task requiring expert opinions, often share the common 
+feature that they rely on repetitive human judgments.  Therefore, such 
+applications all stand to benefit from the findings and suggestions 
+presented here.
 
@@
 	\end{equation}
-	where $f_w$ is the frequency with wich the word occured (correctly 
+	where $f_w$ is the frequency with which the word occurred (correctly 
 	spelled)
@@
 	one edit, then $p_2 = 1$.  Any edit that did not involve adding a space
-	(i.e. separating a word) incured a penalty of 0.5, while the addition of
+	(i.e. separating a word) incurred a penalty of 0.5, while the addition of
 	a space incurred a penalty of 0.1.  Word-separation edits were more 
@@
 	were shown a set of 
-	500 words that were randomly sampled from the labels attirubuted during 
+	500 words that were randomly sampled from the labels attributed during 
 	test tasks (50 for each test task).  Before sampling, the labels from all
@@
 	descriptions, ingredients lists, and preparation instructions were
-	collected, and saved as an auxiliary set to aument the \textit{legal set}
+	collected, and saved as an auxiliary set to augment the \textit{legal set}
 	used in spelling correction.
@@
 workers and which had been seen during crawling of the allrecipes.com website,
-but which were not included in wordnet.  We graphted these extra words into
+but which were not included in wordnet.  We grafted these extra words into
 the wordnet hyponym-hypernym graph manually, which ensured that any references
@@
 spelling correction (if any) that the spell-correction algorithm had made,
-to help interpret mispelled words \td{we describe the spelling correction 
+to help interpret misspelled words \td{we describe the spelling correction 
 algorithm in section X}.
@@
 majority code given by the human coders, we determined the accuracy of the
-food-detection algorithm.  Data sumarizing this validation process are given
+food-detection algorithm.  Data summarizing this validation process are given
 in table S1.
@@
 as described in the main text.  The first step in performing this calculation
-was therefore to map the words occuring from (the labels of) a given 
+was therefore to map the words occurring from (the labels of) a given 
 experimental treatment onto the wordnet synsets.  In general, a given word
@@
 hypernym-hyponym graph two sets of counts, one set per treatment, 
-indicating the number of times a word from a given synset occured among the
+indicating the number of times a word from a given synset occurred among the
 labels of the treatment.  Then, for every synset in one treatment, we looked
@@
 were more specific (reachable by following hyponym relations).  This quantity
-tallied for all words in the original synset gives a (non-normalied) measure
+tallied for all words in the original synset gives a (non-normalized) measure
 of the degree to which words from the first treatment are more specific
@@
 \subsection*{S7: Analysis of variance}
-\begin{itemize}
-	\item{
-		classifier accuracy.  Why we used a one-tail CI.  
-		Why certain error bars are smaller.
-	}
-	\item{error in $\delta$ \%food.}
-	\item{error in size of food vocabulary}
-	\item{error in food specificity}
-\end{itemize}
+	\paragraph{Variance in the average fraction food-related labels}
+	In the main text, Fig.~\ref{fig:specificity}A shows the difference in 
+	the fraction of food related labels used by workers in from different 
+	treatments.  The error bars show the 95\% confidence intervals around 
+	the estimated difference of means.  It was computed from the
+	observed sample standard deviation in the fraction of food labels given
+	by individual workers.
+
+	\paragraph{Variance in food vocabulary size.}
+	\td{Not sure how to calculate this yet.}
+
+	\paragraph{Variance in food specificity.}
+	\td{Need to calculate this using bootstrapping.}
 
 \subsection*{S8: Measuring computational hysteresis}
-\begin{itemize}
 	\paragraph{Using cross-validation accuracy to lower-bound L1-distance.}
@@
 	in our classifier, and then test it's accuracy using cross validation,
-	with no optimization performed on the data.  It was cruicial for 
+	with no optimization performed on the data.  It was crucial for 
 	the statistical validity of our approach that we test our classifier on 
@@
 
+	\textit{Lemmatization.}  In some cases it is helpful to simplify words 
+	before providing them to the classifier.  For example, the words 
+	``berries'' and ``berry'' only differ in number, but would normally be
+	treated as completely different features.  Lemmatization ensures that
+	nouns are in their singular form, which helps to eliminate variations in
+	labels that increase sparsity without conveying discriminative 
+	information.
+
+	\textit{Removal of stop-words.}  Certain very common words such as `the',
+	``to'', and ``it'' are extremely common but don't help discriminate a 
+	worker's exposure.  Removing these words is a common practice because
+	they otherwise introduce noise into the classifier learning process.
+
 	\textit{Whether to split multiple words.}  Although workers were 
@@
 
-	\textit{Lemmatization.}  In some cases it is helpful to simplify words 
-	before providing them to the classifier.  For example, the words 
-	``berries'' and ``berry'' only differ in number, but would normally be
-	treated as completely different features.  Lemmatization ensures that
-	nouns are in their sigular form, which helps to eliminate variations in
-	labels that increase sparsity without conveying discriminative 
-	information.
-
-	\textit{Removal of stop-words.}  Certain very common words such as `the',
-	``to'', and ``it'' are extremely common but don't help discriminate a 
-	worker's exposure.  Removing these words is a common practice because
-	they otherwise introduce noise into the classifier learning process.
-
-	the were many
-	missipellings
-
-		\item{whether to split multiple words 
-	\end{itemize}
-
-	opt for a one-shot approach where we do not optimize any 
-	\item{Adopting Naive Bayes due to the lack of optimization required.}
-	\item{
-		Usage of a principled set of pre-processing and representation 
-		techniques.
-	}
-	\item{
-		Comparison to other choices of representation
-	}
-	\item{
-		Comparison to SVM classifier
-	}
-	\item{
-		Reiterate why we cannot report optimized results.
-	}
-\end{itemize}
+	\textit{Preserving the location of labels.}  When workers completed image
+	labeling tasks, they had to fill five text inputs, which were stacked
+	vertically.  Presumably, they began with the top input and proceeded 
+	downwards.  It seems likely that exposure effects might influence the
+	\textit{order} in which workers apply labels, so when processing the 
+	labels we prepended an integer to indicate into which text input the 
+	label been input.  This meant that the classifier could distinguish
+	``bread'' entered into the first text input from ``bread'' entered into
+	the second.  A drawback is that this increases sparsity, preventing the
+	classifier from accounting for the fact that different though they are,
+	these entries should be treated similarly.  For this reason, we also
+	provided features to the classifier which did not encode the particular
+	input that had been used.  Thus, two workers that entered ``bread''
+	into different inputs would generate both a feature in common indicating
+	the use of the word ``bread'', as well as distinct features, indicating
+	entry of the word ``bread'' \textit{in a particular input}.
+
+	\textit{Preserving the connection between tasks and labels.}  In many
+	cases a particular label would appear in many tasks.  For example, the
+	word ``food'' appears in all test tasks.  It stands to reason that
+	exposure effects play out differently for different tasks, and that
+	the attribution of a particular label during one task provides different
+	information from the attribution of the same label during a different 
+	task.  So, as we did in the case of input location, we prepended labels
+	with the identity of the task in which they were added, so that the 
+	two otherwise identical labels added for different tasks were treated
+	by the classifier as unique features.  Unlike in the case of input 
+	position attribution, we didn't include raw labels unadorned with 
+	the task number.  Our rationale for this is that the task defines the 
+	context in which a label is applied, and so the elicitation of a label 
+	during one task represents a distinct output from the elicitation of the 
+	same label during a different task.
+
+\paragraph{Selection of the naive Bayes classifier.}
+A great deal of work has been done in the application of classifiers to
+text documents, which provides the background for our choice of classifier.
+The Support Vector Machine (SVM) approach is known to perform well, better in 
+general than naive Bayes.  However, three considerations drove us to use
+a naive Bayes classifier in favor of SVM.
+
+First, we used 119 examples (workers) per treatment, but the number of 
+features
+for each worker (i.e. the number of distinct labels, or modifications 
+thereof produced in preprocessing), was generally in the thousands.  
+This tends to
+be problematic for many classifier algorithms, including SVM, because it
+leads to very high variance models, which manifests as overfitting and poor
+performance.  To deal with this, some approach to culling features is 
+generally used, but this raises the issue of how to decide the culling in 
+a principled manner, generally adding further hyperparameters which could
+be optimized.  However, one of the strengths of the naive Bayes classifier
+is that it's performance is not generally degraded from the inclusion of 
+large numbers of features, even when the number of examples is comparatively
+small.  We expected this feature of the naive Bayes classifier to be 
+advantageous in our case.
+
+Second, the standard implementation of the naive Bayes classifier has no 
+hyperparameters to optimize.  This allows us to forgo the common practice 
+of holding out a test set, and instead use cross-validation as a method to
+estimate the true classification error, \textit{since we did not perform
+any kind of model selection or optimization whatsoever using our data}.
+This point is crucial, because if we did optimize our classifier during 
+cross-validation, then the validation error would no longer provide an 
+unbiased estimate of the true classification error, but would instead lead
+to us over-reporting exposure effects.
+
+Third, the naive Bayes algorithm is based on an assumption that the 
+probability of observing one feature is independent from the observation
+of any other, \textit{when conditioned on the class}.  This
+\textit{conditional independence} assumption is generally made for
+pragmatic rather than theoretical reasons, and is rarely satisfied.  However,
+if it \textit{is} satisfied, then the naive Bayes classifier is optimal.
+In our case, conditional independence means that, provided we know the 
+exposure of a worker, knowing one label they provided to an image does
+not in any way help us guess any other label for that image.  In most
+text documents, the existence of topics and language structure certainly
+violates the conditional independence of words.  But in our case, such 
+effects are less likely to carry from one text input to the next, and in the
+small space provided by five inputs, any overarching topics are likely to
+be in relation to the image itself, upon which we are conditioning.  In other
+words, we believe that, in our setup, conditional independence is better 
+satisfied than in most text classification contexts.  That being the case,
+one would not expect much improvement in using a more sophisticated algorithm,
+such as SVM.
+
+\paragraph{Comparison to other classifiers.}
+
+\begin{figure}
+	\centering
+	\includegraphics[scale=0.75]{figs/theta_sup.pdf}
+	\label{fig:theta_sup}
+	\caption{
+		Figure S2: Bias induced by exposure to initial tasks and frames.
+		Bias is defined to be the difference in the probability 
+		distribution over workers' labels (L1-distance).  The plotted values
+		give a lower bound to the L1-distance, $D_{L1}^-$, which was 
+		determined from a classifier's performance in 
+		distinguishing workers that had undergone different exposures.
+		The bias was determined using (A-F) a naive Bayes classifier, and 
+		(G-L) an SVM classifier.
+		In panels A through F, each plot adds an additional
+		preprocessing step to those used in the previous plot; the same is 
+		done for panels G through H: A,G) No 
+		preprocessing; B,H) spelling correction; C,I) stopword removal; 
+		D,J) lemmatization; E,K) splitting of multiple-word labels; 
+		F,L) distinguishing identical labels entered in different form inputs.
+	}
+\end{figure}
+The inequality in Eq.~\ref{l1}
+asserts that a classifiers performance in predicting class membership
+bounds the L1-distance between the distributions of features for the classes.
+This bound is tight for the optimal classifier, and in general, the slack
+depends on how the classifier is constructed.
+
+Therefore there may exist a classifier that is 
+significantly better than the one used to generate our results.  Even before
+committing to a particular classifier algorithm, various decisions about
+preprocessing need to be made.  For example, we chose to remove stopwords,
+lemmatize, split multi-word labels, distinguish the input used to enter 
+labels, and correct spelling.  All of these decisions affect the classifier
+performance.  The particular classifier algorithm chosen also has a strong 
+effect.
+
+Since we did not have enough data to create a separate test set, we could not
+optimize these decisions.  Doing so would lead to the inflation of the 
+performance, which could then only be estimated using an independent test set.
+Instead, we made principled decisions as described above.
+
+Although we cannot optimize these decisions, it is appropriate to look at
+what affect these decisions had, post-hoc.  We reproduce the plot shown in 
+Fig.~\ref{fig:theta}A using different combinations of preprocessing options,
+and using both the naive Bayes and an SVM classifier.
+
+Unlike the naive Bayes classifier, it is necessary to tune the cost and 
+gamma hyperparameters of the SVM classifier, as well as choose a kernel.
+We used simulated annealing to optimize the cost and gamma settings in the
+classification of $task2:food$ vs $task2:cult$.  For this reason, we expect
+the bar for $task2$ in Fig.~S8G-J is likely to be an overestimate due to
+overfitting on those data.
+
+These plots show that the result shown in Fig.~\ref{fig:theta}A is 
+representative, and supports the validity of the lower bounds on the 
+exposures exposure effects presented in the main text, in terms of induced 
+L1-distance.
 
@@
 
-%\subsection*{Assessing task similarity}
-%\begin{table}
-%\centering
-%\begin{tabular}{ l  s s s s}
-%
-%\toprule    
-%Image set   
-%& \multicolumn{1}{c}{Ambig.} 
-%& \multicolumn{1}{c}{Cultural} 
-%& \multicolumn{1}{c}{Ingr.}
-%& \multicolumn{1}{c}{Test} \\
-%  
-%\midrule
-%
-%Ambiguous  & 1 & 0.0418 & 0.142 & 0.167 \\
-%
-%Cultural  & 0.0418  & 1 & 0.0347 & 0.0561 \\
-%
-%Ingredients  & 0.142  & 0.0347 & 1 & 0.110 \\
-%
-%Test & 0.167  & 0.0561 & 0.110 & 1
-%\\
-%\bottomrule
-%
-%\end{tabular}
-%\caption{\footnotesize{
-%Pairwise similarities of each image set based on the labels attributed to them (see \textbf{Eq. 4}).
-%}}
-%\label{table:2}
-%\end{table}
-%
-%One weakness of the above analysis is the reliance on the informal notion
-%of the similarity of one set of images to another. The 
-%characterization of image content is a deeply complex issue that has been 
-%approached by many disciplines \cite{panofsky1939studies,shatford1986analyzing,Tversky1977327,Jaimes20002}. \textit{Perceptual similarity} is a 
-%particularly recalcitrant concept.   But to formalize our claim, we seek a 
-%measure of similarity between two sets of images, 
-%\textit{with respect to the labeling task}.  This can be operationalized
-%in a straightforward way, by using the similarity of the labels given to images
-%as a proxy for the similarity of the images.  Thus, to measure the 
-%similarity between two sets of images, X and Y , we computed the Jacquard 
-%index between the sets of labels attributed to them:
-%$$
-%	\mathrm{Sim}(X,Y) = \frac{L(X) \cap L(Y)}{L(X) \cup L(Y)}
-%$$
-%where $L(X)$ denotes the set of labels attributed to images in $X$.
-%
-%The pairwise similarities of the image sets are presented in Table 2. This 
-%shows that the workers that yielded higher specificity labels were from 
-%treatments whose initial tasks were more similar to the test tasks (c.f.
-%\textbf{Fig 3}).
-%
-%Such a phenomenon would be consistent with the psychological mechanism known as
-%\textit{negative priming}.
-
 \end{document}

### 2014-12-03 src/new_plots.py
update theta plot

@@ -516,7 +516,8 @@ def plot_theta(
 		for a,n in zip(accuracies,[595,119,119,119,119])
 	]
 	err_low = [y-y_err for y, y_err in zip(Y_aggregate, err_low)]
-	err_high = [0 for e in err_low]
+	#err_high = [0 for e in err_low]
+	err_high = err_low
 	err = [err_low, err_high]
 	X = range(len(Y_aggregate))
 
@@ -559,7 +560,8 @@ def plot_theta(
 		for a in avg_accuracies
 	]
 	err_low = [y-y_err for y, y_err in zip(Y_by_pos, err_low)]
-	err_high = [0 for e in err_low]
+	#err_high = [0 for e in err_low]
+	err_high = err_low
 	err = [err_low, err_high]
 
 	series = ax2.bar(

### 2014-12-03 docs/publications/2014.09_SCIENCE/man.tex
another proof-read of the manuscript

@@
 This has lead to broad adoption across a spectrum of disciplines
-in the humanities and computer science, in research into medical imaging
-technologies, and in many applications where expert opinion would normally be 
-sought.  Here we show that an inherent
+in the humanities and computer science, as well as in research into medical 
+imaging technologies and other applications where expert opinion would 
+normally be sought.  Here we show that an inherent
 feature of microtask platforms, the repetition of similar tasks,
@@
 severity of overtly framing a task's purpose.  
-Using image labeling as a canonical microtask, we found that prior 
+Using image-labeling as a canonical microtask, we found that prior 
 tasks influences the vocabulary that a worker uses when labeling 
@@
 but also modulate the richness and specialization of her vocabulary.  
-While they can be a source of systematic bias, our
-results suggest that intertask effects can be leveraged
+While intertask effects can be a source of systematic bias, our
+results suggest that, when properly controlled, they can be leveraged
 to hone worker focus and specificity.  Though we focused on microtask 
@@
 Unlike CPUs and GPUs, the experiments we present here suggest HPUs
-are subject to \textit{hysteresis}, meaning that their output depends
+are subject to \textit{hysteresis}, meaning that their outputs depend
 on the history of their inputs.  Given the
-increasing prevalence of microtask-based methodologies, other factors 
+increasing prevalence of microtask-based research methods, other factors 
 affecting HPU outputs have received considerable attention.
@@
 We investigated intertask effects using image-labeling tasks on the Amazon 
-Mechanical Turk (MTurk) microtask platform.  Image labeling tasks are among
+Mechanical Turk (MTurk) microtask platform.  Image-labeling tasks are among
 the most common MTurk tasks \cite{chandler2013breaking,Berinsky2012351,Finnerty2013,paolacci2010running}, a trend which will probably continue 
@@
 The results showed that intertask effects are stronger than framing effects.  
-Framing effects were comparable to intertask effects only when we had the
-workers actively reiterate the frame by means of a combo-box input.
+Framing effects were comparable to intertask effects only when the workers 
+were asked to actively reiterate the frame by means of a combo-box input.
 Using the wordnet corpus (\#), we found that intertask 
@@
 serious source of bias, they can also be leveraged to help achieve
-expert-level performance in crowdsourcing when properly controlled.
+expert-level performance in crowdsourcing, when properly controlled.
 
@@
 		F) test tasks for \textit{exp2}.  The full set of experimental 
-		materials is shown in the supplementary material.
+		materials is shown in the supplementary text.
 	}
@@
 labeled 5 images containing either food (treatment \textit{task1:food}), or 
-objects, (treatment \textit{task1:obj}), and then performed test tasks, in 
+objects (\textit{task1:obj}), and then performed test tasks, in 
 which they 
@@
 Since culture is more abstract, one might expect different effects 
-in \textit{exp2}.  We again compared
-intertask effects (in treatment pair \textit{task2}) to framing effects 
+in \textit{exp2}.  In \textit{exp2}, we again investigated both
+intertask effects (in treatment pair \textit{task2}) and framing effects 
 (\textit{frame2}), but with a slight variation in the framing treatments.
@@
 
-In all treatments, workers were shown images one at a time, and provided
-5 labels for each.  From the perspective of the worker, there was no
+In all treatments, workers were shown images one at a time, and had to
+provide 5 labels for each.  From the perspective of the worker, there was no
 distinction or interruption between the initial and test tasks.  We used
@@
 While our study builds on research into the psychological mechanisms
-of task performance, there is a crucial difference in the question at issue. 
+of task performance, there is a crucial difference in our present goal. 
 Our goal is to measure the practical ramifications of intertask effects on 
@@
 if small, might be sufficient to distinguish one psychological mechanism 
-from another (\#), in our study 
+from another (\#), in our study, 
 \textit{effect size} is central.  Thus our main goal is not merely to reject 
@@
 below a news article as inappropriate; but for now, we leave 
-$\mathcal{D}$ unspecified.  Since worker's responses may
+$\mathcal{D}$ unspecified.  Since workers' responses may
 vary, repeating the same task might lead to different outcomes for 
-$\mathcal{D}$.  We shall define the notion of \textit{bias} in terms of the
-effect that prior tasks have on the probability of a positive outcome
-from $\mathcal{D}$.
-
-The nature of $\mathcal{D}$ will affect our measurement of bias.
-If $\mathcal{D}$ has random output, or if it always outputs ``yes'' 
+$\mathcal{D}$.  This decision not only models the reality that responses are
+actually used---introducing $\mathcal{D}$ allows us to define of \textit{bias}
+in a practical yet general way. We shall define bias in terms of the
+change in the probability of a positive outcome from $\mathcal{D}$, induced 
+by prior exposures.
+
+The kind of decision that $\mathcal{D}$ represents will affect our 
+measurement of bias.  For instance, if $\mathcal{D}$ is random, or if 
+it always generates ``yes'' 
 irrespective of the worker's response, then of course we will 
@@
 is the most susceptible to workers' biases. In the supplementary text, we 
-show that this
-problem can be formulated as a  machine learning problem, wherein one
-constructs a classifier that infers the exposure of a worker from her 
+show that this can be formulated as a  machine learning problem, wherein one
+constructs a classifier that infers the prior exposure of a worker from her 
 responses in test tasks.  The bias, $\theta$, induced by 
@@
 \paragraph{The strength and dynamics of intertask effects.}
-For each treatment pair, we trained a naive Bayes classifier (\# in the 
+For each treatment pair, we trained a na\"ive Bayes classifier (\# in the 
 supplementary material we discuss the choice of classifier, the
-approach to measuring accuracy, and draw a comparison to results using 
-a support vector machine in place of the naive Bayes classifier) to 
-distinguish workers from one treatment
-(e.g \textit{task1:food}) from those of the conjugate treatment 
+approach to measuring accuracy, and draw a comparison to the results obtained 
+if a support vector machine is used.) to distinguish workers from one 
+treatment (e.g \textit{task1:food}) from those of the conjugate treatment 
 (e.g. \textit{task1:obj}).  In \textit{task1} and \textit{task2}, intertask 
-effects profoundly biased worker outputs, whereas we could not detect 
+effects profoundly biased worker outputs, by approximately 30 and 50\% 
+respectively, whereas we could not detect 
 a statistically significant bias induced by framing in \textit{frame1} and 
-\textit{frame2} (see Fig.~\ref{fig:theta}).  The bias induced
-by framing was only of a comparable level to that induced by intertask 
-effects in \textit{echo1}.  
-Moreover, asking workers to reiterate the
-frame, as was done in \textit{echo1}, is probably interpreted as
-a direct signal from the requester that the frame should be acted upon.  In that sense, 
+\textit{frame2} (see Fig.~\ref{fig:theta}A).  The bias induced
+by framing was only appreciable in \textit{echo1}, reaching approximately 
+35\%.  
+We suspect that asking workers to reiterate the
+frame, as was done in \textit{echo1}, might be interpreted by workers as
+a direct signal that the frame should be acted upon.  In that sense, 
 \textit{echo1} is perhaps more indicative of the effects of an 
-\textit{instruction}.  This shows that
-intertask effects profoundly affect the responses of workers, producing an
+\textit{instruction}.  These observations show that
+prior tasks profoundly influence the responses of workers, producing an
 effect that is stronger than framing, and on par with the combination of 
@@
 		labeling tasks due to worker exposure effects.  The estimate was 
-		based on the performance of a multinomial naive Bayes classifier,
+		based on the performance of a multinomial na\"ive Bayes classifier,
 		trained to infer HPU exposures. A) Bias induced through various
@@
 
-To observe the dynamics of intertask effects, we trained a naive Bayes
+To observe the dynamics of intertask effects, we trained a na\"ive Bayes
 classifier to distinguish workers in \textit{task1} based on responses to
@@
 therein (more details are provided in the supplementary text). The first test 
-task shows the greatest bias, after which the effects drop off, but 
+task shows the greatest bias, after which the effects drop somewhat, but 
 substantial bias persists through the fifth test task
@@
 fact that workers are also influenced by their exposure to the test tasks, 
-which washes out the effects of initial tasks.
+which begins to wash out the effects of initial tasks.
 
@@
 the number of food references in \textit{task2:food} was
-less than that in \textit{task2:cult}. Also, the effects on the
+less than that in \textit{task2:cult} (see Fig.~\ref{fig:specificity}A). Also, the effects on the
 number of food references was, overall, somewhat smaller than one might 
-have expected given the extent of bias observed for \textit{task1}, 
-\textit{echo1}, and \textit{task2}.  This means that task and frame exposures
-induce other effects which are more subtle than a bulk shift in number 
+expect given the extent of bias observed in Fig.~\ref{fig:theta}A.  This means that task and frame exposures
+induce other effects which are more subtle than a bulk shift in the number 
 of references to the primed concept (food).
@@
 the ability to recognize objects in a briefer, quieter, or noisier signal (\#).
-Negative priming occurs when repeated exposure to a stimulus that is 
-perceived to be non-salient begins to be ignored (\#).
+Negative priming occurs when, after being repeatedly exposed to a stimulus 
+that is perceived to be non-salient, the person begins to ignore that 
+stimulus (\#).
 
@@
 as memories, concepts, and vocabulary related to food are activated.  
-However, as the worker labels successive images containing food, the basic 
-fact that an image contains food does not appear to be salient, since it 
+However, we argue that as the worker labels successive images containing food,
+the basic 
+fact that an image contains food will not appear to be salient, since it 
 does not serve to distinguish one image from another.  Thus, the most 
-generic reference to the fact that food appears, namely the label ``food'', 
-is suppressed, as by negative priming, while more specialized
+generic references to that fact, such as the label ``food'', 
+are suppressed, as by negative priming, while more specialized
 references are activated.  Whether workers in \textit{*:food} treatments
@@
 
+\paragraph{Recommendations and future work.} 
 Based on our observations throughout, we submit the following 
-recommendations for the consideration of those in the position of designing 
+recommendations for the consideration of people designing 
 any microtask, citizen science, or crowdsourcing initiative:
@@
 	\item{
-		Require active feedback to emphasize important details, 
-		as we did in \textit{echo1}.  Similarly, use training tasks rather
-		than (only) examples.
+		Require active feedback to emphasize important details about the 
+		tasks, as we did in \textit{echo1}.  Similarly, use training tasks 
+		rather than only examples.
 	}
@@
 		Although ``clean'' examples may be useful to provide clarity,
-		training tasks should contain the same kinds of noise or otherwise
+		use training tasks that contain the same kinds of noise or otherwise
 		distracting features as are expected in the real tasks.
@@
 		are often used as a quality control measure.
-		These should be dually considered as \textit{calibration tasks}.  
+		Treat these as \textit{calibration tasks}, and use them to regulate
+		the focus of the worker.
 		Feedback, for both correct and incorrect responses may further 
@@
 		For example, in the detection of pre-ictal (pre-seizure) EEG traces, 
-		most traces are not negative (\#).  In the absence of positive 
+		most traces are negative (\#).  In the absence of positive 
 		examples, the target concept may degrade or drift.
-		Drawing validation/calibration tasks from the underrepresented class,
-		while providing feedback might help sustain the target concept.
+		Draw calibration tasks from the underrepresented class,
+		and provide feedback, to help sustain the worker's target concept.
 	}
@@
 		an initial coarse classification.  For example, in detecting 
-		inappropriate comments, workers might initially choose from  
-		\texttt{okay}, \texttt{inappropriate}, and \texttt{borderline}.  
-		Following the coarse classification, the 
-		\texttt{borderline} examples could be batched together.  Workers could
-		then calibrate to finer distinctions while coding a more homogeneous 
-		set of images.
+		inappropriate comments, provide the choices   
+		\texttt{okay}, \texttt{inappropriate}, and \texttt{borderline},
+		and incentivise inter-worker agreement
+		Next, batch the \texttt{borderline}.  Coding this more homogeneous
+		borderline set will help workers to calibrate to the finer 
+		distinctions necessary for the task.
 	}
@@
 intertask effects, which were overlooked until now, merit similar 
-consideration.  Although we found that intertask effects can be a major 
-source of bias, they might be used to drive tune workers' attention and 
+attention.  Although we found that intertask effects can be a major 
+source of bias, they might be used to tune workers' attention and 
 specificity relative to
 a target concept.  Microtask work, citizen science, and other crowdsourcing
-initiatives, as well task requiring expert opinions, often share the common 
-feature that they rely on repetitive human judgments.  Therefore, such 
-applications all stand to benefit from the findings and suggestions 
-presented here.
+initiatives, as well task requiring expert opinions, often rely on repetitive 
+human judgments.  Therefore, such applications all stand to benefit from the 
+findings and suggestions presented here.
 
@@
 		used in \textit{echo:food}; and D) an 
-		example of an image labeling task.
+		example of an image-labeling task.
 	}
@@
 
-	For the purpose of training and testing a naive Bayes classifier, we 
+	For the purpose of training and testing a na\"ive Bayes classifier, we 
 	performed an additional preprocessing step.  We tagged words with the
@@
 
-\paragraph{Selection of the naive Bayes classifier.}
+\paragraph{Selection of the na\"ive Bayes classifier.}
 A great deal of work has been done in the application of classifiers to
@@
 The Support Vector Machine (SVM) approach is known to perform well, better in 
-general than naive Bayes.  However, three considerations drove us to use
-a naive Bayes classifier in favor of SVM.
+general than na\"ive Bayes.  However, three considerations drove us to use
+a na\"ive Bayes classifier in favor of SVM.
 
@@
 a principled manner, generally adding further hyperparameters which could
-be optimized.  However, one of the strengths of the naive Bayes classifier
+be optimized.  However, one of the strengths of the na\"ive Bayes classifier
 is that it's performance is not generally degraded from the inclusion of 
 large numbers of features, even when the number of examples is comparatively
-small.  We expected this feature of the naive Bayes classifier to be 
+small.  We expected this feature of the na\"ive Bayes classifier to be 
 advantageous in our case.
 
-Second, the standard implementation of the naive Bayes classifier has no 
+Second, the standard implementation of the na\"ive Bayes classifier has no 
 hyperparameters to optimize.  This allows us to forgo the common practice 
@@
 
-Third, the naive Bayes algorithm is based on an assumption that the 
+Third, the na\"ive Bayes algorithm is based on an assumption that the 
 probability of observing one feature is independent from the observation
@@
 pragmatic rather than theoretical reasons, and is rarely satisfied.  However,
-if it \textit{is} satisfied, then the naive Bayes classifier is optimal.
+if it \textit{is} satisfied, then the na\"ive Bayes classifier is optimal.
 In our case, conditional independence means that, provided we know the 
@@
 		distinguishing workers that had undergone different exposures.
-		The bias was determined using (A-F) a naive Bayes classifier, and 
+		The bias was determined using (A-F) a na\"ive Bayes classifier, and 
 		(G-L) an SVM classifier.
@@
 Fig.~\ref{fig:theta}A using different combinations of preprocessing options,
-and using both the naive Bayes and an SVM classifier.
-
-Unlike the naive Bayes classifier, it is necessary to tune the cost and 
+and using both the na\"ive Bayes and an SVM classifier.
+
+Unlike the na\"ive Bayes classifier, it is necessary to tune the cost and 
 gamma hyperparameters of the SVM classifier, as well as choose a kernel.

### 2014-12-03 docs/publications/2014.09_SCIENCE/man.tex
small edit

@@
 acts as a strong, but as yet unexplored source of bias.  
-These \textit{intertask effects}, rival the
+These \textit{intertask effects} rival the
 severity of overtly framing a task's purpose.  
 Using image-labeling as a canonical microtask, we found that prior 
-tasks influences the vocabulary that a worker uses when labeling 
-subsequent images in profound an nuanced ways.  Prior tasks not only 
+tasks influence the vocabulary that a worker uses when labeling 
+subsequent images in both profound an nuanced ways.  Prior tasks not only 
 alter what a worker focuses on, 

### 2014-12-03 docs/publications/2014.09_SCIENCE/man.tex
edits and improvements to figs

@@
 		Examples of images used for various experiments and treatments:
-		A) initial tasks for \textit{task1:food}, B) initial tasks for 
-		\textit{task1:obj}, C) test tasks for treatments in \textit{exp1}, 
-		D) initial tasks for \textit{task2:food}, 
-		E) initial tasks for \textit{task2:cult},  
-		F) test tasks for \textit{exp2}.  The full set of experimental 
-		materials is shown in the supplementary text.
+		A) initial task for \textit{task1:food}, B) initial task for 
+		\textit{task1:obj}, C) test task for treatments in \textit{exp1}, 
+		D) initial task for \textit{task2:food}, 
+		E) initial task for \textit{task2:cult},  
+		F) test task for treatments in \textit{exp2}.  
+		The full set of experimental materials is shown in the 
+		supplementary text.
 	}
@@
 
-In all treatments, workers were shown images one at a time, and had to
-provide 5 labels for each.  From the perspective of the worker, there was no
+In all treatments, workers were shown images one at a time, and provided five 
+labels for each.  From the perspective of the worker, there was no
 distinction or interruption between the initial and test tasks.  We used
@@
 		\hline \noalign{\smallskip}
-		\multicolumn{3}{c}{\textbf{Treatment name}} & \parbox[c]{1.6cm}{\centering \textbf{Frame}} & \parbox[c]{1.3cm}{\centering \textbf{Initial\\ tasks}}	\\
+		\multicolumn{3}{c}{\textbf{Treatment name}} & \parbox[c]{1.4cm}{\centering \textbf{Frame}} & \parbox[c]{1.3cm}{\centering \textbf{Initial\\ tasks}}	\\
 
@@
 
-		\multirow{6}{*}{ \parbox[c]{0.7cm}{ \phantom{XXX} exp1}} 
+		\multirow{6}{*}{ \parbox[c]{0.8cm}{ \phantom{XX} exp1}} 
 			& \multirow{2}{*}{task1} & food & none & food\\
@@
 
-		\multirow{4}{*}{exp2} 
+		\multirow{4}{*}{\parbox[c]{0.8cm}{exp2}} 
 			& \multirow{2}{*}{task2}  &  food & none & food\\
@@
 
-	\caption{ \footnotesize{ 
+	\caption{ 
 		We use the treatment names shown to refer to specific sections of 
 		the experimental data.
-	}}
+	}
 	\label{table:treatments}
@@
 	\caption{
-		Lower-bound estimates for the  worst-case bias introduced in image
-		labeling tasks due to worker exposure effects.  The estimate was 
-		based on the performance of a multinomial na\"ive Bayes classifier,
-		trained to infer HPU exposures. A) Bias induced through various
-		modalities and prime concepts (see Table 1). B) Bias induced in 
-		\textit{task1}, as a function of test task position.  Error bars
-		show the one-tailed 95\% confidence interval.
+		Bias as measured by a na\"ive Bayes classifier, $\theta_\mathrm{NB}$,
+		induced in image-labeling tasks, due to framing and 
+		intertask effects. 
+		A) Bias in the responses to five test tasks,
+		measured between the pairs of treatments indicated on the abscissa.  
+		B) Bias between the treatments of \textit{task1}, 
+		measured for individual test tasks, and plotted as a function of 
+		task position.  Error bars show the 95\% confidence intervals.
 	}

### 2014-12-03 src/new_plots.py

@@ -186,8 +186,9 @@ def plot_specificity(
 	# Fuss with axes labelling
 	ax1.set_xticks([x + width/2.0 for x in X_0])
 	plt.ylim(-13, 13)
-	ax1.set_ylabel(r'$\Delta$ % food labels', size=12)
+	ax1.set_ylabel(r'$\Delta$ references $(\%)$', size=12)
 	plt.setp(ax1.get_xticklabels(), visible=False)
+	ax1.yaxis.labelpad = 0
 
 	vocab_data = json.loads(open(read_vocab_fname).read())
 
@@ -239,7 +240,8 @@ def plot_specificity(
 	plt.setp(ax2.get_xticklabels(), visible=False)
 	ylims = plt.ylim()
 	plt.ylim(-6, 22)
-	ax2.set_ylabel(r'$\Delta$ % food vocabulary', size=12)
+	ax2.set_ylabel(r'$\Delta$ richness $(\%)$', size=12)
+	ax2.yaxis.labelpad = 7.5
 
 	# now plot the specificity data.  First get organized
 	specificity_data = json.loads(open(read_specificity_fname).read())
@@ -283,11 +285,12 @@ def plot_specificity(
 	plt.xlim(xlims)
 	ylims = plt.ylim()
 	plt.ylim(ylims[0], 28)
-	ax3.set_ylabel(r'$\Delta$ % food specificity', size=12)
+	ax3.set_ylabel(r'$\Delta$ specialization $(\%)$', size=12)
 	xlabels = [l for k,l in specificity_keys_labels]
 	ax3.set_xticks([x + width/2. for x in X_3])
 	ax3.set_xticklabels(xlabels, rotation=45, size=12,
 		horizontalalignment='right')
+	ax3.yaxis.labelpad = 7.5
 
 	ax1.text(4.7, 11.5, 'A', va='top', ha='right', size=18, color='0.55')
 	ax2.text(4.7, 20.5, 'B', va='top', ha='right', size=18, color='0.55')
@@ -510,9 +513,9 @@ def plot_theta(
 	accuracies = [this_data[tn] for tn in test_names]
 
 	# convert accuracy to priming difference (which is what we want to plot)
-	Y_aggregate = [2*a-1 for a in accuracies]
+	Y_aggregate = [100*(2*a-1) for a in accuracies]
 	err_low = [
[…]

### 2014-12-03 docs/publications/2014.09_SCIENCE/man.tex
updates to figure legends

@@
 	\caption{
-		Detailed exposure effects on workers' label vocabulary, for various
-		exposure modalities and prime concepts (see Table 1).  A) Change in 
-		the number of food-related labels used. B) Change in the total number 
-		of \textit{unique} food-related labels used. C) Relative specificity
-		of treatment pairs, when considering food-related labels.  For all
-		plots, a positive bar height indicates an increase for the 
-		food-exposed treatment for the pair indicated on the abscissa.
+		Intertask and framing effects on the vocabulary workers use to refer 
+		to food(\#), when labeling images, for various treatment pairs.
+		A) Relative change in the number references to food. 
+		B) Relative change in the number of \textit{unique} 
+		references to food (lexical richness). 
+		C) Relative specialization of food references, based on the 
+		hypernym-hyponym relations (this calculation is shown in the 
+		supplementary text).  For all
+		plots, a positive bar height indicates that the \textit{*:food}
+		treatment has more of the quantity than its conjugate treatment.
 	}

### 2014-12-03 docs/publications/2014.09_SCIENCE/man.tex
little fig edit

@@
 			\noalign{\smallskip} \cline{2-5} \noalign{\smallskip}
-			& \multirow{2}{*}{echo} & food & food & none\\
+			& \multirow{2}{*}{echo1} & food & food & none\\
 			& & obj & objects & none\\
@@
 of initial tasks was shown (except for the treatments in \textit{frame2}
-and \textit{echo}) followed by (in all cases) a set of test tasks.  In
+and \textit{echo1}) followed by (in all cases) a set of test tasks.  In
 \textit{exp1}, two kinds of frame were used, one simple frame, and one where
@@
 		\textit{frame2:cult};  
-		C) an echoed frame, as used in \textit{echo:obj}, and similar to that
-		used in \textit{echo:food}; and D) an 
+		C) an echoed frame, as used in \textit{echo1:obj}, and similar to that
+		used in \textit{echo1:food}; and D) an 
 		example of an image-labeling task.
@@
 		\toprule
-		\multicolumn{2}{c}{\textit{echo}} \\
+		\multicolumn{2}{c}{\textit{echo1}} \\
 		\toprule

### 2014-12-04 docs/publications/2014.09_SCIENCE/man.tex
catch more typos and update plot script

@@
 distinction or interruption between the initial and test tasks.  We used
-workers' unique identifiers to ensure that they only participated in a 
+workers' unique identifiers to ensure that they only participated in
 one treatment of a single experiment.
@@
 $\mathcal{D}$.  This decision not only models the reality that responses are
-actually used---introducing $\mathcal{D}$ allows us to define of \textit{bias}
+actually used---introducing $\mathcal{D}$ allows us to define \textit{bias}
 in a practical yet general way. We shall define bias in terms of the
@@
 the \textit{*:food} treatments had more food references than their conjugate
-treatments.  But taken together, these facts indicate that workers are opting 
+treatments.  But taken together, these facts indicate that \textit{*:food}
+workers are opting 
 to use more specialized food-references in place of ``food''.  
@@
 of these factors.  The reduction in food references from workers in 
-\textit{task2:food} relative
-to those in \textit{task2:cult} may also be related to the novelty that 
-workers in 
+\textit{task2:food} relative to \textit{task2:cult}, seen in in 
+Fig.~\ref{fig:specificity}A, may also be
+related to the novelty that workers in 
 \textit{task2:cult} experience when they first encounter food in the test 
@@
 		\texttt{okay}, \texttt{inappropriate}, and \texttt{borderline},
-		and incentivise inter-worker agreement
-		Next, batch the \texttt{borderline}.  Coding this more homogeneous
-		borderline set will help workers to calibrate to the finer 
-		distinctions necessary for the task.
+		and incentivise inter-worker agreement.  Next, have workers 
+		code the \texttt{borderline} cases, but without providing the
+		\texttt{borderline} code.  Coding this more homogeneous
+		set will help workers to calibrate to the finer features that are 
+		salient in distinguishing borderline cases.
 	}
@@
 a target concept.  Microtask work, citizen science, and other crowdsourcing
-initiatives, as well task requiring expert opinions, often rely on repetitive 
-human judgments.  Therefore, such applications all stand to benefit from the 
+initiatives, as well tasks requiring expert opinions, often rely on repetitive
+human judgments.  Such applications all stand to benefit from the 
 findings and suggestions presented here.

### 2014-12-04 src/new_plots.py

@@ -537,7 +537,7 @@ def plot_theta(
 
 	ax1.set_ylabel(r'$\theta_\mathrm{NB}\;(\%)$', size=12)
 
-	xlabels = [r'$task1$', r'$frame1$', r'$echo$', '$task2$', '$frame2$']
+	xlabels = [r'$task1$', r'$frame1$', r'$echo1$', '$task2$', '$frame2$']
 
 	eps = 0.2
 	ax1.set_xticks(map(lambda x: x + width/2. + eps, X))
@@ -581,7 +581,7 @@ def plot_theta(
 	ax2.tick_params(axis='x', colors='0.25')
 	ax2.set_xticklabels(xlabels, rotation=0, size=12,
 		horizontalalignment='center', color='k')
-	ax2.set_xlabel(r'test task position', size=12)
+	ax2.set_xlabel(r'test task position', size=8)
 
 #	# Plot the by_img data series
 #	ax3 = plt.subplot(gs[2], sharey=ax1)

### 2014-12-04 docs/publications/2014.09_SCIENCE/man.tex
tiny edits

@@
 
-To couch intertask effects in a practical yet general setting, we imagine
+To couch intertask effects in a practical setting, we imagine
 that, after a worker performs a task, her response is used to make some 
@@
 actually used---introducing $\mathcal{D}$ allows us to define \textit{bias}
-in a practical yet general way. We shall define bias in terms of the
+in a practical yet general way. We define bias in terms of the
 change in the probability of a positive outcome from $\mathcal{D}$, induced 

### 2014-12-05 docs/publications/2014.09_SCIENCE/man.tex
small change to images.pdf

@@
 	\centering
-	\includegraphics[scale=0.7]{figs/images.pdf}
+	\includegraphics[scale=0.6]{figs/images.pdf}
 	\caption{
@@
 
-\subsection*{S7: Analysis of variance}
+\subsection*{S7: Variance and significance tests}
+
 	\paragraph{Variance in the average fraction food-related labels}
@@
 
-	\paragraph{Variance in food vocabulary size.}
-	\td{Not sure how to calculate this yet.}
+	\paragraph{Variance in food vocabulary size (lexical richness).}
+	The number of unique words in a text is strongly dependant on the size
+	of the text: as more text is sampled, previously unseen words continue
+	to be found, though at a decreasing rate.  This means that when the 
+	lexical richness is measured for a large and small sample, they are not 
+	actually estimates of the same quantity.  It is not clear that drawing 
+	confidence intervals around the lexical richness measured at one sample 
+	size is meaningful, nor is it easily done.
+
+	However, we can construct a null model based on the hypothesis that
+	two treatment's have the same probability distribution over tokens
+	(and hence the same lexical richness). If treatments $A$ and $B$ have
+	the same word frequency distributions, then, they are samples from
+	the same population.  Pooling the workers from both treatments together,
+	then randomly partitioning them into balanced sets $A'$ and $B'$ will
+	still yield samples from the same underlying population.  By repeating 
+	this pooling and re-partitioning many times, and computing the 
+	relative lexical richness, we can determine the critical difference in
+	lexical richness from the 97.5 and 2.5 percentiles.  We can then test 
+	the hypothesis that $A$ and $B$ were from the same population by 
+	observing whether the difference in lexical richness of the original 
+	sets is within this percentile range.
+
+	We performed this calculation using 1000 pooling and resampling 
+	iterations, and plotted the 97.5 percentile as a star in 
+	Fig~\ref{fig:specificity}B in the main text.  All of the differences
+	in lexical richness were significant except that of \textit{frame2}.
 
 	\paragraph{Variance in food specificity.}
-	\td{Need to calculate this using bootstrapping.}
+	The variance in the specificity measurements was calculated using a 
+	bootstrapping proceedure.  For two given treatments $A$ and $B$, 
+	119 workers were sampled from each with replacement, giving the bootstrap
+	samples $A'$ and $B'$, and the relative specificity between these 
+	was measured as described in \textsection S6.
+	This was repeated 1000 times.  The 2.5 and 97.5 percentiles were used
+	to create the 95\% confidence intervals.
 

### 2014-12-17 docs/publications/2014.09_SCIENCE/man.tex
major revisions based on Dereks v1 critiques

@@
 \author
-{Edward Newell, Derek Ruths,\\
+{Edward Newell \\ Derek Ruths\\
 \\
@@
 
-Faced with the scale and complexity of the data revolution, researchers and
-industry are increasingly relying on \textit{human computation}.  Microtask
+Faced with the ever-growing scale and complexity of data, researchers and
+industry are increasingly relying on \textit{human computation} as a means
+to extract useful knowledge.  Microtask
 platforms, like Amazon Mechanical Turk, act like a human compute server,
@@
 This has lead to broad adoption across a spectrum of disciplines
-in the humanities and computer science, as well as in research into medical 
-imaging technologies and other applications where expert opinion would 
-normally be sought.  Here we show that an inherent
-feature of microtask platforms, the repetition of similar tasks,
-acts as a strong, but as yet unexplored source of bias.  
-These \textit{intertask effects} rival the
+in the social sciences and computer science, as well as in research into 
+medical imaging technologies and other applications where expert opinion 
+would normally be sought.  Here we show that an inherent
+feature of microtask platforms and most crowdsourcing settings---the 
+repetition of similar tasks---acts as a strong, but as yet unexplored source 
+of bias.  These \textit{intertask effects} rival the
 severity of overtly framing a task's purpose.  
-Using image-labeling as a canonical microtask, we found that prior 
-tasks influence the vocabulary that a worker uses when labeling 
-subsequent images in both profound an nuanced ways.  Prior tasks not only 
-alter what a worker focuses on, 
-but also modulate the richness and specialization of her vocabulary.  
+Using image-labeling as a canonical microtask, we show that prior 
+tasks influence the content that workers focus on, and the richness and
+specialization of their vocabulary.    
 While intertask effects can be a source of systematic bias, our
-results suggest that, when properly controlled, they can be leveraged
-to hone worker focus and specificity.  Though we focused on microtask 
-platforms due to their emerging prominence, our results apply to  
-citizen science, crowdsourcing, and any application involving repetitive 
-tasks relying on human judgment.
+results suggest that, when properly controlled, they might be leveraged
+to hone worker focus and specificity, and could play a key role in designing 
+tasks that elicit expert-level judgments.
 \end{sciabstract}
 
-\section*{Introduction}
-Microtask platforms are online marketplaces on which \textit{requesters} 
+\section*{Main text}
+Microtask platforms are online marketplaces in which \textit{requesters} 
 post batches of tasks, and \textit{workers} complete them
@@
 
-Unlike CPUs and GPUs, the experiments we present here suggest HPUs
-are subject to \textit{hysteresis}, meaning that their outputs depend
-on the history of their inputs.  Given the
-increasing prevalence of microtask-based research methods, other factors 
-affecting HPU outputs have received considerable attention.
-This includes various task-design parameters such as the level of 
-pay \cite{kazai2013analysis}, the training \cite{le2010ensuring} and 
+Given the increasing prevalence of microtask-based research methods, there
+is a desire to understand the factors affecting the reliability of HPU
+outputs.  Researchers have investigated task-design parameters such as the 
+level of pay \cite{kazai2013analysis}, the training \cite{le2010ensuring} and 
 pre-screening \cite{paolacci2010running} of workers, and user-interface 
@@
 \cite{BJOP1796,No2007,beller1971priming}, and, in particular, 
-task-repetition effects \cite{Gass1999549,sohn2001task}.  But to our 
-knowledge, no study has investigated the practical ramifications 
-of intertask effects on human computation.
+task-repetition effects \cite{Gass1999549,sohn2001task}.  
+Yet to our knowledge, no study has investigated the practical ramifications 
+of intertask effects on human computation. The experiments we 
+present here show that, unlike CPUs and GPUs, HPUs are subject to 
+\textit{hysteresis}, meaning that their outputs depend on the 
+\textit{history} of their inputs.
 
@@
 Mechanical Turk (MTurk) microtask platform.  Image-labeling tasks are among
-the most common MTurk tasks \cite{chandler2013breaking,Berinsky2012351,Finnerty2013,paolacci2010running}, a trend which will probably continue 
+the most common MTurk tasks \cite{chandler2013breaking,Berinsky2012351,Finnerty2013,paolacci2010running}.  This trend will probably continue 
 in the long term because of their role in computer vision research 
-\cite{5543192}.
-In our experiments, workers performed a set of \textit{initial tasks}, 
-followed by a set of \textit{test tasks}. Crucially, no distinction was
-made between these sets from the perspective of the worker. We varied the 
-initial tasks (for example, having workers label images of food or objects), 
-and observed the ensuing effects on responses in test tasks.  
-As a point of 
-comparison, we also included treatments in which we framed the tasks in terms 
-of different purposes.
-
-The results showed that intertask effects are stronger than framing effects.  
-Framing effects were comparable to intertask effects only when the workers 
-were asked to actively reiterate the frame by means of a combo-box input.
-Using the wordnet corpus (\#), we found that intertask 
-effects can hone a worker's focus, and boost the specialization
-and lexical richness of her labels.  Thus, while intertask effects may be a 
-serious source of bias, they can also be leveraged to help achieve
-expert-level performance in crowdsourcing, when properly controlled.
-
-\paragraph{Experimental setup.}
+\td{find another application} \cite{5543192}.  In microtask platforms, it is typical for work to be divided 
+into bundles; on MTurk, these bundles are called Human Intelligence Tasks 
+(HITs). Because of this bundling pattern, even if workers perform only one 
+HIT, the opportunity for intertask effects arises.  For clarity, 
+we will use ``task'' to mean the smallest repeatable unit of work, which, 
+in our study, consists of labeling a single image.
+
+In our first experiment, which we will refer to as 
+\textit{intertask-food-objects}, workers were either assigned to the 
+\textit{food} or \textit{objects} treatment.  Workers in these treatments
+performed a set of five \textit{initial tasks}, which involved labeling
+images depicting either food or (non-food) objects, depending on the worker's 
+treatment (see Fig.~\ref{fig:task}A and B).  Following the initial 
+tasks, workers performed five \textit{test tasks}, which were identical for 
+both treatments.  The test tasks contained images depicting a 
+mixture of food and other objects (see Fig.~\ref{fig:task}C).  Five initial 
+tasks, together with the test tasks, comprised one HIT 
+(\# workers were only allowed to participate once). During the HIT, workers 
+were presented images one at a time, and, crucially, there was no distinction
+or interruption between the initial and test tasks.
+
+A $\chi^2$ test (\#) shows that the frequency of word usage by
+workers in the \textit{food} and \textit{objects} treatments differed
+significantly during test tasks, even though the test tasks were identical 
+for the treatments.  This shows that earlier tasks have a 
+significant effect on later ones, and raises concerns about the 
+design of microtasks, and possibly the microtask methodology itself.
+
+While this affirms the \textit{existence} of intertask effects, we wish to
+understand the nature and severity of the bias induced by prior task 
+exposure.  To formalize a notion of the extent of bias, we must first 
+acknowledge that workers' responses to microtasks
+carry an element of stochasticity: two workers will not, in general, provide
+the same response to a given task.  Because worker responses are stochastic,
+we take the extent of bias, $\theta$, to be the total shift in probability 
+mass, for giving certain responses (i.e. certain words),
+caused by a perturbation like intertask effects (\# in other words, the 
+bias is the L1-distance between the probability distributions for responses
+under one treatment, to that for responses under another.)
+
+It is difficult to measure the change in a probability distribution based on
+samples alone (\#), so we reformulate the problem slightly. Consider that,  
+no matter the ultimate purpose of a microtask study, a microtask response
+is used in \textit{some kind} of subsequent decision or 
+further processing.
+We denote this dowstream decision by $\mathcal{D}$.  Since $\mathcal{D}$
+takes a microtask response as input, biases in the microtask response will 
+in general lead to biases in the output of $\mathcal{D}$.  
+We can make use of this fact, 
+by placing a machine learning algorithm (a classifier), in the role of 
+$\mathcal{D}$.  This classifier takes as input a worker's responses to test 
+tasks, from which it learns to infer the worker's treatment 
+(i.e. the initial tasks she was given). 
+Intuitively, the classifier's ability to infer the worker's treatment
+depends on how strongly the exposure to prior tasks influences responses to 
+subsequent ones.  Formally, the bias, $\theta$, is bounded 
+by the accuracy of the classifier, $\eta$ (\#):
+\begin{equation}
+	\theta \geq 2\eta - 1.
+	\label{l1}
+\end{equation}
+Thus, measuring the performance of the classifier allows us to establish a
+lower bound on the extent of bias. This approach can be used to bound the 
+bias induced by any purturbation, including both intertask effects and 
+framing.  Bias ranges from 0 (meaning there are no intertask effects), to 1 
+(or 100\%) (meaning that changing initial tasks leads to a completely 
+different set of responses to test tasks).
+
 \begin{figure}
@@
 		Examples of images used for various experiments and treatments:
-		A) initial task for \textit{task1:food}, B) initial task for 
-		\textit{task1:obj}, C) test task for treatments in \textit{exp1}, 
-		D) initial task for \textit{task2:food}, 
-		E) initial task for \textit{task2:cult},  
-		F) test task for treatments in \textit{exp2}.  
+		(A) initial task for \textit{task1:food}, (B) initial task for 
+		\textit{task1:obj}, (C) test task for treatments in \textit{exp1}, 
+		(D) initial task for \textit{task2:food}, 
+		(E) initial task for \textit{task2:cult},  
+		(F) test task for treatments in \textit{exp2}.  
 		The full set of experimental materials is shown in the 
@@
 
-We performed two experiments, \textit{exp1} and \textit{exp2}, which consisted
-of various pairs of treatments.  The treatments in each pair were subjected to
-the same exposure modality, either initial tasks or framing, but differed in
-the content of the exposure.  Table \ref{table:treatments}  
-summarizes the treatments and introduces a naming convention that we use 
-in what follows.
-In \textit{exp1}, workers in the treatment pair \textit{task1} initially
-labeled 5 images containing either food (treatment \textit{task1:food}), or 
-objects (\textit{task1:obj}), and then performed test tasks, in 
-which they 
-labeled images containing both food and objects (see Fig.~\ref{fig:task} for 
-examples of the images used). In \textit{exp1}, we included two other 
-treatment pairs, \textit{frame1} and \textit{echo1}, in which workers did not 
-perform initial tasks, but instead were given information which framed the 
-purpose of the tasks.  Workers in \textit{frame1} were told that the tasks 
-were ``Funded by the laboratory for the visual perception of 
-\{ Food and Ingredients $\vert$ Objects and Tools~\}''.  In \textit{echo1},
-we sharpened the frame, by indicating that ``The purpose of this study is to 
-understand the visual perception of 
-\{ Food and Ingredients $\vert$ Objects and Tools~\}'' and then asking the
-worker to reiterate the purpose of the task using a combo-box input.
-
-In contrast to \textit{exp1}, which was based on concepts of food and
-objects, \textit{exp2} was based food and \textit{culture}.
-Since culture is more abstract, one might expect different effects 
-in \textit{exp2}.  In \textit{exp2}, we again investigated both
-intertask effects (in treatment pair \textit{task2}) and framing effects 
-(\textit{frame2}), but with a slight variation in the framing treatments.
-In \textit{frame2}, workers were not only exposed to a frame, but also 
-performed a set of initial tasks before the test tasks.  Since its purpose 
-was still
-to investigate framing effects, the initial tasks in \textit{frame2}
-were not varied. Thus, \textit{frame2} provides insight into the moderating 
-effect that intervening tasks might have on framing effects.
-
-In all treatments, workers were shown images one at a time, and provided five 
-labels for each.  From the perspective of the worker, there was no
-distinction or interruption between the initial and test tasks.  We used
-workers' unique identifiers to ensure that they only participated in
-one treatment of a single experiment.
-
-\setlength{\tabcolsep}{2pt}
-\begin{table}[t]
-\centering
-\begin{tabular}{ c c c c c }
-		\hline \noalign{\smallskip}
-		\multicolumn{3}{c}{\textbf{Treatment name}} & \parbox[c]{1.4cm}{\centering \textbf{Frame}} & \parbox[c]{1.3cm}{\centering \textbf{Initial\\ tasks}}	\\
-
-		\noalign{\smallskip} \hline \noalign{\smallskip}
-
-		\multirow{6}{*}{ \parbox[c]{0.8cm}{ \phantom{XX} exp1}} 
-			& \multirow{2}{*}{task1} & food & none & food\\
-			& & obj & none & objects\\
-
-			\noalign{\smallskip} \cline{2-5} \noalign{\smallskip}
-			& \multirow{2}{*}{frame1} & food & food & none\\
-			& & obj & objects & none\\
-
-			\noalign{\smallskip} \cline{2-5} \noalign{\smallskip}
-			& \multirow{2}{*}{echo1} & food & food & none\\
-			& & obj & objects & none\\
-
-		\noalign{\smallskip} \hline \noalign{\smallskip}
-
-		\multirow{4}{*}{\parbox[c]{0.8cm}{exp2}} 
-			& \multirow{2}{*}{task2}  &  food & none & food\\
-			& 	&  cult & none & culture\\
-			\noalign{\smallskip} \cline{2-5} \noalign{\smallskip}
-			& \multirow{2}{*}{frame2} & food & food & food\\
-			& 	& cult & culture & food\\
-
-		\noalign{\smallskip} \hline  
-	\end{tabular}
-
-	\caption{ 
-		We use the treatment names shown to refer to specific sections of 
-		the experimental data.
-	}
-	\label{table:treatments}
-\end{table}
-
-\paragraph*{Measuring computational hysteresis.}
-While our study builds on research into the psychological mechanisms
-of task performance, there is a crucial difference in our present goal. 
-Our goal is to measure the practical ramifications of intertask effects on 
-the microtask methodology. Whereas a statistically significant effect, even 
-if small, might be sufficient to distinguish one psychological mechanism 
-from another (\#), in our study, 
-\textit{effect size} is central.  Thus our main goal is not merely to reject 
-the null hypothesis that initial tasks have no effect
-(we do this in the supplementary text).
-
-To couch intertask effects in a practical setting, we imagine
-that, after a worker performs a task, her response is used to make some 
-kind of yes-or-no decision, $\mathcal{D}$.  For example, this decision 
-could be whether or not to flag a certain comment
-below a news article as inappropriate; but for now, we leave 
-$\mathcal{D}$ unspecified.  Since workers' responses may
-vary, repeating the same task might lead to different outcomes for 
-$\mathcal{D}$.  This decision not only models the reality that responses are
-actually used---introducing $\mathcal{D}$ allows us to define \textit{bias}
-in a practical yet general way. We define bias in terms of the
-change in the probability of a positive outcome from $\mathcal{D}$, induced 
-by prior exposures.
-
-The kind of decision that $\mathcal{D}$ represents will affect our 
-measurement of bias.  For instance, if $\mathcal{D}$ is random, or if 
-it always generates ``yes'' 
-irrespective of the worker's response, then of course we will 
-find zero bias.  Likewise, there is an upper limit to the bias induced on $\mathcal{D}$. In a precise sense, the bias of $\mathcal{D}$ can only be as
-great as the bias inherent in the worker's response 
-(this is formalized in the supplementary text).  Therefore, to estimate the 
-bias induced in workers' outputs, we adopt an 
-adversarial approach: we seek to construct the decision that 
-is the most susceptible to workers' biases. In the supplementary text, we 
-show that this can be formulated as a  machine learning problem, wherein one
-constructs a classifier that infers the prior exposure of a worker from her 
-responses in test tasks.  The bias, $\theta$, induced by 
-prior exposures, can then be bounded using the classifier's accuracy, 
-$\eta$ (\#):
-\begin{equation}
-	\theta \geq 2\eta - 1
-	\label{l1}
-\end{equation}
-
-\paragraph{The strength and dynamics of intertask effects.}
-For each treatment pair, we trained a na\"ive Bayes classifier (\# in the 
+%\setlength{\tabcolsep}{2pt}
+%\begin{table}[t]
+%\centering
+%\begin{tabular}{ c c c c c }
+%		\hline \noalign{\smallskip}
+%		\multicolumn{3}{c}{\textbf{Treatment name}} & \parbox[c]{1.4cm}{\centering \textbf{Frame}} & \parbox[c]{1.3cm}{\centering \textbf{Initial\\ tasks}}	\\ 
+%
+%		\noalign{\smallskip} \hline \noalign{\smallskip}
+%
+%		\multirow{6}{*}{ \parbox[c]{0.8cm}{ \phantom{XX} exp1}} 
+%			& \multirow{2}{*}{task1} & food & none & food\\
+%			& & obj & none & objects\\
+%
+%			\noalign{\smallskip} \cline{2-5} \noalign{\smallskip}
+%			& \multirow{2}{*}{frame1} & food & food & none\\
+%			& & obj & objects & none\\
+%
+%			\noalign{\smallskip} \cline{2-5} \noalign{\smallskip}
+%			& \multirow{2}{*}{echo1} & food & food & none\\
+%			& & obj & objects & none\\
+%
+%		\noalign{\smallskip} \hline \noalign{\smallskip}
+%
+%		\multirow{4}{*}{\parbox[c]{0.8cm}{exp2}} 
+%			& \multirow{2}{*}{task2}  &  food & none & food\\
+%			& 	&  cult & none & culture\\
+%			\noalign{\smallskip} \cline{2-5} \noalign{\smallskip}
+%			& \multirow{2}{*}{frame2} & food & food & food\\
+%			& 	& cult & culture & food\\
+%
+%		\noalign{\smallskip} \hline  
+%	\end{tabular}
+%
+%	\caption{ 
+%		We use the treatment names shown to refer to specific sections of 
+%		the experimental data.
+%	}
+%	\label{table:treatments}
+%\end{table}
+
+Using a na\"ive Bayes classifier (\# in the 
 supplementary material we discuss the choice of classifier, the
 approach to measuring accuracy, and draw a comparison to the results obtained 
-if a support vector machine is used.) to distinguish workers from one 
-treatment (e.g \textit{task1:food}) from those of the conjugate treatment 
-(e.g. \textit{task1:obj}).  In \textit{task1} and \textit{task2}, intertask 
-effects profoundly biased worker outputs, by approximately 30 and 50\% 
-respectively, whereas we could not detect 
-a statistically significant bias induced by framing in \textit{frame1} and 
-\textit{frame2} (see Fig.~\ref{fig:theta}A).  The bias induced
-by framing was only appreciable in \textit{echo1}, reaching approximately 
-35\%.  
-We suspect that asking workers to reiterate the
-frame, as was done in \textit{echo1}, might be interpreted by workers as
-a direct signal that the frame should be acted upon.  In that sense, 
-\textit{echo1} is perhaps more indicative of the effects of an 
-\textit{instruction}.  These observations show that
-prior tasks profoundly influence the responses of workers, producing an
-effect that is stronger than framing, and on par with the combination of 
-framing and reiteration.
+if a support vector machine is used.), we found a bias of 30\% between 
+workers from the \textit{food} and \textit{objects} treatments, due to 
+intertask effects.
+As a point of comparison, we performed a similar experiment in which we 
+framed the purpose of the tasks.  Workers were either told that the tasks 
+were ``Funded by the laboratory for the visual perception of Food and 
+Ingredients'', or ``\ldots of Objects and Tools''.  We estimated the bias 
+induced by framing using a na\"ive Bayes classifier, but did not find a 
+statistically significant effect (see Fig.~\ref{fig:theta}).  This suggests
+that prior task exposure is a stronger priming modality than framing.
+
+We conducted variants of these experiments using different images, to see 
+whether this trend was robust.  In the experiment 
+\textit{intertask-food-culture},
+workers were either assigned to a \textit{food} or \textit{culture} treatment.
+As before, the initial tasks for the \textit{food} treatment contained images 
+depicting food (\#) (see Fig.~\ref{fig:task}D). 
+In the \textit{culture} treatment, 
+the initial tasks contained images depicting cultural scenes 
+(of dance, sport, or music) (see Fig.~\ref{fig:task}E).  The test tasks, which were identical for both
+treatments, included images depicting meals of identifiable cultural 
+origin 
+(see Fig.~\ref{fig:task}F).  Results for this experiment again showed a 
+strong bias (about 50\%; see Fig.~\ref{fig:theta}A) between the labels 
+provided by workers from the two 
+treatmens during test tasks.  Again, we compared intertask effects to framing,
+by performing an experiment (\textit{frame-food-culture}) using 
+the same test tasks as in \textit{intertask-food-culture}, in which we exposed
+workers to a statement framing the purpose of the tasks as the recognition 
+of either food or cultures.  
+For this framing experiment, we did not observe a statistically significant 
+difference between the labels attributed by the \textit{food} and 
+\textit{culture} treatments during test tasks (see Fig.~\ref{fig:theta}).
+
+It was only when we combined the use of framing, with an active 
+reiteration step, that bias reached a level comparable to that achieved 
+by intertask effects.  In the experiment \textit{echo-food-objects},
+after framing the purpose of the task around either the recognition of food
+or objects, we required the worker to echo back the purpose of the task
+using combo-box input.  In this case, workers exposed to different 
+``echoed framing'' showed a bias of about 35\% in the labels provided during 
+test tasks
+(see Fig.~\ref{fig:theta}A). However, it is possible that by requiring 
+workers to reiterate the language used in framing, we provided an implicit 
+but nonetheless strong signal that the worker must act on the framing 
+statement.  In this sense, \textit{echo-food-culture} may reflect the 
+influence of an instruction rather than framing.
 
@@
 		intertask effects. 
-		A) Bias in the responses to five test tasks,
+		(A) Bias in the responses to five test tasks,
 		measured between the pairs of treatments indicated on the abscissa.  
-		B) Bias between the treatments of \textit{task1}, 
+		(B) Bias between the treatments of \textit{task1}, 
 		measured for individual test tasks, and plotted as a function of 
@@
 
-To observe the dynamics of intertask effects, we trained a na\"ive Bayes
-classifier to distinguish workers in \textit{task1} based on responses to
-individual test tasks.  We permuted 
-the test tasks to eliminate effects arising from differences in the images 
-therein (more details are provided in the supplementary text). The first test 
-task shows the greatest bias, after which the effects drop somewhat, but 
-substantial bias persists through the fifth test task
-(see Fig. \ref{fig:theta}B).  Presumably, this decay profile reflects the
-fact that workers are also influenced by their exposure to the test tasks, 
-which begins to wash out the effects of initial tasks.
-
-\paragraph{Detailed influences on worker outputs.} 
 \begin{figure}
@@
 		to food(\#), when labeling images, for various treatment pairs.
-		A) Relative change in the number references to food. 
-		B) Relative change in the number of \textit{unique} 
+		(A) Relative change in the number references to food. 
+		(B) Relative change in the number of \textit{unique} 
 		references to food (lexical richness). 
-		C) Relative specialization of food references, based on the 
+		(C) Relative specialization of food references, based on the 
 		hypernym-hyponym relations (this calculation is shown in the 
@@
 
-Using the wordnet corpus, we analyzed exposure effects in finer detail.
-Wordnet encodes semantic information in various ways, including in the form 
-of synsets (groups of synonymous words), and hypernym-hyponym relations.
-Hypernyms are generalizations (``bread'' is a hypernym of ``pumpernickel''),
-while hyponyms are specialisations.
-
-First, we used wordnet to identify nouns depicting foods (\# We 
-operationalized food-references by taking all hyponyms of the synsets 
-\texttt{food.n.01} and \texttt{food.n.02}, with the addition of ethnic foods 
-learned by crawling a recipe website, as described in the supplementary text),
-to see whether 
-workers from the various food-exposed treatments (\textit{*:food}), 
-provided more references to food than their conjugate treatments, overall.
-The \textit{exp1:*:food} treatments
-did produce more food references, but, unexpectedly, 
-the number of food references in \textit{task2:food} was
-less than that in \textit{task2:cult} (see Fig.~\ref{fig:specificity}A). Also, the effects on the
-number of food references was, overall, somewhat smaller than one might 
-expect given the extent of bias observed in Fig.~\ref{fig:theta}A.  This means that task and frame exposures
-induce other effects which are more subtle than a bulk shift in the number 
-of references to the primed concept (food).
-
-Next, we looked at the change in the frequency of occurrence of particular 
-words.  Surprisingly, the word ``food'' was the \textit{most suppressed} word
-for workers in \textit{*:food} across all treatment pairs (Table S1 shows the
-top five most promoted and suppressed words for each treatment pair).
-Initially, this seems at odds with the fact that (at least in \textit{exp1})
-the \textit{*:food} treatments had more food references than their conjugate
-treatments.  But taken together, these facts indicate that \textit{*:food}
-workers are opting 
-to use more specialized food-references in place of ``food''.  
-Indeed, when we look at the total number of unique
-words (lexical richness) used to refer to food, we found that 
-a significantly richer lexicon was used by all \textit{*:food} treatments,
-except in \textit{frame2} (see Fig.~\ref{fig:specificity}B).  This effect 
-was especially pronounced in \textit{task1} and 
-\textit{task2}.
-
-Finally, we directly calculated the degree of specialization of food 
-references using wordnet's hypernym-hyponym relations.  To determine the 
-relative specialization between the words of two treatments, we computed 
-the proportion of words in the first treatment that were hyponyms of the 
-those in the 
-second, less those in the first that were hypernyms of those in the second 
-(this calculation is formalized in the supplementary text).  Except in the
-case of \textit{frame2}, workers in \textit{*:food} treatments used 
-substantially more specialized terms in reference to food than workers 
-from the conjugate treatments.
-
-\paragraph{Positive and negative priming.}
-Taken together, the results of the experiments presented here can be 
+To better understand the nature of the 
+intertask effects, we investigated the vocabulary
+that workers used to label test tasks. A natural expectation is that, within
+a given experiment, the food-primed workers would use more food-related words 
+than their non-food-primed counterparts.  However, this was not generally 
+the case. In the \textit{intertask-food-culture} experiment, food-primed
+workers actually used significantly \textit{fewer} food-related words 
+during test tasks
+(\# food related words were identified using the wordnet corpus, augmented
+with additional words obtained by crawling a recipe website (see supplementary
+information for details)) (see Fig.~\ref{fig:specificity}).  This finding
+rules out a simplistic conception of how intertask effects guide the worker's
+attention.  It seems that when workers encounter content in 
+prior tasks, the probability that they will refer to similar content in 
+test tasks changes significantly, although it does not necessarily increase.
+
+To clarify this observation, we investigated workers' lexical richness in 
+reference to food, that is, the number of \textit{unique} food-related words
+used.
+Both \textit{intertask} experiments showed that food-exposed workers had 
+greater lexical richness, in reference to food, than their non-food-primed 
+counterparts (as much as 20\% more; see Fig.~\ref{fig:specificity}).  This
+held in the case of \textit{intertask-food-culture}, even though, in that 
+experiment, food-primed workers referred to food less often overall.  
+This enrichment of the food-related lexicon 
+was also observed in the \textit{priming-food-objects}, and 
+\textit{echo-food-objects} experiments, but to a lesser extent.
+
+This suggests that priming, by prior task exposure as well as framing,
+might have led workers to use more refined or specialized words to refer to
+the concept present in the prime.
+To test this directly, we used the wordnet corpus to operationalize the 
+notion of word specialization.
+Wordnet provides a set of hypernym-hyponym relations between \# English 
+nouns.  
+Hypernyms are generalizations (for example, ``bread'' is a hypernym for 
+``pumpernickel''), while hyponyms are specializations.
+To assess the relative specialization of words from two different treatments,
+we compared all pairs of words from one treatment to the other. 
+We tallied the cases where a word from one treatment was more specialized
+than one from the other, as well as the cases with roles reversed.  
+The difference of these tallies, as a percentage of their total, gave the
+relative specialization of one treatments vocabulary over the other
+(\#) (see Fig.~\ref{fig:specificity}).  
+Using this approach, we compared the specialization of food-related words 
+for the treatments of all experiments.
+
+In all experiments except \textit{frame-food-culture}, food-primed workers 
+used significantly more specialized words than their non-food-primed 
+counterparts (about 15\% more; see Fig.~\ref{fig:specificity}C).
+It is interesting that such substantial increases in both the lexical 
+richness and specialization of food-related words among food-primed workers
+held for \textit{intertask-food-culture}, where, again, we observed fewer 
+references to food by food-primed workers overall. These observations point 
+to countervailing factors: one tending to activate the more specialized and 
+less common food-related words (yielding greater lexical richness and 
+specialization), and the other tending to suppress certain, presumably more 
+common or generic words (yielding fewer food-related words in total).
+
+This hypothesis is corroborated when we look at those words whose 
+frequencies changed the most from one treatment to another (see Table S1).  
+The word ``food'', which is the most generic possible food-related word, was 
+always \textit{suppressed} among food-primed workers.  In fact, 
+for all experiments, ``food'' was the \textit{most suppressed} word.
+
+Taken together, our results can be 
 explained through a combination of positive and negative priming.
@@
 is often observed as an increase in the speed or accuracy of a response, or
-the ability to recognize objects in a briefer, quieter, or noisier signal (\#).
+the ability to recognize features of a briefer, quieter, or noisier stimulus 
+(\#).
 Negative priming occurs when, after being repeatedly exposed to a stimulus 
-that is perceived to be non-salient, the person begins to ignore that 
+considered to be non-salient, a person begins to ignore that 
 stimulus (\#).
@@
 Workers exposed to images containing food will be (positively) primed, 
-as memories, concepts, and vocabulary related to food are activated.  
-However, we argue that as the worker labels successive images containing food,
-the basic 
+activating memories, concepts, and vocabulary related to food.  
+However, as the worker labels successive images containing food, the basic 
 fact that an image contains food will not appear to be salient, since it 
@@
 generic references to that fact, such as the label ``food'', 
-are suppressed, as by negative priming, while more specialized
-references are activated.  Whether workers in \textit{*:food} treatments
-produce an excess of food references overall depends in part on the balance 
-of these factors.  The reduction in food references from workers in 
-\textit{task2:food} relative to \textit{task2:cult}, seen in in 
-Fig.~\ref{fig:specificity}A, may also be
-related to the novelty that workers in 
-\textit{task2:cult} experience when they first encounter food in the test 
-tasks.
+will be suppressed, while more specialized references will be elicited.  
+Meanwhile, the number of references to food overall might increase or 
+decrease, depending on the balance of these factors.
 
 More generally, we are suggesting that, even though workers are not 
-instructed to compare the content of tasks in any way, prior tasks form a 
-context relative to which workers judge salience.  Thus, a worker's focus 
+instructed to compare tasks in any way, prior tasks form a 
+context relative to which workers judge salience.  Thus, due to a combination 
+of negative and positive priming, a worker's focus 
 in repeated tasks tends to be directed away from generic, shared features, 
@@
 
-\paragraph{Recommendations and future work.} 
-Based on our observations throughout, we submit the following 
-recommendations for the consideration of people designing 
-any microtask, citizen science, or crowdsourcing initiative:
-\begin{enumerate}
-	\item{
-		Require active feedback to emphasize important details about the 
-		tasks, as we did in \textit{echo1}.  Similarly, use training tasks 
-		rather than only examples.
-	}
-	\item{
-		Although ``clean'' examples may be useful to provide clarity,
-		use training tasks that contain the same kinds of noise or otherwise
-		distracting features as are expected in the real tasks.
-		This exposure will negatively prime the worker against non-salient 
-		features.
-	}
-	\item{
-		\textit{Validation tasks}, for which the correct output is known,
-		are often used as a quality control measure.
-		Treat these as \textit{calibration tasks}, and use them to regulate
-		the focus of the worker.
-		Feedback, for both correct and incorrect responses may further 
-		reinforce the desired competency. \label{item:valid}
-	}
-	\item{
-		A special case of item~\ref{item:valid} applies when workers are 
-		required to detect rare occurrences.
-		For example, in the detection of pre-ictal (pre-seizure) EEG traces, 
-		most traces are negative (\#).  In the absence of positive 
-		examples, the target concept may degrade or drift.
-		Draw calibration tasks from the underrepresented class,
-		and provide feedback, to help sustain the worker's target concept.
-	}
-	\item{
-		For more precise classifications, it may help to begin with
-		an initial coarse classification.  For example, in detecting 
-		inappropriate comments, provide the choices   
-		\texttt{okay}, \texttt{inappropriate}, and \texttt{borderline},
-		and incentivise inter-worker agreement.  Next, have workers 
-		code the \texttt{borderline} cases, but without providing the
-		\texttt{borderline} code.  Coding this more homogeneous
-		set will help workers to calibrate to the finer features that are 
-		salient in distinguishing borderline cases.
-	}
-\end{enumerate}
-
-While these recommendations are informed by the observations we have made 
-here, we hope to see them tested directly in future work.
-
-\paragraph{Conclusion.}
-We have shown that intertask effects are stronger than framing effects, and
-as strong as the effects induced when framing is combined with reiteration.
-Intertask and framing effects act on workers' vocabulary in subtle ways.  
-Both increase the richness of workers' vocabulary in reference a target
-concept, with a more pronounced effect induced by task exposure.
-Both exposures also increase the specialization of workers' vocabulary in 
-reference to the target concept.  Framing, and other aspects of task design 
-have received substantial methodological scrutiny; our results show that 
-intertask effects, which were overlooked until now, merit similar 
-attention.  Although we found that intertask effects can be a major 
-source of bias, they might be used to tune workers' attention and 
-specificity relative to
-a target concept.  Microtask work, citizen science, and other crowdsourcing
-initiatives, as well tasks requiring expert opinions, often rely on repetitive
-human judgments.  Such applications all stand to benefit from the 
-findings and suggestions presented here.
+Prior to this study, little thought appears to have been given to the 
+ordering and bundling of tasks.  But our findings show that these are 
+powerful design factors.  A natural response to our findings 
+might be simply to randomize task ordering, a practice that is commonly 
+observed.  But the sheer extent of bias that we observed leads us to question 
+whether that is the best approach, since this would tend to raise 
+the ``noise floor'' of the study.
+
+Furthermore, our findings suggest that, through careful task engineering,
+it might be able to achieve much more.  The boost that we observed to the 
+specialization and richness of workers' responses motivates further 
+investigation to acquire a deeper understanding of intertask effects.  
+We hope that future work will yield techniques to leverage intertask effects, 
+enabling one to tune the focus, diversity, and specialization of worker 
+responses.
+
+A consistent goal in human computation is the achievement of expert-level
+judgments from non-expert workers.  This has been achieved in some
+applications (\#). The distinction between experts and novices can be 
+attributed in part to the knowledge of facts and 
+heuristics. But to a large degree, this distinction lies in the ability of 
+experts to direct their focus towards salient features, while filtering out 
+non-salient ones \cite{kellman2009perceptual}.  Using prior task exposure to 
+guide focus and salience attribution might well enable expert-level 
+judgment in a wider variety of crowdsourced applications.
+
+Here we have shown that a large bias can be introduced into microtask 
+responses, simply from the performance of earlier tasks. 
+These effects are much stronger than framing, and are only comparable when
+framing is combined with a requirement that the worker actively echo
+the framing language.  While our findings raise serious concerns about the 
+current state of microtask design, it also reveals opportunities for more 
+refined control over worker focus and acuity.  Any application that relies
+on the repetitive use of human judgment is likely subject to the phenomena
+we described here.  It remains to be determined whether intertask effects 
+can be leveraged to increase the performance and reliability of human 
+computation.
 
@@
 consumable.  So, ``orange'' is food, but ``salty'' is not.  Although ``salty''
-would usually refer to something edible, it is not itself an edible thing.
+would usually qualify something edible, it is not itself an edible thing.
 On the other hand, ``salt'' would be considered a reference to food under 

### 2014-12-17 docs/publications/2014.09_SCIENCE/man.tex
fix a couple typos

@@
 further processing.
-We denote this dowstream decision by $\mathcal{D}$.  Since $\mathcal{D}$
+We denote this downstream decision by $\mathcal{D}$.  Since $\mathcal{D}$
 takes a microtask response as input, biases in the microtask response will 
@@
 lower bound on the extent of bias. This approach can be used to bound the 
-bias induced by any purturbation, including both intertask effects and 
+bias induced by any perturbation, including both intertask effects and 
 framing.  Bias ranges from 0 (meaning there are no intertask effects), to 1 
@@
 provided by workers from the two 
-treatmens during test tasks.  Again, we compared intertask effects to framing,
+treatments during test tasks.  Again, we compared intertask effects to 
+framing,
 by performing an experiment (\textit{frame-food-culture}) using 
@@
 	The variance in the specificity measurements was calculated using a 
-	bootstrapping proceedure.  For two given treatments $A$ and $B$, 
+	bootstrapping procedure.  For two given treatments $A$ and $B$, 
 	119 workers were sampled from each with replacement, giving the bootstrap

### 2014-12-17 docs/publications/2014.09_SCIENCE/man.tex
another quick passt

@@
 Given the increasing prevalence of microtask-based research methods, there
-is a desire to understand the factors affecting the reliability of HPU
+is a desire to understand factors affecting the reliability of HPU
 outputs.  Researchers have investigated task-design parameters such as the 
@@
 in general lead to biases in the output of $\mathcal{D}$.  
-We can make use of this fact, 
+We can make use of this fact, to estimate the bias, 
 by placing a machine learning algorithm (a classifier), in the role of 
@@
 (i.e. the initial tasks she was given). 
-Intuitively, the classifier's ability to infer the worker's treatment
-depends on how strongly the exposure to prior tasks influences responses to 
+Intuitively, the classifier's ability to infer worker treatments
+depends on how strongly prior tasks affect responses to 
 subsequent ones.  Formally, the bias, $\theta$, is bounded 
@@
 framing.  Bias ranges from 0 (meaning there are no intertask effects), to 1 
-(or 100\%) (meaning that changing initial tasks leads to a completely 
+(or 100\%) (meaning that the change of initial tasks induced a completely 
 different set of responses to test tasks).
@@
 intertask effects.
+
 As a point of comparison, we performed a similar experiment in which we 
@@
 were ``Funded by the laboratory for the visual perception of Food and 
-Ingredients'', or ``\ldots of Objects and Tools''.  We estimated the bias 
-induced by framing using a na\"ive Bayes classifier, but did not find a 
-statistically significant effect (see Fig.~\ref{fig:theta}).  This suggests
+Ingredients'', or ``\ldots of Objects and Tools''.  We did not observe a 
+statistically significant framing-induced bias, using a na\"ive Bayes 
+classifier (see Fig.~\ref{fig:theta}).  This suggests
 that prior task exposure is a stronger priming modality than framing.
@@
 or objects, we required the worker to echo back the purpose of the task
-using combo-box input.  In this case, workers exposed to different 
+using a combo-box input.  In this case, workers exposed to different 
 ``echoed framing'' showed a bias of about 35\% in the labels provided during 
@@
 (see Fig.~\ref{fig:theta}A). However, it is possible that by requiring 
-workers to reiterate the language used in framing, we provided an implicit 
-but nonetheless strong signal that the worker must act on the framing 
-statement.  In this sense, \textit{echo-food-culture} may reflect the 
-influence of an instruction rather than framing.
+workers to echo the language used in framing, we provided an implicit 
+but nonetheless strong signal of our intent that workers act on the 
+framing statement.  In this sense, \textit{echo-food-culture} may reflect the 
+influence of an \textit{instruction} rather than framing.
 
@@
 
-To better understand the nature of the 
+To better understand the nature of 
 intertask effects, we investigated the vocabulary
@@
 prior tasks, the probability that they will refer to similar content in 
-test tasks changes significantly, although it does not necessarily increase.
+subsequent tasks changes significantly, although it does not necessarily 
+increase.
 
@@
 
-This suggests that priming, by prior task exposure as well as framing,
-might have led workers to use more refined or specialized words to refer to
-the concept present in the prime.
+This lexical enrichment suggests that priming, whether by prior task 
+exposure or framing, leads workers to use more refined 
+or specialized words, in reference to concepts present in the prime.
 To test this directly, we used the wordnet corpus to operationalize the 
@@
 we compared all pairs of words from one treatment to the other. 
-We tallied the cases where a word from one treatment was more specialized
-than one from the other, as well as the cases with roles reversed.  
-The difference of these tallies, as a percentage of their total, gave the
-relative specialization of one treatments vocabulary over the other
-(\#) (see Fig.~\ref{fig:specificity}).  
+We tallied the cases where one treatment's word was more specialized
+than the other, as well as the cases wher roles were reversed.  
+The difference of these tallies, as a percentage of their total, served as 
+the relative specialization of one treatment's vocabulary relative to the 
+other (\#) (see Fig.~\ref{fig:specificity}).  
 Using this approach, we compared the specialization of food-related words 
@@
 It is interesting that such substantial increases in both the lexical 
-richness and specialization of food-related words among food-primed workers
+richness and specialization of food-related words 
 held for \textit{intertask-food-culture}, where, again, we observed fewer 
 references to food by food-primed workers overall. These observations point 
-to countervailing factors: one tending to activate the more specialized and 
-less common food-related words (yielding greater lexical richness and 
-specialization), and the other tending to suppress certain, presumably more 
-common or generic words (yielding fewer food-related words in total).
+to countervailing factors: one factor tending to activate the more 
+specialized and less common food-related words 
+(yielding greater lexical richness and specialization), and the other tending 
+to suppress certain, presumably more common or generic words 
+(yielding fewer food-related words in total).
 
@@
 Prior to this study, little thought appears to have been given to the 
-ordering and bundling of tasks.  But our findings show that these are 
+ordering and bundling of microtasks.  But our findings show that these are 
 powerful design factors.  A natural response to our findings 
@@
 Furthermore, our findings suggest that, through careful task engineering,
-it might be able to achieve much more.  The boost that we observed to the 
-specialization and richness of workers' responses motivates further 
+it might be possible to achieve much more.  The boost that we observed to the 
+richness and specialization of workers' responses motivates further 
 investigation to acquire a deeper understanding of intertask effects.  
 We hope that future work will yield techniques to leverage intertask effects, 
-enabling one to tune the focus, diversity, and specialization of worker 
+enabling one to tune the focus, diversity, and specificity of worker 
 responses.
@@
 A consistent goal in human computation is the achievement of expert-level
-judgments from non-expert workers.  This has been achieved in some
+judgments from non-expert workers (\#).  This has been achieved in some
 applications (\#). The distinction between experts and novices can be 
-attributed in part to the knowledge of facts and 
-heuristics. But to a large degree, this distinction lies in the ability of 
-experts to direct their focus towards salient features, while filtering out 
+attributed in part to the posession of specialized knowledge and heuristics. 
+But to a large degree, this distinction lies in the ability of 
+experts to direct their focus toward salient features, while filtering out 
 non-salient ones \cite{kellman2009perceptual}.  Using prior task exposure to 
-guide focus and salience attribution might well enable expert-level 
+guide focus and salience attribution might enable expert-level 
 judgment in a wider variety of crowdsourced applications.
@@
 responses, simply from the performance of earlier tasks. 
-These effects are much stronger than framing, and are only comparable when
-framing is combined with a requirement that the worker actively echo
-the framing language.  While our findings raise serious concerns about the 
-current state of microtask design, it also reveals opportunities for more 
+These effects are much stronger than framing.  
+While our findings raise serious concerns about the 
+current state of microtask design, they also reveal potential opportunities 
+for more 
 refined control over worker focus and acuity.  Any application that relies
 on the repetitive use of human judgment is likely subject to the phenomena
-we described here.  It remains to be determined whether intertask effects 
-can be leveraged to increase the performance and reliability of human 
+we described here.  It remains to be determined by future work whether 
+intertask effects can be leveraged for more performant and reliable human 
 computation.

### 2015-01-07 docs/publications/2014.09_SCIENCE/man.tex
add chi2 analysis, work on manuscript

@@
 
-Faced with the ever-growing scale and complexity of data, researchers and
-industry are increasingly relying on \textit{human computation} as a means
-to extract useful knowledge.  Microtask
-platforms, like Amazon Mechanical Turk, act like a human compute server,
+Faced with the ever-growing scale and complexity of data, academic and 
+industrial researchers are increasingly relying on \textit{human computation} 
+as a means to extract useful knowledge.  Microtask
+platforms, like Amazon Mechanical Turk, act like a human compute cluster,
 making it possible to access human cognition quickly and inexpensively. 
-This has lead to broad adoption across a spectrum of disciplines
-in the social sciences and computer science, as well as in research into 
-medical imaging technologies and other applications where expert opinion 
-would normally be sought.  Here we show that an inherent
-feature of microtask platforms and most crowdsourcing settings---the 
-repetition of similar tasks---acts as a strong, but as yet unexplored source 
-of bias.  These \textit{intertask effects} rival the
-severity of overtly framing a task's purpose.  
-Using image-labeling as a canonical microtask, we show that prior 
-tasks influence the content that workers focus on, and the richness and
-specialization of their vocabulary.    
+This has lead to their broad adoption by social and computer scientists.  
+Human computation is being used in applications
+where expert opinion would normally be sought, such as in reviewing 
+medical images.
+Here we show that the repetition of similar tasks, which is an inherent
+feature of microtask and crowdsourcing platforms, acts as a strong
+and largely unexplored source of bias.  The effects of previous tasks on
+later ones---\textit{intertask effects}---are more severe than the effects 
+of framing, such as by disclosing a task's purpose.  
+Using image-labeling, the canonical microtask, we show that prior 
+tasks influence the content that workers chose to focus on, as well as the 
+richness and specialization of their vocabulary.    
 While intertask effects can be a source of systematic bias, our
 results suggest that, when properly controlled, they might be leveraged
-to hone worker focus and specificity, and could play a key role in designing 
-tasks that elicit expert-level judgments.
+to hone worker focus and specificity, and could play a key role in engineering
+tasks that elicit reproducible, expert-level judgments.
 \end{sciabstract}
@@
 Davis \textit{et al} invoked the \textit{human processing unit}, or HPU \cite{5543192}.
-Meanwhile, researchers have sought to define a basic HPU instruction set, and
+Researchers have sought to define a basic HPU instruction set, and
 libraries for HPU programming are under active development
@@
 outputs.  Researchers have investigated task-design parameters such as the 
-level of pay \cite{kazai2013analysis}, the training \cite{le2010ensuring} and 
-pre-screening \cite{paolacci2010running} of workers, and user-interface 
-design factors \cite{Finnerty2013}.  
-Researchers have also investigated \textit{framing} effects, 
-such as the effects of describing the workflow context 
+level of pay \cite{kazai2013analysis}, the training and pre-screening of 
+workers \cite{le2010ensuring,paolacci2010running}, and user-interface 
+design \cite{Finnerty2013}.  
+Researchers have also investigated the effects of \textit{framing}, 
+by altering the description of the workflow context 
 \cite{Kinnaird2012281}, the purpose of tasks 
-\cite{chandler2013breaking}, or altering the problem description
-\cite{thibodeau2013natural}.  Results in psychology show that people are 
-susceptible to various kinds of priming 
-\cite{BJOP1796,No2007,beller1971priming}, and, in particular, 
+\cite{chandler2013breaking}, and the problem description
+\cite{thibodeau2013natural}.
+
+Microtasks are typically distributed to workers in bundles.  For example, a 
+worker might be assigned a set of ten images, and asked to provide 
+descriptive words (or \textit{labels}) for each.  
+On MTurk, these bundles are called Human Intelligence Tasks (HITs).
+But for the sake of clarity, we will use ``task'' to mean the smallest 
+repeatable unit of work, which, in our study, consists of labeling a single
+image.
+
+Results in psychology show that people are susceptible to various kinds of 
+priming \cite{BJOP1796,No2007,beller1971priming}, including 
 task-repetition effects \cite{Gass1999549,sohn2001task}.  
-Yet to our knowledge, no study has investigated the practical ramifications 
-of intertask effects on human computation. The experiments we 
-present here show that, unlike CPUs and GPUs, HPUs are subject to 
+Yet to our knowledge, no study has investigated the bias that might
+result from the fact that microtask workers typically perform many tasks in 
+succession.  The experiments we present here show that a worker's response 
+to a task depends strongly on the tasks she had performed beforehand.
+In other words, unlike CPUs and GPUs, HPUs are subject to 
 \textit{hysteresis}, meaning that their outputs depend on the 
 \textit{history} of their inputs.
+We call the effects that prior tasks induce on later ones 
+\textit{intertask effects}.
 
@@
 in the long term because of their role in computer vision research 
-\td{find another application} \cite{5543192}.  In microtask platforms, it is typical for work to be divided 
-into bundles; on MTurk, these bundles are called Human Intelligence Tasks 
-(HITs). Because of this bundling pattern, even if workers perform only one 
-HIT, the opportunity for intertask effects arises.  For clarity, 
-we will use ``task'' to mean the smallest repeatable unit of work, which, 
-in our study, consists of labeling a single image.
-
-In our first experiment, which we will refer to as 
-\textit{intertask-food-objects}, workers were either assigned to the 
+\td{find another application} \cite{5543192}.  In our first experiment, 
+which we will refer to as 
+\textit{intertask-food-objects}, workers were assigned to either a
 \textit{food} or \textit{objects} treatment.  Workers in these treatments
-performed a set of five \textit{initial tasks}, which involved labeling
-images depicting either food or (non-food) objects, depending on the worker's 
+performed a set of five \textit{initial tasks}, which each involved 
+providing five descriptive labels for an image depicting 
+either food or (non-food) objects, depending on the worker's 
 treatment (see Fig.~\ref{fig:task}A and B).  Following the initial 
@@
 both treatments.  The test tasks contained images depicting a 
-mixture of food and other objects (see Fig.~\ref{fig:task}C).  Five initial 
+mixture of food and other objects (see Fig.~\ref{fig:task}C), and workers
+were again asked to supply five labels.  Five initial 
 tasks, together with the test tasks, comprised one HIT 
@@
 
-A $\chi^2$ test (\#) shows that the frequency of word usage by
+A $\chi^2$ test shows that the frequency of word usage by
 workers in the \textit{food} and \textit{objects} treatments differed
-significantly during test tasks, even though the test tasks were identical 
-for the treatments.  This shows that earlier tasks have a 
+significantly during test tasks ($p = 6.0 \times 10^{-14}$), even though the test tasks were identical 
+in both treatments (\# see supplementary text for tabulated statistics).  This shows that earlier tasks have a 
 significant effect on later ones, and raises concerns about the 
@@
 understand the nature and severity of the bias induced by prior task 
-exposure.  To formalize a notion of the extent of bias, we must first 
-acknowledge that workers' responses to microtasks
-carry an element of stochasticity: two workers will not, in general, provide
-the same response to a given task.  Because worker responses are stochastic,
-we take the extent of bias, $\theta$, to be the total shift in probability 
-mass, for giving certain responses (i.e. certain words),
-caused by a perturbation like intertask effects (\# in other words, the 
-bias is the L1-distance between the probability distributions for responses
-under one treatment, to that for responses under another.)
-
-It is difficult to measure the change in a probability distribution based on
-samples alone (\#), so we reformulate the problem slightly. Consider that,  
-no matter the ultimate purpose of a microtask study, a microtask response
-is used in \textit{some kind} of subsequent decision or 
-further processing.
-We denote this downstream decision by $\mathcal{D}$.  Since $\mathcal{D}$
-takes a microtask response as input, biases in the microtask response will 
-in general lead to biases in the output of $\mathcal{D}$.  
-We can make use of this fact, to estimate the bias, 
-by placing a machine learning algorithm (a classifier), in the role of 
-$\mathcal{D}$.  This classifier takes as input a worker's responses to test 
-tasks, from which it learns to infer the worker's treatment 
-(i.e. the initial tasks she was given). 
-Intuitively, the classifier's ability to infer worker treatments
-depends on how strongly prior tasks affect responses to 
-subsequent ones.  Formally, the bias, $\theta$, is bounded 
-by the accuracy of the classifier, $\eta$ (\#):
+exposures.  
+We define the extent of bias, $\theta$, induced by alternative exposures, to 
+be the resulting change in the probability with which workers provide given 
+responses (formally the totatal variation distance):
+\begin{equation}
+	\theta = \frac{1}{2}\sum_{x \in X} \left| p_1(x) - p_2(x) \right|,
+\end{equation}
+where $p_i(x)$ is the probability that a worker subjected to treatment $i$
+provides response $x$, from the set of possible responses $X$.
+The problem of determining $\theta$ from finite samples of responses is 
+difficult, which leads us to reformulate it as a classification problem: 
+given a worker's 
+response, can a machine reliably infer what her priming exposure had been?  
+Intuitively, the greater the effect that priming exposures have on workers' 
+responses, the more accurate the classifier can be.  Formally, as we show
+in the supplementary text, the performance of such a classifier, $\eta$,
+yields a lower bound on the true bias:
 \begin{equation}
@@
 \end{equation}
-Thus, measuring the performance of the classifier allows us to establish a
+Thus, measuring the performance of a classifier allows us to establish a
 lower bound on the extent of bias. This approach can be used to bound the 
 bias induced by any perturbation, including both intertask effects and 
-framing.  Bias ranges from 0 (meaning there are no intertask effects), to 1 
-(or 100\%) (meaning that the change of initial tasks induced a completely 
-different set of responses to test tasks).
+framing.  As we have defined it, bias ranges from 0 (meaning the exposures 
+do not affect the probabilities of respnoses), to 1 
+(or 100\%) (meaning that under different exposures, workers provide completely
+different sets of responses).
 
@@
 approach to measuring accuracy, and draw a comparison to the results obtained 
-if a support vector machine is used.), we found a bias of 30\% between 
-workers from the \textit{food} and \textit{objects} treatments, due to 
-intertask effects.
-
-As a point of comparison, we performed a similar experiment in which we 
-framed the purpose of the tasks.  Workers were either told that the tasks 
-were ``Funded by the laboratory for the visual perception of Food and 
-Ingredients'', or ``\ldots of Objects and Tools''.  We did not observe a 
+if a support vector machine is used.), we found that intertask effects 
+lead to a 30\% bias between workers from the \textit{food} and 
+\textit{objects} treatments.
+
+As mentioned, the effects of framing on workers' responses to microtasks has 
+been studied in various ways 
+\cite{Kinnaird2012281,chandler2013breaking,thibodeau2013natural}.
+Therefore, as a point of comparison, we performed a similar experiment 
+in which we framed the purpose of the tasks.  Workers were either told that 
+the tasks were ``Funded by the laboratory for the visual perception of Food 
+and Ingredients'', or ``\ldots of Objects and Tools''.  We did not observe a 
 statistically significant framing-induced bias, using a na\"ive Bayes 
@@
 that prior task exposure is a stronger priming modality than framing.
+\td{I need to talk about the $\chi^2$ result here.}
 
@@
 (see Fig.~\ref{fig:task}F).  Results for this experiment again showed a 
-strong bias (about 50\%; see Fig.~\ref{fig:theta}A) between the labels 
-provided by workers from the two 
-treatments during test tasks.  Again, we compared intertask effects to 
-framing,
-by performing an experiment (\textit{frame-food-culture}) using 
+strong bias as a result of intertask effects (about 50\%) 
+(see Fig.~\ref{fig:theta}A).  Again, we compared intertask effects to 
+framing, by performing an experiment (\textit{frame-food-culture}) using 
 the same test tasks as in \textit{intertask-food-culture}, in which we exposed
@@
 		(A) Bias in the responses to five test tasks,
-		measured between the pairs of treatments indicated on the abscissa.  
+		measured between the pairs of treatments indicated on the $x$-axis.  
 		(B) Bias between the treatments of \textit{task1}, 
@@
 information for details)) (see Fig.~\ref{fig:specificity}).  This finding
-rules out a simplistic conception of how intertask effects guide the worker's
-attention.  It seems that when workers encounter content in 
-prior tasks, the probability that they will refer to similar content in 
-subsequent tasks changes significantly, although it does not necessarily 
-increase.
-
-To clarify this observation, we investigated workers' lexical richness in 
+rules out a simple mechanism in which worker's attention is drawn toward
+content that had been found in earlier tasks.  Seeing content in prior tasks 
+seems to affect the probability that a worker refers to that content it in 
+subsequent tasks, but does not necessarily increase it.
+
+To deepen our understanding, we investigated workers' lexical richness in 
 reference to food, that is, the number of \textit{unique} food-related words
@@
 \subsection*{S3: Additional results not shown in the main text}
-		the top 5 most suppressed and most activated terms between treatment
-		pairs.
+\paragraph{Testing intertask and framing effects using 
+	Pearson's $\chi^2$ test of homogeneity.
+}
+To test whether intertask and framing effects induced statistically 
+significant changes in word frequencies, we assembled a contingency table
+for each experiment, containing the frequencies of words in each treatment
+for a given experiment.  Any words that appeared less than 10 times for
+an experiment (i.e. appearing less than 5 averaged over each treatment)
+were lumped together into a separate `OTHER' category, to ensure validity
+of the test.  The degrees of freedom, test statistic, and $p$-values were
+then calculated according to Pearson's $\chi^2$ test, using 
+Yate's correction.  Results are tabulated in Table~\ref{table:chi2}.
+All experiments showed significant changes in word-frequencies in response
+to the task or framing exposures, at $\alpha=0.05$, leading us to 
+reject the null hypothesis that the priming exposures had no effect.
+Note, however, that while the other tests showed very high significance, 
+\textit{frame-food-culture} was marginally significant.  This is consistent 
+with our finding weak effects for \textit{frame-food-culture}, throughout our 
+results.
+
+The use of Pearson's $\chi^2$ test has been criticized in linguistic 
+applications, due to the finding that many corpuses are not themselves
+homogeneous \cite{kilgarriff1996comparing}.  
+This results from the fact that corpuses are made of many
+distinct texts, together with the fact that words tend to come in bursts.
+When a rare word is encountered in a given text, it is much more likely
+to be encountered again in the same text, which making the word's frequency
+within the text far from the average.  As a result,
+if a corpus is randomly split, putting half of the texts in one set, 
+and half in another, there can be a significant non-homogeneity between the 
+two halves, when tested using Pearson's $\chi^2$ test.  Thus, finding two
+corpuses to be different might simply be an artifact of the corpus' own
+inhomogeneity.
+
+We don't expect this to be a concern in our case, because the ``texts'' are 
+individual responses from workers, which will not, in general, be subject to 
+the burstiness phenomenon.  But to test this, we randomly divided the workers 
+from each experimental treatment into two sets, and tested the homogeneity 
+between these sets.  Results are tabulated in Table~\ref{table:chi2_within}, 
+and show that treatments 
+\textit{are} homogeneous.  Thus, the lack of homogeneity \textit{between} 
+the treatments of given experiments can be attributed to the framing / 
+intertask effects.
+
+\begin{table}
+\centering
+\begin{tabular}{c c c c}
+\toprule
+Experiment & Degrees of freedom & $\chi^2$ & $p$-value\\
+\toprule
+\textit{intertask-food-objects} & 117 & 268.7 & $6.0 \times 10^{-14}$\\
+\textit{frame-food-objects} & 116 & 167.8 & $1.2 \times 10^{-3}$\\
+\textit{echo-food-objects} & 126 & 381.3 & $1.7 \times 10^{-27}$\\
+\textit{intertask-food-culture} & 120 & 447.5 & $2.8 \times 10^{-39}$\\
+\textit{frame-food-culture} & 119 & 127.2 & $0.29$\\
+\bottomrule
+\end{tabular}
+\caption{
+	Results for Pearson's $\chi^2$ test of homogeneity of the word-frequencies
+	between treatments from each experiment.  This shows that the treatments
+	significantly affected word usage, 
+	except in the case of \textit{frame-food-culture}.
+}
+\label{table:chi2}
+\end{table}
+
+\begin{table}
+\centering
+\begin{tabular}{c c c c c}
+\toprule
+Experiment & Treatment & Degrees of freedom & $\chi^2$ & $p$-value\\
+\toprule
+\noalign{\smallskip}
+\multirow{2}{*}{\textit{intertask-food-objects}} & \textit{food} & 65 & 39.0 & $1.0$\\
+ & \textit{objects} & 65 & 53.2 & $0.85$\\
+\noalign{\smallskip}
+\multirow{2}{*}{\textit{frame-food-objects}} & \textit{food} & 67 & 41.3 & $0.99$\\
+ & \textit{objects} & 62 & 66.9 & $0.31$\\
+\noalign{\smallskip}
+\multirow{2}{*}{\textit{echo-food-objects}} & \textit{food} & 66 & 40.9 & $0.99$\\
+ & \textit{objects} & 66 & 35.6 & $1.0$\\
+\noalign{\smallskip}
+\multirow{2}{*}{\textit{intertask-food-culture}} & \textit{food} & 62 & 65.9 & $0.34$\\
+ & \textit{culture} & 68 & 57.2 & $0.82$\\
+\noalign{\smallskip}
+\multirow{2}{*}{\textit{frame-food-culture}} & \textit{food} & 57 & 49.6 & $0.75$\\
+ & \textit{culture} & 64 & 55.1 & $0.78$\\
+\noalign{\smallskip}
+\bottomrule
+\end{tabular}
+\caption{
+	Results for Pearson's $\chi^2$ test of homogeneity of the word-frequencies
+	within treatments, which were randomly partitioned for the test.  This
+	shows that word-usage within treatments is homogeneous.
+}
+\label{table:chi2_within}
+\end{table}
+
+\paragraph{Most suppressed / activated terms.}
+The words whose frequencies differed most between the treatments of given 
+experiments are shown in Table~\ref{table:top-words}.  Note that 
+the word that was most suppressed in food-exposed treatments was always 
+``food''.
 
@@
 	\end{tabular}
-	\caption{blah}
+	\caption{
+		Top 5 words, used to label the first test image, whose usage frequency
+		increased or decreased the most between treatments of given 
+		experiments.  Positive values indicate that the food-exposed treatment
+		used the word with higher frequency.  Word frequencies for 
+		\textit{intertask-food-objects} are aggregated accross 5 
+		permutations, and hence tend to show larger absolute differences.
+	}
+	\label{table:top-words}
 \end{table}
@@
 	performed a series of preprocessing steps.  
-	\td{does this reflect the actual order in which the steps were done?}
-	First, words wore lematized 
-	using the
-	\td{whatzit} lemmatizer.  This lemmatizer is very mild, tending only to 
-	change plural words to their singular form.  Common
-	words such as ``the'', ``to'', or ``with'', were found using the
-	the \td{whatzit} stop-word list and removed.  Then, misspelled words were
-	automatically corrected using a spelling correction algorithm described 
-	below.  Finally, labels that contained
+	Labels that contained
 	multiple words (separated by spaces or punctuation) were split, with
@@
 	features in subsequent analysis.
+	Misspelled words were automatically corrected using a spelling 
+	correction algorithm described below.  
+	Next, words were lematized using the
+	wordnet lemmatizer \cite{miller1995wordnet,felbaum1998wordnet}.  
+	Common words such as ``the'', ``to'', or ``with'', were found using the
+	the NLTK's English stop-word list and removed \cite{loper2002nltk}.
 
@@
 	automated scripts.  A total of 2642 recipe listings and 15621 recipe
-	instruction pages were crawled.  Recipe listings were pages that provided 
-	lists of recipes, and contained a title and short description for each.  
+	instruction pages were retrieved.  Recipe listings were pages that 
+	provided lists of recipes, and contained a title and short description 
+	for each.  
 	The recipe instruction pages had lists of ingredients and preparation 
@@
 
-We chose the synsets \textit{food.n.01} and \textit{food.n.02} to act as roots
+We chose the synsets \texttt{food.n.01} and \texttt{food.n.02} to act as roots
 in defining which words should be considered food-related.  Any word form
@@
 The subset of the wordnet corpus induced by the hyponyms of \textit{food.n.01}
-and \textit{food.n.02} provide an extensive set of \td{X} words.  Manual
-testing appeared to show that the coverage was very extensive, except in 
-some cases references to ethnic foods were missing.  Since, especially in
-\textit{exp2} we had images containing many ethnic foods, we decided to 
-augment the wordnet corpus with words learned by crawling the world food
-section of the allrecipes.com website.
+and \textit{food.n.02} provide a set of 3590 words.  Manual
+testing showed good coverage, except for references to ethnic foods.  
+Since, especially in \textit{exp2}, we had images containing many ethnic 
+foods, we decided to augment the wordnet corpus with words learned by 
+crawling the world food section of the allrecipes.com website.
 
 After collecting a set of words using an automated script 
-(\td{described above}), we collected the set of words that had been used by
+(described above), we collected the set of words that had been used by
 workers and which had been seen during crawling of the allrecipes.com website,
@@
 To determine whether our extended version of wordnet provided a good approach
-to detecting food-related words, we sampled 500 words from the set of labels
-produced by workers and had three human coders manually decide if they were 
-food-related or not.  The method for randomly sampling the 500 words was 
-described in above in \td{section number}.
+to detecting food-related words, we sampled 500 words 
+(50 from each test task)  from the set of labels produced by workers and had 
+three human coders manually decide if they were 
+food-related or not.
 
@@
 an edible item.  The guiding principle was, for the coder to ask herself,
-``can I eat this X'', where X is the word she is coding.  The coders were
+``can I eat X'', where X is the word she is coding.  The coders were
 shown the used in the task from which the word came, to help resolve ambiguity
@@
 spelling correction (if any) that the spell-correction algorithm had made,
-to help interpret misspelled words \td{we describe the spelling correction 
-algorithm in section X}.
+to help interpret misspelled words.
 
@@
 
-	\textit{whether to correct misspelled words.}  Because we used free-text
+	\textit{Spelling correction.}  Because we used free-text
 	entry for the labels, there was bound to be many spelling mistakes.
@@
 
-	\textit{Whether to split multiple words.}  Although workers were 
+	\textit{Splitting multiple words.}  Although workers were 
 	instructed to put one word per text input, many put multiple words.

### 2015-01-07 src/analysis.py

@@ -34,6 +34,7 @@ from collections import defaultdict, Counter
 import os
 import copy
 import csv
+from scipy.stats import chi2_contingency as chi2
 
 CORRECTIONS_PATH = 'data/new_data/dictionaries/with_allrecipes/'
 DICTIONARY_FNAMES = ['dictionary_1.json', 'dictionary_2.json']
@@ -84,10 +85,206 @@ COMPARISONS = [
 	{'name':'exp2.*', 'experiment':2, 'treatments': [12,13]}
 ]
 
+
 class AnalysisError(Exception):
 	pass
 
 
+def do_all_chi_squared_tests(
+		data_fname='data/new_data/chi2.json',
+		table_fname='data/new_data/chi2.tex'
+	):
+
+	data_fh = open(data_fname, 'w')
+	table_fh = open(table_fname, 'w')
+	comparisons = {
+		'intertask-food-objects':[0,5], 
+		'frame-food-objects':[10,11], 
+		'echo-food-objects':[12,13], 
+		'intertask-food-culture':[0,1], 
+		'frame-food-culture':[3,5]
+	}
+	treatments = {
+		'intertask-food-objects': {
+			'food': (2,0),
+			'objects': (2,5),
+		},
+		'frame-food-objects': {
+			'food': (2,10),
+			'objects': (2,11),
+		},
+		'echo-food-objects': {
+			'food': (2,12),
+			'objects': (2,13),
+		},
+		'intertask-food-culture': {
+			'food': (1,0),
+			'culture': (1,1),
+		},
+		'frame-food-culture': {
+			'food': (1,3),
+			'culture': (1,5),
+		}
+	}
+	experiments = [
+		['intertask-food-culture', 'frame-food-culture'], 
+		['intertask-food-objects', 'frame-food-objects', 'echo-food-objects']
+	]
+
+	# Test within-treatment homogeneity 
+	within_treatment_chi2_vals = {}
+	table_fh.write(
+		'\\begin{table}\n\\centering\n\\begin{tabular}{c c c c c}\n'
+		'\\toprule\nExperiment & Treatment & Degrees of freedom & $\chi^2$ & $p$-value'
+		'\\\\\n\\toprule\n'
+	)
+	for exp_idx in [1,0]:
+		for key in experiments[exp_idx]:
+			spec = treatments[key]
+			table_fh.write(
+				'\\noalign{\\smallskip}\n\\multirow{2}{*}{\\textit{%s}}' % key
+			)
[…]

### 2015-01-07 src/util.py

@@ -1,6 +1,43 @@
 import sys
 import random
 
+def as_scientific(float_number, precision):
+	formatter = '%%1.%de' % (precision-1)
+	as_str = formatter % float_number
+	digits, exp = as_str.split('e')
+	return float(digits), int(exp)
+
+def as_scientific_latex(
+		float_number,
+		precision,
+		min_exp=None, 
+		math_delimiters=True
+	):
+	'''
+		renders a float as latex-formatted string with pretty scientific 
+		notation.  min_exp is the minimum absolute value of the exponent,
+		below which the string will be prented in plain decimals.
+	'''
+
+	if min_exp is None:
+		min_exp = precision
+
+	digits, exp = as_scientific(float_number, precision)
+
+	if abs(exp) < min_exp:
+		formatter = '%%1.%df' % (abs(exp) + precision - 1)
+		formatted =  formatter % (float_number)
+
+	else:
+		formatter = '%%1.%df \\times 10^{%%d}' % (precision-1)
+		formatted = formatter % (digits, exp)
+
+	if math_delimiters:
+		return '$%s$' % formatted
+
+	return formatted
+
+
 def writeNow(string):
 	sys.stdout.write(string)
 	sys.stdout.flush()

### 2015-01-07 src/wordnet_analysis.py

@@ -565,11 +565,11 @@ class WordnetFoodDetector(object):
 		self.food_synsets = [
 			'food.n.02', 
 			'food.n.01', 
-			'helping.n.01',
-			'taste.n.01', 
-			'taste.n.05', 
-			'taste.n.06', 
-			'taste.n.07'
+			#'helping.n.01',
+			#'taste.n.01', 
+			#'taste.n.05', 
+			#'taste.n.06', 
+			#'taste.n.07'
 		]
 
 		self.foodish_cache = dict([(s,True) for s in self.food_synsets])

### 2015-01-08 docs/publications/2014.09_SCIENCE/man.tex
proofed latest draft; still need to update figure legends

@@
 industrial researchers are increasingly relying on \textit{human computation} 
-as a means to extract useful knowledge.  Microtask
+to extract useful knowledge.  Microtask
 platforms, like Amazon Mechanical Turk, act like a human compute cluster,
@@
 This has lead to their broad adoption by social and computer scientists.  
-Human computation is being used in applications
+Human computation is being used experimentally in applications
 where expert opinion would normally be sought, such as in reviewing 
 medical images.
-Here we show that the repetition of similar tasks, which is an inherent
+Here we show that the repeated performance of similar tasks, an inherent
 feature of microtask and crowdsourcing platforms, acts as a strong
-and largely unexplored source of bias.  The effects of previous tasks on
-later ones---\textit{intertask effects}---are more severe than the effects 
-of framing, such as by disclosing a task's purpose.  
+and largely unexplored source of bias.  Previous tasks exert strong 
+influences on how workers perform later tasks, which we call 
+\textit{intertask effects}.  These effects are more severe than effects 
+caused by framing, such as by disclosing a task's purpose.  
 Using image-labeling, the canonical microtask, we show that prior 
@@
 While intertask effects can be a source of systematic bias, our
-results suggest that, when properly controlled, they might be leveraged
-to hone worker focus and specificity, and could play a key role in engineering
-tasks that elicit reproducible, expert-level judgments.
+results suggest that with appropriate task-engineering, it might be possible
+to leverage intertask effects to hone worker focus and specificity, helping
+to elicit reproducible, expert-level judgments.
 \end{sciabstract}
@@
 
-Microtasks are typically distributed to workers in bundles.  For example, a 
-worker might be assigned a set of ten images, and asked to provide 
-descriptive words (or \textit{labels}) for each.  
-On MTurk, these bundles are called Human Intelligence Tasks (HITs).
+Here we focus on an aspect of the microtask setup that is ubiquitous, but 
+has not yet received much attention.  Microtasks are typically distributed 
+to workers in bundles.  For example, a worker might be assigned a set of ten 
+images, and asked to provide descriptive words (or \textit{labels}) for 
+each.  On MTurk, these bundles are called Human Intelligence Tasks (HITs).
 But for the sake of clarity, we will use ``task'' to mean the smallest 
@@
 
-Results in psychology show that people are susceptible to various kinds of 
-priming \cite{BJOP1796,No2007,beller1971priming}, including 
+Results in psychology show that people are 
+susceptible to various kinds of priming 
+\cite{BJOP1796,No2007,beller1971priming}, including 
 task-repetition effects \cite{Gass1999549,sohn2001task}.  
-Yet to our knowledge, no study has investigated the bias that might
+But to our knowledge, no study has investigated the bias that might
 result from the fact that microtask workers typically perform many tasks in 
 succession.  The experiments we present here show that a worker's response 
-to a task depends strongly on the tasks she had performed beforehand.
+during a task depends strongly on the tasks performed beforehand.
 In other words, unlike CPUs and GPUs, HPUs are subject to 
@@
 the most common MTurk tasks \cite{chandler2013breaking,Berinsky2012351,Finnerty2013,paolacci2010running}.  This trend will probably continue 
-in the long term because of their role in computer vision research 
-\td{find another application} \cite{5543192}.  In our first experiment, 
-which we will refer to as 
+in the long term, because image labeling is still very difficult to automate
+\cite{5543192}, and is used in many applications, such as website moderation, 
+computer vision research, and social media analytics (\# insert other refs) 
+\cite{5543192}.  In our first experiment, which we will refer to as 
 \textit{intertask-food-objects}, workers were assigned to either a
@@
 both treatments.  The test tasks contained images depicting a 
-mixture of food and other objects (see Fig.~\ref{fig:task}C), and workers
-were again asked to supply five labels.  Five initial 
+mixture of food and objects (see Fig.~\ref{fig:task}C), and workers
+were again asked to provide five labels.  Five initial 
 tasks, together with the test tasks, comprised one HIT 
@@
 be the resulting change in the probability with which workers provide given 
-responses (formally the totatal variation distance):
+responses (formally the total variation distance):
 \begin{equation}
@@
 provides response $x$, from the set of possible responses $X$.
-The problem of determining $\theta$ from finite samples of responses is 
-difficult, which leads us to reformulate it as a classification problem: 
-given a worker's 
-response, can a machine reliably infer what her priming exposure had been?  
-Intuitively, the greater the effect that priming exposures have on workers' 
+It is important to emphasize that a sigificant result from a $\chi^2$ test 
+only allows us to conclude that $\theta$ is non-zero.  Determining $\theta$ from finite samples of 
+responses, using purely statistical approaches, is difficult (\#), which 
+leads us to reformulate the
+problem in terms of classification: given a worker's 
+response, can a machine reliably infer what her prior task-exposure had 
+been?  Intuitively, the greater the effect that prior tasks have on subsequent
 responses, the more accurate the classifier can be.  Formally, as we show
-in the supplementary text, the performance of such a classifier, $\eta$,
-yields a lower bound on the true bias:
+in the supplementary text, the accuracy of such a classifier, $\eta$,
+yields a lower bound on the bias:
 \begin{equation}
@@
 \end{equation}
-Thus, measuring the performance of a classifier allows us to establish a
+Thus, measuring the accuracy of a classifier allows us to establish a
 lower bound on the extent of bias. This approach can be used to bound the 
@@
 approach to measuring accuracy, and draw a comparison to the results obtained 
-if a support vector machine is used.), we found that intertask effects 
+if a support vector machine is used), we found that intertask effects 
 lead to a 30\% bias between workers from the \textit{food} and 
@@
 
-As mentioned, the effects of framing on workers' responses to microtasks has 
-been studied in various ways 
-\cite{Kinnaird2012281,chandler2013breaking,thibodeau2013natural}.
-Therefore, as a point of comparison, we performed a similar experiment 
-in which we framed the purpose of the tasks.  Workers were either told that 
+There has been considerable interest in the effects that framing can have
+on microtask responses
+\cite{Kinnaird2012281,chandler2013breaking,thibodeau2013natural}, so,
+as a point of comparison, we performed a similar experiment 
+in which we framed the purpose of the tasks.  In the experiment 
+\textit{frame-food-objects}, workers were either told that 
 the tasks were ``Funded by the laboratory for the visual perception of Food 
-and Ingredients'', or ``\ldots of Objects and Tools''.  We did not observe a 
-statistically significant framing-induced bias, using a na\"ive Bayes 
-classifier (see Fig.~\ref{fig:theta}).  This suggests
-that prior task exposure is a stronger priming modality than framing.
-\td{I need to talk about the $\chi^2$ result here.}
+and Ingredients'', or ``\ldots of Objects and Tools''.  
+Framing did induce statistically significant changes in the frequencies of 
+word usage (as determined by $\chi^2$ test; $p=0.0012$), albeit at a much 
+lower significance than for intertask effects.  But we did not find a 
+significant amount of framing-induced bias, using a na\"ive Bayes classifier 
+(see Fig.~\ref{fig:theta}).  This suggests that prior task exposure is a 
+stronger priming modality than framing.
 
@@
 workers to a statement framing the purpose of the tasks as the recognition 
-of either food or cultures.  
+of either food or culture.  
 For this framing experiment, we did not observe a statistically significant 
@@
 reference to food, that is, the number of \textit{unique} food-related words
-used.
+used.  Even if workers provide an abundance of food-related words, if the 
+same words are often repeated, there will of course be a smaller total 
+diversity.  This could happen, for example, if workers use generic references 
+to food.
 Both \textit{intertask} experiments showed that food-exposed workers had 
 greater lexical richness, in reference to food, than their non-food-primed 
-counterparts (as much as 20\% more; see Fig.~\ref{fig:specificity}).  This
-held in the case of \textit{intertask-food-culture}, even though, in that 
-experiment, food-primed workers referred to food less often overall.  
-This enrichment of the food-related lexicon 
-was also observed in the \textit{priming-food-objects}, and 
-\textit{echo-food-objects} experiments, but to a lesser extent.
-
-This lexical enrichment suggests that priming, whether by prior task 
-exposure or framing, leads workers to use more refined 
-or specialized words, in reference to concepts present in the prime.
-To test this directly, we used the wordnet corpus to operationalize the 
-notion of word specialization.
-Wordnet provides a set of hypernym-hyponym relations between \# English 
-nouns.  
-Hypernyms are generalizations (for example, ``bread'' is a hypernym for 
+counterparts (as much as 20\% more) (see Fig.~\ref{fig:specificity}).  
+The increase in lexical richness in the case of 
+\textit{intertask-food-culture} is quite interesting, because in that 
+experiment, food-primed workers made fewer total references to food.  
+We also observed enrichment of the food-related lexicon in the 
+\textit{priming-food-objects}, and \textit{echo-food-objects} experiments, 
+although to a lesser extent.
+
+The observations regarding lexical richness lead us to suspect that 
+initial tasks might influence workers to use more refined or specialized 
+words, when refering to aspects of content that had been present in the 
+initial tasks (i.e. food).  This would help explain why, in the case of 
+\textit{intertask-food-culture}, we observed a significantly greater 
+\textit{diversity} of food-related words despite their significantly lesser 
+\textit{total amount}.
+To test whether exposure to food in initial tasks increased the specialization
+of food-references, we used the wordnet corpus to operationalize the 
+notion of word specialization.  Wordnet provides a set of hypernym-hyponym 
+relations between \# English nouns.  Hypernyms are generalizations 
+(for example, ``bread'' is a hypernym for 
 ``pumpernickel''), while hyponyms are specializations.
-To assess the relative specialization of words from two different treatments,
-we compared all pairs of words from one treatment to the other. 
-We tallied the cases where one treatment's word was more specialized
-than the other, as well as the cases wher roles were reversed.  
-The difference of these tallies, as a percentage of their total, served as 
-the relative specialization of one treatment's vocabulary relative to the 
-other (\#) (see Fig.~\ref{fig:specificity}).  
-Using this approach, we compared the specialization of food-related words 
-for the treatments of all experiments.
+For each experiment, we compared food-related words provided by workers from 
+one treatment to those from the other, and tallied the excess number of cases
+where one treatment's words were more specialized than the other.
+Expressed as a percentage of their total, this tally served to 
+measure the relative specialization of the vocabulary used in one 
+treatment's vocabulary relative to the other 
+(\# full detail for this calculation is provided the supplementary text) 
+(see Fig.~\ref{fig:specificity}).
 
@@
 richness and specialization of food-related words 
-held for \textit{intertask-food-culture}, where, again, we observed fewer 
-references to food by food-primed workers overall. These observations point 
+held for \textit{intertask-food-culture}, where, as mentioned, we observed 
+that food-exposed workers had made \textit{fewer} references to food overall. 
+These observations point 
 to countervailing factors: one factor tending to activate the more 
@@
 (yielding greater lexical richness and specialization), and the other tending 
-to suppress certain, presumably more common or generic words 
+to suppress certain, presumably more common and generic words 
 (yielding fewer food-related words in total).
@@
 Taken together, our results can be 
-explained through a combination of positive and negative priming.
+explained through a combination of positive and negative priming effects.
 Positive priming (usually simply ``priming'') occurs when a prior stimulus 
@@
 might be simply to randomize task ordering, a practice that is commonly 
-observed.  But the sheer extent of bias that we observed leads us to question 
-whether that is the best approach, since this would tend to raise 
-the ``noise floor'' of the study.
-
-Furthermore, our findings suggest that, through careful task engineering,
-it might be possible to achieve much more.  The boost that we observed to the 
-richness and specialization of workers' responses motivates further 
-investigation to acquire a deeper understanding of intertask effects.  
-We hope that future work will yield techniques to leverage intertask effects, 
-enabling one to tune the focus, diversity, and specificity of worker 
-responses.
-
+employed.  But the sheer extent of bias that we observed leads us to question 
+whether that is the best approach.  Although the bias is random in 
+that case, it is still on the order of 30-50\%, which is a major contribution
+to noise in the results.  It would be preferable to understand intertask
+effects in greater depth so that they might \textit{controlled} rather than
+simply randomized.
+
+Our findings suggest that, through careful task engineering,
+it might be possible to achieve greater quality and reproducibility
+of responses.  
 A consistent goal in human computation is the achievement of expert-level
@@
 experts to direct their focus toward salient features, while filtering out 
-non-salient ones \cite{kellman2009perceptual}.  Using prior task exposure to 
-guide focus and salience attribution might enable expert-level 
-judgment in a wider variety of crowdsourced applications.
+non-salient ones \cite{kellman2009perceptual}.  Using strategic exposure to
+prior tasks, it might be possible to guide workers' focus and salience 
+attribution, enabling expert-level judgment in a wider variety of 
+crowdsourced applications.
+We anticipate that future work will yield techniques to control intertask 
+effects, enabling one to both reduce unwanted bias, as well as tune the 
+focus, diversity, and specificity of worker responses.
 
@@
 on the repetitive use of human judgment is likely subject to the phenomena
-we described here.  It remains to be determined by future work whether 
-intertask effects can be leveraged for more performant and reliable human 
+we described here.  Exploring the concerns and opportunities posed by 
+intertask effects are important directions for future work, 
+in the effort to develop performant and reliable methods for human 
 computation.
-
 \bibliography{newbib}

### 2015-01-09 docs/publications/2014.09_SCIENCE/man.tex
proofed latest revisions, updated figures and figure legends

@@
 feature of microtask and crowdsourcing platforms, acts as a strong
-and largely unexplored source of bias.  Previous tasks exert strong 
-influences on how workers perform later tasks, which we call 
-\textit{intertask effects}.  These effects are more severe than effects 
-caused by framing, such as by disclosing a task's purpose.  
+and largely unexplored source of bias.  The effects that earlier tasks exert
+on later ones are more severe than effects caused by framing, 
+such as by disclosing a task's purpose.  
 Using image-labeling, the canonical microtask, we show that prior 
@@
 
-Here we focus on an aspect of the microtask setup that is ubiquitous, but 
-has not yet received much attention.  Microtasks are typically distributed 
-to workers in bundles.  For example, a worker might be assigned a set of ten 
-images, and asked to provide descriptive words (or \textit{labels}) for 
-each.  On MTurk, these bundles are called Human Intelligence Tasks (HITs).
-But for the sake of clarity, we will use ``task'' to mean the smallest 
-repeatable unit of work, which, in our study, consists of labeling a single
-image.
-
-Results in psychology show that people are 
-susceptible to various kinds of priming 
-\cite{BJOP1796,No2007,beller1971priming}, including 
-task-repetition effects \cite{Gass1999549,sohn2001task}.  
-But to our knowledge, no study has investigated the bias that might
-result from the fact that microtask workers typically perform many tasks in 
-succession.  The experiments we present here show that a worker's response 
-during a task depends strongly on the tasks performed beforehand.
-In other words, unlike CPUs and GPUs, HPUs are subject to 
-\textit{hysteresis}, meaning that their outputs depend on the 
-\textit{history} of their inputs.
-We call the effects that prior tasks induce on later ones 
+Here we focus on a ubiquitous feature of the microtask setup: the 
+tendency for microtask workers to perform many tasks in quick succession. 
+Even if a worker performs the minimum possible amount of work, 
+she will likely have performed several microtasks, since they are typically 
+distributed to workers in bundles.  For example, in one bundle, a worker 
+might be assigned a set of ten images, and asked to provide descriptive words 
+(or \textit{labels}) for each.  On MTurk, these bundles are called Human 
+Intelligence Tasks (HITs), but for the sake of clarity, we will use 
+``task'' to mean the smallest repeatable unit of work, which, in our study, 
+consists of labeling a single image.
+
+The repetitive completion of tasks is of concern because people's responses
+to a prompt can be strongly influenced by their recent exposure to stimuli,
+due to the well-known phenomenon of \textit{priming} 
+\cite{BJOP1796,No2007,beller1971priming}.  Priming is typically relevant when 
+the prior stimuli bear some conceptual or perceptual connection to the 
+ensuing task, and so, the repetition of similar tasks within the typical 
+microtask setup creates an ideal context for strong priming effects
+\cite{Gass1999549,sohn2001task}.
+
+Researchers investigating a somewhat similar class of psychological phenomena,
+found that ratings that microtask workers give to items in a list
+depend on the order in which the list is presented, an effect known as
+\textit{positional bias} \cite{lerman2014leveraging}.  While this 
+result applies mainly to tasks of a 
+particular design, it shows that basic psychological phenomena
+can profoundly influence crowdsourced data.  If human computation is to be
+understood as a kind of computing architecture, it will certainly be 
+necessary to account for the computational ramifications of these 
+psychological phenomena at play in the HPU.
+
+The results we present here show that a worker's response during a task
+does indeed depend strongly on the tasks performed beforehand.   
+In engineering terms, 
+unlike CPUs and GPUs, HPUs are subject to \textit{hysteresis}, meaning
+that their outputs depend on the history of their inputs.  Because 
+task-repetition is inherent in their design, virtually all microtask studies,
+and most crowdsourced studies are at risk from the form of bias we 
+investigate here. We call the effects that earlier tasks exert on later ones 
 \textit{intertask effects}.
@@
 Mechanical Turk (MTurk) microtask platform.  Image-labeling tasks are among
-the most common MTurk tasks \cite{chandler2013breaking,Berinsky2012351,Finnerty2013,paolacci2010running}.  This trend will probably continue 
-in the long term, because image labeling is still very difficult to automate
+the most common MTurk tasks 
+\cite{chandler2013breaking,Berinsky2012351,Finnerty2013,paolacci2010running}. 
+This trend is likely to continue 
+in the long run, because image labeling is still very difficult to automate
 \cite{5543192}, and is used in many applications, such as website moderation, 
@@
 understand the nature and severity of the bias induced by prior task 
-exposures.  
-We define the extent of bias, $\theta$, induced by alternative exposures, to 
+exposures.  To this end, we define the extent of bias, $\theta$, induced by 
+alternative exposures, to 
 be the resulting change in the probability with which workers provide given 
-responses (formally the total variation distance):
+responses (\# this is a general divergence metric between probability 
+distributions known as the \textit{total variation distance}):
 \begin{equation}
@@
 provides response $x$, from the set of possible responses $X$.
-It is important to emphasize that a sigificant result from a $\chi^2$ test 
+It is important to emphasize that a significant result from a $\chi^2$ test 
 only allows us to conclude that $\theta$ is non-zero.  Determining $\theta$ from finite samples of 
@@
 \end{equation}
-Thus, measuring the accuracy of a classifier allows us to establish a
-lower bound on the extent of bias. This approach can be used to bound the 
+By measuring the accuracy of a classifier, we can bound the 
 bias induced by any perturbation, including both intertask effects and 
-framing.  As we have defined it, bias ranges from 0 (meaning the exposures 
-do not affect the probabilities of respnoses), to 1 
+framing.  As defined, bias ranges from 0 (meaning the exposures 
+do not affect the probabilities of responses), to 1 
 (or 100\%) (meaning that under different exposures, workers provide completely
@@
 	\caption{
-		Examples of images used for various experiments and treatments:
-		(A) initial task for \textit{task1:food}, (B) initial task for 
-		\textit{task1:obj}, (C) test task for treatments in \textit{exp1}, 
-		(D) initial task for \textit{task2:food}, 
-		(E) initial task for \textit{task2:cult},  
-		(F) test task for treatments in \textit{exp2}.  
+		Examples of images used in
+		initial tasks for the (\textbf{A}) \textit{food} and (\textbf{B}) 
+		\textit{objects} treatments of \textit{intertask-food-objects};
+		(\textbf{C}) test tasks for \textit{intertask-food-objects} and 
+		\textit{frame-food-objects};
+		initial tasks for the (\textbf{D}) \textit{food} and (\textbf{E}) 
+		\textit{culture} treatments of \textit{intertask-food-culture};
+		and (\textbf{F}) test tasks for \textit{intertask-food-culture} and 
+		\textit{frame-food-culture}.
 		The full set of experimental materials is shown in the 
@@
 lead to a 30\% bias between workers from the \textit{food} and 
-\textit{objects} treatments.
+\textit{objects} treatments.  This represents a substantial potential to 
+distort microtask data.
 
@@
 and Ingredients'', or ``\ldots of Objects and Tools''.  
-Framing did induce statistically significant changes in the frequencies of 
-word usage (as determined by $\chi^2$ test; $p=0.0012$), albeit at a much 
-lower significance than for intertask effects.  But we did not find a 
-significant amount of framing-induced bias, using a na\"ive Bayes classifier 
-(see Fig.~\ref{fig:theta}).  This suggests that prior task exposure is a 
-stronger priming modality than framing.
+Framing did induce changes in the frequencies of 
+word usage at significance (as determined by $\chi^2$ test; $p=0.0012$), but 
+the \textit{extent} of framing-induced bias we found was insignificant 
+(see Fig.~\ref{fig:theta}).  This suggests 
+that prior task exposure is a stronger priming modality than framing.
 
@@
 As before, the initial tasks for the \textit{food} treatment contained images 
-depicting food (\#) (see Fig.~\ref{fig:task}D). 
+depicting food (see Fig.~\ref{fig:task}D). 
 In the \textit{culture} treatment, 
@@
 	\caption{
-		Bias as measured by a na\"ive Bayes classifier, $\theta_\mathrm{NB}$,
-		induced in image-labeling tasks, due to framing and 
-		intertask effects. 
-		(A) Bias in the responses to five test tasks,
-		measured between the pairs of treatments indicated on the $x$-axis.  
-		(B) Bias between the treatments of \textit{task1}, 
-		measured for individual test tasks, and plotted as a function of 
-		task position.  Error bars show the 95\% confidence intervals.
+		Empirical bias, $\theta_\mathrm{NB}$, measured using a na\"ive Bayes 
+		classifier, induced in image labeling tasks,
+		(\textbf{A}) by exposing workers to initial tasks or framing. 
+		As workers proceed through test tasks, the effects of initial tasks 
+		wane, as shown (\textbf{B}) for \textit{intertask-food-objects}, but 
+		remain significant even after five tasks.  Standard error bars are 
+		shown.
 	}
@@
 	\centering
-	\includegraphics[scale=1]{figs/vocab_specificity.pdf}
+	\includegraphics[scale=0.94]{figs/vocab_specificity.pdf}
 	\caption{
-		Intertask and framing effects on the vocabulary workers use to refer 
-		to food(\#), when labeling images, for various treatment pairs.
-		(A) Relative change in the number references to food. 
-		(B) Relative change in the number of \textit{unique} 
-		references to food (lexical richness). 
-		(C) Relative specialization of food references, based on the 
-		hypernym-hyponym relations (this calculation is shown in the 
-		supplementary text).  For all
-		plots, a positive bar height indicates that the \textit{*:food}
-		treatment has more of the quantity than its conjugate treatment.
+		(\textbf{A}) Exposing workers to initial tasks and framing 
+		involving food changed how often they referred to food 
+		during test tasks, but did not always increase it (in all three plots,
+		positive values indicate a larger quantity for food-exposed workers).
+		(\textbf{B}) The number of unique food-related
+		words (richness) was greater for food-exposed workers, except in the 
+		case of \textit{frame-food-culture} (stars indicate the threshold
+		for a significant deviation from the null hypothesis, $\alpha=0.05$). 
+		(\textbf{C}) Food-exposed
+		workers also used more specialized words to refer to food.
+		Standard error bars are shown in (\textbf{A} and \textbf{C}).
 	}
@@
 intertask effects, we investigated the vocabulary
-that workers used to label test tasks. A natural expectation is that, within
-a given experiment, the food-primed workers would use more food-related words 
-than their non-food-primed counterparts.  However, this was not generally 
+that workers used to label test tasks. A natural expectation is that, during
+the test tasks within
+a given experiment, the food-primed workers would use food-related words 
+more often than their non-food-primed counterparts.  However, this was not 
+generally 
 the case. In the \textit{intertask-food-culture} experiment, food-primed
@@
 information for details)) (see Fig.~\ref{fig:specificity}).  This finding
-rules out a simple mechanism in which worker's attention is drawn toward
-content that had been found in earlier tasks.  Seeing content in prior tasks 
-seems to affect the probability that a worker refers to that content it in 
-subsequent tasks, but does not necessarily increase it.
+rules out a seemingly-simple mechanism in which workers emphasize
+content that had been present in earlier tasks.  Seeing content in prior tasks
+affects the probability that a worker refers to it in subsequent tasks, but 
+does not necessarily \textit{increase} the probability.
 
@@
 used.  Even if workers provide an abundance of food-related words, if the 
-same words are often repeated, there will of course be a smaller total 
+same words are often repeated, there will of course be a smaller 
 diversity.  This could happen, for example, if workers use generic references 
@@
 initial tasks might influence workers to use more refined or specialized 
-words, when refering to aspects of content that had been present in the 
+words, when referring to aspects of content that had been present in the 
 initial tasks (i.e. food).  This would help explain why, in the case of 
@@
 one treatment to those from the other, and tallied the excess number of cases
-where one treatment's words were more specialized than the other.
-Expressed as a percentage of their total, this tally served to 
-measure the relative specialization of the vocabulary used in one 
-treatment's vocabulary relative to the other 
-(\# full detail for this calculation is provided the supplementary text) 
-(see Fig.~\ref{fig:specificity}).
+where one treatment's words were more specialized than the other, as a 
+percentage of the total (see Fig.~\ref{fig:specificity}B) (\# full detail for 
+this calculation is provided the supplementary text).
 
@@
 held for \textit{intertask-food-culture}, where, as mentioned, we observed 
-that food-exposed workers had made \textit{fewer} references to food overall. 
+that food-exposed workers made \textit{fewer} references to food overall. 
 These observations point 
@@
 ordering and bundling of microtasks.  But our findings show that these are 
-powerful design factors.  A natural response to our findings 
-might be simply to randomize task ordering, a practice that is commonly 
-employed.  But the sheer extent of bias that we observed leads us to question 
-whether that is the best approach.  Although the bias is random in 
+powerful design factors.  A natural response might be simply to randomize 
+task ordering, a practice that is commonly employed.  But the sheer extent of 
+bias that we observed leads us to question 
+whether that is the best approach.  Although the bias would be random in 
 that case, it is still on the order of 30-50\%, which is a major contribution
@@
 applications (\#). The distinction between experts and novices can be 
-attributed in part to the posession of specialized knowledge and heuristics. 
+attributed in part to the possession of specialized knowledge and heuristics. 
 But to a large degree, this distinction lies in the ability of 
 experts to direct their focus toward salient features, while filtering out 
-non-salient ones \cite{kellman2009perceptual}.  Using strategic exposure to
-prior tasks, it might be possible to guide workers' focus and salience 
+non-salient ones \cite{kellman2009perceptual}.  Using strategic task 
+exposures, it might be possible to guide workers' focus and salience 
 attribution, enabling expert-level judgment in a wider variety of 
@@
 		used the word with higher frequency.  Word frequencies for 
-		\textit{intertask-food-objects} are aggregated accross 5 
+		\textit{intertask-food-objects} are aggregated across 5 
 		permutations, and hence tend to show larger absolute differences.
@@
 	correction algorithm described below.  
-	Next, words were lematized using the
+	Next, words were lemmatized using the
 	wordnet lemmatizer \cite{miller1995wordnet,felbaum1998wordnet}.  
@@
 	\paragraph{Variance in food vocabulary size (lexical richness).}
-	The number of unique words in a text is strongly dependant on the size
+	The number of unique words in a text is strongly dependent on the size
 	of the text: as more text is sampled, previously unseen words continue

### 2015-01-09 src/analysis.py

@@ -696,7 +696,6 @@ def vocabulary_null_model(
 		num_bootstraps=1000,
 		num_workers=119,
 		images=range(5,10),
-		fname='data/new_data/vacabulary_null.json'
 	):
 
 	fname = 'data/new_data/vocabulary/vocabulary_null_%s.json' % comparison
@@ -710,6 +709,7 @@ def vocabulary_null_model(
 	assert(comparison in comparisons)
 	fh = open(fname, 'w')
 
+	
 	upper_CI_idx = int(np.ceil(0.975 * num_bootstraps)) - 1
 	lower_CI_idx = int(np.floor(0.025 * num_bootstraps))
 

### 2015-01-09 src/new_plots.py

@@ -264,8 +264,8 @@ def plot_specificity(
 		fh = open('data/new_data/specificity/specificity_%s.json' % key)
 		data = json.loads(fh.read())
 		mean = 100 * data['mean']
-		err_high = abs(100 * data['lower_CI'] - mean)
-		err_low = abs(100 * data['upper_CI'] - mean)
+		err_high = abs(100 * data['std'])
+		err_low = abs(100 * data['std'])
 		specificity_data.append(mean)
 		specificity_error_high.append(err_high)
 		specificity_error_low.append(err_low)
@@ -515,7 +515,7 @@ def plot_theta(
 	# convert accuracy to priming difference (which is what we want to plot)
 	Y_aggregate = [100*(2*a-1) for a in accuracies]
 	err_low = [
-		100*(2*binomial_lower_confidence_p(n, int(n*a)) - 1)
+		100*(2*binomial_lower_confidence_p(n, int(n*a), alpha=0.15865) - 1)
 		for a,n in zip(accuracies,[595,119,119,119,119])
 	]
 	err_low = [y-y_err for y, y_err in zip(Y_aggregate, err_low)]
@@ -537,12 +537,14 @@ def plot_theta(
 
 	ax1.set_ylabel(r'$\theta_\mathrm{NB}\;(\%)$', size=12)
 
-	xlabels = [r'$task1$', r'$frame1$', r'$echo1$', '$task2$', '$frame2$']
+	xlabels = [
+		r'$intertask$', r'$frame$', r'$echo$', '$intertask$', '$frame$'
+	]
 
 	eps = 0.2
 	ax1.set_xticks(map(lambda x: x + width/2. + eps, X))
 	ax1.tick_params(axis='x', colors='0.25')
-	ax1.set_xticklabels(xlabels, rotation=45, size=12,
+	ax1.set_xticklabels(xlabels, rotation=45, size=10,
 		horizontalalignment='right', color='k')
 
 	# Plot the by_pos data series
@@ -559,7 +561,7 @@ def plot_theta(
 	X = range(len(Y_by_pos))
 
 	err_low = [
-		100*(2*binomial_lower_confidence_p(595, int(595*a)) - 1)
+		100*(2*binomial_lower_confidence_p(595, int(595*a),alpha=0.15865) - 1)
 		for a in avg_accuracies
 	]
 	err_low = [y-y_err for y, y_err in zip(Y_by_pos, err_low)]

### 2015-01-14 docs/publications/2014.09_SCIENCE/man.tex
incorporate some revisions

@@
 
-Given the increasing prevalence of microtask-based research methods, there
-is a desire to understand factors affecting the reliability of HPU
-outputs.  Researchers have investigated task-design parameters such as the 
+Given the increasing prevalence of microtask-based methods, there
+is a desire to understand factors affecting the reliability of microtask
+platforms.  Researchers have investigated task-design parameters such as the 
 level of pay \cite{kazai2013analysis}, the training and pre-screening of 
@@
 word usage at significance (as determined by $\chi^2$ test; $p=0.0012$), but 
-the \textit{extent} of framing-induced bias we found was insignificant 
+the \textit{extent} of framing-induced bias we found was statistically 
+insignificant (\td{insert p-value})
 (see Fig.~\ref{fig:theta}).  This suggests 
@@
 information for details)) (see Fig.~\ref{fig:specificity}).  This finding
-rules out a seemingly-simple mechanism in which workers emphasize
-content that had been present in earlier tasks.  Seeing content in prior tasks
+rules out a seemingly-simple idea that workers emphasize
+content that has been present in earlier tasks: seeing content in prior tasks
 affects the probability that a worker refers to it in subsequent tasks, but 
@@
 used.  Even if workers provide an abundance of food-related words, if the 
-same words are often repeated, there will of course be a smaller 
-diversity.  This could happen, for example, if workers use generic references 
+same words are often repeated, there will be less diversity.  
+This could happen, for example, if workers use generic references 
 to food.
@@
 The increase in lexical richness in the case of 
-\textit{intertask-food-culture} is quite interesting, because in that 
+\textit{intertask-food-culture} is particularly noteworthy, because in that 
 experiment, food-primed workers made fewer total references to food.  
@@
 whether that is the best approach.  Although the bias would be random in 
-that case, it is still on the order of 30-50\%, which is a major contribution
-to noise in the results.  It would be preferable to understand intertask
+that case, our results suggest that it is on the order of 30-50\%, 
+which is a major contribution to noise in the results.
+It would be preferable to understand intertask
 effects in greater depth so that they might \textit{controlled} rather than
@@
 on the repetitive use of human judgment is likely subject to the phenomena
-we described here.  Exploring the concerns and opportunities posed by 
+we described here.  Exploring the issues and opportunities posed by 
 intertask effects are important directions for future work, 

### 2015-01-20 docs/publications/2014.09_SCIENCE/man.tex
work on manuscript, add hypothesis tests, put dictionaries in repo

@@
 
+\usepackage{amsmath}
 \usepackage{framed, color}
@@
 
-While microtask platforms have been widely adopted as a research tool,
-computer scientists also hold such platforms as the object of 
-research, viewing  microtask platforms as a new kind of computing 
-architecture.  In analogy to CPUs (central 
-processing units) and GPUs (graphics processing units), 
-Davis \textit{et al} invoked the \textit{human processing unit}, or HPU \cite{5543192}.
-Researchers have sought to define a basic HPU instruction set, and
-libraries for HPU programming are under active development
- \cite{little2010turkit,minder2011crowdlang,minder2012crowdlang,kittur2011crowdforge}.
+These platforms allow requesters to make use of human intelligence
+\textit{algorithmically}.  Tasks are posted and results fetched by transfering
+files over the Internet, making it possible to embed microtask work in an
+automated process.  To the surrounding process, workers seem like 
+input-output devices, which provides much of the flexibility and 
+cost-savings of actually automating the work: the workforce is available
+on demand, over the Internet, without any contracts or interviews, at a rate
+of about 6 USD\$/ hr.  Many kinds of work can be performed at a fraction of 
+the cost that would otherwise be required, either to recruit temporary 
+workers, or to research and design a sophisticated automated solution.
+
+For this reason, there has been a surge in demand for microtask work
+in both industry and academia.  Industry employs microtask workers
+for clerical tasks, such as digitizing records and correcting errors; 
+and for marketing activities, such as running focus groups, writing product 
+reviews,
+and moderating website content.  Academia turns to microtask workers as 
+a way to recruit study participants, and to annotate datasets, for example,
+to provide ground-truth in training artificial intelligence systems.
 
 Given the increasing prevalence of microtask-based methods, there
-is a desire to understand factors affecting the reliability of microtask
+is a desire to understand the factors affecting the reliability of microtask
 platforms.  Researchers have investigated task-design parameters such as the 
@@
 depend on the order in which the list is presented, an effect known as
-\textit{positional bias} \cite{lerman2014leveraging}.  While this 
-result applies mainly to tasks of a 
-particular design, it shows that basic psychological phenomena
-can profoundly influence crowdsourced data.  If human computation is to be
-understood as a kind of computing architecture, it will certainly be 
-necessary to account for the computational ramifications of these 
-psychological phenomena at play in the HPU.
-
+\textit{positional bias} \cite{lerman2014leveraging}.  This serves as an 
+example of a basic psychological phenomenon impacting crowdsourced data,
+and raises a serious question about what other cognitive biases might
+affect microtask work, and how prevelant induced bias might be.
+
+We therefore turn to the question of bias induced by taks-repetition effects, 
+which, if present, would impact virtually every microtask workflow.
 The results we present here show that a worker's response during a task
 does indeed depend strongly on the tasks performed beforehand.   
-In engineering terms, 
-unlike CPUs and GPUs, HPUs are subject to \textit{hysteresis}, meaning
-that their outputs depend on the history of their inputs.  Because 
-task-repetition is inherent in their design, virtually all microtask studies,
-and most crowdsourced studies are at risk from the form of bias we 
-investigate here. We call the effects that earlier tasks exert on later ones 
+We call the effects that earlier tasks exert on later ones 
 \textit{intertask effects}.
 
+As we have described, microtask platforms have been widely adopted as a 
+tool, but computer scientists also hold such platforms as the object of 
+research, viewing  microtask platforms as a new kind of computing 
+architecture.  In analogy to CPUs (central 
+processing units) and GPUs (graphics processing units), 
+Davis \textit{et al} invoked the \textit{human processing unit}, or HPU \cite{5543192}.
+Researchers sought to define a basic HPU instruction set, and
+libraries for HPU programming are under active development
+ \cite{little2010turkit,minder2011crowdlang,minder2012crowdlang,kittur2011crowdforge}.  
+HPU outputs are inherently stochastic, but our revelation of strong intertask 
+effects shows that HPUs are subject to \textit{hysteresis}, 
+meaning that their 
+outputs depend on the history of their inputs.  Reproducibility and 
+path-independance are crucial for properties for the basic components in a 
+computing architecture, so it will be necessary to understand the 
+computational ramifications of these psychological phenomena to further this 
+interesting line of investigation.
+
 We investigated intertask effects using image-labeling tasks on the Amazon 
-Mechanical Turk (MTurk) microtask platform.  Image-labeling tasks are among
-the most common MTurk tasks 
-\cite{chandler2013breaking,Berinsky2012351,Finnerty2013,paolacci2010running}. 
-This trend is likely to continue 
-in the long run, because image labeling is still very difficult to automate
-\cite{5543192}, and is used in many applications, such as website moderation, 
-computer vision research, and social media analytics (\# insert other refs) 
-\cite{5543192}.  In our first experiment, which we will refer to as 
+Mechanical Turk (MTurk) microtask platform.  
+In addition to being one of the most common kinds of tasks
+\cite{chandler2013breaking,Berinsky2012351,Finnerty2013,paolacci2010running},
+image-labeling is prototypical for any kind of task in which the worker is 
+asked to provide a qualitative free-text response to a prompt.  
+This includes such such examples as describing
+video and audio recordings, summarizing texts, or providing personal 
+experiential feedback to a product review.
+%in the long run, because image labeling is still very difficult to automate
+%\cite{5543192}, and is used in many applications, such as website moderation, 
+%computer vision research, and social media analytics (\# insert other refs) 
+%\cite{5543192}.
+
+In our first experiment, which we will refer to as 
 \textit{intertask-food-objects}, workers were assigned to either a
@@
 (\# workers were only allowed to participate once). During the HIT, workers 
-were presented images one at a time, and, crucially, there was no distinction
-or interruption between the initial and test tasks.
+were presented images one at a time, and, crucially, we made no 
+distinction between the initial and test tasks.
 
@@
 understand the nature and severity of the bias induced by prior task 
-exposures.  To this end, we define the extent of bias, $\theta$, induced by 
-alternative exposures, to 
-be the resulting change in the probability with which workers provide given 
-responses (\# this is a general divergence metric between probability 
+exposures.  To this end, we define the extent of bias, $\theta$, in terms of
+the strength of influence that a perturbation has on worker's responses.
+Since different workers generally provide different responses for the same 
+task, we characterize worker's responses by a probability distribution.  
+The extent of bias is then defined by the difference in the response 
+distribution for different treatments of workers
+(\# this is a general divergence metric between probability 
 distributions known as the \textit{total variation distance}):
 \begin{equation}
-	\theta = \frac{1}{2}\sum_{x \in X} \left| p_1(x) - p_2(x) \right|,
+	\theta = \frac{1}{2}\sum_{x \in X} \left| p_0(x) - p_1(x) \right|,
+	\label{eq:theta}
 \end{equation}
@@
 treatments, included images depicting meals of identifiable cultural 
-origin 
-(see Fig.~\ref{fig:task}F).  Results for this experiment again showed a 
+origin (\# the initial tasks in 
+\textit{intertask-food-culture} are arguably also of identifiable cultural 
+origin, but this would tend to reduce, rather than inflate, our results
+(we discuss this further in the supplementary material).)
+(see Fig.~\ref{fig:task}F).
+
+Results for this experiment again showed a 
 strong bias as a result of intertask effects (about 50\%) 
@@
 task ordering, a practice that is commonly employed.  But the sheer extent of 
-bias that we observed leads us to question 
-whether that is the best approach.  Although the bias would be random in 
-that case, our results suggest that it is on the order of 30-50\%, 
-which is a major contribution to noise in the results.
+bias suggests that this will still introduce a significant amount of noise
+into the results.  Even chains of two or three similar tasks, which
+will not be reliably eliminated in random permutations, could lead
+to the levels of bias we observed in our experiments.
 It would be preferable to understand intertask
-effects in greater depth so that they might \textit{controlled} rather than
-simply randomized.
+effects in greater depth so that they might be properly \textit{controlled}.
 
@@
 
+\subsection*{Determination of $\theta$}
+
 \subsection*{S5: Identification of food-related terms}
@@
 which words correspond to nouns that refer to edible things, and which ones
-don't, which provides a clear and simple interpretation for the machine
+do not, which provides a clear and simple interpretation for the machine
 coding of food and non-food words.
@@
 
+\paragraph{Statistical significance and confidence intervals for $\theta$.}
+The measurements of $\theta$ were based on the number of correct 
+classifications during validation tests.  We used leave-one-out validation,
+and count the number of correct classifications, $X$, which has a binomial
+distribution.  We take the null hypothesis that the classifier performs
+no better than chance, $X \sim \mathrm{Bin}(N,0.5)$, where $N$ is the number 
+of workers in both treatments of an experiment.  Then, the critical number 
+of correct classifications, $x^*$, in for a one-tailed hypothesis test with
+significance $\alpha$ is:
+\begin{align}
+	&x^* = \sup \left\{
+			x: \mathrm{Pr}\{ \mathrm{Bin}(N;0.5) \geq x \} < \alpha
+		\right\}\\
+	\text{where}\quad &\mathrm{Pr}\{ \mathrm{Bin}(N,p) \geq x \} = 
+		\sum_{x'=x}^{N} \binom{N}{x'}p^{x'}(1-p)^{(N-x')}
+\end{align}
+For the treatments in \textit{intertask-food-objects}, 5 different 
+permutations of each treatment was tested, and a different classifier was 
+built for each permutation.  For the sake of estimating the accuracy of 
+these classifiers, we assume that they have the same accuracy, which means
+that \textit{intertask-food-objects} has a larger number of validation tests
+(larger $N$), and for this hypothesis test we assume that $X$ has a normal 
+distribution, with $\mu=N/2$ and $\sigma = \frac{1}{2}\sqrt{N}$.
+
+To determining the confidence intervals for measured $\theta$ values we 
+use the exact Clopper-Pearson method.  
+Based on the observed number of successes, $X$, we calculate 
+$\eta^*_\mathrm{low}$ and $\eta^*_\mathrm{high}$ from:
+\begin{align}
+	\eta^*_\mathrm{high} &= \sup
+		\left\{
+			\eta : \mathrm{Pr}\{\mathrm{Bin}(N; \eta) \leq X \} > 
+				\frac{\alpha}{2}
+		\right\} \\
+	\eta^*_\mathrm{low} &= \inf
+		\left\{
+			\eta : \mathrm{Pr}\{\mathrm{Bin}(N; \eta) \geq X \} > 
+				\frac{\alpha}{2}
+		\right\}
+\end{align}
+Again, for the experiment \textit{intertask-food-objects}, which had 
+more validation tests than the others, we derive the confidence intervals
+assuming $X$ is normally distributed.
+Since the significance values are to be shown on a plot of $\theta$, we 
+transform them into equivalent values of 
+$\theta$: $\theta^*_\mathrm{high} = 2\eta^*_\mathrm{high} - 1$ and 
+$\theta^*_\mathrm{low} = 2\eta^*_\mathrm{low} - 1$.
+The statistics collected for the measurement of $\theta$ are tabulated in 
+table X.
+
+\begin{table}
+\begin{center}
+\begin{tabular}{c c c c c c c}
+	\toprule
+	Experiment & $N$ & $X$ & $x^*$ &
+		$\hat{\theta}$ & $\theta^*_\mathrm{low}$ & 
+		$\theta^*_\mathrm{high}$ \\
+	\midrule
+	\textit{intertask-food-objects} & 1190 & 777 & 624 & \textbf{30.6} 
+		& 25.2 & 36.0 \\
+	\textit{frame-food-objects} & 238 & 122 & 133 & 2.5 & -10.6 & 14.7 \\
+	\textit{echo-food-objects} & 238 & 162 &  133 & \textbf{36.1} & 23.4 
+		& 47.1  \\
+	\textit{intertask-food-culture} & 238 & 180 & 133 & \textbf{51.3} & 39.3 
+		& 61.1 \\
+	\textit{frame-food-culture} & 238 & 130 & 133 & 9.2 & -3.9 & 21.3 \\
+	\bottomrule
+\end{tabular}
+\caption{Statistics for the measurement of the extent of bias, $\theta$,
+	induced by intertask and framing effects in various experiments.
+	Number of validation tests, $N$; number of successful classifications, 
+	$X$; critical number of succesful classifications to reject the null 
+	hypotheses that the classifier does no better than chance 
+	(one-tailed test), $x^*$; 
+	lower bound estimate of bias based on observed number of successful
+	classifications, $\hat{\theta}$; lower confidence interval for lower
+	bound estimate of bias, $\theta^*_\mathrm{low}$; upper confidence 
+	interval for same, $\theta^*_\mathrm{high}$.  Hypothesis test and 
+	confidence intervals are based on a significance of $\alpha=0.05$.
+	Values for $\hat{\theta}$ in boldface are significantly greater than 0.
+}
+
+\end{center}
+\end{table}
+
 \subsection*{S9: Justifications and statistical properties of classifier-based measurement of computational hysteresis}
-\begin{itemize}
-	\item{Relationship to L1-Distance}
-	\item{Relationship to bias}
-	\item{Relationship to Jenson-Shannon divergence}
-	\item{Other approaches to measuring L1-distance}
-	\item{Comparison to hypothesis testing using $\chi^2$}
-\end{itemize}
+
+\paragraph{Comparing $\theta$ to a $\chi^2$ significance test}
+Suppose that we have a very slightly unfairly weighted coin, which turns
+up heads ($x=\mathbf{H}$) more often than expected by 1 part in one hundred:
+$\Pr\{x=\mathbf{H}\} = 0.500001$. Such a coin would be fine for many 
+practical purposes, like deciding who buys lunch.  We could
+perform a $\chi^2$ test to determine if the coin is biased, by flipping 
+it 100 million times, while doing the same with a coin we know is fair.
+Simulating this with a random number generator yields the following results:
+
+\begin{center}
+\begin{tabular}{c c c c}
+\toprule
+coin & $N_\mathbf{H}$ & $N_{\mathbf{T}}$ & total \\
+\toprule
+\textit{fair} & 50002283 & 49997717 & $10^8$\\
+\textit{biased} & 50101115 & 49898885 & $10^8$ \\
+\bottomrule
+total & 100103398 & 99896602 & $2\times 10^8$ \\
+\bottomrule
+\end{tabular}
+\end{center}
+A $\chi^2$ test yields the following results:
+\begin{center}
+	\begin{tabular}{c c c c }
+	\toprule
+	Degrees of freedom & $\chi^2$ & $p$-value \\
+	\toprule
+	1 & 195.4 & $2.2 \times 10^{-44}$ \\
+	\bottomrule
+	\end{tabular}
+\end{center}
+Even though the $\chi^2$ test shows, with tremendous statistical 
+significance, that the unfair coin is indeed unfair, the actual extent
+of bias is small, 
+$\theta = \frac{1}{2}\left( |0.501 - 0.499| + |0.499 - 0.501| \right) = 0.002$.
+A sufficiently large sample size will lead to the detection an arbitrarily 
+small bias with arbitrarily high statistical significance.
+This is why to measure the practical significance of intertask effects
+we rely on a measure of effect size, which is in this case a measure
+of statistical divergence, $\theta$.
+
+\paragraph{Statistical approaches to measuring bias.}
+Recall that in Eq.~\ref{eq:theta} in the main text, we defined the
+extent of bias that exists between two groups of workers to be $\theta$:
+$$
+	\theta = \frac{1}{2}\sum_{x \in X} \left| p_0(x) - p_1(x) \right|,
+$$
+where $p_0(x)$ and $p_1(x)$ represent the probability mass functions
+for responses from two differently treated populations of workers.  
+Let us denote these two populations by $P_0$ and $P_1$.
+As mentioned, this is a measure of the divergence between $p_0$ and $p_1$ 
+which is called either the \textit{total variation} or the 
+\textit{L1-distance}.
+
+Measuring the \textit{L1-distance} between two probability distributions,
+given only samples, is difficult.  The na\"ive approach is to take
+the maximum likelihood estimate of $p(x)$, which sets it equal to the 
+frequency with which the response $x$ has been observed, 
+$\hat{p}(x) = \frac{N_x}{N}$, and then estimate $\theta$ 
+using these frequencies: 
+$\hat{\theta} = \sum_{x \in X}|\hat{p}_1(x) - \hat{p}_2(x)|$.  
+However, this method tends to drastically overestimate $\theta$.
+Recently progress has been made on this problem, and two algorithms have 
+been proposed to estimate the L1-distance between distributions
+given only samples.  But these methods provide only asymptotic guarantees
+which cannot be directly applied to our case.  However, machine learning
+approaches provide a general alternative that we describe in the next 
+section.
+
+\paragraph{Using classifiers to measure bias.}
+
+We will now show that, any classifier algorithm, $\mathcal{A}$, that
+takes the response, $x$, of a worker, and guesses the population to which
+the worker belongs ($P_0$ or $P_1$), will do so with an accuracy, $\eta$,
+that is bounded according to Eq.~\ref{l1}, which is reproduced here:
+$$
+	\theta \geq 2\eta - 1.
+$$
+
+To do so, we will first formalize $\eta$ by defining a 
+\textit{validation test}.  In a validation test, a uniform random bit 
+$z\in\{0,1\}$ is sampled, and then, according to the value of $z$, the
+response of a worker, $x$, is sampled uniformly randomly from $P_z$.  
+The algorithm is provided
+with $x$ and yields a guess, $b=\mathcal{A}(x)$, as to whether the worker was 
+from $P_0$ or $P_1$.  We shall denote such a validation test by 
+$V(P_0, P_1, \mathcal{A})$, and define the value of the test to be 1 if 
+$b=z$ and zero otherwise.
+
+We then define the accuracy of classifier $\mathcal{A}$ to be $\eta$ according
+to:
+$$
+\eta = \mathrm{E\{V(P_0, P_1, \mathcal{A})\}} 
+	= \mathrm{Pr}\{V(P_0, P_1, \mathcal{A})=1\}.
+$$
+
+To develop the relationship between $\eta$ and $\theta$, let us consider
+the accuracy $\eta^*$ of the best possible classifier $\mathcal{A}^*$.
+The best possible classifier will not in general have perfect accuracy:
+if the responses from workers in $P_0$ and $P_1$ are distributed 
+identically, then there is no hope of determining which population the worker 
+came from given only her response $x$.  But, assuming that responses are
+not distributed identically, then given some $x$, the best possible 
+classifier must always guess 1 whenever $p_1(x) > p_0(x)$ and otherwise 
+guess 0.
+
+Sacrificing, for a moment, some generality, let us assume that, for a given 
+$x$, $p_1(x) > p_0(x)$.  
+Then, given some $x'$ has been chosen during a 
+validation test, the optimal classifier must guess that 
+$z = \arg\!\max_{z'}(p_{z'}(x)) = 1$.
+The probability that the classifier guesses correctly, given a validation
+test in which the resonse $x$ was chosen, is therefore:
+\begin{align}
+	\mathrm{Pr}\{V = 1 | x' = x \} 
+		&= \mathrm{Pr}\{\mathcal{A^*}(x) = z | x' = x \} \\
+		&= \mathrm{Pr}\{z = 1 | x' = x \}  \\
+		&= \frac{\mathrm{Pr}\{z = 1 , x' = x\}}
+			{ \mathrm{Pr}\{z=0 , x'=x\} + \mathrm{Pr}\{z=1 , x'=x\}} \\
+		&= \frac{p_1(x)}{p_0(x) + p_1(x)}.
+\end{align}
+And now, with full generally,
+\begin{align}
+	\mathrm{Pr}\{V=1 | x' = x \} 
+		&= \mathrm{Pr}\{\mathcal{A^*}(x) = z | x' = x \} \\
+		&= \mathrm{Pr}\{z = \arg\!\max_{z'}\big(p_{z'}(x)\big)| x' = x \}  \\
+		&= \frac{\max\big( p_0(x),p_1(x) \big)}
+		{ p_0(x) + p_1(x) }.
+\end{align}
+We can rewrite:
+\begin{align}
+	\max\big(p_0(x),p_1(x)\big) = \frac{1}{2}
+		\big(
+			p_0(x) + p_1(x) + |p_0(x) - p_1(x)|
+		\big),
+\end{align}
+so,
+\begin{align}
+	\mathrm{Pr}\{V = 1 | x' = x \} 
+	&= \frac{1}{2} + \frac{|p_0(x) - p_1(x)|}{2 \big(p_0(x) + p_1(x) \big)}.
+\end{align}
+Then the overall accuracy that probability that $\mathcal{A^*}$ guesses correctly in 
+any validation test is:
+\begin{align}
+	\eta^* &= \mathrm{Pr}\{V=1\} \\
+		&=\sum_{x\in X} \mathrm{Pr}\{V = 1 | x' = x \} \mathrm{Pr}\{x' = x\}\\
+		&= \sum_{x\in X} \left(
+				\frac{1}{2} + 
+				\frac{|p_0(x) - p_1(x)|}{2 \big(p_0(x) + p_1(x) \big)}
+			\right)
+			\left(
+				\frac{p_0(x) + p_1(x)}{2}
+			\right)\\
+		&= \frac{1}{2}\left(
+				\frac{1}{2}(
+					\sum_{x \in X}p_0(x) + \sum_{x \in X}p_1(x)
+				) + 
+				\frac{1}{2} \sum_{x \in X} \big(|p_0(x) + p_1(x)|\big)
+			\right) \\
+		&= \frac{1}{2} \left( \frac{1}{2}(1 + 1) + \theta \right)\\
+		&= \frac{1 + \theta}{2}\\
+		\implies \theta &= 2\eta^* - 1.
+\end{align}
+By definition, no classifier can be more accurate than $\mathcal{A^*}$, so
+for every $\mathcal{A}$
+\begin{align}
+		\theta \geq 2\eta - 1.
+\end{align}
 

### 2015-01-20 src/analysis.py

@@ -1175,11 +1175,55 @@ def get_k_star(n, alpha):
 	return k_star
 
 
-def binomial_lower_confidence_p(n,k,alpha=0.05, tolerance=1e-6):
+def binomial_confidence_intervals(
+		n,k,alpha=0.05, tolerance=1e-6, as_theta=False
+	):
 	'''
-		Given a bernouli variable B(p), that has been sampled n times, find 
-		the threshold probability p, at or below which, 95% of the time,
-		we would find less than k successes
+		Gets both the upper and lower confidence intervals for 
+		the single-experiment probability of success, for a binomial
+		variable sampled n times, observed to have k succeses, according 
+		to significance level alpha.  The numerical error on the calculation
+		(not the statistical error mind you) is given by tolerance.
+		as_theta controls whether to return the results as the probability
+		of success (p) or as theta = 2p-1
+	'''
+	try:
+		upper = binomial_upper_confidence_p(n,k,alpha, tolerance, as_theta)
+		lower = binomial_lower_confidence_p(n,k,alpha, tolerance, as_theta)
+
+	except OverflowError:
+		# get it from normal distribution
+		if alpha==0.05:
+			z = CONFIDENCE_95
+
+		elif alpha==0.15865:
+			z = 1.0
+
+		else:
+			raise NotImplementedError(
+				'this function currently only supports alpha=0.05 when the '
+				'sample size is large.  Youll need to code up something to '
+				'produce z-scores for non alpha=0.05 cases.'
+			)
+
+		std_dev = np.sqrt(1/float(n)*(k/float(n))*(1-k/float(n)))
+		upper = k/float(n) + z * std_dev
+		lower = k/float(n) - z * std_dev
+
+		if as_theta:
+			upper = 2*upper - 1
+			lower = 2*lower - 1
+
+	return upper, lower
+
+
+
+def binomial_upper_confidence_p(
+	n,k,alpha=0.05, tolerance=1e-6, as_theta=False):
+	'''
+		For a Binomial RV Bin(n,p), with unknown p,
+		the largest probability p for which we expect to observe at least
+		k successes with probability 1 - alpha/2.
 	'''
 
 	high_p = 1
[…]

### 2015-01-20 src/new_plots.py

@@ -5,7 +5,7 @@ in the paper
 
 import json
 import util
-from analysis import get_theta_star, binomial_lower_confidence_p
+from analysis import get_theta_star, binomial_lower_confidence_p, binomial_confidence_intervals
 import sys
 import random
 import naive_bayes
@@ -456,14 +456,22 @@ def plot_theta_panel(ax, data):
 	accuracies = [this_data[tn] for tn in test_names]
 
 	# convert accuracy to priming difference (which is what we want to plot)
-	Y_aggregate = [2*a-1 for a in accuracies]
-	err_low = [
-		2*binomial_lower_confidence_p(n, int(n*a)) - 1
-		for a,n in zip(accuracies,[595,119,119,119,119])
+	Y_aggregate = [100*(2*a-1) for a in accuracies]
+
+	# construct the confidence intervals
+	confidence_intervals = [
+		binomial_confidence_intervals(n, int(round(n*a)), alpha=0.15865, as_theta=True)
+		for n,a in zip([1190,238,238,238,238], accuracies)
 	]
-	err_low = [y-y_err for y, y_err in zip(Y_aggregate, err_low)]
-	err_high = [0 for e in err_low]
+
+	err_low = [
+		y - 100*c[1] for y,c in zip(Y_aggregate, confidence_intervals)
+	]
+	err_high = [
+		100*c[0] - y for y,c in zip(Y_aggregate, confidence_intervals)
+	]
 	err = [err_low, err_high]
+
 	X = range(len(Y_aggregate))
 
 	series = ax.bar(
@@ -474,10 +482,9 @@ def plot_theta_panel(ax, data):
 	xlims = (-padding, len(X) - 1 + width + padding)
 	plt.xlim(xlims)
 
+	ax.set_yticks([10,20,30,40,50,60])
 
-	ax.set_yticks([0.1,0.2,0.3,0.4,0.5, 0.6])
-
-	ylims = (0, 0.62)
+	ylims = (0, 62)
 	plt.ylim(ylims)
 
 
@@ -514,14 +521,20 @@ def plot_theta(
 
 	# convert accuracy to priming difference (which is what we want to plot)
 	Y_aggregate = [100*(2*a-1) for a in accuracies]
-	err_low = [
-		100*(2*binomial_lower_confidence_p(n, int(n*a), alpha=0.15865) - 1)
-		for a,n in zip(accuracies,[595,119,119,119,119])
+
[…]

### 2015-01-20 src/svm.py

@@ -216,7 +216,7 @@ class LognormalSimulatedAnnealer(object):
 		return best_val, best_params
 
 
-def get_annealing_func(reps=1, CV=20):
+def get_annealing_func(exp=1, reps=1, CV=20):
 	'''
 	wrapper for svm cross_validation on experiment 1 data.
 	It's output is used as the annealing_func argument to the simulated 
@@ -225,14 +225,14 @@ def get_annealing_func(reps=1, CV=20):
 
 	datas = [
 		dp.SimpleDataset(
-			which_experiment=1,
+			which_experiment=exp,
 			show_token_pos=True,
 			show_plain_token=True,
 			show_token_img=True,
 			do_split=True,
-			class_idxs=[1,2],
+			class_idxs=[1,2] if exp==1 else [0,5],
 			img_idxs=[img_idx],
-			spellcheck=False,
+			spellcheck=True,
 			lemmatize=True,
 			remove_stops=True,
 			balance_classes=True,

### 2015-01-20 src/svm.py
add exp2 svm optimizations

@@ -1,4 +1,5 @@
 import os
+import sys
 import numpy as np
 from sklearn import cross_validation
 from sklearn import svm
@@ -8,9 +9,9 @@ import naive_bayes as nb
 import random as r
 import json
 
+BEST_PARAMS_FNAME = 'best.json'
 SVM_EXP2_L1_FNAME = 'exp2.l1.svm.json'
 SVM_OPTIMIZATION_DIR = 'data/new_data/svm_optimization'
-BEST_PARAMS_FNAME = 'exp1.best.json'
 DATA_DIR = 'data/new_data'
 
 
@@ -37,17 +38,30 @@ def find_best_svm_params(write_fname=BEST_PARAMS_FNAME):
 	on each, and take the best result.  
 
 	This is to defend against the fact that variance in reported accuracy
-	during cross validation can to a particular parameter value seeming 
+	during cross validation can lead to a particular parameter value seeming 
 	better than the others when it is not.
 	'''
 
-	# open a file where results will be written
+	# open a file for writing
 	write_fh = open(os.path.join(SVM_OPTIMIZATION_DIR, write_fname), 'w')
 
-	# get a listing of the simulated annealing results which will be ranked
-	fnames = os.popen(
-		'ls %s | grep exp1.run' % SVM_OPTIMIZATION_DIR).read().split()
+	# for exp1 and exp2, find the best parameter settings
+	rescored_params = {}
+	for exp in [1, 2]:
 
+		# get a listing of the simulated annealing results for this exp
+		fnames = os.popen(
+			'ls %s | grep exp%d.run' % (SVM_OPTIMIZATION_DIR, exp)
+		).read().split()
+
+		# independantly rescore and rank these parameter settings
+		rescored_params['exp%d' % exp] = rescore_svm_params(fnames, exp)
+
+	write_fh.write(json.dumps(rescored_params, indent=2))
+	write_fh.close()
+
+
+def rescore_svm_params(fnames, exp):
 	# read all simulated annealing results.  Take the best 5 from each.
 	top_params = []
 	for fname in fnames:
@@ -66,7 +80,13 @@ def find_best_svm_params(write_fname=BEST_PARAMS_FNAME):
 	# for better performance, use the same function that was designed for
 	# testing in simulated annealing (it loads the data vectors into memory
 	# only once)
[…]

### 2015-01-20 src/new_plots.py
add new supplementary plot

@@ -418,7 +418,7 @@ def plot_theta_supplementary(
 			ax.set_xticks(map(lambda x: x + width/2. + eps, range(5)))
 			ax.tick_params(axis='x', colors='0.25')
 			xlabels = [
-				r'$task1$', r'$frame1$', r'$echo$', '$task2$', '$frame2$'
+				r'$intertask$', r'$frame$', r'$echo$', '$intertask$', '$frame$'
 			]
 			ax.set_xticklabels(xlabels, rotation=45, size=12,
 				horizontalalignment='right', color='k')
@@ -431,7 +431,7 @@ def plot_theta_supplementary(
 			ax.set_ylabel(r'$D^-_\mathrm{L1}$', size=12)
 
 		left = 4.7
-		height = 0.59
+		height = 59
 		plot_label = plot_labels[i]
 		ax.text(left, height, plot_label, 
 			va='top', ha='right', size=16, color='0.55')

### 2015-01-22 docs/publications/2014.09_SCIENCE/man.tex
revisions to manuscript -- lots of work on supplementary material

@@
 \begin{sciabstract}
-
-Faced with the ever-growing scale and complexity of data, academic and 
-industrial researchers are increasingly relying on \textit{human computation} 
-to extract useful knowledge.  Microtask
-platforms, like Amazon Mechanical Turk, act like a human compute cluster,
-making it possible to access human cognition quickly and inexpensively. 
-This has lead to their broad adoption by social and computer scientists.  
-Human computation is being used experimentally in applications
-where expert opinion would normally be sought, such as in reviewing 
-medical images.
-Here we show that the repeated performance of similar tasks, an inherent
-feature of microtask and crowdsourcing platforms, acts as a strong
-and largely unexplored source of bias.  The effects that earlier tasks exert
-on later ones are more severe than effects caused by framing, 
-such as by disclosing a task's purpose.  
-Using image-labeling, the canonical microtask, we show that prior 
-tasks influence the content that workers chose to focus on, as well as the 
-richness and specialization of their vocabulary.    
-While intertask effects can be a source of systematic bias, our
-results suggest that with appropriate task-engineering, it might be possible
-to leverage intertask effects to hone worker focus and specificity, helping
-to elicit reproducible, expert-level judgments.
+Microtask platforms have become commonplace tools for obtaining human 
+annotations for large datasets.  Such platforms connect requesters 
+(researchers or companies) with large populations (crowds) of workers, who 
+will individually complete small information-processing jobs, each taking 
+typically between one to five minutes.  
+A major challenge in using such platforms, 
+and a topic of ongoing research, concerns designing jobs that elicit high 
+quality annotations. Here we identify a feature of nearly all crowdsourcing 
+jobs that can act as a strong and systemic source of bias in annotations 
+produced by workers. Specifically, many microtask jobs consist of a sequence 
+of tasks which share a common format (e.g., label pictures, identify people, 
+circle galaxies). Using image-labeling, a canonical microtask job format, we 
+discover that earlier tasks shift the distribution of future answers by 
+30-50\%, irrespective of the images used. 
+Moreover, we show that prior tasks influence 
+the content that workers chose to focus on, as well as the richness and 
+specialization of their word choice. While these intertask effects can be a 
+source of systematic bias, our results suggest that, with appropriate job 
+design, it might be possible to leverage these biases to hone worker focus 
+and specificity, helping to elicit reproducible, expert-level judgments.
+
+%Faced with the ever-growing scale and complexity of data, academic and 
+%industrial researchers are increasingly relying on \textit{human computation} 
+%to extract useful knowledge.  Microtask
+%platforms, like Amazon Mechanical Turk, act like a human compute cluster,
+%making it possible to access human cognition quickly and inexpensively. 
+%This has lead to their broad adoption by social and computer scientists.  
+%Human computation is being used experimentally in applications
+%where expert opinion would normally be sought, such as in reviewing 
+%medical images.
+%Here we show that the repeated performance of similar tasks, an inherent
+%feature of microtask and crowdsourcing platforms, acts as a strong
+%and largely unexplored source of bias.  The effects that earlier tasks exert
+%on later ones are more severe than effects caused by framing, 
+%such as by disclosing a task's purpose.  
+%Using image-labeling, the canonical microtask, we show that prior 
+%tasks influence the content that workers chose to focus on, as well as the 
+%richness and specialization of their vocabulary.    
+%While intertask effects can be a source of systematic bias, our
+%results suggest that with appropriate task-engineering, it might be possible
+%to leverage intertask effects to hone worker focus and specificity, helping
+%to elicit reproducible, expert-level judgments.
 \end{sciabstract}
@@
 
-These platforms allow requesters to make use of human intelligence
-\textit{algorithmically}.  Tasks are posted and results fetched by transfering
-files over the Internet, making it possible to embed microtask work in an
-automated process.  To the surrounding process, workers seem like 
-input-output devices, which provides much of the flexibility and 
-cost-savings of actually automating the work: the workforce is available
-on demand, over the Internet, without any contracts or interviews, at a rate
-of about 6 USD\$/ hr.  Many kinds of work can be performed at a fraction of 
-the cost that would otherwise be required, either to recruit temporary 
-workers, or to research and design a sophisticated automated solution.
+Microtask platforms enable a workflow in which workers are like 
+input-output devices.  This provides much of the flexibility and 
+cost-savings of fully automating the work in a computer program: 
+the workforce is available on demand over the Internet using automated 
+scripts, and  no contracts or interviews are required.  Many tasks can be
+can be performed at a fraction of the cost of recruiting temporary workers.
 
@@
 and for marketing activities, such as running focus groups, writing product 
-reviews,
-and moderating website content.  Academia turns to microtask workers as 
-a way to recruit study participants, and to annotate datasets, for example,
-to provide ground-truth in training artificial intelligence systems.
-
-Given the increasing prevalence of microtask-based methods, there
-is a desire to understand the factors affecting the reliability of microtask
-platforms.  Researchers have investigated task-design parameters such as the 
+reviews, and moderating website content.  
+Academia turns to microtask workers as a way to recruit study participants, 
+and to annotate datasets, for example, to provide ground-truth in training 
+artificial intelligence systems.
+
+Given their increasing prevalence, there
+is a desire to understand the factors affecting the reliability of 
+microtask-based methods.  Researchers have investigated task-design 
+parameters such as the 
 level of pay \cite{kazai2013analysis}, the training and pre-screening of 
@@
 might be assigned a set of ten images, and asked to provide descriptive words 
-(or \textit{labels}) for each.  On MTurk, these bundles are called Human 
+(or \textit{labels}) for each.  On one popular microtask platforms,
+Amazon's Mechanical Turk (MTurk), these bundles are called Human 
 Intelligence Tasks (HITs), but for the sake of clarity, we will use 
@@
 example of a basic psychological phenomenon impacting crowdsourced data,
-and raises a serious question about what other cognitive biases might
+and raises questions about what other cognitive biases might
 affect microtask work, and how prevelant induced bias might be.
 
-We therefore turn to the question of bias induced by taks-repetition effects, 
-which, if present, would impact virtually every microtask workflow.
+Here we investigate the potential for task-repetition to induce bias in 
+microtask-based work.  If such bias is present, it would impact virtually 
+every microtask and crowdsourced workflow.
 The results we present here show that a worker's response during a task
 does indeed depend strongly on the tasks performed beforehand.   
-We call the effects that earlier tasks exert on later ones 
+We call these effects that earlier tasks exert on later ones 
 \textit{intertask effects}.
@@
 outputs depend on the history of their inputs.  Reproducibility and 
-path-independance are crucial for properties for the basic components in a 
-computing architecture, so it will be necessary to understand the 
-computational ramifications of these psychological phenomena to further this 
-interesting line of investigation.
+path-independance are crucial properties of the components in a 
+computing architecture, so it to maintaning the view of the HPU computing 
+architecture, necessitates a better understanding of the computational 
+ramifications of many psychological phenomena.
 
@@
 asked to provide a qualitative free-text response to a prompt.  
-This includes such such examples as describing
+This includes such examples as describing
 video and audio recordings, summarizing texts, or providing personal 
@@
 were again asked to provide five labels.  Five initial 
-tasks, together with the test tasks, comprised one HIT 
-(\# workers were only allowed to participate once). During the HIT, workers 
+tasks, together with the test tasks, comprised one HIT\footnote{
+	Workers were only allowed to participate in one HIT of a single treatment 
+	of a single experiment.
+}. During the HIT, workers 
 were presented images one at a time, and, crucially, we made no 
@@
 The extent of bias is then defined by the difference in the response 
-distribution for different treatments of workers
-(\# this is a general divergence metric between probability 
-distributions known as the \textit{total variation distance}):
+distribution for different treatments of workers\footnote{
+	This is a general divergence metric between probability 
+	distributions known as the \textit{total variation distance.}
+}:
 \begin{equation}
@@
 It is important to emphasize that a significant result from a $\chi^2$ test 
-only allows us to conclude that $\theta$ is non-zero.  Determining $\theta$ from finite samples of 
+only allows us to conclude that $\theta$ is non-zero 
+(see the supplementary text).  
+Determining $\theta$ from finite samples of 
 responses, using purely statistical approaches, is difficult (\#), which 
@@
 been?  Intuitively, the greater the effect that prior tasks have on subsequent
-responses, the more accurate the classifier can be.  Formally, as we show
-in the supplementary text, the accuracy of such a classifier, $\eta$,
+responses, the more accurate the classifier can be.  Formally (as shown
+in the supplementary text), the accuracy of such a classifier, $\eta$,
 yields a lower bound on the bias:
@@
 
-Using a na\"ive Bayes classifier (\# in the 
-supplementary material we discuss the choice of classifier, the
-approach to measuring accuracy, and draw a comparison to the results obtained 
-if a support vector machine is used), we found that intertask effects 
+Using a na\"ive Bayes classifier\footnote{
+	We discuss our choice of classifier and preprocessing methods, 
+	and show similar results obtained by using a support vector 
+	machine, in the supplementary material.
+}, we found that intertask effects 
 lead to a 30\% bias between workers from the \textit{food} and 
@@
 the \textit{extent} of framing-induced bias we found was statistically 
-insignificant (\td{insert p-value})
-(see Fig.~\ref{fig:theta}).  This suggests 
+insignificant ($p =0.37$) (see Fig.~\ref{fig:theta}).  This suggests 
 that prior task exposure is a stronger priming modality than framing.
@@
 treatments, included images depicting meals of identifiable cultural 
-origin (\# the initial tasks in 
-\textit{intertask-food-culture} are arguably also of identifiable cultural 
-origin, but this would tend to reduce, rather than inflate, our results
-(we discuss this further in the supplementary material).)
+origin\footnote{
+	Though we attempted to choose more globalized foods, the initial tasks 
+	in \textit{intertask-food-culture} are arguably still of
+	identifiable cultural origin. This would tend to reduce, rather than 
+	inflate, the bias observed in our results 
+	(we discuss this further in the supplementary text).
+}
 (see Fig.~\ref{fig:task}F).
@@
 Results for this experiment again showed a 
-strong bias as a result of intertask effects (about 50\%) 
+strong bias as a result of intertask effects ($\theta$~about 50\%) 
 (see Fig.~\ref{fig:theta}A).  Again, we compared intertask effects to 
@@
 difference between the labels attributed by the \textit{food} and 
-\textit{culture} treatments during test tasks (see Fig.~\ref{fig:theta}).
+\textit{culture} treatments during test tasks ($p=0.29$) 
+(see Fig.~\ref{fig:theta}).
 
@@
 workers actually used significantly \textit{fewer} food-related words 
-during test tasks
-(\# food related words were identified using the wordnet corpus, augmented
-with additional words obtained by crawling a recipe website (see supplementary
-information for details)) (see Fig.~\ref{fig:specificity}).  This finding
+during test tasks\footnote{
+	food-related words were identified using the wordnet corpus, 
+	augmented with additional words obtained by crawling a recipe website 
+	(see supplementary information for details)
+} (see Fig.~\ref{fig:specificity}).  This finding
 rules out a seemingly-simple idea that workers emphasize
@@
 reference to food, that is, the number of \textit{unique} food-related words
-used.  Even if workers provide an abundance of food-related words, if the 
-same words are often repeated, there will be less diversity.  
+used.  Even if workers provide an abundance of food-related words, there
+can be less diversity if the same words are often repeated.  
 This could happen, for example, if workers use generic references 
@@
 notion of word specialization.  Wordnet provides a set of hypernym-hyponym 
-relations between \# English nouns.  Hypernyms are generalizations 
+relations between 117,798 English nouns (\#).  Hypernyms are generalizations 
 (for example, ``bread'' is a hypernym for 
@@
 where one treatment's words were more specialized than the other, as a 
-percentage of the total (see Fig.~\ref{fig:specificity}B) (\# full detail for 
-this calculation is provided the supplementary text).
+percentage of the total 
+(see Fig.~\ref{fig:specificity}B) 
+(details for this calculation are in the supplementary text).
 
@@
 used significantly more specialized words than their non-food-primed 
-counterparts (about 15\% more; see Fig.~\ref{fig:specificity}C).
+counterparts (about 15\% more) (see Fig.~\ref{fig:specificity}C).
 It is interesting that such substantial increases in both the lexical 
@@
 \section*{Supplementary Material}
-
-\subsection*{S1: Experimental materials}
-The tasks for both experiments were presented as a series of slides.  In
-both cases, the first slide consisted of a brief set of instructions, followed
-by the frame if shown (only some treatments involved a frame), see 
-Fig. S\ref{fig:hit_preamble}.  Following the instructions and prime, a set
-of initial tasks was shown (except for the treatments in \textit{frame2}
-and \textit{echo1}) followed by (in all cases) a set of test tasks.  In
-\textit{exp1}, two kinds of frame were used, one simple frame, and one where
+\renewcommand{\figurename}{Figure S\!\!}
+\renewcommand{\tablename}{Table S\!\!}
+\setcounter{figure}{0}
+\setcounter{table}{0}
+
+\subsection*{Materials and Methods}
+
+\paragraph{Microtask setup.}
+Altogether the experiments presented here consisted of data from 3200 HITs 
+(bundles of 10-image labeling tasks).  In all experiments, each treatment
+consisted of results from at least 119 workers.  
+For the purpose of statistical calculations,
+treatments having more than 119 workers were subsampled, producing a uniform
+sample size accross all treatments.  The \textit{food} and \textit{objects}
+treatments in the \textit{intertask-food-objects} experiment were further
+broken down into sub-treatments (each containing at least 119 workers),
+corresponding to different orderings of the test tasks.  These alternative
+orderings were obtained by rotation of the test tasks 
+(i.e. moving all tasks forward by one position, and making the last task 
+become the first test task).  This ensured that each test task appeared in
+each of the five test-task positions.
+
+The HITs (as defined in the main text) for all treatments were presented as 
+a series of slides.  The first 
+slide consisted of a brief set of instructions.  In framing-treatments, a 
+framing slide was shown immediately after the instructions, see 
+Fig. S\ref{fig:hit_preamble}.  In intertask-treatments, a set of initial
+tasks were presented (and no framing slide).  Following the
+framing slide or initial tasks, the test-tasks were presented.
+
+All initial and test tasks had the format shown in 
+Fig.~S\ref{fig:hit_preamble}: an image taking up most of
+the task pane, with five text inputs and a ``next'' button.  Images were
+presented in this way, one at a time. 
+For treatments having initial tasks, the test
+tasks followed seemlessly, and no distinction was made between the test 
+tasks and the initial tasks.
+
+In an attempt to increase the strength of framing, we included the
+\textit{echo-food-objects} treatment, in which, during the framing slide,
 the worker was required to echo the frame using a combo-box input.  The
-instructions, both kinds of frame, and an example task slide, are shown 
-in Fig. S1.
+instructions, both kinds of framing slide (simple and echoed), 
+and an example task slide, are shown 
+in Fig.~S\ref{fig:hit_preamble}.
+
+Given the setup described above, the only tasks that workers in framing 
+treatments perform are the test tasks, whereas in the 
+intertask-treatments, the test tasks were performed as tasks
+5 through 10.  
+It could be argued that a better comparison would be achieved
+by having all workers perform some initial tasks, and simply ensuring that
+the initial tasks are \textit{not} varied between framing treatments. 
+We took this approach in the experiment 
+\textit{frame-food-culture}, in which workers performed the same 
+initial tasks containing images that depicted food in both the \textit{food}
+and \textit{culture} treatments.  If anything, this appears
+to have reduced the strength of framing for that experiment.
+
 \begin{figure}
 	\includegraphics[scale=0.8]{figs/tasks.pdf}
-	\label{fig:hit_preamble}
 	\caption{Examples of A) instructions; B) a frame, as shown in 
@@
 	}
+	\label{fig:hit_preamble}
 \end{figure}
 
-All of the initial tasks had the format shown in Fig. S1D.  The images used
-in the initial tasks for \textit{task1:food} and \textit{task1:obj} are
-shown in Fig. S2 and S3, and the images used in the test tasks for 
-\textit{exp1} are shown in Fig. S4.  The images used in the initial tasks
-for \textit{task2:food} and \textit{task2:cult} are shown in Fig. S5 and
-Fig. S6 respectively, and the images used in the test tasks for \textit{exp2} 
-are shown in Fig. S7.
+\paragraph{Selection of images.}
+
+The images used in the initial tasks for \textit{intertask-food-objects}  
+are shown in Figs.~S\ref{fig:task1:food} (\textit{food} treatment) and 
+S\ref{fig:task1:obj} (\textit{objects} treatment).
+We selected images for the initial tasks that show either food or objects, 
+according to the treatment in which they were used.  
+We took care to exclude objects from
+the food-images (except in some cases a dish supporting the food), and 
+to exclude food from the object-images.  The images used for the test tasks
+of \textit{intertask-food-objects} and \textit{frame-food-objects} are shown 
+in Fig.~S\ref{fig:task1:test}.
+
+The images used in the initial tasks
+for \textit{intertask-food-culture} are shown in Figs.~S\ref{fig:task2:food} 
+(\textit{food} treatment) and S\ref{fig:task2:cult} 
+(\textit{culture} treatment).
+We selected the initial images for the treatments of this experiment to 
+respectively reflect depict food and culture.
+
+Naturally, since food is a very
+important aspect of culture, pictorial depictions of the two concepts 
+cannot be cleanly separated,
+and images depicting food inevitably also depict culture.
+The fact that the inital-task images for the food treatment of 
+\textit{intertask-food-culture} do also depict culture
+will only tend to make them more similar to those from the \textit{culture}
+treatment, which would tend to \textit{reduce} the severity of intertask 
+effects.  In any case, since we still found strong intertask effects, 
+the presence of culture in the food-related initial images of 
+\textit{intertask-food-culture} does not seem to have been problematic.
+The images used in the test tasks of \textit{intertask-food-culture} and
+\textit{frame-food-culture} are shown in Fig.~S\ref{fig:task2:test}.
 
@@
 	\includegraphics{figs/task1-food.pdf}
+	\caption{
+		Images used in the initial tasks for the
+		\textit{food} treatment of \textit{intertask-food-objects}.  
+		The numbers show the order in which the 
+		images were presented to workers.
+	}
 	\label{fig:task1:food}
-	\caption{
-		Figure S2: Images used in the initial tasks for 
-		\textit{task1:food}.  The numbers show the order in which the 
-		images were presented to workers.
-	}
 \end{figure}
@@
 	\includegraphics{figs/task1-obj.pdf}
+	\caption{
+		Images used in the initial tasks for the
+		\textit{objects} treatment of \textit{intertask-food-objects}.  
+		The numbers show the order in which the images were presented to 
+		workers.
+	}
 	\label{fig:task1:obj}
-	\caption{
-		Figure S3: Images used in the initial tasks for 
-		\textit{task1:obj}.  The numbers show the order in which the 
-		images were presented to workers.
-	}
 \end{figure}
@@
 	\includegraphics{figs/task1-test.pdf}
+	\caption{
+		Images used in the test tasks for \textit{intertask-food-objects}
+		and \textit{frame-food-objects}.  
+		The numbers show the order in which the 
+		images were presented to workers in \textit{frame-food-objects};
+		in \textit{intertask-food-objects}, five different orderings were
+		used, which can be obtained by taking the numbers shown, $n$,
+		and replacing them by $n + c \bmod 5$ for $c$ running from 0 to 4.
+	}
 	\label{fig:task1:test}
-	\caption{
-		Figure S2: Images used in the test tasks for 
-		\textit{exp1}.  The numbers show the order in which the 
-		images were presented to workers.
-	}
 \end{figure}
@@
 	\includegraphics{figs/task2-food.pdf}
+	\caption{
+		Images used in the initial tasks for the
+		\textit{food} treatment of \textit{intertask-food-culture}.  
+		The numbers show the order in which the 
+		images were presented to workers.
+	}
 	\label{fig:task2:food}
-	\caption{
-		Figure S2: Images used in the initial tasks for 
-		\textit{task2:food}.  The numbers show the order in which the 
-		images were presented to workers.
-	}
 \end{figure}
@@
 	\includegraphics{figs/task2-cult.pdf}
+	\caption{
+		Images used in the initial tasks for the
+		\textit{culture} treatment of \textit{intertask-food-culture}.  
+		The numbers show the order in which the 
+		images were presented to workers.
+	}
 	\label{fig:task2:cult}
-	\caption{
-		Figure S2: Images used in the initial tasks for 
-		\textit{task2:cult}.  The numbers show the order in which the 
-		images were presented to workers.
-	}
 \end{figure}
@@
 	\includegraphics{figs/task2-test.pdf}
+	\caption{
+		Images used in the test tasks for \textit{intertask-food-culture} 
+		and \textit{frame-food-culture}.  
+		The numbers show the order in which the 
+		images were presented to workers.
+	}
 	\label{fig:task2:test}
-	\caption{
-		Figure S2: Images used in the test tasks for 
-		\textit{exp2}.  The numbers show the order in which the 
-		images were presented to workers.
-	}
 \end{figure}
 
-\subsection*{S2: Access to raw data and code}
-The raw data and source code needed to reproduce the analyses 
-shown here and in the main text can be downloaded from 
-http://networkdynamics.org/publications/public/priming2014.09.
-
-\subsection*{S3: Additional results not shown in the main text}
-\paragraph{Testing intertask and framing effects using 
-	Pearson's $\chi^2$ test of homogeneity.
-}
+\subsection*{Testing for intertask and framing effects using $\chi^2$}
 To test whether intertask and framing effects induced statistically 
 significant changes in word frequencies, we assembled a contingency table
-for each experiment, containing the frequencies of words in each treatment
-for a given experiment.  Any words that appeared less than 10 times for
-an experiment (i.e. appearing less than 5 averaged over each treatment)
+for each experiment, containing the frequencies of words in each treatment.  
+Any words that appeared less than ten times for
+an experiment (i.e. appearing less than five times averaged over each 
+treatment)
 were lumped together into a separate `OTHER' category, to ensure validity
@@
 then calculated according to Pearson's $\chi^2$ test, using 
-Yate's correction.  Results are tabulated in Table~\ref{table:chi2}.
-All experiments showed significant changes in word-frequencies in response
+Yate's correction.  Results are tabulated in Table~S\ref{table:chi2}.
+With the exception of \textit{frame-food-culture}, all experiments showed s
+ignificant changes in word-frequencies in response
 to the task or framing exposures, at $\alpha=0.05$, leading us to 
 reject the null hypothesis that the priming exposures had no effect.
-Note, however, that while the other tests showed very high significance, 
-\textit{frame-food-culture} was marginally significant.  This is consistent 
-with our finding weak effects for \textit{frame-food-culture}, throughout our 
-results.
 
@@
 and half in another, there can be a significant non-homogeneity between the 
-two halves, when tested using Pearson's $\chi^2$ test.  Thus, finding two
-corpuses to be different might simply be an artifact of the corpus' own
-inhomogeneity.
-
-We don't expect this to be a concern in our case, because the ``texts'' are 
+two halves, when tested using Pearson's $\chi^2$ test.  Thus, it has 
+been argued that finding two
+corpuses to be different according to a $\chi^2$ test might simply be an 
+artifact of the corpus' own inhomogeneity.
+
+This concern does not apply to our case, because the ``texts'' are 
 individual responses from workers, which will not, in general, be subject to 
-the burstiness phenomenon.  But to test this, we randomly divided the workers 
+the burstiness phenomenon.  Nevertheless, to test this, 
+we randomly divided the workers 
 from each experimental treatment into two sets, and tested the homogeneity 
-between these sets.  Results are tabulated in Table~\ref{table:chi2_within}, 
+between these sets.  Results are tabulated in Table~S\ref{table:chi2_within}, 
 and show that treatments 
@@
 \noalign{\smallskip}
+\noalign{\smallskip}
 \multirow{2}{*}{\textit{frame-food-objects}} & \textit{food} & 67 & 41.3 & $0.99$\\
  & \textit{objects} & 62 & 66.9 & $0.31$\\
+\noalign{\smallskip}
 \noalign{\smallskip}
@@
 \noalign{\smallskip}
+\noalign{\smallskip}
 \multirow{2}{*}{\textit{intertask-food-culture}} & \textit{food} & 62 & 65.9 & $0.34$\\
@@
 \noalign{\smallskip}
+\noalign{\smallskip}
 \multirow{2}{*}{\textit{frame-food-culture}} & \textit{food} & 57 & 49.6 & $0.75$\\
  & \textit{culture} & 64 & 55.1 & $0.78$\\
+\noalign{\smallskip}
 \noalign{\smallskip}
@@
 
-\paragraph{Most suppressed / activated terms.}
-The words whose frequencies differed most between the treatments of given 
-experiments are shown in Table~\ref{table:top-words}.  Note that 
-the word that was most suppressed in food-exposed treatments was always 
-``food''.
-
-\begin{table}
-	\centering
-	\setlength{\tabcolsep}{10pt}
-	\begin{tabular}{ c c c c c }
-
-		\setlength{\tabcolsep}{4pt}
-		\begin{tabular}{ r | c }
-		\toprule
-		\multicolumn{2}{c}{\textit{task1}} \\
-		\toprule
-		coffee & 38 \\
-		meal & 34 \\
-		cheese & 34 \\
-		apple & 32 \\
-		dessert & 21 \\
-		cup & -30 \\
-		glass & -45 \\
-		table & -70 \\
-		candle & -74 \\
-		food & -80 \\
-		\bottomrule
-		\end{tabular}
-
-&
-
-		\setlength{\tabcolsep}{4pt}
-		\begin{tabular}{ r | c }
-		\toprule
-		\multicolumn{2}{c}{\textit{frame1}} \\
-		\toprule
-		bread & 18 \\
-		wine & 18 \\
-		cheese & 16 \\
-		apple & 14 \\
-		oil & 12 \\
-		table & -9 \\
-		meal & -10 \\
-		candle & -12 \\
-		dinner & -13 \\
-		food & -32 \\
-		\bottomrule
-		\end{tabular}
-
-&
-
-		\setlength{\tabcolsep}{4pt}
-		\begin{tabular}{ r | c }
-		\toprule
-		\multicolumn{2}{c}{\textit{echo1}} \\
-		\toprule
-		apple & 24 \\
-		cheese & 23 \\
-		wine & 15 \\
-		coffee & 14 \\
-		oil & 7 \\
-		knife & -24 \\
-		dinner & -26 \\
-		fork & -27 \\
-		candle & -35 \\
-		food & -55 \\
-		\bottomrule
-		\end{tabular}
-
-&
-
-		\setlength{\tabcolsep}{4pt}
-		\begin{tabular}{ r | c }
-		\toprule
-		\multicolumn{2}{c}{\textit{task2}} \\
-		\toprule
-		spicy & 26 \\
-		sauce & 17 \\
-		indian & 15 \\
-		buffet & 14 \\
-		exotic & 12 \\
-		festival & -11 \\
-		offering & -12 \\
-		statue & -15 \\
-		india & -20 \\
-		food & -56 \\
-		\bottomrule
-		\end{tabular}
-
-&
-
-		\setlength{\tabcolsep}{4pt}
-		\begin{tabular}{ r | c }
-		\toprule
-		\multicolumn{2}{c}{\textit{frame2}} \\
-		\toprule
-		indian & 11 \\
-		banquet & 8 \\
-		spicy & 7 \\
-		asian & 6 \\
-		variety & 6 \\
-		delicious & -6 \\
-		meat & -7 \\
-		festival & -7 \\
-		spice & -7 \\
-		food & -9 \\
-		\bottomrule
-		\end{tabular}
-
-	\end{tabular}
-	\caption{
-		Top 5 words, used to label the first test image, whose usage frequency
-		increased or decreased the most between treatments of given 
-		experiments.  Positive values indicate that the food-exposed treatment
-		used the word with higher frequency.  Word frequencies for 
-		\textit{intertask-food-objects} are aggregated across 5 
-		permutations, and hence tend to show larger absolute differences.
-	}
-	\label{table:top-words}
-\end{table}
-
-\subsection*{S4: Data preprocessing}
-	\paragraph{Splitting, Lemmatization, removal of stop-words, and 
-		addition of position tags.}
-
-	Before performing any analysis on the labels that workers provided, we
-	performed a series of preprocessing steps.  
-	Labels that contained
-	multiple words (separated by spaces or punctuation) were split, with
-	punctuation removed, and the separated words were treated as distinct 
-	features in subsequent analysis.
-	Misspelled words were automatically corrected using a spelling 
-	correction algorithm described below.  
-	Next, words were lemmatized using the
-	wordnet lemmatizer \cite{miller1995wordnet,felbaum1998wordnet}.  
-	Common words such as ``the'', ``to'', or ``with'', were found using the
-	the NLTK's English stop-word list and removed \cite{loper2002nltk}.
-
-	For the purpose of training and testing a na\"ive Bayes classifier, we 
-	performed an additional preprocessing step.  We tagged words with the
-	position in which they had been entered (i.e. which of the five text 
-	inputs in the task interface) as well as the test tasks in which the word 
-	had been provided.
-	So, if the word ``wine'' was entered into the second text-input for 
-	the third test-task, after preprocessing, the feature ``3\_2\_wine'' would
-	appear.  Prepending the task number onto words was simply a means to 
-	retain correct attribution, which itself was essential since providing a
-	word during one task is not equivalent to providing the same word during 
-	another task.
-
-	\paragraph{Spelling correction.}  
-	Spelling correction was performed using an algorithm that first detected
-	if a word was likely to be misspelled, then generated a set of candidate 
-	corrections, and chose the best candidate based on a scoring mechanism.
-
-	A word was considered misspelled if it was not contained in the 
-	\textit{legal set}, which was formed by the union of
-	the wordnet corpus, the stop-word list, and a set of words seen while 
-	crawling the world food section of the allrecipes.com website.  We
-	describe the crawling of the allrecipes.com website in a section below.
-
-	To correct misspellings, we first produced all possible modified forms 
-	that could be obtained applying one or two edits.  An edit consisted of 
-	adding or removing a letter, changing one letter into another, or 
-	swapping the positions of two adjacent letters.  For the purpose of these 
-	edits, spaces were treated as any other letter.
-
-	The candidates produced by these edits which were in the legal set were
-	then ranked based on a scoring mechanism, and the highest scoring word
-	was chosen as the correction.  A candidate $w$'s score, $s_w$, was 
-	calculated according to the following formula:
-	\begin{equation}
-		s_w = (f_w + 1) * p_1 * p_2,
-	\end{equation}
-	where $f_w$ is the frequency with which the word occurred (correctly 
-	spelled)
-	within the given task, $p_1$ was a penalty for the first edit, and
-	$p_2$ was a penalty for the second edit.  If the word was made using only
-	one edit, then $p_2 = 1$.  Any edit that did not involve adding a space
-	(i.e. separating a word) incurred a penalty of 0.5, while the addition of
-	a space incurred a penalty of 0.1.  Word-separation edits were more 
-	strongly penalized because it is often possible to split a series of 
-	letters into many short two- or three-letter words, which otherwise leads 
-	to many erroneous corrections.  We found that setting the penalty for
-	word splitting at 0.1 worked well by testing on words taken from
-	initial tasks.
-
-	After all of our analyses had been performed, we checked the accuracy of 
-	the spelling correction algorithm using three human coders.  The coders
-	were shown a set of 
-	500 words that were randomly sampled from the labels attributed during 
-	test tasks (50 for each test task).  Before sampling, the labels from all
-	experimental treatments, for the given test task, were pooled together.
-	The coders did not know which treatment any given word came from.  
-	In addition to the words, coders were shown the spelling correction 
-	produced by the algorithm, as well as the image from the test task.
-	The coders were asked to identify any misspelled words which had not 
-	been corrected, as well as any corrections that appeared to be erroneous,
-	by indicating their own correction.
-
-	Based on this exercise, we found that, according to the human coders,
-	17\% of the words were misspelled, but that after applying the 
-	automated spelling correction, only 3.2\% of words were misspelled.
-
-	\paragraph{Crawling the world food section of allrecipes.com.}
-	The website allrecipes.com was accessed on 3-4 November 2014 using 
-	automated scripts.  A total of 2642 recipe listings and 15621 recipe
-	instruction pages were retrieved.  Recipe listings were pages that 
-	provided lists of recipes, and contained a title and short description 
-	for each.  
-	The recipe instruction pages had lists of ingredients and preparation 
-	instructions.  All of the words found in recipe titles, short
-	descriptions, ingredients lists, and preparation instructions were
-	collected, and saved as an auxiliary set to augment the \textit{legal set}
-	used in spelling correction.
-
-\subsection*{Determination of $\theta$}
-
-\subsection*{S5: Identification of food-related terms}
-The wordnet corpus is composed of synsets, which are particular senses 
-(meanings) and a set of word forms bearing that meaning. A given word form, 
-such as ``ring'' has multiple senses (``to ring a bell'', ``a wedding ring''), 
-and so can be part of many synsets.  Since the wordnet corpus was designed
-to carry semantic information, the synset is the basic organizing element
-of wordnet.
-
-We chose the synsets \texttt{food.n.01} and \texttt{food.n.02} to act as roots
-in defining which words should be considered food-related.  Any word form
-belonging to a synset which was a hyponym of one of the two root synsets
-identified above was considered to be a reference to food.  Here, as in the
-main text, when we say hyponym, we mean either a direct hyponym, or a hyponym
-of a hyponym, and so on.
-
-This is a stringent notion of a word being a food reference.  It roughly
-corresponds to whether or not a given thing is reasonably considered 
-consumable.  So, ``orange'' is food, but ``salty'' is not.  Although ``salty''
-would usually qualify something edible, it is not itself an edible thing.
-On the other hand, ``salt'' would be considered a reference to food under 
-this operationalization.
-
-The subset of the wordnet corpus induced by the hyponyms of \textit{food.n.01}
-and \textit{food.n.02} provide a set of 3590 words.  Manual
-testing showed good coverage, except for references to ethnic foods.  
-Since, especially in \textit{exp2}, we had images containing many ethnic 
-foods, we decided to augment the wordnet corpus with words learned by 
-crawling the world food section of the allrecipes.com website.
-
-After collecting a set of words using an automated script 
-(described above), we collected the set of words that had been used by
-workers and which had been seen during crawling of the allrecipes.com website,
-but which were not included in wordnet.  We grafted these extra words into
-the wordnet hyponym-hypernym graph manually, which ensured that any references
-to ethnic words learned from crawling would be properly classified as 
-food references.
-
-\paragraph{Validation of the detection of food references.}
-To determine whether our extended version of wordnet provided a good approach
-to detecting food-related words, we sampled 500 words 
-(50 from each test task)  from the set of labels produced by workers and had 
-three human coders manually decide if they were 
-food-related or not.
-
-The coders were instructed to consider whether a word was a noun signifying
-an edible item.  The guiding principle was, for the coder to ask herself,
-``can I eat X'', where X is the word she is coding.  The coders were
-shown the used in the task from which the word came, to help resolve ambiguity
-in the sense of the word that had been given.  Coders were also shown the 
-spelling correction (if any) that the spell-correction algorithm had made,
-to help interpret misspelled words.
-
-We evaluated the food detection algorithm in two ways.  First, we measured
-the inter-rater reliability between the three human coders and the algorithm
-(treating the algorithm just like any other coder).  Second, adopting the 
-majority code given by the human coders, we determined the accuracy of the
-food-detection algorithm.  Data summarizing this validation process are given
-in table S1.
-
-\begin{table}
-\centering
-\setlength{\tabcolsep}{12pt}
-\begin{tabular}{ r | c }
-\toprule    
-\# terms coded & 500 \\
-\# food references & 130 \\
-\# correct machine codes & 440 \\
-inter-rater reliability & 82.4\% \\
-human-machine code agreement & 88\% \\
-%machine recall & 80 \% \\
-%machine precision & 75.4 \% \\
-%machine code F1 & 0.78 \\
-\bottomrule
-\end{tabular}
-\caption{\footnotesize{
-	\td{remove the automatic numbering}. Table S1. Results for the validation 
-	of the automatic detection of food references, by comparison to
-	human-generated coding on randomly sampled words.  In calculating the 
-	human-machine code agreement, the majority human code was used.
-	Inter-rater reliability was calculated as Krippendorff's alpha.
-}}
-\end{table}
-
-The results show that good inter-rater reliability was achieved during the
-validation (82.4\%).  Looking at the agreement between the 
-machine codes and the majority human-generated codes, we find they agree
-88\% of the time.  This means that the concept used to instruct human coders
-provides a good approximation to what the wordnet-based machine codes actually
-represent. In other words, the machine codes correspond closely to indicating
-which words correspond to nouns that refer to edible things, and which ones
-do not, which provides a clear and simple interpretation for the machine
-coding of food and non-food words.
-
-\subsection*{S6: Calculation of relative specificity}
-In the main text we present results for the relative specificity of labels
-produced by two experimental treatments.  In performing this calculation,
-we used the wordnet corpus, which has a set of hypernym-hyponym relationships
-as described in the main text.  The first step in performing this calculation
-was therefore to map the words occurring from (the labels of) a given 
-experimental treatment onto the wordnet synsets.  In general, a given word
-form can have multiple meanings, and therefore maps onto multiple wordnet 
-synsets.
-
-The result of mapping the words from two treatments onto the wordnet 
-hypernym-hyponym graph two sets of counts, one set per treatment, 
-indicating the number of times a word from a given synset occurred among the
-labels of the treatment.  Then, for every synset in one treatment, we looked
-at the number of synsets in the other treatment that were more generic
-(reachable by following hypernym relations) less the number of words that
-were more specific (reachable by following hyponym relations).  This quantity
-tallied for all words in the original synset gives a (non-normalized) measure
-of the degree to which words from the first treatment are more specific
-than words from the second treatment, overall.  We then normalized this 
-quantity by the total number of possible comparisons between the words of
-one treatment to those of the other, where two words are considered comparable
-only if one word is the hypernym or hyponym of the other.  Hence, ``statue'' 
-and ``bread'' are not comparable, but ``pumpernickel'' and ``bread'' are.
-
-This calculation can be summarized by the following equation:
-\begin{equation}
-	S(P,Q) = \frac{
-		\sum_{w\in P}\sum_{v\in Q} \left(
-			\mathbf{1}_{[w>v]} - \mathbf{1}_{[v>w]} \right)
-	}{
-		\sum_{w\in P}\sum_{v\in Q} \left(
-			\mathbf{1}_{[w>v]} + \mathbf{1}_{[v>w]} \right)
-	},
-\end{equation}
-where $P$ and $Q$ are sets of synsets, and $\mathbf{1}_{[w>v]}$ evaluates
-to 1 if synset $w$ is more specific than (i.e. is a hyponym of) synset $v$.
-This measure counts the excess of cases where synsets from $P$ are more
-specific then synsets from $Q$, as a fraction of all comparable synset pairs.
-
-In computing this quantity between two treatments, we first computed it 
-using the labels attributed to a particular test task, and then
-averaged the result obtained in this way for each of the five test tasks.
-
-\subsection*{S7: Variance and significance tests}
-
-	\paragraph{Variance in the average fraction food-related labels}
-	In the main text, Fig.~\ref{fig:specificity}A shows the difference in 
-	the fraction of food related labels used by workers in from different 
-	treatments.  The error bars show the 95\% confidence intervals around 
-	the estimated difference of means.  It was computed from the
-	observed sample standard deviation in the fraction of food labels given
-	by individual workers.
-
-	\paragraph{Variance in food vocabulary size (lexical richness).}
-	The number of unique words in a text is strongly dependent on the size
-	of the text: as more text is sampled, previously unseen words continue
-	to be found, though at a decreasing rate.  This means that when the 
-	lexical richness is measured for a large and small sample, they are not 
-	actually estimates of the same quantity.  It is not clear that drawing 
-	confidence intervals around the lexical richness measured at one sample 
-	size is meaningful, nor is it easily done.
-
-	However, we can construct a null model based on the hypothesis that
-	two treatment's have the same probability distribution over tokens
-	(and hence the same lexical richness). If treatments $A$ and $B$ have
-	the same word frequency distributions, then, they are samples from
-	the same population.  Pooling the workers from both treatments together,
-	then randomly partitioning them into balanced sets $A'$ and $B'$ will
-	still yield samples from the same underlying population.  By repeating 
-	this pooling and re-partitioning many times, and computing the 
-	relative lexical richness, we can determine the critical difference in
-	lexical richness from the 97.5 and 2.5 percentiles.  We can then test 
-	the hypothesis that $A$ and $B$ were from the same population by 
-	observing whether the difference in lexical richness of the original 
-	sets is within this percentile range.
-
-	We performed this calculation using 1000 pooling and resampling 
-	iterations, and plotted the 97.5 percentile as a star in 
-	Fig~\ref{fig:specificity}B in the main text.  All of the differences
-	in lexical richness were significant except that of \textit{frame2}.
-
-	\paragraph{Variance in food specificity.}
-	The variance in the specificity measurements was calculated using a 
-	bootstrapping procedure.  For two given treatments $A$ and $B$, 
-	119 workers were sampled from each with replacement, giving the bootstrap
-	samples $A'$ and $B'$, and the relative specificity between these 
-	was measured as described in \textsection S6.
-	This was repeated 1000 times.  The 2.5 and 97.5 percentiles were used
-	to create the 95\% confidence intervals.
-
-\subsection*{S8: Measuring computational hysteresis}
-	\paragraph{Using cross-validation accuracy to lower-bound L1-distance.}
-	In order for Eq.~\ref{l1} to be applicable, it is necessary to obtain
-	an unbiased estimate of a classifier's performance.  One well-known
-	pitfall in measuring this error is to underestimate it due to 
-	over-fitting of the data used.  As an example, if one were to try 
-	a large number of classifiers, eventually one would find one that
-	classifies the data perfectly, even though it might non generalize to
-	new data.
-
-	It is customary to use part of a data set to optimize hyperparameters of
-	a model, and then test the model on as-yet unseen data.  In our case,
-	don't have enough samples in each treatment to do this.  Instead, for 
-	this reason, we make principled decisions for all of the options used
-	in our classifier, and then test it's accuracy using cross validation,
-	with no optimization performed on the data.  It was crucial for 
-	the statistical validity of our approach that we test our classifier on 
-	each datum only once, and report these results without any optimizations
-	of the classifier.
-
-	In performing the classification we had various options, and since we
-	could not optimize these choices, we made principled decisions based on
-	prior knowledge from text classification applications.  We describe the
-	options we faced and the choices we made below.
-
-	\textit{Spelling correction.}  Because we used free-text
-	entry for the labels, there was bound to be many spelling mistakes.
-	This would tend to reduce the accuracy of a classifier, because the 
-	entries ``bread'' and ``braed'' would be regarded as completely different
-	features, even though they clearly correspond to the same 
-	\textit{intended word}.  While no algorithm can determine a worker's 
-	intentions, it is possible to check words against a corpus, and, in the
-	case of a misspelled word, look for plausible corrections based on 
-	edit distance.
-
-	\textit{Lemmatization.}  In some cases it is helpful to simplify words 
-	before providing them to the classifier.  For example, the words 
-	``berries'' and ``berry'' only differ in number, but would normally be
-	treated as completely different features.  Lemmatization ensures that
-	nouns are in their singular form, which helps to eliminate variations in
-	labels that increase sparsity without conveying discriminative 
-	information.
-
-	\textit{Removal of stop-words.}  Certain very common words such as `the',
-	``to'', and ``it'' are extremely common but don't help discriminate a 
-	worker's exposure.  Removing these words is a common practice because
-	they otherwise introduce noise into the classifier learning process.
-
-	\textit{Splitting multiple words.}  Although workers were 
-	instructed to put one word per text input, many put multiple words.
-	Theoretically the original multi-word entry might bear additional 
-	information that could be useful in discerning a worker's exposure. 
-	In practice, it would be necessary for that word combination to recur,
-	which is unlikely.  Therefore we chose to split multi-word entries,
-	using the individual words as features.  This meant that the outputs of
-	some workers generated more features than those of others.
-
-	\textit{Preserving the location of labels.}  When workers completed image
-	labeling tasks, they had to fill five text inputs, which were stacked
-	vertically.  Presumably, they began with the top input and proceeded 
-	downwards.  It seems likely that exposure effects might influence the
-	\textit{order} in which workers apply labels, so when processing the 
-	labels we prepended an integer to indicate into which text input the 
-	label been input.  This meant that the classifier could distinguish
-	``bread'' entered into the first text input from ``bread'' entered into
-	the second.  A drawback is that this increases sparsity, preventing the
-	classifier from accounting for the fact that different though they are,
-	these entries should be treated similarly.  For this reason, we also
-	provided features to the classifier which did not encode the particular
-	input that had been used.  Thus, two workers that entered ``bread''
-	into different inputs would generate both a feature in common indicating
-	the use of the word ``bread'', as well as distinct features, indicating
-	entry of the word ``bread'' \textit{in a particular input}.
-
-	\textit{Preserving the connection between tasks and labels.}  In many
-	cases a particular label would appear in many tasks.  For example, the
-	word ``food'' appears in all test tasks.  It stands to reason that
-	exposure effects play out differently for different tasks, and that
-	the attribution of a particular label during one task provides different
-	information from the attribution of the same label during a different 
-	task.  So, as we did in the case of input location, we prepended labels
-	with the identity of the task in which they were added, so that the 
-	two otherwise identical labels added for different tasks were treated
-	by the classifier as unique features.  Unlike in the case of input 
-	position attribution, we didn't include raw labels unadorned with 
-	the task number.  Our rationale for this is that the task defines the 
-	context in which a label is applied, and so the elicitation of a label 
-	during one task represents a distinct output from the elicitation of the 
-	same label during a different task.
-
-\paragraph{Selection of the na\"ive Bayes classifier.}
-A great deal of work has been done in the application of classifiers to
-text documents, which provides the background for our choice of classifier.
-The Support Vector Machine (SVM) approach is known to perform well, better in 
-general than na\"ive Bayes.  However, three considerations drove us to use
-a na\"ive Bayes classifier in favor of SVM.
-
-First, we used 119 examples (workers) per treatment, but the number of 
-features
-for each worker (i.e. the number of distinct labels, or modifications 
-thereof produced in preprocessing), was generally in the thousands.  
-This tends to
-be problematic for many classifier algorithms, including SVM, because it
-leads to very high variance models, which manifests as overfitting and poor
-performance.  To deal with this, some approach to culling features is 
-generally used, but this raises the issue of how to decide the culling in 
-a principled manner, generally adding further hyperparameters which could
-be optimized.  However, one of the strengths of the na\"ive Bayes classifier
-is that it's performance is not generally degraded from the inclusion of 
-large numbers of features, even when the number of examples is comparatively
-small.  We expected this feature of the na\"ive Bayes classifier to be 
-advantageous in our case.
-
-Second, the standard implementation of the na\"ive Bayes classifier has no 
-hyperparameters to optimize.  This allows us to forgo the common practice 
-of holding out a test set, and instead use cross-validation as a method to
-estimate the true classification error, \textit{since we did not perform
-any kind of model selection or optimization whatsoever using our data}.
-This point is crucial, because if we did optimize our classifier during 
-cross-validation, then the validation error would no longer provide an 
-unbiased estimate of the true classification error, but would instead lead
-to us over-reporting exposure effects.
-
-Third, the na\"ive Bayes algorithm is based on an assumption that the 
-probability of observing one feature is independent from the observation
-of any other, \textit{when conditioned on the class}.  This
-\textit{conditional independence} assumption is generally made for
-pragmatic rather than theoretical reasons, and is rarely satisfied.  However,
-if it \textit{is} satisfied, then the na\"ive Bayes classifier is optimal.
-In our case, conditional independence means that, provided we know the 
-exposure of a worker, knowing one label they provided to an image does
-not in any way help us guess any other label for that image.  In most
-text documents, the existence of topics and language structure certainly
-violates the conditional independence of words.  But in our case, such 
-effects are less likely to carry from one text input to the next, and in the
-small space provided by five inputs, any overarching topics are likely to
-be in relation to the image itself, upon which we are conditioning.  In other
-words, we believe that, in our setup, conditional independence is better 
-satisfied than in most text classification contexts.  That being the case,
-one would not expect much improvement in using a more sophisticated algorithm,
-such as SVM.
-
-\paragraph{Comparison to other classifiers.}
-
-\begin{figure}
-	\centering
-	\includegraphics[scale=0.75]{figs/theta_sup.pdf}
-	\label{fig:theta_sup}
-	\caption{
-		Figure S2: Bias induced by exposure to initial tasks and frames.
-		Bias is defined to be the difference in the probability 
-		distribution over workers' labels (L1-distance).  The plotted values
-		give a lower bound to the L1-distance, $D_{L1}^-$, which was 
-		determined from a classifier's performance in 
-		distinguishing workers that had undergone different exposures.
-		The bias was determined using (A-F) a na\"ive Bayes classifier, and 
-		(G-L) an SVM classifier.
-		In panels A through F, each plot adds an additional
-		preprocessing step to those used in the previous plot; the same is 
-		done for panels G through H: A,G) No 
-		preprocessing; B,H) spelling correction; C,I) stopword removal; 
-		D,J) lemmatization; E,K) splitting of multiple-word labels; 
-		F,L) distinguishing identical labels entered in different form inputs.
-	}
-\end{figure}
-The inequality in Eq.~\ref{l1}
-asserts that a classifiers performance in predicting class membership
-bounds the L1-distance between the distributions of features for the classes.
-This bound is tight for the optimal classifier, and in general, the slack
-depends on how the classifier is constructed.
-
-Therefore there may exist a classifier that is 
-significantly better than the one used to generate our results.  Even before
-committing to a particular classifier algorithm, various decisions about
-preprocessing need to be made.  For example, we chose to remove stopwords,
-lemmatize, split multi-word labels, distinguish the input used to enter 
-labels, and correct spelling.  All of these decisions affect the classifier
-performance.  The particular classifier algorithm chosen also has a strong 
-effect.
-
-Since we did not have enough data to create a separate test set, we could not
-optimize these decisions.  Doing so would lead to the inflation of the 
-performance, which could then only be estimated using an independent test set.
-Instead, we made principled decisions as described above.
-
-Although we cannot optimize these decisions, it is appropriate to look at
-what affect these decisions had, post-hoc.  We reproduce the plot shown in 
-Fig.~\ref{fig:theta}A using different combinations of preprocessing options,
-and using both the na\"ive Bayes and an SVM classifier.
-
-Unlike the na\"ive Bayes classifier, it is necessary to tune the cost and 
-gamma hyperparameters of the SVM classifier, as well as choose a kernel.
-We used simulated annealing to optimize the cost and gamma settings in the
-classification of $task2:food$ vs $task2:cult$.  For this reason, we expect
-the bar for $task2$ in Fig.~S8G-J is likely to be an overestimate due to
-overfitting on those data.
-
-These plots show that the result shown in Fig.~\ref{fig:theta}A is 
-representative, and supports the validity of the lower bounds on the 
-exposures exposure effects presented in the main text, in terms of induced 
-L1-distance.
-
-\paragraph{Statistical significance and confidence intervals for $\theta$.}
-The measurements of $\theta$ were based on the number of correct 
-classifications during validation tests.  We used leave-one-out validation,
-and count the number of correct classifications, $X$, which has a binomial
-distribution.  We take the null hypothesis that the classifier performs
-no better than chance, $X \sim \mathrm{Bin}(N,0.5)$, where $N$ is the number 
-of workers in both treatments of an experiment.  Then, the critical number 
-of correct classifications, $x^*$, in for a one-tailed hypothesis test with
-significance $\alpha$ is:
-\begin{align}
-	&x^* = \sup \left\{
-			x: \mathrm{Pr}\{ \mathrm{Bin}(N;0.5) \geq x \} < \alpha
-		\right\}\\
-	\text{where}\quad &\mathrm{Pr}\{ \mathrm{Bin}(N,p) \geq x \} = 
-		\sum_{x'=x}^{N} \binom{N}{x'}p^{x'}(1-p)^{(N-x')}
-\end{align}
-For the treatments in \textit{intertask-food-objects}, 5 different 
-permutations of each treatment was tested, and a different classifier was 
-built for each permutation.  For the sake of estimating the accuracy of 
-these classifiers, we assume that they have the same accuracy, which means
-that \textit{intertask-food-objects} has a larger number of validation tests
-(larger $N$), and for this hypothesis test we assume that $X$ has a normal 
-distribution, with $\mu=N/2$ and $\sigma = \frac{1}{2}\sqrt{N}$.
-
-To determining the confidence intervals for measured $\theta$ values we 
-use the exact Clopper-Pearson method.  
-Based on the observed number of successes, $X$, we calculate 
-$\eta^*_\mathrm{low}$ and $\eta^*_\mathrm{high}$ from:
-\begin{align}
-	\eta^*_\mathrm{high} &= \sup
-		\left\{
-			\eta : \mathrm{Pr}\{\mathrm{Bin}(N; \eta) \leq X \} > 
-				\frac{\alpha}{2}
-		\right\} \\
-	\eta^*_\mathrm{low} &= \inf
-		\left\{
-			\eta : \mathrm{Pr}\{\mathrm{Bin}(N; \eta) \geq X \} > 
-				\frac{\alpha}{2}
-		\right\}
-\end{align}
-Again, for the experiment \textit{intertask-food-objects}, which had 
-more validation tests than the others, we derive the confidence intervals
-assuming $X$ is normally distributed.
-Since the significance values are to be shown on a plot of $\theta$, we 
-transform them into equivalent values of 
-$\theta$: $\theta^*_\mathrm{high} = 2\eta^*_\mathrm{high} - 1$ and 
-$\theta^*_\mathrm{low} = 2\eta^*_\mathrm{low} - 1$.
-The statistics collected for the measurement of $\theta$ are tabulated in 
-table X.
-
-\begin{table}
-\begin{center}
-\begin{tabular}{c c c c c c c}
-	\toprule
-	Experiment & $N$ & $X$ & $x^*$ &
-		$\hat{\theta}$ & $\theta^*_\mathrm{low}$ & 
-		$\theta^*_\mathrm{high}$ \\
-	\midrule
-	\textit{intertask-food-objects} & 1190 & 777 & 624 & \textbf{30.6} 
-		& 25.2 & 36.0 \\
-	\textit{frame-food-objects} & 238 & 122 & 133 & 2.5 & -10.6 & 14.7 \\
-	\textit{echo-food-objects} & 238 & 162 &  133 & \textbf{36.1} & 23.4 
-		& 47.1  \\
-	\textit{intertask-food-culture} & 238 & 180 & 133 & \textbf{51.3} & 39.3 
-		& 61.1 \\
-	\textit{frame-food-culture} & 238 & 130 & 133 & 9.2 & -3.9 & 21.3 \\
-	\bottomrule
-\end{tabular}
-\caption{Statistics for the measurement of the extent of bias, $\theta$,
-	induced by intertask and framing effects in various experiments.
-	Number of validation tests, $N$; number of successful classifications, 
-	$X$; critical number of succesful classifications to reject the null 
-	hypotheses that the classifier does no better than chance 
-	(one-tailed test), $x^*$; 
-	lower bound estimate of bias based on observed number of successful
-	classifications, $\hat{\theta}$; lower confidence interval for lower
-	bound estimate of bias, $\theta^*_\mathrm{low}$; upper confidence 
-	interval for same, $\theta^*_\mathrm{high}$.  Hypothesis test and 
-	confidence intervals are based on a significance of $\alpha=0.05$.
-	Values for $\hat{\theta}$ in boldface are significantly greater than 0.
-}
-
-\end{center}
-\end{table}
-
-\subsection*{S9: Justifications and statistical properties of classifier-based measurement of computational hysteresis}
-
-\paragraph{Comparing $\theta$ to a $\chi^2$ significance test}
+\subsection*{Measuring intertask and framing effects.}
+
+\paragraph{Comparing $\theta$ and $\chi^2$.}
+The following is an illustrative example to show why it is important to 
+have a measure of effect size, like $\theta$, in addition to effect 
+significance, like $\chi^2$.
 Suppose that we have a very slightly unfairly weighted coin, which turns
-up heads ($x=\mathbf{H}$) more often than expected by 1 part in one hundred:
-$\Pr\{x=\mathbf{H}\} = 0.500001$. Such a coin would be fine for many 
+up heads ($x=\mathbf{H}$) more often than expected by one part in one hundred:
+$\Pr\{x=\mathbf{H}\} = 0.501$. Such a coin would be fine for many 
 practical purposes, like deciding who buys lunch.  We could
@@
 it 100 million times, while doing the same with a coin we know is fair.
-Simulating this with a random number generator yields the following results:
-
-\begin{center}
+Simulating this with a random number generator yields the results shown
+in Table~S\ref{table:coin}, and results from a $\chi^2$ test of the 
+hypothesis that the two coins have the same probability of turning up heads 
+is shown in Table~S\ref{table:coin_stats}.
+
+\setlength{\floatsep}{30pt plus 1.0pt minus 2.0pt}
+
+\begin{table}
+\centering
 \begin{tabular}{c c c c}
@@
 \end{tabular}
-\end{center}
-A $\chi^2$ test yields the following results:
-\begin{center}
+\caption{
+	Simulated counts of heads ($N_\mathbf{H}$) and tails ($N_\mathbf{T}$)
+	occurences, for a fair coin, and a coin biased to have a probability
+	of turning up heads of 0.501.
+}
+\label{table:coin}
+\end{table}
+
+\begin{table}
+\centering
 	\begin{tabular}{c c c c }
@@
 	\end{tabular}
-\end{center}
+\caption{
+	Statistics for a $\chi^2$ test of the hypothesis that a fair and 
+	unfair coin have the same probability of turning up heads.  
+	The result overwhelmingly favors rejection of the hypothesis, even
+	though the coins differ only slightly.
+}
+\label{table:coin_stats}
+\end{table}
+
 Even though the $\chi^2$ test shows, with tremendous statistical 
@@
 $\theta = \frac{1}{2}\left( |0.501 - 0.499| + |0.499 - 0.501| \right) = 0.002$.
-A sufficiently large sample size will lead to the detection an arbitrarily 
+This demonstrates how a sufficiently large sample size will lead to the 
+detection an arbitrarily 
 small bias with arbitrarily high statistical significance. 
-This is why to measure the practical significance of intertask effects
+This is why, to measure the practical significance of intertask effects,
 we rely on a measure of effect size, which is in this case a measure
@@
 been proposed to estimate the L1-distance between distributions
-given only samples.  But these methods provide only asymptotic guarantees
+given only samples.  \td{cite these} But these methods provide only asymptotic guarantees
 which cannot be directly applied to our case.  However, machine learning
@@
 
-\paragraph{Using classifiers to measure bias.}
-
+\paragraph{The relationship of bias and classifier accuracy.}
 We will now show that, any classifier algorithm, $\mathcal{A}$, that
@@
 
+\paragraph{Using cross-validation accuracy to lower-bound bias.}
+	In order for Eq.~\ref{l1} to be applicable, it is necessary to obtain
+	an unbiased estimate of a classifier's accuracy.  One well-known
+	pitfall in measuring classifier accuracy is to underestimate it due to 
+	over-fitting to the data used.  As an example, if one were to try 
+	a large number of classifiers, eventually one would find one that
+	classifies the data perfectly, even though it might non generalize to
+	new data.
+
+	It is customary to use part of a data set to optimize hyperparameters of
+	a model, and then test the model on as-yet unseen data.  In our case,
+	don't have enough samples in each treatment to do this.  Instead, for 
+	this reason, we make principled decisions for all of the options used
+	in our classifier, and then test it's accuracy using cross validation,
+	with no optimization performed on the data.  It was crucial for 
+	the statistical validity of our approach that we test our classifier on 
+	each datum only once, and report these results without any optimizations
+	of the classifier.
+
+	In performing the classification we had various options, and since we
+	could not optimize these choices, we made principled decisions based on
+	prior knowledge from text classification applications.  We describe the
+	options we faced and the choices we made below.
+
+	\textit{Spelling correction.}  Because we used free-text
+	entry for the labels, there was bound to be many spelling mistakes.
+	This would tend to reduce the accuracy of a classifier, because the 
+	entries ``bread'' and ``braed'' would be regarded as completely different
+	features, even though they clearly correspond to the same 
+	\textit{intended word}.  While no algorithm can determine a worker's 
+	intentions, it is possible to check words against a corpus, and, in the
+	case of a misspelled word, look for plausible corrections based on 
+	edit distance.
+
+	\textit{Lemmatization.}  In some cases it is helpful to simplify words 
+	before providing them to the classifier.  For example, the words 
+	``berries'' and ``berry'' only differ in number, but would normally be
+	treated as completely different features.  Lemmatization ensures that
+	nouns are in their singular form, which helps to eliminate variations in
+	labels that increase sparsity without conveying discriminative 
+	information.
+
+	\textit{Removal of stop-words.}  Certain very common words such as `the',
+	``to'', and ``it'' are extremely common but don't help discriminate a 
+	worker's exposure.  Removing these words is a common practice because
+	they otherwise introduce noise into the classifier learning process.
+
+	\textit{Splitting multiple words.}  Although workers were 
+	instructed to put one word per text input, many put multiple words.
+	Theoretically the original multi-word entry might bear additional 
+	information that could be useful in discerning a worker's exposure. 
+	In practice, it would be necessary for that word combination to recur,
+	which is unlikely.  Therefore we chose to split multi-word entries,
+	using the individual words as features.  This meant that the outputs of
+	some workers generated more features than those of others.
+
+	\textit{Preserving the location of labels.}  When workers completed image
+	labeling tasks, they had to fill five text inputs, which were stacked
+	vertically.  Presumably, they began with the top input and proceeded 
+	downwards.  It seems likely that exposure effects might influence the
+	\textit{order} in which workers apply labels, so when processing the 
+	labels we prepended an integer to indicate into which text input the 
+	label been input.  This meant that the classifier could distinguish
+	``bread'' entered into the first text input from ``bread'' entered into
+	the second.  A drawback is that this increases sparsity, preventing the
+	classifier from accounting for the fact that different though they are,
+	these entries should be treated similarly.  For this reason, we also
+	provided features to the classifier which did not encode the particular
+	input that had been used.  Thus, two workers that entered ``bread''
+	into different inputs would generate both a feature in common indicating
+	the use of the word ``bread'', as well as distinct features, indicating
+	entry of the word ``bread'' \textit{in a particular input}.
+
+	\textit{Preserving the connection between tasks and labels.}  In many
+	cases a particular label would appear in many tasks.  For example, the
+	word ``food'' appears in all test tasks.  It stands to reason that
+	exposure effects play out differently for different tasks, and that
+	the attribution of a particular label during one task provides different
+	information from the attribution of the same label during a different 
+	task.  So, as we did in the case of input location, we prepended labels
+	with the identity of the task in which they were added, so that the 
+	two otherwise identical labels added for different tasks were treated
+	by the classifier as unique features.  Unlike in the case of input 
+	position attribution, we didn't include raw labels unadorned with 
+	the task number.  Our rationale for this is that the task defines the 
+	context in which a label is applied, and so the elicitation of a label 
+	during one task represents a distinct output from the elicitation of the 
+	same label during a different task.
+
+\paragraph{Selection of the na\"ive Bayes classifier.}
+A great deal of work has been done in the application of classifiers to
+text documents, which provides the background for our choice of classifier.
+The Support Vector Machine (SVM) approach is known to perform well, better in 
+general than na\"ive Bayes.  However, three considerations drove us to use
+a na\"ive Bayes classifier in favor of SVM.
+
+First, we used 119 examples (workers) per treatment, but the number of 
+features
+for each worker (i.e. the number of distinct labels, or modifications 
+thereof produced in preprocessing), was generally in the thousands.  
+This tends to
+be problematic for many classifier algorithms, including SVM, because it
+leads to very high variance models, which manifests as overfitting and poor
+performance.  To deal with this, some approach to culling features is 
+generally used, but this raises the issue of how to decide the culling in 
+a principled manner, generally adding further hyperparameters which could
+be optimized.  However, one of the strengths of the na\"ive Bayes classifier
+is that it's performance is not generally degraded from the inclusion of 
+large numbers of features, even when the number of examples is comparatively
+small.  We expected this feature of the na\"ive Bayes classifier to be 
+advantageous in our case.
+
+Second, the standard implementation of the na\"ive Bayes classifier has no 
+hyperparameters to optimize.  This allows us to forgo the common practice 
+of holding out a test set, and instead use cross-validation as a method to
+estimate the true classification error, \textit{since we did not perform
+any kind of model selection or optimization whatsoever using our data}.
+This point is crucial, because if we did optimize our classifier during 
+cross-validation, then the validation error would no longer provide an 
+unbiased estimate of the true classification error, but would instead lead
+to us over-reporting exposure effects.
+
+Third, the na\"ive Bayes algorithm is based on an assumption that the 
+probability of observing one feature is independent from the observation
+of any other, \textit{when conditioned on the class}.  This
+\textit{conditional independence} assumption is generally made for
+pragmatic rather than theoretical reasons, and is rarely satisfied.  However,
+if it \textit{is} satisfied, then the na\"ive Bayes classifier is optimal.
+In our case, conditional independence means that, provided we know the 
+exposure of a worker, knowing one label they provided to an image does
+not in any way help us guess any other label for that image.  In most
+text documents, the existence of topics and language structure certainly
+violates the conditional independence of words.  But in our case, such 
+effects are less likely to carry from one text input to the next, and in the
+small space provided by five inputs, any overarching topics are likely to
+be in relation to the image itself, upon which we are conditioning.  In other
+words, we believe that, in our setup, conditional independence is better 
+satisfied than in most text classification contexts.  That being the case,
+one would not expect much improvement in using a more sophisticated algorithm,
+such as SVM.
+
+\paragraph{Comparison to other classifiers.}
+
+\begin{figure}
+	\centering
+	\includegraphics[scale=0.75]{figs/theta_sup.pdf}
+	\label{fig:theta_sup}
+	\caption{
+		Figure S2: Bias induced by exposure to initial tasks and frames.
+		Bias is defined to be the difference in the probability 
+		distribution over workers' labels (L1-distance).  The plotted values
+		give a lower bound to the L1-distance, $D_{L1}^-$, which was 
+		determined from a classifier's performance in 
+		distinguishing workers that had undergone different exposures.
+		The bias was determined using (A-F) a na\"ive Bayes classifier, and 
+		(G-L) an SVM classifier.
+		In panels A through F, each plot adds an additional
+		preprocessing step to those used in the previous plot; the same is 
+		done for panels G through H: A,G) No 
+		preprocessing; B,H) spelling correction; C,I) stopword removal; 
+		D,J) lemmatization; E,K) splitting of multiple-word labels; 
+		F,L) distinguishing identical labels entered in different form inputs.
+	}
+\end{figure}
+The inequality in Eq.~\ref{l1}
+asserts that a classifiers performance in predicting class membership
+bounds the L1-distance between the distributions of features for the classes.
+This bound is tight for the optimal classifier, and in general, the slack
+depends on how the classifier is constructed.
+
+Therefore there may exist a classifier that is 
+significantly better than the one used to generate our results.  Even before
+committing to a particular classifier algorithm, various decisions about
+preprocessing need to be made.  For example, we chose to remove stopwords,
+lemmatize, split multi-word labels, distinguish the input used to enter 
+labels, and correct spelling.  All of these decisions affect the classifier
+performance.  The particular classifier algorithm chosen also has a strong 
+effect.
+
+Since we did not have enough data to create a separate test set, we could not
+optimize these decisions.  Doing so would lead to the inflation of the 
+performance, which could then only be estimated using an independent test set.
+Instead, we made principled decisions as described above.
+
+Although we cannot optimize these decisions, it is appropriate to look at
+what affect these decisions had, post-hoc.  We reproduce the plot shown in 
+Fig.~\ref{fig:theta}A using different combinations of preprocessing options,
+and using both the na\"ive Bayes and an SVM classifier.
+
+Unlike the na\"ive Bayes classifier, it is necessary to tune the cost and 
+gamma hyperparameters of the SVM classifier, as well as choose a kernel.
+We used simulated annealing to optimize the cost and gamma settings in the
+classification of $task2:food$ vs $task2:cult$.  For this reason, we expect
+the bar for $task2$ in Fig.~S8G-J is likely to be an overestimate due to
+overfitting on those data.
+
+These plots show that the result shown in Fig.~\ref{fig:theta}A is 
+representative, and supports the validity of the lower bounds on the 
+exposures exposure effects presented in the main text, in terms of induced 
+L1-distance.
+
+\paragraph{Statistical significance and confidence intervals for $\theta$.}
+The measurements of $\theta$ were based on the number of correct 
+classifications during validation tests.  We used leave-one-out validation,
+and count the number of correct classifications, $X$, which has a binomial
+distribution.  We take the null hypothesis that the classifier performs
+no better than chance, $X \sim \mathrm{Bin}(N,0.5)$, where $N$ is the number 
+of workers in both treatments of an experiment.  Then, the critical number 
+of correct classifications, $x^*$, in for a one-tailed hypothesis test with
+significance $\alpha$ is:
+\begin{align}
+	&x^* = \sup \left\{
+			x: \mathrm{Pr}\{ \mathrm{Bin}(N;0.5) \geq x \} < \alpha
+		\right\}\\
+	\text{where}\quad &\mathrm{Pr}\{ \mathrm{Bin}(N,p) \geq x \} = 
+		\sum_{x'=x}^{N} \binom{N}{x'}p^{x'}(1-p)^{(N-x')}
+\end{align}
+For the treatments in \textit{intertask-food-objects}, 5 different 
+permutations of each treatment was tested, and a different classifier was 
+built for each permutation.  For the sake of estimating the accuracy of 
+these classifiers, we assume that they have the same accuracy, which means
+that \textit{intertask-food-objects} has a larger number of validation tests
+(larger $N$), and for this hypothesis test we assume that $X$ has a normal 
+distribution, with $\mu=N/2$ and $\sigma = \frac{1}{2}\sqrt{N}$.
+
+To determining the confidence intervals for measured $\theta$ values we 
+use the exact Clopper-Pearson method.  
+Based on the observed number of successes, $X$, we calculate 
+$\eta^*_\mathrm{low}$ and $\eta^*_\mathrm{high}$ from:
+\begin{align}
+	\eta^*_\mathrm{high} &= \sup
+		\left\{
+			\eta : \mathrm{Pr}\{\mathrm{Bin}(N; \eta) \leq X \} > 
+				\frac{\alpha}{2}
+		\right\} \\
+	\eta^*_\mathrm{low} &= \inf
+		\left\{
+			\eta : \mathrm{Pr}\{\mathrm{Bin}(N; \eta) \geq X \} > 
+				\frac{\alpha}{2}
+		\right\}
+\end{align}
+Again, for the experiment \textit{intertask-food-objects}, which had 
+more validation tests than the others, we derive the confidence intervals
+assuming $X$ is normally distributed.
+Since the significance values are to be shown on a plot of $\theta$, we 
+transform them into equivalent values of 
+$\theta$: $\theta^*_\mathrm{high} = 2\eta^*_\mathrm{high} - 1$ and 
+$\theta^*_\mathrm{low} = 2\eta^*_\mathrm{low} - 1$.
+The statistics collected for the measurement of $\theta$, corresponding to
+Fig.~\ref{fig:theta}A are tabulated in 
+table X.
+
+\begin{table}
+\begin{center}
+\begin{tabular}{c c c c c c c c }
+	\toprule
+	\multirow{2}{*}{Experiment} & \multirow{2}{*}{$N$} & 
+	\multirow{2}{*}{$X$} & \multirow{2}{*}{$x^*$} & \multicolumn{3}{c}{(\%)}
+		& \multirow{2}{*}{$p$}\\ \cline{5-7} \noalign{\smallskip}
+	& & & & $\hat{\theta}$ & $\theta^*_\mathrm{low}$ 
+		& $\theta^*_\mathrm{high}$  \\
+	\midrule
+	\textit{intertask-food-objects} & 1190 & 777 & 624 & \textbf{30.6} 
+		& 25.2 & 36.0 & $2.5 \times 10^{-26}$ \\
+	\textit{frame-food-objects} & 238 & 122 & 133 & 2.5 & -10.6 & 14.7
+		& 0.37 \\
+	\textit{echo-food-objects} & 238 & 162 &  133 & \textbf{36.1} & 23.4 
+		& 47.1 & $1.3 \times 10^{-8}$ \\
+	\textit{intertask-food-culture} & 238 & 180 & 133 & \textbf{51.3} & 39.3 
+		& 61.1 & $5.0 \times 10^{-16}$ \\
+	\textit{frame-food-culture} & 238 & 130 & 133 & 9.2 & -3.9 & 21.3 
+		& 0.087\\
+	\bottomrule
+
+\end{tabular}
+
+\caption{Statistics for the measurement of the extent of bias, $\theta$,
+	induced by intertask and framing effects in various experiments.
+	Number of validation tests, $N$; number of successful classifications, 
+	$X$; critical number of succesful classifications to reject the null 
+	hypotheses that the classifier does no better than chance 
+	(one-tailed test), $x^*$; 
+	lower bound estimate of bias based on observed number of successful
+	classifications, $\hat{\theta}$; lower confidence interval for lower
+	bound estimate of bias, $\theta^*_\mathrm{low}$; upper confidence 
+	interval for same, $\theta^*_\mathrm{high}$.  Hypothesis test and 
+	confidence intervals are based on a significance of $\alpha=0.05$.
+	Values for $\hat{\theta}$ in boldface are significantly greater than 0.
+}
+\end{center}
+\end{table}
+
+The statistics for Fig.~\ref{fig:theta}B are shown in table X.
+
+\begin{table}
+\begin{center}
+\begin{tabular}{c c c c c c c c }
+	\toprule
+	\multirow{2}{*}{Task position} & \multirow{2}{*}{$N$} & 
+	\multirow{2}{*}{$X$} & \multirow{2}{*}{$x^*$} & \multicolumn{3}{c}{(\%)}
+		& \multirow{2}{*}{$p$}\\ \cline{5-7}\noalign{\smallskip}
+	& & & & $\hat{\theta}$ & $\theta^*_\mathrm{low}$ 
+		& $\theta^*_\mathrm{high}$  \\
+	\midrule
+	1 & 238 & 152 & 133 & \textbf{28.1} & 14.8 & 39.1 
+		& $1.12 \times 10^{-5}$\\
+	2 & 238 & 138 & 133 & \textbf{15.6} & 2.9 & 27.8  
+		& $8.14 \times 10^{-3}$\\
+	3 & 238 & 140 & 133 & \textbf{17.8} & 4.6 & 29.5  
+		& $3.87 \times 10^{-3}$\\
+	4 & 238 & 135 & 133 & \textbf{13.6} & 0.3 & 25.4  
+		& $0.0221$ \\
+	5 & 238 & 134 & 133 & \textbf{12.4} & 0.5 & 24.6 & $0.0300$ \\
+	\bottomrule
+\end{tabular}
+\caption{Statistics for the measurement of the extent of bias, $\theta$,
+	induced by intertask for \textit{intertask-food-objects}, measured 
+	for test images at specific positions in the sequence of 5 test images.
+	These values are averaged over 5 different permutations, such that 
+	the strength of intertask effects are measured for each of the test images
+	in each of the positions.
+	Number of validation tests, $N$; number of successful classifications, 
+	$X$; critical number of succesful classifications to reject the null 
+	hypotheses that the classifier does no better than chance 
+	(one-tailed test), $x^*$; 
+	lower bound estimate of bias based on observed number of successful
+	classifications, $\hat{\theta}$; lower confidence interval for lower
+	bound estimate of bias, $\theta^*_\mathrm{low}$; upper confidence 
+	interval for same, $\theta^*_\mathrm{high}$.  Hypothesis test and 
+	confidence intervals are based on a significance of $\alpha=0.05$.
+	Values for $\hat{\theta}$ in boldface are significantly greater than 0.
+}
+
+\end{center}
+\end{table}
+
+\subsection*{Data preprocessing}
+	\paragraph{Splitting, Lemmatization, removal of stop-words, and 
+		addition of position tags.}
+
+	Before performing any analysis on the labels that workers provided, we
+	performed a series of preprocessing steps.  
+	Labels that contained
+	multiple words (separated by spaces or punctuation) were split, with
+	punctuation removed, and the separated words were treated as distinct 
+	features in subsequent analysis.
+	Misspelled words were automatically corrected using a spelling 
+	correction algorithm described below.  
+	Next, words were lemmatized using the
+	wordnet lemmatizer \cite{miller1995wordnet,felbaum1998wordnet}.  
+	Common words such as ``the'', ``to'', or ``with'', were found using the
+	the NLTK's English stop-word list and removed \cite{loper2002nltk}.
+
+	For the purpose of training and testing a na\"ive Bayes classifier, we 
+	performed an additional preprocessing step.  We tagged words with the
+	position in which they had been entered (i.e. which of the five text 
+	inputs in the task interface) as well as the test tasks in which the word 
+	had been provided.
+	So, if the word ``wine'' was entered into the second text-input for 
+	the third test-task, after preprocessing, the feature ``3\_2\_wine'' would
+	appear.  Prepending the task number onto words was simply a means to 
+	retain correct attribution, which itself was essential since providing a
+	word during one task is not equivalent to providing the same word during 
+	another task.
+
+	\paragraph{Spelling correction.}  
+	Spelling correction was performed using an algorithm that first detected
+	if a word was likely to be misspelled, then generated a set of candidate 
+	corrections, and chose the best candidate based on a scoring mechanism.
+
+	A word was considered misspelled if it was not contained in the 
+	\textit{legal set}, which was formed by the union of
+	the wordnet corpus, the stop-word list, and a set of words seen while 
+	crawling the world food section of the allrecipes.com website.  We
+	describe the crawling of the allrecipes.com website in a section below.
+
+	To correct misspellings, we first produced all possible modified forms 
+	that could be obtained applying one or two edits.  An edit consisted of 
+	adding or removing a letter, changing one letter into another, or 
+	swapping the positions of two adjacent letters.  For the purpose of these 
+	edits, spaces were treated as any other letter.
+
+	The candidates produced by these edits which were in the legal set were
+	then ranked based on a scoring mechanism, and the highest scoring word
+	was chosen as the correction.  A candidate $w$'s score, $s_w$, was 
+	calculated according to the following formula:
+	\begin{equation}
+		s_w = (f_w + 1) \times p_1 \times p_2,
+	\end{equation}
+	where $f_w$ is the frequency with which the word occurred (correctly 
+	spelled)
+	within the given task, $p_1$ was a penalty for the first edit, and
+	$p_2$ was a penalty for the second edit.  If the word was made using only
+	one edit, then $p_2 = 1$.  Any edit that did not involve adding a space
+	(i.e. separating a word) incurred a penalty of 0.5, while the addition of
+	a space incurred a penalty of 0.1.  Word-separation edits were more 
+	strongly penalized because it is often possible to split a series of 
+	letters into many short two- or three-letter words, which otherwise leads 
+	to many erroneous corrections.  We found that setting the penalty for
+	word splitting at 0.1 worked well by testing on words taken from
+	initial tasks.
+
+	After all of our analyses had been performed, we checked the accuracy of 
+	the spelling correction algorithm using three human coders.  The coders
+	were shown a set of 
+	500 words that were randomly sampled from the labels attributed during 
+	test tasks (50 for each test task).  Before sampling, the labels from all
+	experimental treatments, for the given test task, were pooled together.
+	The coders did not know which treatment any given word came from.  
+	In addition to the words, coders were shown the spelling correction 
+	produced by the algorithm, as well as the image from the test task.
+	The coders were asked to identify any misspelled words which had not 
+	been corrected, as well as any corrections that appeared to be erroneous,
+	by indicating their own correction.
+
+	Based on this exercise, we found that, according to the human coders,
+	17\% of the words were misspelled, but that after applying the 
+	automated spelling correction, only 3.2\% of words were misspelled.
+
+	\paragraph{Crawling the world food section of allrecipes.com.}
+	The website allrecipes.com was accessed on 3-4 November 2014 using 
+	automated scripts.  A total of 2642 recipe listings and 15621 recipe
+	instruction pages were retrieved.  Recipe listings were pages that 
+	provided lists of recipes, and contained a title and short description 
+	for each.  
+	The recipe instruction pages had lists of ingredients and preparation 
+	instructions.  All of the words found in recipe titles, short
+	descriptions, ingredients lists, and preparation instructions were
+	collected, and saved as an auxiliary set to augment the \textit{legal set}
+	used in spelling correction.
+
+\subsection*{Most suppressed / activated terms}
+The words whose frequencies differed most between the treatments of given 
+experiments are shown in Table~S\ref{table:top-words}.  Note that 
+the word that was most suppressed in food-exposed treatments was always 
+``food''.
+
+\begin{table}
+	\centering
+	\setlength{\tabcolsep}{10pt}
+	\begin{tabular}{ c c c c c }
+
+		\setlength{\tabcolsep}{4pt}
+		\begin{tabular}{ r | c }
+		\toprule
+		\multicolumn{2}{c}{\textit{task1}} \\
+		\toprule
+		coffee & 38 \\
+		meal & 34 \\
+		cheese & 34 \\
+		apple & 32 \\
+		dessert & 21 \\
+		cup & -30 \\
+		glass & -45 \\
+		table & -70 \\
+		candle & -74 \\
+		food & -80 \\
+		\bottomrule
+		\end{tabular}
+
+&
+
+		\setlength{\tabcolsep}{4pt}
+		\begin{tabular}{ r | c }
+		\toprule
+		\multicolumn{2}{c}{\textit{frame1}} \\
+		\toprule
+		bread & 18 \\
+		wine & 18 \\
+		cheese & 16 \\
+		apple & 14 \\
+		oil & 12 \\
+		table & -9 \\
+		meal & -10 \\
+		candle & -12 \\
+		dinner & -13 \\
+		food & -32 \\
+		\bottomrule
+		\end{tabular}
+
+&
+
+		\setlength{\tabcolsep}{4pt}
+		\begin{tabular}{ r | c }
+		\toprule
+		\multicolumn{2}{c}{\textit{echo1}} \\
+		\toprule
+		apple & 24 \\
+		cheese & 23 \\
+		wine & 15 \\
+		coffee & 14 \\
+		oil & 7 \\
+		knife & -24 \\
+		dinner & -26 \\
+		fork & -27 \\
+		candle & -35 \\
+		food & -55 \\
+		\bottomrule
+		\end{tabular}
+
+&
+
+		\setlength{\tabcolsep}{4pt}
+		\begin{tabular}{ r | c }
+		\toprule
+		\multicolumn{2}{c}{\textit{task2}} \\
+		\toprule
+		spicy & 26 \\
+		sauce & 17 \\
+		indian & 15 \\
+		buffet & 14 \\
+		exotic & 12 \\
+		festival & -11 \\
+		offering & -12 \\
+		statue & -15 \\
+		india & -20 \\
+		food & -56 \\
+		\bottomrule
+		\end{tabular}
+
+&
+
+		\setlength{\tabcolsep}{4pt}
+		\begin{tabular}{ r | c }
+		\toprule
+		\multicolumn{2}{c}{\textit{frame2}} \\
+		\toprule
+		indian & 11 \\
+		banquet & 8 \\
+		spicy & 7 \\
+		asian & 6 \\
+		variety & 6 \\
+		delicious & -6 \\
+		meat & -7 \\
+		festival & -7 \\
+		spice & -7 \\
+		food & -9 \\
+		\bottomrule
+		\end{tabular}
+
+	\end{tabular}
+	\caption{
+		Top 5 words, used to label the first test image, whose usage frequency
+		increased or decreased the most between treatments of given 
+		experiments.  Positive values indicate that the food-exposed treatment
+		used the word with higher frequency.  Word frequencies for 
+		\textit{intertask-food-objects} are aggregated across 5 
+		permutations, and hence tend to show larger absolute differences.
+	}
+	\label{table:top-words}
+\end{table}
+
+\subsection*{Identification of food-related terms}
+The wordnet corpus is composed of synsets, which are particular senses 
+(meanings) and a set of word forms bearing that meaning. A given word form, 
+such as ``ring'' has multiple senses (``to ring a bell'', ``a wedding ring''), 
+and so can be part of many synsets.  Since the wordnet corpus was designed
+to carry semantic information, the synset is the basic organizing element
+of wordnet.
+
+We chose the synsets \texttt{food.n.01} and \texttt{food.n.02} to act as roots
+in defining which words should be considered food-related.  Any word form
+belonging to a synset which was a hyponym of one of the two root synsets
+identified above was considered to be a reference to food.  Here, as in the
+main text, when we say hyponym, we mean either a direct hyponym, or a hyponym
+of a hyponym, and so on.
+
+This is a stringent notion of a word being a food reference.  It roughly
+corresponds to whether or not a given thing is reasonably considered 
+consumable.  So, ``orange'' is food, but ``salty'' is not.  Although ``salty''
+would usually qualify something edible, it is not itself an edible thing.
+On the other hand, ``salt'' would be considered a reference to food under 
+this operationalization.
+
+The subset of the wordnet corpus induced by the hyponyms of \textit{food.n.01}
+and \textit{food.n.02} provide a set of 3590 words.  Manual
+testing showed good coverage, except for references to ethnic foods.  
+Since, especially in \textit{exp2}, we had images containing many ethnic 
+foods, we decided to augment the wordnet corpus with words learned by 
+crawling the world food section of the allrecipes.com website.
+
+After collecting a set of words using an automated script 
+(described above), we collected the set of words that had been used by
+workers and which had been seen during crawling of the allrecipes.com website,
+but which were not included in wordnet.  We grafted these extra words into
+the wordnet hyponym-hypernym graph manually, which ensured that any references
+to ethnic words learned from crawling would be properly classified as 
+food references.
+
+\paragraph{Validation of the detection of food references.}
+To determine whether our extended version of wordnet provided a good approach
+to detecting food-related words, we sampled 500 words 
+(50 from each test task)  from the set of labels produced by workers and had 
+three human coders manually decide if they were 
+food-related or not.
+
+The coders were instructed to consider whether a word was a noun signifying
+an edible item.  The guiding principle was, for the coder to ask herself,
+``can I eat X'', where X is the word she is coding.  The coders were
+shown the used in the task from which the word came, to help resolve ambiguity
+in the sense of the word that had been given.  Coders were also shown the 
+spelling correction (if any) that the spell-correction algorithm had made,
+to help interpret misspelled words.
+
+We evaluated the food detection algorithm in two ways.  First, we measured
+the inter-rater reliability between the three human coders and the algorithm
+(treating the algorithm just like any other coder).  Second, adopting the 
+majority code given by the human coders, we determined the accuracy of the
+food-detection algorithm.  Data summarizing this validation process are given
+in Table~S\ref{table:inter-rater}.
+
+\begin{table}
+\centering
+\setlength{\tabcolsep}{12pt}
+\begin{tabular}{ r | c }
+\toprule    
+\# terms coded & 500 \\
+\# food references & 130 \\
+\# correct machine codes & 440 \\
+inter-rater reliability & 82.4\% \\
+human-machine code agreement & 88\% \\
+%machine recall & 80 \% \\
+%machine precision & 75.4 \% \\
+%machine code F1 & 0.78 \\
+\bottomrule
+\end{tabular}
+\caption{
+	Results for the validation 
+	of the automatic detection of food references, by comparison to
+	human-generated coding on randomly sampled words.  In calculating the 
+	human-machine code agreement, the majority human code was used.
+	Inter-rater reliability was calculated as Krippendorff's alpha.
+}
+\label{table:inter-rater}
+\end{table}
+
+The results show that good inter-rater reliability was achieved during the
+validation (82.4\%).  Looking at the agreement between the 
+machine codes and the majority human-generated codes, we find they agree
+88\% of the time.  This means that the concept used to instruct human coders
+provides a good approximation to what the wordnet-based machine codes actually
+represent. In other words, the machine codes correspond closely to indicating
+which words correspond to nouns that refer to edible things, and which ones
+do not, which provides a clear and simple interpretation for the machine
+coding of food and non-food words.
+
+\paragraph{Testing differences in proportions of food-related labels.}
+We calculate the proportion of food-related labels in a treatment by first
+calculating the proportion of food-related labels per worker, and then
+taking the average of this value for all workers.  We calculate the
+sample standard deviation for workers' proportions of food-related terms,
+$s_w$ and then estimate the standard deviation of the average proportion
+to be $s = s_w / \sqrt{N}$, where $N$ is the number of workers in the 
+treatment.  The proportions of food-related words for all treatments,
+and the statistics for the hypothesis test that the proportions between
+treatments within given experiments differ, are shown in 
+Table~S\ref{table:proportion-food}.
+
+\begin{table}
+\centering{
+\setlength{\tabcolsep}{4pt}
+\setlength{\tabcolsep}{3pt}
+\begin{tabular}{c c c c c c c c c c c}
+	\toprule
+	\multirow{2}{*}{Experiment} 
+		& \multicolumn{2}{c}{food treatment}
+		& \ 
+		& \multicolumn{2}{c}{other treatment} 
+		& \
+		& \multicolumn{2}{c}{(other - food)} 
+	& \multirow{2}{*}{$z$-score}
+	& \multirow{2}{*}{$p$-value} \\ \cline{2-3} \cline{5-6} \cline{8-9}
+	& \% refs. 
+	& $s$ 					
+	& \
+	& \% refs. 
+	& $s$ 					
+	& \
+	& $\Delta$\% refs. 
+	& $s$ 					 \\ 
+	\midrule
+	\textit{intertask-food-objects} & 54.5 & 0.6 & \ & 57.4 & 0.8 & \ 
+		& \textbf{2.9} & 1.0 & 3.0 & $1.3 \times 10^{-3}$\\
+	\textit{frame-food-objects} & 56.2 & 1.4 & \ & 60.1 & 1.4 & \ 
+		& \textbf{3.9} & 1.9 & 2.0 & $2.2 \times 10^{-2}$\\
+	\textit{echo-food-objects} & 54.0 & 1.4 & \ & 62.8 & 1.7 & \ 
+		& \textbf{8.8} & 2.2 & 4.0 & $3.5 \times 10^{-5}$\\
+	\textit{intertask-food-culture} & 48.8 & 1.6 & \ & 40.8 & 2.0 & \ 
+		& \textbf{-8.0} & 2.6 & -3.1 & $9.2 \times 10^{-4}$\\
+	\textit{frame-food-culture} & 45.8 & 2.0 & \ & 45.2 & 1.8 & \ 
+		& -0.6 & 2.6 & -0.2 & $0.41$\\
+	\bottomrule
+\end{tabular}
+}
+\caption{Statistics for the comparison of the proportions of food-related
+	labels between treatments of all experiments.  $s$: sample standard
+	deviation.
+}
+\label{table:proportion-food}
+\end{table}
+
+\subsection*{Calculation of relative specificity}
+In the main text we present results for the relative specificity of labels
+produced by two experimental treatments.  In performing this calculation,
+we used the wordnet corpus, which has a set of hypernym-hyponym relationships
+as described in the main text.  The first step in performing this calculation
+was therefore to map the words occurring from (the labels of) a given 
+experimental treatment onto the wordnet synsets.  In general, a given word
+form can have multiple meanings, and therefore maps onto multiple wordnet 
+synsets.
+
+The result of mapping the words from two treatments onto the wordnet 
+hypernym-hyponym graph two sets of counts, one set per treatment, 
+indicating the number of times a word from a given synset occurred among the
+labels of the treatment.  Then, for every synset in one treatment, we looked
+at the number of synsets in the other treatment that were more generic
+(reachable by following hypernym relations) less the number of words that
+were more specific (reachable by following hyponym relations).  This quantity
+tallied for all words in the original synset gives a (non-normalized) measure
+of the degree to which words from the first treatment are more specific
+than words from the second treatment, overall.  We then normalized this 
+quantity by the total number of possible comparisons between the words of
+one treatment to those of the other, where two words are considered comparable
+only if one word is the hypernym or hyponym of the other.  Hence, ``statue'' 
+and ``bread'' are not comparable, but ``pumpernickel'' and ``bread'' are.
+
+This calculation can be summarized by the following equation:
+\begin{equation}
+	S(P,Q) = \frac{
+		\sum_{w\in P}\sum_{v\in Q} \left(
+			\mathbf{1}_{[w>v]} - \mathbf{1}_{[v>w]} \right)
+	}{
+		\sum_{w\in P}\sum_{v\in Q} \left(
+			\mathbf{1}_{[w>v]} + \mathbf{1}_{[v>w]} \right)
+	},
+\end{equation}
+where $P$ and $Q$ are sets of synsets, and $\mathbf{1}_{[w>v]}$ evaluates
+to 1 if synset $w$ is more specific than (i.e. is a hyponym of) synset $v$.
+This measure counts the excess of cases where synsets from $P$ are more
+specific then synsets from $Q$, as a fraction of all comparable synset pairs.
+
+In computing this quantity between two treatments, we first computed it 
+using the labels attributed to a particular test task, and then
+averaged the result obtained in this way for each of the five test tasks.
+
+To assess statistical significance, we used the bootstrap method.
+For two given treatments $A$ and $B$, 
+119 workers were sampled from each with replacement, giving the bootstrap
+samples $A'$ and $B'$, and the relative specificity between these 
+was measured as described in \textsection S6.
+This was repeated 1000 times.  The 2.5 and 97.5 percentiles from the 
+bootstrap sample to create the 95\% confidence intervals.  If the confidence
+interval did not contain zero it indicates a statistically significant 
+difference in specificity.  The statistics for relative specificity 
+calculations are shown in Table~S\ref{table:specificity}.
+
+\begin{table}
+\centering{
+	\setlength{\tabcolsep}{4pt}
+\begin{tabular}{c c c c c c c c c c c}
+	\toprule
+	Experiment & $S$ & $S^*_\mathrm{lowCI}$ & $S^*_\mathrm{highCI}$ \\ 
+	\midrule
+	\textit{intertask-food-objects} & \textbf{13.6} & 9.1 & 17.8 \\
+	\textit{frame-food-objects} & \textbf{12.4}     & 7.6 & 17.0 \\
+	\textit{echo-food-objects} & \textbf{17.1}      & 12.1 & 21.9 \\
+	\textit{intertask-food-culture} & \textbf{19.6} & 13.7 & 25.4 \\
+	\textit{frame-food-culture} & \textbf{7.0}      & 2.1 & 15.3 \\
+	\bottomrule
+\end{tabular}
+}
+\caption{Relative specificity ($S$) of food-related words between the food- 
+	and non-food-exposed treatments of all experiments. 
+	Positive values indicates the food-exposed treatment was relatively more
+	specific; boldfaced values indicate a disparity in specificity that 
+	is statistically significant.  
+	$S^*_\mathrm{lowCI}, S^*_\mathrm{upCI}$: lower and upper
+	confidence intervals for $S$ based on the bootstrapping approach.  All
+values are expressed as percentages.}
+\label{table:specificity}
+\end{table}
+
+	\paragraph{Variance in food vocabulary size (lexical richness).}
+	The number of unique words in a text is strongly dependent on the size
+	of the text: as more text is sampled, previously unseen words continue
+	to be found, though at a decreasing rate.  
+	This means that the vocabulary size of a population of documents is 
+	not well-approximated by a sample.  Nevertheless the vocabulary sizes
+	obtained by taking equally-sized samples of two different populations
+	provides a means to compare the populations on an equal footing.
+
+	Taking the difference between one sample's vocabulary and the 
+	other gives us a measure of their difference in vocabulary size, but 
+	the variance of this measure needs to be characterized to know whether
+	there is a significant difference.
+
+	To test whether one sample has a (statistically) significantly larger
+	vocabulary size than another, we adopt the null hypothesis that they
+	have the same vocabulary, and pool the documents sampled from both 
+	populations together.  We then randomly partition the pooled sample
+	back into two balanced sets and take the difference in the sets' 
+	vocabulary sizes.  This models the difference that would be observed
+	under the null hypothesis that the documents are drawn from the same
+	population.  We repeat the pooling and partitioning of the samples
+	1000 times to generate a bootstrap sample of the difference in 
+	vocabulary sizes under the null hypothesis.  The 
+	2.5th and 97.5th percentiles of the bootstrap sample then serve as the
+	critical values of vocabulary size-difference that would justify 
+	rejection of the null hypothesis that the original samples have the same 
+	vocabulary size.
+
+	Statistics for these hypothesis tests are shown in 
+	Table~S\ref{table:vocab}.
+
+\begin{table}
+\centering{
+\begin{tabular}{c c c c c c c }
+	\toprule
+	\multirow{2}{*}{Experiment} & \multicolumn{2}{c}{$|V|$} 
+		 & \ & \multicolumn{3}{c}{$(\%)$} \\ \cline{2-3} \cline{5-7}
+	& food trtmt. & other trtmt. & \ & $\Delta|V|$ & $\Delta|V|^*_{low}$
+		& $\Delta|V|^*_{high}$  \\
+	\midrule
+	\textit{intertask-food-objects} & 297 & 247 & \ 
+		& \textbf{20.2} & -10.7 & 11.5 \\
+	\textit{frame-food-objects} & 296 & 261 & \ 
+		& \textbf{13.4} & -9.7 & 10.1 \\
+	\textit{echo-food-objects} & 316 & 280 & \ & 
+		\textbf{12.9} & -11.8 & 11.1 \\
+	\textit{intertask-food-culture} & 289 & 244 & \ 
+		& \textbf{18.4} & -11.4 & 11.6 \\
+	\textit{frame-food-culture} & 318 & 332 & \ & -4.2 & -11.9 & 11.2 \\
+	\bottomrule
+\end{tabular}
+}
+\caption{
+	Statistics for the measurement of vocabulary size difference, for each
+	experiment, between the food and non-food treatments. $|V|$: vocabulary
+	size; $\Delta|V|$: vocabulary size of non-food less food treatments;
+	$\Delta|V|^*_{low}, \Delta|V|^*_{low}$: lower and upper critical values
+	for statistically significant $\Delta|V|$, at $\alpha=0.05$, 
+	based on bootstrapping.  
+	Boldfaced values for $\Delta|V|$ are statistically significant.
+}
+\label{table:vocab}
+\end{table}
+
 \end{document}

### 2015-01-22 src/analysis.py

@@ -35,9 +35,11 @@ import os
 import copy
 import csv
 from scipy.stats import chi2_contingency as chi2
+from scipy.stats import norm
 
 CORRECTIONS_PATH = 'data/new_data/dictionaries/with_allrecipes/'
 DICTIONARY_FNAMES = ['dictionary_1.json', 'dictionary_2.json']
+IMAGE_NAMES = ['test%d' %i for i in range(5)]
 
 # Number of stardard deviations equivalent to the % condifdence for a 
 # normal variate
@@ -1175,6 +1177,142 @@ def get_k_star(n, alpha):
 	return k_star
 
 
+def get_all_theta_stats_per_image(
+		read_fname='data/new_data/l1.json',
+		as_latex=False
+	):
+	N=238
+	data = json.loads(open(read_fname).read())
+	this_data = data['exp2.task']
+
+	avg_accuracies = [
+		np.mean([this_data[img][i] for img in IMAGE_NAMES]) 
+		for i in range(5)
+	]
+
+	theta_stats = [get_theta_stats(N, aa) for aa in avg_accuracies]
+
+	if not as_latex:
+		return theta_stats
+
+	latex_out = ''
+	for ts in theta_stats:
+		latex_out += '%d & %d & %d & %f & %f & %f \\\\\n' % (
+			ts['n'], ts['x'], ts['x_star'], ts['theta'], ts['theta_low'],
+			ts['theta_high'])
+
+	return latex_out
+
+def calc_specificity_stats():
+
+	specificity_keys_labels = [
+		('task1', 'task1', 'intertask-food-objects'),
+		('frame1', 'frame1', 'frame-food-objects'),
+		('echo', 'echo', 'echo-food-objects'),
+		('task2', 'task2', 'intertask-food-culture'),
+		('frame2', 'frame2', 'frame-food-culture'),
+	]
+
+	latex_out = ''
+	for key, label, exp_name in specificity_keys_labels:
+		fh = open('data/new_data/specificity/specificity_%s.json' % key)
+		data = json.loads(fh.read())
+
+		S = 100 * data['mean']
+		upper_CI = abs(100 * data['upper_CI'])
+		lower_CI = abs(100 * data['lower_CI'])
+
+		latex_out += '%s & %2.1f & %2.1f & %2.1f \\\\\n' % (
[…]

### 2015-01-22 src/data_processing.py

@@ -20,6 +20,8 @@ from random import shuffle
 from nltk.corpus import wordnet as wn
 import nltk
 
+# ensure that we don't include the
+from ignore_workers import workers_to_ignore
 
 def get_correct_treatments(image_num, pos):
 	'''
@@ -164,6 +166,9 @@ class SimpleDataset(object):
 		# state variables
 		self.data = defaultdict(lambda: [])
 		self.worker_ids = set()
+		self.workers_to_ignore = (set() if which_experiment==1 
+			else workers_to_ignore)
+		self.these_worker_ids = set()
 		self.vocab_list = []
 		self.vocab_counts = Counter()
 		self.num_docs = 0
@@ -190,6 +195,12 @@ class SimpleDataset(object):
 		# what is the min number of examples in each class?
 		if truncate_to is None:
 			truncate_to = min([len(self.data[idx]) for idx in self.data])
+
+		print 'truncated to: %d' % truncate_to
+		for idx in self.data:
+			if len(self.data[idx]) == truncate_to:
+				print idx
+
 
 		# truncate all data (randomly) to even out number of examples
 		for idx in self.data:
@@ -266,6 +277,9 @@ class SimpleDataset(object):
 		'''
 
 		if worker_id in self.worker_ids:
+			return True
+
+		if worker_id in self.workers_to_ignore:
 			return True
 
 		self.worker_ids.add(worker_id)
@@ -359,6 +373,8 @@ class SimpleDataset(object):
 			# we only load data for the desired classes
 			if class_idx not in self.class_idxs and self.class_idxs != 'all':
 				continue
+
+			self.these_worker_ids.add(record['WorkerId'])
 
 			# we look at the position where the desired images are found
 			# note that the images are permuted based on treatment (class)

### 2015-01-22 src/new_plots.py

@@ -170,7 +170,7 @@ def plot_specificity(
 		for p in pairs
 	]
 	Y_err = [
-		(food_data[p[0]]['std'] + food_data[p[1]]['std'])*100 
+		np.sqrt( food_data[p[0]]['std']**2 + food_data[p[1]]['std']**2 )*100 
 		for p in pairs
 	]
 	X_0 = range(len(Y_0))

### 2015-01-29 docs/publications/2014.09_SCIENCE/man.tex
proof supplementary material (upgrade figs)

@@
 \newcolumntype{s}{D{.}{.}{1.4}}
+
+\usepackage{arydshln}
 
@@
 and raises questions about what other cognitive biases might
-affect microtask work, and how prevelant induced bias might be.
+affect microtask work, and how prevalent induced bias might be.
 
@@
 outputs depend on the history of their inputs.  Reproducibility and 
-path-independance are crucial properties of the components in a 
-computing architecture, so it to maintaning the view of the HPU computing 
+path-independence are crucial properties of the components in a 
+computing architecture, so it to maintaining the view of the HPU computing 
 architecture, necessitates a better understanding of the computational 
@@
 
-%\setlength{\tabcolsep}{2pt}
-%\begin{table}[t]
-%\centering
-%\begin{tabular}{ c c c c c }
-%		\hline \noalign{\smallskip}
-%		\multicolumn{3}{c}{\textbf{Treatment name}} & \parbox[c]{1.4cm}{\centering \textbf{Frame}} & \parbox[c]{1.3cm}{\centering \textbf{Initial\\ tasks}}	\\ 
-%
-%		\noalign{\smallskip} \hline \noalign{\smallskip}
-%
-%		\multirow{6}{*}{ \parbox[c]{0.8cm}{ \phantom{XX} exp1}} 
-%			& \multirow{2}{*}{task1} & food & none & food\\
-%			& & obj & none & objects\\
-%
-%			\noalign{\smallskip} \cline{2-5} \noalign{\smallskip}
-%			& \multirow{2}{*}{frame1} & food & food & none\\
-%			& & obj & objects & none\\
-%
-%			\noalign{\smallskip} \cline{2-5} \noalign{\smallskip}
-%			& \multirow{2}{*}{echo1} & food & food & none\\
-%			& & obj & objects & none\\
-%
-%		\noalign{\smallskip} \hline \noalign{\smallskip}
-%
-%		\multirow{4}{*}{\parbox[c]{0.8cm}{exp2}} 
-%			& \multirow{2}{*}{task2}  &  food & none & food\\
-%			& 	&  cult & none & culture\\
-%			\noalign{\smallskip} \cline{2-5} \noalign{\smallskip}
-%			& \multirow{2}{*}{frame2} & food & food & food\\
-%			& 	& cult & culture & food\\
-%
-%		\noalign{\smallskip} \hline  
-%	\end{tabular}
-%
-%	\caption{ 
-%		We use the treatment names shown to refer to specific sections of 
-%		the experimental data.
-%	}
-%	\label{table:treatments}
-%\end{table}
-
 Using a na\"ive Bayes classifier\footnote{
@@
 origin\footnote{
-	Though we attempted to choose more globalized foods, the initial tasks 
+	Though we attempted to choose foods with less specific or iconic cultural
+	associations, the initial tasks 
 	in \textit{intertask-food-culture} are arguably still of
@@
 \renewcommand{\tablename}{Table S\!\!}
+\renewcommand{\theequation}{S\arabic{equation}}
 \setcounter{figure}{0}
 \setcounter{table}{0}
+\setcounter{equation}{0}
 
@@
 \paragraph{Microtask setup.}
-Altogether the experiments presented here consisted of data from 3200 HITs 
-(bundles of 10-image labeling tasks).  In all experiments, each treatment
-consisted of results from at least 119 workers.  
-For the purpose of statistical calculations,
-treatments having more than 119 workers were subsampled, producing a uniform
-sample size accross all treatments.  The \textit{food} and \textit{objects}
-treatments in the \textit{intertask-food-objects} experiment were further
-broken down into sub-treatments (each containing at least 119 workers),
-corresponding to different orderings of the test tasks.  These alternative
-orderings were obtained by rotation of the test tasks 
-(i.e. moving all tasks forward by one position, and making the last task 
-become the first test task).  This ensured that each test task appeared in
-each of the five test-task positions.
-
-The HITs (as defined in the main text) for all treatments were presented as 
-a series of slides.  The first 
-slide consisted of a brief set of instructions.  In framing-treatments, a 
-framing slide was shown immediately after the instructions, see 
-Fig. S\ref{fig:hit_preamble}.  In intertask-treatments, a set of initial
-tasks were presented (and no framing slide).  Following the
-framing slide or initial tasks, the test-tasks were presented.
-
-All initial and test tasks had the format shown in 
-Fig.~S\ref{fig:hit_preamble}: an image taking up most of
-the task pane, with five text inputs and a ``next'' button.  Images were
-presented in this way, one at a time. 
-For treatments having initial tasks, the test
-tasks followed seemlessly, and no distinction was made between the test 
-tasks and the initial tasks.
-
-In an attempt to increase the strength of framing, we included the
-\textit{echo-food-objects} treatment, in which, during the framing slide,
-the worker was required to echo the frame using a combo-box input.  The
-instructions, both kinds of framing slide (simple and echoed), 
-and an example task slide, are shown 
-in Fig.~S\ref{fig:hit_preamble}.
-
-Given the setup described above, the only tasks that workers in framing 
-treatments perform are the test tasks, whereas in the 
-intertask-treatments, the test tasks were performed as tasks
-5 through 10.  
-It could be argued that a better comparison would be achieved
-by having all workers perform some initial tasks, and simply ensuring that
-the initial tasks are \textit{not} varied between framing treatments. 
-We took this approach in the experiment 
-\textit{frame-food-culture}, in which workers performed the same 
-initial tasks containing images that depicted food in both the \textit{food}
-and \textit{culture} treatments.  If anything, this appears
-to have reduced the strength of framing for that experiment.
+\begin{table}
+\centering
+\setlength{\tabcolsep}{2pt}
+\begin{tabular}{c c c c c c}
+\toprule
+Experiment & \parbox[c]{3.8cm}{\centering{Priming modality}} & Treatment & Frame & 
+	Initial tasks & \parbox[c]{2.0cm}{\centering{Test tasks}} \\
+\midrule
+\multirow{2}{*}{\textit{intertask-food-objects}} 
+& \multirow{2}{*}{initial tasks} & \textit{food} & none 
+	& Fig.~S\ref{fig:task1:food} 
+	& \multirow{2}{*}{Fig.~S\ref{fig:task1:test}\textsuperscript{e}} \\
+& & \textit{objects} & none & Fig.~S\ref{fig:task1:obj} & \\
+
+\noalign{\smallskip}
+\hdashline
+\noalign{\smallskip}
+
+\multirow{2}{*}{\textit{frame-food-objects}} 
+& \multirow{2}{*}{framing} & \textit{food} 
+	& ``food''\textsuperscript{a}
+	& none & \multirow{2}{*}{Fig.~S\ref{fig:task1:test}} \\
+& & \textit{objects} 
+	& ``objects''\textsuperscript{b}
+	& none & \\
+
+\noalign{\smallskip}
+\hdashline
+\noalign{\smallskip}
+
+\multirow{2}{*}{\textit{echo-food-objects}} 
+& \multirow{2}{*}{echoed framing} & \textit{food} 
+	& ``food''\textsuperscript{a}
+	& none & \multirow{2}{*}{Fig.~S\ref{fig:task1:test}} \\
+& & \textit{objects} 
+	& ``objects''\textsuperscript{b}
+	& none & \\
+
+\noalign{\smallskip}
+\hdashline
+\noalign{\smallskip}
+
+\multirow{2}{*}{\textit{intertask-food-culture}} 
+& \multirow{2}{*}{initial tasks} & \textit{food} 
+	& none
+	& Fig.~S\ref{fig:task2:food} 
+	& \multirow{2}{*}{Fig.~S\ref{fig:task2:test}} \\
+& & \textit{objects} 
+	& none & Fig.~S\ref{fig:task2:cult} & \\
+
+\noalign{\smallskip}
+\hdashline
+\noalign{\smallskip}
+
+\multirow{2}{*}{\textit{frame-food-culture}} 
+& \multirow{2}{*}{framing} & \textit{food} 
+	& ``food''\textsuperscript{c}
+	& Fig.~S\ref{fig:frame2:ingr} 
+	& \multirow{2}{*}{Fig.~S\ref{fig:task2:test}} \\
+& & \textit{objects} 
+	& ``culture''\textsuperscript{d} 
+	& Fig.~S\ref{fig:frame2:ingr} & \\
+
+\bottomrule
+\end{tabular}
+\caption{
+	Description of experiments performed.  Each experiment had two treatments
+	which differed either in the initial tasks shown or the framing used 
+	(the priming modality).  
+	During echoed framing, the worker had to respond to the framing language
+	using a combo box input (see Fig.~S\ref{fig:hit_preamble}C).
+	\newline\textsuperscript{a} ``Funded by the laboratory for the visual 
+		perception of Food and Ingredients''
+	\newline\textsuperscript{b} ``Funded by the laboratory for the visual 
+		perception of Objects and Tools''
+	\newline\textsuperscript{c} ``The purpose of this study is to understand the visual perception of Food and Ingredients''
+	\newline\textsuperscript{d} ``The purpose of this study is to understand the visual perception of Objects and Tools''
+	\newline\textsuperscript{e} ``This research is proudly funded by The National 
+		Foundation for Nutrition Awareness''
+	\newline\textsuperscript{f} ``This research is proudly funded by The Global 
+		Foundation for the Recognition of Cultures''
+	\newline\textsuperscript{g} Both treatments were divided into five 
+	sub-treatments having a different permutation of test tasks.
+}
+\label{table:experiments}
+\end{table}
 
@@
 	\includegraphics[scale=0.8]{figs/tasks.pdf}
-	\caption{Examples of A) instructions; B) a frame, as shown in 
-		\textit{frame1:obj}, and similar to those shown in 
-		\textit{frame1:food} and \textit{frame2:food}, and 
-		\textit{frame2:cult};  
-		C) an echoed frame, as used in \textit{echo1:obj}, and similar to that
-		used in \textit{echo1:food}; and D) an 
-		example of an image-labeling task.
+	\caption{Examples of (A) task instructions, (B) a framing slide
+		(C) an echoed framing slide, and (D) an image-labeling 
+		task.
 	}
@@
 \end{figure}
+
+The work presented in the main text consisted of six experiments involving
+HITs (bundles of microtasks) performed on Amazon's Mechanical Turk platform.  
+Each experiment was divided into two treatments.  Treatments for a given 
+experiment differed with respect to a particular priming modality, which 
+served as the independent variable
+(as specified in Table~\ref{table:experiments}).  
+The HITs for treatments of the same experiment always involved the same
+test tasks (the last five tasks in the HIT),
+the results of which served as the dependent variable.
+
+All HITs were presented as a series of slides.  The first 
+slide consisted of a brief set of instructions.  For HITs that included 
+framing, a framing statement was shown on a slide immediately after the 
+instructions (see Fig. S\ref{fig:hit_preamble}B and C).  
+Initial tasks, when included, followed next.  The initial tasks consisted of 
+a series of 5 slides, each containing an image-labeling task like the one 
+shown in 
+Fig.~S\ref{fig:hit_preamble}D.  Finally, for all HITs, five slides were shown
+containing test tasks, in the same format as the initial tasks.
+
+Workers were randomly assigned to the treatments, and 
+a given worker could only complete one HIT related to this study.  
+In \textit{intertask-food-culture}, the \textit{food} and \textit{culture}
+treatments were both divided into five sub-treatments, 
+in which the test tasks were permuted.  
+The permutations were obtained by rotating 
+the order shown in Fig.~\ref{fig:task1:test} by different amounts. 
+For example, rotating by one position involves moving the first image to the 
+second position, the second image to the third position, and so on, and 
+moving the last image to the first position.  
+The five different possible rotations were used for the five 
+sub-treatments.  This enabled us to study the effects on each image when
+it occurred in different positions relative to the initial tasks.
 
@@
 S\ref{fig:task1:obj} (\textit{objects} treatment).
-We selected images for the initial tasks that show either food or objects, 
-according to the treatment in which they were used.  
 We took care to exclude objects from
-the food-images (except in some cases a dish supporting the food), and 
+the food-images (except for the dish supporting the food in some cases), and 
 to exclude food from the object-images.  The images used for the test tasks
@@
 respectively reflect depict food and culture.
-
 Naturally, since food is a very
@@
 and images depicting food inevitably also depict culture.
-The fact that the inital-task images for the food treatment of 
-\textit{intertask-food-culture} do also depict culture
-will only tend to make them more similar to those from the \textit{culture}
-treatment, which would tend to \textit{reduce} the severity of intertask 
-effects.  In any case, since we still found strong intertask effects, 
-the presence of culture in the food-related initial images of 
+However, the fact that the images for the initial tasks in the 
+\textit{food} treatment 
+of \textit{intertask-food-culture} also depict culture
+will only tend to make the \textit{food} and \textit{culture}
+treatments more similar. 
+This would tend to reduce the severity of intertask 
+effects, but we nevertheless still observed strong intertask effects.
+Thus, the presence of culture in the food-related initial images of 
 \textit{intertask-food-culture} does not seem to have been problematic.
@@
 
+\begin{figure}
+	\begin{center}
+		\includegraphics{figs/task2-ingr.pdf}
+	\end{center}
+	\caption{
+		Images used in initial tasks for \textit{frame-food-culture} 
+		(both for the \textit{food} and \textit{culture} treatments).
+		The numbers show the order in which the images were presented to 
+		workers.
+	}
+	\label{fig:frame2:ingr}
+\end{figure}
+
+\paragraph{Framing.}
+We framed tasks by including a message, near the beginning of the HIT, that 
+suggested the purpose of the tasks.
+The precise language used is shown in 
+Table~S\ref{table:experiments}, and an example of a framing slide is shown in
+Fig.~S\ref{fig:hit_preamble}(B and C).  In \textit{frame-food-objects}
+and \textit{frame-food-culture}, the framing language was based on
+naming the (fictitious) entity running the study, for example
+``The Global Foundation for the Recognition of Cultures'',
+or ``Laboratory for the visual perception of Objects and Tools''.
+In \textit{echo-food-objects}, we stated the purpose explicitly 
+(``The purpose of this task is \dots''), and then required the worker to
+echo back the purpose of the task by selecting it from a combo box
+Fig.~S\ref{fig:hit_preamble}(C).
+
+This \textit{echo-food-objects} treatment certainly produced the 
+strongest effect of the framing experiments, but it is difficult to say 
+whether that should be considered indicative of framing textit{per se}.  
+The explicitness of the statement would tend to make it more like an 
+instruction in its effect.  Perhaps more importantly, requiring the worker
+to re-iterate the framing statement by means of a combo-box emphasizes 
+the framing to a greater degree than the instructions, which would probably
+tend to give the impression that the framing statement is intended as an
+instruction to be acted upon.  Framing or not, the fact that initial tasks
+can produce an effect that is on par with that of \textit{echo-food-objects}
+shows just how strong intertask effects are.
+
+In \textit{frame-food-objects} and \textit{echo-food-objects}, we did not
+include any initial tasks, meaning that the test tasks followed the framing
+slide immediately.  One could argue that a better comparison would be achieved
+including initial tasks even for framing experiments (but keeping the
+initial tasks constant while varying the framing language), since the worker
+would be ``warmed up'' before performing the test tasks, as is the case for
+the experiments investigating the effect of initial tasks. 
+We therefore adopted this approach in the experiment 
+\textit{frame-food-culture}, in which workers performed the same 
+initial tasks containing images that depicted food in both the \textit{food}
+and \textit{culture} treatments.  It would seem that the framing effect in 
+\textit{frame-food-culture} was reduced by the initial tasks, possibly because
+intertask effects tend to override framing. Further experimentation 
+would be necessary to be sure, but this was not the purpose of our study.
+
 \subsection*{Testing for intertask and framing effects using $\chi^2$}
-To test whether intertask and framing effects induced statistically 
-significant changes in word frequencies, we assembled a contingency table
-for each experiment, containing the frequencies of words in each treatment.  
-Any words that appeared less than ten times for
-an experiment (i.e. appearing less than five times averaged over each 
-treatment)
-were lumped together into a separate `OTHER' category, to ensure validity
-of the test.  The degrees of freedom, test statistic, and $p$-values were
-then calculated according to Pearson's $\chi^2$ test, using 
-Yate's correction.  Results are tabulated in Table~S\ref{table:chi2}.
-With the exception of \textit{frame-food-culture}, all experiments showed s
-ignificant changes in word-frequencies in response
-to the task or framing exposures, at $\alpha=0.05$, leading us to 
-reject the null hypothesis that the priming exposures had no effect.
-
-The use of Pearson's $\chi^2$ test has been criticized in linguistic 
-applications, due to the finding that many corpuses are not themselves
-homogeneous \cite{kilgarriff1996comparing}.  
-This results from the fact that corpuses are made of many
-distinct texts, together with the fact that words tend to come in bursts.
-When a rare word is encountered in a given text, it is much more likely
-to be encountered again in the same text, which making the word's frequency
-within the text far from the average.  As a result,
-if a corpus is randomly split, putting half of the texts in one set, 
-and half in another, there can be a significant non-homogeneity between the 
-two halves, when tested using Pearson's $\chi^2$ test.  Thus, it has 
-been argued that finding two
-corpuses to be different according to a $\chi^2$ test might simply be an 
-artifact of the corpus' own inhomogeneity.
-
-This concern does not apply to our case, because the ``texts'' are 
-individual responses from workers, which will not, in general, be subject to 
-the burstiness phenomenon.  Nevertheless, to test this, 
-we randomly divided the workers 
-from each experimental treatment into two sets, and tested the homogeneity 
-between these sets.  Results are tabulated in Table~S\ref{table:chi2_within}, 
-and show that treatments 
-\textit{are} homogeneous.  Thus, the lack of homogeneity \textit{between} 
-the treatments of given experiments can be attributed to the framing / 
-intertask effects.
 
@@
  & \textit{objects} & 65 & 53.2 & $0.85$\\
+
 \noalign{\smallskip}
+\hdashline
 \noalign{\smallskip}
+
 \multirow{2}{*}{\textit{frame-food-objects}} & \textit{food} & 67 & 41.3 & $0.99$\\
  & \textit{objects} & 62 & 66.9 & $0.31$\\
+
 \noalign{\smallskip}
+\hdashline
 \noalign{\smallskip}
+
 \multirow{2}{*}{\textit{echo-food-objects}} & \textit{food} & 66 & 40.9 & $0.99$\\
  & \textit{objects} & 66 & 35.6 & $1.0$\\
+
 \noalign{\smallskip}
+\hdashline
 \noalign{\smallskip}
+
 \multirow{2}{*}{\textit{intertask-food-culture}} & \textit{food} & 62 & 65.9 & $0.34$\\
  & \textit{culture} & 68 & 57.2 & $0.82$\\
+
 \noalign{\smallskip}
+\hdashline
 \noalign{\smallskip}
+
 \multirow{2}{*}{\textit{frame-food-culture}} & \textit{food} & 57 & 49.6 & $0.75$\\
  & \textit{culture} & 64 & 55.1 & $0.78$\\
-\noalign{\smallskip}
-\noalign{\smallskip}
+
 \bottomrule
@@
 
-\subsection*{Measuring intertask and framing effects.}
+To test whether intertask and framing effects induced statistically 
+significant changes in word frequencies, we assembled a contingency table
+for each experiment, containing the frequencies of words in each treatment.  
+Any words appearing less than ten times for
+an experiment (i.e. one whose expected frequency would be less than five in a 
+given cell of the contingency table)
+were lumped together into a separate `OTHER' category, to ensure validity
+of the test.  The degrees of freedom, test statistic, and $p$-values were
+then calculated according to Pearson's $\chi^2$ test, using 
+Yate's correction.  Results are tabulated in Table~S\ref{table:chi2}.
+With the exception of \textit{frame-food-culture}, all experiments showed 
+significant changes in word-frequencies in response
+to the task or framing exposures, at $\alpha=0.05$, leading us to 
+reject the null hypothesis that the priming exposures had no effect.
+
+The use of Pearson's $\chi^2$ test has been criticized in linguistic 
+applications, due to the finding that many corpera are not themselves
+homogeneous \cite{kilgarriff1996comparing}.  
+This results from the fact that corpera are made of many
+distinct texts, together with the fact that words tend to come in bursts.
+When a rare word is encountered in a given text, it is much more likely
+to be encountered again in the same text. This means that
+frequencies within given texts are often far from the average, causing 
+corpera to be heterogeneous.
+As a result, if a corpus is randomly split, putting half of the texts in one 
+set, and half in another, there can be a significant non-homogeneity between 
+the halves (when tested using Pearson's $\chi^2$ test).  Thus, finding two
+corpera to be different according to a $\chi^2$ test might not 
+indicate that they are meaningfully different.
+
+This concern does not apply to our case, because the ``texts'' are 
+individual responses from workers, which will not, in general, be subject to 
+the ``burstiness'' phenomenon.  Nevertheless, to test this, we randomly 
+divided the workers from each experimental treatment into two sets, and 
+tested the homogeneity 
+between these sets.  Results are tabulated in Table~S\ref{table:chi2_within}, 
+and show that treatments 
+\textit{are} homogeneous.  Thus, the lack of homogeneity \textit{between} 
+the treatments of given experiments can be rightly attributed to the 
+framing / intertask effects.
+
+\subsection*{Measuring the extent of intertask and framing effects}
 
@@
 The following is an illustrative example to show why it is important to 
-have a measure of effect size, like $\theta$, in addition to effect 
-significance, like $\chi^2$.
+have a measure of effect size, like $\theta$, in addition to a test of the 
+null hypothesis like $\chi^2$.
 Suppose that we have a very slightly unfairly weighted coin, which turns
-up heads ($x=\mathbf{H}$) more often than expected by one part in one hundred:
-$\Pr\{x=\mathbf{H}\} = 0.501$. Such a coin would be fine for many 
-practical purposes, like deciding who buys lunch.  We could
-perform a $\chi^2$ test to determine if the coin is biased, by flipping 
-it 100 million times, while doing the same with a coin we know is fair.
+up heads ($X=\mathbf{H}$) more often than expected by one part in one hundred:
+$\Pr\{X=\mathbf{H}\} = 0.501$. Such a coin is only mildly biased, and would 
+be fine for many purposes.  If we did not know that the coin was
+biased, we could determine whether it was biased by flipping the coin in 
+question, along with a coin we know to be fair, many times 
+(say 100 million times), and then using a $\chi^2$ test to decide whether 
+the two coins have the same probability of turning up heads.
 Simulating this with a random number generator yields the results shown
-in Table~S\ref{table:coin}, and results from a $\chi^2$ test of the 
+in Table~S\ref{table:coin}.  Results from a $\chi^2$ test of the
 hypothesis that the two coins have the same probability of turning up heads 
@@
 	Simulated counts of heads ($N_\mathbf{H}$) and tails ($N_\mathbf{T}$)
-	occurences, for a fair coin, and a coin biased to have a probability
+	occurrences, for a fair coin, and a coin biased to have a probability
 	of turning up heads of 0.501.
@@
 Even though the $\chi^2$ test shows, with tremendous statistical 
-significance, that the unfair coin is indeed unfair, the actual extent
-of bias is small, 
+significance, that the unfair coin is indeed unfair, we know that actual 
+extent of bias is small, 
 $\theta = \frac{1}{2}\left( |0.501 - 0.499| + |0.499 - 0.501| \right) = 0.002$.
@@
 \paragraph{Statistical approaches to measuring bias.}
-Recall that in Eq.~\ref{eq:theta} in the main text, we defined the
-extent of bias that exists between two groups of workers to be $\theta$:
-$$
+Recall that Eq.~\ref{eq:theta} in the main text defined the
+extent of bias between the microtask responses from two groups
+of workers to be $\theta$ (reproduced here):
+\begin{equation}
 	\theta = \frac{1}{2}\sum_{x \in X} \left| p_0(x) - p_1(x) \right|,
-$$
-where $p_0(x)$ and $p_1(x)$ represent the probability mass functions
-for responses from two differently treated populations of workers.  
-Let us denote these two populations by $P_0$ and $P_1$.
-As mentioned, this is a measure of the divergence between $p_0$ and $p_1$ 
-which is called either the \textit{total variation} or the 
+\end{equation}
+where $p_0(x)$ and $p_1(x)$ represent the probability that a worker from
+treatment 1 (respectively 2) produces response $x$, from a set of possible
+responses $X$.  As defined, $\theta$ corresponds to a measure of divergence 
+between $p_0$ and $p_1$, called the \textit{total variation distance} or the
 \textit{L1-distance}.
@@
 $\hat{p}(x) = \frac{N_x}{N}$, and then estimate $\theta$ 
-using these frequencies: 
+using these frequencies\cite{batu2013testing}: 
 $\hat{\theta} = \sum_{x \in X}|\hat{p}_1(x) - \hat{p}_2(x)|$.  
-However, this method tends to drastically overestimate $\theta$.
-Recently progress has been made on this problem, and two algorithms have 
-been proposed to estimate the L1-distance between distributions
-given only samples.  \td{cite these} But these methods provide only asymptotic guarantees
-which cannot be directly applied to our case.  However, machine learning
-approaches provide a general alternative that we describe in the next 
-section.
+However, this method tends to drastically overestimate $\theta$
+\cite{val-thesis}.
+Recently there has been theoretical progress on this problem.
+An estimator of L1-distance, and a tests of whether the L1-distance is
+greater than a specified threshold, have been proposed 
+\cite{val-thesis,batu2013testing,chan2014optimal}.  
+These methods have excellent theoretical convergence guarantees, but
+cannot easily be used to establish estimates with confidence intervals or 
+perform hypothesis tests for a given fixed sample size.  
+We therefore turn to an alternative approach using machine learning. 
+While this method yields an estimator that converges more slowly,
+it is straightforward to establish confidence intervals for estimates and 
+use the estimator in hypothesis tests.
 
@@
 the worker belongs ($P_0$ or $P_1$), will do so with an accuracy, $\eta$,
-that is bounded according to Eq.~\ref{l1}, which is reproduced here:
-$$
+that is bounded according to Eq.~\ref{l1} from the main text 
+(reproduced here):
+\begin{equation}
 	\theta \geq 2\eta - 1.
-$$
+	\label{eq:sup:l1}
+\end{equation}
 
@@
 to:
-$$
+\begin{equation}
 \eta = \mathrm{E\{V(P_0, P_1, \mathcal{A})\}} 
 	= \mathrm{Pr}\{V(P_0, P_1, \mathcal{A})=1\}.
-$$
+\end{equation}
 
@@
 The probability that the classifier guesses correctly, given a validation
-test in which the resonse $x$ was chosen, is therefore:
+test in which the response $x$ was chosen, is therefore:
 \begin{align}
+	\begin{split}
 	\mathrm{Pr}\{V = 1 | x' = x \} 
@@
 		&= \frac{p_1(x)}{p_0(x) + p_1(x)}.
+	\end{split}
 \end{align}
@@
 \begin{align}
+	\begin{split}
 	\mathrm{Pr}\{V=1 | x' = x \} 
@@
 		{ p_0(x) + p_1(x) }.
+	\end{split}
 \end{align}
-We can rewrite:
+Note that we can rewrite $\max\big(p_0(x),p_1(x)\big)$:
 \begin{align}
@@
 \begin{align}
+	\begin{split}
 	\eta^* &= \mathrm{Pr}\{V=1\} \\
@@
 		\implies \theta &= 2\eta^* - 1.
+	\end{split}
 \end{align}
@@
 \paragraph{Using cross-validation accuracy to lower-bound bias.}
-	In order for Eq.~\ref{l1} to be applicable, it is necessary to obtain
-	an unbiased estimate of a classifier's accuracy.  One well-known
-	pitfall in measuring classifier accuracy is to underestimate it due to 
-	over-fitting to the data used.  As an example, if one were to try 
-	a large number of classifiers, eventually one would find one that
-	classifies the data perfectly, even though it might non generalize to
-	new data.
-
-	It is customary to use part of a data set to optimize hyperparameters of
-	a model, and then test the model on as-yet unseen data.  In our case,
-	don't have enough samples in each treatment to do this.  Instead, for 
-	this reason, we make principled decisions for all of the options used
-	in our classifier, and then test it's accuracy using cross validation,
-	with no optimization performed on the data.  It was crucial for 
-	the statistical validity of our approach that we test our classifier on 
-	each datum only once, and report these results without any optimizations
-	of the classifier.
-
-	In performing the classification we had various options, and since we
-	could not optimize these choices, we made principled decisions based on
-	prior knowledge from text classification applications.  We describe the
-	options we faced and the choices we made below.
-
-	\textit{Spelling correction.}  Because we used free-text
-	entry for the labels, there was bound to be many spelling mistakes.
-	This would tend to reduce the accuracy of a classifier, because the 
-	entries ``bread'' and ``braed'' would be regarded as completely different
-	features, even though they clearly correspond to the same 
-	\textit{intended word}.  While no algorithm can determine a worker's 
-	intentions, it is possible to check words against a corpus, and, in the
-	case of a misspelled word, look for plausible corrections based on 
-	edit distance.
-
-	\textit{Lemmatization.}  In some cases it is helpful to simplify words 
-	before providing them to the classifier.  For example, the words 
-	``berries'' and ``berry'' only differ in number, but would normally be
-	treated as completely different features.  Lemmatization ensures that
-	nouns are in their singular form, which helps to eliminate variations in
-	labels that increase sparsity without conveying discriminative 
-	information.
-
-	\textit{Removal of stop-words.}  Certain very common words such as `the',
-	``to'', and ``it'' are extremely common but don't help discriminate a 
-	worker's exposure.  Removing these words is a common practice because
-	they otherwise introduce noise into the classifier learning process.
-
-	\textit{Splitting multiple words.}  Although workers were 
-	instructed to put one word per text input, many put multiple words.
-	Theoretically the original multi-word entry might bear additional 
-	information that could be useful in discerning a worker's exposure. 
-	In practice, it would be necessary for that word combination to recur,
-	which is unlikely.  Therefore we chose to split multi-word entries,
-	using the individual words as features.  This meant that the outputs of
-	some workers generated more features than those of others.
-
-	\textit{Preserving the location of labels.}  When workers completed image
-	labeling tasks, they had to fill five text inputs, which were stacked
-	vertically.  Presumably, they began with the top input and proceeded 
-	downwards.  It seems likely that exposure effects might influence the
-	\textit{order} in which workers apply labels, so when processing the 
-	labels we prepended an integer to indicate into which text input the 
-	label been input.  This meant that the classifier could distinguish
-	``bread'' entered into the first text input from ``bread'' entered into
-	the second.  A drawback is that this increases sparsity, preventing the
-	classifier from accounting for the fact that different though they are,
-	these entries should be treated similarly.  For this reason, we also
-	provided features to the classifier which did not encode the particular
-	input that had been used.  Thus, two workers that entered ``bread''
-	into different inputs would generate both a feature in common indicating
-	the use of the word ``bread'', as well as distinct features, indicating
-	entry of the word ``bread'' \textit{in a particular input}.
-
-	\textit{Preserving the connection between tasks and labels.}  In many
-	cases a particular label would appear in many tasks.  For example, the
-	word ``food'' appears in all test tasks.  It stands to reason that
-	exposure effects play out differently for different tasks, and that
-	the attribution of a particular label during one task provides different
-	information from the attribution of the same label during a different 
-	task.  So, as we did in the case of input location, we prepended labels
-	with the identity of the task in which they were added, so that the 
-	two otherwise identical labels added for different tasks were treated
-	by the classifier as unique features.  Unlike in the case of input 
-	position attribution, we didn't include raw labels unadorned with 
-	the task number.  Our rationale for this is that the task defines the 
-	context in which a label is applied, and so the elicitation of a label 
-	during one task represents a distinct output from the elicitation of the 
-	same label during a different task.
+	In order for Eq.~\ref{eq:sup:l1} to be applicable, it is necessary to 
+	obtain an unbiased estimate of a classifier's accuracy.  To do so it is
+	essential to test the classifier on data that were not used to build 
+	the classifier.  Generally, a portion of the data is used to test
+	optimize preprocessing, perform feature selection, and optimize 
+	classifier hyper-parameters, while keeping another portion of the data
+	set aside for validation.
+
+	In our case, samples are expensive, and must be divided between 18
+	experimental treatments, so we sought to keep as many samples available 
+	for validation
+	as possible.  For this reason, we made principled decisions 
+	between alternative preprocessing options and features, 
+	rather than spending samples to empirically test these options.  Making
+	suboptimal choices can only moderate the observed values 
+	of $\theta$, making our experiments more conservative. 
+	However, having more samples for validation tests enables us to estimate
+	those values more precisely.  
+	Using a Na\"ive Bayes classifier, which does not require hyper-parameters 
+	optimization, meant that we also did not need to spend samples on 
+	optimizing hyper-parameters.
+
+	Thus, no samples at all were used for optimizations.  We performed 
+	leave-one-out validation, which involves training a classifier using 
+	all but one sample, and then having the classifier guess the class
+	(in our case, the priming exposure) of the left-out sample.  This is 
+	repeated $n$ times, where $n$ is the pooled number of samples in both
+	classes, each time leaving out a different sample.
 
 \paragraph{Selection of the na\"ive Bayes classifier.}
-A great deal of work has been done in the application of classifiers to
-text documents, which provides the background for our choice of classifier.
-The Support Vector Machine (SVM) approach is known to perform well, better in 
-general than na\"ive Bayes.  However, three considerations drove us to use
-a na\"ive Bayes classifier in favor of SVM.
-
-First, we used 119 examples (workers) per treatment, but the number of 
-features
-for each worker (i.e. the number of distinct labels, or modifications 
-thereof produced in preprocessing), was generally in the thousands.  
-This tends to
-be problematic for many classifier algorithms, including SVM, because it
-leads to very high variance models, which manifests as overfitting and poor
-performance.  To deal with this, some approach to culling features is 
-generally used, but this raises the issue of how to decide the culling in 
-a principled manner, generally adding further hyperparameters which could
-be optimized.  However, one of the strengths of the na\"ive Bayes classifier
-is that it's performance is not generally degraded from the inclusion of 
-large numbers of features, even when the number of examples is comparatively
-small.  We expected this feature of the na\"ive Bayes classifier to be 
-advantageous in our case.
+We chose to use the na\"ive Bayes classifier as our basis for measuring 
+bias for three reasons.  First, we had 119 examples (workers) per class 
+(treatment), but thousands of distinct features 
+(i.e. the number of distinct words occuring in an experiment).  
+Having many more features than examples is problematic for many classifiers
+because, a large number of features leads to a high-variance, over-fit model
+resulting in poor performance.  But one of the strengths of the na\"ive 
+Bayes classifier is that it performs well even when the number of features
+exceeds the number of examples\cite{bickel2004, hastie2009elements}
 
 Second, the standard implementation of the na\"ive Bayes classifier has no 
-hyperparameters to optimize.  This allows us to forgo the common practice 
-of holding out a test set, and instead use cross-validation as a method to
-estimate the true classification error, \textit{since we did not perform
-any kind of model selection or optimization whatsoever using our data}.
-This point is crucial, because if we did optimize our classifier during 
-cross-validation, then the validation error would no longer provide an 
-unbiased estimate of the true classification error, but would instead lead
-to us over-reporting exposure effects.
+hyper-parameters to optimize. This meant that we did not need to use 
+samples for hyper-parameters optimization, which would reduce the number
+of samples available for validation tests to estimate $\theta$.
 
 Third, the na\"ive Bayes algorithm is based on an assumption that the 
-probability of observing one feature is independent from the observation
-of any other, \textit{when conditioned on the class}.  This
-\textit{conditional independence} assumption is generally made for
+observation one feature is independent from the observation of any 
+other, once we have conditioned on the class under observation 
+\cite{bishop2006} (i.e. the priming treatment).  This
+conditional independence assumption is made for
 pragmatic rather than theoretical reasons, and is rarely satisfied.  However,
-if it \textit{is} satisfied, then the na\"ive Bayes classifier is optimal.
-In our case, conditional independence means that, provided we know the 
-exposure of a worker, knowing one label they provided to an image does
-not in any way help us guess any other label for that image.  In most
-text documents, the existence of topics and language structure certainly
-violates the conditional independence of words.  But in our case, such 
-effects are less likely to carry from one text input to the next, and in the
-small space provided by five inputs, any overarching topics are likely to
-be in relation to the image itself, upon which we are conditioning.  In other
-words, we believe that, in our setup, conditional independence is better 
-satisfied than in most text classification contexts.  That being the case,
-one would not expect much improvement in using a more sophisticated algorithm,
-such as SVM.
+if it \textit{is} satisfied, then the na\"ive Bayes classifier is 
+optimal \cite{Zhang2004562}.  In most text documents, 
+the existence of long-range dependencies in language 
+violates the conditional independence of words: when a rare word is mentioned,
+it is more likely to be mentioned again, and topics introduced early in a
+text are likely to be revisited.
+But in our case, there is little opportunity for such effects.  Workers 
+generally do not use the same word in multiple labels for the same image. 
+Any overarching ``topics'' within the labels that workers use will tend to 
+relate to the test images, which are held in common.
+Therefore, in our setup, conditional independence is likely to be 
+a realistic approximation, and so the na\"ive Bayes classifier is likely to
+be closer to optimal than in other text classification applications.
 
@@
 	\includegraphics[scale=0.75]{figs/theta_sup.pdf}
-	\label{fig:theta_sup}
 	\caption{
@@
 	}
+	\label{fig:theta_sup}
 \end{figure}
@@
 
-Therefore there may exist a classifier that is 
-significantly better than the one used to generate our results.  Even before
-committing to a particular classifier algorithm, various decisions about
-preprocessing need to be made.  For example, we chose to remove stopwords,
-lemmatize, split multi-word labels, distinguish the input used to enter 
-labels, and correct spelling.  All of these decisions affect the classifier
-performance.  The particular classifier algorithm chosen also has a strong 
-effect.
-
-Since we did not have enough data to create a separate test set, we could not
-optimize these decisions.  Doing so would lead to the inflation of the 
-performance, which could then only be estimated using an independent test set.
-Instead, we made principled decisions as described above.
-
-Although we cannot optimize these decisions, it is appropriate to look at
-what affect these decisions had, post-hoc.  We reproduce the plot shown in 
-Fig.~\ref{fig:theta}A using different combinations of preprocessing options,
-and using both the na\"ive Bayes and an SVM classifier.
-
-Unlike the na\"ive Bayes classifier, it is necessary to tune the cost and 
-gamma hyperparameters of the SVM classifier, as well as choose a kernel.
-We used simulated annealing to optimize the cost and gamma settings in the
-classification of $task2:food$ vs $task2:cult$.  For this reason, we expect
-the bar for $task2$ in Fig.~S8G-J is likely to be an overestimate due to
-overfitting on those data.
-
-These plots show that the result shown in Fig.~\ref{fig:theta}A is 
-representative, and supports the validity of the lower bounds on the 
-exposures exposure effects presented in the main text, in terms of induced 
-L1-distance.
+Although we believe the na\"ive Bayes classifier is nearly optimal in this
+setting, some other classifier may exist that is significantly better than 
+the one used to generate our results.  Furthermore, various decisions about
+preprocessing and feature representation must inevitably be made also
+impact the classifier performance.  
+For example, we chose to correct spelling, remove stop-words,
+lemmatize words, and to distinguish which text-input was used to enter a 
+given label.  All of these decisions have some effect on classifier 
+performance.
+
+We chose not to optimize these decisions, since it would require the
+use of samples (worker-responses), which could then not be used in 
+cross-validation to measure $\theta$.  Nevertheless, it is
+appropriate to look at what affect these decisions had, \textit{post-hoc}.  
+We reproduce the plot from Fig.~\ref{fig:theta}A in the main text, 
+this time using different combinations of preprocessing options,
+and using both the na\"ive Bayes and an SVM classifier, in 
+Fig.~S\ref{fig:theta_sup}.
+
+Unlike the na\"ive Bayes classifier, when using SVM it is necessary to tune 
+the cost and gamma hyper-parameters of the SVM classifier, as well as choose 
+a kernel.  We used simulated annealing to optimize the cost and gamma settings
+data from \textit{intertask-food-culture}.  For this reason, the estimate
+of $\theta$ estimate for this experiment in 
+Fig.~S\ref{fig:theta_sup} (G to J) is inflated.
+
+These plots suggest that the values of $\theta$ obtained using the 
+na\"ive Bayes classifier and our particular choice of preprocessing steps, 
+as shown in in Fig.~\ref{fig:theta} of the main text, are representative.
 
@@
 The measurements of $\theta$ were based on the number of correct 
-classifications during validation tests.  We used leave-one-out validation,
-and count the number of correct classifications, $X$, which has a binomial
-distribution.  We take the null hypothesis that the classifier performs
+classifications during validation tests.  The number of correct 
+classifications, $X$, has a binomial distribution.  
+We take the null hypothesis that the classifier performs
 no better than chance, $X \sim \mathrm{Bin}(N,0.5)$, where $N$ is the number 
 of workers in both treatments of an experiment.  Then, the critical number 
-of correct classifications, $x^*$, in for a one-tailed hypothesis test with
+of correct classifications, $x^*$, for a one-tailed hypothesis test with
 significance $\alpha$ is:
@@
 \end{align}
-For the treatments in \textit{intertask-food-objects}, 5 different 
-permutations of each treatment was tested, and a different classifier was 
-built for each permutation.  For the sake of estimating the accuracy of 
-these classifiers, we assume that they have the same accuracy, which means
-that \textit{intertask-food-objects} has a larger number of validation tests
-(larger $N$), and for this hypothesis test we assume that $X$ has a normal 
-distribution, with $\mu=N/2$ and $\sigma = \frac{1}{2}\sqrt{N}$.
-
-To determining the confidence intervals for measured $\theta$ values we 
-use the exact Clopper-Pearson method.  
+For the treatments in \textit{intertask-food-objects}, five different 
+permutations of each treatment were tested, and a different classifier was 
+built for each permutation.  For the sake of estimating accuracy, we assume
+that the classifiers under different permutations have the same accuracy,
+and so we pool their results.  This means that 
+\textit{intertask-food-objects} has five times as many validation tests
+(larger $N$) compared to the other experiments.  We therefore assume 
+that $X$ has a normal distribution for the classification of workers from
+\textit{intertask-food-objects}, with $\mu=N/2$ and 
+$\sigma = \frac{1}{2}\sqrt{N}$.
+
+To determine the confidence intervals for measured $\theta$ values we 
+use the exact Clopper-Pearson method \cite{clopper1934use}.  
 Based on the observed number of successes, $X$, we calculate 
@@
 The statistics collected for the measurement of $\theta$, corresponding to
-Fig.~\ref{fig:theta}A are tabulated in 
-table X.
+Figs.~\ref{fig:theta} (A and B) are tabulated in Tables~S\ref{table:theta} and
+S\ref{table:theta_pos} respectively.
 
@@
 	Number of validation tests, $N$; number of successful classifications, 
-	$X$; critical number of succesful classifications to reject the null 
+	$X$; critical number of successful classifications to reject the null 
 	hypotheses that the classifier does no better than chance 
@@
 	confidence intervals are based on a significance of $\alpha=0.05$.
-	Values for $\hat{\theta}$ in boldface are significantly greater than 0.
-}
+	Values for $\hat{\theta}$ in boldface are significantly greater than zero.
+}
+\label{table:theta}
 \end{center}
 \end{table}
-
-The statistics for Fig.~\ref{fig:theta}B are shown in table X.
 
@@
 	confidence intervals are based on a significance of $\alpha=0.05$.
-	Values for $\hat{\theta}$ in boldface are significantly greater than 0.
-}
-
+	Values for $\hat{\theta}$ in boldface are significantly greater than zero.
+}
+\label{table:theta_pos}
 \end{center}
@@
 	wordnet lemmatizer \cite{miller1995wordnet,felbaum1998wordnet}.  
-	Common words such as ``the'', ``to'', or ``with'', were found using the
-	the NLTK's English stop-word list and removed \cite{loper2002nltk}.
+	Common words such as ``the'', ``to'', or ``with'', were found using
+	NLTK's English stop-word list and removed \cite{loper2002nltk}.
 
@@
 	position in which they had been entered (i.e. which of the five text 
-	inputs in the task interface) as well as the test tasks in which the word 
-	had been provided.
+	inputs in the task interface, see Fig.~S\ref{fig:hit_preamble}) 
+	as well as the test tasks in which the word had been provided.
 	So, if the word ``wine'' was entered into the second text-input for 
@@
 	appear.  Prepending the task number onto words was simply a means to 
-	retain correct attribution, which itself was essential since providing a
-	word during one task is not equivalent to providing the same word during 
-	another task.
+	retain correct of words to images, since providing a word during one task 
+	is not equivalent to providing the same word during another task.
 
@@
 	letters into many short two- or three-letter words, which otherwise leads 
-	to many erroneous corrections.  We found that setting the penalty for
-	word splitting at 0.1 worked well by testing on words taken from
-	initial tasks.
+	to many erroneous corrections.  We found these penalties worked well when
+	testing on words taken from initial tasks.
 
@@
 
-	Based on this exercise, we found that, according to the human coders,
-	17\% of the words were misspelled, but that after applying the 
-	automated spelling correction, only 3.2\% of words were misspelled.
+	According to the human coders, before spelling correction, 17\% of words 
+	were misspelled, but only 3.2\% were mispelled after correction.
 
@@
 
-\subsection*{Most suppressed / activated terms}
+\subsection*{Analysis of worker vocabulary}
+\paragraph{Most suppressed and activated terms.}
 The words whose frequencies differed most between the treatments of given 
@@
 
-\subsection*{Identification of food-related terms}
+\paragraph{Identification of food-related terms}
 The wordnet corpus is composed of synsets, which are particular senses 
@@
 
-\subsection*{Calculation of relative specificity}
+\paragraph{Calculation of relative specificity}
 In the main text we present results for the relative specificity of labels

### 2015-01-30 docs/publications/2014.09_SCIENCE/man.tex
Add statistical comparison of framing and intertask
Another full pass was made over the manuscript.

@@
 the workforce is available on demand over the Internet using automated 
-scripts, and  no contracts or interviews are required.  Many tasks can be
-can be performed at a fraction of the cost of recruiting temporary workers.
+scripts, and  no contracts or interviews are required 
+\cite{wolfson2011look,5543192}.  Many tasks can be
+can be performed at a fraction of the cost of traditional methods for 
+recruiting temporary workers or experimental subjects\cite{Berinsky2012351,paolacci2010running,ranade2012crowdsource}.
 
 For this reason, there has been a surge in demand for microtask work
-in both industry and academia.  Industry employs microtask workers
-for clerical tasks, such as digitizing records and correcting errors; 
-and for marketing activities, such as running focus groups, writing product 
-reviews, and moderating website content.  
-Academia turns to microtask workers as a way to recruit study participants, 
-and to annotate datasets, for example, to provide ground-truth in training 
-artificial intelligence systems.
-
+in both industry and academia\cite{wolfson2011look,Berinsky2012351}.  
 Given their increasing prevalence, there
@@
 level of pay \cite{kazai2013analysis}, the training and pre-screening of 
-workers \cite{le2010ensuring,paolacci2010running}, and user-interface 
-design \cite{Finnerty2013}.  
+workers \cite{le2010ensuring,paolacci2010running,kazai2013analysis}, 
+and user-interface design \cite{Finnerty2013}.  
 Researchers have also investigated the effects of \textit{framing}, 
@@
 does indeed depend strongly on the tasks performed beforehand.   
-We call these effects that earlier tasks exert on later ones 
+We call the effects that earlier tasks exert on later ones 
 \textit{intertask effects}.
@@
 Davis \textit{et al} invoked the \textit{human processing unit}, or HPU \cite{5543192}.
-Researchers sought to define a basic HPU instruction set, and
-libraries for HPU programming are under active development
- \cite{little2010turkit,minder2011crowdlang,minder2012crowdlang,kittur2011crowdforge}.  
-HPU outputs are inherently stochastic, but our revelation of strong intertask 
-effects shows that HPUs are subject to \textit{hysteresis}, 
+Researchers have sought to define a set of basic HPU operations, and
+have developed libraries and frameworks to simplify HPU programming 
+and make it more like CPU programming 
+\cite{little2010turkit,minder2012crowdlang,kittur2011crowdforge}.  
+As an example, one operation overcomes the inherent stochasticity of HPU 
+outputs, by automatically aggregate votes from multiple HPUs under a single
+function call.  But our revelation of strong intertask effects shows that, 
+in addition to stochasticity, HPUs are subject to \textit{hysteresis}, 
 meaning that their 
@@
 path-independence are crucial properties of the components in a 
-computing architecture, so it to maintaining the view of the HPU computing 
-architecture, necessitates a better understanding of the computational 
-ramifications of many psychological phenomena.
+computing architecture, so a better understanding of the computational 
+ramifications of many psychological phenomena is clearly needed.
 
@@
 asked to provide a qualitative free-text response to a prompt.  
-This includes such examples as describing
-video and audio recordings, summarizing texts, or providing personal 
-experiential feedback to a product review.
+This includes such diverse tasks as describing
+video and audio recordings, summarizing texts, or providing feedback to a 
+product review.
 %in the long run, because image labeling is still very difficult to automate
@@
 
-In our first experiment, which we will refer to as 
+In our first experiment, which we call
 \textit{intertask-food-objects}, workers were assigned to either a
@@
 either food or (non-food) objects, depending on the worker's 
-treatment (see Fig.~\ref{fig:task}A and B).  Following the initial 
+treatment (Fig.~\ref{fig:task}A and B).  Following the initial 
 tasks, workers performed five \textit{test tasks}, which were identical for 
 both treatments.  The test tasks contained images depicting a 
-mixture of food and objects (see Fig.~\ref{fig:task}C), and workers
+mixture of food and objects (Fig.~\ref{fig:task}C), and workers
 were again asked to provide five labels.  Five initial 
 tasks, together with the test tasks, comprised one HIT\footnote{
-	Workers were only allowed to participate in one HIT of a single treatment 
-	of a single experiment.
+	Workers were only allowed to participate in one HIT relating to this study.
 }. During the HIT, workers 
@@
 significantly during test tasks ($p = 6.0 \times 10^{-14}$), even though the test tasks were identical 
-in both treatments (\# see supplementary text for tabulated statistics).  This shows that earlier tasks have a 
+in both treatments\footnote{see supplementary text for tabulated statistics.}.  This shows that earlier tasks have a 
 significant effect on later ones, and raises concerns about the 
@@
 the strength of influence that a perturbation has on worker's responses.
-Since different workers generally provide different responses for the same 
-task, we characterize worker's responses by a probability distribution.  
-The extent of bias is then defined by the difference in the response 
-distribution for different treatments of workers\footnote{
+Since workers' responses are stochastic, we define the extent of bias in 
+terms of the shift induced in the distribution of responses\footnote{
 	This is a general divergence metric between probability 
@@
 only allows us to conclude that $\theta$ is non-zero 
-(see the supplementary text).  
-Determining $\theta$ from finite samples of 
-responses, using purely statistical approaches, is difficult (\#), which 
-leads us to reformulate the
+(see supplementary text).  
+Determining $\theta$ from finite samples of responses, using purely 
+statistical approaches, is difficult (see supplementary text),
+which leads us to reformulate the
 problem in terms of classification: given a worker's 
-response, can a machine reliably infer what her prior task-exposure had 
+responses, can a machine reliably infer what her prior exposure had 
 been?  Intuitively, the greater the effect that prior tasks have on subsequent
@@
 framing.  As defined, bias ranges from 0 (meaning the exposures 
-do not affect the probabilities of responses), to 1 
-(or 100\%) (meaning that under different exposures, workers provide completely
-different sets of responses).
+does not affect the distribution of responses), to 1 
+(or 100\%) (meaning that the exposure leads workers to provide a completely
+different set of responses).
 
@@
 Using a na\"ive Bayes classifier\footnote{
-	We discuss our choice of classifier and preprocessing methods, 
-	and show similar results obtained by using a support vector 
-	machine, in the supplementary material.
+	We believe na\"ive Bayes is the best choice in this setting, as discussed
+	in the supplementary material, and we show results when a support vector
+	machine is used instead. 
+	We also discuss data preprocessing and show results for alternatives.
 }, we found that intertask effects 
 lead to a 30\% bias between workers from the \textit{food} and 
-\textit{objects} treatments.  This represents a substantial potential to 
-distort microtask data.
+\textit{objects} treatments (Fig.~\ref{fig:theta}A).  
+This represents a substantial potential to distort microtask data.
 
@@
 word usage at significance (as determined by $\chi^2$ test; $p=0.0012$), but 
-the \textit{extent} of framing-induced bias we found was statistically 
-insignificant ($p =0.37$) (see Fig.~\ref{fig:theta}).  This suggests 
-that prior task exposure is a stronger priming modality than framing.
+the \textit{extent} of framing-induced was not statistically 
+distinguishable from zero ($p =0.37$) (Fig.~\ref{fig:theta}), and was
+weaker than the bias due to intertask effects ($p=2.1\times 10^{-5}$).
 
@@
 As before, the initial tasks for the \textit{food} treatment contained images 
-depicting food (see Fig.~\ref{fig:task}D). 
+depicting food (Fig.~\ref{fig:task}D). 
 In the \textit{culture} treatment, 
 the initial tasks contained images depicting cultural scenes 
-(of dance, sport, or music) (see Fig.~\ref{fig:task}E).  The test tasks, which were identical for both
+(of dance, sport, or music) (Fig.~\ref{fig:task}E).  The test tasks, which were identical for both
 treatments, included images depicting meals of identifiable cultural 
 origin\footnote{
-	Though we attempted to choose foods with less specific or iconic cultural
-	associations, the initial tasks 
+	Despite efforts to the contrary, initial tasks 
 	in \textit{intertask-food-culture} are arguably still of
-	identifiable cultural origin. This would tend to reduce, rather than 
-	inflate, the bias observed in our results 
-	(we discuss this further in the supplementary text).
-}
-(see Fig.~\ref{fig:task}F).
+	identifiable cultural origin, but this would only tend to make our 
+	results more conservative (we discuss this further in the supplementary 
+	text).
+}
+(Fig.~\ref{fig:task}F).
 
@@
 strong bias as a result of intertask effects ($\theta$~about 50\%) 
-(see Fig.~\ref{fig:theta}A).  Again, we compared intertask effects to 
+(Fig.~\ref{fig:theta}A).  Again, we compared intertask effects to 
 framing, by performing an experiment (\textit{frame-food-culture}) using 
@@
 difference between the labels attributed by the \textit{food} and 
-\textit{culture} treatments during test tasks ($p=0.29$) 
-(see Fig.~\ref{fig:theta}).
+\textit{culture} treatments during test tasks (by $\chi^2$ test, $p=0.29$) 
+(Fig.~\ref{fig:theta}), .
 
@@
 test tasks
-(see Fig.~\ref{fig:theta}A). However, it is possible that by requiring 
-workers to echo the language used in framing, we provided an implicit 
-but nonetheless strong signal of our intent that workers act on the 
-framing statement.  In this sense, \textit{echo-food-culture} may reflect the 
-influence of an \textit{instruction} rather than framing.
+(Fig.~\ref{fig:theta}A). However, it is difficult to say whether this 
+should be considered as a framing treatment \textit{per se}.
+Requiring the worker to reiterate the frame signals our intent, as the 
+requester, to ensure that the worker has taken note of the framing statement, 
+possibly leading the worker to interpret it as an instruction.  
+In any case, we find it remarkable that intertask effects
+were on par with an explicit statement of purpose that was emphasized 
+through reiteration.
 
@@
 	augmented with additional words obtained by crawling a recipe website 
-	(see supplementary information for details)
-} (see Fig.~\ref{fig:specificity}).  This finding
+	(see supplementary text for details)
+} (Fig.~\ref{fig:specificity}).  This finding
 rules out a seemingly-simple idea that workers emphasize
 content that has been present in earlier tasks: seeing content in prior tasks
-affects the probability that a worker refers to it in subsequent tasks, but 
-does not necessarily \textit{increase} the probability.
+influences, but does not necessarily \textit{increase}, the probability of 
+referring to the content in subsequent tasks.
 
@@
 greater lexical richness, in reference to food, than their non-food-primed 
-counterparts (as much as 20\% more) (see Fig.~\ref{fig:specificity}).  
+counterparts (as much as 20\% more) (Fig.~\ref{fig:specificity}).  
 The increase in lexical richness in the case of 
@@
 notion of word specialization.  Wordnet provides a set of hypernym-hyponym 
-relations between 117,798 English nouns (\#).  Hypernyms are generalizations 
+relations between 117,798 English nouns 
+\cite{miller1995wordnet,felbaum1998wordnet}.  Hypernyms are generalizations 
 (for example, ``bread'' is a hypernym for 
@@
 For each experiment, we compared food-related words provided by workers from 
-one treatment to those from the other, and tallied the excess number of cases
-where one treatment's words were more specialized than the other, as a 
-percentage of the total 
-(see Fig.~\ref{fig:specificity}B) 
-(details for this calculation are in the supplementary text).
+one treatment to those from the other, tallying the percent-excess of
+cases where one treatment's words were more specialized than the other 
+(Fig.~\ref{fig:specificity}B) 
+(detailed calculation in the supplementary text).
 
 In all experiments except \textit{frame-food-culture}, food-primed workers 
-used significantly more specialized words than their non-food-primed 
-counterparts (about 15\% more) (see Fig.~\ref{fig:specificity}C).
+used significantly more specialized words, in reference to food, 
+than their non-food-primed 
+counterparts (about 15\% more) (Fig.~\ref{fig:specificity}C).
 It is interesting that such substantial increases in both the lexical 
@@
 This hypothesis is corroborated when we look at those words whose 
-frequencies changed the most from one treatment to another (see Table S1).  
+frequencies changed the most from one treatment to another 
+(Table~S\ref{table:top-words}).  
 The word ``food'', which is the most generic possible food-related word, was 
@@
 is often observed as an increase in the speed or accuracy of a response, or
-the ability to recognize features of a briefer, quieter, or noisier stimulus 
-(\#).
-Negative priming occurs when, after being repeatedly exposed to a stimulus 
-considered to be non-salient, a person begins to ignore that 
-stimulus (\#).
+the ability to recognize briefer or noisier stimuli 
+\cite{BJOP1796,BJOP1826,Huber2008324}.
+Negative priming occurs when, after exposure to a stimulus 
+considered to be non-salient, subsequent recognition of the stimulus is 
+inhibited \cite{mayr2007negative}.
 
@@
 It would be preferable to understand intertask
-effects in greater depth so that they might be properly \textit{controlled}.
+effects in greater depth so that they might be properly controlled.
 
@@
 A consistent goal in human computation is the achievement of expert-level
-judgments from non-expert workers (\#).  This has been achieved in some
-applications (\#). The distinction between experts and novices can be 
+judgments from non-expert workers \cite{kittur2011crowdforge}.  This has been achieved in some
+applications \cite{Mortensen20131020}. 
+The distinction between experts and novices can be 
 attributed in part to the possession of specialized knowledge and heuristics. 
@@
 non-salient ones \cite{kellman2009perceptual}.  Using strategic task 
-exposures, it might be possible to guide workers' focus and salience 
+exposure, it might be possible to guide workers' focus and salience 
 attribution, enabling expert-level judgment in a wider variety of 
@@
 We anticipate that future work will yield techniques to control intertask 
-effects, enabling one to both reduce unwanted bias, as well as tune the 
+effects, both to reduce unwanted bias, as well as tune the 
 focus, diversity, and specificity of worker responses.
 
-Here we have shown that a large bias can be introduced into microtask 
+Here we have shown that a severe bias can be introduced into microtask 
 responses, simply from the performance of earlier tasks. 
-These effects are much stronger than framing.  
+These effects are much stronger than the effects of framing.  
 While our findings raise serious concerns about the 
-current state of microtask design, they also reveal potential opportunities 
+current state of microtask design, they reveal potential opportunities 
 for more 
@@
 on the repetitive use of human judgment is likely subject to the phenomena
-we described here.  Exploring the issues and opportunities posed by 
-intertask effects are important directions for future work, 
+we described here.  Exploring the pitfalls and opportunities posed by
+intertask effects is an important direction for future work, 
 in the effort to develop performant and reliable methods for human 
@@
 	During echoed framing, the worker had to respond to the framing language
-	using a combo box input (see Fig.~S\ref{fig:hit_preamble}C).
+	using a combo box input (Fig.~S\ref{fig:hit_preamble}C).
 	\newline\textsuperscript{a} ``Funded by the laboratory for the visual 
@@
 framing, a framing statement was shown on a slide immediately after the 
-instructions (see Fig. S\ref{fig:hit_preamble}B and C).  
+instructions (Fig. S\ref{fig:hit_preamble}B and C).  
 Initial tasks, when included, followed next.  The initial tasks consisted of 
-a series of 5 slides, each containing an image-labeling task like the one 
+a series of five slides, each containing an image-labeling task like the one 
 shown in 
@@
 \begin{figure}
+	\begin{center}
 	\includegraphics{figs/task1-food.pdf}
+	\end{center}
 	\caption{
@@
 \begin{figure}
+	\begin{center}
 	\includegraphics{figs/task1-obj.pdf}
+	\end{center}
 	\caption{
@@
 \begin{figure}
+	\begin{center}
 	\includegraphics{figs/task1-test.pdf}
+	\end{center}
 	\caption{
@@
 \begin{figure}
+	\begin{center}
 	\includegraphics{figs/task2-food.pdf}
+	\end{center}
 	\caption{
@@
 \begin{figure}
+	\begin{center}
 	\includegraphics{figs/task2-cult.pdf}
+	\end{center}
 	\caption{
@@
 \begin{figure}
+	\begin{center}
 	\includegraphics{figs/task2-test.pdf}
+	\end{center}
 	\caption{
@@
 We framed tasks by including a message, near the beginning of the HIT, that 
-suggested the purpose of the tasks.
+suggested a particular purpose for the tasks.
 The precise language used is shown in 
@@
 Fig.~S\ref{fig:hit_preamble}(C).
-
-This \textit{echo-food-objects} treatment certainly produced the 
-strongest effect of the framing experiments, but it is difficult to say 
-whether that should be considered indicative of framing textit{per se}.  
-The explicitness of the statement would tend to make it more like an 
-instruction in its effect.  Perhaps more importantly, requiring the worker
-to re-iterate the framing statement by means of a combo-box emphasizes 
-the framing to a greater degree than the instructions, which would probably
-tend to give the impression that the framing statement is intended as an
-instruction to be acted upon.  Framing or not, the fact that initial tasks
-can produce an effect that is on par with that of \textit{echo-food-objects}
-shows just how strong intertask effects are.
 
@@
 then calculated according to Pearson's $\chi^2$ test, using 
-Yate's correction.  Results are tabulated in Table~S\ref{table:chi2}.
+Yates' correction.  Results are tabulated in Table~S\ref{table:chi2}.
 With the exception of \textit{frame-food-culture}, all experiments showed 
@@
 The use of Pearson's $\chi^2$ test has been criticized in linguistic 
-applications, due to the finding that many corpera are not themselves
+applications, due to the finding that many corpora are not themselves
 homogeneous \cite{kilgarriff1996comparing}.  
-This results from the fact that corpera are made of many
+This results from the fact that corpora are made of many
 distinct texts, together with the fact that words tend to come in bursts.
@@
 frequencies within given texts are often far from the average, causing 
-corpera to be heterogeneous.
+corpora to be heterogeneous.
 As a result, if a corpus is randomly split, putting half of the texts in one 
@@
 the halves (when tested using Pearson's $\chi^2$ test).  Thus, finding two
-corpera to be different according to a $\chi^2$ test might not 
+corpora to be different according to a $\chi^2$ test might not 
 indicate that they are meaningfully different.
@@
 (treatment), but thousands of distinct features 
-(i.e. the number of distinct words occuring in an experiment).  
+(i.e. the number of distinct words occurring in an experiment).  
 Having many more features than examples is problematic for many classifiers
@@
 	\caption{
-		Figure S2: Bias induced by exposure to initial tasks and frames.
+		Bias induced by exposure to initial tasks and frames.
 		Bias is defined to be the difference in the probability 
@@
 		done for panels G through H: A,G) No 
-		preprocessing; B,H) spelling correction; C,I) stopword removal; 
+		preprocessing; B,H) spelling correction; C,I) stop word removal; 
 		D,J) lemmatization; E,K) splitting of multiple-word labels; 
@@
 impact the classifier performance.  
-For example, we chose to correct spelling, remove stop-words,
+For example, we chose to correct spelling, remove stop words,
 lemmatize words, and to distinguish which text-input was used to enter a 
@@
 		\right\}\\
-	\text{where}\quad &\mathrm{Pr}\{ \mathrm{Bin}(N,p) \geq x \} = 
-		\sum_{x'=x}^{N} \binom{N}{x'}p^{x'}(1-p)^{(N-x')}
+	\text{where}\quad &\mathrm{Pr}\{ \mathrm{Bin}(N,\eta) \geq x \} = 
+		\sum_{x'=x}^{N} \binom{N}{x'}\eta^{x'}(1-\eta)^{(N-x')}
 \end{align}
@@
 
+To determine whether intertask effects were stronger than framing, we 
+perform a two-proportion $z$-test, approximating the binomial distributions
+as normal distributions, where the test statistic is given by:
+\begin{align}
+	z = \frac{\hat{\eta}_1 - \hat{\eta}_2}
+		{\sqrt{
+			\hat{\eta} (1 - \hat{\eta}) 
+			\left( \frac{1}{N_1} + \frac{1}{N_2}\right)
+		}},
+\end{align}
+where
+\begin{align}
+	\hat{\eta} = \frac{X_1 + X_2}{N_1 + N_2}
+\end{align}
+
+Since, \textit{a priori}, we do not which effects
+should be stronger (if any), we perform a two-tailed test.
+
 \begin{table}
@@
 \label{table:theta}
+\end{center}
+\end{table}
+
+\begin{table}
+\begin{center}
+\begin{tabular}{c c c c c c c c c c c }
+	\toprule
+	Comparison & $N_1$ & $N_2$ & $X_1$ & $X_2$ & $\hat{\eta}_1$ 
+		& $\hat{\eta}_2$ & $z$ & $p$-value \\ 
+	\midrule
+	\parbox[c]{4cm}{\textit{intertask-food-objects} 
+	\textit{vs} \textit{frame-food-objects}} & 1190 & 238 & 777 & 122 &
+	0.653 & 0.513 & \textbf{4.1} & $2.1 \times 10^{-5}$ \\
+
+\noalign{\smallskip}
+\hdashline
+\noalign{\smallskip}
+
+	\parbox[c]{4cm}{\textit{intertask-food-objects} 
+	\textit{vs} \textit{echo-food-objects}} & 1190 & 238 & 777 & 162 
+		& 0.653 & 0.681 & -0.82 & 0.79 \\
+
+\noalign{\smallskip}
+\hdashline
+\noalign{\smallskip}
+
+	\parbox[c]{4cm}{\textit{intertask-food-culture} 
+	\textit{vs} \textit{frame-food-culture}} & 238 & 238 & 180 & 130 
+	& 0.756 & 0.546 & \textbf{4.8} & $7.6 \times 10^{-7}$ \\
+	\bottomrule
+
+\end{tabular}
+
+\caption{
+	Results for two-proportion z-tests, leading to the rejection of the null 
+	hypothesis that intertask and (passive) framing effects are equally 
+	strong.  However, the echoed framing effects are on par with intertask
+	effects (second row). 
+	Numbers in boldface indicate a $z$-statistic significantly 
+	different from zero ($\alpha=0.05$).
+}
+\label{table:intertask_framing}
 \end{center}
@@
 	induced by intertask for \textit{intertask-food-objects}, measured 
-	for test images at specific positions in the sequence of 5 test images.
-	These values are averaged over 5 different permutations, such that 
+	for test images at specific positions in the sequence of five test images.
+	These values are averaged over five different permutations, such that 
 	the strength of intertask effects are measured for each of the test images
@@
 \subsection*{Data preprocessing}
-	\paragraph{Splitting, Lemmatization, removal of stop-words, and 
+	\paragraph{Splitting, lemmatization, removal of stop words, and 
 		addition of position tags.}
@@
 	Common words such as ``the'', ``to'', or ``with'', were found using
-	NLTK's English stop-word list and removed \cite{loper2002nltk}.
+	NLTK's English stop word list and removed \cite{loper2002nltk}.
 
@@
 	position in which they had been entered (i.e. which of the five text 
-	inputs in the task interface, see Fig.~S\ref{fig:hit_preamble}) 
+	inputs in the task interface, Fig.~S\ref{fig:hit_preamble}) 
 	as well as the test tasks in which the word had been provided.
@@
 	\textit{legal set}, which was formed by the union of
-	the wordnet corpus, the stop-word list, and a set of words seen while 
+	the wordnet corpus, the stop word list, and a set of words seen while 
 	crawling the world food section of the allrecipes.com website.  We
@@
 	According to the human coders, before spelling correction, 17\% of words 
-	were misspelled, but only 3.2\% were mispelled after correction.
+	were misspelled, but only 3.2\% were misspelled after correction.
 
@@
 	\centering
-	\setlength{\tabcolsep}{10pt}
+	\setlength{\tabcolsep}{4pt}
 	\begin{tabular}{ c c c c c }
@@
 		\toprule
-		\multicolumn{2}{c}{\textit{task1}} \\
-		\toprule
+		\multicolumn{2}{c}{
+			\parbox[c]{2.5cm}{
+				\centering
+					\textit{intertask-food-objects}
+			}} \\
+		\midrule
 		coffee & 38 \\
@@
 		\toprule
-		\multicolumn{2}{c}{\textit{frame1}} \\
-		\toprule
+		\multicolumn{2}{c}{
+			\parbox[c]{2.5cm}{
+				\centering
+				\textit{frame-food-objects}
+			}
+		}\\
+		\midrule
 		bread & 18 \\
@@
 		\toprule
-		\multicolumn{2}{c}{\textit{echo1}} \\
-		\toprule
+		\multicolumn{2}{c}{
+			\parbox[c]{2.5cm}{
+				\centering
+			\textit{echo-food-objects}} 
+		}\\
+		\midrule
 		apple & 24 \\
@@
 		\toprule
-		\multicolumn{2}{c}{\textit{task2}} \\
-		\toprule
+		\multicolumn{2}{c}{
+			\parbox[c]{2.5cm}{
+				\centering
+			\textit{intertask-food-culture}} 
+		}\\
+		\midrule
 		spicy & 26 \\
@@
 		\toprule
-		\multicolumn{2}{c}{\textit{frame2}} \\
-		\toprule
+		\multicolumn{2}{c}{
+			\parbox[c]{2.5cm}{
+				\centering
+			\textit{frame-food-culture}} 
+		}\\
+		\noalign{\smallskip}
+		\midrule
 		indian & 11 \\
@@
 	\caption{
-		Top 5 words, used to label the first test image, whose usage frequency
+		Top five words, used to label the first test image, whose usage frequency
 		increased or decreased the most between treatments of given 
@@
 		used the word with higher frequency.  Word frequencies for 
-		\textit{intertask-food-objects} are aggregated across 5 
+		\textit{intertask-food-objects} are aggregated across five 
 		permutations, and hence tend to show larger absolute differences.
@@
 		 & \ & \multicolumn{3}{c}{$(\%)$} \\ \cline{2-3} \cline{5-7}
-	& food trtmt. & other trtmt. & \ & $\Delta|V|$ & $\Delta|V|^*_{low}$
+	& Food trtmt. & Other trtmt. & \ & $\Delta|V|$ & $\Delta|V|^*_{low}$
 		& $\Delta|V|^*_{high}$  \\

### 2015-01-30 src/analysis.py

@@ -1148,6 +1148,20 @@ def do_cross_val(simple_dataset):
 	return overall_accuracy
 
 
+def two_proportion_test(n1, n2, x1, x2):
+	'''
+		Produce a test statistic for the hypothesis that two binomial 
+		variables have the same probability of success.  The binomials are
+		approximated as normals, so a z-statistic is constructed
+	'''
+	n1, n2 = float(n1), float(n2)
+	p1, p2, p= (x1 / n1), (x2 / n2), (x1 + x2)/(n1 + n2)
+	A = p1 - p2
+	B = np.sqrt(p*(1-p)*(1/n1 + 1/n2))
+	z = A / B
+	p = norm.sf(z)
+
+	return z, p
 
 def theta_NB_significance(n,k_star):
 	significance = 0

### 2015-02-10 docs/publications/2014.09_SCIENCE/man.tex
work on manuscript

@@
 \normalsize{\texttt{edward.newell@mail.mcgill.ca}}\\
-\normalsize{\texttt{druths@networkdynamics.org}}\\
-\normalsize{School of computer science, McGill University,}\\
-\normalsize{3630 rue University, Montreal, Quebec, H3A 0C6, Canada}\\
+\normalsize{\texttt{derek.ruths@mcgill.ca}}\\
+\normalsize{School of Computer Science, McGill University,}\\
+\normalsize{3480 University Street, Room 318, Montreal, Quebec, Canada, H3A 2A7}\\
 \\
@@
 discover that earlier tasks shift the distribution of future answers by 
-30-50\%, irrespective of the images used. 
+30-50\%. 
 Moreover, we show that prior tasks influence 
@@
 and specificity, helping to elicit reproducible, expert-level judgments.
-
-%Faced with the ever-growing scale and complexity of data, academic and 
-%industrial researchers are increasingly relying on \textit{human computation} 
-%to extract useful knowledge.  Microtask
-%platforms, like Amazon Mechanical Turk, act like a human compute cluster,
-%making it possible to access human cognition quickly and inexpensively. 
-%This has lead to their broad adoption by social and computer scientists.  
-%Human computation is being used experimentally in applications
-%where expert opinion would normally be sought, such as in reviewing 
-%medical images.
-%Here we show that the repeated performance of similar tasks, an inherent
-%feature of microtask and crowdsourcing platforms, acts as a strong
-%and largely unexplored source of bias.  The effects that earlier tasks exert
-%on later ones are more severe than effects caused by framing, 
-%such as by disclosing a task's purpose.  
-%Using image-labeling, the canonical microtask, we show that prior 
-%tasks influence the content that workers chose to focus on, as well as the 
-%richness and specialization of their vocabulary.    
-%While intertask effects can be a source of systematic bias, our
-%results suggest that with appropriate task-engineering, it might be possible
-%to leverage intertask effects to hone worker focus and specificity, helping
-%to elicit reproducible, expert-level judgments.
 \end{sciabstract}
@@
 post batches of tasks, and \textit{workers} complete them
-for remuneration, a sense of purpose, and for fun
+for remuneration, a sense of purpose, and fun
 \cite{kazai2013analysis,Antin20122925}.
 Typical tasks include tagging and categorizing images 
-\cite{6116320,Zhai2012357}, transcribing voice recordings 
-\cite{chandler2013breaking,paolacci2010running}
-or handwritten notes \cite{Berinsky2012351,Finnerty2013}, and judging the 
-relevancy of search results 
-\cite{le2010ensuring,grady2010crowdsourcing,alonso2009can,kazai2013analysis}.
-
-Microtask platforms enable a workflow in which workers are like 
-input-output devices.  This provides much of the flexibility and 
+\cite{6116320,Zhai2012357}, coding and transcription, such as of voice recordings or handwritten notes
+\cite{chandler2013breaking,paolacci2010running,Berinsky2012351,Finnerty2013}, 
+and judging relevancy and quality, for example, to rate information 
+retrieval systems \cite{le2010ensuring,grady2010crowdsourcing,alonso2009can,kazai2013analysis}.
+
+Microtask platforms are a form of crowdsourcing in which workers appear like 
+input-output devices.  They provide much of the flexibility and 
 cost-savings of fully automating the work in a computer program: 
 the workforce is available on demand over the Internet using automated 
-scripts, and  no contracts or interviews are required 
-\cite{wolfson2011look,5543192}.  Many tasks can be
+scripts, and  no interviews or contracts are required 
+\cite{wolfson2011look,5543192}.  Many tasks
 can be performed at a fraction of the cost of traditional methods for 
-recruiting temporary workers or experimental subjects\cite{Berinsky2012351,paolacci2010running,ranade2012crowdsource}.
-
-For this reason, there has been a surge in demand for microtask work
+recruiting temporary workers or experimental subjects
+\cite{Berinsky2012351,paolacci2010running,ranade2012crowdsource}.
+From the requester's perspective, using microtask platforms resembles
+running a computer program on a remote server, leading some to investigate
+these platforms as a new computing architecture \cite{5543192,little2010turkit,minder2012crowdlang,kittur2011crowdforge}.
+
+Due to its flexibility and cost-effectiveness, 
+there has been a surge in demand for microtask work
 in both industry and academia\cite{wolfson2011look,Berinsky2012351}.  
-Given their increasing prevalence, there
-is a desire to understand the factors affecting the reliability of 
-microtask-based methods.  Researchers have investigated task-design 
-parameters such as the 
+Naturally, there is a desire to understand the factors affecting the 
+reliability of microtask-based methods.  Researchers have investigated 
+task-design parameters such as the 
 level of pay \cite{kazai2013analysis}, the training and pre-screening of 
@@
 
-Here we focus on a ubiquitous feature of the microtask setup: the 
-tendency for microtask workers to perform many tasks in quick succession. 
-Even if a worker performs the minimum possible amount of work, 
-she will likely have performed several microtasks, since they are typically 
-distributed to workers in bundles.  For example, in one bundle, a worker 
-might be assigned a set of ten images, and asked to provide descriptive words 
-(or \textit{labels}) for each.  On one popular microtask platforms,
+Here we focus on a ubiquitous feature of the microtask setup: the tendency
+to bundle a set of similar tasks together. 
+For example, in one bundle, a worker might be assigned a set of ten images, 
+and asked to provide descriptive words 
+(or \textit{labels}) for each.  
+On one popular microtask platform,
 Amazon's Mechanical Turk (MTurk), these bundles are called Human 
@@
 ``task'' to mean the smallest repeatable unit of work, which, in our study, 
-consists of labeling a single image.
+consists of labeling a single image.  This bundling tendency leads
+workers to perform a series of similar tasks in quick succession.
 
@@
 the prior stimuli bear some conceptual or perceptual connection to the 
-ensuing task, and so, the repetition of similar tasks within the typical 
-microtask setup creates an ideal context for strong priming effects
-\cite{Gass1999549,sohn2001task}.
+ensuing task\cite{Gass1999549,sohn2001task}, and so, the repetition of 
+similar tasks within the typical microtask setup creates an ideal context for 
+strong priming effects.
 
@@
 and raises questions about what other cognitive biases might
-affect microtask work, and how prevalent induced bias might be.
+affect microtask work, and how prevalent the induced bias might be.
 
@@
 As an example, one operation overcomes the inherent stochasticity of HPU 
-outputs, by automatically aggregate votes from multiple HPUs under a single
+outputs, by automatically aggregating votes from multiple HPUs under a single
 function call.  But our revelation of strong intertask effects shows that, 
@@
 outputs depend on the history of their inputs.  Reproducibility and 
-path-independence are crucial properties of the components in a 
+path-independence are crucial properties for the components of a 
 computing architecture, so a better understanding of the computational 
-ramifications of many psychological phenomena is clearly needed.
+ramifications of many psychological phenomena is needed.
 
@@
 image-labeling is prototypical for any kind of task in which the worker is 
-asked to provide a qualitative free-text response to a prompt.  
+asked to provide a high-level judgment, incorporating prior knowledge, in 
+response to a prompt.  
 This includes such diverse tasks as describing
@@
 product review.
-%in the long run, because image labeling is still very difficult to automate
-%\cite{5543192}, and is used in many applications, such as website moderation, 
-%computer vision research, and social media analytics (\# insert other refs) 
-%\cite{5543192}.
 
@@
 mixture of food and objects (Fig.~\ref{fig:task}C), and workers
-were again asked to provide five labels.  Five initial 
+were again asked to provide five labels for each.  Five initial 
 tasks, together with the test tasks, comprised one HIT\footnote{
@@
 
-A $\chi^2$ test shows that the frequency of word usage by
+A $\chi^2$ test shows that the frequencies of words used by
 workers in the \textit{food} and \textit{objects} treatments differed
@@
 problem in terms of classification: given a worker's 
-responses, can a machine reliably infer what her prior exposure had 
-been?  Intuitively, the greater the effect that prior tasks have on subsequent
+responses to test tasks, can a machine reliably infer what her prior exposure 
+had been?  Intuitively, the greater the effect that prior tasks have on 
+subsequent
 responses, the more accurate the classifier can be.  Formally (as shown
@@
 word usage at significance (as determined by $\chi^2$ test; $p=0.0012$), but 
-the \textit{extent} of framing-induced was not statistically 
-distinguishable from zero ($p =0.37$) (Fig.~\ref{fig:theta}), and was
+the \textit{extent} of framing-induced bias was not statistically 
+distinguishable from zero ($p =0.37$) (Fig.~\ref{fig:theta}A), and was
 weaker than the bias due to intertask effects ($p=2.1\times 10^{-5}$).
+
+To assess the permenance of intertask effects, we replicated the experiment
+\textit{intertask-food-objects} five times, each time using a different 
+permutation of the test tasks.  This enabled us to measure the severity
+of bias as a function of task position, independant of the content
+of the test task.  We found that bias was strongest for the first test task
+(about 28\%), but remained significant through all five test tasks 
+($\alpha=0.05$) sustaining nearly 15\% bias (Fig. \ref{fig:theta}B).
 
@@
 Results for this experiment again showed a 
-strong bias as a result of intertask effects ($\theta$~about 50\%) 
+strong bias as a result of intertask effects (about 50\%) 
 (Fig.~\ref{fig:theta}A).  Again, we compared intertask effects to 
@@
 of either food or culture.  
-For this framing experiment, we did not observe a statistically significant 
-difference between the labels attributed by the \textit{food} and 
-\textit{culture} treatments during test tasks (by $\chi^2$ test, $p=0.29$) 
-(Fig.~\ref{fig:theta}), .
+In this experiment, framing did not induce significant changes in the 
+frequencies of words used during test tasks (by $\chi^2$ test, $p=0.29$) 
+(Fig.~\ref{fig:theta}A).
 
@@
 possibly leading the worker to interpret it as an instruction.  
-In any case, we find it remarkable that intertask effects
+In any case, it is remarkable that intertask effects
 were on par with an explicit statement of purpose that was emphasized 
@@
 	\centering
-	\includegraphics[scale=0.94]{figs/vocab_specificity.pdf}
+	\includegraphics[scale=0.92]{figs/vocab_specificity.pdf}
 	\caption{
-		(\textbf{A}) Exposing workers to initial tasks and framing 
-		involving food changed how often they referred to food 
-		during test tasks, but did not always increase it (in all three plots,
+		(\textbf{A}) Exposing workers to initial tasks or framing, 
+		involving food, changed the subsequent fraction of words that 
+		referred to food during test tasks, 
+		but did not always increase that fraction (in all three plots,
 		positive values indicate a larger quantity for food-exposed workers).
@@
 		case of \textit{frame-food-culture} (stars indicate the threshold
-		for a significant deviation from the null hypothesis, $\alpha=0.05$). 
+		for a significant deviation under the null hypothesis of equal 
+		richness, $\alpha=0.05$). 
 		(\textbf{C}) Food-exposed
-		workers also used more specialized words to refer to food.
+		workers used more specialized words to refer to food (see 
+		supplementary text for calculation of relative specialization).
 		Standard error bars are shown in (\textbf{A} and \textbf{C}).
@@
 	augmented with additional words obtained by crawling a recipe website 
-	(see supplementary text for details)
-} (Fig.~\ref{fig:specificity}).  This finding
+	(see supplementary text for details).
+} (Fig.~\ref{fig:specificity}A).  This finding
 rules out a seemingly-simple idea that workers emphasize
@@
 greater lexical richness, in reference to food, than their non-food-primed 
-counterparts (as much as 20\% more) (Fig.~\ref{fig:specificity}).  
+counterparts (as much as 20\% more) (Fig.~\ref{fig:specificity}B).  
 The increase in lexical richness in the case of 
@@
 cases where one treatment's words were more specialized than the other 
-(Fig.~\ref{fig:specificity}B) 
 (detailed calculation in the supplementary text).
@@
 A consistent goal in human computation is the achievement of expert-level
-judgments from non-expert workers \cite{kittur2011crowdforge}.  This has been achieved in some
-applications \cite{Mortensen20131020}. 
+judgments from non-expert workers \cite{kittur2011crowdforge}.  
+This has been achieved in some
+applications \cite{Mortensen20131020,Warby2014385}. 
 The distinction between experts and novices can be 
@@
 
+\pagebreak
 \section*{Supplementary Material}
@@
 
+Microtask platforms are increasingly popular for the annotation of large
+datasets, and obtaining other judgments that require prior knowledge and 
+hence are difficult to automate using only a computer.  Due to their 
+popularity, there is interest in understanding how various task design factors
+influence the reliabality of data obtained using microtask platforms.  
+Since tasks are typically bundled together, microtask 
+workers tend to perform several similar tasks in quick succession, creating an opportunity for priming effects to induce bias in the results obtained.
+Here we describe in detail experiments presented in the main text, in which
+we investigate the effect that prior tasks have on the responses given during
+subsequent tasks.
+
 \subsection*{Materials and Methods}
@@
 \paragraph{Microtask setup.}
+
+The work presented in the main text consisted of six experiments involving
+HITs (bundles of microtasks) performed on Amazon's Mechanical Turk platform.  
+Each experiment was divided into two treatments.  Treatments for a given 
+experiment differed with respect to a particular priming modality, which 
+served as the independent variable
+(as specified in Table~S\ref{table:experiments}).  
+The HITs for treatments of the same experiment always involved the same
+test tasks (the last five tasks in the HIT),
+the results of which served as the dependent variable.
+
+All HITs were presented as a series of slides.  The first 
+slide consisted of a brief set of instructions.  For HITs that included 
+framing, a framing statement was shown on a slide immediately after the 
+instructions (Fig. S\ref{fig:hit_preamble}B and C).  
+Initial tasks, when included, followed next.  The initial tasks consisted of 
+a series of five slides, each containing an image-labeling task like the one 
+shown in 
+Fig.~S\ref{fig:hit_preamble}D.  Finally, for all HITs, five slides were shown
+containing test tasks, in the same format as the initial tasks.
+
 \begin{table}
@@
 \end{figure}
-
-The work presented in the main text consisted of six experiments involving
-HITs (bundles of microtasks) performed on Amazon's Mechanical Turk platform.  
-Each experiment was divided into two treatments.  Treatments for a given 
-experiment differed with respect to a particular priming modality, which 
-served as the independent variable
-(as specified in Table~\ref{table:experiments}).  
-The HITs for treatments of the same experiment always involved the same
-test tasks (the last five tasks in the HIT),
-the results of which served as the dependent variable.
-
-All HITs were presented as a series of slides.  The first 
-slide consisted of a brief set of instructions.  For HITs that included 
-framing, a framing statement was shown on a slide immediately after the 
-instructions (Fig. S\ref{fig:hit_preamble}B and C).  
-Initial tasks, when included, followed next.  The initial tasks consisted of 
-a series of five slides, each containing an image-labeling task like the one 
-shown in 
-Fig.~S\ref{fig:hit_preamble}D.  Finally, for all HITs, five slides were shown
-containing test tasks, in the same format as the initial tasks.
-
 Workers were randomly assigned to the treatments, and 

### 2015-02-10 docs/publications/2014.09_SCIENCE/man.tex
more work on manuscript

@@
 	& Fig.~S\ref{fig:task1:food} 
-	& \multirow{2}{*}{Fig.~S\ref{fig:task1:test}\textsuperscript{e}} \\
+	& \multirow{2}{*}{Fig.~S\ref{fig:task1:test}\textsuperscript{g}} \\
 & & \textit{objects} & none & Fig.~S\ref{fig:task1:obj} & \\
@@
 & \multirow{2}{*}{echoed framing} & \textit{food} 
-	& ``food''\textsuperscript{a}
+	& ``food''\textsuperscript{c}
 	& none & \multirow{2}{*}{Fig.~S\ref{fig:task1:test}} \\
 & & \textit{objects} 
-	& ``objects''\textsuperscript{b}
+	& ``objects''\textsuperscript{d}
 	& none & \\
@@
 	& \multirow{2}{*}{Fig.~S\ref{fig:task2:test}} \\
-& & \textit{objects} 
+& & \textit{culture} 
 	& none & Fig.~S\ref{fig:task2:cult} & \\
@@
 & \multirow{2}{*}{framing} & \textit{food} 
-	& ``food''\textsuperscript{c}
+	& ``food''\textsuperscript{e}
 	& Fig.~S\ref{fig:frame2:ingr} 
 	& \multirow{2}{*}{Fig.~S\ref{fig:task2:test}} \\
-& & \textit{objects} 
-	& ``culture''\textsuperscript{d} 
+& & \textit{culture} 
+	& ``culture''\textsuperscript{f} 
 	& Fig.~S\ref{fig:frame2:ingr} & \\
@@
 	\newline\textsuperscript{e} ``This research is proudly funded by The National 
-		Foundation for Nutrition Awareness''
+		Foundation for Nutritional Awareness''
 	\newline\textsuperscript{f} ``This research is proudly funded by The Global 
@@
 The permutations were obtained by rotating 
-the order shown in Fig.~\ref{fig:task1:test} by different amounts. 
+the order shown in Fig.~S\ref{fig:task1:test} by different amounts. 
 For example, rotating by one position involves moving the first image to the 
@@
 Table~S\ref{table:experiments}, and an example of a framing slide is shown in
-Fig.~S\ref{fig:hit_preamble}(B and C).  In \textit{frame-food-objects}
+Fig.~S\ref{fig:hit_preamble}B and C.  In \textit{frame-food-objects}
 and \textit{frame-food-culture}, the framing language was based on
@@
 echo back the purpose of the task by selecting it from a combo box
-Fig.~S\ref{fig:hit_preamble}(C).
+Fig.~S\ref{fig:hit_preamble}C.
 
@@
 include any initial tasks, meaning that the test tasks followed the framing
-slide immediately.  One could argue that a better comparison would be achieved
-including initial tasks even for framing experiments (but keeping the
+slide immediately.  One could argue that a fairer comparison would be achieved
+by including initial tasks even for framing experiments (but keeping the
 initial tasks constant while varying the framing language), since the worker
@@
 the treatments of given experiments can be rightly attributed to the 
-framing / intertask effects.
+framing and intertask effects.
 
@@
 Recently there has been theoretical progress on this problem.
-An estimator of L1-distance, and a tests of whether the L1-distance is
+An estimator of L1-distance, and tests of whether the L1-distance is
 greater than a specified threshold, have been proposed 
@@
 cannot easily be used to establish estimates with confidence intervals or 
-perform hypothesis tests for a given fixed sample size.  
+perform hypothesis tests for fixed sample size and significance level.  
 We therefore turn to an alternative approach using machine learning. 
 While this method yields an estimator that converges more slowly,
-it is straightforward to establish confidence intervals for estimates and 
+it is straightforward to establish confidence intervals and 
 use the estimator in hypothesis tests.
@@
 The algorithm is provided
-with $x$ and yields a guess, $b=\mathcal{A}(x)$, as to whether the worker was 
+with $x$ and yields a \textit{guess}, $b=\mathcal{A}(x)$, as to whether the 
+worker was 
 from $P_0$ or $P_1$.  We shall denote such a validation test by 
 $V(P_0, P_1, \mathcal{A})$, and define the value of the test to be 1 if 
-$b=z$ and zero otherwise.
+$b=z$ and 0 otherwise.
 
@@
 not distributed identically, then given some $x$, the best possible 
-classifier must always guess 1 whenever $p_1(x) > p_0(x)$ and otherwise 
-guess 0.
-
-Sacrificing, for a moment, some generality, let us assume that, for a given 
-$x$, $p_1(x) > p_0(x)$.  
-Then, given some $x'$ has been chosen during a 
-validation test, the optimal classifier must guess that 
-$z = \arg\!\max_{z'}(p_{z'}(x)) = 1$.
-The probability that the classifier guesses correctly, given a validation
-test in which the response $x$ was chosen, is therefore:
+classifier must always guess 1 whenever $p_1(x) > p_0(x)$ and guess 0 whenever
+$p_0(x) > p_1(x)$.
+
+Sacrificing, for a moment, some generality, let us assume that, for some give 
+$x'$, $p_1(x') > p_0(x')$.  
+When this $x'$ is encounterend in a validation test, the optimal classifier
+must guess $b = \arg\!\max_{z}(p_{z}(x'))$, which in this case is $b=1$.
+The probability that the classifier guesses correctly in this case is:
 \begin{align}
 	\begin{split}
-	\mathrm{Pr}\{V = 1 | x' = x \} 
-		&= \mathrm{Pr}\{\mathcal{A^*}(x) = z | x' = x \} \\
-		&= \mathrm{Pr}\{z = 1 | x' = x \}  \\
-		&= \frac{\mathrm{Pr}\{z = 1 , x' = x\}}
-			{ \mathrm{Pr}\{z=0 , x'=x\} + \mathrm{Pr}\{z=1 , x'=x\}} \\
-		&= \frac{p_1(x)}{p_0(x) + p_1(x)}.
+	\mathrm{Pr}\{V(P_0, P_1, \mathcal{A}^*) = 1 | x = x' \} 
+		&= \mathrm{Pr}\{z = \mathcal{A^*}(x) | x = x' \} \\
+		&= \mathrm{Pr}\{z = 1 | x = x' \}  \\
+		&= \frac{\mathrm{Pr}\{z = 1 , x = x'\}}
+			{ \mathrm{Pr}\{z=0 , x=x'\} + \mathrm{Pr}\{z=1 , x=x'\}} \\
+		&= \frac{p_1(x')}{p_0(x') + p_1(x')}.
 	\end{split}
 \end{align}
-And now, with full generally,
+And now, with full generally, for any $x'$, where $p_1(x')$ is not necessarily
+greater than $p_0(x')$:
 \begin{align}
 	\begin{split}
-	\mathrm{Pr}\{V=1 | x' = x \} 
-		&= \mathrm{Pr}\{\mathcal{A^*}(x) = z | x' = x \} \\
-		&= \mathrm{Pr}\{z = \arg\!\max_{z'}\big(p_{z'}(x)\big)| x' = x \}  \\
-		&= \frac{\max\big( p_0(x),p_1(x) \big)}
-		{ p_0(x) + p_1(x) }.
+		\mathrm{Pr}\{V(P_0,P_1,\mathcal{A}^*)=1 | x = x' \} 
+		&= \mathrm{Pr}\{z=\mathcal{A^*}(x)  | x' = x' \} \\
+		&= \mathrm{Pr}\{z = \arg\!\max_{z'}\big(p_{z'}(x)\big)| x = x' \}  \\
+		&= \frac{\max\big( p_0(x'),p_1(x') \big)}
+		{ p_0(x') + p_1(x') }.
 	\end{split}
 \end{align}
-Note that we can rewrite $\max\big(p_0(x),p_1(x)\big)$:
+Note that we can rewrite $\max\big(p_0(x'),p_1(x')\big)$:
 \begin{align}
-	\max\big(p_0(x),p_1(x)\big) = \frac{1}{2}
+	\max\big(p_0(x'),p_1(x')\big) = \frac{1}{2}
 		\big(
-			p_0(x) + p_1(x) + |p_0(x) - p_1(x)|
+			p_0(x') + p_1(x') + |p_0(x') - p_1(x')|
 		\big),
@@
 \begin{align}
-	\mathrm{Pr}\{V = 1 | x' = x \} 
-	&= \frac{1}{2} + \frac{|p_0(x) - p_1(x)|}{2 \big(p_0(x) + p_1(x) \big)}.
+	\mathrm{Pr}\{V(P_0,P_1,\mathcal{A}^*) = 1 | x = x' \} 
+	&= \frac{1}{2} + \frac{|p_0(x') - p_1(x')|}{2 \big(p_0(x') + p_1(x') \big)}.
 \end{align}
-Then the overall accuracy that probability that $\mathcal{A^*}$ guesses correctly in 
-any validation test is:
+Then, summing over all possible responses $X$, 
+the overall accuracy of the optimal classifier, $\mathcal{A^*}$, is:
 \begin{align}
 	\begin{split}
-	\eta^* &= \mathrm{Pr}\{V=1\} \\
-		&=\sum_{x\in X} \mathrm{Pr}\{V = 1 | x' = x \} \mathrm{Pr}\{x' = x\}\\
-		&= \sum_{x\in X} \left(
+	\eta^* &= \mathrm{Pr}\{V(P_0, P_1, \mathcal{A}^*)=1\} \\
+	&=\sum_{x'\in X} \mathrm{Pr}\{V(P_0,P_1,\mathcal{A}^*) = 1 | x = x' \} \mathrm{Pr}\{x = x'\}\\
+		&= \sum_{x'\in X} \left(
 				\frac{1}{2} + 
-				\frac{|p_0(x) - p_1(x)|}{2 \big(p_0(x) + p_1(x) \big)}
+				\frac{|p_0(x') - p_1(x')|}{2 \big(p_0(x') + p_1(x') \big)}
 			\right)
 			\left(
-				\frac{p_0(x) + p_1(x)}{2}
+				\frac{p_0(x') + p_1(x')}{2}
 			\right)\\
@@
 				\frac{1}{2}(
-					\sum_{x \in X}p_0(x) + \sum_{x \in X}p_1(x)
+					\sum_{x' \in X}p_0(x') + \sum_{x' \in X}p_1(x')
 				) + 
-				\frac{1}{2} \sum_{x \in X} \big(|p_0(x) + p_1(x)|\big)
+				\frac{1}{2} \sum_{x' \in X} \big(|p_0(x') + p_1(x')|\big)
 			\right) \\
@@
 		\theta \geq 2\eta - 1.
+		\label{eq:sup:l1_again}
 \end{align}
@@
 \paragraph{Using cross-validation accuracy to lower-bound bias.}
-	In order for Eq.~\ref{eq:sup:l1} to be applicable, it is necessary to 
-	obtain an unbiased estimate of a classifier's accuracy.  To do so it is
+	In order for Eq.~\ref{eq:sup:l1_again} to be applicable, it is necessary to 
+	obtain an unbiased estimate of a classifier's accuracy.  To do so, it is
 	essential to test the classifier on data that were not used to build 
-	the classifier.  Generally, a portion of the data is used to test
-	optimize preprocessing, perform feature selection, and optimize 
+	the classifier.  Generally, a portion of the data is used to
+	optimize preprocessing, select features, and optimize 
 	classifier hyper-parameters, while keeping another portion of the data
@@
 
-	In our case, samples are expensive, and must be divided between 18
-	experimental treatments, so we sought to keep as many samples available 
+	In our case, the data are expensive, and must be divided between 18
+	experimental treatments, so we sought to keep as many worker responses
+	available 
 	for validation
@@
 	between alternative preprocessing options and features, 
-	rather than spending samples to empirically test these options.  Making
+	rather than spending sampled responses on empirically testing these 
+	options.  Making
 	suboptimal choices can only moderate the observed values 
 	of $\theta$, making our experiments more conservative. 
-	However, having more samples for validation tests enables us to estimate
-	those values more precisely.  
-	Using a Na\"ive Bayes classifier, which does not require hyper-parameters 
-	optimization, meant that we also did not need to spend samples on 
+	However, conserving more responses for validation 
+	tests, by not using them for classifier optimization, 
+	enables us to estimate the resulting classifier's accuracy more precisely.
+	Using a Na\"ive Bayes classifier, which does not require hyper-parameter 
+	optimization, meant that we also did not need to spend data on 
 	optimizing hyper-parameters.
 
-	Thus, no samples at all were used for optimizations.  We performed 
+	Thus, no worker responses at all were used for optimizations.  We 
+	performed 
 	leave-one-out validation, which involves training a classifier using 
-	all but one sample, and then having the classifier guess the class
-	(in our case, the priming exposure) of the left-out sample.  This is 
-	repeated $n$ times, where $n$ is the pooled number of samples in both
-	classes, each time leaving out a different sample.
+	all but one response, and then having the classifier guess the class
+	(in our case, the priming exposure) of the left-out worker.  This is 
+	repeated $n$ times, where $n$ is the pooled number of worker responses 
+	in both
+	classes (both treatments in a given experiment), 
+	each time leaving out the response of a different worker.
 
@@
 Having many more features than examples is problematic for many classifiers
-because, a large number of features leads to a high-variance, over-fit model
+because a large number of features leads to a high-variance, over-fit model,
 resulting in poor performance.  But one of the strengths of the na\"ive 
@@
 Second, the standard implementation of the na\"ive Bayes classifier has no 
-hyper-parameters to optimize. This meant that we did not need to use 
+hyper-parameter to optimize. This meant that we did not need to use 
 samples for hyper-parameters optimization, which would reduce the number
@@
 Third, the na\"ive Bayes algorithm is based on an assumption that the 
-observation one feature is independent from the observation of any 
+observation of one feature is independent from the observation of any 
 other, once we have conditioned on the class under observation 
@@
 \end{figure}
-The inequality in Eq.~\ref{l1}
-asserts that a classifiers performance in predicting class membership
-bounds the L1-distance between the distributions of features for the classes.
+The inequality in Eq.~\ref{eq:sup:l1_again}
+asserts that a classifier's performance in predicting class membership
+sets a lower bound on the L1-distance between the distributions of features 
+for the classes.
 This bound is tight for the optimal classifier, and in general, the slack
@@
 the one used to generate our results.  Furthermore, various decisions about
-preprocessing and feature representation must inevitably be made also
+preprocessing and feature representation also
 impact the classifier performance.  
@@
 no better than chance, $X \sim \mathrm{Bin}(N,0.5)$, where $N$ is the number 
-of workers in both treatments of an experiment.  Then, the critical number 
+of workers in both treatments of an experiment, and consider an alternative
+hypothesis, that the classifier does perform better than chance.  Then, the 
+critical number 
 of correct classifications, $x^*$, for a one-tailed hypothesis test with
@@
 			x: \mathrm{Pr}\{ \mathrm{Bin}(N;0.5) \geq x \} < \alpha
-		\right\}\\
+		\right\} \label{eq:sup:crit}\\
 	\text{where}\quad &\mathrm{Pr}\{ \mathrm{Bin}(N,\eta) \geq x \} = 
@@
 \textit{intertask-food-objects} has five times as many validation tests
-(larger $N$) compared to the other experiments.  We therefore assume 
+(larger $N$) compared to the other experiments.  This larger $N$ makes 
+evaluation of \ref{eq:sup:crit} difficult, but also makes the normal 
+distribution a very good approximation.  We therefore assume 
 that $X$ has a normal distribution for the classification of workers from
 \textit{intertask-food-objects}, with $\mu=N/2$ and 
-$\sigma = \frac{1}{2}\sqrt{N}$.
+$\sigma = \frac{1}{2}\sqrt{N}$.  The statistics for these hypothesis tests
+are tabulated in Tables~S\ref{table:theta} and S\ref{table:theta_pos}.
 
@@
 assuming $X$ is normally distributed.
-Since the significance values are to be shown on a plot of $\theta$, we 
+Since the confidence intervals are to be shown on a plot of $\theta$, we 
 transform them into equivalent values of 
@@
 The statistics collected for the measurement of $\theta$, corresponding to
-Figs.~\ref{fig:theta} (A and B) are tabulated in Tables~S\ref{table:theta} and
+Figs.~\ref{fig:theta}A and B are tabulated in Tables~S\ref{table:theta} and
 S\ref{table:theta_pos} respectively.
@@
 
-Since, \textit{a priori}, we do not which effects
-should be stronger (if any), we perform a two-tailed test.
+Since, \textit{a priori}, we do not know which effects
+should be stronger (if any), we perform a two-tailed test.  The results for 
+these hypothesis tests are tabulated in Table~S\ref{table:intertask_framing}.
+The results show that intertask effects are stronger than framing, but are
+on-par with echoed framing.
 
@@
 \label{table:theta}
-\end{center}
-\end{table}
-
-\begin{table}
-\begin{center}
-\begin{tabular}{c c c c c c c c c c c }
-	\toprule
-	Comparison & $N_1$ & $N_2$ & $X_1$ & $X_2$ & $\hat{\eta}_1$ 
-		& $\hat{\eta}_2$ & $z$ & $p$-value \\ 
-	\midrule
-	\parbox[c]{4cm}{\textit{intertask-food-objects} 
-	\textit{vs} \textit{frame-food-objects}} & 1190 & 238 & 777 & 122 &
-	0.653 & 0.513 & \textbf{4.1} & $2.1 \times 10^{-5}$ \\
-
-\noalign{\smallskip}
-\hdashline
-\noalign{\smallskip}
-
-	\parbox[c]{4cm}{\textit{intertask-food-objects} 
-	\textit{vs} \textit{echo-food-objects}} & 1190 & 238 & 777 & 162 
-		& 0.653 & 0.681 & -0.82 & 0.79 \\
-
-\noalign{\smallskip}
-\hdashline
-\noalign{\smallskip}
-
-	\parbox[c]{4cm}{\textit{intertask-food-culture} 
-	\textit{vs} \textit{frame-food-culture}} & 238 & 238 & 180 & 130 
-	& 0.756 & 0.546 & \textbf{4.8} & $7.6 \times 10^{-7}$ \\
-	\bottomrule
-
-\end{tabular}
-
-\caption{
-	Results for two-proportion z-tests, leading to the rejection of the null 
-	hypothesis that intertask and (passive) framing effects are equally 
-	strong.  However, the echoed framing effects are on par with intertask
-	effects (second row). 
-	Numbers in boldface indicate a $z$-statistic significantly 
-	different from zero ($\alpha=0.05$).
-}
-\label{table:intertask_framing}
 \end{center}
@@
 
+\begin{table}
+\begin{center}
+\begin{tabular}{c c c c c c c c c c c }
+	\toprule
+	Comparison & $N_1$ & $N_2$ & $X_1$ & $X_2$ & $\hat{\eta}_1$ 
+		& $\hat{\eta}_2$ & $z$ & $p$-value \\ 
+	\midrule
+	\parbox[c]{4cm}{\textit{intertask-food-objects} 
+	\textit{vs} \textit{frame-food-objects}} & 1190 & 238 & 777 & 122 &
+	0.653 & 0.513 & \textbf{4.1} & $2.1 \times 10^{-5}$ \\
+
+\noalign{\smallskip}
+\hdashline
+\noalign{\smallskip}
+
+	\parbox[c]{4cm}{\textit{intertask-food-objects} 
+	\textit{vs} \textit{echo-food-objects}} & 1190 & 238 & 777 & 162 
+		& 0.653 & 0.681 & -0.82 & 0.79 \\
+
+\noalign{\smallskip}
+\hdashline
+\noalign{\smallskip}
+
+	\parbox[c]{4cm}{\textit{intertask-food-culture} 
+	\textit{vs} \textit{frame-food-culture}} & 238 & 238 & 180 & 130 
+	& 0.756 & 0.546 & \textbf{4.8} & $7.6 \times 10^{-7}$ \\
+	\bottomrule
+
+\end{tabular}
+
+\caption{
+	Results for two-proportion z-tests, leading to the rejection of the null 
+	hypothesis that intertask and (passive) framing effects are equally 
+	strong.  However, the echoed framing effects are on par with intertask
+	effects (second row). 
+	Numbers in boldface indicate a $z$-statistic significantly 
+	different from zero ($\alpha=0.05$).
+}
+\label{table:intertask_framing}
+\end{center}
+\end{table}
+
 \subsection*{Data preprocessing}
@@
 	appear.  Prepending the task number onto words was simply a means to 
-	retain correct of words to images, since providing a word during one task 
+	retain correct attribution of words to images, since providing a word 
+	during one task 
 	is not equivalent to providing the same word during another task.
@@
 	strongly penalized because it is often possible to split a series of 
-	letters into many short two- or three-letter words, which otherwise leads 
+	letters into short two- or three-letter words, which leads 
 	to many erroneous corrections.  We found these penalties worked well when
@@
 	\caption{
-		Top five words, used to label the first test image, whose usage frequency
-		increased or decreased the most between treatments of given 
-		experiments.  Positive values indicate that the food-exposed treatment
+		The five words whose frequencies increased, and those whose 
+		frequencies decreased, the most, between treatments of given 
+		experiments, within labels attributed to the first test task.
+		Positive values indicate that the food-exposed treatment
 		used the word with higher frequency.  Word frequencies for 
-		\textit{intertask-food-objects} are aggregated across five 
-		permutations, and hence tend to show larger absolute differences.
+		\textit{intertask-food-objects} correspond to the labels attributed
+		to image 1 (see Fig. \ref{fig:task1:test}) which is not necessarily 
+		the first 
+		test task due to the tasks being permuted.  There were five times
+		as many workers in \textit{intertask-food-objects}, hence
+		larger absolute differences are observed.
 	}
@@
 
-\paragraph{Identification of food-related terms}
+\paragraph{Identification of food-related terms.}
 The wordnet corpus is composed of synsets, which are particular senses 
@@
 The subset of the wordnet corpus induced by the hyponyms of \textit{food.n.01}
-and \textit{food.n.02} provide a set of 3590 words.  Manual
+and \textit{food.n.02} consists of 3590 word-forms.  Manual
 testing showed good coverage, except for references to ethnic foods.  
-Since, especially in \textit{exp2}, we had images containing many ethnic 
+Since, especially in \textit{intertask-food-culture} and 
+\textit{frame-food-culture}, we had images containing many ethnic 
 foods, we decided to augment the wordnet corpus with words learned by 
@@
 After collecting a set of words using an automated script 
-(described above), we collected the set of words that had been used by
+(described above), we filtered down to the set of words that had been used by
 workers and which had been seen during crawling of the allrecipes.com website,
 but which were not included in wordnet.  We grafted these extra words into
-the wordnet hyponym-hypernym graph manually, which ensured that any references
-to ethnic words learned from crawling would be properly classified as 
-food references.
+the wordnet hyponym-hypernym graph manually, looking at the image to which 
+they had been attributed (to help disambiguate the intended meaning), but 
+without revealing the treatment(s) in which
+the word was used.  Many (but not all) of the words added this way did refer 
+to ethnic foods, and so this helped increase the coverage of wordnet in that 
+respect.
 
@@
 ``can I eat X'', where X is the word she is coding.  The coders were
-shown the used in the task from which the word came, to help resolve ambiguity
+shown the image used in the task from which the word came, to help resolve ambiguity
 in the sense of the word that had been given.  Coders were also shown the 
@@
 (treating the algorithm just like any other coder).  Second, adopting the 
-majority code given by the human coders, we determined the accuracy of the
-food-detection algorithm.  Data summarizing this validation process are given
+majority code given by the human coders as ground-truth, we determined the 
+accuracy of the food-detection algorithm.  
+Data summarizing this validation process are given
 in Table~S\ref{table:inter-rater}.
@@
 	human-machine code agreement, the majority human code was used.
-	Inter-rater reliability was calculated as Krippendorff's alpha.
+	Inter-rater reliability was calculated as Krippendorff's alpha, treating
+	the machine as any other coder.
 }
@@
 
-\paragraph{Calculation of relative specificity}
-In the main text we present results for the relative specificity of labels
-produced by two experimental treatments.  In performing this calculation,
-we used the wordnet corpus, which has a set of hypernym-hyponym relationships
-as described in the main text.  The first step in performing this calculation
-was therefore to map the words occurring from (the labels of) a given 
-experimental treatment onto the wordnet synsets.  In general, a given word
-form can have multiple meanings, and therefore maps onto multiple wordnet 
-synsets.
-
-The result of mapping the words from two treatments onto the wordnet 
-hypernym-hyponym graph two sets of counts, one set per treatment, 
-indicating the number of times a word from a given synset occurred among the
-labels of the treatment.  Then, for every synset in one treatment, we looked
-at the number of synsets in the other treatment that were more generic
-(reachable by following hypernym relations) less the number of words that
-were more specific (reachable by following hyponym relations).  This quantity
-tallied for all words in the original synset gives a (non-normalized) measure
-of the degree to which words from the first treatment are more specific
-than words from the second treatment, overall.  We then normalized this 
-quantity by the total number of possible comparisons between the words of
-one treatment to those of the other, where two words are considered comparable
-only if one word is the hypernym or hyponym of the other.  Hence, ``statue'' 
-and ``bread'' are not comparable, but ``pumpernickel'' and ``bread'' are.
-
-This calculation can be summarized by the following equation:
-\begin{equation}
-	S(P,Q) = \frac{
-		\sum_{w\in P}\sum_{v\in Q} \left(
-			\mathbf{1}_{[w>v]} - \mathbf{1}_{[v>w]} \right)
-	}{
-		\sum_{w\in P}\sum_{v\in Q} \left(
-			\mathbf{1}_{[w>v]} + \mathbf{1}_{[v>w]} \right)
-	},
-\end{equation}
-where $P$ and $Q$ are sets of synsets, and $\mathbf{1}_{[w>v]}$ evaluates
-to 1 if synset $w$ is more specific than (i.e. is a hyponym of) synset $v$.
-This measure counts the excess of cases where synsets from $P$ are more
-specific then synsets from $Q$, as a fraction of all comparable synset pairs.
-
-In computing this quantity between two treatments, we first computed it 
-using the labels attributed to a particular test task, and then
-averaged the result obtained in this way for each of the five test tasks.
-
-To assess statistical significance, we used the bootstrap method.
-For two given treatments $A$ and $B$, 
-119 workers were sampled from each with replacement, giving the bootstrap
-samples $A'$ and $B'$, and the relative specificity between these 
-was measured as described in \textsection S6.
-This was repeated 1000 times.  The 2.5 and 97.5 percentiles from the 
-bootstrap sample to create the 95\% confidence intervals.  If the confidence
-interval did not contain zero it indicates a statistically significant 
-difference in specificity.  The statistics for relative specificity 
-calculations are shown in Table~S\ref{table:specificity}.
-
-\begin{table}
-\centering{
-	\setlength{\tabcolsep}{4pt}
-\begin{tabular}{c c c c c c c c c c c}
-	\toprule
-	Experiment & $S$ & $S^*_\mathrm{lowCI}$ & $S^*_\mathrm{highCI}$ \\ 
-	\midrule
-	\textit{intertask-food-objects} & \textbf{13.6} & 9.1 & 17.8 \\
-	\textit{frame-food-objects} & \textbf{12.4}     & 7.6 & 17.0 \\
-	\textit{echo-food-objects} & \textbf{17.1}      & 12.1 & 21.9 \\
-	\textit{intertask-food-culture} & \textbf{19.6} & 13.7 & 25.4 \\
-	\textit{frame-food-culture} & \textbf{7.0}      & 2.1 & 15.3 \\
-	\bottomrule
-\end{tabular}
-}
-\caption{Relative specificity ($S$) of food-related words between the food- 
-	and non-food-exposed treatments of all experiments. 
-	Positive values indicates the food-exposed treatment was relatively more
-	specific; boldfaced values indicate a disparity in specificity that 
-	is statistically significant.  
-	$S^*_\mathrm{lowCI}, S^*_\mathrm{upCI}$: lower and upper
-	confidence intervals for $S$ based on the bootstrapping approach.  All
-values are expressed as percentages.}
-\label{table:specificity}
-\end{table}
-
 \paragraph{Variance in food vocabulary size (lexical richness).}
@@
 To test whether one sample has a (statistically) significantly larger
-	vocabulary size than another, we adopt the null hypothesis that they
+vocabulary size, in reference to food-related words, than another, we adopt 
+the null hypothesis that they
 have the same vocabulary, and pool the documents sampled from both 
@@
 2.5th and 97.5th percentiles of the bootstrap sample then serve as the
-	critical values of vocabulary size-difference that would justify 
-	rejection of the null hypothesis that the original samples have the same 
-	vocabulary size.
-
+critical values of vocabulary size-difference beyond which the null hypothesis
+should be rejected (at $\alpha=0.05$).
 Statistics for these hypothesis tests are shown in 
@@
 	size; $\Delta|V|$: vocabulary size of non-food less food treatments;
-	$\Delta|V|^*_{low}, \Delta|V|^*_{low}$: lower and upper critical values
+	$\Delta|V|^*_{low}, \Delta|V|^*_{high}$: lower and upper critical values
 	for statistically significant $\Delta|V|$, at $\alpha=0.05$, 
@@
 
+\paragraph{Calculation of relative specificity}
+In the main text we present results for the relative specificity of labels
+produced by two experimental treatments.  In performing this calculation,
+we used the wordnet corpus, which has a set of hypernym-hyponym relationships.
+The first step in performing this calculation was to map the words occurring 
+in (the labels of) a given experimental treatment onto the wordnet synsets.  
+In general, a given word
+form can have multiple meanings, and therefore maps onto multiple wordnet 
+synsets.
+
+Mapping the words from two treatments onto the wordnet 
+hypernym-hyponym graph yields two sets of counts, one set per treatment, 
+indicating the number of times a word from a given synset occurred among the
+labels of the treatment.  For every synset in one treatment, we looked
+at the number of synsets in the other treatment that were more generic
+(reachable by following hypernym relations) less the number of words that
+were more specific (reachable by following hyponym relations).  This quantity,
+tallied over all words in the original synset, gives a (non-normalized) 
+measure of the overall degree to which words from the first treatment are more
+specific than words from the second treatment.  We then normalized this 
+quantity by the total number of possible comparisons between the words of
+one treatment to those of the other, where two words are considered comparable
+only if one word is the hypernym or hyponym of the other.  Hence, ``statue'' 
+and ``bread'' are not comparable, but ``pumpernickel'' and ``bread'' are.
+
+This calculation can be summarized by the following equation:
+\begin{equation}
+	S(P,Q) = \frac{
+		\sum_{w\in P}\sum_{v\in Q} \left(
+			\mathbf{1}_{[w>v]} - \mathbf{1}_{[v>w]} \right)
+	}{
+		\sum_{w\in P}\sum_{v\in Q} \left(
+			\mathbf{1}_{[w>v]} + \mathbf{1}_{[v>w]} \right)
+	},
+\end{equation}
+where $P$ and $Q$ are sets of synsets associated to different experimental 
+treatments, and $\mathbf{1}_{[w>v]}$ evaluates
+to 1 if synset $w$ is more specific than (i.e. is a hyponym of) synset $v$.
+This measure counts the excess number of cases where synsets from $P$ are more
+specific then synsets from $Q$, as a fraction of all comparable synset pairs. 
+The relative specificity lies within $[-1,1]$; we report it as a percentage 
+in Table~S\ref{table:proportion-food} and in the main text.
+
+In computing this quantity between two treatments, we first computed the 
+relative specificity for the treatments separately for each test task, and 
+averaged the results obtained accross the five test tasks.
+
+To assess statistical significance, we used the bootstrap method.
+For two given treatments $A$ and $B$, 
+119 workers were sampled from each with replacement, giving the bootstrap
+samples $A'$ and $B'$, and the relative specificity between these 
+was measured as described above.
+This was repeated 1000 times.  The 2.5 and 97.5 percentiles from the 
+bootstrap sample were used to estimate 95\% confidence intervals.  
+A confidence interval not containing zero indicates a statistically 
+significant difference in specificity.  
+The statistics for relative specificity 
+calculations are shown in Table~S\ref{table:specificity}.
+
+\begin{table}
+\centering{
+	\setlength{\tabcolsep}{4pt}
+\begin{tabular}{c c c c c c c c c c c}
+	\toprule
+	Experiment & $S$ & $S^*_\mathrm{lowCI}$ & $S^*_\mathrm{highCI}$ \\ 
+	\midrule
+	\textit{intertask-food-objects} & \textbf{13.6} & 9.1 & 17.8 \\
+	\textit{frame-food-objects} & \textbf{12.4}     & 7.6 & 17.0 \\
+	\textit{echo-food-objects} & \textbf{17.1}      & 12.1 & 21.9 \\
+	\textit{intertask-food-culture} & \textbf{19.6} & 13.7 & 25.4 \\
+	\textit{frame-food-culture} & \textbf{7.0}      & 2.1 & 15.3 \\
+	\bottomrule
+\end{tabular}
+}
+\caption{Relative specificity ($S$) of food-related words between the food- 
+	and non-food-exposed treatments of all experiments. 
+	Positive values indicates the food-exposed treatment was relatively more
+	specific (which was always the case); 
+	boldfaced values indicate a disparity in specificity that 
+	is statistically significant.  
+	$S^*_\mathrm{lowCI}, S^*_\mathrm{upCI}$: lower and upper
+	confidence intervals for $S$ based on the bootstrapping approach.  
+	Specificites are expressed as percentages.}
+\label{table:specificity}
+\end{table}
+
 \end{document}

### 2015-02-10 docs/publications/2014.09_SCIENCE/man.tex
more work on manuscript

@@
 
-Microtask platforms are increasingly popular for the annotation of large
-datasets, and obtaining other judgments that require prior knowledge and 
+Microtask platforms are an increasingly popular way to solicit experimental
+participants, as well as to annotate large datasets and obtaining other 
+judgments that require prior knowledge and 
 hence are difficult to automate using only a computer.  Due to their 
@@
 HITs (bundles of microtasks) performed on Amazon's Mechanical Turk platform.  
+The flow of events experienced by a worker when participating in this study 
+is depicted in Fig.~S\ref{fig:task_schematic}.  
+The steps depicted in an orange box are those
+in which the worker interacts with Amazon's Mechanical Turk interface, and 
+are the same for any microtask completed on that platform, and similar
+on other microtask platforms.  While the steps depicted in a black box 
+are specific to our study, the general setup, in which a bundle of tasks
+follows instructions, is typical.
+\begin{figure}
+	\begin{center}
+	\includegraphics[scale=0.8]{figs/task_schematic.pdf}
+	\caption{Flow of events as experienced by a worker participating in
+		our study.  Steps with a dash outlined are only performed by 
+		workers assigned to certain treatments 
+		(see Table~S\ref{table:experiments}).  Steps outlined in orange are
+		part of Amazon's Mechanical Turk interface, and are common to any 
+		microtask performed on that platform.  Steps outlined in black are
+		specific to our HIT.
+	}
+	\label{fig:task_schematic}
+	\end{center}
+\end{figure}
+
 Each experiment was divided into two treatments.  Treatments for a given 
@@
 	Common words such as ``the'', ``to'', or ``with'', were found using
-	NLTK's English stop word list and removed \cite{loper2002nltk}.
+	NLTK's English stop word list \cite{loper2002nltk} and removed.
 

### 2015-02-12 docs/publications/2014.09_SCIENCE/man.tex
more work on manuscript

@@
 
-Microtask platforms are a form of crowdsourcing in which workers appear like 
-input-output devices.  They provide much of the flexibility and 
+In this form of crowdsourcing, workers appear like input-output devices.  
+Such platforms provide much of the flexibility and 
 cost-savings of fully automating the work in a computer program: 
@@
 task-design parameters such as the 
-level of pay \cite{kazai2013analysis}, the training and pre-screening of 
-workers \cite{le2010ensuring,paolacci2010running,kazai2013analysis}, 
-and user-interface design \cite{Finnerty2013}.  
+level of pay \cite{Mason200977,kazai2013analysis}, 
+the training and pre-screening of workers 
+\cite{le2010ensuring,paolacci2010running,kazai2013analysis}, 
+user-interface design \cite{Finnerty2013}, and timely feedback 
+\cite{Dow20121013}.
 Researchers have also investigated the effects of \textit{framing}, 
@@
 \cite{chandler2013breaking}, and the problem description
-\cite{thibodeau2013natural}.
-
-Here we focus on a ubiquitous feature of the microtask setup: the tendency
-to bundle a set of similar tasks together. 
-For example, in one bundle, a worker might be assigned a set of ten images, 
-and asked to provide descriptive words 
-(or \textit{labels}) for each.  
-On one popular microtask platform,
-Amazon's Mechanical Turk (MTurk), these bundles are called Human 
-Intelligence Tasks (HITs), but for the sake of clarity, we will use 
-``task'' to mean the smallest repeatable unit of work, which, in our study, 
-consists of labeling a single image.  This bundling tendency leads
-workers to perform a series of similar tasks in quick succession.
+\cite{thibodeau2013natural}.  Another important avenue of research concerns
+workflow design: how to break down a complex problem into microtasks
+\cite{kittur2011crowdforge}, the effect of microtask size 
+\cite{Huang201077}, and the effects of interruptions \cite{laseckieffects}.
+
+Here, we focus on a ubiquitous feature of microtask work: the tendency
+for workers to perform many similar tasks in quick succession.  
+To describe this tendency, it is necessary to clarify terminology.
+On one popular microtask platform, Amazon's Mechanical Turk (MTurk), 
+tasks are delivered in bundles called Human Intelligence Tasks (HITs).  
+But for clarity, we will use ``task'' to mean 
+the smallest repeatable unit of work; for example, labeling one image with
+some descriptive words (\textit{labels}).  
+Using this terminology, it is typical for a HIT to
+actually consist of \textit{several tasks}, 
+such as labeling ten images consecutively.
+
+In addition to the task-repetition occuring \textit{within} HITs, 
+workers prefer HITs that are part of a large set of HITs
+having the same format, and cite speed and repeatability 
+as desireable traits \cite{Chilton20101}.  When the tasks in a sequence are 
+sufficiently similar, workers are more efficient \cite{laseckieffects}, 
+and the cognitive load resulting from task-switching \cite{Adamczyk2004271} 
+is eliminated.  Meanwhile, breaking complex jobs down into simpler tasks 
+appears to improve results \cite{kittur2011crowdforge}.  
+Thus, from the perspectives of both the worker and requester, 
+it is desireable for workers to perform repetitive sequences of similar 
+tasks in quick succession.
 
@@
 Here we investigate the potential for task-repetition to induce bias in 
-microtask-based work.  If such bias is present, it would impact virtually 
+microtask-based work in a highly generalizeable setting.  
+If such bias is present, it would impact virtually 
 every microtask and crowdsourced workflow.
-The results we present here show that a worker's response during a task
+Our results show that a worker's response during a task
 does indeed depend strongly on the tasks performed beforehand.   
@@
 outputs, by automatically aggregating votes from multiple HPUs under a single
-function call.  But our revelation of strong intertask effects shows that, 
+function call.
+
+But our revelation of strong intertask effects shows that, 
 in addition to stochasticity, HPUs are subject to \textit{hysteresis}, 
@@
 (about 28\%), but remained significant through all five test tasks 
-($\alpha=0.05$) sustaining nearly 15\% bias (Fig. \ref{fig:theta}B).
+($\alpha=0.05$) sustaining over 12\% bias (Fig. \ref{fig:theta}B).
 
@@
 Prior to this study, little thought appears to have been given to the 
-ordering and bundling of microtasks.  But our findings show that these are 
-powerful design factors.  A natural response might be simply to randomize 
+priming effect that a task can have on those tasks that follow. 
+But our findings show this is an  
+important design consideration.  
+A natural response might be simply to randomize 
 task ordering, a practice that is commonly employed.  But the sheer extent of 
@@
 This has been achieved in some
-applications \cite{Mortensen20131020,Warby2014385}. 
+applications \cite{snow2008cheap,Mortensen20131020,Warby2014385}. 
 The distinction between experts and novices can be 
@@
 Microtask platforms are an increasingly popular way to solicit experimental
-participants, as well as to annotate large datasets and obtaining other 
-judgments that require prior knowledge and 
-hence are difficult to automate using only a computer.  Due to their 
-popularity, there is interest in understanding how various task design factors
+participants, as well as to annotate large datasets and obtain other 
+judgments which are difficult to automate using only a computer.  
+Due to the popularity of microtask platforms, there is interest in 
+understanding how various task design factors
 influence the reliabality of data obtained using microtask platforms.  
-Since tasks are typically bundled together, microtask 
-workers tend to perform several similar tasks in quick succession, creating an opportunity for priming effects to induce bias in the results obtained.
+Since workers typically perform similar tasks in quick succession, there is
+an opportunity for earlier tasks to effectively prime workers, and induce 
+bias in the results obtained.
 Here we describe in detail experiments presented in the main text, in which
 we investigate the effect that prior tasks have on the responses given during
-subsequent tasks.
+subsequent ones.
 
@@
 The work presented in the main text consisted of six experiments involving
-HITs (bundles of microtasks) performed on Amazon's Mechanical Turk platform.  
+HITs (bundles of tasks) performed on Amazon's Mechanical Turk platform.  
 The flow of events experienced by a worker when participating in this study 
 is depicted in Fig.~S\ref{fig:task_schematic}.  
-The steps depicted in an orange box are those
-in which the worker interacts with Amazon's Mechanical Turk interface, and 
-are the same for any microtask completed on that platform, and similar
-on other microtask platforms.  While the steps depicted in a black box 
-are specific to our study, the general setup, in which a bundle of tasks
-follows instructions, is typical.
+Each experiment was divided into two treatments.  Treatments for a given 
+experiment differed with respect to a particular priming modality, which 
+served as the independent variable
+(as specified in Table~S\ref{table:experiments}).  
+The HITs for treatments of the same experiment always involved the same
+test tasks (the last five tasks in the HIT),
+the results of which served as the dependent variable.
 \begin{figure}
@@
 \end{figure}
-
-Each experiment was divided into two treatments.  Treatments for a given 
-experiment differed with respect to a particular priming modality, which 
-served as the independent variable
-(as specified in Table~S\ref{table:experiments}).  
-The HITs for treatments of the same experiment always involved the same
-test tasks (the last five tasks in the HIT),
-the results of which served as the dependent variable.
 
@@
 question, along with a coin we know to be fair, many times 
-(say 100 million times), and then using a $\chi^2$ test to decide whether 
+(say 100 million times), and then use a $\chi^2$ test to decide whether 
 the two coins have the same probability of turning up heads.
@@
 	\caption{
-		Bias induced by exposure to initial tasks and frames.
-		Bias is defined to be the difference in the probability 
-		distribution over workers' labels (L1-distance).  The plotted values
-		give a lower bound to the L1-distance, $D_{L1}^-$, which was 
-		determined from a classifier's performance in 
-		distinguishing workers that had undergone different exposures.
+		Empirical bias, measured using classifiers, induced in image 
+		labeling tasks, by exposing workers to initial tasks or framing. 
 		The bias was determined using (A-F) a na\"ive Bayes classifier, and 
-		(G-L) an SVM classifier.
+		(G-L) an SVM classifier, according to Eq.~\ref{eq:sup:l1}.
 		In panels A through F, each plot adds an additional
 		preprocessing step to those used in the previous plot; the same is 
-		done for panels G through H: A,G) No 
+		done for panels G through H: A,G) no 
 		preprocessing; B,H) spelling correction; C,I) stop word removal; 
@@
 		F,L) distinguishing identical labels entered in different form inputs.
+		Standard error bars are shown.
 	}
@@
 	(one-tailed test), $x^*$; 
-	lower bound estimate of bias based on observed number of successful
-	classifications, $\hat{\theta}$; lower confidence interval for lower
-	bound estimate of bias, $\theta^*_\mathrm{low}$; upper confidence 
-	interval for same, $\theta^*_\mathrm{high}$.  Hypothesis test and 
+	estimate of bias based on observed number of successful
+	classifications, $\hat{\theta}$; lower confidence interval limit 
+	for the estimate of bias, $\theta^*_\mathrm{low}$; upper confidence 
+	interval limit for same, $\theta^*_\mathrm{high}$.  Hypothesis test and 
 	confidence intervals are based on a significance of $\alpha=0.05$.
@@
 	for test images at specific positions in the sequence of five test images.
-	These values are averaged over five different permutations, such that 
-	the strength of intertask effects are measured for each of the test images
-	in each of the positions.
+	These values are averaged over five different permutations.
 	Number of validation tests, $N$; number of successful classifications, 
@@
 	(one-tailed test), $x^*$; 
-	lower bound estimate of bias based on observed number of successful
-	classifications, $\hat{\theta}$; lower confidence interval for lower
-	bound estimate of bias, $\theta^*_\mathrm{low}$; upper confidence 
+	estimate of bias based on observed number of successful
+	classifications, $\hat{\theta}$; lower confidence interval limit
+	for the estimate of bias, $\theta^*_\mathrm{low}$; upper confidence 
 	interval for same, $\theta^*_\mathrm{high}$.  Hypothesis test and 
@@
 \caption{
-	Results for two-proportion z-tests, leading to the rejection of the null 
-	hypothesis that intertask and (passive) framing effects are equally 
-	strong.  However, the echoed framing effects are on par with intertask
-	effects (second row). 
-	Numbers in boldface indicate a $z$-statistic significantly 
-	different from zero ($\alpha=0.05$).
+	Results for two-proportion z-tests, testing the null hypothesis that 
+	intertask and framing effects are equally strong.
+	In the cases of comparing intertask effects to passive framing, the
+	null hypothesis should be rejected ($\alpha=0.05$), but 
+	echoed framing effects are on par with intertask effects (second row). 
+	$z$-statistics in boldface are significantly different from zero.
 }
@@
 		Positive values indicate that the food-exposed treatment
-		used the word with higher frequency.  Word frequencies for 
+		used the word with higher frequency.  
+		Note that the word ``food'' is always the most suppressed among
+		food-exposed workers.
+		Word frequencies for 
 		\textit{intertask-food-objects} correspond to the labels attributed
@@
 }
-\caption{Statistics for the comparison of the proportions of food-related
-	labels between treatments of all experiments.  $s$: sample standard
-	deviation.
+\caption{Statistics for the comparison of the proportions of food-references
+	among words used in labels, between treatments of all experiments.  
+	$s$: sample standard deviation.
 }
@@
 	Statistics for the measurement of vocabulary size difference, for each
-	experiment, between the food and non-food treatments. $|V|$: vocabulary
-	size; $\Delta|V|$: vocabulary size of non-food less food treatments;
-	$\Delta|V|^*_{low}, \Delta|V|^*_{high}$: lower and upper critical values
-	for statistically significant $\Delta|V|$, at $\alpha=0.05$, 
-	based on bootstrapping.  
+	experiment, between the food and non-food treatments. Vocabulary
+	size, $|V|$; vocabulary size of non-food less food treatments, 
+	$\Delta|V|$; lower and upper critical values, $\Delta|V|^*_{low}$ and 
+	$\Delta|V|^*_{high}$, for statistically significant 
+	$\Delta|V|$, at $\alpha=0.05$, based on bootstrapping.  
 	Boldfaced values for $\Delta|V|$ are statistically significant.
@@
 	is statistically significant.  
-	$S^*_\mathrm{lowCI}, S^*_\mathrm{upCI}$: lower and upper
+	$S^*_\mathrm{lowCI}, S^*_\mathrm{highCI}$: lower and upper
 	confidence intervals for $S$ based on the bootstrapping approach.  

### 2015-02-13 docs/publications/2014.09_SCIENCE/man.tex
major chop

@@
 the content that workers chose to focus on, as well as the richness and 
-specialization of their word choice. While these intertask effects can be a 
+specialization of their word choice. While these \textit{intertask effects} 
+can be a 
 source of systematic bias, our results suggest that, with appropriate job 
@@
 for remuneration, a sense of purpose, and fun
-\cite{kazai2013analysis,Antin20122925}.
-Typical tasks include tagging and categorizing images 
-\cite{6116320,Zhai2012357}, coding and transcription, such as of voice recordings or handwritten notes
-\cite{chandler2013breaking,paolacci2010running,Berinsky2012351,Finnerty2013}, 
+\cite{kazai2013analysis}.
+Typical tasks include tagging and categorizing images,
+%\cite{6116320,Zhai2012357}, 
+coding and transcription, such as of voice recordings or handwritten notes,
+%\cite{chandler2013breaking,Berinsky2012351,Finnerty2013},%paolacci2010running}, 
 and judging relevancy and quality, for example, to rate information 
-retrieval systems \cite{le2010ensuring,grady2010crowdsourcing,alonso2009can,kazai2013analysis}.
+retrieval systems\footnote{We provide a survey of task types in the supplementary text.}.
+%\cite{le2010ensuring,grady2010crowdsourcing,alonso2009can,kazai2013analysis}.
 
@@
 recruiting temporary workers or experimental subjects
-\cite{Berinsky2012351,paolacci2010running,ranade2012crowdsource}.
-From the requester's perspective, using microtask platforms resembles
-running a computer program on a remote server, leading some to investigate
-these platforms as a new computing architecture \cite{5543192,little2010turkit,minder2012crowdlang,kittur2011crowdforge}.
-
-Due to its flexibility and cost-effectiveness, 
-there has been a surge in demand for microtask work
-in both industry and academia\cite{wolfson2011look,Berinsky2012351}.  
-Naturally, there is a desire to understand the factors affecting the 
-reliability of microtask-based methods.  Researchers have investigated 
-task-design parameters such as the 
-level of pay \cite{Mason200977,kazai2013analysis}, 
+\cite{Berinsky2012351}. %,ranade2012crowdsource}%,paolacci2010running}.
+From the requester's perspective, microtask platforms resemble
+a remote compute server, and some seriously consider microtask platforms 
+as a new kind of computing architecture
+\cite{5543192}. %,little2010turkit,minder2012crowdlang,kittur2011crowdforge}.
+
+The flexibility and cost-effectiveness of microtask labour
+has led to a surge in demand from industry and 
+academia\cite{wolfson2011look,Berinsky2012351},
+leading researchers to investigate the factors affecting its reliability.  
+Among these factors are
+the level of pay \cite{Mason200977,kazai2013analysis}, 
 the training and pre-screening of workers 
-\cite{le2010ensuring,paolacci2010running,kazai2013analysis}, 
-user-interface design \cite{Finnerty2013}, and timely feedback 
-\cite{Dow20121013}.
-Researchers have also investigated the effects of \textit{framing}, 
+\cite{le2010ensuring,kazai2013analysis}, %paolacci2010running}, 
+user-interface design \cite{Finnerty2013}, and the provision of timely 
+feedback \cite{Dow20121013}.
+Researchers have also investigated \textit{framing}, 
 by altering the description of the workflow context 
-\cite{Kinnaird2012281}, the purpose of tasks 
+\cite{Kinnaird2012281}, the stated purpose of tasks 
 \cite{chandler2013breaking}, and the problem description
-\cite{thibodeau2013natural}.  Another important avenue of research concerns
-workflow design: how to break down a complex problem into microtasks
-\cite{kittur2011crowdforge}, the effect of microtask size 
-\cite{Huang201077}, and the effects of interruptions \cite{laseckieffects}.
+\cite{thibodeau2013natural}.  Another important optimization concerns
+workflow design: how breaking down a complex problem into microtasks
+\cite{kittur2011crowdforge}, altering microtask size 
+\cite{Huang201077}, and introducing workflow interruptions 
+\cite{laseckieffects} impact worker quality and efficiency.
 
@@
 for workers to perform many similar tasks in quick succession.  
-To describe this tendency, it is necessary to clarify terminology.
+%To describe this tendency, it is necessary to clarify terminology.
 On one popular microtask platform, Amazon's Mechanical Turk (MTurk), 
-tasks are delivered in bundles called Human Intelligence Tasks (HITs).  
-But for clarity, we will use ``task'' to mean 
-the smallest repeatable unit of work; for example, labeling one image with
-some descriptive words (\textit{labels}).  
-Using this terminology, it is typical for a HIT to
-actually consist of \textit{several tasks}, 
-such as labeling ten images consecutively.
-
+tasks are delivered in bundles called HITs.
+Although HIT stands for ``Human Intelligence Task'', we use ``task'' to mean
+the smallest repeatable unit of work.  For example, one HIT may involve 
+labeling ten images with descriptive words (\textit{labels}), while for
+the present discussion, we consider labeling a single image to be a task.
 In addition to the task-repetition occuring \textit{within} HITs, 
-workers prefer HITs that are part of a large set of HITs
-having the same format, and cite speed and repeatability 
-as desireable traits \cite{Chilton20101}.  When the tasks in a sequence are 
-sufficiently similar, workers are more efficient \cite{laseckieffects}, 
-and the cognitive load resulting from task-switching \cite{Adamczyk2004271} 
-is eliminated.  Meanwhile, breaking complex jobs down into simpler tasks 
-appears to improve results \cite{kittur2011crowdforge}.  
-Thus, from the perspectives of both the worker and requester, 
-it is desireable for workers to perform repetitive sequences of similar 
-tasks in quick succession.
+workers prefer those HITs that have many available repetitions (that is,
+many more HITs of the same format, but with different data) 
+\cite{Chilton20101}.
+
+%Complex work consists of heterogeneous subtasks; when complex work is
+%broken down and workers perform sequences of very similar simple tasks
+%cognitive load is reduced, and workers are more efficient and accurate 
+%\cite{Adamczyk2004271,laseckieffects,kittur2011crowdforge}.
+%Thus, the tendency for workers to perform series of repetitive, similar
+%tasks would appear to be beneficial.
 
@@
 to a prompt can be strongly influenced by their recent exposure to stimuli,
-due to the well-known phenomenon of \textit{priming} 
-\cite{BJOP1796,No2007,beller1971priming}.  Priming is typically relevant when 
-the prior stimuli bear some conceptual or perceptual connection to the 
-ensuing task\cite{Gass1999549,sohn2001task}, and so, the repetition of 
-similar tasks within the typical microtask setup creates an ideal context for 
-strong priming effects.
-
-Researchers investigating a somewhat similar class of psychological phenomena,
-found that ratings that microtask workers give to items in a list
-depend on the order in which the list is presented, an effect known as
-\textit{positional bias} \cite{lerman2014leveraging}.  This serves as an 
-example of a basic psychological phenomenon impacting crowdsourced data,
-and raises questions about what other cognitive biases might
-affect microtask work, and how prevalent the induced bias might be.
-
-Here we investigate the potential for task-repetition to induce bias in 
-microtask-based work in a highly generalizeable setting.  
-If such bias is present, it would impact virtually 
-every microtask and crowdsourced workflow.
+due to \textit{priming} 
+\cite{BJOP1796}. %,No2007}. %,beller1971priming}.  
+Priming can arise when 
+a prior stimulus is conceptually or perceptually related to an ensuing 
+task, so the repetition of 
+similar tasks may create an opportunity for strong priming effects
+\cite{Gass1999549} %,sohn2001task}
+.
+
+%Researchers investigating a somewhat similar class of psychological phenomena,
+%found that ratings that microtask workers give to items in a list
+%depend on the order in which the list is presented, an effect known as
+%\textit{positional bias} \cite{lerman2014leveraging}.  This serves as an 
+%example of a basic psychological phenomenon impacting crowdsourced data,
+%and raises questions about what other cognitive biases might
+%affect microtask work, and how prevalent the induced bias might be.
+
+We investigate the potential for task repetition to induce bias in 
+a highly generalizeable microtask setup, in which workers label a 
+series of images.  If task-induced priming arises in our setup, 
+it should be expected in virtually every microtask and crowdsourced workflow
+where workers are called upon to exercise their judgment.
 Our results show that a worker's response during a task
@@
 We call the effects that earlier tasks exert on later ones 
-\textit{intertask effects}.
-
-As we have described, microtask platforms have been widely adopted as a 
-tool, but computer scientists also hold such platforms as the object of 
-research, viewing  microtask platforms as a new kind of computing 
-architecture.  In analogy to CPUs (central 
-processing units) and GPUs (graphics processing units), 
-Davis \textit{et al} invoked the \textit{human processing unit}, or HPU \cite{5543192}.
-Researchers have sought to define a set of basic HPU operations, and
-have developed libraries and frameworks to simplify HPU programming 
-and make it more like CPU programming 
-\cite{little2010turkit,minder2012crowdlang,kittur2011crowdforge}.  
-As an example, one operation overcomes the inherent stochasticity of HPU 
-outputs, by automatically aggregating votes from multiple HPUs under a single
-function call.
-
-But our revelation of strong intertask effects shows that, 
-in addition to stochasticity, HPUs are subject to \textit{hysteresis}, 
-meaning that their 
-outputs depend on the history of their inputs.  Reproducibility and 
-path-independence are crucial properties for the components of a 
-computing architecture, so a better understanding of the computational 
-ramifications of many psychological phenomena is needed.
-
-We investigated intertask effects using image-labeling tasks on the Amazon 
-Mechanical Turk (MTurk) microtask platform.  
-In addition to being one of the most common kinds of tasks
-\cite{chandler2013breaking,Berinsky2012351,Finnerty2013,paolacci2010running},
-image-labeling is prototypical for any kind of task in which the worker is 
-asked to provide a high-level judgment, incorporating prior knowledge, in 
-response to a prompt.  
-This includes such diverse tasks as describing
-video and audio recordings, summarizing texts, or providing feedback to a 
-product review.
-
-In our first experiment, which we call
-\textit{intertask-food-objects}, workers were assigned to either a
-\textit{food} or \textit{objects} treatment.  Workers in these treatments
+\textit{intertask effects}.  If, as has been suggested \cite{5543192}, 
+microtask platforms are to be considered as a new form of computing 
+architecture, it will be necessary to consider that the computing elements 
+exhibit \textit{hysteresis}, meaning that microtask workers' outputs depend 
+on the \textit{history} of their inputs.
+
+%As we have described, microtask platforms have been widely adopted as a 
+%tool, but computer scientists also hold such platforms as the object of 
+%research, viewing  microtask platforms as a new kind of computing 
+%architecture.  In analogy to CPUs (central 
+%processing units) and GPUs (graphics processing units), 
+%Davis \textit{et al} invoked the \textit{human processing unit}, or HPU \cite{5543192}.
+%Researchers have sought to define a set of basic HPU operations, and
+%have developed libraries and frameworks to simplify HPU programming 
+%and make it more like CPU programming 
+%\cite{little2010turkit,minder2012crowdlang,kittur2011crowdforge}.  
+%As an example, one operation overcomes the inherent stochasticity of HPU 
+%outputs, by automatically aggregating votes from multiple HPUs under a single
+%function call.  
+%
+%But our revelation of strong intertask effects shows that, 
+%in addition to stochasticity, HPUs are subject to \textit{hysteresis}, 
+%meaning that their 
+%outputs depend on the history of their inputs.  Reproducibility and 
+%path-independence are crucial properties for the components of a 
+%computing architecture, so a better understanding of the computational 
+%ramifications of many psychological phenomena is needed.
+
+Our image-labeling tasks were performed on the MTurk microtask platform.  
+We chose image labeling because it is very common\footnote{
+	We discuss task composition in the supplementary text.
+},
+%\cite{chandler2013breaking,Finnerty2013},%,paolacci2010running},
+and because it is prototypical for any kind of task in which the worker is 
+asked to provide a response that is not precisely determined by 
+the prompt, but instead depends on the worker's judgment.  
+This includes such diverse tasks as describing video and audio recordings, 
+summarizing texts, or providing feedback to a product review.
+
+In our first experiment, called \textit{intertask-food-objects},
+workers were assigned to either a
+\textit{food} or \textit{objects} treatment.  Workers in both treatments
 performed a set of five \textit{initial tasks}, which each involved 
-providing five descriptive labels for an image depicting 
+providing descriptive labels for an image depicting 
 either food or (non-food) objects, depending on the worker's 
@@
 tasks, workers performed five \textit{test tasks}, which were identical for 
-both treatments.  The test tasks contained images depicting a 
-mixture of food and objects (Fig.~\ref{fig:task}C), and workers
-were again asked to provide five labels for each.  Five initial 
-tasks, together with the test tasks, comprised one HIT\footnote{
+both treatments.  In the the test tasks, workers labeled images depicting a 
+mixture of food and objects (Fig.~\ref{fig:task}C).  The five initial 
+and test tasks performed by each worker comprised one HIT\footnote{
 	Workers were only allowed to participate in one HIT relating to this study.
-}. During the HIT, workers 
-were presented images one at a time, and, crucially, we made no 
+}. The images were presented one at a time, and we made no 
 distinction between the initial and test tasks.
 
-A $\chi^2$ test shows that the frequencies of words used by
+The frequencies of words used by
 workers in the \textit{food} and \textit{objects} treatments differed
-significantly during test tasks ($p = 6.0 \times 10^{-14}$), even though the test tasks were identical 
-in both treatments\footnote{see supplementary text for tabulated statistics.}.  This shows that earlier tasks have a 
-significant effect on later ones, and raises concerns about the 
-design of microtasks, and possibly the microtask methodology itself.
-
-While this affirms the \textit{existence} of intertask effects, we wish to
-understand the nature and severity of the bias induced by prior task 
-exposures.  To this end, we define the extent of bias, $\theta$, in terms of
-the strength of influence that a perturbation has on worker's responses.
+significantly during test tasks (by $\chi^2$ test, $p = 6.0 \times 10^{-14}$),
+even though the test tasks were identical in both treatments\footnote{
+	see supplementary text for tabulated statistics.
+}.  Thus earlier tasks significant affect later ones, raising concerns 
+about the the microtask methodology itself.
+
+Having affirmed the \textit{existence} of intertask effects, we wish to
+understand the nature and severity of the bias thus induced.
+We therefore define the extent of bias, $\theta$, in terms of
+the strength of influence that a prior perturbation has on workers' responses.
 Since workers' responses are stochastic, we define the extent of bias in 
-terms of the shift induced in the distribution of responses\footnote{
+terms of the change induced in the distribution of responses\footnote{
 	This is a general divergence metric between probability 
@@
 \end{equation}
-where $p_i(x)$ is the probability that a worker subjected to treatment $i$
+where $p_i(x)$ is the probability that a worker, subjected to treatment $i$,
 provides response $x$, from the set of possible responses $X$.
-It is important to emphasize that a significant result from a $\chi^2$ test 
-only allows us to conclude that $\theta$ is non-zero 
-(see supplementary text).  
+A significant result from a $\chi^2$ test only allows us to conclude that 
+$\theta$ is non-zero (see supplementary text).  
 Determining $\theta$ from finite samples of responses, using purely 
@@
 had been?  Intuitively, the greater the effect that prior tasks have on 
-subsequent
-responses, the more accurate the classifier can be.  Formally (as shown
-in the supplementary text), the accuracy of such a classifier, $\eta$,
-yields a lower bound on the bias:
+subsequent responses, the more accurate the classifier can be.  
+Formally (as shown in the supplementary text), the accuracy of such a 
+classifier, $\eta$, establishes a lower bound on the bias:
 \begin{equation}
@@
 bias induced by any perturbation, including both intertask effects and 
-framing.  As defined, bias ranges from 0 (meaning the exposures 
+framing.  Bias ranges from 0 (meaning the exposures 
 does not affect the distribution of responses), to 1 
@@
 \cite{Kinnaird2012281,chandler2013breaking,thibodeau2013natural}, so,
-as a point of comparison, we performed a similar experiment 
+as a point of comparison, we describe a similar experiment 
 in which we framed the purpose of the tasks.  In the experiment 
-\textit{frame-food-objects}, workers were either told that 
+\textit{frame-food-objects}, the same test-tasks were used, but rather
+than exposing workers to initial tasks, workers were either told that 
 the tasks were ``Funded by the laboratory for the visual perception of Food 
@@
 
-To assess the permenance of intertask effects, we replicated the experiment
-\textit{intertask-food-objects} five times, each time using a different 
-permutation of the test tasks.  This enabled us to measure the severity
-of bias as a function of task position, independant of the content
-of the test task.  We found that bias was strongest for the first test task
-(about 28\%), but remained significant through all five test tasks 
+To assess the persistence of intertask effects, we replicated the experiment
+\textit{intertask-food-objects} while permuting the test tasks, to reveal the 
+dependence of intertask effects on task position.
+We found that bias was strongest for the first test task (about 28\%), 
+but remained significant through all five test tasks 
 ($\alpha=0.05$) sustaining over 12\% bias (Fig. \ref{fig:theta}B).
@@
 workers were either assigned to a \textit{food} or \textit{culture} treatment.
-As before, the initial tasks for the \textit{food} treatment contained images 
-depicting food (Fig.~\ref{fig:task}D). 
-In the \textit{culture} treatment, 
-the initial tasks contained images depicting cultural scenes 
-(of dance, sport, or music) (Fig.~\ref{fig:task}E).  The test tasks, which were identical for both
-treatments, included images depicting meals of identifiable cultural 
-origin\footnote{
+The initial tasks contained either images 
+depicting food (Fig.~\ref{fig:task}D), or depictions of cultural scenes 
+(of dance, sport, or music) (Fig.~\ref{fig:task}E).  The test tasks, which 
+were, again, identical for both treatments, depicted meals of identifiable 
+cultural origin\footnote{
 	Despite efforts to the contrary, initial tasks 
@@
 strong bias as a result of intertask effects (about 50\%) 
-(Fig.~\ref{fig:theta}A).  Again, we compared intertask effects to 
-framing, by performing an experiment (\textit{frame-food-culture}) using 
-the same test tasks as in \textit{intertask-food-culture}, in which we exposed
-workers to a statement framing the purpose of the tasks as the recognition 
-of either food or culture.  
-In this experiment, framing did not induce significant changes in the 
-frequencies of words used during test tasks (by $\chi^2$ test, $p=0.29$) 
-(Fig.~\ref{fig:theta}A).
-
-It was only when we combined the use of framing, with an active 
-reiteration step, that bias reached a level comparable to that achieved 
-by intertask effects.  In the experiment \textit{echo-food-objects},
-after framing the purpose of the task around either the recognition of food
-or objects, we required the worker to echo back the purpose of the task
-using a combo-box input.  In this case, workers exposed to different 
-``echoed framing'' showed a bias of about 35\% in the labels provided during 
-test tasks
-(Fig.~\ref{fig:theta}A). However, it is difficult to say whether this 
+(Fig.~\ref{fig:theta}A).  Again, comparing intertask effects to 
+framing, the experiment (\textit{frame-food-culture}) used
+the same test tasks as in \textit{intertask-food-culture}, but exposed
+workers to statements framing the purpose of the tasks as the recognition 
+of either food or culture.  In this experiment, framing did not induce 
+significant changes in word frequencies (by $\chi^2$ test, $p=0.29$) (Fig.~\ref{fig:theta}A).
+
+It was only when framing was combined with an active reiteration step, 
+that bias reached a comparable extent to that induced by intertask effects.  
+In the experiment \textit{echo-food-objects},
+after framing the purpose of the task (as the recognition of food
+or objects), workers were asked to echo the purpose of the task
+using a combo-box input.  This  ``echoed framing'' induced a bias of about 
+35\% (Fig.~\ref{fig:theta}A). However, it is difficult to say whether this 
 should be considered as a framing treatment \textit{per se}.
-Requiring the worker to reiterate the frame signals our intent, as the 
-requester, to ensure that the worker has taken note of the framing statement, 
-possibly leading the worker to interpret it as an instruction.  
+Requiring the worker to reiterate the purpose signals our intent, as the 
+requester, to ensure that the worker has taken note of it, possibly leading 
+the worker to interpret the exchange as an instruction.  
 In any case, it is remarkable that intertask effects
-were on par with an explicit statement of purpose that was emphasized 
-through reiteration.
+were on par with an explicit, actively reinforced statement of purpose.
 
@@
 intertask effects, we investigated the vocabulary
-that workers used to label test tasks. A natural expectation is that, during
-the test tasks within
-a given experiment, the food-primed workers would use food-related words 
-more often than their non-food-primed counterparts.  However, this was not 
-generally 
+that workers used to label test tasks. One might expect that, within a given 
+experiment, the food-primed workers would label test tasks using 
+food-related words more often.  However, this was not generally 
 the case. In the \textit{intertask-food-culture} experiment, food-primed
@@
 rules out a seemingly-simple idea that workers emphasize
-content that has been present in earlier tasks: seeing content in prior tasks
+content that has been present in earlier tasks: seeing content 
 influences, but does not necessarily \textit{increase}, the probability of 
-referring to the content in subsequent tasks.
+referring to it in subsequent tasks.
 
@@
 used.  Even if workers provide an abundance of food-related words, there
-can be less diversity if the same words are often repeated.  
-This could happen, for example, if workers use generic references 
+can be less diversity, if, for example, workers repeat generic references 
 to food.
 Both \textit{intertask} experiments showed that food-exposed workers had 
-greater lexical richness, in reference to food, than their non-food-primed 
-counterparts (as much as 20\% more) (Fig.~\ref{fig:specificity}B).  
-The increase in lexical richness in the case of 
-\textit{intertask-food-culture} is particularly noteworthy, because in that 
-experiment, food-primed workers made fewer total references to food.  
-We also observed enrichment of the food-related lexicon in the 
-\textit{priming-food-objects}, and \textit{echo-food-objects} experiments, 
-although to a lesser extent.
-
-The observations regarding lexical richness lead us to suspect that 
+greater lexical richness, in reference to food, than their counterparts 
+(as much as 20\% more) (Fig.~\ref{fig:specificity}B).  
+This is particularly noteworthy in the experiment
+\textit{intertask-food-culture}, because there
+food-primed workers made fewer total references to food.  
+%We also observed enrichment of the food-related lexicon in the 
+%\textit{priming-food-objects}, and \textit{echo-food-objects} experiments, 
+%although to a lesser extent.
+
+The observations regarding lexical richness suggest that 
 initial tasks might influence workers to use more refined or specialized 
 words, when referring to aspects of content that had been present in the 
-initial tasks (i.e. food).  This would help explain why, in the case of 
-\textit{intertask-food-culture}, we observed a significantly greater 
-\textit{diversity} of food-related words despite their significantly lesser 
-\textit{total amount}.
-To test whether exposure to food in initial tasks increased the specialization
-of food-references, we used the wordnet corpus to operationalize the 
-notion of word specialization.  Wordnet provides a set of hypernym-hyponym 
-relations between 117,798 English nouns 
-\cite{miller1995wordnet,felbaum1998wordnet}.  Hypernyms are generalizations 
-(for example, ``bread'' is a hypernym for 
-``pumpernickel''), while hyponyms are specializations.
-For each experiment, we compared food-related words provided by workers from 
-one treatment to those from the other, tallying the percent-excess of
-cases where one treatment's words were more specialized than the other 
-(detailed calculation in the supplementary text).
+initial tasks.  
+To test this, we used the wordnet corpus to operationalize the 
+notion of word specialization.  Wordnet establishes relationships between
+117,798 English nouns, indicating which words are specializations
+(or generalizations) of others \cite{felbaum1998wordnet}. 
+%miller1995wordnet,}.  
+For example, ``pumpernickel'' is a specialization of ``bread''.
+Within each experiment, we determined the percent-excess of food-related
+words that were more specialized in the food-exposed treatment relative
+to the other treatment (detailed calculation in the supplementary text).
 
 In all experiments except \textit{frame-food-culture}, food-primed workers 
-used significantly more specialized words, in reference to food, 
-than their non-food-primed 
-counterparts (about 15\% more) (Fig.~\ref{fig:specificity}C).
+were used significantly more specialized words, in reference to food 
+(about 15\% more) (Fig.~\ref{fig:specificity}C).
 It is interesting that such substantial increases in both the lexical 
@@
 
-Taken together, our results can be 
-explained through a combination of positive and negative priming effects.
+Our results can be 
+explained through a combination of positive and negative priming.
 Positive priming (usually simply ``priming'') occurs when a prior stimulus 
@@
 
-Workers exposed to images containing food will be (positively) primed, 
+Workers exposed to images containing food are (positively) primed, 
 activating memories, concepts, and vocabulary related to food.  
-However, as the worker labels successive images containing food, the basic 
-fact that an image contains food will not appear to be salient, since it 
-does not serve to distinguish one image from another.  Thus, the most 
+However, if the worker labels several images containing food, the basic 
+fact that an image contains food will not seem salient, since it 
+does not distinguish one image from another.  Thus, the most 
 generic references to that fact, such as the label ``food'', 
@@
 
-Prior to this study, little thought appears to have been given to the 
-priming effect that a task can have on those tasks that follow. 
-But our findings show this is an  
-important design consideration.  
-A natural response might be simply to randomize 
-task ordering, a practice that is commonly employed.  But the sheer extent of 
-bias suggests that this will still introduce a significant amount of noise
-into the results.  Even chains of two or three similar tasks, which
+Prior to this study, little thought appears to have been given to
+earlier tasks as a priming vector for later tasks.
+But our findings show this is an important design consideration.  
+One recourse might be to randomize task ordering, a practice that is 
+commonly employed.  But the sheer extent of bias we observed suggests that 
+this will still admit a significant amount of noise.  
+Even chains of two or three similar tasks, which
 will not be reliably eliminated in random permutations, could lead
 to the levels of bias we observed in our experiments.
-It would be preferable to understand intertask
-effects in greater depth so that they might be properly controlled.
-
-Our findings suggest that, through careful task engineering,
-it might be possible to achieve greater quality and reproducibility
-of responses.  
+Preferably, a deeper understanding of intertask effects might allow them
+to be properly controlled.
+
+Our findings also suggest that careful task engineering might leverage
+intertask effects to achieve greater quality and reproducibility in 
+crowdsourcing.
 A consistent goal in human computation is the achievement of expert-level
@@
 applications \cite{snow2008cheap,Mortensen20131020,Warby2014385}. 
-The distinction between experts and novices can be 
-attributed in part to the possession of specialized knowledge and heuristics. 
-But to a large degree, this distinction lies in the ability of 
-experts to direct their focus toward salient features, while filtering out 
-non-salient ones \cite{kellman2009perceptual}.  Using strategic task 
-exposure, it might be possible to guide workers' focus and salience 
-attribution, enabling expert-level judgment in a wider variety of 
+The distinction between experts and novices is partly attributable
+to specialized knowledge and heuristics. 
+But experts also simplify tasks by more efficiently directing 
+their focus toward salient features \cite{kellman2009perceptual}.  
+Using strategic task exposure, it might be possible to guide workers' focus 
+and salience attribution, enabling expert-level judgment in a wider variety of
 crowdsourced applications.
-We anticipate that future work will yield techniques to control intertask 
-effects, both to reduce unwanted bias, as well as tune the 
-focus, diversity, and specificity of worker responses.
-
-Here we have shown that a severe bias can be introduced into microtask 
+We anticipate future work will yield techniques to control intertask 
+effects, to reduce unwanted bias, and to tune the focus, diversity, and 
+specificity of worker responses.
+
+We have shown that a severe bias can be introduced into microtask 
 responses, simply from the performance of earlier tasks. 
-These effects are much stronger than the effects of framing.  
+These effects are much stronger than those of framing.  
 While our findings raise serious concerns about the 
 current state of microtask design, they reveal potential opportunities 
-for more 
-refined control over worker focus and acuity.  Any application that relies
+to refine worker focus and acuity.  Any application that relies
 on the repetitive use of human judgment is likely subject to the phenomena
-we described here.  Exploring the pitfalls and opportunities posed by
+described here.  Exploring the pitfalls and opportunities posed by
 intertask effects is an important direction for future work, 
-in the effort to develop performant and reliable methods for human 
-computation.
+in the effort to develop performant and reliable human computation.
 \bibliography{newbib}
@@
 other, once we have conditioned on the class under observation 
-\cite{bishop2006} (i.e. the priming treatment).  This
+%\cite{bishop2006} 
+(i.e. the priming treatment).  This
 conditional independence assumption is made for
@@
 na\"ive Bayes classifier and our particular choice of preprocessing steps, 
-as shown in in Fig.~\ref{fig:theta} of the main text, are representative.
+as shown in Fig.~\ref{fig:theta} of the main text, are representative.
 
@@
 To determine the confidence intervals for measured $\theta$ values we 
-use the exact Clopper-Pearson method \cite{clopper1934use}.  
+use the exact Clopper-Pearson method. % \cite{clopper1934use}.  
 Based on the observed number of successes, $X$, we calculate 
@@
 	Next, words were lemmatized using the
-	wordnet lemmatizer \cite{miller1995wordnet,felbaum1998wordnet}.  
+	wordnet lemmatizer \cite{felbaum1998wordnet}.  %miller1995wordnet,
 	Common words such as ``the'', ``to'', or ``with'', were found using
-	NLTK's English stop word list \cite{loper2002nltk} and removed.
+	the natural language toolkit (NLTK) English stop word list 
+	\cite{loper2002nltk} and removed.
 

### 2015-02-15 docs/publications/2014.09_SCIENCE/man.tex
shortened, and proofed

@@
 \begin{sciabstract}
-Microtask platforms have become commonplace tools for obtaining human 
-annotations for large datasets.  Such platforms connect requesters 
+Microtask platforms are becoming commonplace tools for performing human
+research, producing gold-standard data, and annotating large datasets.
+These platforms connect \textit{requesters}
 (researchers or companies) with large populations (crowds) of workers, who 
-will individually complete small information-processing jobs, each taking 
-typically between one to five minutes.  
-A major challenge in using such platforms, 
-and a topic of ongoing research, concerns designing jobs that elicit high 
+perform clerical jobs, typically taking less than five minutes each.
+Recently, they have been studied as a way for untrained workers to perform 
+clinical diagnostic functions, where expert human resources are
+a bottleneck \cite{Warby2014385}.
+A topic of ongoing research concerns designing jobs that elicit high 
 quality annotations. Here we identify a feature of nearly all crowdsourcing 
-jobs that can act as a strong and systemic source of bias in annotations 
-produced by workers. Specifically, many microtask jobs consist of a sequence 
-of tasks which share a common format (e.g., label pictures, identify people, 
-circle galaxies). Using image-labeling, a canonical microtask job format, we 
-discover that earlier tasks shift the distribution of future answers by 
-30-50\%. 
-Moreover, we show that prior tasks influence 
-the content that workers chose to focus on, as well as the richness and 
-specialization of their word choice. While these \textit{intertask effects} 
-can be a 
-source of systematic bias, our results suggest that, with appropriate job 
-design, it might be possible to leverage these biases to hone worker focus 
-and specificity, helping to elicit reproducible, expert-level judgments.
+jobs that acts as a strong systemic source of bias. 
+Microtask jobs typically consist of a sequence 
+of tasks sharing common format 
+(e.g., circle galaxies in an image). 
+Using image-labeling, a canonical microtask job format, we 
+discover that a priming effect, induced by earlier tasks, shifts the 
+distribution of future answers by 30-50\%. 
+Moreover, prior tasks influence the content that workers focus on, 
+as well as the richness and specialization of responses. 
+Understanding these \textit{intertask effects} is crucial 
+to embracing micratask platforms in critical applications.
+While intertask effects can be a source of systematic bias, 
+our results suggest that, with appropriate job design, 
+it might be possible to leverage them to 
+hone worker focus and acuity, helping to elicit reproducible, 
+expert-level judgments.
 \end{sciabstract}
@@
 %\cite{6116320,Zhai2012357}, 
-coding and transcription, such as of voice recordings or handwritten notes,
+coding and transcribing media,
 %\cite{chandler2013breaking,Berinsky2012351,Finnerty2013},%paolacci2010running}, 
-and judging relevancy and quality, for example, to rate information 
-retrieval systems\footnote{We provide a survey of task types in the supplementary text.}.
+judging the relevancy or quality of content, 
+and performing surveys for academic or market reserach purposes\footnote{We provide a survey of task types in the supplementary text.}.
 %\cite{le2010ensuring,grady2010crowdsourcing,alonso2009can,kazai2013analysis}.
 
-In this form of crowdsourcing, workers appear like input-output devices.  
-Such platforms provide much of the flexibility and 
+This form of crowdsourcing embeds workers in a controlled but flexible
+task infrastructure.  To the requester, workers seem almost like input-output 
+devices.  
+This provides much of the flexibility and 
 cost-savings of fully automating the work in a computer program: 
 the workforce is available on demand over the Internet using automated 
-scripts, and  no interviews or contracts are required 
-\cite{wolfson2011look,5543192}.  Many tasks
-can be performed at a fraction of the cost of traditional methods for 
+scripts, without the need for interviews or contracts 
+\cite{wolfson2011look,5543192}.
+Jobs can be performed at a fraction of the cost of traditional methods for 
 recruiting temporary workers or experimental subjects
 \cite{Berinsky2012351}. %,ranade2012crowdsource}%,paolacci2010running}.
-From the requester's perspective, microtask platforms resemble
-a remote compute server, and some seriously consider microtask platforms 
-as a new kind of computing architecture
+Many researchers consider microtask platforms 
+as a new kind of \textit{human computing} architecture
 \cite{5543192}. %,little2010turkit,minder2012crowdlang,kittur2011crowdforge}.
@@
 has led to a surge in demand from industry and 
-academia\cite{wolfson2011look,Berinsky2012351},
-leading researchers to investigate the factors affecting its reliability.  
-Among these factors are
+academia\cite{wolfson2011look,Berinsky2012351}.  More recently microtask 
+platforms have
+been assessed as a way to supplement expert human resources to increase
+capacity in critical applications, such as in medical diagnostic functions,
+with promising results \cite{Warby2014385}.
+Naturally, researchers have investigated the factors affecting the reliability
+of microtask work, including
 the level of pay \cite{Mason200977,kazai2013analysis}, 
@@
 tasks are delivered in bundles called HITs.
-Although HIT stands for ``Human Intelligence Task'', we use ``task'' to mean
-the smallest repeatable unit of work.  For example, one HIT may involve 
-labeling ten images with descriptive words (\textit{labels}), while for
-the present discussion, we consider labeling a single image to be a task.
+Although HIT stands for ``Human Intelligence Task'', here we use ``task'' to 
+mean the smallest repeatable unit of work.  For example, one HIT may involve 
+labeling ten images with descriptive words (\textit{labels}), which amounts
+to ten tasks, each being the labeling of a single image.
 In addition to the task-repetition occuring \textit{within} HITs, 
@@
 many more HITs of the same format, but with different data) 
-\cite{Chilton20101}.
+\cite{Chilton20101}, probably because performing similar tasks reduces 
+cognitive load from task-switching\cite{Adamczyk2004271}.
+%Furthermore, on average, workers report spending over 4 hours per day on 
+%microtasks, taking breaks only every 1.24 hours, while some take no breaks 
+%at all
+%\cite{laseckieffects}.
 
@@
 
-The repetitive completion of tasks is of concern because people's responses
-to a prompt can be strongly influenced by their recent exposure to stimuli,
-due to \textit{priming} 
+The repetitive completion of similar tasks is of concern because people's 
+responses to a prompt can be strongly influenced by their recent exposure to 
+stimuli, due to \textit{priming} 
 \cite{BJOP1796}. %,No2007}. %,beller1971priming}.  
@@
 similar tasks may create an opportunity for strong priming effects
-\cite{Gass1999549} %,sohn2001task}
-.
+\cite{Gass1999549}. %,sohn2001task}
 
@@
 it should be expected in virtually every microtask and crowdsourced workflow
-where workers are called upon to exercise their judgment.
+where workers are called upon to exercise their judgment\footnote{
+	As opposed to those tasks where a single clear correct answer exists.
+}.
 Our results show that a worker's response during a task
@@
 microtask platforms are to be considered as a new form of computing 
-architecture, it will be necessary to consider that the computing elements 
+architecture, it will be necessary reconcile the fact that the human computing 
+elements 
 exhibit \textit{hysteresis}, meaning that microtask workers' outputs depend 
@@
 This includes such diverse tasks as describing video and audio recordings, 
-summarizing texts, or providing feedback to a product review.
+summarizing texts, or in clinical diagnostic judgments.
 
@@
 	see supplementary text for tabulated statistics.
-}.  Thus earlier tasks significant affect later ones, raising concerns 
-about the the microtask methodology itself.
+}.  Thus earlier tasks do significantly affect later ones, raising concerns 
+about the the microtask methodology.
 
@@
 provides response $x$, from the set of possible responses $X$.
-A significant result from a $\chi^2$ test only allows us to conclude that 
-$\theta$ is non-zero (see supplementary text).  
+%A significant result from a $\chi^2$ test only allows us to conclude that 
+%$\theta$ is non-zero (see supplementary text).  
 Determining $\theta$ from finite samples of responses, using purely 
@@
 \end{equation}
-By measuring the accuracy of a classifier, we can bound the 
-bias induced by any perturbation, including both intertask effects and 
-framing.  Bias ranges from 0 (meaning the exposures 
+
+By measuring the accuracy of a classifier, we bound the 
+bias induced by a perturbation, such as the exposure to prior tasks or 
+framing.
+Bias ranges from 0 (meaning the exposure 
 does not affect the distribution of responses), to 1 
@@
 	machine is used instead. 
-	We also discuss data preprocessing and show results for alternatives.
+	We also discuss data preprocessing and show results for alternative 
+	preprocessing.
 }, we found that intertask effects 
@@
 but remained significant through all five test tasks 
-($\alpha=0.05$) sustaining over 12\% bias (Fig. \ref{fig:theta}B).
+($\alpha=0.05$) sustaining over 12\% bias even when the initial and test 
+tasks were separated by four intervening tasks (Fig. \ref{fig:theta}B).
 
@@
 35\% (Fig.~\ref{fig:theta}A). However, it is difficult to say whether this 
-should be considered as a framing treatment \textit{per se}.
-Requiring the worker to reiterate the purpose signals our intent, as the 
+should be considered as a framing treatment \textit{per se}:
+requiring the worker to reiterate the purpose signals our intent, as the 
 requester, to ensure that the worker has taken note of it, possibly leading 
@@
 In any case, it is remarkable that intertask effects
-were on par with an explicit, actively reinforced statement of purpose.
+were on par with an explicit, actively reinforced statement of the tasks' 
+purpose.
 
@@
 		Empirical bias, $\theta_\mathrm{NB}$, measured using a na\"ive Bayes 
-		classifier, induced in image labeling tasks,
-		(\textbf{A}) by exposing workers to initial tasks or framing. 
-		As workers proceed through test tasks, the effects of initial tasks 
-		wane, as shown (\textbf{B}) for \textit{intertask-food-objects}, but 
-		remain significant even after five tasks.  Standard error bars are 
-		shown.
+		classifier, induced in image labeling tasks, due to workers' 
+		exposure to framing and initial tasks.  
+		(\textbf{A}) Exposing workers to initial tasks induces more severe
+		bias than framing, except when echoed framing is used. 
+		(\textbf{B}) As workers proceed through test tasks, 
+		the bias due to initial tasks wanes, 
+		but remains significant even after five tasks.  
+		Standard error bars are shown.
 	}
@@
 	\centering
-	\includegraphics[scale=0.92]{figs/vocab_specificity.pdf}
+	\includegraphics[scale=0.87]{figs/vocab_specificity.pdf}
 	\caption{
-		(\textbf{A}) Exposing workers to initial tasks or framing, 
-		involving food, changed the subsequent fraction of words that 
-		referred to food during test tasks, 
-		but did not always increase that fraction (in all three plots,
-		positive values indicate a larger quantity for food-exposed workers).
+		Exposing workers to a priming concept, e.g. food, through
+		initial tasks or framing, affects their tendency to focus
+		on that concept, and the richness and specialization of their 
+		vocaubulary in reference to it.
+		In all three plots, positive values indicate a larger quantity for 
+		the food-exposed workers.
+		(\textbf{A}) Exposing workers to food does not necessarily increase
+		the fraction food references they provide during test tasks.
 		(\textbf{B}) The number of unique food-related
@@
 		case of \textit{frame-food-culture} (stars indicate the threshold
-		for a significant deviation under the null hypothesis of equal 
-		richness, $\alpha=0.05$). 
+		for a significant deviation, $\alpha=0.05$). 
 		(\textbf{C}) Food-exposed
@@
 that workers used to label test tasks. One might expect that, within a given 
-experiment, the food-primed workers would label test tasks using 
+experiment, those workers exposed to food (whether through framing or initial
+tasks) would label test tasks using 
 food-related words more often.  However, this was not generally 
-the case. In the \textit{intertask-food-culture} experiment, food-primed
+the case. In \textit{intertask-food-culture}, food-exposed
 workers actually used significantly \textit{fewer} food-related words 
@@
 This is particularly noteworthy in the experiment
-\textit{intertask-food-culture}, because there
+\textit{intertask-food-culture}, because there,
 food-primed workers made fewer total references to food.  
@@
 In all experiments except \textit{frame-food-culture}, food-primed workers 
-were used significantly more specialized words, in reference to food 
+used significantly more specialized words, in reference to food 
 (about 15\% more) (Fig.~\ref{fig:specificity}C).
@@
 The work presented in the main text consisted of six experiments involving
-HITs (bundles of tasks) performed on Amazon's Mechanical Turk platform.  
+HITs (bundles of tasks) performed on Amazon's Mechanical Turk (MTurk)
+platform.  
 The flow of events experienced by a worker when participating in this study 
@@
 		(see Table~S\ref{table:experiments}).  Steps outlined in orange are
-		part of Amazon's Mechanical Turk interface, and are common to any 
+		part of MTurk's interface, and are common to any 
 		microtask performed on that platform.  Steps outlined in black are
@@
 would be necessary to be sure, but this was not the purpose of our study.
+
+\subsection*{MTurk's task composition}
+
+\begin{table}
+\centering
+\begin{tabular}{l c c}
+\toprule
+Task Type & Number Seen & Fraction of total (\%) \\
+\toprule
+Image transcription & 57 & 28.5 \\
+Information gathering & 46 & 23.0 \\
+Image tagging and classification & 36 & 18.0 \\
+Copy writing and editing & 18 & 9.0 \\
+Text tagging and classification & 15 & 7.5 \\
+Audio/Video transcription & 12 & 6.0 \\
+Survey & 9 & 4.5 \\
+Unknown & 7 & 3.5 \\
+\bottomrule
+\end{tabular}
+\caption{
+	Frequency of various broad task types seen among the 200 most 
+	recently posted tasks on MTurk, accessed on 12 February, 2015.
+}
+\label{table:task_composition}
+\end{table}
+Image labeling tasks are one of the most often cited kinds of tasks in the
+literature.  To determine whether they do indeed reflect an important fraction
+of MTurk tasks, we accessed MTurk on 12 February, 2015, and coded the 200 
+most recently posted tasks based on their title and description, 
+into one of seven categories.
+
+Tasks relating to image tagging and categorization represented 18\% of the 
+total.  Of all tasks seen, those in which images are the primary input
+account for 46.5\%.  Considering tasks regardless of input modality (e.g.
+text, image, audio, or multimedia), those that involved some kind of tagging
+or categorization accounted for 25.5\%.  
+The detailed counts for our categorization
+of task types are shown in Table~S\ref{table:task_composition}.  
+While this does not reflect a full and
+a systematic characterization of MTurk task composition, it does support our
+choice of image labeling as a representative microtask.
 

### 2015-02-18 docs/publications/2014.09_SCIENCE/man.tex
small edits, fix bib

@@
 (researchers or companies) with large populations (crowds) of workers, who 
-perform clerical jobs, typically taking less than five minutes each.
-Recently, they have been studied as a way for untrained workers to perform 
-clinical diagnostic functions, where expert human resources are
-a bottleneck \cite{Warby2014385}.
+perform small jobs, typically taking less than five minutes each.
 A topic of ongoing research concerns designing jobs that elicit high 
@@
 Using image-labeling, a canonical microtask job format, we 
-discover that a priming effect, induced by earlier tasks, shifts the 
+discover that earlier tasks have a priming effect on the worker, shifting the 
 distribution of future answers by 30-50\%. 
@@
 our results suggest that, with appropriate job design, 
-it might be possible to leverage them to 
-hone worker focus and acuity, helping to elicit reproducible, 
-expert-level judgments.
+they might be leveraged to hone worker focus and acuity, 
+helping to elicit reproducible, expert-level judgments.
 \end{sciabstract}
@@
 microtask platforms are to be considered as a new form of computing 
-architecture, it will be necessary reconcile the fact that the human computing 
-elements 
+architecture, it will be necessary to reconcile the fact that the human 
+computing elements 
 exhibit \textit{hysteresis}, meaning that microtask workers' outputs depend 
@@
 tasks, workers performed five \textit{test tasks}, which were identical for 
-both treatments.  In the the test tasks, workers labeled images depicting a 
-mixture of food and objects (Fig.~\ref{fig:task}C).  The five initial 
+both treatments.  In the the test tasks, workers labeled images, each of 
+which depicted a mixture of food and objects (Fig.~\ref{fig:task}C).  
+The five initial 
 and test tasks performed by each worker comprised one HIT\footnote{
@@
 Having affirmed the \textit{existence} of intertask effects, we wish to
-understand the nature and severity of the bias thus induced.
+understand the nature and severity of the bias induced.
 We therefore define the extent of bias, $\theta$, in terms of
@@
 	\centering
-	\includegraphics[scale=0.6]{figs/images.pdf}
+	\includegraphics[scale=1.0]{figs/images.jpg}
 	\caption{
@@
 distinguishable from zero ($p =0.37$) (Fig.~\ref{fig:theta}A), and was
-weaker than the bias due to intertask effects ($p=2.1\times 10^{-5}$).
+much weaker than the bias due to intertask effects ($p=2.1\times 10^{-5}$).
+\begin{figure}
+	\centering
+	\includegraphics[scale=1]{figs/theta.pdf}
+	\caption{
+		Empirical bias, $\theta_\mathrm{NB}$, measured using a na\"ive Bayes 
+		classifier, induced in image labeling tasks, due to workers' 
+		exposure to framing and initial tasks.  
+		(\textbf{A}) Exposing workers to initial tasks induces more severe
+		bias than framing, except when echoed framing is used. 
+		(\textbf{B}) As workers proceed through test tasks, 
+		the bias due to initial tasks wanes, 
+		but remains significant even after five tasks.  
+		Standard error bars are shown.
+	}
+	\label{fig:theta}
+\end{figure}
 
@@
 purpose.
-
-\begin{figure}
-	\centering
-	\includegraphics[scale=1]{figs/theta.pdf}
-	\caption{
-		Empirical bias, $\theta_\mathrm{NB}$, measured using a na\"ive Bayes 
-		classifier, induced in image labeling tasks, due to workers' 
-		exposure to framing and initial tasks.  
-		(\textbf{A}) Exposing workers to initial tasks induces more severe
-		bias than framing, except when echoed framing is used. 
-		(\textbf{B}) As workers proceed through test tasks, 
-		the bias due to initial tasks wanes, 
-		but remains significant even after five tasks.  
-		Standard error bars are shown.
-	}
-	\label{fig:theta}
-\end{figure}
 
@@
 \begin{figure}
-	\includegraphics[scale=0.8]{figs/tasks.pdf}
+	\includegraphics[scale=0.8]{figs/tasks.jpg}
 	\caption{Examples of (A) task instructions, (B) a framing slide
@@
 	\begin{center}
-	\includegraphics{figs/task1-food.pdf}
+	\includegraphics{figs/task1-food.jpg}
 	\end{center}
@@
 	\begin{center}
-	\includegraphics{figs/task1-obj.pdf}
+	\includegraphics{figs/task1-obj.jpg}
 	\end{center}
@@
 	\begin{center}
-	\includegraphics{figs/task1-test.pdf}
+	\includegraphics{figs/task1-test.jpg}
 	\end{center}
@@
 	\begin{center}
-	\includegraphics{figs/task2-food.pdf}
+	\includegraphics{figs/task2-food.jpg}
 	\end{center}
@@
 	\begin{center}
-	\includegraphics{figs/task2-cult.pdf}
+	\includegraphics{figs/task2-cult.jpg}
 	\end{center}
@@
 	\begin{center}
-	\includegraphics{figs/task2-test.pdf}
+	\includegraphics{figs/task2-test.jpg}
 	\end{center}
@@
 	\begin{center}
-		\includegraphics{figs/task2-ingr.pdf}
+		\includegraphics{figs/task2-ingr.jpg}
 	\end{center}

### 2015-03-23 docs/publications/2014.09_SCIENCE/delete/ban.tex
added all missing files

--- 2014-11-19 docs/publications/2014.09_SCIENCE/new_man.tex
@@
 Exposure to both framing and initial tasks significantly altered the 
-diversity of vocabulary that workers used when refering to the prime concept,
+diversity of vocabulary that workers used when referring to the prime concept,
 as well as the degree to which workers used specialized (rather than generic) 
@@
 (hereafter collectively \textit{exposure effects}).  
-In trying to establish a mesure of exposure effects, it might be tempting to 
+In trying to establish a measure of exposure effects, it might be tempting to 
 invoke the notion of a ``neutral frame of mind'' to serve as a baseline. 
@@
 
-Our goal in measuring exposure effects is to show that they can actually 
+Our goal in measuring exposure effects is determine whether they can actually 
 alter the course of algorithms.
@@
 measure intertask effects as a function of task position, while factoring
-out the content-dependant differences between tasks
+out the content-dependent differences between tasks
 (see Fig.~\ref{fig:theta}B). 
@@
 significant effect through until the fifth test task.  
-This shows that the range of intertask effects extends accross at least five 
+This shows that the range of intertask effects extends across at least five 
 tasks, and probably substantially more.
@@
 In future work, it would be interesting to investigate whether a worker's
-susceptibility to intertask effects varies accross a large batch.  For example,
+susceptibility to intertask effects varies across a large batch.  For example,
 It is conceivable that the first few tasks induce especially strong
@@
 it should perhaps not be surprising that the effect of initial task exposure 
-is different.  It would appear that we must be prepared to accomodate multiple 
+is different.  It would appear that we must be prepared to accommodate 
+multiple 
 countervailing factors influencing the number of references to the prime 
@@
 vocabulary is crucial to the reliability of results.  The interface of
-galaxy zoo helps by contstraining and prompting the user with this basic 
+galaxy zoo helps by constraining and prompting the user with this basic 
 vocabulary.  But this would not appear to be sufficient, since
@@
 
-\subsection*{Assessing task similarity}
+\subsection*{S1: Experimental materials}
+The tasks for both experiments were presented as a series of slides.  In
+both cases, the first slide consisted of a brief set of instructions, followed
+by the frame if shown (only some treatments involved a frame), see 
+Fig. S\ref{fig:hit_preamble}.  Following the instructions and prime, a set
+of initial tasks was shown (except for the treatments in \textit{frame2}
+and \textit{echo}) followed by (in all cases) a set of test tasks.  In
+\textit{exp1}, two kinds of frame were used, one simple frame, and one where
+the worker was required to echo the frame using a combo-box input.  The
+instructions, both kinds of frame, and an example task slide, are shown 
+in Fig. S1.
+\begin{figure}
+	\includegraphics[scale=0.8]{figs/tasks.pdf}
+	\label{fig:hit_preamble}
+	\caption{Examples of A) instructions; B) a frame, as shown in 
+		\textit{frame1:obj}, and similar to those shown in 
+		\textit{frame1:food} and \textit{frame2:food}, and 
+		\textit{frame2:cult};  
+		C) an echoed frame, as used in \textit{echo:obj}, and similar to that
+		used in \textit{echo:food}; and D) an 
+		example of an image labeling task.
+	}
+\end{figure}
+
+All of the initial tasks had the format shown in Fig. S1D.  The images used
+in the initial tasks for \textit{task1:food} and \textit{task1:obj} are
+shown in Fig. S2 and S3, and the images used in the test tasks for 
+\textit{exp1} are shown in Fig. S4.  The images used in the initial tasks
+for \textit{task2:food} and \textit{task2:cult} are shown in Fig. S5 and
+Fig. S6 respectively, and the images used in the test tasks for \textit{exp2} 
+are shown in Fig. S7.
+
+\begin{figure}
+	\includegraphics{figs/task1-food.pdf}
+	\label{fig:task1:food}
+	\caption{
+		Figure S2: Images used in the initial tasks for 
+		\textit{task1:food}.  The numbers show the order in which the 
+		images were presented to workers.
+	}
+\end{figure}
+
+\begin{figure}
+	\includegraphics{figs/task1-obj.pdf}
+	\label{fig:task1:obj}
+	\caption{
+		Figure S3: Images used in the initial tasks for 
+		\textit{task1:obj}.  The numbers show the order in which the 
+		images were presented to workers.
+	}
+\end{figure}
+
+\begin{figure}
+	\includegraphics{figs/task1-test.pdf}
+	\label{fig:task1:test}
+	\caption{
+		Figure S2: Images used in the test tasks for 
+		\textit{exp1}.  The numbers show the order in which the 
+		images were presented to workers.
+	}
+\end{figure}
+
+\begin{figure}
+	\includegraphics{figs/task2-food.pdf}
+	\label{fig:task2:food}
+	\caption{
+		Figure S2: Images used in the initial tasks for 
+		\textit{task2:food}.  The numbers show the order in which the 
+		images were presented to workers.
+	}
+\end{figure}
+
+\begin{figure}
+	\includegraphics{figs/task2-cult.pdf}
+	\label{fig:task2:cult}
+	\caption{
+		Figure S2: Images used in the initial tasks for 
+		\textit{task2:cult}.  The numbers show the order in which the 
+		images were presented to workers.
+	}
+\end{figure}
+
+\begin{figure}
+	\includegraphics{figs/task2-test.pdf}
+	\label{fig:task2:test}
+	\caption{
+		Figure S2: Images used in the test tasks for 
+		\textit{exp2}.  The numbers show the order in which the 
+		images were presented to workers.
+	}
+\end{figure}
+
+\subsection*{S2: Access to raw data and code}
+The raw data and source code needed to reproduce the analyses 
+shown here and in the main text can be downloaded from 
+http://networkdynamics.org/publications/public/priming2014.09.
+
+\subsection*{S3: Additional results not shown in the main text}
+		the top 5 most suppressed and most activated terms between treatment
+		pairs.
+
 \begin{table}
 	\centering
-\begin{tabular}{ l  s s s s}
+	\setlength{\tabcolsep}{10pt}
+	\begin{tabular}{ c c c c c }
 
+		\setlength{\tabcolsep}{4pt}
+		\begin{tabular}{ r | c }
 		\toprule
-Image set   
-& \multicolumn{1}{c}{Ambig.} 
-& \multicolumn{1}{c}{Cultural} 
-& \multicolumn{1}{c}{Ingr.}
-& \multicolumn{1}{c}{Test} \\
+		\multicolumn{2}{c}{\textit{task1}} \\
+		\toprule
+		coffee & 38 \\
+		meal & 34 \\
+		cheese & 34 \\
+		apple & 32 \\
+		dessert & 21 \\
+		cup & -30 \\
+		glass & -45 \\
+		table & -70 \\
+		candle & -74 \\
+		food & -80 \\
+		\bottomrule
+		\end{tabular}
 
-\midrule
+&
 
-Ambiguous  & 1 & 0.0418 & 0.142 & 0.167 \\
+		\setlength{\tabcolsep}{4pt}
+		\begin{tabular}{ r | c }
+		\toprule
+		\multicolumn{2}{c}{\textit{frame1}} \\
+		\toprule
+		bread & 18 \\
+		wine & 18 \\
+		cheese & 16 \\
+		apple & 14 \\
+		oil & 12 \\
+		table & -9 \\
+		meal & -10 \\
+		candle & -12 \\
+		dinner & -13 \\
+		food & -32 \\
+		\bottomrule
+		\end{tabular}
 
-Cultural  & 0.0418  & 1 & 0.0347 & 0.0561 \\
+&
 
-Ingredients  & 0.142  & 0.0347 & 1 & 0.110 \\
+		\setlength{\tabcolsep}{4pt}
+		\begin{tabular}{ r | c }
+		\toprule
+		\multicolumn{2}{c}{\textit{echo}} \\
+		\toprule
+		apple & 24 \\
+		cheese & 23 \\
+		wine & 15 \\
+		coffee & 14 \\
+		oil & 7 \\
+		knife & -24 \\
+		dinner & -26 \\
+		fork & -27 \\
+		candle & -35 \\
+		food & -55 \\
+		\bottomrule
+		\end{tabular}
 
-Test & 0.167  & 0.0561 & 0.110 & 1
-\\
+&
+
+		\setlength{\tabcolsep}{4pt}
+		\begin{tabular}{ r | c }
+		\toprule
+		\multicolumn{2}{c}{\textit{task2}} \\
+		\toprule
+		spicy & 26 \\
+		sauce & 17 \\
+		indian & 15 \\
+		buffet & 14 \\
+		exotic & 12 \\
+		festival & -11 \\
+		offering & -12 \\
+		statue & -15 \\
+		india & -20 \\
+		food & -56 \\
 		\bottomrule
+		\end{tabular}
+
+&
+
+		\setlength{\tabcolsep}{4pt}
+		\begin{tabular}{ r | c }
+		\toprule
+		\multicolumn{2}{c}{\textit{frame2}} \\
+		\toprule
+		indian & 11 \\
+		banquet & 8 \\
+		spicy & 7 \\
+		asian & 6 \\
+		variety & 6 \\
+		delicious & -6 \\
+		meat & -7 \\
+		festival & -7 \\
+		spice & -7 \\
+		food & -9 \\
+		\bottomrule
+		\end{tabular}
 
 	\end{tabular}
-\caption{\footnotesize{
-Pairwise similarities of each image set based on the labels attributed to them (see \textbf{Eq. 4}).
-}}
-\label{table:2}
+	\caption{blah}
 \end{table}
 
-One weakness of the above analysis is the reliance on the informal notion
-of the similarity of one set of images to another. The 
-characterization of image content is a deeply complex issue that has been 
-approached by many disciplines \cite{panofsky1939studies,shatford1986analyzing,Tversky1977327,Jaimes20002}. \textit{Perceptual similarity} is a 
-particularly recalcitrant concept.   But to formalize our claim, we seek a 
-measure of similarity between two sets of images, 
-\textit{with respect to the labeling task}.  This can be operationalized
-in a straightforward way, by using the similarity of the labels given to images
-as a proxy for the similarity of the images.  Thus, to measure the 
-similarity between two sets of images, X and Y , we computed the Jacquard 
-index between the sets of labels attributed to them:
-$$
-	\mathrm{Sim}(X,Y) = \frac{L(X) \cap L(Y)}{L(X) \cup L(Y)}
-$$
-where $L(X)$ denotes the set of labels attributed to images in $X$.
+\subsection*{S4: Data preprocessing}
+	\paragraph{Splitting, Lemmatization, removal of stop-words, and 
+		addition of position tags.}
 
-The pairwise similarities of the image sets are presented in Table 2. This 
-shows that the workers that yielded higher specificity labels were from 
-treatments whose initial tasks were more similar to the test tasks (c.f.
-\textbf{Fig 3}).
+	Before performing any analysis on the labels that workers provided, we
+	performed a series of preprocessing steps.  
+	\td{does this reflect the actual order in which the steps were done?}
+	First, words wore lematized 
+	using the
+	\td{whatzit} lemmatizer.  This lemmatizer is very mild, tending only to 
+	change plural words to their singular form.  Common
+	words such as ``the'', ``to'', or ``with'', were found using the
+	the \td{whatzit} stop-word list and removed.  Then, misspelled words were
+	automatically corrected using a spelling correction algorithm described 
+	below.  Finally, labels that contained
+	multiple words (separated by spaces or punctuation) were split, with
+	punctuation removed, and the separated words were treated as distinct 
+	features in subsequent analysis.
 
-Such a phenomenon would be consistent with the psychological mechanism known as
-\textit{negative priming}.
+	For the purpose of training and testing a naive Bayes classifier, we 
+	performed an additional preprocessing step.  We tagged words with the
+	position in which they had been entered (i.e. which of the five text 
+	inputs in the task interface) as well as the test tasks in which the word 
+	had been provided.
+	So, if the word ``wine'' was entered into the second text-input for 
+	the third test-task, after preprocessing, the feature ``3\_2\_wine'' would
+	appear.  Prepending the task number onto words was simply a means to 
+	retain correct attribution, which itself was essential since providing a
+	word during one task is not equivalent to providing the same word during 
+	another task.
+
+	\paragraph{Spelling correction.}  
+	Spelling correction was performed using an algorithm that first detected
+	if a word was likely to be misspelled, then generated a set of candidate 
+	corrections, and chose the best candidate based on a scoring mechanism.
+
+	A word was considered misspelled if it was not contained in the 
+	\textit{legal set}, which was formed by the union of
+	the wordnet corpus, the stop-word list, and a set of words seen while 
+	crawling the world food section of the allrecipes.com website.  We
+	describe the crawling of the allrecipes.com website in a section below.
+
+	To correct misspellings, we first produced all possible modified forms 
+	that could be obtained applying one or two edits.  An edit consisted of 
+	adding or removing a letter, changing one letter into another, or 
+	swapping the positions of two adjacent letters.  For the purpose of these 
+	edits, spaces were treated as any other letter.
+
+	The candidates produced by these edits which were in the legal set were
+	then ranked based on a scoring mechanism, and the highest scoring word
+	was chosen as the correction.  A candidate $w$'s score, $s_w$, was 
+	calculated according to the following formula:
+	\begin{equation}
+		s_w = (f_w + 1) * p_1 * p_2,
+	\end{equation}
+	where $f_w$ is the frequency with wich the word occured (correctly 
+	spelled)
+	within the given task, $p_1$ was a penalty for the first edit, and
+	$p_2$ was a penalty for the second edit.  If the word was made using only
+	one edit, then $p_2 = 1$.  Any edit that did not involve adding a space
+	(i.e. separating a word) incured a penalty of 0.5, while the addition of
+	a space incurred a penalty of 0.1.  Word-separation edits were more 
+	strongly penalized because it is often possible to split a series of 
+	letters into many short two- or three-letter words, which otherwise leads 
+	to many erroneous corrections.  We found that setting the penalty for
+	word splitting at 0.1 worked well by testing on words taken from
+	initial tasks.
+
+	After all of our analyses had been performed, we checked the accuracy of 
+	the spelling correction algorithm using three human coders.  The coders
+	were shown a set of 
+	500 words that were randomly sampled from the labels attirubuted during 
+	test tasks (50 for each test task).  Before sampling, the labels from all
+	experimental treatments, for the given test task, were pooled together.
+	The coders did not know which treatment any given word came from.  
+	In addition to the words, coders were shown the spelling correction 
+	produced by the algorithm, as well as the image from the test task.
+	The coders were asked to identify any misspelled words which had not 
+	been corrected, as well as any corrections that appeared to be erroneous,
+	by indicating their own correction.
+
+	Based on this exercise, we found that, according to the human coders,
+	17\% of the words were misspelled, but that after applying the 
+	automated spelling correction, only 3.2\% of words were misspelled.
+
+	\paragraph{Crawling the world food section of allrecipes.com.}
+	The website allrecipes.com was accessed on 3-4 November 2014 using 
+	automated scripts.  A total of 2642 recipe listings and 15621 recipe
+	instruction pages were crawled.  Recipe listings were pages that provided 
+	lists of recipes, and contained a title and short description for each.  
+	The recipe instruction pages had lists of ingredients and preparation 
+	instructions.  All of the words found in recipe titles, short
+	descriptions, ingredients lists, and preparation instructions were
+	collected, and saved as an auxiliary set to aument the \textit{legal set}
+	used in spelling correction.
+
+\subsection*{S5: Identification of food-related terms}
+The wordnet corpus is composed of synsets, which are particular senses 
+(meanings) and a set of word forms bearing that meaning. A given word form, 
+such as ``ring'' has multiple senses (``to ring a bell'', ``a wedding ring''), 
+and so can be part of many synsets.  Since the wordnet corpus was designed
+to carry semantic information, the synset is the basic organizing element
+of wordnet.
+
+We chose the synsets \textit{food.n.01} and \textit{food.n.02} to act as roots
+in defining which words should be considered food-related.  Any word form
+belonging to a synset which was a hyponym of one of the two root synsets
+identified above was considered to be a reference to food.  Here, as in the
+main text, when we say hyponym, we mean either a direct hyponym, or a hyponym
+of a hyponym, and so on.
+
+This is a stringent notion of a word being a food reference.  It roughly
+corresponds to whether or not a given thing is reasonably considered 
+consumable.  So, ``orange'' is food, but ``salty'' is not.  Although ``salty''
+would usually refer to something edible, it is not itself an edible thing.
+On the other hand, ``salt'' would be considered a reference to food under 
+this operationalization.
+
+The subset of the wordnet corpus induced by the hyponyms of \textit{food.n.01}
+and \textit{food.n.02} provide an extensive set of \td{X} words.  Manual
+testing appeared to show that the coverage was very extensive, except in 
+some cases references to ethnic foods were missing.  Since, especially in
+\textit{exp2} we had images containing many ethnic foods, we decided to 
+augment the wordnet corpus with words learned by crawling the world food
+section of the allrecipes.com website.
+
+After collecting a set of words using an automated script 
+(\td{described above}), we collected the set of words that had been used by
+workers and which had been seen during crawling of the allrecipes.com website,
+but which were not included in wordnet.  We graphted these extra words into
+the wordnet hyponym-hypernym graph manually, which ensured that any references
+to ethnic words learned from crawling would be properly classified as 
+food references.
+
+\paragraph{Validation of the detection of food references.}
+To determine whether our extended version of wordnet provided a good approach
+to detecting food-related words, we sampled 500 words from the set of labels
+produced by workers and had three human coders manually decide if they were 
+food-related or not.  The method for randomly sampling the 500 words was 
+described in above in \td{section number}.
+
+The coders were instructed to consider whether a word was a noun signifying
+an edible item.  The guiding principle was, for the coder to ask herself,
+``can I eat this X'', where X is the word she is coding.  The coders were
+shown the used in the task from which the word came, to help resolve ambiguity
+in the sense of the word that had been given.  Coders were also shown the 
+spelling correction (if any) that the spell-correction algorithm had made,
+to help interpret mispelled words \td{we describe the spelling correction 
+algorithm in section X}.
+
+We evaluated the food detection algorithm in two ways.  First, we measured
+the inter-rater reliability between the three human coders and the algorithm
+(treating the algorithm just like any other coder).  Second, adopting the 
+majority code given by the human coders, we determined the accuracy of the
+food-detection algorithm.  Data sumarizing this validation process are given
+in table S1.
+
+\begin{table}
+\centering
+\setlength{\tabcolsep}{12pt}
+\begin{tabular}{ r | c }
+\toprule    
+\# terms coded & 500 \\
+\# food references & 130 \\
+\# correct machine codes & 440 \\
+inter-rater reliability & 82.4\% \\
+human-machine code agreement & 88\% \\
+%machine recall & 80 \% \\
+%machine precision & 75.4 \% \\
+%machine code F1 & 0.78 \\
+\bottomrule
+\end{tabular}
+\caption{\footnotesize{
+	\td{remove the automatic numbering}. Table S1. Results for the validation 
+	of the automatic detection of food references, by comparison to
+	human-generated coding on randomly sampled words.  In calculating the 
+	human-machine code agreement, the majority human code was used.
+	Inter-rater reliability was calculated as Krippendorff's alpha.
+}}
+\end{table}
+
+The results show that good inter-rater reliability was achieved during the
+validation (82.4\%).  Looking at the agreement between the 
+machine codes and the majority human-generated codes, we find they agree
+88\% of the time.  This means that the concept used to instruct human coders
+provides a good approximation to what the wordnet-based machine codes actually
+represent. In other words, the machine codes correspond closely to indicating
+which words correspond to nouns that refer to edible things, and which ones
+don't, which provides a clear and simple interpretation for the machine
+coding of food and non-food words.
+
+\subsection*{S6: Calculation of relative specificity}
+In the main text we present results for the relative specificity of labels
+produced by two experimental treatments.  In performing this calculation,
+we used the wordnet corpus, which has a set of hypernym-hyponym relationships
+as described in the main text.  The first step in performing this calculation
+was therefore to map the words occuring from (the labels of) a given 
+experimental treatment onto the wordnet synsets.  In general, a given word
+form can have multiple meanings, and therefore maps onto multiple wordnet 
+synsets.
+
+The result of mapping the words from two treatments onto the wordnet 
+hypernym-hyponym graph two sets of counts, one set per treatment, 
+indicating the number of times a word from a given synset occured among the
+labels of the treatment.  Then, for every synset in one treatment, we looked
+at the number of synsets in the other treatment that were more generic
+(reachable by following hypernym relations) less the number of words that
+were more specific (reachable by following hyponym relations).  This quantity
+tallied for all words in the original synset gives a (non-normalied) measure
+of the degree to which words from the first treatment are more specific
+than words from the second treatment, overall.  We then normalized this 
+quantity by the total number of possible comparisons between the words of
+one treatment to those of the other, where two words are considered comparable
+only if one word is the hypernym or hyponym of the other.  Hence, ``statue'' 
+and ``bread'' are not comparable, but ``pumpernickel'' and ``bread'' are.
+
+This calculation can be summarized by the following equation:
+\begin{equation}
+	S(P,Q) = \frac{
+		\sum_{w\in P}\sum_{v\in Q} \left(
+			\mathbf{1}_{[w>v]} - \mathbf{1}_{[v>w]} \right)
+	}{
+		\sum_{w\in P}\sum_{v\in Q} \left(
+			\mathbf{1}_{[w>v]} + \mathbf{1}_{[v>w]} \right)
+	},
+\end{equation}
+where $P$ and $Q$ are sets of synsets, and $\mathbf{1}_{[w>v]}$ evaluates
+to 1 if synset $w$ is more specific than (i.e. is a hyponym of) synset $v$.
+This measure counts the excess of cases where synsets from $P$ are more
+specific then synsets from $Q$, as a fraction of all comparable synset pairs.
+
+In computing this quantity between two treatments, we first computed it 
+using the labels attributed to a particular test task, and then
+averaged the result obtained in this way for each of the five test tasks.
+
+\subsection*{S7: Analysis of variance}
+	\paragraph{Variance in the average fraction food-related labels}
+	In the main text, Fig.~\ref{fig:specificity}A shows the difference in 
+	the fraction of food related labels used by workers in from different 
+	treatments.  The error bars show the 95\% confidence intervals around 
+	the estimated difference of means.  It was computed from the
+	observed sample standard deviation in the fraction of food labels given
+	by individual workers.
+
+	\paragraph{Variance in food vocabulary size.}
+	\td{Not sure how to calculate this yet.}
+
+	\paragraph{Variance in food specificity.}
+	\td{Need to calculate this using bootstrapping.}
+
+\subsection*{S8: Measuring computational hysteresis}
+	\paragraph{Using cross-validation accuracy to lower-bound L1-distance.}
+	In order for Eq.~\ref{l1} to be applicable, it is necessary to obtain
+	an unbiased estimate of a classifier's performance.  One well-known
+	pitfall in measuring this error is to underestimate it due to 
+	over-fitting of the data used.  As an example, if one were to try 
+	a large number of classifiers, eventually one would find one that
+	classifies the data perfectly, even though it might non generalize to
+	new data.
+
+	It is customary to use part of a data set to optimize hyperparameters of
+	a model, and then test the model on as-yet unseen data.  In our case,
+	don't have enough samples in each treatment to do this.  Instead, for 
+	this reason, we make principled decisions for all of the options used
+	in our classifier, and then test it's accuracy using cross validation,
+	with no optimization performed on the data.  It was cruicial for 
+	the statistical validity of our approach that we test our classifier on 
+	each datum only once, and report these results without any optimizations
+	of the classifier.
+
+	In performing the classification we had various options, and since we
+	could not optimize these choices, we made principled decisions based on
+	prior knowledge from text classification applications.  We describe the
+	options we faced and the choices we made below.
+
+	\textit{whether to correct misspelled words.}  Because we used free-text
+	entry for the labels, there was bound to be many spelling mistakes.
+	This would tend to reduce the accuracy of a classifier, because the 
+	entries ``bread'' and ``braed'' would be regarded as completely different
+	features, even though they clearly correspond to the same 
+	\textit{intended word}.  While no algorithm can determine a worker's 
+	intentions, it is possible to check words against a corpus, and, in the
+	case of a misspelled word, look for plausible corrections based on 
+	edit distance.
+
+	\textit{Lemmatization.}  In some cases it is helpful to simplify words 
+	before providing them to the classifier.  For example, the words 
+	``berries'' and ``berry'' only differ in number, but would normally be
+	treated as completely different features.  Lemmatization ensures that
+	nouns are in their sigular form, which helps to eliminate variations in
+	labels that increase sparsity without conveying discriminative 
+	information.
+
+	\textit{Removal of stop-words.}  Certain very common words such as `the',
+	``to'', and ``it'' are extremely common but don't help discriminate a 
+	worker's exposure.  Removing these words is a common practice because
+	they otherwise introduce noise into the classifier learning process.
+
+	\textit{Whether to split multiple words.}  Although workers were 
+	instructed to put one word per text input, many put multiple words.
+	Theoretically the original multi-word entry might bear additional 
+	information that could be useful in discerning a worker's exposure. 
+	In practice, it would be necessary for that word combination to recur,
+	which is unlikely.  Therefore we chose to split multi-word entries,
+	using the individual words as features.  This meant that the outputs of
+	some workers generated more features than those of others.
+
+	\textit{Preserving the location of labels.}  When workers completed image
+	labeling tasks, they had to fill five text inputs, which were stacked
+	vertically.  Presumably, they began with the top input and proceeded 
+	downwards.  It seems likely that exposure effects might influence the
+	\textit{order} in which workers apply labels, so when processing the 
+	labels we prepended an integer to indicate into which text input the 
+	label been input.  This meant that the classifier could distinguish
+	``bread'' entered into the first text input from ``bread'' entered into
+	the second.  A drawback is that this increases sparsity, preventing the
+	classifier from accounting for the fact that different though they are,
+	these entries should be treated similarly.  For this reason, we also
+	provided features to the classifier which did not encode the particular
+	input that had been used.  Thus, two workers that entered ``bread''
+	into different inputs would generate both a feature in common indicating
+	the use of the word ``bread'', as well as distinct features, indicating
+	entry of the word ``bread'' \textit{in a particular input}.
+
+	\textit{Preserving the connection between tasks and labels.}  In many
+	cases a particular label would appear in many tasks.  For example, the
+	word ``food'' appears in all test tasks.  It stands to reason that
+	exposure effects play out differently for different tasks, and that
+	the attribution of a particular label during one task provides different
+	information from the attribution of the same label during a different 
+	task.  So, as we did in the case of input location, we prepended labels
+	with the identity of the task in which they were added, so that the 
+	two otherwise identical labels added for different tasks were treated
+	by the classifier as unique features.  Unlike in the case of input 
+	position attribution, we didn't include raw labels unadorned with 
+	the task number.  Our rationale for this is that the task defines the 
+	context in which a label is applied, and so the elicitation of a label 
+	during one task represents a distinct output from the elicitaiton of the 
+	same label during a different task.
+
+\paragraph{Selection of the naive Bayes classifier.}
+A great deal of work has been done in the application of classifiers to
+text documents, which provides the bacground for our choice of classifier.
+The Support Vector Machine (SVM) approach is known to perform well, better in 
+general than naive Bayes.  However, three considerations drove us to use
+a naive Bayes classifier in favor of SVM.
+
+First, we used 119 examples (workers) per treatment, but the number of 
+features
+for each worker (i.e. the number of distinct labels, or modifications 
+thereof produced in preprocessing), was generally in the thousands.  
+This tends to
+be problematic for many classifier algorithms, including SVM, because it
+leads to very high variance models, which manifests as overfitting and poor
+performance.  To deal with this, some approach to culling features is 
+generally used, but this raises the issue of how to decide the culling in 
+a principled manner, generally adding further hyperparameters which could
+be optimized.  However, one of the strengths of the naive Bayes classifier
+is that it's performance is not generally degraded from the inclusion of 
+large numbers of features, even when the number of examples is comparatively
+small.  We expected this feature of the naive Bayes classifier to be 
+advantageous in our case.
+
+Second, the standard implementation of the naive Bayes classifier has no 
+hyperparameters to optimize.  This allows us to forgo the common practice 
+of holding out a test set, and instead use cross-validation as a method to
+estimate the true classification error, \textit{since we did not perform
+any kind of model selection or optimization whatsoever using our data}.
+This point is crucial, because if we did optimize our classifier during 
+cross-validation, then the validation error would no longer provide an 
+unbiased estimate of the true classification error, but would instead lead
+to us over-reporting exposure effects.
+
+Third, the naive Bayes algorithm is based on an assumption that the 
+probability of observing one feature is independant from the observation
+of any other, \textit{when conditioned on the class}.  This
+\textit{conditional independance} assumption is generally made for
+pragmatic rather than theoretical reasons, and is rarely satisfied.  However,
+if it \textit{is} satisfied, then the naive Bayes classifier is optimal.
+In our case, conditional independence means that, provided we know the 
+exposure of a worker, knowing one label they provided to an image does
+not in any way help us guess any other label for that image.  In most
+text documents, the existence of topics and language structure certainly
+vioalates the conditional independance of words.  But in our case, such 
+effects are less likely to carry from one text input to the next, and in the
+small space provided by five inputs, any overarching topics are likely to
+be in relation to the image itself, upon which we are conditioning.  In other
+words, we believe that, in our setup, conditional independence is better 
+satisfied than in most text classification contexts.  That being the case,
+one would not expect much improvement in using a more sophisticated algorithm,
+such as SVM.
+
+\paragraph{Comparison to other classifiers.}
+
+\begin{figure}
+	\centering
+	\includegraphics[scale=0.75]{figs/theta_sup.pdf}
+	\label{fig:theta_sup}
+	\caption{
+		Figure S2: Bias induced by exposure to initial tasks and frames.
+		Bias is defined to be the difference in the probability 
+		distribution over workers' labels (L1-distance).  The plotted values
+		give a lower bound to the L1-distance, $D_{L1}^-$, which was 
+		determined from a classifier's performance in 
+		distinguishing workers that had undergone different exposures.
+		The bias was determined using (A-F) a naive Bayes classifier, and 
+		(G-L) an SVM classifier.
+		In panels A through F, each plot adds an additional
+		preprocessing step to those used in the previous plot; the same is 
+		done for panels G through H: A,G) No 
+		preprocessing; B,H) spelling correction; C,I) stopword removal; 
+		D,J) lemmatization; E,K) splitting of multiple-word labels; 
+		F,L) distinguishing identical labels entered in different form inputs.
+	}
+\end{figure}
+The inequality in Eq.~\ref{l1}
+asserts that a classifiers performance in predicting class membership
+bounds the L1-distance between the distributions of features for the classes.
+This bound is tight for the optimal classifier, and in general, the slack
+depends on how the classifier is constructed.
+
+Therefore there may exist a classifier that is 
+significantly better than the one used to generate our results.  Even before
+commiting to a particular classifier algorithm, various decisions about
+preprocessing need to be made.  For example, we chose to remove stopwords,
+lemmatize, split multi-word labels, distinguish the input used to enter 
+labels, and correct spelling.  All of these decisions affect the classifier
+performance.  The particular classifier algorithm chosen also has a strong 
+effect.
+
+Since we did not have enough data to create a separate test set, we could not
+optimize these decisions.  Doing so would lead to the inflation of the 
+performance, which could then only be estimated using an independant test set.
+Instead, we made principled decisions as described above.
+
+Although we cannot optimize these decisions, it is appropriate to look at
+what affect these decisions had, post-hoc.  We reproduce the plot shown in 
+Fig.~\ref{fig:theta}A using different combinations of pre-processing options,
+and using both the naive Bayes and an SVM classifier.
+
+Unlike the naive Bayes classifier, it is necesarry to tune the cost and 
+gamma hyperparameters of the SVM classifier, as well as choose a kernel.
+We used simulated annealing to optimize the cost and gamma settings in the
+classification of $task2:food$ vs $task2:cult$.  For this reason, we expect
+the bar for $task2$ in Fig.~S8G-J is likely to be an overestimate due to
+overfitting on those data.
+
+These plots show that the result shown in Fig.~\ref{fig:theta}A is 
+representative, and supports the validity of the lower bounds on the 
+exposures exposure effects presented in the main text, in terms of induced 
+L1-distance.
+
+\subsection*{S9: Justifications and statistical properties of classifier-based measurement of computational hysteresis}
+\begin{itemize}
+	\item{Relationship to L1-Distance}
+	\item{Relationship to bias}
+	\item{Relationship to Jenson-Shannon divergence}
+	\item{Other approaches to measuring L1-distance}
+	\item{Comparison to hypothesis testing using $\chi^2$}
+\end{itemize}
 

### 2015-03-23 docs/publications/2014.09_SCIENCE/delete/main.tex
added all missing files

% ULaTeX2e, calling the article.cls class and 12-point type.

\documentclass[12pt]{article}

% My packages

\usepackage{amsmath}
\usepackage{framed, color}
\usepackage{soul}
\definecolor{blu}{rgb}{0,0,1}
\newcommand{\td}[1]{{\color{blu}\hl{TODO: #1}}}
\usepackage{graphicx}
\usepackage{amsthm}
\newtheorem{mydef}{Definition}
\usepackage{dcolumn}
\usepackage{multirow}
\usepackage{booktabs}
\newcolumntype{d}{D{.}{.}{4.0}}
\newcolumntype{s}{D{.}{.}{1.4}}

\usepackage{arydshln}

% Users of the {thebibliography} environment or BibTeX should use the
% scicite.sty package, downloadable from *Science* at
% www.sciencemag.org/about/authors/prep/TeX_help/ .
% This package should properly format in-text
% reference calls and reference-list numbers.

\usepackage{scicite}

% Use times if you have the font installed; otherwise, comment out the
% following line.

\usepackage{times}

% The preamble here sets up a lot of new/revised commands and
% environments.  It's annoying, but please do *not* try to strip these
% out into a separate .sty file (which could lead to the loss of some
% information when we convert the file to other formats).  Instead, keep
% them in the preamble of your main LaTeX source file.

% The following parameters seem to provide a reasonable page setup.

\topmargin 0.0cm
\oddsidemargin 0.2cm
\textwidth 16cm 
\textheight 21cm
\footskip 1.0cm

%The next command sets up an environment for the abstract to your paper.

\newenvironment{sciabstract}{%
\begin{quote} \bf}
{\end{quote}}

% If your reference list includes text notes as well as references,
% include the following line; otherwise, comment it out.

\renewcommand\refname{References and Notes}

% The following lines set up an environment for the last note in the
% reference list, which commonly includes acknowledgments of funding,
% help, etc.  It's intended for users of BibTeX or the {thebibliography}
% environment.  Users who are hand-coding their references at the end
% using a list environment such as {enumerate} can simply add another
% item at the end, and it will be numbered automatically.

\newcounter{lastnote}
\newenvironment{scilastnote}{%
\setcounter{lastnote}{\value{enumiv}}%
\addtocounter{lastnote}{+1}%
\begin{list}%
{\arabic{lastnote}.}
{\setlength{\leftmargin}{.22in}}
{\setlength{\labelsep}{.5em}}}
{\end{list}}

% Include your paper's title here

\title{Hysteresis in human computation:\\ how one task affects another}

% Place the author information here.  Please hand-code the contact
% information and notecalls; do *not* use \footnote commands.  Let the
% author contact information appear immediately below the author names
% as shown.  We would also prefer that you don't change the type-size
% settings shown here.

\author
{Edward Newell \\ Derek Ruths\\
\\
\normalsize{\texttt{edward.newell@mail.mcgill.ca}}\\
\normalsize{\texttt{derek.ruths@mcgill.ca}}\\
\normalsize{School of Computer Science, McGill University,}\\
\normalsize{3480 University Street, Room 318, Montreal, Quebec, Canada, H3A 2A7}\\
\\
}

% Include the date command, but leave its argument blank.

\date{}

%%%%%%%%%%%%%%%%% END OF PREAMBLE %%%%%%%%%%%%%%%%

\begin{document}

% Double-space the manuscript.

\baselineskip24pt

% Make the title.

\maketitle

% Place your abstract within the special {sciabstract} environment.

\begin{sciabstract}
Microtask platforms have become commonplace tools for obtaining human 
annotations for large datasets.  Such platforms connect requesters 
(researchers or companies) with large populations (crowds) of workers, who 
will individually complete small information-processing jobs, each taking 
typically between one to five minutes.  
A major challenge in using such platforms, 
and a topic of ongoing research, concerns designing jobs that elicit high 
quality annotations. Here we identify a feature of nearly all crowdsourcing 
jobs that can act as a strong and systemic source of bias in annotations 
produced by workers. Specifically, many microtask jobs consist of a sequence 
of tasks which share a common format (e.g., label pictures, identify people, 
circle galaxies). Using image-labeling, a canonical microtask job format, we 
discover that earlier tasks shift the distribution of future answers by 
30-50\%. 
Moreover, we show that prior tasks influence 
the content that workers chose to focus on, as well as the richness and 
specialization of their word choice. While these intertask effects can be a 
source of systematic bias, our results suggest that, with appropriate job 
design, it might be possible to leverage these biases to hone worker focus 
and specificity, helping to elicit reproducible, expert-level judgments.
\end{sciabstract}

\section*{Main text}
Microtask platforms are online marketplaces in which \textit{requesters} 
post batches of tasks, and \textit{workers} complete them
for remuneration, a sense of purpose, and fun
\cite{kazai2013analysis,Antin20122925}.
Typical tasks include tagging and categorizing images 
\cite{6116320,Zhai2012357}, coding and transcription, such as of voice recordings or handwritten notes
\cite{chandler2013breaking,paolacci2010running,Berinsky2012351,Finnerty2013}, 
and judging relevancy and quality, for example, to rate information 
retrieval systems \cite{le2010ensuring,grady2010crowdsourcing,alonso2009can,kazai2013analysis}.

In this form of crowdsourcing, workers appear like input-output devices.  
Such platforms provide much of the flexibility and 
cost-savings of fully automating the work in a computer program: 
the workforce is available on demand over the Internet using automated 
scripts, and  no interviews or contracts are required 
\cite{wolfson2011look,5543192}.  Many tasks
can be performed at a fraction of the cost of traditional methods for 
recruiting temporary workers or experimental subjects
\cite{Berinsky2012351,paolacci2010running,ranade2012crowdsource}.
From the requester's perspective, using microtask platforms resembles
running a computer program on a remote server, leading some to investigate
these platforms as a new computing architecture \cite{5543192,little2010turkit,minder2012crowdlang,kittur2011crowdforge}.

Due to its flexibility and cost-effectiveness, 
there has been a surge in demand for microtask work
in both industry and academia\cite{wolfson2011look,Berinsky2012351}.  
Naturally, there is a desire to understand the factors affecting the 
reliability of microtask-based methods.  Researchers have investigated 
task-design parameters such as the 
level of pay \cite{Mason200977,kazai2013analysis}, 
the training and pre-screening of workers 
\cite{le2010ensuring,paolacci2010running,kazai2013analysis}, 
user-interface design \cite{Finnerty2013}, and timely feedback 
\cite{Dow20121013}.
Researchers have also investigated the effects of \textit{framing}, 
by altering the description of the workflow context 
\cite{Kinnaird2012281}, the purpose of tasks 
\cite{chandler2013breaking}, and the problem description
\cite{thibodeau2013natural}.  Another important avenue of research concerns
workflow design: how to break down a complex problem into microtasks
\cite{kittur2011crowdforge}, the effect of microtask size 
\cite{Huang201077}, and the effects of interruptions \cite{laseckieffects}.

Here, we focus on a ubiquitous feature of microtask work: the tendency
for workers to perform many similar tasks in quick succession.  
To describe this tendency, it is necessary to clarify terminology.
On one popular microtask platform, Amazon's Mechanical Turk (MTurk), 
tasks are delivered in bundles called Human Intelligence Tasks (HITs).  
But for clarity, we will use ``task'' to mean 
the smallest repeatable unit of work; for example, labeling one image with
some descriptive words (\textit{labels}).  
Using this terminology, it is typical for a HIT to
actually consist of \textit{several tasks}, 
such as labeling ten images consecutively.

In addition to the task-repetition occuring \textit{within} HITs, 
workers prefer HITs that are part of a large set of HITs
having the same format, and cite speed and repeatability 
as desireable traits \cite{Chilton20101}.  When the tasks in a sequence are 
sufficiently similar, workers are more efficient \cite{laseckieffects}, 
and the cognitive load resulting from task-switching \cite{Adamczyk2004271} 
is eliminated.  Meanwhile, breaking complex jobs down into simpler tasks 
appears to improve results \cite{kittur2011crowdforge}.  
Thus, from the perspectives of both the worker and requester, 
it is desireable for workers to perform repetitive sequences of similar 
tasks in quick succession.

The repetitive completion of tasks is of concern because people's responses
to a prompt can be strongly influenced by their recent exposure to stimuli,
due to the well-known phenomenon of \textit{priming} 
\cite{BJOP1796,No2007,beller1971priming}.  Priming is typically relevant when 
the prior stimuli bear some conceptual or perceptual connection to the 
ensuing task\cite{Gass1999549,sohn2001task}, and so, the repetition of 
similar tasks within the typical microtask setup creates an ideal context for 
strong priming effects.

Researchers investigating a somewhat similar class of psychological phenomena,
found that ratings that microtask workers give to items in a list
depend on the order in which the list is presented, an effect known as
\textit{positional bias} \cite{lerman2014leveraging}.  This serves as an 
example of a basic psychological phenomenon impacting crowdsourced data,
and raises questions about what other cognitive biases might
affect microtask work, and how prevalent the induced bias might be.

Here we investigate the potential for task-repetition to induce bias in 
microtask-based work in a highly generalizeable setting.  
If such bias is present, it would impact virtually 
every microtask and crowdsourced workflow.
Our results show that a worker's response during a task
does indeed depend strongly on the tasks performed beforehand.   
We call the effects that earlier tasks exert on later ones 
\textit{intertask effects}.

As we have described, microtask platforms have been widely adopted as a 
tool, but computer scientists also hold such platforms as the object of 
research, viewing  microtask platforms as a new kind of computing 
architecture.  In analogy to CPUs (central 
processing units) and GPUs (graphics processing units), 
Davis \textit{et al} invoked the \textit{human processing unit}, or HPU \cite{5543192}.
Researchers have sought to define a set of basic HPU operations, and
have developed libraries and frameworks to simplify HPU programming 
and make it more like CPU programming 
\cite{little2010turkit,minder2012crowdlang,kittur2011crowdforge}.  
As an example, one operation overcomes the inherent stochasticity of HPU 
outputs, by automatically aggregating votes from multiple HPUs under a single
function call.

But our revelation of strong intertask effects shows that, 
in addition to stochasticity, HPUs are subject to \textit{hysteresis}, 
meaning that their 
outputs depend on the history of their inputs.  Reproducibility and 
path-independence are crucial properties for the components of a 
computing architecture, so a better understanding of the computational 
ramifications of many psychological phenomena is needed.

We investigated intertask effects using image-labeling tasks on the Amazon 
Mechanical Turk (MTurk) microtask platform.  
In addition to being one of the most common kinds of tasks
\cite{chandler2013breaking,Berinsky2012351,Finnerty2013,paolacci2010running},
image-labeling is prototypical for any kind of task in which the worker is 
asked to provide a high-level judgment, incorporating prior knowledge, in 
response to a prompt.  
This includes such diverse tasks as describing
video and audio recordings, summarizing texts, or providing feedback to a 
product review.

In our first experiment, which we call
\textit{intertask-food-objects}, workers were assigned to either a
\textit{food} or \textit{objects} treatment.  Workers in these treatments
performed a set of five \textit{initial tasks}, which each involved 
providing five descriptive labels for an image depicting 
either food or (non-food) objects, depending on the worker's 
treatment (Fig.~\ref{fig:task}A and B).  Following the initial 
tasks, workers performed five \textit{test tasks}, which were identical for 
both treatments.  The test tasks contained images depicting a 
mixture of food and objects (Fig.~\ref{fig:task}C), and workers
were again asked to provide five labels for each.  Five initial 
tasks, together with the test tasks, comprised one HIT\footnote{
	Workers were only allowed to participate in one HIT relating to this study.
}. During the HIT, workers 
were presented images one at a time, and, crucially, we made no 
distinction between the initial and test tasks.

A $\chi^2$ test shows that the frequencies of words used by
workers in the \textit{food} and \textit{objects} treatments differed
significantly during test tasks ($p = 6.0 \times 10^{-14}$), even though the test tasks were identical 
in both treatments\footnote{see supplementary text for tabulated statistics.}.  This shows that earlier tasks have a 
significant effect on later ones, and raises concerns about the 
design of microtasks, and possibly the microtask methodology itself.

While this affirms the \textit{existence} of intertask effects, we wish to
understand the nature and severity of the bias induced by prior task 
exposures.  To this end, we define the extent of bias, $\theta$, in terms of
the strength of influence that a perturbation has on worker's responses.
Since workers' responses are stochastic, we define the extent of bias in 
terms of the shift induced in the distribution of responses\footnote{
	This is a general divergence metric between probability 
	distributions known as the \textit{total variation distance.}
}:
\begin{equation}
	\theta = \frac{1}{2}\sum_{x \in X} \left| p_0(x) - p_1(x) \right|,
	\label{eq:theta}
\end{equation}
where $p_i(x)$ is the probability that a worker subjected to treatment $i$
provides response $x$, from the set of possible responses $X$.
It is important to emphasize that a significant result from a $\chi^2$ test 
only allows us to conclude that $\theta$ is non-zero 
(see supplementary text).  
Determining $\theta$ from finite samples of responses, using purely 
statistical approaches, is difficult (see supplementary text),
which leads us to reformulate the
problem in terms of classification: given a worker's 
responses to test tasks, can a machine reliably infer what her prior exposure 
had been?  Intuitively, the greater the effect that prior tasks have on 
subsequent
responses, the more accurate the classifier can be.  Formally (as shown
in the supplementary text), the accuracy of such a classifier, $\eta$,
yields a lower bound on the bias:
\begin{equation}
	\theta \geq 2\eta - 1.
	\label{l1}
\end{equation}
By measuring the accuracy of a classifier, we can bound the 
bias induced by any perturbation, including both intertask effects and 
framing.  As defined, bias ranges from 0 (meaning the exposures 
does not affect the distribution of responses), to 1 
(or 100\%) (meaning that the exposure leads workers to provide a completely
different set of responses).

\begin{figure}
	\centering
	\includegraphics[scale=0.6]{figs/images.pdf}
	\caption{
		Examples of images used in
		initial tasks for the (\textbf{A}) \textit{food} and (\textbf{B}) 
		\textit{objects} treatments of \textit{intertask-food-objects};
		(\textbf{C}) test tasks for \textit{intertask-food-objects} and 
		\textit{frame-food-objects};
		initial tasks for the (\textbf{D}) \textit{food} and (\textbf{E}) 
		\textit{culture} treatments of \textit{intertask-food-culture};
		and (\textbf{F}) test tasks for \textit{intertask-food-culture} and 
		\textit{frame-food-culture}.
		The full set of experimental materials is shown in the 
		supplementary text.
	}

	\label{fig:task}
\end{figure}

Using a na\"ive Bayes classifier\footnote{
	We believe na\"ive Bayes is the best choice in this setting, as discussed
	in the supplementary material, and we show results when a support vector
	machine is used instead. 
	We also discuss data preprocessing and show results for alternatives.
}, we found that intertask effects 
lead to a 30\% bias between workers from the \textit{food} and 
\textit{objects} treatments (Fig.~\ref{fig:theta}A).  
This represents a substantial potential to distort microtask data.

There has been considerable interest in the effects that framing can have
on microtask responses
\cite{Kinnaird2012281,chandler2013breaking,thibodeau2013natural}, so,
as a point of comparison, we performed a similar experiment 
in which we framed the purpose of the tasks.  In the experiment 
\textit{frame-food-objects}, workers were either told that 
the tasks were ``Funded by the laboratory for the visual perception of Food 
and Ingredients'', or ``\ldots of Objects and Tools''.  
Framing did induce changes in the frequencies of 
word usage at significance (as determined by $\chi^2$ test; $p=0.0012$), but 
the \textit{extent} of framing-induced bias was not statistically 
distinguishable from zero ($p =0.37$) (Fig.~\ref{fig:theta}A), and was
weaker than the bias due to intertask effects ($p=2.1\times 10^{-5}$).

To assess the permenance of intertask effects, we replicated the experiment
\textit{intertask-food-objects} five times, each time using a different 
permutation of the test tasks.  This enabled us to measure the severity
of bias as a function of task position, independant of the content
of the test task.  We found that bias was strongest for the first test task
(about 28\%), but remained significant through all five test tasks 
($\alpha=0.05$) sustaining over 12\% bias (Fig. \ref{fig:theta}B).

We conducted variants of these experiments using different images, to see 
whether this trend was robust.  In the experiment 
\textit{intertask-food-culture},
workers were either assigned to a \textit{food} or \textit{culture} treatment.
As before, the initial tasks for the \textit{food} treatment contained images 
depicting food (Fig.~\ref{fig:task}D). 
In the \textit{culture} treatment, 
the initial tasks contained images depicting cultural scenes 
(of dance, sport, or music) (Fig.~\ref{fig:task}E).  The test tasks, which were identical for both
treatments, included images depicting meals of identifiable cultural 
origin\footnote{
	Despite efforts to the contrary, initial tasks 
	in \textit{intertask-food-culture} are arguably still of
	identifiable cultural origin, but this would only tend to make our 
	results more conservative (we discuss this further in the supplementary 
	text).
}
(Fig.~\ref{fig:task}F).

Results for this experiment again showed a 
strong bias as a result of intertask effects (about 50\%) 
(Fig.~\ref{fig:theta}A).  Again, we compared intertask effects to 
framing, by performing an experiment (\textit{frame-food-culture}) using 
the same test tasks as in \textit{intertask-food-culture}, in which we exposed
workers to a statement framing the purpose of the tasks as the recognition 
of either food or culture.  
In this experiment, framing did not induce significant changes in the 
frequencies of words used during test tasks (by $\chi^2$ test, $p=0.29$) 
(Fig.~\ref{fig:theta}A).

It was only when we combined the use of framing, with an active 
reiteration step, that bias reached a level comparable to that achieved 
by intertask effects.  In the experiment \textit{echo-food-objects},
after framing the purpose of the task around either the recognition of food
or objects, we required the worker to echo back the purpose of the task
using a combo-box input.  In this case, workers exposed to different 
``echoed framing'' showed a bias of about 35\% in the labels provided during 
test tasks
(Fig.~\ref{fig:theta}A). However, it is difficult to say whether this 
should be considered as a framing treatment \textit{per se}.
Requiring the worker to reiterate the frame signals our intent, as the 
requester, to ensure that the worker has taken note of the framing statement, 
possibly leading the worker to interpret it as an instruction.  
In any case, it is remarkable that intertask effects
were on par with an explicit statement of purpose that was emphasized 
through reiteration.

\begin{figure}
	\centering
	\includegraphics[scale=1]{figs/theta.pdf}
	\caption{
		Empirical bias, $\theta_\mathrm{NB}$, measured using a na\"ive Bayes 
		classifier, induced in image labeling tasks,
		(\textbf{A}) by exposing workers to initial tasks or framing. 
		As workers proceed through test tasks, the effects of initial tasks 
		wane, as shown (\textbf{B}) for \textit{intertask-food-objects}, but 
		remain significant even after five tasks.  Standard error bars are 
		shown.
	}
	\label{fig:theta}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[scale=0.92]{figs/vocab_specificity.pdf}
	\caption{
		(\textbf{A}) Exposing workers to initial tasks or framing, 
		involving food, changed the subsequent fraction of words that 
		referred to food during test tasks, 
		but did not always increase that fraction (in all three plots,
		positive values indicate a larger quantity for food-exposed workers).
		(\textbf{B}) The number of unique food-related
		words (richness) was greater for food-exposed workers, except in the 
		case of \textit{frame-food-culture} (stars indicate the threshold
		for a significant deviation under the null hypothesis of equal 
		richness, $\alpha=0.05$). 
		(\textbf{C}) Food-exposed
		workers used more specialized words to refer to food (see 
		supplementary text for calculation of relative specialization).
		Standard error bars are shown in (\textbf{A} and \textbf{C}).
	}
	\label{fig:specificity}
\end{figure}

To better understand the nature of 
intertask effects, we investigated the vocabulary
that workers used to label test tasks. A natural expectation is that, during
the test tasks within
a given experiment, the food-primed workers would use food-related words 
more often than their non-food-primed counterparts.  However, this was not 
generally 
the case. In the \textit{intertask-food-culture} experiment, food-primed
workers actually used significantly \textit{fewer} food-related words 
during test tasks\footnote{
	food-related words were identified using the wordnet corpus, 
	augmented with additional words obtained by crawling a recipe website 
	(see supplementary text for details).
} (Fig.~\ref{fig:specificity}A).  This finding
rules out a seemingly-simple idea that workers emphasize
content that has been present in earlier tasks: seeing content in prior tasks
influences, but does not necessarily \textit{increase}, the probability of 
referring to the content in subsequent tasks.

To deepen our understanding, we investigated workers' lexical richness in 
reference to food, that is, the number of \textit{unique} food-related words
used.  Even if workers provide an abundance of food-related words, there
can be less diversity if the same words are often repeated.  
This could happen, for example, if workers use generic references 
to food.
Both \textit{intertask} experiments showed that food-exposed workers had 
greater lexical richness, in reference to food, than their non-food-primed 
counterparts (as much as 20\% more) (Fig.~\ref{fig:specificity}B).  
The increase in lexical richness in the case of 
\textit{intertask-food-culture} is particularly noteworthy, because in that 
experiment, food-primed workers made fewer total references to food.  
We also observed enrichment of the food-related lexicon in the 
\textit{priming-food-objects}, and \textit{echo-food-objects} experiments, 
although to a lesser extent.

The observations regarding lexical richness lead us to suspect that 
initial tasks might influence workers to use more refined or specialized 
words, when referring to aspects of content that had been present in the 
initial tasks (i.e. food).  This would help explain why, in the case of 
\textit{intertask-food-culture}, we observed a significantly greater 
\textit{diversity} of food-related words despite their significantly lesser 
\textit{total amount}.
To test whether exposure to food in initial tasks increased the specialization
of food-references, we used the wordnet corpus to operationalize the 
notion of word specialization.  Wordnet provides a set of hypernym-hyponym 
relations between 117,798 English nouns 
\cite{miller1995wordnet,felbaum1998wordnet}.  Hypernyms are generalizations 
(for example, ``bread'' is a hypernym for 
``pumpernickel''), while hyponyms are specializations.
For each experiment, we compared food-related words provided by workers from 
one treatment to those from the other, tallying the percent-excess of
cases where one treatment's words were more specialized than the other 
(detailed calculation in the supplementary text).

In all experiments except \textit{frame-food-culture}, food-primed workers 
used significantly more specialized words, in reference to food, 
than their non-food-primed 
counterparts (about 15\% more) (Fig.~\ref{fig:specificity}C).
It is interesting that such substantial increases in both the lexical 
richness and specialization of food-related words 
held for \textit{intertask-food-culture}, where, as mentioned, we observed 
that food-exposed workers made \textit{fewer} references to food overall. 
These observations point 
to countervailing factors: one factor tending to activate the more 
specialized and less common food-related words 
(yielding greater lexical richness and specialization), and the other tending 
to suppress certain, presumably more common and generic words 
(yielding fewer food-related words in total).

This hypothesis is corroborated when we look at those words whose 
frequencies changed the most from one treatment to another 
(Table~S\ref{table:top-words}).  
The word ``food'', which is the most generic possible food-related word, was 
always \textit{suppressed} among food-primed workers.  In fact, 
for all experiments, ``food'' was the \textit{most suppressed} word.

Taken together, our results can be 
explained through a combination of positive and negative priming effects.
Positive priming (usually simply ``priming'') occurs when a prior stimulus 
predisposes a person to give certain responses in an ensuing task, and
is often observed as an increase in the speed or accuracy of a response, or
the ability to recognize briefer or noisier stimuli 
\cite{BJOP1796,BJOP1826,Huber2008324}.
Negative priming occurs when, after exposure to a stimulus 
considered to be non-salient, subsequent recognition of the stimulus is 
inhibited \cite{mayr2007negative}.

Workers exposed to images containing food will be (positively) primed, 
activating memories, concepts, and vocabulary related to food.  
However, as the worker labels successive images containing food, the basic 
fact that an image contains food will not appear to be salient, since it 
does not serve to distinguish one image from another.  Thus, the most 
generic references to that fact, such as the label ``food'', 
will be suppressed, while more specialized references will be elicited.  
Meanwhile, the number of references to food overall might increase or 
decrease, depending on the balance of these factors.

More generally, we are suggesting that, even though workers are not 
instructed to compare tasks in any way, prior tasks form a 
context relative to which workers judge salience.  Thus, due to a combination 
of negative and positive priming, a worker's focus 
in repeated tasks tends to be directed away from generic, shared features, 
toward specific and distinguishing ones.

Prior to this study, little thought appears to have been given to the 
priming effect that a task can have on those tasks that follow. 
But our findings show this is an  
important design consideration.  
A natural response might be simply to randomize 
task ordering, a practice that is commonly employed.  But the sheer extent of 
bias suggests that this will still introduce a significant amount of noise
into the results.  Even chains of two or three similar tasks, which
will not be reliably eliminated in random permutations, could lead
to the levels of bias we observed in our experiments.
It would be preferable to understand intertask
effects in greater depth so that they might be properly controlled.

Our findings suggest that, through careful task engineering,
it might be possible to achieve greater quality and reproducibility
of responses.  
A consistent goal in human computation is the achievement of expert-level
judgments from non-expert workers \cite{kittur2011crowdforge}.  
This has been achieved in some
applications \cite{snow2008cheap,Mortensen20131020,Warby2014385}. 
The distinction between experts and novices can be 
attributed in part to the possession of specialized knowledge and heuristics. 
But to a large degree, this distinction lies in the ability of 
experts to direct their focus toward salient features, while filtering out 
non-salient ones \cite{kellman2009perceptual}.  Using strategic task 
exposure, it might be possible to guide workers' focus and salience 
attribution, enabling expert-level judgment in a wider variety of 
crowdsourced applications.
We anticipate that future work will yield techniques to control intertask 
effects, both to reduce unwanted bias, as well as tune the 
focus, diversity, and specificity of worker responses.

Here we have shown that a severe bias can be introduced into microtask 
responses, simply from the performance of earlier tasks. 
These effects are much stronger than the effects of framing.  
While our findings raise serious concerns about the 
current state of microtask design, they reveal potential opportunities 
for more 
refined control over worker focus and acuity.  Any application that relies
on the repetitive use of human judgment is likely subject to the phenomena
we described here.  Exploring the pitfalls and opportunities posed by
intertask effects is an important direction for future work, 
in the effort to develop performant and reliable methods for human 
computation.
\bibliography{newbib}
\bibliographystyle{Science}
\end{document}

### 2015-03-23 src/ignore_workers.py

@@ -1,0 +1,98 @@
+workers_to_ignore = set([
+	#'A3RJ8NZQ8BRTZM', 'AO1EONHY8NCO1', 'A1F0HIZYHTCJRB','A3B5X1ILYJFWQ0',
+	'A1TKOHOHB3P6Y0',
+	'A1MADOUB1BA0A5',
+	'AMD1LYNQAH3R8',
+	'A2NXDGNJXC6KFJ',
+	'A93D9W3UFM3FS',
+	'A1153ZIEQX0ZJ8',
+	'A3FRJKOYCI9Q53',
+	'AR9GO00XRXMK5',
+	'A1QYORNO0GY308',
+	'A3HBQMBW7XGZUM',
+	'A33KTU8KJ5CP2T',
+	'A1FQCA4TQ4I0DA',
+	'A14GSKVEQOSIFD',
+	'AF18OIZ0GWGP2',
+	'A3NLI62ZXQZTY6',
+	'A32FIOOQE8U98U',
+	'A3O9E7SFME6EHN',
+	'A3PKJ0CX86ZAWN',
+	'A2RJ4DUP52FKVG',
+	'A2KK3WI0A1R8R4',
+	'A3A45A5YUM61LK',
+	'A5BE7AD48CGRI',
+	'A1IIS53RHR01J3',
+	'A3BMYHXTRC70O',
+	'A3EJ44J2ZNRMDA',
+	'A37DFWV5W6PXMS',
+	'A3UC45GKCAZ7ZU',
+	'A2LEY4X3LD8G26',
+	'A47P5PR27PW3B',
+	'A2SYRFPPV9WDEG',
+	'A1DRFDGG2KCOI2',
+	'A1BPHW0KCTG34P',
+	'A1TGSYR7H0PKEI',
+	'A1NSDCVK7C0UTU',
+	'A2TLYMTFPCZVMM',
+	'A2V99E4YEP14RI',
+	'AU2C0Q45DVGJO',
+	'A187NHMKI4HSA',
+	'A3B2O3SOMXJ2OF',
+	'A1TSMYQDZGYWBS',
+	'A3M6TIBELIT0GK',
+	'A3OZ3ZUUGTX29P',
+	'A1IU5OP7BBZHZ7',
+	'A37WXDYYT7RCZ0',
+	'A1RIKXU9XOQ67',
+	'A3G2AQM5CPACH4',
+	'A2DPYFATSL6L2J',
[…]

### 2015-03-23 src/scrape_amt.py

@@ -1,0 +1,21 @@
+from selenium import webdriver
+from selenium.common.exceptions import TimeoutException
+from selenium.webdriver.support.ui import WebDriverWait 
+from selenium.webdriver.support import expected_conditions as EC
+from selenium.webdriver.support.select import Select
+from selenium.webdriver.common.by import By
+
+def get_job_descriptions():
+	driver = webdriver.Firefox()
+	url=( 
+		"https://www.mturk.com/mturk/viewhits?"
+		"searchWords=&"
+		"selectedSearchType=hitgroups"
+		"&sortType=LastUpdatedTime%3A1"
+		"&pageNumber=1"
+		"&searchSpec=HITGroupSearch%23T%232%2310%23-1%23T%23!%23!LastUpdatedTime!1!%23!"
+	)
+	driver.get(url)
+	table = driver.find_elements_by_tag_name('table')[6]
+	for i, td in enumerate(table.find_elements_by_tag_name('td')):
+		print td.text

### 2015-04-25 docs/publications/2015.04_PNAS/man.tex
Created PNAS draft

--- 2015-02-18 docs/publications/2014.09_SCIENCE/man.tex
@@
-% ULaTeX2e, calling the article.cls class and 12-point type.
-
-\documentclass[12pt]{article}
-
-% My packages
-
-\usepackage{amsmath}
-\usepackage{framed, color}
-\usepackage{soul}
-\definecolor{blu}{rgb}{0,0,1}
-\newcommand{\td}[1]{{\color{blu}\hl{TODO: #1}}}
-\usepackage{graphicx}
-\usepackage{amsthm}
-\newtheorem{mydef}{Definition}
-\usepackage{dcolumn}
-\usepackage{multirow}
-\usepackage{booktabs}
-\newcolumntype{d}{D{.}{.}{4.0}}
-\newcolumntype{s}{D{.}{.}{1.4}}
-
-\usepackage{arydshln}
-
-% Users of the {thebibliography} environment or BibTeX should use the
-% scicite.sty package, downloadable from *Science* at
-% www.sciencemag.org/about/authors/prep/TeX_help/ .
-% This package should properly format in-text
-% reference calls and reference-list numbers.
-
-\usepackage{scicite}
-
-% Use times if you have the font installed; otherwise, comment out the
-% following line.
-
-\usepackage{times}
-
-% The preamble here sets up a lot of new/revised commands and
-% environments.  It's annoying, but please do *not* try to strip these
-% out into a separate .sty file (which could lead to the loss of some
-% information when we convert the file to other formats).  Instead, keep
-% them in the preamble of your main LaTeX source file.
-
-% The following parameters seem to provide a reasonable page setup.
-
-\topmargin 0.0cm
-\oddsidemargin 0.2cm
-\textwidth 16cm 
-\textheight 21cm
-\footskip 1.0cm
-
-%The next command sets up an environment for the abstract to your paper.
-
-\newenvironment{sciabstract}{%
-\begin{quote} \bf}
-{\end{quote}}
-
-% If your reference list includes text notes as well as references,
-% include the following line; otherwise, comment it out.
-
-\renewcommand\refname{References and Notes}
-
-% The following lines set up an environment for the last note in the
-% reference list, which commonly includes acknowledgments of funding,
-% help, etc.  It's intended for users of BibTeX or the {thebibliography}
-% environment.  Users who are hand-coding their references at the end
-% using a list environment such as {enumerate} can simply add another
-% item at the end, and it will be numbered automatically.
-
-\newcounter{lastnote}
-\newenvironment{scilastnote}{%
-\setcounter{lastnote}{\value{enumiv}}%
-\addtocounter{lastnote}{+1}%
-\begin{list}%
-{\arabic{lastnote}.}
-{\setlength{\leftmargin}{.22in}}
-{\setlength{\labelsep}{.5em}}}
-{\end{list}}
-
-% Include your paper's title here
+%% PNAStwoS.tex
+%% Sample file to use for PNAS articles prepared in LaTeX
+%% For two column PNAS articles
+%% Version1: Apr 15, 2008
+%% Version2: Oct 04, 2013
+
+%% BASIC CLASS FILE
+\documentclass{pnastwo}
+
+%% ADDITIONAL OPTIONAL STYLE FILES Font specification
+
+%\usepackage{pnastwoF}
+
+%% OPTIONAL MACRO DEFINITIONS
+\def\s{\sigma}
+%%%%%%%%%%%%
+%% For PNAS Only:
+\url{www.pnas.org/cgi/doi/10.1073/pnas.0709640104}
+\copyrightyear{2008}
+\issuedate{Issue Date}
+\volume{Volume}
+\issuenumber{Issue Number}
+%\setcounter{page}{2687} %Set page number here if desired
+%%%%%%%%%%%%
+
+\begin{document}
 
@@
 
-% Place the author information here.  Please hand-code the contact
-% information and notecalls; do *not* use \footnote commands.  Let the
-% author contact information appear immediately below the author names
-% as shown.  We would also prefer that you don't change the type-size
-% settings shown here.
-
-\author
-{Edward Newell \\ Derek Ruths\\
-\\
-\normalsize{\texttt{edward.newell@mail.mcgill.ca}}\\
-\normalsize{\texttt{derek.ruths@mcgill.ca}}\\
-\normalsize{School of Computer Science, McGill University,}\\
-\normalsize{3480 University Street, Room 318, Montreal, Quebec, Canada, H3A 2A7}\\
-\\
-}
-
-% Include the date command, but leave its argument blank.
-
-\date{}
-
-%%%%%%%%%%%%%%%%% END OF PREAMBLE %%%%%%%%%%%%%%%%
-
-\begin{document}
-
-% Double-space the manuscript.
-
-\baselineskip24pt
-
-% Make the title.
+\author{Edward Newell\affil{1}{McGill University, School of Computer Science,
+Canada}
+\and
+Derek Ruths\affil{1}{}}
+
+\contributor{Submitted to Proceedings of the National Academy of Sciences
+of the United States of America}
+
+%%%Newly updated.
+%%% If significance statement need, then can use the below command otherwise just delete it.
+%\significancetext{RJSM and ACAC developed the concept of the study.
+RJSM conducted the analysis, data interpretation and drafted the manuscript.
+AGB contributed to the development of the statistical methods, data interpretation and drafting of the manuscript.}
 
@@
 
-% Place your abstract within the special {sciabstract} environment.
-
-\begin{sciabstract}
-Microtask platforms are becoming commonplace tools for performing human
+\begin{article}
+\begin{abstract}
+
+{Microtask platforms are becoming commonplace tools for performing human
 research, producing gold-standard data, and annotating large datasets.
@@
 quality annotations. Here we identify a feature of nearly all crowdsourcing 
-jobs that acts as a strong systemic source of bias. 
+jobs that can seriously bias the results produced by workers.  %acts as a strong, systemic source of bias. 
 Microtask jobs typically consist of a sequence 
@@
 Understanding these \textit{intertask effects} is crucial 
-to embracing micratask platforms in critical applications.
+to ensuring the utility of microtask platforms in diverse applications.
 While intertask effects can be a source of systematic bias, 
@@
 they might be leveraged to hone worker focus and acuity, 
-helping to elicit reproducible, expert-level judgments.
-\end{sciabstract}
-
-\section*{Main text}
-Microtask platforms are online marketplaces in which \textit{requesters} 
+helping to elicit reproducible, expert-level judgments.}
+
+\end{abstract}
+
+\keywords{human computing | crowd sourcing | priming}
+
+%\abbreviations{SAM, self-assembled monolayer; OTS, octadecyltrichlorosilane}
+
+\dropcap{M}icrotask platforms are online marketplaces in which \textit{requesters} 
 post batches of tasks, and \textit{workers} complete them
@@
 judging the relevancy or quality of content, 
-and performing surveys for academic or market reserach purposes\footnote{We provide a survey of task types in the supplementary text.}.
+and performing surveys for academic or market reserach purposes (see Table SX for a survey of task types).
 %\cite{le2010ensuring,grady2010crowdsourcing,alonso2009can,kazai2013analysis}.
@@
 
-The flexibility and cost-effectiveness of microtask labour
-has led to a surge in demand from industry and 
-academia\cite{wolfson2011look,Berinsky2012351}.  More recently microtask 
-platforms have
-been assessed as a way to supplement expert human resources to increase
-capacity in critical applications, such as in medical diagnostic functions,
-with promising results \cite{Warby2014385}.
-Naturally, researchers have investigated the factors affecting the reliability
+%The flexibility and cost-effectiveness of microtask labour
+%has led to a surge in demand from industry and 
+%academia\cite{wolfson2011look,Berinsky2012351}.  More recently, microtask 
+%platforms have
+%been proposed as a means to use non-specialized workers to supplement expert human resources in critical applications, such as in medical diagnostics,
+%with promising results \cite{Warby2014385}.
+To be useful, these platforms must be reliable, leading researchers to investigate the factors affecting the reliability
 of microtask work, including
@@
 
-Here, we focus on a ubiquitous feature of microtask work: the tendency
-for workers to perform many similar tasks in quick succession.  
-%To describe this tendency, it is necessary to clarify terminology.
-On one popular microtask platform, Amazon's Mechanical Turk (MTurk), 
-tasks are delivered in bundles called HITs.
+Here, we focus on how a ubiquitous feature of microtask work affects reliability.
+Because tasks are short (hence the term `microtask'), there is a tendency for workers to perform many similar tasks in quick succession.
+In fact, on the most popular microtask platform, Amazon's Mechanical Turk (MTurk),
+tasks are typically delivered in bundles called HITs.
 Although HIT stands for ``Human Intelligence Task'', here we use ``task'' to 
@@
 cognitive load from task-switching\cite{Adamczyk2004271}.
-%Furthermore, on average, workers report spending over 4 hours per day on 
-%microtasks, taking breaks only every 1.24 hours, while some take no breaks 
-%at all
-%\cite{laseckieffects}.
-
-%Complex work consists of heterogeneous subtasks; when complex work is
-%broken down and workers perform sequences of very similar simple tasks
-%cognitive load is reduced, and workers are more efficient and accurate 
-%\cite{Adamczyk2004271,laseckieffects,kittur2011crowdforge}.
-%Thus, the tendency for workers to perform series of repetitive, similar
-%tasks would appear to be beneficial.
 
@@
 
-We investigate the potential for task repetition to induce bias in 
+Here, we investigate the potential for task repetition to induce bias in 
 a highly generalizeable microtask setup, in which workers label a 
-series of images.  If task-induced priming arises in our setup, 
-it should be expected in virtually every microtask and crowdsourced workflow
-where workers are called upon to exercise their judgment\footnote{
-	As opposed to those tasks where a single clear correct answer exists.
-}.
+series of images.  If task-induced priming arises in this setup, 
+it can be expected in virtually every microtask and crowdsourced workflow
+where workers are called upon to exercise their judgment.
+
 Our results show that a worker's response during a task
@@
 
-%As we have described, microtask platforms have been widely adopted as a 
-%tool, but computer scientists also hold such platforms as the object of 
-%research, viewing  microtask platforms as a new kind of computing 
-%architecture.  In analogy to CPUs (central 
-%processing units) and GPUs (graphics processing units), 
-%Davis \textit{et al} invoked the \textit{human processing unit}, or HPU \cite{5543192}.
-%Researchers have sought to define a set of basic HPU operations, and
-%have developed libraries and frameworks to simplify HPU programming 
-%and make it more like CPU programming 
-%\cite{little2010turkit,minder2012crowdlang,kittur2011crowdforge}.  
-%As an example, one operation overcomes the inherent stochasticity of HPU 
-%outputs, by automatically aggregating votes from multiple HPUs under a single
-%function call.  
-%
-%But our revelation of strong intertask effects shows that, 
-%in addition to stochasticity, HPUs are subject to \textit{hysteresis}, 
-%meaning that their 
-%outputs depend on the history of their inputs.  Reproducibility and 
-%path-independence are crucial properties for the components of a 
-%computing architecture, so a better understanding of the computational 
-%ramifications of many psychological phenomena is needed.
-
-Our image-labeling tasks were performed on the MTurk microtask platform.  
-We chose image labeling because it is very common\footnote{
-	We discuss task composition in the supplementary text.
-},
-%\cite{chandler2013breaking,Finnerty2013},%,paolacci2010running},
+\section{Results}
+
+Our image-labeling tasks were performed on the MTurk microtask platform.  We
+chose image labeling because it is very common,
+%,paolacci2010running},
 and because it is prototypical for any kind of task in which the worker is
-asked to provide a response that is not precisely determined by 
-the prompt, but instead depends on the worker's judgment.  
-This includes such diverse tasks as describing video and audio recordings, 
-summarizing texts, or in clinical diagnostic judgments.
-
-In our first experiment, called \textit{intertask-food-objects},
-workers were assigned to either a
-\textit{food} or \textit{objects} treatment.  Workers in both treatments
-performed a set of five \textit{initial tasks}, which each involved 
-providing descriptive labels for an image depicting 
-either food or (non-food) objects, depending on the worker's 
-treatment (Fig.~\ref{fig:task}A and B).  Following the initial 
-tasks, workers performed five \textit{test tasks}, which were identical for 
-both treatments.  In the the test tasks, workers labeled images, each of 
-which depicted a mixture of food and objects (Fig.~\ref{fig:task}C).  
-The five initial 
-and test tasks performed by each worker comprised one HIT\footnote{
-	Workers were only allowed to participate in one HIT relating to this study.
-}. The images were presented one at a time, and we made no 
-distinction between the initial and test tasks.
-
-The frequencies of words used by
-workers in the \textit{food} and \textit{objects} treatments differed
-significantly during test tasks (by $\chi^2$ test, $p = 6.0 \times 10^{-14}$),
-even though the test tasks were identical in both treatments\footnote{
-	see supplementary text for tabulated statistics.
-}.  Thus earlier tasks do significantly affect later ones, raising concerns 
-about the the microtask methodology.
+asked to provide a response that is not precisely determined by the prompt, but
+instead depends on the worker's judgment
+\cite{chandler2013breaking,Finnerty2013}.  This includes such diverse tasks as
+describing video and audio recordings, summarizing texts, or in clinical
+diagnostic judgments.
+
+In our first experiment, called \textit{intertask-food-objects}, workers were
+assigned to either a \textit{food} or \textit{objects} treatment.  Workers in
+both treatments performed a set of five \textit{initial tasks}, which each
+involved providing descriptive labels for an image depicting either food or
+(non-food) objects, depending on the worker's treatment (Fig.~\ref{fig:task}A
+and B).  Following the initial tasks, workers performed five \textit{test
+tasks}, which were identical for both treatments.  In the test tasks, workers
+labeled images, each of which depicted a mixture of food and objects
+(Fig.~\ref{fig:task}C).  The five initial and test tasks performed by each
+worker comprised one HIT. The images were presented one at a time, and we made
+no distinction between the initial and test tasks. Finally, workers were only
+allowed to participate in one HIT relating to this study, ensuring that prior
+exposure to the experiment design and content was not an issue.
+
+The frequencies of words used by workers in the \textit{food} and
+\textit{objects} treatments differed significantly during test tasks (by
+$\chi^2$ test, $p = 6.0 \times 10^{-14}$), even though the test tasks were
+identical in both treatments (see Supplementary Material for tabulated
+statistics).  This establishes our most fundamental finding: earlier tasks do affect
+later ones. %, raising concerns about the the microtask methodology.
 
 Having affirmed the \textit{existence} of intertask effects, we wish to
-understand the nature and severity of the bias induced.
-We therefore define the extent of bias, $\theta$, in terms of
-the strength of influence that a prior perturbation has on workers' responses.
-Since workers' responses are stochastic, we define the extent of bias in 
-terms of the change induced in the distribution of responses\footnote{
-	This is a general divergence metric between probability 
-	distributions known as the \textit{total variation distance.}
-}:
+understand the nature and severity of the bias induced.  We therefore define
+the extent of bias, $\theta$, in terms of the strength of influence that a
+prior perturbation has on workers' responses.  Since workers' responses are
+stochastic, we define the extent of bias in terms of the change induced in the
+distribution of responses:
+
 \begin{equation}
@@
 \end{equation}
+
 where $p_i(x)$ is the probability that a worker, subjected to treatment $i$,
-provides response $x$, from the set of possible responses $X$.
-%A significant result from a $\chi^2$ test only allows us to conclude that 
-%$\theta$ is non-zero (see supplementary text).  
-Determining $\theta$ from finite samples of responses, using purely 
-statistical approaches, is difficult (see supplementary text),
-which leads us to reformulate the
-problem in terms of classification: given a worker's 
-responses to test tasks, can a machine reliably infer what her prior exposure 
-had been?  Intuitively, the greater the effect that prior tasks have on 
-subsequent responses, the more accurate the classifier can be.  
-Formally (as shown in the supplementary text), the accuracy of such a 
+provides response $x$, from the set of possible responses $X$. This formulation
+is a general divergence metric between probability distributions known as the
+{\it total variation distance}. Determining $\theta$ from finite samples of
+responses, using purely statistical approaches, is difficult (see supplementary
+text), which leads us to reformulate the problem in terms of classification:
+given a worker's responses to test tasks, can a machine reliably infer what her
+prior exposure had been?  Intuitively, the greater the effect that prior tasks
+have on subsequent responses, the more accurate the classifier can be.
+Formally (as shown in the supplementary material), the accuracy of such a
 classifier, $\eta$, establishes a lower bound on the bias:
+
 \begin{equation}
@@
 
-By measuring the accuracy of a classifier, we bound the 
-bias induced by a perturbation, such as the exposure to prior tasks or 
-framing.
-Bias ranges from 0 (meaning the exposure 
-does not affect the distribution of responses), to 1 
+By measuring the accuracy of a classifier, we bound the bias induced by a
+perturbation, such as the exposure to prior tasks or framing.  Bias ranges from
+0 (meaning the exposure does not affect the distribution of responses), to 1
 (or 100\%) (meaning that the exposure leads workers to provide a completely
@@
 
-\begin{figure}
+\begin{figure*}
 	\centering
@@
 	\label{fig:task}
-\end{figure}
-
-Using a na\"ive Bayes classifier\footnote{
-	We believe na\"ive Bayes is the best choice in this setting, as discussed
-	in the supplementary material, and we show results when a support vector
-	machine is used instead. 
-	We also discuss data preprocessing and show results for alternative 
-	preprocessing.
-}, we found that intertask effects 
-lead to a 30\% bias between workers from the \textit{food} and 
-\textit{objects} treatments (Fig.~\ref{fig:theta}A).  
+\end{figure*}
+
+Using a na\"ive Bayes classifier (other classifiers were considered and tested,
+see SM), we found that intertask effects lead to {\it at least} a 30\% bias between workers
+from the \textit{food} and \textit{objects} treatments (Fig.~\ref{fig:theta}A).
 This represents a substantial potential to distort microtask data.
 
-There has been considerable interest in the effects that framing can have
-on microtask responses
-\cite{Kinnaird2012281,chandler2013breaking,thibodeau2013natural}, so,
-as a point of comparison, we describe a similar experiment 
-in which we framed the purpose of the tasks.  In the experiment 
-\textit{frame-food-objects}, the same test-tasks were used, but rather
-than exposing workers to initial tasks, workers were either told that 
-the tasks were ``Funded by the laboratory for the visual perception of Food 
-and Ingredients'', or ``\ldots of Objects and Tools''.  
-Framing did induce changes in the frequencies of 
-word usage at significance (as determined by $\chi^2$ test; $p=0.0012$), but 
-the \textit{extent} of framing-induced bias was not statistically 
-distinguishable from zero ($p =0.37$) (Fig.~\ref{fig:theta}A), and was
-much weaker than the bias due to intertask effects ($p=2.1\times 10^{-5}$).
+Of course, intertask effects are not the only means of introducing bias into
+worker responses. In particular, there has been considerable interest in the effects that
+framing can have on microtask responses
+\cite{Kinnaird2012281,chandler2013breaking,thibodeau2013natural}. Therefore, as a point of
+comparison, we conducted an experiment, similar to the first, in which we
+framed the purpose of the tasks.  In this experiment, called
+\textit{frame-food-objects}, the same test-tasks were used, but rather than
+exposing workers to initial tasks, workers were either told that the tasks were
+``Funded by the laboratory for the visual perception of Food and Ingredients'',
+or ``\ldots of Objects and Tools''.  Framing did induce changes in the
+frequencies of word usage at significance (as determined by $\chi^2$ test;
+$p=0.0012$), but the \textit{extent} of framing-induced bias was not
+statistically distinguishable from zero ($p =0.37$) (Fig.~\ref{fig:theta}A),
+and was much weaker than the bias due to intertask effects ($p=2.1\times
+10^{-5}$).
+
 \begin{figure}
 	\centering
-	\includegraphics[scale=1]{figs/theta.pdf}
+	\includegraphics[scale=0.8]{figs/theta.pdf}
 	\caption{
@@
 \textit{intertask-food-objects} while permuting the test tasks, to reveal the
-dependence of intertask effects on task position.
-We found that bias was strongest for the first test task (about 28\%), 
-but remained significant through all five test tasks 
-($\alpha=0.05$) sustaining over 12\% bias even when the initial and test 
-tasks were separated by four intervening tasks (Fig. \ref{fig:theta}B).
+dependence of intertask effects on task position.  We found that, as expected,
+bias was strongest for the first test task (about 28\%), but remained
+significant through all five test tasks ($\alpha=0.05$) sustaining over 12\%
+bias even when the initial and test tasks were separated by four intervening
+tasks (Fig. \ref{fig:theta}B).
 
@@
 whether this trend was robust.  In the experiment
-\textit{intertask-food-culture},
-workers were either assigned to a \textit{food} or \textit{culture} treatment.
-The initial tasks contained either images 
-depicting food (Fig.~\ref{fig:task}D), or depictions of cultural scenes 
-(of dance, sport, or music) (Fig.~\ref{fig:task}E).  The test tasks, which 
-were, again, identical for both treatments, depicted meals of identifiable 
-cultural origin\footnote{
-	Despite efforts to the contrary, initial tasks 
-	in \textit{intertask-food-culture} are arguably still of
-	identifiable cultural origin, but this would only tend to make our 
-	results more conservative (we discuss this further in the supplementary 
-	text).
-}
-(Fig.~\ref{fig:task}F).
-
-Results for this experiment again showed a 
-strong bias as a result of intertask effects (about 50\%) 
-(Fig.~\ref{fig:theta}A).  Again, comparing intertask effects to 
-framing, the experiment (\textit{frame-food-culture}) used
-the same test tasks as in \textit{intertask-food-culture}, but exposed
-workers to statements framing the purpose of the tasks as the recognition 
-of either food or culture.  In this experiment, framing did not induce 
-significant changes in word frequencies (by $\chi^2$ test, $p=0.29$) (Fig.~\ref{fig:theta}A).
-
-It was only when framing was combined with an active reiteration step, 
-that bias reached a comparable extent to that induced by intertask effects.  
-In the experiment \textit{echo-food-objects},
-after framing the purpose of the task (as the recognition of food
-or objects), workers were asked to echo the purpose of the task
-using a combo-box input.  This  ``echoed framing'' induced a bias of about 
-35\% (Fig.~\ref{fig:theta}A). However, it is difficult to say whether this 
-should be considered as a framing treatment \textit{per se}:
-requiring the worker to reiterate the purpose signals our intent, as the 
-requester, to ensure that the worker has taken note of it, possibly leading 
-the worker to interpret the exchange as an instruction.  
-In any case, it is remarkable that intertask effects
-were on par with an explicit, actively reinforced statement of the tasks' 
-purpose.
-
-\begin{figure}
+\textit{intertask-food-culture}, workers were either assigned to a
+\textit{food} or \textit{culture} treatment.  The initial tasks contained
+either images depicting food (Fig.~\ref{fig:task}D), or depictions of cultural
+scenes (of dance, sport, or music) (Fig.~\ref{fig:task}E).  The test tasks,
+which were, again, identical for both treatments, depicted meals of
+identifiable cultural origin (Fig.~\ref{fig:task}F).  As an aside, we recognize
+that, despite efforts to the contrary, initial tasks in
+\textit{intertask-food-culture} are arguably still of identifiable cultural
+origin, but this fact would only tend to make our results more conservative (we
+discuss this further in the supplementary text).
+
+Results for this experiment again showed a strong bias as a result of intertask
+effects (about 50\%) (Fig.~\ref{fig:theta}A).  Again, comparing intertask
+effects to framing, the experiment (\textit{frame-food-culture}) used the same
+test tasks as in \textit{intertask-food-culture}, but exposed workers to
+statements framing the purpose of the tasks as the recognition of either food
+or culture.  In this experiment, framing did not induce significant changes in
+word frequencies (by $\chi^2$ test, $p=0.29$) (Fig.~\ref{fig:theta}A).
+
+It was only when framing was combined with an active reiteration step, that
+bias reached a comparable extent to that induced by intertask effects.  In the
+experiment \textit{echo-food-objects}, after framing the purpose of the task
+(as the recognition of food or objects), workers were asked to echo the purpose
+of the task using a combo-box input.  This  ``echoed framing'' induced a bias
+of about 35\% (Fig.~\ref{fig:theta}A). However, it is difficult to say whether
+this should be considered as a framing treatment \textit{per se}: requiring the
+worker to reiterate the purpose signals our intent, as the requester, to ensure
+that the worker has taken note of it, possibly leading the worker to interpret
+the exchange as an instruction.  In any case, it is remarkable that intertask
+effects were on par with an explicit, actively reinforced statement of the
+tasks' purpose.
+
+% Specificity
+To better understand the nature of intertask effects, we investigated the
+vocabulary that workers used to label test tasks. One might expect that, within
+a given experiment, those workers exposed to food (whether through framing or
+initial tasks) would label test tasks using food-related words more often.
+Food-related words in labels were identified using the wordnet corpus,
+augmented with additional words obtained by crawling a recipe website (see
+supplementary text for details).  Surprisingly, we discovered that food-primed
+workers typically did not use food words more often. In
+\textit{intertask-food-culture}, food-exposed workers actually used
+significantly \textit{fewer} food-related words during test tasks
+(Fig.~\ref{fig:specificity}A).  This finding rules out the seemingly-simple and
+intuitive idea that workers emphasize content that has been present in earlier
+tasks: seeing content influences, but does not necessarily \textit{increase},
+the probability of referring to it in subsequent tasks.
+
+To deepen our understanding, we investigated workers' lexical richness in
+reference to food, that is, the number of \textit{unique} food-related words
+used.  Even if workers provide an abundance of food-related words, there can be
+less diversity, if, for example, workers repeat generic references to food.
+Both \textit{intertask} experiments showed that food-exposed workers had
+greater lexical richness, in reference to food, than their counterparts (as
+much as 20\% more) (Fig.~\ref{fig:specificity}B).  This is particularly
+noteworthy in the experiment \textit{intertask-food-culture}, because there,
+food-primed workers made fewer total references to food.
+
+The observations regarding lexical richness suggest that initial tasks might
+influence workers to use more refined or specialized words, when referring to
+aspects of content that had been present in the initial tasks.  To test this,
+we used the wordnet corpus to operationalize the notion of word specialization.
+Wordnet establishes relationships between 117,798 English nouns, indicating
+which words are specializations (or generalizations) of others
+\cite{felbaum1998wordnet}.  For example, ``pumpernickel'' is a specialization
+of ``bread''.  Within each experiment, we determined the percent-excess of
+food-related words that were more specialized in the food-exposed treatment
+relative to the other treatment (details in the supplementary material).
+
+In all experiments except \textit{frame-food-culture} (which had only a weak
+priming effect), food-primed workers used significantly more
+specialized words, in reference to food (about 15\% more)
+(Fig.~\ref{fig:specificity}C).  It is interesting that such substantial
+increases in both the lexical richness and specialization of food-related words
+held for \textit{intertask-food-culture}, where, as mentioned, we observed that
+food-exposed workers made \textit{fewer} references to food overall.  These
+observations point to countervailing factors: one factor tending to activate
+the more specialized and less common food-related words (yielding greater
+lexical richness and specialization), and the other tending to suppress
+certain, presumably more common and generic words (yielding fewer food-related
+words in total).
+
+This hypothesis is corroborated when we look at those words whose frequencies
+changed the most from one treatment to another (Table~S\ref{table:top-words}).
+The word ``food'', which is the most generic possible food-related word, was
+always \textit{suppressed} among food-primed workers, relative to the
+non-food-primed workers.  In fact, for all experiments, ``food'' was the
+\textit{most suppressed} word.
+
+Our results can be explained through a combination of positive and negative
+priming.  Positive priming (usually simply ``priming'') occurs when a prior
+stimulus predisposes a person to give certain responses in an ensuing task, and
+is often observed as an increase in the speed or accuracy of a response, or the
+ability to recognize briefer or noisier stimuli
+\cite{BJOP1796,BJOP1826,Huber2008324}.  Negative priming occurs when, after
+exposure to a stimulus considered to be non-salient, subsequent recognition of
+the stimulus is inhibited \cite{mayr2007negative}.
+
+Workers exposed to images containing food are (positively) primed, activating
+memories, concepts, and vocabulary related to food.  However, if the worker
+labels several images containing food, the basic fact that an image contains
+food will not seem salient, since it does not distinguish one image from
+another.  Thus, the most generic references to that fact, such as the label
+``food'', will be suppressed, while more specialized references will be
+elicited.  Meanwhile, the number of references to food overall might increase
+or decrease, depending on the balance of these factors.
+
+More generally, we are suggesting that, even though workers are not instructed
+to compare tasks in any way, prior tasks form a context relative to which
+workers judge salience.  Thus, due to a combination of negative and positive
+priming, a worker's focus in repeated tasks tends to be directed away from
+generic, shared features, toward specific and distinguishing ones.
+
+\begin{figure}[h]
 	\centering
@@
 
-To better understand the nature of 
-intertask effects, we investigated the vocabulary
-that workers used to label test tasks. One might expect that, within a given 
-experiment, those workers exposed to food (whether through framing or initial
-tasks) would label test tasks using 
-food-related words more often.  However, this was not generally 
-the case. In \textit{intertask-food-culture}, food-exposed
-workers actually used significantly \textit{fewer} food-related words 
-during test tasks\footnote{
-	food-related words were identified using the wordnet corpus, 
-	augmented with additional words obtained by crawling a recipe website 
-	(see supplementary text for details).
-} (Fig.~\ref{fig:specificity}A).  This finding
-rules out a seemingly-simple idea that workers emphasize
-content that has been present in earlier tasks: seeing content 
-influences, but does not necessarily \textit{increase}, the probability of 
-referring to it in subsequent tasks.
-
-To deepen our understanding, we investigated workers' lexical richness in 
-reference to food, that is, the number of \textit{unique} food-related words
-used.  Even if workers provide an abundance of food-related words, there
-can be less diversity, if, for example, workers repeat generic references 
-to food.
-Both \textit{intertask} experiments showed that food-exposed workers had 
-greater lexical richness, in reference to food, than their counterparts 
-(as much as 20\% more) (Fig.~\ref{fig:specificity}B).  
-This is particularly noteworthy in the experiment
-\textit{intertask-food-culture}, because there,
-food-primed workers made fewer total references to food.  
-%We also observed enrichment of the food-related lexicon in the 
-%\textit{priming-food-objects}, and \textit{echo-food-objects} experiments, 
-%although to a lesser extent.
-
-The observations regarding lexical richness suggest that 
-initial tasks might influence workers to use more refined or specialized 
-words, when referring to aspects of content that had been present in the 
+\section{Discussion}
+
+Prior to this study, little thought appears to have been given to earlier tasks
+as a priming vector for later tasks.  But our findings show this is an
+important design consideration.
+
+Our most urgent discovery is that a severe bias can be introduced into
+microtask responses, simply from the performance of earlier tasks.  These
+effects are much stronger than those of framing. This result impacts a
+staggering number of crowdsourcing studies that have been, are currently being,
+and will be done.  One approach to minimizing bias could be to randomize task
+ordering. This is, in fact, common practice among the crowd sourcing
+community already.  Our results, however, indicate that this is an unreliable fix
+at best: the sheer magnitude of bias we observed suggests that random ordering
+can still admit a significant amount of noise.  Even chains of two or three
+similar tasks, which will not be reliably eliminated in random permutations,
+could lead to levels of bias like those we observed in our experiments.
+Preferably, a deeper understanding of intertask effects might allow them to be
+properly controlled.
+
+If controlled in the right way, our findings actually suggest that careful task
+engineering might be able to leverage intertask effects to achieve higher 
+quality and greater reproducibility in crowdsourcing tasks.  A consistent goal
+in human computation is the achievement of expert-level judgments from
+non-expert workers \cite{kittur2011crowdforge}.  This has been achieved in some
+applications \cite{snow2008cheap,Mortensen20131020,Warby2014385}.  The
+distinction between experts and novices is partly attributable to specialized
+knowledge and heuristics.  But experts also simplify tasks by more efficiently
+directing their focus toward salient features \cite{kellman2009perceptual}.
+Our discovery that inter-task effects can produce levels of specificity in
+labels indicate that, using strategic task exposure, it might be possible to
+guide workers' focus and salience attribution, enabling expert-level judgment
+in a wider variety of crowdsourced applications.  We anticipate future work
+will yield techniques to control intertask effects, to reduce unwanted bias,
+and to tune the focus, diversity, and specificity of worker responses.
+
+Fundamentally, while our findings raise serious concerns about the current
+state of microtask design, they also reveal potential opportunities to refine
+worker focus and acuity.  Any application that relies on the repetitive use of
+human judgment is likely subject to the phenomena described here.  Exploring
+the pitfalls and opportunities posed by intertask effects is an important
+direction for future work, in the effort to develop more performant and
+reliable human computation systems.
+
+\begin{materials}
+
+\section{Microtask setup} The work presented in the main text consisted of six
+experiments involving HITs (bundles of tasks) performed on Amazon's Mechanical
+Turk (MTurk) platform.  The flow of events experienced by a worker when
+participating in this study is depicted in Fig.~S\ref{fig:task_schematic}.
+Each experiment was divided into two treatments.  Treatments for a given
+experiment differed with respect to a particular priming modality, which served
+as the independent variable (as specified in Table~S\ref{table:experiments}).
+The HITs for treatments of the same experiment always involved the same test
+tasks (the last five tasks in the HIT), the results of which served as the
+dependent variable.
+
+All HITs were presented as a series of slides.  The first slide consisted of a
+brief set of instructions.  For HITs that included framing, a framing statement
+was shown on a slide immediately after the instructions (Fig.
+S\ref{fig:hit_preamble}B and C).  Initial tasks, when included, followed next.
+The initial tasks consisted of a series of five slides, each containing an
+image-labeling task like the one shown in Fig.~S\ref{fig:hit_preamble}D.
+Finally, for all HITs, five slides were shown containing test tasks, in the
+same format as the initial tasks.
+
+Workers were randomly assigned to the treatments, and a given worker could only
+complete one HIT related to this study.  In \textit{intertask-food-culture},
+the \textit{food} and \textit{culture} treatments were both divided into five
+sub-treatments, in which the test tasks were permuted.  The permutations were
+obtained by rotating the order shown in Fig.~S\ref{fig:task1:test} by different
+amounts.  For example, rotating by one position involves moving the first image
+to the second position, the second image to the third position, and so on, and
+moving the last image to the first position.  The five different possible
+rotations were used for the five sub-treatments.  This enabled us to study the
+effects on each image when it occurred in different positions relative to the
 initial tasks.
-To test this, we used the wordnet corpus to operationalize the 
-notion of word specialization.  Wordnet establishes relationships between
-117,798 English nouns, indicating which words are specializations
-(or generalizations) of others \cite{felbaum1998wordnet}. 
-%miller1995wordnet,}.  
-For example, ``pumpernickel'' is a specialization of ``bread''.
-Within each experiment, we determined the percent-excess of food-related
-words that were more specialized in the food-exposed treatment relative
-to the other treatment (detailed calculation in the supplementary text).
-
-In all experiments except \textit{frame-food-culture}, food-primed workers 
-used significantly more specialized words, in reference to food 
-(about 15\% more) (Fig.~\ref{fig:specificity}C).
-It is interesting that such substantial increases in both the lexical 
-richness and specialization of food-related words 
-held for \textit{intertask-food-culture}, where, as mentioned, we observed 
-that food-exposed workers made \textit{fewer} references to food overall. 
-These observations point 
-to countervailing factors: one factor tending to activate the more 
-specialized and less common food-related words 
-(yielding greater lexical richness and specialization), and the other tending 
-to suppress certain, presumably more common and generic words 
-(yielding fewer food-related words in total).
-
-This hypothesis is corroborated when we look at those words whose 
-frequencies changed the most from one treatment to another 
-(Table~S\ref{table:top-words}).  
-The word ``food'', which is the most generic possible food-related word, was 
-always \textit{suppressed} among food-primed workers.  In fact, 
-for all experiments, ``food'' was the \textit{most suppressed} word.
-
-Our results can be 
-explained through a combination of positive and negative priming.
-Positive priming (usually simply ``priming'') occurs when a prior stimulus 
-predisposes a person to give certain responses in an ensuing task, and
-is often observed as an increase in the speed or accuracy of a response, or
-the ability to recognize briefer or noisier stimuli 
-\cite{BJOP1796,BJOP1826,Huber2008324}.
-Negative priming occurs when, after exposure to a stimulus 
-considered to be non-salient, subsequent recognition of the stimulus is 
-inhibited \cite{mayr2007negative}.
-
-Workers exposed to images containing food are (positively) primed, 
-activating memories, concepts, and vocabulary related to food.  
-However, if the worker labels several images containing food, the basic 
-fact that an image contains food will not seem salient, since it 
-does not distinguish one image from another.  Thus, the most 
-generic references to that fact, such as the label ``food'', 
-will be suppressed, while more specialized references will be elicited.  
-Meanwhile, the number of references to food overall might increase or 
-decrease, depending on the balance of these factors.
-
-More generally, we are suggesting that, even though workers are not 
-instructed to compare tasks in any way, prior tasks form a 
-context relative to which workers judge salience.  Thus, due to a combination 
-of negative and positive priming, a worker's focus 
-in repeated tasks tends to be directed away from generic, shared features, 
-toward specific and distinguishing ones.
-
-Prior to this study, little thought appears to have been given to
-earlier tasks as a priming vector for later tasks.
-But our findings show this is an important design consideration.  
-One recourse might be to randomize task ordering, a practice that is 
-commonly employed.  But the sheer extent of bias we observed suggests that 
-this will still admit a significant amount of noise.  
-Even chains of two or three similar tasks, which
-will not be reliably eliminated in random permutations, could lead
-to the levels of bias we observed in our experiments.
-Preferably, a deeper understanding of intertask effects might allow them
-to be properly controlled.
-
-Our findings also suggest that careful task engineering might leverage
-intertask effects to achieve greater quality and reproducibility in 
-crowdsourcing.
-A consistent goal in human computation is the achievement of expert-level
-judgments from non-expert workers \cite{kittur2011crowdforge}.  
-This has been achieved in some
-applications \cite{snow2008cheap,Mortensen20131020,Warby2014385}. 
-The distinction between experts and novices is partly attributable
-to specialized knowledge and heuristics. 
-But experts also simplify tasks by more efficiently directing 
-their focus toward salient features \cite{kellman2009perceptual}.  
-Using strategic task exposure, it might be possible to guide workers' focus 
-and salience attribution, enabling expert-level judgment in a wider variety of
-crowdsourced applications.
-We anticipate future work will yield techniques to control intertask 
-effects, to reduce unwanted bias, and to tune the focus, diversity, and 
-specificity of worker responses.
-
-We have shown that a severe bias can be introduced into microtask 
-responses, simply from the performance of earlier tasks. 
-These effects are much stronger than those of framing.  
-While our findings raise serious concerns about the 
-current state of microtask design, they reveal potential opportunities 
-to refine worker focus and acuity.  Any application that relies
-on the repetitive use of human judgment is likely subject to the phenomena
-described here.  Exploring the pitfalls and opportunities posed by
-intertask effects is an important direction for future work, 
-in the effort to develop performant and reliable human computation.
-\bibliography{newbib}
-\bibliographystyle{Science}
-
-\pagebreak
-\section*{Supplementary Material}
-\renewcommand{\figurename}{Figure S\!\!}
-\renewcommand{\tablename}{Table S\!\!}
-\renewcommand{\theequation}{S\arabic{equation}}
-\setcounter{figure}{0}
-\setcounter{table}{0}
-\setcounter{equation}{0}
-
-Microtask platforms are an increasingly popular way to solicit experimental
-participants, as well as to annotate large datasets and obtain other 
-judgments which are difficult to automate using only a computer.  
-Due to the popularity of microtask platforms, there is interest in 
-understanding how various task design factors
-influence the reliabality of data obtained using microtask platforms.  
-Since workers typically perform similar tasks in quick succession, there is
-an opportunity for earlier tasks to effectively prime workers, and induce 
-bias in the results obtained.
-Here we describe in detail experiments presented in the main text, in which
-we investigate the effect that prior tasks have on the responses given during
-subsequent ones.
-
-\subsection*{Materials and Methods}
-
-\paragraph{Microtask setup.}
-
-The work presented in the main text consisted of six experiments involving
-HITs (bundles of tasks) performed on Amazon's Mechanical Turk (MTurk)
-platform.  
-The flow of events experienced by a worker when participating in this study 
-is depicted in Fig.~S\ref{fig:task_schematic}.  
-Each experiment was divided into two treatments.  Treatments for a given 
-experiment differed with respect to a particular priming modality, which 
-served as the independent variable
-(as specified in Table~S\ref{table:experiments}).  
-The HITs for treatments of the same experiment always involved the same
-test tasks (the last five tasks in the HIT),
-the results of which served as the dependent variable.
-\begin{figure}
-	\begin{center}
-	\includegraphics[scale=0.8]{figs/task_schematic.pdf}
-	\caption{Flow of events as experienced by a worker participating in
-		our study.  Steps with a dash outlined are only performed by 
-		workers assigned to certain treatments 
-		(see Table~S\ref{table:experiments}).  Steps outlined in orange are
-		part of MTurk's interface, and are common to any 
-		microtask performed on that platform.  Steps outlined in black are
-		specific to our HIT.
-	}
-	\label{fig:task_schematic}
-	\end{center}
-\end{figure}
-
-All HITs were presented as a series of slides.  The first 
-slide consisted of a brief set of instructions.  For HITs that included 
-framing, a framing statement was shown on a slide immediately after the 
-instructions (Fig. S\ref{fig:hit_preamble}B and C).  
-Initial tasks, when included, followed next.  The initial tasks consisted of 
-a series of five slides, each containing an image-labeling task like the one 
-shown in 
-Fig.~S\ref{fig:hit_preamble}D.  Finally, for all HITs, five slides were shown
-containing test tasks, in the same format as the initial tasks.
-
-\begin{table}
-\centering
-\setlength{\tabcolsep}{2pt}
-\begin{tabular}{c c c c c c}
-\toprule
-Experiment & \parbox[c]{3.8cm}{\centering{Priming modality}} & Treatment & Frame & 
-	Initial tasks & \parbox[c]{2.0cm}{\centering{Test tasks}} \\
-\midrule
-\multirow{2}{*}{\textit{intertask-food-objects}} 
-& \multirow{2}{*}{initial tasks} & \textit{food} & none 
-	& Fig.~S\ref{fig:task1:food} 
-	& \multirow{2}{*}{Fig.~S\ref{fig:task1:test}\textsuperscript{g}} \\
-& & \textit{objects} & none & Fig.~S\ref{fig:task1:obj} & \\
-
-\noalign{\smallskip}
-\hdashline
-\noalign{\smallskip}
-
-\multirow{2}{*}{\textit{frame-food-objects}} 
-& \multirow{2}{*}{framing} & \textit{food} 
-	& ``food''\textsuperscript{a}
-	& none & \multirow{2}{*}{Fig.~S\ref{fig:task1:test}} \\
-& & \textit{objects} 
-	& ``objects''\textsuperscript{b}
-	& none & \\
-
-\noalign{\smallskip}
-\hdashline
-\noalign{\smallskip}
-
-\multirow{2}{*}{\textit{echo-food-objects}} 
-& \multirow{2}{*}{echoed framing} & \textit{food} 
-	& ``food''\textsuperscript{c}
-	& none & \multirow{2}{*}{Fig.~S\ref{fig:task1:test}} \\
-& & \textit{objects} 
-	& ``objects''\textsuperscript{d}
-	& none & \\
-
-\noalign{\smallskip}
-\hdashline
-\noalign{\smallskip}
-
-\multirow{2}{*}{\textit{intertask-food-culture}} 
-& \multirow{2}{*}{initial tasks} & \textit{food} 
-	& none
-	& Fig.~S\ref{fig:task2:food} 
-	& \multirow{2}{*}{Fig.~S\ref{fig:task2:test}} \\
-& & \textit{culture} 
-	& none & Fig.~S\ref{fig:task2:cult} & \\
-
-\noalign{\smallskip}
-\hdashline
-\noalign{\smallskip}
-
-\multirow{2}{*}{\textit{frame-food-culture}} 
-& \multirow{2}{*}{framing} & \textit{food} 
-	& ``food''\textsuperscript{e}
-	& Fig.~S\ref{fig:frame2:ingr} 
-	& \multirow{2}{*}{Fig.~S\ref{fig:task2:test}} \\
-& & \textit{culture} 
-	& ``culture''\textsuperscript{f} 
-	& Fig.~S\ref{fig:frame2:ingr} & \\
-
-\bottomrule
-\end{tabular}
-\caption{
-	Description of experiments performed.  Each experiment had two treatments
-	which differed either in the initial tasks shown or the framing used 
-	(the priming modality).  
-	During echoed framing, the worker had to respond to the framing language
-	using a combo box input (Fig.~S\ref{fig:hit_preamble}C).
-	\newline\textsuperscript{a} ``Funded by the laboratory for the visual 
-		perception of Food and Ingredients''
-	\newline\textsuperscript{b} ``Funded by the laboratory for the visual 
-		perception of Objects and Tools''
-	\newline\textsuperscript{c} ``The purpose of this study is to understand the visual perception of Food and Ingredients''
-	\newline\textsuperscript{d} ``The purpose of this study is to understand the visual perception of Objects and Tools''
-	\newline\textsuperscript{e} ``This research is proudly funded by The National 
-		Foundation for Nutritional Awareness''
-	\newline\textsuperscript{f} ``This research is proudly funded by The Global 
-		Foundation for the Recognition of Cultures''
-	\newline\textsuperscript{g} Both treatments were divided into five 
-	sub-treatments having a different permutation of test tasks.
-}
-\label{table:experiments}
-\end{table}
-
-\begin{figure}
-	\includegraphics[scale=0.8]{figs/tasks.jpg}
-	\caption{Examples of (A) task instructions, (B) a framing slide
-		(C) an echoed framing slide, and (D) an image-labeling 
-		task.
-	}
-	\label{fig:hit_preamble}
-\end{figure}
-Workers were randomly assigned to the treatments, and 
-a given worker could only complete one HIT related to this study.  
-In \textit{intertask-food-culture}, the \textit{food} and \textit{culture}
-treatments were both divided into five sub-treatments, 
-in which the test tasks were permuted.  
-The permutations were obtained by rotating 
-the order shown in Fig.~S\ref{fig:task1:test} by different amounts. 
-For example, rotating by one position involves moving the first image to the 
-second position, the second image to the third position, and so on, and 
-moving the last image to the first position.  
-The five different possible rotations were used for the five 
-sub-treatments.  This enabled us to study the effects on each image when
-it occurred in different positions relative to the initial tasks.
-
-\paragraph{Selection of images.}
-
-The images used in the initial tasks for \textit{intertask-food-objects}  
-are shown in Figs.~S\ref{fig:task1:food} (\textit{food} treatment) and 
-S\ref{fig:task1:obj} (\textit{objects} treatment).
-We took care to exclude objects from
-the food-images (except for the dish supporting the food in some cases), and 
-to exclude food from the object-images.  The images used for the test tasks
-of \textit{intertask-food-objects} and \textit{frame-food-objects} are shown 
-in Fig.~S\ref{fig:task1:test}.
-
-The images used in the initial tasks
-for \textit{intertask-food-culture} are shown in Figs.~S\ref{fig:task2:food} 
-(\textit{food} treatment) and S\ref{fig:task2:cult} 
-(\textit{culture} treatment).
-We selected the initial images for the treatments of this experiment to 
-respectively reflect depict food and culture.
-Naturally, since food is a very
-important aspect of culture, pictorial depictions of the two concepts 
-cannot be cleanly separated,
-and images depicting food inevitably also depict culture.
-However, the fact that the images for the initial tasks in the 
-\textit{food} treatment 
-of \textit{intertask-food-culture} also depict culture
-will only tend to make the \textit{food} and \textit{culture}
-treatments more similar. 
-This would tend to reduce the severity of intertask 
-effects, but we nevertheless still observed strong intertask effects.
-Thus, the presence of culture in the food-related initial images of 
-\textit{intertask-food-culture} does not seem to have been problematic.
-The images used in the test tasks of \textit{intertask-food-culture} and
-\textit{frame-food-culture} are shown in Fig.~S\ref{fig:task2:test}.
-
-\begin{figure}
-	\begin{center}
-	\includegraphics{figs/task1-food.jpg}
-	\end{center}
-	\caption{
-		Images used in the initial tasks for the
-		\textit{food} treatment of \textit{intertask-food-objects}.  
-		The numbers show the order in which the 
-		images were presented to workers.
-	}
-	\label{fig:task1:food}
-\end{figure}
-
-\begin{figure}
-	\begin{center}
-	\includegraphics{figs/task1-obj.jpg}
-	\end{center}
-	\caption{
-		Images used in the initial tasks for the
-		\textit{objects} treatment of \textit{intertask-food-objects}.  
-		The numbers show the order in which the images were presented to 
-		workers.
-	}
-	\label{fig:task1:obj}
-\end{figure}
-
-\begin{figure}
-	\begin{center}
-	\includegraphics{figs/task1-test.jpg}
-	\end{center}
-	\caption{
-		Images used in the test tasks for \textit{intertask-food-objects}
-		and \textit{frame-food-objects}.  
-		The numbers show the order in which the 
-		images were presented to workers in \textit{frame-food-objects};
-		in \textit{intertask-food-objects}, five different orderings were
-		used, which can be obtained by taking the numbers shown, $n$,
-		and replacing them by $n + c \bmod 5$ for $c$ running from 0 to 4.
-	}
-	\label{fig:task1:test}
-\end{figure}
-
-\begin{figure}
-	\begin{center}
-	\includegraphics{figs/task2-food.jpg}
-	\end{center}
-	\caption{
-		Images used in the initial tasks for the
-		\textit{food} treatment of \textit{intertask-food-culture}.  
-		The numbers show the order in which the 
-		images were presented to workers.
-	}
-	\label{fig:task2:food}
-\end{figure}
-
-\begin{figure}
-	\begin{center}
-	\includegraphics{figs/task2-cult.jpg}
-	\end{center}
-	\caption{
-		Images used in the initial tasks for the
-		\textit{culture} treatment of \textit{intertask-food-culture}.  
-		The numbers show the order in which the 
-		images were presented to workers.
-	}
-	\label{fig:task2:cult}
-\end{figure}
-
-\begin{figure}
-	\begin{center}
-	\includegraphics{figs/task2-test.jpg}
-	\end{center}
-	\caption{
-		Images used in the test tasks for \textit{intertask-food-culture} 
-		and \textit{frame-food-culture}.  
-		The numbers show the order in which the 
-		images were presented to workers.
-	}
-	\label{fig:task2:test}
-\end{figure}
-
-\begin{figure}
-	\begin{center}
-		\includegraphics{figs/task2-ingr.jpg}
-	\end{center}
-	\caption{
-		Images used in initial tasks for \textit{frame-food-culture} 
-		(both for the \textit{food} and \textit{culture} treatments).
-		The numbers show the order in which the images were presented to 
-		workers.
-	}
-	\label{fig:frame2:ingr}
-\end{figure}
-
-\paragraph{Framing.}
-We framed tasks by including a message, near the beginning of the HIT, that 
-suggested a particular purpose for the tasks.
-The precise language used is shown in 
-Table~S\ref{table:experiments}, and an example of a framing slide is shown in
-Fig.~S\ref{fig:hit_preamble}B and C.  In \textit{frame-food-objects}
-and \textit{frame-food-culture}, the framing language was based on
-naming the (fictitious) entity running the study, for example
-``The Global Foundation for the Recognition of Cultures'',
-or ``Laboratory for the visual perception of Objects and Tools''.
-In \textit{echo-food-objects}, we stated the purpose explicitly 
-(``The purpose of this task is \dots''), and then required the worker to
-echo back the purpose of the task by selecting it from a combo box
-Fig.~S\ref{fig:hit_preamble}C.
+
+\section{Selection of images} The images used in the initial tasks for
+\textit{intertask-food-objects}  are shown in Figs.~S\ref{fig:task1:food}
+(\textit{food} treatment) and S\ref{fig:task1:obj} (\textit{objects}
+treatment).  We took care to exclude objects from the food-images (except for
+the dish supporting the food in some cases), and to exclude food from the
+object-images.  The images used for the test tasks of
+\textit{intertask-food-objects} and \textit{frame-food-objects} are shown in
+Fig.~S\ref{fig:task1:test}.
+
+The images used in the initial tasks for \textit{intertask-food-culture} are
+shown in Figs.~S\ref{fig:task2:food} (\textit{food} treatment) and
+S\ref{fig:task2:cult} (\textit{culture} treatment).  We selected the initial
+images for the treatments of this experiment to respectively reflect depict
+food and culture.  Naturally, since food is a very important aspect of culture,
+pictorial depictions of the two concepts cannot be cleanly separated, and
+images depicting food inevitably also depict culture.  However, the fact that
+the images for the initial tasks in the \textit{food} treatment of
+\textit{intertask-food-culture} also depict culture will only tend to make the
+\textit{food} and \textit{culture} treatments more similar.  This would tend to
+reduce the severity of intertask effects, but we nevertheless still observed
+strong intertask effects.  Thus, the presence of culture in the food-related
+initial images of \textit{intertask-food-culture} does not seem to have been
+problematic.  The images used in the test tasks of
+\textit{intertask-food-culture} and \textit{frame-food-culture} are shown in
+Fig.~S\ref{fig:task2:test}.
+
+\section{Framing} We framed tasks by including a message, near the beginning
+of the HIT, that suggested a particular purpose for the tasks.  The precise
+language used is shown in Table~S\ref{table:experiments}, and an example of a
+framing slide is shown in Fig.~S\ref{fig:hit_preamble}B and C.  In
+\textit{frame-food-objects} and \textit{frame-food-culture}, the framing
+language was based on naming the (fictitious) entity running the study, for
+example ``The Global Foundation for the Recognition of Cultures'', or
+``Laboratory for the visual perception of Objects and Tools''.  In
+\textit{echo-food-objects}, we stated the purpose explicitly (``The purpose of
+this task is \dots''), and then required the worker to echo back the purpose of
+the task by selecting it from a combo box Fig.~S\ref{fig:hit_preamble}C.
 
@@
 initial tasks constant while varying the framing language), since the worker
-would be ``warmed up'' before performing the test tasks, as is the case for
-the experiments investigating the effect of initial tasks. 
-We therefore adopted this approach in the experiment 
-\textit{frame-food-culture}, in which workers performed the same 
-initial tasks containing images that depicted food in both the \textit{food}
-and \textit{culture} treatments.  It would seem that the framing effect in 
-\textit{frame-food-culture} was reduced by the initial tasks, possibly because
-intertask effects tend to override framing. Further experimentation 
-would be necessary to be sure, but this was not the purpose of our study.
-
-\subsection*{MTurk's task composition}
-
-\begin{table}
-\centering
-\begin{tabular}{l c c}
-\toprule
-Task Type & Number Seen & Fraction of total (\%) \\
-\toprule
-Image transcription & 57 & 28.5 \\
-Information gathering & 46 & 23.0 \\
-Image tagging and classification & 36 & 18.0 \\
-Copy writing and editing & 18 & 9.0 \\
-Text tagging and classification & 15 & 7.5 \\
-Audio/Video transcription & 12 & 6.0 \\
-Survey & 9 & 4.5 \\
-Unknown & 7 & 3.5 \\
-\bottomrule
-\end{tabular}
-\caption{
-	Frequency of various broad task types seen among the 200 most 
-	recently posted tasks on MTurk, accessed on 12 February, 2015.
-}
-\label{table:task_composition}
-\end{table}
-Image labeling tasks are one of the most often cited kinds of tasks in the
-literature.  To determine whether they do indeed reflect an important fraction
-of MTurk tasks, we accessed MTurk on 12 February, 2015, and coded the 200 
-most recently posted tasks based on their title and description, 
-into one of seven categories.
-
-Tasks relating to image tagging and categorization represented 18\% of the 
-total.  Of all tasks seen, those in which images are the primary input
-account for 46.5\%.  Considering tasks regardless of input modality (e.g.
-text, image, audio, or multimedia), those that involved some kind of tagging
-or categorization accounted for 25.5\%.  
-The detailed counts for our categorization
-of task types are shown in Table~S\ref{table:task_composition}.  
-While this does not reflect a full and
-a systematic characterization of MTurk task composition, it does support our
-choice of image labeling as a representative microtask.
-
-\subsection*{Testing for intertask and framing effects using $\chi^2$}
-
-\begin{table}
-\centering
-\begin{tabular}{c c c c}
-\toprule
-Experiment & Degrees of freedom & $\chi^2$ & $p$-value\\
-\toprule
-\textit{intertask-food-objects} & 117 & 268.7 & $6.0 \times 10^{-14}$\\
-\textit{frame-food-objects} & 116 & 167.8 & $1.2 \times 10^{-3}$\\
-\textit{echo-food-objects} & 126 & 381.3 & $1.7 \times 10^{-27}$\\
-\textit{intertask-food-culture} & 120 & 447.5 & $2.8 \times 10^{-39}$\\
-\textit{frame-food-culture} & 119 & 127.2 & $0.29$\\
-\bottomrule
-\end{tabular}
-\caption{
-	Results for Pearson's $\chi^2$ test of homogeneity of the word-frequencies
-	between treatments from each experiment.  This shows that the treatments
-	significantly affected word usage, 
-	except in the case of \textit{frame-food-culture}.
-}
-\label{table:chi2}
-\end{table}
-
-\begin{table}
-\centering
-\begin{tabular}{c c c c c}
-\toprule
-Experiment & Treatment & Degrees of freedom & $\chi^2$ & $p$-value\\
-\toprule
-\noalign{\smallskip}
-\multirow{2}{*}{\textit{intertask-food-objects}} & \textit{food} & 65 & 39.0 & $1.0$\\
- & \textit{objects} & 65 & 53.2 & $0.85$\\
-
-\noalign{\smallskip}
-\hdashline
-\noalign{\smallskip}
-
-\multirow{2}{*}{\textit{frame-food-objects}} & \textit{food} & 67 & 41.3 & $0.99$\\
- & \textit{objects} & 62 & 66.9 & $0.31$\\
-
-\noalign{\smallskip}
-\hdashline
-\noalign{\smallskip}
-
-\multirow{2}{*}{\textit{echo-food-objects}} & \textit{food} & 66 & 40.9 & $0.99$\\
- & \textit{objects} & 66 & 35.6 & $1.0$\\
-
-\noalign{\smallskip}
-\hdashline
-\noalign{\smallskip}
-
-\multirow{2}{*}{\textit{intertask-food-culture}} & \textit{food} & 62 & 65.9 & $0.34$\\
- & \textit{culture} & 68 & 57.2 & $0.82$\\
-
-\noalign{\smallskip}
-\hdashline
-\noalign{\smallskip}
-
-\multirow{2}{*}{\textit{frame-food-culture}} & \textit{food} & 57 & 49.6 & $0.75$\\
- & \textit{culture} & 64 & 55.1 & $0.78$\\
-
-\bottomrule
-\end{tabular}
-\caption{
-	Results for Pearson's $\chi^2$ test of homogeneity of the word-frequencies
-	within treatments, which were randomly partitioned for the test.  This
-	shows that word-usage within treatments is homogeneous.
-}
-\label{table:chi2_within}
-\end{table}
-
-To test whether intertask and framing effects induced statistically 
-significant changes in word frequencies, we assembled a contingency table
-for each experiment, containing the frequencies of words in each treatment.  
-Any words appearing less than ten times for
-an experiment (i.e. one whose expected frequency would be less than five in a 
-given cell of the contingency table)
-were lumped together into a separate `OTHER' category, to ensure validity
-of the test.  The degrees of freedom, test statistic, and $p$-values were
-then calculated according to Pearson's $\chi^2$ test, using 
-Yates' correction.  Results are tabulated in Table~S\ref{table:chi2}.
-With the exception of \textit{frame-food-culture}, all experiments showed 
-significant changes in word-frequencies in response
-to the task or framing exposures, at $\alpha=0.05$, leading us to 
-reject the null hypothesis that the priming exposures had no effect.
-
-The use of Pearson's $\chi^2$ test has been criticized in linguistic 
-applications, due to the finding that many corpora are not themselves
-homogeneous \cite{kilgarriff1996comparing}.  
-This results from the fact that corpora are made of many
-distinct texts, together with the fact that words tend to come in bursts.
-When a rare word is encountered in a given text, it is much more likely
-to be encountered again in the same text. This means that
-frequencies within given texts are often far from the average, causing 
-corpora to be heterogeneous.
-As a result, if a corpus is randomly split, putting half of the texts in one 
-set, and half in another, there can be a significant non-homogeneity between 
-the halves (when tested using Pearson's $\chi^2$ test).  Thus, finding two
-corpora to be different according to a $\chi^2$ test might not 
-indicate that they are meaningfully different.
-
-This concern does not apply to our case, because the ``texts'' are 
-individual responses from workers, which will not, in general, be subject to 
-the ``burstiness'' phenomenon.  Nevertheless, to test this, we randomly 
-divided the workers from each experimental treatment into two sets, and 
-tested the homogeneity 
-between these sets.  Results are tabulated in Table~S\ref{table:chi2_within}, 
-and show that treatments 
-\textit{are} homogeneous.  Thus, the lack of homogeneity \textit{between} 
-the treatments of given experiments can be rightly attributed to the 
-framing and intertask effects.
-
-\subsection*{Measuring the extent of intertask and framing effects}
-
-\paragraph{Comparing $\theta$ and $\chi^2$.}
-The following is an illustrative example to show why it is important to 
-have a measure of effect size, like $\theta$, in addition to a test of the 
-null hypothesis like $\chi^2$.
-Suppose that we have a very slightly unfairly weighted coin, which turns
-up heads ($X=\mathbf{H}$) more often than expected by one part in one hundred:
-$\Pr\{X=\mathbf{H}\} = 0.501$. Such a coin is only mildly biased, and would 
-be fine for many purposes.  If we did not know that the coin was
-biased, we could determine whether it was biased by flipping the coin in 
-question, along with a coin we know to be fair, many times 
-(say 100 million times), and then use a $\chi^2$ test to decide whether 
-the two coins have the same probability of turning up heads.
-Simulating this with a random number generator yields the results shown
-in Table~S\ref{table:coin}.  Results from a $\chi^2$ test of the
-hypothesis that the two coins have the same probability of turning up heads 
-is shown in Table~S\ref{table:coin_stats}.
-
-\setlength{\floatsep}{30pt plus 1.0pt minus 2.0pt}
-
-\begin{table}
-\centering
-\begin{tabular}{c c c c}
-\toprule
-coin & $N_\mathbf{H}$ & $N_{\mathbf{T}}$ & total \\
-\toprule
-\textit{fair} & 50002283 & 49997717 & $10^8$\\
-\textit{biased} & 50101115 & 49898885 & $10^8$ \\
-\bottomrule
-total & 100103398 & 99896602 & $2\times 10^8$ \\
-\bottomrule
-\end{tabular}
-\caption{
-	Simulated counts of heads ($N_\mathbf{H}$) and tails ($N_\mathbf{T}$)
-	occurrences, for a fair coin, and a coin biased to have a probability
-	of turning up heads of 0.501.
-}
-\label{table:coin}
-\end{table}
-
-\begin{table}
-\centering
-	\begin{tabular}{c c c c }
-	\toprule
-	Degrees of freedom & $\chi^2$ & $p$-value \\
-	\toprule
-	1 & 195.4 & $2.2 \times 10^{-44}$ \\
-	\bottomrule
-	\end{tabular}
-\caption{
-	Statistics for a $\chi^2$ test of the hypothesis that a fair and 
-	unfair coin have the same probability of turning up heads.  
-	The result overwhelmingly favors rejection of the hypothesis, even
-	though the coins differ only slightly.
-}
-\label{table:coin_stats}
-\end{table}
-
-Even though the $\chi^2$ test shows, with tremendous statistical 
-significance, that the unfair coin is indeed unfair, we know that actual 
-extent of bias is small, 
-$\theta = \frac{1}{2}\left( |0.501 - 0.499| + |0.499 - 0.501| \right) = 0.002$.
-This demonstrates how a sufficiently large sample size will lead to the 
-detection an arbitrarily 
-small bias with arbitrarily high statistical significance. 
-This is why, to measure the practical significance of intertask effects,
-we rely on a measure of effect size, which is in this case a measure
-of statistical divergence, $\theta$.
-
-\paragraph{Statistical approaches to measuring bias.}
-Recall that Eq.~\ref{eq:theta} in the main text defined the
-extent of bias between the microtask responses from two groups
-of workers to be $\theta$ (reproduced here):
-\begin{equation}
-	\theta = \frac{1}{2}\sum_{x \in X} \left| p_0(x) - p_1(x) \right|,
-\end{equation}
-where $p_0(x)$ and $p_1(x)$ represent the probability that a worker from
-treatment 1 (respectively 2) produces response $x$, from a set of possible
-responses $X$.  As defined, $\theta$ corresponds to a measure of divergence 
-between $p_0$ and $p_1$, called the \textit{total variation distance} or the
-\textit{L1-distance}.
-
-Measuring the \textit{L1-distance} between two probability distributions,
-given only samples, is difficult.  The na\"ive approach is to take
-the maximum likelihood estimate of $p(x)$, which sets it equal to the 
-frequency with which the response $x$ has been observed, 
-$\hat{p}(x) = \frac{N_x}{N}$, and then estimate $\theta$ 
-using these frequencies\cite{batu2013testing}: 
-$\hat{\theta} = \sum_{x \in X}|\hat{p}_1(x) - \hat{p}_2(x)|$.  
-However, this method tends to drastically overestimate $\theta$
-\cite{val-thesis}.
-Recently there has been theoretical progress on this problem.
-An estimator of L1-distance, and tests of whether the L1-distance is
-greater than a specified threshold, have been proposed 
-\cite{val-thesis,batu2013testing,chan2014optimal}.  
-These methods have excellent theoretical convergence guarantees, but
-cannot easily be used to establish estimates with confidence intervals or 
-perform hypothesis tests for fixed sample size and significance level.  
-We therefore turn to an alternative approach using machine learning. 
-While this method yields an estimator that converges more slowly,
-it is straightforward to establish confidence intervals and 
-use the estimator in hypothesis tests.
-
-\paragraph{The relationship of bias and classifier accuracy.}
-We will now show that, any classifier algorithm, $\mathcal{A}$, that
-takes the response, $x$, of a worker, and guesses the population to which
-the worker belongs ($P_0$ or $P_1$), will do so with an accuracy, $\eta$,
-that is bounded according to Eq.~\ref{l1} from the main text 
-(reproduced here):
-\begin{equation}
-	\theta \geq 2\eta - 1.
-	\label{eq:sup:l1}
-\end{equation}
-
-To do so, we will first formalize $\eta$ by defining a 
-\textit{validation test}.  In a validation test, a uniform random bit 
-$z\in\{0,1\}$ is sampled, and then, according to the value of $z$, the
-response of a worker, $x$, is sampled uniformly randomly from $P_z$.  
-The algorithm is provided
-with $x$ and yields a \textit{guess}, $b=\mathcal{A}(x)$, as to whether the 
-worker was 
-from $P_0$ or $P_1$.  We shall denote such a validation test by 
-$V(P_0, P_1, \mathcal{A})$, and define the value of the test to be 1 if 
-$b=z$ and 0 otherwise.
-
-We then define the accuracy of classifier $\mathcal{A}$ to be $\eta$ according
-to:
-\begin{equation}
-\eta = \mathrm{E\{V(P_0, P_1, \mathcal{A})\}} 
-	= \mathrm{Pr}\{V(P_0, P_1, \mathcal{A})=1\}.
-\end{equation}
-
-To develop the relationship between $\eta$ and $\theta$, let us consider
-the accuracy $\eta^*$ of the best possible classifier $\mathcal{A}^*$.
-The best possible classifier will not in general have perfect accuracy:
-if the responses from workers in $P_0$ and $P_1$ are distributed 
-identically, then there is no hope of determining which population the worker 
-came from given only her response $x$.  But, assuming that responses are
-not distributed identically, then given some $x$, the best possible 
-classifier must always guess 1 whenever $p_1(x) > p_0(x)$ and guess 0 whenever
-$p_0(x) > p_1(x)$.
-
-Sacrificing, for a moment, some generality, let us assume that, for some give 
-$x'$, $p_1(x') > p_0(x')$.  
-When this $x'$ is encounterend in a validation test, the optimal classifier
-must guess $b = \arg\!\max_{z}(p_{z}(x'))$, which in this case is $b=1$.
-The probability that the classifier guesses correctly in this case is:
-\begin{align}
-	\begin{split}
-	\mathrm{Pr}\{V(P_0, P_1, \mathcal{A}^*) = 1 | x = x' \} 
-		&= \mathrm{Pr}\{z = \mathcal{A^*}(x) | x = x' \} \\
-		&= \mathrm{Pr}\{z = 1 | x = x' \}  \\
-		&= \frac{\mathrm{Pr}\{z = 1 , x = x'\}}
-			{ \mathrm{Pr}\{z=0 , x=x'\} + \mathrm{Pr}\{z=1 , x=x'\}} \\
-		&= \frac{p_1(x')}{p_0(x') + p_1(x')}.
-	\end{split}
-\end{align}
-And now, with full generally, for any $x'$, where $p_1(x')$ is not necessarily
-greater than $p_0(x')$:
-\begin{align}
-	\begin{split}
-		\mathrm{Pr}\{V(P_0,P_1,\mathcal{A}^*)=1 | x = x' \} 
-		&= \mathrm{Pr}\{z=\mathcal{A^*}(x)  | x' = x' \} \\
-		&= \mathrm{Pr}\{z = \arg\!\max_{z'}\big(p_{z'}(x)\big)| x = x' \}  \\
-		&= \frac{\max\big( p_0(x'),p_1(x') \big)}
-		{ p_0(x') + p_1(x') }.
-	\end{split}
-\end{align}
-Note that we can rewrite $\max\big(p_0(x'),p_1(x')\big)$:
-\begin{align}
-	\max\big(p_0(x'),p_1(x')\big) = \frac{1}{2}
-		\big(
-			p_0(x') + p_1(x') + |p_0(x') - p_1(x')|
-		\big),
-\end{align}
-so,
-\begin{align}
-	\mathrm{Pr}\{V(P_0,P_1,\mathcal{A}^*) = 1 | x = x' \} 
-	&= \frac{1}{2} + \frac{|p_0(x') - p_1(x')|}{2 \big(p_0(x') + p_1(x') \big)}.
-\end{align}
-Then, summing over all possible responses $X$, 
-the overall accuracy of the optimal classifier, $\mathcal{A^*}$, is:
-\begin{align}
-	\begin{split}
-	\eta^* &= \mathrm{Pr}\{V(P_0, P_1, \mathcal{A}^*)=1\} \\
-	&=\sum_{x'\in X} \mathrm{Pr}\{V(P_0,P_1,\mathcal{A}^*) = 1 | x = x' \} \mathrm{Pr}\{x = x'\}\\
-		&= \sum_{x'\in X} \left(
-				\frac{1}{2} + 
-				\frac{|p_0(x') - p_1(x')|}{2 \big(p_0(x') + p_1(x') \big)}
-			\right)
-			\left(
-				\frac{p_0(x') + p_1(x')}{2}
-			\right)\\
-		&= \frac{1}{2}\left(
-				\frac{1}{2}(
-					\sum_{x' \in X}p_0(x') + \sum_{x' \in X}p_1(x')
-				) + 
-				\frac{1}{2} \sum_{x' \in X} \big(|p_0(x') + p_1(x')|\big)
-			\right) \\
-		&= \frac{1}{2} \left( \frac{1}{2}(1 + 1) + \theta \right)\\
-		&= \frac{1 + \theta}{2}\\
-		\implies \theta &= 2\eta^* - 1.
-	\end{split}
-\end{align}
-By definition, no classifier can be more accurate than $\mathcal{A^*}$, so
-for every $\mathcal{A}$
-\begin{align}
-		\theta \geq 2\eta - 1.
-		\label{eq:sup:l1_again}
-\end{align}
-
-\paragraph{Using cross-validation accuracy to lower-bound bias.}
-	In order for Eq.~\ref{eq:sup:l1_again} to be applicable, it is necessary to 
-	obtain an unbiased estimate of a classifier's accuracy.  To do so, it is
-	essential to test the classifier on data that were not used to build 
-	the classifier.  Generally, a portion of the data is used to
-	optimize preprocessing, select features, and optimize 
-	classifier hyper-parameters, while keeping another portion of the data
-	set aside for validation.
-
-	In our case, the data are expensive, and must be divided between 18
-	experimental treatments, so we sought to keep as many worker responses
-	available 
-	for validation
-	as possible.  For this reason, we made principled decisions 
-	between alternative preprocessing options and features, 
-	rather than spending sampled responses on empirically testing these 
-	options.  Making
-	suboptimal choices can only moderate the observed values 
-	of $\theta$, making our experiments more conservative. 
-	However, conserving more responses for validation 
-	tests, by not using them for classifier optimization, 
-	enables us to estimate the resulting classifier's accuracy more precisely.
-	Using a Na\"ive Bayes classifier, which does not require hyper-parameter 
-	optimization, meant that we also did not need to spend data on 
-	optimizing hyper-parameters.
-
-	Thus, no worker responses at all were used for optimizations.  We 
-	performed 
-	leave-one-out validation, which involves training a classifier using 
-	all but one response, and then having the classifier guess the class
-	(in our case, the priming exposure) of the left-out worker.  This is 
-	repeated $n$ times, where $n$ is the pooled number of worker responses 
-	in both
-	classes (both treatments in a given experiment), 
-	each time leaving out the response of a different worker.
-
-\paragraph{Selection of the na\"ive Bayes classifier.}
-We chose to use the na\"ive Bayes classifier as our basis for measuring 
-bias for three reasons.  First, we had 119 examples (workers) per class 
-(treatment), but thousands of distinct features 
-(i.e. the number of distinct words occurring in an experiment).  
-Having many more features than examples is problematic for many classifiers
-because a large number of features leads to a high-variance, over-fit model,
-resulting in poor performance.  But one of the strengths of the na\"ive 
-Bayes classifier is that it performs well even when the number of features
-exceeds the number of examples\cite{bickel2004, hastie2009elements}
-
-Second, the standard implementation of the na\"ive Bayes classifier has no 
-hyper-parameter to optimize. This meant that we did not need to use 
-samples for hyper-parameters optimization, which would reduce the number
-of samples available for validation tests to estimate $\theta$.
-
-Third, the na\"ive Bayes algorithm is based on an assumption that the 
-observation of one feature is independent from the observation of any 
-other, once we have conditioned on the class under observation 
-%\cite{bishop2006} 
-(i.e. the priming treatment).  This
-conditional independence assumption is made for
-pragmatic rather than theoretical reasons, and is rarely satisfied.  However,
-if it \textit{is} satisfied, then the na\"ive Bayes classifier is 
-optimal \cite{Zhang2004562}.  In most text documents, 
-the existence of long-range dependencies in language 
-violates the conditional independence of words: when a rare word is mentioned,
-it is more likely to be mentioned again, and topics introduced early in a
-text are likely to be revisited.
-But in our case, there is little opportunity for such effects.  Workers 
-generally do not use the same word in multiple labels for the same image. 
-Any overarching ``topics'' within the labels that workers use will tend to 
-relate to the test images, which are held in common.
-Therefore, in our setup, conditional independence is likely to be 
-a realistic approximation, and so the na\"ive Bayes classifier is likely to
-be closer to optimal than in other text classification applications.
-
-\paragraph{Comparison to other classifiers.}
-
-\begin{figure}
-	\centering
-	\includegraphics[scale=0.75]{figs/theta_sup.pdf}
-	\caption{
-		Empirical bias, measured using classifiers, induced in image 
-		labeling tasks, by exposing workers to initial tasks or framing. 
-		The bias was determined using (A-F) a na\"ive Bayes classifier, and 
-		(G-L) an SVM classifier, according to Eq.~\ref{eq:sup:l1}.
-		In panels A through F, each plot adds an additional
-		preprocessing step to those used in the previous plot; the same is 
-		done for panels G through H: A,G) no 
-		preprocessing; B,H) spelling correction; C,I) stop word removal; 
-		D,J) lemmatization; E,K) splitting of multiple-word labels; 
-		F,L) distinguishing identical labels entered in different form inputs.
-		Standard error bars are shown.
-	}
-	\label{fig:theta_sup}
-\end{figure}
-The inequality in Eq.~\ref{eq:sup:l1_again}
-asserts that a classifier's performance in predicting class membership
-sets a lower bound on the L1-distance between the distributions of features 
-for the classes.
-This bound is tight for the optimal classifier, and in general, the slack
-depends on how the classifier is constructed.
-
-Although we believe the na\"ive Bayes classifier is nearly optimal in this
-setting, some other classifier may exist that is significantly better than 
-the one used to generate our results.  Furthermore, various decisions about
-preprocessing and feature representation also
-impact the classifier performance.  
-For example, we chose to correct spelling, remove stop words,
-lemmatize words, and to distinguish which text-input was used to enter a 
-given label.  All of these decisions have some effect on classifier 
-performance.
-
-We chose not to optimize these decisions, since it would require the
-use of samples (worker-responses), which could then not be used in 
-cross-validation to measure $\theta$.  Nevertheless, it is
-appropriate to look at what affect these decisions had, \textit{post-hoc}.  
-We reproduce the plot from Fig.~\ref{fig:theta}A in the main text, 
-this time using different combinations of preprocessing options,
-and using both the na\"ive Bayes and an SVM classifier, in 
-Fig.~S\ref{fig:theta_sup}.
-
-Unlike the na\"ive Bayes classifier, when using SVM it is necessary to tune 
-the cost and gamma hyper-parameters of the SVM classifier, as well as choose 
-a kernel.  We used simulated annealing to optimize the cost and gamma settings
-data from \textit{intertask-food-culture}.  For this reason, the estimate
-of $\theta$ estimate for this experiment in 
-Fig.~S\ref{fig:theta_sup} (G to J) is inflated.
-
-These plots suggest that the values of $\theta$ obtained using the 
-na\"ive Bayes classifier and our particular choice of preprocessing steps, 
-as shown in Fig.~\ref{fig:theta} of the main text, are representative.
-
-\paragraph{Statistical significance and confidence intervals for $\theta$.}
-The measurements of $\theta$ were based on the number of correct 
-classifications during validation tests.  The number of correct 
-classifications, $X$, has a binomial distribution.  
-We take the null hypothesis that the classifier performs
-no better than chance, $X \sim \mathrm{Bin}(N,0.5)$, where $N$ is the number 
-of workers in both treatments of an experiment, and consider an alternative
-hypothesis, that the classifier does perform better than chance.  Then, the 
-critical number 
-of correct classifications, $x^*$, for a one-tailed hypothesis test with
-significance $\alpha$ is:
-\begin{align}
-	&x^* = \sup \left\{
-			x: \mathrm{Pr}\{ \mathrm{Bin}(N;0.5) \geq x \} < \alpha
-		\right\} \label{eq:sup:crit}\\
-	\text{where}\quad &\mathrm{Pr}\{ \mathrm{Bin}(N,\eta) \geq x \} = 
-		\sum_{x'=x}^{N} \binom{N}{x'}\eta^{x'}(1-\eta)^{(N-x')}
-\end{align}
-For the treatments in \textit{intertask-food-objects}, five different 
-permutations of each treatment were tested, and a different classifier was 
-built for each permutation.  For the sake of estimating accuracy, we assume
-that the classifiers under different permutations have the same accuracy,
-and so we pool their results.  This means that 
-\textit{intertask-food-objects} has five times as many validation tests
-(larger $N$) compared to the other experiments.  This larger $N$ makes 
-evaluation of \ref{eq:sup:crit} difficult, but also makes the normal 
-distribution a very good approximation.  We therefore assume 
-that $X$ has a normal distribution for the classification of workers from
-\textit{intertask-food-objects}, with $\mu=N/2$ and 
-$\sigma = \frac{1}{2}\sqrt{N}$.  The statistics for these hypothesis tests
-are tabulated in Tables~S\ref{table:theta} and S\ref{table:theta_pos}.
-
-To determine the confidence intervals for measured $\theta$ values we 
-use the exact Clopper-Pearson method. % \cite{clopper1934use}.  
-Based on the observed number of successes, $X$, we calculate 
-$\eta^*_\mathrm{low}$ and $\eta^*_\mathrm{high}$ from:
-\begin{align}
-	\eta^*_\mathrm{high} &= \sup
-		\left\{
-			\eta : \mathrm{Pr}\{\mathrm{Bin}(N; \eta) \leq X \} > 
-				\frac{\alpha}{2}
-		\right\} \\
-	\eta^*_\mathrm{low} &= \inf
-		\left\{
-			\eta : \mathrm{Pr}\{\mathrm{Bin}(N; \eta) \geq X \} > 
-				\frac{\alpha}{2}
-		\right\}
-\end{align}
-Again, for the experiment \textit{intertask-food-objects}, which had 
-more validation tests than the others, we derive the confidence intervals
-assuming $X$ is normally distributed.
-Since the confidence intervals are to be shown on a plot of $\theta$, we 
-transform them into equivalent values of 
-$\theta$: $\theta^*_\mathrm{high} = 2\eta^*_\mathrm{high} - 1$ and 
-$\theta^*_\mathrm{low} = 2\eta^*_\mathrm{low} - 1$.
-The statistics collected for the measurement of $\theta$, corresponding to
-Figs.~\ref{fig:theta}A and B are tabulated in Tables~S\ref{table:theta} and
-S\ref{table:theta_pos} respectively.
-
-To determine whether intertask effects were stronger than framing, we 
-perform a two-proportion $z$-test, approximating the binomial distributions
-as normal distributions, where the test statistic is given by:
-\begin{align}
-	z = \frac{\hat{\eta}_1 - \hat{\eta}_2}
-		{\sqrt{
-			\hat{\eta} (1 - \hat{\eta}) 
-			\left( \frac{1}{N_1} + \frac{1}{N_2}\right)
-		}},
-\end{align}
-where
-\begin{align}
-	\hat{\eta} = \frac{X_1 + X_2}{N_1 + N_2}
-\end{align}
-
-Since, \textit{a priori}, we do not know which effects
-should be stronger (if any), we perform a two-tailed test.  The results for 
-these hypothesis tests are tabulated in Table~S\ref{table:intertask_framing}.
-The results show that intertask effects are stronger than framing, but are
-on-par with echoed framing.
-
-\begin{table}
-\begin{center}
-\begin{tabular}{c c c c c c c c }
-	\toprule
-	\multirow{2}{*}{Experiment} & \multirow{2}{*}{$N$} & 
-	\multirow{2}{*}{$X$} & \multirow{2}{*}{$x^*$} & \multicolumn{3}{c}{(\%)}
-		& \multirow{2}{*}{$p$}\\ \cline{5-7} \noalign{\smallskip}
-	& & & & $\hat{\theta}$ & $\theta^*_\mathrm{low}$ 
-		& $\theta^*_\mathrm{high}$  \\
-	\midrule
-	\textit{intertask-food-objects} & 1190 & 777 & 624 & \textbf{30.6} 
-		& 25.2 & 36.0 & $2.5 \times 10^{-26}$ \\
-	\textit{frame-food-objects} & 238 & 122 & 133 & 2.5 & -10.6 & 14.7
-		& 0.37 \\
-	\textit{echo-food-objects} & 238 & 162 &  133 & \textbf{36.1} & 23.4 
-		& 47.1 & $1.3 \times 10^{-8}$ \\
-	\textit{intertask-food-culture} & 238 & 180 & 133 & \textbf{51.3} & 39.3 
-		& 61.1 & $5.0 \times 10^{-16}$ \\
-	\textit{frame-food-culture} & 238 & 130 & 133 & 9.2 & -3.9 & 21.3 
-		& 0.087\\
-	\bottomrule
-
-\end{tabular}
-
-\caption{Statistics for the measurement of the extent of bias, $\theta$,
-	induced by intertask and framing effects in various experiments.
-	Number of validation tests, $N$; number of successful classifications, 
-	$X$; critical number of successful classifications to reject the null 
-	hypotheses that the classifier does no better than chance 
-	(one-tailed test), $x^*$; 
-	estimate of bias based on observed number of successful
-	classifications, $\hat{\theta}$; lower confidence interval limit 
-	for the estimate of bias, $\theta^*_\mathrm{low}$; upper confidence 
-	interval limit for same, $\theta^*_\mathrm{high}$.  Hypothesis test and 
-	confidence intervals are based on a significance of $\alpha=0.05$.
-	Values for $\hat{\theta}$ in boldface are significantly greater than zero.
-}
-\label{table:theta}
-\end{center}
-\end{table}
-
-\begin{table}
-\begin{center}
-\begin{tabular}{c c c c c c c c }
-	\toprule
-	\multirow{2}{*}{Task position} & \multirow{2}{*}{$N$} & 
-	\multirow{2}{*}{$X$} & \multirow{2}{*}{$x^*$} & \multicolumn{3}{c}{(\%)}
-		& \multirow{2}{*}{$p$}\\ \cline{5-7}\noalign{\smallskip}
-	& & & & $\hat{\theta}$ & $\theta^*_\mathrm{low}$ 
-		& $\theta^*_\mathrm{high}$  \\
-	\midrule
-	1 & 238 & 152 & 133 & \textbf{28.1} & 14.8 & 39.1 
-		& $1.12 \times 10^{-5}$\\
-	2 & 238 & 138 & 133 & \textbf{15.6} & 2.9 & 27.8  
-		& $8.14 \times 10^{-3}$\\
-	3 & 238 & 140 & 133 & \textbf{17.8} & 4.6 & 29.5  
-		& $3.87 \times 10^{-3}$\\
-	4 & 238 & 135 & 133 & \textbf{13.6} & 0.3 & 25.4  
-		& $0.0221$ \\
-	5 & 238 & 134 & 133 & \textbf{12.4} & 0.5 & 24.6 & $0.0300$ \\
-	\bottomrule
-\end{tabular}
-\caption{Statistics for the measurement of the extent of bias, $\theta$,
-	induced by intertask for \textit{intertask-food-objects}, measured 
-	for test images at specific positions in the sequence of five test images.
-	These values are averaged over five different permutations.
-	Number of validation tests, $N$; number of successful classifications, 
-	$X$; critical number of successful classifications to reject the null 
-	hypotheses that the classifier does no better than chance 
-	(one-tailed test), $x^*$; 
-	estimate of bias based on observed number of successful
-	classifications, $\hat{\theta}$; lower confidence interval limit
-	for the estimate of bias, $\theta^*_\mathrm{low}$; upper confidence 
-	interval for same, $\theta^*_\mathrm{high}$.  Hypothesis test and 
-	confidence intervals are based on a significance of $\alpha=0.05$.
-	Values for $\hat{\theta}$ in boldface are significantly greater than zero.
-}
-\label{table:theta_pos}
-\end{center}
-\end{table}
-
-\begin{table}
-\begin{center}
-\begin{tabular}{c c c c c c c c c c c }
-	\toprule
-	Comparison & $N_1$ & $N_2$ & $X_1$ & $X_2$ & $\hat{\eta}_1$ 
-		& $\hat{\eta}_2$ & $z$ & $p$-value \\ 
-	\midrule
-	\parbox[c]{4cm}{\textit{intertask-food-objects} 
-	\textit{vs} \textit{frame-food-objects}} & 1190 & 238 & 777 & 122 &
-	0.653 & 0.513 & \textbf{4.1} & $2.1 \times 10^{-5}$ \\
-
-\noalign{\smallskip}
-\hdashline
-\noalign{\smallskip}
-
-	\parbox[c]{4cm}{\textit{intertask-food-objects} 
-	\textit{vs} \textit{echo-food-objects}} & 1190 & 238 & 777 & 162 
-		& 0.653 & 0.681 & -0.82 & 0.79 \\
-
-\noalign{\smallskip}
-\hdashline
-\noalign{\smallskip}
-
-	\parbox[c]{4cm}{\textit{intertask-food-culture} 
-	\textit{vs} \textit{frame-food-culture}} & 238 & 238 & 180 & 130 
-	& 0.756 & 0.546 & \textbf{4.8} & $7.6 \times 10^{-7}$ \\
-	\bottomrule
-
-\end{tabular}
-
-\caption{
-	Results for two-proportion z-tests, testing the null hypothesis that 
-	intertask and framing effects are equally strong.
-	In the cases of comparing intertask effects to passive framing, the
-	null hypothesis should be rejected ($\alpha=0.05$), but 
-	echoed framing effects are on par with intertask effects (second row). 
-	$z$-statistics in boldface are significantly different from zero.
-}
-\label{table:intertask_framing}
-\end{center}
-\end{table}
-
-\subsection*{Data preprocessing}
-	\paragraph{Splitting, lemmatization, removal of stop words, and 
-		addition of position tags.}
-
-	Before performing any analysis on the labels that workers provided, we
-	performed a series of preprocessing steps.  
-	Labels that contained
-	multiple words (separated by spaces or punctuation) were split, with
-	punctuation removed, and the separated words were treated as distinct 
-	features in subsequent analysis.
-	Misspelled words were automatically corrected using a spelling 
-	correction algorithm described below.  
-	Next, words were lemmatized using the
-	wordnet lemmatizer \cite{felbaum1998wordnet}.  %miller1995wordnet,
-	Common words such as ``the'', ``to'', or ``with'', were found using
-	the natural language toolkit (NLTK) English stop word list 
-	\cite{loper2002nltk} and removed.
-
-	For the purpose of training and testing a na\"ive Bayes classifier, we 
-	performed an additional preprocessing step.  We tagged words with the
-	position in which they had been entered (i.e. which of the five text 
-	inputs in the task interface, Fig.~S\ref{fig:hit_preamble}) 
-	as well as the test tasks in which the word had been provided.
-	So, if the word ``wine'' was entered into the second text-input for 
-	the third test-task, after preprocessing, the feature ``3\_2\_wine'' would
-	appear.  Prepending the task number onto words was simply a means to 
-	retain correct attribution of words to images, since providing a word 
-	during one task 
-	is not equivalent to providing the same word during another task.
-
-	\paragraph{Spelling correction.}  
-	Spelling correction was performed using an algorithm that first detected
-	if a word was likely to be misspelled, then generated a set of candidate 
-	corrections, and chose the best candidate based on a scoring mechanism.
-
-	A word was considered misspelled if it was not contained in the 
-	\textit{legal set}, which was formed by the union of
-	the wordnet corpus, the stop word list, and a set of words seen while 
-	crawling the world food section of the allrecipes.com website.  We
-	describe the crawling of the allrecipes.com website in a section below.
-
-	To correct misspellings, we first produced all possible modified forms 
-	that could be obtained applying one or two edits.  An edit consisted of 
-	adding or removing a letter, changing one letter into another, or 
-	swapping the positions of two adjacent letters.  For the purpose of these 
-	edits, spaces were treated as any other letter.
-
-	The candidates produced by these edits which were in the legal set were
-	then ranked based on a scoring mechanism, and the highest scoring word
-	was chosen as the correction.  A candidate $w$'s score, $s_w$, was 
-	calculated according to the following formula:
-	\begin{equation}
-		s_w = (f_w + 1) \times p_1 \times p_2,
-	\end{equation}
-	where $f_w$ is the frequency with which the word occurred (correctly 
-	spelled)
-	within the given task, $p_1$ was a penalty for the first edit, and
-	$p_2$ was a penalty for the second edit.  If the word was made using only
-	one edit, then $p_2 = 1$.  Any edit that did not involve adding a space
-	(i.e. separating a word) incurred a penalty of 0.5, while the addition of
-	a space incurred a penalty of 0.1.  Word-separation edits were more 
-	strongly penalized because it is often possible to split a series of 
-	letters into short two- or three-letter words, which leads 
-	to many erroneous corrections.  We found these penalties worked well when
-	testing on words taken from initial tasks.
-
-	After all of our analyses had been performed, we checked the accuracy of 
-	the spelling correction algorithm using three human coders.  The coders
-	were shown a set of 
-	500 words that were randomly sampled from the labels attributed during 
-	test tasks (50 for each test task).  Before sampling, the labels from all
-	experimental treatments, for the given test task, were pooled together.
-	The coders did not know which treatment any given word came from.  
-	In addition to the words, coders were shown the spelling correction 
-	produced by the algorithm, as well as the image from the test task.
-	The coders were asked to identify any misspelled words which had not 
-	been corrected, as well as any corrections that appeared to be erroneous,
-	by indicating their own correction.
-
-	According to the human coders, before spelling correction, 17\% of words 
-	were misspelled, but only 3.2\% were misspelled after correction.
-
-	\paragraph{Crawling the world food section of allrecipes.com.}
-	The website allrecipes.com was accessed on 3-4 November 2014 using 
-	automated scripts.  A total of 2642 recipe listings and 15621 recipe
-	instruction pages were retrieved.  Recipe listings were pages that 
-	provided lists of recipes, and contained a title and short description 
-	for each.  
-	The recipe instruction pages had lists of ingredients and preparation 
-	instructions.  All of the words found in recipe titles, short
-	descriptions, ingredients lists, and preparation instructions were
-	collected, and saved as an auxiliary set to augment the \textit{legal set}
-	used in spelling correction.
-
-\subsection*{Analysis of worker vocabulary}
-\paragraph{Most suppressed and activated terms.}
-The words whose frequencies differed most between the treatments of given 
-experiments are shown in Table~S\ref{table:top-words}.  Note that 
-the word that was most suppressed in food-exposed treatments was always 
-``food''.
-
-\begin{table}
-	\centering
-	\setlength{\tabcolsep}{4pt}
-	\begin{tabular}{ c c c c c }
-
-		\setlength{\tabcolsep}{4pt}
-		\begin{tabular}{ r | c }
-		\toprule
-		\multicolumn{2}{c}{
-			\parbox[c]{2.5cm}{
-				\centering
-					\textit{intertask-food-objects}
-			}} \\
-		\midrule
-		coffee & 38 \\
-		meal & 34 \\
-		cheese & 34 \\
-		apple & 32 \\
-		dessert & 21 \\
-		cup & -30 \\
-		glass & -45 \\
-		table & -70 \\
-		candle & -74 \\
-		food & -80 \\
-		\bottomrule
-		\end{tabular}
-
-&
-
-		\setlength{\tabcolsep}{4pt}
-		\begin{tabular}{ r | c }
-		\toprule
-		\multicolumn{2}{c}{
-			\parbox[c]{2.5cm}{
-				\centering
-				\textit{frame-food-objects}
-			}
-		}\\
-		\midrule
-		bread & 18 \\
-		wine & 18 \\
-		cheese & 16 \\
-		apple & 14 \\
-		oil & 12 \\
-		table & -9 \\
-		meal & -10 \\
-		candle & -12 \\
-		dinner & -13 \\
-		food & -32 \\
-		\bottomrule
-		\end{tabular}
-
-&
-
-		\setlength{\tabcolsep}{4pt}
-		\begin{tabular}{ r | c }
-		\toprule
-		\multicolumn{2}{c}{
-			\parbox[c]{2.5cm}{
-				\centering
-			\textit{echo-food-objects}} 
-		}\\
-		\midrule
-		apple & 24 \\
-		cheese & 23 \\
-		wine & 15 \\
-		coffee & 14 \\
-		oil & 7 \\
-		knife & -24 \\
-		dinner & -26 \\
-		fork & -27 \\
-		candle & -35 \\
-		food & -55 \\
-		\bottomrule
-		\end{tabular}
-
-&
-
-		\setlength{\tabcolsep}{4pt}
-		\begin{tabular}{ r | c }
-		\toprule
-		\multicolumn{2}{c}{
-			\parbox[c]{2.5cm}{
-				\centering
-			\textit{intertask-food-culture}} 
-		}\\
-		\midrule
-		spicy & 26 \\
-		sauce & 17 \\
-		indian & 15 \\
-		buffet & 14 \\
-		exotic & 12 \\
-		festival & -11 \\
-		offering & -12 \\
-		statue & -15 \\
-		india & -20 \\
-		food & -56 \\
-		\bottomrule
-		\end{tabular}
-
-&
-
-		\setlength{\tabcolsep}{4pt}
-		\begin{tabular}{ r | c }
-		\toprule
-		\multicolumn{2}{c}{
-			\parbox[c]{2.5cm}{
-				\centering
-			\textit{frame-food-culture}} 
-		}\\
-		\noalign{\smallskip}
-		\midrule
-		indian & 11 \\
-		banquet & 8 \\
-		spicy & 7 \\
-		asian & 6 \\
-		variety & 6 \\
-		delicious & -6 \\
-		meat & -7 \\
-		festival & -7 \\
-		spice & -7 \\
-		food & -9 \\
-		\bottomrule
-		\end{tabular}
-
-	\end{tabular}
-	\caption{
-		The five words whose frequencies increased, and those whose 
-		frequencies decreased, the most, between treatments of given 
-		experiments, within labels attributed to the first test task.
-		Positive values indicate that the food-exposed treatment
-		used the word with higher frequency.  
-		Note that the word ``food'' is always the most suppressed among
-		food-exposed workers.
-		Word frequencies for 
-		\textit{intertask-food-objects} correspond to the labels attributed
-		to image 1 (see Fig. \ref{fig:task1:test}) which is not necessarily 
-		the first 
-		test task due to the tasks being permuted.  There were five times
-		as many workers in \textit{intertask-food-objects}, hence
-		larger absolute differences are observed.
-	}
-	\label{table:top-words}
-\end{table}
-
-\paragraph{Identification of food-related terms.}
-The wordnet corpus is composed of synsets, which are particular senses 
-(meanings) and a set of word forms bearing that meaning. A given word form, 
-such as ``ring'' has multiple senses (``to ring a bell'', ``a wedding ring''),
-and so can be part of many synsets.  Since the wordnet corpus was designed
-to carry semantic information, the synset is the basic organizing element
-of wordnet.
-
-We chose the synsets \texttt{food.n.01} and \texttt{food.n.02} to act as roots
-in defining which words should be considered food-related.  Any word form
-belonging to a synset which was a hyponym of one of the two root synsets
-identified above was considered to be a reference to food.  Here, as in the
-main text, when we say hyponym, we mean either a direct hyponym, or a hyponym
-of a hyponym, and so on.
-
-This is a stringent notion of a word being a food reference.  It roughly
-corresponds to whether or not a given thing is reasonably considered 
-consumable.  So, ``orange'' is food, but ``salty'' is not.  Although ``salty''
-would usually qualify something edible, it is not itself an edible thing.
-On the other hand, ``salt'' would be considered a reference to food under 
-this operationalization.
-
-The subset of the wordnet corpus induced by the hyponyms of \textit{food.n.01}
-and \textit{food.n.02} consists of 3590 word-forms.  Manual
-testing showed good coverage, except for references to ethnic foods.  
-Since, especially in \textit{intertask-food-culture} and 
-\textit{frame-food-culture}, we had images containing many ethnic 
-foods, we decided to augment the wordnet corpus with words learned by 
-crawling the world food section of the allrecipes.com website.
-
-After collecting a set of words using an automated script 
-(described above), we filtered down to the set of words that had been used by
-workers and which had been seen during crawling of the allrecipes.com website,
-but which were not included in wordnet.  We grafted these extra words into
-the wordnet hyponym-hypernym graph manually, looking at the image to which 
-they had been attributed (to help disambiguate the intended meaning), but 
-without revealing the treatment(s) in which
-the word was used.  Many (but not all) of the words added this way did refer 
-to ethnic foods, and so this helped increase the coverage of wordnet in that 
-respect.
-
-\paragraph{Validation of the detection of food references.}
-To determine whether our extended version of wordnet provided a good approach
-to detecting food-related words, we sampled 500 words 
-(50 from each test task)  from the set of labels produced by workers and had 
-three human coders manually decide if they were 
-food-related or not.
-
-The coders were instructed to consider whether a word was a noun signifying
-an edible item.  The guiding principle was, for the coder to ask herself,
-``can I eat X'', where X is the word she is coding.  The coders were
-shown the image used in the task from which the word came, to help resolve ambiguity
-in the sense of the word that had been given.  Coders were also shown the 
-spelling correction (if any) that the spell-correction algorithm had made,
-to help interpret misspelled words.
-
-We evaluated the food detection algorithm in two ways.  First, we measured
-the inter-rater reliability between the three human coders and the algorithm
-(treating the algorithm just like any other coder).  Second, adopting the 
-majority code given by the human coders as ground-truth, we determined the 
-accuracy of the food-detection algorithm.  
-Data summarizing this validation process are given
-in Table~S\ref{table:inter-rater}.
-
-\begin{table}
-\centering
-\setlength{\tabcolsep}{12pt}
-\begin{tabular}{ r | c }
-\toprule    
-\# terms coded & 500 \\
-\# food references & 130 \\
-\# correct machine codes & 440 \\
-inter-rater reliability & 82.4\% \\
-human-machine code agreement & 88\% \\
-%machine recall & 80 \% \\
-%machine precision & 75.4 \% \\
-%machine code F1 & 0.78 \\
-\bottomrule
-\end{tabular}
-\caption{
-	Results for the validation 
-	of the automatic detection of food references, by comparison to
-	human-generated coding on randomly sampled words.  In calculating the 
-	human-machine code agreement, the majority human code was used.
-	Inter-rater reliability was calculated as Krippendorff's alpha, treating
-	the machine as any other coder.
-}
-\label{table:inter-rater}
-\end{table}
-
-The results show that good inter-rater reliability was achieved during the
-validation (82.4\%).  Looking at the agreement between the 
-machine codes and the majority human-generated codes, we find they agree
-88\% of the time.  This means that the concept used to instruct human coders
-provides a good approximation to what the wordnet-based machine codes actually
-represent. In other words, the machine codes correspond closely to indicating
-which words correspond to nouns that refer to edible things, and which ones
-do not, which provides a clear and simple interpretation for the machine
-coding of food and non-food words.
-
-\paragraph{Testing differences in proportions of food-related labels.}
-We calculate the proportion of food-related labels in a treatment by first
-calculating the proportion of food-related labels per worker, and then
-taking the average of this value for all workers.  We calculate the
-sample standard deviation for workers' proportions of food-related terms,
-$s_w$ and then estimate the standard deviation of the average proportion
-to be $s = s_w / \sqrt{N}$, where $N$ is the number of workers in the 
-treatment.  The proportions of food-related words for all treatments,
-and the statistics for the hypothesis test that the proportions between
-treatments within given experiments differ, are shown in 
-Table~S\ref{table:proportion-food}.
-
-\begin{table}
-\centering{
-\setlength{\tabcolsep}{4pt}
-\setlength{\tabcolsep}{3pt}
-\begin{tabular}{c c c c c c c c c c c}
-	\toprule
-	\multirow{2}{*}{Experiment} 
-		& \multicolumn{2}{c}{food treatment}
-		& \ 
-		& \multicolumn{2}{c}{other treatment} 
-		& \
-		& \multicolumn{2}{c}{(other - food)} 
-	& \multirow{2}{*}{$z$-score}
-	& \multirow{2}{*}{$p$-value} \\ \cline{2-3} \cline{5-6} \cline{8-9}
-	& \% refs. 
-	& $s$ 					
-	& \
-	& \% refs. 
-	& $s$ 					
-	& \
-	& $\Delta$\% refs. 
-	& $s$ 					 \\ 
-	\midrule
-	\textit{intertask-food-objects} & 54.5 & 0.6 & \ & 57.4 & 0.8 & \ 
-		& \textbf{2.9} & 1.0 & 3.0 & $1.3 \times 10^{-3}$\\
-	\textit{frame-food-objects} & 56.2 & 1.4 & \ & 60.1 & 1.4 & \ 
-		& \textbf{3.9} & 1.9 & 2.0 & $2.2 \times 10^{-2}$\\
-	\textit{echo-food-objects} & 54.0 & 1.4 & \ & 62.8 & 1.7 & \ 
-		& \textbf{8.8} & 2.2 & 4.0 & $3.5 \times 10^{-5}$\\
-	\textit{intertask-food-culture} & 48.8 & 1.6 & \ & 40.8 & 2.0 & \ 
-		& \textbf{-8.0} & 2.6 & -3.1 & $9.2 \times 10^{-4}$\\
-	\textit{frame-food-culture} & 45.8 & 2.0 & \ & 45.2 & 1.8 & \ 
-		& -0.6 & 2.6 & -0.2 & $0.41$\\
-	\bottomrule
-\end{tabular}
-}
-\caption{Statistics for the comparison of the proportions of food-references
-	among words used in labels, between treatments of all experiments.  
-	$s$: sample standard deviation.
-}
-\label{table:proportion-food}
-\end{table}
-
-\paragraph{Variance in food vocabulary size (lexical richness).}
-The number of unique words in a text is strongly dependent on the size
-of the text: as more text is sampled, previously unseen words continue
-to be found, though at a decreasing rate.  
-This means that the vocabulary size of a population of documents is 
-not well-approximated by a sample.  Nevertheless the vocabulary sizes
-obtained by taking equally-sized samples of two different populations
-provides a means to compare the populations on an equal footing.
-
-Taking the difference between one sample's vocabulary and the 
-other gives us a measure of their difference in vocabulary size, but 
-the variance of this measure needs to be characterized to know whether
-there is a significant difference.
-
-To test whether one sample has a (statistically) significantly larger
-vocabulary size, in reference to food-related words, than another, we adopt 
-the null hypothesis that they
-have the same vocabulary, and pool the documents sampled from both 
-populations together.  We then randomly partition the pooled sample
-back into two balanced sets and take the difference in the sets' 
-vocabulary sizes.  This models the difference that would be observed
-under the null hypothesis that the documents are drawn from the same
-population.  We repeat the pooling and partitioning of the samples
-1000 times to generate a bootstrap sample of the difference in 
-vocabulary sizes under the null hypothesis.  The 
-2.5th and 97.5th percentiles of the bootstrap sample then serve as the
-critical values of vocabulary size-difference beyond which the null hypothesis
-should be rejected (at $\alpha=0.05$).
-Statistics for these hypothesis tests are shown in 
-Table~S\ref{table:vocab}.
-
-\begin{table}
-\centering{
-\begin{tabular}{c c c c c c c }
-	\toprule
-	\multirow{2}{*}{Experiment} & \multicolumn{2}{c}{$|V|$} 
-		 & \ & \multicolumn{3}{c}{$(\%)$} \\ \cline{2-3} \cline{5-7}
-	& Food trtmt. & Other trtmt. & \ & $\Delta|V|$ & $\Delta|V|^*_{low}$
-		& $\Delta|V|^*_{high}$  \\
-	\midrule
-	\textit{intertask-food-objects} & 297 & 247 & \ 
-		& \textbf{20.2} & -10.7 & 11.5 \\
-	\textit{frame-food-objects} & 296 & 261 & \ 
-		& \textbf{13.4} & -9.7 & 10.1 \\
-	\textit{echo-food-objects} & 316 & 280 & \ & 
-		\textbf{12.9} & -11.8 & 11.1 \\
-	\textit{intertask-food-culture} & 289 & 244 & \ 
-		& \textbf{18.4} & -11.4 & 11.6 \\
-	\textit{frame-food-culture} & 318 & 332 & \ & -4.2 & -11.9 & 11.2 \\
-	\bottomrule
-\end{tabular}
-}
-\caption{
-	Statistics for the measurement of vocabulary size difference, for each
-	experiment, between the food and non-food treatments. Vocabulary
-	size, $|V|$; vocabulary size of non-food less food treatments, 
-	$\Delta|V|$; lower and upper critical values, $\Delta|V|^*_{low}$ and 
-	$\Delta|V|^*_{high}$, for statistically significant 
-	$\Delta|V|$, at $\alpha=0.05$, based on bootstrapping.  
-	Boldfaced values for $\Delta|V|$ are statistically significant.
-}
-\label{table:vocab}
-\end{table}
-
-\paragraph{Calculation of relative specificity}
-In the main text we present results for the relative specificity of labels
-produced by two experimental treatments.  In performing this calculation,
-we used the wordnet corpus, which has a set of hypernym-hyponym relationships.
-The first step in performing this calculation was to map the words occurring 
-in (the labels of) a given experimental treatment onto the wordnet synsets.  
-In general, a given word
-form can have multiple meanings, and therefore maps onto multiple wordnet 
-synsets.
-
-Mapping the words from two treatments onto the wordnet 
-hypernym-hyponym graph yields two sets of counts, one set per treatment, 
-indicating the number of times a word from a given synset occurred among the
-labels of the treatment.  For every synset in one treatment, we looked
-at the number of synsets in the other treatment that were more generic
-(reachable by following hypernym relations) less the number of words that
-were more specific (reachable by following hyponym relations).  This quantity,
-tallied over all words in the original synset, gives a (non-normalized) 
-measure of the overall degree to which words from the first treatment are more
-specific than words from the second treatment.  We then normalized this 
-quantity by the total number of possible comparisons between the words of
-one treatment to those of the other, where two words are considered comparable
-only if one word is the hypernym or hyponym of the other.  Hence, ``statue'' 
-and ``bread'' are not comparable, but ``pumpernickel'' and ``bread'' are.
-
-This calculation can be summarized by the following equation:
-\begin{equation}
-	S(P,Q) = \frac{
-		\sum_{w\in P}\sum_{v\in Q} \left(
-			\mathbf{1}_{[w>v]} - \mathbf{1}_{[v>w]} \right)
-	}{
-		\sum_{w\in P}\sum_{v\in Q} \left(
-			\mathbf{1}_{[w>v]} + \mathbf{1}_{[v>w]} \right)
-	},
-\end{equation}
-where $P$ and $Q$ are sets of synsets associated to different experimental 
-treatments, and $\mathbf{1}_{[w>v]}$ evaluates
-to 1 if synset $w$ is more specific than (i.e. is a hyponym of) synset $v$.
-This measure counts the excess number of cases where synsets from $P$ are more
-specific then synsets from $Q$, as a fraction of all comparable synset pairs. 
-The relative specificity lies within $[-1,1]$; we report it as a percentage 
-in Table~S\ref{table:proportion-food} and in the main text.
-
-In computing this quantity between two treatments, we first computed the 
-relative specificity for the treatments separately for each test task, and 
-averaged the results obtained accross the five test tasks.
-
-To assess statistical significance, we used the bootstrap method.
-For two given treatments $A$ and $B$, 
-119 workers were sampled from each with replacement, giving the bootstrap
-samples $A'$ and $B'$, and the relative specificity between these 
-was measured as described above.
-This was repeated 1000 times.  The 2.5 and 97.5 percentiles from the 
-bootstrap sample were used to estimate 95\% confidence intervals.  
-A confidence interval not containing zero indicates a statistically 
-significant difference in specificity.  
-The statistics for relative specificity 
-calculations are shown in Table~S\ref{table:specificity}.
-
-\begin{table}
-\centering{
-	\setlength{\tabcolsep}{4pt}
-\begin{tabular}{c c c c c c c c c c c}
-	\toprule
-	Experiment & $S$ & $S^*_\mathrm{lowCI}$ & $S^*_\mathrm{highCI}$ \\ 
-	\midrule
-	\textit{intertask-food-objects} & \textbf{13.6} & 9.1 & 17.8 \\
-	\textit{frame-food-objects} & \textbf{12.4}     & 7.6 & 17.0 \\
-	\textit{echo-food-objects} & \textbf{17.1}      & 12.1 & 21.9 \\
-	\textit{intertask-food-culture} & \textbf{19.6} & 13.7 & 25.4 \\
-	\textit{frame-food-culture} & \textbf{7.0}      & 2.1 & 15.3 \\
-	\bottomrule
-\end{tabular}
-}
-\caption{Relative specificity ($S$) of food-related words between the food- 
-	and non-food-exposed treatments of all experiments. 
-	Positive values indicates the food-exposed treatment was relatively more
-	specific (which was always the case); 
-	boldfaced values indicate a disparity in specificity that 
-	is statistically significant.  
-	$S^*_\mathrm{lowCI}, S^*_\mathrm{highCI}$: lower and upper
-	confidence intervals for $S$ based on the bootstrapping approach.  
-	Specificites are expressed as percentages.}
-\label{table:specificity}
-\end{table}
+would be ``warmed up'' before performing the test tasks, as is the case for the
+experiments investigating the effect of initial tasks.  We therefore adopted
+this approach in the experiment \textit{frame-food-culture}, in which workers
+performed the same initial tasks containing images that depicted food in both
+the \textit{food} and \textit{culture} treatments.  It would seem that the
+framing effect in \textit{frame-food-culture} was reduced by the initial tasks,
+possibly because intertask effects tend to override framing. Further
+experimentation would be necessary to be sure, but this was not the purpose of
+our study.
+
+\end{materials}
+
+\begin{acknowledgments}
+This work was partially supported by an Insight Grant from the Canadian Social Sciences and Humanities Research Council.
+\end{acknowledgments}
+
+\bibliography{newbib}
+\bibliographystyle{plain}
+
+%
+%\begin{thebibliography}{10}
+%\bibitem{BN}
+%M.~Belkin and P.~Niyogi, {\em Using manifold structure for partially
+%  labelled classification}, Advances in NIPS, 15 (2003).
+%
+%\bibitem{BBG:EmbeddingRiemannianManifoldHeatKernel}
+%P.~B\'erard, G.~Besson, and S.~Gallot, {\em Embedding {R}iemannian
+%  manifolds by their heat kernel}, Geom. and Fun. Anal., 4 (1994),
+%  pp.~374--398.
+%
+%\bibitem{CLAcha1}
+%R.R.~Coifman and S.~Lafon, {\em Diffusion maps}, Appl. Comp. Harm. Anal.,
+%  21 (2006), pp.~5--30.
+%
+%\bibitem{DiffusionPNAS}
+%R.R.~Coifman, S.~Lafon, A.~Lee, M.~Maggioni, B.~Nadler, F.~Warner, and
+%  S.~Zucker, {\em Geometric diffusions as a tool for harmonic analysis and
+%  structure definition of data. {P}art {I}: Diffusion maps}, Proc. of Nat.
+%  Acad. Sci.,  (2005), pp.~7426--7431.
+%
+%\bibitem{Clementi:LowDimensionaFreeEnergyLandscapesProteinFolding}
+%P.~Das, M.~Moll, H.~Stamati, L.~Kavraki, and C.~Clementi, {\em
+%  Low-dimensional, free-energy landscapes of protein-folding reactions by
+%  nonlinear dimensionality reduction}, P.N.A.S., 103 (2006), pp.~9885--9890.
+%
+%\bibitem{DoGri}
+%D.~Donoho and C.~Grimes, {\em Hessian eigenmaps: new locally linear
+%  embedding techniques for high-dimensional data}, Proceedings of the National
+%  Academy of Sciences, 100 (2003), pp.~5591--5596.
+%
+%\bibitem{DoGri:WhenDoesIsoMap}
+%D.~L. Donoho and C.~Grimes, {\em When does isomap recover natural
+%  parameterization of families of articulated images?}, Tech. Report Tech. Rep.
+%  2002-27, Department of Statistics, Stanford University, August 2002.
+%
+%\bibitem{GruterWidman:GreenFunction}
+%M.~Gr\"uter and K.-O. Widman, {\em The {G}reen function for uniformly
+%  elliptic equations}, Man. Math., 37 (1982), pp.~303--342.
+%
+%\bibitem{Simon:NeumannEssentialSpectrum}
+%R.~Hempel, L.~Seco, and B.~Simon, {\em The essential spectrum of neumann
+%  laplacians on some bounded singular domains}, 1991.
+%
+%\bibitem{1}
+%Kadison, R.\ V.\ and Singer, I.\ M.\ (1959)
+%Extensions of pure states, {\it Amer.\ J.\ Math.\ \bf
+%81}, 383-400.
+%
+%\bibitem{2}
+%Anderson, J.\ (1981) A conjecture concerning the pure states of
+%$B(H)$ and a related theorem. in {\it Topics in Modern Operator
+%Theory}, Birkha\"user, pp.\ 27-43.
+%
+%\bibitem{3}
+%Anderson, J.\ (1979) Extreme points in sets of
+%positive linear maps on $B(H)$. {\it J.\ Funct.\
+%Anal.\
+%\bf 31}, 195-217.
+%
+%\bibitem{4}
+%Anderson, J.\ (1979) Pathology in the Calkin algebra. {\it J.\
+%Operator Theory \bf 2}, 159-167.
+%
+%\bibitem{5}
+%Johnson, B.\ E.\ and Parrott, S.\ K.\ (1972) Operators commuting
+%with a von Neumann algebra modulo the set of compact operators.
+%{\it J.\ Funct.\ Anal.\ \bf 11}, 39-61.
+%
+%\bibitem{6}
+%Akemann, C.\ and Weaver, N.\ (2004) Consistency of a
+%counterexample to Naimark's problem. {\it Proc.\ Nat.\ Acad.\
+%Sci.\ USA \bf 101}, 7522-7525.
+%
+%\bibitem{TSL}
+%J.~Tenenbaum, V.~de~Silva, and J.~Langford, {\em A global geometric
+%  framework for nonlinear dimensionality reduction}, Science, 290 (2000),
+%  pp.~2319--2323.
+%
+%\bibitem{ZhaZha}
+%Z.~Zhang and H.~Zha, {\em Principal manifolds and nonlinear dimension
+%  reduction via local tangent space alignement}, Tech. Report CSE-02-019,
+%  Department of computer science and engineering, Pennsylvania State
+%  University, 2002.
+%\end{thebibliography}
+%
+
+\end{article}
 

### 2015-04-25 docs/publications/2015.04_PNAS/supp.tex
Created PNAS draft

--- 2015-02-13 docs/publications/2014.09_SCIENCE/man.tex
@@
 
-\begin{sciabstract}
-Microtask platforms have become commonplace tools for obtaining human 
-annotations for large datasets.  Such platforms connect requesters 
-(researchers or companies) with large populations (crowds) of workers, who 
-will individually complete small information-processing jobs, each taking 
-typically between one to five minutes.  
-A major challenge in using such platforms, 
-and a topic of ongoing research, concerns designing jobs that elicit high 
-quality annotations. Here we identify a feature of nearly all crowdsourcing 
-jobs that can act as a strong and systemic source of bias in annotations 
-produced by workers. Specifically, many microtask jobs consist of a sequence 
-of tasks which share a common format (e.g., label pictures, identify people, 
-circle galaxies). Using image-labeling, a canonical microtask job format, we 
-discover that earlier tasks shift the distribution of future answers by 
-30-50\%. 
-Moreover, we show that prior tasks influence 
-the content that workers chose to focus on, as well as the richness and 
-specialization of their word choice. While these \textit{intertask effects} 
-can be a 
-source of systematic bias, our results suggest that, with appropriate job 
-design, it might be possible to leverage these biases to hone worker focus 
-and specificity, helping to elicit reproducible, expert-level judgments.
-\end{sciabstract}
-
-\section*{Main text}
-Microtask platforms are online marketplaces in which \textit{requesters} 
-post batches of tasks, and \textit{workers} complete them
-for remuneration, a sense of purpose, and fun
-\cite{kazai2013analysis}.
-Typical tasks include tagging and categorizing images,
-%\cite{6116320,Zhai2012357}, 
-coding and transcription, such as of voice recordings or handwritten notes,
-%\cite{chandler2013breaking,Berinsky2012351,Finnerty2013},%paolacci2010running}, 
-and judging relevancy and quality, for example, to rate information 
-retrieval systems\footnote{We provide a survey of task types in the supplementary text.}.
-%\cite{le2010ensuring,grady2010crowdsourcing,alonso2009can,kazai2013analysis}.
-
-In this form of crowdsourcing, workers appear like input-output devices.  
-Such platforms provide much of the flexibility and 
-cost-savings of fully automating the work in a computer program: 
-the workforce is available on demand over the Internet using automated 
-scripts, and  no interviews or contracts are required 
-\cite{wolfson2011look,5543192}.  Many tasks
-can be performed at a fraction of the cost of traditional methods for 
-recruiting temporary workers or experimental subjects
-\cite{Berinsky2012351}. %,ranade2012crowdsource}%,paolacci2010running}.
-From the requester's perspective, microtask platforms resemble
-a remote compute server, and some seriously consider microtask platforms 
-as a new kind of computing architecture
-\cite{5543192}. %,little2010turkit,minder2012crowdlang,kittur2011crowdforge}.
-
-The flexibility and cost-effectiveness of microtask labour
-has led to a surge in demand from industry and 
-academia\cite{wolfson2011look,Berinsky2012351},
-leading researchers to investigate the factors affecting its reliability.  
-Among these factors are
-the level of pay \cite{Mason200977,kazai2013analysis}, 
-the training and pre-screening of workers 
-\cite{le2010ensuring,kazai2013analysis}, %paolacci2010running}, 
-user-interface design \cite{Finnerty2013}, and the provision of timely 
-feedback \cite{Dow20121013}.
-Researchers have also investigated \textit{framing}, 
-by altering the description of the workflow context 
-\cite{Kinnaird2012281}, the stated purpose of tasks 
-\cite{chandler2013breaking}, and the problem description
-\cite{thibodeau2013natural}.  Another important optimization concerns
-workflow design: how breaking down a complex problem into microtasks
-\cite{kittur2011crowdforge}, altering microtask size 
-\cite{Huang201077}, and introducing workflow interruptions 
-\cite{laseckieffects} impact worker quality and efficiency.
-
-Here, we focus on a ubiquitous feature of microtask work: the tendency
-for workers to perform many similar tasks in quick succession.  
-%To describe this tendency, it is necessary to clarify terminology.
-On one popular microtask platform, Amazon's Mechanical Turk (MTurk), 
-tasks are delivered in bundles called HITs.
-Although HIT stands for ``Human Intelligence Task'', we use ``task'' to mean
-the smallest repeatable unit of work.  For example, one HIT may involve 
-labeling ten images with descriptive words (\textit{labels}), while for
-the present discussion, we consider labeling a single image to be a task.
-In addition to the task-repetition occuring \textit{within} HITs, 
-workers prefer those HITs that have many available repetitions (that is,
-many more HITs of the same format, but with different data) 
-\cite{Chilton20101}.
-
-%Complex work consists of heterogeneous subtasks; when complex work is
-%broken down and workers perform sequences of very similar simple tasks
-%cognitive load is reduced, and workers are more efficient and accurate 
-%\cite{Adamczyk2004271,laseckieffects,kittur2011crowdforge}.
-%Thus, the tendency for workers to perform series of repetitive, similar
-%tasks would appear to be beneficial.
-
-The repetitive completion of tasks is of concern because people's responses
-to a prompt can be strongly influenced by their recent exposure to stimuli,
-due to \textit{priming} 
-\cite{BJOP1796}. %,No2007}. %,beller1971priming}.  
-Priming can arise when 
-a prior stimulus is conceptually or perceptually related to an ensuing 
-task, so the repetition of 
-similar tasks may create an opportunity for strong priming effects
-\cite{Gass1999549} %,sohn2001task}
-.
-
-%Researchers investigating a somewhat similar class of psychological phenomena,
-%found that ratings that microtask workers give to items in a list
-%depend on the order in which the list is presented, an effect known as
-%\textit{positional bias} \cite{lerman2014leveraging}.  This serves as an 
-%example of a basic psychological phenomenon impacting crowdsourced data,
-%and raises questions about what other cognitive biases might
-%affect microtask work, and how prevalent the induced bias might be.
-
-We investigate the potential for task repetition to induce bias in 
-a highly generalizeable microtask setup, in which workers label a 
-series of images.  If task-induced priming arises in our setup, 
-it should be expected in virtually every microtask and crowdsourced workflow
-where workers are called upon to exercise their judgment.
-Our results show that a worker's response during a task
-does indeed depend strongly on the tasks performed beforehand.   
-We call the effects that earlier tasks exert on later ones 
-\textit{intertask effects}.  If, as has been suggested \cite{5543192}, 
-microtask platforms are to be considered as a new form of computing 
-architecture, it will be necessary to consider that the computing elements 
-exhibit \textit{hysteresis}, meaning that microtask workers' outputs depend 
-on the \textit{history} of their inputs.
-
-%As we have described, microtask platforms have been widely adopted as a 
-%tool, but computer scientists also hold such platforms as the object of 
-%research, viewing  microtask platforms as a new kind of computing 
-%architecture.  In analogy to CPUs (central 
-%processing units) and GPUs (graphics processing units), 
-%Davis \textit{et al} invoked the \textit{human processing unit}, or HPU \cite{5543192}.
-%Researchers have sought to define a set of basic HPU operations, and
-%have developed libraries and frameworks to simplify HPU programming 
-%and make it more like CPU programming 
-%\cite{little2010turkit,minder2012crowdlang,kittur2011crowdforge}.  
-%As an example, one operation overcomes the inherent stochasticity of HPU 
-%outputs, by automatically aggregating votes from multiple HPUs under a single
-%function call.  
-%
-%But our revelation of strong intertask effects shows that, 
-%in addition to stochasticity, HPUs are subject to \textit{hysteresis}, 
-%meaning that their 
-%outputs depend on the history of their inputs.  Reproducibility and 
-%path-independence are crucial properties for the components of a 
-%computing architecture, so a better understanding of the computational 
-%ramifications of many psychological phenomena is needed.
-
-Our image-labeling tasks were performed on the MTurk microtask platform.  
-We chose image labeling because it is very common\footnote{
-	We discuss task composition in the supplementary text.
-},
-%\cite{chandler2013breaking,Finnerty2013},%,paolacci2010running},
-and because it is prototypical for any kind of task in which the worker is 
-asked to provide a response that is not precisely determined by 
-the prompt, but instead depends on the worker's judgment.  
-This includes such diverse tasks as describing video and audio recordings, 
-summarizing texts, or providing feedback to a product review.
-
-In our first experiment, called \textit{intertask-food-objects},
-workers were assigned to either a
-\textit{food} or \textit{objects} treatment.  Workers in both treatments
-performed a set of five \textit{initial tasks}, which each involved 
-providing descriptive labels for an image depicting 
-either food or (non-food) objects, depending on the worker's 
-treatment (Fig.~\ref{fig:task}A and B).  Following the initial 
-tasks, workers performed five \textit{test tasks}, which were identical for 
-both treatments.  In the the test tasks, workers labeled images depicting a 
-mixture of food and objects (Fig.~\ref{fig:task}C).  The five initial 
-and test tasks performed by each worker comprised one HIT\footnote{
-	Workers were only allowed to participate in one HIT relating to this study.
-}. The images were presented one at a time, and we made no 
-distinction between the initial and test tasks.
-
-The frequencies of words used by
-workers in the \textit{food} and \textit{objects} treatments differed
-significantly during test tasks (by $\chi^2$ test, $p = 6.0 \times 10^{-14}$),
-even though the test tasks were identical in both treatments\footnote{
-	see supplementary text for tabulated statistics.
-}.  Thus earlier tasks significant affect later ones, raising concerns 
-about the the microtask methodology itself.
-
-Having affirmed the \textit{existence} of intertask effects, we wish to
-understand the nature and severity of the bias thus induced.
-We therefore define the extent of bias, $\theta$, in terms of
-the strength of influence that a prior perturbation has on workers' responses.
-Since workers' responses are stochastic, we define the extent of bias in 
-terms of the change induced in the distribution of responses\footnote{
-	This is a general divergence metric between probability 
-	distributions known as the \textit{total variation distance.}
-}:
-\begin{equation}
-	\theta = \frac{1}{2}\sum_{x \in X} \left| p_0(x) - p_1(x) \right|,
-	\label{eq:theta}
-\end{equation}
-where $p_i(x)$ is the probability that a worker, subjected to treatment $i$,
-provides response $x$, from the set of possible responses $X$.
-A significant result from a $\chi^2$ test only allows us to conclude that 
-$\theta$ is non-zero (see supplementary text).  
-Determining $\theta$ from finite samples of responses, using purely 
-statistical approaches, is difficult (see supplementary text),
-which leads us to reformulate the
-problem in terms of classification: given a worker's 
-responses to test tasks, can a machine reliably infer what her prior exposure 
-had been?  Intuitively, the greater the effect that prior tasks have on 
-subsequent responses, the more accurate the classifier can be.  
-Formally (as shown in the supplementary text), the accuracy of such a 
-classifier, $\eta$, establishes a lower bound on the bias:
-\begin{equation}
-	\theta \geq 2\eta - 1.
-	\label{l1}
-\end{equation}
-By measuring the accuracy of a classifier, we can bound the 
-bias induced by any perturbation, including both intertask effects and 
-framing.  Bias ranges from 0 (meaning the exposures 
-does not affect the distribution of responses), to 1 
-(or 100\%) (meaning that the exposure leads workers to provide a completely
-different set of responses).
-
-\begin{figure}
-	\centering
-	\includegraphics[scale=0.6]{figs/images.pdf}
-	\caption{
-		Examples of images used in
-		initial tasks for the (\textbf{A}) \textit{food} and (\textbf{B}) 
-		\textit{objects} treatments of \textit{intertask-food-objects};
-		(\textbf{C}) test tasks for \textit{intertask-food-objects} and 
-		\textit{frame-food-objects};
-		initial tasks for the (\textbf{D}) \textit{food} and (\textbf{E}) 
-		\textit{culture} treatments of \textit{intertask-food-culture};
-		and (\textbf{F}) test tasks for \textit{intertask-food-culture} and 
-		\textit{frame-food-culture}.
-		The full set of experimental materials is shown in the 
-		supplementary text.
-	}
-
-	\label{fig:task}
-\end{figure}
-
-Using a na\"ive Bayes classifier\footnote{
-	We believe na\"ive Bayes is the best choice in this setting, as discussed
-	in the supplementary material, and we show results when a support vector
-	machine is used instead. 
-	We also discuss data preprocessing and show results for alternatives.
-}, we found that intertask effects 
-lead to a 30\% bias between workers from the \textit{food} and 
-\textit{objects} treatments (Fig.~\ref{fig:theta}A).  
-This represents a substantial potential to distort microtask data.
-
-There has been considerable interest in the effects that framing can have
-on microtask responses
-\cite{Kinnaird2012281,chandler2013breaking,thibodeau2013natural}, so,
-as a point of comparison, we describe a similar experiment 
-in which we framed the purpose of the tasks.  In the experiment 
-\textit{frame-food-objects}, the same test-tasks were used, but rather
-than exposing workers to initial tasks, workers were either told that 
-the tasks were ``Funded by the laboratory for the visual perception of Food 
-and Ingredients'', or ``\ldots of Objects and Tools''.  
-Framing did induce changes in the frequencies of 
-word usage at significance (as determined by $\chi^2$ test; $p=0.0012$), but 
-the \textit{extent} of framing-induced bias was not statistically 
-distinguishable from zero ($p =0.37$) (Fig.~\ref{fig:theta}A), and was
-weaker than the bias due to intertask effects ($p=2.1\times 10^{-5}$).
-
-To assess the persistence of intertask effects, we replicated the experiment
-\textit{intertask-food-objects} while permuting the test tasks, to reveal the 
-dependence of intertask effects on task position.
-We found that bias was strongest for the first test task (about 28\%), 
-but remained significant through all five test tasks 
-($\alpha=0.05$) sustaining over 12\% bias (Fig. \ref{fig:theta}B).
-
-We conducted variants of these experiments using different images, to see 
-whether this trend was robust.  In the experiment 
-\textit{intertask-food-culture},
-workers were either assigned to a \textit{food} or \textit{culture} treatment.
-The initial tasks contained either images 
-depicting food (Fig.~\ref{fig:task}D), or depictions of cultural scenes 
-(of dance, sport, or music) (Fig.~\ref{fig:task}E).  The test tasks, which 
-were, again, identical for both treatments, depicted meals of identifiable 
-cultural origin\footnote{
-	Despite efforts to the contrary, initial tasks 
-	in \textit{intertask-food-culture} are arguably still of
-	identifiable cultural origin, but this would only tend to make our 
-	results more conservative (we discuss this further in the supplementary 
-	text).
-}
-(Fig.~\ref{fig:task}F).
-
-Results for this experiment again showed a 
-strong bias as a result of intertask effects (about 50\%) 
-(Fig.~\ref{fig:theta}A).  Again, comparing intertask effects to 
-framing, the experiment (\textit{frame-food-culture}) used
-the same test tasks as in \textit{intertask-food-culture}, but exposed
-workers to statements framing the purpose of the tasks as the recognition 
-of either food or culture.  In this experiment, framing did not induce 
-significant changes in word frequencies (by $\chi^2$ test, $p=0.29$) (Fig.~\ref{fig:theta}A).
-
-It was only when framing was combined with an active reiteration step, 
-that bias reached a comparable extent to that induced by intertask effects.  
-In the experiment \textit{echo-food-objects},
-after framing the purpose of the task (as the recognition of food
-or objects), workers were asked to echo the purpose of the task
-using a combo-box input.  This  ``echoed framing'' induced a bias of about 
-35\% (Fig.~\ref{fig:theta}A). However, it is difficult to say whether this 
-should be considered as a framing treatment \textit{per se}.
-Requiring the worker to reiterate the purpose signals our intent, as the 
-requester, to ensure that the worker has taken note of it, possibly leading 
-the worker to interpret the exchange as an instruction.  
-In any case, it is remarkable that intertask effects
-were on par with an explicit, actively reinforced statement of purpose.
-
-\begin{figure}
-	\centering
-	\includegraphics[scale=1]{figs/theta.pdf}
-	\caption{
-		Empirical bias, $\theta_\mathrm{NB}$, measured using a na\"ive Bayes 
-		classifier, induced in image labeling tasks,
-		(\textbf{A}) by exposing workers to initial tasks or framing. 
-		As workers proceed through test tasks, the effects of initial tasks 
-		wane, as shown (\textbf{B}) for \textit{intertask-food-objects}, but 
-		remain significant even after five tasks.  Standard error bars are 
-		shown.
-	}
-	\label{fig:theta}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[scale=0.92]{figs/vocab_specificity.pdf}
-	\caption{
-		(\textbf{A}) Exposing workers to initial tasks or framing, 
-		involving food, changed the subsequent fraction of words that 
-		referred to food during test tasks, 
-		but did not always increase that fraction (in all three plots,
-		positive values indicate a larger quantity for food-exposed workers).
-		(\textbf{B}) The number of unique food-related
-		words (richness) was greater for food-exposed workers, except in the 
-		case of \textit{frame-food-culture} (stars indicate the threshold
-		for a significant deviation under the null hypothesis of equal 
-		richness, $\alpha=0.05$). 
-		(\textbf{C}) Food-exposed
-		workers used more specialized words to refer to food (see 
-		supplementary text for calculation of relative specialization).
-		Standard error bars are shown in (\textbf{A} and \textbf{C}).
-	}
-	\label{fig:specificity}
-\end{figure}
-
-To better understand the nature of 
-intertask effects, we investigated the vocabulary
-that workers used to label test tasks. One might expect that, within a given 
-experiment, the food-primed workers would label test tasks using 
-food-related words more often.  However, this was not generally 
-the case. In the \textit{intertask-food-culture} experiment, food-primed
-workers actually used significantly \textit{fewer} food-related words 
-during test tasks\footnote{
-	food-related words were identified using the wordnet corpus, 
-	augmented with additional words obtained by crawling a recipe website 
-	(see supplementary text for details).
-} (Fig.~\ref{fig:specificity}A).  This finding
-rules out a seemingly-simple idea that workers emphasize
-content that has been present in earlier tasks: seeing content 
-influences, but does not necessarily \textit{increase}, the probability of 
-referring to it in subsequent tasks.
-
-To deepen our understanding, we investigated workers' lexical richness in 
-reference to food, that is, the number of \textit{unique} food-related words
-used.  Even if workers provide an abundance of food-related words, there
-can be less diversity, if, for example, workers repeat generic references 
-to food.
-Both \textit{intertask} experiments showed that food-exposed workers had 
-greater lexical richness, in reference to food, than their counterparts 
-(as much as 20\% more) (Fig.~\ref{fig:specificity}B).  
-This is particularly noteworthy in the experiment
-\textit{intertask-food-culture}, because there
-food-primed workers made fewer total references to food.  
-%We also observed enrichment of the food-related lexicon in the 
-%\textit{priming-food-objects}, and \textit{echo-food-objects} experiments, 
-%although to a lesser extent.
-
-The observations regarding lexical richness suggest that 
-initial tasks might influence workers to use more refined or specialized 
-words, when referring to aspects of content that had been present in the 
-initial tasks.  
-To test this, we used the wordnet corpus to operationalize the 
-notion of word specialization.  Wordnet establishes relationships between
-117,798 English nouns, indicating which words are specializations
-(or generalizations) of others \cite{felbaum1998wordnet}. 
-%miller1995wordnet,}.  
-For example, ``pumpernickel'' is a specialization of ``bread''.
-Within each experiment, we determined the percent-excess of food-related
-words that were more specialized in the food-exposed treatment relative
-to the other treatment (detailed calculation in the supplementary text).
-
-In all experiments except \textit{frame-food-culture}, food-primed workers 
-were used significantly more specialized words, in reference to food 
-(about 15\% more) (Fig.~\ref{fig:specificity}C).
-It is interesting that such substantial increases in both the lexical 
-richness and specialization of food-related words 
-held for \textit{intertask-food-culture}, where, as mentioned, we observed 
-that food-exposed workers made \textit{fewer} references to food overall. 
-These observations point 
-to countervailing factors: one factor tending to activate the more 
-specialized and less common food-related words 
-(yielding greater lexical richness and specialization), and the other tending 
-to suppress certain, presumably more common and generic words 
-(yielding fewer food-related words in total).
-
-This hypothesis is corroborated when we look at those words whose 
-frequencies changed the most from one treatment to another 
-(Table~S\ref{table:top-words}).  
-The word ``food'', which is the most generic possible food-related word, was 
-always \textit{suppressed} among food-primed workers.  In fact, 
-for all experiments, ``food'' was the \textit{most suppressed} word.
-
-Our results can be 
-explained through a combination of positive and negative priming.
-Positive priming (usually simply ``priming'') occurs when a prior stimulus 
-predisposes a person to give certain responses in an ensuing task, and
-is often observed as an increase in the speed or accuracy of a response, or
-the ability to recognize briefer or noisier stimuli 
-\cite{BJOP1796,BJOP1826,Huber2008324}.
-Negative priming occurs when, after exposure to a stimulus 
-considered to be non-salient, subsequent recognition of the stimulus is 
-inhibited \cite{mayr2007negative}.
-
-Workers exposed to images containing food are (positively) primed, 
-activating memories, concepts, and vocabulary related to food.  
-However, if the worker labels several images containing food, the basic 
-fact that an image contains food will not seem salient, since it 
-does not distinguish one image from another.  Thus, the most 
-generic references to that fact, such as the label ``food'', 
-will be suppressed, while more specialized references will be elicited.  
-Meanwhile, the number of references to food overall might increase or 
-decrease, depending on the balance of these factors.
-
-More generally, we are suggesting that, even though workers are not 
-instructed to compare tasks in any way, prior tasks form a 
-context relative to which workers judge salience.  Thus, due to a combination 
-of negative and positive priming, a worker's focus 
-in repeated tasks tends to be directed away from generic, shared features, 
-toward specific and distinguishing ones.
-
-Prior to this study, little thought appears to have been given to
-earlier tasks as a priming vector for later tasks.
-But our findings show this is an important design consideration.  
-One recourse might be to randomize task ordering, a practice that is 
-commonly employed.  But the sheer extent of bias we observed suggests that 
-this will still admit a significant amount of noise.  
-Even chains of two or three similar tasks, which
-will not be reliably eliminated in random permutations, could lead
-to the levels of bias we observed in our experiments.
-Preferably, a deeper understanding of intertask effects might allow them
-to be properly controlled.
-
-Our findings also suggest that careful task engineering might leverage
-intertask effects to achieve greater quality and reproducibility in 
-crowdsourcing.
-A consistent goal in human computation is the achievement of expert-level
-judgments from non-expert workers \cite{kittur2011crowdforge}.  
-This has been achieved in some
-applications \cite{snow2008cheap,Mortensen20131020,Warby2014385}. 
-The distinction between experts and novices is partly attributable
-to specialized knowledge and heuristics. 
-But experts also simplify tasks by more efficiently directing 
-their focus toward salient features \cite{kellman2009perceptual}.  
-Using strategic task exposure, it might be possible to guide workers' focus 
-and salience attribution, enabling expert-level judgment in a wider variety of
-crowdsourced applications.
-We anticipate future work will yield techniques to control intertask 
-effects, to reduce unwanted bias, and to tune the focus, diversity, and 
-specificity of worker responses.
-
-We have shown that a severe bias can be introduced into microtask 
-responses, simply from the performance of earlier tasks. 
-These effects are much stronger than those of framing.  
-While our findings raise serious concerns about the 
-current state of microtask design, they reveal potential opportunities 
-to refine worker focus and acuity.  Any application that relies
-on the repetitive use of human judgment is likely subject to the phenomena
-described here.  Exploring the pitfalls and opportunities posed by
-intertask effects is an important direction for future work, 
-in the effort to develop performant and reliable human computation.
-\bibliography{newbib}
-\bibliographystyle{Science}
-
-\pagebreak
 \section*{Supplementary Material}
@@
 \paragraph{Statistical approaches to measuring bias.}
-Recall that Eq.~\ref{eq:theta} in the main text defined the
+Recall that Eq.~1 in the main text defined the
 extent of bias between the microtask responses from two groups
@@
 the worker belongs ($P_0$ or $P_1$), will do so with an accuracy, $\eta$,
-that is bounded according to Eq.~\ref{l1} from the main text 
+that is bounded according to Eq.~2 from the main text 
 (reproduced here):
@@
 other, once we have conditioned on the class under observation 
-%\cite{bishop2006} 
-(i.e. the priming treatment).  This
+\cite{bishop2006} (i.e. the priming treatment).  This
 conditional independence assumption is made for
@@
 appropriate to look at what affect these decisions had, \textit{post-hoc}.  
-We reproduce the plot from Fig.~\ref{fig:theta}A in the main text, 
+We reproduce the plot from Fig.~2A in the main text, 
 this time using different combinations of preprocessing options,
@@
 na\"ive Bayes classifier and our particular choice of preprocessing steps, 
-as shown in Fig.~\ref{fig:theta} of the main text, are representative.
+as shown in in Fig.~2A of the main text, are representative.
 
@@
 To determine the confidence intervals for measured $\theta$ values we 
-use the exact Clopper-Pearson method. % \cite{clopper1934use}.  
+use the exact Clopper-Pearson method \cite{clopper1934use}.  
 Based on the observed number of successes, $X$, we calculate 
@@
 The statistics collected for the measurement of $\theta$, corresponding to
-Figs.~\ref{fig:theta}A and B are tabulated in Tables~S\ref{table:theta} and
+Figs.~2A and B are tabulated in Tables~S\ref{table:theta} and
 S\ref{table:theta_pos} respectively.
@@
 	Next, words were lemmatized using the
-	wordnet lemmatizer \cite{felbaum1998wordnet}.  %miller1995wordnet,
+	wordnet lemmatizer \cite{miller1995wordnet,felbaum1998wordnet}.  
 	Common words such as ``the'', ``to'', or ``with'', were found using
-	the natural language toolkit (NLTK) English stop word list 
-	\cite{loper2002nltk} and removed.
+	NLTK's English stop word list \cite{loper2002nltk} and removed.
 

### 2015-04-27 docs/publications/2015.04_PNAS/man.tex
EN edits to PNAS 2015.04

@@
 %\usepackage{pnastwoF}
+
+\usepackage{xr}
+\externaldocument[S]{supp}
+\usepackage{dcolumn}
+\usepackage{multirow}
+\usepackage{booktabs}
+\newcolumntype{d}{D{.}{.}{4.0}}
+\newcolumntype{s}{D{.}{.}{1.4}}
 
@@
 identifiable cultural origin (Fig.~\ref{fig:task}F).  As an aside, we recognize
-that, despite efforts to the contrary, initial tasks in
+that, despite efforts to the contrary, initial tasks in the food treatment of
 \textit{intertask-food-culture} are arguably still of identifiable cultural
@@
 statements framing the purpose of the tasks as the recognition of either food
-or culture.  In this experiment, framing did not induce significant changes in
-word frequencies (by $\chi^2$ test, $p=0.29$) (Fig.~\ref{fig:theta}A).
+or culture.  Again, we found that framing effects were weaker than 
+intertask effects ($p=7.6\times10^{-7}$).  In fact, framing did not induce 
+significant changes in word frequencies (by $\chi^2$ test, $p=0.29$) 
+(Fig.~\ref{fig:theta}A).
 
@@
 This hypothesis is corroborated when we look at those words whose frequencies
-changed the most from one treatment to another (Table~S\ref{table:top-words}).
-The word ``food'', which is the most generic possible food-related word, was
-always \textit{suppressed} among food-primed workers, relative to the
-non-food-primed workers.  In fact, for all experiments, ``food'' was the
-\textit{most suppressed} word.
+changed the most from one treatment to another (Table~\ref{table:top-words}).
+As one would expect, references to objects, such as ``candle'', ``fork'', 
+or ``statue'' appear less frequently among the labels provided by workers in 
+food-exposed treatments.  But, the food-exposed workers also provide the most
+generic references to to food less often, such as the word ``food'' itself, 
+or ``meal''.  
+In fact, the word ``food'', which is the most generic possible food-related 
+word, was always \textit{the most suppressed} among food-primed workers, 
+relative to their non-food-primed counterparts.  
+Meanwhile, food-exposed workers provide more specific references to food more 
+often, such as ``coffee'', ``cheese'', or ``wine''.
+
+\begin{table*}
+	\centering
+	\setlength{\tabcolsep}{4pt}
+	\begin{tabular}{ c c c c c }
+
+		\setlength{\tabcolsep}{4pt}
+		\begin{tabular}{ r | c }
+		\toprule
+		\multicolumn{2}{c}{
+			\parbox[c]{2.5cm}{
+				\centering
+					\textit{intertask-food-objects}
+			}} \\
+		\midrule
+		coffee & 38 \\
+		meal & 34 \\
+		cheese & 34 \\
+		apple & 32 \\
+		dessert & 21 \\
+		cup & -30 \\
+		glass & -45 \\
+		table & -70 \\
+		candle & -74 \\
+		food & -80 \\
+		\bottomrule
+		\end{tabular}
+
+&
+
+		\setlength{\tabcolsep}{4pt}
+		\begin{tabular}{ r | c }
+		\toprule
+		\multicolumn{2}{c}{
+			\parbox[c]{2.5cm}{
+				\centering
+				\textit{frame-food-objects}
+			}
+		}\\
+		\midrule
+		bread & 18 \\
+		wine & 18 \\
+		cheese & 16 \\
+		apple & 14 \\
+		oil & 12 \\
+		table & -9 \\
+		meal & -10 \\
+		candle & -12 \\
+		dinner & -13 \\
+		food & -32 \\
+		\bottomrule
+		\end{tabular}
+
+&
+
+		\setlength{\tabcolsep}{4pt}
+		\begin{tabular}{ r | c }
+		\toprule
+		\multicolumn{2}{c}{
+			\parbox[c]{2.3cm}{
+				\centering
+			\textit{echo-food-objects}} 
+		}\\
+		\midrule
+		apple & 24 \\
+		cheese & 23 \\
+		wine & 15 \\
+		coffee & 14 \\
+		oil & 7 \\
+		knife & -24 \\
+		dinner & -26 \\
+		fork & -27 \\
+		candle & -35 \\
+		food & -55 \\
+		\bottomrule
+		\end{tabular}
+
+&
+
+		\setlength{\tabcolsep}{4pt}
+		\begin{tabular}{ r | c }
+		\toprule
+		\multicolumn{2}{c}{
+			\parbox[c]{2.5cm}{
+				\centering
+			\textit{intertask-food-culture}} 
+			\smallskip
+		}\\
+
+		\midrule
+		spicy & 26 \\
+		sauce & 17 \\
+		indian & 15 \\
+		buffet & 14 \\
+		exotic & 12 \\
+		festival & -11 \\
+		offering & -12 \\
+		statue & -15 \\
+		india & -20 \\
+		food & -56 \\
+		\bottomrule
+		\end{tabular}
+
+&
+
+		\setlength{\tabcolsep}{4pt}
+		\begin{tabular}{ r | c }
+		\toprule
+		\multicolumn{2}{c}{
+			\parbox[c]{2.5cm}{
+				\centering
+			\textit{frame-food-culture}} 
+		}\\
+		\noalign{\smallskip}
+		\midrule
+		indian & 11 \\
+		banquet & 8 \\
+		spicy & 7 \\
+		asian & 6 \\
+		variety & 6 \\
+		delicious & -6 \\
+		meat & -7 \\
+		festival & -7 \\
+		spice & -7 \\
+		food & -9 \\
+		\bottomrule
+		\end{tabular}
+
+	\end{tabular}
+	\caption{
+		The five words whose frequencies increased, and those whose 
+		frequencies decreased, the most, between treatments of given 
+		experiments, within labels attributed to the first test task.
+		Positive values indicate that the food-exposed treatment
+		used the word with higher frequency.  
+		Note that the word ``food'' is always the most suppressed among
+		food-exposed workers.
+		Word frequencies for 
+		\textit{intertask-food-objects} correspond to the labels attributed
+		to image 1 (see Fig. \ref{Sfig:task1:test}) which is not necessarily 
+		the first 
+		test task due to the tasks being permuted.  There were five times
+		as many workers in \textit{intertask-food-objects}, hence
+		larger absolute differences are observed.
+	}
+	\label{table:top-words}
+\end{table*}
 
@@
 Turk (MTurk) platform.  The flow of events experienced by a worker when
-participating in this study is depicted in Fig.~S\ref{fig:task_schematic}.
+participating in this study is depicted in Fig.~S\ref{Sfig:task_schematic}.
 Each experiment was divided into two treatments.  Treatments for a given
 experiment differed with respect to a particular priming modality, which served
-as the independent variable (as specified in Table~S\ref{table:experiments}).
+as the independent variable (as specified in Table~S\ref{Stable:experiments}).
 The HITs for treatments of the same experiment always involved the same test
@@
 was shown on a slide immediately after the instructions (Fig.
-S\ref{fig:hit_preamble}B and C).  Initial tasks, when included, followed next.
+S\ref{Sfig:hit_preamble}B and C).  Initial tasks, when included, followed next.
 The initial tasks consisted of a series of five slides, each containing an
-image-labeling task like the one shown in Fig.~S\ref{fig:hit_preamble}D.
+image-labeling task like the one shown in Fig.~S\ref{Sfig:hit_preamble}D.
 Finally, for all HITs, five slides were shown containing test tasks, in the
@@
 sub-treatments, in which the test tasks were permuted.  The permutations were
-obtained by rotating the order shown in Fig.~S\ref{fig:task1:test} by different
+obtained by rotating the order shown in Fig.~S\ref{Sfig:task1:test} by different
 amounts.  For example, rotating by one position involves moving the first image
@@
 \section{Selection of images} The images used in the initial tasks for
-\textit{intertask-food-objects}  are shown in Figs.~S\ref{fig:task1:food}
-(\textit{food} treatment) and S\ref{fig:task1:obj} (\textit{objects}
+\textit{intertask-food-objects}  are shown in Figs.~S\ref{Sfig:task1:food}
+(\textit{food} treatment) and S\ref{Sfig:task1:obj} (\textit{objects}
 treatment).  We took care to exclude objects from the food-images (except for
@@
 \textit{intertask-food-objects} and \textit{frame-food-objects} are shown in
-Fig.~S\ref{fig:task1:test}.
+Fig.~S\ref{Sfig:task1:test}.
 
 The images used in the initial tasks for \textit{intertask-food-culture} are
-shown in Figs.~S\ref{fig:task2:food} (\textit{food} treatment) and
-S\ref{fig:task2:cult} (\textit{culture} treatment).  We selected the initial
-images for the treatments of this experiment to respectively reflect depict
+shown in Figs.~S\ref{Sfig:task2:food} (\textit{food} treatment) and
+S\ref{Sfig:task2:cult} (\textit{culture} treatment).  We selected the initial
+images for the treatments of this experiment to respectively depict
 food and culture.  Naturally, since food is a very important aspect of culture,
@@
 \textit{intertask-food-culture} and \textit{frame-food-culture} are shown in
-Fig.~S\ref{fig:task2:test}.
+Fig.~S\ref{Sfig:task2:test}.
 
@@
 of the HIT, that suggested a particular purpose for the tasks.  The precise
-language used is shown in Table~S\ref{table:experiments}, and an example of a
-framing slide is shown in Fig.~S\ref{fig:hit_preamble}B and C.  In
+language used is shown in Table~S\ref{Stable:experiments}, and an example of a
+framing slide is shown in Fig.~S\ref{Sfig:hit_preamble}B and C.  In
 \textit{frame-food-objects} and \textit{frame-food-culture}, the framing
@@
 this task is \dots''), and then required the worker to echo back the purpose of
-the task by selecting it from a combo box Fig.~S\ref{fig:hit_preamble}C.
+the task by selecting it from a combo box Fig.~S\ref{Sfig:hit_preamble}C.
 
@@
 our study.
+
+\section{Derivation of bias inequality}
+A sketch of the derivation of the lower bound on the degree of bias 
+$\theta$ in terms of the observed accuracy of a classifier, $\eta$, follows
+(see the supplementary material for a detailed derivation). 
+Consider the accuracy of the best possible classifier, $\eta^*$.  
+Assume two groups of workers, have been
+exposed to different treatments, 1 and 2, and as a result have
+a different probability of yielding response $x$ during a task: 
+$p_1(x)$ and $p_2(x)$.  Upon observing response $x$, it is optimal to guess 
+that the worker came from the treatment that produces response $x$ more 
+often: i.e. to guess $z=\arg\max_z(p_z(x))$.
+
+The probability that this guess is correct is:
+\begin{align}
+	\Pr\{\mathrm{correct}\vert x\} 	&= \frac{1}{2} + \frac{|p_0(x') - p_1(x')|}{2 \big(p_0(x') + p_1(x') \big)}.
+\end{align}
+The probability that the optimal classifier will be correct in general,
+which is by definition $\eta^*$, can be found by summing over all values of 
+$x$:
+
+\begin{align}
+	\eta^* &= \sum_{x' \in \mathcal{X}} \mathrm{Pr}\{\mathrm{correct}\vert x'\}
+			\mathrm{Pr}\{x'\} \\
+		&= \sum_{x'\in X} \left(
+				\frac{1}{2} + 
+				\frac{|p_0(x') - p_1(x')|}{2 \big(p_0(x') + p_1(x') \big)}
+			\right)
+			\left(
+				\frac{p_0(x') + p_1(x')}{2}
+			\right)\\
+		&= \frac{1 + \theta}{2}\\
+		\implies \theta &= 2\eta^* - 1.
+\end{align}
+
+Since no classifier can be more accurate than the optimal classifier, we 
+obtain the bound stated in Eq.~\ref{l1}.
 

### 2015-04-27 docs/publications/2015.04_PNAS/man.tex
additional EN edits to 2015.04_PNAS man.tex; add supp_with_man.tex

@@
 		frequencies decreased, the most, between treatments of given 
-		experiments, within labels attributed to the first test task.
-		Positive values indicate that the food-exposed treatment
+		experiments.  The label frequencies shown apply to the first test
+		task.  Positive values indicate that the food-exposed treatment
 		used the word with higher frequency.  
 		Note that the word ``food'' is always the most suppressed among
-		food-exposed workers.
-		Word frequencies for 
+		food-exposed workers.  Word frequencies for 
 		\textit{intertask-food-objects} correspond to the labels attributed
@@
 \begin{align}
-	\Pr\{\mathrm{correct}\vert x\} 	&= \frac{1}{2} + \frac{|p_0(x') - p_1(x')|}{2 \big(p_0(x') + p_1(x') \big)}.
+	\Pr\{\mathrm{correct}\vert x\} 	&= \frac{1}{2} + \frac{|p_0(x) - p_1(x)|}{2 \big(p_0(x) + p_1(x) \big)}.
 \end{align}
 The probability that the optimal classifier will be correct in general,
-which is by definition $\eta^*$, can be found by summing over all values of 
-$x$:
+which is by definition $\eta^*$, can be found by summing over all possible
+responses $x \in \mathcal{X}$:
 
 \begin{align}
-	\eta^* &= \sum_{x' \in \mathcal{X}} \mathrm{Pr}\{\mathrm{correct}\vert x'\}
-			\mathrm{Pr}\{x'\} \\
-		&= \sum_{x'\in X} \left(
+	\eta^* &= \sum_{x \in \mathcal{X}} \mathrm{Pr}\{\mathrm{correct}\vert x\}
+			\mathrm{Pr}\{x\} \\
+		&= \sum_{x\in X} \left(
 				\frac{1}{2} + 
-				\frac{|p_0(x') - p_1(x')|}{2 \big(p_0(x') + p_1(x') \big)}
+				\frac{|p_0(x) - p_1(x)|}{2 \big(p_0(x) + p_1(x) \big)}
 			\right)
 			\left(
-				\frac{p_0(x') + p_1(x')}{2}
+				\frac{p_0(x) + p_1(x)}{2}
 			\right)\\
-		&= \frac{1 + \theta}{2}\\
-		\implies \theta &= 2\eta^* - 1.
+		&= \frac{1 + \theta}{2}
 \end{align}

### 2015-04-27 docs/publications/2015.04_PNAS/supp_with_man.tex
additional EN edits to 2015.04_PNAS man.tex; add supp_with_man.tex

--- 2015-02-18 docs/publications/2014.09_SCIENCE/man.tex
@@
 quality annotations. Here we identify a feature of nearly all crowdsourcing 
-jobs that acts as a strong systemic source of bias. 
+jobs that acts as a strong, systemic source of bias. 
 Microtask jobs typically consist of a sequence 
@@
 Understanding these \textit{intertask effects} is crucial 
-to embracing micratask platforms in critical applications.
+to embracing microtask platforms in critical applications.
 While intertask effects can be a source of systematic bias, 

### 2015-04-27 docs/publications/2015.04_PNAS/supp.tex
correct supplementary material

@@
 \usepackage{arydshln}
+\usepackage{xr}
+\externaldocument{man}
 
@@
 \paragraph{Statistical approaches to measuring bias.}
-Recall that Eq.~1 in the main text defined the
+Recall that Eq.~\ref{eq:theta} in the main text defined the
 extent of bias between the microtask responses from two groups
@@
 the worker belongs ($P_0$ or $P_1$), will do so with an accuracy, $\eta$,
-that is bounded according to Eq.~2 from the main text 
+that is bounded according to Eq.~\ref{l1} from the main text 
 (reproduced here):
@@
 appropriate to look at what affect these decisions had, \textit{post-hoc}.  
-We reproduce the plot from Fig.~2A in the main text, 
+We reproduce the plot from Fig.~\ref{fig:theta}A in the main text, 
 this time using different combinations of preprocessing options,
@@
 na\"ive Bayes classifier and our particular choice of preprocessing steps, 
-as shown in in Fig.~2A of the main text, are representative.
+as shown in Fig.~\ref{fig:theta} of the main text, are representative.
 
@@
 The statistics collected for the measurement of $\theta$, corresponding to
-Figs.~2A and B are tabulated in Tables~S\ref{table:theta} and
+Figs.~\ref{fig:theta}A and B are tabulated in Tables~S\ref{table:theta} and
 S\ref{table:theta_pos} respectively.
@@
 \subsection*{Analysis of worker vocabulary}
-\paragraph{Most suppressed and activated terms.}
-The words whose frequencies differed most between the treatments of given 
-experiments are shown in Table~S\ref{table:top-words}.  Note that 
-the word that was most suppressed in food-exposed treatments was always 
-``food''.
-
-\begin{table}
-	\centering
-	\setlength{\tabcolsep}{4pt}
-	\begin{tabular}{ c c c c c }
-
-		\setlength{\tabcolsep}{4pt}
-		\begin{tabular}{ r | c }
-		\toprule
-		\multicolumn{2}{c}{
-			\parbox[c]{2.5cm}{
-				\centering
-					\textit{intertask-food-objects}
-			}} \\
-		\midrule
-		coffee & 38 \\
-		meal & 34 \\
-		cheese & 34 \\
-		apple & 32 \\
-		dessert & 21 \\
-		cup & -30 \\
-		glass & -45 \\
-		table & -70 \\
-		candle & -74 \\
-		food & -80 \\
-		\bottomrule
-		\end{tabular}
-
-&
-
-		\setlength{\tabcolsep}{4pt}
-		\begin{tabular}{ r | c }
-		\toprule
-		\multicolumn{2}{c}{
-			\parbox[c]{2.5cm}{
-				\centering
-				\textit{frame-food-objects}
-			}
-		}\\
-		\midrule
-		bread & 18 \\
-		wine & 18 \\
-		cheese & 16 \\
-		apple & 14 \\
-		oil & 12 \\
-		table & -9 \\
-		meal & -10 \\
-		candle & -12 \\
-		dinner & -13 \\
-		food & -32 \\
-		\bottomrule
-		\end{tabular}
-
-&
-
-		\setlength{\tabcolsep}{4pt}
-		\begin{tabular}{ r | c }
-		\toprule
-		\multicolumn{2}{c}{
-			\parbox[c]{2.5cm}{
-				\centering
-			\textit{echo-food-objects}} 
-		}\\
-		\midrule
-		apple & 24 \\
-		cheese & 23 \\
-		wine & 15 \\
-		coffee & 14 \\
-		oil & 7 \\
-		knife & -24 \\
-		dinner & -26 \\
-		fork & -27 \\
-		candle & -35 \\
-		food & -55 \\
-		\bottomrule
-		\end{tabular}
-
-&
-
-		\setlength{\tabcolsep}{4pt}
-		\begin{tabular}{ r | c }
-		\toprule
-		\multicolumn{2}{c}{
-			\parbox[c]{2.5cm}{
-				\centering
-			\textit{intertask-food-culture}} 
-		}\\
-		\midrule
-		spicy & 26 \\
-		sauce & 17 \\
-		indian & 15 \\
-		buffet & 14 \\
-		exotic & 12 \\
-		festival & -11 \\
-		offering & -12 \\
-		statue & -15 \\
-		india & -20 \\
-		food & -56 \\
-		\bottomrule
-		\end{tabular}
-
-&
-
-		\setlength{\tabcolsep}{4pt}
-		\begin{tabular}{ r | c }
-		\toprule
-		\multicolumn{2}{c}{
-			\parbox[c]{2.5cm}{
-				\centering
-			\textit{frame-food-culture}} 
-		}\\
-		\noalign{\smallskip}
-		\midrule
-		indian & 11 \\
-		banquet & 8 \\
-		spicy & 7 \\
-		asian & 6 \\
-		variety & 6 \\
-		delicious & -6 \\
-		meat & -7 \\
-		festival & -7 \\
-		spice & -7 \\
-		food & -9 \\
-		\bottomrule
-		\end{tabular}
-
-	\end{tabular}
-	\caption{
-		The five words whose frequencies increased, and those whose 
-		frequencies decreased, the most, between treatments of given 
-		experiments, within labels attributed to the first test task.
-		Positive values indicate that the food-exposed treatment
-		used the word with higher frequency.  
-		Note that the word ``food'' is always the most suppressed among
-		food-exposed workers.
-		Word frequencies for 
-		\textit{intertask-food-objects} correspond to the labels attributed
-		to image 1 (see Fig. \ref{fig:task1:test}) which is not necessarily 
-		the first 
-		test task due to the tasks being permuted.  There were five times
-		as many workers in \textit{intertask-food-objects}, hence
-		larger absolute differences are observed.
-	}
-	\label{table:top-words}
-\end{table}
 

### 2015-09-10 docs/publications/2015.08_CHI/man.tex
add chi manuscript

--- 2015-02-18 docs/publications/2014.09_SCIENCE/man.tex
@@
-% ULaTeX2e, calling the article.cls class and 12-point type.
-
-\documentclass[12pt]{article}
+\documentclass{sigchi}
+
+% Use this command to override the default ACM copyright statement
+% (e.g. for preprints).  Consult the conference website for the
+% camera-ready copyright statement.
+
+%% EXAMPLE BEGIN -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)
+% \toappear{Permission to make digital or hard copies of all or part of this work for personal or classroom use is      granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page.
+Copyrights for components of this work owned by others than ACM must be honored.
+Abstracting with credit is permitted.
+To copy otherwise, or republish, to post on servers or to redistribute to lists, requires prior specific permission and/or a fee.
+Request permissions from permissions@acm.org.
+\\
+% {\emph{CHI'14}}, April 26--May 1, 2014, Toronto, Canada. \\
+% Copyright \copyright~2014 ACM ISBN/14/04...\$15.00. \\
+% DOI string from ACM form confirmation}
+%% EXAMPLE END -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)
+
+% Arabic page numbers for submission.  Remove this line to eliminate
+% page numbers for the camera ready copy
+
+%\pagenumbering{arabic}
+
+% Load basic packages
+\usepackage{balance}  % to better equalize the last page
+\usepackage{graphics} % for EPS, load graphicx instead 
+%\usepackage[T1]{fontenc}
+\usepackage{txfonts}
+\usepackage{times}    % comment if you want LaTeX's default font
+\usepackage[pdftex]{hyperref}
+% \usepackage{url}      % llt: nicely formatted URLs
+\usepackage{color}
+\usepackage{textcomp}
+\usepackage{booktabs}
+\usepackage{ccicons}
+\usepackage{todonotes}
 
 % My packages
-
-\usepackage{amsmath}
-\usepackage{framed, color}
-\usepackage{soul}
-\definecolor{blu}{rgb}{0,0,1}
-\newcommand{\td}[1]{{\color{blu}\hl{TODO: #1}}}
-\usepackage{graphicx}
-\usepackage{amsthm}
-\newtheorem{mydef}{Definition}
 \usepackage{dcolumn}
 \usepackage{multirow}
-\usepackage{booktabs}
 \newcolumntype{d}{D{.}{.}{4.0}}
 \newcolumntype{s}{D{.}{.}{1.4}}
-
 \usepackage{arydshln}
 
-% Users of the {thebibliography} environment or BibTeX should use the
-% scicite.sty package, downloadable from *Science* at
-% www.sciencemag.org/about/authors/prep/TeX_help/ .
-% This package should properly format in-text
-% reference calls and reference-list numbers.
-
-\usepackage{scicite}
-
-% Use times if you have the font installed; otherwise, comment out the
-% following line.
-
-\usepackage{times}
-
-% The preamble here sets up a lot of new/revised commands and
-% environments.  It's annoying, but please do *not* try to strip these
-% out into a separate .sty file (which could lead to the loss of some
-% information when we convert the file to other formats).  Instead, keep
-% them in the preamble of your main LaTeX source file.
-
-% The following parameters seem to provide a reasonable page setup.
-
-\topmargin 0.0cm
-\oddsidemargin 0.2cm
-\textwidth 16cm 
-\textheight 21cm
-\footskip 1.0cm
-
-%The next command sets up an environment for the abstract to your paper.
-
-\newenvironment{sciabstract}{%
-\begin{quote} \bf}
-{\end{quote}}
-
-% If your reference list includes text notes as well as references,
-% include the following line; otherwise, comment it out.
-
-\renewcommand\refname{References and Notes}
-
-% The following lines set up an environment for the last note in the
-% reference list, which commonly includes acknowledgments of funding,
-% help, etc.  It's intended for users of BibTeX or the {thebibliography}
-% environment.  Users who are hand-coding their references at the end
-% using a list environment such as {enumerate} can simply add another
-% item at the end, and it will be numbered automatically.
-
-\newcounter{lastnote}
-\newenvironment{scilastnote}{%
-\setcounter{lastnote}{\value{enumiv}}%
-\addtocounter{lastnote}{+1}%
-\begin{list}%
-{\arabic{lastnote}.}
-{\setlength{\leftmargin}{.22in}}
-{\setlength{\labelsep}{.5em}}}
-{\end{list}}
-
-% Include your paper's title here
-
-\title{Hysteresis in human computation:\\ how one task affects another}
-
-% Place the author information here.  Please hand-code the contact
-% information and notecalls; do *not* use \footnote commands.  Let the
-% author contact information appear immediately below the author names
-% as shown.  We would also prefer that you don't change the type-size
-% settings shown here.
-
-\author
-{Edward Newell \\ Derek Ruths\\
-\\
-\normalsize{\texttt{edward.newell@mail.mcgill.ca}}\\
-\normalsize{\texttt{derek.ruths@mcgill.ca}}\\
-\normalsize{School of Computer Science, McGill University,}\\
-\normalsize{3480 University Street, Room 318, Montreal, Quebec, Canada, H3A 2A7}\\
-\\
-}
-
-% Include the date command, but leave its argument blank.
-
-\date{}
-
-%%%%%%%%%%%%%%%%% END OF PREAMBLE %%%%%%%%%%%%%%%%
-
+% llt: Define a global style for URLs, rather that the default one
+\makeatletter
+\def\url@leostyle{%
+  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\bf\ttfamily}}}
+\makeatother
+\urlstyle{leo}
+
+% To make various LaTeX processors do the right thing with page size.
+\def\pprw{8.5in}
+\def\pprh{11in}
+\special{papersize=\pprw,\pprh}
+\setlength{\paperwidth}{\pprw}
+\setlength{\paperheight}{\pprh}
+\setlength{\pdfpagewidth}{\pprw}
+\setlength{\pdfpageheight}{\pprh}
+
+% Make sure hyperref comes last of your loaded packages, to give it a
+% fighting chance of not being over-written, since its job is to
+% redefine many LaTeX commands.
+\definecolor{linkColor}{RGB}{6,125,233}
+\hypersetup{%
+  pdftitle={SIGCHI Conference Proceedings Format},
+  pdfauthor={LaTeX},
+  pdfkeywords={SIGCHI, proceedings, archival format},
+  bookmarksnumbered,
+  pdfstartview={FitH},
+  colorlinks,
+  citecolor=black,
+  filecolor=black,
+  linkcolor=black,
+  urlcolor=linkColor,
+  breaklinks=true,
+}
+
+% create a shortcut to typeset table headings
+% \newcommand\tabhead[1]{\small\textbf{#1}}
+
+% End of preamble. Here it comes the document.
 \begin{document}
 
-% Double-space the manuscript.
-
-\baselineskip24pt
-
-% Make the title.
+\title{How One Microtask Affects Another}
+
+\numberofauthors{3}
+\author{%
+  \alignauthor{Edward Newell\\
+    \affaddr{Network Dynamics Group\\
+	School of Computer Science\\ McGill University}\\
+    \affaddr{Montreal, Qu\'ebec}\\
+    \email{e-mail address}}\\
+  \alignauthor{2nd Author Name\\
+    \affaddr{Affiliation}\\
+    \affaddr{City, Country}\\
+    \email{e-mail address}}\\
+  \alignauthor{3rd Author Name\\
+    \affaddr{Affiliation}\\
+    \affaddr{City, Country}\\
+    \email{e-mail address}}\\
+}
 
@@
 
-% Place your abstract within the special {sciabstract} environment.
-
-\begin{sciabstract}
+\begin{abstract}
 Microtask platforms are becoming commonplace tools for performing human
@@
 A topic of ongoing research concerns designing jobs that elicit high
-quality annotations. Here we identify a feature of nearly all crowdsourcing 
-jobs that acts as a strong systemic source of bias. 
+quality annotation.
+Here we identify a feature of nearly all crowdsourcing 
+jobs that profoundly impacts workers' responses.
 Microtask jobs typically consist of a sequence 
@@
 Using image-labeling, a canonical microtask job format, we 
-discover that earlier tasks have a priming effect on the worker, shifting the 
-distribution of future answers by 30-50\%. 
+discover that earlier tasks have a priming effect on the worker, shifting 
+the distribution of future responses by 30-50\% 
+(total variational distance). 
 Moreover, prior tasks influence the content that workers focus on, 
 as well as the richness and specialization of responses. 
-Understanding these \textit{intertask effects} is crucial 
-to embracing micratask platforms in critical applications.
+In comparison to overtly framing the job, by stating the requester's 
+research interest, we find prior-task effects are on par or stronger
+than those of framing.
 While intertask effects can be a source of systematic bias, 
-our results suggest that, with appropriate job design, 
+our results suggest that, with appropriate task design, 
 they might be leveraged to hone worker focus and acuity, 
 helping to elicit reproducible, expert-level judgments.
-\end{sciabstract}
-
-\section*{Main text}
-Microtask platforms are online marketplaces in which \textit{requesters} 
-post batches of tasks, and \textit{workers} complete them
-for remuneration, a sense of purpose, and fun
-\cite{kazai2013analysis}.
-Typical tasks include tagging and categorizing images,
+Prior-task effects are a crucial aspect of human computation that should be
+considered in the design of any crowdsourced study.
+\end{abstract}
+
+\keywords{Authors' choice; of terms; separated; by semi\-colons;
+  commas, within terms only; this section is required.}
+
+\category{H.5.m.}{Information Interfaces and Presentation
+  (e.g. HCI)}{Miscellaneous} \category{See
+  \url{http://acm.org/about/class/1998/} for the full list of ACM
+  classifiers. This section is required.}{}{}
+
+\section{Introduction}
+There are many tasks that are trivial for people, but difficult to solve
+programatically.  
+Typical tasks include tagging and categorizing images
 %\cite{6116320,Zhai2012357}, 
@@
 %\cite{chandler2013breaking,Berinsky2012351,Finnerty2013},%paolacci2010running},
-judging the relevancy or quality of content, 
-and performing surveys for academic or market reserach purposes\footnote{We provide a survey of task types in the supplementary text.}.
+judging the relevancy or quality of content, and performing surveys for 
+academic or market reserach purposes\footnote{We provide a survey of task 
+types in the supplementary text.}.
 %\cite{le2010ensuring,grady2010crowdsourcing,alonso2009can,kazai2013analysis}.
+Often these tasks are ill-defined and require some kind of high-level 
+judgment.
+Microtask platforms are marketplaces that help fill the gap in current 
+computational capabilities, by matching requesters, who need to have such 
+tasks completed, with human workers.  Amazon's Mechanical Turk, and 
+CrowdFlower are two popular microtask platforms.
 
@@
 for workers to perform many similar tasks in quick succession.  
-%To describe this tendency, it is necessary to clarify terminology.
-On one popular microtask platform, Amazon's Mechanical Turk (MTurk), 
-tasks are delivered in bundles called HITs.
-Although HIT stands for ``Human Intelligence Task'', here we use ``task'' to 
-mean the smallest repeatable unit of work.  For example, one HIT may involve 
-labeling ten images with descriptive words (\textit{labels}), which amounts
-to ten tasks, each being the labeling of a single image.
-In addition to the task-repetition occuring \textit{within} HITs, 
-workers prefer those HITs that have many available repetitions (that is,
-many more HITs of the same format, but with different data) 
-\cite{Chilton20101}, probably because performing similar tasks reduces 
+This tendency arises from a combination of worker preferences and the 
+logistics of serving small tasks.  
+Workers have a preference for performing sequences of similar microtasks
+\cite{Chilton20101}, probably because it reduces 
 cognitive load from task-switching\cite{Adamczyk2004271}.
-%Furthermore, on average, workers report spending over 4 hours per day on 
-%microtasks, taking breaks only every 1.24 hours, while some take no breaks 
-%at all
-%\cite{laseckieffects}.
-
-%Complex work consists of heterogeneous subtasks; when complex work is
-%broken down and workers perform sequences of very similar simple tasks
-%cognitive load is reduced, and workers are more efficient and accurate 
-%\cite{Adamczyk2004271,laseckieffects,kittur2011crowdforge}.
-%Thus, the tendency for workers to perform series of repetitive, similar
-%tasks would appear to be beneficial.
-
-The repetitive completion of similar tasks is of concern because people's 
-responses to a prompt can be strongly influenced by their recent exposure to 
-stimuli, due to \textit{priming} 
+Morever, as workers complete task assignments, they must continually 
+switch between working on an assignment and choosing their next 
+assignment (weighing such factors as the wage paid, and effort required).  
+Bundling tasks together reduces the amount of time spent choosing 
+assignments and reduces the overhead of switching between working and 
+choosing.  This may explain why the the pre-defined templates offered to 
+help requesters set up their microtask jobs generally bundle many tasks 
+together by default\footnote{mturk.com}.
+
+The effects of task-repetition have been studied in the context of 
+monitoring tasks by facility operators.  There the main concern is 
+operator error due to boredom and distraction.  
+However, in the microtask context, tasks are often ill-defined, and lack 
+a clear notion of error.  For example for an image-labeling task
+it would be difficult to decide which labels are `correct'.
+Not only does this complicate the measurement of task-repitition effects, 
+it suggests that their effect may be better understood as introducing 
+\textit{bias} into responses, rather than \textit{error}.
+
+One of our present contributions is a method for determining
+the extent of this bias.  Generally, there may be many possible responses 
+to an ill-defined, qualitative microtask, so the responses actually
+obtained can be viewed as being drawn from a distribution.
+Design factors that affect how workers respond to a microtask will change 
+this distribution.  Measuring the effect of such a design factor therefore
+amounts to measuring how much the distribution of responses changes
+There are good statistical techniques for detecting \textit{whether}
+samples come from two different distributions, such as the $\chi^2$ test.  
+But to properly weigh design decisions, a method is needed to measure
+the \textit{extent} by which response distributions differ.
+The direct substitution of sample frequencies in divergence 
+calculations, although occaisionally seen in literature, has no statistical
+basis and can easily lead to the ``detection'' of large changes when none 
+exist.  We present a convenient and statistically sound method that can be 
+applied even when the set of possible responses is very large 
+(or infinite), such as for free text responses.  
+While our purpose is to measure the 
+effects of prior microtasks on later ones, this method can be used to 
+calculate an empirical divergence of distributions from samples in any 
+context.
+
+[\#\#]
+Unlike tasks that have a clear correct response, tasks that rely on 
+worker's qualitative judgments may be particularly susceptible to 
+\textit{priming effects}.
+Priming is the phenomenon by which a person's response to a prompt is
+influenced by their recent exposure to stimuli
 \cite{BJOP1796}. %,No2007}. %,beller1971priming}.  
@@
 a prior stimulus is conceptually or perceptually related to an ensuing 
-task, so the repetition of 
-similar tasks may create an opportunity for strong priming effects
-\cite{Gass1999549}. %,sohn2001task}
+task \cite{Gass1999549} %sohn2001task}
+so the repetition of similar tasks creates many opportunities for 
+strong priming effects. 
+If tasks can act as primes for other tasks, it may help explain an earlier 
+observation [*] that when interrupting one microtask with another,
+the interruption is more disruptive when the tasks are \textit{similar} to 
+one another.
 
@@
 frequencies changed the most from one treatment to another 
-(Table~S\ref{table:top-words}).  
+(Table~\ref{table:top-words}).  
 The word ``food'', which is the most generic possible food-related word, was 
@@
 in the effort to develop performant and reliable human computation.
+
+\bibliographystyle{SIGCHI-Reference-Format}
 \bibliography{newbib}
-\bibliographystyle{Science}
 
@@
 \section*{Supplementary Material}
-\renewcommand{\figurename}{Figure S\!\!}
-\renewcommand{\tablename}{Table S\!\!}
-\renewcommand{\theequation}{S\arabic{equation}}
-\setcounter{figure}{0}
-\setcounter{table}{0}
-\setcounter{equation}{0}
 
@@
 \end{document}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2015-09-10 docs/publications/2015.04_PNAS/man.tex
fix table caption

@@
 \usepackage{dcolumn}
-\usepackage{multirow}
 \usepackage{booktabs}
-\newcolumntype{d}{D{.}{.}{4.0}}
-\newcolumntype{s}{D{.}{.}{1.4}}
 
@@
 judging the relevancy or quality of content, 
-and performing surveys for academic or market reserach purposes (see Table SX for a survey of task types).
+and performing surveys for academic or market reserach purposes (see Table S\ref{Stable:task_composition} for a survey of task types).
 %\cite{le2010ensuring,grady2010crowdsourcing,alonso2009can,kazai2013analysis}.
@@
 %,paolacci2010running},
-and because it is prototypical for any kind of task in which the worker is
+and because it is prototypical for tasks in which the worker is
 asked to provide a response that is not precisely determined by the prompt, but
@@
 		Standard error bars are shown.
+	\label{fig:theta}
 	}
-	\label{fig:theta}
 \end{figure}
@@
 
-To deepen our understanding, we investigated workers' lexical richness in
-reference to food, that is, the number of \textit{unique} food-related words
-used.  Even if workers provide an abundance of food-related words, there can be
-less diversity, if, for example, workers repeat generic references to food.
-Both \textit{intertask} experiments showed that food-exposed workers had
-greater lexical richness, in reference to food, than their counterparts (as
-much as 20\% more) (Fig.~\ref{fig:specificity}B).  This is particularly
-noteworthy in the experiment \textit{intertask-food-culture}, because there,
-food-primed workers made fewer total references to food.
-
-The observations regarding lexical richness suggest that initial tasks might
-influence workers to use more refined or specialized words, when referring to
-aspects of content that had been present in the initial tasks.  To test this,
-we used the wordnet corpus to operationalize the notion of word specialization.
-Wordnet establishes relationships between 117,798 English nouns, indicating
-which words are specializations (or generalizations) of others
-\cite{felbaum1998wordnet}.  For example, ``pumpernickel'' is a specialization
-of ``bread''.  Within each experiment, we determined the percent-excess of
-food-related words that were more specialized in the food-exposed treatment
-relative to the other treatment (details in the supplementary material).
-
-In all experiments except \textit{frame-food-culture} (which had only a weak
-priming effect), food-primed workers used significantly more
-specialized words, in reference to food (about 15\% more)
-(Fig.~\ref{fig:specificity}C).  It is interesting that such substantial
-increases in both the lexical richness and specialization of food-related words
-held for \textit{intertask-food-culture}, where, as mentioned, we observed that
-food-exposed workers made \textit{fewer} references to food overall.  These
-observations point to countervailing factors: one factor tending to activate
-the more specialized and less common food-related words (yielding greater
-lexical richness and specialization), and the other tending to suppress
-certain, presumably more common and generic words (yielding fewer food-related
-words in total).
-
-This hypothesis is corroborated when we look at those words whose frequencies
-changed the most from one treatment to another (Table~\ref{table:top-words}).
-As one would expect, references to objects, such as ``candle'', ``fork'', 
-or ``statue'' appear less frequently among the labels provided by workers in 
-food-exposed treatments.  But, the food-exposed workers also provide the most
-generic references to to food less often, such as the word ``food'' itself, 
-or ``meal''.  
-In fact, the word ``food'', which is the most generic possible food-related 
-word, was always \textit{the most suppressed} among food-primed workers, 
-relative to their non-food-primed counterparts.  
-Meanwhile, food-exposed workers provide more specific references to food more 
-often, such as ``coffee'', ``cheese'', or ``wine''.
-
-\begin{table*}
+\begin{table*}[b]
 	\centering
@@
 
+To deepen our understanding, we investigated workers' lexical richness in
+reference to food, that is, the number of \textit{unique} food-related words
+used.  Even if workers provide an abundance of food-related words, there can be
+less diversity, if, for example, workers repeat generic references to food.
+Both \textit{intertask} experiments showed that food-exposed workers had
+greater lexical richness, in reference to food, than their counterparts (as
+much as 20\% more) (Fig.~\ref{fig:specificity}B).  This is particularly
+noteworthy in the experiment \textit{intertask-food-culture}, because there,
+food-primed workers made fewer total references to food.
+
+The observations regarding lexical richness suggest that initial tasks might
+influence workers to use more refined or specialized words, when referring to
+aspects of content that had been present in the initial tasks.  To test this,
+we used the wordnet corpus to operationalize the notion of word specialization.
+Wordnet establishes relationships between 117,798 English nouns, indicating
+which words are specializations (or generalizations) of others
+\cite{felbaum1998wordnet}.  For example, ``pumpernickel'' is a specialization
+of ``bread''.  Within each experiment, we determined the percent-excess of
+food-related words that were more specialized in the food-exposed treatment
+relative to the other treatment (details in the supplementary material).
+
+In all experiments except \textit{frame-food-culture} (which had only a weak
+priming effect), food-primed workers used significantly more
+specialized words, in reference to food (about 15\% more)
+(Fig.~\ref{fig:specificity}C).  It is interesting that such substantial
+increases in both the lexical richness and specialization of food-related words
+held for \textit{intertask-food-culture}, where, as mentioned, we observed that
+food-exposed workers made \textit{fewer} references to food overall.  These
+observations point to countervailing factors: one factor tending to activate
+the more specialized and less common food-related words (yielding greater
+lexical richness and specialization), and the other tending to suppress
+certain, presumably more common and generic words (yielding fewer food-related
+words in total).
+
+This hypothesis is corroborated when we look at those words whose frequencies
+changed the most from one treatment to another (Table~\ref{table:top-words}).
+As one would expect, references to objects, such as ``candle'', ``fork'', 
+or ``statue'' appear less frequently among the labels provided by workers in 
+food-exposed treatments.  But, the food-exposed workers also provide the most
+generic references to to food less often, such as the word ``food'' itself, 
+or ``meal''.  
+In fact, the word ``food'', which is the most generic possible food-related 
+word, was always \textit{the most suppressed} among food-primed workers, 
+relative to their non-food-primed counterparts.  
+Meanwhile, food-exposed workers provide more specific references to food more 
+often, such as ``coffee'', ``cheese'', or ``wine''.
+
 Our results can be explained through a combination of positive and negative
@@
 
-\begin{figure}[h]
+\begin{figure}[t]
 	\centering
@@
 
-\section{Microtask setup} The work presented in the main text consisted of six
-experiments involving HITs (bundles of tasks) performed on Amazon's Mechanical
-Turk (MTurk) platform.  The flow of events experienced by a worker when
-participating in this study is depicted in Fig.~S\ref{Sfig:task_schematic}.
-Each experiment was divided into two treatments.  Treatments for a given
-experiment differed with respect to a particular priming modality, which served
-as the independent variable (as specified in Table~S\ref{Stable:experiments}).
-The HITs for treatments of the same experiment always involved the same test
-tasks (the last five tasks in the HIT), the results of which served as the
-dependent variable.
+\section{Microtask setup} This study involved six experiments involving HITs
+(bundles of tasks) performed on Amazon's Mechanical Turk (MTurk) platform.  The
+flow of events experienced by a worker when participating in this study is
+depicted in Fig.~S\ref{Sfig:task_schematic}.  Each experiment was divided into
+two treatments.  Treatments for a given experiment differed with respect to a
+particular priming modality, which served as the independent variable (as
+specified in Table~S\ref{Stable:experiments}).  The HITs for treatments of the
+same experiment always involved the same test tasks (the last five tasks in the
+HIT), the results of which served as the dependent variable.
 

### 2015-09-22 docs/publications/2015.08_CHI/man.tex
chi manuscript nearly complete

@@
 \usepackage{arydshln}
+\usepackage{enumitem}
 
@@
 (researchers or companies) with large populations (crowds) of workers, who 
-perform small jobs, typically taking less than five minutes each.
-A topic of ongoing research concerns designing jobs that elicit high
+perform small tasks, typically taking less than five minutes each.
+A topic of ongoing research concerns the design of tasks that elicit high
 quality annotation.
 Here we identify a feature of nearly all crowdsourcing 
-jobs that profoundly impacts workers' responses.
-Microtask jobs typically consist of a sequence 
-of tasks sharing common format 
-(e.g., circle galaxies in an image). 
-Using image-labeling, a canonical microtask job format, we 
+workflows that profoundly impacts workers' responses.
+Microtask assignments typically consist of a sequence 
+of tasks sharing a common format (e.g., circle galaxies in an image). 
+Using image-labeling, a canonical microtask format, we 
 discover that earlier tasks have a priming effect on the worker, shifting 
@@
 (total variational distance). 
-Moreover, prior tasks influence the content that workers focus on, 
+Specifically, prior tasks influence the content that workers focus on, 
 as well as the richness and specialization of responses. 
-In comparison to overtly framing the job, by stating the requester's 
-research interest, we find prior-task effects are on par or stronger
-than those of framing.
+We call this phenomenon \textit{intertask effects}.
+We compare intertask effects to the overt framing of the assignment, 
+effected by stating the requester's research interest, 
+and find that intertask effects are on par or stronger.
 While intertask effects can be a source of systematic bias, 
@@
 helping to elicit reproducible, expert-level judgments.
-Prior-task effects are a crucial aspect of human computation that should be
+Intertask effects are a crucial aspect of human computation that should be
 considered in the design of any crowdsourced study.
@@
 programatically.  
-Typical tasks include tagging and categorizing images
+Typical tasks include tagging and categorizing images,
 %\cite{6116320,Zhai2012357}, 
@@
 %\cite{chandler2013breaking,Berinsky2012351,Finnerty2013},%paolacci2010running},
-judging the relevancy or quality of content, and performing surveys for 
-academic or market reserach purposes\footnote{We provide a survey of task 
-types in the supplementary text.}.
+%judging the relevancy or quality of content,
+and performing surveys for 
+academic or market reserach purposes (see Table~\ref{table:task_composition} for a listing of task types seen on the Amazon's Mechanical Turk 
+microtask platform).
 %\cite{le2010ensuring,grady2010crowdsourcing,alonso2009can,kazai2013analysis}.
-Often these tasks are ill-defined and require some kind of high-level 
-judgment.
+Many tasks are ill-defined, in the sense that they do not have
+a clear ``correct'' response, and require high-level, qualitative judgment.
 Microtask platforms are marketplaces that help fill the gap in current 
@@
 This form of crowdsourcing embeds workers in a controlled but flexible
-task infrastructure.  To the requester, workers seem almost like input-output 
-devices.  
+task infrastructure.  
+To the requester, workers seem almost like input-output devices.  
 This provides much of the flexibility and 
@@
 \cite{wolfson2011look,5543192}.
-Jobs can be performed at a fraction of the cost of traditional methods for 
+Work can be performed at a fraction of the cost of traditional methods for 
 recruiting temporary workers or experimental subjects
@@
 has led to a surge in demand from industry and 
-academia\cite{wolfson2011look,Berinsky2012351}.  More recently microtask 
+academia \cite{wolfson2011look,Berinsky2012351}.  More recently microtask 
 platforms have
@@
 with promising results \cite{Warby2014385}.
-Naturally, researchers have investigated the factors affecting the reliability
-of microtask work, including
-the level of pay \cite{Mason200977,kazai2013analysis}, 
-the training and pre-screening of workers 
-\cite{le2010ensuring,kazai2013analysis}, %paolacci2010running}, 
-user-interface design \cite{Finnerty2013}, and the provision of timely 
-feedback \cite{Dow20121013}.
-Researchers have also investigated \textit{framing}, 
-by altering the description of the workflow context 
-\cite{Kinnaird2012281}, the stated purpose of tasks 
-\cite{chandler2013breaking}, and the problem description
-\cite{thibodeau2013natural}.  Another important optimization concerns
-workflow design: how breaking down a complex problem into microtasks
-\cite{kittur2011crowdforge}, altering microtask size 
-\cite{Huang201077}, and introducing workflow interruptions 
-\cite{laseckieffects} impact worker quality and efficiency.
-
-Here, we focus on a ubiquitous feature of microtask work: the tendency
-for workers to perform many similar tasks in quick succession.  
+
+Naturally, researchers have investigated the factors affecting the 
+reliability of microtask work, including the design of the task interface
+\cite{Finnerty2013},
+the design of workflows (how work is divided into tasks)
+\cite{kittur2011crowdforge,Huang201077,laseckieffects},
+and the framing of tasks
+\cite{Kinnaird2012281,chandler2013breaking,thibodeau2013natural}.
+Here we draw attention to a ubiquitous yet overlooked feature of microtask 
+work: the tendency for workers to perform many similar tasks in quick 
+succession.
+
 This tendency arises from a combination of worker preferences and the 
@@
 \cite{Chilton20101}, probably because it reduces 
-cognitive load from task-switching\cite{Adamczyk2004271}.
+cognitive load arising from task-switching \cite{Adamczyk2004271}.
 Morever, as workers complete task assignments, they must continually 
@@
 assignment (weighing such factors as the wage paid, and effort required).  
-Bundling tasks together reduces the amount of time spent choosing 
-assignments and reduces the overhead of switching between working and 
-choosing.  This may explain why the the pre-defined templates offered to 
-help requesters set up their microtask jobs generally bundle many tasks 
-together by default\footnote{mturk.com}.
-
-The effects of task-repetition have been studied in the context of 
-monitoring tasks by facility operators.  There the main concern is 
-operator error due to boredom and distraction.  
-However, in the microtask context, tasks are often ill-defined, and lack 
-a clear notion of error.  For example for an image-labeling task
-it would be difficult to decide which labels are `correct'.
-Not only does this complicate the measurement of task-repitition effects, 
-it suggests that their effect may be better understood as introducing 
-\textit{bias} into responses, rather than \textit{error}.
-
-One of our present contributions is a method for determining
-the extent of this bias.  Generally, there may be many possible responses 
-to an ill-defined, qualitative microtask, so the responses actually
-obtained can be viewed as being drawn from a distribution.
-Design factors that affect how workers respond to a microtask will change 
-this distribution.  Measuring the effect of such a design factor therefore
-amounts to measuring how much the distribution of responses changes
-There are good statistical techniques for detecting \textit{whether}
-samples come from two different distributions, such as the $\chi^2$ test.  
-But to properly weigh design decisions, a method is needed to measure
-the \textit{extent} by which response distributions differ.
-The direct substitution of sample frequencies in divergence 
-calculations, although occaisionally seen in literature, has no statistical
-basis and can easily lead to the ``detection'' of large changes when none 
-exist.  We present a convenient and statistically sound method that can be 
-applied even when the set of possible responses is very large 
-(or infinite), such as for free text responses.  
-While our purpose is to measure the 
-effects of prior microtasks on later ones, this method can be used to 
-calculate an empirical divergence of distributions from samples in any 
-context.
-
-[\#\#]
-Unlike tasks that have a clear correct response, tasks that rely on 
-worker's qualitative judgments may be particularly susceptible to 
-\textit{priming effects}.
-Priming is the phenomenon by which a person's response to a prompt is
-influenced by their recent exposure to stimuli
-\cite{BJOP1796}. %,No2007}. %,beller1971priming}.  
-Priming can arise when 
-a prior stimulus is conceptually or perceptually related to an ensuing 
-task \cite{Gass1999549} %sohn2001task}
-so the repetition of similar tasks creates many opportunities for 
-strong priming effects. 
-If tasks can act as primes for other tasks, it may help explain an earlier 
-observation [*] that when interrupting one microtask with another,
-the interruption is more disruptive when the tasks are \textit{similar} to 
-one another.
-
-%Researchers investigating a somewhat similar class of psychological phenomena,
-%found that ratings that microtask workers give to items in a list
-%depend on the order in which the list is presented, an effect known as
-%\textit{positional bias} \cite{lerman2014leveraging}.  This serves as an 
-%example of a basic psychological phenomenon impacting crowdsourced data,
-%and raises questions about what other cognitive biases might
-%affect microtask work, and how prevalent the induced bias might be.
-
-We investigate the potential for task repetition to induce bias in 
-a highly generalizeable microtask setup, in which workers label a 
-series of images.  If task-induced priming arises in our setup, 
-it should be expected in virtually every microtask and crowdsourced workflow
-where workers are called upon to exercise their judgment\footnote{
-	As opposed to those tasks where a single clear correct answer exists.
-}.
-Our results show that a worker's response during a task
-does indeed depend strongly on the tasks performed beforehand.   
+Since microtasks are very short,
+it makes sense to bundle tasks together into
+larger assignments, to reduce the overhead of switching between  
+working on assignments and choosing them.
+This may explain why the pre-defined assignment templates available on 
+microtask platforms generally bundle many tasks together by 
+default\footnote{e.g. on \url{mturk.com} and \url{crowdflower.com}}.
+
+Psychological experiments show that the exposure to stimuli immediately 
+before performing a task influences performance, an effect known as 
+\textit{priming} \cite{BJOP1796}.
+The effect of priming appears to be stronger when the modality of the
+prime is the same as the task.
+Thus, the typical microtask setup creates the conditions in which
+earlier tasks could induce bias in later ones, through priming.
+
+We seek to determine if any significant priming effect occurs between
+tasks, and if so, to measure and characterize it.
+Certain tasks admit a well-defined notion of ``correct'' and 
+``incorrect'' responses.  But many tasks involving qualitative judgment
+do not.  To provide a generalized measure of bias, we seek to quantify the
+extent to which intertask priming can shift the distribution of responses 
+to a task.  
+Measuring the \textit{extent} of the shift in response distribution,
+i.e. the extent of bias, is substantially harder than
+simply determining \textit{whether} a biasing effect has occured.  
+Our first contribution is a statistically grounded method for doing so.
+
+To investigate the phenomenon in a
+highly generalizable setting, we sought a task that would involve 
+qualitative judgment and enable relatively unconstrained responses. 
+We also sought a task that would be a typical exemplar of the kinds of
+tasks actually seen on microtask platforms (see 
+Table~\ref{table:task_composition} for examples).  For this purpose, we 
+adopted
+image-labeling as a canonical micratask, in which workers provide 
+descriptive labels to images using free-text inputs.  Image labeling is
+a qualitative task without clearly ``correct'' or ``incorrect'' responses,
+and is among the most common kinds of tasks on the major crowdsourcing
+platform Amazon's Mechanical Turk.  If task-induced priming arises in our 
+setup, it should be expected in virtually every microtask and 
+crowdsourced workflow where workers are called upon to provide qualitative
+judgment.
+
+In our experiments, workers label a series of images, one at a time.
+Depending on the treatment to which a worker is assigned, we vary the
+images in the first five tasks, while keeping those in the last five tasks 
+the same.  For example, in one experiment, the first five images shown to
+one group of workers contained food, while those shown to the other 
+contained (non-food) objects.  The last five images for both
+groups contained both food and objects.
+
+Our results show that a worker's responses are strongly influenced by 
+the content of tasks performed beforehand, leading to as much as 50\%
+bias (measured as total variational distance, 
+see Figure~\ref{fig:l1_example} for illustrative definition).  
+Using the wordnet 
+knowledge base, we analyze worker's word choices to characterize the 
+the nature of these effects in detail.  We find that, when workers 
+label a series of images that are more similar, their responses become 
+more specialized more diverse.  Prior tasks can shift the topical focus of 
+worker's labels, inducing them to focus on different aspects of the images.
+
+As a point of comparison, we perform similar experiments, in which we
+alter the framing of microtask assignments, in terms of the stated purpose
+of the task.  Remarkably, the effects prior microtasks themselves,
+which are virtually ubiquitous, are on par with, or stronger than, 
+overtly framing the purpose of an assignment.
+
 We call the effects that earlier tasks exert on later ones 
@@
 architecture, it will be necessary to reconcile the fact that the human 
-computing elements 
-exhibit \textit{hysteresis}, meaning that microtask workers' outputs depend 
-on the \textit{history} of their inputs.
-
-%As we have described, microtask platforms have been widely adopted as a 
-%tool, but computer scientists also hold such platforms as the object of 
-%research, viewing  microtask platforms as a new kind of computing 
-%architecture.  In analogy to CPUs (central 
-%processing units) and GPUs (graphics processing units), 
-%Davis \textit{et al} invoked the \textit{human processing unit}, or HPU \cite{5543192}.
-%Researchers have sought to define a set of basic HPU operations, and
-%have developed libraries and frameworks to simplify HPU programming 
-%and make it more like CPU programming 
-%\cite{little2010turkit,minder2012crowdlang,kittur2011crowdforge}.  
-%As an example, one operation overcomes the inherent stochasticity of HPU 
-%outputs, by automatically aggregating votes from multiple HPUs under a single
-%function call.  
+computing elements exhibit \textit{hysteresis}, 
+meaning that microtask workers' outputs 
+depend on the \textit{history} of their inputs.
+We propose a dual priming mechanism which can exaplain our
+observations.  Irrespective of the underlying mechanism, this 
+very strong effect might be exploited in task design to tune worker 
+focus and acuity.
+
+As our main contributions, we
+\begin{itemize}[noitemsep,nolistsep]
+  \item{derive a general method for measuring bias in responses;}
+  \item{measure bias in microtasks due to prior tasks;}
+  \item{show this effect is stronger than, or on par with framing;}
+  \item{
+	show that when completing a series of similar microtasks,
+	worker's responses become more specialized and diverse;
+  }
+  \item{provide design considerations in light of our observations.}
+\end{itemize}
+
+The rest of the paper is organized as follows.  In the next section, we 
+review the relevant prior work.  We then present a method for 
+measuring bias due to intertask effects.  
+Next we present our experimental results, followed by a discussion 
+of interpretations and ramefications for microtask-based and crowdsourced 
+work.  We conclude with suggestions for task design and future work.
+
+\section{Prior work}
+\subsection{Effects of microtask design on response quality}
+% Accuracy, reproducibility, and a controlled task environment are 
+% important
+Microtask platforms are increasingly used clean and codify datasets,
+administer experiments with human participants, and distribute 
+surveys.  Accuracy and replicability are crucial in all of these 
+applications.
+
+\begin{table}
+\centering
+\begin{tabular}{l c c}
+\toprule
+Task Type & Count & Fraction (\%) \\
+\toprule
+Image transcription & 57 & 28.5 \\
+Information gathering & 46 & 23.0 \\
+Image tagging and classification & 36 & 18.0 \\
+Copy writing and editing & 18 & 9.0 \\
+Text tagging and classification & 15 & 7.5 \\
+Audio/Video transcription & 12 & 6.0 \\
+Survey & 9 & 4.5 \\
+Unknown & 7 & 3.5 \\
+\bottomrule
+\end{tabular}
+\caption{
+	Frequency of various broad task types seen among the 200 most 
+	recently posted tasks on MTurk, accessed on 12 February, 2015.
+}
+\label{table:task_composition}
+\end{table}
+
+% These things are definitely not assured, and people have tried to 
+% figure out what to do about it
+Accuracy and replicability are central to any crowdsourcing study.
+There is ongoing research investigating how the desing of microtasks,
+and their context, affect the quality of responses.  
+One of the most basic issues with crowd work
+is that workers vary in the amount of attention they pay to tasks, 
+and in their understanding of instructions.
+Workers who disregard or misunderstand instructions can be effectively 
+screened out by including quiz-questions among the tasks, while
+instruction comprehension can be improved using a training phase before
+actual tasks begin
+\cite{le2010ensuring,kazai2013analysis}. %paolacci2010running},
+In addition, providing real-time feedback to workers encourages  
+higher-quality responses, while prompting workers to review their work
+according to a set of criteria increases the worker's response quality 
+over time \cite{Dow20121013}.
+
+% Designing tasks themselves
+The design of the task interface also has important effects on response
+quality.  A simpler user interface can improve accuracy 
+\cite{Finnerty2013}, and certain input controls
+are inherently less effortful and error-prone than others
+\cite{cheng2015measuring}.
+
+% Task pricing
+Since microtask work is generally paid, wage is a basic parameter in
+the requesters control that might influence response quality.
+One might expect a higher wage to \textit{buy} better performance,
+but results are ambiguous.  One study found that increasing wage
+has no effect on response quality, but does increase the amount of 
+responses \cite{Mason200977}.
+Another study \cite{kazai2013analysis} showed that increasing
+wages does increse quality, but that this effect saturates, and 
+eventually increases in wage attract a larger porportion of workers who 
+disregard the task instructions.
+
+% Task framing
+Workers have other motivations for completeing tasks aside from 
+remuneration \cite{kazai2013analysis}.  
+Researchers have attempted to appeal to
+worker's motivation to do work that has a meaningful purpose:
+when a task was framed as assisting with medical research,
+workers are more likely to participate and completed more tasks, than
+when they were not provided any context \cite{chandler2013breaking}.
+Providing a meaninful context did not, however, increase the 
+\textit{quality} of work.
+
+Other studies have investigating different means of framing.  
+When asked to rate various policy interventions, 
+workers emphasized respectively more or less punitive approaches
+depending on whether the phrase ``crime is a beast'' or 
+``crime is a virus'' appeared in the problem description
+\cite{thibodeau2013natural}.
+When workers perform a task within the context of larger workflow, 
+explaining how the task fits into the workflow, 
+which amounts to a kind a framing, increased both the quantity and 
+quality of responses \cite{Kinnaird2012281}.
+
+% Optimization based on the breakdown of tasks
+Breaking down of complex jobs into simpler tasks, can increasing worker
+efficiency by enabling greater parallelism.
+While this could disrupt the natural context provided by performing the
+whole job as a single task, it turns out that, 
+for complex tasks such as writing an article, 
+dividing the job into subtasks, including outlining, 
+information-gathering, and paragraph-synthesis, actually improves the
+quality of the end-product \cite{kittur2011crowdforge}.
+
+% effects of task interruption
+Perhaps the most similar study to the work we describe here 
+investigated the effects of interruptions on task performance
+\cite{laseckieffects}.  There, workers 
+completed a series of tasks that required them to answer questions about
+an illustrated map.  When interruptions were introduced
+in the form of either a time delay, or a different task involving a
+different map, workers took longer to complete the task which 
+followed the interruption.  However this study did not test for
+effects on the quality of responses.
+%\cite{kreifeldt1981interruption}
+
+Taken together, the prior work suggests that, beyond the design
+of tasks themselves, the design of the context of tasks has a major
+effect on responses.
+However, the potential of earlier tasks to act as primes for later ones 
+has not been adequately investigated.
+
+%\subsection{Performance during repetitive tasks}
+%Studies of worker performance during repetitive work have been studied 
+%in the context of long-running monitoring tasks, such as those required
+%of some facility operators.
+%Studies show that performance tends to decline, in terms of
+%lengthening reaction time and increased rates of error, as a function of 
+%time-on-task \cite{pattyn2008psychophysiological}.  In such 
+%contexts, interruptions may actually serve to restore mental attention.
+%Studies have shown that improved recall during tasks that were 
+%interrupted.  
 %
-%But our revelation of strong intertask effects shows that, 
-%in addition to stochasticity, HPUs are subject to \textit{hysteresis}, 
-%meaning that their 
-%outputs depend on the history of their inputs.  Reproducibility and 
-%path-independence are crucial properties for the components of a 
-%computing architecture, so a better understanding of the computational 
-%ramifications of many psychological phenomena is needed.
-
-Our image-labeling tasks were performed on the MTurk microtask platform.  
-We chose image labeling because it is very common\footnote{
-	We discuss task composition in the supplementary text.
-},
-%\cite{chandler2013breaking,Finnerty2013},%,paolacci2010running},
-and because it is prototypical for any kind of task in which the worker is 
-asked to provide a response that is not precisely determined by 
-the prompt, but instead depends on the worker's judgment.  
-This includes such diverse tasks as describing video and audio recordings, 
-summarizing texts, or in clinical diagnostic judgments.
-
-In our first experiment, called \textit{intertask-food-objects},
-workers were assigned to either a
-\textit{food} or \textit{objects} treatment.  Workers in both treatments
-performed a set of five \textit{initial tasks}, which each involved 
-providing descriptive labels for an image depicting 
-either food or (non-food) objects, depending on the worker's 
-treatment (Fig.~\ref{fig:task}A and B).  Following the initial 
-tasks, workers performed five \textit{test tasks}, which were identical for 
-both treatments.  In the the test tasks, workers labeled images, each of 
-which depicted a mixture of food and objects (Fig.~\ref{fig:task}C).  
-The five initial 
-and test tasks performed by each worker comprised one HIT\footnote{
-	Workers were only allowed to participate in one HIT relating to this study.
-}. The images were presented one at a time, and we made no 
-distinction between the initial and test tasks.
-
-The frequencies of words used by
-workers in the \textit{food} and \textit{objects} treatments differed
-significantly during test tasks (by $\chi^2$ test, $p = 6.0 \times 10^{-14}$),
-even though the test tasks were identical in both treatments\footnote{
-	see supplementary text for tabulated statistics.
-}.  Thus earlier tasks do significantly affect later ones, raising concerns 
-about the the microtask methodology.
-
-Having affirmed the \textit{existence} of intertask effects, we wish to
-understand the nature and severity of the bias induced.
-We therefore define the extent of bias, $\theta$, in terms of
-the strength of influence that a prior perturbation has on workers' responses.
-Since workers' responses are stochastic, we define the extent of bias in 
-terms of the change induced in the distribution of responses\footnote{
-	This is a general divergence metric between probability 
-	distributions known as the \textit{total variation distance.}
-}:
+%These studies illustrate the impact of task-duration and
+%repetition on performance.  However, the
+%relatively low-input monitoring tasks involved in such studies are very
+%different from typical microtasks, which require continuous cognitive 
+%effort and input from the worker.
+%
+%In the microtask setting, one study investigated the effect of delays
+%and interruptions introduced into a microtask setting.  This study
+%found that interruptions and delays
+%leading to a significant increase in the time needed to complete the
+%interrupted task once resumed.
+%However, the researchers did not investigate
+%whether interruptions could affect the content of responses.
+%
+%Here we focus on how the content of earlier tasks can influence responses
+%to tasks later ones.  Because qualitative judgment tasks are difficult
+%to automate, but often easy for people to perform, many microtasks are of 
+%this kind.  We hypothesize that such tasks are highly susceptible to 
+%priming effects, and that in the repetitive pattern of microtask work
+%(and most crowdsourced work), earlier tasks may act as primes to later 
+%ones, and thereby introduce singificant amounts of bias.
+
+\subsection{Priming}
+Priming is a psychological phenomenon whereby previous exposure to a 
+stimulus leads to faster or more accurate responses to similar stimuli 
+\cite{Ghuman17062008},
+or to lower response thresholds \cite{BJOP1826}.  
+Priming occurs by means of pre-activation, which can influence
+stimulus encodings (during perception) \cite{BJOP1826}, 
+the top-down application of object-knowledge \cite{Ghuman17062008},
+and memory access \cite{beller1971priming}.
+Priming is more 
+effective when the prime and the target task involve the kind of 
+activity.  For example, exposing participants to an image helps them 
+subsequently recognize that image when shown very breifly in a 
+tachistoscope; however, being presented with a related \textit{word}, 
+and reading it aloud, does not \cite{BJOP1796}.
+
+As we have mentioned, workers prefer to perform series of similar tasks
+series of similar tasks in quick succession.  Moreover, the many 
+microtasks involve tasks based on visual and auditory perception 
+similar to the kinds used in priming studies.
+Thus, in a typical microtask assignment, there are many opportunities for 
+priming, the effects of which should be explored.
+
+\subsection{Measuring the extent of priming}
+If a prior task acts as a prime for a later one, it will 
+result in a shift in the responses workers provide for the later task.
+A variety of tests exist to determine \textit{whether} two samples, 
+i.e. sets of responses, come from different distributions, 
+most notably the $\chi^2$ test.  
+This will suffice to determine whether there are any grounds for conern 
+about priming effects in the first place.  However, such tests
+do not tell us \textit{how much} two distributions differ, and hence
+how severe the priming effects are.
+
+Determining the severity of priming effects amounts to measuring a 
+distance, or \textit{divergence}, between response distributions, by
+sampling responses from workers exposed to different priming conditions.
+We will present a method for bounding a kind of divergence known as 
+\textit{total variational distance}\footnote{
+  Other formulation such as the Kulback-Leibler and 
+  Jenson-Shannon divergence can be calculated from the total variational
+  distance
+}, which we will henceforth denote by $\theta$.
+The value of $\theta$ between two distributions $P$ and $Q$ 
+is the fraction under the graph of $P$ that does not overlap with that
+under $Q$ (or vice-versa; see Figure~\ref{fig:l1_example}).  
+Formally:
+\begin{align}
+	\theta = \frac{1}{2}\sum_{x \in X} \left| p(x) - q(x) \right|,
+	\label{eq:theta}
+\end{align}
+Where $p(x)$ and $q(x)$ are the respective probabilities 
+that a worker submits response $x$, from a set of possible responses 
+$\mathcal{X}$, under distributions $P$ and $Q$.
+The divergence is constrained to 
+$0 \leq \theta \leq 1$ (or from 0 to 100\%).
+When $\theta = 100\%$, the distributions do not overlap at all.  
+When $\theta = 0\%$, the distributions are identical.
+For reference, the distributions plotted in 
+Figure~\ref{fig:l1_example}A and B have $\theta=30\%$ and $\theta=50\%$ 
+respectively.
+
+\begin{figure}
+	\centering
+	\includegraphics[scale=1.0]{figs/normal_example.pdf}
+	\caption{
+	  	Normal distributions exhibiting a total variational distance
+		of A) 50\% and B) 30\%.  The total variational distance is 
+		the non-overlapping portion of the distributions, e.g. in
+		A) it is given by 
+		$\theta = a_1 / (a_1 + a_2) = a_2 / (a_2 + a_3)$.
+	}
+	\label{fig:l1_example}
+\end{figure}
+
+Empirically measuring the divergence between distributions
+is a matter of ongoing
+research \cite{val-thesis,batu2013testing,chan2014optimal}.
+In the ``na\"ive'' approach one first uses the samples to reconstruct 
+empirical
+distributions, by calculating their maximum likelihood parameters.
+Then, one substitutes the empirical values of $p(x)$ and $q(x)$ into 
+Equation~\ref{eq:theta} \cite{batu2013testing}.  
+For example, one might directly estimate $\hat{p}(x) = N_x/N$, 
+where $N_x$ is the number of times response $x$ is observed among $N$ 
+total responses.
+
+However this approach can \textit{drastically} overestimate $\theta$
+\cite{val-thesis}.  As an illustrative example,
+suppose that we have sampled two sets of 1000 words from \textit{possibly} 
+different distributions, and that we wish to estimate the divergence 
+between these distributions.  
+It turns out that, if both sets of words were actually drawn from 
+an identical Zipf distribution\footnote{The 
+  Zipf distribution is a common model for word frequencies 
+  \cite{powers1998applications,zipf1949human}:
+  \begin{align}
+	p(x) = \frac{x^{-1}}{\sum_{n=1}^{\infty}x^{-1}},
+	\label{eq:zipf}
+  \end{align}
+  where $p(x)$ is the probability of the $x$th most common word.
+}, the na\"ive approach would typically lead one to report 
+$\hat{\theta} \approx 65\%$, event though, in reality $\theta = 0\%$
+(this can be shown by simulated sampling).
+
+However, we can establish a lower bound for $\theta$ by 
+exploiting a fact about the theoretical limits on the accuracy of a 
+classifier algorithm.  The intuition is as follows: 
+suppose workers are shown one of two alternative designs\footnote{We will
+use ``design'' in a general sense, to include both the design of the task
+and of its context.  In particular, the ``design'' might include the
+particular tasks that were shown beforehand, or the use of framing.}
+for an otherwise
+similar task, and that we build a classifier which, 
+based on a worker's response, infers which of the designs had been 
+used.
+If worker's responses are not affected by the design alternative,
+then the classification problem will be hard, and the classifier's 
+accuracy poor.
+Conversely, if the classifier accuracy is good, then design alternative 
+must have a strong effect on the response distribution.
+
+Stated formally, any classifier algorithm, $\mathcal{A}$, that
+takes the response, $x$, of a worker, and guesses the 
+design that elicited the response (from two possibilities:
+$\mathrm{design}_1$ or $\mathrm{design}_2$), will do so with accuracy 
+$\eta_\mathcal{A}$, that is bounded according to:
 \begin{equation}
-	\theta = \frac{1}{2}\sum_{x \in X} \left| p_0(x) - p_1(x) \right|,
-	\label{eq:theta}
+	\theta \geq 2\eta_\mathcal{A} - 1,
+	\label{eq:sup:l1}
 \end{equation}
-where $p_i(x)$ is the probability that a worker, subjected to treatment $i$,
-provides response $x$, from the set of possible responses $X$.
-%A significant result from a $\chi^2$ test only allows us to conclude that 
-%$\theta$ is non-zero (see supplementary text).  
-Determining $\theta$ from finite samples of responses, using purely 
-statistical approaches, is difficult (see supplementary text),
-which leads us to reformulate the
-problem in terms of classification: given a worker's 
-responses to test tasks, can a machine reliably infer what her prior exposure 
-had been?  Intuitively, the greater the effect that prior tasks have on 
-subsequent responses, the more accurate the classifier can be.  
-Formally (as shown in the supplementary text), the accuracy of such a 
-classifier, $\eta$, establishes a lower bound on the bias:
-\begin{equation}
-	\theta \geq 2\eta - 1.
-	\label{l1}
-\end{equation}
-
-By measuring the accuracy of a classifier, we bound the 
-bias induced by a perturbation, such as the exposure to prior tasks or 
-framing.
-Bias ranges from 0 (meaning the exposure 
-does not affect the distribution of responses), to 1 
-(or 100\%) (meaning that the exposure leads workers to provide a completely
-different set of responses).
-
+where $\theta$ is the divergence between the distributions of responses
+to $\mathrm{design}_1$ and $\mathrm{design}_2$.
+
+We will now establish Inequality~\ref{eq:sup:l1} by considering an
+optimal classifier having accuracy $\eta_*$.  
+Let us assume that workers are shown 
+$\mathrm{design}_1$ or $\mathrm{design}_2$ with equal probability.
+If the worker gives the response $x$, it is optimal to guess
+that the worker was shown the design most likely to elicit $x$.
+In other words, if $p_i(x)$ is the probability that a worker shown 
+$\mathrm{design}_i$ responds with $x$, then it is optimal to 
+guess that the worker saw $\mathrm{design}_j$, where 
+$j = \arg\max_j{p_j(x)}$.
+
+Of course, neither $p_1(x)$ nor $p_2(x)$ are known.  But, on seeing $x$,
+the probability that such a classifier would be correct is:
+\begin{align}
+  \mathrm{Pr}\{\mathrm{correct}|x\} = \frac{1}{2} 
+	+ \frac{|p_0(x) - p_1(x)|}{2(p_0(x) + p_1(x))}
+\end{align}
+Summing over all possible responses that a worker could provide, 
+$x \in \mathcal{X}$, weighted by the probability of observing $x$, 
+we obtain the accuracy of the optimal classifier:
+\begin{align}
+\eta_* 
+  &= \sum_{x\in\mathcal{X}} 
+	\mathrm{Pr}\{\mathrm{correct}|x\}\mathrm{Pr}\{x\} \\
+  &= \sum_{x\in\mathcal{X}} 
+	\left(
+	\frac{1}{2} + \frac{|p_0(x) - p_1(x)|}{2(p_0(x) + p_1(x))}
+  \right) \left( 
+	\frac{p_0(x) + p_1(x)}{2} 
+  \right) \\
+  &= \frac{1 + \theta}{2}
+\end{align}
+Since no classifier can be more accurate than an optimal classifier,
+it follows that, for any \textit{practical classifier} 
+with accuracy $\eta_\mathcal{A}$, the bound 
+$\theta \geq 2\eta_\mathcal{A} -1$ holds.
+
+Thus, we can establish a \textit{lower bound} on $\theta$ by first 
+building a classifier that infers the design shown to workers from their 
+responses, and then measuring its accuracy.
+
+\section{Results}
 \begin{figure}
+	\includegraphics[scale=0.36]{figs/task-schematic-2.pdf}
+	\caption{
+	  Template for the experiments described in the main text.
+	  After selecting our assignment on Mechanical 
+	  Turk, workers were separated into two treatments.
+	  Workers from each treatment were subjected to framing and/or
+	  five initial tasks, which differed between treatments, and then 
+	  completed a set of five test tasks that were identical for both
+	  treatments.  Most experiments involved either framing or initial
+	  tasks (see table \ref{table:experiments}), 
+	  but \textit{frame-food-culture} involved both.
+	  After the experiment, workers return to the Mechanical Turk 
+	  task-selection interface.
+	}
+	\label{fig:task-schematic}
+\end{figure}
+
+\begin{figure*}
 	\centering
@@
 	\label{fig:task}
-\end{figure}
-
-Using a na\"ive Bayes classifier\footnote{
-	We believe na\"ive Bayes is the best choice in this setting, as discussed
-	in the supplementary material, and we show results when a support vector
-	machine is used instead. 
-	We also discuss data preprocessing and show results for alternative 
-	preprocessing.
-}, we found that intertask effects 
-lead to a 30\% bias between workers from the \textit{food} and 
-\textit{objects} treatments (Fig.~\ref{fig:theta}A).  
-This represents a substantial potential to distort microtask data.
-
-There has been considerable interest in the effects that framing can have
-on microtask responses
-\cite{Kinnaird2012281,chandler2013breaking,thibodeau2013natural}, so,
-as a point of comparison, we describe a similar experiment 
-in which we framed the purpose of the tasks.  In the experiment 
-\textit{frame-food-objects}, the same test-tasks were used, but rather
-than exposing workers to initial tasks, workers were either told that 
-the tasks were ``Funded by the laboratory for the visual perception of Food 
-and Ingredients'', or ``\ldots of Objects and Tools''.  
-Framing did induce changes in the frequencies of 
-word usage at significance (as determined by $\chi^2$ test; $p=0.0012$), but 
-the \textit{extent} of framing-induced bias was not statistically 
-distinguishable from zero ($p =0.37$) (Fig.~\ref{fig:theta}A), and was
-much weaker than the bias due to intertask effects ($p=2.1\times 10^{-5}$).
+\end{figure*}
+
 \begin{figure}
-	\centering
-	\includegraphics[scale=1]{figs/theta.pdf}
+	\includegraphics[scale=0.75]{figs/theta.pdf}
 	\caption{
 		Empirical bias, $\theta_\mathrm{NB}$, measured using a na\"ive Bayes 
-		classifier, induced in image labeling tasks, due to workers' 
-		exposure to framing and initial tasks.  
-		(\textbf{A}) Exposing workers to initial tasks induces more severe
-		bias than framing, except when echoed framing is used. 
-		(\textbf{B}) As workers proceed through test tasks, 
-		the bias due to initial tasks wanes, 
-		but remains significant even after five tasks.  
+		classifier, induced in image-labeling tasks, due to workers' 
+		exposure to framing and prior tasks.  
+		(\textbf{A}) Exposing workers to initial tasks induced more severe
+		bias than framing, except when echoed framing was used. 
+		(\textbf{B}) As workers proceeded through test tasks, 
+		the bias due to initial tasks waned, 
+		but remained significant even after five tasks.  
 		Standard error bars are shown.
@@
 
-To assess the persistence of intertask effects, we replicated the experiment
-\textit{intertask-food-objects} while permuting the test tasks, to reveal the 
-dependence of intertask effects on task position.
-We found that bias was strongest for the first test task (about 28\%), 
+\begin{table}
+\small
+\centering
+\setlength{\tabcolsep}{1pt}
+\begin{tabular}{c c c c c}
+\toprule
+Experiment & \parbox[c]{3.0cm}{\centering{Priming modality}} & Initial Tasks & Frame \\
+\midrule
+\multirow{2}{*}{\textit{intertask-food-objects}} 
+& \multirow{2}{*}{initial tasks} & \textit{food} & none \\
+  & & \textit{objects} & none  \\
+
+\noalign{\smallskip}
+\hdashline
+\noalign{\smallskip}
+
+\multirow{2}{*}{\textit{frame-food-objects}} 
+& \multirow{2}{*}{framing} & none 
+	& ``food''\textsuperscript{a} \\
+& & none 
+	& ``objects''\textsuperscript{b} \\
+
+\noalign{\smallskip}
+\hdashline
+\noalign{\smallskip}
+
+\multirow{2}{*}{\textit{echo-food-objects}} 
+& \multirow{2}{*}{echoed framing} & none
+	& ``food''\textsuperscript{c} \\
+& & none & ``objects''\textsuperscript{d} \\
+
+\noalign{\smallskip}
+\hdashline
+\noalign{\smallskip}
+
+\multirow{2}{*}{\textit{intertask-food-culture}} 
+& \multirow{2}{*}{initial tasks} & \textit{food} 
+	& none \\
+& & \textit{culture} 
+	& none \\
+
+\noalign{\smallskip}
+\hdashline
+\noalign{\smallskip}
+
+\multirow{2}{*}{\textit{frame-food-culture}} 
+& \multirow{2}{*}{framing} & \textit{food} 
+	& ``food''\textsuperscript{e} \\
+  & & \textit{food}
+	& ``culture''\textsuperscript{f} \\
+
+\bottomrule
+\end{tabular}
+\caption{
+	Description of experiments performed.  Each experiment had two treatments
+	which differed either in the initial tasks shown or the framing used 
+	(the priming modality).  
+	During echoed framing, the worker had to respond to the framing language
+	using a combo box input.  The framing language used was as follows:
+	\newline\textsuperscript{a} ``Funded by the laboratory for the visual 
+		perception of Food and Ingredients''
+	\newline\textsuperscript{b} ``Funded by the laboratory for the visual 
+		perception of Objects and Tools''
+	\newline\textsuperscript{c} ``The purpose of this study is to understand the visual perception of Food and Ingredients''
+	\newline\textsuperscript{d} ``The purpose of this study is to understand the visual perception of Objects and Tools''
+	\newline\textsuperscript{e} ``This research is proudly funded by The National 
+		Foundation for Nutritional Awareness''
+	\newline\textsuperscript{f} ``This research is proudly funded by The Global 
+		Foundation for the Recognition of Cultures''
+}
+\label{table:experiments}
+\end{table}
+
+We performed a series of five experiments
+on Amazon's Mechanical Turk\footnote{\url{mturk.com}} using 1071 workers.  
+Every experiment consisted of two treatments, each with 119 workers,
+who performed a single assignment\footnote{Workers could not participate 
+multiple times in our study}\textsuperscript{,}\footnote{On Mechanical Turk, individual 
+assignments are called Human Intelligence Tasks (HITs), but this use of 
+``task'' is 
+different from our current one: in our experiment each HIT actually 
+involves 10 image-labeling tasks.}.  
+The setup in each experiment followed the template depicted in 
+Figure~\ref{fig:task-schematic}.  
+The assignments had two parts.  The first part of the assignment differed
+between the two treatments, and consisted of a set of initial tasks 
+and/or framing (by describing the purpose of the assignment or source of 
+funding).  In the second part of the assignment, workers from both
+treatments completed the same five \textit{test tasks}.  Each of the 
+initial and test tasks required workers to provide five descriptive labels
+for an image.  The tasks were performed one at a time,
+and, in treatments involving both initial and test tasks, there was no
+interruption or distinction made between the initial and test tasks from
+the perspective of the worker.
+
+We analyzed the
+workers' responses to the test tasks to determine whether
+they were influenced by the initial tasks (or framing).  We looked for 
+differences in the distributions of test responses 
+using a $\chi^2$ test.  We then measured the 
+severity of bias induced by initial tasks and framing, by 
+constructing a na\"ive Bayes classifier to infer the workers' 
+treatments based on their responses to test tasks, 
+and measuring its accuracy.
+
+In our first experiment called \textit{intertask-food-objects},
+workers were assigned to either a \textit{food} or \textit{objects} 
+treatment.  Workers from these treatments performed initial tasks 
+in which they labeled, respectively, 
+images depicting either food or (non-food) objects
+(see example images in Figure~\ref{fig:task}A and B).  
+Workers from both treatments then performed five test tasks, which
+contained images
+depicting both food and objects (Figure~\ref{fig:task}C).
+
+The frequencies of words used by
+workers in the \textit{food} and \textit{objects} treatments differed
+significantly during test tasks (by $\chi^2$ test, $p = 6.0 \times 10^{-14}$),
+even though the test tasks were identical in both treatments\footnote{
+	see supplementary text for tabulated statistics.
+}.  Thus earlier tasks do significantly affect later ones, which 
+validates our concerns about the typical microtask methodology.
+
+Having affirmed the \textit{existence} of intertask effects, we sought to
+measure the severity of the bias induced, i.e. $\theta$.
+To measure $\theta$ we used a na\"ive Bayes classifier based on a 
+multinomial distribution over the word frequencies in worker's labels, 
+and measured it's accuracy using leave-one-out cross-validation.  
+We chose the na\"ive Bayes
+classifier for three reasons\footnote{In the supplementary material we 
+  compare alternate classifier configurations, and show that they produce
+similar results.}.  First, it performs well even when the 
+number of features is large compared to the number of training examples.  
+Second, there are no hyperparameters to 
+optimize, which eliminates the need to partition the response data into
+dev and test sets.
+Third, the conditional independance assumption, normally 
+undertaken for pragmatic reasons, is probably a relatively mild in 
+relation to image labels, since they are likely to be less dependent
+on one another than in a coherent passage of text.
+
+To produce word frequency features, worker's labels were split on white
+space and punctuation, and the resulting tokens were spell-corrected based
+on edit-distance to a dictionary of words, followed by stop-word removal
+and lemmatization\footnote{A detailed description of preprocessing steps 
+is available in the supplementary material.}.  The spelling correction
+dictionary was compiled from a combination of WordNet 
+\cite{felbaum1998wordnet} and words
+collected by crawling the World Food section of \url{allrecipes.com}.
+
+Based on the classifier accuracy, intertask effects in the 
+experiment \textit{intertask-food-objects}
+lead to (a lower bound) bias of $\theta=30\%$ between workers from the 
+\textit{food} and \textit{objects} treatments (Figure~\ref{fig:theta}A).
+For reference, the distributions shown in 
+Figure~\ref{fig:l1_example}B have $\theta = 30\%$.  This represents a 
+substantial potential to distort microtask data.
+
+As already discussed, there has been considerable interest in the 
+effects that framing can have on microtask responses
+\cite{Kinnaird2012281,chandler2013breaking,thibodeau2013natural}, and 
+framing effects are arguably similar to inter-task effects in the sense 
+that both arise from the worker's experiences immediately before 
+performing a task.
+Therefore, as a point of comparison, we performed a similar experiment 
+in which we framed the purpose of the tasks.  In the experiment 
+\textit{frame-food-objects}, we used the same test tasks as in 
+\textit{intertask-food-objects}, but the initial tasks were omitted, 
+and in their stead, workers were either told that the study was 
+``Funded by the laboratory for the 
+visual perception of Food and Ingredients'', 
+or ``\ldots of Objects and Tools''.
+
+Framing induced changes in the frequencies of 
+word usage at significance 
+(as determined by $\chi^2$ test; $p=0.0012$).  But, 
+the \textit{extent} of framing-induced bias was not statistically 
+distinguishable from zero ($p =0.37$) (Figure~\ref{fig:theta}A).
+Remarkably, the extent of bias due to framing was weaker than that 
+due to intertask effects ($p=2.1\times 10^{-5}$).
+In other words, the \textit{microtasks themselves}
+had a stronger biasing effect than overt framing.
+
+To assess the persistence of intertask effects, we replicated the 
+\textit{intertask-food-objects} experiments, rotating the ordering of the
+test tasks, so that each test task occupied each of the possible 5 
+positions.  By taking the average bias induced for each test task when 
+occupying a given position, we determined $\theta$ as a function of the 
+task position.
+Bias was strongest for the first test task (about 28\%), 
 but remained significant through all five test tasks 
 ($\alpha=0.05$) sustaining over 12\% bias even when the initial and test 
-tasks were separated by four intervening tasks (Fig. \ref{fig:theta}B).
+tasks were separated by four intervening tasks (Figure~\ref{fig:theta}B).
 
@@
 The initial tasks contained either images 
-depicting food (Fig.~\ref{fig:task}D), or depictions of cultural scenes 
-(of dance, sport, or music) (Fig.~\ref{fig:task}E).  The test tasks, which 
-were, again, identical for both treatments, depicted meals of identifiable 
-cultural origin\footnote{
-	Despite efforts to the contrary, initial tasks 
-	in \textit{intertask-food-culture} are arguably still of
-	identifiable cultural origin, but this would only tend to make our 
-	results more conservative (we discuss this further in the supplementary 
-	text).
-}
-(Fig.~\ref{fig:task}F).
+depicting food (Figure~\ref{fig:task}D), or depictions of cultural scenes 
+(of dance, sport, or music) (Figure~\ref{fig:task}E).  The test tasks, which 
+were, again, identical for both treatments, depicted meals of diverse 
+cultural origin
+%\footnote{
+%  	The food depicted in the initial tasks 
+%	in \textit{intertask-food-culture} are arguably still of
+%	diverse cultural origin, but this would only tend to make our 
+%	results more conservative.
+%}
+(Figure~\ref{fig:task}F).
 
@@
 strong bias as a result of intertask effects (about 50\%) 
-(Fig.~\ref{fig:theta}A).  Again, comparing intertask effects to 
-framing, the experiment (\textit{frame-food-culture}) used
-the same test tasks as in \textit{intertask-food-culture}, but exposed
-workers to statements framing the purpose of the tasks as the recognition 
-of either food or culture.  In this experiment, framing did not induce 
-significant changes in word frequencies (by $\chi^2$ test, $p=0.29$) (Fig.~\ref{fig:theta}A).
+(Figure~\ref{fig:theta}A).  Again, visualizing the word frequencies 
+themselves is difficult, but Figure~\ref{fig:l1_example} provides an 
+example of distributions having $\theta = 50\%$.
+
+Once again, we compared the strength of intertask effects to those due to 
+framing. In the experiment \textit{frame-food-culture} used
+the same test tasks as in \textit{intertask-food-culture}, but before
+workers begin the tasks, we indicated
+that the purpose of the task was either the the recognition of food or 
+culture, depending on the treatment to which the worker was assigned.  
+However, unlike in the previous framing experiment, this time we also 
+included initial tasks in the framing experiment (although they were 
+identical for both treatments).  We did this so that in both experiments,
+workers would have completed the same number of tasks before starting the
+test tasks.  In \textit{frame-food-culture}, framing did not induce 
+significant changes in word frequencies 
+(by $\chi^2$ test, $p=0.29$) (Figure~\ref{fig:theta}A).
 
 It was only when framing was combined with an active reiteration step, 
-that bias reached a comparable extent to that induced by intertask effects.  
-In the experiment \textit{echo-food-objects},
+that bias reached a comparable extent to that induced by intertask 
+effects.  In the experiment \textit{echo-food-objects},
 after framing the purpose of the task (as the recognition of food
@@
 using a combo-box input.  This  ``echoed framing'' induced a bias of about 
-35\% (Fig.~\ref{fig:theta}A). However, it is difficult to say whether this 
+35\% (Figure~\ref{fig:theta}A). However, it is difficult to say whether this 
 should be considered as a framing treatment \textit{per se}:
@@
 
+\begin{table*}
+	\centering
+	\setlength{\tabcolsep}{4pt}
+	\begin{tabular}{ c c c c c }
+
+		\setlength{\tabcolsep}{4pt}
+		\begin{tabular}{ r | c }
+		\toprule
+		\multicolumn{2}{c}{
+			\parbox[c]{2.5cm}{
+				\centering
+					\textit{intertask-food-objects}
+			}} \\
+		\midrule
+		coffee & 38 \\
+		meal & 34 \\
+		cheese & 34 \\
+		apple & 32 \\
+		dessert & 21 \\
+		cup & -30 \\
+		glass & -45 \\
+		table & -70 \\
+		candle & -74 \\
+		food & -80 \\
+		\bottomrule
+		\end{tabular}
+
+&
+
+		\setlength{\tabcolsep}{4pt}
+		\begin{tabular}{ r | c }
+		\toprule
+		\multicolumn{2}{c}{
+			\parbox[c]{2.5cm}{
+				\centering
+				\textit{frame-food-objects}
+			}
+		}\\
+		\midrule
+		bread & 18 \\
+		wine & 18 \\
+		cheese & 16 \\
+		apple & 14 \\
+		oil & 12 \\
+		table & -9 \\
+		meal & -10 \\
+		candle & -12 \\
+		dinner & -13 \\
+		food & -32 \\
+		\bottomrule
+		\end{tabular}
+
+&
+
+		\setlength{\tabcolsep}{4pt}
+		\begin{tabular}{ r | c }
+		\toprule
+		\multicolumn{2}{c}{
+			\parbox[c]{2.5cm}{
+				\centering
+			\textit{echo-food-objects}} 
+		}\\
+		\midrule
+		apple & 24 \\
+		cheese & 23 \\
+		wine & 15 \\
+		coffee & 14 \\
+		oil & 7 \\
+		knife & -24 \\
+		dinner & -26 \\
+		fork & -27 \\
+		candle & -35 \\
+		food & -55 \\
+		\bottomrule
+		\end{tabular}
+
+&
+
+		\setlength{\tabcolsep}{4pt}
+		\begin{tabular}{ r | c }
+		\toprule
+		\multicolumn{2}{c}{
+			\parbox[c]{2.5cm}{
+				\centering
+			\textit{intertask-food-culture}} 
+		}\\
+		\midrule
+		spicy & 26 \\
+		sauce & 17 \\
+		indian & 15 \\
+		buffet & 14 \\
+		exotic & 12 \\
+		festival & -11 \\
+		offering & -12 \\
+		statue & -15 \\
+		india & -20 \\
+		food & -56 \\
+		\bottomrule
+		\end{tabular}
+
+&
+
+		\setlength{\tabcolsep}{4pt}
+		\begin{tabular}{ r | c }
+		\toprule
+		\multicolumn{2}{c}{
+			\parbox[c]{2.5cm}{
+				\centering
+			\textit{frame-food-culture}} 
+		}\\
+		\noalign{\smallskip}
+		\midrule
+		indian & 11 \\
+		banquet & 8 \\
+		spicy & 7 \\
+		asian & 6 \\
+		variety & 6 \\
+		delicious & -6 \\
+		meat & -7 \\
+		festival & -7 \\
+		spice & -7 \\
+		food & -9 \\
+		\bottomrule
+		\end{tabular}
+
+	\end{tabular}
+	\caption{
+		The five words whose frequencies increased, and those whose 
+		frequencies decreased, the most, between treatments of given 
+		experiments, within labels attributed to the first test task.
+		Values indicate the absolute change in number of occurences
+		of the word, and positive values indicate that the food-exposed
+		treatment 
+		used the word with higher frequency.  
+		Note that the word ``food'' is always the most suppressed among
+		food-exposed workers.
+		Word frequencies for 
+		\textit{intertask-food-objects} correspond to the labels attributed
+		to image 1 (see Figure \ref{fig:task1:test}) which is not necessarily 
+		the first 
+		test task due to the tasks being permuted.  There were five times
+		as many workers in \textit{intertask-food-objects}, hence
+		larger absolute differences are observed.
+	}
+	\label{table:top-words}
+\end{table*}
+
 To better understand the nature of 
@@
 during test tasks\footnote{
-	food-related words were identified using the wordnet corpus, 
+	food-related words were identified using the WordNet knowledge base, 
 	augmented with additional words obtained by crawling a recipe website 
 	(see supplementary text for details).
-} (Fig.~\ref{fig:specificity}A).  This finding
+} (Figure~\ref{fig:specificity}A).  This finding
 rules out a seemingly-simple idea that workers emphasize
@@
 greater lexical richness, in reference to food, than their counterparts 
-(as much as 20\% more) (Fig.~\ref{fig:specificity}B).  
+(as much as 20\% more) (Figure~\ref{fig:specificity}B).  
 This is particularly noteworthy in the experiment
@@
 initial tasks.  
-To test this, we used the wordnet corpus to operationalize the 
+To test this, we used the WordNet knowledge base to operationalize the 
 notion of word specialization.  Wordnet establishes relationships between
@@
 used significantly more specialized words, in reference to food 
-(about 15\% more) (Fig.~\ref{fig:specificity}C).
+(about 15\% more) (Figure~\ref{fig:specificity}C).
 It is interesting that such substantial increases in both the lexical 
@@
 
+\section{Discussion}
 Our results can be 
@@
 
+\begin{figure}
+	\includegraphics[scale=0.8]{figs/tasks.jpg}
+	\caption{Examples of (A) task instructions, (B) a framing slide
+		(C) an echoed framing slide, and (D) an image-labeling 
+		task.
+	}
+	\label{fig:hit_preamble}
+\end{figure}
 \paragraph{Microtask setup.}
@@
 The flow of events experienced by a worker when participating in this study 
-is depicted in Fig.~S\ref{fig:task_schematic}.  
+is depicted in Figure~S\ref{fig:task_schematic}.  
 Each experiment was divided into two treatments.  Treatments for a given 
@@
 framing, a framing statement was shown on a slide immediately after the 
-instructions (Fig. S\ref{fig:hit_preamble}B and C).  
+instructions (Figure S\ref{fig:hit_preamble}B and C).  
 Initial tasks, when included, followed next.  The initial tasks consisted of 
@@
 shown in 
-Fig.~S\ref{fig:hit_preamble}D.  Finally, for all HITs, five slides were shown
+Figure~S\ref{fig:hit_preamble}D.  Finally, for all HITs, five slides were shown
 containing test tasks, in the same format as the initial tasks.
 
-\begin{table}
-\centering
-\setlength{\tabcolsep}{2pt}
-\begin{tabular}{c c c c c c}
-\toprule
-Experiment & \parbox[c]{3.8cm}{\centering{Priming modality}} & Treatment & Frame & 
-	Initial tasks & \parbox[c]{2.0cm}{\centering{Test tasks}} \\
-\midrule
-\multirow{2}{*}{\textit{intertask-food-objects}} 
-& \multirow{2}{*}{initial tasks} & \textit{food} & none 
-	& Fig.~S\ref{fig:task1:food} 
-	& \multirow{2}{*}{Fig.~S\ref{fig:task1:test}\textsuperscript{g}} \\
-& & \textit{objects} & none & Fig.~S\ref{fig:task1:obj} & \\
-
-\noalign{\smallskip}
-\hdashline
-\noalign{\smallskip}
-
-\multirow{2}{*}{\textit{frame-food-objects}} 
-& \multirow{2}{*}{framing} & \textit{food} 
-	& ``food''\textsuperscript{a}
-	& none & \multirow{2}{*}{Fig.~S\ref{fig:task1:test}} \\
-& & \textit{objects} 
-	& ``objects''\textsuperscript{b}
-	& none & \\
-
-\noalign{\smallskip}
-\hdashline
-\noalign{\smallskip}
-
-\multirow{2}{*}{\textit{echo-food-objects}} 
-& \multirow{2}{*}{echoed framing} & \textit{food} 
-	& ``food''\textsuperscript{c}
-	& none & \multirow{2}{*}{Fig.~S\ref{fig:task1:test}} \\
-& & \textit{objects} 
-	& ``objects''\textsuperscript{d}
-	& none & \\
-
-\noalign{\smallskip}
-\hdashline
-\noalign{\smallskip}
-
-\multirow{2}{*}{\textit{intertask-food-culture}} 
-& \multirow{2}{*}{initial tasks} & \textit{food} 
-	& none
-	& Fig.~S\ref{fig:task2:food} 
-	& \multirow{2}{*}{Fig.~S\ref{fig:task2:test}} \\
-& & \textit{culture} 
-	& none & Fig.~S\ref{fig:task2:cult} & \\
-
-\noalign{\smallskip}
-\hdashline
-\noalign{\smallskip}
-
-\multirow{2}{*}{\textit{frame-food-culture}} 
-& \multirow{2}{*}{framing} & \textit{food} 
-	& ``food''\textsuperscript{e}
-	& Fig.~S\ref{fig:frame2:ingr} 
-	& \multirow{2}{*}{Fig.~S\ref{fig:task2:test}} \\
-& & \textit{culture} 
-	& ``culture''\textsuperscript{f} 
-	& Fig.~S\ref{fig:frame2:ingr} & \\
-
-\bottomrule
-\end{tabular}
-\caption{
-	Description of experiments performed.  Each experiment had two treatments
-	which differed either in the initial tasks shown or the framing used 
-	(the priming modality).  
-	During echoed framing, the worker had to respond to the framing language
-	using a combo box input (Fig.~S\ref{fig:hit_preamble}C).
-	\newline\textsuperscript{a} ``Funded by the laboratory for the visual 
-		perception of Food and Ingredients''
-	\newline\textsuperscript{b} ``Funded by the laboratory for the visual 
-		perception of Objects and Tools''
-	\newline\textsuperscript{c} ``The purpose of this study is to understand the visual perception of Food and Ingredients''
-	\newline\textsuperscript{d} ``The purpose of this study is to understand the visual perception of Objects and Tools''
-	\newline\textsuperscript{e} ``This research is proudly funded by The National 
-		Foundation for Nutritional Awareness''
-	\newline\textsuperscript{f} ``This research is proudly funded by The Global 
-		Foundation for the Recognition of Cultures''
-	\newline\textsuperscript{g} Both treatments were divided into five 
-	sub-treatments having a different permutation of test tasks.
-}
-\label{table:experiments}
-\end{table}
-
-\begin{figure}
-	\includegraphics[scale=0.8]{figs/tasks.jpg}
-	\caption{Examples of (A) task instructions, (B) a framing slide
-		(C) an echoed framing slide, and (D) an image-labeling 
-		task.
-	}
-	\label{fig:hit_preamble}
-\end{figure}
 Workers were randomly assigned to the treatments, and 
@@
 The permutations were obtained by rotating 
-the order shown in Fig.~S\ref{fig:task1:test} by different amounts. 
+the order shown in Figure~S\ref{fig:task1:test} by different amounts. 
 For example, rotating by one position involves moving the first image to the 
@@
 of \textit{intertask-food-objects} and \textit{frame-food-objects} are shown 
-in Fig.~S\ref{fig:task1:test}.
+in Figure~S\ref{fig:task1:test}.
 
@@
 The images used in the test tasks of \textit{intertask-food-culture} and
-\textit{frame-food-culture} are shown in Fig.~S\ref{fig:task2:test}.
+\textit{frame-food-culture} are shown in Figure~S\ref{fig:task2:test}.
 
@@
 Table~S\ref{table:experiments}, and an example of a framing slide is shown in
-Fig.~S\ref{fig:hit_preamble}B and C.  In \textit{frame-food-objects}
+Figure~S\ref{fig:hit_preamble}B and C.  In \textit{frame-food-objects}
 and \textit{frame-food-culture}, the framing language was based on
@@
 echo back the purpose of the task by selecting it from a combo box
-Fig.~S\ref{fig:hit_preamble}C.
+Figure~S\ref{fig:hit_preamble}C.
 
@@
 
-\begin{table}
-\centering
-\begin{tabular}{l c c}
-\toprule
-Task Type & Number Seen & Fraction of total (\%) \\
-\toprule
-Image transcription & 57 & 28.5 \\
-Information gathering & 46 & 23.0 \\
-Image tagging and classification & 36 & 18.0 \\
-Copy writing and editing & 18 & 9.0 \\
-Text tagging and classification & 15 & 7.5 \\
-Audio/Video transcription & 12 & 6.0 \\
-Survey & 9 & 4.5 \\
-Unknown & 7 & 3.5 \\
-\bottomrule
-\end{tabular}
-\caption{
-	Frequency of various broad task types seen among the 200 most 
-	recently posted tasks on MTurk, accessed on 12 February, 2015.
-}
-\label{table:task_composition}
-\end{table}
 Image labeling tasks are one of the most often cited kinds of tasks in the
@@
 a systematic characterization of MTurk task composition, it does support our
-choice of image labeling as a representative microtask.
+choice of image-labeling as a representative microtask.
 
@@
 the worker belongs ($P_0$ or $P_1$), will do so with an accuracy, $\eta$,
-that is bounded according to Eq.~\ref{l1} from the main text 
+that is bounded according to Eq.~ from the main text 
 (reproduced here):
-\begin{equation}
-	\theta \geq 2\eta - 1.
-	\label{eq:sup:l1}
-\end{equation}
+%\begin{equation}
+%	\theta \geq 2\eta - 1.
+%	\label{eq:sup:l1}
+%\end{equation}
 
@@
 for every $\mathcal{A}$
-\begin{align}
-		\theta \geq 2\eta - 1.
-		\label{eq:sup:l1_again}
-\end{align}
+%\begin{align}
+%		\theta \geq 2\eta - 1.
+%		\label{eq:sup:l1_again}
+%\end{align}
 
 \paragraph{Using cross-validation accuracy to lower-bound bias.}
-	In order for Eq.~\ref{eq:sup:l1_again} to be applicable, it is necessary to 
+	In order for Eq.~ to be applicable, it is necessary to 
 	obtain an unbiased estimate of a classifier's accuracy.  To do so, it is
@@
 \end{figure}
-The inequality in Eq.~\ref{eq:sup:l1_again}
+The inequality in Eq.~
 asserts that a classifier's performance in predicting class membership
@@
 appropriate to look at what affect these decisions had, \textit{post-hoc}.  
-We reproduce the plot from Fig.~\ref{fig:theta}A in the main text, 
+We reproduce the plot from Figure~\ref{fig:theta}A in the main text, 
 this time using different combinations of preprocessing options,
 and using both the na\"ive Bayes and an SVM classifier, in 
-Fig.~S\ref{fig:theta_sup}.
+Figure~S\ref{fig:theta_sup}.
 
@@
 of $\theta$ estimate for this experiment in 
-Fig.~S\ref{fig:theta_sup} (G to J) is inflated.
+Figure~S\ref{fig:theta_sup} (G to J) is inflated.
 
@@
 na\"ive Bayes classifier and our particular choice of preprocessing steps, 
-as shown in Fig.~\ref{fig:theta} of the main text, are representative.
+as shown in Figure~\ref{fig:theta} of the main text, are representative.
 
@@
 	position in which they had been entered (i.e. which of the five text 
-	inputs in the task interface, Fig.~S\ref{fig:hit_preamble}) 
+	inputs in the task interface, Figure~S\ref{fig:hit_preamble}) 
 	as well as the test tasks in which the word had been provided.
@@
 	\textit{legal set}, which was formed by the union of
-	the wordnet corpus, the stop word list, and a set of words seen while 
+	the wordnet knowledge base, the stop word list, and a set of words 
+	seen while 
 	crawling the world food section of the allrecipes.com website.  We
@@
 
-\begin{table}
-	\centering
-	\setlength{\tabcolsep}{4pt}
-	\begin{tabular}{ c c c c c }
-
-		\setlength{\tabcolsep}{4pt}
-		\begin{tabular}{ r | c }
-		\toprule
-		\multicolumn{2}{c}{
-			\parbox[c]{2.5cm}{
-				\centering
-					\textit{intertask-food-objects}
-			}} \\
-		\midrule
-		coffee & 38 \\
-		meal & 34 \\
-		cheese & 34 \\
-		apple & 32 \\
-		dessert & 21 \\
-		cup & -30 \\
-		glass & -45 \\
-		table & -70 \\
-		candle & -74 \\
-		food & -80 \\
-		\bottomrule
-		\end{tabular}
-
-&
-
-		\setlength{\tabcolsep}{4pt}
-		\begin{tabular}{ r | c }
-		\toprule
-		\multicolumn{2}{c}{
-			\parbox[c]{2.5cm}{
-				\centering
-				\textit{frame-food-objects}
-			}
-		}\\
-		\midrule
-		bread & 18 \\
-		wine & 18 \\
-		cheese & 16 \\
-		apple & 14 \\
-		oil & 12 \\
-		table & -9 \\
-		meal & -10 \\
-		candle & -12 \\
-		dinner & -13 \\
-		food & -32 \\
-		\bottomrule
-		\end{tabular}
-
-&
-
-		\setlength{\tabcolsep}{4pt}
-		\begin{tabular}{ r | c }
-		\toprule
-		\multicolumn{2}{c}{
-			\parbox[c]{2.5cm}{
-				\centering
-			\textit{echo-food-objects}} 
-		}\\
-		\midrule
-		apple & 24 \\
-		cheese & 23 \\
-		wine & 15 \\
-		coffee & 14 \\
-		oil & 7 \\
-		knife & -24 \\
-		dinner & -26 \\
-		fork & -27 \\
-		candle & -35 \\
-		food & -55 \\
-		\bottomrule
-		\end{tabular}
-
-&
-
-		\setlength{\tabcolsep}{4pt}
-		\begin{tabular}{ r | c }
-		\toprule
-		\multicolumn{2}{c}{
-			\parbox[c]{2.5cm}{
-				\centering
-			\textit{intertask-food-culture}} 
-		}\\
-		\midrule
-		spicy & 26 \\
-		sauce & 17 \\
-		indian & 15 \\
-		buffet & 14 \\
-		exotic & 12 \\
-		festival & -11 \\
-		offering & -12 \\
-		statue & -15 \\
-		india & -20 \\
-		food & -56 \\
-		\bottomrule
-		\end{tabular}
-
-&
-
-		\setlength{\tabcolsep}{4pt}
-		\begin{tabular}{ r | c }
-		\toprule
-		\multicolumn{2}{c}{
-			\parbox[c]{2.5cm}{
-				\centering
-			\textit{frame-food-culture}} 
-		}\\
-		\noalign{\smallskip}
-		\midrule
-		indian & 11 \\
-		banquet & 8 \\
-		spicy & 7 \\
-		asian & 6 \\
-		variety & 6 \\
-		delicious & -6 \\
-		meat & -7 \\
-		festival & -7 \\
-		spice & -7 \\
-		food & -9 \\
-		\bottomrule
-		\end{tabular}
-
-	\end{tabular}
-	\caption{
-		The five words whose frequencies increased, and those whose 
-		frequencies decreased, the most, between treatments of given 
-		experiments, within labels attributed to the first test task.
-		Positive values indicate that the food-exposed treatment
-		used the word with higher frequency.  
-		Note that the word ``food'' is always the most suppressed among
-		food-exposed workers.
-		Word frequencies for 
-		\textit{intertask-food-objects} correspond to the labels attributed
-		to image 1 (see Fig. \ref{fig:task1:test}) which is not necessarily 
-		the first 
-		test task due to the tasks being permuted.  There were five times
-		as many workers in \textit{intertask-food-objects}, hence
-		larger absolute differences are observed.
-	}
-	\label{table:top-words}
-\end{table}
-
 \paragraph{Identification of food-related terms.}
-The wordnet corpus is composed of synsets, which are particular senses 
+The wordnet knowledge base is composed of synsets, 
+which are particular senses 
 (meanings) and a set of word forms bearing that meaning. A given word form, 
 such as ``ring'' has multiple senses (``to ring a bell'', ``a wedding ring''),
-and so can be part of many synsets.  Since the wordnet corpus was designed
+and so can be part of many synsets.  Since the wordnet 
+knowledge base was designed
 to carry semantic information, the synset is the basic organizing element
@@
 
-The subset of the wordnet corpus induced by the hyponyms of \textit{food.n.01}
+The subset of the wordnet knowledge base induced by the hyponyms of \textit{food.n.01}
 and \textit{food.n.02} consists of 3590 word-forms.  Manual
@@
 \textit{frame-food-culture}, we had images containing many ethnic 
-foods, we decided to augment the wordnet corpus with words learned by 
+foods, we decided to augment the wordnet knowledge base with words learned by 
 crawling the world food section of the allrecipes.com website.
@@
 produced by two experimental treatments.  In performing this calculation,
-we used the wordnet corpus, which has a set of hypernym-hyponym relationships.
+we used the wordnet knowledge base, which has a set of hypernym-hyponym relationships.
 The first step in performing this calculation was to map the words occurring 

### 2015-09-22 docs/publications/2015.08_CHI/example.py

@@ -1,0 +1,23 @@
+
+
+
+
+
+def extract_post(soup):
+	comments_container = soup.find('div', class_='snapComments')
+	post['comments'] = [
+		extract_comment(c) 
+		for c in comment_container.find_all('ul', class_='comments')
+	]
+
+def extract_comment(comment_div)
+	comment['body'] = 'stuff found in comment'
+
+	replies_container = comment_div.find('li').find('ul')
+	comment['comments'] = [
+		extract_comment(c)
+		for c in replies_container.find_all('ul', class_='comments')
+	]
+
+def extract_deep_comments()
+	pass

### 2015-09-22 src/example_distributions.py

@@ -1,0 +1,132 @@
+#!/usr/bin/env python
+
+import json
+import util
+import sys
+import random
+import numpy as np
+import time
+import os
+
+try:
+	import matplotlib.pyplot as plt
+	import matplotlib 
+	import matplotlib.gridspec as gridspec
+	from matplotlib.ticker import MultipleLocator, FormatStrFormatter
+except ImportError:
+	print 'could not import matplotlib.'
+
+FIG_PATH = (
+	'/Users/enewel3/projects/priming/docs/publications/'
+	'2014.09_SCIENCE/figs/normal_example.pdf'
+)
+
+def calculate_l1(dist1, dist2):
+	l1 = 0
+	total_area = 0
+	for x1, x2 in zip(dist1, dist2):
+		l1 += max(0, x1 - x2)
+		total_area += x1
+
+	l1 = l1 / float(total_area)
+	return l1
+
+
+def get_normal_dist(mu,sigma,X):
+	sigma = float(sigma)
+	return [
+		np.e**(-(x - mu)**2 / sigma**2)
+		for x in X
+	]
+
+
+def plot_normal_distributions():
+
+	# make a figure with three subplots
+	figWidth = 8.7 / 2.54 	# conversion from PNAS spec in cm to inches
+	figHeight = 3/5.5*figWidth	# a reasonable aspect ratio
+	fig = plt.figure(figsize=(figWidth, figHeight))
+	gs = gridspec.GridSpec(1,2)
+
+	# now plot the vocabulary data
+	ax1 = plt.subplot(gs[0])
+
+	X = range(1000)
+	Y1 = get_normal_dist(428, 150, X)
+	Y2 = get_normal_dist(572, 150, X)
+
+	print calculate_l1(Y1, Y2)
+	series_1 = ax1.plot(X, Y1, color='0.25')
+	series_2 = ax1.plot(X, Y2, color='0.25', linestyle=':')
+	plt.tick_params(
+		axis='y', which='both', left='off', right='off', labelleft='off')
+	plt.tick_params(
+		axis='x', which='both', bottom='off', top='off', labelbottom='off')
+
+	Y1 = get_normal_dist(459, 150, X)
+	Y2 = get_normal_dist(541, 150, X)
+
+	ax2 = plt.subplot(gs[1], sharey=ax1)
+	print calculate_l1(Y1, Y2)
[…]

### 2015-09-22 src/zipf.py

@@ -1,0 +1,124 @@
+#!/usr/bin/env python
+from collections import Counter
+import json
+import util
+import sys
+import random
+import numpy as np
+import time
+import os
+
+try:
+	import matplotlib.pyplot as plt
+	import matplotlib 
+	import matplotlib.gridspec as gridspec
+	from matplotlib.ticker import MultipleLocator, FormatStrFormatter
+except ImportError:
+	print 'could not import matplotlib.'
+
+
+def harmonic(N,s):
+	H = 0
+	for n in range(1,N+1):
+		H += 1/float(n**s)
+
+	return H
+
+def p_zipf(x,s=1,N=1000):
+	H = harmonic(N,s)
+	numerator = 1 / float(x**s)
+	return numerator / H
+	
+
+def calculate_zipf_divergence(zipf_sampler1, zipf_sampler2):
+
+	max_index = max(zipf_sampler1.N, zipf_sampler2.N)
+	TV = 0
+
+	for i in range(1, max_index+1):
+		TV += abs(zipf_sampler1.pdf(i) - zipf_sampler2.pdf(i))
+
+	return TV
+
+
+class zipf_sampler(object):
+	def __init__(self, s=1, N=1000):
+		self.s = s
+		self.N = N
+		self.H = harmonic(N,s)
+		self.cdf = self.make_cdf(self.s, self.N)
+
+	def pdf(self, x):
+		if x > self.N:
+			return 0
+		return 1 / (float(x**self.s) * self.H)
+
+	def make_cdf(self, s, N):
+		cdf = []
+		last_entry = 0
+		for x in range(1, N+1):
+			this_entry = last_entry + self.pdf(x)
+			cdf.append(this_entry)
+			last_entry = this_entry
+
+		return cdf
+
+	def sample(self):
+		q = random.random()
+		i = 1
+		while q > self.cdf[i]:
+			i += 1
+
+		return i
+
+
+def measure_TV_naive(counts1, counts2):
+	score = 0
+	k = float(sum(counts1.values()))
+	keys = set(counts1.keys() + counts2.keys())
+	for key in keys:
+		score += max(counts1[key], counts2[key])
+
+	return score / k - 1
+
+
+def measure_TV_adjusted(counts1, counts2):
+	score = 0
+	k = float(sum(counts1.values()))
+	keys = set(counts1.keys() + counts2.keys())
+	for key in keys:
+
+		big = max(counts1[key], counts2[key])
[…]

### 2015-09-22 docs/publications/2015.08_CHI/man.tex
almost done

@@
 \author{%
-  \alignauthor{Edward Newell\\
-    \affaddr{Network Dynamics Group\\
+  \alignauthor{Edward Newell\textsuperscript{*}, Derek Ruths\\
 	School of Computer Science\\ McGill University}\\
     \affaddr{Montreal, Qu\'ebec}\\
-    \email{e-mail address}}\\
+	\textsuperscript{*}\email{edward.newell@mail.mcgill.ca} }\\
+
   \alignauthor{2nd Author Name\\
@@
 \textit{food} and \textit{objects} treatments (Figure~\ref{fig:theta}A).
-For reference, the distributions shown in 
+It is difficult to visualize the distributions of word frequencies,
+but for reference, the distributions shown in 
 Figure~\ref{fig:l1_example}B have $\theta = 30\%$.  This represents a 
@@
 Therefore, as a point of comparison, we performed a similar experiment 
-in which we framed the purpose of the tasks.  In the experiment 
+in which we suggested the focus of the study by stating a name for
+the requester within the task.
+In the experiment 
 \textit{frame-food-objects}, we used the same test tasks as in 
@@
 distinguishable from zero ($p =0.37$) (Figure~\ref{fig:theta}A).
-Remarkably, the extent of bias due to framing was weaker than that 
+And so, remarkably, the extent of bias due to framing was weaker than that 
 due to intertask effects ($p=2.1\times 10^{-5}$).
 In other words, the \textit{microtasks themselves}
-had a stronger biasing effect than overt framing.
+had a stronger biasing effect than framing.
 
@@
 test tasks, so that each test task occupied each of the possible 5 
-positions.  By taking the average bias induced for each test task when 
+test-task positions (see Figure \ref{fig:task-schematic}).  
+By taking the average bias induced for each test task when 
 occupying a given position, we determined $\theta$ as a function of the 
@@
 depicting food (Figure~\ref{fig:task}D), or depictions of cultural scenes 
-(of dance, sport, or music) (Figure~\ref{fig:task}E).  The test tasks, which 
+(of dance, sport, or music) (Figure~\ref{fig:task}E).  The test tasks, 
+which 
 were, again, identical for both treatments, depicted meals of diverse 
@@
 Once again, we compared the strength of intertask effects to those due to 
-framing. In the experiment \textit{frame-food-culture} used
+framing. In the experiment \textit{frame-food-culture} we used
 the same test tasks as in \textit{intertask-food-culture}, but before
-workers begin the tasks, we indicated
+workers began the tasks, we indicated
 that the purpose of the task was either the the recognition of food or 
@@
 included initial tasks in the framing experiment (although they were 
-identical for both treatments).  We did this so that in both experiments,
-workers would have completed the same number of tasks before starting the
-test tasks.  In \textit{frame-food-culture}, framing did not induce 
+identical for both treatments).  We did this in order to include a pair of
+comparable priming- and framing-based experiments
+for which both had the same overall number of tasks.
+In \textit{frame-food-culture}, framing did not induce 
 significant changes in word frequencies 
@@
 It was only when framing was combined with an active reiteration step, 
-that bias reached a comparable extent to that induced by intertask 
-effects.  In the experiment \textit{echo-food-objects},
+that framing-induced bias reached a comparable extent to that induced by 
+intertask effects.  In the experiment \textit{echo-food-objects},
 after framing the purpose of the task (as the recognition of food
@@
 		\textit{intertask-food-objects} correspond to the labels attributed
-		to image 1 (see Figure \ref{fig:task1:test}) which is not necessarily 
-		the first 
+		to image 1 which is not necessarily the first 
 		test task due to the tasks being permuted.  There were five times
@@
 tasks) would label test tasks using 
-food-related words more often.  However, this was not generally 
-the case. In \textit{intertask-food-culture}, food-exposed
+food-related words more often.  To test this we developed an 
+automated approach to labeling food-words based on the 
+WordNet knowledge base \cite{felbaum1998wordnet}.
+
+WordNet provides
+hyponym and hypernym relations between words.  A hypernym is a 
+generalization (for example, ``bread'' is a hypernym of ``pumpernickle''), 
+while a hyponym is a specialization.  We took took the set of food-words
+to be all those reachable through
+a chain of hyponym relations from the wordsenses 
+\texttt{food.n.01} and \texttt{food.n.02}, in other words, all words
+denoting a specific kind of food (a total of 3590 words).  
+To improve the coverage of words for
+less widespread foods, we augmented this set with all words
+discovered while crawling the World Food section of \url{allrecipes.com} 
+which were not already in WordNet.
+
+To validate the resulting set of 
+food words, three independant annotators labeled 500 words selected from 
+workers' responses as either food or non-food, and these were
+compared to the labels derived using the automated approach.
+Among those words, 26\% were 
+deemed to be food by the majority of annotators.  
+Taking the majority label among annotators to be the correct one, 
+the automatically-identified food-words
+had 88\% correspondence to the human annotators.  Treating the
+automated identification of food words as another annotator, there 
+was an inter-rater reliability of 82.4\%.
+
+Using the automated labeling of food words, we found that, in fact
+workers exposed to food (via prior tasks or framing) did not necessarily
+use more food-words when labelng images in the test tasks.
+In \textit{intertask-food-culture}, food-exposed
 workers actually used significantly \textit{fewer} food-related words 
-during test tasks\footnote{
-	food-related words were identified using the WordNet knowledge base, 
-	augmented with additional words obtained by crawling a recipe website 
-	(see supplementary text for details).
-} (Figure~\ref{fig:specificity}A).  This finding
+during test tasks (Figure~\ref{fig:specificity}A).  This finding
 rules out a seemingly-simple idea that workers emphasize
@@
 initial tasks.  
-To test this, we used the WordNet knowledge base to operationalize the 
-notion of word specialization.  Wordnet establishes relationships between
-117,798 English nouns, indicating which words are specializations
-(or generalizations) of others \cite{felbaum1998wordnet}. 
-%miller1995wordnet,}.  
-For example, ``pumpernickel'' is a specialization of ``bread''.
-Within each experiment, we determined the percent-excess of food-related
-words that were more specialized in the food-exposed treatment relative
-to the other treatment (detailed calculation in the supplementary text).
+To test this, we used the hypernym and hyponym relations in WordNet 
+to operationalize the notion of word specialization.  
+Within each experiment, we determined relative specificity
+of the food-words, between the treatments using the following equation:
+\begin{equation}
+	S(P,Q) = \frac{
+		\sum_{w\in P}\sum_{v\in Q} \left(
+			\mathbf{1}_{[w>v]} - \mathbf{1}_{[v>w]} \right)
+	}{
+		\sum_{w\in P}\sum_{v\in Q} \left(
+			\mathbf{1}_{[w>v]} + \mathbf{1}_{[v>w]} \right)
+	},
+\end{equation}
+where $P$ and $Q$ are sets of words associated to different experimental 
+treatments, and $\mathbf{1}_{[w>v]}$ evaluates
+to 1 if synset $w$ is more specific than (i.e. is a hyponym of) synset $v$.
+The relative specificity lies within $[-1,1]$; 
+we report it as a percentage.
+In computing this quantity between two treatments, we first computed the 
+relative specificity for the treatments separately for each test task, and 
+averaged the results obtained accross the five test tasks.
 
@@
 their focus toward salient features \cite{kellman2009perceptual}.  
-Using strategic task exposure, it might be possible to guide workers' focus 
-and salience attribution, enabling expert-level judgment in a wider variety of
+Using strategic task exposure during training, 
+it might be possible to guide workers' focus 
+and salience attribution, enabling expert-level 
+judgment in a wider variety of
 crowdsourced applications.
@@
 
-\pagebreak
-\section*{Supplementary Material}
-
-Microtask platforms are an increasingly popular way to solicit experimental
-participants, as well as to annotate large datasets and obtain other 
-judgments which are difficult to automate using only a computer.  
-Due to the popularity of microtask platforms, there is interest in 
-understanding how various task design factors
-influence the reliabality of data obtained using microtask platforms.  
-Since workers typically perform similar tasks in quick succession, there is
-an opportunity for earlier tasks to effectively prime workers, and induce 
-bias in the results obtained.
-Here we describe in detail experiments presented in the main text, in which
-we investigate the effect that prior tasks have on the responses given during
-subsequent ones.
-
-\subsection*{Materials and Methods}
-
-\begin{figure}
-	\includegraphics[scale=0.8]{figs/tasks.jpg}
-	\caption{Examples of (A) task instructions, (B) a framing slide
-		(C) an echoed framing slide, and (D) an image-labeling 
-		task.
-	}
-	\label{fig:hit_preamble}
-\end{figure}
-\paragraph{Microtask setup.}
-
-The work presented in the main text consisted of six experiments involving
-HITs (bundles of tasks) performed on Amazon's Mechanical Turk (MTurk)
-platform.  
-The flow of events experienced by a worker when participating in this study 
-is depicted in Figure~S\ref{fig:task_schematic}.  
-Each experiment was divided into two treatments.  Treatments for a given 
-experiment differed with respect to a particular priming modality, which 
-served as the independent variable
-(as specified in Table~S\ref{table:experiments}).  
-The HITs for treatments of the same experiment always involved the same
-test tasks (the last five tasks in the HIT),
-the results of which served as the dependent variable.
-\begin{figure}
-	\begin{center}
-	\includegraphics[scale=0.8]{figs/task_schematic.pdf}
-	\caption{Flow of events as experienced by a worker participating in
-		our study.  Steps with a dash outlined are only performed by 
-		workers assigned to certain treatments 
-		(see Table~S\ref{table:experiments}).  Steps outlined in orange are
-		part of MTurk's interface, and are common to any 
-		microtask performed on that platform.  Steps outlined in black are
-		specific to our HIT.
-	}
-	\label{fig:task_schematic}
-	\end{center}
-\end{figure}
-
-All HITs were presented as a series of slides.  The first 
-slide consisted of a brief set of instructions.  For HITs that included 
-framing, a framing statement was shown on a slide immediately after the 
-instructions (Figure S\ref{fig:hit_preamble}B and C).  
-Initial tasks, when included, followed next.  The initial tasks consisted of 
-a series of five slides, each containing an image-labeling task like the one 
-shown in 
-Figure~S\ref{fig:hit_preamble}D.  Finally, for all HITs, five slides were shown
-containing test tasks, in the same format as the initial tasks.
-
-Workers were randomly assigned to the treatments, and 
-a given worker could only complete one HIT related to this study.  
-In \textit{intertask-food-culture}, the \textit{food} and \textit{culture}
-treatments were both divided into five sub-treatments, 
-in which the test tasks were permuted.  
-The permutations were obtained by rotating 
-the order shown in Figure~S\ref{fig:task1:test} by different amounts. 
-For example, rotating by one position involves moving the first image to the 
-second position, the second image to the third position, and so on, and 
-moving the last image to the first position.  
-The five different possible rotations were used for the five 
-sub-treatments.  This enabled us to study the effects on each image when
-it occurred in different positions relative to the initial tasks.
-
-\paragraph{Selection of images.}
-
-The images used in the initial tasks for \textit{intertask-food-objects}  
-are shown in Figs.~S\ref{fig:task1:food} (\textit{food} treatment) and 
-S\ref{fig:task1:obj} (\textit{objects} treatment).
-We took care to exclude objects from
-the food-images (except for the dish supporting the food in some cases), and 
-to exclude food from the object-images.  The images used for the test tasks
-of \textit{intertask-food-objects} and \textit{frame-food-objects} are shown 
-in Figure~S\ref{fig:task1:test}.
-
-The images used in the initial tasks
-for \textit{intertask-food-culture} are shown in Figs.~S\ref{fig:task2:food} 
-(\textit{food} treatment) and S\ref{fig:task2:cult} 
-(\textit{culture} treatment).
-We selected the initial images for the treatments of this experiment to 
-respectively reflect depict food and culture.
-Naturally, since food is a very
-important aspect of culture, pictorial depictions of the two concepts 
-cannot be cleanly separated,
-and images depicting food inevitably also depict culture.
-However, the fact that the images for the initial tasks in the 
-\textit{food} treatment 
-of \textit{intertask-food-culture} also depict culture
-will only tend to make the \textit{food} and \textit{culture}
-treatments more similar. 
-This would tend to reduce the severity of intertask 
-effects, but we nevertheless still observed strong intertask effects.
-Thus, the presence of culture in the food-related initial images of 
-\textit{intertask-food-culture} does not seem to have been problematic.
-The images used in the test tasks of \textit{intertask-food-culture} and
-\textit{frame-food-culture} are shown in Figure~S\ref{fig:task2:test}.
-
-\begin{figure}
-	\begin{center}
-	\includegraphics{figs/task1-food.jpg}
-	\end{center}
-	\caption{
-		Images used in the initial tasks for the
-		\textit{food} treatment of \textit{intertask-food-objects}.  
-		The numbers show the order in which the 
-		images were presented to workers.
-	}
-	\label{fig:task1:food}
-\end{figure}
-
-\begin{figure}
-	\begin{center}
-	\includegraphics{figs/task1-obj.jpg}
-	\end{center}
-	\caption{
-		Images used in the initial tasks for the
-		\textit{objects} treatment of \textit{intertask-food-objects}.  
-		The numbers show the order in which the images were presented to 
-		workers.
-	}
-	\label{fig:task1:obj}
-\end{figure}
-
-\begin{figure}
-	\begin{center}
-	\includegraphics{figs/task1-test.jpg}
-	\end{center}
-	\caption{
-		Images used in the test tasks for \textit{intertask-food-objects}
-		and \textit{frame-food-objects}.  
-		The numbers show the order in which the 
-		images were presented to workers in \textit{frame-food-objects};
-		in \textit{intertask-food-objects}, five different orderings were
-		used, which can be obtained by taking the numbers shown, $n$,
-		and replacing them by $n + c \bmod 5$ for $c$ running from 0 to 4.
-	}
-	\label{fig:task1:test}
-\end{figure}
-
-\begin{figure}
-	\begin{center}
-	\includegraphics{figs/task2-food.jpg}
-	\end{center}
-	\caption{
-		Images used in the initial tasks for the
-		\textit{food} treatment of \textit{intertask-food-culture}.  
-		The numbers show the order in which the 
-		images were presented to workers.
-	}
-	\label{fig:task2:food}
-\end{figure}
-
-\begin{figure}
-	\begin{center}
-	\includegraphics{figs/task2-cult.jpg}
-	\end{center}
-	\caption{
-		Images used in the initial tasks for the
-		\textit{culture} treatment of \textit{intertask-food-culture}.  
-		The numbers show the order in which the 
-		images were presented to workers.
-	}
-	\label{fig:task2:cult}
-\end{figure}
-
-\begin{figure}
-	\begin{center}
-	\includegraphics{figs/task2-test.jpg}
-	\end{center}
-	\caption{
-		Images used in the test tasks for \textit{intertask-food-culture} 
-		and \textit{frame-food-culture}.  
-		The numbers show the order in which the 
-		images were presented to workers.
-	}
-	\label{fig:task2:test}
-\end{figure}
-
-\begin{figure}
-	\begin{center}
-		\includegraphics{figs/task2-ingr.jpg}
-	\end{center}
-	\caption{
-		Images used in initial tasks for \textit{frame-food-culture} 
-		(both for the \textit{food} and \textit{culture} treatments).
-		The numbers show the order in which the images were presented to 
-		workers.
-	}
-	\label{fig:frame2:ingr}
-\end{figure}
-
-\paragraph{Framing.}
-We framed tasks by including a message, near the beginning of the HIT, that 
-suggested a particular purpose for the tasks.
-The precise language used is shown in 
-Table~S\ref{table:experiments}, and an example of a framing slide is shown in
-Figure~S\ref{fig:hit_preamble}B and C.  In \textit{frame-food-objects}
-and \textit{frame-food-culture}, the framing language was based on
-naming the (fictitious) entity running the study, for example
-``The Global Foundation for the Recognition of Cultures'',
-or ``Laboratory for the visual perception of Objects and Tools''.
-In \textit{echo-food-objects}, we stated the purpose explicitly 
-(``The purpose of this task is \dots''), and then required the worker to
-echo back the purpose of the task by selecting it from a combo box
-Figure~S\ref{fig:hit_preamble}C.
-
-In \textit{frame-food-objects} and \textit{echo-food-objects}, we did not
-include any initial tasks, meaning that the test tasks followed the framing
-slide immediately.  One could argue that a fairer comparison would be achieved
-by including initial tasks even for framing experiments (but keeping the
-initial tasks constant while varying the framing language), since the worker
-would be ``warmed up'' before performing the test tasks, as is the case for
-the experiments investigating the effect of initial tasks. 
-We therefore adopted this approach in the experiment 
-\textit{frame-food-culture}, in which workers performed the same 
-initial tasks containing images that depicted food in both the \textit{food}
-and \textit{culture} treatments.  It would seem that the framing effect in 
-\textit{frame-food-culture} was reduced by the initial tasks, possibly because
-intertask effects tend to override framing. Further experimentation 
-would be necessary to be sure, but this was not the purpose of our study.
-
-\subsection*{MTurk's task composition}
-
-Image labeling tasks are one of the most often cited kinds of tasks in the
-literature.  To determine whether they do indeed reflect an important fraction
-of MTurk tasks, we accessed MTurk on 12 February, 2015, and coded the 200 
-most recently posted tasks based on their title and description, 
-into one of seven categories.
-
-Tasks relating to image tagging and categorization represented 18\% of the 
-total.  Of all tasks seen, those in which images are the primary input
-account for 46.5\%.  Considering tasks regardless of input modality (e.g.
-text, image, audio, or multimedia), those that involved some kind of tagging
-or categorization accounted for 25.5\%.  
-The detailed counts for our categorization
-of task types are shown in Table~S\ref{table:task_composition}.  
-While this does not reflect a full and
-a systematic characterization of MTurk task composition, it does support our
-choice of image-labeling as a representative microtask.
-
-\subsection*{Testing for intertask and framing effects using $\chi^2$}
-
-\begin{table}
-\centering
-\begin{tabular}{c c c c}
-\toprule
-Experiment & Degrees of freedom & $\chi^2$ & $p$-value\\
-\toprule
-\textit{intertask-food-objects} & 117 & 268.7 & $6.0 \times 10^{-14}$\\
-\textit{frame-food-objects} & 116 & 167.8 & $1.2 \times 10^{-3}$\\
-\textit{echo-food-objects} & 126 & 381.3 & $1.7 \times 10^{-27}$\\
-\textit{intertask-food-culture} & 120 & 447.5 & $2.8 \times 10^{-39}$\\
-\textit{frame-food-culture} & 119 & 127.2 & $0.29$\\
-\bottomrule
-\end{tabular}
-\caption{
-	Results for Pearson's $\chi^2$ test of homogeneity of the word-frequencies
-	between treatments from each experiment.  This shows that the treatments
-	significantly affected word usage, 
-	except in the case of \textit{frame-food-culture}.
-}
-\label{table:chi2}
-\end{table}
-
-\begin{table}
-\centering
-\begin{tabular}{c c c c c}
-\toprule
-Experiment & Treatment & Degrees of freedom & $\chi^2$ & $p$-value\\
-\toprule
-\noalign{\smallskip}
-\multirow{2}{*}{\textit{intertask-food-objects}} & \textit{food} & 65 & 39.0 & $1.0$\\
- & \textit{objects} & 65 & 53.2 & $0.85$\\
-
-\noalign{\smallskip}
-\hdashline
-\noalign{\smallskip}
-
-\multirow{2}{*}{\textit{frame-food-objects}} & \textit{food} & 67 & 41.3 & $0.99$\\
- & \textit{objects} & 62 & 66.9 & $0.31$\\
-
-\noalign{\smallskip}
-\hdashline
-\noalign{\smallskip}
-
-\multirow{2}{*}{\textit{echo-food-objects}} & \textit{food} & 66 & 40.9 & $0.99$\\
- & \textit{objects} & 66 & 35.6 & $1.0$\\
-
-\noalign{\smallskip}
-\hdashline
-\noalign{\smallskip}
-
-\multirow{2}{*}{\textit{intertask-food-culture}} & \textit{food} & 62 & 65.9 & $0.34$\\
- & \textit{culture} & 68 & 57.2 & $0.82$\\
-
-\noalign{\smallskip}
-\hdashline
-\noalign{\smallskip}
-
-\multirow{2}{*}{\textit{frame-food-culture}} & \textit{food} & 57 & 49.6 & $0.75$\\
- & \textit{culture} & 64 & 55.1 & $0.78$\\
-
-\bottomrule
-\end{tabular}
-\caption{
-	Results for Pearson's $\chi^2$ test of homogeneity of the word-frequencies
-	within treatments, which were randomly partitioned for the test.  This
-	shows that word-usage within treatments is homogeneous.
-}
-\label{table:chi2_within}
-\end{table}
-
-To test whether intertask and framing effects induced statistically 
-significant changes in word frequencies, we assembled a contingency table
-for each experiment, containing the frequencies of words in each treatment.  
-Any words appearing less than ten times for
-an experiment (i.e. one whose expected frequency would be less than five in a 
-given cell of the contingency table)
-were lumped together into a separate `OTHER' category, to ensure validity
-of the test.  The degrees of freedom, test statistic, and $p$-values were
-then calculated according to Pearson's $\chi^2$ test, using 
-Yates' correction.  Results are tabulated in Table~S\ref{table:chi2}.
-With the exception of \textit{frame-food-culture}, all experiments showed 
-significant changes in word-frequencies in response
-to the task or framing exposures, at $\alpha=0.05$, leading us to 
-reject the null hypothesis that the priming exposures had no effect.
-
-The use of Pearson's $\chi^2$ test has been criticized in linguistic 
-applications, due to the finding that many corpora are not themselves
-homogeneous \cite{kilgarriff1996comparing}.  
-This results from the fact that corpora are made of many
-distinct texts, together with the fact that words tend to come in bursts.
-When a rare word is encountered in a given text, it is much more likely
-to be encountered again in the same text. This means that
-frequencies within given texts are often far from the average, causing 
-corpora to be heterogeneous.
-As a result, if a corpus is randomly split, putting half of the texts in one 
-set, and half in another, there can be a significant non-homogeneity between 
-the halves (when tested using Pearson's $\chi^2$ test).  Thus, finding two
-corpora to be different according to a $\chi^2$ test might not 
-indicate that they are meaningfully different.
-
-This concern does not apply to our case, because the ``texts'' are 
-individual responses from workers, which will not, in general, be subject to 
-the ``burstiness'' phenomenon.  Nevertheless, to test this, we randomly 
-divided the workers from each experimental treatment into two sets, and 
-tested the homogeneity 
-between these sets.  Results are tabulated in Table~S\ref{table:chi2_within}, 
-and show that treatments 
-\textit{are} homogeneous.  Thus, the lack of homogeneity \textit{between} 
-the treatments of given experiments can be rightly attributed to the 
-framing and intertask effects.
-
-\subsection*{Measuring the extent of intertask and framing effects}
-
-\paragraph{Comparing $\theta$ and $\chi^2$.}
-The following is an illustrative example to show why it is important to 
-have a measure of effect size, like $\theta$, in addition to a test of the 
-null hypothesis like $\chi^2$.
-Suppose that we have a very slightly unfairly weighted coin, which turns
-up heads ($X=\mathbf{H}$) more often than expected by one part in one hundred:
-$\Pr\{X=\mathbf{H}\} = 0.501$. Such a coin is only mildly biased, and would 
-be fine for many purposes.  If we did not know that the coin was
-biased, we could determine whether it was biased by flipping the coin in 
-question, along with a coin we know to be fair, many times 
-(say 100 million times), and then use a $\chi^2$ test to decide whether 
-the two coins have the same probability of turning up heads.
-Simulating this with a random number generator yields the results shown
-in Table~S\ref{table:coin}.  Results from a $\chi^2$ test of the
-hypothesis that the two coins have the same probability of turning up heads 
-is shown in Table~S\ref{table:coin_stats}.
-
-\setlength{\floatsep}{30pt plus 1.0pt minus 2.0pt}
-
-\begin{table}
-\centering
-\begin{tabular}{c c c c}
-\toprule
-coin & $N_\mathbf{H}$ & $N_{\mathbf{T}}$ & total \\
-\toprule
-\textit{fair} & 50002283 & 49997717 & $10^8$\\
-\textit{biased} & 50101115 & 49898885 & $10^8$ \\
-\bottomrule
-total & 100103398 & 99896602 & $2\times 10^8$ \\
-\bottomrule
-\end{tabular}
-\caption{
-	Simulated counts of heads ($N_\mathbf{H}$) and tails ($N_\mathbf{T}$)
-	occurrences, for a fair coin, and a coin biased to have a probability
-	of turning up heads of 0.501.
-}
-\label{table:coin}
-\end{table}
-
-\begin{table}
-\centering
-	\begin{tabular}{c c c c }
-	\toprule
-	Degrees of freedom & $\chi^2$ & $p$-value \\
-	\toprule
-	1 & 195.4 & $2.2 \times 10^{-44}$ \\
-	\bottomrule
-	\end{tabular}
-\caption{
-	Statistics for a $\chi^2$ test of the hypothesis that a fair and 
-	unfair coin have the same probability of turning up heads.  
-	The result overwhelmingly favors rejection of the hypothesis, even
-	though the coins differ only slightly.
-}
-\label{table:coin_stats}
-\end{table}
-
-Even though the $\chi^2$ test shows, with tremendous statistical 
-significance, that the unfair coin is indeed unfair, we know that actual 
-extent of bias is small, 
-$\theta = \frac{1}{2}\left( |0.501 - 0.499| + |0.499 - 0.501| \right) = 0.002$.
-This demonstrates how a sufficiently large sample size will lead to the 
-detection an arbitrarily 
-small bias with arbitrarily high statistical significance. 
-This is why, to measure the practical significance of intertask effects,
-we rely on a measure of effect size, which is in this case a measure
-of statistical divergence, $\theta$.
-
-\paragraph{Statistical approaches to measuring bias.}
-Recall that Eq.~\ref{eq:theta} in the main text defined the
-extent of bias between the microtask responses from two groups
-of workers to be $\theta$ (reproduced here):
-\begin{equation}
-	\theta = \frac{1}{2}\sum_{x \in X} \left| p_0(x) - p_1(x) \right|,
-\end{equation}
-where $p_0(x)$ and $p_1(x)$ represent the probability that a worker from
-treatment 1 (respectively 2) produces response $x$, from a set of possible
-responses $X$.  As defined, $\theta$ corresponds to a measure of divergence 
-between $p_0$ and $p_1$, called the \textit{total variation distance} or the
-\textit{L1-distance}.
-
-Measuring the \textit{L1-distance} between two probability distributions,
-given only samples, is difficult.  The na\"ive approach is to take
-the maximum likelihood estimate of $p(x)$, which sets it equal to the 
-frequency with which the response $x$ has been observed, 
-$\hat{p}(x) = \frac{N_x}{N}$, and then estimate $\theta$ 
-using these frequencies\cite{batu2013testing}: 
-$\hat{\theta} = \sum_{x \in X}|\hat{p}_1(x) - \hat{p}_2(x)|$.  
-However, this method tends to drastically overestimate $\theta$
-\cite{val-thesis}.
-Recently there has been theoretical progress on this problem.
-An estimator of L1-distance, and tests of whether the L1-distance is
-greater than a specified threshold, have been proposed 
-\cite{val-thesis,batu2013testing,chan2014optimal}.  
-These methods have excellent theoretical convergence guarantees, but
-cannot easily be used to establish estimates with confidence intervals or 
-perform hypothesis tests for fixed sample size and significance level.  
-We therefore turn to an alternative approach using machine learning. 
-While this method yields an estimator that converges more slowly,
-it is straightforward to establish confidence intervals and 
-use the estimator in hypothesis tests.
-
-\paragraph{The relationship of bias and classifier accuracy.}
-We will now show that, any classifier algorithm, $\mathcal{A}$, that
-takes the response, $x$, of a worker, and guesses the population to which
-the worker belongs ($P_0$ or $P_1$), will do so with an accuracy, $\eta$,
-that is bounded according to Eq.~ from the main text 
-(reproduced here):
-%\begin{equation}
-%	\theta \geq 2\eta - 1.
-%	\label{eq:sup:l1}
-%\end{equation}
-
-To do so, we will first formalize $\eta$ by defining a 
-\textit{validation test}.  In a validation test, a uniform random bit 
-$z\in\{0,1\}$ is sampled, and then, according to the value of $z$, the
-response of a worker, $x$, is sampled uniformly randomly from $P_z$.  
-The algorithm is provided
-with $x$ and yields a \textit{guess}, $b=\mathcal{A}(x)$, as to whether the 
-worker was 
-from $P_0$ or $P_1$.  We shall denote such a validation test by 
-$V(P_0, P_1, \mathcal{A})$, and define the value of the test to be 1 if 
-$b=z$ and 0 otherwise.
-
-We then define the accuracy of classifier $\mathcal{A}$ to be $\eta$ according
-to:
-\begin{equation}
-\eta = \mathrm{E\{V(P_0, P_1, \mathcal{A})\}} 
-	= \mathrm{Pr}\{V(P_0, P_1, \mathcal{A})=1\}.
-\end{equation}
-
-To develop the relationship between $\eta$ and $\theta$, let us consider
-the accuracy $\eta^*$ of the best possible classifier $\mathcal{A}^*$.
-The best possible classifier will not in general have perfect accuracy:
-if the responses from workers in $P_0$ and $P_1$ are distributed 
-identically, then there is no hope of determining which population the worker 
-came from given only her response $x$.  But, assuming that responses are
-not distributed identically, then given some $x$, the best possible 
-classifier must always guess 1 whenever $p_1(x) > p_0(x)$ and guess 0 whenever
-$p_0(x) > p_1(x)$.
-
-Sacrificing, for a moment, some generality, let us assume that, for some give 
-$x'$, $p_1(x') > p_0(x')$.  
-When this $x'$ is encounterend in a validation test, the optimal classifier
-must guess $b = \arg\!\max_{z}(p_{z}(x'))$, which in this case is $b=1$.
-The probability that the classifier guesses correctly in this case is:
-\begin{align}
-	\begin{split}
-	\mathrm{Pr}\{V(P_0, P_1, \mathcal{A}^*) = 1 | x = x' \} 
-		&= \mathrm{Pr}\{z = \mathcal{A^*}(x) | x = x' \} \\
-		&= \mathrm{Pr}\{z = 1 | x = x' \}  \\
-		&= \frac{\mathrm{Pr}\{z = 1 , x = x'\}}
-			{ \mathrm{Pr}\{z=0 , x=x'\} + \mathrm{Pr}\{z=1 , x=x'\}} \\
-		&= \frac{p_1(x')}{p_0(x') + p_1(x')}.
-	\end{split}
-\end{align}
-And now, with full generally, for any $x'$, where $p_1(x')$ is not necessarily
-greater than $p_0(x')$:
-\begin{align}
-	\begin{split}
-		\mathrm{Pr}\{V(P_0,P_1,\mathcal{A}^*)=1 | x = x' \} 
-		&= \mathrm{Pr}\{z=\mathcal{A^*}(x)  | x' = x' \} \\
-		&= \mathrm{Pr}\{z = \arg\!\max_{z'}\big(p_{z'}(x)\big)| x = x' \}  \\
-		&= \frac{\max\big( p_0(x'),p_1(x') \big)}
-		{ p_0(x') + p_1(x') }.
-	\end{split}
-\end{align}
-Note that we can rewrite $\max\big(p_0(x'),p_1(x')\big)$:
-\begin{align}
-	\max\big(p_0(x'),p_1(x')\big) = \frac{1}{2}
-		\big(
-			p_0(x') + p_1(x') + |p_0(x') - p_1(x')|
-		\big),
-\end{align}
-so,
-\begin{align}
-	\mathrm{Pr}\{V(P_0,P_1,\mathcal{A}^*) = 1 | x = x' \} 
-	&= \frac{1}{2} + \frac{|p_0(x') - p_1(x')|}{2 \big(p_0(x') + p_1(x') \big)}.
-\end{align}
-Then, summing over all possible responses $X$, 
-the overall accuracy of the optimal classifier, $\mathcal{A^*}$, is:
-\begin{align}
-	\begin{split}
-	\eta^* &= \mathrm{Pr}\{V(P_0, P_1, \mathcal{A}^*)=1\} \\
-	&=\sum_{x'\in X} \mathrm{Pr}\{V(P_0,P_1,\mathcal{A}^*) = 1 | x = x' \} \mathrm{Pr}\{x = x'\}\\
-		&= \sum_{x'\in X} \left(
-				\frac{1}{2} + 
-				\frac{|p_0(x') - p_1(x')|}{2 \big(p_0(x') + p_1(x') \big)}
-			\right)
-			\left(
-				\frac{p_0(x') + p_1(x')}{2}
-			\right)\\
-		&= \frac{1}{2}\left(
-				\frac{1}{2}(
-					\sum_{x' \in X}p_0(x') + \sum_{x' \in X}p_1(x')
-				) + 
-				\frac{1}{2} \sum_{x' \in X} \big(|p_0(x') + p_1(x')|\big)
-			\right) \\
-		&= \frac{1}{2} \left( \frac{1}{2}(1 + 1) + \theta \right)\\
-		&= \frac{1 + \theta}{2}\\
-		\implies \theta &= 2\eta^* - 1.
-	\end{split}
-\end{align}
-By definition, no classifier can be more accurate than $\mathcal{A^*}$, so
-for every $\mathcal{A}$
-%\begin{align}
-%		\theta \geq 2\eta - 1.
-%		\label{eq:sup:l1_again}
-%\end{align}
-
-\paragraph{Using cross-validation accuracy to lower-bound bias.}
-	In order for Eq.~ to be applicable, it is necessary to 
-	obtain an unbiased estimate of a classifier's accuracy.  To do so, it is
-	essential to test the classifier on data that were not used to build 
-	the classifier.  Generally, a portion of the data is used to
-	optimize preprocessing, select features, and optimize 
-	classifier hyper-parameters, while keeping another portion of the data
-	set aside for validation.
-
-	In our case, the data are expensive, and must be divided between 18
-	experimental treatments, so we sought to keep as many worker responses
-	available 
-	for validation
-	as possible.  For this reason, we made principled decisions 
-	between alternative preprocessing options and features, 
-	rather than spending sampled responses on empirically testing these 
-	options.  Making
-	suboptimal choices can only moderate the observed values 
-	of $\theta$, making our experiments more conservative. 
-	However, conserving more responses for validation 
-	tests, by not using them for classifier optimization, 
-	enables us to estimate the resulting classifier's accuracy more precisely.
-	Using a Na\"ive Bayes classifier, which does not require hyper-parameter 
-	optimization, meant that we also did not need to spend data on 
-	optimizing hyper-parameters.
-
-	Thus, no worker responses at all were used for optimizations.  We 
-	performed 
-	leave-one-out validation, which involves training a classifier using 
-	all but one response, and then having the classifier guess the class
-	(in our case, the priming exposure) of the left-out worker.  This is 
-	repeated $n$ times, where $n$ is the pooled number of worker responses 
-	in both
-	classes (both treatments in a given experiment), 
-	each time leaving out the response of a different worker.
-
-\paragraph{Selection of the na\"ive Bayes classifier.}
-We chose to use the na\"ive Bayes classifier as our basis for measuring 
-bias for three reasons.  First, we had 119 examples (workers) per class 
-(treatment), but thousands of distinct features 
-(i.e. the number of distinct words occurring in an experiment).  
-Having many more features than examples is problematic for many classifiers
-because a large number of features leads to a high-variance, over-fit model,
-resulting in poor performance.  But one of the strengths of the na\"ive 
-Bayes classifier is that it performs well even when the number of features
-exceeds the number of examples\cite{bickel2004, hastie2009elements}
-
-Second, the standard implementation of the na\"ive Bayes classifier has no 
-hyper-parameter to optimize. This meant that we did not need to use 
-samples for hyper-parameters optimization, which would reduce the number
-of samples available for validation tests to estimate $\theta$.
-
-Third, the na\"ive Bayes algorithm is based on an assumption that the 
-observation of one feature is independent from the observation of any 
-other, once we have conditioned on the class under observation 
-%\cite{bishop2006} 
-(i.e. the priming treatment).  This
-conditional independence assumption is made for
-pragmatic rather than theoretical reasons, and is rarely satisfied.  However,
-if it \textit{is} satisfied, then the na\"ive Bayes classifier is 
-optimal \cite{Zhang2004562}.  In most text documents, 
-the existence of long-range dependencies in language 
-violates the conditional independence of words: when a rare word is mentioned,
-it is more likely to be mentioned again, and topics introduced early in a
-text are likely to be revisited.
-But in our case, there is little opportunity for such effects.  Workers 
-generally do not use the same word in multiple labels for the same image. 
-Any overarching ``topics'' within the labels that workers use will tend to 
-relate to the test images, which are held in common.
-Therefore, in our setup, conditional independence is likely to be 
-a realistic approximation, and so the na\"ive Bayes classifier is likely to
-be closer to optimal than in other text classification applications.
-
-\paragraph{Comparison to other classifiers.}
-
-\begin{figure}
-	\centering
-	\includegraphics[scale=0.75]{figs/theta_sup.pdf}
-	\caption{
-		Empirical bias, measured using classifiers, induced in image 
-		labeling tasks, by exposing workers to initial tasks or framing. 
-		The bias was determined using (A-F) a na\"ive Bayes classifier, and 
-		(G-L) an SVM classifier, according to Eq.~\ref{eq:sup:l1}.
-		In panels A through F, each plot adds an additional
-		preprocessing step to those used in the previous plot; the same is 
-		done for panels G through H: A,G) no 
-		preprocessing; B,H) spelling correction; C,I) stop word removal; 
-		D,J) lemmatization; E,K) splitting of multiple-word labels; 
-		F,L) distinguishing identical labels entered in different form inputs.
-		Standard error bars are shown.
-	}
-	\label{fig:theta_sup}
-\end{figure}
-The inequality in Eq.~
-asserts that a classifier's performance in predicting class membership
-sets a lower bound on the L1-distance between the distributions of features 
-for the classes.
-This bound is tight for the optimal classifier, and in general, the slack
-depends on how the classifier is constructed.
-
-Although we believe the na\"ive Bayes classifier is nearly optimal in this
-setting, some other classifier may exist that is significantly better than 
-the one used to generate our results.  Furthermore, various decisions about
-preprocessing and feature representation also
-impact the classifier performance.  
-For example, we chose to correct spelling, remove stop words,
-lemmatize words, and to distinguish which text-input was used to enter a 
-given label.  All of these decisions have some effect on classifier 
-performance.
-
-We chose not to optimize these decisions, since it would require the
-use of samples (worker-responses), which could then not be used in 
-cross-validation to measure $\theta$.  Nevertheless, it is
-appropriate to look at what affect these decisions had, \textit{post-hoc}.  
-We reproduce the plot from Figure~\ref{fig:theta}A in the main text, 
-this time using different combinations of preprocessing options,
-and using both the na\"ive Bayes and an SVM classifier, in 
-Figure~S\ref{fig:theta_sup}.
-
-Unlike the na\"ive Bayes classifier, when using SVM it is necessary to tune 
-the cost and gamma hyper-parameters of the SVM classifier, as well as choose 
-a kernel.  We used simulated annealing to optimize the cost and gamma settings
-data from \textit{intertask-food-culture}.  For this reason, the estimate
-of $\theta$ estimate for this experiment in 
-Figure~S\ref{fig:theta_sup} (G to J) is inflated.
-
-These plots suggest that the values of $\theta$ obtained using the 
-na\"ive Bayes classifier and our particular choice of preprocessing steps, 
-as shown in Figure~\ref{fig:theta} of the main text, are representative.
-
-\paragraph{Statistical significance and confidence intervals for $\theta$.}
-The measurements of $\theta$ were based on the number of correct 
-classifications during validation tests.  The number of correct 
-classifications, $X$, has a binomial distribution.  
-We take the null hypothesis that the classifier performs
-no better than chance, $X \sim \mathrm{Bin}(N,0.5)$, where $N$ is the number 
-of workers in both treatments of an experiment, and consider an alternative
-hypothesis, that the classifier does perform better than chance.  Then, the 
-critical number 
-of correct classifications, $x^*$, for a one-tailed hypothesis test with
-significance $\alpha$ is:
-\begin{align}
-	&x^* = \sup \left\{
-			x: \mathrm{Pr}\{ \mathrm{Bin}(N;0.5) \geq x \} < \alpha
-		\right\} \label{eq:sup:crit}\\
-	\text{where}\quad &\mathrm{Pr}\{ \mathrm{Bin}(N,\eta) \geq x \} = 
-		\sum_{x'=x}^{N} \binom{N}{x'}\eta^{x'}(1-\eta)^{(N-x')}
-\end{align}
-For the treatments in \textit{intertask-food-objects}, five different 
-permutations of each treatment were tested, and a different classifier was 
-built for each permutation.  For the sake of estimating accuracy, we assume
-that the classifiers under different permutations have the same accuracy,
-and so we pool their results.  This means that 
-\textit{intertask-food-objects} has five times as many validation tests
-(larger $N$) compared to the other experiments.  This larger $N$ makes 
-evaluation of \ref{eq:sup:crit} difficult, but also makes the normal 
-distribution a very good approximation.  We therefore assume 
-that $X$ has a normal distribution for the classification of workers from
-\textit{intertask-food-objects}, with $\mu=N/2$ and 
-$\sigma = \frac{1}{2}\sqrt{N}$.  The statistics for these hypothesis tests
-are tabulated in Tables~S\ref{table:theta} and S\ref{table:theta_pos}.
-
-To determine the confidence intervals for measured $\theta$ values we 
-use the exact Clopper-Pearson method. % \cite{clopper1934use}.  
-Based on the observed number of successes, $X$, we calculate 
-$\eta^*_\mathrm{low}$ and $\eta^*_\mathrm{high}$ from:
-\begin{align}
-	\eta^*_\mathrm{high} &= \sup
-		\left\{
-			\eta : \mathrm{Pr}\{\mathrm{Bin}(N; \eta) \leq X \} > 
-				\frac{\alpha}{2}
-		\right\} \\
-	\eta^*_\mathrm{low} &= \inf
-		\left\{
-			\eta : \mathrm{Pr}\{\mathrm{Bin}(N; \eta) \geq X \} > 
-				\frac{\alpha}{2}
-		\right\}
-\end{align}
-Again, for the experiment \textit{intertask-food-objects}, which had 
-more validation tests than the others, we derive the confidence intervals
-assuming $X$ is normally distributed.
-Since the confidence intervals are to be shown on a plot of $\theta$, we 
-transform them into equivalent values of 
-$\theta$: $\theta^*_\mathrm{high} = 2\eta^*_\mathrm{high} - 1$ and 
-$\theta^*_\mathrm{low} = 2\eta^*_\mathrm{low} - 1$.
-The statistics collected for the measurement of $\theta$, corresponding to
-Figs.~\ref{fig:theta}A and B are tabulated in Tables~S\ref{table:theta} and
-S\ref{table:theta_pos} respectively.
-
-To determine whether intertask effects were stronger than framing, we 
-perform a two-proportion $z$-test, approximating the binomial distributions
-as normal distributions, where the test statistic is given by:
-\begin{align}
-	z = \frac{\hat{\eta}_1 - \hat{\eta}_2}
-		{\sqrt{
-			\hat{\eta} (1 - \hat{\eta}) 
-			\left( \frac{1}{N_1} + \frac{1}{N_2}\right)
-		}},
-\end{align}
-where
-\begin{align}
-	\hat{\eta} = \frac{X_1 + X_2}{N_1 + N_2}
-\end{align}
-
-Since, \textit{a priori}, we do not know which effects
-should be stronger (if any), we perform a two-tailed test.  The results for 
-these hypothesis tests are tabulated in Table~S\ref{table:intertask_framing}.
-The results show that intertask effects are stronger than framing, but are
-on-par with echoed framing.
-
-\begin{table}
-\begin{center}
-\begin{tabular}{c c c c c c c c }
-	\toprule
-	\multirow{2}{*}{Experiment} & \multirow{2}{*}{$N$} & 
-	\multirow{2}{*}{$X$} & \multirow{2}{*}{$x^*$} & \multicolumn{3}{c}{(\%)}
-		& \multirow{2}{*}{$p$}\\ \cline{5-7} \noalign{\smallskip}
-	& & & & $\hat{\theta}$ & $\theta^*_\mathrm{low}$ 
-		& $\theta^*_\mathrm{high}$  \\
-	\midrule
-	\textit{intertask-food-objects} & 1190 & 777 & 624 & \textbf{30.6} 
-		& 25.2 & 36.0 & $2.5 \times 10^{-26}$ \\
-	\textit{frame-food-objects} & 238 & 122 & 133 & 2.5 & -10.6 & 14.7
-		& 0.37 \\
-	\textit{echo-food-objects} & 238 & 162 &  133 & \textbf{36.1} & 23.4 
-		& 47.1 & $1.3 \times 10^{-8}$ \\
-	\textit{intertask-food-culture} & 238 & 180 & 133 & \textbf{51.3} & 39.3 
-		& 61.1 & $5.0 \times 10^{-16}$ \\
-	\textit{frame-food-culture} & 238 & 130 & 133 & 9.2 & -3.9 & 21.3 
-		& 0.087\\
-	\bottomrule
-
-\end{tabular}
-
-\caption{Statistics for the measurement of the extent of bias, $\theta$,
-	induced by intertask and framing effects in various experiments.
-	Number of validation tests, $N$; number of successful classifications, 
-	$X$; critical number of successful classifications to reject the null 
-	hypotheses that the classifier does no better than chance 
-	(one-tailed test), $x^*$; 
-	estimate of bias based on observed number of successful
-	classifications, $\hat{\theta}$; lower confidence interval limit 
-	for the estimate of bias, $\theta^*_\mathrm{low}$; upper confidence 
-	interval limit for same, $\theta^*_\mathrm{high}$.  Hypothesis test and 
-	confidence intervals are based on a significance of $\alpha=0.05$.
-	Values for $\hat{\theta}$ in boldface are significantly greater than zero.
-}
-\label{table:theta}
-\end{center}
-\end{table}
-
-\begin{table}
-\begin{center}
-\begin{tabular}{c c c c c c c c }
-	\toprule
-	\multirow{2}{*}{Task position} & \multirow{2}{*}{$N$} & 
-	\multirow{2}{*}{$X$} & \multirow{2}{*}{$x^*$} & \multicolumn{3}{c}{(\%)}
-		& \multirow{2}{*}{$p$}\\ \cline{5-7}\noalign{\smallskip}
-	& & & & $\hat{\theta}$ & $\theta^*_\mathrm{low}$ 
-		& $\theta^*_\mathrm{high}$  \\
-	\midrule
-	1 & 238 & 152 & 133 & \textbf{28.1} & 14.8 & 39.1 
-		& $1.12 \times 10^{-5}$\\
-	2 & 238 & 138 & 133 & \textbf{15.6} & 2.9 & 27.8  
-		& $8.14 \times 10^{-3}$\\
-	3 & 238 & 140 & 133 & \textbf{17.8} & 4.6 & 29.5  
-		& $3.87 \times 10^{-3}$\\
-	4 & 238 & 135 & 133 & \textbf{13.6} & 0.3 & 25.4  
-		& $0.0221$ \\
-	5 & 238 & 134 & 133 & \textbf{12.4} & 0.5 & 24.6 & $0.0300$ \\
-	\bottomrule
-\end{tabular}
-\caption{Statistics for the measurement of the extent of bias, $\theta$,
-	induced by intertask for \textit{intertask-food-objects}, measured 
-	for test images at specific positions in the sequence of five test images.
-	These values are averaged over five different permutations.
-	Number of validation tests, $N$; number of successful classifications, 
-	$X$; critical number of successful classifications to reject the null 
-	hypotheses that the classifier does no better than chance 
-	(one-tailed test), $x^*$; 
-	estimate of bias based on observed number of successful
-	classifications, $\hat{\theta}$; lower confidence interval limit
-	for the estimate of bias, $\theta^*_\mathrm{low}$; upper confidence 
-	interval for same, $\theta^*_\mathrm{high}$.  Hypothesis test and 
-	confidence intervals are based on a significance of $\alpha=0.05$.
-	Values for $\hat{\theta}$ in boldface are significantly greater than zero.
-}
-\label{table:theta_pos}
-\end{center}
-\end{table}
-
-\begin{table}
-\begin{center}
-\begin{tabular}{c c c c c c c c c c c }
-	\toprule
-	Comparison & $N_1$ & $N_2$ & $X_1$ & $X_2$ & $\hat{\eta}_1$ 
-		& $\hat{\eta}_2$ & $z$ & $p$-value \\ 
-	\midrule
-	\parbox[c]{4cm}{\textit{intertask-food-objects} 
-	\textit{vs} \textit{frame-food-objects}} & 1190 & 238 & 777 & 122 &
-	0.653 & 0.513 & \textbf{4.1} & $2.1 \times 10^{-5}$ \\
-
-\noalign{\smallskip}
-\hdashline
-\noalign{\smallskip}
-
-	\parbox[c]{4cm}{\textit{intertask-food-objects} 
-	\textit{vs} \textit{echo-food-objects}} & 1190 & 238 & 777 & 162 
-		& 0.653 & 0.681 & -0.82 & 0.79 \\
-
-\noalign{\smallskip}
-\hdashline
-\noalign{\smallskip}
-
-	\parbox[c]{4cm}{\textit{intertask-food-culture} 
-	\textit{vs} \textit{frame-food-culture}} & 238 & 238 & 180 & 130 
-	& 0.756 & 0.546 & \textbf{4.8} & $7.6 \times 10^{-7}$ \\
-	\bottomrule
-
-\end{tabular}
-
-\caption{
-	Results for two-proportion z-tests, testing the null hypothesis that 
-	intertask and framing effects are equally strong.
-	In the cases of comparing intertask effects to passive framing, the
-	null hypothesis should be rejected ($\alpha=0.05$), but 
-	echoed framing effects are on par with intertask effects (second row). 
-	$z$-statistics in boldface are significantly different from zero.
-}
-\label{table:intertask_framing}
-\end{center}
-\end{table}
-
-\subsection*{Data preprocessing}
-	\paragraph{Splitting, lemmatization, removal of stop words, and 
-		addition of position tags.}
-
-	Before performing any analysis on the labels that workers provided, we
-	performed a series of preprocessing steps.  
-	Labels that contained
-	multiple words (separated by spaces or punctuation) were split, with
-	punctuation removed, and the separated words were treated as distinct 
-	features in subsequent analysis.
-	Misspelled words were automatically corrected using a spelling 
-	correction algorithm described below.  
-	Next, words were lemmatized using the
-	wordnet lemmatizer \cite{felbaum1998wordnet}.  %miller1995wordnet,
-	Common words such as ``the'', ``to'', or ``with'', were found using
-	the natural language toolkit (NLTK) English stop word list 
-	\cite{loper2002nltk} and removed.
-
-	For the purpose of training and testing a na\"ive Bayes classifier, we 
-	performed an additional preprocessing step.  We tagged words with the
-	position in which they had been entered (i.e. which of the five text 
-	inputs in the task interface, Figure~S\ref{fig:hit_preamble}) 
-	as well as the test tasks in which the word had been provided.
-	So, if the word ``wine'' was entered into the second text-input for 
-	the third test-task, after preprocessing, the feature ``3\_2\_wine'' would
-	appear.  Prepending the task number onto words was simply a means to 
-	retain correct attribution of words to images, since providing a word 
-	during one task 
-	is not equivalent to providing the same word during another task.
-
-	\paragraph{Spelling correction.}  
-	Spelling correction was performed using an algorithm that first detected
-	if a word was likely to be misspelled, then generated a set of candidate 
-	corrections, and chose the best candidate based on a scoring mechanism.
-
-	A word was considered misspelled if it was not contained in the 
-	\textit{legal set}, which was formed by the union of
-	the wordnet knowledge base, the stop word list, and a set of words 
-	seen while 
-	crawling the world food section of the allrecipes.com website.  We
-	describe the crawling of the allrecipes.com website in a section below.
-
-	To correct misspellings, we first produced all possible modified forms 
-	that could be obtained applying one or two edits.  An edit consisted of 
-	adding or removing a letter, changing one letter into another, or 
-	swapping the positions of two adjacent letters.  For the purpose of these 
-	edits, spaces were treated as any other letter.
-
-	The candidates produced by these edits which were in the legal set were
-	then ranked based on a scoring mechanism, and the highest scoring word
-	was chosen as the correction.  A candidate $w$'s score, $s_w$, was 
-	calculated according to the following formula:
-	\begin{equation}
-		s_w = (f_w + 1) \times p_1 \times p_2,
-	\end{equation}
-	where $f_w$ is the frequency with which the word occurred (correctly 
-	spelled)
-	within the given task, $p_1$ was a penalty for the first edit, and
-	$p_2$ was a penalty for the second edit.  If the word was made using only
-	one edit, then $p_2 = 1$.  Any edit that did not involve adding a space
-	(i.e. separating a word) incurred a penalty of 0.5, while the addition of
-	a space incurred a penalty of 0.1.  Word-separation edits were more 
-	strongly penalized because it is often possible to split a series of 
-	letters into short two- or three-letter words, which leads 
-	to many erroneous corrections.  We found these penalties worked well when
-	testing on words taken from initial tasks.
-
-	After all of our analyses had been performed, we checked the accuracy of 
-	the spelling correction algorithm using three human coders.  The coders
-	were shown a set of 
-	500 words that were randomly sampled from the labels attributed during 
-	test tasks (50 for each test task).  Before sampling, the labels from all
-	experimental treatments, for the given test task, were pooled together.
-	The coders did not know which treatment any given word came from.  
-	In addition to the words, coders were shown the spelling correction 
-	produced by the algorithm, as well as the image from the test task.
-	The coders were asked to identify any misspelled words which had not 
-	been corrected, as well as any corrections that appeared to be erroneous,
-	by indicating their own correction.
-
-	According to the human coders, before spelling correction, 17\% of words 
-	were misspelled, but only 3.2\% were misspelled after correction.
-
-	\paragraph{Crawling the world food section of allrecipes.com.}
-	The website allrecipes.com was accessed on 3-4 November 2014 using 
-	automated scripts.  A total of 2642 recipe listings and 15621 recipe
-	instruction pages were retrieved.  Recipe listings were pages that 
-	provided lists of recipes, and contained a title and short description 
-	for each.  
-	The recipe instruction pages had lists of ingredients and preparation 
-	instructions.  All of the words found in recipe titles, short
-	descriptions, ingredients lists, and preparation instructions were
-	collected, and saved as an auxiliary set to augment the \textit{legal set}
-	used in spelling correction.
-
-\subsection*{Analysis of worker vocabulary}
-\paragraph{Most suppressed and activated terms.}
-The words whose frequencies differed most between the treatments of given 
-experiments are shown in Table~S\ref{table:top-words}.  Note that 
-the word that was most suppressed in food-exposed treatments was always 
-``food''.
-
-\paragraph{Identification of food-related terms.}
-The wordnet knowledge base is composed of synsets, 
-which are particular senses 
-(meanings) and a set of word forms bearing that meaning. A given word form, 
-such as ``ring'' has multiple senses (``to ring a bell'', ``a wedding ring''),
-and so can be part of many synsets.  Since the wordnet 
-knowledge base was designed
-to carry semantic information, the synset is the basic organizing element
-of wordnet.
-
-We chose the synsets \texttt{food.n.01} and \texttt{food.n.02} to act as roots
-in defining which words should be considered food-related.  Any word form
-belonging to a synset which was a hyponym of one of the two root synsets
-identified above was considered to be a reference to food.  Here, as in the
-main text, when we say hyponym, we mean either a direct hyponym, or a hyponym
-of a hyponym, and so on.
-
-This is a stringent notion of a word being a food reference.  It roughly
-corresponds to whether or not a given thing is reasonably considered 
-consumable.  So, ``orange'' is food, but ``salty'' is not.  Although ``salty''
-would usually qualify something edible, it is not itself an edible thing.
-On the other hand, ``salt'' would be considered a reference to food under 
-this operationalization.
-
-The subset of the wordnet knowledge base induced by the hyponyms of \textit{food.n.01}
-and \textit{food.n.02} consists of 3590 word-forms.  Manual
-testing showed good coverage, except for references to ethnic foods.  
-Since, especially in \textit{intertask-food-culture} and 
-\textit{frame-food-culture}, we had images containing many ethnic 
-foods, we decided to augment the wordnet knowledge base with words learned by 
-crawling the world food section of the allrecipes.com website.
-
-After collecting a set of words using an automated script 
-(described above), we filtered down to the set of words that had been used by
-workers and which had been seen during crawling of the allrecipes.com website,
-but which were not included in wordnet.  We grafted these extra words into
-the wordnet hyponym-hypernym graph manually, looking at the image to which 
-they had been attributed (to help disambiguate the intended meaning), but 
-without revealing the treatment(s) in which
-the word was used.  Many (but not all) of the words added this way did refer 
-to ethnic foods, and so this helped increase the coverage of wordnet in that 
-respect.
-
-\paragraph{Validation of the detection of food references.}
-To determine whether our extended version of wordnet provided a good approach
-to detecting food-related words, we sampled 500 words 
-(50 from each test task)  from the set of labels produced by workers and had 
-three human coders manually decide if they were 
-food-related or not.
-
-The coders were instructed to consider whether a word was a noun signifying
-an edible item.  The guiding principle was, for the coder to ask herself,
-``can I eat X'', where X is the word she is coding.  The coders were
-shown the image used in the task from which the word came, to help resolve ambiguity
-in the sense of the word that had been given.  Coders were also shown the 
-spelling correction (if any) that the spell-correction algorithm had made,
-to help interpret misspelled words.
-
-We evaluated the food detection algorithm in two ways.  First, we measured
-the inter-rater reliability between the three human coders and the algorithm
-(treating the algorithm just like any other coder).  Second, adopting the 
-majority code given by the human coders as ground-truth, we determined the 
-accuracy of the food-detection algorithm.  
-Data summarizing this validation process are given
-in Table~S\ref{table:inter-rater}.
-
-\begin{table}
-\centering
-\setlength{\tabcolsep}{12pt}
-\begin{tabular}{ r | c }
-\toprule    
-\# terms coded & 500 \\
-\# food references & 130 \\
-\# correct machine codes & 440 \\
-inter-rater reliability & 82.4\% \\
-human-machine code agreement & 88\% \\
-%machine recall & 80 \% \\
-%machine precision & 75.4 \% \\
-%machine code F1 & 0.78 \\
-\bottomrule
-\end{tabular}
-\caption{
-	Results for the validation 
-	of the automatic detection of food references, by comparison to
-	human-generated coding on randomly sampled words.  In calculating the 
-	human-machine code agreement, the majority human code was used.
-	Inter-rater reliability was calculated as Krippendorff's alpha, treating
-	the machine as any other coder.
-}
-\label{table:inter-rater}
-\end{table}
-
-The results show that good inter-rater reliability was achieved during the
-validation (82.4\%).  Looking at the agreement between the 
-machine codes and the majority human-generated codes, we find they agree
-88\% of the time.  This means that the concept used to instruct human coders
-provides a good approximation to what the wordnet-based machine codes actually
-represent. In other words, the machine codes correspond closely to indicating
-which words correspond to nouns that refer to edible things, and which ones
-do not, which provides a clear and simple interpretation for the machine
-coding of food and non-food words.
-
-\paragraph{Testing differences in proportions of food-related labels.}
-We calculate the proportion of food-related labels in a treatment by first
-calculating the proportion of food-related labels per worker, and then
-taking the average of this value for all workers.  We calculate the
-sample standard deviation for workers' proportions of food-related terms,
-$s_w$ and then estimate the standard deviation of the average proportion
-to be $s = s_w / \sqrt{N}$, where $N$ is the number of workers in the 
-treatment.  The proportions of food-related words for all treatments,
-and the statistics for the hypothesis test that the proportions between
-treatments within given experiments differ, are shown in 
-Table~S\ref{table:proportion-food}.
-
-\begin{table}
-\centering{
-\setlength{\tabcolsep}{4pt}
-\setlength{\tabcolsep}{3pt}
-\begin{tabular}{c c c c c c c c c c c}
-	\toprule
-	\multirow{2}{*}{Experiment} 
-		& \multicolumn{2}{c}{food treatment}
-		& \ 
-		& \multicolumn{2}{c}{other treatment} 
-		& \
-		& \multicolumn{2}{c}{(other - food)} 
-	& \multirow{2}{*}{$z$-score}
-	& \multirow{2}{*}{$p$-value} \\ \cline{2-3} \cline{5-6} \cline{8-9}
-	& \% refs. 
-	& $s$ 					
-	& \
-	& \% refs. 
-	& $s$ 					
-	& \
-	& $\Delta$\% refs. 
-	& $s$ 					 \\ 
-	\midrule
-	\textit{intertask-food-objects} & 54.5 & 0.6 & \ & 57.4 & 0.8 & \ 
-		& \textbf{2.9} & 1.0 & 3.0 & $1.3 \times 10^{-3}$\\
-	\textit{frame-food-objects} & 56.2 & 1.4 & \ & 60.1 & 1.4 & \ 
-		& \textbf{3.9} & 1.9 & 2.0 & $2.2 \times 10^{-2}$\\
-	\textit{echo-food-objects} & 54.0 & 1.4 & \ & 62.8 & 1.7 & \ 
-		& \textbf{8.8} & 2.2 & 4.0 & $3.5 \times 10^{-5}$\\
-	\textit{intertask-food-culture} & 48.8 & 1.6 & \ & 40.8 & 2.0 & \ 
-		& \textbf{-8.0} & 2.6 & -3.1 & $9.2 \times 10^{-4}$\\
-	\textit{frame-food-culture} & 45.8 & 2.0 & \ & 45.2 & 1.8 & \ 
-		& -0.6 & 2.6 & -0.2 & $0.41$\\
-	\bottomrule
-\end{tabular}
-}
-\caption{Statistics for the comparison of the proportions of food-references
-	among words used in labels, between treatments of all experiments.  
-	$s$: sample standard deviation.
-}
-\label{table:proportion-food}
-\end{table}
-
-\paragraph{Variance in food vocabulary size (lexical richness).}
-The number of unique words in a text is strongly dependent on the size
-of the text: as more text is sampled, previously unseen words continue
-to be found, though at a decreasing rate.  
-This means that the vocabulary size of a population of documents is 
-not well-approximated by a sample.  Nevertheless the vocabulary sizes
-obtained by taking equally-sized samples of two different populations
-provides a means to compare the populations on an equal footing.
-
-Taking the difference between one sample's vocabulary and the 
-other gives us a measure of their difference in vocabulary size, but 
-the variance of this measure needs to be characterized to know whether
-there is a significant difference.
-
-To test whether one sample has a (statistically) significantly larger
-vocabulary size, in reference to food-related words, than another, we adopt 
-the null hypothesis that they
-have the same vocabulary, and pool the documents sampled from both 
-populations together.  We then randomly partition the pooled sample
-back into two balanced sets and take the difference in the sets' 
-vocabulary sizes.  This models the difference that would be observed
-under the null hypothesis that the documents are drawn from the same
-population.  We repeat the pooling and partitioning of the samples
-1000 times to generate a bootstrap sample of the difference in 
-vocabulary sizes under the null hypothesis.  The 
-2.5th and 97.5th percentiles of the bootstrap sample then serve as the
-critical values of vocabulary size-difference beyond which the null hypothesis
-should be rejected (at $\alpha=0.05$).
-Statistics for these hypothesis tests are shown in 
-Table~S\ref{table:vocab}.
-
-\begin{table}
-\centering{
-\begin{tabular}{c c c c c c c }
-	\toprule
-	\multirow{2}{*}{Experiment} & \multicolumn{2}{c}{$|V|$} 
-		 & \ & \multicolumn{3}{c}{$(\%)$} \\ \cline{2-3} \cline{5-7}
-	& Food trtmt. & Other trtmt. & \ & $\Delta|V|$ & $\Delta|V|^*_{low}$
-		& $\Delta|V|^*_{high}$  \\
-	\midrule
-	\textit{intertask-food-objects} & 297 & 247 & \ 
-		& \textbf{20.2} & -10.7 & 11.5 \\
-	\textit{frame-food-objects} & 296 & 261 & \ 
-		& \textbf{13.4} & -9.7 & 10.1 \\
-	\textit{echo-food-objects} & 316 & 280 & \ & 
-		\textbf{12.9} & -11.8 & 11.1 \\
-	\textit{intertask-food-culture} & 289 & 244 & \ 
-		& \textbf{18.4} & -11.4 & 11.6 \\
-	\textit{frame-food-culture} & 318 & 332 & \ & -4.2 & -11.9 & 11.2 \\
-	\bottomrule
-\end{tabular}
-}
-\caption{
-	Statistics for the measurement of vocabulary size difference, for each
-	experiment, between the food and non-food treatments. Vocabulary
-	size, $|V|$; vocabulary size of non-food less food treatments, 
-	$\Delta|V|$; lower and upper critical values, $\Delta|V|^*_{low}$ and 
-	$\Delta|V|^*_{high}$, for statistically significant 
-	$\Delta|V|$, at $\alpha=0.05$, based on bootstrapping.  
-	Boldfaced values for $\Delta|V|$ are statistically significant.
-}
-\label{table:vocab}
-\end{table}
-
-\paragraph{Calculation of relative specificity}
-In the main text we present results for the relative specificity of labels
-produced by two experimental treatments.  In performing this calculation,
-we used the wordnet knowledge base, which has a set of hypernym-hyponym relationships.
-The first step in performing this calculation was to map the words occurring 
-in (the labels of) a given experimental treatment onto the wordnet synsets.  
-In general, a given word
-form can have multiple meanings, and therefore maps onto multiple wordnet 
-synsets.
-
-Mapping the words from two treatments onto the wordnet 
-hypernym-hyponym graph yields two sets of counts, one set per treatment, 
-indicating the number of times a word from a given synset occurred among the
-labels of the treatment.  For every synset in one treatment, we looked
-at the number of synsets in the other treatment that were more generic
-(reachable by following hypernym relations) less the number of words that
-were more specific (reachable by following hyponym relations).  This quantity,
-tallied over all words in the original synset, gives a (non-normalized) 
-measure of the overall degree to which words from the first treatment are more
-specific than words from the second treatment.  We then normalized this 
-quantity by the total number of possible comparisons between the words of
-one treatment to those of the other, where two words are considered comparable
-only if one word is the hypernym or hyponym of the other.  Hence, ``statue'' 
-and ``bread'' are not comparable, but ``pumpernickel'' and ``bread'' are.
-
-This calculation can be summarized by the following equation:
-\begin{equation}
-	S(P,Q) = \frac{
-		\sum_{w\in P}\sum_{v\in Q} \left(
-			\mathbf{1}_{[w>v]} - \mathbf{1}_{[v>w]} \right)
-	}{
-		\sum_{w\in P}\sum_{v\in Q} \left(
-			\mathbf{1}_{[w>v]} + \mathbf{1}_{[v>w]} \right)
-	},
-\end{equation}
-where $P$ and $Q$ are sets of synsets associated to different experimental 
-treatments, and $\mathbf{1}_{[w>v]}$ evaluates
-to 1 if synset $w$ is more specific than (i.e. is a hyponym of) synset $v$.
-This measure counts the excess number of cases where synsets from $P$ are more
-specific then synsets from $Q$, as a fraction of all comparable synset pairs. 
-The relative specificity lies within $[-1,1]$; we report it as a percentage 
-in Table~S\ref{table:proportion-food} and in the main text.
-
-In computing this quantity between two treatments, we first computed the 
-relative specificity for the treatments separately for each test task, and 
-averaged the results obtained accross the five test tasks.
-
-To assess statistical significance, we used the bootstrap method.
-For two given treatments $A$ and $B$, 
-119 workers were sampled from each with replacement, giving the bootstrap
-samples $A'$ and $B'$, and the relative specificity between these 
-was measured as described above.
-This was repeated 1000 times.  The 2.5 and 97.5 percentiles from the 
-bootstrap sample were used to estimate 95\% confidence intervals.  
-A confidence interval not containing zero indicates a statistically 
-significant difference in specificity.  
-The statistics for relative specificity 
-calculations are shown in Table~S\ref{table:specificity}.
-
-\begin{table}
-\centering{
-	\setlength{\tabcolsep}{4pt}
-\begin{tabular}{c c c c c c c c c c c}
-	\toprule
-	Experiment & $S$ & $S^*_\mathrm{lowCI}$ & $S^*_\mathrm{highCI}$ \\ 
-	\midrule
-	\textit{intertask-food-objects} & \textbf{13.6} & 9.1 & 17.8 \\
-	\textit{frame-food-objects} & \textbf{12.4}     & 7.6 & 17.0 \\
-	\textit{echo-food-objects} & \textbf{17.1}      & 12.1 & 21.9 \\
-	\textit{intertask-food-culture} & \textbf{19.6} & 13.7 & 25.4 \\
-	\textit{frame-food-culture} & \textbf{7.0}      & 2.1 & 15.3 \\
-	\bottomrule
-\end{tabular}
-}
-\caption{Relative specificity ($S$) of food-related words between the food- 
-	and non-food-exposed treatments of all experiments. 
-	Positive values indicates the food-exposed treatment was relatively more
-	specific (which was always the case); 
-	boldfaced values indicate a disparity in specificity that 
-	is statistically significant.  
-	$S^*_\mathrm{lowCI}, S^*_\mathrm{highCI}$: lower and upper
-	confidence intervals for $S$ based on the bootstrapping approach.  
-	Specificites are expressed as percentages.}
-\label{table:specificity}
-\end{table}
-
 \end{document}

### 2015-09-22 docs/publications/2015.08_CHI/man.tex
add all figs for new manuscript

@@
 \author{%
-  \alignauthor{Edward Newell\textsuperscript{*}, Derek Ruths\\
-	School of Computer Science\\ McGill University}\\
-    \affaddr{Montreal, Qu\'ebec}\\
-	\textsuperscript{*}\email{edward.newell@mail.mcgill.ca} }\\
-
-  \alignauthor{2nd Author Name\\
-    \affaddr{Affiliation}\\
-    \affaddr{City, Country}\\
-    \email{e-mail address}}\\
-  \alignauthor{3rd Author Name\\
-    \affaddr{Affiliation}\\
-    \affaddr{City, Country}\\
-    \email{e-mail address}}\\
+  \alignauthor{
+	Edward Newell \\
+    \affaddr{School of Computer Science, McGill University}\\
+    \affaddr{3480 University Street, Room 318, Montreal, Qu\'ebec,
+	  Canada, H3A 2A7
+	}\\
+	\email{edward.newell@mail.mcgill.ca}}\\
+  \alignauthor{
+	Derek Ruths \\
+    \affaddr{School of Computer Science, McGill University}\\
+    \affaddr{3480 University Street, Room 318, Montreal, Qu\'ebec,
+	  Canada, H3A 2A7
+	}\\
+	\email{derek.ruths@mcgill.ca}
+  }\\
 }
@@
 There are many tasks that are trivial for people, but difficult to solve
-programatically.  
+programmatically.  
 Typical tasks include tagging and categorizing images,
@@
 and performing surveys for 
-academic or market reserach purposes (see Table~\ref{table:task_composition} for a listing of task types seen on the Amazon's Mechanical Turk 
+academic or market research purposes (see Table~\ref{table:task_composition} for a listing of task types seen on the Amazon's Mechanical Turk 
 microtask platform).
@@
 
-The flexibility and cost-effectiveness of microtask labour
+The flexibility and cost-effectiveness of microtask labor
 has led to a surge in demand from industry and 
@@
 cognitive load arising from task-switching \cite{Adamczyk2004271}.
-Morever, as workers complete task assignments, they must continually 
+Moreover, as workers complete task assignments, they must continually 
 switch between working on an assignment and choosing their next 
@@
 working on assignments and choosing them.
-This may explain why the pre-defined assignment templates available on 
+This may explain why the predefined assignment templates available on 
 microtask platforms generally bundle many tasks together by 
@@
 i.e. the extent of bias, is substantially harder than
-simply determining \textit{whether} a biasing effect has occured.  
+simply determining \textit{whether} a biasing effect has occurred.  
 Our first contribution is a statistically grounded method for doing so.
@@
 adopted
-image-labeling as a canonical micratask, in which workers provide 
+image-labeling as a canonical microtask, in which workers provide 
 descriptive labels to images using free-text inputs.  Image labeling is
@@
 see Figure~\ref{fig:l1_example} for illustrative definition).  
-Using the wordnet 
-knowledge base, we analyze worker's word choices to characterize the 
+Using the WordNet 
+knowledge base, we analyze worker's word choices to characterize 
 the nature of these effects in detail.  We find that, when workers 
@@
 depend on the \textit{history} of their inputs.
-We propose a dual priming mechanism which can exaplain our
+We propose a dual priming mechanism which can explain our
 observations.  Irrespective of the underlying mechanism, this 
@@
   }
-  \item{provide design considerations in light of our observations.}
 \end{itemize}
@@
 Next we present our experimental results, followed by a discussion 
-of interpretations and ramefications for microtask-based and crowdsourced 
+of interpretations and ramifications for microtask-based and crowdsourced 
 work.  We conclude with suggestions for task design and future work.
@@
 	Frequency of various broad task types seen among the 200 most 
-	recently posted tasks on MTurk, accessed on 12 February, 2015.
+	recently posted tasks on Amazon's Mechanical Turk, 
+	accessed on 12 February, 2015.
 }
@@
 Accuracy and replicability are central to any crowdsourcing study.
-There is ongoing research investigating how the desing of microtasks,
+There is ongoing research investigating how the design of microtasks,
 and their context, affect the quality of responses.  
@@
 Another study \cite{kazai2013analysis} showed that increasing
-wages does increse quality, but that this effect saturates, and 
-eventually increases in wage attract a larger porportion of workers who 
+wages does increase quality, but that this effect saturates, and 
+eventually increases in wage attract a larger proportion of workers who 
 disregard the task instructions.
@@
 % Task framing
-Workers have other motivations for completeing tasks aside from 
+Workers have other motivations for completing tasks aside from 
 remuneration \cite{kazai2013analysis}.  
@@
 when they were not provided any context \cite{chandler2013breaking}.
-Providing a meaninful context did not, however, increase the 
+Providing a meaningful context did not, however, increase the 
 \textit{quality} of work.
@@
 activity.  For example, exposing participants to an image helps them 
-subsequently recognize that image when shown very breifly in a 
+subsequently recognize that image when shown very briefly in a 
 tachistoscope; however, being presented with a related \textit{word}, 
@@
 most notably the $\chi^2$ test.  
-This will suffice to determine whether there are any grounds for conern 
+This will suffice to determine whether there are any grounds for concern 
 about priming effects in the first place.  However, such tests
@@
 \textit{total variational distance}\footnote{
-  Other formulation such as the Kulback-Leibler and 
-  Jenson-Shannon divergence can be calculated from the total variational
+  Other formulation such as the Kullback-Leibler and 
+  Jensen-Shannon divergence can be calculated from the total variational
   distance
@@
 		\textit{frame-food-culture}.
-		The full set of experimental materials is shown in the 
-		supplementary text.
 	}
@@
 significantly during test tasks (by $\chi^2$ test, $p = 6.0 \times 10^{-14}$),
-even though the test tasks were identical in both treatments\footnote{
-	see supplementary text for tabulated statistics.
-}.  Thus earlier tasks do significantly affect later ones, which 
+even though the test tasks were identical in both treatments.  
+Thus earlier tasks do significantly affect later ones, which 
 validates our concerns about the typical microtask methodology.
@@
 We chose the na\"ive Bayes
-classifier for three reasons\footnote{In the supplementary material we 
-  compare alternate classifier configurations, and show that they produce
-similar results.}.  First, it performs well even when the 
+classifier for three reasons.  First, it performs well even when the 
 number of features is large compared to the number of training examples.  
@@
 dev and test sets.
-Third, the conditional independance assumption, normally 
+Third, the conditional independence assumption, normally 
 undertaken for pragmatic reasons, is probably a relatively mild in 
 relation to image labels, since they are likely to be less dependent
-on one another than in a coherent passage of text.
+on one another than in a coherent passage of text.  We also used a 
+support vector machine and found very similar results.
 
@@
 on edit-distance to a dictionary of words, followed by stop-word removal
-and lemmatization\footnote{A detailed description of preprocessing steps 
-is available in the supplementary material.}.  The spelling correction
+and lemmatization.  The spelling correction
 dictionary was compiled from a combination of WordNet 
@@
 workers began the tasks, we indicated
-that the purpose of the task was either the the recognition of food or 
+that the purpose of the task was either the recognition of food or 
 culture, depending on the treatment to which the worker was assigned.  
@@
 		on that concept, and the richness and specialization of their 
-		vocaubulary in reference to it.
+		vocabulary in reference to it.
 		In all three plots, positive values indicate a larger quantity for 
@@
 		(\textbf{C}) Food-exposed
-		workers used more specialized words to refer to food (see 
-		supplementary text for calculation of relative specialization).
+		workers used more specialized words to refer to food.
 		Standard error bars are shown in (\textbf{A} and \textbf{C}).
@@
 		experiments, within labels attributed to the first test task.
-		Values indicate the absolute change in number of occurences
+		Values indicate the absolute change in number of occurrences
 		of the word, and positive values indicate that the food-exposed
@@
 hyponym and hypernym relations between words.  A hypernym is a 
-generalization (for example, ``bread'' is a hypernym of ``pumpernickle''), 
+generalization (for example, ``bread'' is a hypernym of ``pumpernickel''), 
 while a hyponym is a specialization.  We took took the set of food-words
 to be all those reachable through
-a chain of hyponym relations from the wordsenses 
+a chain of hyponym relations from the word senses 
 \texttt{food.n.01} and \texttt{food.n.02}, in other words, all words
@@
 To validate the resulting set of 
-food words, three independant annotators labeled 500 words selected from 
+food words, three independent annotators labeled 500 words selected from 
 workers' responses as either food or non-food, and these were
@@
 workers exposed to food (via prior tasks or framing) did not necessarily
-use more food-words when labelng images in the test tasks.
+use more food-words when labeling images in the test tasks.
 In \textit{intertask-food-culture}, food-exposed
@@
 relative specificity for the treatments separately for each test task, and 
-averaged the results obtained accross the five test tasks.
+averaged the results obtained across the five test tasks.
 

### 2015-09-24 docs/publications/2015.08_CHI/man.tex
edwards final pass

@@
 A topic of ongoing research concerns the design of tasks that elicit high
-quality annotation.
+quality annotations.
 Here we identify a feature of nearly all crowdsourcing 
@@
 We call this phenomenon \textit{intertask effects}.
-We compare intertask effects to the overt framing of the assignment, 
+We compare intertask effects to the overt framing, 
 effected by stating the requester's research interest, 
@@
 
-\keywords{Authors' choice; of terms; separated; by semi\-colons;
-  commas, within terms only; this section is required.}
-
-\category{H.5.m.}{Information Interfaces and Presentation
-  (e.g. HCI)}{Miscellaneous} \category{See
-  \url{http://acm.org/about/class/1998/} for the full list of ACM
-  classifiers. This section is required.}{}{}
+\keywords{Microtask; crowdsourcing; priming; task-design; bias; classifier}
+
+\category{H.1.2.}{Information Systems}{Models and Principles}
+\category{Human information processing}{}{}
 
@@
 computational capabilities, by matching requesters, who need to have such 
-tasks completed, with human workers.  Amazon's Mechanical Turk, and 
-CrowdFlower are two popular microtask platforms.
+tasks completed, with human workers.  Amazon's Mechanical Turk\footnote{\url{mturk.com}}, and 
+CrowdFlower\footnote{\url{crowdflower.com}} are two popular microtask 
+platforms.
 
@@
 prime is the same as the task.
-Thus, the typical microtask setup creates the conditions in which
+Thus, the typical microtask setup creates conditions in which
 earlier tasks could induce bias in later ones, through priming.
@@
 ``incorrect'' responses.  But many tasks involving qualitative judgment
-do not.  To provide a generalized measure of bias, we seek to quantify the
-extent to which intertask priming can shift the distribution of responses 
+do not.  Rather than simply characterizing effects on accuracy, we seek
+to provide a generalized measure of bias, by quantifying the
+extent to which intertask effects can shift the distribution of responses 
 to a task.  
@@
 label a series of images that are more similar, their responses become 
-more specialized more diverse.  Prior tasks can shift the topical focus of 
+more specialized and more diverse.  
+Prior tasks can shift the topical focus of 
 worker's labels, inducing them to focus on different aspects of the images.
@@
 alter the framing of microtask assignments, in terms of the stated purpose
-of the task.  Remarkably, the effects prior microtasks themselves,
+of the task, or by naming the funder.
+Remarkably, the effects of prior microtasks themselves,
 which are virtually ubiquitous, are on par with, or stronger than, 
-overtly framing the purpose of an assignment.
+overtly framing an assignment.
 
@@
 % figure out what to do about it
-Accuracy and replicability are central to any crowdsourcing study.
 There is ongoing research investigating how the design of microtasks,
@@
 Since microtask work is generally paid, wage is a basic parameter in
-the requesters control that might influence response quality.
+the requester's control that might influence response quality.
 One might expect a higher wage to \textit{buy} better performance,
@@
 % Optimization based on the breakdown of tasks
-Breaking down of complex jobs into simpler tasks, can increasing worker
+The breaking down of complex jobs into simpler tasks can increase
 efficiency by enabling greater parallelism.
@@
 Priming is more 
-effective when the prime and the target task involve the kind of 
+effective when the prime and the target task involve the same kind of 
 activity.  For example, exposing participants to an image helps them 
@@
 
-As we have mentioned, workers prefer to perform series of similar tasks
-series of similar tasks in quick succession.  Moreover, the many 
+As we have mentioned, workers prefer to perform a series of tasks that
+are similar to one another.
+Moreover, many 
 microtasks involve tasks based on visual and auditory perception 
@@
 
-\subsection{Measuring the extent of priming}
-If a prior task acts as a prime for a later one, it will 
-result in a shift in the responses workers provide for the later task.
+\section{Measuring the extent of priming}
+If a prior task acts as a prime for a later one, 
+and thereby introduces bias, the bias will manifest as
+a shift in the distribution of responses 
+workers provide for the later task.
 A variety of tests exist to determine \textit{whether} two samples, 
@@
 \textit{total variational distance}\footnote{
-  Other formulation such as the Kullback-Leibler and 
+  Other formulations such as the Kullback-Leibler and 
   Jensen-Shannon divergence can be calculated from the total variational
-  distance
+  distance.
 }, which we will henceforth denote by $\theta$.
@@
 For reference, the distributions plotted in 
-Figure~\ref{fig:l1_example}A and B have $\theta=30\%$ and $\theta=50\%$ 
+Figure~\ref{fig:l1_example}A and B have $\theta=50\%$ and $\theta=30\%$ 
 respectively.
@@
 		A) it is given by 
-		$\theta = a_1 / (a_1 + a_2) = a_2 / (a_2 + a_3)$.
+		$\theta = a_1 / (a_1 + a_2) = a_3 / (a_2 + a_3)$.
 	}
@@
 
-However, we can establish a lower bound for $\theta$ by 
+Nevertheless, we can establish a lower bound for $\theta$ by 
 exploiting a fact about the theoretical limits on the accuracy of a 
 classifier algorithm.  The intuition is as follows: 
-suppose workers are shown one of two alternative designs\footnote{We will
+suppose workers are shown one of two alternative designs\footnote{We
 use ``design'' in a general sense, to include both the design of the task
 and of its context.  In particular, the ``design'' might include the
-particular tasks that were shown beforehand, or the use of framing.}
+selection of tasks that were shown beforehand, or the use of framing.}
 for an otherwise
@@
 Conversely, if the classifier accuracy is good, then design alternative 
-must have a strong effect on the response distribution.
+must have had a strong effect on the response distribution.
 
@@
 We performed a series of five experiments
-on Amazon's Mechanical Turk\footnote{\url{mturk.com}} using 1071 workers.  
+on Amazon's Mechanical Turk using 1071 workers.  
 Every experiment consisted of two treatments, each with 119 workers,
 who performed a single assignment\footnote{Workers could not participate 
-multiple times in our study}\textsuperscript{,}\footnote{On Mechanical Turk, individual 
+multiple times in our study.}\textsuperscript{,}\footnote{On Mechanical Turk, individual 
 assignments are called Human Intelligence Tasks (HITs), but this use of 
@@
 workers in the \textit{food} and \textit{objects} treatments differed
-significantly during test tasks (by $\chi^2$ test, $p = 6.0 \times 10^{-14}$),
+significantly during test tasks ($p = 6.0 \times 10^{-14}$),
 even though the test tasks were identical in both treatments.  
@@
 validates our concerns about the typical microtask methodology.
+
+The heterogeneity of word-frequencies between treatments was based on 
+Pearson's $\chi^2$ test with Yates' correction.
+In linguistics applications, the use of a $\chi^2$ to test for 
+heterogeneity between corpora has been called
+into question, because there is frequently heterogeneity \textit{within}
+a given corpus \cite{kilgarriff1996comparing}.
+This occurs because certain documents in a corpus will regard certain 
+topics, leading to bursty word usage.  While our setup is substantially
+remote from the applications for which this concern was raised, 
+one could argue that the responses to a given treatment
+constitute a ``corpus'', and the responses of a given worker to a 
+``document''.
+To address this concern, we randomly split responses to given treatment
+into two sets, and tested for hetererogeneity between the sets.
+In all cases, we failed to find heterogeneity \textit{within} a given 
+treatment (with $p > 0.3$ for all treatments and $p > 0.8$ for most).
+Thus, the heterogeneity we observed \textit{between} treatments is 
+meaningful.
 
@@
 classifier for three reasons.  First, it performs well even when the 
-number of features is large compared to the number of training examples.  
+number of features is large compared to the number of training examples
+\cite{bickel2004,hastie2009elements}.  
 Second, there are no hyperparameters to 
@@
 Third, the conditional independence assumption, normally 
-undertaken for pragmatic reasons, is probably a relatively mild in 
+undertaken for pragmatic reasons \cite{Zhang2004562}, 
+is probably a relatively mild in 
 relation to image labels, since they are likely to be less dependent
-on one another than in a coherent passage of text.  We also used a 
-support vector machine and found very similar results.
+on one another than in a coherent passage of text.  We repeated our
+analysis used a support vector machine and found very similar results.
 
@@
 experiment \textit{intertask-food-objects}
-lead to (a lower bound) bias of $\theta=30\%$ between workers from the 
+lead to (a lower bound) bias of $\theta=30.6\%$ between workers from the 
 \textit{food} and \textit{objects} treatments (Figure~\ref{fig:theta}A).
@@
 substantial potential to distort microtask data.
+
+When observing the classifier's accuracy, in order to calculate $\theta$,
+the number of correct inferences made by the classifier follows a binomial 
+distribution.  The fraction of successes yields the maximum likelihood
+estimate of the classifier's accuracy (used to generate $\theta$), 
+and we derived confidence intervals using the exact Clopper-Pearson method.
 
@@
 And so, remarkably, the extent of bias due to framing was weaker than that 
-due to intertask effects ($p=2.1\times 10^{-5}$).
+due to intertask effects ($p=2.1\times 10^{-5}$)\footnote{To compare bias
+  due to framing and inter-task effects, we approximated the distribution
+  of correct classifications as a normal distribution, and performed
+a (two-tailed) two-proportion $z$-test.}.
 In other words, the \textit{microtasks themselves}
@@
 task position.
-Bias was strongest for the first test task (about 28\%), 
+Bias was strongest for the first test task (28.1\%), 
 but remained significant through all five test tasks 
@@
 Results for this experiment again showed a 
-strong bias as a result of intertask effects (about 50\%) 
+strong bias as a result of intertask effects (51.3\%) 
 (Figure~\ref{fig:theta}A).  Again, visualizing the word frequencies 
@@
 or objects), workers were asked to echo the purpose of the task
-using a combo-box input.  This  ``echoed framing'' induced a bias of about 
-35\% (Figure~\ref{fig:theta}A). However, it is difficult to say whether this 
+using a combo-box input.  This  ``echoed framing'' induced a bias of 
+36.1\% (Figure~\ref{fig:theta}A). However, it is difficult to say whether this 
 should be considered as a framing treatment \textit{per se}:
@@
 to be all those reachable through
-a chain of hyponym relations from the word senses 
+a chain of hyponym relations from the word-senses 
 \texttt{food.n.01} and \texttt{food.n.02}, in other words, all words
@@
 automated identification of food words as another annotator, there 
-was an inter-rater reliability of 82.4\%.
-
-Using the automated labeling of food words, we found that, in fact
+was an 82.4\% agreement between annotators.
+
+Using the automated labeling of food words, we found that, contrary to
+expectations,
 workers exposed to food (via prior tasks or framing) did not necessarily
@@
 In \textit{intertask-food-culture}, food-exposed
-workers actually used significantly \textit{fewer} food-related words 
+workers actually used significantly\footnote{
+  Frequencies of food references within a treatment were calculated as
+  an average across workers, and modeled as normally distributed.
+} \textit{fewer} food-related words 
 during test tasks (Figure~\ref{fig:specificity}A).  This finding
@@
 content that has been present in earlier tasks: seeing content 
-influences, but does not necessarily \textit{increase}, the probability of 
-referring to it in subsequent tasks.
+significantly influences, but does not necessarily 
+\textit{increase}, the probability of referring to it in subsequent tasks.
 
@@
 %although to a lesser extent.
+
+To test the significance of the difference in sizes of food
+lexicons,
+we created a null model for each experiment, by assuming that
+responses for both treatments were in fact drawn from the same 
+distribution.
+This was accomplished by pooling responses for both treatments 
+of a given experiment, then 
+drawing two bootstrap samples of 119 responses and calculating
+the difference in the size of their food lexicons.  
+We repeated this 1000 times and took the 2.5th and 97.5th percentiles 
+as the critical values for the rejection of the null hypothesis 
+(the latter shown by stars in Figure~\ref{fig:specificity}B).
 
@@
 relative specificity for the treatments separately for each test task, and 
-averaged the results obtained across the five test tasks.
+averaged the results obtained across the five test tasks.  To establish
+significance, we again used a null model, based on bootstrapping.
 
@@
 used significantly more specialized words, in reference to food 
-(about 15\% more) (Figure~\ref{fig:specificity}C).
+(about 15\% more; $p > 0.05$) (Figure~\ref{fig:specificity}C).
 It is interesting that such substantial increases in both the lexical 
@@
 responses, simply from the performance of earlier tasks. 
-These effects are much stronger than those of framing.  
+These effects can be much stronger than those of framing.  
 While our findings raise serious concerns about the 

### 2015-09-25 docs/publications/2015.08_CHI/man.tex
Revised manuscript

@@
     \affaddr{School of Computer Science, McGill University}\\
-    \affaddr{3480 University Street, Room 318, Montreal, Qu\'ebec,
-	  Canada, H3A 2A7
+    \affaddr{Montreal, Qu\'ebec,
+	  Canada
 	}\\
@@
 quality annotations.
-Here we identify a feature of nearly all crowdsourcing 
+Here we identify a seemingly banal feature of nearly all crowdsourcing 
 workflows that profoundly impacts workers' responses.
@@
 programmatically.  
-Typical tasks include tagging and categorizing images,
+Such tasks include tagging and categorizing images,
 %\cite{6116320,Zhai2012357}, 
@@
 and is among the most common kinds of tasks on the major crowdsourcing
-platform Amazon's Mechanical Turk.  If task-induced priming arises in our 
-setup, it should be expected in virtually every microtask and 
-crowdsourced workflow where workers are called upon to provide qualitative
+platform Amazon's Mechanical Turk (see Table \ref{table:task_composition}).  If task-induced priming arises in our 
+setup, it should be expected in an overwhelming number of microtasks and 
+crowdsourced workflows where workers are called upon to provide qualitative
 judgment.
@@
 % important
-Microtask platforms are increasingly used clean and codify datasets,
+Microtask platforms are increasingly used to clean and codify datasets,
 administer experiments with human participants, and distribute 
@@
 }, the na\"ive approach would typically lead one to report 
-$\hat{\theta} \approx 65\%$, event though, in reality $\theta = 0\%$
+$\hat{\theta} \approx 65\%$, even though, in reality $\theta = 0\%$
 (this can be shown by simulated sampling).
@@
 
-We will now establish Inequality~\ref{eq:sup:l1} by considering an
+We can establish Inequality~\ref{eq:sup:l1} by considering an
 optimal classifier having accuracy $\eta_*$.  
@@
 
-\begin{figure}
+\begin{figure}[t]
 	\includegraphics[scale=0.75]{figs/theta.pdf}
@@
 
-\begin{table}
+We performed a series of five experiments
+on Amazon's Mechanical Turk using 1071 workers.  
+Every experiment consisted of two treatments, each with 119 workers,
+who performed a single assignment\footnote{Workers could not participate 
+multiple times in our study.}\textsuperscript{,}\footnote{On Mechanical Turk, individual 
+assignments are called Human Intelligence Tasks (HITs), but this use of 
+``task'' is 
+different from our current one: in our experiment each HIT actually 
+involves 10 image-labeling tasks.}.  
+The setup in each experiment followed the template depicted in 
+Figure~\ref{fig:task-schematic}.  
+The assignments had two parts.  The first part of the assignment differed
+between the two treatments, and consisted of a set of initial tasks 
+and/or framing (by describing the purpose of the assignment or source of 
+funding).  In the second part of the assignment, workers from both
+treatments completed the same five \textit{test tasks}.  Each of the 
+initial and test tasks required workers to provide five descriptive labels
+for an image.  The tasks were performed one at a time,
+and, in treatments involving both initial and test tasks, there was no
+interruption or distinction made between the initial and test tasks from
+the perspective of the worker.
+
+We analyzed the
+workers' responses to the test tasks to determine whether
+they were influenced by the initial tasks (or framing).  We looked for 
+differences in the distributions of test responses 
+using a $\chi^2$ test.  We then measured the 
+severity of bias induced by initial tasks and framing, by 
+constructing a na\"ive Bayes classifier to infer the workers' 
+treatments based on their responses to test tasks, 
+and measuring its accuracy.
+
+\begin{table}[b!]
 \small
@@
 
-We performed a series of five experiments
-on Amazon's Mechanical Turk using 1071 workers.  
-Every experiment consisted of two treatments, each with 119 workers,
-who performed a single assignment\footnote{Workers could not participate 
-multiple times in our study.}\textsuperscript{,}\footnote{On Mechanical Turk, individual 
-assignments are called Human Intelligence Tasks (HITs), but this use of 
-``task'' is 
-different from our current one: in our experiment each HIT actually 
-involves 10 image-labeling tasks.}.  
-The setup in each experiment followed the template depicted in 
-Figure~\ref{fig:task-schematic}.  
-The assignments had two parts.  The first part of the assignment differed
-between the two treatments, and consisted of a set of initial tasks 
-and/or framing (by describing the purpose of the assignment or source of 
-funding).  In the second part of the assignment, workers from both
-treatments completed the same five \textit{test tasks}.  Each of the 
-initial and test tasks required workers to provide five descriptive labels
-for an image.  The tasks were performed one at a time,
-and, in treatments involving both initial and test tasks, there was no
-interruption or distinction made between the initial and test tasks from
-the perspective of the worker.
-
-We analyzed the
-workers' responses to the test tasks to determine whether
-they were influenced by the initial tasks (or framing).  We looked for 
-differences in the distributions of test responses 
-using a $\chi^2$ test.  We then measured the 
-severity of bias induced by initial tasks and framing, by 
-constructing a na\"ive Bayes classifier to infer the workers' 
-treatments based on their responses to test tasks, 
-and measuring its accuracy.
-
-In our first experiment called \textit{intertask-food-objects},
+{\bf Existence of inter-task effects.} In our first experiment called \textit{intertask-food-objects},
 workers were assigned to either a \textit{food} or \textit{objects} 
@@
 
-Having affirmed the \textit{existence} of intertask effects, we sought to
+{\bf Strength of inter-task effects.} Having affirmed the \textit{existence} of intertask effects, we sought to
 measure the severity of the bias induced, i.e. $\theta$.
@@
 Figure~\ref{fig:l1_example}B have $\theta = 30\%$.  This represents a 
-substantial potential to distort microtask data.
+substantial potential to distort microtask results.
 
@@
 
-To assess the persistence of intertask effects, we replicated the 
+{\bf Persistence of inter-task effects.} To assess the persistence of intertask effects, we replicated the 
 \textit{intertask-food-objects} experiments, rotating the ordering of the
@@
 
-We conducted variants of these experiments using different images, to see 
+{\bf Different tasks, similar effects.} We conducted variants of these experiments using different images, to see 
 whether this trend was robust.  In the experiment 
@@
 
-To better understand the nature of 
+{\bf Inter-task effects and concept activation.} To better understand the nature of 
 intertask effects, we investigated the vocabulary
@@
 generalization (for example, ``bread'' is a hypernym of ``pumpernickel''), 
-while a hyponym is a specialization.  We took took the set of food-words
+while a hyponym is a specialization.  We took the set of food-words
 to be all those reachable through

### 2016-01-03 docs/publications/2015.12_CHI/man.tex
add revised CHI manuscript

--- 2015-09-25 docs/publications/2015.08_CHI/man.tex
@@
 
-\numberofauthors{3}
+\numberofauthors{1}
 \author{%
   \alignauthor{
-	Edward Newell \\
-    \affaddr{School of Computer Science, McGill University}\\
-    \affaddr{Montreal, Qu\'ebec,
-	  Canada
+	Authors\\
+    \affaddr{Affiliations}\\
+    \affaddr{Addresses 	}\\
+	\email{email@domain.com}
   }\\
-	\email{edward.newell@mail.mcgill.ca}}\\
-  \alignauthor{
-	Derek Ruths \\
-    \affaddr{School of Computer Science, McGill University}\\
-    \affaddr{Montreal, Qu\'ebec,
-	  Canada
-	}\\
-	\email{derek.ruths@mcgill.ca}
-  }\\
+  %\alignauthor{
+  %  Author 2 \\
+  %  \affaddr{Affiliation 1}\\
+  %  \affaddr{Montreal, Qu\'ebec,
+  %    Canada
+  %  }\\
+  %  \email{derek.ruths@mcgill.ca}
+  %}\\
 }
+
+%\numberofauthors{2}
+%\author{%
+%  \alignauthor{
+%	Edward Newell \\
+%    \affaddr{School of Computer Science, McGill University}\\
+%    \affaddr{Montreal, Qu\'ebec,
+%	  Canada
+%	}\\
+%	\email{edward.newell@mail.mcgill.ca}}\\
+%  \alignauthor{
+%	Derek Ruths \\
+%    \affaddr{School of Computer Science, McGill University}\\
+%    \affaddr{Montreal, Qu\'ebec,
+%	  Canada
+%	}\\
+%	\email{derek.ruths@mcgill.ca}
+%  }\\
+%}
 
@@
 and find that intertask effects are on par or stronger.
-While intertask effects can be a source of systematic bias, 
-our results suggest that, with appropriate task design, 
+If uncontrolled, intertask effects could be a source of systematic bias, 
+but our results suggest that, with appropriate task design, 
 they might be leveraged to hone worker focus and acuity, 
@@
 Thus, the typical microtask setup creates conditions in which
-earlier tasks could induce bias in later ones, through priming.
-
-We seek to determine if any significant priming effect occurs between
-tasks, and if so, to measure and characterize it.
+the contents of earlier tasks could influence responses to later ones.
+
+We seek to determine if any such effects in fact occur and if so, 
+to measure and characterize them.
 Certain tasks admit a well-defined notion of ``correct'' and 
@@
 do not.  Rather than simply characterizing effects on accuracy, we seek
-to provide a generalized measure of bias, by quantifying the
-extent to which intertask effects can shift the distribution of responses 
-to a task.  
-Measuring the \textit{extent} of the shift in response distribution,
-i.e. the extent of bias, is substantially harder than
-simply determining \textit{whether} a biasing effect has occurred.  
-Our first contribution is a statistically grounded method for doing so.
+to provide a generalized measure of the extent to which prior tasks
+can alter the distribution of responses to a task.  
+Measuring the \textit{extent} of the shift in response distribution, is 
+substantially harder than simply determining \textit{whether} an effect 
+has occurred.  Our first contribution is a statistically grounded method 
+for doing so.
 
@@
 and is among the most common kinds of tasks on the major crowdsourcing
-platform Amazon's Mechanical Turk (see Table \ref{table:task_composition}).  If task-induced priming arises in our 
-setup, it should be expected in an overwhelming number of microtasks and 
+platform Amazon's Mechanical Turk (see Table \ref{table:task_composition}).
+If task-induced priming arises in our 
+setup, it could be expected in a large number of microtasks and 
 crowdsourced workflows where workers are called upon to provide qualitative
@@
 the content of tasks performed beforehand, leading to as much as 50\%
-bias (measured as total variational distance, 
-see Figure~\ref{fig:l1_example} for illustrative definition).  
+total variational distance (see Figure~\ref{fig:l1_example} for 
+illustrative definition of total variational distance).  
 Using the WordNet 
@@
 
-As a point of comparison, we perform similar experiments, in which we
-alter the framing of microtask assignments, in terms of the stated purpose
-of the task, or by naming the funder.
+As a point of comparison, our experiments included framing treatments, 
+in which we altered the framing of microtask assignments, in terms of the 
+stated purpose of the task, or by naming the funder.
 Remarkably, the effects of prior microtasks themselves,
@@
 depend on the \textit{history} of their inputs.
-We propose a dual priming mechanism which can explain our
-observations.  Irrespective of the underlying mechanism, this 
-very strong effect might be exploited in task design to tune worker 
-focus and acuity.
+
+Unraveling the psychological mechanisms that give rise to such strong 
+effects will require further investigation.  We describe a possible 
+mechanism based on positive and negative priming, consistent with the
+observations from our experiments.
+Irrespective of the underlying mechanism, this very strong effect might 
+be exploited in task design to tune worker focus and acuity.
 
@@
 \begin{itemize}[noitemsep,nolistsep]
-  \item{derive a general method for measuring bias in responses;}
-  \item{measure bias in microtasks due to prior tasks;}
+  \item{
+	derive a method for measuring changes in response distributions;
+  }
+  \item{measure the influence of initial microtasks on later ones;}
   \item{show this effect is stronger than, or on par with framing;}
@@
 The rest of the paper is organized as follows.  In the next section, we 
-review the relevant prior work.  We then present a method for 
-measuring bias due to intertask effects.  
+review the relevant prior work.  We then present our method for 
+measuring changes to response distributions.
 Next we present our experimental results, followed by a discussion 
@@
 Information gathering & 46 & 23.0 \\
-Image tagging and classification & 36 & 18.0 \\
+Image labeling and classification & 36 & 18.0 \\
 Copy writing and editing & 18 & 9.0 \\
@@
 
-\section{Measuring the extent of priming}
-If a prior task acts as a prime for a later one, 
-and thereby introduces bias, the bias will manifest as
-a shift in the distribution of responses 
-workers provide for the later task.
+\section{Measuring changes to response distributions}
+When a prior task influences a later one, this influence will manifest as
+a shift in the distribution of responses workers provide for the later 
+task.
 A variety of tests exist to determine \textit{whether} two samples, 
@@
 most notably the $\chi^2$ test.  
-This will suffice to determine whether there are any grounds for concern 
-about priming effects in the first place.  However, such tests
+However, such tests
 do not tell us \textit{how much} two distributions differ, and hence
-how severe the priming effects are.
-
-Determining the severity of priming effects amounts to measuring a 
-distance, or \textit{divergence}, between response distributions, by
-sampling responses from workers exposed to different priming conditions.
+how strongly the initial task's influence is.
+
+Determining the strength of intertask effects amounts to measuring a 
+distance, or \textit{divergence}, between response distributions.
 We will present a method for bounding a kind of divergence known as 
@@
 research \cite{val-thesis,batu2013testing,chan2014optimal}.
-In the ``na\"ive'' approach one first uses the samples to reconstruct 
+In the ``naive'' approach one first uses the samples to reconstruct 
 empirical
@@
   where $p(x)$ is the probability of the $x$th most common word.
-}, the na\"ive approach would typically lead one to report 
+}, the naive approach would typically lead one to report 
 $\hat{\theta} \approx 65\%$, even though, in reality $\theta = 0\%$
@@
 
-\section{Results}
-\begin{figure}
-	\includegraphics[scale=0.36]{figs/task-schematic-2.pdf}
-	\caption{
-	  Template for the experiments described in the main text.
-	  After selecting our assignment on Mechanical 
-	  Turk, workers were separated into two treatments.
-	  Workers from each treatment were subjected to framing and/or
-	  five initial tasks, which differed between treatments, and then 
-	  completed a set of five test tasks that were identical for both
-	  treatments.  Most experiments involved either framing or initial
-	  tasks (see table \ref{table:experiments}), 
-	  but \textit{frame-food-culture} involved both.
-	  After the experiment, workers return to the Mechanical Turk 
-	  task-selection interface.
-	}
-	\label{fig:task-schematic}
-\end{figure}
+\section{Experiment 1}
+\subsection{Setup}
+%\begin{figure}
+%	\includegraphics[scale=0.36]{figs/task-schematic-2.pdf}
+%	\caption{
+%	  Template for the experiments described in the main text.
+%	  After selecting our assignment on Mechanical 
+%	  Turk, workers were separated into two treatments.
+%	  Workers from each treatment were subjected to framing and/or
+%	  five initial tasks, which differed between treatments, and then 
+%	  completed a set of five test tasks that were identical for both
+%	  treatments.  Most experiments involved either framing or initial
+%	  tasks (see table \ref{table:experiments}), 
+%	  but \textit{frame-food-culture} involved both.
+%	  After the experiment, workers return to the Mechanical Turk 
+%	  task-selection interface.
+%	}
+%	\label{fig:task-schematic}
+%\end{figure}
 
@@
 	\caption{
-		Empirical bias, $\theta_\mathrm{NB}$, measured using a na\"ive Bayes 
+		Empirical bias, $\theta_\mathrm{NB}$, measured using a naive Bayes 
 		classifier, induced in image-labeling tasks, due to workers' 
@@
 
-We performed a series of five experiments
-on Amazon's Mechanical Turk using 1071 workers.  
-Every experiment consisted of two treatments, each with 119 workers,
-who performed a single assignment\footnote{Workers could not participate 
-multiple times in our study.}\textsuperscript{,}\footnote{On Mechanical Turk, individual 
-assignments are called Human Intelligence Tasks (HITs), but this use of 
-``task'' is 
-different from our current one: in our experiment each HIT actually 
-involves 10 image-labeling tasks.}.  
-The setup in each experiment followed the template depicted in 
-Figure~\ref{fig:task-schematic}.  
-The assignments had two parts.  The first part of the assignment differed
-between the two treatments, and consisted of a set of initial tasks 
-and/or framing (by describing the purpose of the assignment or source of 
-funding).  In the second part of the assignment, workers from both
-treatments completed the same five \textit{test tasks}.  Each of the 
-initial and test tasks required workers to provide five descriptive labels
-for an image.  The tasks were performed one at a time,
-and, in treatments involving both initial and test tasks, there was no
-interruption or distinction made between the initial and test tasks from
-the perspective of the worker.
-
-We analyzed the
-workers' responses to the test tasks to determine whether
-they were influenced by the initial tasks (or framing).  We looked for 
-differences in the distributions of test responses 
-using a $\chi^2$ test.  We then measured the 
-severity of bias induced by initial tasks and framing, by 
-constructing a na\"ive Bayes classifier to infer the workers' 
-treatments based on their responses to test tasks, 
-and measuring its accuracy.
-
-\begin{table}[b!]
-\small
-\centering
-\setlength{\tabcolsep}{1pt}
-\begin{tabular}{c c c c c}
-\toprule
-Experiment & \parbox[c]{3.0cm}{\centering{Priming modality}} & Initial Tasks & Frame \\
-\midrule
-\multirow{2}{*}{\textit{intertask-food-objects}} 
-& \multirow{2}{*}{initial tasks} & \textit{food} & none \\
-  & & \textit{objects} & none  \\
-
-\noalign{\smallskip}
-\hdashline
-\noalign{\smallskip}
-
-\multirow{2}{*}{\textit{frame-food-objects}} 
-& \multirow{2}{*}{framing} & none 
-	& ``food''\textsuperscript{a} \\
-& & none 
-	& ``objects''\textsuperscript{b} \\
-
-\noalign{\smallskip}
-\hdashline
-\noalign{\smallskip}
-
-\multirow{2}{*}{\textit{echo-food-objects}} 
-& \multirow{2}{*}{echoed framing} & none
-	& ``food''\textsuperscript{c} \\
-& & none & ``objects''\textsuperscript{d} \\
-
-\noalign{\smallskip}
-\hdashline
-\noalign{\smallskip}
-
-\multirow{2}{*}{\textit{intertask-food-culture}} 
-& \multirow{2}{*}{initial tasks} & \textit{food} 
-	& none \\
-& & \textit{culture} 
-	& none \\
-
-\noalign{\smallskip}
-\hdashline
-\noalign{\smallskip}
-
-\multirow{2}{*}{\textit{frame-food-culture}} 
-& \multirow{2}{*}{framing} & \textit{food} 
-	& ``food''\textsuperscript{e} \\
-  & & \textit{food}
-	& ``culture''\textsuperscript{f} \\
-
-\bottomrule
-\end{tabular}
-\caption{
-	Description of experiments performed.  Each experiment had two treatments
-	which differed either in the initial tasks shown or the framing used 
-	(the priming modality).  
-	During echoed framing, the worker had to respond to the framing language
-	using a combo box input.  The framing language used was as follows:
-	\newline\textsuperscript{a} ``Funded by the laboratory for the visual 
-		perception of Food and Ingredients''
-	\newline\textsuperscript{b} ``Funded by the laboratory for the visual 
-		perception of Objects and Tools''
-	\newline\textsuperscript{c} ``The purpose of this study is to understand the visual perception of Food and Ingredients''
-	\newline\textsuperscript{d} ``The purpose of this study is to understand the visual perception of Objects and Tools''
-	\newline\textsuperscript{e} ``This research is proudly funded by The National 
-		Foundation for Nutritional Awareness''
-	\newline\textsuperscript{f} ``This research is proudly funded by The Global 
-		Foundation for the Recognition of Cultures''
-}
-\label{table:experiments}
-\end{table}
-
-{\bf Existence of inter-task effects.} In our first experiment called \textit{intertask-food-objects},
-workers were assigned to either a \textit{food} or \textit{objects} 
-treatment.  Workers from these treatments performed initial tasks 
-in which they labeled, respectively, 
-images depicting either food or (non-food) objects
-(see example images in Figure~\ref{fig:task}A and B).  
-Workers from both treatments then performed five test tasks, which
-contained images
-depicting both food and objects (Figure~\ref{fig:task}C).
-
-The frequencies of words used by
-workers in the \textit{food} and \textit{objects} treatments differed
-significantly during test tasks ($p = 6.0 \times 10^{-14}$),
-even though the test tasks were identical in both treatments.  
-Thus earlier tasks do significantly affect later ones, which 
-validates our concerns about the typical microtask methodology.
-
-The heterogeneity of word-frequencies between treatments was based on 
+The first experiment we performed consisted of two sub-experiments which
+we will call ``intertask'' and ``framing'', because they are respectively
+designed to measure intertask and framing effects.  The experiment was 
+performed on Amazon's Mechanical Turk (MTurk) using 476 workers.  Workers
+could only participate once in a given experiment, and could only 
+participate in one of the experiments we present here.
+
+The experiment was conducted using a single HIT\footnote{
+  On MTurk, a HIT (or Human Intelligence Task) is the smallest 
+  assignable unit of work.  The use of ``Task'' in HIT differs from that
+  used here; here labeling a single image is considered to be one ``task'',
+  and so a HIT is actually composed of 10 tasks.
+}.  Workers who accepted the HIT were randomly assigned to one of the two
+sub-experiments.  Both sub-experiments consisted of two treatments, which
+we call ``food'' and ``culture'', and workers were also randomly 
+assigned to a treatment.  In both treatments of both sub-experiments,
+workers were asked to perform ten image-labeling tasks, each of which 
+required the worker to assign five descriptive labels to an image.  
+In all cases, the last five tasks were 
+identical, and were presented in the same order.  
+These last five tasks constituted the ``test tasks'', whose distribution
+of responses could admit intertask or framing effects.
+
+In the intertask sub-experiment, we varied the first five tasks given to 
+workers based on the treatment.  Workers assigned to the ``food'' 
+treatment were shown images of food, while workers assigned to the 
+``culture'' treatment were shown other kinds of cultural depictions, such
+as dance, sport, and music\footnote{We do not assert that cultural 
+practices can be cleanly separated into food-related and non-food related 
+ones; that is not necessary for our analysis.}.  
+However, within a given treatment, workers were shown the same images in
+the same order.  As mentioned, workers 
+from both treatments then performed the same five test tasks.  The test
+tasks consisted of images depicting meals of diverse ethnic origin.
+From the perspective of the worker, there was no distinction between the 
+initial and test tasks.
+
+In the framing sub-experiment, we did not vary the initial tasks, but 
+instead, introduced a \textit{framing slide} before the tasks.  
+Depending on the treatment, the framing slide read 
+``This research is proudly funded by The National Foundation for 
+Nutritional Awareness'', or ``\ldots by the Global Foundation for the 
+Recognition of Cultures''.  The intention here was to frame the task by
+providing the name of a (fictitious) funder, and using names that
+invite the worker to focus on different aspects of the image content.  
+As already mentioned, the test tasks consisted of images depicting meals 
+of diverse ethnic origin.
+
+\subsection{Results}
+
+\paragraph{Existence of intertask and framing effects.} 
+Looking at the frequencies with which workers use words, we tested for
+heterogeneity between the two treatments of each sub-experiment.
+For the intertask sub-experiment, we found the distribution of responses 
+for the two treatments differed significantly ($p=?$), 
+demonstrating that intertask effects do exist.  However, we did not find 
+significant effects due to framing, however (by $\chi^2$ test, $p=0.29$) 
+(Figure~\ref{fig:theta}A).
+
+Testing for heterogeneity of word-frequencies was based on 
 Pearson's $\chi^2$ test with Yates' correction.
@@
 treatment (with $p > 0.3$ for all treatments and $p > 0.8$ for most).
+These results hold for Experiment 2 as well, to be discussed later.
 Thus, the heterogeneity we observed \textit{between} treatments is 
@@
 
-{\bf Strength of inter-task effects.} Having affirmed the \textit{existence} of intertask effects, we sought to
-measure the severity of the bias induced, i.e. $\theta$.
-To measure $\theta$ we used a na\"ive Bayes classifier based on a 
+\paragraph{Strength of intertask and framing effects.}
+Having affirmed the \textit{existence} of intertask effects, we sought to
+measure the strength of the effect, i.e. $\theta$.
+To measure $\theta$ we created a naive Bayes classifier based on a 
 multinomial distribution over the word frequencies in worker's labels, 
 and measured it's accuracy using leave-one-out cross-validation.  
-We chose the na\"ive Bayes
+We chose the naive Bayes
 classifier for three reasons.  First, it performs well even when the 
@@
 undertaken for pragmatic reasons \cite{Zhang2004562}, 
-is probably a relatively mild in 
+is probably a mild in 
 relation to image labels, since they are likely to be less dependent
 on one another than in a coherent passage of text.  We repeated our
-analysis used a support vector machine and found very similar results.
+analysis using a support vector machine and found very similar results.
 
@@
 
-Based on the classifier accuracy, intertask effects in the 
-experiment \textit{intertask-food-objects}
-lead to (a lower bound) bias of $\theta=30.6\%$ between workers from the 
-\textit{food} and \textit{objects} treatments (Figure~\ref{fig:theta}A).
-It is difficult to visualize the distributions of word frequencies,
-but for reference, the distributions shown in 
-Figure~\ref{fig:l1_example}B have $\theta = 30\%$.  This represents a 
-substantial potential to distort microtask results.
+Based on the performance of the classifier, intertask effects generated
+51.3\% total variational distance (Figure~\ref{fig:theta}A).  
+Visualy comparing two word frequency distributions is difficult, but 
+Figure~\ref{fig:l1_example} provides an example of distributions having 
+$\theta = 50\%$.  In contrast to intertask effects, the effect due to 
+framing, was not significantly different from zero 
+(Figure~\ref{fig:theta}A).
+And so, the effect framing was weaker than that due to prior tasks 
+($p=7.6\times 10^{-7}$)\footnote{To compare bias
+  due to framing and intertask effects, we approximated the distribution
+  of correct classifications as a normal distribution, and performed
+a (two-tailed) two-proportion $z$-test.}.
+In other words, the \textit{microtasks themselves}
+had a stronger effect than framing.
 
@@
 
-As already discussed, there has been considerable interest in the 
-effects that framing can have on microtask responses
-\cite{Kinnaird2012281,chandler2013breaking,thibodeau2013natural}, and 
-framing effects are arguably similar to inter-task effects in the sense 
-that both arise from the worker's experiences immediately before 
-performing a task.
-Therefore, as a point of comparison, we performed a similar experiment 
-in which we suggested the focus of the study by stating a name for
-the requester within the task.
-In the experiment 
-\textit{frame-food-objects}, we used the same test tasks as in 
-\textit{intertask-food-objects}, but the initial tasks were omitted, 
-and in their stead, workers were either told that the study was 
-``Funded by the laboratory for the 
-visual perception of Food and Ingredients'', 
-or ``\ldots of Objects and Tools''.
-
-Framing induced changes in the frequencies of 
-word usage at significance 
-(as determined by $\chi^2$ test; $p=0.0012$).  But, 
-the \textit{extent} of framing-induced bias was not statistically 
-distinguishable from zero ($p =0.37$) (Figure~\ref{fig:theta}A).
-And so, remarkably, the extent of bias due to framing was weaker than that 
-due to intertask effects ($p=2.1\times 10^{-5}$)\footnote{To compare bias
-  due to framing and inter-task effects, we approximated the distribution
-  of correct classifications as a normal distribution, and performed
-a (two-tailed) two-proportion $z$-test.}.
-In other words, the \textit{microtasks themselves}
-had a stronger biasing effect than framing.
-
-{\bf Persistence of inter-task effects.} To assess the persistence of intertask effects, we replicated the 
-\textit{intertask-food-objects} experiments, rotating the ordering of the
-test tasks, so that each test task occupied each of the possible 5 
-test-task positions (see Figure \ref{fig:task-schematic}).  
-By taking the average bias induced for each test task when 
-occupying a given position, we determined $\theta$ as a function of the 
-task position.
-Bias was strongest for the first test task (28.1\%), 
-but remained significant through all five test tasks 
-($\alpha=0.05$) sustaining over 12\% bias even when the initial and test 
-tasks were separated by four intervening tasks (Figure~\ref{fig:theta}B).
-
-{\bf Different tasks, similar effects.} We conducted variants of these experiments using different images, to see 
-whether this trend was robust.  In the experiment 
-\textit{intertask-food-culture},
-workers were either assigned to a \textit{food} or \textit{culture} treatment.
-The initial tasks contained either images 
-depicting food (Figure~\ref{fig:task}D), or depictions of cultural scenes 
-(of dance, sport, or music) (Figure~\ref{fig:task}E).  The test tasks, 
-which 
-were, again, identical for both treatments, depicted meals of diverse 
-cultural origin
-%\footnote{
-%  	The food depicted in the initial tasks 
-%	in \textit{intertask-food-culture} are arguably still of
-%	diverse cultural origin, but this would only tend to make our 
-%	results more conservative.
+The results from the first experiment clearly show that intertask effects 
+arise and are strong.  On the other hand, we were scarcely able to observe
+any effect due to framing.  This raises a few questions which we seek
+to answer using a second experiment.  The first question is simply whether
+the result will replicate using different sets of images.  
+If they do, then the next question is how intertask effects evolve
+as the worker performs tasks.  Presumbaly, intertask effects wear off at 
+some point, but is it after one task, two, or more?
+
+Using the results from Experiment 1, 
+we could look at the intertask effects for individual test questions, 
+however, each question uses a distinct image, whose own content may
+modulate the extent to which it can be influenced by intertask effects.
+We cannot disentangle the question of task proximity from image content
+in the results for Experiment 1.
+
+In setting up Experiment 2, we also wish to increase the strength of 
+framing.  While finding that intertask effects were stronger than framing 
+was surprising and remarkable, perhaps the most meaningful comparison
+would be one which shows just how extreme framing treatments need to be 
+to produce effects on par with intertask effects.  
+One factor that may have weakened the effects of framing in Experiment 1 
+is the inclusion of initial tasks between the framing slide and the test 
+tasks. They were included to ensure that workers had always completed the
+same number of tasks before begining the test tasks.  However, their 
+inclusion gives time for differential framing effects to 
+subside, while also generating intertask effects that are 
+\textit{shared} between the treatments, potentially masking the framing 
+effects that remain.  In the next experiment, we measure framing effects 
+immediately after onset of framing.
+
+\section{Experiment 2}
+\subsection{Setup}
+In Experiment 2 we again have ``intertask'' and ``framing'' 
+sub-experiments, but we include a third sub-experiment, ``echo'', which 
+incorporates more extreme framing treatments.  
+As before, each sub-experiment has
+two treatments, but this time they are ``food'' and ``objects''.
+Keeping a food treatment enables us to perform deeper lexical analysis of 
+both experiments (discussed in the results for Experiment 2).  
+The experiment was again performed using a single HIT on MTurk, 
+and involved 1666 workers.
+Workers were randomly assigned to a sub-experiment and treatment upon
+starting the HIT.
+
+The intertask sub-experiment was similar to that in Experiment 1: workers
+perform a set of five initial tasks, whose images depend on the treatment
+to which they were assigned, and then perform the test tasks, which are
+common not only to both intertask treatments, but to both treatments of 
+all sub-experiments.  In the food treatment, initial tasks contained
+images of food.  This time, care was taken to exclude any non-food items, 
+such as utensils or place-settings, except, in some cases, for the plate
+supporting the food itself.  In the objects treatment, initial tasks 
+contained images depicting table settings and various non-food objects one 
+might find in a kitchen, but no food is shown.  Images in the test tasks,
+which, again, are the same for both treatments,
+depict both food and non-food objects together.
+
+In contrast to Experiment 1, we performed five replicates of the intertask
+sub-experiment, each time permuting the test tasks.  The test tasks were
+``rotated'' in such a way that, what was the first test task became
+the second, the second became the third, and so on up until the last test
+task, which became the first.  In this way, each of the five positions
+was occupied by each test task, enabling us to disentangle the effect of
+test task position (relative to initial tasks) from test task content,
+and thereby see how intertask effects vary as a function of position.
+
+The framing sub-experiment was similar to that from Experiment 1, except
+that we omitted initial tasks altogether, so that the test tasks followed
+immediately after framing.  This meant that workers would not have 
+performed any tasks by the time they begin the test tasks.  While that will
+hold constant for both framing treatments, and thus not produce a 
+differential effect, the workers may be more (or less) susceptible to 
+influences during their first few tasks.  One can expect framing effects
+to be stronger than in Experiment 1, because of the immediacy with which
+the test tasks follow the framing.  The framing slide for the food 
+treatment read ``Funded by the laboratory for the visual perception of 
+Food and Ingredients'', and for the objects treatment it read ``\ldots
+perception of Objects and Tools''.
+
+We introduced the echo sub-experiment to produce the strongest framing 
+effects.  This sub-experiment was similar to the framing sub-experiment,
+but differed in two ways.  First, the framing language stated an explicit
+purpose for the study: ``The purpose of this study is to understand the 
+visual perception of Food and Ingredients'' 
+and ``\ldots of Objects and Tools''.  Second, before moving past the
+framing slide, workers were asked what the purpose of the study was, and
+had to respond by selecting one of the two statements from among a short
+list in a combo-box.  It is because workers had to echo the framing 
+statement using a combo-box that we call this sub-experiment ``echo''.
+
+\subsection{Results}
+
+%\begin{table}[b!]
+%\small
+%\centering
+%\setlength{\tabcolsep}{1pt}
+%\begin{tabular}{c c c c c}
+%\toprule
+%Experiment & \parbox[c]{3.0cm}{\centering{Priming modality}} & Initial Tasks & Frame \\
+%\midrule
+%\multirow{2}{*}{\textit{intertask-food-objects}} 
+%& \multirow{2}{*}{initial tasks} & \textit{food} & none \\
+%  & & \textit{objects} & none  \\
+%
+%\noalign{\smallskip}
+%\hdashline
+%\noalign{\smallskip}
+%
+%\multirow{2}{*}{\textit{frame-food-objects}} 
+%& \multirow{2}{*}{framing} & none 
+%	& ``food''\textsuperscript{a} \\
+%& & none 
+%	& ``objects''\textsuperscript{b} \\
+%
+%\noalign{\smallskip}
+%\hdashline
+%\noalign{\smallskip}
+%
+%\multirow{2}{*}{\textit{echo-food-objects}} 
+%& \multirow{2}{*}{echoed framing} & none
+%	& ``food''\textsuperscript{c} \\
+%& & none & ``objects''\textsuperscript{d} \\
+%
+%\noalign{\smallskip}
+%\hdashline
+%\noalign{\smallskip}
+%
+%\multirow{2}{*}{\textit{intertask-food-culture}} 
+%& \multirow{2}{*}{initial tasks} & \textit{food} 
+%	& none \\
+%& & \textit{culture} 
+%	& none \\
+%
+%\noalign{\smallskip}
+%\hdashline
+%\noalign{\smallskip}
+%
+%\multirow{2}{*}{\textit{frame-food-culture}} 
+%& \multirow{2}{*}{framing} & \textit{food} 
+%	& ``food''\textsuperscript{e} \\
+%  & & \textit{food}
+%	& ``culture''\textsuperscript{f} \\
+%
+%\bottomrule
+%\end{tabular}
+%\caption{
+%	Description of experiments performed.  Each experiment had two treatments
+%	which differed either in the initial tasks shown or the framing used 
+%	(the priming modality).  
+%	During echoed framing, the worker had to respond to the framing language
+%	using a combo box input.  The framing language used was as follows:
+%	\newline\textsuperscript{a} ``Funded by the laboratory for the visual 
+%		perception of Food and Ingredients''
+%	\newline\textsuperscript{b} ``Funded by the laboratory for the visual 
+%		perception of Objects and Tools''
+%	\newline\textsuperscript{c} ``The purpose of this study is to understand the visual perception of Food and Ingredients''
+%	\newline\textsuperscript{d} ``The purpose of this study is to understand the visual perception of Objects and Tools''
+%	\newline\textsuperscript{e} ``This research is proudly funded by The National 
+%		Foundation for Nutritional Awareness''
+%	\newline\textsuperscript{f} ``This research is proudly funded by The Global 
+%		Foundation for the Recognition of Cultures''
 %}
-(Figure~\ref{fig:task}F).
-
-Results for this experiment again showed a 
-strong bias as a result of intertask effects (51.3\%) 
-(Figure~\ref{fig:theta}A).  Again, visualizing the word frequencies 
-themselves is difficult, but Figure~\ref{fig:l1_example} provides an 
-example of distributions having $\theta = 50\%$.
-
-Once again, we compared the strength of intertask effects to those due to 
-framing. In the experiment \textit{frame-food-culture} we used
-the same test tasks as in \textit{intertask-food-culture}, but before
-workers began the tasks, we indicated
-that the purpose of the task was either the recognition of food or 
-culture, depending on the treatment to which the worker was assigned.  
-However, unlike in the previous framing experiment, this time we also 
-included initial tasks in the framing experiment (although they were 
-identical for both treatments).  We did this in order to include a pair of
-comparable priming- and framing-based experiments
-for which both had the same overall number of tasks.
-In \textit{frame-food-culture}, framing did not induce 
-significant changes in word frequencies 
-(by $\chi^2$ test, $p=0.29$) (Figure~\ref{fig:theta}A).
-
-It was only when framing was combined with an active reiteration step, 
-that framing-induced bias reached a comparable extent to that induced by 
-intertask effects.  In the experiment \textit{echo-food-objects},
-after framing the purpose of the task (as the recognition of food
-or objects), workers were asked to echo the purpose of the task
-using a combo-box input.  This  ``echoed framing'' induced a bias of 
-36.1\% (Figure~\ref{fig:theta}A). However, it is difficult to say whether this 
-should be considered as a framing treatment \textit{per se}:
-requiring the worker to reiterate the purpose signals our intent, as the 
-requester, to ensure that the worker has taken note of it, possibly leading 
-the worker to interpret the exchange as an instruction.  
-In any case, it is remarkable that intertask effects
-were on par with an explicit, actively reinforced statement of the tasks' 
-purpose.
+%\label{table:experiments}
+%\end{table}
+
+\paragraph{Existence and strength of effects.}
+The frequencies of words used by
+workers in the \textit{food} and \textit{objects} treatments differed
+significantly during test tasks ($p = 6.0 \times 10^{-14}$).  Based on
+the performance of a naive Bayes classifier, the strength of the effect 
+was (as a lower bound) $\theta=30.6\%$ total variational distance
+(Figure~\ref{fig:theta}A).  Again, it is difficult to visualize the 
+distributions of word frequencies, but for reference, the distributions 
+shown in Figure~\ref{fig:l1_example}B have $\theta = 30\%$.
+
+This time, the framing sub-experiment also showed a significant effect.
+Framing induced changes in the frequencies of word usage at significance 
+(as determined by $\chi^2$ test; $p=0.0012$).  However, 
+the \textit{extent} of the effect could not be distinguished from zero
+($p =0.37$) based on the performance of a naive Bayes classifier 
+(Figure~\ref{fig:theta}A).
+As in Experiment 1, the effect due to prior tasks was still stronger than 
+that due to framing ($p=2.1\times 10^{-5}$).
+
+It was only when in the echo sub-experiment 
+that framing effects were on par with intertask effects.  
+In this sub-experiment, framing influenced workers responses ($p=1.3\times10^{-8}$), and the performance of a naive Bayes classifier showed that 
+it produced (lower bound) 36.1\% total variational distance in worker
+responses (Figure~\ref{fig:theta}A).  This effect is on-par with the
+effect produced by prior tasks ($p=0.79$).
+
+It is remarkable that intertask effects were on par with an explicit, 
+actively reinforced statement of the tasks' purpose.
+Requiring the worker to reiterate the purpose signals our intent, as the 
+requester, to ensure that the worker has taken note of it, 
+possibly leading the worker to interpret the exchange as an instruction.  
+Yet, the strength of the effect was equivalent to that of the worker having
+started with different initial tasks.
+
+\paragraph{Persistence of intertask effects.} 
+Taking advantage of the replicated intertask sub-experiment, we created
+a naive Bayes classifier for each task, when found at each test task 
+position.  Thus, for each of the five test task positions, we obtained 
+five separate measures of the intertask effect strength (one for each of 
+the test tasks when occupying that position).  We averaged these five 
+measurements to produce the final intertask effect strength for the task
+position, as shown in Figure~XX.
+
+Not surprisingly, the first test task shows the strongest intertask 
+effects, at 28.1\% total variational distance.  The effect appears to 
+drop suddenly after the first test task, but remain significant 
+right through until the fifth task position ($p=0.030$).
+Remarkably, even after four intervening tasks, the effect of 
+having performed different initial tasks shifts worker's responses to the
+fifth test task by 12.4\% total variational distance.
 
@@
 
-{\bf Inter-task effects and concept activation.} To better understand the nature of 
-intertask effects, we investigated the vocabulary
-that workers used to label test tasks. One might expect that, within a given 
-experiment, those workers exposed to food (whether through framing or initial
+\paragraph{Intertask effects and concept activation.} 
+To gain further insight into the nature of intertask effects, 
+we investigated the vocabulary that workers used to label test tasks. 
+One might expect that, within a given experiment, those workers exposed 
+to food (whether through framing or initial
 tasks) would label test tasks using 
@@
 To improve the coverage of words for
-less widespread foods, we augmented this set with all words
+less common foods, we augmented this set with all words
 discovered while crawling the World Food section of \url{allrecipes.com} 
@@
 use more food-words when labeling images in the test tasks.
-In \textit{intertask-food-culture}, food-exposed
-workers actually used significantly\footnote{
+In the intertask treatment of Experiment 1, workers from the food treatment
+actually used significantly\footnote{
   Frequencies of food references within a treatment were calculated as
@@
 rules out a seemingly-simple idea that workers emphasize
-content that has been present in earlier tasks: seeing content 
-significantly influences, but does not necessarily 
-\textit{increase}, the probability of referring to it in subsequent tasks.
+content seen in earlier tasks.  Seeing given content does significantly 
+influence workers' propensity to refer to it in subsequent tasks, but it 
+does not necessarily \textit{increase} it.
 
 To deepen our understanding, we investigated workers' lexical richness in 
-reference to food, that is, the number of \textit{unique} food-related words
-used.  Even if workers provide an abundance of food-related words, there
-can be less diversity, if, for example, workers repeat generic references 
-to food.
-Both \textit{intertask} experiments showed that food-exposed workers had 
+reference to food, that is, the number of \textit{unique} food-related 
+words used.  Even if workers provide an abundance of food-related words, 
+there can be less diversity, if, for example, workers repeat generic 
+references to food.
+The \textit{intertask} sub-experiments from both Experiments 1 and 2 showed
+that workers from the food treatments had
 greater lexical richness, in reference to food, than their counterparts 
 (as much as 20\% more) (Figure~\ref{fig:specificity}B).  
-This is particularly noteworthy in the experiment
-\textit{intertask-food-culture}, because there,
-food-primed workers made fewer total references to food.  
-%We also observed enrichment of the food-related lexicon in the 
-%\textit{priming-food-objects}, and \textit{echo-food-objects} experiments, 
-%although to a lesser extent.
+This is particularly noteworthy for Experiment 1, because there,
+workers from the food treatment made fewer total references to food.  
+Thus, although prior task exposure does not necessarily increase the 
+propensity
+to identify content in later tasks, it does appear to activate concepts
+and related vocabulary regarding, pertaining to content in the prior tasks.
 
@@
 
-The observations regarding lexical richness suggest that 
-initial tasks might influence workers to use more refined or specialized 
-words, when referring to aspects of content that had been present in the 
-initial tasks.  
-To test this, we used the hypernym and hyponym relations in WordNet 
-to operationalize the notion of word specialization.  
-Within each experiment, we determined relative specificity
+The above observations regarding lexical richness, suggest that initial 
+tasks might influence workers to use more \textit{refined} or 
+\textit{specialized} words, when referring to aspects 
+of content that had been present in the initial tasks.  
+To test this directly, we used the hypernym and hyponym relations in 
+WordNet to operationalize the notion of word specialization.  
+Within each sub-experiment, we determined the relative specificity
 of the food-words, between the treatments using the following equation:
@@
 
-In all experiments except \textit{frame-food-culture}, food-primed workers 
-used significantly more specialized words, in reference to food 
+In all sub-experiments except for Experiment 1 framing sub-experiment, 
+workers from the food treatment used significantly more specialized words, 
+in reference to food 
 (about 15\% more; $p > 0.05$) (Figure~\ref{fig:specificity}C).
@@
 \section{Discussion}
-Our results can be 
-explained through a combination of positive and negative priming.
-Positive priming (usually simply ``priming'') occurs when a prior stimulus 
-predisposes a person to give certain responses in an ensuing task, and
-is often observed as an increase in the speed or accuracy of a response, or
-the ability to recognize briefer or noisier stimuli 
-\cite{BJOP1796,BJOP1826,Huber2008324}.
+Our results show that intertask effects exist, are very strong, and are
+on par with an explicit statement of a task's purpose reinforced by
+requiring the worker to repeat that purpose.  This very surprising 
+result immediately raises follow-on questions: what are the psychological
+mechanisms at play? How are other kinds of tasks (i.e. other than image 
+labeling) impacted by intertask effects?  How can intertask effects best 
+be used to produce optimal task design?  We expect these questions will
+be fruitfully explored in future work.
+
+While our setup does not allow us to tell what psychological mechanism(s) 
+are responsible for intertask effects, we suspect that priming is involved.
+It was the fact that microtasks create conditions conducive to priming 
+which first lead us to suspect intertask effects might exist.  
+Priming occurs when a prior stimulus causes a person to respond to a 
+subsequent task with ncreased speed or 
+accuracy of a response, or with the ability to recognize briefer or 
+noisier stimuli \cite{BJOP1796,BJOP1826,Huber2008324}.
+In the case of image labeling, pre-activation of 
+vocabulary relating to prior tasks, through a priming mechanism, 
+could lead to more rapid retrieval of those words in subsequent tasks.  
+Since a worker is likely to submit those words which enter her mind first, 
+priming could therefore lead these words to be prefered.  As the worker
+completes many tasks with a common theme, the worker's vocabulary relating
+to that theme will be increasingly activated, enabling more specialized
+words to be retrieved quickly, and therefore be submitted as responses.
+
+However, as we aluded to above, there appears to be countervailing factors:
+while richness and specialization always increased (or were not 
+significantly changed), the total number of references to content in 
+prior tasks was observed to significantly increase in some cases, but
+significantly decreased in another.  Here we suspect 
+\textit{negative} priming to be at play.
 Negative priming occurs when, after exposure to a stimulus 
 considered to be non-salient, subsequent recognition of the stimulus is 
-inhibited \cite{mayr2007negative}.
-
-Workers exposed to images containing food are (positively) primed, 
-activating memories, concepts, and vocabulary related to food.  
-However, if the worker labels several images containing food, the basic 
-fact that an image contains food will not seem salient, since it 
-does not distinguish one image from another.  Thus, the most 
-generic references to that fact, such as the label ``food'', 
-will be suppressed, while more specialized references will be elicited.  
-Meanwhile, the number of references to food overall might increase or 
-decrease, depending on the balance of these factors.
-
-More generally, we are suggesting that, even though workers are not 
-instructed to compare tasks in any way, prior tasks form a 
-context relative to which workers judge salience.  Thus, due to a combination 
-of negative and positive priming, a worker's focus 
-in repeated tasks tends to be directed away from generic, shared features, 
-toward specific and distinguishing ones.
-
-Prior to this study, little thought appears to have been given to
-earlier tasks as a priming vector for later tasks.
-But our findings show this is an important design consideration.  
-One recourse might be to randomize task ordering, a practice that is 
-commonly employed.  But the sheer extent of bias we observed suggests that 
-this will still admit a significant amount of noise.  
-Even chains of two or three similar tasks, which
-will not be reliably eliminated in random permutations, could lead
-to the levels of bias we observed in our experiments.
-Preferably, a deeper understanding of intertask effects might allow them
-to be properly controlled.
-
-Our findings also suggest that careful task engineering might leverage
-intertask effects to achieve greater quality and reproducibility in 
+inhibited \cite{mayr2007negative}.  In the case of our image labeling 
+tasks,
+repeated exposure to images depicting food may cause the worker to 
+stop using very generic references to food (as we observed for the words
+``food'', ``meal'', ``dinner'', see table XX), since the basic presence
+of food does not seem salient.  In other words, we are suggesting that
+workers may judge salience within a task relative to previous tasks,
+and that this might provide the inhibitory effect observed, via a negative
+priming mechanism.
+
+Prior to this study, it was not realized that earlier microtasks could 
+have such strong effects on later ones.
+But our findings show this is an important design consideration that 
+should be considered by anyone using microtask platforms.
+The commonly employed practice of randomizing task ordering probably
+introduces a significant amount of noise due to intertask effects:
+Even chains of two or three similar tasks, which will not be reliably 
+eliminated in random permutations, could lead to the levels of influence 
+we observed in our experiments.  Preferably, a deeper understanding of 
+intertask effects might allow them to be properly controlled.
+
+But perhaps more importantly, our findings show that intertask effects 
+might be leveraged achieve greater quality and reproducibility in 
 crowdsourcing.
@@
 their focus toward salient features \cite{kellman2009perceptual}.  
-Using strategic task exposure during training, 
-it might be possible to guide workers' focus 
-and salience attribution, enabling expert-level 
-judgment in a wider variety of
-crowdsourced applications.
+Using strategic task exposure during training, it might be possible to 
+guide workers' focus and salience attribution, enabling expert-level 
+judgment in a wider variety of crowdsourced applications.
+
+The discovery of intertask effects provides an exciting new advance
+in the quest to design reliable and reproducible tasks for human 
+computation.
 We anticipate future work will yield techniques to control intertask 
@@
 specificity of worker responses.
-
-We have shown that a severe bias can be introduced into microtask 
-responses, simply from the performance of earlier tasks. 
-These effects can be much stronger than those of framing.  
-While our findings raise serious concerns about the 
-current state of microtask design, they reveal potential opportunities 
-to refine worker focus and acuity.  Any application that relies
-on the repetitive use of human judgment is likely subject to the phenomena
-described here.  Exploring the pitfalls and opportunities posed by
-intertask effects is an important direction for future work, 
-in the effort to develop performant and reliable human computation.
 

### 2016-01-04 docs/publications/2015.12_CHI/man.tex
new version of manuscript -- first sheparding iteration

@@
 Using image-labeling, a canonical microtask format, we 
-discover that earlier tasks have a priming effect on the worker, shifting 
-the distribution of future responses by 30-50\% 
+show that earlier tasks can have a strong influence on responses to later 
+tasks, shifting the distribution of future responses by 30-50\% 
 (total variational distance). 
@@
 We call this phenomenon \textit{intertask effects}.
-We compare intertask effects to the overt framing, 
-effected by stating the requester's research interest, 
-and find that intertask effects are on par or stronger.
+We compare intertask effects to framing, effected by stating the 
+requester's research interest, and find that intertask effects are on 
+par or stronger.
 If uncontrolled, intertask effects could be a source of systematic bias, 
@@
 
-\keywords{Microtask; crowdsourcing; priming; task-design; bias; classifier}
+\keywords{Microtask; crowdsourcing; priming; framing; task-design; bias; classifier}
 
@@
 computational capabilities, by matching requesters, who need to have such 
-tasks completed, with human workers.  Amazon's Mechanical Turk\footnote{\url{mturk.com}}, and 
+tasks completed, with human workers.  Amazon's Mechanical Turk (MTurk)\footnote{\url{mturk.com}}, and 
 CrowdFlower\footnote{\url{crowdflower.com}} are two popular microtask 
@@
 prime is the same as the task.
-Thus, the typical microtask setup creates conditions in which
-the contents of earlier tasks could influence responses to later ones.
+Thus, for the typical microtask worker, who does many similar tasks in
+quick succession, there is a potential for earlier tasks to influence
+later ones, via priming or other mechanisms.
 
@@
 ``incorrect'' responses.  But many tasks involving qualitative judgment
-do not.  Rather than simply characterizing effects on accuracy, we seek
+do not.  So, rather than simply characterizing effects on accuracy, we seek
 to provide a generalized measure of the extent to which prior tasks
-can alter the distribution of responses to a task.  
-Measuring the \textit{extent} of the shift in response distribution, is 
-substantially harder than simply determining \textit{whether} an effect 
+can alter the distribution of responses to later tasks.  
+Measuring the \textit{extent} of the shift in a distribution of responses 
+is substantially harder than simply determining \textit{whether} an effect 
 has occurred.  Our first contribution is a statistically grounded method 
@@
 adopted
-image-labeling as a canonical microtask, in which workers provide 
+image-labeling as a canonical microtask, a task in which workers provide 
 descriptive labels to images using free-text inputs.  Image labeling is
 a qualitative task without clearly ``correct'' or ``incorrect'' responses,
-and is among the most common kinds of tasks on the major crowdsourcing
-platform Amazon's Mechanical Turk (see Table \ref{table:task_composition}).
+and is among the most common kinds of tasks on MTurk 
+(see Table \ref{table:task_composition}).
 If task-induced priming arises in our 
@@
 the same.  For example, in one experiment, the first five images shown to
-one group of workers contained food, while those shown to the other 
-contained (non-food) objects.  The last five images for both
-groups contained both food and objects.
+one group of workers contain food, while those shown to the other 
+contain (non-food) objects.  The last five images for both
+groups contain both food and objects.
 
@@
 
-As a point of comparison, our experiments included framing treatments, 
+As a point of comparison, we also conducted framing experiments, 
 in which we altered the framing of microtask assignments, in terms of the 
 stated purpose of the task, or by naming the funder.
-Remarkably, the effects of prior microtasks themselves,
+Remarkably, the effects of prior microtasks,
 which are virtually ubiquitous, are on par with, or stronger than, 
-overtly framing an assignment.
-
-We call the effects that earlier tasks exert on later ones 
-\textit{intertask effects}.  If, as has been suggested \cite{5543192}, 
-microtask platforms are to be considered as a new form of computing 
-architecture, it will be necessary to reconcile the fact that the human 
-computing elements exhibit \textit{hysteresis}, 
-meaning that microtask workers' outputs 
-depend on the \textit{history} of their inputs.
-
-Unraveling the psychological mechanisms that give rise to such strong 
-effects will require further investigation.  We describe a possible 
-mechanism based on positive and negative priming, consistent with the
-observations from our experiments.
-Irrespective of the underlying mechanism, this very strong effect might 
-be exploited in task design to tune worker focus and acuity.
-
-As our main contributions, we
-\begin{itemize}[noitemsep,nolistsep]
-  \item{
-	derive a method for measuring changes in response distributions;
-  }
-  \item{measure the influence of initial microtasks on later ones;}
-  \item{show this effect is stronger than, or on par with framing;}
-  \item{
-	show that when completing a series of similar microtasks,
-	worker's responses become more specialized and diverse;
-  }
-\end{itemize}
-
-The rest of the paper is organized as follows.  In the next section, we 
-review the relevant prior work.  We then present our method for 
-measuring changes to response distributions.
-Next we present our experimental results, followed by a discussion 
-of interpretations and ramifications for microtask-based and crowdsourced 
-work.  We conclude with suggestions for task design and future work.
-
-\section{Prior work}
-\subsection{Effects of microtask design on response quality}
-% Accuracy, reproducibility, and a controlled task environment are 
-% important
-Microtask platforms are increasingly used to clean and codify datasets,
-administer experiments with human participants, and distribute 
-surveys.  Accuracy and replicability are crucial in all of these 
-applications.
+the effects of overtly framing an assignment.
 
@@
 
+We call the effects that earlier tasks exert on later ones 
+\textit{intertask effects}.  If, as has been suggested \cite{5543192}, 
+microtask platforms are to be considered as a new form of computing 
+architecture, it will be necessary to reconcile the fact that the human 
+computing elements exhibit \textit{hysteresis}, 
+meaning that microtask workers' outputs 
+depend on the \textit{history} of their inputs.
+
+Unraveling the psychological mechanisms that give rise to such strong 
+effects will require further investigation.  We describe a possible 
+mechanism based on positive and negative priming, consistent with the
+observations from our experiments.
+Irrespective of the underlying mechanism, this very strong effect might 
+be exploited in task design to tune worker focus and acuity.
+
+As our main contributions, we
+\begin{itemize}[noitemsep,nolistsep]
+  \item{
+	derive a method for measuring changes in response distributions;
+  }
+  \item{measure the strength of intertask effects;}
+  \item{show that intertask effects are stronger than,
+	or on par with framing;}
+  \item{
+	show that when completing a series of similar microtasks,
+	worker's responses become more specialized and diverse;
+  }
+\end{itemize}
+
+The rest of the paper is organized as follows.  In the next section, we 
+review the relevant prior work.  We then present our method for 
+measuring changes to response distributions.
+Next we present our first experiment which measures intertask effects and
+compares them to framing. We then describe a second experiment which 
+extends these results, addressing questions raised by the first experiment.
+We conclude by discussing interpretations and ramifications, suggesting
+a possible mechanism for intertask effects based on priming, and
+describing directions for future work.
+
+\pagebreak
+\section{Prior work}
+\subsection{Effects of microtask design on response quality}
+% Accuracy, reproducibility, and a controlled task environment are 
+% important
+Microtask platforms are increasingly used to clean and codify datasets,
+administer experiments with human participants, and distribute 
+surveys.  Accuracy and replicability are crucial in all of these 
+applications.
+
 % These things are definitely not assured, and people have tried to 
@@
 when a task was framed as assisting with medical research,
-workers are more likely to participate and completed more tasks, than
+workers were more likely to participate and completed more tasks, than
 when they were not provided any context \cite{chandler2013breaking}.
@@
 % effects of task interruption
-Perhaps the most similar study to the work we describe here 
-investigated the effects of interruptions on task performance
+Other work investigated the effects of interruptions on task performance
 \cite{laseckieffects}.  There, workers 
@@
 effects on the quality of responses.
-%\cite{kreifeldt1981interruption}
-
-Taken together, the prior work suggests that, beyond the design
-of tasks themselves, the design of the context of tasks has a major
-effect on responses.
-However, the potential of earlier tasks to act as primes for later ones 
-has not been adequately investigated.
+
+In a somewhat related vein, other researchers investigated 
+the effects of task-switching \cite{yin2014monetary}.  During 
+\textit{switch-tasks} (tasks which differ in nature from the immediately 
+preceeding task), workers were more inclined to make mistakes, 
+and took longer to complete the task.  
+However, the reserchers found that by offering a performance-based
+bonus, which paid if workers completed the task quickly and correctly,
+performance during switch-tasks was both faster and more accurate.
+
+However, long periods of performing the same task can lead to fatigue,
+which can be relieved by well placed-interruptions.  A study 
+\cite{dai2015and} found that introducing ``micro-diversions'' 
+periodically between tasks caused workers to complete more tasks overall, 
+and to complete them more quickly.  This was more pronounced for more 
+cognitively taxing tasks.
 
@@
 As we have mentioned, workers prefer to perform a series of tasks that
-are similar to one another.
-Moreover, many 
+are similar to one another.  Moreover, many 
 microtasks involve tasks based on visual and auditory perception 
@@
 Thus, in a typical microtask assignment, there are many opportunities for 
-priming, the effects of which should be explored.
+priming to arise.
+
+Researchers have begun to explore the potential 
+applications of priming in microtask design.  One study found that 
+showing workers an image of a laughing baby (so as to stimulate positive
+affect), led to better performance in a task requiring creativity
+\cite{lewis2011affective}.  This shows that priming effects can play a 
+role in microtask design.  The question we seek to answer, however, is 
+whether earlier tasks can affect responses to later tasks.
+
+Taken together, the prior work suggests that, beyond the design
+of tasks themselves, the design of the context of tasks has a major
+effect on responses.  There is reason to believe that, even in a series
+of similar tasks, earlier microtasks may influence later ones, such as
+through a priming mechanism.  However, no direct investigation of whether 
+this phenomenon exists has yet been made, which is the goal of the present 
+work.
 
@@
   Other formulations such as the Kullback-Leibler and 
-  Jensen-Shannon divergence can be calculated from the total variational
+  Jensen-Shannon divergence can be related to the total variational
   distance.
@@
 	  	Normal distributions exhibiting a total variational distance
-		of A) 50\% and B) 30\%.  The total variational distance is 
+		of (A) 50\% and (B) 30\%.  The total variational distance is 
 		the non-overlapping portion of the distributions, e.g. in
-		A) it is given by 
+		(A) it is given by 
 		$\theta = a_1 / (a_1 + a_2) = a_3 / (a_2 + a_3)$.
@@
 an identical Zipf distribution\footnote{The 
-  Zipf distribution is a common model for word frequencies 
+  Zipf distribution is a model for word frequencies 
   \cite{powers1998applications,zipf1949human}:
@@
 \end{equation}
-where $\theta$ is the divergence between the distributions of responses
+where $\theta$ is the total variational distance between the 
+distributions of responses
 to $\mathrm{design}_1$ and $\mathrm{design}_2$.
+
+\begin{figure*}
+	\centering
+	\includegraphics[scale=0.60]{figs/images.png}
+	\caption{
+		Examples of images used in
+		initial tasks for the (\textbf{A}) \textit{food} and (\textbf{B}) 
+		\textit{objects} treatments of \textit{intertask-food-objects};
+		(\textbf{C}) test tasks for \textit{intertask-food-objects} and 
+		\textit{frame-food-objects};
+		initial tasks for the (\textbf{D}) \textit{food} and (\textbf{E}) 
+		\textit{culture} treatments of \textit{intertask-food-culture};
+		and (\textbf{F}) test tasks for \textit{intertask-food-culture} and 
+		\textit{frame-food-culture}.
+	}
+
+	\label{fig:task}
+\end{figure*}
 
@@
 $\mathrm{design}_1$ or $\mathrm{design}_2$ with equal probability.
-If the worker gives the response $x$, it is optimal to guess
+If the worker gives the response $x$, the opitimal classifier must guess
 that the worker was shown the design most likely to elicit $x$.
@@
 
-\begin{figure*}
-	\centering
-	\includegraphics[scale=1.0]{figs/images.jpg}
-	\caption{
-		Examples of images used in
-		initial tasks for the (\textbf{A}) \textit{food} and (\textbf{B}) 
-		\textit{objects} treatments of \textit{intertask-food-objects};
-		(\textbf{C}) test tasks for \textit{intertask-food-objects} and 
-		\textit{frame-food-objects};
-		initial tasks for the (\textbf{D}) \textit{food} and (\textbf{E}) 
-		\textit{culture} treatments of \textit{intertask-food-culture};
-		and (\textbf{F}) test tasks for \textit{intertask-food-culture} and 
-		\textit{frame-food-culture}.
-	}
-
-	\label{fig:task}
-\end{figure*}
-
-\begin{figure}[t]
-	\includegraphics[scale=0.75]{figs/theta.pdf}
-	\caption{
-		Empirical bias, $\theta_\mathrm{NB}$, measured using a naive Bayes 
-		classifier, induced in image-labeling tasks, due to workers' 
-		exposure to framing and prior tasks.  
-		(\textbf{A}) Exposing workers to initial tasks induced more severe
-		bias than framing, except when echoed framing was used. 
-		(\textbf{B}) As workers proceeded through test tasks, 
-		the bias due to initial tasks waned, 
-		but remained significant even after five tasks.  
-		Standard error bars are shown.
-	}
-	\label{fig:theta}
-\end{figure}
-
 The first experiment we performed consisted of two sub-experiments which
@@
 designed to measure intertask and framing effects.  The experiment was 
-performed on Amazon's Mechanical Turk (MTurk) using 476 workers.  Workers
+performed on MTurk using 476 workers.  Workers
 could only participate once in a given experiment, and could only 
@@
 required the worker to assign five descriptive labels to an image.  
-In all cases, the last five tasks were 
-identical, and were presented in the same order.  
+In all cases, the last five tasks were identical among all treatments 
+(and across sub-experiments), and were presented in the same order.  
 These last five tasks constituted the ``test tasks'', whose distribution
@@
 workers based on the treatment.  Workers assigned to the ``food'' 
-treatment were shown images of food, while workers assigned to the 
-``culture'' treatment were shown other kinds of cultural depictions, such
-as dance, sport, and music\footnote{We do not assert that cultural 
-practices can be cleanly separated into food-related and non-food related 
-ones; that is not necessary for our analysis.}.  
+treatment were shown images of food (see Figure~\ref{fig:task}A), 
+while workers assigned to the ``culture'' treatment were shown other kinds 
+of cultural depictions, such as dance, sport, and 
+music\footnote{
+  We do not assert that cultural practices can be cleanly separated into 
+  food-related and non-food related ones, nor is a strict division 
+  necessary for our analysis.
+} (see Figure~\ref{fig:task}B).  
 However, within a given treatment, workers were shown the same images in
@@
 from both treatments then performed the same five test tasks.  The test
-tasks consisted of images depicting meals of diverse ethnic origin.
+tasks consisted of images depicting meals of diverse ethnic origin
+(see Figure~\ref{fig:task}C).
 From the perspective of the worker, there was no distinction between the 
@@
 Nutritional Awareness'', or ``\ldots by the Global Foundation for the 
-Recognition of Cultures''.  The intention here was to frame the task by
-providing the name of a (fictitious) funder, and using names that
+Recognition of Cultures''.  The intention was to frame the task by
+providing the name of a (fictitious) funder, while using names that
 invite the worker to focus on different aspects of the image content.  
@@
 
+\begin{figure}[t]
+    \centering
+	\includegraphics[scale=0.85]{figs/theta-exp1.pdf}
+	\caption{
+	    Lower bound total variational distance ($\theta_\mathrm{NB}$) 
+		between responses given
+		by workers on test tasks in Experiment 1, when they have been 
+		shown different initial tasks (intertask), or been exposed to
+		different framing (framing), as determined using naive Bayes 
+		classifiers.  Standard error bars are shown.
+	}
+	\label{fig:theta-exp1}
+\end{figure}
+
 \paragraph{Existence of intertask and framing effects.} 
-Looking at the frequencies with which workers use words, we tested for
+Looking at the frequencies with which workers used words, we tested for
 heterogeneity between the two treatments of each sub-experiment.
-For the intertask sub-experiment, we found the distribution of responses 
-for the two treatments differed significantly ($p=?$), 
+For the intertask sub-experiment, we found the responses 
+for the two treatments differed significantly 
+(by $\chi^2$ test, $p<0.001$), 
 demonstrating that intertask effects do exist.  However, we did not find 
-significant effects due to framing, however (by $\chi^2$ test, $p=0.29$) 
+significant effects due to framing ($p=0.29$) 
 (Figure~\ref{fig:theta}A).
@@
 treatment (with $p > 0.3$ for all treatments and $p > 0.8$ for most).
-These results hold for Experiment 2 as well, to be discussed later.
-Thus, the heterogeneity we observed \textit{between} treatments is 
-meaningful.
+These results hold for Experiment 2, to be discussed later.
+Thus, the heterogeneity we observed \textit{between} the intertask 
+treatments indicates a meaningful effect.
 
@@
 Having affirmed the \textit{existence} of intertask effects, we sought to
-measure the strength of the effect, i.e. $\theta$.
+measure their strength, i.e. $\theta$.
 To measure $\theta$ we created a naive Bayes classifier based on a 
@@
 undertaken for pragmatic reasons \cite{Zhang2004562}, 
-is probably a mild in 
+is probably mild in 
 relation to image labels, since they are likely to be less dependent
@@
 
-To produce word frequency features, worker's labels were split on white
+To produce word frequency features, worker-submitted labels were split on 
+white
 space and punctuation, and the resulting tokens were spell-corrected based
@@
 
-Based on the performance of the classifier, intertask effects generated
-51.3\% total variational distance (Figure~\ref{fig:theta}A).  
-Visualy comparing two word frequency distributions is difficult, but 
+Based on the performance of the classifier, intertask effects altered
+workers' responses, leading to (a lower bound of) 51.3\% total variational 
+distance in their response distributions (Figure~\ref{fig:theta-exp1}).  
+This represents a remarkably strong effect.
+Visually comparing two word frequency distributions is difficult, but 
 Figure~\ref{fig:l1_example} provides an example of distributions having 
-$\theta = 50\%$.  In contrast to intertask effects, the effect due to 
-framing, was not significantly different from zero 
-(Figure~\ref{fig:theta}A).
-And so, the effect framing was weaker than that due to prior tasks 
-($p=7.6\times 10^{-7}$)\footnote{To compare bias
-  due to framing and intertask effects, we approximated the distribution
+$\theta = 50\%$.  In contrast, the effect due to framing, was not 
+significantly different from zero (Figure~\ref{fig:theta-exp1}).
+And so, intertask effects were stronger than the effects due to 
+framing ($p<0.001$)\footnote{
+  To compare framing and intertask 
+  effects, we approximated the distribution
   of correct classifications as a normal distribution, and performed
-a (two-tailed) two-proportion $z$-test.}.
-In other words, the \textit{microtasks themselves}
-had a stronger effect than framing.
+  a (two-tailed) two-proportion $z$-test.
+}.
+In other words, the \textit{microtasks themselves} had a stronger effect 
+than framing.
 
@@
 the result will replicate using different sets of images.  
-If they do, then the next question is how intertask effects evolve
+If so, then as the next question, we may ask how intertask effects evolve
 as the worker performs tasks.  Presumbaly, intertask effects wear off at 
@@
 modulate the extent to which it can be influenced by intertask effects.
-We cannot disentangle the question of task proximity from image content
-in the results for Experiment 1.
+We cannot disentangle the effects of task position from that of image 
+content in Experiment 1.
 
@@
 effects that remain.  In the next experiment, we measure framing effects 
-immediately after onset of framing.
-
+immediately after the application of framing.
+
+\pagebreak
 \section{Experiment 2}
 \subsection{Setup}
-In Experiment 2 we again have ``intertask'' and ``framing'' 
-sub-experiments, but we include a third sub-experiment, ``echo'', which 
-incorporates more extreme framing treatments.  
-As before, each sub-experiment has
-two treatments, but this time they are ``food'' and ``objects''.
-Keeping a food treatment enables us to perform deeper lexical analysis of 
+In Experiment 2 we again had ``intertask'' and ``framing'' 
+sub-experiments, but we included a third sub-experiment, ``echo'', which 
+incorporated more extreme framing treatments.  
+As before, each sub-experiment had
+two treatments, but this time they were ``food'' and ``objects''.
+Keeping a food treatment enabled us to perform deeper lexical analysis of 
 both experiments (discussed in the results for Experiment 2).  
@@
 The intertask sub-experiment was similar to that in Experiment 1: workers
-perform a set of five initial tasks, whose images depend on the treatment
-to which they were assigned, and then perform the test tasks, which are
-common not only to both intertask treatments, but to both treatments of 
-all sub-experiments.  In the food treatment, initial tasks contained
-images of food.  This time, care was taken to exclude any non-food items, 
+performed a set of five initial tasks, whose images depended on the 
+treatment to which they had been assigned, and then performed the test 
+tasks, which were common to both intertask treatments (as well as to both 
+treatments of the other sub-experiments in Experiment 2).  
+In the food treatment, 
+the initial tasks contained images of food (see Figure~\ref{fig:task}D).  
+This time, care was taken to exclude any non-food items, 
 such as utensils or place-settings, except, in some cases, for the plate
@@
 contained images depicting table settings and various non-food objects one 
-might find in a kitchen, but no food is shown.  Images in the test tasks,
-which, again, are the same for both treatments,
-depict both food and non-food objects together.
+might find in a kitchen, but no food (see Figure~\ref{fig:task}E).  
+The images in the test tasks,
+depicted both food and non-food objects together 
+(see Figure~\ref{fig:task}F).
 
@@
 effects.  This sub-experiment was similar to the framing sub-experiment,
-but differed in two ways.  First, the framing language stated an explicit
+but differed in two ways.  First, the framing slide stated an explicit
 purpose for the study: ``The purpose of this study is to understand the 
@@
 framing slide, workers were asked what the purpose of the study was, and
-had to respond by selecting one of the two statements from among a short
+had to respond by selecting the framing statement from among a short
 list in a combo-box.  It is because workers had to echo the framing 
@@
 \subsection{Results}
+
+\begin{figure}[t]
+    \centering
+	\includegraphics[scale=0.85]{figs/theta-exp2.pdf}
+	\caption{
+	    (\textbf{A}) Lower bound total variational distance 
+		($\theta_\mathrm{NB}$), between 
+		responses given to test tasks in experiment 2 
+		when workers were shown different initial tasks (intertask), 
+		or were exposed to different framing treatments (framing), or 
+		echoed framing treatments (echo).
+		(\textbf{B}) Detail of the effects seen from showing
+		workers different initial tasks (corresponding to intertask in 
+		panel A), now broken out for each of the five test task positions.
+		As workers proceeded through test tasks, intertask effects waned
+		but remained significant ($p<0.05$) even for the fifth test task.
+		Standard error bars are shown.
+	}
+	\label{fig:theta}
+\end{figure}
 
@@
 \paragraph{Existence and strength of effects.}
-The frequencies of words used by
-workers in the \textit{food} and \textit{objects} treatments differed
-significantly during test tasks ($p = 6.0 \times 10^{-14}$).  Based on
+As in the previous experiment, intertask effects led to significant 
+changes in the words workers used to labele images in the intertask 
+sub-experiment ($p<0.001$).  Based on
 the performance of a naive Bayes classifier, the strength of the effect 
 was (as a lower bound) $\theta=30.6\%$ total variational distance
-(Figure~\ref{fig:theta}A).  Again, it is difficult to visualize the 
+(see Figure~\ref{fig:theta}A).  Again, it is difficult to visualize the 
 distributions of word frequencies, but for reference, the distributions 
@@
 (Figure~\ref{fig:theta}A).
-As in Experiment 1, the effect due to prior tasks was still stronger than 
-that due to framing ($p=2.1\times 10^{-5}$).
-
-It was only when in the echo sub-experiment 
-that framing effects were on par with intertask effects.  
-In this sub-experiment, framing influenced workers responses ($p=1.3\times10^{-8}$), and the performance of a naive Bayes classifier showed that 
-it produced (lower bound) 36.1\% total variational distance in worker
-responses (Figure~\ref{fig:theta}A).  This effect is on-par with the
-effect produced by prior tasks ($p=0.79$).
+As in Experiment 1, we found that intertask effects were stronger than
+framing effects ($p<0.001$).
+
+It was only in the echo sub-experiment that framing effects were on par 
+with intertask effects.  In this sub-experiment, framing influenced 
+workers responses ($p<0.001$), and the performance of a naive 
+Bayes classifier showed that it produced (lower bound) 36.1\% total 
+variational distance in worker responses (Figure~\ref{fig:theta}A).  The
+strength of effects due to echoed framing could not be distinguished
+from that of intertask effects ($p=0.79$).
 
@@
 possibly leading the worker to interpret the exchange as an instruction.
-Yet, the strength of the effect was equivalent to that of the worker having
-started with different initial tasks.
 
@@
 Taking advantage of the replicated intertask sub-experiment, we created
-a naive Bayes classifier for each task, when found at each test task 
-position.  Thus, for each of the five test task positions, we obtained 
+a naive Bayes classifier for each test task, when it occurs at each test 
+task position.  
+Thus, for each of the five test task positions, we obtained 
 five separate measures of the intertask effect strength (one for each of 
-the test tasks when occupying that position).  We averaged these five 
-measurements to produce the final intertask effect strength for the task
-position, as shown in Figure~XX.
+the test tasks, when occupying that position).  We averaged these five 
+measurements to produce the intertask effect strength for the given task
+position, and these values are shown in Figure~\ref{fig:theta}B.
 
@@
 	\centering
-	\includegraphics[scale=0.87]{figs/vocab_specificity.pdf}
+	\includegraphics[scale=0.87]{figs/specificity.pdf}
 	\caption{
-		Exposing workers to a priming concept, e.g. food, through
-		initial tasks or framing, affects their tendency to focus
-		on that concept, and the richness and specialization of their 
-		vocabulary in reference to it.
+		Workers exposed to food (either in framing or initial tasks)
+		show a different tendency to focus on food when labeling
+		test tasks, and their vocabulary in reference to food is affected.
 		In all three plots, positive values indicate a larger quantity for 
-		the food-exposed workers.
+		workers from the food treatment.
 		(\textbf{A}) Exposing workers to food does not necessarily increase
-		the fraction food references they provide during test tasks.
+		the fraction of food references they provide during test tasks.
 		(\textbf{B}) The number of unique food-related
-		words (richness) was greater for food-exposed workers, except in the 
-		case of \textit{frame-food-culture} (stars indicate the threshold
+		words (richness) was greater for food-exposed workers, 
+		except in the 
+		case of the framing sub-experiment of Experiment 1 
+		(stars indicate the threshold
 		for a significant deviation, $\alpha=0.05$). 
@@
 		workers used more specialized words to refer to food.
-		Standard error bars are shown in (\textbf{A} and \textbf{C}).
+		Standard error bars are shown in (\textbf{A}) and (\textbf{C}).
 	}
@@
 				\centering
-					\textit{intertask-food-objects}
+			Exp. 1 intertask} 
+		}\\
+		\midrule
+		spicy & 26 \\
+		sauce & 17 \\
+		indian & 15 \\
+		buffet & 14 \\
+		exotic & 12 \\
+		festival & -11 \\
+		offering & -12 \\
+		statue & -15 \\
+		india & -20 \\
+		food & -56 \\
+		\bottomrule
+		\end{tabular}
+
+&
+
+		\setlength{\tabcolsep}{4pt}
+		\begin{tabular}{ r | c }
+		\toprule
+		\multicolumn{2}{c}{
+			\parbox[c]{2.5cm}{
+				\centering
+			Exp. 1 framing} 
+		}\\
+		\noalign{\smallskip}
+		\midrule
+		indian & 11 \\
+		banquet & 8 \\
+		spicy & 7 \\
+		asian & 6 \\
+		variety & 6 \\
+		delicious & -6 \\
+		meat & -7 \\
+		festival & -7 \\
+		spice & -7 \\
+		food & -9 \\
+		\bottomrule
+		\end{tabular}
+
+&
+
+		\setlength{\tabcolsep}{4pt}
+		\begin{tabular}{ r | c }
+		\toprule
+		\multicolumn{2}{c}{
+			\parbox[c]{2.5cm}{
+				\centering
+					Exp. 2 intertask
 			}} \\
@@
 				\centering
-				\textit{frame-food-objects}
+				Exp. 2 framing
 			}
@@
 				\centering
-			\textit{echo-food-objects}} 
+			Exp. 2 echo } 
 		}\\
@@
 
-&
-
-		\setlength{\tabcolsep}{4pt}
-		\begin{tabular}{ r | c }
-		\toprule
-		\multicolumn{2}{c}{
-			\parbox[c]{2.5cm}{
-				\centering
-			\textit{intertask-food-culture}} 
-		}\\
-		\midrule
-		spicy & 26 \\
-		sauce & 17 \\
-		indian & 15 \\
-		buffet & 14 \\
-		exotic & 12 \\
-		festival & -11 \\
-		offering & -12 \\
-		statue & -15 \\
-		india & -20 \\
-		food & -56 \\
-		\bottomrule
-		\end{tabular}
-
-&
-
-		\setlength{\tabcolsep}{4pt}
-		\begin{tabular}{ r | c }
-		\toprule
-		\multicolumn{2}{c}{
-			\parbox[c]{2.5cm}{
-				\centering
-			\textit{frame-food-culture}} 
-		}\\
-		\noalign{\smallskip}
-		\midrule
-		indian & 11 \\
-		banquet & 8 \\
-		spicy & 7 \\
-		asian & 6 \\
-		variety & 6 \\
-		delicious & -6 \\
-		meat & -7 \\
-		festival & -7 \\
-		spice & -7 \\
-		food & -9 \\
-		\bottomrule
-		\end{tabular}
-
 	\end{tabular}
 	\caption{
-		The five words whose frequencies increased, and those whose 
-		frequencies decreased, the most, between treatments of given 
-		experiments, within labels attributed to the first test task.
+		The five words whose frequencies as labels for the first test
+		task increased (or decreased) the most between treatments of the
+		given sub-experiments.
 		Values indicate the absolute change in number of occurrences
@@
 		food-exposed workers.
-		Word frequencies for 
-		\textit{intertask-food-objects} correspond to the labels attributed
-		to image 1 which is not necessarily the first 
-		test task due to the tasks being permuted.  There were five times
-		as many workers in \textit{intertask-food-objects}, hence
-		larger absolute differences are observed.
 	}
@@
 propensity
-to identify content in later tasks, it does appear to activate concepts
-and related vocabulary regarding, pertaining to content in the prior tasks.
+to identify content in later tasks, it does appear to activate vocabulary 
+pertaining to content in the prior tasks.
 
@@
 treatments, and $\mathbf{1}_{[w>v]}$ evaluates
-to 1 if synset $w$ is more specific than (i.e. is a hyponym of) synset $v$.
+to 1 if word $w$ is more specific than (i.e. is a hyponym of) word $v$.
 The relative specificity lies within $[-1,1]$; 
@@
 in reference to food 
-(about 15\% more; $p > 0.05$) (Figure~\ref{fig:specificity}C).
+(about 15\% more; $p < 0.05$) (Figure~\ref{fig:specificity}C).
 It is interesting that such substantial increases in both the lexical 
 richness and specialization of food-related words 
-held for \textit{intertask-food-culture}, where, as mentioned, we observed 
+held for the intertask sub-experiment of Experiment 1, where, as mentioned,
+we observed 
 that food-exposed workers made \textit{fewer} references to food overall. 
@@
 Our results show that intertask effects exist, are very strong, and are
-on par with an explicit statement of a task's purpose reinforced by
-requiring the worker to repeat that purpose.  This very surprising 
-result immediately raises follow-on questions: what are the psychological
-mechanisms at play? How are other kinds of tasks (i.e. other than image 
+on par with the effect of an explicit statement of a task's purpose 
+reinforced by requiring the worker to repeat that purpose.  
+This very surprising 
+result immediately raises follow-on questions for future work: 
+what are the psychological mechanisms at play? How are other kinds of 
+tasks (i.e. other than image 
 labeling) impacted by intertask effects?  How can intertask effects best 
@@
 are responsible for intertask effects, we suspect that priming is involved.
-It was the fact that microtasks create conditions conducive to priming 
-which first lead us to suspect intertask effects might exist.  
+As mentioned, we believe microtasks create conditions conducive to priming,
+and this is what first lead us to suspect intertask effects might exist.  
 Priming occurs when a prior stimulus causes a person to respond to a 
-subsequent task with ncreased speed or 
-accuracy of a response, or with the ability to recognize briefer or 
+subsequent task with increased speed or 
+accuracy, or with the ability to recognize briefer or 
 noisier stimuli \cite{BJOP1796,BJOP1826,Huber2008324}.
@@
 could lead to more rapid retrieval of those words in subsequent tasks.  
-Since a worker is likely to submit those words which enter her mind first, 
-priming could therefore lead these words to be prefered.  As the worker
+A worker may be more likely to enter those words which enter her mind 
+first, so priming could lead to certain words being prefered.  
+As the worker
 completes many tasks with a common theme, the worker's vocabulary relating
 to that theme will be increasingly activated, enabling more specialized
-words to be retrieved quickly, and therefore be submitted as responses.
+words to be retrieved quickly, and therefore to be submitted as responses.
 
@@
 significantly changed), the total number of references to content in 
-prior tasks was observed to significantly increase in some cases, but
-significantly decreased in another.  Here we suspect 
+prior tasks was observed to significantly increase in most cases, but
+it significantly decreased in one.  Here we suspect 
 \textit{negative} priming to be at play.
@@
 inhibited \cite{mayr2007negative}.  In the case of our image labeling 
-tasks,
-repeated exposure to images depicting food may cause the worker to 
-stop using very generic references to food (as we observed for the words
-``food'', ``meal'', ``dinner'', see table XX), since the basic presence
-of food does not seem salient.  In other words, we are suggesting that
-workers may judge salience within a task relative to previous tasks,
-and that this might provide the inhibitory effect observed, via a negative
-priming mechanism.
+tasks, repeated exposure to images depicting food may cause the worker to 
+stop regarding the basic presence of food as salient, and direct their 
+attention instead to the features that are specific to the food in a given 
+image.  This could lead the worker to suppress very generic references to 
+food (as we observed for the words ``food'', ``meal'', ``dinner'', see 
+Table~\ref{table:top-words}).  This could hold even when, due to positive
+priming, more specialized food-related words are activated.
+The balance of these factors would determine whether the worker makes 
+more references to food overall.  This would explain the paradoxical
+changes in number of references to food, along with the observed 
+changes to the richness and specificity of workers' food-related 
+vocabulary.
 
@@
 
-The discovery of intertask effects provides an exciting new advance
+Intertask effects are a new basic discovery
 in the quest to design reliable and reproducible tasks for human 

### 2016-01-04 src/analysis_utils.py

@@ -1,0 +1,171 @@
+import numpy as np
+import util
+
+CONFIDENCE_95 = 1.96
+CONFIDENCE_99 = 2.975
+
+def prob_k_successes(n,k,p=0.5):
+	return util.choose(n,k) * (p**k)*(1-p)**(n-k)
+
+def get_k_star(n, alpha):
+
+	k = n
+	prob_tot = prob_k_successes(n,k)
+	k_star = None
+
+	while prob_tot < alpha:
+		k_star = k
+		k -= 1
+		prob_tot += prob_k_successes(n,k)
+
+	return k_star
+
+def get_theta_star(n, alpha):
+	k_star = get_k_star(n,alpha)
+	return 2 * k_star / float(n) - 1
+
+
+def binomial_confidence_intervals(
+		n,k,alpha=0.05, tolerance=1e-6, as_theta=False
+	):
+	'''
+		Gets both the upper and lower confidence intervals for 
+		the single-experiment probability of success, for a binomial
+		variable sampled n times, observed to have k succeses, according 
+		to significance level alpha.  The numerical error on the calculation
+		(not the statistical error mind you) is given by tolerance.
+		as_theta controls whether to return the results as the probability
+		of success (p) or as theta = 2p-1
+	'''
+	try:
+		upper = binomial_upper_confidence_p(n,k,alpha, tolerance, as_theta)
+		lower = binomial_lower_confidence_p(n,k,alpha, tolerance, as_theta)
+
+	except OverflowError:
+		# get it from normal distribution
+		if alpha==0.05:
+			z = CONFIDENCE_95
+
+		elif alpha==0.15865:
+			z = 1.0
+
+		else:
+			raise NotImplementedError(
+				'this function currently only supports alpha=0.05 when the '
+				'sample size is large.  Youll need to code up something to '
+				'produce z-scores for non alpha=0.05 cases.'
+			)
+
+		std_dev = np.sqrt(
+			1/float(n)*(k/float(n))*(1-k/float(n))
+		)
+		upper = k/float(n) + z * std_dev
+		lower = k/float(n) - z * std_dev
+
+		if as_theta:
+			upper = 2*upper - 1
+			lower = 2*lower - 1
+
+	return upper, lower
+
+
+def binomial_upper_confidence_p(
+	n,k,alpha=0.05, tolerance=1e-6, as_theta=False):
[…]

### 2016-01-04 docs/publications/2015.12_CHI/man.tex
more revisions to manuscript (minor)

@@
 (see Table \ref{table:task_composition}).
-If task-induced priming arises in our 
-setup, it could be expected in a large number of microtasks and 
-crowdsourced workflows where workers are called upon to provide qualitative
-judgment.
+If effects from earlier tasks arise in our setup, similar effects could be 
+expected in 
+a large number of microtasks and crowdsourced workflows where workers are 
+called upon to provide qualitative judgment.
 
@@
 
-As a point of comparison, we also conducted framing experiments, 
-in which we altered the framing of microtask assignments, in terms of the 
+As a point of comparison, we also conduct framing experiments, 
+in which we alter the framing of microtask assignments, in terms of the 
 stated purpose of the task, or by naming the funder.
@@
 \textit{switch-tasks} (tasks which differ in nature from the immediately 
-preceeding task), workers were more inclined to make mistakes, 
+preceding task), workers were more inclined to make mistakes, 
 and took longer to complete the task.  
-However, the reserchers found that by offering a performance-based
+However, the researchers found that by offering a performance-based
 bonus, which paid if workers completed the task quickly and correctly,
@@
 $\mathrm{design}_1$ or $\mathrm{design}_2$ with equal probability.
-If the worker gives the response $x$, the opitimal classifier must guess
+If the worker gives the response $x$, the optimal classifier must guess
 that the worker was shown the design most likely to elicit $x$.
@@
 demonstrating that intertask effects do exist.  However, we did not find 
-significant effects due to framing ($p=0.29$) 
-(Figure~\ref{fig:theta}A).
+significant effects due to framing ($p=0.29$).
 
@@
 To address this concern, we randomly split responses to given treatment
-into two sets, and tested for hetererogeneity between the sets.
+into two sets, and tested for heterogeneity between the sets.
 In all cases, we failed to find heterogeneity \textit{within} a given 
@@
 If so, then as the next question, we may ask how intertask effects evolve
-as the worker performs tasks.  Presumbaly, intertask effects wear off at 
+as the worker performs tasks.  Presumably, intertask effects wear off at 
 some point, but is it after one task, two, or more?
@@
 In setting up Experiment 2, we also wish to increase the strength of 
-framing.  While finding that intertask effects were stronger than framing 
-was surprising and remarkable, perhaps the most meaningful comparison
-would be one which shows just how extreme framing treatments need to be 
-to produce effects on par with intertask effects.  
+framing.  While it was remarkable that intertask effects were stronger 
+than the framing effects elicited in the first experiment, perhaps the 
+most meaningful comparison is one which shows just how extreme framing 
+treatments need to be to produce effects on par with intertask effects.  
 One factor that may have weakened the effects of framing in Experiment 1 
@@
 tasks. They were included to ensure that workers had always completed the
-same number of tasks before begining the test tasks.  However, their 
+same number of tasks before beginning the test tasks.  However, their 
 inclusion gives time for differential framing effects to 
@@
 Keeping a food treatment enabled us to perform deeper lexical analysis of 
-both experiments (discussed in the results for Experiment 2).  
+both experiments (to be discussed in the results for Experiment 2).  
 The experiment was again performed using a single HIT on MTurk, 
@@
 test task position (relative to initial tasks) from test task content,
-and thereby see how intertask effects vary as a function of position.
+and thereby see how intertask effects vary as a function of position in
+the task sequence.
 
@@
 immediately after framing.  This meant that workers would not have 
-performed any tasks by the time they begin the test tasks.  While that will
+performed any tasks by the time they began the test tasks.  While that will
 hold constant for both framing treatments, and thus not produce a 
@@
 As in the previous experiment, intertask effects led to significant 
-changes in the words workers used to labele images in the intertask 
+changes in the words workers used to label images in the intertask 
 sub-experiment ($p<0.001$).  Based on
@@
 	\centering
-	\includegraphics[scale=0.87]{figs/specificity.pdf}
+	\includegraphics[scale=1.05]{figs/specificity.pdf}
 	\caption{
@@
 rules out a seemingly-simple idea that workers emphasize
-content seen in earlier tasks.  Seeing given content does significantly 
-influence workers' propensity to refer to it in subsequent tasks, but it 
+content seen in earlier tasks.  Seeing given content significantly 
+influences workers' propensity to refer to it in subsequent tasks, but it 
 does not necessarily \textit{increase} it.
@@
 (as much as 20\% more) (Figure~\ref{fig:specificity}B).  
-This is particularly noteworthy for Experiment 1, because there,
+This is particularly noteworthy for the intertask sub-experiment in 
+Experiment 1, because there,
 workers from the food treatment made fewer total references to food.  
@@
 The relative specificity lies within $[-1,1]$; 
-we report it as a percentage.
+we report it as a signed percentage.
 In computing this quantity between two treatments, we first computed the 
@@
 
-In all sub-experiments except for Experiment 1 framing sub-experiment, 
-workers from the food treatment used significantly more specialized words, 
+In all sub-experiments,
+workers from the food treatment used more specialized words, 
 in reference to food 
 (about 15\% more; $p < 0.05$) (Figure~\ref{fig:specificity}C).
+Except in the case of the framing treatment of Experiment 1, these 
+between-treatment differences in word specialization were significant 
+($p<0.05$).
+
 It is interesting that such substantial increases in both the lexical 
@@
 (Table~\ref{table:top-words}).  
-The word ``food'', which is the most generic possible food-related word, was 
-always \textit{suppressed} among food-primed workers.  In fact, 
+The word ``food'', which is the most generic possible food-related word, 
+was always \textit{suppressed} among food-exposed workers, along with other
+very generic food references being suppressed too, such as ``meal'' and 
+``dinner''.  In fact, 
 for all experiments, ``food'' was the \textit{most suppressed} word.
+Meanwhile, the most activated food-related words, among food-exposed 
+workers, tended to refer to specific foods, 
+like ``apple'', ``cheese'', and ``bread''.
 
@@
 A worker may be more likely to enter those words which enter her mind 
-first, so priming could lead to certain words being prefered.  
+first, so priming could lead to certain words being preferred.  
 As the worker
@@
 
-However, as we aluded to above, there appears to be countervailing factors:
-while richness and specialization always increased (or were not 
-significantly changed), the total number of references to content in 
-prior tasks was observed to significantly increase in most cases, but
-it significantly decreased in one.  Here we suspect 
-\textit{negative} priming to be at play.
+However, as we alluded to above, there appears to be countervailing 
+factors:
+while richness and specialization of food-related words always increased 
+(or were not significantly changed) among workers exposed to food in 
+initial tasks, the total number of references to food significantly 
+\textit{decreased} in one case.  
+Here we suspect \textit{negative} priming to be at play.
 Negative priming occurs when, after exposure to a stimulus 
@@
 inhibited \cite{mayr2007negative}.  In the case of our image labeling 
-tasks, repeated exposure to images depicting food may cause the worker to 
-stop regarding the basic presence of food as salient, and direct their 
+tasks, repeated exposure to images depicting food might cause the worker to
+stop regarding the basic presence of food as salient, and to direct her 
 attention instead to the features that are specific to the food in a given 
-image.  This could lead the worker to suppress very generic references to 
-food (as we observed for the words ``food'', ``meal'', ``dinner'', see 
-Table~\ref{table:top-words}).  This could hold even when, due to positive
-priming, more specialized food-related words are activated.
-The balance of these factors would determine whether the worker makes 
-more references to food overall.  This would explain the paradoxical
-changes in number of references to food, along with the observed 
-changes to the richness and specificity of workers' food-related 
-vocabulary.
+image.  This would explain the suppression very generic references to 
+food observed in Table~\ref{table:top-words}.  
+The balance between the inhibition of generic food-related words, with 
+activation of specific ones could lead to more or less food references
+overall, so this dual priming mechanism is consistent with our 
+observations.  Direct experimentation would be needed to determine whether
+priming mechanisms, positive or negative, are in able to explain intertask
+effects.
 
@@
 
-Intertask effects are a new basic discovery
-in the quest to design reliable and reproducible tasks for human 
-computation.
+Intertask effects are a new basic discovery in the quest to design 
+reliable and reproducible tasks for human computation.
 We anticipate future work will yield techniques to control intertask 

### 2016-01-08 docs/publications/2015.12_CHI/man.tex
camera ready for chi

@@
 %% EXAMPLE BEGIN -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)
-% \toappear{Permission to make digital or hard copies of all or part of this work for personal or classroom use is      granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page.
+\toappear{Permission to make digital or hard copies of all or part of this work for personal or classroom use is      granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page.
 Copyrights for components of this work owned by others than ACM must be honored.
@@
 \\
-% {\emph{CHI'14}}, April 26--May 1, 2014, Toronto, Canada. \\
-% Copyright \copyright~2014 ACM ISBN/14/04...\$15.00. \\
-% DOI string from ACM form confirmation}
+{\emph{CHI'16}}, May 07--12, 2016, San Jose, CA, USA. \\
+Copyright is held by the owner/author(s). Publication rights licensed to ACM. \\
+ACM 978-1-4503-3362-7/16/05 \$15.00  \\
+DOI http://dx.doi.org/10.1145/2858036.2858490
+}
+%Copyright \copyright~2014 ACM ISBN/14/04...\$15.00. \\
+%http://dx.doi.org/10.1145/2858036.2858490}
 %% EXAMPLE END -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)
@@
 \usepackage{todonotes}
+\usepackage{paralist}
 
@@
 
+%\CopyrightYear{2016}
+%\setcopyright{acmlicensed}
+%\conferenceinfo{CHI'16,}{May 07 - 12, 2016, San Jose, CA, USA}
+%\isbn{978-1-4503-3362-7/16/05}\acmPrice{\$15.00}
+%\doi{http://dx.doi.org/10.1145/2858036.2858490}
+
 \title{How One Microtask Affects Another}
 
-\numberofauthors{1}
+\numberofauthors{2}
 \author{%
   \alignauthor{
-	Authors\\
-    \affaddr{Affiliations}\\
-    \affaddr{Addresses 	}\\
-	\email{email@domain.com}
+	Edward Newell\\
+    \affaddr{School of Computer Science}\\
+    \affaddr{McGill University}\\
+	\email{\texttt{edward.newell@mail.mcgill.ca}}
   }\\
-  %\alignauthor{
-  %  Author 2 \\
-  %  \affaddr{Affiliation 1}\\
-  %  \affaddr{Montreal, Qu\'ebec,
-  %    Canada
-  %  }\\
-  %  \email{derek.ruths@mcgill.ca}
-  %}\\
+  \alignauthor{
+    Derek Ruths\\
+    \affaddr{School of Computer Science}\\
+	\affaddr{McGill University}\\
+	\email{\texttt{derek.ruths@mcgill.ca}}
+  }\\
 }
@@
 
-Psychological experiments show that the exposure to stimuli immediately 
-before performing a task influences performance, an effect known as 
-\textit{priming} \cite{BJOP1796}.
-The effect of priming appears to be stronger when the modality of the
-prime is the same as the task.
-Thus, for the typical microtask worker, who does many similar tasks in
-quick succession, there is a potential for earlier tasks to influence
-later ones, via priming or other mechanisms.
-
-We seek to determine if any such effects in fact occur and if so, 
-to measure and characterize them.
-Certain tasks admit a well-defined notion of ``correct'' and 
-``incorrect'' responses.  But many tasks involving qualitative judgment
-do not.  So, rather than simply characterizing effects on accuracy, we seek
-to provide a generalized measure of the extent to which prior tasks
-can alter the distribution of responses to later tasks.  
-Measuring the \textit{extent} of the shift in a distribution of responses 
-is substantially harder than simply determining \textit{whether} an effect 
-has occurred.  Our first contribution is a statistically grounded method 
-for doing so.
-
-To investigate the phenomenon in a
-highly generalizable setting, we sought a task that would involve 
-qualitative judgment and enable relatively unconstrained responses. 
-We also sought a task that would be a typical exemplar of the kinds of
-tasks actually seen on microtask platforms (see 
-Table~\ref{table:task_composition} for examples).  For this purpose, we 
-adopted
-image-labeling as a canonical microtask, a task in which workers provide 
-descriptive labels to images using free-text inputs.  Image labeling is
-a qualitative task without clearly ``correct'' or ``incorrect'' responses,
-and is among the most common kinds of tasks on MTurk 
-(see Table \ref{table:task_composition}).
-If effects from earlier tasks arise in our setup, similar effects could be 
-expected in 
-a large number of microtasks and crowdsourced workflows where workers are 
-called upon to provide qualitative judgment.
-
-In our experiments, workers label a series of images, one at a time.
-Depending on the treatment to which a worker is assigned, we vary the
-images in the first five tasks, while keeping those in the last five tasks 
-the same.  For example, in one experiment, the first five images shown to
-one group of workers contain food, while those shown to the other 
-contain (non-food) objects.  The last five images for both
-groups contain both food and objects.
-
-Our results show that a worker's responses are strongly influenced by 
-the content of tasks performed beforehand, leading to as much as 50\%
-total variational distance (see Figure~\ref{fig:l1_example} for 
-illustrative definition of total variational distance).  
-Using the WordNet 
-knowledge base, we analyze worker's word choices to characterize 
-the nature of these effects in detail.  We find that, when workers 
-label a series of images that are more similar, their responses become 
-more specialized and more diverse.  
-Prior tasks can shift the topical focus of 
-worker's labels, inducing them to focus on different aspects of the images.
-
-As a point of comparison, we also conduct framing experiments, 
-in which we alter the framing of microtask assignments, in terms of the 
-stated purpose of the task, or by naming the funder.
-Remarkably, the effects of prior microtasks,
-which are virtually ubiquitous, are on par with, or stronger than, 
-the effects of overtly framing an assignment.
-
 \begin{table}
@@
 
+Psychological experiments show that the exposure to stimuli immediately 
+before performing a task influences performance, an effect known as 
+\textit{priming} 
+\cite{Ghuman17062008,BJOP1826,beller1971priming,BJOP1796}.
+The effect of priming appears to be stronger when the modality of the
+prime is the same as the task \cite{BJOP1796}.
+Thus, for the typical microtask worker, who does many similar tasks in
+quick succession, there is a potential for earlier tasks to influence
+later ones, via priming or other mechanisms.
+
+We seek to determine if any such effects in fact occur and if so, 
+to measure and characterize them.
+Certain tasks admit a well-defined notion of ``correct'' and 
+``incorrect'' responses.  But many tasks involving qualitative judgment
+do not.  So, rather than simply characterizing effects on accuracy, we seek
+to provide a generalized measure of the extent to which prior tasks
+can alter the distribution of responses to later tasks.  
+Measuring the \textit{extent} of the shift in a distribution of responses 
+is substantially harder than simply determining \textit{whether} an effect 
+has occurred.  Our first contribution is a statistically grounded method 
+for doing so.
+
+To investigate the phenomenon in a
+highly generalizable setting, we sought a task that would involve 
+qualitative judgment and enable relatively unconstrained responses. 
+We also sought a task that would be a typical exemplar of the kinds of
+tasks actually seen on microtask platforms (see 
+Table~\ref{table:task_composition} for examples).  For this purpose, we 
+adopted
+image-labeling as a canonical microtask, a task in which workers provide 
+descriptive labels to images using free-text inputs.  Image labeling is
+a qualitative task without clearly ``correct'' or ``incorrect'' responses,
+and is among the most common kinds of tasks on MTurk 
+(see Table \ref{table:task_composition}).
+If effects from earlier tasks arise in our setup, similar effects could be 
+expected in 
+a large number of microtasks and crowdsourced workflows where workers are 
+called upon to provide qualitative judgment.
+
+In our experiments, workers label a series of images, one at a time.
+Depending on the treatment to which a worker is assigned, we vary the
+images in the first five tasks, while keeping those in the last five tasks 
+the same.  For example, in one experiment, the first five images shown to
+one group of workers contain food, while those shown to the other 
+contain (non-food) objects.  The last five images for both
+groups contain both food and objects.
+
+Our results show that a worker's responses are strongly influenced by 
+the content of tasks performed beforehand, leading to as much as 50\%
+total variational distance (see Figure~\ref{fig:l1_example} for 
+illustrative definition of total variational distance).  
+Using the WordNet 
+knowledge base, we analyze worker's word choices to characterize 
+the nature of these effects in detail.  We find that, when workers 
+label a series of images that are more similar, their responses become 
+more specialized and more diverse.  
+Prior tasks can shift the topical focus of 
+worker's labels, inducing them to focus on different aspects of the images.
+
+As a point of comparison, we also conduct framing experiments, 
+in which we alter the framing of microtask assignments, in terms of the 
+stated purpose of the task, or by naming the funder.
+Remarkably, the effects of prior microtasks,
+which are virtually ubiquitous, are on par with, or stronger than, 
+the effects of overtly framing an assignment.
+
 We call the effects that earlier tasks exert on later ones 
@@
 As our main contributions, we
-\begin{itemize}[noitemsep,nolistsep]
+\begin{compactitem}%[noitemsep,nolistsep]
   \item{
@@
   }
-\end{itemize}
+\end{compactitem}
 
@@
 %(and most crowdsourced work), earlier tasks may act as primes to later 
-%ones, and thereby introduce singificant amounts of bias.
+%ones, and thereby introduce significant amounts of bias.
 
@@
 \begin{align}
-	\theta = \frac{1}{2}\sum_{x \in X} \left| p(x) - q(x) \right|,
+  \theta = \frac{1}{2}\sum_{x \in \mathcal{X}} \left| p(x) - q(x) \right|,
 	\label{eq:theta}
@@
   \mathrm{Pr}\{\mathrm{correct}|x\} = \frac{1}{2} 
-	+ \frac{|p_0(x) - p_1(x)|}{2(p_0(x) + p_1(x))}
+	+ \frac{|p_1(x) - p_2(x)|}{2(p_1(x) + p_2(x))}
 \end{align}
@@
 	\left(
-	\frac{1}{2} + \frac{|p_0(x) - p_1(x)|}{2(p_0(x) + p_1(x))}
+	\frac{1}{2} + \frac{|p_1(x) - p_2(x)|}{2(p_1(x) + p_2(x))}
   \right) \left( 
-	\frac{p_0(x) + p_1(x)}{2} 
+	\frac{p_1(x) + p_2(x)}{2} 
   \right) \\
@@
 could only participate once in a given experiment, and could only 
-participate in one of the experiments we present here.
+participate in one of the experiments we present here.  Workers were 
+required to have had 90\% of their previously submitted work on Mturk 
+accepted by other requesters to participate.  No other screening 
+was applied to workers.
 
@@
 we call ``food'' and ``culture'', and workers were also randomly 
-assigned to a treatment.  In both treatments of both sub-experiments,
+assigned to a treatment, resulting in 119 workers per treatment.  
+In both treatments of both sub-experiments,
 workers were asked to perform ten image-labeling tasks, each of which 
 required the worker to assign five descriptive labels to an image.  
+Labels had to contain at least two letters to be accepted. 
+Workers were paid USD\$0.45 for their work.
 In all cases, the last five tasks were identical among all treatments 
@@
 invite the worker to focus on different aspects of the image content.  
-As already mentioned, the test tasks consisted of images depicting meals 
-of diverse ethnic origin.
+Initial tasks were still included to ensure that learning or fatigue 
+effects were equalized between the sub-experiments.  
+For the initial tasks, we used the same images as had been shown to the 
+food treatment of the intertask sub-experiment.  
+If intertask effects exist, any choice of images for the initial tasks 
+will have an effect.  This choice makes the food treatments of both 
+sub-experiments very similar, so that the culture treatments of both 
+sub-experiments can be viewed as perturbations from a similar baseline.  
+The test tasks were the same as for the intertask sub-experiment.
+
+Manual inspection showed that the vast majority of labels were of 
+high-quality.  Less than 1\% of submissions were problematic, having
+redundant labels or entries that were not English words.
+We chose to include all submissions for analysis in the experiments
+presented here.
 
@@
 
+\pagebreak
 \paragraph{Strength of intertask and framing effects.}
@@
 on one another than in a coherent passage of text.  We repeated our
-analysis using a support vector machine and found very similar results.
+analysis using support vector machines and found very similar results.
 
@@
 
-\pagebreak
 \section{Experiment 2}
@@
 Workers were randomly assigned to a sub-experiment and treatment upon
-starting the HIT.
+starting the HIT, resulting in 119 workers per treatment.
 
@@
 	\centering
-	\includegraphics[scale=1.05]{figs/specificity.pdf}
+	\includegraphics[scale=0.97]{figs/specificity.pdf}
 	\caption{
 		Workers exposed to food (either in framing or initial tasks)
-		show a different tendency to focus on food when labeling
-		test tasks, and their vocabulary in reference to food is affected.
+		showed a different tendency to focus on food when labeling
+		test tasks, and their vocabulary in reference to food was affected.
 		In all three plots, positive values indicate a larger quantity for 
 		workers from the food treatment.
-		(\textbf{A}) Exposing workers to food does not necessarily increase
-		the fraction of food references they provide during test tasks.
+		(\textbf{A}) Exposing workers to food significantly changed the 
+		fraction of food references they provide, but did not necessarily 
+		\textit{increase} it.
 		(\textbf{B}) The number of unique food-related
@@
 
-The above observations regarding lexical richness, suggest that initial 
+The above observations regarding lexical richness suggest that initial 
 tasks might influence workers to use more \textit{refined} or 
@@
 attention instead to the features that are specific to the food in a given 
-image.  This would explain the suppression very generic references to 
+image.  This would explain the suppression of very generic references to 
 food observed in Table~\ref{table:top-words}.  
-The balance between the inhibition of generic food-related words, with 
-activation of specific ones could lead to more or less food references
+The balance between the inhibition of generic food-related words, and the 
+activation of specialized ones, could lead to more or less food references
 overall, so this dual priming mechanism is consistent with our 
-observations.  Direct experimentation would be needed to determine whether
-priming mechanisms, positive or negative, are in able to explain intertask
+observations.  Direct experimentation is needed to determine whether
+priming mechanisms, positive or negative, can explain intertask
 effects.
@@
 have such strong effects on later ones.
-But our findings show this is an important design consideration that 
+But our findings show this is an important design factor that 
 should be considered by anyone using microtask platforms.
@@
 introduces a significant amount of noise due to intertask effects:
-Even chains of two or three similar tasks, which will not be reliably 
+even chains of two or three similar tasks, which will not be reliably 
 eliminated in random permutations, could lead to the levels of influence 
@@
 But perhaps more importantly, our findings show that intertask effects 
-might be leveraged achieve greater quality and reproducibility in 
+might be leveraged obtain greater quality and reproducibility in 
 crowdsourcing.
-A consistent goal in human computation is the achievement of expert-level
+A consistent goal in human computation is the elicitation of expert-level
 judgments from non-expert workers \cite{kittur2011crowdforge}.  
